### 2009-11-10 ltx/BrainIDE.tex
initial commit

%% bare_jrnl.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

\documentclass[journal]{IEEEtran}

\usepackage{graphicx}
\usepackage{color}                    % For creating coloured text and background
\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

% can use linebreaks \\ within to get better formatting as desired
\title{Estimation of Spatiotemporal Integro-Difference Equations for Dynamical Neural Field Models}

\author{Dean~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Michael~Dewar,~\IEEEmembership{Member,~IEEE,}
        Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
        and Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
        and~other~Bosses/Supervisors,~\IEEEmembership{Member,~IEEE.}% <-this % stops a space% <-this % stops a space

\thanks{D. Freestone is with the Department
of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
Vic, 3010 Australia {\tt\small dfreestone@bionicear.org}.}% <-this % stops a space
\thanks{P. Aram is with Sheffield...}
\thanks{M. Dewar is with Edinburgh...}
\thanks{K. Scerri is with Malta...}
\thanks{V. Kadirkamanathan is with Sheffield...}

\thanks{Manuscript received Month Day, Year; revised Month Day, Year.}}

% The paper headers
\markboth{Journal of \"{U}ber C\~{o}\~{o}l Engineering,~Vol.~1, No.~1, Christmas~2009}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}

\maketitle

\begin{abstract}
Will save this for last.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Integro-Difference Equation (IDE), Neural Field Model, Cortical Connectivity.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

\IEEEPARstart{T}{he} human brain is arguably the world's most complex system. Approximately 100 billion neurons and 60 trillion synapses operate in concert to process information, resulting in the cognition that determines our behavior. The brain's efficiency, robustness, and adaptability are unparalleled by any man-made device and, despite decades of concerted research, our understanding of its complex dynamics remains modest. This has led researchers to study different scales of dynamics: starting from individual proteins, synapses, and neurons; moving through to neuronal networks and ensembles of neuronal networks. Whilst our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.  Understanding the brain at this level is extremely important since this is the level where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.

To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at this meso/macroscopic scale. Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews). These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies (ref, Parkinsons Scitzo) that would be impossible to gain from experimental data . Unfortunately, to date the use of these models in the clinic has very limited, since these models are very general and pathologies almost always have unique underlying patient specific causes. Data from EEG and functional magnetic resonance imaging (fMRI) offers the patient specific link to macro-scale cortical dynamics, making these tools readily applicable to the clinic. However the underlying system properties, or system states, are hidden from EEG and fMRI data, making predictions of the underlying physiology inherently difficult.

For models to be clinically viable they must be patient specific. A possible approach to achieve this would be to use a general neural field model, like the \textcolor[rgb]{1.00,0.00,0.00}{Wilson Cohen Jansen and Ritt model ref}, and fit it to a patients EEG data. Fitting the general neural field models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature. This is most likely due to the large parameter set that most models use in order to be physiologically plausible. To our knowledge, the first (and only) published research that attempts parameter estimation with a neural field model used an unscented Kalman filter to track parameters of the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.  This work marks the first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable. Generating patient specific models allows that application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.  Currently available epileptic seizure prediction and control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".  That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neurodynamics and information about their particular pathologies. Given access to an accurate model, the application of control theory in these circumstances would allow for robust therapeutic stimulations.
The work from Schiff and Sauer~\cite{schiff2008kalman} successfully demonstrated  estimation of two parameters from the WC equations, whilst the other parameters were fixed. This motivates the question, what parameters are the most important? How patient specific do the assumed parameters have to be for the model to be useful? In this paper we address both of these questions and provide a theoretical platform to perform patient specific grey-box modeling of the human neocortex.

\section{The Importance of Cortical Structure}

The neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials. Each neural population represents a functional cortical processing unit referred to as a column. The columnar organization of the cortex is not discrete, but is continuous, where pyramidal cells are members of many columns. In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range corticocortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}. Locally, each column is thought to have symmetric short range local excitation, with surround inhibition~\cite{Braitenberg1998}. For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes column to a particular receptive visual field~\cite{Sullivan2006}.
Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}. This implies that if we could estimate the connectivity structure for individuals we may be able to model patient specific dynamics.

Estimating function cortical connectivity via EEG measures is currently a highly active area of research. There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks. Most works are based on auto-regressive (AR) modeling of the times series. Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients. This approach has yielded interesting results but is limited in the sense that structure is not estimated hence this work cannot be related to the theoretical bifurcation analysis and the underlying system structure. (Granger causality, DTF, partial coherence)
An alternative approach to estimating the connectivity structure between brain regions is dynamic causal modeling (DCM). The DCM approach essentially studies the causality of information transform between pre-determined brain regions. DCM asks what connectivity structure between brain regions best explains a data set. The approach has generated several publications (ref) and generated evidence in understanding specific hierarchical networks of neural information processing.
Changes in connectivity would reflect learning.
Longrange connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
In this work we aim to estimate local intracortical connectivity. This is most invariant.
\section{Neural Field Model}

The Wilson-Cowan model has shown to be descriptive of a range of neurodynamics of the cortex. The model is capable of generating patterns of activity such as Turing patterns, spirals, .... The general form of the model is described here.
The post-synaptic potentials generated at a neuronal population $s$ by action potentials arriving from all other connected populations at position $r$ can be described by
\begin{equation}\label{Eq1}
v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {r,t'} \right)dt'}.
\end{equation}
The post-synaptic response kernel $h(t)$ is described by
\begin{equation}\label{Eq2}
h(t) = \left\{ {\begin{array}{*{20}{c}}
   {\exp ( - {t \mathord{\left/
 {\vphantom {t \tau }} \right.
 \kern-\nulldelimiterspace} \tau })} & {t \ge 0}  \\
   0 & {t < 0}  \\
\end{array}} \right.,
\end{equation}
where $\tau$ is the synaptic time constant and typically has values from 10-20~ms (\textcolor[rgb]{1.00,0.00,0.00}{refs}). The synaptic response kernel can be more elaborate, using a rise and fall time constant, however this simple form serves our purposes. Equation~\ref{Eq1} relates average firing rate of a presynaptic neural population to the mean membrane potential of the post-synaptic neurons. The mean firing rate, $J$, is convolved with the response kernel to give membrane potential since the firing rate is assumed to follow a (homogeneous?) Poisson process. Nonlocal interactions between cortical populations are described by	
\begin{equation}\label{Eq3}
J\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right)
\end{equation}
where $\bar t = t - \frac{{\left| {s - r} \right|}}{d}$, $P$ is a mean pulse rate of population at $y$, $W$ is the connectivity kernel, $E$ is an external input, $\Omega$ is the spatial domain and $d$ is the propagation velocity from $r$ to $s$.

The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the sigmoid function
\begin{equation}\label{Eq4}
P\left( {v\left( {r,\bar t} \right)} \right) = {R_0}{\left( {1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - v\left( {r,\bar t} \right)} \right)} \right)} \right)^{ - 1}}.
\end{equation}
Even though $v_0$ is a constant, we show express it as a field allowing for inhomogenaities and for clarity in constructing the state-space representation in the next section. The parameters in equation~\ref{Eq4} are... $v_0$ is typically 6~mV, $R_0$ is 5~$s^{-1}$ and $\beta$ is 0.56~mV$^{-1}$ (from Wendling and David papers). By combining equations~\ref{Eq1} and \ref{Eq3} we get the spatiotemporal model
\begin{equation}\label{Eq5}
v\left( {s,t} \right) = \int\limits_{ - \infty }^t {\int\limits_\Omega  {h\left( {t - t'} \right)W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dy} dt'}  + E\left( {s,t} \right).
\end{equation}
To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
\begin{equation}\label{Eq6}
Lh\left( t \right) = \delta \left( t \right),
\end{equation}
where $L$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
\begin{equation}\label{Eq7}
L\left( {\frac{\partial }{{dt}}} \right)v\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right),
\end{equation}
where $L$ is a polynomial of order $n$ with constant coefficients. This provides an $n^{th}$ order model. Most studies considering this model use first or second order time derivatives. We shall use the first order model giving
\begin{equation}\label{Eq8}
\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{{v\left( {s,t} \right)}}{\tau } = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
\end{equation}
The neural field model can be represented as a discrete-time stochastic IDE by
\begin{equation}\label{Eq9}
{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {{v_{\bar t}}\left( r \right)} \right)dr}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right),
\end{equation}
where $\epsilon(t)$ is the discrete time stochastic input. The IDE representation of equation~\ref{Eq9} is discrete in time and continuous in space. The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.

\subsection{Assumptions and Simplifications}
We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population. In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity. Standing, but not traveling waves? This is a common assumption when dealing with models in this form. We will also assume the velocity of the action potentials is infinite. This is also a common assumption that is made in the neural field modeling community. Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics (Coombes paper, and Atay paper). The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences. Therefore, the model simply has to be 'good enough' for this purpose. Starting with this simplified version of the general model is a logical choice. The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, and not on their spatial location. Again, this is a common assumption in this field.  This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible. The IDE estimation is derived for a general heterogeneous structure, however for clarity of results we shall only present the heterogeneous case. With these assumptions we have the model in the form
\begin{equation}\label{Eq10}
{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {\left| {s - r} \right|} \right)P\left( {{v_t}\left( r \right)} \right)dy}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right).
\end{equation}
In addition to the assumptions above we shall linearize the model by approximating the sigmoid function $P$ as a piece-wise linear function, $P_{L}$, where
\begin{equation}\label{Eq11}
\begin{array}{*{20}{c}}
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = 0,} \hfill & {f\left( {{v_t}\left( r \right)} \right) \le 0} \hfill  \\
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = f\left( {{v_t}\left( r \right)} \right),} \hfill & {0 < f\left( {{v_t}\left( r \right)} \right) < {R_0}} \hfill  \\
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = {R_0},} \hfill & {f\left( {{v_t}\left( r \right)} \right) \ge {R_0}} \hfill  \\
\end{array}
\end{equation}
and
\begin{equation}\label{Eq12}
f\left( {{v_t}\left( r \right)} \right) = \frac{{{R_0}}}{2}\left( {1 + \frac{\beta }{2}\left( {{v_t}\left( r \right) - {v_0}\left( r \right)} \right)} \right).
\end{equation}
For the derivation of the state-space model we shall assume that the model is operating in the active dynamic region, since this is the most interesting case, and the other cases correspond to the neural populations either being saturated (at $R_0$) or being silent. We shall show be stability analysis that the model will not saturate for the given parameters and nor will it be silent since it is continuously driven by noise. Substituting equation~\ref{Eq11} into equation~\ref{Eq10} and expanding we get
\begin{align}\label{Eq13}
 {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
  + \frac{{{R_0}}}{2}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber
\end{align}
where ${\bar v_0}\left( r \right) = 1 - \frac{\beta }{2}{v_0}\left( r \right)$.

\section{State-Space Neural Field Model}
In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations. The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data. To simplify the notation in the derivation we will let the external input $\epsilon(t)=0$. Also, we shall define
\begin{equation}\label{Eq14}
W\left( {s,r} \right) = {\theta ^T}\psi \left( {s,r} \right)
\end{equation}
and
\begin{equation}\label{Eq15}
{v_t}\left( s \right) = \phi {\left( s \right)^T}{x_t},
\end{equation}
where $\Theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\Theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$. The voltage field at $t$ is comprised of a scaled version (by the state $x_t$) of the basis functions $\phi(s)$.
 The spatial kernel $W$ and the field $v$ are decomposed using the same basis functions, and we will define them as being complete and orthogonal. Also, we shall define
\begin{equation}\label{Eq16}
\Phi \left( s \right) = \int_\Omega  {\psi \left( {s,r} \right)\phi {{\left( r \right)}^T}dr}
\end{equation}
and
\begin{equation}\label{Eq17}
\Gamma \left( s \right) = \int_\Omega  {\psi \left( {s,r} \right){{\bar v}_0}\left( r \right)dr}.
\end{equation}
By substituting equations~\ref{Eq14} and \ref{Eq15} into equation~\ref{Eq13} we get
\begin{align}\label{Eq18}
 {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}{\theta ^T}\int_\Omega  {\psi \left( {s,r} \right){{\bar v}_0}\left( r \right)dr} \nonumber \\
  + \frac{{{R_0}}}{2}\beta {\theta ^T}\int_\Omega  {\psi \left( {s,r} \right)\phi {{\left( r \right)}^T}dr} {x_t} \\
  - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t} \nonumber
\end{align}
and substituting in equations~\ref{Eq16} and \ref{Eq17} into equation~\ref{Eq18} we get
\begin{equation}\label{Eq19}
{v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}{\theta ^T}\Gamma \left( s \right) + \frac{{{R_0}}}{2}\beta {\theta ^T}\Phi \left( s \right){x_t} - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t}.
\end{equation}
By substituting the field for the basis functions weighted by the state vector we get
\begin{equation}\label{Eq20}
\phi {\left( s \right)^T}{x_{t + 1}} = \frac{{{R_0}}}{2}{\theta ^T}\Gamma \left( s \right) + \frac{{{R_0}}}{2}\beta {\theta ^T}\Phi \left( s \right){x_t} - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t}.
\end{equation}
Multiplying both sides by $\phi(s)$ and integrating over $s$ we get
\begin{align}\label{21}
 \int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds{x_{t + 1}}}  = \frac{{{R_0}}}{2}\int_\Omega  {\phi \left( s \right){\theta ^T}\Gamma \left( s \right)ds}  \nonumber \\
  + \frac{{{R_0}}}{2}\beta \int_\Omega  {\phi \left( s \right){\theta ^T}\Phi \left( s \right)ds} {x_t} \\
  - \frac{1}{\tau }\int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds} {x_t}. \nonumber
\end{align}
Now we define
\begin{equation}\label{22}
\Psi  = \int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds}
\end{equation}
and
\begin{equation}\label{23}
\Upsilon  = \int_\Omega  {\phi \left( s \right){\theta ^T}\Phi \left( s \right)ds}
\end{equation}
and
\begin{equation}\label{24}
\Pi  = \int_\Omega  {\phi \left( s \right){\theta ^T}\Gamma \left( s \right)ds},
\end{equation}
where $\Psi$ is a square positive definite matrix. Substituting equations~\ref{22}, ~\ref{23} and \ref{24} into equation~\ref{21} we get
\begin{equation}\label{25}
\Psi {x_{t + 1}} = \frac{{{R_0}}}{2}\Pi  + \frac{{{R_0}}}{2}\beta \Upsilon {x_t} - \frac{1}{\tau }\Psi {x_t}.
\end{equation}
Since $\Psi$ is a square positive definite matrix we can invert it to isolate $x_t$ yielding
\begin{equation}\label{26}
{x_{t + 1}} = \frac{{{R_0}}}{2}{\Psi _x}^{ - 1}\Pi  + \left( {\frac{{{R_0}}}{2}\beta {\Psi _x}^{ - 1}\Upsilon  - \frac{1}{\tau }{\bf{I}}} \right){x_t},
\end{equation}
where \textbf{I} is the identity matrix. The model can now be written in the canonical state-space form
\begin{equation}\label{27}
\begin{array}{c}
 {x_{t + 1}} = A{x_t} + Bu \\
 {v_t}\left( s \right) = C{x_t}, \\
 \end{array}
\end{equation}
where 
\begin{equation}\label{28}
\begin{array}{l}
 A = \frac{{{R_0}}}{4}\beta {\Psi _x}^{ - 1}\Upsilon  - \frac{1}{\tau }{\bf{I}} \\
 B = \frac{{{R_0}}}{2}{\Psi _x}^{ - 1}\Pi  \\
 C = {\phi ^T}\left( s \right) \\
 u = 1. \\
 \end{array}
\end{equation}
Next we shall demonstrate the stability of the model and in the following section the estimator for the state vector and connectivity structure is derived.

\section{Stability Analysis}
Using the analytically calculated basis functions. Need to show that the linearized model will not blow up.

\section{Estimation of the IDE Neural Field Model}
Based on the other papers.

\section{Comparison of Estimated and True Connectivity}
Try and estimate the linear and nonlinear model based on the linear estimator. Might work ok?

\subsection{Linear Model}

\subsection{Nonlinear Model}

\section{Discussion}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.
%
% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Conclusion}
The conclusion goes here.

\appendices
\section{}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

% use section* for acknowledgement
\section*{Acknowledgment}
The authors would like to thank...

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% references section

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,BrainIDE}

% biography section
%
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Dean Freestone}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}{Parham Aram}
Biography text here.
\end{IEEEbiography}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiography}{Michael Dewar}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Kenneth Scerri}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Visakan Kadirkamanathani}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Other Bosses}
Biography text here.
\end{IEEEbiography}

% that's all folks
\end{document}

### 2009-11-11 ltx/BrainIDE.tex
Added references about neural models in intro of tex file andded refs to bib file

@@
 Whilst our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
-Understanding the brain at this level is extremely important since this is the level where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 
-To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at this meso/macroscopic scale.
+To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at the meso/macroscopic scale.
 Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies (ref, Parkinsons Scitzo) that would be impossible to gain from experimental data .
-Unfortunately, to date the use of these models in the clinic has very limited, since these models are very general and pathologies almost always have unique underlying patient specific causes.
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} that would be impossible to gain from experimental data alone.
+Unfortunately, to date the use of these models in the clinic has very limited, since the neural field model are constructed for a general brain and pathologies almost always have unique underlying patient specific causes.
 Data from EEG and functional magnetic resonance imaging (fMRI) offers the patient specific link to macro-scale cortical dynamics, making these tools readily applicable to the clinic.
@@
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to use a general neural field model, like the \textcolor[rgb]{1.00,0.00,0.00}{Wilson Cohen Jansen and Ritt model ref}, and fit it to a patients EEG data.
+A possible approach to achieve this would be to use a general neural field model, like the Wilson and Cohen~\cite{Wilson1973} or Jansen and Ritt model~\cite{Jansen1995}, and fit it to a patients EEG data.
 Fitting the general neural field models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
@@
 Locally, each column is thought to have symmetric short range local excitation, with surround inhibition~\cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes column to a particular receptive visual field~\cite{Sullivan2006}.
+For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes column to a particular receptive visual field~\cite{Sullivan2006}.
 Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
@@
 Most works are based on auto-regressive (AR) modeling of the times series.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients.
-This approach has yielded interesting results but is limited in the sense that structure is not estimated hence this work cannot be related to the theoretical bifurcation analysis and the underlying system structure.
-(Granger causality, DTF, partial coherence)
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients(Granger causality, DTF, partial coherence).
 An alternative approach to estimating the connectivity structure between brain regions is dynamic causal modeling (DCM).
 The DCM approach essentially studies the causality of information transform between pre-determined brain regions.
-DCM asks what connectivity structure between brain regions best explains a data set.
+These regions are determined from prior information from fMRI, AR modeling or source inversion for example.
+DCM asks what connectivity structure between the specific isolated brain regions best explains a data set.
 The approach has generated several publications (ref) and generated evidence in understanding specific hierarchical networks of neural information processing.
+These approaches have yielded interesting results but is limited in the sense that structure is not estimated hence this work cannot be related to the theoretical bifurcation analysis and the underlying system structure.
 Changes in connectivity would reflect learning.
@@
 In this work we aim to estimate local intracortical connectivity. This is most invariant.
+
 \section{Neural Field Model}
-
-The Wilson-Cowan model has shown to be descriptive of a range of neurodynamics of the cortex.
-The model is capable of generating patterns of activity such as Turing patterns, spirals, ....
+In this section we describe a variant of the Jansen and Ritt neural field model~\cite{Jansen1995} that will be used to create our connectivity estimator.
+This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials and epileptic behavior and is capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations.
 The general form of the model is described here.

### 2009-11-12 ltx/BrainIDE.tex
Updated Introductory section of the paper (tex and bib files) and added more references about AR eeg modelling

@@
 These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} that would be impossible to gain from experimental data alone.
-Unfortunately, to date the use of these models in the clinic has very limited, since the neural field model are constructed for a general brain and pathologies almost always have unique underlying patient specific causes.
+Unfortunately, to date the use of these models in the clinic has been limited, since the neural field model are constructed for a general brain dynamics and pathologies almost always have unique underlying patient specific causes.
 Data from EEG and functional magnetic resonance imaging (fMRI) offers the patient specific link to macro-scale cortical dynamics, making these tools readily applicable to the clinic.
@@
 Fitting the general neural field models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
-This is most likely due to the large parameter set that most models use in order to be physiologically plausible.
-To our knowledge, the first (and only) published research that attempts parameter estimation with a neural field model used an unscented Kalman filter to track parameters of the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
-This work marks the first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+An estimation frame work for neural field model known as dynamical causal modeling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
+Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
+The approach has proven very useful in understanding specific hierarchical networks of neural information processing.
+Another recent publication describing parameter estimation method with a neural field model used an unscented Kalman filter with the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
+This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+
 Generating patient specific models allows that application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
@@
 In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range corticocortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
-Locally, each column is thought to have symmetric short range local excitation, with surround inhibition~\cite{Braitenberg1998}.
-For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes column to a particular receptive visual field~\cite{Sullivan2006}.
-Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
+Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition~\cite{Braitenberg1998}.
+For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
+
+Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure of the cortical columns, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
 This implies that if we could estimate the connectivity structure for individuals we may be able to model patient specific dynamics.
+Estimating function cortical connectivity via EEG measures is currently a highly active area of research.
+There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modeling of the times series.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, direct transfer function~\cite{Kaminski1991}, partial directed coherence~\cite{Sameshima1999}).
+Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear between the general field models and the data.
+Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
 
-Estimating function cortical connectivity via EEG measures is currently a highly active area of research.
-There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks.
-Most works are based on auto-regressive (AR) modeling of the times series.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients(Granger causality, DTF, partial coherence).
-An alternative approach to estimating the connectivity structure between brain regions is dynamic causal modeling (DCM).
-The DCM approach essentially studies the causality of information transform between pre-determined brain regions.
-These regions are determined from prior information from fMRI, AR modeling or source inversion for example.
-DCM asks what connectivity structure between the specific isolated brain regions best explains a data set.
-The approach has generated several publications (ref) and generated evidence in understanding specific hierarchical networks of neural information processing.
-These approaches have yielded interesting results but is limited in the sense that structure is not estimated hence this work cannot be related to the theoretical bifurcation analysis and the underlying system structure.
-Changes in connectivity would reflect learning.
+Until now, estimation of local connectivity structure has not been attempted.
+Recently it has been shown that it is possible to estimate local connectivity of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
+In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
+In this paper we demonstrate how intracortical connectivity can be inferred from EEG data, based on a variant Jansen and Ritt neural field model.
+
 Longrange connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
-In this work we aim to estimate local intracortical connectivity. This is most invariant.
 

### 2009-11-12 ltx/BrainIDE.tex
Fixed a couple of typos in intro

@@
 
-Until now, estimation of local connectivity structure has not been attempted.
-Recently it has been shown that it is possible to estimate local connectivity of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
+Until now, estimation of local intracortical connectivity structure has not been attempted.
+Recently it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-In this paper we demonstrate how intracortical connectivity can be inferred from EEG data, based on a variant Jansen and Ritt neural field model.
+In this paper we demonstrate for the first time how intracortical connectivity can be inferred from EEG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
+This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.
 
@@
 \section{Neural Field Model}
-In this section we describe a variant of the Jansen and Ritt neural field model~\cite{Jansen1995} that will be used to create our connectivity estimator.
+In this section we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our connectivity estimator.
 This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials and epileptic behavior and is capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations.

### 2009-11-13 ltx/BrainIDE.tex
Fixed some more typos in intro

@@
 Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} that would be impossible to gain from experimental data alone.
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} \cite{Schiff2009} that would be impossible to gain from experimental data alone.
 Unfortunately, to date the use of these models in the clinic has been limited, since the neural field model are constructed for a general brain dynamics and pathologies almost always have unique underlying patient specific causes.
@@
 Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure of the cortical columns, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for individuals we may be able to model patient specific dynamics.
-Estimating function cortical connectivity via EEG measures is currently a highly active area of research.
+This implies that if we could estimate the connectivity structure for an individual, than we could model patient specific neurodynamics.
+Estimating functional cortical connectivity via EEG measures is currently a highly active area of research.
 There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modeling of the times series.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, direct transfer function~\cite{Kaminski1991}, partial directed coherence~\cite{Sameshima1999}).
-Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear between the general field models and the data.
+Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG or fMRI times series.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}).
+Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
 Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
@@
 Until now, estimation of local intracortical connectivity structure has not been attempted.
-Recently it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
+Recently, it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
+The key development in this work was to define the state-space model order independent of the number of observations (or ECoG recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-In this paper we demonstrate for the first time how intracortical connectivity can be inferred from EEG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
+Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria.
+In this paper we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.
 
-Longrange connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
+Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
 
@@
 In this section we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our connectivity estimator.
-This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials and epileptic behavior and is capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations.
+This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behavior.
+It is also capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations.
 The general form of the model is described here.
@@
 \end{equation}
-Even though $v_0$ is a constant, we show express it as a field allowing for inhomogenaities and for clarity in constructing the state-space representation in the next section.
+Even though $v_0$ is a constant, we show express it as a field allowing for inhomogeneities and for clarity in constructing the state-space representation in the next section.
 The parameters in equation~\ref{Eq4} are...
@@
 In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity.
-Standing, but not traveling waves?
-This is a common assumption when dealing with models in this form.
+This reduced the model to a single field.
+I am not sure how this will limit the dynamics??
 We will also assume the velocity of the action potentials is infinite.
-This is also a common assumption that is made in the neural field modeling community.
+This is also a common assumption that is made when modeling intracortical circuits.
+As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being infinite.
 Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics (Coombes paper, and Atay paper).
@@
 The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, and not on their spatial location.
-Again, this is a common assumption in this field.
+Again, this is a common assumption when dealing with intracortical connectivity.
 This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible.
@@
 
+Alternatively we replace the sigmoidal firing mechanism with a Heaviside function.
 \section{State-Space Neural Field Model}
@@
 \end{equation}
-where $\Theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\Theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$.
+where $\theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$.
 The voltage field at $t$ is comprised of a scaled version (by the state $x_t$) of the basis functions $\phi(s)$.

### 2009-11-14 Discussion/131009/BrainIDE131009.tex

\documentclass[a4paper,12pt]{article}
 \setlength{\textwidth}{460pt}
 \setlength{\textheight}{660pt}
 \setlength{\headheight}{12pt}
 \setlength{\headsep}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\oddsidemargin}{0pt}
\usepackage{enumerate}
% Maths
\usepackage{amssymb,amsmath,amsthm}
\usepackage{amsfonts}
% Graphics Package
%\usepackage{graphicx}
\usepackage[pdftex]{graphicx}
\usepackage[font=footnotesize]{subfig}

%opening
% \title{}
% \author{}

\begin{document}
\begin{enumerate}
 	\item Can you explain how you get from (5) to (7)?
	\begin{itemize}
 		\item Answer:
\end{itemize}
	\item What is the external input? is it the same as the field disturbance? if it is we can't set it to zero, and if it is not we need to consider field disturbance.
	\begin{itemize}
	 	\item  Answer:
	\end{itemize}
	\item For the simulation are we treating  $v_0(r)$ as a constant? otherwise I think it causes some difficulties for us in (17) as we need to be able to calculate the convolution integral.
	\begin{itemize}
		\item Answer:
	\end{itemize}
	\item We need observation noise in (27)- I have a silly question, the signal we are measuring by implanted EEG is $v_t$ right?
	\begin{itemize}
		\item Answer:
	\end{itemize}
\end{enumerate}
\section*{Some comments}
Our basis functions are not orthonormal(see above 16).  Although it might worth investigating since it makes things easier.
There are some typo in equations:
\\equation1:
\begin{equation}\label{Eq1}
v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {s,t'} \right)dt'}.
\end{equation}
equation5:\\
\begin{equation}\label{Eq5}
v\left(s,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega \left[ h\left(t - t'\right)W\left(s,r\right)P\left( v\left( r,\bar t \right)\right)+E\left(s,t'\right)\right] dr dt'
\end{equation}
\\equation13:
\begin{align}\label{Eq13}
 {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
  + \frac{{{R_0}}}{4}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber
\end{align}

\end{document}

### 2009-11-14 ltx/BrainIDE.tex
added a TODO environment. Use like \todo{Something we should do!}. Have also changed the formatting to draft onecolumn mode so I can sit with it and a coffee and cover it in ink. Which is what I am going to do right now. Saturdays are great!
Fixed typos in equations (3), (5) and (13)
trying to remove files
Attempted to make the model description clearer by adding an alternate derivation

@@
 
-\documentclass[journal]{IEEEtran}
+\documentclass[onecolumn,draftcls]{IEEEtran}
 
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+% TODO environment
+\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
 
@@
 \begin{equation}\label{Eq1}
-v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {r,t'} \right)dt'}.
+v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {s,t'} \right)dt'}.
 \end{equation}
@@
 \begin{equation}\label{Eq5}
-v\left( {s,t} \right) = \int\limits_{ - \infty }^t {\int\limits_\Omega  {h\left( {t - t'} \right)W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dy} dt'}  + E\left( {s,t} \right).
+v\left(s,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega \left[ h\left(t - t'\right)W\left(s,r\right)P\left( v\left( r,\bar t \right)\right)+E\left(s,t'\right)\right] dr dt'
 \end{equation}
@@
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
+
+\subsection{Alternate model description}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.4]{BasicStructureOfModel.eps}
+\caption[NeuralMassModel]{This figure describes the basic interactions of neural masses that constitute the neural field model.}
+\label{NeuralMassModel}
+\end{figure*}
+
+An alternative description of the model is as follows.
+The model can be thought of as a continuum of neural masses.
+To illustrate this idea we shall first describe the interaction of discrete neural masses.
+Assuming post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
+\begin{equation}\label{Eq1.1}
+{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t \right)} H\left( {t - {t_k}} \right),
+\end{equation}
+where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $H$ is the Heaviside step function and action potential arrive at neuron I at times $t_k$.
+Alternatively the membrane potential can described by
+\begin{equation}\label{1.2}
+{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt',
+\end{equation}
+where $r_j(t)$ is the firing rates of the presynaptic neurons. To convert the equation system into and integral differential system we shall take derivative of~\ref{Eq1.1} yielding
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t \right)\frac{d}{{dt}}H\left( {t - {t_k}} \right) + {w_{ij}}H\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t \right)} \right)} \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}H\left( {t - {t_k}} \right)\frac{1}{{{\tau _j}}}{h_j}\left( t \right)}   \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t \right)\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber  \\
+   &=& \sum\nolimits_j {{w_{ij}}{r_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber \\
+   &=& \sum\nolimits_j {{w_{ij}}S\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}}. 
+\end{eqnarray}
+This form can easily be extended to represent a continuous field.
 
@@
  {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
-  + \frac{{{R_0}}}{2}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
+  + \frac{{{R_0}}}{4}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
   + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber

### 2009-11-15 ltx/BrainIDE.tex
Fixed typos in alternative model description in tex file

--- 2009-11-13 ltx/BrainIDE.tex
@@
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
+
+\subsection{Alternate model description}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.4]{NeuralMassFigure.eps}
+\caption[NeuralMassModel]{This figure describes the basic interactions of neural masses that constitute the neural field model.}
+\label{NeuralMassModel}
+\end{figure*}
+
+An alternative description of the model is as follows.
+The model can be thought of as a continuum of neural masses.
+To illustrate this idea we shall first describe the interaction of discrete neural masses as seen in Figure~\ref{NeuralMassModel}.
+Assuming post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
+\begin{equation}\label{Eq1.1}
+{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} H\left( {t - {t_k}} \right),
+\end{equation}
+where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $H$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
+Alternatively the membrane potential can described by the convolution of synaptic response kernel with the pre-synaptic firing rate $r_j(t)$ where
+\begin{equation}\label{1.2}
+{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
+\end{equation}
+To convert the equation system into and integral differential system we shall take derivative of~\ref{Eq1.1} yielding
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}H\left( {t - {t_k}} \right) + {w_{ij}}H\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}H\left( {t - {t_k}} \right)\frac{1}{{{\tau _j}}}{h_j}\left( t- {t_k} \right)}   \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber  \\
+   &=& \sum\nolimits_j {{w_{ij}}{r_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber \\
+   &=& \sum\nolimits_j {{w_{ij}}P\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}}.
+\end{eqnarray}
+This form can easily be extended to represent a continuous field.
 

### 2009-11-15 ltx/BrainIDE.tex
Began making adjustments of the field model derivation following our Sunday meeting

@@
 
-The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the sigmoid function
+The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the Heaviside step function
 \begin{equation}\label{Eq4}
-P\left( {v\left( {r,\bar t} \right)} \right) = {R_0}{\left( {1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - v\left( {r,\bar t} \right)} \right)} \right)} \right)^{ - 1}}.
+P\left( {v\left( {r,\bar t} \right)} \right) = {r_0}S\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
 \end{equation}
-Even though $v_0$ is a constant, we show express it as a field allowing for inhomogeneities and for clarity in constructing the state-space representation in the next section.
+\begin{equation}\label{Eq4.1}
+S\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
+   1 & {v\left( {r,\bar t} \right) \ge {v_0}\left( r \right)}  \\
+   0 & {otherwise}  \\
+\end{array}} \right.
+\end{equation}
+Even though $v_0$ is a constant in this research we show express it as a field allowing for inhomogeneities and for clarity and generality in constructing the state-space representation in the next section.
 The parameters in equation~\ref{Eq4} are...
-$v_0$ is typically 6~mV, $R_0$ is 5~$s^{-1}$ and $\beta$ is 0.56~mV$^{-1}$ (from Wendling and David papers).
+$v_0$ is typically 6~mV, $r_0$ is 5~$s^{-1}$ (from Wendling and David papers).
 By combining equations~\ref{Eq1} and \ref{Eq3} we get the spatiotemporal model
 \begin{equation}\label{Eq5}
-v\left(s,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega \left[ h\left(t - t'\right)W\left(s,r\right)P\left( v\left( r,\bar t \right)\right)+E\left(s,t'\right)\right] dr dt'
+v\left(s,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)W\left(s,r\right)P\left( v\left( r,\bar t \right)\right)dr dt'+E\left(s,t'\right)
 \end{equation}
@@
 \end{equation}
-The neural field model can be represented as a discrete-time stochastic IDE by
-\begin{equation}\label{Eq9}
-{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {{v_{\bar t}}\left( r \right)} \right)dr}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right),
+\subsection{Alternate Model Description I}
+An alternate and equivalent way to remove the temporal integration is through the Laplace transform.
+We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
+\begin{equation}\label{Eq9.1}
+{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}P\left( {{v_j}\left( t \right)} \right)dt'},
 \end{equation}
-where $\epsilon(t)$ is the discrete time stochastic input.
-The IDE representation of equation~\ref{Eq9} is discrete in time and continuous in space.
+where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform yielding
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
+   &=& {\left( {s + \frac{1}{\tau }} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
+  \Rightarrow s{V_i}\left( s \right) + \frac{1}{\tau }{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
+\end{eqnarray}
+Now taking the inverse Laplace transform we get
+\begin{equation}\label{9.3}
+\frac{{d{v_i}\left( t \right)}}{{dt}} + \frac{1}{\tau }{v_i}\left( t \right) = {w_{ij}}P\left( {{v_j}\left( t \right)} \right).
+\end{equation}
+Next we convert the model from discrete neural masses to a continuum by
+\begin{equation}\label{Eq9.4}
+\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{1}{\tau }{v\left( {s,t} \right)} = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
+\end{equation}
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
 
-\subsection{Alternate model description}
+\subsection{Alternate Model Description II}
 
@@
    &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}H\left( {t - {t_k}} \right)\frac{1}{{{\tau _j}}}{h_j}\left( t- {t_k} \right)}   \nonumber \\
-   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber  \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber  \\
    &=& \sum\nolimits_j {{w_{ij}}{r_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber \\
@@
 \subsection{Assumptions and Simplifications}
-We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population.
-In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity.
-This reduced the model to a single field.
-I am not sure how this will limit the dynamics??
-We will also assume the velocity of the action potentials is infinite.
+We assume the velocity of the action potentials is infinite.
 This is also a common assumption that is made when modeling intracortical circuits.
@@
 The IDE estimation is derived for a general heterogeneous structure, however for clarity of results we shall only present the heterogeneous case.
+We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population.
+In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity.
+This reduced the model to a single field.
+I am not sure how this will limit the dynamics??
 With these assumptions we have the model in the form
@@
 \end{equation}
-In addition to the assumptions above we shall linearize the model by approximating the sigmoid function $P$ as a piece-wise linear function, $P_{L}$, where
-\begin{equation}\label{Eq11}
-\begin{array}{*{20}{c}}
-   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = 0,} \hfill & {f\left( {{v_t}\left( r \right)} \right) \le 0} \hfill  \\
-   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = f\left( {{v_t}\left( r \right)} \right),} \hfill & {0 < f\left( {{v_t}\left( r \right)} \right) < {R_0}} \hfill  \\
-   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = {R_0},} \hfill & {f\left( {{v_t}\left( r \right)} \right) \ge {R_0}} \hfill  \\
-\end{array}
-\end{equation}
-and
-\begin{equation}\label{Eq12}
-f\left( {{v_t}\left( r \right)} \right) = \frac{{{R_0}}}{2}\left( {1 + \frac{\beta }{2}\left( {{v_t}\left( r \right) - {v_0}\left( r \right)} \right)} \right).
-\end{equation}
-For the derivation of the state-space model we shall assume that the model is operating in the active dynamic region, since this is the most interesting case, and the other cases correspond to the neural populations either being saturated (at $R_0$) or being silent.
-We shall show be stability analysis that the model will not saturate for the given parameters and nor will it be silent since it is continuously driven by noise.
-Substituting equation~\ref{Eq11} into equation~\ref{Eq10} and expanding we get
-\begin{align}\label{Eq13}
- {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
-  + \frac{{{R_0}}}{4}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
-  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber
-\end{align}
-where ${\bar v_0}\left( r \right) = 1 - \frac{\beta }{2}{v_0}\left( r \right)$.
 
-Alternatively we replace the sigmoidal firing mechanism with a Heaviside function.
 \section{State-Space Neural Field Model}

### 2009-11-16 ltx/BrainIDE.tex
Fixed notational things in model derivation and fixed some typos

@@
 The general form of the model is described here.
-The post-synaptic potentials generated at a neuronal population $s$ by action potentials arriving from all other connected populations at position $r$ can be described by
-\begin{equation}\label{Eq1}
-v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {s,t'} \right)dt'}.
+The post-synaptic potentials generated at a neuronal population $r$ by action potentials arriving from all other connected populations at position $r'$ can be described by
+\begin{equation}\label{SpikesToPotential}
+v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)f\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
 \end{equation}
+Equation~\ref{SpikesToPotential} relates, $f$, or the average number of action potentials arriving at $r$ to the post synaptic potential at $r$, to the local membrane voltage.
+The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity.
 The post-synaptic response kernel $h(t)$ is described by
-\begin{equation}\label{Eq2}
+\begin{equation}\label{SynapticRespKernel}
 h(t) = \left\{ {\begin{array}{*{20}{c}}
-   {\exp ( - {t \mathord{\left/
- {\vphantom {t \tau }} \right.
- \kern-\nulldelimiterspace} \tau })} & {t \ge 0}  \\
+   {\exp ( - \alpha t)} & {t \ge 0}  \\
    0 & {t < 0}  \\
-\end{array}} \right.,
+\end{array}} \right.
 \end{equation}
-where $\tau$ is the synaptic time constant and typically has values from 10-20~ms (\textcolor[rgb]{1.00,0.00,0.00}{refs}).
-The synaptic response kernel can be more elaborate, using a rise and fall time constant, however this simple form serves our purposes.
-Equation~\ref{Eq1} relates average firing rate of a presynaptic neural population to the mean membrane potential of the post-synaptic neurons.
-The mean firing rate, $J$, is convolved with the response kernel to give membrane potential since the firing rate is assumed to follow a (homogeneous?) Poisson process.
+where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant.
+The synaptic response kernel can be more elaborate, using a rise and fall time constants, however this simple form serves our purposes.
 Nonlocal interactions between cortical populations are described by
-\begin{equation}\label{Eq3}
-J\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right)
+\begin{equation}\label{RateBasedInteractions}
+f\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}
 \end{equation}
-where $\bar t = t - \frac{{\left| {s - r} \right|}}{d}$, $P$ is a mean pulse rate of population at $y$, $W$ is the connectivity kernel, $E$ is an external input, $\Omega$ is the spatial domain and $d$ is the propagation velocity from $r$ to $s$.
+where $\bar t = t - d\left| {r - r'} \right|$, $p$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, $\Omega$ is the spatial domain, representing a cortical sheet or surface and $d$ is the propagation delay from $r'$ to $r$.
 
-The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the Heaviside step function
-\begin{equation}\label{Eq4}
-P\left( {v\left( {r,\bar t} \right)} \right) = {r_0}S\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
+The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the Heaviside step function
+\begin{equation}\label{RateOfPreSynPops}
+p\left( {v\left( {r,\bar t} \right)} \right) = {\nu_0}u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
 \end{equation}
-\begin{equation}\label{Eq4.1}
-S\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
+\begin{equation}\label{HeavisideDef}
+u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
    1 & {v\left( {r,\bar t} \right) \ge {v_0}\left( r \right)}  \\
@@
 \end{equation}
-Even though $v_0$ is a constant in this research we show express it as a field allowing for inhomogeneities and for clarity and generality in constructing the state-space representation in the next section.
-The parameters in equation~\ref{Eq4} are...
-$v_0$ is typically 6~mV, $r_0$ is 5~$s^{-1}$ (from Wendling and David papers).
-By combining equations~\ref{Eq1} and \ref{Eq3} we get the spatiotemporal model
-\begin{equation}\label{Eq5}
-v\left(s,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)W\left(s,r\right)P\left( v\left( r,\bar t \right)\right)dr dt'+E\left(s,t'\right)
+Even though we will model  $v_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality when constructing the state-space representation in the next section.
+The parameters in equation~\ref{RateOfPreSynPops} are...
+$v_0$ is typically 6~mV, $\nu_0$ is 5~$s^{-1}$ (from Wendling and David papers).
+By combining equations~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
+\begin{equation}\label{FullDoubleIntModel}
+v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)p\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
 \end{equation}
 To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
-\begin{equation}\label{Eq6}
+\begin{equation}\label{GreensFuncDef}
 Lh\left( t \right) = \delta \left( t \right),
@@
 where $L$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
-\begin{equation}\label{Eq7}
-L\left( {\frac{\partial }{{dt}}} \right)v\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right),
+\begin{equation}\label{GenForm}
+L\left( {\frac{\partial }{{dt}}} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {r,t} \right),
 \end{equation}
-where $L$ is a polynomial of order $n$ with constant coefficients.
-This provides an $n^{th}$ order model.
+where $L$ is a polynomial of order $n$ with constant coefficients that provides an $n^{th}$ order model.
 Most studies considering this model use first or second order time derivatives.
 We shall use the first order model giving
-\begin{equation}\label{Eq8}
-\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{{v\left( {s,t} \right)}}{\tau } = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
+\begin{equation}\label{FinalForm1}
+\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  +e\left( {r,t} \right).
 \end{equation}
 \subsection{Alternate Model Description I}
-An alternate and equivalent way to remove the temporal integration is through the Laplace transform.
+An alternate and equivalent way to remove the temporal integration using the Laplace transform .
 We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
-\begin{equation}\label{Eq9.1}
-{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}P\left( {{v_j}\left( t \right)} \right)dt'},
+\begin{equation}\label{TwoDiscreteMasses}
+{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
 \end{equation}
-where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform yielding
+where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
 \begin{eqnarray}
@@
   {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
-   &=& {\left( {s + \frac{1}{\tau }} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
-  \Rightarrow s{V_i}\left( s \right) + \frac{1}{\tau }{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
+   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
+  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
 \end{eqnarray}
 Now taking the inverse Laplace transform we get
-\begin{equation}\label{9.3}
-\frac{{d{v_i}\left( t \right)}}{{dt}} + \frac{1}{\tau }{v_i}\left( t \right) = {w_{ij}}P\left( {{v_j}\left( t \right)} \right).
+\begin{equation}\label{InverseLaplace}
+\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
 \end{equation}
 Next we convert the model from discrete neural masses to a continuum by
-\begin{equation}\label{Eq9.4}
-\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{1}{\tau }{v\left( {s,t} \right)} = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
+\begin{equation}\label{Discrete2Continuum}
+\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
 \end{equation}
@@
 Assuming post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
-\begin{equation}\label{Eq1.1}
-{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} H\left( {t - {t_k}} \right),
+\begin{equation}\label{VoltageFromPSPs}
+{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} u\left( {t - {t_k}} \right),
 \end{equation}
-where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $H$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
+where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $S$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
 Alternatively the membrane potential can described by the convolution of synaptic response kernel with the pre-synaptic firing rate $r_j(t)$ where
-\begin{equation}\label{1.2}
+\begin{equation}\label{VoltageFromRate}
 {v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
@@
 % \nonumber to remove numbering (before each equation)
-  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}H\left( {t - {t_k}} \right) + {w_{ij}}H\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
-   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}H\left( {t - {t_k}} \right)\frac{1}{{{\tau _j}}}{h_j}\left( t- {t_k} \right)}   \nonumber \\
-   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber  \\
-   &=& \sum\nolimits_j {{w_{ij}}{r_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber \\
-   &=& \sum\nolimits_j {{w_{ij}}P\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}}.
+  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}u\left( {t - {t_k}} \right) + {w_{ij}}u\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}u\left( {t - {t_k}} \right)\alpha_j{h_j}\left( t- {t_k} \right)}   \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber  \\
+   &=& \sum\nolimits_j {{w_{ij}}{\nu_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber \\
+   &=& \sum\nolimits_j {{w_{ij}}p\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j}.
 \end{eqnarray}
@@
 With these assumptions we have the model in the form
-\begin{equation}\label{Eq10}
-{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {\left| {s - r} \right|} \right)P\left( {{v_t}\left( r \right)} \right)dy}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right).
+\begin{equation}\label{SimplifiedModel}
+\frac{{dv\left( {s,t} \right)}}{{dt}} = \int_\Omega  {w\left( {s-r} \right)P\left( {v\left( {r,t} \right)} \right)dr}  - \alpha{v\left( {s,t} \right)} + e\left( {s,t} \right).
+\end{equation}
+
+\subsection{IDE Formulation}
+
+\begin{equation}\label{new_spatiotemporal_kernels}
+\frac{{dv\left( {s,t} \right)}}{{dt}} = \int_\Omega  {k\left( {s - r} \right)\tilde v\left( {r,t} \right) - \alpha \delta \left( {s - r} \right)\bar v\left( {s,t} \right)dr}  + e\left( {s,t} \right)
+\end{equation}
+
+\begin{equation}\label{define_v_tilde}
+\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
+   0 & {otherwise}  \\
+\end{array}} \right.
+\end{equation}
+
+\begin{equation}\label{define_v_bar}
+\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
+   0 & {otherwise}  \\
+\end{array}} \right.
 \end{equation}

### 2009-11-16 ltx/BrainIDE.tex
Added Parham's state-space derivation to the paper, replace the older incorrect version

@@
 \end{equation}
-To convert the equation system into and integral differential system we shall take derivative of~\ref{Eq1.1} yielding
+To convert the equation system into and integral differential system we shall take derivative of~\ref{EqVoltageFromPSPs} yielding
 \begin{eqnarray}
@@
 As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being infinite.
-Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics (Coombes paper, and Atay paper).
+Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics~\cite{Atay2005}.
 The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences.
@@
 \begin{equation}\label{SimplifiedModel}
-\frac{{dv\left( {s,t} \right)}}{{dt}} = \int_\Omega  {w\left( {s-r} \right)P\left( {v\left( {r,t} \right)} \right)dr}  - \alpha{v\left( {s,t} \right)} + e\left( {s,t} \right).
+\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)P\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
 \end{equation}
@@
 \begin{equation}\label{new_spatiotemporal_kernels}
-\frac{{dv\left( {s,t} \right)}}{{dt}} = \int_\Omega  {k\left( {s - r} \right)\tilde v\left( {r,t} \right) - \alpha \delta \left( {s - r} \right)\bar v\left( {s,t} \right)dr}  + e\left( {s,t} \right)
+\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
 \end{equation}
@@
 The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
-To simplify the notation in the derivation we will let the external input $\epsilon(t)=0$.
-Also, we shall define
-\begin{equation}\label{Eq14}
-W\left( {s,r} \right) = {\theta ^T}\psi \left( {s,r} \right)
+\begin{equation}
+ v_{t+1}(\mathbf s)=\int_{\mathcal S} \alpha \delta(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d \mathbf r+\int_{\mathcal S} W(\mathbf s -\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+e_t(\mathbf s)
+\label{eq:cortexfield}
 \end{equation}
-and
-\begin{equation}\label{Eq15}
-{v_t}\left( s \right) = \phi {\left( s \right)^T}{x_t},
+decomposing the field and the kernel we have
+\begin{equation}
+\bar v_t(\mathbf s)=\boldsymbol \phi^{\top}(\mathbf s)\bar{\mathbf x}_t
+\label{eq:cortexfieldlv0}
 \end{equation}
-where $\theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$.
-The voltage field at $t$ is comprised of a scaled version (by the state $x_t$) of the basis functions $\phi(s)$.
- The spatial kernel $W$ and the field $v$ are decomposed using the same basis functions, and we will define them as being complete and orthogonal. Also, we shall define
-\begin{equation}\label{Eq16}
-\Phi \left( s \right) = \int_\Omega  {\psi \left( {s,r} \right)\phi {{\left( r \right)}^T}dr}
+\begin{equation}
+\tilde v_t(\mathbf s)=\boldsymbol \phi^{\top}(\mathbf s)\tilde{\mathbf x}_t
+\label{eq:cortexfieldgv0}
 \end{equation}
-and
-\begin{equation}\label{Eq17}
-\Gamma \left( s \right) = \int_\Omega  {\psi \left( {s,r} \right){{\bar v}_0}\left( r \right)dr}.
+\begin{equation}
+ W(\mathbf s -\mathbf r)=\boldsymbol \theta^{\top}\psi(\mathbf s -\mathbf r)
+\label{eq:kerneldecomposition}
 \end{equation}
-By substituting equations~\ref{Eq14} and \ref{Eq15} into equation~\ref{Eq13} we get
-\begin{align}\label{Eq18}
- {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}{\theta ^T}\int_\Omega  {\psi \left( {s,r} \right){{\bar v}_0}\left( r \right)dr} \nonumber \\
-  + \frac{{{R_0}}}{2}\beta {\theta ^T}\int_\Omega  {\psi \left( {s,r} \right)\phi {{\left( r \right)}^T}dr} {x_t} \\
-  - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t} \nonumber
-\end{align}
-and substituting in equations~\ref{Eq16} and \ref{Eq17} into equation~\ref{Eq18} we get
-\begin{equation}\label{Eq19}
-{v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}{\theta ^T}\Gamma \left( s \right) + \frac{{{R_0}}}{2}\beta {\theta ^T}\Phi \left( s \right){x_t} - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t}.
+Substituting (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:kerneldecomposition}) in (\ref{eq:cortexfield}) we get
+\begin{equation}
+ \boldsymbol \phi^{\top}(\mathbf s)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf s)\tilde{\mathbf x}_{t+1}=
+\int_\mathcal{S}\alpha\delta(\mathbf s- \mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r+\int_\mathcal{S}\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\tilde{\mathbf x}_td\mathbf r+e_t(\mathbf s)
+\label{eq:decomposedcortexfield}
 \end{equation}
-By substituting the field for the basis functions weighted by the state vector we get
-\begin{equation}\label{Eq20}
-\phi {\left( s \right)^T}{x_{t + 1}} = \frac{{{R_0}}}{2}{\theta ^T}\Gamma \left( s \right) + \frac{{{R_0}}}{2}\beta {\theta ^T}\Phi \left( s \right){x_t} - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t}.
+\begin{equation}
+ \boldsymbol \phi^{\top}(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf s)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\mathcal S}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\tilde{\mathbf x}_td\mathbf r+e_t(\mathbf s)
 \end{equation}
-Multiplying both sides by $\phi(s)$ and integrating over $s$ we get
-\begin{align}\label{21}
- \int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds{x_{t + 1}}}  = \frac{{{R_0}}}{2}\int_\Omega  {\phi \left( s \right){\theta ^T}\Gamma \left( s \right)ds}  \nonumber \\
-  + \frac{{{R_0}}}{2}\beta \int_\Omega  {\phi \left( s \right){\theta ^T}\Phi \left( s \right)ds} {x_t} \\
-  - \frac{1}{\tau }\int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds} {x_t}. \nonumber
-\end{align}
+by defining
+\begin{equation}
+ \boldsymbol\Phi(\mathbf s)=\int_{\mathcal S}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
+\label{eq:convolution}
+\end{equation}
+we have
+\begin{equation}
+ \boldsymbol \phi^{\top}(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf s)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)\tilde{\mathbf x}_t+e_t(\mathbf s)
+\label{eq:cortexfieldwithPhi}
+\end{equation}
+Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf s) $, and integrating over $\mathbf s$
+\begin{equation}
+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s \bar{\mathbf x}_{t}+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s\tilde{\mathbf x}_t+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\label{eq:cortexfieldversion2}
+\end{equation}
 Now we define
-\begin{equation}\label{22}
-\Psi  = \int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds}
+\begin{equation}
+ \boldsymbol\Psi_x(\mathbf s)=\int_{\mathcal S}\boldsymbol\phi(\mathbf s)\boldsymbol\phi^{\top}(\mathbf s)d\mathbf s
+\label{eq:psix}
 \end{equation}
-and
-\begin{equation}\label{23}
-\Upsilon  = \int_\Omega  {\phi \left( s \right){\theta ^T}\Phi \left( s \right)ds}
+\begin{equation}
+  \boldsymbol\Psi_{\theta}(\mathbf s)=\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s
+\label{eq:psitheta}
 \end{equation}
-and
-\begin{equation}\label{24}
-\Pi  = \int_\Omega  {\phi \left( s \right){\theta ^T}\Gamma \left( s \right)ds},
+substituting (\ref{eq:psix}) and (\ref{eq:psitheta}) in (\ref{eq:cortexfieldversion2}) we get
+\begin{equation}
+\boldsymbol\Psi_x(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf s) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf s)\tilde{\mathbf x}_t+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
 \end{equation}
-where $\Psi$ is a square positive definite matrix. Substituting equations~\ref{22}, ~\ref{23} and \ref{24} into equation~\ref{21} we get
-\begin{equation}\label{25}
-\Psi {x_{t + 1}} = \frac{{{R_0}}}{2}\Pi  + \frac{{{R_0}}}{2}\beta \Upsilon {x_t} - \frac{1}{\tau }\Psi {x_t}.
+pre-multiplying both sides by $\boldsymbol\Psi_x^{-1}$
+\begin{equation}
+\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
 \end{equation}
-Since $\Psi$ is a square positive definite matrix we can invert it to isolate $x_t$ yielding
-\begin{equation}\label{26}
-{x_{t + 1}} = \frac{{{R_0}}}{2}{\Psi _x}^{ - 1}\Pi  + \left( {\frac{{{R_0}}}{2}\beta {\Psi _x}^{ - 1}\Upsilon  - \frac{1}{\tau }{\bf{I}}} \right){x_t},
+????????????????????????????????
+\subsection{Observation equation}
+\begin{eqnarray}
+ \mathbf y_t(\mathbf s)&=&\\
+&=&\int_{\mathcal S}H(\mathbf s-\mathbf r)v_t(\mathbf r)d\mathbf r+\boldsymbol\epsilon_t \\
+&=&\int_{\mathcal S}H(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d\mathbf r+\int_{\mathcal S}H(\mathbf s-\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+\epsilon_t
+\label{eq:observationequation}
+\end{eqnarray}
+
+ we decompose $ H(\mathbf s-\mathbf r)$ as
+ \begin{equation}
+  H(\mathbf s-\mathbf r)= \mathbf c^{\top}\mu(\mathbf s-\mathbf r)
+\label{eq:decomposedobservationkernel}
 \end{equation}
-where \textbf{I} is the identity matrix. The model can now be written in the canonical state-space form
-\begin{equation}\label{27}
-\begin{array}{c}
- {x_{t + 1}} = A{x_t} + Bu \\
- {v_t}\left( s \right) = C{x_t}, \\
- \end{array}
+and substituting  (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:decomposedobservationkernel}) in (\ref{eq:observationequation}) we get
+\begin{equation}
+ \mathbf y_t(\mathbf s)=\int_{\mathcal S}\mathbf c^{\top}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}d\mathbf r+\int_{\mathcal S}\mathbf c^{\top}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t}d\mathbf r+\epsilon_t
+\end{equation}
+and finally we have
+\begin{equation}
+\mathbf y_t(\mathbf s)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf s)&\mathbf c^{\top}\mathbf M(\mathbf s)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
 \end{equation}
 where
-\begin{equation}\label{28}
-\begin{array}{l}
- A = \frac{{{R_0}}}{4}\beta {\Psi _x}^{ - 1}\Upsilon  - \frac{1}{\tau }{\bf{I}} \\
- B = \frac{{{R_0}}}{2}{\Psi _x}^{ - 1}\Pi  \\
- C = {\phi ^T}\left( s \right) \\
- u = 1. \\
- \end{array}
+\begin{equation}
+ \mathbf M(\mathbf s)=\int_{\mathcal S}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)d\mathbf r
 \end{equation}

### 2009-11-17 ltx/BrainIDE.tex
Added alternative state-space derivation with Heaviside function

@@
 
-The neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+Neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
 Each neural population represents a functional cortical processing unit referred to as a column.
@@
 
+For the state-space derivation, to create an estimator, the model can be reformulated like so
 \begin{equation}\label{new_spatiotemporal_kernels}
@@
 
+\begin{figure*}
+\centering
+\includegraphics[scale=0.4]{ExampleFieldDecomposition.eps}
+\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
+Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
+\label{ExampleFieldDecomposition}
+\end{figure*}
+
 \section{State-Space Neural Field Model}
@@
 \begin{equation}
- v_{t+1}(\mathbf s)=\int_{\mathcal S} \alpha \delta(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d \mathbf r+\int_{\mathcal S} W(\mathbf s -\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+e_t(\mathbf s)
+ v_{t+1}(\mathbf s)=\int_{\mathcal S} \alpha \delta(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d \mathbf r+\int_{\mathcal S} w(\mathbf s -\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+e_t(\mathbf s)
 \label{eq:cortexfield}
@@
 \begin{equation}
-\bar v_t(\mathbf s)=\boldsymbol \phi^{\top}(\mathbf s)\bar{\mathbf x}_t
+\bar v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
 \label{eq:cortexfieldlv0}
@@
 \begin{equation}
-\tilde v_t(\mathbf s)=\boldsymbol \phi^{\top}(\mathbf s)\tilde{\mathbf x}_t
+\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0
 \label{eq:cortexfieldgv0}
@@
 \begin{equation}
- W(\mathbf s -\mathbf r)=\boldsymbol \theta^{\top}\psi(\mathbf s -\mathbf r)
+ w(\mathbf r -\mathbf r')=\boldsymbol \theta^{\top}\psi(\mathbf r -\mathbf r')
 \label{eq:kerneldecomposition}
@@
 
+\subsection{State-Space Model Alternative Approach}
+First we define
+\begin{equation}\label{DefineKappa}
+\kappa \left( r' \right) = \left\{ {\begin{array}{*{20}{c}}
+   {{\nu _0}} & {v\left( {r',t} \right) \ge {v_0}}  \\
+   0 & {otherwise}  \\
+\end{array}} \right.
+\end{equation}
+
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  {v_{t + 1}}\left( r \right)  &=& \int_\Omega  {k\left( {r - r'} \right)\kappa \left( r' \right) - \alpha \delta \left( {r - r'} \right)v\left( {r,t} \right)dr'}  + \varepsilon\left( {r,t} \right) \\
+   &=& \int_\Omega  {k\left( {r - r'} \right)\kappa \left( r' \right)dr'}  - \alpha\int_\Omega  { \delta \left( {r - r'} \right)v\left( {r,t} \right)dr'}  + \varepsilon\left( {r,t} \right)
+\end{eqnarray}
+Defining
+\begin{equation}\label{FieldDecomp}
+{v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
+\end{equation}
+\begin{equation}\label{KernelDecomp}
+k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right)
+\end{equation}
+Making substitutions
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  {\phi ^T}\left( r \right){x_{t+1}}  &=& {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( r' \right)dr'}  - \alpha \int_\Omega  {\delta \left( {r - r'} \right){\phi ^T}\left( r \right){x_t}dr'}  + \varepsilon \left( {r,t} \right) \\
+   &=& {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( r' \right)dr'}  - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
+\end{eqnarray}
+Now we define
+\begin{equation}\label{DefFiringConnectivity}
+\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( r' \right)dr'}.
+\end{equation}
+Substituting in
+\begin{equation}\label{Dunno}
+{\phi ^T}\left( r \right){x_{t+1}} = {\theta ^T}\Phi \left( r \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
+\end{equation}
+Cross multiply by $\phi(r)$ and integrating over $r$ we get
+\begin{equation}\label{TooTired}
+\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t+1}} = \int_\Omega  {\phi \left( r \right){\theta ^T}\Phi \left( r \right)dr}  - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+Now let us define
+\begin{equation}\label{DefinePsix}
+{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr}
+\end{equation}
+\begin{equation}\label{DefinePsiTheta}
+{\Psi _\theta } = \int_\Omega  {\phi \left( r \right){\theta ^T}\Phi \left( r \right)dr}.
+\end{equation}
+Making substitutions
+\begin{equation}\label{poo}
+{\Psi _x}{x_{t+1}} = {\Psi _\theta } - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+\end{equation}
+Isolating the state we get
+\begin{equation}\label{IsolatingState}
+{x_{t+1}} = {\Psi _x}^{ - 1}{\Psi _\theta } - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+
+\begin{equation}\label{SSmodel}
+{x_{t+1}} = A{x_t} + Bu + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  A &=& -\alpha \\
+  B &=& {\Psi _x}^{ - 1}{\Psi _\theta } \\
+  u &=& 1 
+\end{eqnarray}
+Here we have a horrible nonlinearity with term $B = \Psi _x^{ - 1}\Psi_\theta$, which is on or off depending on if the field is past the threshold.
+Unfortunately, this is the place where the spatial kernel parameters live.
+The unscented Kalman filter or a particle filter could possibly estimate C.
+What do you think?
+
 \section{Stability Analysis}
@@
 Try and estimate the linear and nonlinear model based on the linear estimator. Might work ok?
-
-\subsection{Linear Model}
-
-\subsection{Nonlinear Model}
 

### 2009-11-17 ltx/BrainIDE.tex
Attempted to make a derivation of state-space formulation for a general nonlinearity (needs checking)

--- 2009-11-16 ltx/BrainIDE.tex
@@
 
+\subsection{State-Space Model Alternative Approach}
+First we define
+
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon \left( {r,t} \right) \\
+   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon \left( {r,t} \right)
+\end{eqnarray}
+
+Defining
+\begin{equation}\label{Def1}
+   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
+\end{equation}
+\begin{equation}\label{Def2}
+k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right)
+\end{equation}
+Since we assume knowledge of $\phi(r')$ and $p(.)$, and $\phi(r')$ is independent of $x_t$ we can uniquely define the functions $\kappa(.)$ and $\rho(.)$ such that
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \\
+   &=& \kappa \left( {{\phi ^T}\left( {r'} \right)} \right)\rho \left( {{x_t}} \right) 
+\end{eqnarray}
+Making substitutions we get
+\begin{equation}\label{Subs}
+{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( {{\phi ^T}\left( {r'} \right)} \right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
+\end{equation}
+now defining
+\begin{equation}\label{Def4}
+\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( {{\phi ^T}\left( {r'} \right)} \right)dr'}
+\end{equation}
+\begin{equation}\label{Sub2}
+{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
+\end{equation}
+cross multiply in integrate over $r'$
+\begin{equation}\label{CorssMultAndInt}
+\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+Now we define
+\begin{equation}\label{Def5}
+{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} 
+\end{equation}
+\begin{equation}\label{Def6}
+{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}
+\end{equation}
+Making substitutions
+\begin{equation}\label{Subs3}
+{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+Now we isolate the state by inverting $\Psi_x$
+\begin{equation}\label{IsolateState}
+{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+Gives the state-space model
+\begin{equation}\label{StateSpaceModel}
+{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
+\end{equation}
+
 \section{Stability Analysis}

### 2009-11-18 ltx/BrainIDE.tex
Made some general edits, commented out alternative model descriptions, and added identity (Eq12) the may sort out Parham's derivation of the state-space model

--- 2009-11-16 ltx/BrainIDE.tex
@@
 \section{Introduction}
-
 \IEEEPARstart{T}{he} human brain is arguably the world's most complex system.
@@
 This has led researchers to study different scales of dynamics: starting from individual proteins, synapses, and neurons; moving through to neuronal networks and ensembles of neuronal networks.
-Whilst our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
+While our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
 Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
@@
 To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at the meso/macroscopic scale.
-Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
+Mathematical neural field  models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
 These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} \cite{Schiff2009} that would be impossible to gain from experimental data alone.
@@
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to use a general neural field model, like the Wilson and Cohen~\cite{Wilson1973} or Jansen and Ritt model~\cite{Jansen1995}, and fit it to a patients EEG data.
-Fitting the general neural field models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
+A possible approach to achieve this would be to use a general neural field model, like the Wilson and Cohen~\cite{Wilson1973} model or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, and fit it to a patients EEG data.
+Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
 An estimation frame work for neural field model known as dynamical causal modeling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
+The interconnected brain regions are modeled by the Jansen and Ritt equations.
 The approach has proven very useful in understanding specific hierarchical networks of neural information processing.
-Another recent publication describing parameter estimation method with a neural field model used an unscented Kalman filter with the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
+Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
 This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
-Generating patient specific models allows that application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
+Generating patient specific models allows the application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
 Currently available epileptic seizure prediction and control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
@@
 Given access to an accurate model, the application of control theory in these circumstances would allow for robust therapeutic stimulations.
-The work from Schiff and Sauer~\cite{schiff2008kalman} successfully demonstrated  estimation of two parameters from the WC equations, whilst the other parameters were fixed.
+The work from Schiff and Sauer~\cite{schiff2008kalman} successfully demonstrated  it is possible to estimate parameters from the WC equations.
 This motivates the question, what parameters are the most important?
 How patient specific do the assumed parameters have to be for the model to be useful?
-In this paper we address both of these questions and provide a theoretical platform to perform patient specific grey-box modeling of the human neocortex.
+In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modeling of the human neocortex.
 
 \section{The Importance of Cortical Structure}
-
-The neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+Neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
 Each neural population represents a functional cortical processing unit referred to as a column.
@@
 
-Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure of the cortical columns, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, than we could model patient specific neurodynamics.
+Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture the essential patient specific neurodynamics that lead to various oscillatory states.
 Estimating functional cortical connectivity via EEG measures is currently a highly active area of research.
-There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG or fMRI times series.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}).
+There is a lot of interest in understanding the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG, or fMRI times series.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}.
 Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
-Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
+%Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
 
@@
 Recently, it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
-The key development in this work was to define the state-space model order independent of the number of observations (or ECoG recording electrodes in this case).
+The key development in this work was to define a state-space model with an order independent of the number of observations (or ECoG recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria.
-In this paper we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
+Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions (three in the paper) is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria (AIC or BIC).
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.
-
-Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
+%Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
 
 \section{Neural Field Model}
-In this section we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our connectivity estimator.
-This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behavior.
-It is also capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations.
-The general form of the model is described here.
-The post-synaptic potentials generated at a neuronal population $r$ by action potentials arriving from all other connected populations at position $r'$ can be described by
+In this section, we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
+This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behavior.
+It is also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations.
+The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
+The model relates the average number of action potentials $f$ arriving at $r$ to the local post synaptic membrane voltage.
+The post-synaptic potentials generated at a neuronal population at location $r$ by action potentials arriving from all other connected populations at locations $r'$ can be described by
 \begin{equation}\label{SpikesToPotential}
@@
 \end{equation}
-Equation~\ref{SpikesToPotential} relates, $f$, or the average number of action potentials arriving at $r$ to the post synaptic potential at $r$, to the local membrane voltage.
-The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity.
-The post-synaptic response kernel $h(t)$ is described by
+The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity. The post-synaptic response kernel $h(t)$ is described by
 \begin{equation}\label{SynapticRespKernel}
@@
 where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant.
-The synaptic response kernel can be more elaborate, using a rise and fall time constants, however this simple form serves our purposes.
+The synaptic response kernel can be more elaborate, using rise and fall time constants, however, this simple form serves our purposes.
 Nonlocal interactions between cortical populations are described by
@@
 \end{equation}
-where $\bar t = t - d\left| {r - r'} \right|$, $p$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, $\Omega$ is the spatial domain, representing a cortical sheet or surface and $d$ is the propagation delay from $r'$ to $r$.
+where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $p$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
 
-The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the Heaviside step function
-\begin{equation}\label{RateOfPreSynPops}
-p\left( {v\left( {r,\bar t} \right)} \right) = {\nu_0}u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
+The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
+\begin{equation}\label{ActivationFunction}
+p\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v_t}\left( {r'} \right)} \right)} \right)}}.
 \end{equation}
-\begin{equation}\label{HeavisideDef}
-u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
-   1 & {v\left( {r,\bar t} \right) \ge {v_0}\left( r \right)}  \\
-   0 & {otherwise}  \\
-\end{array}} \right.
-\end{equation}
+%\begin{equation}\label{RateOfPreSynPops}
+%p\left( {v\left( {r,\bar t} \right)} \right) = {\nu_0}u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
+%\end{equation}
+%\begin{equation}\label{HeavisideDef}
+%u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
+%   1 & {v\left( {r,\bar t} \right) \ge {v_0}\left( r \right)}  \\
+%   0 & {otherwise}  \\
+%\end{array}} \right.
+%\end{equation}
 Even though we will model  $v_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality when constructing the state-space representation in the next section.
-The parameters in equation~\ref{RateOfPreSynPops} are...
-$v_0$ is typically 6~mV, $\nu_0$ is 5~$s^{-1}$ (from Wendling and David papers).
+The parameters in equation~\ref{ActivationFunction} are detailed in Table 1.
 By combining equations~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
@@
 \end{equation}
-\subsection{Alternate Model Description I}
-An alternate and equivalent way to remove the temporal integration using the Laplace transform .
+%\subsection{Alternate Model Description I}
+%An alternate and equivalent way to remove the temporal integration using the Laplace transform .
 We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
-\begin{equation}\label{TwoDiscreteMasses}
-{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
-\end{equation}
-where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
-\begin{eqnarray}
-% \nonumber to remove numbering (before each equation)
-  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
-   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
-  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
-\end{eqnarray}
-Now taking the inverse Laplace transform we get
-\begin{equation}\label{InverseLaplace}
-\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
-\end{equation}
-Next we convert the model from discrete neural masses to a continuum by
-\begin{equation}\label{Discrete2Continuum}
-\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
-\end{equation}
-The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
-
-\subsection{Alternate Model Description II}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.4]{NeuralMassFigure.eps}
-\caption[NeuralMassModel]{This figure describes the basic interactions of neural masses that constitute the neural field model.}
-\label{NeuralMassModel}
-\end{figure*}
-
-An alternative description of the model is as follows.
+%\begin{equation}\label{TwoDiscreteMasses}
+%{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
+%\end{equation}
+%where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
+%\begin{eqnarray}
+%% \nonumber to remove numbering (before each equation)
+%  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
+%   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
+%  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
+%\end{eqnarray}
+%Now taking the inverse Laplace transform we get
+%\begin{equation}\label{InverseLaplace}
+%\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
+%\end{equation}
+%Next we convert the model from discrete neural masses to a continuum by
+%\begin{equation}\label{Discrete2Continuum}
+%\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
+%\end{equation}
+%
+%\subsection{Alternate Model Description II}
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.4]{NeuralMassFigure.eps}
+%\caption[NeuralMassModel]{This figure describes the basic interactions of neural masses that constitute the neural field model.}
+%\label{NeuralMassModel}
+%\end{figure*}
+%An alternative description of the model is as follows.
 The model can be thought of as a continuum of neural masses.
-To illustrate this idea we shall first describe the interaction of discrete neural masses as seen in Figure~\ref{NeuralMassModel}.
-Assuming post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
-\begin{equation}\label{VoltageFromPSPs}
-{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} u\left( {t - {t_k}} \right),
-\end{equation}
-where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $S$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
+To illustrate this idea, we shall first describe the interaction of discrete neural masses as seen in Figure~\ref{NeuralMassModel}.
+Assuming that post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
+%\begin{equation}\label{VoltageFromPSPs}
+%{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} u\left( {t - {t_k}} \right),
+%\end{equation}
+%where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $S$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
 Alternatively the membrane potential can described by the convolution of synaptic response kernel with the pre-synaptic firing rate $r_j(t)$ where
-\begin{equation}\label{VoltageFromRate}
-{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
-\end{equation}
-To convert the equation system into and integral differential system we shall take derivative of~\ref{EqVoltageFromPSPs} yielding
-\begin{eqnarray}
-% \nonumber to remove numbering (before each equation)
-  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}u\left( {t - {t_k}} \right) + {w_{ij}}u\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
-   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}u\left( {t - {t_k}} \right)\alpha_j{h_j}\left( t- {t_k} \right)}   \nonumber \\
-   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber  \\
-   &=& \sum\nolimits_j {{w_{ij}}{\nu_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber \\
-   &=& \sum\nolimits_j {{w_{ij}}p\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j}.
-\end{eqnarray}
-This form can easily be extended to represent a continuous field.
+%\begin{equation}\label{VoltageFromRate}
+%{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
+%\end{equation}
+%To convert the equation system into an integral differential system, we shall take derivative of~\ref{EqVoltageFromPSPs} yielding
+%\begin{eqnarray}
+%% \nonumber to remove numbering (before each equation)
+%  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}u\left( {t - {t_k}} \right) + {w_{ij}}u\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
+%   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}u\left( {t - {t_k}} \right)\alpha_j{h_j}\left( t- {t_k} \right)}   \nonumber \\
+%   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber  \\
+%   &=& \sum\nolimits_j {{w_{ij}}{\nu_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber \\
+%   &=& \sum\nolimits_j {{w_{ij}}p\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j}.
+%\end{eqnarray}
+%This form can easily be extended to represent a continuous field.
 
 \subsection{Assumptions and Simplifications}
-We assume the velocity of the action potentials is infinite.
-This is also a common assumption that is made when modeling intracortical circuits.
-As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being infinite.
+We assume that the propagation delay of action potentials is zero.
+This is a common assumption that is made when modeling intracortical circuits (\textcolor[rgb]{1.00,0.00,0.00}{refs}).
+As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being negligible.
 Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics~\cite{Atay2005}.
 The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences.
-Therefore, the model simply has to be 'good enough' for this purpose.
+Therefore, the model simply has to be `good enough' for this purpose.
 Starting with this simplified version of the general model is a logical choice.
-The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, and not on their spatial location.
-Again, this is a common assumption when dealing with intracortical connectivity.
+The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, not on their spatial location.
+Again, this is a common assumption when dealing with intracortical connectivity (\textcolor[rgb]{1.00,0.00,0.00}{ref}).
 This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible.
-The IDE estimation is derived for a general heterogeneous structure, however for clarity of results we shall only present the heterogeneous case.
+The IDE estimation is derived for a general heterogeneous structure however, for clarity of results we shall only present the heterogeneous case.
 We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population.
-In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity.
-This reduced the model to a single field.
-I am not sure how this will limit the dynamics??
-With these assumptions we have the model in the form
+In this case, inhibition can be modeled by having a negative response kernel and excitation with a positive response kernel, where the connectivity kernel provides the (scaled) polarity.
+This reduces the model to a single field.
+We will also assume the activation function $p(.)$ is a Heaviside step function.
+This is in agreement with the work of Schiff and Sauer~\cite{schiff2008kalman}.
+With these assumptions, the model has the form
 \begin{equation}\label{SimplifiedModel}
-\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)P\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
+\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)p\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
 \end{equation}
-
-\subsection{IDE Formulation}
-
-\begin{equation}\label{new_spatiotemporal_kernels}
-\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
-\end{equation}
-
-\begin{equation}\label{define_v_tilde}
-\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
-   0 & {otherwise}  \\
-\end{array}} \right.
-\end{equation}
-
-\begin{equation}\label{define_v_bar}
-\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
-   0 & {otherwise}  \\
-\end{array}} \right.
-\end{equation}
-
+In order to make the problem trackable, in terms of model order, we assume that we can decompose the field (membranes voltages) into a set of $n_\phi$ Gaussian basis functions.
+We will also assume that we know the location and width of the basis function that is required to decompose the field.
+The state of the system is the height basis functions, rather than the membrane potential.
+Therefore, the number of basis functions required to decompose the field is equal to the number of states.
+Also, we assume that we can represent the connectivity by a regular grid of three connectivity Gaussian basis functions (corresponding to short, mid and long range connectivity) of known width.
+The height of the connectivity basis functions ($\theta$ parameter) is to be estimated.
+%\subsection{IDE Formulation}
+%
+%For the state-space derivation, to create an estimator, the model can be reformulated like so
+%\begin{equation}\label{new_spatiotemporal_kernels}
+%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
+%\end{equation}
+%
+%\begin{equation}\label{define_v_tilde}
+%\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
+%   0 & {otherwise}  \\
+%\end{array}} \right.
+%\end{equation}
+%
+%\begin{equation}\label{define_v_bar}
+%\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
+%   0 & {otherwise}  \\
+%\end{array}} \right.
+%\end{equation}
+%
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.4]{ExampleFieldDecomposition.eps}
+%\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
+Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
+%\label{ExampleFieldDecomposition}
+%\end{figure*}
+%
 \section{State-Space Neural Field Model}
@@
 \begin{equation}
-\tilde v_t(\mathbf s)=\boldsymbol \phi^{\top}(\mathbf s)\tilde{\mathbf x}_t
+\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0 + \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
 \label{eq:cortexfieldgv0}
@@
 
+\subsection{State-Space Neural Field Model}
+In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
+The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
+We begin with the model in the form
+\begin{eqnarray}\label{InitialModel}
+% \nonumber to remove numbering (before each equation)
+  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon \left( {r,t} \right) \nonumber \\
+   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon \left( {r,t} \right).
+\end{eqnarray}
+Next we defining the basis functions the decompositions of the field and connectivity kernel, where $\phi(s)$ is a vector is Gaussian basis functions, $x_t$ is the state, $\psi(r-r')$ is a vector of three connectivity basis functions and $\theta$ is the corresponding weight of the connectivity
+\begin{equation}\label{FieldDecomp}
+   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
+\end{equation}
+\begin{equation}\label{KernelDecomp}
+k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right).
+\end{equation}
+Assume we know $\phi(r')$ and it is constant, and the form of the activation function $p(.)$ is known, and $\phi(r')$ is independent of $x_t$, then we can uniquely define the function $\rho(.)$ such that
+\begin{eqnarray}\label{NonlinearState}
+% \nonumber to remove numbering (before each equation)
+  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \nonumber \\
+   &=& \phi ^T\left(r'\right)\rho \left( {{x_t}} \right).
+\end{eqnarray}
+Making substitutions of~\ref{FieldDecomp}, \ref{KernelDecomp} and \ref{NonlinearState} into \ref{InitialModel} we get
+\begin{equation}\label{ModelDecomposed}
+{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'}\right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
+\end{equation}
+Now we define
+\begin{equation}\label{DefPhi}
+\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'} \right)dr'}.
+\end{equation}
+Substituting~\ref{DefPhi} into \ref{ModelDecomposed} we get
+\begin{equation}\label{Sub2}
+{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right).
+\end{equation}
+Cross multiplying by $\phi(r)$ in integrating over $r$ gives
+\begin{equation}\label{CorssMultAndInt}
+\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+\end{equation}
+Now we define
+\begin{equation}\label{DefPsix}
+{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr}
+\end{equation}
+\begin{equation}\label{DefPsitheta}
+{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}.
+\end{equation}
+Substituting~\ref{DefPsix} and \ref{DefPsitheta} into \ref{CorssMultAndInt} we get 
+\begin{equation}\label{Subs3}
+{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+\end{equation}
+Now we isolate the state by inverting $\Psi_x$
+\begin{equation}\label{IsolateState}
+{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+\end{equation}
+This gives the state-space model
+\begin{equation}\label{StateSpaceModel}
+{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+\end{equation}
+
 \section{Stability Analysis}
-Using the analytically calculated basis functions. Need to show that the linearized model will not blow up.
+This section will not probably be included
 
 \section{Estimation of the IDE Neural Field Model}
-Based on the other papers.
+Based on the other papers. Although it appears to be a job for a nonlinear versions of the Kalman filter.
 
 \section{Comparison of Estimated and True Connectivity}
-Try and estimate the linear and nonlinear model based on the linear estimator. Might work ok?
-
-\subsection{Linear Model}
-
-\subsection{Nonlinear Model}
 

### 2009-11-18 ltx/BrainIDE.tex
added yet another SS derivation. I made an error with previous derivation where I separated a spatial and time variable incorrectly

@@
 
-\author{Dean~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
+\author{Dean~R.~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
         Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
@@
         Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
-        and Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
+        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
+        David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
+        Anthony~N.~Burkitt,~\IEEEmembership{Member,~IEEE,}
         and~other~Bosses/Supervisors,~\IEEEmembership{Member,~IEEE.}% <-this % stops a space% <-this % stops a space
@@
 The height of the connectivity basis functions ($\theta$ parameter) is to be estimated.
-%\subsection{IDE Formulation}
-%
-%For the state-space derivation, to create an estimator, the model can be reformulated like so
-%\begin{equation}\label{new_spatiotemporal_kernels}
-%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
-%\end{equation}
-%
-%\begin{equation}\label{define_v_tilde}
-%\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
-%
-%\begin{equation}\label{define_v_bar}
-%\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
-%
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.4]{ExampleFieldDecomposition.eps}
-%\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
+\subsection{IDE Formulation}
+For the state-space derivation, to create an estimator, the model can be reformulated like so
+\begin{equation}\label{new_spatiotemporal_kernels}
+\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
+\end{equation}
+\begin{equation}\label{define_v_tilde}
+\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
+   0 & {otherwise}  \\
+\end{array}} \right.
+\end{equation}
+\begin{equation}\label{define_v_bar}
+\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
+   0 & {otherwise}  \\
+\end{array}} \right.
+\end{equation}
+\begin{figure*}
+\centering
+\includegraphics[scale=0.3]{ExampleFieldDecomposition.eps}
+\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
 Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
-%\label{ExampleFieldDecomposition}
-%\end{figure*}
-%
+\label{ExampleFieldDecomposition}
+\end{figure*}
+
 \section{State-Space Neural Field Model}
@@
 \begin{equation}
- v_{t+1}(\mathbf s)=\int_{\mathcal S} \alpha \delta(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d \mathbf r+\int_{\mathcal S} w(\mathbf s -\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+e_t(\mathbf s)
+ v_{t+1}(\mathbf r)=\int_{\Omega} \alpha \delta(\mathbf r-\mathbf r')\bar v_t(\mathbf r)d \mathbf r'+\int_{\Omega} w(\mathbf r -\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+e_t(\mathbf r)
 \label{eq:cortexfield}
@@
 \begin{equation}
-\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0 + \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
+\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0
 \label{eq:cortexfieldgv0}
@@
 \begin{equation}
- \boldsymbol \phi^{\top}(\mathbf s)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf s)\tilde{\mathbf x}_{t+1}=
-\int_\mathcal{S}\alpha\delta(\mathbf s- \mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r+\int_\mathcal{S}\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\tilde{\mathbf x}_td\mathbf r+e_t(\mathbf s)
+ \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t+1}=
+\int_\Omega\alpha\delta(\mathbf r- \mathbf r')\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r'+\int_\Omega\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
 \label{eq:decomposedcortexfield}
@@
 \begin{equation}
- \boldsymbol \phi^{\top}(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf s)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\mathcal S}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\tilde{\mathbf x}_td\mathbf r+e_t(\mathbf s)
+ \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
 \end{equation}
@@
 \begin{equation}
- \boldsymbol\Phi(\mathbf s)=\int_{\mathcal S}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
+ \boldsymbol\Phi(\mathbf r)=\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')d\mathbf r'
 \label{eq:convolution}
@@
 \begin{equation}
- \boldsymbol \phi^{\top}(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf s)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)\tilde{\mathbf x}_t+e_t(\mathbf s)
+ \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)\tilde{\mathbf x}_t+e_t(\mathbf r)
 \label{eq:cortexfieldwithPhi}
 \end{equation}
-Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf s) $, and integrating over $\mathbf s$
+Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf r) $, and integrating over $\mathbf r$
 \begin{equation}
-\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s \bar{\mathbf x}_{t}+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s\tilde{\mathbf x}_t+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf r \bar{\mathbf x}_{t}+\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
 \label{eq:cortexfieldversion2}
@@
 \begin{equation}
- \boldsymbol\Psi_x(\mathbf s)=\int_{\mathcal S}\boldsymbol\phi(\mathbf s)\boldsymbol\phi^{\top}(\mathbf s)d\mathbf s
+ \boldsymbol\Psi_x(\mathbf r)=\int_{\Omega}\boldsymbol\phi(\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
 \label{eq:psix}
@@
 \begin{equation}
-  \boldsymbol\Psi_{\theta}(\mathbf s)=\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s
+  \boldsymbol\Psi_{\theta}(\mathbf r)=\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r
 \label{eq:psitheta}
@@
 \begin{equation}
-\boldsymbol\Psi_x(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf s) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf s)\tilde{\mathbf x}_t+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\boldsymbol\Psi_x(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf r) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf r)\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
 \end{equation}
@@
 \begin{equation}
-\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
 \end{equation}
@@
 \begin{eqnarray}
- \mathbf y_t(\mathbf s)&=&\\
-&=&\int_{\mathcal S}H(\mathbf s-\mathbf r)v_t(\mathbf r)d\mathbf r+\boldsymbol\epsilon_t \\
-&=&\int_{\mathcal S}H(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d\mathbf r+\int_{\mathcal S}H(\mathbf s-\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+\epsilon_t
+ \mathbf y_t(\mathbf r)&=&\\
+&=&\int_{\Omega}H(\mathbf r-\mathbf r')v_t(\mathbf r')d\mathbf r'+\boldsymbol\epsilon_t \\
+&=&\int_{\Omega}H(\mathbf r-\mathbf r')\bar v_t(\mathbf r')d\mathbf r'+\int_{\Omega}H(\mathbf r-\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+\epsilon_t
 \label{eq:observationequation}
@@
 
- we decompose $ H(\mathbf s-\mathbf r)$ as
+ we decompose $ H(\mathbf r-\mathbf r')$ as
  \begin{equation}
-  H(\mathbf s-\mathbf r)= \mathbf c^{\top}\mu(\mathbf s-\mathbf r)
+  H(\mathbf r-\mathbf r')= \mathbf c^{\top}\mu(\mathbf r-\mathbf r')
 \label{eq:decomposedobservationkernel}
@@
 \begin{equation}
- \mathbf y_t(\mathbf s)=\int_{\mathcal S}\mathbf c^{\top}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}d\mathbf r+\int_{\mathcal S}\mathbf c^{\top}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t}d\mathbf r+\epsilon_t
+ \mathbf y_t(\mathbf r)=\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\bar{\mathbf x}_{t}d\mathbf r'+\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\tilde{\mathbf x}_{t}d\mathbf r'+\epsilon_t
 \end{equation}
@@
 \begin{equation}
-\mathbf y_t(\mathbf s)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf s)&\mathbf c^{\top}\mathbf M(\mathbf s)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
+\mathbf y_t(\mathbf r)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf r)&\mathbf c^{\top}\mathbf M(\mathbf r)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
 \end{equation}
@@
 \begin{equation}
- \mathbf M(\mathbf s)=\int_{\mathcal S}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)d\mathbf r
+ \mathbf M(\mathbf r)=\int_{\Omega}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')d\mathbf r'
 \end{equation}
@@
 
-\subsection{State-Space Neural Field Model}
-In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
+%\subsection{State-Space Neural Field Model}
+%In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
 The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
 We begin with the model in the form
-\begin{eqnarray}\label{InitialModel}
-% \nonumber to remove numbering (before each equation)
-  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon \left( {r,t} \right) \nonumber \\
-   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon \left( {r,t} \right).
-\end{eqnarray}
-Next we defining the basis functions the decompositions of the field and connectivity kernel, where $\phi(s)$ is a vector is Gaussian basis functions, $x_t$ is the state, $\psi(r-r')$ is a vector of three connectivity basis functions and $\theta$ is the corresponding weight of the connectivity
-\begin{equation}\label{FieldDecomp}
-   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
+%\begin{eqnarray}\label{InitialModel}
+%% \nonumber to remove numbering (before each equation)
+%  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon_t \left( {r} \right) \nonumber \\
+%   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon_t \left( {r} \right).
+%\end{eqnarray}
+%Next we defining the basis functions the decompositions of the field and connectivity kernel, where $\phi(s)$ is a vector is Gaussian basis functions, $x_t$ is the state, $\psi(r-r')$ is a vector of three connectivity basis functions and $\theta$ is the corresponding weight of the connectivity
+%\begin{equation}\label{FieldDecomp}
+%   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
+%\end{equation}
+%\begin{equation}\label{KernelDecomp}
+%k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right).
+%\end{equation}
+%Assume we know $\phi(r')$ and it is constant, and the form of the activation function $p(.)$ is known, and $\phi(r')$ is independent of $x_t$, then we can uniquely define the function $\rho(.)$ such that
+%\begin{eqnarray}\label{NonlinearState}
+%% \nonumber to remove numbering (before each equation)
+%  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \nonumber \\
+%   &=& \phi ^T\left(r'\right)\rho \left( {{x_t}} \right).
+%\end{eqnarray}
+%Making substitutions of~\ref{FieldDecomp}, \ref{KernelDecomp} and \ref{NonlinearState} into \ref{InitialModel} we get
+%\begin{equation}\label{ModelDecomposed}
+%{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'}\right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon_t \left( {r} \right)
+%\end{equation}
+%Now we define
+%\begin{equation}\label{DefPhi}
+%\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'} \right)dr'}.
+%\end{equation}
+%Substituting~\ref{DefPhi} into \ref{ModelDecomposed} we get
+%\begin{equation}\label{Sub2}
+%{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon_t \left( {r} \right).
+%\end{equation}
+%Cross multiplying by $\phi(r)$ in integrating over $r$ gives
+%\begin{equation}\label{CorssMultAndInt}
+%\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
+%\end{equation}
+%Now we define
+%\begin{equation}\label{DefPsix}
+%{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr}
+%\end{equation}
+%\begin{equation}\label{DefPsitheta}
+%{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}.
+%\end{equation}
+%Substituting~\ref{DefPsix} and \ref{DefPsitheta} into \ref{CorssMultAndInt} we get
+%\begin{equation}\label{Subs3}
+%{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
+%\end{equation}
+%Now we isolate the state by inverting $\Psi_x$
+%\begin{equation}\label{IsolateState}
+%{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
+%\end{equation}
+%This gives the state-space model
+%\begin{equation}\label{StateSpaceModel}
+%{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
+%\end{equation}
+
+\section{State-Space Model}
+If we are going to use a particle filter or a extended Kalman filter we might as well go for this case.
+If the temporal and spatial part of the nonlinearity can not be separated, than this is the best choice.
+\begin{equation}\label{SystemEq}
+{v_{t + 1}}\left( {\bf{r}} \right) = \int_\Omega  {w\left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + {\varepsilon _t}\left( {\bf{r}} \right)
 \end{equation}
-\begin{equation}\label{KernelDecomp}
-k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right).
+Defining
+\begin{equation}\label{CombiningKernels}
+k\left( {{\bf{r}} - {\bf{r'}}} \right) = w\left( {{\bf{r}} - {\bf{r'}}} \right) - \hat{\alpha}\delta \left( {{\bf{r}} - {\bf{r'}}} \right).
 \end{equation}
-Assume we know $\phi(r')$ and it is constant, and the form of the activation function $p(.)$ is known, and $\phi(r')$ is independent of $x_t$, then we can uniquely define the function $\rho(.)$ such that
-\begin{eqnarray}\label{NonlinearState}
-% \nonumber to remove numbering (before each equation)
-  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \nonumber \\
-   &=& \phi ^T\left(r'\right)\rho \left( {{x_t}} \right).
-\end{eqnarray}
-Making substitutions of~\ref{FieldDecomp}, \ref{KernelDecomp} and \ref{NonlinearState} into \ref{InitialModel} we get
-\begin{equation}\label{ModelDecomposed}
-{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'}\right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
+Making substitution we get
+\begin{equation}\label{OneKernelModel}
+{v_{t + 1}}\left( {\bf{r}} \right) = \int_\Omega  {k\left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  + {\varepsilon _t}\left( {\bf{r}} \right).
 \end{equation}
-Now we define
-\begin{equation}\label{DefPhi}
-\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'} \right)dr'}.
+Defining
+\begin{equation}\label{DefFieldDecomp}
+{v_t}\left( {\bf{r}} \right) = {\phi ^T}\left( {\bf{r}} \right){x_t}
 \end{equation}
-Substituting~\ref{DefPhi} into \ref{ModelDecomposed} we get
-\begin{equation}\label{Sub2}
-{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right).
+\begin{equation}\label{DefKernelDecomp}
+k\left( {{\bf{r}} - {\bf{r'}}} \right) = {\theta ^T}\psi \left( {{\bf{r}} - {\bf{r'}}} \right)
 \end{equation}
-Cross multiplying by $\phi(r)$ in integrating over $r$ gives
-\begin{equation}\label{CorssMultAndInt}
-\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+Now we have four basis functions (the fourth being the delta/local connectivity) and four parameters to estimate. Making substitutions
+\begin{equation}\label{DecompModel}
+{\phi ^T}\left( {\bf{r}} \right){x_t} = {\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}}  + {\varepsilon _t}\left( {\bf{r}} \right)
 \end{equation}
-Now we define
-\begin{equation}\label{DefPsix}
-{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr}
+Cross multiply and integrate over $\bf{r}$
+\begin{equation}\label{Poo}
+\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_t}}  = \int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + \int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
 \end{equation}
-\begin{equation}\label{DefPsitheta}
-{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}.
+Defining
+\begin{equation}\label{DefPsi}
+\Psi  = \int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}}
 \end{equation}
-Substituting~\ref{DefPsix} and \ref{DefPsitheta} into \ref{CorssMultAndInt} we get 
-\begin{equation}\label{Subs3}
-{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+Making substitution
+\begin{equation}\label{SS Model}
+{x_t} = {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
 \end{equation}
-Now we isolate the state by inverting $\Psi_x$
-\begin{equation}\label{IsolateState}
-{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
-\end{equation}
-This gives the state-space model
-\begin{equation}\label{StateSpaceModel}
-{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
+\begin{equation}\label{AbbrevSSModel}
+{x_{t + 1}} = f\left( {x;\theta } \right) + {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
 \end{equation}
@@
 
-\begin{IEEEbiography}{Dean Freestone}
+\begin{IEEEbiography}{Dean R. Freestone}
 Biography text here.

### 2009-11-19 ltx/BrainIDE.tex
general edits
Alternative model- Unlimited function for mean pulse rate

@@
 \end{equation}
-\begin{figure*}
-\centering
-\includegraphics[scale=0.3]{ExampleFieldDecomposition.eps}
-\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.3]{ExampleFieldDecomposition.eps}
+% \caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
 Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
-\label{ExampleFieldDecomposition}
-\end{figure*}
+% \label{ExampleFieldDecomposition}
+% \end{figure*}
 
@@
 \end{equation}
-Now we have four basis functions (the fourth being the delta/local connectivity) and four parameters to estimate. Making substitutions
+Now we have four basis functions (the fourth being the delta/local connectivity) and four parameters to estimate.
+Each connectivity basis function is equivalent to a layer in the WC model.
+Making substitutions
 \begin{equation}\label{DecompModel}
-{\phi ^T}\left( {\bf{r}} \right){x_t} = {\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}}  + {\varepsilon _t}\left( {\bf{r}} \right)
+{\phi ^T}\left( {\bf{r}} \right){x_{t+1}} = {\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}}  + {\varepsilon _t}\left( {\bf{r}} \right)
 \end{equation}
@@
 \begin{equation}\label{Poo}
-\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_t}}  = \int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + \int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
+\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = \int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + \int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
 \end{equation}
@@
 \begin{equation}\label{SS Model}
-{x_t} = {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
+{x_{t+1}} = {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
 \end{equation}
@@
 \end{equation}
+\section{Alternative model-Unlimited function for $p(v_t(r))$}
+We assume
+\begin{equation}
+ p(v_t(r))=\beta(v_t(\mathbf r)-v_0))=\beta v'_t(\mathbf r)
+\end{equation}
+adding $-v_0$ to the both side of the equation we have
+\begin{equation}
+ v_{t+1}(\mathbf s)-v_0=\beta\int_{\Omega} W(\mathbf s-\mathbf r) v'_t(\mathbf r)d\mathbf r-\frac{1}{\tau} v_t(\mathbf s)-v_0+e_t(\mathbf s)
+\end{equation}
+we add $\frac{1}{\tau}v_0-\frac{1}{\tau}v_0$ to the right side of the equation
+\begin{equation}
+ v'_{t+1}(\mathbf s)=\beta\int_{\Omega} W(\mathbf s-\mathbf r) v'_t(\mathbf r)d\mathbf r-\frac{1}{\tau} v'_t(\mathbf s)-(1+\frac{1}{\tau})v_0+e_t(\mathbf s)
+\end{equation}
 
+\begin{equation}
+ v'_t(\mathbf s)=\boldsymbol \phi^{\top}(\mathbf s){\mathbf x}_t
+\end{equation}
+\begin{equation}
+ w(\mathbf s -\mathbf r)=\boldsymbol \theta^{\top}\psi(\mathbf s -\mathbf r)
+\end{equation}
+\begin{equation}
+\boldsymbol \phi^{\top}(\mathbf s){\mathbf x}_{t+1}=\beta\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)\mathbf x_t-\frac{1}{\tau×}\boldsymbol \phi^{\top}(\mathbf s){\mathbf x}_t-(1+\frac{1}{\tau})v_0+e_t(\mathbf s)
+\end{equation}
+where
+\begin{equation}
+ \boldsymbol\Phi(\mathbf s)=\int_\Omega \psi(\mathbf s -\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf r
+\end{equation}
+Cross multiplying by $\phi(s)$ and integrating over $\mathbf s$ gives
+\begin{equation}
+\int_{\Omega}\boldsymbol \phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s{\mathbf x}_{t+1}=\beta\int_{\Omega}\boldsymbol \phi(\mathbf s) \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s\mathbf x_t-\frac{1}{\tau×}\int_{\Omega}\boldsymbol \phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s{\mathbf x}_t-(1+\frac{1}{\tau})v_0\int_{\Omega}\boldsymbol \phi(\mathbf s)d\mathbf s+\int_{\Omega}\boldsymbol \phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\end{equation}
+we define
+\begin{equation}
+ \boldsymbol\psi(\mathbf s)=\int_{\Omega}\boldsymbol \phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s
+\end{equation}
+and
+\begin{equation}
+ \Gamma(\mathbf s)=\int_{\Omega}\boldsymbol \phi(\mathbf s) \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s
+\end{equation}
+therefore
+\begin{equation}
+\boldsymbol\psi(\mathbf s){\mathbf x}_{t+1}=\beta\Gamma(\mathbf s)\mathbf x_t-\frac{1}{\tau×}\boldsymbol\psi(\mathbf s){\mathbf x}_t-(1+\frac{1}{\tau})v_0\int_{\Omega}\boldsymbol \phi(\mathbf s)d\mathbf s+\int_{\Omega}\boldsymbol \phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\end{equation}
+Multiplying by $\psi(\mathbf s)^{-1}$
+\begin{equation}
+ {\mathbf x}_{t+1}=\beta\psi(\mathbf s)^{-1}\Gamma(\mathbf s)\mathbf x_t-\frac{1}{\tau×}{\mathbf x}_t-(1+\frac{1}{\tau})v_0\psi(\mathbf s)^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf s)d\mathbf s+\psi(\mathbf s)^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\end{equation}
+therefore
+\begin{equation}
+ {\mathbf x}_{t+1}=(\beta\psi(\mathbf s)^{-1}\Gamma(\mathbf s)-\frac{1}{\tau×}\mathbf I){\mathbf x}_t-\frac{1}{\tau×}{\mathbf x}_t-(1+\frac{1}{\tau})v_0\psi(\mathbf s)^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf s)d\mathbf s+\psi(\mathbf s)^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\end{equation}
+\begin{equation}
+ {\mathbf x}_{t+1}=\mathbf A(\boldsymbol\theta){\mathbf x}_t-(1+\frac{1}{\tau})v_0\psi(\mathbf s)^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf s)d\mathbf s+\psi(\mathbf s)^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf s)e_t(\mathbf s)d\mathbf s
+\end{equation}
+where
+\begin{equation}
+\mathbf A(\boldsymbol\theta)=(\beta\psi(\mathbf s)^{-1}\Gamma(\mathbf s)-\frac{1}{\tau×}\mathbf I)
+\end{equation}
 \section{Stability Analysis}

### 2009-12-01 ltx/BrainIDE.tex
I'm not sure what this is ... make made me write this

--- 2009-11-18 ltx/BrainIDE.tex
@@
 \section{Introduction}
+
 \IEEEPARstart{T}{he} human brain is arguably the world's most complex system.
@@
 This has led researchers to study different scales of dynamics: starting from individual proteins, synapses, and neurons; moving through to neuronal networks and ensembles of neuronal networks.
-While our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
+Whilst our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
 Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
@@
 To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at the meso/macroscopic scale.
-Mathematical neural field  models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
+Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
 These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} \cite{Schiff2009} that would be impossible to gain from experimental data alone.
@@
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to use a general neural field model, like the Wilson and Cohen~\cite{Wilson1973} model or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, and fit it to a patients EEG data.
-Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
+A possible approach to achieve this would be to use a general neural field model, like the Wilson and Cohen~\cite{Wilson1973} or Jansen and Ritt model~\cite{Jansen1995}, and fit it to a patients EEG data.
+Fitting the general neural field models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
 An estimation frame work for neural field model known as dynamical causal modeling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
-The interconnected brain regions are modeled by the Jansen and Ritt equations.
 The approach has proven very useful in understanding specific hierarchical networks of neural information processing.
-Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
+Another recent publication describing parameter estimation method with a neural field model used an unscented Kalman filter with the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
 This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
-Generating patient specific models allows the application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
+Generating patient specific models allows that application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
 Currently available epileptic seizure prediction and control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
@@
 Given access to an accurate model, the application of control theory in these circumstances would allow for robust therapeutic stimulations.
-The work from Schiff and Sauer~\cite{schiff2008kalman} successfully demonstrated  it is possible to estimate parameters from the WC equations.
+The work from Schiff and Sauer~\cite{schiff2008kalman} successfully demonstrated  estimation of two parameters from the WC equations, whilst the other parameters were fixed.
 This motivates the question, what parameters are the most important?
 How patient specific do the assumed parameters have to be for the model to be useful?
-In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modeling of the human neocortex.
+In this paper we address both of these questions and provide a theoretical platform to perform patient specific grey-box modeling of the human neocortex.
 
 \section{The Importance of Cortical Structure}
-Neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+
+The neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
 Each neural population represents a functional cortical processing unit referred to as a column.
@@
 
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture the essential patient specific neurodynamics that lead to various oscillatory states.
+Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure of the cortical columns, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, than we could model patient specific neurodynamics.
 Estimating functional cortical connectivity via EEG measures is currently a highly active area of research.
-There is a lot of interest in understanding the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG, or fMRI times series.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}.
+There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG or fMRI times series.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}).
 Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
-%Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
+Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
 
@@
 Recently, it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
-The key development in this work was to define a state-space model with an order independent of the number of observations (or ECoG recording electrodes in this case).
+The key development in this work was to define the state-space model order independent of the number of observations (or ECoG recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions (three in the paper) is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria (AIC or BIC).
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
+Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria.
+In this paper we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.
-%Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
+
+Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
 
 \section{Neural Field Model}
-In this section, we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
-This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behavior.
-It is also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations.
-The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
-The model relates the average number of action potentials $f$ arriving at $r$ to the local post synaptic membrane voltage.
-The post-synaptic potentials generated at a neuronal population at location $r$ by action potentials arriving from all other connected populations at locations $r'$ can be described by
-\begin{equation}\label{SpikesToPotential}
-v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)f\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
+In this section we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our connectivity estimator.
+This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behavior.
+It is also capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations.
+The general form of the model is described here.
+The post-synaptic potentials generated at a neuronal population $s$ by action potentials arriving from all other connected populations at position $r$ can be described by
+\begin{equation}\label{Eq1}
+v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {s,t'} \right)dt'}.
 \end{equation}
-The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity. The post-synaptic response kernel $h(t)$ is described by
-\begin{equation}\label{SynapticRespKernel}
+The post-synaptic response kernel $h(t)$ is described by
+\begin{equation}\label{Eq2}
 h(t) = \left\{ {\begin{array}{*{20}{c}}
-   {\exp ( - \alpha t)} & {t \ge 0}  \\
+   {\exp ( - {t \mathord{\left/
+ {\vphantom {t \tau }} \right.
+ \kern-\nulldelimiterspace} \tau })} & {t \ge 0}  \\
    0 & {t < 0}  \\
-\end{array}} \right.
+\end{array}} \right.,
 \end{equation}
-where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant.
-The synaptic response kernel can be more elaborate, using rise and fall time constants, however, this simple form serves our purposes.
+where $\tau$ is the synaptic time constant and typically has values from 10-20~ms (\textcolor[rgb]{1.00,0.00,0.00}{refs}).
+The synaptic response kernel can be more elaborate, using a rise and fall time constant, however this simple form serves our purposes.
+Equation~\ref{Eq1} relates average firing rate of a presynaptic neural population to the mean membrane potential of the post-synaptic neurons.
+The mean firing rate, $J$, is convolved with the response kernel to give membrane potential since the firing rate is assumed to follow a (homogeneous?) Poisson process.
 Nonlocal interactions between cortical populations are described by
-\begin{equation}\label{RateBasedInteractions}
-f\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}
+\begin{equation}\label{Eq3}
+J\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right)
 \end{equation}
-where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $p$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+where $\bar t = t - \frac{{\left| {s - r} \right|}}{d}$, $P$ is a mean pulse rate of population at $y$, $W$ is the connectivity kernel, $E$ is an external input, $\Omega$ is the spatial domain and $d$ is the propagation velocity from $r$ to $s$.
 
-The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
-\begin{equation}\label{ActivationFunction}
-p\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v_t}\left( {r'} \right)} \right)} \right)}}.
+The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the sigmoid function
+\begin{equation}\label{Eq4}
+P\left( {v\left( {r,\bar t} \right)} \right) = {R_0}{\left( {1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - v\left( {r,\bar t} \right)} \right)} \right)} \right)^{ - 1}}.
 \end{equation}
-%\begin{equation}\label{RateOfPreSynPops}
-%p\left( {v\left( {r,\bar t} \right)} \right) = {\nu_0}u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
-%\end{equation}
-%\begin{equation}\label{HeavisideDef}
-%u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   1 & {v\left( {r,\bar t} \right) \ge {v_0}\left( r \right)}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
-Even though we will model  $v_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality when constructing the state-space representation in the next section.
-The parameters in equation~\ref{ActivationFunction} are detailed in Table 1.
-By combining equations~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
-\begin{equation}\label{FullDoubleIntModel}
-v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)p\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
+Even though $v_0$ is a constant, we show express it as a field allowing for inhomogeneities and for clarity in constructing the state-space representation in the next section.
+The parameters in equation~\ref{Eq4} are...
+$v_0$ is typically 6~mV, $R_0$ is 5~$s^{-1}$ and $\beta$ is 0.56~mV$^{-1}$ (from Wendling and David papers).
+By combining equations~\ref{Eq1} and \ref{Eq3} we get the spatiotemporal model
+\begin{equation}\label{Eq5}
+v\left(s,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega \left[ h\left(t - t'\right)W\left(s,r\right)P\left( v\left( r,\bar t \right)\right)+E\left(s,t'\right)\right] dr dt'
 \end{equation}
 To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
-\begin{equation}\label{GreensFuncDef}
+\begin{equation}\label{Eq6}
 Lh\left( t \right) = \delta \left( t \right),
@@
 where $L$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
-\begin{equation}\label{GenForm}
-L\left( {\frac{\partial }{{dt}}} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {r,t} \right),
+\begin{equation}\label{Eq7}
+L\left( {\frac{\partial }{{dt}}} \right)v\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right),
 \end{equation}
-where $L$ is a polynomial of order $n$ with constant coefficients that provides an $n^{th}$ order model.
+where $L$ is a polynomial of order $n$ with constant coefficients.
+This provides an $n^{th}$ order model.
 Most studies considering this model use first or second order time derivatives.
 We shall use the first order model giving
-\begin{equation}\label{FinalForm1}
-\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  +e\left( {r,t} \right).
+\begin{equation}\label{Eq8}
+\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{{v\left( {s,t} \right)}}{\tau } = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
 \end{equation}
-%\subsection{Alternate Model Description I}
-%An alternate and equivalent way to remove the temporal integration using the Laplace transform .
-We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
-%\begin{equation}\label{TwoDiscreteMasses}
-%{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
-%\end{equation}
-%where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
-%\begin{eqnarray}
-%% \nonumber to remove numbering (before each equation)
-%  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
-%   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
-%  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
-%\end{eqnarray}
-%Now taking the inverse Laplace transform we get
-%\begin{equation}\label{InverseLaplace}
-%\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
-%\end{equation}
-%Next we convert the model from discrete neural masses to a continuum by
-%\begin{equation}\label{Discrete2Continuum}
-%\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
-%\end{equation}
-%
-%\subsection{Alternate Model Description II}
+The neural field model can be represented as a discrete-time stochastic IDE by
+\begin{equation}\label{Eq9}
+{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {{v_{\bar t}}\left( r \right)} \right)dr}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right),
+\end{equation}
+where $\epsilon(t)$ is the discrete time stochastic input.
+The IDE representation of equation~\ref{Eq9} is discrete in time and continuous in space.
+The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
+
+\subsection{Alternate model description}
+
 %\begin{figure*}
@@
 %\includegraphics[scale=0.4]{NeuralMassFigure.eps}
-%\caption[NeuralMassModel]{This figure describes the basic interactions of neural masses that constitute the neural field model.}
+%\caption[NeuralMassModel]{This figure describes the basic interactions of %neural masses that constitute the neural field model.}
 %\label{NeuralMassModel}
 %\end{figure*}
-%An alternative description of the model is as follows.
+
+An alternative description of the model is as follows.
 The model can be thought of as a continuum of neural masses.
-To illustrate this idea, we shall first describe the interaction of discrete neural masses as seen in Figure~\ref{NeuralMassModel}.
-Assuming that post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
-%\begin{equation}\label{VoltageFromPSPs}
-%{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} u\left( {t - {t_k}} \right),
-%\end{equation}
-%where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $S$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
+To illustrate this idea we shall first describe the interaction of discrete neural masses as seen in Figure~\ref{NeuralMassModel}.
+Assuming post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
+\begin{equation}\label{Eq1.1}
+{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} H\left( {t - {t_k}} \right),
+\end{equation}
+where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $H$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
 Alternatively the membrane potential can described by the convolution of synaptic response kernel with the pre-synaptic firing rate $r_j(t)$ where
-%\begin{equation}\label{VoltageFromRate}
-%{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
-%\end{equation}
-%To convert the equation system into an integral differential system, we shall take derivative of~\ref{EqVoltageFromPSPs} yielding
-%\begin{eqnarray}
-%% \nonumber to remove numbering (before each equation)
-%  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}u\left( {t - {t_k}} \right) + {w_{ij}}u\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
-%   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}u\left( {t - {t_k}} \right)\alpha_j{h_j}\left( t- {t_k} \right)}   \nonumber \\
-%   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber  \\
-%   &=& \sum\nolimits_j {{w_{ij}}{\nu_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber \\
-%   &=& \sum\nolimits_j {{w_{ij}}p\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j}.
-%\end{eqnarray}
-%This form can easily be extended to represent a continuous field.
+\begin{equation}\label{1.2}
+{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
+\end{equation}
+To convert the equation system into and integral differential system we shall take derivative of~\ref{Eq1.1} yielding
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}H\left( {t - {t_k}} \right) + {w_{ij}}H\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}H\left( {t - {t_k}} \right)\frac{1}{{{\tau _j}}}{h_j}\left( t- {t_k} \right)}   \nonumber \\
+   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber  \\
+   &=& \sum\nolimits_j {{w_{ij}}{r_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}} \nonumber \\
+   &=& \sum\nolimits_j {{w_{ij}}P\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\frac{1}{{{\tau _j}}}}.
+\end{eqnarray}
+This form can easily be extended to represent a continuous field.
 
 \subsection{Assumptions and Simplifications}
-We assume that the propagation delay of action potentials is zero.
-This is a common assumption that is made when modeling intracortical circuits (\textcolor[rgb]{1.00,0.00,0.00}{refs}).
-As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being negligible.
-Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics~\cite{Atay2005}.
+We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population.
+In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity.
+This reduced the model to a single field.
+I am not sure how this will limit the dynamics??
+We will also assume the velocity of the action potentials is infinite.
+This is also a common assumption that is made when modeling intracortical circuits.
+As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being infinite.
+Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics (Coombes paper, and Atay paper).
 The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences.
-Therefore, the model simply has to be `good enough' for this purpose.
+Therefore, the model simply has to be 'good enough' for this purpose.
 Starting with this simplified version of the general model is a logical choice.
-The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, not on their spatial location.
-Again, this is a common assumption when dealing with intracortical connectivity (\textcolor[rgb]{1.00,0.00,0.00}{ref}).
+The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, and not on their spatial location.
+Again, this is a common assumption when dealing with intracortical connectivity.
 This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible.
-The IDE estimation is derived for a general heterogeneous structure however, for clarity of results we shall only present the heterogeneous case.
-We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population.
-In this case, inhibition can be modeled by having a negative response kernel and excitation with a positive response kernel, where the connectivity kernel provides the (scaled) polarity.
-This reduces the model to a single field.
-We will also assume the activation function $p(.)$ is a Heaviside step function.
-This is in agreement with the work of Schiff and Sauer~\cite{schiff2008kalman}.
-With these assumptions, the model has the form
-\begin{equation}\label{SimplifiedModel}
-\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)p\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
+The IDE estimation is derived for a general heterogeneous structure, however for clarity of results we shall only present the heterogeneous case.
+With these assumptions we have the model in the form
+\begin{equation}\label{Eq10}
+{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {\left| {s - r} \right|} \right)P\left( {{v_t}\left( r \right)} \right)dy}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right).
 \end{equation}
-In order to make the problem trackable, in terms of model order, we assume that we can decompose the field (membranes voltages) into a set of $n_\phi$ Gaussian basis functions.
-We will also assume that we know the location and width of the basis function that is required to decompose the field.
-The state of the system is the height basis functions, rather than the membrane potential.
-Therefore, the number of basis functions required to decompose the field is equal to the number of states.
-Also, we assume that we can represent the connectivity by a regular grid of three connectivity Gaussian basis functions (corresponding to short, mid and long range connectivity) of known width.
-The height of the connectivity basis functions ($\theta$ parameter) is to be estimated.
-%\subsection{IDE Formulation}
-%
-%For the state-space derivation, to create an estimator, the model can be reformulated like so
-%\begin{equation}\label{new_spatiotemporal_kernels}
-%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
-%\end{equation}
-%
-%\begin{equation}\label{define_v_tilde}
-%\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
-%
-%\begin{equation}\label{define_v_bar}
-%\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
-%
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.4]{ExampleFieldDecomposition.eps}
-%\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
-Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
-%\label{ExampleFieldDecomposition}
-%\end{figure*}
-%
+In addition to the assumptions above we shall linearize the model by approximating the sigmoid function $P$ as a piece-wise linear function, $P_{L}$, where
+\begin{equation}\label{Eq11}
+\begin{array}{*{20}{c}}
+   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = 0,} \hfill & {f\left( {{v_t}\left( r \right)} \right) \le 0} \hfill  \\
+   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = f\left( {{v_t}\left( r \right)} \right),} \hfill & {0 < f\left( {{v_t}\left( r \right)} \right) < {R_0}} \hfill  \\
+   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = {R_0},} \hfill & {f\left( {{v_t}\left( r \right)} \right) \ge {R_0}} \hfill  \\
+\end{array}
+\end{equation}
+and
+\begin{equation}\label{Eq12}
+f\left( {{v_t}\left( r \right)} \right) = \frac{{{R_0}}}{2}\left( {1 + \frac{\beta }{2}\left( {{v_t}\left( r \right) - {v_0}\left( r \right)} \right)} \right).
+\end{equation}
+For the derivation of the state-space model we shall assume that the model is operating in the active dynamic region, since this is the most interesting case, and the other cases correspond to the neural populations either being saturated (at $R_0$) or being silent.
+We shall show be stability analysis that the model will not saturate for the given parameters and nor will it be silent since it is continuously driven by noise.
+Substituting equation~\ref{Eq11} into equation~\ref{Eq10} and expanding we get
+\begin{align}\label{Eq13}
+ {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
+  + \frac{{{R_0}}}{4}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
+  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber
+\end{align}
+where ${\bar v_0}\left( r \right) = 1 - \frac{\beta }{2}{v_0}\left( r \right)$.
+
+Alternatively we replace the sigmoidal firing mechanism with a Heaviside function.
 \section{State-Space Neural Field Model}
@@
 The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
-\begin{equation}
- v_{t+1}(\mathbf s)=\int_{\mathcal S} \alpha \delta(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d \mathbf r+\int_{\mathcal S} w(\mathbf s -\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+e_t(\mathbf s)
-\label{eq:cortexfield}
+To simplify the notation in the derivation we will let the external input $\epsilon(t)=0$.
+Also, we shall define
+\begin{equation}\label{Eq14}
+W\left( {s,r} \right) = {\theta ^T}\psi \left( {s,r} \right)
 \end{equation}
-decomposing the field and the kernel we have
-\begin{equation}
-\bar v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
-\label{eq:cortexfieldlv0}
+and
+\begin{equation}\label{Eq15}
+{v_t}\left( s \right) = \phi {\left( s \right)^T}{x_t},
 \end{equation}
-\begin{equation}
-\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0 + \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
-\label{eq:cortexfieldgv0}
+where $\theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$.
+The voltage field at $t$ is comprised of a scaled version (by the state $x_t$) of the basis functions $\phi(s)$.
+ The spatial kernel $W$ and the field $v$ are decomposed using the same basis functions, and we will define them as being complete and orthogonal. Also, we shall define
+\begin{equation}\label{Eq16}
+\Phi \left( s \right) = \int_\Omega  {\psi \left( {s,r} \right)\phi {{\left( r \right)}^T}dr}
 \end{equation}
-\begin{equation}
- w(\mathbf r -\mathbf r')=\boldsymbol \theta^{\top}\psi(\mathbf r -\mathbf r')
-\label{eq:kerneldecomposition}
+and
+\begin{equation}\label{Eq17}
+\Gamma \left( s \right) = \int_\Omega  {\psi \left( {s,r} \right){{\bar v}_0}\left( r \right)dr}.
 \end{equation}
-Substituting (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:kerneldecomposition}) in (\ref{eq:cortexfield}) we get
-\begin{equation}
- \boldsymbol \phi^{\top}(\mathbf s)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf s)\tilde{\mathbf x}_{t+1}=
-\int_\mathcal{S}\alpha\delta(\mathbf s- \mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r+\int_\mathcal{S}\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\tilde{\mathbf x}_td\mathbf r+e_t(\mathbf s)
-\label{eq:decomposedcortexfield}
+By substituting equations~\ref{Eq14} and \ref{Eq15} into equation~\ref{Eq13} we get
+\begin{align}\label{Eq18}
+ {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}{\theta ^T}\int_\Omega  {\psi \left( {s,r} \right){{\bar v}_0}\left( r \right)dr} \nonumber \\
+  + \frac{{{R_0}}}{2}\beta {\theta ^T}\int_\Omega  {\psi \left( {s,r} \right)\phi {{\left( r \right)}^T}dr} {x_t} \\
+  - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t} \nonumber
+\end{align}
+and substituting in equations~\ref{Eq16} and \ref{Eq17} into equation~\ref{Eq18} we get
+\begin{equation}\label{Eq19}
+{v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}{\theta ^T}\Gamma \left( s \right) + \frac{{{R_0}}}{2}\beta {\theta ^T}\Phi \left( s \right){x_t} - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t}.
 \end{equation}
-\begin{equation}
- \boldsymbol \phi^{\top}(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf s)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\mathcal S}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)\tilde{\mathbf x}_td\mathbf r+e_t(\mathbf s)
+By substituting the field for the basis functions weighted by the state vector we get
+\begin{equation}\label{Eq20}
+\phi {\left( s \right)^T}{x_{t + 1}} = \frac{{{R_0}}}{2}{\theta ^T}\Gamma \left( s \right) + \frac{{{R_0}}}{2}\beta {\theta ^T}\Phi \left( s \right){x_t} - \frac{1}{\tau }\phi {\left( s \right)^T}{x_t}.
 \end{equation}
-by defining
-\begin{equation}
- \boldsymbol\Phi(\mathbf s)=\int_{\mathcal S}\boldsymbol\psi(\mathbf s -\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
-\label{eq:convolution}
+Multiplying both sides by $\phi(s)$ and integrating over $s$ we get
+\begin{align}\label{21}
+ \int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds{x_{t + 1}}}  = \frac{{{R_0}}}{2}\int_\Omega  {\phi \left( s \right){\theta ^T}\Gamma \left( s \right)ds}  \nonumber \\
+  + \frac{{{R_0}}}{2}\beta \int_\Omega  {\phi \left( s \right){\theta ^T}\Phi \left( s \right)ds} {x_t} \\
+  - \frac{1}{\tau }\int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds} {x_t}. \nonumber
+\end{align}
+Now we define
+\begin{equation}\label{22}
+\Psi  = \int_\Omega  {\phi \left( s \right)\phi {{\left( s \right)}^T}ds}
 \end{equation}
-we have
-\begin{equation}
- \boldsymbol \phi^{\top}(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf s)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)\tilde{\mathbf x}_t+e_t(\mathbf s)
-\label{eq:cortexfieldwithPhi}
+and
+\begin{equation}\label{23}
+\Upsilon  = \int_\Omega  {\phi \left( s \right){\theta ^T}\Phi \left( s \right)ds}
 \end{equation}
-Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf s) $, and integrating over $\mathbf s$
-\begin{equation}
-\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \phi^{\top}(\mathbf s)d\mathbf s \bar{\mathbf x}_{t}+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s\tilde{\mathbf x}_t+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
-\label{eq:cortexfieldversion2}
+and
+\begin{equation}\label{24}
+\Pi  = \int_\Omega  {\phi \left( s \right){\theta ^T}\Gamma \left( s \right)ds},
 \end{equation}
-Now we define
-\begin{equation}
- \boldsymbol\Psi_x(\mathbf s)=\int_{\mathcal S}\boldsymbol\phi(\mathbf s)\boldsymbol\phi^{\top}(\mathbf s)d\mathbf s
-\label{eq:psix}
+where $\Psi$ is a square positive definite matrix. Substituting equations~\ref{22}, ~\ref{23} and \ref{24} into equation~\ref{21} we get
+\begin{equation}\label{25}
+\Psi {x_{t + 1}} = \frac{{{R_0}}}{2}\Pi  + \frac{{{R_0}}}{2}\beta \Upsilon {x_t} - \frac{1}{\tau }\Psi {x_t}.
 \end{equation}
-\begin{equation}
-  \boldsymbol\Psi_{\theta}(\mathbf s)=\int_{\mathcal S} \boldsymbol\phi(\mathbf s)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf s)d\mathbf s
-\label{eq:psitheta}
+Since $\Psi$ is a square positive definite matrix we can invert it to isolate $x_t$ yielding
+\begin{equation}\label{26}
+{x_{t + 1}} = \frac{{{R_0}}}{2}{\Psi _x}^{ - 1}\Pi  + \left( {\frac{{{R_0}}}{2}\beta {\Psi _x}^{ - 1}\Upsilon  - \frac{1}{\tau }{\bf{I}}} \right){x_t},
 \end{equation}
-substituting (\ref{eq:psix}) and (\ref{eq:psitheta}) in (\ref{eq:cortexfieldversion2}) we get
-\begin{equation}
-\boldsymbol\Psi_x(\mathbf s)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf s) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf s)\tilde{\mathbf x}_t+\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
-\end{equation}
-pre-multiplying both sides by $\boldsymbol\Psi_x^{-1}$
-\begin{equation}
-\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\mathcal S} \boldsymbol\phi(\mathbf s)e_t(\mathbf s)d\mathbf s
-\end{equation}
-????????????????????????????????
-\subsection{Observation equation}
-\begin{eqnarray}
- \mathbf y_t(\mathbf s)&=&\\
-&=&\int_{\mathcal S}H(\mathbf s-\mathbf r)v_t(\mathbf r)d\mathbf r+\boldsymbol\epsilon_t \\
-&=&\int_{\mathcal S}H(\mathbf s-\mathbf r)\bar v_t(\mathbf r)d\mathbf r+\int_{\mathcal S}H(\mathbf s-\mathbf r)\tilde v_t(\mathbf r)d\mathbf r+\epsilon_t
-\label{eq:observationequation}
-\end{eqnarray}
-
- we decompose $ H(\mathbf s-\mathbf r)$ as
- \begin{equation}
-  H(\mathbf s-\mathbf r)= \mathbf c^{\top}\mu(\mathbf s-\mathbf r)
-\label{eq:decomposedobservationkernel}
-\end{equation}
-and substituting  (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:decomposedobservationkernel}) in (\ref{eq:observationequation}) we get
-\begin{equation}
- \mathbf y_t(\mathbf s)=\int_{\mathcal S}\mathbf c^{\top}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}d\mathbf r+\int_{\mathcal S}\mathbf c^{\top}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t}d\mathbf r+\epsilon_t
-\end{equation}
-and finally we have
-\begin{equation}
-\mathbf y_t(\mathbf s)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf s)&\mathbf c^{\top}\mathbf M(\mathbf s)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
+where \textbf{I} is the identity matrix. The model can now be written in the canonical state-space form
+\begin{equation}\label{27}
+\begin{array}{c}
+ {x_{t + 1}} = A{x_t} + Bu \\
+ {v_t}\left( s \right) = C{x_t}, \\
+ \end{array}
 \end{equation}
 where
-\begin{equation}
- \mathbf M(\mathbf s)=\int_{\mathcal S}\mu(\mathbf s-\mathbf r)\phi^{\top}(\mathbf r)d\mathbf r
+\begin{equation}\label{28}
+\begin{array}{l}
+ A = \frac{{{R_0}}}{4}\beta {\Psi _x}^{ - 1}\Upsilon  - \frac{1}{\tau }{\bf{I}} \\
+ B = \frac{{{R_0}}}{2}{\Psi _x}^{ - 1}\Pi  \\
+ C = {\phi ^T}\left( s \right) \\
+ u = 1. \\
+ \end{array}
 \end{equation}
@@
 
-\subsection{State-Space Neural Field Model}
-In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
-The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
-We begin with the model in the form
-\begin{eqnarray}\label{InitialModel}
-% \nonumber to remove numbering (before each equation)
-  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon \left( {r,t} \right) \nonumber \\
-   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon \left( {r,t} \right).
-\end{eqnarray}
-Next we defining the basis functions the decompositions of the field and connectivity kernel, where $\phi(s)$ is a vector is Gaussian basis functions, $x_t$ is the state, $\psi(r-r')$ is a vector of three connectivity basis functions and $\theta$ is the corresponding weight of the connectivity
-\begin{equation}\label{FieldDecomp}
-   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
-\end{equation}
-\begin{equation}\label{KernelDecomp}
-k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right).
-\end{equation}
-Assume we know $\phi(r')$ and it is constant, and the form of the activation function $p(.)$ is known, and $\phi(r')$ is independent of $x_t$, then we can uniquely define the function $\rho(.)$ such that
-\begin{eqnarray}\label{NonlinearState}
-% \nonumber to remove numbering (before each equation)
-  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \nonumber \\
-   &=& \phi ^T\left(r'\right)\rho \left( {{x_t}} \right).
-\end{eqnarray}
-Making substitutions of~\ref{FieldDecomp}, \ref{KernelDecomp} and \ref{NonlinearState} into \ref{InitialModel} we get
-\begin{equation}\label{ModelDecomposed}
-{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'}\right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
-\end{equation}
-Now we define
-\begin{equation}\label{DefPhi}
-\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'} \right)dr'}.
-\end{equation}
-Substituting~\ref{DefPhi} into \ref{ModelDecomposed} we get
-\begin{equation}\label{Sub2}
-{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right).
-\end{equation}
-Cross multiplying by $\phi(r)$ in integrating over $r$ gives
-\begin{equation}\label{CorssMultAndInt}
-\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
-\end{equation}
-Now we define
-\begin{equation}\label{DefPsix}
-{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr}
-\end{equation}
-\begin{equation}\label{DefPsitheta}
-{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}.
-\end{equation}
-Substituting~\ref{DefPsix} and \ref{DefPsitheta} into \ref{CorssMultAndInt} we get 
-\begin{equation}\label{Subs3}
-{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
-\end{equation}
-Now we isolate the state by inverting $\Psi_x$
-\begin{equation}\label{IsolateState}
-{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
-\end{equation}
-This gives the state-space model
-\begin{equation}\label{StateSpaceModel}
-{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}.
-\end{equation}
-
 \section{Stability Analysis}
-This section will not probably be included
+Using the analytically calculated basis functions. Need to show that the linearized model will not blow up.
 
 \section{Estimation of the IDE Neural Field Model}
-Based on the other papers. Although it appears to be a job for a nonlinear versions of the Kalman filter.
+Based on the other papers.
 
 \section{Comparison of Estimated and True Connectivity}
+Try and estimate the linear and nonlinear model based on the linear estimator. Might work ok?
+
+\subsection{Linear Model}
+
+\subsection{Nonlinear Model}
 

### 2009-12-03 ltx/BrainIDE.tex
adjusted paper to include state-space model derived in Sheffield

--- 2009-11-18 ltx/BrainIDE.tex
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Estimation of Spatiotemporal Integro-Difference Equations for Dynamical Neural Field Models}
+\title{Estimation of Intracortical Connectivity in a Dynamical Neural Field Model}
 
@@
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
-The model relates the average number of action potentials $f$ arriving at $r$ to the local post synaptic membrane voltage.
+The model relates the average number of action potentials $g$ arriving at $r$ to the local post synaptic membrane voltage.
 The post-synaptic potentials generated at a neuronal population at location $r$ by action potentials arriving from all other connected populations at locations $r'$ can be described by
 \begin{equation}\label{SpikesToPotential}
-v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)f\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
+v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
 \end{equation}
@@
 \begin{equation}\label{RateBasedInteractions}
-f\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}
+g\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}
 \end{equation}
-where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $p$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
 
@@
 \begin{equation}\label{ActivationFunction}
-p\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v_t}\left( {r'} \right)} \right)} \right)}}.
+f\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v_t}\left( {r'} \right)} \right)} \right)}}.
 \end{equation}
@@
 \begin{equation}\label{FullDoubleIntModel}
-v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)p\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
+v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
 \end{equation}
@@
 \begin{equation}\label{GenForm}
-L\left( {\frac{\partial }{{dt}}} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {r,t} \right),
+L\left( {\frac{\partial }{{dt}}} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {r,t} \right),
 \end{equation}
@@
 \begin{equation}\label{FinalForm1}
-\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  +e\left( {r,t} \right).
+\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}  +e\left( {r,t} \right).
 \end{equation}
@@
 
-\subsection{Assumptions and Simplifications}
-We assume that the propagation delay of action potentials is zero.
+%\subsection{Assumptions and Simplifications}
+%We assume that the propagation delay of action potentials is zero.
 This is a common assumption that is made when modeling intracortical circuits (\textcolor[rgb]{1.00,0.00,0.00}{refs}).
@@
 With these assumptions, the model has the form
-\begin{equation}\label{SimplifiedModel}
-\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)p\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
-\end{equation}
-In order to make the problem trackable, in terms of model order, we assume that we can decompose the field (membranes voltages) into a set of $n_\phi$ Gaussian basis functions.
+%\begin{equation}\label{SimplifiedModel}
+%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)f\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
+%\end{equation}
+%In order to make the problem trackable, in terms of model order, we assume that we can decompose the field (membranes voltages) into a set of $n_\phi$ Gaussian basis functions.
 We will also assume that we know the location and width of the basis function that is required to decompose the field.
@@
 The height of the connectivity basis functions ($\theta$ parameter) is to be estimated.
-\subsection{IDE Formulation}
-For the state-space derivation, to create an estimator, the model can be reformulated like so
-\begin{equation}\label{new_spatiotemporal_kernels}
-\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
-\end{equation}
-\begin{equation}\label{define_v_tilde}
-\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
-   0 & {otherwise}  \\
-\end{array}} \right.
-\end{equation}
-\begin{equation}\label{define_v_bar}
-\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
-   0 & {otherwise}  \\
-\end{array}} \right.
-\end{equation}
-\begin{figure*}
-\centering
-\includegraphics[scale=0.3]{ExampleFieldDecomposition.eps}
-\caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
+%\subsection{IDE Formulation}
+
+%For the state-space derivation, to create an estimator, the model can be reformulated like so
+%\begin{equation}\label{new_spatiotemporal_kernels}
+%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
+%\end{equation}
+%\begin{equation}\label{define_v_tilde}
+%\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
+%   0 & {otherwise}  \\
+%\end{array}} \right.
+%\end{equation}
+%\begin{equation}\label{define_v_bar}
+%\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
+%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
+%   0 & {otherwise}  \\
+%\end{array}} \right.
+%\end%equation}
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.3]{ExampleFieldDecomposition.eps}
+% \caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
 Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
-\label{ExampleFieldDecomposition}
-\end{figure*}
+% \label{ExampleFieldDecomposition}
+% \end{figure*}
 
-\section{State-Space Neural Field Model}
-In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
+%\section{State-Space Neural Field Model}
+%In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
 The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
 \begin{equation}
- v_{t+1}(\mathbf r)=\int_{\Omega} \alpha \delta(\mathbf r-\mathbf r')\bar v_t(\mathbf r)d \mathbf r'+\int_{\Omega} w(\mathbf r -\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+e_t(\mathbf r)
-\label{eq:cortexfield}
-\end{equation}
-decomposing the field and the kernel we have
-\begin{equation}
-\bar v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
-\label{eq:cortexfieldlv0}
-\end{equation}
-\begin{equation}
-\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0
-\label{eq:cortexfieldgv0}
-\end{equation}
-\begin{equation}
- w(\mathbf r -\mathbf r')=\boldsymbol \theta^{\top}\psi(\mathbf r -\mathbf r')
-\label{eq:kerneldecomposition}
-\end{equation}
-Substituting (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:kerneldecomposition}) in (\ref{eq:cortexfield}) we get
-\begin{equation}
- \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t+1}=
-\int_\Omega\alpha\delta(\mathbf r- \mathbf r')\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r'+\int_\Omega\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
-\label{eq:decomposedcortexfield}
-\end{equation}
-\begin{equation}
- \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
-\end{equation}
-by defining
-\begin{equation}
- \boldsymbol\Phi(\mathbf r)=\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')d\mathbf r'
-\label{eq:convolution}
-\end{equation}
-we have
-\begin{equation}
- \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)\tilde{\mathbf x}_t+e_t(\mathbf r)
-\label{eq:cortexfieldwithPhi}
-\end{equation}
-Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf r) $, and integrating over $\mathbf r$
-\begin{equation}
-\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf r \bar{\mathbf x}_{t}+\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
-\label{eq:cortexfieldversion2}
-\end{equation}
-Now we define
-\begin{equation}
- \boldsymbol\Psi_x(\mathbf r)=\int_{\Omega}\boldsymbol\phi(\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
-\label{eq:psix}
-\end{equation}
-\begin{equation}
-  \boldsymbol\Psi_{\theta}(\mathbf r)=\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r
-\label{eq:psitheta}
-\end{equation}
-substituting (\ref{eq:psix}) and (\ref{eq:psitheta}) in (\ref{eq:cortexfieldversion2}) we get
-\begin{equation}
-\boldsymbol\Psi_x(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf r) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf r)\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
-\end{equation}
-pre-multiplying both sides by $\boldsymbol\Psi_x^{-1}$
-\begin{equation}
-\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
-\end{equation}
-????????????????????????????????
-\subsection{Observation equation}
-\begin{eqnarray}
- \mathbf y_t(\mathbf r)&=&\\
-&=&\int_{\Omega}H(\mathbf r-\mathbf r')v_t(\mathbf r')d\mathbf r'+\boldsymbol\epsilon_t \\
-&=&\int_{\Omega}H(\mathbf r-\mathbf r')\bar v_t(\mathbf r')d\mathbf r'+\int_{\Omega}H(\mathbf r-\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+\epsilon_t
-\label{eq:observationequation}
-\end{eqnarray}
-
- we decompose $ H(\mathbf r-\mathbf r')$ as
- \begin{equation}
-  H(\mathbf r-\mathbf r')= \mathbf c^{\top}\mu(\mathbf r-\mathbf r')
-\label{eq:decomposedobservationkernel}
-\end{equation}
-and substituting  (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:decomposedobservationkernel}) in (\ref{eq:observationequation}) we get
-\begin{equation}
- \mathbf y_t(\mathbf r)=\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\bar{\mathbf x}_{t}d\mathbf r'+\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\tilde{\mathbf x}_{t}d\mathbf r'+\epsilon_t
-\end{equation}
-and finally we have
-\begin{equation}
-\mathbf y_t(\mathbf r)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf r)&\mathbf c^{\top}\mathbf M(\mathbf r)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
-\end{equation}
-where
-\begin{equation}
- \mathbf M(\mathbf r)=\int_{\Omega}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')d\mathbf r'
-\end{equation}
-Next we shall demonstrate the stability of the model and in the following section the estimator for the state vector and connectivity structure is derived.
+% v_{t+1}(\mathbf r)=\int_{\Omega} \alpha \delta(\mathbf r-\mathbf r')\bar v_t(\mathbf r)d \mathbf r'+\int_{\Omega} w(\mathbf r -\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+e_t(\mathbf r)
+%\label{eq:cortexfield}
+%\end{equation}
+%decomposing the field and the kernel we have
+%\begin{equation}
+%\bar v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
+%\label{eq:cortexfieldlv0}
+%\end{equation}
+%\begin{equation}
+%\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0
+%\label{eq:cortexfieldgv0}
+%\end{equation}
+%\begin{equation}
+% w(\mathbf r -\mathbf r')=\boldsymbol \theta^{\top}\psi(\mathbf r -\mathbf r')
+%\label{eq:kerneldecomposition}
+%\end{equation}
+%Substituting (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:kerneldecomposition}) in (\ref{eq:cortexfield}) we get
+%\begin{equation}
+% \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t+1}=
+%\int_\Omega\alpha\delta(\mathbf r- \mathbf r')\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r'+\int_\Omega\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
+%\label{eq:decomposedcortexfield}
+%\end{equation}
+%\begin{equation}
+% \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
+%\end{equation}
+%by defining
+%\begin{equation}
+% \boldsymbol\Phi(\mathbf r)=\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')d\mathbf r'
+%\label{eq:convolution}
+%\end{equation}
+%we have
+%\begin{equation}
+% \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)\tilde{\mathbf x}_t+e_t(\mathbf r)
+%\label{eq:cortexfieldwithPhi}
+%\end{equation}
+%Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf r) $, and integrating over $\mathbf r$
+%\begin{equation}
+%\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf r \bar{\mathbf x}_{t}+\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
+%\label{eq:cortexfieldversion2}
+%\end{equation}
+%Now we define
+%\begin{equation}
+% \boldsymbol\Psi_x(\mathbf r)=\int_{\Omega}\boldsymbol\phi(\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
+%\label{eq:psix}
+%\end{equation}
+%\begin{equation}
+%  \boldsymbol\Psi_{\theta}(\mathbf r)=\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r
+%\label{eq:psitheta}
+%\end{equation}
+%substituting (\ref{eq:psix}) and (\ref{eq:psitheta}) in (\ref{eq:cortexfieldversion2}) we get
+%\begin{equation}
+%\boldsymbol\Psi_x(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf r) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf r)\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
+%\end{equation}
+%pre-multiplying both sides by $\boldsymbol\Psi_x^{-1}$
+%\begin{equation}
+%\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
+%\end{equation}
+%????????????????????????????????
+%\subsection{Observation equation}
+%\begin{eqnarray}
+% \mathbf y_t(\mathbf r)&=&\\
+%&=&\int_{\Omega}H(\mathbf r-\mathbf r')v_t(\mathbf r')d\mathbf r'+\boldsymbol\epsilon_t \\
+%&=&\int_{\Omega}H(\mathbf r-\mathbf r')\bar v_t(\mathbf r')d\mathbf r'+\int_{\Omega}H(\mathbf r-\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+\epsilon_t
+%\label{eq:observationequation}
+%\end{eqnarray}
+%
+% we decompose $ H(\mathbf r-\mathbf r')$ as
+% \begin{equation}
+%  H(\mathbf r-\mathbf r')= \mathbf c^{\top}\mu(\mathbf r-\mathbf r')
+%\label{eq:decomposedobservationkernel}
+%\end{equation}
+%and substituting  (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:decomposedobservationkernel}) in (\ref{eq:observationequation}) we get
+%\begin{equation}
+% \mathbf y_t(\mathbf r)=\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\bar{\mathbf x}_{t}d\mathbf r'+\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\tilde{\mathbf x}_{t}d\mathbf r'+\epsilon_t
+%\end{equation}
+%and finally we have
+%\begin{equation}
+%\mathbf y_t(\mathbf r)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf r)&\mathbf c^{\top}\mathbf M(\mathbf r)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
+%\end{equation}
+%where
+%\begin{equation}
+% \mathbf M(\mathbf r)=\int_{\Omega}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')d\mathbf r'
+%\end{equation}
+%Next we shall demonstrate the stability of the model and in the following section the estimator for the state vector and connectivity structure is derived.
 
@@
 \section{State-Space Model}
-If we are going to use a particle filter or a extended Kalman filter we might as well go for this case.
-If the temporal and spatial part of the nonlinearity can not be separated, than this is the best choice.
+We begin the derivation of the state-space model with the discrete time, continuous space IDE neural field model
 \begin{equation}\label{SystemEq}
-{v_{t + 1}}\left( {\bf{r}} \right) = \int_\Omega  {w\left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + {\varepsilon _t}\left( {\bf{r}} \right)
+{v_{t + 1}}\left( {\bf{r}} \right) = \int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + e_t\left( {\mathbf{r}} \right),
 \end{equation}
-Defining
-\begin{equation}\label{CombiningKernels}
-k\left( {{\bf{r}} - {\bf{r'}}} \right) = w\left( {{\bf{r}} - {\bf{r'}}} \right) - \hat{\alpha}\delta \left( {{\bf{r}} - {\bf{r'}}} \right).
+where $e_t(r)\sim \mathcal{GP}(0,R)$. The observation equation for the model is
+\begin{equation}\label{ObservationEquation}
+    y_t( k ) = \int_\Omega  m( k,\mathbf{r} )v_t( \mathbf{r}\rm ) d\mathbf{r}  + \varepsilon ( k ),
 \end{equation}
-Making substitution we get
-\begin{equation}\label{OneKernelModel}
-{v_{t + 1}}\left( {\bf{r}} \right) = \int_\Omega  {k\left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  + {\varepsilon _t}\left( {\bf{r}} \right).
+where $\varepsilon( k )\sim\mathcal{N}(0,\Sigma)$, $k$ indexes the iEEG electrodes, and $m(k,r)$ is the observation kernel relating the neural field to EEG measurements accounting for electrodes characteristics.
+To infer the state from observations we can write the likelihood function
+\begin{equation}\label{Likelihood}
+p\left( {{y_{1,...,T}}|{v_{1,...,T}}} \right) = \prod\limits_{t = 1}^T {p\left( {{y_t}|{v_t}} \right)} \prod\limits_{t = 2}^T {p\left( {{v_{t + 1}}|{v_t}} \right)} p\left( {{v_0}} \right)
 \end{equation}
-Defining
+where
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  p\left( {{y_t}|{v_t}} \right) &=& \mathcal{N}\left( {\int_\Omega  {m\left( {k,r} \right)v_t( r )dr} ,R} \right) \\
+  p\left( {{v_{t + 1}}|{v_t}} \right) &=& ??? \\
+  p\left( {{v_0}} \right) &=& \mathcal{GP}\left( {{\mu _0},{\pi _0}} \right).
+\end{eqnarray}
+We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can ellaborate), so we need to decompose the field into weighted basis functions. Therefore we define
 \begin{equation}\label{DefFieldDecomp}
@@
 \begin{equation}\label{DefKernelDecomp}
-k\left( {{\bf{r}} - {\bf{r'}}} \right) = {\theta ^T}\psi \left( {{\bf{r}} - {\bf{r'}}} \right)
+k( \mathbf{r} , \mathbf{r'} ) = \theta^T(\mathbf{r})\psi(\mathbf{r} , \mathbf{r'} )
 \end{equation}
-Now we have four basis functions (the fourth being the delta/local connectivity) and four parameters to estimate. Making substitutions
+Will will assume we know the parametric form of the basis functions, where the parameter $\theta$ is unknown.
+Each connectivity basis function can be considered a layer in the WC model.
+Making substitutions we get
 \begin{equation}\label{DecompModel}
-{\phi ^T}\left( {\bf{r}} \right){x_t} = {\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}}  + {\varepsilon _t}\left( {\bf{r}} \right)
+{\phi ^T}\left( \mathbf{r} \right){x_{t+1}} = \theta^T(\mathbf{r})\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \alpha\phi^T(r)x_t + {\varepsilon _t}\left( {\mathbf{r}} \right).
 \end{equation}
-Cross multiply and integrate over $\bf{r}$
+To isolate the state we cross multiply by $\phi(r)$ and integrate over $\bf{r}$
 \begin{equation}\label{Poo}
-\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_t}}  = \int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + \int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
+\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = \int_\Omega  {\phi ( \mathbf{r} )\theta^T(\mathbf{r})\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  - \alpha\int_\Omega \phi(r)\phi^T(r)d\bf{r} x_t  + \int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}
-Defining
-\begin{equation}\label{DefPsi}
-\Psi  = \int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}}
+Now we define
+\begin{equation}\label{DefGamma}
+\Gamma  = \int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}
-Making substitution
+Substituting equation~\ref{DefGamma} into \ref{Poo} and rearranging gives
 \begin{equation}\label{SS Model}
-{x_t} = {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\theta ^T}\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)p\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  + {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
+{x_{t+1}} = {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\theta^T(\mathbf{r})\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}-\alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}
+Under the assumption of spatial homogeneity we can write
+\begin{equation}\label{Homogeneous SS Model}
+{x_{t+1}} = \theta^T{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}-\alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
+\end{equation}
+This provides the final state-space model
 \begin{equation}\label{AbbrevSSModel}
-{x_{t + 1}} = f\left( {x;\theta } \right) + {\Psi ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}
+x_{t + 1} = \theta^T q(x) -\alpha x + \Gamma ^{ - 1}\int_\Omega  {\phi ( \mathbf{r} ){\varepsilon _t}( \mathbf{r} )d\mathbf{r}}
+\end{equation}
+with observation equation
+\begin{equation}\label{ObservationEquation}
+    y_t( k ) = \int_\Omega  m( k,\mathbf{r} )\phi^T( \mathbf{r} ) d\mathbf{r}x_t  + \varepsilon ( k ),
 \end{equation}
 
-\section{Stability Analysis}
-This section will not probably be included
-
-\section{Estimation of the IDE Neural Field Model}
+\section{Estimation of the Nonlinear Homogeneous IDE Neural Field Model}
 Based on the other papers. Although it appears to be a job for a nonlinear versions of the Kalman filter.

### 2009-12-04 ltx/BrainIDE.tex
added MATLAB code of model

@@
 \end{eqnarray}
-We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can ellaborate), so we need to decompose the field into weighted basis functions. Therefore we define
+We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can ellaborate), so we need to decompose the field into weighted basis functions.
+
+In order to implement standard estimation techniques we propose a decomposition of the The field using a set of Gaussian basis functions.
+Decomposition allows a continuous field to be represented by a finite dimensional state vector.
+This allows for the application of standard nonlinear, non-Gaussian state estimation methods such as sequential Monte-Carlo techniques like particle filtering.
+The field decomposition is described by
 \begin{equation}\label{DefFieldDecomp}
-{v_t}\left( {\bf{r}} \right) = {\phi ^T}\left( {\bf{r}} \right){x_t}
+{v_t}\left( {\bf{r}} \right) = {\phi ^T}\left( {\bf{r}} \right){x_t}.
 \end{equation}
+where $\phi(r)$ is the Gaussian basis functions that are scaled by the the state vector. The connectivity kernel can all be decomposed into a set of basis functions
 \begin{equation}\label{DefKernelDecomp}
@@
 Will will assume we know the parametric form of the basis functions, where the parameter $\theta$ is unknown.
-Each connectivity basis function can be considered a layer in the WC model.
+Each connectivity basis function can be considered a layer in the WC model, representing short range excitation, surround inhibition and long range excitation.
 Making substitutions we get
@@
 \section{Estimation of the Nonlinear Homogeneous IDE Neural Field Model}
-Based on the other papers. Although it appears to be a job for a nonlinear versions of the Kalman filter.
 

### 2009-12-06 ltx/BrainIDE.tex
added MATLAB code of model

@@
 \begin{equation}\label{DefKernelDecomp}
-k( \mathbf{r} , \mathbf{r'} ) = \theta^T(\mathbf{r})\psi(\mathbf{r} , \mathbf{r'} )
+k( \mathbf{r} , \mathbf{r'} ) = \theta^T\psi(\mathbf{r} , \mathbf{r'} )
 \end{equation}
@@
 \begin{equation}\label{DecompModel}
-{\phi ^T}\left( \mathbf{r} \right){x_{t+1}} = \theta^T(\mathbf{r})\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \alpha\phi^T(r)x_t + {\varepsilon _t}\left( {\mathbf{r}} \right).
+{\phi ^T}\left( \mathbf{r} \right){x_{t+1}} = \theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \alpha\phi^T(\mathbf{r})x_t + {\varepsilon _t}\left( {\mathbf{r}} \right).
 \end{equation}
-To isolate the state we cross multiply by $\phi(r)$ and integrate over $\bf{r}$
+To isolate the state we cross multiply by $\phi(\mathbf{r})$ and integrate over $\mathbf{r}$
 \begin{equation}\label{Poo}
-\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = \int_\Omega  {\phi ( \mathbf{r} )\theta^T(\mathbf{r})\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  - \alpha\int_\Omega \phi(r)\phi^T(r)d\bf{r} x_t  + \int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
+\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = \int_\Omega  {\phi ( \mathbf{r} )\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  - \alpha\int_\Omega \phi(\mathbf{r})\phi^T(\mathbf{r})d\mathbf{r} x_t  + \int_\Omega  {\phi \left( {\mathbf{r}} \right){\varepsilon _t}\left( {\mathbf{r}} \right)d{\mathbf{r}}}.
 \end{equation}
@@
 \begin{equation}\label{SS Model}
-{x_{t+1}} = {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\theta^T(\mathbf{r})\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}-\alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
+{x_{t+1}} = {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}-\alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}
-Under the assumption of spatial homogeneity we can write
+We can rearrange to get
 \begin{equation}\label{Homogeneous SS Model}
-{x_{t+1}} = \theta^T{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\int_\Omega  {\psi \left( {{\bf{r}} - {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}-\alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
+{x_{t+1}} = {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\int_\Omega  {f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)\psi^T \left( {{\bf{r}} - {\bf{r'}}} \right)d{\bf{r'}}} d{\bf{r}}}\theta - \alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}

### 2009-12-08 ltx/BrainIDE.tex
added multilayer model to latex doco

@@
 \end{equation}
+\subsection{Multi-Layer Model}
+\begin{equation}\label{ExcitatoryLayer}
+\frac{dv_e\left( {r,t} \right)}{{dt}} + \alpha_ev_e\left( {r,t} \right) = \int_\Omega  {w_{ee}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ei}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_e\left( {r,t} \right)
+\end{equation}
+\begin{equation}\label{InhibitoryLayer}
+\frac{dv_i\left( {r,t} \right)}{{dt}} + \alpha_iv_i\left( {r,t} \right) = \int_\Omega  {w_{ie}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ii}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_i\left( {r,t} \right)
+\end{equation}
+The subscript $ei$ denotes connectivity from an inhibitory neural element to an excitatory neural element. We can write the model in matrix form
+\begin{equation}\label{matrixEquation}
+\left[ {\begin{array}{*{20}{c}}
+   {\frac{{d{v_e}\left( t \right)}}
+{{dt}}}  \\
+   {\frac{{d{v_i}\left( t \right)}}
+{{dt}}}  \\
+
+ \end{array} } \right] = \int_\Omega  {\left[ {\begin{array}{*{20}{c}}
+   {{w_{ee}}\left( {r,r'} \right)} & {{w_{ei}}\left( {r,r'} \right)}  \\
+   {{w_{ie}}\left( {r,r'} \right)} & {{w_{ii}}\left( {r,r'} \right)}  \\
+
+ \end{array} } \right]} \left[ {\begin{array}{*{20}{c}}
+   {f\left( {{v_e}\left( {r',t} \right)} \right)}  \\
+   {f\left( {{v_i}\left( {r',t} \right)} \right)}  \\
+
+ \end{array} } \right]dr' - \left[ {\begin{array}{*{20}{c}}
+   {{\alpha _e}{v_e}\left( {r,t} \right)}  \\
+   {{\alpha _i}{v_i}\left( {r,t} \right)}  \\
+
+ \end{array} } \right] + \left[ {\begin{array}{*{20}{c}}
+   {{\varepsilon _e}\left( t \right)}  \\
+   {{\varepsilon _i}\left( t \right)}  \\
+
+ \end{array} } \right]
+\end{equation}
+The iEEG observation equation is
+\begin{equation}\label{iEEGObservationEquation}
+    y(k,t) = \int_{\Omega} m(k,r)\left(v_e(r,t) + v_i(r,t)\right)dr' + w(k,t) 
+\end{equation}
+
 %\subsection{Alternate Model Description I}
@@
 \section{State-Space Model}
-We begin the derivation of the state-space model with the discrete time, continuous space IDE neural field model
+We begin the derivation of the state-space model with the discrete time, continuous space IDE neural field model. A one-step Euler method was used to transform the ODE to a discrete time form.
 \begin{equation}\label{SystemEq}
-{v_{t + 1}}\left( {\bf{r}} \right) = \int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + e_t\left( {\mathbf{r}} \right),
+\frac{v_{t + 1}\left( \mathbf{r} \right) - v_t(\mathbf{r})}{T_s} = \int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + e_t\left( {\mathbf{r}} \right),
 \end{equation}
-where $e_t(r)\sim \mathcal{GP}(0,R)$. The observation equation for the model is
+\begin{equation}\label{SystemEq}
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}} - T_s\alpha {v_t}\left( {\bf{r}} \right) + v_t(\mathbf{r}) + T_se_t\left( {\mathbf{r}} \right),
+\end{equation}
+\begin{equation}\label{SystemEq}
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}} + (1 - T_s\alpha) v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right),
+\end{equation}
+\begin{equation}\label{SystemEq}
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
+\end{equation}
+where $e_t(r)\sim \mathcal{GP}(0,R)$, $\lambda = 1-T_s\alpha$ and $T_s$ is the time step or sampling step.
+
+The observation equation for the model is
 \begin{equation}\label{ObservationEquation}
@@
 where $\varepsilon( k )\sim\mathcal{N}(0,\Sigma)$, $k$ indexes the iEEG electrodes, and $m(k,r)$ is the observation kernel relating the neural field to EEG measurements accounting for electrodes characteristics.
+
 To infer the state from observations we can write the likelihood function
@@
 \end{eqnarray}
-We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can ellaborate), so we need to decompose the field into weighted basis functions.
+We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can elaborate), so we need to decompose the field into weighted basis functions.
 

### 2009-12-14 scripts/Create_Field_From_States.m
Initial commit of matlab scripts

@@ -1,0 +1,10 @@
+
+function Field = Create_Field_From_States(phi, x)
+
+    FieldLayer = zeros(size(phi,1),size(phi,2),size(phi,2));
+    
+    for FieldBasisIndex=1:size(phi,1) 
+        FieldLayer(FieldBasisIndex,:,:) = x(FieldBasisIndex)*phi(FieldBasisIndex,:,:);
+    end
+
+    Field = sum(FieldLayer,1);

### 2009-12-14 scripts/DefineObservationKernel.m

@@ -1,0 +1,38 @@
+
+% define observation kernels
+
+SensorWidth = 1;        % diameter in mm
+SensorSpacing = 3;     % in mm
+
+BoundryEffectWidth = 4; % how much space to ignore
+
+ObservationCentre = (-FieldWidth/2 + BoundryEffectWidth):SensorSpacing:(FieldWidth/2 - BoundryEffectWidth);
+NSensors = length(ObservationCentre)^2;
+RightDistance = abs((FieldWidth/2 - BoundryEffectWidth) - ObservationCentre(end));              % to edge of the usable field
+
+ObservationCentre = ObservationCentre + RightDistance/2;        % recenter grid
+
+angle = linspace(-pi,pi,100);
+ObservationFunctionIndex = 1;
+
+for CenterIndex_x=1:length(ObservationCentre)
+    for CenterIndex_y=1:length(ObservationCentre)
+        
+        plot(ObservationCentre(CenterIndex_x),ObservationCentre(CenterIndex_y),'+')
+        hold on
+        plot(SensorWidth*cos(angle)+ObservationCentre(CenterIndex_x),SensorWidth*sin(angle)+ObservationCentre(CenterIndex_y),'k')
+        
+        for x_space_index=1:N_masses_in_width                                     % sum over the x direction
+            for y_space_index=1:N_masses_in_width
+                
+                m(ObservationFunctionIndex,x_space_index,y_space_index) = exp(-((ObservationCentre(CenterIndex_x) - Space_x(x_space_index)).^2./(SensorWidth.^2)...
+                    + (ObservationCentre(CenterIndex_y) - Space_y(y_space_index)).^2./(SensorWidth.^2)));
+                
+            end
+        end
+        ObservationFunctionIndex = ObservationFunctionIndex+1;
+    end
+end
+
+figure
+imagesc(Space_x,Space_y,squeeze(sum(m,1)))

### 2009-12-14 scripts/Example_From_Paper.m

@@ -1,0 +1,54 @@
+% 1 d example from paper
+clear
+close all
+clc
+
+LW = 5;
+
+x(1) = 0;                   % define initial state
+
+Q = 2;                     % process disturbance variance
+R = 1;                      % measure noise variance
+N_Samples = 100;             % number of time points
+
+% get true state and measurements
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+for k=2:N_Samples
+    [x(k) z(k)] = UpdateStateAndObservation(x(k-1), k-1 , Q, R);
+end
+plot(1:N_Samples,x,'g','linewidth',LW)
+hold on
+
+% run particle filter to estimate state
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+Particle_Variance = 10;
+N_Particles = 100;
+x_p_prior = sqrt(Particle_Variance)*randn(1,N_Particles);                            % subscript p means particle
+% x_p_prior = sqrt(Particle_Variance)*randn(1,1)*ones(1,N_Particles);          % subscript p means particle
+x_p = x_p_prior;
+
+
+for k=2:N_Samples
+    for Particle_Index = 1: N_Particles
+
+        [x_p_update(k,Particle_Index) z_p(Particle_Index)] = UpdateStateAndObservation(x_p(k-1,Particle_Index), k-1 , Q, R);
+        w(Particle_Index) = StateWeight2(z(k), R, z_p(Particle_Index));
+
+    end
+    
+    
+    [x_new w_new] = Resampler(x_p_update(k,:),w);
+%     x_p(k,:) = mean(x_new)*ones(1,N_Particles);
+    x_p(k,:) = x_new;
+    
+end
+
+plot(mean(x_p,2),'k','linewidth',LW)
+boxplot(x_p')
+% legend('true state','prediction','x_mike')
+for Particle_Index = 1: N_Particles
+    plot(1:N_Samples,x_p(:,Particle_Index),'.')
+end
+
+
+legend('True State','Mean Particles', 'Particles')

### 2009-12-14 scripts/Get_Observations.m

@@ -1,0 +1,23 @@
+
+
+function y = Get_Observations(Noise_Covariance_Coefficient, N_Sensors, N_Masses_In_Width, Field, Space_Step, m)
+
+    Observation_Noise_Covariance = Noise_Covariance_Coefficient*eye(N_Sensors);
+    Observation_Noise_mean = zeros(N_Sensors,1);
+    Observation_Noise = mvnrnd(Observation_Noise_mean,Observation_Noise_Covariance,1)';
+    
+    y = zeros(N_Sensors,1);
+    
+    for Sensor_Index=1:N_Sensors
+        for x_space_index=1:N_Masses_In_Width                                     % sum over the x direction
+            for y_space_index=1:N_Masses_In_Width
+                
+                y(Sensor_Index) = sum(sum(squeeze( m(Sensor_Index,:,:).*Field ),1)) * Space_Step^2;
+                
+            end
+        end
+    end
+
+    y = y + Observation_Noise;
+    
+end

### 2009-12-14 scripts/InitialiseStates.m

@@ -1,0 +1,22 @@
+% define initial states and predefine matrices 
+
+function [x Field] = InitialiseStates(N_Samples, N_Masses_In_Width, N_Field_Basis_Functions, phi, Use_Basis_Functions, Initial_Variance)
+
+Field = 0.5*randn(N_Samples,N_Masses_In_Width,N_Masses_In_Width);
+
+if Use_Basis_Functions
+    x = zeros(N_Field_Basis_Functions,N_Samples);
+    initial_state_variance = Initial_Variance*eye(N_Field_Basis_Functions);
+    Init_State_Mean = zeros(N_Field_Basis_Functions,1);
+    x(:,1) = mvnrnd(Init_State_Mean,initial_state_variance,1)';
+
+    for FieldBasisIndex=1:N_Field_Basis_Functions 
+        FieldLayer(FieldBasisIndex,:,:) = x(FieldBasisIndex,1)*phi(FieldBasisIndex,:,:);
+    end
+    
+    Field(1,:,:) = sum(FieldLayer,1);
+    
+else
+    x = [];
+    Field = Initial_Variance*randn(N_Samples, N_Masses_In_Width, N_Masses_In_Width);
+end

### 2009-12-14 scripts/Mult_By_phi_And_Integrate.m

@@ -1,0 +1,14 @@
+
+
+function Int_Phi_Mult_With_Convolved_Firing = Mult_By_phi_And_Integrate(Firing_Convolved_With_Kernel,N_Field_Basis_Functions, Space_Step, phi, N_Masses_In_Width)
+
+    Mult_With_Basis_Function = zeros(N_Field_Basis_Functions, N_Masses_In_Width, N_Masses_In_Width);
+
+    for Field_Basis_Index=1:N_Field_Basis_Functions
+        Mult_With_Basis_Function(Field_Basis_Index,:,:) = squeeze(Firing_Convolved_With_Kernel) .* squeeze(phi(Field_Basis_Index,:,:));
+    end
+
+    IntOver_x = squeeze(sum(Mult_With_Basis_Function,2));
+    Int_Phi_Mult_With_Convolved_Firing = squeeze(sum(IntOver_x,2))*Space_Step^2;
+    
+end

### 2009-12-14 scripts/RecordAVI.m

@@ -1,0 +1,50 @@
+
+fig=figure('name','Field and Firing Rates','units','normalized','position',[0.1 0.1 .8 .8]);
+aviobj = avifile('WC_Simulation3.avi');
+
+for n=1:2:NSamples
+    subplot(231)
+    h=imagesc(Space_x,Space_y,squeeze(Field(n,:,:)));
+    axis off
+    axis square
+    colorbar
+    title(['$v_t(r\prime)$, Time = ' num2str(floor(n*Ts*1e3)) ' ms'], 'interpreter','latex')
+    
+    subplot(232)
+    hh=imagesc(Space_x,Space_y,squeeze(Firing_Rate(n,:,:)));
+    title('$f(v_t(r\prime))$', 'interpreter','latex')
+    axis off
+    axis square
+    colorbar
+    
+    subplot(233)
+    hhh=imagesc(Space_x,Space_y,squeeze(Firing_Convolved_With_Kernel(n,:,:)));
+    title('$\int_\Omega k(r-r\prime)f(v_t(r))dr\prime$', 'interpreter','latex')
+    axis off
+    axis square
+    colorbar
+    
+    subplot(212)
+    plot(y')
+    F = getframe(fig);
+    aviobj = addframe(aviobj,F);
+end
+
+close(fig)
+aviobj = close(aviobj);
+
+% fig=figure;
+% aviobj = avifile('WC_Simulation_FiringRate.avi');
+% 
+% for n=1:5:5000
+%     
+%     h=imagesc(squeeze(FiringRate(n,:,:)));
+%     axis off
+%     colorbar
+%     title(['Time = ' num2str(floor(n*Ts*1e3)) ' ms, $f(v_t(r\prime))$'], 'interpreter','latex')
+%     F = getframe(fig);
+%     aviobj = addframe(aviobj,F);
+% end
+% 
+% close(fig)
+% aviobj = close(aviobj);

### 2009-12-14 scripts/Resampler.m

@@ -1,0 +1,24 @@
+function [new_x new_w] = Resampler(x,w)
+    
+    N = length(w);              % number of particles
+    N_inv = 1/N;                % 
+    new_x = zeros(N,1);         % initialise
+    
+    c = cumsum(w);              % cumulative dist of weights
+    c = c/max(c);               % normalise
+    u1 = rand(1,1)/N;       % with a uniform distribution there is no need to use the sqrt 
+
+    i = 1;
+    for j = 1:N       
+        u(j) = u1 + N_inv*(j-1);    % this guy should never be  > 1 but it is with the definition in the tutorial paper
+        
+        while u(j) > c(i)           % find where the cdf is greater than u
+            i = i + 1;
+        end       
+        
+        new_x(j) = x(i);              % use the state corresponding to where u > than cdf
+        new_w(j) = 1/N;
+        i_j(j) = i;
+        
+    end
+end

### 2009-12-14 scripts/StateWeight.m

@@ -1,0 +1,12 @@
+
+function w = StateWeight(Observation, Observation_Noise_Covariance, Observation_Particle, NSensors)
+    
+    Coef = (1/(2*pi)^(NSensors/2))*(1/sqrt((det(Observation_Noise_Covariance))));
+    
+    ParticleMinusObser = Observation - Observation_Particle;
+    InverseNoise = Observation_Noise_Covariance^-1;
+        
+    ExponentialPart = exp(-0.5*ParticleMinusObser'*InverseNoise*ParticleMinusObser);
+    w = Coef*ExponentialPart;
+
+end

### 2009-12-14 scripts/Two_D_model_12122009.m

@@ -1,0 +1,216 @@
+% 2D WC neural field model
+% Dean Freestone 04/12/09
+
+% 04/12/09, begin coding of model, DF
+% 05/12/09, made code clearer and checked for errors, DF
+
+% table of interesting parameters
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+CalcGamma = 1;
+if CalcGamma
+    clear
+    CalcGamma = 1;
+end
+
+clc
+close all
+
+UseBasisFunctions = 1;
+
+
+% initialise receptor kinetics
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+alpha = 100;                                            % alpha = 1/tau, post-synaptic time constant, (Wendling, 2002, 100 for excitatory, 500 for inhibitory), Schiff = 3
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+
+% initialise activation function
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+beta = 0.56;                                            % slope of sigmoid, spikes/mV           (Wendling, 2002, 0.56 mV^-1)
+nu = 1;                                                 % maximum firing rate, spikes/s         (Wendling, 2002, 2*e0 = 5, or nu = 5 s^-1)                           
+threshold = 6;                                          % firing threshold, mV                  (Wendling, 2002, 6 mV), (Schiff, 2007, threshold = 0.24 (Heaviside))
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+
+%initialise connectivity basis functions
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+N_ConnBasisFuns = 3;
+sigma1 = 4;                                             % width of connectivity kernels
+sigma2 = 6;                                                                                       % Schiff, 0.91
+sigma3 = 15;
+
+theta1 = 1.00;                                           % amplitudes of connectivity kernels 
+theta2 = -0.9;                                                                                        % Schiff, -1.38
+theta3 = 0.045;
+
[…]

### 2009-12-14 scripts/UpdateStateAndObservation.m

@@ -1,0 +1,12 @@
+
+function [x_1 z_1] = UpdateStateAndObservation(x_0, k , Q, R)
+
+    v = sqrt(Q)*randn(1,1);         % define process disturbance
+    n = sqrt(R)*randn(1,1);         % define measure noise
+    
+    f = x_0/2 + 25*x_0/(1+x_0^2) + 8*cos(1.2*k);    % state evolution equation
+    
+    x_1 = f + v;                                    % update state
+    z_1 = (x_1^2)/20 + n;                           % create measurement
+    
+end

### 2009-12-14 scripts/bootstrap_estimator.m

@@ -1,0 +1,37 @@
+% bootstrp 12/12/2009 Parham and Dean
+clc
+
+% define initial state, zero mean and large std dev
+initial_state_variance = Initial_Variance*eye(N_field_basis_function);
+Init_State_Mean = zeros(N_field_basis_function,1);
+
+initial_x_estimate = mvnrnd(Init_State_Mean,initial_state_variance,1)';
+Observation_Noise_Covariance=0.2*eye(NSensors);
+
+
+% create initial field from initial states
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+for FieldBasisIndex=1:size(phi,1) 
+    Field_Layer_Init(FieldBasisIndex,:,:) = initial_x_estimate(FieldBasisIndex)*phi(FieldBasisIndex,:,:);
+end
+Field_Init = squeeze(sum(Field_Layer_Init,1));
+
+N_particles = 50; 
+for Particle_Index=1: N_particles
+
+    f = Sigmoid_Firing_Rate(nu, beta, threshold, Field_Init);                           % compute firing rate
+    Firing_Convolved_With_Kernel = Convolve_Kernel_With_Firing_Rate(N_masses_in_width, f, SpaceStep, ConnectivityKernel);
+    Int_Phi_Mult_With_Convolved_Firing = Mult_By_phi_And_Integrate(Firing_Convolved_With_Kernel, N_field_basis_function, SpaceStep, phi, N_masses_in_width);
+    x_particles(:,Particle_Index) = Ts*Gamma\Int_Phi_Mult_With_Convolved_Firing + lambda*initial_x_estimate + R*randn(N_field_basis_function,1)*SpaceStep^2;
+                                                                                                            %~~~~~
+                                                                                                            %scaled
+    Field_particle(Particle_Index,:,:) = Create_Field_From_States(phi, x_particles(:,Particle_Index)); 
+    y_particle(:,Particle_Index) = Get_Observations(Noise_Covariance_Coefficient, NSensors, N_masses_in_width, Field(t,:,:), SpaceStep, m);
+        
+% multivariate distribution of mean of true measurement and std deviation of observation noise
+    w(Particle_Index) = StateWeight(y(:,2), Observation_Noise_Covariance, y_particle(:,Particle_Index), NSensors);
+    
+end
+
+% define weights for particle filter
+Initial_Weights = ones(1,N_particles)/N_particles;

### 2009-12-14 scripts/create_field_basis_functions.m

@@ -1,0 +1,78 @@
+% create field basis functions
+% Dean Freestone 6/12/09
+% ~~~~~~~~~~~~~~~~~~~~~~
+
+% for a staggered grid we need ...
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+
+x_separation = field_basis_separation/sqrt(2);              % field_basis_separation = diagonal distance between basis functions
+y_separation = 2*field_basis_separation/sqrt(2);
+
+FieldBasisCenters_x = -FieldWidth/2:x_separation:FieldWidth/2;
+FieldBasisCenters_x = FieldBasisCenters_x + (FieldWidth/2-FieldBasisCenters_x(end))/2;      % centre basis function
+
+FieldBasisCenters_y = -FieldWidth/2+y_separation/2:y_separation:FieldWidth/2;
+FieldBasisCenters_y = FieldBasisCenters_y + (FieldWidth/2-FieldBasisCenters_y(end))/2;      % centre basis function
+
+N_field_basis_function = length(FieldBasisCenters_x)* length(FieldBasisCenters_y);
+
+% plot basis function grid
+% ~~~~~~~~~~~~~~~~~~~~~~~~
+figure
+angle = linspace(-pi,pi,100);
+for Centre_index_x = 1:length(FieldBasisCenters_x)
+    
+    for Centre_index_y = 1:length(FieldBasisCenters_y)
+
+        if (floor(Centre_index_x/2) - Centre_index_x/2) == 0                                            % will be even
+            plot(FieldBasisCenters_x(Centre_index_x), FieldBasisCenters_y(Centre_index_y),'+')
+            hold on
+            plot(sigma_field*cos(angle)+FieldBasisCenters_x(Centre_index_x),sigma_field*sin(angle)+FieldBasisCenters_y(Centre_index_y),'k')
+        else                                                                                            % it is odd
+            plot(FieldBasisCenters_x(Centre_index_x), FieldBasisCenters_y(Centre_index_y)-y_separation/2,'r+')
+            plot(sigma_field*cos(angle)+FieldBasisCenters_x(Centre_index_x),sigma_field*sin(angle)+FieldBasisCenters_y(Centre_index_y)-y_separation/2,'k')
+            hold on
+        end
+        
+    end
+end
+axis square
+
+% create basis functions
+% ~~~~~~~~~~~~~~~~~~~~~~
+n=1;
+for Centre_index_x = 1:length(FieldBasisCenters_x)
[…]

### 2009-12-14 scripts/create_field_basis_functions2.m

@@ -1,0 +1,69 @@
+
+
+% define outer grid
+% ~~~~~~~~~~~~~~~~~
+x_center_outer = linspace(-FieldWidth/2,FieldWidth/2,N_masses_in_width/(2*field_basis_separation/sqrt(2)));
+y_center_outer = x_center_outer;
+
+% define inner grid
+% ~~~~~~~~~~~~~~~~~
+distance_between_centers = abs(x_center_outer(2)-x_center_outer(1));
+x_center_inner = linspace(-FieldWidth/2+distance_between_centers/2,FieldWidth/2-distance_between_centers/2,N_masses_in_width/(2*field_basis_separation/sqrt(2))-1);
+y_center_inner = x_center_inner;
+
+% combine the vectors of centers
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+x_centers = [x_center_outer x_center_inner];
+y_centers = [y_center_outer y_center_inner];
+
+
+% plot basis function grid
+% ~~~~~~~~~~~~~~~~~~~~~~~~
+figure
+angle = linspace(-pi,pi,100);
+BasisFunctionIndex = 1;
+for x_center_outer_index=1:length(x_center_outer)
+    for y_center_outer_index=1:length(y_center_outer)
+        plot(x_center_outer(x_center_outer_index), y_center_outer(y_center_outer_index),'+')
+        hold on
+        plot(sigma_field*cos(angle)+x_center_outer(x_center_outer_index),sigma_field*sin(angle)+y_center_outer(y_center_outer_index),'k')
+        
+        
+        for x_space_index=1:N_masses_in_width                                     % sum over the x direction
+            for y_space_index=1:N_masses_in_width
+                
+                phi(BasisFunctionIndex,x_space_index,y_space_index) = exp(-((x_center_outer(x_center_outer_index) - Space_x(x_space_index)).^2./(sigma_field.^2)...
+                    + (y_center_outer(y_center_outer_index) - Space_y(y_space_index)).^2./(sigma_field.^2)));
+                
+            end
+        end
+        BasisFunctionIndex = BasisFunctionIndex+1;
+    end
+end
+
+
+for x_center_inner_index=1:length(x_center_inner)
+    for y_center_inner_index=1:length(y_center_inner)
+        plot(x_center_inner(x_center_inner_index), y_center_inner(y_center_inner_index),'+')
+        hold on
[…]

### 2009-12-19 ltx/BrainIDE.tex
Initial commit of matlab scripts
Updated matlab following Parhams correction

@@
 \begin{equation}\label{ActivationFunction}
-f\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v_t}\left( {r'} \right)} \right)} \right)}}.
+f\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v}\left(r',\bar{t} \right)} \right)} \right)}}.
 \end{equation}
@@
  \end{array} } \right]} \left[ {\begin{array}{*{20}{c}}
-   {f\left( {{v_e}\left( {r',t} \right)} \right)}  \\
-   {f\left( {{v_i}\left( {r',t} \right)} \right)}  \\
+   {f\left( {{v_e}\left( {r',\bar{t}} \right)} \right)}  \\
+   {f\left( {{v_i}\left( {r',\bar{t}} \right)} \right)}  \\
 
@@
 \end{equation}
+
+\begin{equation}\label{matrix_equation_in_vector_notation}
+   \frac{d\mathbf{V}(r,t)}{dt} = \int_\Omega \mathbf{W}(r,r')f\left(\mathbf{V}(r,t)\right)dr' - \mathbf{A}\mathbf{V}(r,t) + \mathbf{E}(r,t)
+\end{equation}
+
 The iEEG observation equation is
@@
 
-%\subsection{Alternate Model Description I}
-%An alternate and equivalent way to remove the temporal integration using the Laplace transform .
+\subsection{Alternate Model Description I}
+An alternate and equivalent way to remove the temporal integration using the Laplace transform .
 We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
-%\begin{equation}\label{TwoDiscreteMasses}
-%{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
-%\end{equation}
-%where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
-%\begin{eqnarray}
-%% \nonumber to remove numbering (before each equation)
-%  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
-%   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
-%  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
-%\end{eqnarray}
-%Now taking the inverse Laplace transform we get
-%\begin{equation}\label{InverseLaplace}
-%\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
-%\end{equation}
-%Next we convert the model from discrete neural masses to a continuum by
-%\begin{equation}\label{Discrete2Continuum}
-%\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
-%\end{equation}
-%
+\begin{equation}\label{TwoDiscreteMasses}
+{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
+\end{equation}
+where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
+\begin{eqnarray}
+% \nonumber to remove numbering (before each equation)
+  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
+   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
+  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
+\end{eqnarray}
+Now taking the inverse Laplace transform we get
+\begin{equation}\label{InverseLaplace}
+\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
+\end{equation}
+Next we convert the model from discrete neural masses to a continuum by
+\begin{equation}\label{Discrete2Continuum}
+\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
+\end{equation}
+
 %\subsection{Alternate Model Description II}
@@
 
-To infer the state from observations we can write the likelihood function
-\begin{equation}\label{Likelihood}
-p\left( {{y_{1,...,T}}|{v_{1,...,T}}} \right) = \prod\limits_{t = 1}^T {p\left( {{y_t}|{v_t}} \right)} \prod\limits_{t = 2}^T {p\left( {{v_{t + 1}}|{v_t}} \right)} p\left( {{v_0}} \right)
-\end{equation}
-where
-\begin{eqnarray}
-% \nonumber to remove numbering (before each equation)
-  p\left( {{y_t}|{v_t}} \right) &=& \mathcal{N}\left( {\int_\Omega  {m\left( {k,r} \right)v_t( r )dr} ,R} \right) \\
-  p\left( {{v_{t + 1}}|{v_t}} \right) &=& ??? \\
-  p\left( {{v_0}} \right) &=& \mathcal{GP}\left( {{\mu _0},{\pi _0}} \right).
-\end{eqnarray}
-We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can elaborate), so we need to decompose the field into weighted basis functions.
+%To infer the state from observations we can write the likelihood function
+%\begin{equation}\label{Likelihood}
+%p\left( {{y_{1,...,T}}|{v_{1,...,T}}} \right) = \prod\limits_{t = 1}^T {p\left( {{y_t}|{v_t}} \right)} \prod\limits_{t = 2}^T {p\left( {{v_{t + 1}}|{v_t}} \right)} p\left( {{v_0}} \right)
+%\end{equation}
+%where
+%\begin{eqnarray}
+%% \nonumber to remove numbering (before each equation)
+%  p\left( {{y_t}|{v_t}} \right) &=& \mathcal{N}\left( {\int_\Omega  {m\left( {k,r} \right)v_t( r )dr} ,R} \right) \\
+%  p\left( {{v_{t + 1}}|{v_t}} \right) &=& ??? \\
+%  p\left( {{v_0}} \right) &=& \mathcal{GP}\left( {{\mu _0},{\pi _0}} \right).
+%\end{eqnarray}
+%We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can elaborate), so we need to decompose the field into weighted basis functions.
 

### 2009-12-19 scripts/DefineObservationKernel.m

@@ -1,10 +1,6 @@
 
 % define observation kernels
 
-SensorWidth = 1;        % diameter in mm
-SensorSpacing = 3;     % in mm
-
-BoundryEffectWidth = 4; % how much space to ignore
 
 ObservationCentre = (-FieldWidth/2 + BoundryEffectWidth):SensorSpacing:(FieldWidth/2 - BoundryEffectWidth);
 NSensors = length(ObservationCentre)^2;

### 2009-12-19 scripts/Two_D_model_12122009.m

@@ -47,7 +47,7 @@ theta2 = -0.9;                                                                  
 theta3 = 0.045;
 
 if UseBasisFunctions
-    theta = 0.0001*[theta1 ; theta2; theta3];               % scaled for basis functions
+    theta = 0.001*[theta1 ; theta2; theta3];               % scaled for basis functions
 else
     theta = 2200*[theta1 ; theta2; theta3];
 end
@@ -58,7 +58,7 @@ sigma = 0.5*[sigma1 ; sigma2 ; sigma3];                 % scaled by two to simul
 
 % initialise field basis functions
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-sigma_field = 1;                                       % width of the field basis function
+sigma_field = 2.5;                                       % width of the field basis function
 field_basis_separation = 2;                             % distance wrt masses, must be > 1, diagonal distance
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@ -75,9 +75,9 @@ time = linspace(0,t_end,NSamples);
 
 % initialise space properties
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-MassDensity = 2;                                        % masses per mm
+MassDensity = 1;                                        % masses per mm
 SpaceStep = 1/MassDensity;
-FieldWidth = 20;                                        % mm in each axis, should be even
+FieldWidth = 40;                                        % mm in each axis, should be even
 N_masses_in_width = MassDensity*FieldWidth+1;
 Space_x = -FieldWidth/2:1/MassDensity:FieldWidth/2;
 Space_y = Space_x;
@@ -85,6 +85,10 @@ Space_y = Space_x;
 
 % initialize observation kernel
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+SensorWidth = 3;        % diameter in mm
+SensorSpacing = 10;     % in mm
+BoundryEffectWidth = 4; % how much space to ignore
+
 DefineObservationKernel
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@ -123,7 +127,7 @@ end
 % Disturbance properties
 % ~~~~~~~~~~~~~~~~~~~~~~
 DisturbanceMean = 0;
[…]

### 2009-12-19 scripts/DefineObservationKernel.m
small update to paper draft

@@ -26,7 +26,9 @@ for CenterIndex_x=1:length(ObservationCentre)
                 
             end
         end
+        
         ObservationFunctionIndex = ObservationFunctionIndex+1;
+        
     end
 end
 

### 2009-12-19 scripts/Example_From_Paper.m

@@ -19,6 +19,7 @@ end
 plot(1:N_Samples,x,'g','linewidth',LW)
 hold on
 
+
 % run particle filter to estimate state
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 Particle_Variance = 10;

### 2009-12-19 scripts/Resampler.m

@@ -6,10 +6,11 @@ function [new_x new_w] = Resampler(x,w)
     
     c = cumsum(w);              % cumulative dist of weights
     c = c/max(c);               % normalise
-    u1 = rand(1,1)/N;       % with a uniform distribution there is no need to use the sqrt 
+    u1 = rand(1,1)/N;           % with a uniform distribution there is no need to use the sqrt 
 
     i = 1;
-    for j = 1:N       
+    for j = 1:N  
+        
         u(j) = u1 + N_inv*(j-1);    % this guy should never be  > 1 but it is with the definition in the tutorial paper
         
         while u(j) > c(i)           % find where the cdf is greater than u
@@ -21,4 +22,5 @@ function [new_x new_w] = Resampler(x,w)
         i_j(j) = i;
         
     end
+    
 end

### 2010-01-14 ltx/BrainIDE.tex
small update to paper draft
Added comments on discretization ... comments please

@@
 \appendices
-\section{}
-Appendix one text goes here.
+\section{Ken's Discretization}
+Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
+\begin{equation}\label{differential eq}	
+\tau dv\left( r,t \right) = \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
+\end{equation}
+where $e\left( r,t \right)$ is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
+(not too sure about this noise since it needs to be white temporally but coloured spatially - which in continuous space-time I have never seen written ...
+has anyone?)
+To simplify the notation, but without loss of generality, \ref{differential eq} can be rewritten as
+\begin{equation}\label{differential simplified}
+	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
+\end{equation}
+Had $q\left(v(r,t) \right)$ been a linear function in $v$, then \ref{differential simplified} could be rewritten as
+\begin{equation}\label{differential linear}
+	dv\left( r,t \right) = Av(r,t)dt  + d e\left( r,t \right)
+\end{equation}
+Considering temporal sampling instances $\delta$ apart given by $\{t_k = 0,~1,~2, \ldots$ \}, then a solution to \ref{differential linear} at each sampling time is given by
+\begin{equation}\label{linear solution}
+	v(r,t_k+\delta) = \exp\{A(\delta)\}x(t) + \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
+\end{equation}
+Let the discrete time random variable $e'(r,t_k)$ be
+\begin{equation}\label{discrete noise}
+	e'(r,t_k) = \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
+\end{equation}
+then, $e'(r,t_k)$ is a zero mean, temporally white noise term with covariance
+\begin{equation}\label{covariance of noise}
+	E\left[e'(r,t_k),e'^\top(r,t_k) \right] = \int_t^{t+\delta}\exp\{A(t_k+\delta-\tau)\} \Sigma_e(r) \exp\{A(t+\delta-\tau)\} d\tau
+\end{equation}
+
+But we are not so luck as to be able to go from \ref{differential simplified} to \ref{differential linear} and thus I doubt if we can obtain an exact solution to \ref{differential simplified} without an approximation.
+Agreed?
+
+A possible approximate solution is the one you have already used. Thus, interpreting the difference equation \ref{differential simplified} as an integral equation gives
+\begin{equation}\label{euler}
+	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
+\end{equation}
+Using an Euler approximation, \ref{euler} can be approximated at each sampling time by
+\begin{equation}\label{euler approx 1}
+	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
+\end{equation}
+which can be rewritten as
+\begin{equation}\label{euler approx 2}
+	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
+\end{equation}
+where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
+(Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$)
 

### 2010-02-11 ltx/BrainIDE.tex
some things

@@
 \end{equation}
-\subsection{Multi-Layer Model}
-\begin{equation}\label{ExcitatoryLayer}
-\frac{dv_e\left( {r,t} \right)}{{dt}} + \alpha_ev_e\left( {r,t} \right) = \int_\Omega  {w_{ee}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ei}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_e\left( {r,t} \right)
-\end{equation}
-\begin{equation}\label{InhibitoryLayer}
-\frac{dv_i\left( {r,t} \right)}{{dt}} + \alpha_iv_i\left( {r,t} \right) = \int_\Omega  {w_{ie}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ii}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_i\left( {r,t} \right)
-\end{equation}
-The subscript $ei$ denotes connectivity from an inhibitory neural element to an excitatory neural element. We can write the model in matrix form
-\begin{equation}\label{matrixEquation}
-\left[ {\begin{array}{*{20}{c}}
-   {\frac{{d{v_e}\left( t \right)}}
-{{dt}}}  \\
-   {\frac{{d{v_i}\left( t \right)}}
-{{dt}}}  \\
 
- \end{array} } \right] = \int_\Omega  {\left[ {\begin{array}{*{20}{c}}
-   {{w_{ee}}\left( {r,r'} \right)} & {{w_{ei}}\left( {r,r'} \right)}  \\
-   {{w_{ie}}\left( {r,r'} \right)} & {{w_{ii}}\left( {r,r'} \right)}  \\
+% \subsection{Multi-Layer Model}
+% \begin{equation}\label{ExcitatoryLayer}
+% \frac{dv_e\left( {r,t} \right)}{{dt}} + \alpha_ev_e\left( {r,t} \right) = \int_\Omega  {w_{ee}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ei}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_e\left( {r,t} \right)
+% \end{equation}
+% \begin{equation}\label{InhibitoryLayer}
+% \frac{dv_i\left( {r,t} \right)}{{dt}} + \alpha_iv_i\left( {r,t} \right) = \int_\Omega  {w_{ie}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ii}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_i\left( {r,t} \right)
+% \end{equation}
+% The subscript  denotes connectivity from an inhibitory neural element to an excitatory neural element. We can write the model in matrix form
+% \begin{equation}\label{matrixEquation}
+% \left[ {\begin{array}{*{20}{c}}
+%    {\frac{{d{v_e}\left( t \right)}}
+% {{dt}}}  \
+%    {\frac{{d{v_i}\left( t \right)}}
+% {{dt}}}  \
+% 
+%  \end{array} } \right] = \int_\Omega  {\left[ {\begin{array}{*{20}{c}}
+%    {{w_{ee}}\left( {r,r'} \right)} & {{w_{ei}}\left( {r,r'} \right)}  \
+%    {{w_{ie}}\left( {r,r'} \right)} & {{w_{ii}}\left( {r,r'} \right)}  \
+% 
+%  \end{array} } \right]} \left[ {\begin{array}{*{20}{c}}
+%    {f\left( {{v_e}\left( {r',\bar{t}} \right)} \right)}  \
+%    {f\left( {{v_i}\left( {r',\bar{t}} \right)} \right)}  \
+% 
+%  \end{array} } \right]dr' - \left[ {\begin{array}{*{20}{c}}
+%    {{\alpha _e}{v_e}\left( {r,t} \right)}  \
+%    {{\alpha _i}{v_i}\left( {r,t} \right)}  \
+% 
+%  \end{array} } \right] + \left[ {\begin{array}{*{20}{c}}
+%    {{\varepsilon _e}\left( t \right)}  \
+%    {{\varepsilon _i}\left( t \right)}  \
+% 
+%  \end{array} } \right]
+% \end{equation}
+% 
+% \begin{equation}\label{matrix_equation_in_vector_notation}
+%    \frac{d\mathbf{V}(r,t)}{dt} = \int_\Omega \mathbf{W}(r,r')f\left(\mathbf{V}(r,t)\right)dr' - \mathbf{A}\mathbf{V}(r,t) + \mathbf{E}(r,t)
+% \end{equation}
+% 
+% The iEEG observation equation is
+% \begin{equation}\label{iEEGObservationEquation}
+%     y(k,t) = \int_{\Omega} m(k,r)\left(v_e(r,t) + v_i(r,t)\right)dr' + w(k,t)
+% \end{equation}{}
 
- \end{array} } \right]} \left[ {\begin{array}{*{20}{c}}
-   {f\left( {{v_e}\left( {r',\bar{t}} \right)} \right)}  \\
-   {f\left( {{v_i}\left( {r',\bar{t}} \right)} \right)}  \\
-
- \end{array} } \right]dr' - \left[ {\begin{array}{*{20}{c}}
-   {{\alpha _e}{v_e}\left( {r,t} \right)}  \\
-   {{\alpha _i}{v_i}\left( {r,t} \right)}  \\
-
- \end{array} } \right] + \left[ {\begin{array}{*{20}{c}}
-   {{\varepsilon _e}\left( t \right)}  \\
-   {{\varepsilon _i}\left( t \right)}  \\
-
- \end{array} } \right]
-\end{equation}
-
-\begin{equation}\label{matrix_equation_in_vector_notation}
-   \frac{d\mathbf{V}(r,t)}{dt} = \int_\Omega \mathbf{W}(r,r')f\left(\mathbf{V}(r,t)\right)dr' - \mathbf{A}\mathbf{V}(r,t) + \mathbf{E}(r,t)
-\end{equation}
-
-The iEEG observation equation is
-\begin{equation}\label{iEEGObservationEquation}
-    y(k,t) = \int_{\Omega} m(k,r)\left(v_e(r,t) + v_i(r,t)\right)dr' + w(k,t)
-\end{equation}
-
-\subsection{Alternate Model Description I}
-An alternate and equivalent way to remove the temporal integration using the Laplace transform .
+% \subsection{Alternate Model Description I}
+% An alternate and equivalent way to remove the temporal integration using the Laplace transform .
 We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
-\begin{equation}\label{TwoDiscreteMasses}
-{v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
-\end{equation}
-where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
-\begin{eqnarray}
-% \nonumber to remove numbering (before each equation)
-  {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
-   &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
-  \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
-\end{eqnarray}
-Now taking the inverse Laplace transform we get
-\begin{equation}\label{InverseLaplace}
-\frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
-\end{equation}
-Next we convert the model from discrete neural masses to a continuum by
-\begin{equation}\label{Discrete2Continuum}
-\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
-\end{equation}
+% \begin{equation}\label{TwoDiscreteMasses}
+% {v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
+% \end{equation}
+% where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
+% \begin{eqnarray}
+% % \nonumber to remove numbering (before each equation)
+%   {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
+%    &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
+%   \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
+% \end{eqnarray}
+% Now taking the inverse Laplace transform we get
+% \begin{equation}\label{InverseLaplace}
+% \frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
+% \end{equation}
+% Next we convert the model from discrete neural masses to a continuum by
+% \begin{equation}\label{Discrete2Continuum}
+% \frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
+% \end{equation}
 
@@
 \begin{equation}\label{SystemEq}
-\frac{v_{t + 1}\left( \mathbf{r} \right) - v_t(\mathbf{r})}{T_s} = \int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + e_t\left( {\mathbf{r}} \right),
+\frac{v_{t + 1}\left( \mathbf{r} \right) - v_t(\mathbf{r})}{T_s} = \int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + e_t\left( {\mathbf{r}} \right),
 \end{equation}
 \begin{equation}\label{SystemEq}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}} - T_s\alpha {v_t}\left( {\bf{r}} \right) + v_t(\mathbf{r}) + T_se_t\left( {\mathbf{r}} \right),
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} - T_s\alpha {v_t}\left( {\bf{r}} \right) + v_t(\mathbf{r}) + T_se_t\left( {\mathbf{r}} \right),
 \end{equation}
 \begin{equation}\label{SystemEq}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}} + (1 - T_s\alpha) v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right),
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \mathbf{r'} \right)} \right)d{\bf{r'}}} + (1 - T_s\alpha) v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right),
 \end{equation}
 \begin{equation}\label{SystemEq}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( {{\bf{r'}}} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
 \end{equation}
@@
 \begin{equation}\label{DecompModel}
-{\phi ^T}\left( \mathbf{r} \right){x_{t+1}} = \theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \alpha\phi^T(\mathbf{r})x_t + {\varepsilon _t}\left( {\mathbf{r}} \right).
+{\phi ^T}\left( \mathbf{r} \right){x_{t+1}} = T_s\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \lambda\phi^T(\mathbf{r})x_t + T_s{e_t}\left( {\mathbf{r}} \right).
 \end{equation}
@@
 \begin{equation}\label{Poo}
-\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = \int_\Omega  {\phi ( \mathbf{r} )\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  - \alpha\int_\Omega \phi(\mathbf{r})\phi^T(\mathbf{r})d\mathbf{r} x_t  + \int_\Omega  {\phi \left( {\mathbf{r}} \right){\varepsilon _t}\left( {\mathbf{r}} \right)d{\mathbf{r}}}.
+\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = T_s\int_\Omega  {\phi ( \mathbf{r} )\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  - \lambda\int_\Omega \phi(\mathbf{r})\phi^T(\mathbf{r})d\mathbf{r} x_t  + T_s\int_\Omega  {\phi \left( {\mathbf{r}} \right)e_t\left( {\mathbf{r}} \right)d{\mathbf{r}}}.
 \end{equation}
@@
 \begin{equation}\label{SS Model}
-{x_{t+1}} = {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}-\alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
+{x_{t+1}} = T_s{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}} - \lambda x_t + T_s{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)e_t\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}
@@
 \begin{equation}\label{Homogeneous SS Model}
-{x_{t+1}} = {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\int_\Omega  {f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)\psi^T \left( {{\bf{r}} - {\bf{r'}}} \right)d{\bf{r'}}} d{\bf{r}}}\theta - \alpha x_t + {\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right){\varepsilon _t}\left( {\bf{r}} \right)d{\bf{r}}}.
+	x_{t+1} = T_s\Gamma ^{ - 1}\int_\Omega  {\phi \left( {\bf{r}} \right)\int_\Omega  {f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)\psi^T \left( {{\bf{r}} - {\bf{r'}}} \right)d{\bf{r'}}} d{\bf{r}}}\theta - \lambda x_t + T_s{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)e_t\left( {\bf{r}} \right)d{\bf{r}}}.
 \end{equation}
-This provides the final state-space model
+The disturbance term can be rewritten as 
+\begin{equation}
+	\Gamma ^{ - 1}\int_\Omega  {\phi \left( \bf{r} \right)e_t\left( \bf{r} \right)d\bf{r}} = \int_\Omega  {\phi \left( \bf{r} \right)\tilde{e}_t\left( \bf{r} \right)d\bf{r}},
+\end{equation}
+where $\tilde{e}_t(r)~N(0,R'R)$ and $R'$ is the Cholesky decomposition of $\Gamma^{-1}$. This provides the final state-space model
 \begin{equation}\label{AbbrevSSModel}
-x_{t + 1} = \theta^T q(x) -\alpha x + \Gamma ^{ - 1}\int_\Omega  {\phi ( \mathbf{r} ){\varepsilon _t}( \mathbf{r} )d\mathbf{r}}
+x_{t + 1} = T_sq(x_t)\theta -\lambda x_t + T_s\int_\Omega  {\phi ( \mathbf{r} )\tilde{e}_t( \mathbf{r} )d\mathbf{r}}
 \end{equation}
@@
 
+\subsection{Discrete Space For Simulation}
+
+In this section we describe a discrete time, discrete space model that we are using for the simulations.
+Now we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta \mathbf{r}$ giving
+\begin{equation}\label{DiscreteSpaceModelij}
+	x_{t+1} = T_s\Gamma ^{ - 1}\sum_i \sum_j  {\phi \left( \mathbf{r} \right)\sum_i\sum_j  {f\left( \phi^T \left( \mathbf{r'} \right) x_t \right)\psi^T \left( \mathbf{r} - \bf{r'} \right)\Delta\mathbf{r'}^2} \Delta\mathbf{r}^2} \theta - \lambda x_t + T_s\sum_i\sum_j  {\phi \left( {\bf{r}} \right)\tilde{e}_t\left( \bf{r} \right)\Delta\mathbf{r}^2}.
+\end{equation}
 \section{Estimation of the Nonlinear Homogeneous IDE Neural Field Model}

### 2010-02-11 scripts/Two_D_model_12122009.m

@@ -126,10 +126,12 @@ end
 
 % Disturbance properties
 % ~~~~~~~~~~~~~~~~~~~~~~
-DisturbanceMean = 0;
-SigmaDisturbance = 1000;           % no basis decomposition
+DisturbanceMean = 0*ones(N_field_basis_function,1);
+SigmaDisturbance = 8000*eye(N_field_basis_function,N_field_basis_function);           % no basis decomposition
 if UseBasisFunctions
-    R = SigmaDisturbance*chol(Gamma^-1);               % use cholesky decomp
+    R = chol(Gamma^-1);               % use cholesky decomp
+    DisturbanceCovariance = R*SigmaDisturbance*R';
+    DisturbanceMean = R*DisturbanceMean;
 else
     Disturbance = sqrt(SigmaDisturbance)*randn(NSamples,N_masses_in_width,N_masses_in_width);
 end
@@ -171,10 +173,17 @@ for t=2:NSamples
         
         Int_Phi_Mult_With_Convolved_Firing = Mult_By_phi_And_Integrate(Firing_Convolved_With_Kernel(t-1,:,:), ...
             N_field_basis_function, SpaceStep, phi, N_masses_in_width);
-
-        x(:,t) = Ts*Gamma\Int_Phi_Mult_With_Convolved_Firing + lambda*x(:,t-1) + Ts*R*randn(N_field_basis_function,1)*SpaceStep^2;
+        
+        Disturbance = DisturbanceMean+DisturbanceCovariance*randn(N_field_basis_function,1);
+        
+        for Field_Basis_Index=1:N_field_basis_function
+            Disturbance_with_Phi(Field_Basis_Index) = sum(sum(Disturbance(Field_Basis_Index)*squeeze(phi(Field_Basis_Index,:,:)),1))*SpaceStep^2;
+        end
+        
+        x(:,t) = Ts*Gamma\Int_Phi_Mult_With_Convolved_Firing + lambda*x(:,t-1) + Ts^2*Disturbance_with_Phi';
         
         Field(t,:,:) = Create_Field_From_States(phi, x(:,t));
+        
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
     else

### 2010-02-16 ltx/BrainIDE.tex
Least Square parameter estimation

@@
 % if you want by leaving the argument blank
-\section{}
-Appendix two text goes here.
+\section{Parameter estimation using LS}
+\begin{equation}
+ \mathbf x_{t+1}=\mathbf x_{t}+T_s \mathbf Q(\mathbf x_t)\mathbf \theta-\alpha T_s\mathbf x_t+T_s\boldsymbol\Gamma^{-1}\int_\Omega\boldsymbol\phi^\top(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+\label{eq:statespacemodel}
+\end{equation}
+where the matrix $\mathbf Q_{n_x \times n_{\theta}}(\mathbf x_t)$ is defined as
+\begin{equation}
+ Q_{n_x \times n_{\theta}}=\boldsymbol\Gamma^{-1}\int_\Omega\boldsymbol\phi(\mathbf r)\int_\Omega f(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)\boldsymbol\psi^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
+\end{equation}
+and $T_s$ is the sampling period. Least Square method can be used as (\ref{eq:statespacemodel}) is linear in parameters. At each time instant we have
 
+\begin{eqnarray}
+ \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0)\mathbf \theta-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+ \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1)\mathbf \theta-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+&\vdots& \nonumber\\
+ \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1})\mathbf \theta-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
+\end{eqnarray}
+in matrix form
+\begin{equation}
+ \begin{bmatrix} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{bmatrix}-\begin{bmatrix} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{bmatrix}=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix}\begin{bmatrix}\mathbf \theta \\ \alpha\end{bmatrix}+T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
+\end{equation}
+or in compact form we have
+\begin{equation}
+ \mathbf Z=\mathbf X \mathbf W+\boldsymbol \xi
+\end{equation}
+where
+\begin{equation}
+ \mathbf Z=\begin{bmatrix} \mathbf x_{1}-\mathbf x_{0}\\\mathbf x_{2}-\mathbf x_{1}\\\vdots\\\mathbf x_{n}-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf X=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf W=\begin{bmatrix}\mathbf \theta \\ \alpha\end{bmatrix} \text{and}\quad \boldsymbol \xi=T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
+\end{equation}
+using the method of Least Square $ \mathbf W$ can be estimated
+\begin{equation}
+ \mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z
+\end{equation}
 % use section* for acknowledgement

### 2010-03-04 ltx/BrainIDE.tex
colored noise derivation is added in the appendix
updated ltx doco to include pde

@@
 \begin{equation}\label{SpikesToPotential}
-v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
+v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'} + de\left( {r,t} \right).
 \end{equation}
-The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity. The post-synaptic response kernel $h(t)$ is described by
+The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity and is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
+The post-synaptic response kernel $h(t)$ is described by
 \begin{equation}\label{SynapticRespKernel}
@@
 \begin{equation}\label{RateBasedInteractions}
-g\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}
+g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'}
 \end{equation}
@@
 \begin{equation}\label{FullDoubleIntModel}
-v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
+v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' dt'+de\left(r,t\right)
 \end{equation}
@@
 \begin{equation}\label{GenForm}
-L\left( {\frac{\partial }{{dt}}} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {r,t} \right),
+L\left( \frac{\partial }{dt} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}  + de\left( r,t \right),
 \end{equation}
@@
 \begin{equation}\label{FinalForm1}
-\frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}  +e\left( {r,t} \right).
+\frac{dv\left( {r,t} \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'}  +de\left( r,t \right).
 \end{equation}
-
+The PDE form of the model is
+\begin{equation}\label{PDE}
+\frac{\partial^2}{\partial t \partial r'} v\left( r,t \right) + \alpha \frac{\partial}{\partial r'} v\left( r,t \right) = w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)  + \frac{\partial}{\partial r'}de\left( {r,t} \right).
+\end{equation}
 % \subsection{Multi-Layer Model}
@@
 \section{State-Space Model}
-We begin the derivation of the state-space model with the discrete time, continuous space IDE neural field model. A one-step Euler method was used to transform the ODE to a discrete time form.
+We begin the derivation of the state-space model with the discrete time, continuous space IDE neural field model.
+A one-step Euler method was used to transform the nonlinear stochastic IDE to a discrete time form.
 \begin{equation}\label{SystemEq}
-\frac{v_{t + 1}\left( \mathbf{r} \right) - v_t(\mathbf{r})}{T_s} = \int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}}  - \alpha {v_t}\left( {\bf{r}} \right) + e_t\left( {\mathbf{r}} \right),
+\frac{v_{t + 1}\left( \mathbf{r} \right) - v_t(\mathbf{r})}{T_s} = \int_\Omega  {k\left( \mathbf{r} , \mathbf{r'} \right)f\left( {v_t\left( \mathbf{r'} \right)} \right)d{\bf{r'}}}  - \alpha v_t\left( \mathbf{r} \right) + e_t\left( \mathbf{r} \right),
 \end{equation}
@@
 % if you want by leaving the argument blank
+\section{Colored noise}
+We have
+\begin{equation}
+v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
+\end{equation}
+where the disturbance $e_t(\mathbf r)$ is a zero-mean normally distributed noise process, spatially coloured but temporally independent, with covariance
+
+\begin{equation}
+cov(e_t(\mathbf{s}),e_{t+\tau}(\mathbf{r}))=
+\begin{cases}
+\beta\left(\mathbf{s}-\mathbf{r}\right), & \tau=0 \\
+0 & \mathrm{otherwise}
+\end{cases}
+\label{eq:FieldCovariance}
+\end{equation}
+The final state-space model is given by
+\begin{equation}
+x_{t + 1} = T_sq(x_t)\theta -\lambda x_t + T_s\Gamma^{-1}\int_\Omega  {\phi ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
+\end{equation}
+then the covariance of the noise term is given by
+\begin{eqnarray}
+\mathbf \Sigma_w&{}={}&T_s^2 \times \mathbf{\Gamma}^{-1}\mathbf E[\int_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right)e_t\left(\mathbf s\right)d\mathbf s\int_{\mathcal{S}}\boldsymbol\phi\left(\mathbf r\right)^{\top}e_t\left(\mathbf r\right)d\mathbf r]\mathbf{\Gamma}_{x}^{- \top} \nonumber \\
+&=&T_s^2 \times\mathbf{\Gamma}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right) \mathbf E[e_t\left(\mathbf s\right)e_t\left(\mathbf r\right)]\boldsymbol\phi\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Gamma}^{- \top} \nonumber\\
+&=&{}T_s^2 \times\mathbf{\Gamma}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right) \beta\left(\mathbf s- \mathbf r \right)\boldsymbol\phi\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Gamma}^{- \top}
+\end{eqnarray}
+
 \section{Parameter estimation using LS}
 \begin{equation}
- \mathbf x_{t+1}=\mathbf x_{t}+T_s \mathbf Q(\mathbf x_t)\mathbf \theta-\alpha T_s\mathbf x_t+T_s\boldsymbol\Gamma^{-1}\int_\Omega\boldsymbol\phi^\top(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+ \mathbf x_{t+1}=\mathbf x_{t}+T_s \mathbf Q(\mathbf x_t)\mathbf \theta-\alpha T_s\mathbf x_t+T_s\boldsymbol\Gamma^{-1}\int_\Omega\boldsymbol\phi(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
 \label{eq:statespacemodel}

### 2010-03-04 scripts/Two_D_model_12122009.m

@@ -44,7 +44,7 @@ sigma3 = 15;
 
 theta1 = 1.00;                                           % amplitudes of connectivity kernels 
 theta2 = -0.9;                                                                                        % Schiff, -1.38
-theta3 = 0.045;
+theta3 = 0.00;
 
 if UseBasisFunctions
     theta = 0.001*[theta1 ; theta2; theta3];               % scaled for basis functions
@@ -67,7 +67,7 @@ field_basis_separation = 2;                             % distance wrt masses, m
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~
 Fs = 1e3;                                               % sampling rate, s^-1
 Ts = 1/Fs;                                              % sampling period, seconds
-t_end = .1;                                              % seconds
+t_end = 1000;                                              % seconds
 NSamples = t_end*Fs;
 time = linspace(0,t_end,NSamples);
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@ -127,7 +127,7 @@ end
 % Disturbance properties
 % ~~~~~~~~~~~~~~~~~~~~~~
 DisturbanceMean = 0*ones(N_field_basis_function,1);
-SigmaDisturbance = 8000*eye(N_field_basis_function,N_field_basis_function);           % no basis decomposition
+SigmaDisturbance = 8000;           % no basis decomposition
 if UseBasisFunctions
     R = chol(Gamma^-1);               % use cholesky decomp
     DisturbanceCovariance = R*SigmaDisturbance*R';

### 2010-03-11 ltx/BrainIDE.tex
changes to eq(1),(5) and (8)
small changes to ltx adding pde

@@
 \end{equation}
-The term $e(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity and is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
+The term $de(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity and is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
 The post-synaptic response kernel $h(t)$ is described by
@@
 \end{equation}
+The spatial derivative of the Weiner process can be calculated since it is smooth in space (colored) although it is temporally white. 
 % \subsection{Multi-Layer Model}

### 2010-03-11 ltx/BrainIDE.tex
added appendix D for clarification

@@
 \begin{equation}\label{SpikesToPotential}
-v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'} + de\left( {r,t} \right).
+v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
 \end{equation}
@@
 \begin{equation}\label{FullDoubleIntModel}
-v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' dt'+de\left(r,t\right)
+v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
 \end{equation}
@@
 \begin{equation}\label{FinalForm1}
-\frac{dv\left( {r,t} \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'}  +de\left( r,t \right).
+dv\left( {r,t} \right) + \alpha v\left( r,t \right)dt = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
 \end{equation}
@@
 % use section* for acknowledgement
+\section{From (5) to (8)}
+I ignore noise here. From equation (\ref{SpikesToPotential}) we can say $h$ is the foundamental solution to the equation
+\begin{equation}
+ LV(r,t)=g(r,t)
+\label{eq:LV}
+\end{equation}
+where $L$ is a temporal differential operator, since $h(t)$ is the foundamental solution to (\ref{eq:LV}) it can be written as a Green's function
+\begin{equation}
+ Lh(t)=\delta(t)
+\end{equation}
+where $L=\alpha+\frac{d}{dt}$ therefore equation (\ref{eq:LV}) becomes:
+\begin{equation}
+\frac{dv(r,t)}{dt}+\alpha v(r,t)=g(r,t)
+\end{equation}
+substituting (\ref{RateBasedInteractions}) for $g(r,t)$ gives
+\begin{equation}
+\frac{dv\left( {r,t} \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'} 
+\end{equation}
+
 \section*{Acknowledgment}

### 2010-03-15 ltx/BrainIDE.tex
Explaination to the derivation
added/updated discrete space-time

@@
 \end{equation}
-%\begin{equation}\label{RateOfPreSynPops}
-%p\left( {v\left( {r,\bar t} \right)} \right) = {\nu_0}u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right)
-%\end{equation}
-%\begin{equation}\label{HeavisideDef}
-%u\left( {v\left( {r,\bar t} \right) - {v_0}\left( r \right)} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   1 & {v\left( {r,\bar t} \right) \ge {v_0}\left( r \right)}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
+
 Even though we will model  $v_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality when constructing the state-space representation in the next section.
@@
 \begin{equation}\label{FinalForm1}
-dv\left( {r,t} \right) + \alpha v\left( r,t \right)dt = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
+dv\left( {r,t} \right) + \alpha v\left( r,t \right)dt = \alpha\int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
 \end{equation}
-The PDE form of the model is
-\begin{equation}\label{PDE}
-\frac{\partial^2}{\partial t \partial r'} v\left( r,t \right) + \alpha \frac{\partial}{\partial r'} v\left( r,t \right) = w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)  + \frac{\partial}{\partial r'}de\left( {r,t} \right).
+
+\section{Discrete Time and Space Model}
+We begin the derivation of the state-space model with the continuous time, continuous space IDE neural field model. 
+Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
+\begin{equation}\label{differential eq}	
+dv\left( r,t \right) = \alpha \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
 \end{equation}
-The spatial derivative of the Weiner process can be calculated since it is smooth in space (colored) although it is temporally white. 
-% \subsection{Multi-Layer Model}
-% \begin{equation}\label{ExcitatoryLayer}
-% \frac{dv_e\left( {r,t} \right)}{{dt}} + \alpha_ev_e\left( {r,t} \right) = \int_\Omega  {w_{ee}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ei}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_e\left( {r,t} \right)
-% \end{equation}
-% \begin{equation}\label{InhibitoryLayer}
-% \frac{dv_i\left( {r,t} \right)}{{dt}} + \alpha_iv_i\left( {r,t} \right) = \int_\Omega  {w_{ie}\left( {r,r'} \right)f\left( v_e\left( r',\bar t \right) \right) + w_{ii}\left( {r,r'} \right)f\left( v_i\left( r',\bar t \right) \right)dr'}  +\varepsilon_i\left( {r,t} \right)
-% \end{equation}
-% The subscript  denotes connectivity from an inhibitory neural element to an excitatory neural element. We can write the model in matrix form
-% \begin{equation}\label{matrixEquation}
-% \left[ {\begin{array}{*{20}{c}}
-%    {\frac{{d{v_e}\left( t \right)}}
-% {{dt}}}  \
-%    {\frac{{d{v_i}\left( t \right)}}
-% {{dt}}}  \
-% 
-%  \end{array} } \right] = \int_\Omega  {\left[ {\begin{array}{*{20}{c}}
-%    {{w_{ee}}\left( {r,r'} \right)} & {{w_{ei}}\left( {r,r'} \right)}  \
-%    {{w_{ie}}\left( {r,r'} \right)} & {{w_{ii}}\left( {r,r'} \right)}  \
-% 
-%  \end{array} } \right]} \left[ {\begin{array}{*{20}{c}}
-%    {f\left( {{v_e}\left( {r',\bar{t}} \right)} \right)}  \
-%    {f\left( {{v_i}\left( {r',\bar{t}} \right)} \right)}  \
-% 
-%  \end{array} } \right]dr' - \left[ {\begin{array}{*{20}{c}}
-%    {{\alpha _e}{v_e}\left( {r,t} \right)}  \
-%    {{\alpha _i}{v_i}\left( {r,t} \right)}  \
-% 
-%  \end{array} } \right] + \left[ {\begin{array}{*{20}{c}}
-%    {{\varepsilon _e}\left( t \right)}  \
-%    {{\varepsilon _i}\left( t \right)}  \
-% 
-%  \end{array} } \right]
-% \end{equation}
-% 
-% \begin{equation}\label{matrix_equation_in_vector_notation}
-%    \frac{d\mathbf{V}(r,t)}{dt} = \int_\Omega \mathbf{W}(r,r')f\left(\mathbf{V}(r,t)\right)dr' - \mathbf{A}\mathbf{V}(r,t) + \mathbf{E}(r,t)
-% \end{equation}
-% 
-% The iEEG observation equation is
-% \begin{equation}\label{iEEGObservationEquation}
-%     y(k,t) = \int_{\Omega} m(k,r)\left(v_e(r,t) + v_i(r,t)\right)dr' + w(k,t)
-% \end{equation}{}
+To simplify the notation, but without loss of generality, \ref{FinalForm1} can be rewritten as
+\begin{equation}\label{differential simplified}
+	dv\left( r,t \right) = \alpha q\left(v(r,t) \right) dt  + d e\left( r,t \right)
+\end{equation}
+A one-step Euler method was used to approximate the nonlinear stochastic IDE to a discrete time form. 
+\begin{equation}\label{euler}
+	v\left(r,t\right) =  v(r,t_0) + \alpha \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
+\end{equation}
+Using an Euler approximation,~\ref{euler} can be approximated at each sampling time by
+\begin{equation}\label{euler approx 1}
+	v\left(r,t_{k+1} \right) =  v(r,t_k) + \alpha q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
+\end{equation}
+which can be rewritten as
+\begin{equation}\label{euler approx 2}
+	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta \alpha q\left(v(r,t_k)\right) + e'(r,t_k)
+\end{equation}
+where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
+(Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$).
+Expanding $q\left(v(r,t_k)\right)$ we have
+\begin{equation}\label{discrete time model}
+	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta \alpha \left( -v\left( r,t_k \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} \right) + e'(r,t_k)
+\end{equation}
+which can be simplified to
+\begin{equation}\label{discrete time model2}
+	v\left(r,t_k + \delta \right) =  (1 - \delta \alpha) v(r,t_k) + \delta \alpha \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} + e'(r,t_k)
+\end{equation}
+Now we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
+\begin{equation}\label{discrete space}
+	v\left(r_{ij},t_k + \delta \right) =  (1 - \delta \alpha)v(r_{ij},t_k) + \delta \alpha \Delta^2 \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\tilde{w}\left( r_{ij},r_{ij}' \right)f\left( v\left( r_{ij}',t_k \right) \right)} }+ e'(r_{i,j},t_k).
+\end{equation}
+where $\tilde{w}(r_{ij},r_{ij}')$ discretized connectivity kernel.
+In Eq~\ref{discrete space} we have used periodic boundary conditions to alleviate problems associated with edge effects.
+The connectivity kernel is in the form of a modified Mexican hat, and is described by the sum of three weighted Gaussian functions as
+\begin{equation}
+	\tilde{w}(r_{ij},r_{ij}') = \mathbf{\theta}^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\mathbf{\sigma})^2} + \frac{\left()\left(r_j'-r_j\right)\Delta\right)^2}{(2\mathbf{\sigma})^2}}
+\end{equation}
+where
+\begin{equation}
+ \mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf \theta_{3}\end{bmatrix},\quad \mathbf{\sigma}=\begin{bmatrix}\mathbf{\sigma}_1\\\mathbf{\sigma}_2\\ \mathbf{\sigma}_3\end{bmatrix}.
+\end{equation}.
+The first Gaussian function (parametrized by $\mathbf{\theta}_1, \mathbf{\sigma}_1$) describes local excitation, the second describes lateral inhibition and the third describes medium range excitation.
 
-% \subsection{Alternate Model Description I}
-% An alternate and equivalent way to remove the temporal integration using the Laplace transform .
-We start by considering a discrete neural mass $i$ with inputs with zero delay from another discrete mass $j$ and
-% \begin{equation}\label{TwoDiscreteMasses}
-% {v_i}\left( t \right) = \int_{ - \infty }^t {{h_j}(t - t'){w_{ij}}p\left( {{v_j}\left( t \right)} \right)dt'},
-% \end{equation}
-% where $w_{ij}$ can be considered the synaptic efficiency from $j$ to $i$. Now we take the Laplace transform $\mathcal{L}(v_i(t))=V(s)$ yielding
-% \begin{eqnarray}
-% % \nonumber to remove numbering (before each equation)
-%   {V_i}\left( s \right) &=& {H_j}\left( s \right){w_{ij}}P\left( {{V_j}\left( s \right)} \right) \nonumber \\
-%    &=& {\left( {s + \alpha} \right)^{ - 1}}{w_{ij}}P\left( {{V_j}\left( s \right)} \right)  \\
-%   \Rightarrow s{V_i}\left( s \right) + \alpha{V_i}\left( s \right) &=& {w_{ij}}P\left( {{V_j}\left( s \right)} \right).
-% \end{eqnarray}
-% Now taking the inverse Laplace transform we get
-% \begin{equation}\label{InverseLaplace}
-% \frac{{d{v_i}\left( t \right)}}{{dt}} + \alpha{v_i}\left( t \right) = {w_{ij}}p\left( {{v_j}\left( t \right)} \right).
-% \end{equation}
-% Next we convert the model from discrete neural masses to a continuum by
-% \begin{equation}\label{Discrete2Continuum}
-% \frac{{dv\left( {r,t} \right)}}{{dt}} + \alpha{v\left( {r,t} \right)} = \int_\Omega  {w\left( {r,r'} \right)p\left( {v\left( {r',\bar t} \right)} \right)dr'}  + e\left( {s,t} \right).
-% \end{equation}
+To generate data will approximate either local field potential recordings or intracranial EEG we have used the observation equation
+\begin{equation}\label{ObservationEquation}
+    y(r_n,t_k') = \int_\Omega  m( r_n,r' ) v( r',t_k' ) dr'  + \varepsilon ( r_n,t_k ),
+\end{equation}
+where $\varepsilon( n )\sim\mathcal{N}(0,\Sigma)$, $n$ indexes the iEEG electrodes, and $m(r_n,r)$ is the observation kernel relating the neural field to measurements accounting for electrodes characteristics (spatial averaging).
+In Eq.~\ref{ObservationEquation} we have indexed time by $t_k'$, which is a decimated version of $t_k$.
 
-%\subsection{Alternate Model Description II}
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.4]{NeuralMassFigure.eps}
-%\caption[NeuralMassModel]{This figure describes the basic interactions of neural masses that constitute the neural field model.}
-%\label{NeuralMassModel}
-%\end{figure*}
-%An alternative description of the model is as follows.
-The model can be thought of as a continuum of neural masses.
-To illustrate this idea, we shall first describe the interaction of discrete neural masses as seen in Figure~\ref{NeuralMassModel}.
-Assuming that post-synaptic potentials sum linearly, the membrane potential at the soma of neuron $i$ is described as
-%\begin{equation}\label{VoltageFromPSPs}
-%{v_i}\left( t \right) = \sum\nolimits_{j,k} {{w_{ij}}{h_{j}}\left( t - {t_k}\right)} u\left( {t - {t_k}} \right),
-%\end{equation}
-%where $w_{ij}$ is the synaptic weight from neuron $j$ to $i$, $h(t)$ is the synaptic response kernel, $S$ is the Heaviside step function and action potential arrive at neuron $i$ at times $t_k$.
-Alternatively the membrane potential can described by the convolution of synaptic response kernel with the pre-synaptic firing rate $r_j(t)$ where
-%\begin{equation}\label{VoltageFromRate}
-%{v_i}\left( t \right) = \sum\nolimits_j {\int_{ - \infty }^t {{w_{ij}}{h_j}\left( {t - t'} \right){r_j}\left( t \right)} } dt'.
-%\end{equation}
-%To convert the equation system into an integral differential system, we shall take derivative of~\ref{EqVoltageFromPSPs} yielding
-%\begin{eqnarray}
-%% \nonumber to remove numbering (before each equation)
-%  \frac{{d{v_i}\left( t \right)}}{{dt}} &=& \sum\nolimits_{j,k} {\left( {{w_{ij}}{h_j}\left( t- {t_k} \right)\frac{d}{{dt}}u\left( {t - {t_k}} \right) + {w_{ij}}u\left( {t - {t_k}} \right)\frac{d}{{dt}}{h_j}\left( t- {t_k} \right)} \right)} \nonumber \\
-%   &=& \sum\nolimits_{j,k} {{w_{ij}}{h_j}\left( t- {t_k} \right)\delta \left( {t - {t_k}} \right)}  - \sum\nolimits_{j,k} {{w_{ij}}u\left( {t - {t_k}} \right)\alpha_j{h_j}\left( t- {t_k} \right)}   \nonumber \\
-%   &=& \sum\nolimits_{j,k} {{w_{ij}}\delta \left( {t - {t_k}} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber  \\
-%   &=& \sum\nolimits_j {{w_{ij}}{\nu_j}\left( t \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j} \nonumber \\
-%   &=& \sum\nolimits_j {{w_{ij}}p\left( {{v_j}\left( t \right)} \right)}  - {v_i}\left( t \right)\sum\nolimits_j {\alpha_j}.
-%\end{eqnarray}
-%This form can easily be extended to represent a continuous field.
+All the model parameters are described in Table 1.
 
-%\subsection{Assumptions and Simplifications}
-%We assume that the propagation delay of action potentials is zero.
-This is a common assumption that is made when modeling intracortical circuits (\textcolor[rgb]{1.00,0.00,0.00}{refs}).
-As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being negligible.
-Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics~\cite{Atay2005}.
-The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences.
-Therefore, the model simply has to be `good enough' for this purpose.
-Starting with this simplified version of the general model is a logical choice.
-The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, not on their spatial location.
-Again, this is a common assumption when dealing with intracortical connectivity (\textcolor[rgb]{1.00,0.00,0.00}{ref}).
-This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible.
-The IDE estimation is derived for a general heterogeneous structure however, for clarity of results we shall only present the heterogeneous case.
-We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population.
-In this case, inhibition can be modeled by having a negative response kernel and excitation with a positive response kernel, where the connectivity kernel provides the (scaled) polarity.
-This reduces the model to a single field.
-We will also assume the activation function $p(.)$ is a Heaviside step function.
-This is in agreement with the work of Schiff and Sauer~\cite{schiff2008kalman}.
-With these assumptions, the model has the form
-%\begin{equation}\label{SimplifiedModel}
-%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {w\left( {r-r'} \right)f\left( {v\left( {r',t} \right)} \right)dr'}  - \alpha{v\left( {r,t} \right)} + e\left( {r,t} \right).
-%\end{equation}
-%In order to make the problem trackable, in terms of model order, we assume that we can decompose the field (membranes voltages) into a set of $n_\phi$ Gaussian basis functions.
-We will also assume that we know the location and width of the basis function that is required to decompose the field.
-The state of the system is the height basis functions, rather than the membrane potential.
-Therefore, the number of basis functions required to decompose the field is equal to the number of states.
-Also, we assume that we can represent the connectivity by a regular grid of three connectivity Gaussian basis functions (corresponding to short, mid and long range connectivity) of known width.
-The height of the connectivity basis functions ($\theta$ parameter) is to be estimated.
-%\subsection{IDE Formulation}
+\begin{tabular}{ccc}
+\hline
+Parameter & Value & Reference\\
+\hline
+$\alpha$ & $100$ s$^{-1}$ &\\
+\hline
+$\nu_0$ & $1$ s$^{-1}$ &\\
+\hline
+$v_0$ & $6$ mV &\\
+\hline
+$\beta$ & $0.56$ spikes/mV$^{-1}$ & \\
+\hline
+$\delta$ & $1\times10^{-4}$ s &\\
+\hline
+$\Delta$ & $1$ &\\
+\hline
+$\theta_1$ &  &\\
+\hline
+$\theta_2$ &  &\\
+\hline
+$\theta_3$ &  &\\
+\hline
+$\sigma_1$ &  &\\
+\hline
+$\sigma_2$ &  &\\
+\hline
+$\sigma_3$ &  &\\
+\hline
+\end{tabular}
 
-%For the state-space derivation, to create an estimator, the model can be reformulated like so
-%\begin{equation}\label{new_spatiotemporal_kernels}
-%\frac{{dv\left( {r,t} \right)}}{{dt}} = \int_\Omega  {k\left( {r - r'} \right)\tilde v\left( {r',t} \right) - \alpha \delta \left( {r - r'} \right)\bar v\left( {r,t} \right)dr'}  + e\left( {r,t} \right)
-%\end{equation}
-%\begin{equation}\label{define_v_tilde}
-%\tilde v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) \ge {v_0}}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end{equation}
-%\begin{equation}\label{define_v_bar}
-%\bar v\left( {r,t} \right) = \left\{ {\begin{array}{*{20}{c}}
-%   {v\left( {r,t} \right)} & {v\left( {r,t} \right) < {v_0}}  \\
-%   0 & {otherwise}  \\
-%\end{array}} \right.
-%\end%equation}
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.3]{ExampleFieldDecomposition.eps}
-% \caption[ExampleFieldDecomposition]{Illustration of a one dimensional field decomposition using 5 Gaussian basis functions, each weighted an element of the state vector.
-Each basis function has a width of 0.01 and is uniformly positioned with a separation of 0.25 (with arbitrary units).}
-% \label{ExampleFieldDecomposition}
-% \end{figure*}
+\section{Reduced Model For Estimation}
 
-%\section{State-Space Neural Field Model}
-%In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
-The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
-\begin{equation}
-% v_{t+1}(\mathbf r)=\int_{\Omega} \alpha \delta(\mathbf r-\mathbf r')\bar v_t(\mathbf r)d \mathbf r'+\int_{\Omega} w(\mathbf r -\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+e_t(\mathbf r)
-%\label{eq:cortexfield}
-%\end{equation}
-%decomposing the field and the kernel we have
-%\begin{equation}
-%\bar v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_t
-%\label{eq:cortexfieldlv0}
-%\end{equation}
-%\begin{equation}
-%\tilde v_t(\mathbf r)=\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_t=\nu_0
-%\label{eq:cortexfieldgv0}
-%\end{equation}
-%\begin{equation}
-% w(\mathbf r -\mathbf r')=\boldsymbol \theta^{\top}\psi(\mathbf r -\mathbf r')
-%\label{eq:kerneldecomposition}
-%\end{equation}
-%Substituting (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:kerneldecomposition}) in (\ref{eq:cortexfield}) we get
-%\begin{equation}
-% \boldsymbol \phi^{\top}(\mathbf r)\bar{\mathbf x}_{t+1}+\boldsymbol \phi^{\top}(\mathbf r)\tilde{\mathbf x}_{t+1}=
-%\int_\Omega\alpha\delta(\mathbf r- \mathbf r')\boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_td\mathbf r'+\int_\Omega\boldsymbol \theta^{\top}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
-%\label{eq:decomposedcortexfield}
-%\end{equation}
-%\begin{equation}
-% \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')\tilde{\mathbf x}_td\mathbf r'+e_t(\mathbf r)
-%\end{equation}
-%by defining
-%\begin{equation}
-% \boldsymbol\Phi(\mathbf r)=\int_{\Omega}\boldsymbol\psi(\mathbf r -\mathbf r')\boldsymbol\phi^{\top}(\mathbf r')d\mathbf r'
-%\label{eq:convolution}
-%\end{equation}
-%we have
-%\begin{equation}
-% \boldsymbol \phi^{\top}(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha \boldsymbol\phi^{\top}(\mathbf r)\bar{\mathbf x}_{t}+\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)\tilde{\mathbf x}_t+e_t(\mathbf r)
-%\label{eq:cortexfieldwithPhi}
-%\end{equation}
-%Premultiplying (\ref{eq:cortexfieldwithPhi}) by $\boldsymbol\phi(\mathbf r) $, and integrating over $\mathbf r$
-%\begin{equation}
-%\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf s(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \phi^{\top}(\mathbf r)d\mathbf r \bar{\mathbf x}_{t}+\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
-%\label{eq:cortexfieldversion2}
-%\end{equation}
-%Now we define
-%\begin{equation}
-% \boldsymbol\Psi_x(\mathbf r)=\int_{\Omega}\boldsymbol\phi(\mathbf r)\boldsymbol\phi^{\top}(\mathbf r)d\mathbf r
-%\label{eq:psix}
-%\end{equation}
-%\begin{equation}
-%  \boldsymbol\Psi_{\theta}(\mathbf r)=\int_{\Omega} \boldsymbol\phi(\mathbf r)\boldsymbol \theta^{\top}\boldsymbol\Phi(\mathbf r)d\mathbf r
-%\label{eq:psitheta}
-%\end{equation}
-%substituting (\ref{eq:psix}) and (\ref{eq:psitheta}) in (\ref{eq:cortexfieldversion2}) we get
-%\begin{equation}
-%\boldsymbol\Psi_x(\mathbf r)(\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1})=\alpha\boldsymbol\Psi_x(\mathbf r) \bar{\mathbf x}_{t}+\boldsymbol\Psi_{\theta}(\mathbf r)\tilde{\mathbf x}_t+\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
-%\end{equation}
-%pre-multiplying both sides by $\boldsymbol\Psi_x^{-1}$
-%\begin{equation}
-%\bar{\mathbf x}_{t+1}+\tilde{\mathbf x}_{t+1}=\alpha\bar{\mathbf x}_{t}+\boldsymbol\Psi_x^{-1}\boldsymbol\Psi_{\theta}\tilde{\mathbf x}_t+\boldsymbol\Psi_x^{-1}\int_{\Omega} \boldsymbol\phi(\mathbf r)e_t(\mathbf r)d\mathbf r
-%\end{equation}
-%????????????????????????????????
-%\subsection{Observation equation}
-%\begin{eqnarray}
-% \mathbf y_t(\mathbf r)&=&\\
-%&=&\int_{\Omega}H(\mathbf r-\mathbf r')v_t(\mathbf r')d\mathbf r'+\boldsymbol\epsilon_t \\
-%&=&\int_{\Omega}H(\mathbf r-\mathbf r')\bar v_t(\mathbf r')d\mathbf r'+\int_{\Omega}H(\mathbf r-\mathbf r')\tilde v_t(\mathbf r')d\mathbf r'+\epsilon_t
-%\label{eq:observationequation}
-%\end{eqnarray}
-%
-% we decompose $ H(\mathbf r-\mathbf r')$ as
-% \begin{equation}
-%  H(\mathbf r-\mathbf r')= \mathbf c^{\top}\mu(\mathbf r-\mathbf r')
-%\label{eq:decomposedobservationkernel}
-%\end{equation}
-%and substituting  (\ref{eq:cortexfieldlv0}), (\ref{eq:cortexfieldgv0}) and (\ref{eq:decomposedobservationkernel}) in (\ref{eq:observationequation}) we get
-%\begin{equation}
-% \mathbf y_t(\mathbf r)=\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\bar{\mathbf x}_{t}d\mathbf r'+\int_{\Omega}\mathbf c^{\top}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')\tilde{\mathbf x}_{t}d\mathbf r'+\epsilon_t
-%\end{equation}
-%and finally we have
-%\begin{equation}
-%\mathbf y_t(\mathbf r)= \begin{bmatrix}\mathbf c^{\top}\mathbf M(\mathbf r)&\mathbf c^{\top}\mathbf M(\mathbf r)\end{bmatrix}\underline{\mathbf x}_t+\epsilon_t
-%\end{equation}
-%where
-%\begin{equation}
-% \mathbf M(\mathbf r)=\int_{\Omega}\mu(\mathbf r-\mathbf r')\phi^{\top}(\mathbf r')d\mathbf r'
-%\end{equation}
-%Next we shall demonstrate the stability of the model and in the following section the estimator for the state vector and connectivity structure is derived.
-
-%\subsection{State-Space Neural Field Model}
-%In this section we shall reconstruct the model in a state-space form that is a novel representation of the neural field equations.
-The benefit of restating the model in this format is that it becomes easier to simulate and allows the connectivity to be inferred from data.
-We begin with the model in the form
-%\begin{eqnarray}\label{InitialModel}
-%% \nonumber to remove numbering (before each equation)
-%  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon_t \left( {r} \right) \nonumber \\
-%   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon_t \left( {r} \right).
-%\end{eqnarray}
-%Next we defining the basis functions the decompositions of the field and connectivity kernel, where $\phi(s)$ is a vector is Gaussian basis functions, $x_t$ is the state, $\psi(r-r')$ is a vector of three connectivity basis functions and $\theta$ is the corresponding weight of the connectivity
-%\begin{equation}\label{FieldDecomp}
-%   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
-%\end{equation}
-%\begin{equation}\label{KernelDecomp}
-%k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right).
-%\end{equation}
-%Assume we know $\phi(r')$ and it is constant, and the form of the activation function $p(.)$ is known, and $\phi(r')$ is independent of $x_t$, then we can uniquely define the function $\rho(.)$ such that
-%\begin{eqnarray}\label{NonlinearState}
-%% \nonumber to remove numbering (before each equation)
-%  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \nonumber \\
-%   &=& \phi ^T\left(r'\right)\rho \left( {{x_t}} \right).
-%\end{eqnarray}
-%Making substitutions of~\ref{FieldDecomp}, \ref{KernelDecomp} and \ref{NonlinearState} into \ref{InitialModel} we get
-%\begin{equation}\label{ModelDecomposed}
-%{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'}\right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon_t \left( {r} \right)
-%\end{equation}
-%Now we define
-%\begin{equation}\label{DefPhi}
-%\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right){\phi ^T}\left( {r'} \right)dr'}.
-%\end{equation}
-%Substituting~\ref{DefPhi} into \ref{ModelDecomposed} we get
-%\begin{equation}\label{Sub2}
-%{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon_t \left( {r} \right).
-%\end{equation}
-%Cross multiplying by $\phi(r)$ in integrating over $r$ gives
-%\begin{equation}\label{CorssMultAndInt}
-%\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
-%\end{equation}
-%Now we define
-%\begin{equation}\label{DefPsix}
-%{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr}
-%\end{equation}
-%\begin{equation}\label{DefPsitheta}
-%{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}.
-%\end{equation}
-%Substituting~\ref{DefPsix} and \ref{DefPsitheta} into \ref{CorssMultAndInt} we get
-%\begin{equation}\label{Subs3}
-%{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
-%\end{equation}
-%Now we isolate the state by inverting $\Psi_x$
-%\begin{equation}\label{IsolateState}
-%{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
-%\end{equation}
-%This gives the state-space model
-%\begin{equation}\label{StateSpaceModel}
-%{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon_t \left( {r} \right)dr}.
-%\end{equation}
-
-\section{State-Space Model}
-We begin the derivation of the state-space model with the discrete time, continuous space IDE neural field model.
-A one-step Euler method was used to transform the nonlinear stochastic IDE to a discrete time form.
-\begin{equation}\label{SystemEq}
-\frac{v_{t + 1}\left( \mathbf{r} \right) - v_t(\mathbf{r})}{T_s} = \int_\Omega  {k\left( \mathbf{r} , \mathbf{r'} \right)f\left( {v_t\left( \mathbf{r'} \right)} \right)d{\bf{r'}}}  - \alpha v_t\left( \mathbf{r} \right) + e_t\left( \mathbf{r} \right),
-\end{equation}
-\begin{equation}\label{SystemEq}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} - T_s\alpha {v_t}\left( {\bf{r}} \right) + v_t(\mathbf{r}) + T_se_t\left( {\mathbf{r}} \right),
-\end{equation}
-\begin{equation}\label{SystemEq}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \mathbf{r'} \right)} \right)d{\bf{r'}}} + (1 - T_s\alpha) v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right),
-\end{equation}
-\begin{equation}\label{SystemEq}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
-\end{equation}
-where $e_t(r)\sim \mathcal{GP}(0,R)$, $\lambda = 1-T_s\alpha$ and $T_s$ is the time step or sampling step.
-
-The observation equation for the model is
-\begin{equation}\label{ObservationEquation}
-    y_t( k ) = \int_\Omega  m( k,\mathbf{r} )v_t( \mathbf{r}\rm ) d\mathbf{r}  + \varepsilon ( k ),
-\end{equation}
-where $\varepsilon( k )\sim\mathcal{N}(0,\Sigma)$, $k$ indexes the iEEG electrodes, and $m(k,r)$ is the observation kernel relating the neural field to EEG measurements accounting for electrodes characteristics.
-
-%To infer the state from observations we can write the likelihood function
-%\begin{equation}\label{Likelihood}
-%p\left( {{y_{1,...,T}}|{v_{1,...,T}}} \right) = \prod\limits_{t = 1}^T {p\left( {{y_t}|{v_t}} \right)} \prod\limits_{t = 2}^T {p\left( {{v_{t + 1}}|{v_t}} \right)} p\left( {{v_0}} \right)
-%\end{equation}
-%where
-%\begin{eqnarray}
-%% \nonumber to remove numbering (before each equation)
-%  p\left( {{y_t}|{v_t}} \right) &=& \mathcal{N}\left( {\int_\Omega  {m\left( {k,r} \right)v_t( r )dr} ,R} \right) \\
-%  p\left( {{v_{t + 1}}|{v_t}} \right) &=& ??? \\
-%  p\left( {{v_0}} \right) &=& \mathcal{GP}\left( {{\mu _0},{\pi _0}} \right).
-%\end{eqnarray}
-%We can not calculate the posterior in this Bayesian model for some reason (Mike and Ken can elaborate), so we need to decompose the field into weighted basis functions.
-
-In order to implement standard estimation techniques we propose a decomposition of the The field using a set of Gaussian basis functions.
+In order to implement standard estimation techniques we propose a decomposition of the field using a set of Gaussian basis functions.
 Decomposition allows a continuous field to be represented by a finite dimensional state vector.
@@
 
-\section{Comparison of Estimated and True Connectivity}
+\section{Comparison of Estimated Parameters and True Parameters}
 
@@
 % use section* for acknowledgement
-\section{From (5) to (8)}
+\section{clarification for the derivation} 
 I ignore noise here. From equation (\ref{SpikesToPotential}) we can say $h$ is the foundamental solution to the equation
 \begin{equation}
- LV(r,t)=g(r,t)
+ Lv(r,t)=g(r,t)
 \label{eq:LV}
@@
 \end{equation}
-where $L=\alpha+\frac{d}{dt}$ therefore equation (\ref{eq:LV}) becomes:
+where $L=1+\tau\frac{d}{dt}$ therefore equation (\ref{eq:LV}) becomes:
 \begin{equation}
-\frac{dv(r,t)}{dt}+\alpha v(r,t)=g(r,t)
+\tau\frac{dv(r,t)}{dt}+ v(r,t)=g(r,t)
 \end{equation}
@@
 \begin{equation}
-\frac{dv\left( {r,t} \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'} 
+\frac{dv\left( {r,t} \right)}{dt} + \frac{1}{\tau} v\left( r,t \right) = \frac{1}{\tau}\int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'} 
 \end{equation}

### 2010-03-15 ltx/BrainIDE.tex
some updates to the paper

@@
 Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
-An estimation frame work for neural field model known as dynamical causal modeling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
+An estimation frame work for neural field models known as dynamical causal modeling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
@@
 In this section, we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
-This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behavior.
+This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
 It is also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations.
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
-The model relates the average number of action potentials $g$ arriving at $r$ to the local post synaptic membrane voltage.
+The model relates the average number of action potentials $g(r,t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(r,t)$.
 The post-synaptic potentials generated at a neuronal population at location $r$ by action potentials arriving from all other connected populations at locations $r'$ can be described by
 \begin{equation}\label{SpikesToPotential}
-v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'} + e\left( {r,t} \right).
+v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'}.
 \end{equation}
-The term $de(r,t)$ can be considered the potential generated by unmodeled inputs and spontaneous background activity and is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
 The post-synaptic response kernel $h(t)$ is described by
@@
 \begin{equation}\label{RateBasedInteractions}
-g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'}
+g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'} + e\left(r,t\right)
 \end{equation}
 where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+The term $de(r,t)$ can be considered the action potentials generated by unmodeled inputs and spontaneous background activity and is a Wiener process with mean $\mu$ incremental covariance $\Sigma_e(r)dt$.
 
@@
 The parameters in equation~\ref{ActivationFunction} are detailed in Table 1.
-By combining equations~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
+By combining Eqs.~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
 \begin{equation}\label{FullDoubleIntModel}
-v\left(r,t\right) = \int\limits_{-\infty}^t\int\limits_\Omega  h\left(t - t'\right)w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' dt'+e\left(r,t\right)
+v\left(r,t\right) = \int\limits_{-\infty}^t h\left(t - t'\right) \left(\int\limits_\Omega  w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' + e\left(r,t\right)\right) dt'
 \end{equation}
@@
 \begin{equation}
-	\tilde{w}(r_{ij},r_{ij}') = \mathbf{\theta}^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\mathbf{\sigma})^2} + \frac{\left()\left(r_j'-r_j\right)\Delta\right)^2}{(2\mathbf{\sigma})^2}}
+	\tilde{w}(r_{ij},r_{ij}') = \mathbf{\theta}^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\mathbf{\sigma})^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\mathbf{\sigma})^2}}
 \end{equation}

### 2010-03-15 ltx/BrainIDE.tex
some updates to the paper

@@
 \end{equation}
-where $L$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
-\begin{equation}\label{GenForm}
-L\left( \frac{\partial }{dt} \right)v\left( {r,t} \right) = \int_\Omega  {w\left( {r,r'} \right)f\left( {v\left( {r',\bar t} \right)} \right)dr'}  + de\left( r,t \right),
-\end{equation}
-where $L$ is a polynomial of order $n$ with constant coefficients that provides an $n^{th}$ order model.
-Most studies considering this model use first or second order time derivatives.
-We shall use the first order model giving
+where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
 \begin{equation}\label{FinalForm1}
-dv\left( {r,t} \right) + \alpha v\left( r,t \right)dt = \alpha\int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
+dv\left( {r,t} \right) + \alpha v\left( r,t \right)dt = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
 \end{equation}
@@
 \begin{equation}\label{differential eq}	
-dv\left( r,t \right) = \alpha \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
+dv\left( r,t \right) =  \left( -\alpha v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
 \end{equation}
@@
 \begin{equation}\label{differential simplified}
-	dv\left( r,t \right) = \alpha q\left(v(r,t) \right) dt  + d e\left( r,t \right)
+	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
 \end{equation}
@@
 \begin{equation}\label{euler}
-	v\left(r,t\right) =  v(r,t_0) + \alpha \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
+	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
 \end{equation}
@@
 \begin{equation}\label{euler approx 1}
-	v\left(r,t_{k+1} \right) =  v(r,t_k) + \alpha q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
+	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
 \end{equation}
@@
 \begin{equation}\label{euler approx 2}
-	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta \alpha q\left(v(r,t_k)\right) + e'(r,t_k)
+	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
 \end{equation}
@@
 \begin{equation}\label{discrete time model}
-	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta \alpha \left( -v\left( r,t_k \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} \right) + e'(r,t_k)
+	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta  \left( -\alpha v\left( r,t_k \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} \right) + e'(r,t_k)
 \end{equation}
@@
 \begin{equation}\label{discrete time model2}
-	v\left(r,t_k + \delta \right) =  (1 - \delta \alpha) v(r,t_k) + \delta \alpha \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} + e'(r,t_k)
+	v\left(r,t_k + \delta \right) =  (1 - \delta \alpha) v(r,t_k) + \delta \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} + e'(r,t_k)
 \end{equation}
@@
 \begin{equation}\label{discrete space}
-	v\left(r_{ij},t_k + \delta \right) =  (1 - \delta \alpha)v(r_{ij},t_k) + \delta \alpha \Delta^2 \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\tilde{w}\left( r_{ij},r_{ij}' \right)f\left( v\left( r_{ij}',t_k \right) \right)} }+ e'(r_{i,j},t_k).
+	v\left(r_{ij},t_k + \delta \right) =  (1 - \delta \alpha)v(r_{ij},t_k) + \delta \Delta^2 \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\tilde{w}\left( r_{ij},r_{ij}' \right)f\left( v\left( r_{ij}',t_k \right) \right)} }+ e'(r_{i,j},t_k).
 \end{equation}
@@
 Decomposition allows a continuous field to be represented by a finite dimensional state vector.
-This allows for the application of standard nonlinear, non-Gaussian state estimation methods such as sequential Monte-Carlo techniques like particle filtering.
+This allows for the application of standard nonlinear, non-Gaussian state estimation methods such as the unscented Kalman filter.
+The abbreviate the notation we use the subscript $t$ to index the current time step and $t+1$ for next time step.
 The field decomposition is described by
 \begin{equation}\label{DefFieldDecomp}
-{v_t}\left( {\bf{r}} \right) = {\phi ^T}\left( {\bf{r}} \right){x_t}.
+v_t\left( \mathbf{r} \right) = \phi ^T\left( \mathbf{r} \right) x_t.
 \end{equation}
-where $\phi(r)$ is the Gaussian basis functions that are scaled by the the state vector. The connectivity kernel can all be decomposed into a set of basis functions
+where $\phi(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector. The connectivity kernel can all be decomposed into a set of basis functions
 \begin{equation}\label{DefKernelDecomp}
-k( \mathbf{r} , \mathbf{r'} ) = \theta^T\psi(\mathbf{r} , \mathbf{r'} )
+\tilde{w}( \mathbf{r} , \mathbf{r'} ) = \theta^T\psi(\mathbf{r} , \mathbf{r'} )
 \end{equation}
 Will will assume we know the parametric form of the basis functions, where the parameter $\theta$ is unknown.
-Each connectivity basis function can be considered a layer in the WC model, representing short range excitation, surround inhibition and long range excitation.
-Making substitutions we get
+Each connectivity basis function can be considered a layer in the WC model, representing short range excitation, surround inhibition and mid-range excitation.
+Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{discrete space} we get
+
+....up to here....
+
 \begin{equation}\label{DecompModel}

### 2010-03-16 ltx/BrainIDE.tex
some more updates to the paper

@@
 \end{equation}
-To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
-\begin{equation}\label{GreensFuncDef}
-Lh\left( t \right) = \delta \left( t \right),
+The rearrange the model into an intergro-differential we take the Laplace transform of~\ref{FullDoubleIntModel} giving
+\begin{equation}
+	V(s) = H(s)G(s).
 \end{equation}
-where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
+Since $H(s) = (s+\alpha)^{-1}$ we can write
+\begin{equation}
+	(s+\alpha)V(s) = G(s).
+\end{equation}
+% To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
+% \begin{equation}\label{GreensFuncDef}
+% Lh\left( t \right) = \delta \left( t \right),
+% \end{equation}
+% where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. 
+Now taking the inverse Laplace transform provides the final form
 \begin{equation}\label{FinalForm1}
-dv\left( {r,t} \right) + \alpha v\left( r,t \right)dt = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
+dv\left( r,t \right) + \alpha v\left( r,t \right)dt = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
 \end{equation}
@@
 \begin{equation}\label{differential simplified}
-	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
+	dv\left( r,t \right) = q\left(v\left(r,t\right) \right) dt  + d e\left( r,t \right)
 \end{equation}
+where $q\left(v\left(r,t\right)\right)$ is the term insides the brackets in Eq.~\ref{differential eq}.
 A one-step Euler method was used to approximate the nonlinear stochastic IDE to a discrete time form.

### 2010-03-16 ltx/BrainIDE.tex
updates to paper from meeting on 16/03/2010

@@
 \begin{equation}\label{SynapticRespKernel}
-h(t) = \left\{ {\begin{array}{*{20}{c}}
-   {\exp ( - \alpha t)} & {t \ge 0}  \\
-   0 & {t < 0}  \\
-\end{array}} \right.
+	h(t) = u(t)\exp{\left(-\alpha t\right)}.
 \end{equation}
-where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant.
+where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $u(t)$ is the Heaviside step function.
 The synaptic response kernel can be more elaborate, using rise and fall time constants, however, this simple form serves our purposes.
@@
 \begin{equation}\label{RateBasedInteractions}
-g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'} + e\left(r,t\right)
+	g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'}
 \end{equation}
 where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
-The term $de(r,t)$ can be considered the action potentials generated by unmodeled inputs and spontaneous background activity and is a Wiener process with mean $\mu$ incremental covariance $\Sigma_e(r)dt$.
-
+The connectivity kernel is a Mexican hat shape described by the sum of weighted Gaussian functions
+\begin{equation}
+	w\left(r,r'\right) = \theta^T \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_w\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_w\right)^2}\right)}
+\end{equation}
+where
+\begin{equation}
+	\mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf \theta_{3}\end{bmatrix},\quad 		\mathbf{\sigma}=\begin{bmatrix}\mathbf{\sigma}_1\\\mathbf{\sigma}_2\\ \mathbf{\sigma}_3\end{bmatrix}.
+\end{equation}
 The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
 \begin{equation}\label{ActivationFunction}
-f\left( {{v_t}\left( {r'} \right)} \right) = \frac{{{\nu _0}}}{{1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - {v}\left(r',\bar{t} \right)} \right)} \right)}}.
+	f\left( v_t\left( r' \right) \right) = \frac{\nu _0\left(r\right)}{1 + \exp \left( \beta \left( v_0\left( r \right) - v\left(r',\bar{t} \right) \right) \right)}.
+\end{equation}
+Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point.
+By combining Eqs.~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
+\begin{equation}\label{FullDoubleIntModel}
+	v\left(r,t\right) = \int_{-\infty}^t \int_\Omega  h\left(t - t'\right) w\left(r,r'\right) f\left( v\left( r',\bar t \right)\right)dr'dt'
+\end{equation}
+% The rearrange the model into an integro-differential we take the Laplace transform of~\ref{FullDoubleIntModel} giving
+% \begin{equation}
+% 	V(s) = H(s)G(s).
+% \end{equation}
+% Since $H(s) = (s+\alpha)^{-1}$ we can write
+% \begin{equation}
+% 	(s+\alpha)V(s) = G(s).
+% \end{equation}
+To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
+\begin{equation}\label{GreensFuncDef}
+	Lh\left( t \right) = \delta \left( t \right),
+\end{equation}
+where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+\begin{equation}\label{FinalForm1}
+	\frac{dv\left( r,t \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'}.
 \end{equation}
 
-Even though we will model  $v_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality when constructing the state-space representation in the next section.
-The parameters in equation~\ref{ActivationFunction} are detailed in Table 1.
-By combining Eqs.~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
-\begin{equation}\label{FullDoubleIntModel}
-v\left(r,t\right) = \int\limits_{-\infty}^t h\left(t - t'\right) \left(\int\limits_\Omega  w\left(r,r'\right)f\left( v\left( r',\bar t \right)\right)dr' + e\left(r,t\right)\right) dt'
+\section{Generating Data}
+To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(r,r') = w\left(|r-r'|\right)$, $\nu_0(r) = \nu_0$ and $v_0(r) = v_0$.
+In addition we assume the synaptic transmission delay is negligible such that $\bar{t}=t$.
+The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system giving
+\begin{equation}\label{DiscreteTimeModel}
+	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + e_t\left(r\right)
 \end{equation}
-The rearrange the model into an intergro-differential we take the Laplace transform of~\ref{FullDoubleIntModel} giving
+where $\delta$ is the time step, $\lambda = 1-\alpha\delta$ and $e_t(r) \sim \mathcal{GP}(0,\Sigma)$.
+The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}.
+To generate iEEG/LFP like data we used the output function
 \begin{equation}
-	V(s) = H(s)G(s).
+	y_{k}\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_{k}\left(r\right)dr'}
 \end{equation}
-Since $H(s) = (s+\alpha)^{-1}$ we can write
+where $r_n$ defines the location of the sensors in the field, $k$ is the time of sampling instances corresponding to an acquisition system and $m(|r-r'|)$ is the output kernel that governs the geometry of pick-up range of sensors where
 \begin{equation}
-	(s+\alpha)V(s) = G(s).
-\end{equation}
-% To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
-% \begin{equation}\label{GreensFuncDef}
-% Lh\left( t \right) = \delta \left( t \right),
-% \end{equation}
-% where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. 
-Now taking the inverse Laplace transform provides the final form
-\begin{equation}\label{FinalForm1}
-dv\left( r,t \right) + \alpha v\left( r,t \right)dt = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'dt}  +de\left( r,t \right).
+	m\left(|r-r'|\right) = \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_m\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_m\right)^2}\right)}.
 \end{equation}
 
-\section{Discrete Time and Space Model}
+\section{Discretized Model for Simulation}
 We begin the derivation of the state-space model with the continuous time, continuous space IDE neural field model. 
@@
 \begin{equation}\label{discrete space}
-	v\left(r_{ij},t_k + \delta \right) =  (1 - \delta \alpha)v(r_{ij},t_k) + \delta \Delta^2 \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\tilde{w}\left( r_{ij},r_{ij}' \right)f\left( v\left( r_{ij}',t_k \right) \right)} }+ e'(r_{i,j},t_k).
+	v\left(r_{ij},t_k + \delta \right) =  \lambda v(r_{ij},t_k) + \delta \Delta^2 \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\tilde{w}\left( r_{ij},r_{ij}' \right)f\left( v\left( r_{ij}',t_k \right) \right)} }+ e'(r_{i,j},t_k).
 \end{equation}
-where $\tilde{w}(r_{ij},r_{ij}')$ discretized connectivity kernel.
-In Eq~\ref{discrete space} we have used periodic boundary conditions to alleviate problems associated with edge effects.
+where $\tilde{w}(r_{ij},r_{ij}')$ discretized connectivity kernel and $\lambda = 1 - \delta \alpha$.
+In Eq.~\ref{discrete space} we have used periodic boundary conditions to alleviate problems associated with edge effects.
 The connectivity kernel is in the form of a modified Mexican hat, and is described by the sum of three weighted Gaussian functions as
@@
  \mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf \theta_{3}\end{bmatrix},\quad \mathbf{\sigma}=\begin{bmatrix}\mathbf{\sigma}_1\\\mathbf{\sigma}_2\\ \mathbf{\sigma}_3\end{bmatrix}.
-\end{equation}.
+\end{equation}
 The first Gaussian function (parametrized by $\mathbf{\theta}_1, \mathbf{\sigma}_1$) describes local excitation, the second describes lateral inhibition and the third describes medium range excitation.
@@
 \begin{equation}\label{ObservationEquation}
-    y(r_n,t_k') = \int_\Omega  m( r_n,r' ) v( r',t_k' ) dr'  + \varepsilon ( r_n,t_k ),
+    y(r_{i_n j_n},t_l) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J}  m( r_{i_n j_n},r_{ij}' ) v( r_{ij}',t_l )  + \varepsilon ( r_{i_n j_n},t_l ),
 \end{equation}
-where $\varepsilon( n )\sim\mathcal{N}(0,\Sigma)$, $n$ indexes the iEEG electrodes, and $m(r_n,r)$ is the observation kernel relating the neural field to measurements accounting for electrodes characteristics (spatial averaging).
-In Eq.~\ref{ObservationEquation} we have indexed time by $t_k'$, which is a decimated version of $t_k$.
+where $\varepsilon( n )\sim\mathcal{N}(0,\Sigma)$, $n$ indexes the iEEG electrodes, and $m(r_n,r)$ is the observation kernel relating the neural field to measurements accounting for electrodes characteristics is described by
+\begin{equation}
+	m( r_{i_n j_n},r_{ij}' ) = e^{\frac{\left(\left(r_i'-r_{i_n}\right)\Delta\right)^2}{\left(2\sigma_4\right)^2} + \frac{\left(\left(r_j'-r_{j_n}\right)\Delta\right)^2}{\left(2\sigma_4\right)^2}}.
+\end{equation}
+In Eq.~\ref{ObservationEquation} we have indexed time by $t_l$ corresponding to the sampling rate of a data acquisition system, where the model is simulated on a much fine time-scale of $t_k$.
+The sensor positions correspond to positions $i_n,j_n$ and are space on a square grid spaced xx units apart, yy units from the edge of the field.
 
@@
 \hline
+$\sigma_4$ &  &\\
+\hline
 \end{tabular}
@@
 \begin{equation}\label{DefFieldDecomp}
-v_t\left( \mathbf{r} \right) = \phi ^T\left( \mathbf{r} \right) x_t.
+v_t\left( \mathbf{r} \right) \approx \phi ^T\left( \mathbf{r} \right) x_t.
 \end{equation}
-where $\phi(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector. The connectivity kernel can all be decomposed into a set of basis functions
+where $\phi(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $x_t$. The connectivity kernel can all be decomposed into a set of basis functions
 \begin{equation}\label{DefKernelDecomp}
-\tilde{w}( \mathbf{r} , \mathbf{r'} ) = \theta^T\psi(\mathbf{r} , \mathbf{r'} )
+\tilde{w}( r_{ij}, r_{ij}' ) = \theta^T\psi\left(r_{ij},r_{ij}'\right)
 \end{equation}
@@
 
-\begin{equation}\label{DecompModel}
-{\phi ^T}\left( \mathbf{r} \right){x_{t+1}} = T_s\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \lambda\phi^T(\mathbf{r})x_t + T_s{e_t}\left( {\mathbf{r}} \right).
+\begin{equation}\label{reduced discrete model}
+	\phi ^T\left( r_{ij} \right)x_{t+1} =  \lambda \phi ^T\left( r_{ij} \right)x_{t+1} + \delta \Delta^2 \theta^T \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\psi\left(r_{ij},r_{ij}'\right)f\left( \phi ^T\left(r_{ij} \right)x_{t+1} \right)} }+ e'(r_{i,j},t_k).
+\end{equation}
+
+\begin{equation}\label{reduced continuous model}
+\phi ^T\left( \mathbf{r} \right)x_{t+1} = T_s\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \lambda\phi^T(\mathbf{r})x_t + T_s{e_t}\left( {\mathbf{r}} \right).
 \end{equation}
@@
 
-\subsection{Discrete Space For Simulation}
-
-In this section we describe a discrete time, discrete space model that we are using for the simulations.
+% \subsection{Discrete Space For Simulation}
+% 
+% In this section we describe a discrete time, discrete space model that we are using for the simulations.
 Now we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta \mathbf{r}$ giving
-\begin{equation}\label{DiscreteSpaceModelij}
-	x_{t+1} = T_s\Gamma ^{ - 1}\sum_i \sum_j  {\phi \left( \mathbf{r} \right)\sum_i\sum_j  {f\left( \phi^T \left( \mathbf{r'} \right) x_t \right)\psi^T \left( \mathbf{r} - \bf{r'} \right)\Delta\mathbf{r'}^2} \Delta\mathbf{r}^2} \theta - \lambda x_t + T_s\sum_i\sum_j  {\phi \left( {\bf{r}} \right)\tilde{e}_t\left( \bf{r} \right)\Delta\mathbf{r}^2}.
-\end{equation}
+% \begin{equation}\label{DiscreteSpaceModelij}
+% 	x_{t+1} = T_s\Gamma ^{ - 1}\sum_i \sum_j  {\phi \left( \mathbf{r} \right)\sum_i\sum_j  {f\left( \phi^T \left( \mathbf{r'} \right) x_t \right)\psi^T \left( \mathbf{r} - \bf{r'} \right)\Delta\mathbf{r'}^2} \Delta\mathbf{r}^2} \theta - \lambda x_t + T_s\sum_i\sum_j  {\phi \left( {\bf{r}} \right)\tilde{e}_t\left( \bf{r} \right)\Delta\mathbf{r}^2}.
+% \end{equation}
 \section{Estimation of the Nonlinear Homogeneous IDE Neural Field Model}
@@
 \appendices
-\section{Ken's Discretization}
-Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
-\begin{equation}\label{differential eq}	
-\tau dv\left( r,t \right) = \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
-\end{equation}
-where $e\left( r,t \right)$ is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
+
+\section{Discrete Time Model}
+
+\section{Numerically Generating Data}
+
+\section{Reduction to Finite State-Space Model For Estimation}
+
+% \section{Ken's Discretization}
+% Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
+% \begin{equation}\label{differential eq}	
+% \tau dv\left( r,t \right) = \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
+% \end{equation}
+% where $e\left( r,t \right)$ is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
 (not too sure about this noise since it needs to be white temporally but coloured spatially - which in continuous space-time I have never seen written ...
 has anyone?)
-To simplify the notation, but without loss of generality, \ref{differential eq} can be rewritten as
-\begin{equation}\label{differential simplified}
-	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
-\end{equation}
-Had $q\left(v(r,t) \right)$ been a linear function in $v$, then \ref{differential simplified} could be rewritten as
-\begin{equation}\label{differential linear}
-	dv\left( r,t \right) = Av(r,t)dt  + d e\left( r,t \right)
-\end{equation}
-Considering temporal sampling instances $\delta$ apart given by $\{t_k = 0,~1,~2, \ldots$ \}, then a solution to \ref{differential linear} at each sampling time is given by
-\begin{equation}\label{linear solution}
-	v(r,t_k+\delta) = \exp\{A(\delta)\}x(t) + \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
-\end{equation}
-Let the discrete time random variable $e'(r,t_k)$ be
-\begin{equation}\label{discrete noise}
-	e'(r,t_k) = \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
-\end{equation}
-then, $e'(r,t_k)$ is a zero mean, temporally white noise term with covariance
-\begin{equation}\label{covariance of noise}
-	E\left[e'(r,t_k),e'^\top(r,t_k) \right] = \int_t^{t+\delta}\exp\{A(t_k+\delta-\tau)\} \Sigma_e(r) \exp\{A(t+\delta-\tau)\} d\tau
-\end{equation}
-
-But we are not so luck as to be able to go from \ref{differential simplified} to \ref{differential linear} and thus I doubt if we can obtain an exact solution to \ref{differential simplified} without an approximation.
+% To simplify the notation, but without loss of generality, \ref{differential eq} can be rewritten as
+% \begin{equation}\label{differential simplified}
+% 	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
+% \end{equation}
+% Had $q\left(v(r,t) \right)$ been a linear function in $v$, then \ref{differential simplified} could be rewritten as
+% \begin{equation}\label{differential linear}
+% 	dv\left( r,t \right) = Av(r,t)dt  + d e\left( r,t \right)
+% \end{equation}
+% Considering temporal sampling instances $\delta$ apart given by $\{t_k = 0,~1,~2, \ldots$ \}, then a solution to \ref{differential linear} at each sampling time is given by
+% \begin{equation}\label{linear solution}
+% 	v(r,t_k+\delta) = \exp\{A(\delta)\}x(t) + \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
+% \end{equation}
+% Let the discrete time random variable $e'(r,t_k)$ be
+% \begin{equation}\label{discrete noise}
+% 	e'(r,t_k) = \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
+% \end{equation}
+% then, $e'(r,t_k)$ is a zero mean, temporally white noise term with covariance
+% \begin{equation}\label{covariance of noise}
+% 	E\left[e'(r,t_k),e'^\top(r,t_k) \right] = \int_t^{t+\delta}\exp\{A(t_k+\delta-\tau)\} \Sigma_e(r) \exp\{A(t+\delta-\tau)\} d\tau
+% \end{equation}
+% 
+% But we are not so luck as to be able to go from \ref{differential simplified} to \ref{differential linear} and thus I doubt if we can obtain an exact solution to \ref{differential simplified} without an approximation.
 Agreed?
-
-A possible approximate solution is the one you have already used. Thus, interpreting the difference equation \ref{differential simplified} as an integral equation gives
-\begin{equation}\label{euler}
-	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
-\end{equation}
-Using an Euler approximation, \ref{euler} can be approximated at each sampling time by
-\begin{equation}\label{euler approx 1}
-	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
-\end{equation}
-which can be rewritten as
-\begin{equation}\label{euler approx 2}
-	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
-\end{equation}
-where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
+% 
+% A possible approximate solution is the one you have already used. Thus, interpreting the difference equation \ref{differential simplified} as an integral equation gives
+% \begin{equation}\label{euler}
+% 	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
+% \end{equation}
+% Using an Euler approximation, \ref{euler} can be approximated at each sampling time by
+% \begin{equation}\label{euler approx 1}
+% 	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
+% \end{equation}
+% which can be rewritten as
+% \begin{equation}\label{euler approx 2}
+% 	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
+% \end{equation}
+% where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
 (Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$)

### 2010-03-17 ltx/BrainIDE.tex
further updates to paper from meeting on 16/03/2010

@@
 \begin{equation}\label{RateBasedInteractions}
-	g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'}
+	g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'} + I\left(r,t\right)
 \end{equation}
 where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+The term $I\left(r,t\right)$ accounts for spontaneous activity of the neural populations.
 The connectivity kernel is a Mexican hat shape described by the sum of weighted Gaussian functions
-\begin{equation}
+\begin{equation}\label{Connectivity Kernel}
 	w\left(r,r'\right) = \theta^T \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_w\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_w\right)^2}\right)}
@@
 \begin{equation}
-	\mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf \theta_{3}\end{bmatrix},\quad 		\mathbf{\sigma}=\begin{bmatrix}\mathbf{\sigma}_1\\\mathbf{\sigma}_2\\ \mathbf{\sigma}_3\end{bmatrix}.
+	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\sigma=\begin{bmatrix}\sigma_{m1}\\\sigma_{m2}\\ \sigma_{m3}\end{bmatrix}.
 \end{equation}
@@
 \begin{equation}\label{FullDoubleIntModel}
-	v\left(r,t\right) = \int_{-\infty}^t \int_\Omega  h\left(t - t'\right) w\left(r,r'\right) f\left( v\left( r',\bar t \right)\right)dr'dt'
+	v\left(r,t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(r,r'\right) f\left( v\left( r',\bar t \right)\right)dr' + I(r,t) \right)dt'
 \end{equation}
@@
 \begin{equation}\label{FinalForm1}
-	\frac{dv\left( r,t \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'}.
+	\frac{dv\left( r,t \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'} + I\left(r,t\right).
 \end{equation}
@@
 In addition we assume the synaptic transmission delay is negligible such that $\bar{t}=t$.
-The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system giving
+The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system and account for uncertainty in the model giving
 \begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + e_t\left(r\right)
+	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I_t\left(r\right) + e_t\left(r\right)
 \end{equation}
@@
 The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}.
-To generate iEEG/LFP like data we used the output function
+To generate iEEG/LFP data we used the output function
 \begin{equation}
-	y_{k}\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_{k}\left(r\right)dr'}
+	y_t\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r\right)dr'}
 \end{equation}
-where $r_n$ defines the location of the sensors in the field, $k$ is the time of sampling instances corresponding to an acquisition system and $m(|r-r'|)$ is the output kernel that governs the geometry of pick-up range of sensors where
+where $r_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors. The output kernel $m(|r-r'|)$ governs the geometry of pick-up range of sensors where
 \begin{equation}
@@
 
-\section{Discretized Model for Simulation}
-We begin the derivation of the state-space model with the continuous time, continuous space IDE neural field model. 
-Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
-\begin{equation}\label{differential eq}	
-dv\left( r,t \right) =  \left( -\alpha v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
-\end{equation}
-To simplify the notation, but without loss of generality, \ref{FinalForm1} can be rewritten as
-\begin{equation}\label{differential simplified}
-	dv\left( r,t \right) = q\left(v\left(r,t\right) \right) dt  + d e\left( r,t \right)
-\end{equation}
-where $q\left(v\left(r,t\right)\right)$ is the term insides the brackets in Eq.~\ref{differential eq}.
-A one-step Euler method was used to approximate the nonlinear stochastic IDE to a discrete time form.
-\begin{equation}\label{euler}
-	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
-\end{equation}
-Using an Euler approximation,~\ref{euler} can be approximated at each sampling time by
-\begin{equation}\label{euler approx 1}
-	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
-\end{equation}
-which can be rewritten as
-\begin{equation}\label{euler approx 2}
-	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
-\end{equation}
-where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
-(Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$).
-Expanding $q\left(v(r,t_k)\right)$ we have
-\begin{equation}\label{discrete time model}
-	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta  \left( -\alpha v\left( r,t_k \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} \right) + e'(r,t_k)
-\end{equation}
-which can be simplified to
-\begin{equation}\label{discrete time model2}
-	v\left(r,t_k + \delta \right) =  (1 - \delta \alpha) v(r,t_k) + \delta \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t_k \right)} \right)dr'} + e'(r,t_k)
-\end{equation}
-Now we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
-\begin{equation}\label{discrete space}
-	v\left(r_{ij},t_k + \delta \right) =  \lambda v(r_{ij},t_k) + \delta \Delta^2 \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\tilde{w}\left( r_{ij},r_{ij}' \right)f\left( v\left( r_{ij}',t_k \right) \right)} }+ e'(r_{i,j},t_k).
-\end{equation}
-where $\tilde{w}(r_{ij},r_{ij}')$ discretized connectivity kernel and $\lambda = 1 - \delta \alpha$.
-In Eq.~\ref{discrete space} we have used periodic boundary conditions to alleviate problems associated with edge effects.
-The connectivity kernel is in the form of a modified Mexican hat, and is described by the sum of three weighted Gaussian functions as
-\begin{equation}
-	\tilde{w}(r_{ij},r_{ij}') = \mathbf{\theta}^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\mathbf{\sigma})^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\mathbf{\sigma})^2}}
-\end{equation}
-where
-\begin{equation}
- \mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf \theta_{3}\end{bmatrix},\quad \mathbf{\sigma}=\begin{bmatrix}\mathbf{\sigma}_1\\\mathbf{\sigma}_2\\ \mathbf{\sigma}_3\end{bmatrix}.
-\end{equation}
-The first Gaussian function (parametrized by $\mathbf{\theta}_1, \mathbf{\sigma}_1$) describes local excitation, the second describes lateral inhibition and the third describes medium range excitation.
-
-To generate data will approximate either local field potential recordings or intracranial EEG we have used the observation equation
-\begin{equation}\label{ObservationEquation}
-    y(r_{i_n j_n},t_l) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J}  m( r_{i_n j_n},r_{ij}' ) v( r_{ij}',t_l )  + \varepsilon ( r_{i_n j_n},t_l ),
-\end{equation}
-where $\varepsilon( n )\sim\mathcal{N}(0,\Sigma)$, $n$ indexes the iEEG electrodes, and $m(r_n,r)$ is the observation kernel relating the neural field to measurements accounting for electrodes characteristics is described by
-\begin{equation}
-	m( r_{i_n j_n},r_{ij}' ) = e^{\frac{\left(\left(r_i'-r_{i_n}\right)\Delta\right)^2}{\left(2\sigma_4\right)^2} + \frac{\left(\left(r_j'-r_{j_n}\right)\Delta\right)^2}{\left(2\sigma_4\right)^2}}.
-\end{equation}
-In Eq.~\ref{ObservationEquation} we have indexed time by $t_l$ corresponding to the sampling rate of a data acquisition system, where the model is simulated on a much fine time-scale of $t_k$.
-The sensor positions correspond to positions $i_n,j_n$ and are space on a square grid spaced xx units apart, yy units from the edge of the field.
-
 All the model parameters are described in Table 1.
 
-\begin{tabular}{ccc}
+\begin{tabular}{|c|c|c|}
 \hline
@@
 \hline
-$\sigma_1$ &  &\\
+$\sigma_{w1}$ &  &\\
 \hline
-$\sigma_2$ &  &\\
+$\sigma_{w2}$ &  &\\
 \hline
-$\sigma_3$ &  &\\
+$\sigma_{w3}$ &  &\\
 \hline
-$\sigma_4$ &  &\\
+$\sigma_m$ &  &\\
 \hline
@@
 \section{Reduced Model For Estimation}
-
-In order to implement standard estimation techniques we propose a decomposition of the field using a set of Gaussian basis functions.
+In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions.
 Decomposition allows a continuous field to be represented by a finite dimensional state vector.
 This allows for the application of standard nonlinear, non-Gaussian state estimation methods such as the unscented Kalman filter.
-The abbreviate the notation we use the subscript $t$ to index the current time step and $t+1$ for next time step.
 The field decomposition is described by
 \begin{equation}\label{DefFieldDecomp}
-v_t\left( \mathbf{r} \right) \approx \phi ^T\left( \mathbf{r} \right) x_t.
+	v_t\left(r\right) \approx \phi ^T\left(r\right) x_t
 \end{equation}
-where $\phi(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $x_t$. The connectivity kernel can all be decomposed into a set of basis functions
+where $\phi(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $x_t$.
+As described in Eq.~\ref{Connectivity Kernel} the connectivity kernel can also be considered a decomposition into a set of basis functions in
 \begin{equation}\label{DefKernelDecomp}
-\tilde{w}( r_{ij}, r_{ij}' ) = \theta^T\psi\left(r_{ij},r_{ij}'\right)
+	\tilde{w}( |r-r'| ) = \theta^T\psi\left(|r-r'|\right)
 \end{equation}
-Will will assume we know the parametric form of the basis functions, where the parameter $\theta$ is unknown.
+Will will assume we know the parametric form of the connectivity basis functions, where the parameter $\theta$ is unknown.
 Each connectivity basis function can be considered a layer in the WC model, representing short range excitation, surround inhibition and mid-range excitation.
-Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{discrete space} we get
+Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
+\begin{equation}\label{reduced continuous model}
+	\phi^T\left( r \right)x_{t+1} = \delta\theta^T\int_\Omega  {\psi \left(|r-r'|\right)f\left( \phi ^T\left(r'\right)x_t \right)dr'}  - \lambda\phi^T\left(r\right)x_t + \delta I_t\left(r\right) + e_t\left(r\right).
+\end{equation}
+By defining the term
+\begin{equation}\label{DefGamma}
+	\Gamma  = \int_\Omega  {\phi \left(r\right)\phi ^T\left(r\right)dr}
+\end{equation}
+and manipulating the model (see Appendix~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model
+\begin{eqnarray}\label{Homogeneous SS Model}
+	x_{t+1} &=& \delta\Gamma^{ - 1}\int_\Omega {\phi\left(r\right) \int_\Omega {f\left(\phi^T\left(r'\right)x_t\right)\psi^T \left(|r-r'|\right)dr'} dr} \theta - \lambda x_t + \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\phi\left(r\right)\tilde{e}_t\left(r\right)dr} \\
+	&=&\delta q(x_t) \theta -\lambda x_t + + \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\phi(r)\tilde{e}_t(r)dr}
+\end{eqnarray}
+where $\tilde{e}_t\left(r\right) \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
+\begin{eqnarray}\label{ObservationEquation}
+    y_t( r_n ) &=& \int_\Omega  m\left(|r_n-r|\right)\phi^T\left(r\right) dr x_t  + \varepsilon_t ( r_n ) \\
+	&=& C x_t + \varepsilon_t ( r_n ).
+\end{eqnarray}
 
-....up to here....
-
-\begin{equation}\label{reduced discrete model}
-	\phi ^T\left( r_{ij} \right)x_{t+1} =  \lambda \phi ^T\left( r_{ij} \right)x_{t+1} + \delta \Delta^2 \theta^T \sum_{i=-I}^{i=I}{\sum_{j=-J}^{j=J}{\psi\left(r_{ij},r_{ij}'\right)f\left( \phi ^T\left(r_{ij} \right)x_{t+1} \right)} }+ e'(r_{i,j},t_k).
-\end{equation}
-
-\begin{equation}\label{reduced continuous model}
-\phi ^T\left( \mathbf{r} \right)x_{t+1} = T_s\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\mathbf{r'}}} \right)f\left( {{\phi ^T}\left( {{\mathbf{r'}}} \right){x_t}} \right)d{\mathbf{r'}}}  - \lambda\phi^T(\mathbf{r})x_t + T_s{e_t}\left( {\mathbf{r}} \right).
-\end{equation}
-To isolate the state we cross multiply by $\phi(\mathbf{r})$ and integrate over $\mathbf{r}$
-\begin{equation}\label{Poo}
-\int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}{x_{t+1}}}  = T_s\int_\Omega  {\phi ( \mathbf{r} )\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}}  - \lambda\int_\Omega \phi(\mathbf{r})\phi^T(\mathbf{r})d\mathbf{r} x_t  + T_s\int_\Omega  {\phi \left( {\mathbf{r}} \right)e_t\left( {\mathbf{r}} \right)d{\mathbf{r}}}.
-\end{equation}
-Now we define
-\begin{equation}\label{DefGamma}
-\Gamma  = \int_\Omega  {\phi \left( {\bf{r}} \right){\phi ^T}\left( {\bf{r}} \right)d{\bf{r}}}.
-\end{equation}
-Substituting equation~\ref{DefGamma} into \ref{Poo} and rearranging gives
-\begin{equation}\label{SS Model}
-{x_{t+1}} = T_s{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)\theta^T\int_\Omega  {\psi \left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)d{\bf{r'}}} d{\bf{r}}} - \lambda x_t + T_s{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)e_t\left( {\bf{r}} \right)d{\bf{r}}}.
-\end{equation}
-We can rearrange to get
-\begin{equation}\label{Homogeneous SS Model}
-	x_{t+1} = T_s\Gamma ^{ - 1}\int_\Omega  {\phi \left( {\bf{r}} \right)\int_\Omega  {f\left( {{\phi ^T}\left( {{\bf{r'}}} \right){x_t}} \right)\psi^T \left( {{\bf{r}} - {\bf{r'}}} \right)d{\bf{r'}}} d{\bf{r}}}\theta - \lambda x_t + T_s{\Gamma ^{ - 1}}\int_\Omega  {\phi \left( {\bf{r}} \right)e_t\left( {\bf{r}} \right)d{\bf{r}}}.
-\end{equation}
-The disturbance term can be rewritten as 
-\begin{equation}
-	\Gamma ^{ - 1}\int_\Omega  {\phi \left( \bf{r} \right)e_t\left( \bf{r} \right)d\bf{r}} = \int_\Omega  {\phi \left( \bf{r} \right)\tilde{e}_t\left( \bf{r} \right)d\bf{r}},
-\end{equation}
-where $\tilde{e}_t(r)~N(0,R'R)$ and $R'$ is the Cholesky decomposition of $\Gamma^{-1}$. This provides the final state-space model
-\begin{equation}\label{AbbrevSSModel}
-x_{t + 1} = T_sq(x_t)\theta -\lambda x_t + T_s\int_\Omega  {\phi ( \mathbf{r} )\tilde{e}_t( \mathbf{r} )d\mathbf{r}}
-\end{equation}
-with observation equation
-\begin{equation}\label{ObservationEquation}
-    y_t( k ) = \int_\Omega  m( k,\mathbf{r} )\phi^T( \mathbf{r} ) d\mathbf{r}x_t  + \varepsilon ( k ),
-\end{equation}
-
-% \subsection{Discrete Space For Simulation}
-% 
-% In this section we describe a discrete time, discrete space model that we are using for the simulations.
-Now we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta \mathbf{r}$ giving
-% \begin{equation}\label{DiscreteSpaceModelij}
-% 	x_{t+1} = T_s\Gamma ^{ - 1}\sum_i \sum_j  {\phi \left( \mathbf{r} \right)\sum_i\sum_j  {f\left( \phi^T \left( \mathbf{r'} \right) x_t \right)\psi^T \left( \mathbf{r} - \bf{r'} \right)\Delta\mathbf{r'}^2} \Delta\mathbf{r}^2} \theta - \lambda x_t + T_s\sum_i\sum_j  {\phi \left( {\bf{r}} \right)\tilde{e}_t\left( \bf{r} \right)\Delta\mathbf{r}^2}.
-% \end{equation}
-\section{Estimation of the Nonlinear Homogeneous IDE Neural Field Model}
+\section{Estimation of the IDE Neural Field Model using Unscented Kalman Filter with RTS Smooter}
 
@@
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex,
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-%
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
-
 \section{Conclusion}
-The conclusion goes here.
 
@@
 
-\section{Discrete Time Model}
+\section{Discrete Time Model}\label{Time Discretization}
+Using a one-step Euler method we perform the time discretization by
+To form the IDE neural field model a time discretization must be perform. We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by
+\begin{equation}\label{Euler Approximation}	
+\frac{v\left( r,t+\delta \right) - v\left( r,t\right)}{\delta} =   -\alpha v\left( r,t \right) + \int_\Omega  {w\left( |r-r'| \right)f\left( {v\left( r',t \right)} \right)dr'} + I\left(r,t\right).
+\end{equation}
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging Eq.~\ref{Euler Approximation} we get
+\begin{eqnarray}\label{Euler Approximation}	
+v_{t+1}\left( r\right) &=& v_t\left( r\right) -\delta \alpha v_t\left( r\right) + \delta \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + \delta I_t\left(r\right) \\
+&=& \lambda v_t(r) + \delta \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + \delta I_t\left(r\right)
+\end{eqnarray}
+The discrete time form of the model is
+\begin{equation}\label{Discrete Time Model1}
+	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I\left(r,t\right).
+\end{equation}
+where $\lambda = 1 - \delta \alpha$.
 
-\section{Numerically Generating Data}
+\section{Numerical Solution to IDE Model}\label{Space Discretization}
+To solve the PDE we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
+\begin{equation}\label{discrete space}
+	v_{t+1}\left(r_{ij}\right) =  \lambda v_t(r_{ij}) + \delta \Delta^2 \sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{\tilde{w}\left( |r_{ij}-r_{ij}'| \right)f\left( v_t\left( r_{ij}'\right) \right)} } + \delta I_t\left(r\right) + \tilde{e}_t(r_{i,j})
+\end{equation}
+where $\tilde{e}_t(r_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$ and $\tilde{w}(|r_{ij}-r_{ij}'|)$ discretized connectivity kernel described by
+\begin{equation}\label{Discrete Connectivity Kernel}
+	\tilde{w}(r_{ij},r_{ij}') = \theta^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
+\end{equation}
+The observation equation and kernel were discretized in the same way by
+\begin{equation}\label{Discrete Observation Equation}
+    y_k\left(r_{i_n j_n}\right) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J} \tilde{m}( |r_{i_n j_n}-r_{ij}'| ) v_k\left(r_{ij}'\right)  + \varepsilon_k( r_{i_n j_n})
+\end{equation}
+where
+\begin{equation}\label{Discrete Observation Kernel}
+	\tilde{m}(|r_{ij}-r_{ij}'|) = e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
+\end{equation}
+We have used periodic boundary conditions to alleviate problems associated with edge effects.
 
-\section{Reduction to Finite State-Space Model For Estimation}
-
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
+Starting from Eq.~\ref{reduced continuous model} we crossing multiply and integrate over the field to get
+\begin{equation}\label{Poo}
+	\int_\Omega  {\phi \left(r\right)\phi^T\left(r\right) dr} x_{t+1} = \delta \int_\Omega  {\phi (r) \theta^T \int_\Omega  {\psi \left(|r-r'|\right)f\left(\phi^T\left(r'\right) x_t \right)dr'}dr}  - \lambda\int_\Omega {\phi(r)\phi^T(r)dr} x_t + \delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\phi \left(r\right) e_t\left(r\right)dr}.
+\end{equation}
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\Gamma^{-1}$ gives the state-space model
+\begin{equation}\label{Homogeneous SS Model}
+	x_{t+1} = \delta\Gamma^{ - 1}\int_\Omega {\phi\left(r\right) \int_\Omega {f\left(\phi^T\left(r'\right)x_t\right)\psi^T \left(|r-r'|\right)dr'} dr} \theta - \lambda x_t + \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \Gamma^{-1}\int_\Omega{\phi\left(r\right)e_t\left(r\right)dr}.
+\end{equation}
+The disturbance term can be rewritten as 
+\begin{equation}
+	\Gamma ^{ - 1}\int_\Omega  {\phi \left(r\right)e_t\left(r\right)dr} = \int_\Omega{\phi\left(r\right)\tilde{e}_t\left(r\right)dr},
+\end{equation}
+where $\tilde{e}_t\left(r\right) \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. This provides the final simplified state-space model.
 % \section{Ken's Discretization}

### 2010-03-17 ltx/BrainIDE.tex
further updates to paper from meeting on 16/03/2010

@@
 
-\section{Reduced Model For Estimation}
+\section{Derivation of Finite Dimensional State-Space Model}
 In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions.
@@
 
-\section{Estimation of the IDE Neural Field Model using Unscented Kalman Filter with RTS Smooter}
+\section{Spectral Analysis and Decomposition}
+
+\section{State and Parameter Estimation}
+The unscented Kalman filter was used for the state estimation (reference the Julier and Uhlmann paper).
+This method is appropriate for state estimation of stochastic nonlinear dynamical systems.
+Alternatives to this approach are the extended Kalman filter (ref?) (EKF) and sequential Monte Carlo (SMC) filtering (ref?).
+The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) of the state transition equation at each time step.
+The linearization maintains the Gaussianality in the model.
+The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution, whilst maintaining the nonlinearity in the system.
+This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides a second order approximation.
+In addition, the computational requirements of the UKF are smaller than the EKF, since the EKF computes the Jacobian at each time step, where the UKF does not.
+SMC filtering (particle filtering) can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
+However, this method is not appropriate for our problem, since it is not feasible for high dimensional systems, due to computation demands.
+The approximation of the state density is made by propagating the so called sigma points through the state-space model.
+The sigma points describe the mean and covariance of the state estimate.
+The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution.
+To explain the operation of the UKF we begin by explain the traditional Kalman filter with the state-space model
+\begin{eqnarray}
+	x_t = q(x_t,\kappa) + \tilde{e}_t \\
+	y_t = z(x_t) + \varepsilon_t,
+\end{eqnarray}
+where $\kappa$ represents the systems parameters.
 

### 2010-03-17 ltx/BrainIDE.tex
Some minor changes to the derivations and some questions

@@
 This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
+\begin{todo}
+	{Really need to add some citations here.}
+\end{todo}
 It is also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations. 
+\begin{todo}
+	{Same here.}
+\end{todo}
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
@@
 \end{equation}
+\begin{todo}
+	{Is this equation correct? Is it a convolution in time?}
+\end{todo}
 The post-synaptic response kernel $h(t)$ is described by
@@
 \end{equation}
+\begin{todo}
+	{Do we really need this representation with $\bar t$. It makes convolution look wrong.}
+\end{todo}
 where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
@@
 \end{equation}
-The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
+\begin{todo}
+	{Parham ... how are you writing this?}
+\end{todo}The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
 \begin{equation}\label{ActivationFunction}
-	f\left( v_t\left( r' \right) \right) = \frac{\nu _0\left(r\right)}{1 + \exp \left( \beta \left( v_0\left( r \right) - v\left(r',\bar{t} \right) \right) \right)}.
+	f\left( v\left( r', \bar t \right) \right) = \frac{\nu _0\left(r\right)}{1 + \exp \left( \beta \left( v_0\left( r \right) - v\left(r',\bar{t} \right) \right) \right)}.
 \end{equation}
@@
 \begin{equation}
-	y_t\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r\right)dr'}
+	y_t\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'}
 \end{equation}
@@
 \end{equation}
-Will will assume we know the parametric form of the connectivity basis functions, where the parameter $\theta$ is unknown.
-Each connectivity basis function can be considered a layer in the WC model, representing short range excitation, surround inhibition and mid-range excitation.
+We will assume we know the parametric form of the connectivity basis functions, where the parameter $\theta$ is unknown.
+Each connectivity basis function can be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
 Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
@@
 \end{eqnarray}
+\begin{todo}{Define q}\end{todo}
 where $\tilde{e}_t\left(r\right) \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
@@
 \end{eqnarray}
+\begin{todo}{Define C}\end{todo}
 
@@
 \section{Discrete Time Model}\label{Time Discretization}
-Using a one-step Euler method we perform the time discretization by
 To form the IDE neural field model a time discretization must be perform. We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( r\right) &=& v_t\left( r\right) -\delta \alpha v_t\left( r\right) + \delta \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + \delta I_t\left(r\right) \\
-&=& \lambda v_t(r) + \delta \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + \delta I_t\left(r\right)
+v_{t+1}\left( r\right) &=& v_t\left( r\right) -\delta \alpha v_t\left( r\right) + \delta \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + \delta I_t\left(r\right)
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I\left(r,t\right).
+	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I_t\left(r\right).
 \end{equation}
@@
 \section{Numerical Solution to IDE Model}\label{Space Discretization}
-To solve the PDE we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
+To solve the convolution integral in \ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
 \begin{equation}\label{discrete space}
@@
 \section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
-Starting from Eq.~\ref{reduced continuous model} we crossing multiply and integrate over the field to get
+Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\phi(r)$ and integrate over the spatial domain $\Omega$ to get
 \begin{equation}\label{Poo}
@@
 \end{equation}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\Gamma^{-1}$ gives the state-space model
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\Gamma^{-1}$ gives 
 \begin{equation}\label{Homogeneous SS Model}
@@
 \end{equation}
-where the disturbance $e_t(\mathbf r)$ is a zero-mean normally distributed noise process, spatially coloured but temporally independent, with covariance
+where the disturbance $e_t(\mathbf r)$ is a zero-mean normally distributed noise process, spatially coloured but temporally white, with covariance
 

### 2010-03-17 ltx/BrainIDE.tex
further updates to paper from meeting on 16/03/2010

@@
 \begin{todo}
-	{Is this equation correct? Is it a convolution in time?}
+	{Is this equation correct? Is it a convolution in time? Dean: yes}
 \end{todo}
@@
 \begin{todo}
-	{Do we really need this representation with $\bar t$. It makes convolution look wrong.}
+	{Do we really need this representation with $\bar t$.
+It makes convolution look wrong.
+DF: Don't need since we dont include delays.
+The motivation was to be general at the beginning, and for everyone to understand how the model is used elsewhere.}
 \end{todo}
@@
 The connectivity kernel is a Mexican hat shape described by the sum of weighted Gaussian functions
-\begin{equation}\label{Connectivity Kernel}
-	w\left(r,r'\right) = \theta^T \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_w\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_w\right)^2}\right)}
-\end{equation}
+\begin{eqnarray}\label{Connectivity Kernel}
+	w\left(r,r'\right) &=& \theta^T \psi\left(r,r'\right) \\
+	\psi\left(r,r'\right) &=&\exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_w (r'-r)\right)}
+\end{eqnarray}
 where
 \begin{equation}
-	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\sigma=\begin{bmatrix}\sigma_{m1}\\\sigma_{m2}\\ \sigma_{m3}\end{bmatrix}.
+	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
 \end{equation}
 \begin{todo}
-	{Parham ... how are you writing this?}
+	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.}
 \end{todo}The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
@@
 \begin{equation}
-	m\left(|r-r'|\right) = \exp{\left(-\frac{\left(r_x - r_{x_n}\right)^2}{\left(2\sigma_m\right)^2}-\frac{\left(r_y - r_{y_n}\right)^2}{\left(2\sigma_m\right)^2}\right)}.
+	m\left(|r-r'|\right) = \exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_m (r'-r)\right)}.
 \end{equation}
@@
 \section{Spectral Analysis and Decomposition}
+This section provides
 
@@
 \section{Numerical Solution to IDE Model}\label{Space Discretization}
-To solve the convolution integral in \ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
+To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
 \begin{equation}\label{discrete space}

### 2010-03-17 ltx/BrainIDE.tex
made changes following Kens suggestions

@@
 \begin{equation}\label{RateBasedInteractions}
-	g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',\bar t \right) \right)dr'} + I\left(r,t\right)
+	g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',t \right) \right)dr'} + I\left(r,t\right)
 \end{equation}
-\begin{todo}
-	{Do we really need this representation with $\bar t$.
-It makes convolution look wrong.
-DF: Don't need since we dont include delays.
-The motivation was to be general at the beginning, and for everyone to understand how the model is used elsewhere.}
-\end{todo}
-where $\bar t = t - d\left| {r - r'} \right|$, $d$ is the propagation delay of action potentials, $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+
+where $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
 The term $I\left(r,t\right)$ accounts for spontaneous activity of the neural populations.
@@
 \begin{equation}\label{ActivationFunction}
-	f\left( v\left( r', \bar t \right) \right) = \frac{\nu _0\left(r\right)}{1 + \exp \left( \beta \left( v_0\left( r \right) - v\left(r',\bar{t} \right) \right) \right)}.
+	f\left( v\left( r', \bar t \right) \right) = \frac{\nu _0\left(r\right)}{1 + \exp \left( \beta \left( v_0\left( r \right) - v\left(r',t\right) \right) \right)}.
 \end{equation}
@@
 \begin{equation}\label{FullDoubleIntModel}
-	v\left(r,t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(r,r'\right) f\left( v\left( r',\bar t \right)\right)dr' + I(r,t) \right)dt'
+	v\left(r,t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(r,r'\right) f\left( v\left( r',t \right)\right)dr' + I(r,t) \right)dt'
 \end{equation}
@@
 \begin{equation}\label{FinalForm1}
-	\frac{dv\left( r,t \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'} + I\left(r,t\right).
+	\frac{dv\left( r,t \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} + I\left(r,t\right).
 \end{equation}
@@
 To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(r,r') = w\left(|r-r'|\right)$, $\nu_0(r) = \nu_0$ and $v_0(r) = v_0$.
-In addition we assume the synaptic transmission delay is negligible such that $\bar{t}=t$.
+In addition we assume the synaptic transmission delay is negligible.
 The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system and account for uncertainty in the model giving
@@
 \begin{equation}
-	y_t\left(r_n\right) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'}
+	y_t = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'} + \varepsilon_t
 \end{equation}
-where $r_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors. The output kernel $m(|r-r'|)$ governs the geometry of pick-up range of sensors where
+where $r_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma_y\right)$.
+The output kernel $m(|r-r'|)$ governs the geometry of pick-up range of sensors where
 \begin{equation}
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	x_{t+1} &=& \delta\Gamma^{ - 1}\int_\Omega {\phi\left(r\right) \int_\Omega {f\left(\phi^T\left(r'\right)x_t\right)\psi^T \left(|r-r'|\right)dr'} dr} \theta - \lambda x_t + \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\phi\left(r\right)\tilde{e}_t\left(r\right)dr} \\
-	&=&\delta q(x_t) \theta -\lambda x_t + + \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\phi(r)\tilde{e}_t(r)dr}
+	x_t &=& q(x_t,\theta,\lambda) + k(I_t) + \tilde{e}_t \\
+	q(x_t,\theta,\lambda) &=& \delta\Gamma^{ - 1}\int_\Omega {\phi\left(r\right) \int_\Omega {f\left(\phi^T\left(r'\right)x_t\right)\psi^T \left(|r-r'|\right)dr'} dr} \theta - \lambda x_t \\
+	k(I_t) &=& \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} \\
+	\tilde{e}_t &=& \Gamma^{-1}\int_\Omega{\phi\left(r\right)e_t\left(r\right)dr} \\
 \end{eqnarray}
-\begin{todo}{Define q}\end{todo}
-where $\tilde{e}_t\left(r\right) \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
+where $\tilde{e}_t \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
 \begin{eqnarray}\label{ObservationEquation}
-    y_t( r_n ) &=& \int_\Omega  m\left(|r_n-r|\right)\phi^T\left(r\right) dr x_t  + \varepsilon_t ( r_n ) \\
-	&=& C x_t + \varepsilon_t ( r_n ).
+    y_t &=& z\left(x_t\right) + \varepsilon_t \\
+	z\left(x_t\right) &=& \int_\Omega m\left(|r_n-r|\right)\phi^T\left(r\right) dr x_t.
 \end{eqnarray}
-\begin{todo}{Define C}\end{todo}
 
@@
 Alternatives to this approach are the extended Kalman filter (ref?) (EKF) and sequential Monte Carlo (SMC) filtering (ref?).
-The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) of the state transition equation at each time step.
+The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time step.
 The linearization maintains the Gaussianality in the model.
@@
 However, this method is not appropriate for our problem, since it is not feasible for high dimensional systems, due to computation demands.
+
 The approximation of the state density is made by propagating the so called sigma points through the state-space model.
@@
 The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution.
-To explain the operation of the UKF we begin by explain the traditional Kalman filter with the state-space model
+To explain the operation of the UKF we begin by deriving the traditional Kalman filter with the state-space model
 \begin{eqnarray}
-	x_t = q(x_t,\kappa) + \tilde{e}_t \\
+	x_t = q(x_t,\theta,\lambda) + k(I_t) + \tilde{e}_t \\
 	y_t = z(x_t) + \varepsilon_t,
 \end{eqnarray}
-where $\kappa$ represents the systems parameters.
+where $\theta$ and $\lambda$ are the systems parameters.
 

### 2010-03-17 ltx/BrainIDE.tex
changes to equation (4) and (11)

@@
 The term $I\left(r,t\right)$ accounts for spontaneous activity of the neural populations.
-The connectivity kernel is a Mexican hat shape described by the sum of weighted Gaussian functions
+The connectivity kernel is a Mexican hat shape described by the sum of weighted Gaussian functions placed at the origin.
 \begin{eqnarray}\label{Connectivity Kernel}
-	w\left(r,r'\right) &=& \theta^T \psi\left(r,r'\right) \\
-	\psi\left(r,r'\right) &=&\exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_w (r'-r)\right)}
+	w\left(r,r'\right) =&& \\
+&&\theta_1\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_1^2}\right)}+\theta_2\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_2^2}\right)}+\theta_3\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_3^2}\right)}\nonumber
 \end{eqnarray}
-where
-\begin{equation}
-	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
-\end{equation}
+where $\sigma_i$ is the scale parameter.
+% where
+% \begin{equation}
+% 	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
+% \end{equation}
 \begin{todo}
-	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.}
+	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.Parham: I have changed it but I think it's better to include it in the simulation section}
 \end{todo}The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
@@
 \begin{equation}
-	y_t = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'} + \varepsilon_t
+	y_t(r_n) = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'} + \varepsilon_t
 \end{equation}
@@
 \begin{equation}
-	m\left(|r-r'|\right) = \exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_m (r'-r)\right)}.
+	m\left(|r-r'|\right) = \exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_m^2}\right)}.
 \end{equation}

### 2010-03-18 ltx/BrainIDE.tex
Changes to the noise definition

@@
 \end{equation}
-where $\delta$ is the time step, $\lambda = 1-\alpha\delta$ and $e_t(r) \sim \mathcal{GP}(0,\Sigma)$.
+where $\delta$ is the time step, $\lambda = 1-\alpha\delta$ and $e_t(r) \sim \mathcal{GP}(0,\Sigma)$\begin{todo}{
+is a spatially colored but temporally white with covariance
+\begin{equation}
+ cov(e_t(\mathbf{r}),e_{t+\tau}(\mathbf{r'}))=
+\begin{cases}
+\beta\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+0 & \mathrm{otherwise}
+\end{cases}
+\label{eq:FieldCovariance}
+\end{equation}}
+\end{todo}.
 The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}.
@@
 \end{eqnarray}
+\begin{todo}{where $\tilde{e}_t$ is a zero-mean normal white noise term with the covariance (see Appendix D)
+\begin{equation} 
+\mathbf \Sigma_w={}\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol\phi\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol\phi\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+\end{equation}}
+
+\end{todo}
+
 where $\tilde{e}_t \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
@@
 \begin{equation}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
+v_{t + 1}\left( \mathbf{r} \right)  = \delta\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) +e_t\left( {\mathbf{r}} \right).
 \end{equation}
@@
 \begin{equation}
-cov(e_t(\mathbf{s}),e_{t+\tau}(\mathbf{r}))=
+cov(e_t(\mathbf{r}),e_{t+\tau}(\mathbf{r'}))=
 \begin{cases}
-\beta\left(\mathbf{s}-\mathbf{r}\right), & \tau=0 \\
+\beta\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
 0 & \mathrm{otherwise}
@@
 \begin{equation}
-x_{t + 1} = T_sq(x_t)\theta -\lambda x_t + T_s\Gamma^{-1}\int_\Omega  {\phi ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
+x_{t + 1} = \delta q(x_t)\theta -\lambda x_t + \Gamma^{-1}\int_\Omega  {\phi ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
 \end{equation}
@@
 \begin{eqnarray}
-\mathbf \Sigma_w&{}={}&T_s^2 \times \mathbf{\Gamma}^{-1}\mathbf E[\int_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right)e_t\left(\mathbf s\right)d\mathbf s\int_{\mathcal{S}}\boldsymbol\phi\left(\mathbf r\right)^{\top}e_t\left(\mathbf r\right)d\mathbf r]\mathbf{\Gamma}_{x}^{- \top} \nonumber \\
-&=&T_s^2 \times\mathbf{\Gamma}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right) \mathbf E[e_t\left(\mathbf s\right)e_t\left(\mathbf r\right)]\boldsymbol\phi\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Gamma}^{- \top} \nonumber\\
-&=&{}T_s^2 \times\mathbf{\Gamma}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right) \beta\left(\mathbf s- \mathbf r \right)\boldsymbol\phi\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Gamma}^{- \top}
+\mathbf \Sigma_w&{}={}&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol\phi\left(\mathbf r\right)e_t\left(\mathbf r\right)d\mathbf r\int_{\Omega}\boldsymbol\phi\left(\mathbf r'\right)^{\top}e_t\left(\mathbf r'\right)d\mathbf r']\mathbf{\Gamma}^{- \top} \nonumber \\
+&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol\phi\left(\mathbf r\right) \mathbf E[e_t\left(\mathbf r\right)e_t\left(\mathbf r'\right)]\boldsymbol\phi\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+&=&{}\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol\phi\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol\phi\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{eqnarray}

### 2010-03-18 ltx/BrainIDE.tex
updated paper following meeting on the 20/03/2010

--- 2010-03-17 ltx/BrainIDE.tex
@@
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
-The model relates the average number of action potentials $g(r,t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(r,t)$.
-The post-synaptic potentials generated at a neuronal population at location $r$ by action potentials arriving from all other connected populations at locations $r'$ can be described by
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
+The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
 \begin{equation}\label{SpikesToPotential}
-	v\left( {r,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {r,t'} \right)dt'}.
+	v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}.
 \end{equation}
-\begin{todo}
-	{Is this equation correct? Is it a convolution in time? Dean: yes}
-\end{todo}
 The post-synaptic response kernel $h(t)$ is described by
 \begin{equation}\label{SynapticRespKernel}
-	h(t) = u(t)\exp{\left(-\alpha t\right)}.
+	h(t) = \eta(t)\exp{\left(-\alpha t\right)}.
 \end{equation}
-where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $u(t)$ is the Heaviside step function.
+where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function.
 The synaptic response kernel can be more elaborate, using rise and fall time constants, however, this simple form serves our purposes.
@@
 \begin{equation}\label{RateBasedInteractions}
-	g\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( v\left( r',t \right) \right)dr'} + I\left(r,t\right)
+	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right)
 \end{equation}
 
-where $f$ is spiking rate of populations $r'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
-The term $I\left(r,t\right)$ accounts for spontaneous activity of the neural populations.
-The connectivity kernel is a Mexican hat shape described by the sum of weighted Gaussian functions
-\begin{eqnarray}\label{Connectivity Kernel}
-	w\left(r,r'\right) &=& \theta^T \psi\left(r,r'\right) \\
-	\psi\left(r,r'\right) &=&\exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_w (r'-r)\right)}
-\end{eqnarray}
-where
-\begin{equation}
-	\theta=\begin{bmatrix} \theta_{1}\\\theta_{2}\\\theta_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
-\end{equation}
-\begin{todo}
-	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.}
-\end{todo}The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
+where $f$ is spiking rate of populations $\mathbf{r}'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+The term $u\left(\mathbf{r},t\right)$ represents a known external input.
+The connectivity kernel is typically a Mexican hat shape described by the sum of weighted Gaussian functions.
+The shape of the kernel is not a critical parameter for our methodology so we shall not define it here to keep the derivation as general as possible.
+% \begin{eqnarray}\label{Connectivity Kernel}
+% 	w\left(r,r'\right) =&& \\
+% &&\mathbf{\theta}_1\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_1^2}\right)}+\mathbf{\theta}_2\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_2^2}\right)}+\mathbf{\theta}_3\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_3^2}\right)}\nonumber
+% \end{eqnarray}
+% where $\sigma_i$ is the scale parameter.
+% % where
+% % \begin{equation}
+% % 	\mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf{\theta}_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
+% % \end{equation}
+% \begin{todo}
+% 	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.Parham: I have changed it but I think it's better to include it in the simulation section}
+% \end{todo}
+The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
 \begin{equation}\label{ActivationFunction}
-	f\left( v\left( r', \bar t \right) \right) = \frac{\nu _0\left(r\right)}{1 + \exp \left( \beta \left( v_0\left( r \right) - v\left(r',t\right) \right) \right)}.
+	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{\nu _0\left(\mathbf{r}\right)}{1 + \exp \left( \beta \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 \begin{equation}\label{FullDoubleIntModel}
-	v\left(r,t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(r,r'\right) f\left( v\left( r',t \right)\right)dr' + I(r,t) \right)dt'
+	v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'
 \end{equation}
@@
 where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{equation}\label{FinalForm1}
-	\frac{dv\left( r,t \right)}{dt} + \alpha v\left( r,t \right) = \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} + I\left(r,t\right).
+\begin{equation}\label{FinalFormContinuous}
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \alpha v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
+\end{equation}
+To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see Appendix~\ref{Time Discretization}) giving
+\begin{equation}\label{DiscreteTimeModel}
+	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+\end{equation} 
+where $T$ is the time step, $\lambda = 1-\alpha T$ and $e_t(\mathbf{r}) \sim \mathcal{GP}\left(0,\Sigma\left(\mathbf{r}-\mathbf{r}'\right)\right)$ 
+is a spatially colored, temporally white iid. This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
+\begin{equation}
+	y_t(\mathbf{r}_n) = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \varepsilon_t
+\end{equation}
+where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma_y\right)$.
+The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
+\begin{equation}
+	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)}.
 \end{equation}
 
-\section{Generating Data}
-To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(r,r') = w\left(|r-r'|\right)$, $\nu_0(r) = \nu_0$ and $v_0(r) = v_0$.
+% \begin{equation}
+%  cov(e_t(\mathbf{r}),e_{t+\tau}(\mathbf{r'}))=
+% \begin{cases}
+% \beta\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+% 0 & \mathrm{otherwise}
+% \end{cases}
+% \label{eq:FieldCovariance}
+% \end{equation}
+% \section{Generating Data}
+% To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(\mathbf{r},\mathbf{r}') = w\left(\mathbf{r}-\mathbf{r}'\right)$, $\nu_0(\mathbf{r}) = \nu_0$ and $v_0(\mathbf{r}) = v_0$.
 In addition we assume the synaptic transmission delay is negligible.
-The model was discretized in time  (see Appendix~\ref{Time Discretization}) and a stochastic term was added to drive the system and account for uncertainty in the model giving
-\begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I_t\left(r\right) + e_t\left(r\right)
-\end{equation}
-where $\delta$ is the time step, $\lambda = 1-\alpha\delta$ and $e_t(r) \sim \mathcal{GP}(0,\Sigma)$.
-The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}.
-To generate iEEG/LFP data we used the output function
-\begin{equation}
-	y_t = \int_{\Omega}{m\left(|r_n-r'|\right)v_t\left(r'\right)dr'} + \varepsilon_t
-\end{equation}
-where $r_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma_y\right)$.
-The output kernel $m(|r-r'|)$ governs the geometry of pick-up range of sensors where
-\begin{equation}
-	m\left(|r-r'|\right) = \exp{\left(-\frac{1}{2}(r'-r)^T\Sigma_m (r'-r)\right)}.
-\end{equation}
-
-All the model parameters are described in Table 1.
-
-\begin{tabular}{|c|c|c|}
-\hline
-Parameter & Value & Reference\\
-\hline
-$\alpha$ & $100$ s$^{-1}$ &\\
-\hline
-$\nu_0$ & $1$ s$^{-1}$ &\\
-\hline
-$v_0$ & $6$ mV &\\
-\hline
-$\beta$ & $0.56$ spikes/mV$^{-1}$ & \\
-\hline
-$\delta$ & $1\times10^{-4}$ s &\\
-\hline
-$\Delta$ & $1$ &\\
-\hline
-$\theta_1$ &  &\\
-\hline
-$\theta_2$ &  &\\
-\hline
-$\theta_3$ &  &\\
-\hline
-$\sigma_{w1}$ &  &\\
-\hline
-$\sigma_{w2}$ &  &\\
-\hline
-$\sigma_{w3}$ &  &\\
-\hline
-$\sigma_m$ &  &\\
-\hline
-\end{tabular}
+The model was discretized in time   and a stochastic
+% 
+% The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}. 
+% All the model parameters are described in Table 1.
+% 
+% \begin{tabular}{|c|c|c|}
+% \hline
+% Parameter & Value & Reference\\
+% \hline
+% $\alpha$ & $100$ s$^{-1}$ &\\
+% \hline
+% $\nu_0$ & $1$ s$^{-1}$ &\\
+% \hline
+% $v_0$ & $6$ mV &\\
+% \hline
+% $\beta$ & $0.56$ spikes/mV$^{-1}$ & \\
+% \hline
+% $T$ & $1\times10^{-4}$ s &\\
+% \hline
+% $\Delta$ & $1$ &\\
+% \hline
+% $\mathbf{\theta}_1$ &  &\\
+% \hline
+% $\mathbf{\theta}_2$ &  &\\
+% \hline
+% $\mathbf{\theta}_3$ &  &\\
+% \hline
+% $\sigma_{w1}$ &  &\\
+% \hline
+% $\sigma_{w2}$ &  &\\
+% \hline
+% $\sigma_{w3}$ &  &\\
+% \hline
+% $\sigma_m$ &  &\\
+% \hline
+% \end{tabular}
 
@@
 \begin{equation}\label{DefFieldDecomp}
-	v_t\left(r\right) \approx \phi ^T\left(r\right) x_t
+	v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t
 \end{equation}
-where $\phi(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $x_t$.
+where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
 As described in Eq.~\ref{Connectivity Kernel} the connectivity kernel can also be considered a decomposition into a set of basis functions in
 \begin{equation}\label{DefKernelDecomp}
-	\tilde{w}( |r-r'| ) = \theta^T\psi\left(|r-r'|\right)
+	w\left(\mathbf{r}-\mathbf{r}'\right) = \mathbf{\theta}^{\top} \mathbf{\psi}\left(\mathbf{r}-\mathbf{r}'\right)
 \end{equation}
-We will assume we know the parametric form of the connectivity basis functions, where the parameter $\theta$ is unknown.
+We will assume we know the parametric form of the connectivity basis functions, where the parameter $\mathbf{\theta}$ is unknown.
 Each connectivity basis function can be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
@@
 \begin{equation}\label{reduced continuous model}
-	\phi^T\left( r \right)x_{t+1} = \delta\theta^T\int_\Omega  {\psi \left(|r-r'|\right)f\left( \phi ^T\left(r'\right)x_t \right)dr'}  - \lambda\phi^T\left(r\right)x_t + \delta I_t\left(r\right) + e_t\left(r\right).
+	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\mathbf{\theta}^{\top}\int_\Omega  {\psi \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \begin{equation}\label{DefGamma}
-	\Gamma  = \int_\Omega  {\phi \left(r\right)\phi ^T\left(r\right)dr}
+	\Gamma  = \int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}
 \end{equation}
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	x_t &=& q(x_t,\theta,\lambda) + k(I_t) + \tilde{e}_t \\
-	q(x_t,\theta,\lambda) &=& \delta\Gamma^{ - 1}\int_\Omega {\phi\left(r\right) \int_\Omega {f\left(\phi^T\left(r'\right)x_t\right)\psi^T \left(|r-r'|\right)dr'} dr} \theta - \lambda x_t \\
-	k(I_t) &=& \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} \\
-	\tilde{e}_t &=& \Gamma^{-1}\int_\Omega{\phi\left(r\right)e_t\left(r\right)dr} \\
+	\mathbf{x}_t &=& q(\mathbf{x}_t,\mathbf{\theta},\lambda) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	q(\mathbf{x}_t,\mathbf{\theta},\alpha) &=& T\Gamma^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\psi^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \mathbf{\theta} - \lambda \mathbf{x}_t \\
+	k(u_t(\mathbf{r})) &=& \Gamma^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
+	\mathbf{e}_t &=& \Gamma^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}} \\
 \end{eqnarray}
+where $\mathbf{e}_t$ is a zero-mean normal white noise term with the covariance (see Appendix D)
+\begin{equation} 
+\mathbf \Sigma_w=\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\mathbf{\Gamma}^{- \top}
+\end{equation}
+
 where $\tilde{e}_t \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
@@
     y_t &=& z\left(x_t\right) + \varepsilon_t \\
-	z\left(x_t\right) &=& \int_\Omega m\left(|r_n-r|\right)\phi^T\left(r\right) dr x_t.
+	z\left(x_t\right) &=& \int_\Omega m\left(|r_n-r|\right)\boldsymbol{\phi}^{\top}\left(r\right) dr x_t.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	x_t = q(x_t,\theta,\lambda) + k(I_t) + \tilde{e}_t \\
+	x_t = q(x_t,\mathbf{\theta},\lambda) + k(I_t) + \tilde{e}_t \\
 	y_t = z(x_t) + \varepsilon_t,
 \end{eqnarray}
-where $\theta$ and $\lambda$ are the systems parameters.
+where $\mathbf{\theta}$ and $\lambda$ are the systems parameters.
 
@@
 \begin{equation}\label{Euler Approximation}	
-\frac{v\left( r,t+\delta \right) - v\left( r,t\right)}{\delta} =   -\alpha v\left( r,t \right) + \int_\Omega  {w\left( |r-r'| \right)f\left( {v\left( r',t \right)} \right)dr'} + I\left(r,t\right).
+\frac{v\left( r,t+T \right) - v\left( r,t\right)}{T} =   -\alpha v\left( r,t \right) + \int_\Omega  {w\left( |r-r'| \right)f\left( {v\left( r',t \right)} \right)dr'} + I\left(r,t\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( r\right) &=& v_t\left( r\right) -\delta \alpha v_t\left( r\right) + \delta \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + \delta I_t\left(r\right)
+v_{t+1}\left( r\right) &=& v_t\left( r\right) -T \alpha v_t\left( r\right) + T \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + T I_t\left(r\right)
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + \delta \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + \delta I_t\left(r\right).
+	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + T \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + T I_t\left(r\right).
 \end{equation}
-where $\lambda = 1 - \delta \alpha$.
+where $\lambda = 1 - T \alpha$.
 
@@
 \begin{equation}\label{discrete space}
-	v_{t+1}\left(r_{ij}\right) =  \lambda v_t(r_{ij}) + \delta \Delta^2 \sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{\tilde{w}\left( |r_{ij}-r_{ij}'| \right)f\left( v_t\left( r_{ij}'\right) \right)} } + \delta I_t\left(r\right) + \tilde{e}_t(r_{i,j})
+	v_{t+1}\left(r_{ij}\right) =  \lambda v_t(r_{ij}) + T \Delta^2 \sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{\tilde{w}\left( |r_{ij}-r_{ij}'| \right)f\left( v_t\left( r_{ij}'\right) \right)} } + T I_t\left(r\right) + \tilde{e}_t(r_{i,j})
 \end{equation}
@@
 \begin{equation}\label{Discrete Connectivity Kernel}
-	\tilde{w}(r_{ij},r_{ij}') = \theta^T e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
+	\tilde{w}(r_{ij},r_{ij}') = \mathbf{\theta}^{\top} e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
 \end{equation}
@@
 \section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
-Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\phi(r)$ and integrate over the spatial domain $\Omega$ to get
+Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
 \begin{equation}\label{Poo}
-	\int_\Omega  {\phi \left(r\right)\phi^T\left(r\right) dr} x_{t+1} = \delta \int_\Omega  {\phi (r) \theta^T \int_\Omega  {\psi \left(|r-r'|\right)f\left(\phi^T\left(r'\right) x_t \right)dr'}dr}  - \lambda\int_\Omega {\phi(r)\phi^T(r)dr} x_t + \delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\phi \left(r\right) e_t\left(r\right)dr}.
+	\int_\Omega  {\boldsymbol{\phi} \left(r\right)\boldsymbol{\phi}^{\top}\left(r\right) dr} x_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (r) \mathbf{\theta}^{\top} \int_\Omega  {\psi \left(|r-r'|\right)f\left(\boldsymbol{\phi}^{\top}\left(r'\right) x_t \right)dr'}dr}  - \lambda\int_\Omega {\boldsymbol{\phi}(r)\boldsymbol{\phi}^{\top}(r)dr} x_t + T \int_\Omega{\boldsymbol{\phi} \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\boldsymbol{\phi} \left(r\right) e_t\left(r\right)dr}.
 \end{equation}
@@
 \begin{equation}\label{Homogeneous SS Model}
-	x_{t+1} = \delta\Gamma^{ - 1}\int_\Omega {\phi\left(r\right) \int_\Omega {f\left(\phi^T\left(r'\right)x_t\right)\psi^T \left(|r-r'|\right)dr'} dr} \theta - \lambda x_t + \Gamma^{-1}\delta \int_\Omega{\phi \left(r\right) I_t\left(r\right)dr} + \Gamma^{-1}\int_\Omega{\phi\left(r\right)e_t\left(r\right)dr}.
+	x_{t+1} = T\Gamma^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(r\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(r'\right)x_t\right)\psi^{\top} \left(|r-r'|\right)dr'} dr} \mathbf{\theta} - \lambda x_t + \Gamma^{-1}T \int_\Omega{\boldsymbol{\phi} \left(r\right) I_t\left(r\right)dr} + \Gamma^{-1}\int_\Omega{\boldsymbol{\phi}\left(r\right)e_t\left(r\right)dr}.
 \end{equation}
@@
 \begin{equation}
-	\Gamma ^{ - 1}\int_\Omega  {\phi \left(r\right)e_t\left(r\right)dr} = \int_\Omega{\phi\left(r\right)\tilde{e}_t\left(r\right)dr},
+	\Gamma ^{ - 1}\int_\Omega  {\boldsymbol{\phi} \left(r\right)e_t\left(r\right)dr} = \int_\Omega{\boldsymbol{\phi}\left(r\right)\tilde{e}_t\left(r\right)dr},
 \end{equation}
@@
 \begin{equation}
-v_{t + 1}\left( \mathbf{r} \right)  = T_s\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) + T_se_t\left( {\mathbf{r}} \right).
+v_{t + 1}\left( \mathbf{r} \right)  = T\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) +e_t\left( {\mathbf{r}} \right).
 \end{equation}
@@
 \begin{equation}
-x_{t + 1} = T_sq(x_t)\theta -\lambda x_t + T_s\Gamma^{-1}\int_\Omega  {\phi ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
+x_{t + 1} = T q(x_t)\mathbf{\theta} -\lambda x_t + \Gamma^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
 \end{equation}
@@
 \begin{eqnarray}
-\mathbf \Sigma_w&{}={}&T_s^2 \times \mathbf{\Gamma}^{-1}\mathbf E[\int_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right)e_t\left(\mathbf s\right)d\mathbf s\int_{\mathcal{S}}\boldsymbol\phi\left(\mathbf r\right)^{\top}e_t\left(\mathbf r\right)d\mathbf r]\mathbf{\Gamma}_{x}^{- \top} \nonumber \\
-&=&T_s^2 \times\mathbf{\Gamma}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right) \mathbf E[e_t\left(\mathbf s\right)e_t\left(\mathbf r\right)]\boldsymbol\phi\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Gamma}^{- \top} \nonumber\\
-&=&{}T_s^2 \times\mathbf{\Gamma}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\phi\left(\mathbf s\right) \beta\left(\mathbf s- \mathbf r \right)\boldsymbol\phi\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Gamma}^{- \top}
+\mathbf{\Sigma}_w&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top} e_t\left(\mathbf{r}'\right)d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{eqnarray}
@@
 \begin{equation}
- \mathbf x_{t+1}=\mathbf x_{t}+T_s \mathbf Q(\mathbf x_t)\mathbf \theta-\alpha T_s\mathbf x_t+T_s\boldsymbol\Gamma^{-1}\int_\Omega\boldsymbol\phi(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+ \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\mathbf \mathbf{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
 \label{eq:statespacemodel}
 \end{equation}
-where the matrix $\mathbf Q_{n_x \times n_{\theta}}(\mathbf x_t)$ is defined as
+where the matrix $\mathbf Q_{n_x \times n_{\mathbf{\theta}}}(\mathbf x_t)$ is defined as
 \begin{equation}
- Q_{n_x \times n_{\theta}}=\boldsymbol\Gamma^{-1}\int_\Omega\boldsymbol\phi(\mathbf r)\int_\Omega f(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)\boldsymbol\psi^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
+ Q_{n_x \times n_{\mathbf{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
 \end{equation}
@@
 \begin{eqnarray}
- \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0)\mathbf \theta-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
- \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1)\mathbf \theta-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+ \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0)\mathbf \mathbf{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+ \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1)\mathbf \mathbf{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
 &\vdots& \nonumber\\
- \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1})\mathbf \theta-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
+ \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1})\mathbf \mathbf{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
 \end{eqnarray}
@@
 \begin{equation}
- \begin{bmatrix} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{bmatrix}-\begin{bmatrix} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{bmatrix}=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix}\begin{bmatrix}\mathbf \theta \\ \alpha\end{bmatrix}+T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
+ \begin{bmatrix} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{bmatrix}-\begin{bmatrix} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{bmatrix}=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix}\begin{bmatrix}\mathbf \mathbf{\theta} \\ \alpha\end{bmatrix}+T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
 \end{equation}
@@
 \begin{equation}
- \mathbf Z=\begin{bmatrix} \mathbf x_{1}-\mathbf x_{0}\\\mathbf x_{2}-\mathbf x_{1}\\\vdots\\\mathbf x_{n}-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf X=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf W=\begin{bmatrix}\mathbf \theta \\ \alpha\end{bmatrix} \text{and}\quad \boldsymbol \xi=T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
+ \mathbf Z=\begin{bmatrix} \mathbf x_{1}-\mathbf x_{0}\\\mathbf x_{2}-\mathbf x_{1}\\\vdots\\\mathbf x_{n}-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf X=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf W=\begin{bmatrix}\mathbf \mathbf{\theta} \\ \alpha\end{bmatrix} \text{and}\quad \boldsymbol \xi=T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
 \end{equation}

### 2010-03-18 ltx/BrainIDE.tex
further updated paper following meeting on the 20/03/2010

@@
 % 	w\left(r,r'\right) =&& \\
-% &&\mathbf{\theta}_1\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_1^2}\right)}+\mathbf{\theta}_2\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_2^2}\right)}+\mathbf{\theta}_3\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_3^2}\right)}\nonumber
+% &&\boldsymbol{\theta}_1\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_1^2}\right)}+\boldsymbol{\theta}_2\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_2^2}\right)}+\boldsymbol{\theta}_3\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_3^2}\right)}\nonumber
 % \end{eqnarray}
@@
 % % \begin{equation}
-% % 	\mathbf{\theta}=\begin{bmatrix} \mathbf{\theta}_{1}\\\mathbf{\theta}_{2}\\\mathbf{\theta}_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
+% % 	\boldsymbol{\theta}=\begin{bmatrix} \boldsymbol{\theta}_{1}\\\boldsymbol{\theta}_{2}\\\boldsymbol{\theta}_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
 % % \end{equation}
@@
 where $T$ is the time step, $\lambda = 1-\alpha T$ and $e_t(\mathbf{r}) \sim \mathcal{GP}\left(0,\Sigma\left(\mathbf{r}-\mathbf{r}'\right)\right)$ 
-is a spatially colored, temporally white iid. This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
+is an iid spatially colored, temporally white disturbance term. This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
 \begin{equation}
-	y_t(\mathbf{r}_n) = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \varepsilon_t
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t
 \end{equation}
@@
 
-% \begin{equation}
-%  cov(e_t(\mathbf{r}),e_{t+\tau}(\mathbf{r'}))=
-% \begin{cases}
-% \beta\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
-% 0 & \mathrm{otherwise}
-% \end{cases}
-% \label{eq:FieldCovariance}
-% \end{equation}
 % \section{Generating Data}
@@
 \begin{equation}\label{DefKernelDecomp}
-	w\left(\mathbf{r}-\mathbf{r}'\right) = \mathbf{\theta}^{\top} \mathbf{\psi}\left(\mathbf{r}-\mathbf{r}'\right)
+	w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \mathbf{\psi}\left(\mathbf{r}-\mathbf{r}'\right)
 \end{equation}
-We will assume we know the parametric form of the connectivity basis functions, where the parameter $\mathbf{\theta}$ is unknown.
+We will assume we know the parametric form of the connectivity basis functions, where the parameter $\boldsymbol{\theta}$ is unknown.
 Each connectivity basis function can be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
@@
 \begin{equation}\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\mathbf{\theta}^{\top}\int_\Omega  {\psi \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\psi \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \begin{equation}\label{DefGamma}
-	\Gamma  = \int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}
+	\boldsymbol{\Gamma}  = \int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}
 \end{equation}
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_t &=& q(\mathbf{x}_t,\mathbf{\theta},\lambda) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	q(\mathbf{x}_t,\mathbf{\theta},\alpha) &=& T\Gamma^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\psi^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \mathbf{\theta} - \lambda \mathbf{x}_t \\
-	k(u_t(\mathbf{r})) &=& \Gamma^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
-	\mathbf{e}_t &=& \Gamma^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}} \\
+	\mathbf{x}_t &=& q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\psi^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
+	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}} \\
 \end{eqnarray}
@@
 \begin{equation} 
-\mathbf \Sigma_w=\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\mathbf{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
 
-where $\tilde{e}_t \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. The observation equation of the reduced model is
+\begin{equation}
+ cov(\mathbf{e}_t,\mathbf{e}_{t+\tau})=
+\begin{cases}
+\rho\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+0 & \mathrm{otherwise}
+\end{cases}
+\label{eq:FieldCovariance}
+\end{equation}
+
+The observation equation of the reduced model is
 \begin{eqnarray}\label{ObservationEquation}
-    y_t &=& z\left(x_t\right) + \varepsilon_t \\
-	z\left(x_t\right) &=& \int_\Omega m\left(|r_n-r|\right)\boldsymbol{\phi}^{\top}\left(r\right) dr x_t.
+    \mathbf{y}_t &=& z\left(\mathbf{x}_t\right) + \boldsymbol{\varepsilon}_t \\
+	z\left(\mathbf{x}_t\right) &=& \int_\Omega m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}' \mathbf{x}_t.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	x_t = q(x_t,\mathbf{\theta},\lambda) + k(I_t) + \tilde{e}_t \\
-	y_t = z(x_t) + \varepsilon_t,
+	\mathbf{x}_t = q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	\mathbf{y}_t = z(\mathbf{x}_t) + \boldsymbol{\varepsilon}_t,
 \end{eqnarray}
-where $\mathbf{\theta}$ and $\lambda$ are the systems parameters.
+where $\boldsymbol{\theta}$ and $\alpha$ are the systems parameters.
 
@@
 \begin{equation}\label{Discrete Connectivity Kernel}
-	\tilde{w}(r_{ij},r_{ij}') = \mathbf{\theta}^{\top} e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
+	\tilde{w}(r_{ij},r_{ij}') = \boldsymbol{\theta}^{\top} e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
 \end{equation}
@@
 \begin{equation}\label{Poo}
-	\int_\Omega  {\boldsymbol{\phi} \left(r\right)\boldsymbol{\phi}^{\top}\left(r\right) dr} x_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (r) \mathbf{\theta}^{\top} \int_\Omega  {\psi \left(|r-r'|\right)f\left(\boldsymbol{\phi}^{\top}\left(r'\right) x_t \right)dr'}dr}  - \lambda\int_\Omega {\boldsymbol{\phi}(r)\boldsymbol{\phi}^{\top}(r)dr} x_t + T \int_\Omega{\boldsymbol{\phi} \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\boldsymbol{\phi} \left(r\right) e_t\left(r\right)dr}.
+	\int_\Omega  {\boldsymbol{\phi} \left(r\right)\boldsymbol{\phi}^{\top}\left(r\right) dr} x_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (r) \boldsymbol{\theta}^{\top} \int_\Omega  {\psi \left(|r-r'|\right)f\left(\boldsymbol{\phi}^{\top}\left(r'\right) x_t \right)dr'}dr}  - \lambda\int_\Omega {\boldsymbol{\phi}(r)\boldsymbol{\phi}^{\top}(r)dr} x_t + T \int_\Omega{\boldsymbol{\phi} \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\boldsymbol{\phi} \left(r\right) e_t\left(r\right)dr}.
 \end{equation}
@@
 \begin{equation}\label{Homogeneous SS Model}
-	x_{t+1} = T\Gamma^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(r\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(r'\right)x_t\right)\psi^{\top} \left(|r-r'|\right)dr'} dr} \mathbf{\theta} - \lambda x_t + \Gamma^{-1}T \int_\Omega{\boldsymbol{\phi} \left(r\right) I_t\left(r\right)dr} + \Gamma^{-1}\int_\Omega{\boldsymbol{\phi}\left(r\right)e_t\left(r\right)dr}.
+	x_{t+1} = T\Gamma^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(r\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(r'\right)x_t\right)\psi^{\top} \left(|r-r'|\right)dr'} dr} \boldsymbol{\theta} - \lambda x_t + \Gamma^{-1}T \int_\Omega{\boldsymbol{\phi} \left(r\right) u_t\left(r\right)dr} + \Gamma^{-1}\int_\Omega{\boldsymbol{\phi}\left(r\right)e_t\left(r\right)dr}.
 \end{equation}
@@
 \begin{equation}
-x_{t + 1} = T q(x_t)\mathbf{\theta} -\lambda x_t + \Gamma^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
+x_{t + 1} = T q(x_t)\boldsymbol{\theta} -\lambda x_t + \Gamma^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
 \end{equation}
@@
 \begin{equation}
- \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\mathbf \mathbf{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+ \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
 \label{eq:statespacemodel}
 \end{equation}
-where the matrix $\mathbf Q_{n_x \times n_{\mathbf{\theta}}}(\mathbf x_t)$ is defined as
+where the matrix $\mathbf Q_{n_x \times n_{\boldsymbol{\theta}}}(\mathbf x_t)$ is defined as
 \begin{equation}
- Q_{n_x \times n_{\mathbf{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
+ Q_{n_x \times n_{\boldsymbol{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
 \end{equation}
@@
 \begin{eqnarray}
- \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0)\mathbf \mathbf{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
- \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1)\mathbf \mathbf{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+ \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+ \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
 &\vdots& \nonumber\\
- \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1})\mathbf \mathbf{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
+ \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
 \end{eqnarray}
@@
 \begin{equation}
- \begin{bmatrix} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{bmatrix}-\begin{bmatrix} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{bmatrix}=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix}\begin{bmatrix}\mathbf \mathbf{\theta} \\ \alpha\end{bmatrix}+T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
+ \begin{bmatrix} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{bmatrix}-\begin{bmatrix} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{bmatrix}=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix}\begin{bmatrix} \boldsymbol{\theta} \\ \alpha\end{bmatrix}+T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
 \end{equation}
@@
 \begin{equation}
- \mathbf Z=\begin{bmatrix} \mathbf x_{1}-\mathbf x_{0}\\\mathbf x_{2}-\mathbf x_{1}\\\vdots\\\mathbf x_{n}-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf X=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf W=\begin{bmatrix}\mathbf \mathbf{\theta} \\ \alpha\end{bmatrix} \text{and}\quad \boldsymbol \xi=T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
+ \mathbf Z=\begin{bmatrix} \mathbf x_{1}-\mathbf x_{0}\\\mathbf x_{2}-\mathbf x_{1}\\\vdots\\\mathbf x_{n}-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf X=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf W=\begin{bmatrix} \boldsymbol{\theta} \\ \alpha\end{bmatrix} \text{and}\quad \boldsymbol \xi=T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
 \end{equation}

### 2010-03-18 ltx/BrainIDE.tex
further updated paper following meeting on the 20/03/2010

@@
 The connectivity kernel is typically a Mexican hat shape described by the sum of weighted Gaussian functions.
-The shape of the kernel is not a critical parameter for our methodology so we shall not define it here to keep the derivation as general as possible.
+The shape of the kernel is not a critical parameter for our methodology so we shall not define it until later to keep the derivation as general as possible.
 % \begin{eqnarray}\label{Connectivity Kernel}
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-As described in Eq.~\ref{Connectivity Kernel} the connectivity kernel can also be considered a decomposition into a set of basis functions in
+The connectivity kernel can also be considered a decomposition into a set of basis functions in
 \begin{equation}\label{DefKernelDecomp}
@@
 \begin{equation}\label{Euler Approximation}	
-\frac{v\left( r,t+T \right) - v\left( r,t\right)}{T} =   -\alpha v\left( r,t \right) + \int_\Omega  {w\left( |r-r'| \right)f\left( {v\left( r',t \right)} \right)dr'} + I\left(r,t\right).
+\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T} =   -\alpha v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( r\right) &=& v_t\left( r\right) -T \alpha v_t\left( r\right) + T \int_\Omega  {w\left( |r-r'| \right)f\left( {v_t\left( r'\right)} \right)dr'} + T I_t\left(r\right)
+v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \alpha v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right)
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(r\right) = \lambda v_t\left(r\right) + T \int_\Omega { w\left(|r-r'|\right) f\left(v_t\left(r'\right)\right) dr'} + T I_t\left(r\right).
+	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \begin{equation}\label{discrete space}
-	v_{t+1}\left(r_{ij}\right) =  \lambda v_t(r_{ij}) + T \Delta^2 \sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{\tilde{w}\left( |r_{ij}-r_{ij}'| \right)f\left( v_t\left( r_{ij}'\right) \right)} } + T I_t\left(r\right) + \tilde{e}_t(r_{i,j})
+	v_{t+1}\left(\mathbf{r}_{ij}\right) = \lambda v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j})
 \end{equation}
-where $\tilde{e}_t(r_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$ and $\tilde{w}(|r_{ij}-r_{ij}'|)$ discretized connectivity kernel described by
-\begin{equation}\label{Discrete Connectivity Kernel}
-	\tilde{w}(r_{ij},r_{ij}') = \boldsymbol{\theta}^{\top} e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
-\end{equation}
-The observation equation and kernel were discretized in the same way by
-\begin{equation}\label{Discrete Observation Equation}
-    y_k\left(r_{i_n j_n}\right) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J} \tilde{m}( |r_{i_n j_n}-r_{ij}'| ) v_k\left(r_{ij}'\right)  + \varepsilon_k( r_{i_n j_n})
-\end{equation}
-where
-\begin{equation}\label{Discrete Observation Kernel}
-	\tilde{m}(|r_{ij}-r_{ij}'|) = e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
-\end{equation}
+where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$.
+%  and $\tilde{w}(r_{ij}-r_{ij}'|)$ discretized connectivity kernel described by
+% \begin{equation}\label{Discrete Connectivity Kernel}
+% 	\tilde{w}(r_{ij},r_{ij}') = \boldsymbol{\theta}^{\top} e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
+% \end{equation}
+% The observation equation and kernel were discretized in the same way by
+% \begin{equation}\label{Discrete Observation Equation}
+%     y_k\left(r_{i_n j_n}\right) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J} \tilde{m}( |r_{i_n j_n}-r_{ij}'| ) v_k\left(r_{ij}'\right)  + \varepsilon_k( r_{i_n j_n})
+% \end{equation}
+% where
+% \begin{equation}\label{Discrete Observation Kernel}
+% 	\tilde{m}(|r_{ij}-r_{ij}'|) = e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
+% \end{equation}
 We have used periodic boundary conditions to alleviate problems associated with edge effects.
@@
 Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{equation}\label{Poo}
-	\int_\Omega  {\boldsymbol{\phi} \left(r\right)\boldsymbol{\phi}^{\top}\left(r\right) dr} x_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (r) \boldsymbol{\theta}^{\top} \int_\Omega  {\psi \left(|r-r'|\right)f\left(\boldsymbol{\phi}^{\top}\left(r'\right) x_t \right)dr'}dr}  - \lambda\int_\Omega {\boldsymbol{\phi}(r)\boldsymbol{\phi}^{\top}(r)dr} x_t + T \int_\Omega{\boldsymbol{\phi} \left(r\right) I_t\left(r\right)dr} + \int_\Omega{\boldsymbol{\phi} \left(r\right) e_t\left(r\right)dr}.
-\end{equation}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\Gamma^{-1}$ gives 
-\begin{equation}\label{Homogeneous SS Model}
-	x_{t+1} = T\Gamma^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(r\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(r'\right)x_t\right)\psi^{\top} \left(|r-r'|\right)dr'} dr} \boldsymbol{\theta} - \lambda x_t + \Gamma^{-1}T \int_\Omega{\boldsymbol{\phi} \left(r\right) u_t\left(r\right)dr} + \Gamma^{-1}\int_\Omega{\boldsymbol{\phi}\left(r\right)e_t\left(r\right)dr}.
-\end{equation}
-The disturbance term can be rewritten as 
-\begin{equation}
-	\Gamma ^{ - 1}\int_\Omega  {\boldsymbol{\phi} \left(r\right)e_t\left(r\right)dr} = \int_\Omega{\boldsymbol{\phi}\left(r\right)\tilde{e}_t\left(r\right)dr},
-\end{equation}
-where $\tilde{e}_t\left(r\right) \sim \mathcal{N}\left(0,R' \Sigma R\right)$ and $R$ is the Cholesky decomposition of $\Gamma^{-1}$. This provides the final simplified state-space model.
+\begin{eqnarray}\label{Poo}
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\psi \left(\mathbf{r}-\mathbf{r}'\right)f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+\end{eqnarray}
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+\begin{eqnarray}\label{Homogeneous SS Model}
+	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\psi^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+\end{eqnarray}
+
 % \section{Ken's Discretization}
@@
 \begin{equation}
-x_{t + 1} = T q(x_t)\boldsymbol{\theta} -\lambda x_t + \Gamma^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
+\mathbf{x}_{t + 1} = T q(\mathbf{x}_t)\boldsymbol{\theta} -\lambda \mathbf{x}_t + \boldsymbol{\Gamma}^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
 \end{equation}

### 2010-03-19 ltx/BrainIDE.tex
further updated paper following meeting on the 20/03/2010

@@
 \begin{equation}\label{RateBasedInteractions}
-	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right)
+	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right),
 \end{equation}
-
 where $f$ is spiking rate of populations $\mathbf{r}'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
@@
 \begin{equation}\label{FullDoubleIntModel}
-	v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'
+	v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'.
 \end{equation}
@@
 \begin{equation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t,
 \end{equation}
@@
 \begin{equation}\label{DefFieldDecomp}
-	v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t
+	v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t,
 \end{equation}
@@
 \begin{equation}\label{DefKernelDecomp}
-	w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \mathbf{\psi}\left(\mathbf{r}-\mathbf{r}'\right)
+	w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right).
 \end{equation}
@@
 \begin{equation}\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\psi \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 	\mathbf{x}_t &=& q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\psi^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
-	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}} \\
+	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}},
 \end{eqnarray}
@@
 \end{equation}
-
 \begin{equation}
@@
 \rho\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
-0 & \mathrm{otherwise}
+0 & \mathrm{otherwise}.
 \end{cases}
@@
 \end{equation}
-
 The observation equation of the reduced model is
@@
 \section{Discussion}
+\begin{itemize}
+
+	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models.
+
+	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing.
+
+	\item The flexibility of the approach
+
+	\item Combining this method with other to incorporate longer range hetrogeneous connectivity.
+
+	\item The need for activity to perform estimation.
+\end{itemize}
 
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \alpha v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right)
+v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \alpha v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
+	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right),
 \end{equation}
@@
 
-\section{Numerical Solution to IDE Model}\label{Space Discretization}
+\section{Numerical Simulation of IDE Model}\label{Space Discretization}
 To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
 \begin{equation}\label{discrete space}
-	v_{t+1}\left(\mathbf{r}_{ij}\right) = \lambda v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j})
+	v_{t+1}\left(\mathbf{r}_{ij}\right) = \lambda v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
 \end{equation}
@@
 \begin{eqnarray}\label{Poo}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\psi \left(\mathbf{r}-\mathbf{r}'\right)f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\psi^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 
-% \section{Ken's Discretization}
-% Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
-% \begin{equation}\label{differential eq}	
-% \tau dv\left( r,t \right) = \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
-% \end{equation}
-% where $e\left( r,t \right)$ is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
-(not too sure about this noise since it needs to be white temporally but coloured spatially - which in continuous space-time I have never seen written ...
-has anyone?)
-% To simplify the notation, but without loss of generality, \ref{differential eq} can be rewritten as
-% \begin{equation}\label{differential simplified}
-% 	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
-% \end{equation}
-% Had $q\left(v(r,t) \right)$ been a linear function in $v$, then \ref{differential simplified} could be rewritten as
-% \begin{equation}\label{differential linear}
-% 	dv\left( r,t \right) = Av(r,t)dt  + d e\left( r,t \right)
-% \end{equation}
-% Considering temporal sampling instances $\delta$ apart given by $\{t_k = 0,~1,~2, \ldots$ \}, then a solution to \ref{differential linear} at each sampling time is given by
-% \begin{equation}\label{linear solution}
-% 	v(r,t_k+\delta) = \exp\{A(\delta)\}x(t) + \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
-% \end{equation}
-% Let the discrete time random variable $e'(r,t_k)$ be
-% \begin{equation}\label{discrete noise}
-% 	e'(r,t_k) = \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
-% \end{equation}
-% then, $e'(r,t_k)$ is a zero mean, temporally white noise term with covariance
-% \begin{equation}\label{covariance of noise}
-% 	E\left[e'(r,t_k),e'^\top(r,t_k) \right] = \int_t^{t+\delta}\exp\{A(t_k+\delta-\tau)\} \Sigma_e(r) \exp\{A(t+\delta-\tau)\} d\tau
-% \end{equation}
-% 
-% But we are not so luck as to be able to go from \ref{differential simplified} to \ref{differential linear} and thus I doubt if we can obtain an exact solution to \ref{differential simplified} without an approximation.
-Agreed?
-% 
-% A possible approximate solution is the one you have already used. Thus, interpreting the difference equation \ref{differential simplified} as an integral equation gives
-% \begin{equation}\label{euler}
-% 	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
-% \end{equation}
-% Using an Euler approximation, \ref{euler} can be approximated at each sampling time by
-% \begin{equation}\label{euler approx 1}
-% 	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
-% \end{equation}
-% which can be rewritten as
-% \begin{equation}\label{euler approx 2}
-% 	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
-% \end{equation}
-% where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
-(Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$)
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
 \section{Colored noise}
@@
 \begin{equation}
-v_{t + 1}\left( \mathbf{r} \right)  = T\int_\Omega  {k\left( {{\bf{r}} , {\bf{r'}}} \right)f\left( {{v_t}\left( \bf{r'} \right)} \right)d{\bf{r'}}} + \lambda v_t\left( {\bf{r}} \right) +e_t\left( {\mathbf{r}} \right).
+v_{t + 1}\left( \mathbf{r} \right)  = T\int_\Omega  {k\left( {\mathbf{r}} , {\mathbf{r}'} \right)f\left( {{v_t}\left( \mathbf{r'} \right)} \right)d{\mathbf{r'}}} + \lambda v_t\left( {\mathbf{r}} \right) +e_t\left( {\mathbf{r}} \right).
 \end{equation}
-where the disturbance $e_t(\mathbf r)$ is a zero-mean normally distributed noise process, spatially coloured but temporally white, with covariance
+where the disturbance $e_t(\mathbf{r})$ is a zero-mean normally distributed noise process, spatially coloured but temporally white, with covariance
 
@@
 % use section* for acknowledgement
+
 \section{clarification for the derivation} 
@@
 \end{equation}
+
+% \section{Ken's Discretization}
+% Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
+% \begin{equation}\label{differential eq}	
+% \tau dv\left( r,t \right) = \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
+% \end{equation}
+% where $e\left( r,t \right)$ is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
+(not too sure about this noise since it needs to be white temporally but coloured spatially - which in continuous space-time I have never seen written ...
+has anyone?)
+% To simplify the notation, but without loss of generality, \ref{differential eq} can be rewritten as
+% \begin{equation}\label{differential simplified}
+% 	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
+% \end{equation}
+% Had $q\left(v(r,t) \right)$ been a linear function in $v$, then \ref{differential simplified} could be rewritten as
+% \begin{equation}\label{differential linear}
+% 	dv\left( r,t \right) = Av(r,t)dt  + d e\left( r,t \right)
+% \end{equation}
+% Considering temporal sampling instances $\delta$ apart given by $\{t_k = 0,~1,~2, \ldots$ \}, then a solution to \ref{differential linear} at each sampling time is given by
+% \begin{equation}\label{linear solution}
+% 	v(r,t_k+\delta) = \exp\{A(\delta)\}x(t) + \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
+% \end{equation}
+% Let the discrete time random variable $e'(r,t_k)$ be
+% \begin{equation}\label{discrete noise}
+% 	e'(r,t_k) = \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
+% \end{equation}
+% then, $e'(r,t_k)$ is a zero mean, temporally white noise term with covariance
+% \begin{equation}\label{covariance of noise}
+% 	E\left[e'(r,t_k),e'^\top(r,t_k) \right] = \int_t^{t+\delta}\exp\{A(t_k+\delta-\tau)\} \Sigma_e(r) \exp\{A(t+\delta-\tau)\} d\tau
+% \end{equation}
+% 
+% But we are not so luck as to be able to go from \ref{differential simplified} to \ref{differential linear} and thus I doubt if we can obtain an exact solution to \ref{differential simplified} without an approximation.
+Agreed?
+% 
+% A possible approximate solution is the one you have already used. Thus, interpreting the difference equation \ref{differential simplified} as an integral equation gives
+% \begin{equation}\label{euler}
+% 	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
+% \end{equation}
+% Using an Euler approximation, \ref{euler} can be approximated at each sampling time by
+% \begin{equation}\label{euler approx 1}
+% 	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
+% \end{equation}
+% which can be rewritten as
+% \begin{equation}\label{euler approx 2}
+% 	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
+% \end{equation}
+% where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
+(Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$)
 

### 2010-04-09 ltx/BrainIDE.tex
Added spectral analysis section

@@
 \section{Spectral Analysis and Decomposition}
-This section provides
+
+Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations \cite{Sanner1992,Scerri2009}.
+Based on the higher dimension extensions of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
+
+Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
+Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions frequently used \cite{some eeg literature here}.
+Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually bandlimited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
+Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
+Given such a bandlimited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
+Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
+
+Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
+The minimum distance between adjacent basis needs to again satisfy Shannon's sampling theorem.
+Thus the minimum distance between basis must again satisfy $\frac{1}{2\nu_c}$.
+Note that, since the dynamic field is frequently spatially oversampled by using a larger number of sensor then imposed by frequency considerations, the distance between basis functions is usually larger then the distance between sensors.
+Note also that since a limited spatial region and since basis functions placed on a regular square grid are being considered, knowledge of the distance between basis functions directly implies the total number of basis functions required.
+
+For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
+The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by $\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}$.
+Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
 

### 2010-04-11 ltx/BrainIDE.tex
made some little changes and TODOs in the paper

@@
         Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
-        Michael~Dewar,~\IEEEmembership{Member,~IEEE,}
+        Michael~Dewar}
         Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
@@
 
-\thanks{Manuscript received Month Day, Year; revised Month Day, Year.}}
+\thanks{Manuscript received Month Day, Year; revised Month Day, Year.}
 
@@
 \end{equation}
-where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function.
-The synaptic response kernel can be more elaborate, using rise and fall time constants, however, this simple form serves our purposes.
-Nonlocal interactions between cortical populations are described by
+where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
 \begin{equation}\label{RateBasedInteractions}
@@
 \end{equation}
-where $f$ is spiking rate of populations $\mathbf{r}'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
 The term $u\left(\mathbf{r},t\right)$ represents a known external input.
-The connectivity kernel is typically a Mexican hat shape described by the sum of weighted Gaussian functions.
-The shape of the kernel is not a critical parameter for our methodology so we shall not define it until later to keep the derivation as general as possible.
+The connectivity kernel is typically a ``Mexican hat'' function \todo{which describes strong local activation, weak mid-range repression and weak long-range activation \cite{}}.
+The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
 % \begin{eqnarray}\label{Connectivity Kernel}
@@
 % \end{todo}
-The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
+The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
 \begin{equation}\label{ActivationFunction}
@@
 \end{equation}
-Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point.
-By combining Eqs.~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model
+%Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. 
+By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential}  we get the spatiotemporal model
 \begin{equation}\label{FullDoubleIntModel}
@@
 \end{equation}
+\todo{Is the above right? I can't think of any way to make $\frac{d}{dt} h(t) + \alpha h(t)$ equal to $\delta(t)$}
 where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 

### 2010-04-12 ltx/BrainIDE.tex
Small paper updates

@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
+The width and positioning of the basis function can be determined by spectral analysis explain in detail in Section~\ref{SpectralAnalysisSection}.
 The connectivity kernel can also be considered a decomposition into a set of basis functions in
@@
 The observation equation of the reduced model is
-\begin{eqnarray}\label{ObservationEquation}
-    \mathbf{y}_t &=& z\left(\mathbf{x}_t\right) + \boldsymbol{\varepsilon}_t \\
-	z\left(\mathbf{x}_t\right) &=& \int_\Omega m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}' \mathbf{x}_t.
-\end{eqnarray}
+\begin{equation}\label{ObservationEquation}
+    \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t \\
+\end{equation}
+where the observation matrix is
+\begin{equation}
+\mathbf C=\begin{bmatrix}\int_{\Omega}m(\mathbf r_1 - \mathbf
+r')\boldsymbol \phi_1(\mathbf r')d\mathbf r'&\int_{\Omega}m(\mathbf r_1
+- \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r'& \hdots
+&\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
+r')d\mathbf r' \\
+\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
+r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
+\phi_2(\mathbf r')d\mathbf r'& \hdots &\int_{\Omega}m(\mathbf r_2 -
+\mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
+\vdots&\vdots&\ddots&\vdots\\
+\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
+r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
+\phi_2(\mathbf r')d\mathbf r'& \hdots &\int_{\Omega}m(\mathbf r_{n_y} -
+\mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
+\end{bmatrix},
+\end{equation}
+and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
 
-\section{Spectral Analysis and Decomposition}
+\section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
 
@@
 	\mathbf{x}_t = q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	\mathbf{y}_t = z(\mathbf{x}_t) + \boldsymbol{\varepsilon}_t,
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{eqnarray}
@@
 	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. 
-
+	\item The size of the dentritic arbour is consistent in the cortex.
 	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing.

### 2010-04-12 src/ODE_ex.py

@@ -1,7 +1,7 @@
 import pylab as pb
 import numpy as np
 from ODE import *
-import quickio
+# import quickio
 #-------------field--------------------
 field_width=40
 dimension=2
@@ -47,7 +47,7 @@ pb.show()
 # -------Sampling properties-------------
 Fs = 1e3   #sampling rate                                       
 Ts = 1/Fs   #sampling period, second
-t_end = .2 # seconds
+t_end = .002 # seconds
 NSamples = t_end*Fs;
 T = pb.linspace(0,t_end,NSamples);
 #--------------model and simulation------------------

### 2010-04-13 ltx/BrainIDE.tex
Updates and edits to paper

@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_t &=& q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
@@
 
-Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations \cite{Sanner1992,Scerri2009}.
-Based on the higher dimension extensions of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
+Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
+Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
 
@@
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions frequently used \cite{some eeg literature here}.
+In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.
 Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually bandlimited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
@@
 Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
+
+Sensors act as a low-pass filter
 
@@
 \begin{eqnarray}
-	\mathbf{x}_t = q(\mathbf{x}_t,\boldsymbol{\theta},\alpha) + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{eqnarray}
-where $\boldsymbol{\theta}$ and $\alpha$ are the systems parameters.
+where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
 

### 2010-04-13 src/ODE.py

@@ -150,7 +150,7 @@ class IDE():
 			w = self.Swc*pb.matrix(np.random.randn(spatial_location_num,1))
 			print "simulation at time",t
 
-			Kernel_convolution_at_s=signal.convolve2d(self.K,pb.vstack(pb.split(spiking_rate,len(self.field_space))),mode='same',boundary='fill')
+			Kernel_convolution_at_s=signal.convolve2d(pb.vstack(pb.split(spiking_rate,len(self.field_space))),self.K,mode='same',boundary='fill')
 
 
 			Kernel_convolution_at_s= (self.spacestep**2)*pb.matrix(pb.ravel(Kernel_convolution_at_s)).T
@@ -175,10 +175,10 @@ class IDE():
 			#V_matrix_temp.append(pb.hstack(pb.split(w,len(self.field_space))).T)
 			#--------------------------------------------------------------------------------------------------
 			#Finding the convolution of the Sensor with the field
-			v_filtered=(self.spacestep**2)*signal.convolve2d(self.S,v_membrane_matrix,mode='same',boundary='fill')
+			v_filtered=(self.spacestep**2)*signal.convolve2d(v_membrane_matrix,self.S,mode='same',boundary='fill')
 			#-------------------------------------------------------------------------------------------------------
 			#Observation
-			Y.append((self.spacestep**2)*(self.Sensor.Values*v_membrane))#+v)
+			Y.append((self.spacestep**2)*(self.Sensor.Values*v_membrane)+v)
 			#-------------------------------------------------------------------------------------------------------
 			#Free Boundary Condition
 			# we simulate over a bigger field to avoid boundary conditions and then we look at the middle part of

### 2010-04-13 src/ODE_ex.py

@@ -3,9 +3,9 @@ import numpy as np
 from ODE import *
 # import quickio
 #-------------field--------------------
-field_width=40
+field_width=40   #40 = -20 to 20, we cut from -10 to 10
 dimension=2
-spacestep=1
+spacestep=0.5
 f_space=pb.arange(-(field_width)/2.,(field_width)/2+spacestep,spacestep)# the step size should in a way that we have (0,0) in our kernel as the center
 spatial_location_num=(len(f_space))**2
 
@@ -33,21 +33,21 @@ alpha=100
 act_func=ActivationFunction(threshold=2,nu=20,beta=.8)
 #----------observations--------------------------
 Sensorwidth =1.2**2 #equals to 3mm
-S_obs= pb.linspace(-10,10,10)
+S_obs= pb.linspace(-10,10,25)
 #S_obs= pb.arange(-10,10+1.25,1.25)
 obs_locns=gen_spatial_lattice(S_obs)
 ny=len(obs_locns)
 widths=[pb.matrix([[Sensorwidth,0],[0,Sensorwidth]])]
 EEG_signals=Sensor(obs_locns,widths,dimension,f_space,ny,spacestep)
 obs_noise_covariance =.1*pb.matrix(np.eye(len(obs_locns),len(obs_locns)))
-[circle(cent,2*pb.sqrt(pb.log(2),)*pb.sqrt(Sensorwidth)/2,'b') for cent in obs_locns]
-pb.show()
+#[circle(cent,2*pb.sqrt(pb.log(2),)*pb.sqrt(Sensorwidth)/2,'b') for cent in obs_locns]
+#pb.show()
 
 
 # -------Sampling properties-------------
 Fs = 1e3   #sampling rate                                       
 Ts = 1/Fs   #sampling period, second
-t_end = .002 # seconds
+t_end = .2 # seconds
 NSamples = t_end*Fs;
 T = pb.linspace(0,t_end,NSamples);
 #--------------model and simulation------------------

### 2010-04-13 ltx/BrainIDE.tex
some edits to the paper and small edits to python functions

@@
 
+The spectral characteristics of the field are governed by the the shape of the connectivity kernel or the coloring of the covariance of the field disturbance.
+If the bandwidth of the disturbance covariance was greater than the bandwidth of the connectivity kernel than the disturbance governs the bandwidth of the system.
+Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth.
+Note, the observable characteristics of the kernel are governed by how it is excited by the input.
+
 Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
-Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions frequently used \cite{some eeg literature here}.
+Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
 In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.

### 2010-04-13 src/UKF_ex.py

@@ -1,5 +1,6 @@
 import pylab as pb
 import numpy as np
+import quickio
 from UKF import *
 
 #-------------field--------------------

### 2010-04-13 ltx/BrainIDE.tex
added to freq analysis in paper

@@
 Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth.
-Note, the observable characteristics of the kernel are governed by how it is excited by the input.
+Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.
 
@@
 In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.
-Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually bandlimited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
+Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a bandlimited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
 Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
 
-Sensors act as a low-pass filter
+There are two options available to alleviate problems with aliasing.
+The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filter.
+The first option is more desirable, since more information is retained.
+In addition, if sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
+Mild aliasing results in distortions in the high frequency components of the field dynamics.
+The basis function decomposition the high frequency components are usually lost.
 

### 2010-04-13 ltx/BrainIDE.tex
added to freq analysis in paper

@@
 There are two options available to alleviate problems with aliasing.
-The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filter.
+The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filters.
 The first option is more desirable, since more information is retained.
-In addition, if sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
-Mild aliasing results in distortions in the high frequency components of the field dynamics.
-The basis function decomposition the high frequency components are usually lost.
+If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
+In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
+It may be estimated using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques.
+Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
+However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem~\cite{Sanner1992}.
+This is further illustrated our results.
 
 Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
-The minimum distance between adjacent basis needs to again satisfy Shannon's sampling theorem.
+The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem.
 Thus the minimum distance between basis must again satisfy $\frac{1}{2\nu_c}$.
-Note that, since the dynamic field is frequently spatially oversampled by using a larger number of sensor then imposed by frequency considerations, the distance between basis functions is usually larger then the distance between sensors.
-Note also that since a limited spatial region and since basis functions placed on a regular square grid are being considered, knowledge of the distance between basis functions directly implies the total number of basis functions required.
-
 For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
@@
 Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
+
+The dynamic field must be spatially oversampled by using a larger number of sensor then imposed by frequency considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
+Following this, the distance between basis functions is usually larger then the distance between sensors.
+\todo{However this is not the case with this work.} For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
+Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
+
+Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
 

### 2010-04-13 ltx/BrainIDE.tex
changes to state estimation

--- 2010-04-13 ltx/BrainIDE.tex
@@
 \section{State and Parameter Estimation}
-The unscented Kalman filter was used for the state estimation (reference the Julier and Uhlmann paper).
+The Unscented Rauch–Tung–Striebel smoother (URTSS) was used for the state estimation \cite{Sarkka2010}, which uses the Unscented Kalman filter for the forward iteration \cite{Julier1997}.
 This method is appropriate for state estimation of stochastic nonlinear dynamical systems.
-Alternatives to this approach are the extended Kalman filter (ref?) (EKF) and sequential Monte Carlo (SMC) filtering (ref?).
+Alternatives to this approach are the extended Kalman filter (ref?) (EKF) and sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
 The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time step.

### 2010-04-13 ltx/BrainIDE.tex
some more changes and aded the guide for journal of neuroeng

@@
 \begin{equation} 
-\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 \begin{cases}
-\rho\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+\gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
 0 & \mathrm{otherwise}.
@@
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
-Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within
+\begin{equation}
+		\Delta_s = \frac{1}{2\rho\nu_c}
+\end{equation}
+ $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
 
@@
 The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem.
-Thus the minimum distance between basis must again satisfy $\frac{1}{2\nu_c}$.
+Thus the minimum distance between basis must again satisfy
+\begin{equation}
+	\Delta_b = \frac{1}{2\rho\nu_c}.
+\end{equation}
 For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.

### 2010-04-13 ltx/BrainIDE.tex
some more changes and aded the guide for journal of neuroeng

@@
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
-In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.
+In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
 Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
 \begin{equation}
-		\Delta_s = \frac{1}{2\rho\nu_c}
+		\Delta_s = \frac{1}{2\rho\nu_c},
 \end{equation}
- $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
+where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
+Satisfying this condition is required for the hidden dynamic field $w_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
+If the condition is not satisfied, spatial aliasing will occur.
 
@@
 The first option is more desirable, since more information is retained.
-If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
+However, if sensors are modelled as having a Gaussian pickup range than the effective filter will not have a sharp cut-off and high frequency components will still remain and mild aliasing will still occur.
 In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
@@
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
 This is further illustrated our results.
-
+$\mathcal{W}$
 Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
-The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem.
-Thus the minimum distance between basis must again satisfy
+The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
+Thus, the minimum distance between basis must satisfy
 \begin{equation}
-	\Delta_b = \frac{1}{2\rho\nu_c}.
+	\Delta_b < \frac{1}{2\nu_c}.
 \end{equation}
 For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
-The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by $\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}$.
-Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
+The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by
+\begin{equation}
+	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}.
+\end{equation}
+Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
 

### 2010-04-13 ltx/BrainIDE.tex
some more changes and aded the guide for journal of neuroeng

@@
 \documentclass[onecolumn,draftcls]{IEEEtran}
-
-\usepackage{graphicx}
+\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
+% \usepackage{graphicx}
 \usepackage{color}                    % For creating coloured text and background
@@
 \section{State and Parameter Estimation}
-The Unscented Rauch–Tung–Striebel smoother (URTSS) was used for the state estimation \cite{Sarkka2010}, which uses the Unscented Kalman filter for the forward iteration \cite{Julier1997}.
+The Unscented Rauch Tung Striebel Smoother (URTSS) was used for the state estimation \cite{Sarkka2010}, where the Unscented Kalman filter is used for the forward iteration \cite{Julier1997}.
 This method is appropriate for state estimation of stochastic nonlinear dynamical systems.
-Alternatives to this approach are the extended Kalman filter (ref?) (EKF) and sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
+Alternatives to this approach are the Extended Kalman Filter (EKF) \cite{Haykin2001}  and sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
 The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time step.
 The linearization maintains the Gaussianality in the model.
-The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution, whilst maintaining the nonlinearity in the system.
-This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides a second order approximation.
-In addition, the computational requirements of the UKF are smaller than the EKF, since the EKF computes the Jacobian at each time step, where the UKF does not.
-SMC filtering (particle filtering) can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
-However, this method is not appropriate for our problem, since it is not feasible for high dimensional systems, due to computation demands.
+The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
+This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
+In addition, the computation of the Jacobian used in the
+EKF can be problematic.
+SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
+However, currently this method is not appropriate for our problem, due to computation demands.
 
@@
 where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
+In forwards iteration since the observation equation is linear in parameters we only need to use Unsented transformation in prediction step.
+The update step equations remains the same as the standard Kalman filtering formulations.
+In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filterin step, however the predicted cross-covariance of the states need to be calculated.
+A summary of the algorithm is given in Algorithm
 
 \section{Comparison of Estimated Parameters and True Parameters}
+
+\begin{algorithm}
+\caption{The CPT for EMD}\label{CPTEMDAlgorithm}
+\begin{algorithmic}[1]
+\State $k=1$
+\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
+\State find local extrema of $cos\left(\phi_k(n)\right)$
+\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
+\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
+\State find local maxima of $h_k(n)$
+\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
+\While { $x_{0,k}(n)$ is not monotonic }
+    \State $k=k+1$
+    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
+    \State repeats steps 3 to 7 to approximate parameters
+\EndWhile
+
+\end{algorithmic}
+\end{algorithm}
 

### 2010-04-13 ltx/BrainIDE.tex
added algorithmx to paper

--- 2010-04-13 ltx/BrainIDE.tex
@@
 
-\usepackage{graphicx}
+\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
+
+% \usepackage{graphicx}
 \usepackage{color}                    % For creating coloured text and background
@@
         Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
-        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
 		David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
-        Anthony~N.~Burkitt,~\IEEEmembership{Member,~IEEE,}
-        and~other~Bosses/Supervisors,~\IEEEmembership{Member,~IEEE.}% <-this % stops a space% <-this % stops a space
+        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space% <-this % stops a space
 
@@
 
+\begin{algorithm}
+\caption{The CPT for EMD}\label{CPTEMDAlgorithm}
+\begin{algorithmic}[1]
+\State $k=1$
+\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
+\State find local extrema of $cos\left(\phi_k(n)\right)$
+\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
+\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
+\State find local maxima of $h_k(n)$
+\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
+\While { $x_{0,k}(n)$ is not monotonic }
+    \State $k=k+1$
+    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
+    \State repeats steps 3 to 7 to approximate parameters
+\EndWhile
+
+\end{algorithmic}
+\end{algorithm}
+
 \section{Discussion}

### 2010-04-13 ltx/BrainIDE.tex

--- 2010-04-13 ltx/BrainIDE.tex
@@
 \documentclass[onecolumn,draftcls]{IEEEtran}
+
 \usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
+
 % \usepackage{graphicx}

### 2010-04-13 ltx/BrainIDE.tex
changes to parameter state estimation

--- 2010-04-13 ltx/BrainIDE.tex
@@
 \documentclass[onecolumn,draftcls]{IEEEtran}
-\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
-% \usepackage{graphicx}
+
+\usepackage{graphicx}
 \usepackage{color}                    % For creating coloured text and background
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 \begin{cases}
-\gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+\rho\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
 0 & \mathrm{otherwise}.
@@
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
-In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
+In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.
 Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
-\begin{equation}
-		\Delta_s = \frac{1}{2\rho\nu_c},
-\end{equation}
-where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
-Satisfying this condition is required for the hidden dynamic field $w_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
-If the condition is not satisfied, spatial aliasing will occur.
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
+Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
 
@@
 The first option is more desirable, since more information is retained.
-However, if sensors are modelled as having a Gaussian pickup range than the effective filter will not have a sharp cut-off and high frequency components will still remain and mild aliasing will still occur.
+If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
 In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
@@
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem~\cite{Sanner1992}.
 This is further illustrated our results.
-$\mathcal{W}$
+
 Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
-The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
-Thus, the minimum distance between basis must satisfy
-\begin{equation}
-	\Delta_b < \frac{1}{2\nu_c}.
-\end{equation}
+The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem.
+Thus the minimum distance between basis must again satisfy $\frac{1}{2\nu_c}$.
 For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
-The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by
-\begin{equation}
-	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}.
-\end{equation}
-Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
+The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by $\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}$.
+Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
 
@@
 \section{Comparison of Estimated Parameters and True Parameters}
-
-\begin{algorithm}
-\caption{The CPT for EMD}\label{CPTEMDAlgorithm}
-\begin{algorithmic}[1]
-\State $k=1$
-\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
-\State find local extrema of $cos\left(\phi_k(n)\right)$
-\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
-\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
-\State find local maxima of $h_k(n)$
-\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
-\While { $x_{0,k}(n)$ is not monotonic }
-    \State $k=k+1$
-    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
-    \State repeats steps 3 to 7 to approximate parameters
-\EndWhile
-
-\end{algorithmic}
-\end{algorithm}
 

### 2010-04-13 ltx/BrainIDE.tex
added algorithmx to paper

@@
 
-\usepackage{graphicx}
+% \usepackage{graphicx}
+\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
 \usepackage{color}                    % For creating coloured text and background
@@
 
+\begin{algorithm}
+\caption{The Unscented Kalman Filter}\label{CPTEMDAlgorithm}
+\begin{algorithmic}[1]
+\State $k=1$
+\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
+\State find local extrema of $cos\left(\phi_k(n)\right)$
+\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
+\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
+\State find local maxima of $h_k(n)$
+\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
+\While { $x_{0,k}(n)$ is not monotonic }
+    \State $k=k+1$
+    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
+    \State repeats steps 3 to 7 to approximate parameters
+\EndWhile
+
+\end{algorithmic}
+\end{algorithm}
+
 \section{Discussion}

### 2010-04-13 ltx/BrainIDE.tex
trying to fix stoopid conflict
small changes to paper

@@
 \documentclass[onecolumn,draftcls]{IEEEtran}
-
+%this is shit
 % \usepackage{graphicx}
@@
 
-% can use linebreaks \\ within to get better formatting as desired
 \title{Estimation of Intracortical Connectivity in a Dynamical Neural Field Model}
@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ \todo{can this be $V_t(\boldsymbol{\nu})$}, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
@@
 The first option is more desirable, since more information is retained.
-If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
+If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gradual allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
 In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
@@
 
-\section{Comparison of Estimated Parameters and True Parameters}
+\section{Results}
 
-\begin{algorithm}
-\caption{The Unscented Kalman Filter}\label{CPTEMDAlgorithm}
-\begin{algorithmic}[1]
-\State $k=1$
-\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
-\State find local extrema of $cos\left(\phi_k(n)\right)$
-\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
-\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
-\State find local maxima of $h_k(n)$
-\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
-\While { $x_{0,k}(n)$ is not monotonic }
-    \State $k=k+1$
-    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
-    \State repeats steps 3 to 7 to approximate parameters
-\EndWhile
+\subsection{Frequency Analysis}
+Figure~\ref{SprectralAnalysis} shows the spectra of the connectivity kernel, the disturbance covariance, the field filtered by the sensor kernel and the observations.
 
-\end{algorithmic}
-\end{algorithm}
+\subsection{State and Parameter Estimation}
 

### 2010-04-13 ltx/BrainIDE.tex
revived section on frequency analysis after it was lost in a conflict

@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ \todo{can this be $V_t(\boldsymbol{\nu})$}, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ (\todo{can this be $V_t(\boldsymbol{\nu})$}), multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
-In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.
+In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
 Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
-Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+\begin{equation}
+\Delta_s = \frac{1}{2\rho\nu_c},
+\end{equation}
+where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
+Satisfying this condition is required for the hidden dynamic field $w_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
+If the condition is not satisfied, spatial aliasing will occur.
 
@@
 The first option is more desirable, since more information is retained.
-If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gradual allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur.
+However, if sensors are modelled as having a Gaussian pickup range than the effective filter will not have a sharp cut-off and high frequency components will still remain and mild aliasing will still occur.
 In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
@@
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
 This is further illustrated our results.
-
+$\mathcal{W}$
 Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
-The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem.
-Thus the minimum distance between basis must again satisfy $\frac{1}{2\nu_c}$.
+The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
+Thus, the minimum distance between basis must satisfy
+\begin{equation}
+\Delta_b < \frac{1}{2\nu_c}.
+\end{equation}
 For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
-The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by $\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}$.
-Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
+The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by
+\begin{equation}
+\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}.
+\end{equation}
+Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
 

### 2010-04-13 ltx/BrainIDE.tex
changes to coloured noise

--- 2010-04-13 ltx/BrainIDE.tex
@@
 \end{equation} 
-where $T$ is the time step, $\lambda = 1-\alpha T$ and $e_t(\mathbf{r}) \sim \mathcal{GP}\left(0,\Sigma\left(\mathbf{r}-\mathbf{r}'\right)\right)$ 
-is an iid spatially colored, temporally white disturbance term. This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
+where $T$ is the time step, $\lambda = 1-\alpha T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
+\begin{equation}\label{eq:FieldCovariance}
+ cov(\mathbf{e}_t,\mathbf{e}_{t+\tau})=
+\begin{cases}
+\gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+0 & \mathrm{otherwise}.
+\end{cases}
+\end{equation}
+ This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma_y\right)$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma{\varepsilon}\right)$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
@@
 \end{eqnarray}
-where $\mathbf{e}_t$ is a zero-mean normal white noise term with the covariance (see Appendix D)
+where $\mathbf{e}_t$ is a zero-mean normal white noise term with the covariance (see Appendix \ref{ColoredNoise})
 \begin{equation} 
-\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
-\end{equation}
-\begin{equation}
- cov(\mathbf{e}_t,\mathbf{e}_{t+\tau})=
-\begin{cases}
-\rho\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
-0 & \mathrm{otherwise}.
-\end{cases}
-\label{eq:FieldCovariance}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 A summary of the algorithm is given in Algorithm
-
-\section{Comparison of Estimated Parameters and True Parameters}
-
 \begin{algorithm}
@@
 \begin{algorithmic}[1]
-\State $k=1$
-\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
-\State find local extrema of $cos\left(\phi_k(n)\right)$
+\State Initialise
+\begin{equation*}
+\hat{\mathbf x}_0=\mathbb E[\mathbf x_0]
+\end{equation*}
+\begin{equation*}
+\mathbf P_0=\mathbb E[(\mathbf x_0-\hat{\mathbf x}_0)(\mathbf x_0-\hat{\mathbf x}_0)^\top]
+\end{equation*}
+\State Form the sigma vectors 
+\begin{equation*}
+\mathcal X_k=[\hat{\mathbf x}_k \quad \hat{\mathbf x}_k+\gamma\sqrt{\mathbf P_k} \quad \hat{\mathbf x}_k-\gamma\sqrt{\mathbf P_k}]
+\end{equation*}
+\State Update the sigma vectors by propogating them through state transition equation and compute the predicted state and the predicted state covariance
+\begin{equation*}
+ \hat{\mathbf x}_{k +1|k}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,k+1|k}
+\end{equation*}
+\begin{equation*}
+ \mathbf P_{k +1|k}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,k+1|k}-\hat{\mathbf x}_{k +1|k})(\mathcal X_{i,k+1|k}-\hat{\mathbf x}_{k +1|k})^\top+\boldsymbol \Sigma_w
+\end{equation*}
 \State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
@@
 \end{algorithm}
+\section{Comparison of Estimated Parameters and True Parameters}
 
@@
 
+% \section{Discrete Time Model}\label{Time Discretization}
  \section{Discrete Time Model}\label{Time Discretization}
@@
 \end{eqnarray}
-
-\section{Colored noise}
-We have
+\section{}\label{ColoredNoise}
+\newtheorem{lemma}{Lemma}
+\begin{lemma}
+Consider the zero-mean process $e_t\left(\mathbf r\right)$ with covariance as defined by (\ref{eq:FieldCovariance}) then
 \begin{equation}
-v_{t + 1}\left( \mathbf{r} \right)  = T\int_\Omega  {k\left( {\mathbf{r}} , {\mathbf{r}'} \right)f\left( {{v_t}\left( \mathbf{r'} \right)} \right)d{\mathbf{r'}}} + \lambda v_t\left( {\mathbf{r}} \right) +e_t\left( {\mathbf{r}} \right).
+ \mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
+\label{eq:AppendixWt}
 \end{equation}
-where the disturbance $e_t(\mathbf{r})$ is a zero-mean normally distributed noise process, spatially coloured but temporally white, with covariance
-
+is a vector valued, zero mean normally distributed white noise process with covariance
 \begin{equation}
-cov(e_t(\mathbf{r}),e_{t+\tau}(\mathbf{r'}))=
-\begin{cases}
-\beta\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
-0 & \mathrm{otherwise}
-\end{cases}
-\label{eq:FieldCovariance}
+\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{equation}
-The final state-space model is given by
-\begin{equation}
-\mathbf{x}_{t + 1} = T q(\mathbf{x}_t)\boldsymbol{\theta} -\lambda \mathbf{x}_t + \boldsymbol{\Gamma}^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
-\end{equation}
-then the covariance of the noise term is given by
+\label{lemma:FieldCovariance}
+\end{lemma}
+\begin{IEEEproof}
+ Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
 \begin{eqnarray}
-\mathbf{\Sigma}_w&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top} e_t\left(\mathbf{r}'\right)d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+ \mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
+&=&\mathbf 0
+\end{eqnarray}
+The covariance of $\mathbf{e}_t$ is
+\begin{eqnarray}
+\mathbf{\Sigma}_e&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top} e_t\left(\mathbf{r}'\right)d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
 &=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{eqnarray}
-
+\end{IEEEproof}
 \section{Parameter estimation using LS}

### 2010-04-13 ltx/BrainIDE.tex

@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ (\todo{can this be $V_t(\boldsymbol{\nu})$}), multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
-In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field.
+In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
 Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$.
-Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+\begin{equation}
+\Delta_s = \frac{1}{2\rho\nu_c},
+\end{equation}
+where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
+Satisfying this condition is required for the hidden dynamic field $w_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
+If the condition is not satisfied, spatial aliasing will occur.
 

### 2010-04-13 ltx/BrainIDE.tex
commit for merge with parham

--- 2010-04-13 ltx/BrainIDE.tex
@@
 $\mathcal{W}$
+
 Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
@@
 The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
-This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
-In addition, the computation of the Jacobian used in the
-EKF can be problematic.
+This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation with at least second order accuracy.
+In addition, the computation of the Jacobian used in the EKF can be problematic.
 SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
@@
 where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
-In forwards iteration since the observation equation is linear in parameters we only need to use Unsented transformation in prediction step.
+In forwards iteration since the observation equation is linear in parameters we only need to use Unscented transformation in prediction step.
 The update step equations remains the same as the standard Kalman filtering formulations.
-In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filterin step, however the predicted cross-covariance of the states need to be calculated.
+In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filtering step, however the predicted cross-covariance of the states need to be calculated.
 A summary of the algorithm is given in Algorithm
@@
 \section{Results}
+\subsection{Simulation}
+Figure~\ref{} illustrates the simulation used to generate the data. Part A. of the Figure shows the simulated field with the sensors positioned location
 
@@
 	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing.
-
 	\item The flexibility of the approach
-
 	\item Combining this method with other to incorporate longer range hetrogeneous connectivity.
-
 	\item The need for activity to perform estimation.

### 2010-04-13 ltx/BrainIDE.tex

--- 2010-04-13 ltx/BrainIDE.tex
@@
 where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
-In forwards iteration since the observation equation is linear in parameters we only need to use Unsented transformation in prediction step.
+In forwards iteration since the observation equation is linear in parameters we only need to use Unscented transformation in prediction step.
 The update step equations remains the same as the standard Kalman filtering formulations.
-In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filterin step, however the predicted cross-covariance of the states need to be calculated.
+In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filtering step, however the predicted cross-covariance of the states need to be calculated.
 A summary of the algorithm is given in Algorithm
-\begin{algorithm}
-\caption{The Unscented Kalman Filter}\label{CPTEMDAlgorithm}
-\begin{algorithmic}[1]
-\State Initialise
-\begin{equation*}
-\hat{\mathbf x}_0=\mathbb E[\mathbf x_0]
-\end{equation*}
-\begin{equation*}
-\mathbf P_0=\mathbb E[(\mathbf x_0-\hat{\mathbf x}_0)(\mathbf x_0-\hat{\mathbf x}_0)^\top]
-\end{equation*}
-\State Form the sigma vectors 
-\begin{equation*}
-\mathcal X_k=[\hat{\mathbf x}_k \quad \hat{\mathbf x}_k+\gamma\sqrt{\mathbf P_k} \quad \hat{\mathbf x}_k-\gamma\sqrt{\mathbf P_k}]
-\end{equation*}
-\State Update the sigma vectors by propogating them through state transition equation and compute the predicted state and the predicted state covariance
-\begin{equation*}
- \hat{\mathbf x}_{k +1|k}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,k+1|k}
-\end{equation*}
-\begin{equation*}
- \mathbf P_{k +1|k}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,k+1|k}-\hat{\mathbf x}_{k +1|k})(\mathcal X_{i,k+1|k}-\hat{\mathbf x}_{k +1|k})^\top+\boldsymbol \Sigma_w
-\end{equation*}
-\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
-\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
-\State find local maxima of $h_k(n)$
-\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
-\While { $x_{0,k}(n)$ is not monotonic }
-    \State $k=k+1$
-    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
-    \State repeats steps 3 to 7 to approximate parameters
-\EndWhile
 
-\end{algorithmic}
-\end{algorithm}
-\section{Comparison of Estimated Parameters and True Parameters}
+\section{Results}
+\subsection{Simulation}
+Figure~\ref{} illustrates the simulation used to generate the data. Part A. of the Figure shows the simulated field with the sensors positioned location
+
+\subsection{Frequency Analysis}
+Figure~\ref{SprectralAnalysis} shows the spectra of the connectivity kernel, the disturbance covariance, the field filtered by the sensor kernel and the observations.
+
+\subsection{State and Parameter Estimation}
 

### 2010-04-13 ltx/Journal of Neuroengineering/IOPLaTeXGuidelines.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\begin{document}

\title[Author guidelines for IOP journals in  \LaTeXe]{How to prepare and submit an article for 
publication in an IOP journal using \LaTeXe}

\author{Author's name}

\address{Institute of Physics 
Publishing, Dirac
House, Temple Back, Bristol BS1 6BE, UK}
\ead{custserv@iop.org}
\begin{abstract}
This document describes the  preparation of an article using \LaTeXe\ and 
\verb"iopart.cls" (the IOP \LaTeXe\ preprint class file).
This class file is designed to help 
authors produce preprints in a form suitable for submission to any of the
journals published by Institute of Physics Publishing.
Authors submitting to any IOP journal, i.e.\ 
both single- and double-column ones, should follow the guidelines set out here. 
On acceptance, their TeX code will be converted to 
the appropriate format for the journal concerned.

\end{abstract}

%Uncomment for PACS numbers title message
%\pacs{00.00, 20.00, 42.10}
% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
%\vspace{2pc}
%\noindent{\it Keywords}: Article preparation, IOP journals
% Uncomment for Submitted to journal title message
%\submitto{\JPA}
% Comment out if separate title page not required
\maketitle

\section{Introduction: file preparation and submission}
The \verb"iopart" \LaTeXe\ article class file is provided to help authors prepare articles for submission to the IOP journals. Submission is not restricted to those using of this class file and articles prepared using any other class or style files can also be submitted. Use of the \verb"iopart" class file does, however, help to speed the publication process and it is hoped it will make it easy for authors to prepare their articles. This document describes and demonstrates the use of \verb"iopart.cls" to produce a preprint for submission and refereeing. The detailed formatting for print and web use will be undertaken by IOP as part of the production process after the article has been accepted for publication, but use of \verb"iopart" does make this simpler.

\subsection{What you will need to supply}
Full details on how to submit files to a particular IOP journal are contained in the document {\it Guidelines for authors} which is discussed in section \ref{agide}. Here we mention the key points you need to consider when preparing your files for submission.

\subsubsection{{\bf Text}} The \LaTeX\ source code of your paper with all figures included in 
the source code (see section \ref{figinc}). Although we recommend that authors use the \verb"iopart" class file, articles prepared using almost any  version of \TeX\ or \LaTeX\ 
can be handled.  
\begin{itemize}
\item {\bf Using \LaTeX\ packages} Most \LaTeXe\ packages can be used if they are 
available in the normal distribution of \LaTeXe; however, if it is essential to use 
a non-standard package then any extra files needed to process the article must 
also be sent in. Authors should be aware that the final version will be printed on 
a different page size and using different fonts to the preprint version so that any 
special effects used should not contain material that is not easily scalable.
Alterations to the source code will be made during the production process in order to 
conform to IOP house style and journal format.
\end{itemize}
\subsubsection{\bf Figures} Figures must be included in an article as encapsulated PostScript files
(see section \ref{figinc}) or created using standard \LaTeX\ drawing commands. 
 Please name all figure files using the guidelines in section \ref{fname}. For more detail
on preparation of EPS figure files, please refer to IOP's graphics guidelines (\gguide) 
which can be downloaded from authors.iop.org.

\begin{itemize}
\item {\bf Including figures\label{fig1}} All figures can be included within the body of the text 
at an appropriate point or grouped together with their captions at the end of the article. A standard graphics inclusion package such as \verb"graphicx" should be used for figure inclusion.
Authors should avoid using special effects generated by including verbatim
PostScript code. Wherever possible, please try to use standard \LaTeX\ tools 
and packages.
\end{itemize}

\subsubsection{\bf BiBTeX \label{bibby}}  If you use BiBTeX to prepare your
references, our preferred  \verb".bst" styles are:

\begin{itemize}
\item for the numerical (Vancouver) reference style we recommend that authors use 
 \verb"unsrt.bst";
\item for alphabetic (Harvard) style reference we recommend that authors use
the \verb"jphysicsB.bst" BiBTeX style file together with the harvard \LaTeX\ package. 
\verb"jphysicsB.bst" is supplied as part of the \verb"harvard.sty" package which can be 
downloaded from www.ctan.org.
\end{itemize}

Please make sure that you include your .bib bibliographic database file(s) and any 
.bst style file(s) you have used (other than unsrt.bst or jphysicsB.bst).

\subsubsection{\bf Copyrighted material} If you wish to illustrate your article using material for which you do not own the copyright then you must seek permission from the copyright holder, usually both the author and the publisher. It is the author's responsibility to obtain copyright permissions and this should be done prior to submitting your article. If you have obtained permission, please provide full details of the permission granted---for example, copies of the text of any e-mails or a copy of any letters you may have received. Figure captions must include an acknowledgment of the original source of the material even when permission to use has been obtained. Full details on copyright can be found in IOP's {\it Guidelines for authors} which can be accessed online at authors.iop.org.

\subsection{Naming your files}
Please name all your files, both figures and text as follows:
\begin{itemize}
\item use only characters from the set a to z, A to Z, 0 to 9 and underscore (\_); 
\item do not use spaces in file names;
\item include an extension to indicate the file type (e.g., .tex, .eps, .txt, etc);
\item do not use any accented characters in file names; for example, \'a, \^e, \~n, \"o, etc because 
they can cause difficulties when processing your files.
\end{itemize}
\subsubsection{\label{fname}Naming your figure files} In addition to the above points, please give each figure file a name which indicates the number of the figure it contains; for example, figure1.eps, figure2a.eps etc. If the figure file contains a figure with multiple parts, for example figure 2(a) to 2(e), give it a name such as figure2a\_2e.eps, and so forth.
\subsection{Submitting your article files to an IOP journal}
For most IOP journals you send your files directly to us by web, e-mail or FTP; however, there are a number of exceptions to this. For certain IOP journals you need to send your files to a different institution or to an external editor. How to find the submission address for a particular journal is discussed in section 1.4, below.
\subsection{Where to send your files \label{agide}}
Full details of how to submit files to a particular IOP journal are contained in IOP's {\it Guidelines for authors} which can be accessed online by going to authors.iop.org. From this document's table of contents, select the `How to submit' link to access full details of the submission address for a particular journal.

\subsection{Obtaining the class file and documentation}
The  \LaTeXe\ class file and guidelines can be downloaded from \verb"authors.iop.org".
Files are available in zipped format for PCs, tar compressed format files for
Unix or as a stuffit archive for Macintosh.

\section{Preparing your article}

Please follow these guidelines as closely as possible, particularly with regard to the preparation of the reference list.

At the start of the \LaTeX\ source please include 
commented material to identify the journal, author and reference number if 
known. The first non-commented line should be 
\verb"\documentclass[12pt]{iopart}"  to load the preprint class 
file. Omitting \verb"[12pt]" produces an article with the normal journal
page and type sizes. The start of the article text is signalled by 
\verb"\begin{document}".
Authors of very long articles may find it convenient to separate 
their article into a series of files each containing a section, each of which is called 
in turn by the primary file.

Authors may add their own macros 
at the start of an article provided they do not overwrite existing definitions and 
that they send copies of their new macros with their text file. Macros for the individual paper not included 
in a style file should be inserted in the preamble to the paper with comments to
describe any complex or non-obvious ones.
\verb"iopart" can be used with other package files such
as those loading the AMS extension fonts 
\verb"msam" and \verb"msbm" (these fonts provide the 
blackboard bold alphabet and various extra maths symbols as well as symbols useful in figure 
captions); an extra style file \verb"iopams.sty" is provided to load these
packages and provide extra definitions for bold Greek letters.

\subsection{Double-column journals}
Authors writing for double-column journals should use the \verb"iopart" class file. Conversion from the single-column format to the double-column output required for printing will be done during the production process. 
However, authors should bear in mind that all mathematical formulae will need to be fitted
into the width of a single column, so individual lines of equations should not occupy more than two thirds of the line width in this preprint form.

\section{The title and abstract page} 
The code for setting the title page information is slightly different from
the normal default in \LaTeX.

\subsection{Titles and article types}
The title is set using the command
\verb"\title{#1}", where \verb"#1" is the title of the article. The
first letter 
of the title should be capitalized with the rest in lower case. 
Mathematical expressions within the title may be left in light-face type.

If the title is too long to use as a running head at the top of each page (apart from the
first) a short
form can be provided as an optional argument (in square brackets)
before the full title, i.e.\ \verb"\title[Short title]{Full title}".

For article types other than papers, \verb"iopart.cls"
has a generic heading \verb"\article[Short title]{TYPE}{Full title}" 
and the specific definitions given in table~\ref{arttype}. In each case (apart from Letters
to the Editor) an 
optional argument can be used immediately after the control sequence name
to specify the short title; where no short title is given the full title
will be used as the running head. 
For Letters use \verb"\letter{Full title}", no short title is required as 
the running head is automatically defined to be {\it Letter to the Editor}.
The generic heading could be used for 
articles such as those presented at a conference or workshop, e.g.
\small\begin{verbatim}
\article[Short title]{WORKSHOP ON HIGH-ENERGY PHYSICS}{Title}
\end{verbatim}\normalsize
Footnotes to titles may be given, though acknowledgment of 
funding should be included in the acknowledgments section rather than here. A footnote can be included by using \verb"\footnote{Text of footnote.}" immediately after the title.

\begin{table}
\caption{\label{arttype}Types of article defined in the {\tt iopart.cls} 
class file.}
\footnotesize\rm
\begin{tabular*}{\textwidth}{@{}l*{15}{@{\extracolsep{0pt plus12pt}}l}}
\br
Command&Type&Heading on first page\\
\mr
\verb"\title{#1}"&Paper&---\\
\verb"\review{#1}"&Review&REVIEW\\
\verb"\topical{#1}"&Topical review&TOPICAL REVIEW\\
\verb"\comment{#1}"&Comment&COMMENT\\
\verb"\note{#1}"&Note&NOTE\\
\verb"\paper{#1}"&Paper&---\\
\verb"\prelim{#1}"&Preliminary communication&PRELIMINARY COMMUNICATION\\
\verb"\rapid{#1}"&Rapid communication&RAPID COMMUNICATION\\
\verb"\letter{#1}"&Letter&LETTER TO THE EDITOR\\
\verb"\article{#1}{#2}"&Other articles&Whatever is entered as {\tt 
\#1}\\
\br
\end{tabular*}
\end{table}

\subsection{Authors' names and addresses}
The next information required is the list of authors' names and 
their affiliations. For the authors' names type \verb"\author{#1}", 
where \verb"#1" is the 
list of all authors' names. The style for the names is initials then
family name, with a comma after all but the last 
two names, which are separated by `and'. Initials should {\it not} be followed by full stops. First (given) names may be used if 
desired and Chinese-style names included in the form they should be printed in. If the authors are at different addresses a superscripted number, e.g. $^1$, \verb"$^1$", should be used after each 
name to reference the author to his/her address. 
If an author has additional information to appear as a footnote, such as 
a permanent address, a normal \LaTeX\ footnote command
should be given after the family name and address marker 
with this extra information.

The addresses of the authors' affiliations follow the list of authors. 
Each address is set by using
\verb"\address{#1}" with the address as the single parameter in braces. 
If there is more 
than one address then the appropriate superscripted number, followed by a space, should come at the start of
the address.

Please also add the e-mail addresses for at least one of the authors. This is done by inserting the 
command \verb"\ead{#1}" after the postal address(es) where \verb"#1" is the e-mail address.  
See section~\ref{startsample} for sample coding. For more than one e-mail address, please use the command 
\verb"\eads{\mailto{#1}, \mailto{#2}}" with \verb"\mailto" surrounding each e-mail address.

\subsection{The abstract}
The abstract follows the addresses and
should give readers concise information about the content 
of the article and indicate the main results obtained and conclusions 
drawn. It should be self-contained with no reference to 
figures, tables, equations, bibliographic references etc
included and should not normally exceed 200 
words.
To indicate the start 
of the abstract type \verb"\begin{abstract}" followed by the text of the 
abstract (not in braces).  The abstract should normally be restricted 
to a single paragraph and is terminated by the command
\verb"\end{abstract}"

\subsection{Subject classification numbers}
Any Physics and Astronomy Classification System (PACS) 
codes or Mathematics Subject Classification (MSC) scheme 
numbers should come immediately after the abstract. 
Classification codes can greatly help in the choice of suitable 
referees and allocation of articles to subject areas. 
For {\it Inverse Problems} and {\it Nonlinearity} authors may 
use either PACS or MSC codes.

PACS or MSC numbers are included after the abstract 
using \verb"\pacs{#1}" and \verb"\ams{#1}" respectively.

After any classification numbers the command
\verb"\submitto{#1}" can be inserted, where \verb"#1" is the journal name written in full or the appropriate control sequence as
given in table~\ref{jlab1}. This command is not essential to the running of the file.

\subsubsection{Information on PACS and MSC}
For more information on PACS and MSC see
\begin{itemize}
\item MSC: http://www.ams.org/msc
\item PACS: http://www.aip.org/pacs
\end{itemize}

\subsection{Keywords}
Keywords should be provided for submissions to {\it Measurement Science and Technology, Physical Biology, Physiological Measurement}, and both parts of {\it Journal of Optics\/}. Add these as a new paragraph starting \verb"\noindent{\it Keywords\/}:" after the end of the abstract.

\subsection{Making a separate title page}
The command \verb"\maketitle" forces a page break after the point where it
is inserted and so to keep the header material on a separate page from the
body of the text insert \verb"\maketitle" or \verb"\newpage" before the start of the text. 
If \verb"\maketitle" is not included the text of the
article will start immediately after the abstract.

\subsection{Sample coding for the start of an article}
\label{startsample}
The code for the start of a title page of a typical paper might read:
\small\begin{verbatim}
\documentclass[12pt]{iopart}
\begin{document}
\title[The anomalous magnetic moment of the 
neutrino]{The anomalous magnetic moment of the 
neutrino and its relation to the solar neutrino problem}

\author{P J Smith$^1$, T M Collins$^2$, 
R J Jones$^3$\footnote{Present address:
Department of Physics, University of Bristol, Tyndalls Park Road, 
Bristol BS8 1TS, UK.} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, 
Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, 
Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, 
University College London, Gower Street, London WC1E~6BT, UK}
\ead{williams@ucl.ac.uk}

\begin{abstract}
...
\end{abstract}
\pacs{1315, 9440T}
\submitto{\JPG}
\maketitle
\end{verbatim}
\normalsize

\section{The text}
\subsection{Sections, subsections and subsubsections}
The text of articles may be divided into sections, subsections and, where necessary, 
subsubsections. To start a new section, end the previous paragraph and 
then include \verb"\section" followed by the section heading within braces. 
Numbering of sections is done {\it automatically} in the headings: 
sections will be numbered 1, 2, 3, etc, subsections will be numbered 
2.1, 2.2,  3.1, etc, and subsubsections will be numbered 2.3.1, 2.3.2, 
etc.  Cross references to other sections in the text should, where
possible, be made using 
labels (see section~\ref{xrefs}) but can also
be made manually. See section~\ref{eqnum} for information on the numbering of displayed equations. Subsections and subsubsections are 
similar to sections but 
the commands are \verb"\subsection" and \verb"\subsubsection" respectively. 
Sections have a bold heading, subsections an italic heading and 
subsubsections an italic heading with the text following on directly.
\small\begin{verbatim}
\section{This is the section title}
\subsection{This is the subsection title}
\end{verbatim}\normalsize

The first section is normally an introduction,  which should state clearly 
the object of the work, its scope and the main advances reported, with 
brief references to relevant results by other workers. In long papers it is 
helpful to indicate the way in which the paper is arranged and the results 
presented.

Footnotes should be avoided whenever possible and can often be included in the text as phrases or sentences in parentheses. If required, they should be used only for brief notes that do not fit conveniently into the text. The use of 
displayed mathematics in footnotes should be avoided wherever possible and no equations within a footnote should be numbered. 
The standard \LaTeX\ macro \verb"\footnote" should be used.

\subsection{Acknowledgments}
Authors wishing to acknowledge assistance or encouragement from 
colleagues, special work by technical staff or financial support from 
organizations should do so in an unnumbered `Acknowledgments' section 
immediately following the last numbered section of the paper. The 
command \verb"\ack" sets the acknowledgments heading as an unnumbered
section. For Letters 
\verb"\ack" does not set a heading but leaves a line space and does not 
indent the next paragraph.

\subsection{Appendices}
Technical detail that it is necessary to include, but that interrupts 
the flow of the article, may be consigned to an appendix. 
Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
If there are 
two or more appendices they should be called Appendix A, Appendix B, etc. 
Numbered equations will be in the form (A.1), (A.2), etc,
figures will appear as figure A1, figure B1, etc and tables as table A1,
table B1, etc.

The command \verb"\appendix" is used to signify the start of the
appendices. Thereafter \verb"\section", \verb"\subsection", etc, will 
give headings appropriate for an appendix. To obtain a simple heading of 
`Appendix' use the code \verb"\section*{Appendix}". If it contains
numbered equations, figures or tables the command \verb"\appendix" should
precede it and \verb"\setcounter{section}{1}" must follow it.

\subsection{Some matters of style}
It will help the readers if your article is written in a clear,
consistent and concise manner. The Production Department at Institute of Physics
Publishing will try to make sure that your work is presented to its
readers in the best possible way without sacrificing the individuality of
your writing. Some recommended 
points to note, however, are the following.
\begin{enumerate}
\item Authors are often inconsistent in the use of `ize' and `ise' endings.
We recommend using `-ize' spellings (diagonalize, 
renormalization, minimization, etc) but there are some common 
exceptions to this, for example: devise, 
promise and advise.

\item English spellings are mandatory (colour, flavour, behaviour, tunnelling, artefact, focused, focusing, fibre, etc) except in the following journals where either American or English spellings are acceptable: {\it Physical Biology}, {\it Smart Materials and Structures} and {\it Journal of Micromechanics and Microengineering}.

\item The words table and figure should be written 
in full and {\bf not} abbreviaged to tab. and fig. Do not include `eq.'\, `equation' etc before an equation number or `ref.'\, `reference' etc before a reference number.
\end{enumerate}

Please check your article carefully for accuracy, consistency and clarity before
submission. Remember that your article will probably be read by many
people whose native language is not English and who may not therefore 
be aware of many of the subtle meanings of words or idiomatic phases
present in the English language. It therefore helps if you try to keep
sentences as short and simple as possible.

\section{Mathematics}
\subsection{Two-line constructions}
The great advantage of \LaTeX\ 
over other text processing systems is its 
ability to handle mathematics to almost any degree of complexity. However, 
in order to produce an article suitable for publication both within a print journal and online, 
authors should exercise some restraint on the constructions used. Some equations using very small characters which are clear in a preprint style article may be difficult read in a smaller format or online at a relatively low resolution.
For simple fractions in the text the solidus \verb"/", as in 
$\lambda/2\pi$, should be used instead of \verb"\frac" or \verb"\over", 
care being taken to use parentheses where necessary to avoid ambiguity, 
for example to distinguish between $1/(n-1)$ and $1/n-1$. Exceptions to 
this are the proper fractions $\frac12$, $\frac13$, $\frac34$, 
etc, which are better left in this form. In displayed equations 
horizontal lines are preferable to solidi provided the equation is 
kept within a height of two lines. A two-line solidus should be 
avoided where possible; the construction $(\ldots)^{-1}$ should be 
used instead; for example use:
\begin{equation*}
\frac{1}{M_{\rm a}}\left(\int^\infty_0{\rm d}
\omega\;\frac{|S_o|^2}{N}\right)^{-1}\qquad\mbox{instead of}\qquad
\frac{1}{M_{\rm a}}\biggl/\int^\infty_0{\rm d}
\omega\;\frac{|S_o|^2}{N}.
\end{equation*}

\subsection{Roman and italic in mathematics}
In mathematics mode \LaTeX\ automatically sets variables in an italic 
font. In most cases authors should accept this italicization. However, 
there are some cases where it is better to use a Roman font; for 
instance, IOP journals use a Roman d for a differential d, a Roman e 
for an exponential e and a Roman i for the square root of $-1$. To 
accommodate this and to simplify the  typing of equations we have 
provided some extra definitions. \verb"\rmd", \verb"\rme" and \verb"\rmi" 
now give Roman d, e and i respectively for use in equations, 
e.g.\ $\rmi x\rme^{2x}\rmd x/\rmd y$ 
is obtained by typing \verb"$\rmi x\rme^{2x}\rmd x/\rmd y$".

Certain other common mathematical functions, such as cos, sin, det and 
ker, should appear in Roman type. \LaTeX\ provides macros for 
most of these functions 
(in the cases above, \verb"\cos", \verb"\sin", \verb"\det" and \verb"\ker" 
respectively); we have also provided 
additional definitions for $\Tr$, $\tr$ and 
$\Or$ (\verb"\Tr", \verb"\tr" and \verb"\Or", respectively).

Subscripts and superscripts should be in Roman type if they are labels 
rather than variables or characters that take values. For example in the 
equation
\[
\epsilon_m=-g\mu_{\rm n}Bm
\]
$m$, the $z$ component of the nuclear spin, is italic because it can have 
different values whereas n is Roman because it 
is a label meaning nuclear ($\mu_{\rm n}$ 
is the nuclear magneton).

\subsection{Displayed equations in double-column journals}
Authors should bear in mind that all mathematical formulae in double-column journals will need to be fitted
into the width of a single column, so individual lines of equations should not occupy more than two thirds of the line width in this preprint form.

\subsection{Special characters for mathematics}
Bold italic characters can be used in our journals to signify vectors (rather
than using an upright bold or an over arrow). To obtain this effect
use \verb"\bi{#1}" within maths mode, e.g. $\bi{ABCdef}$. If upright 
bold characters are required in maths use \verb"\mathbf{#1}" within maths
mode, e.g. $\mathbf{XYZabc}$. The calligraphic (script) uppercase alphabet
is obtained with \verb"\mathcal{AB}" or \verb"\cal{CD}" 
($\mathcal{AB}\cal{CD}$).

The American Mathematical Society provides a series of extra symbol fonts
to use with \LaTeX\ and packages containing the character definitions to
use these fonts. Authors wishing to use Fraktur 
\ifiopams$\mathfrak{ABC}$ \fi
or Blackboard Bold \ifiopams$\mathbb{XYZ}$ \fi can include the appropriate
AMS package (e.g. amsgen, amsfonts, amsbsy, amssymb) with a 
\verb"\usepackage" command or add the command \verb"\usepackage{iopams}"
which loads the four AMS packages mentioned above and also provides
definitions for extra bold characters (all Greek letters and some
additional other symbols).

The package iopams uses the definition \verb"\boldsymbol" in amsbsy
which allows individual non-alphabetical symbols and Greek letters to be 
made bold within equations.
The bold Greek lowercase letters \ifiopams$\balpha \ldots\bomega$,\fi 
are obtained with the commands 
\verb"\balpha" \dots\ \verb"\bomega" (but note that
bold eta\ifiopams, $\bfeta$,\fi\ is \verb"\bfeta" rather than \verb"\beta")
and the capitals\ifiopams, $\bGamma\ldots\bOmega$,\fi\ with commands 
\verb"\bGamma" \dots\
\verb"\bOmega". Bold versions of the following symbols are
predefined in iopams: 
bold partial\ifiopams, $\bpartial$,\fi\ \verb"\bpartial",
bold `ell'\ifiopams, $\bell$,\fi\  \verb"\bell", 
bold imath\ifiopams, $\bimath$,\fi\  \verb"\bimath", 
bold jmath\ifiopams, $\bjmath$,\fi\  \verb"\bjmath", 
bold infinity\ifiopams, $\binfty$,\fi\ \verb"\binfty", 
bold nabla\ifiopams, $\bnabla$,\fi\ \verb"\bnabla", 
bold centred dot\ifiopams, $\bdot$,\fi\  \verb"\bdot", other 
characters are made bold using 
\verb"\boldsymbol{\symbolname}".

Please do not use the style file \verb"amsmath.sty" (part of the AMSTeX package) in conjunction with \verb"iopart.cls". This will result in several errors. To make use of the macros defined in \verb"amsmath.sty", we have provided the file \verb"setstack.sty" which reproduces the following useful macros from \verb"amsmath.sty":
\small\begin{verbatim}
\overset \underset \sideset \substack \boxed   \leftroot
\uproot  \dddot    \ddddot  \varrow   \harrow
\end{verbatim}\normalsize

Table~\ref{math-tab2} lists some other macros for use in 
mathematics with a brief description of their purpose.

\begin{table}
\caption{\label{math-tab2}Other macros defined in IOP macros for use in maths.}
\begin{tabular*}{\textwidth}{@{}l*{15}{@{\extracolsep{0pt plus
12pt}}l}}
\br
Macro&Result&Description\\
\mr
\verb"\fl"&&Start line of equation full left\\
\verb"\case{#1}{#2}"&$\case{\#1}{\#2}$&Text style fraction in display\\
\verb"\Tr"&$\Tr$&Roman Tr (Trace)\\
\verb"\tr"&$\tr$&Roman tr (trace)\\
\verb"\Or"&$\Or$&Roman O (of order of)\\
\verb"\tdot{#1}"&$\tdot{x}$&Triple dot over character\\
\verb"\lshad"&$\lshad$&Text size left shadow bracket\\
\verb"\rshad"&$\rshad$&Text size right shadow bracket\\
\br
\end{tabular*}
\end{table}

\subsection{Alignment of displayed equations}
The normal style for aligning displayed equations is to align them left rather than centre them. The class file automatically does this and indents each line of a display. To make any line start at the left margin of the page, add \verb"\fl" at its start (to indicate full left).

Using the \verb"eqnarray" environment equations will naturally be aligned left without the use of any ampersands for alignment, see equations (\ref{eq1}) and (\ref{eq2})
\begin{eqnarray}
\alpha + \beta =\gamma^2 \label{eq1}\\
\alpha^2 + 2\gamma + \cos\theta = \delta \label{eq2} 
\end{eqnarray}
This is the normal equation style for our journals.

Where some secondary alignment is needed, for instance a second part of an equation on a second line, a single ampersand is added at the point of alignment in each line  (see  (\ref{eq3}) and (\ref{eq4})).
\begin{eqnarray}
\alpha &=2\gamma^2 + \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta} \label{eq3}\\
 & = \delta\theta PQ \cos\gamma. \label{eq4} 
\end{eqnarray}

Two points of alignment are possible using two ampersands for alignment (see  (\ref{eq5}) and (\ref{eq6})).  Note in this case extra space \verb"\qquad" is added before the second ampersand in the longest line (the top one) to separate the condition from the equation. 
\begin{eqnarray}
\alpha &=2\gamma^2 + \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta}\qquad& \theta > 1 \label{eq5}\\
 & = \delta\theta PQ \cos\gamma &\theta \leq 1\label{eq6} 
\end{eqnarray}

For a long equation which has to be split over more than one line the first line should start at the left margin, this is achieved by inserting \verb"\fl" (full left) at the start of the line, the use of the alignment parameter \verb"&" is not necessary unless some secondary alignment is needed.
\begin{eqnarray}
\fl \alpha + 2\gamma^2 = \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta} +  \frac{XY \sin\theta}{X- Y\cos\theta} +
+ \left(\frac{XY \sin\theta}{X+ Y\cos\theta}\right)^2 \nonumber\\
+  \left(\frac{XY \sin\theta}{X- Y\cos\theta}\right)^2\label{eq7} 
\end{eqnarray}

The Plain \TeX\ command \verb"\eqalign" can be used within an \verb"equation" environment to obtain a multiline equation with a single centred number, for example
\begin{equation}
\eqalign{\alpha + \beta =\gamma^2 \cr
\alpha^2 + 2\gamma + \cos\theta = \delta.}\label{eq2} 
\end{equation}

\subsection{Miscellaneous points}
Exponential expressions, especially those containing subscripts or 
superscripts, are clearer if the notation $\exp(\ldots)$ is used except for 
simple examples. For instance $\exp[\rmi(kx-\omega t)]$ and $\exp(z^2)$ are 
preferred to $\e^{\rmi(kx-\omega t)}$ and $\e^{z^2}$, but 
$\e^x$ 
is acceptable. Similarly the square root sign $\sqrt{\phantom{b}}$ should 
only be used with relatively
simple expressions, e.g.\ $\sqrt2$ and $\sqrt{a^2+b^2}$;
in other cases the 
power $1/2$ should be used; for example, $[(x^2+y^2)/xy(x-y)]^{1/2}$.

It is important to distinguish between $\ln = \log_\e$ and $\lg 
=\log_{10}$. Braces, brackets and parentheses should be used in the 
following order: $\{[(\;)]\}$. The same ordering of brackets should be 
used within each size. However, this ordering can be ignored if the
brackets have a 
special meaning (e.g.\ if they denote an average or a function).  Decimal 
fractions should 
always be preceded by a zero: for example 0.123 {\bf not} .123. For long 
numbers commas are not inserted but instead a thin space is added after 
every third character away from the position of the decimal point unless 
this leaves a single separated character: e.g.\ $60\,000$, $0.123\,456\,78$ 
but 4321 and 0.7325.

Equations should be followed by a full stop (periods) when at the end
of a sentence.

\subsection{Equation numbering}
\label{eqnum}
\LaTeX\ provides facilities for automatically numbering equations 
and these should be used where possible. Sequential numbering (1), (2), 
etc, is the default numbering system although, if the command
\verb"\eqnobysec" is included in the preamble, equation numbering
by section is obtained, e.g.\ 
(2.1), (2.2), etc. In articles with several appendices equation numbering
by section is useful in the appendices even when sequential numbering has
been used throughout the main body of the text and is switched on by the 
\verb"\appendix" command. Equation numbering by section {\it must} 
be used for {\it Reports on Progress in 
Physics}. When referring to an equation in the text it is not normally necessary to include the word equation before the number, 
which should be parentheses. Do not 
use abbreviations such as eqn or eq.
When cross-referencing is used, \verb"(\ref{<label>})"
 will produce `(\verb"<eqnum>")',
\verb"\eref{<label>}" produces `(\verb"<eqnum>")' and
\verb"\Eref{<label>}" produces `Equation (\verb"<eqnum>")', 
where \verb"<label>" is the label to produce equation number \verb"<eqnum>".

Sometimes it is useful to number equations as parts of the same
basic equation. This can be accomplished by inserting the 
commands \verb"\numparts" before the equations concerned and 
\verb"\endnumparts" when reverting to the normal sequential numbering.
The equations below show the previous equations numbered as separate parts
using \verb"\numparts ... \endnumparts" and the \verb"eqnarray"
environment
\numparts
\begin{eqnarray}
T_{11}&=(1+P_\e)I_{\uparrow\uparrow}-(1-P_\e)
I_{\uparrow\downarrow}\\
T_{-1-1}&=(1+P_\e)I_{\downarrow\downarrow}-(1-P_\e)I_{\uparrow\downarrow}\\
S_{11}&=(3+P_\e)I_{\downarrow\uparrow}-(3-P_e)I_{\uparrow\uparrow}\\
S_{-1-1}&=(3+P_\e)I_{\uparrow\downarrow}-(3-P_\e)
I_{\downarrow\downarrow}
\end{eqnarray}
\endnumparts

\subsection{Miscellaneous extra commands for displayed equations}
The \verb"\cases" command of Plain \TeX\ is available
for use with \LaTeX\ but has been amended slightly to 
increase the space between the equation and the condition. 
\Eref{cases} 
demonstrates simply the output from the \verb"\cases" command
\begin{equation}
\label{cases}
X=\cases{1&for $x \ge 0$\\
-1&for $x<0$\\}
\end{equation}
%The code used was:
%\small\begin{verbatim}
%\begin{equation}
%\label{cases}
%X=\cases{1&for $x \ge 0$\\
%-1&for $x<0$\\}
%\end{equation}
%\end{verbatim}
%\normalsize

To obtain text style fractions within displayed maths the command 
\verb"\case{#1}{#2}" can be used (see equations (2) and (5)) instead
of the usual \verb"\frac{#1}{#2}" command or \verb"{#1 \over #2}".

When two or more short equations are on the same line they should be 
separated by a `qquad space' (\verb"\qquad"), rather than
\verb"\quad" or any combination of \verb"\,", \verb"\>", \verb"\;" 
and \verb"\ ".

\section{Referencing\label{except}}
Two different styles of referencing are in common use: 
the Harvard alphabetical system and the Vancouver numerical system. 
All IOP journals allow the use of the Harvard or Vancouver system 
(authors should use the style they are comfortable with), 
apart from the following journals

\begin{itemize}
\item {\it Physics in Medicine and Biology} 
\item {\it Physiological Measurement}
\end{itemize}

\noindent for which authors must use the Harvard referencing style.

\subsection{Alphabetical (Harvard) system}
In the Harvard system the name of the author appears in the text together 
with the year of publication. As appropriate, either the date or the name 
and date are included within parentheses. Where there are only two authors 
both names should be given in the text; if there are more than two 
authors only the first name should appear followed by `{\it et al}' 
(which can be obtained by typing \verb"\etal"). When two or 
more references to work by one author or group of authors occur for the 
same year they should be identified by including a, b, etc after the date 
(e.g.\ 1986a). If several references to different pages of the same article 
occur the appropriate page number may be given in the text, e.g.\ Kitchen 
(1982, p 39).

The reference list at the end of an article consists of an 
unnumbered `References' section containing an
alphabetical listing by authors' names and in date order for each 
author or group of identical authors. The reference list in the 
preprint style is started by including the command \verb"\section*{References}" and then
\verb"\begin{harvard}".
Individual references start with \verb"\item[]" and the reference list is completed with \verb"\end{harvard}".
There is also a shortened form of the coding; \verb"\section*{References}"
and \verb"\begin{harvard}" can be replaced by the single command
\verb"\References" and \verb"\end{harvard}" can be shortened to
\verb"\endrefs".

\subsection{Numerical (Vancouver) system}
In the numerical system references are numbered sequentially 
throughout the text. The numbers occur within square brackets and one 
number can be used to designate several references. A numerical 
reference list in the \verb"iopart" style is started by including the 
command \verb"\section*{References}" and then
\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
number in the reference list (or any other number with the same number
of digits).  The 
reference list gives the references in 
numerical, not alphabetical, order and is completed by
\verb"\end{thebibliography}". Short forms of the commands are again
available: \verb"\Bibliography{<num>}" can be used at the start of the
references section and \verb"\endbib" at the end.

A variant of this system is to use labels instead of numbers within 
square brackets, this method is allowed although not recommended.

\subsection{BiBTeX\label{bibtex}}
Note that for the journals lised at the start of section {\ref{except}} authors should use the
appropriate \verb".bst" file to produce references in the correct style---see section \ref{bibby} for
a list of reccommended \verb".bst" files.

\subsection{References, general}
A complete reference should provide the reader with enough information to 
locate the article concerned. Titles of journal articles can also be included and are required for {\it Inverse problems, Journal of Neural Engineering, Measurement Science and Technology, Physical Biology, Physics in Medicine and Biology\/} and {\it Physiological Measurement}. Final page numbers of references are required for {\it Reports on Progress in Physics\/} and {\it Physiological Measurement}.

Up to ten authors may be given in a particular reference; where 
there are more than ten only the first should be given followed by 
`{\it et al}'. If an author is unsure of an abbreviation and the 
journal is not given in appendix B, it is best to leave the title in full.

The terms {\it loc.\ cit.}\ and {\it ibid}.\ should not be used. 
Unpublished conferences and reports should generally not be included 
in the reference list if a published version of the work exists. Articles in the course of publication should 
include the article title and the journal of publication, if known. 
A reference to a thesis submitted for a higher degree may be included 
if it has not been superseded by a published 
paper but the institution where the work was done should be included.

The basic structure of a reference in the reference list is the same in both the alphabetical and numerical systems, the only difference the code at the start of the reference. Alphabetic references are preceded by \verb"\item[]", numeric by \verb"\bibitem{label}" or just \verb"\item" to generate a number or \verb"\nonum" where a reference is not the first in a group of references under the same number.

Cross referencing between the text and the 
reference list is most useful in the numeric system but is not necessary for alphabetic referencing 
in the Harvard system as adding or deleting a reference 
does not normally change any of the other references. 
Care should, however, be taken to make sure that the text citations match the reference list and vice versa.

Note that footnotes to the text should not be 
included in reference list, but should appear at the bottom of the relevant page by using the \verb"\footnote" command.

\subsection{References to journal articles}
A normal reference to a journal article contains three changes of 
font:
the authors and date appear in Roman type, the journal title in 
italic, the volume number in bold and the page numbers in Roman again. 
A typical journal entry would be:

\smallskip
\begin{harvard}
\item[] Cisneros A 1971 {\it Astrophys.\ Space Sci.} {\bf 10} 87
\end{harvard}
\smallskip

\noindent which would be obtained by typing, within the references
environment 
\small\begin{verbatim}
\item[] Cisneros A 1971 {\it Astrophys. Space Sci.} {\bf 10} 87
\end{verbatim}\normalsize

Features to note are the following.

\begin{enumerate}
\item The authors should be in the form surname (with only the first 
letter capitalized) {\bf followed} by the initials with {\bf no} 
periods after the initials. Authors should be separated by a comma 
except for the last two which should be separated by `and' with no 
comma preceding it. For journals that accept titles of articles in the 
reference list,  the title should be in Roman (upright)
lower case letters, except for an initial 
capital, and should follow the date.

\item The year of publication follows the authors and is not in parentheses. An article title (in Roman) would follow the year.

\item The journal is in italic and is abbreviated. \ref{jlabs} 
gives a list of macros that will give the correct abbreviation for 
many of the common journals. If a journal has several parts denoted by 
different letters the part letter should be inserted after the journal in Roman type, e.g.\ 
{\it Phys.\ Rev.\ \rm A}.

\item The volume number is bold; the page number is Roman.
 Both the initial and final page numbers should be given where possible. The final page number should be in 
the shortest possible form and separated from the initial page number by an en rule (\verb"--"), e.g.\ 1203--14.

\item Where there are two or more references with identical authors, 
the authors' names should be repeated for the second and subsequent references. Each individual publication should be presented as a separate reference, although in the numerical system one number can be used for several references. This facilitates linking in the electronic version of the journal. 
\end{enumerate}
\subsection{Electronic journal references}
These often do not always follow the conventional {\it year-journal-volume-page numbers} pattern. Some examples are:

\numrefs{1}
\item Carlip S and Vera R 1998 {\it Phys. Rev.} D {\bf 58} 011345 
\item Davies K and Brown G 1997 {\it J. High Energy Phys.} JHEP12(1997)002
\item Hannestad S 2005 {\it J. Cosmol. Astropart. Phys.} JCAP02(2005)011
\item Hilhorst H J 2005 {\it J. Stat. Mech.} L02003
\item Gundlach C 1999 {\it Liv. Rev. Rel.} 1994-4
\endnumrefs

\subsection{Preprint references}
Preprint may be referenced but if the article concerned has been published in a peer-reviewed journal, that reference should take precedence. If only a preprint reference can be given, it is helpful to include the article title. Examples are:
\vskip6pt
\numrefs{1}
\item Neilson D and Choptuik M 2000 {\it Class. Quantum Grav.} {\bf 17} 761 ({\it Preprint} gr-qc/9812053)
\item Harrison M 1999 Dipheomorphism-invariant manifolds {\it Preprint} hep-th/9909196
\endnumrefs

\subsection{References to books, conference proceedings and reports}

References to books, proceedings and reports are similar, but have only two
changes of font. The authors and date of publication are in Roman, the 
title of the book is in italic, and the editors, publisher, 
town of publication 
and page number are in Roman. A typical reference to a book and a
conference paper might be

\smallskip
\begin{harvard}
\item[] Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} 
(Moscow: Moscow State University Press) p~103
\item[] Caplar R and Kulisic P 1973 {\it Proc.\
Int.\ Conf.\ on Nuclear Physics (Munich)} vol~1 (Amsterdam:  
North-Holland/American Elsevier) p~517
\end{harvard}
\smallskip

\noindent which would be obtained by typing
\small\begin{verbatim}
\item[] Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} 
(Moscow: Moscow State University Press) p~103
\item[] Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear 
Physics (Munich)} vol~1 (Amsterdam: North-Holland/American 
Elsevier) p~517
\end{verbatim}\normalsize
\noindent respectively.

Features to note are the following.
\begin{enumerate}
\item Book titles are in italic and should be spelt out in full with 
initial capital letters for all except minor words. Words such as 
Proceedings, Symposium, International, Conference, Second, etc should 
be abbreviated to Proc., Symp., Int., Conf., 2nd, 
respectively, but the rest of the title should be given in full, 
followed by the date of the conference and the 
town or city where the conference was held. For 
Laboratory Reports the Laboratory should be spelt out wherever 
possible, e.g.\ {\it Argonne National Laboratory Report}.

\item The volume number as, for example, vol~2, should be followed by 
the editors, if any, in a form such as ed~A~J~Smith and P~R~Jones. Use 
\etal if there are more than two editors. Next comes the town of 
publication and publisher, within brackets and separated by a colon, 
and finally the page numbers preceded by p if only one number is given 
or pp if both the initial and final numbers are given.

\item If a book is part of a series (for examples, {\it Springer Tracts in Modern Physics\/}), the series title and volume number is given in parentheses after the book title. Whereas for an individual volume in a multivolume set, the set title is given first, then the volume title. 
\end{enumerate}
\smallskip
\begin{harvard}
\item[]Morse M 1996 Supersonic beam sources {\it Atomic Molecular and Optical Physics\/} ({\it Experimental Methods in the Physical Sciences\/} vol 29) ed F B Dunning and R Hulet (San Diego: Academic)  
\item[]Fulco C E, Liverman C T and Sox H C (eds) 2000 {\it Gulf War and Health\/} vol 1 {\it Depleted Uranium, Pyridostigmine Bromide, Sarin, and Vaccines\/} (Washington, DC: The National Academies Press)
\end{harvard}

\section{Cross referencing\label{xrefs}}
The facility to cross reference items in the text is very useful when 
composing articles as the precise form of the article may be uncertain at the start 
and  revisions and amendments may subsequently be made. 
\LaTeX\ provides excellent facilities for doing cross-referencing
and these can be very useful in preparing articles.

\subsection{References}
\label{refs}
Cross referencing is useful for numeric reference lists because, if it 
is used, adding 
another reference to the list does not then involve renumbering all 
subsequent references. It is not necessary for referencing 
in the Harvard system where the final reference list is alphabetical 
and normally no other changes are necessary when a reference is added or
deleted.
Two passes are necessary initially to get the cross references right 
but once they are correct a single run is usually sufficient provided an 
\verb".aux" file is available and the file 
is run to the end each time.
\verb"\cite" and \verb"\bibitem" are used to link citations in the text
with their entry in the reference list;
if the 
reference list contains an entry \verb"\bibitem{label}", 
then \verb"\bibitem{label}" 
will produce the correct number in the reference list and 
\verb"\cite{label}" will produce the number within square brackets in the 
text. \verb"label" may contain alphabetic letters, 
or punctuation characters but must not contain spaces or commas. It is also
recommended that the underscore character \_{} is not used in cross
referencing. 
Thus labels for the form 
\verb"eq:partial", \verb"fig:run1", \verb"eq:dy'", 
etc, may be used. When several 
references occur together in the text \verb"\cite" may be used with 
multiple labels with commas but no spaces separating them; 
the output will be the 
numbers within a single pair of square brackets with a comma and a 
thin space separating the numbers. Thus \verb"\cite{label1,label2,label4}"
would give [1,\,2,\,4]. Note that no attempt is made by the style file to sort the 
labels and no shortening of groups of consecutive numbers is done.
Authors should therefore try to use multiple labels in the correct 
order.

The numbers for the cross referencing are generated in the order the 
references appear in the reference list, so that if the entries in the 
list are not in the order in which the references appear in the text 
then the 
numbering within the text will not be sequential. To correct this 
change the ordering of the entries in the reference list and then 
rerun {\it twice}.

\subsection{Equation numbers, sections, subsections, figures and 
tables}
Labels for equation numbers, sections, subsections, figures and tables 
are all defined with the \verb"\label{label}" command and cross references 
to them are made with the \verb"\ref{label}" command.

Any section, subsection, subsubsection, appendix or subappendix 
command defines a section type label, e.g. 1, 2.2, A2, A1.2 depending 
on context. A typical article might have in the code of its introduction 
`The results are discussed in section\verb"~\ref{disc}".' and
the heading for the discussion section would be:
\small\begin{verbatim}
\section{Results}\label{disc}
\end{verbatim}\normalsize
Labels to sections, etc, may occur anywhere within that section except
within another numbered environment. 
Within a maths environment labels can be used to tag equations which are 
referred to within the text.

In addition to the standard \verb"\ref{<label>}" the abbreviated
forms given in the \tref{abrefs}
are available for reference to standard parts of the text

\Table{\label{abrefs}Alternatives to the normal references $\backslash${\tt ref} 
and the text generated by
them. Note it is not normally necessary to include the word equation
before an equation number except where the number starts a sentence. The
versions producing an initial capital should only be used at the start of
sentences.} 
\br
Reference&Text produced\\
\mr
\verb"\eref{<label>}"&(\verb"<num>")\\
\verb"\Eref{<label>}"&Equation (\verb"<num>")\\
\verb"\fref{<label>}"&figure \verb"<num>"\\
\verb"\Fref{<label>}"&Figure \verb"<num>"\\
\verb"\sref{<label>}"&section \verb"<num>"\\
\verb"\Sref{<label>}"&Section \verb"<num>"\\
\verb"\tref{<label>}"&table \verb"<num>"\\
\verb"\Tref{<label>}"&Table \verb"<num>"\\
\br
\endTable

\section{Tables and table captions}
Tables are numbered serially and referred to in the text 
by number (table 1, etc, {\bf not} tab. 1). Each table should have an 
explanatory caption which should be as concise as possible. If a table 
is divided into parts these should be labelled \pt(a), \pt(b), 
\pt(c), etc but there should be only one caption for the whole 
table, not separate ones for each part.

In the preprint style the tables may be included in the text 
or listed separately after the reference list 
starting on a new page.

\subsection{The basic table format}
The standard form for a table is:
\small\begin{verbatim}
\begin{table}
\caption{\label{label}Table caption.}
\begin{indented}
\item[]\begin{tabular}{@{}llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{indented}
\end{table}
\end{verbatim}\normalsize

Points to note are:
\begin{enumerate}
\item The caption comes before the table. It should have a period at
the end.

\item Tables are normally set in a smaller type than the text.
The normal style is for tables to be indented. This is accomplished
by using \verb"\begin{indented}" \dots\ \verb"\end{indented}"
and putting \verb"\item[]" before the start of the tabular environment.
Omit these
commands for any tables which will not fit on the page when indented.

\item The default is for columns to be aligned left and 
adding \verb"@{}" omits the extra space before the first column.

\item Tables have only horizontal rules and no vertical ones. The rules at
the top and bottom are thicker than internal rules and are set with
\verb"\br" (bold rule). 
The rule separating the headings from the entries is set with
\verb"\mr" (medium rule).

\item Numbers in columns should be aligned on the decimal point;
to help do this a control sequence \verb"\lineup" has been defined 
which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
to be a space the width of a minus sign, and \verb"\-" to be a left
overlapping minus sign. \verb"\-" is for use in text mode while the other
two commands may be used in maths or text.
(\verb"\lineup" should only be used within a table
environment after the caption so that \verb"\-" has its normal meaning
elsewhere.) See table~\ref{tabone} for an example of a table where
\verb"\lineup" has been used.
\end{enumerate}

\begin{table}
\caption{\label{tabone}A simple example produced using the standard table commands 
and $\backslash${\tt lineup} to assist in aligning columns on the 
decimal point. The width of the 
table and rules is set automatically by the 
preamble.}

\begin{indented}
\lineup
\item[]\begin{tabular}{@{}*{7}{l}}
\br                              
$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
\mr
\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
\br
\end{tabular}
\end{indented}
\end{table}

\subsection{Simplified coding and extra features for tables}
The basic coding format can be simplified using extra commands provided in
the \verb"iopart" class file. The commands up to and including 
the start of the tabular environment
can be replaced by
\small\begin{verbatim}
\Table{\label{label}Table caption}
\end{verbatim}\normalsize
this also activates the definitions within \verb"\lineup".
The final three lines can also be reduced to \verb"\endTable" or
\verb"\endtab". Similarly for a table which does not fit in when indented
\verb"\fulltable{\label{label}caption}" \dots\ \verb"\endfulltable" or \verb"\endtab"
can be used. \LaTeX\ optional positional parameters can, if desired, be added after 
\verb"\Table{\label{label}caption}" and \verb"\fulltable{\label{label}caption}".

\verb"\centre{#1}{#2}" can be used to centre a heading 
\verb"#2" over \verb"#1" 
columns and \verb"\crule{#1}" puts a rule across 
\verb"#1" columns. A negative 
space \verb"\ns" is usually useful to reduce the space between a centred 
heading and a centred rule. \verb"\ns" should occur immediately after the 
\verb"\\" of the row containing the centred heading (see code for
\tref{tabl3}). A small space can be 
inserted between rows of the table 
with \verb"\ms" and a half line space with \verb"\bs" 
(both must follow a \verb"\\" but should not have a 
\verb"\\" following them).

\Table{\label{tabl3}A table with headings spanning two columns and containing notes. 
To improve the 
visual effect a negative skip ($\backslash${\tt ns})
has been put in between the lines of the 
headings. Commands set-up by $\backslash${\tt lineup} are used to aid 
alignment in columns. $\backslash${\tt lineup} is defined within
the $\backslash${\tt Table} definition.}
\br
&&&\centre{2}{Separation energies}\\
\ns
&Thickness&&\crule{2}\\
Nucleus&(mg\,cm$^{-2}$)&Composition&$\gamma$, n (MeV)&$\gamma$, 2n (MeV)\\
\mr
$^{181}$Ta&$19.3\0\pm 0.1^{\rm a}$&Natural&7.6&14.2\\
$^{208}$Pb&$\03.8\0\pm 0.8^{\rm b}$&99\%\ enriched&7.4&14.1\\
$^{209}$Bi&$\02.86\pm 0.01^{\rm b}$&Natural&7.5&14.4\\
\br
\end{tabular}
\item[] $^{\rm a}$ Self-supporting.
\item[] $^{\rm b}$ Deposited over Al backing.
\end{indented}
\end{table}

Units should not normally be given within the body of a table but 
given in brackets following the column heading; however, they can be 
included in the caption for long column headings or complicated units. 
Where possible tables should not be broken over pages. 
If a table has related notes these should appear directly below the table
rather than at the bottom of the page. Notes can be designated with
footnote symbols (preferable when there are only a few notes) or
superscripted small roman letters. The notes are set to the same width as
the table and in normal tables follow after \verb"\end{tabular}", each
note preceded by \verb"\item[]". For a full width table \verb"\noindent"
should precede the note rather than \verb"\item[]". To simplify the coding 
\verb"\tabnotes" can, if desired, replace \verb"\end{tabular}" and 
\verb"\endtabnotes" replaces
\verb"\end{indented}\end{table}".

If all the tables are grouped at the end of a document
the command \verb"\Tables" is used to start a new page and 
set a heading `Tables and table captions'. If the tables follow an appendix then add the command \verb"\noappendix" to revert to normal style numbering.

\section{Figures and figure captions}

Figures (with their captions) can be incorporated into the text at the appropriate position or grouped together
at the end of the article. If the figures are at the end of the article and follow an appendix then add the command \verb"\noappendix" to revert to normal style numbering.

\subsection{Using copyright material}
If you wish to illustrate your paper using material for which you 
do not own the copyright then you must seek permission from 
the copyright holder, usually both the author and the publisher of the previous work. It is the author's responsibility to obtain 
copyright permissions and this should be done
prior to submitting your paper. 
If you have obtained permission, please provide full details of 
the permission granted---for example, copies of the text of any e-mails 
or a copy of any letters you may have received. Figure captions must include an acknowledgment of the original source of the material even when permission to use has been obtained.

\subsection{Inclusion of graphics files\label{figinc}}
Using the \verb"graphicx" package graphics files can 
be included within figure and center environments at an 
appropriate point within the text using code such as:
\small\begin{verbatim}
\includegraphics{file.eps}
\end{verbatim}\normalsize
The \verb"graphicx" package supports various optional arguments
to control the appearance of the figure. Other similar 
packages can also be used (e.g. \verb"graphics", \verb"epsf"). 
For more detail about graphics inclusion see the documentation 
of the \verb"graphicx" package, refer to one of the books on \LaTeX\ {\cite{book1}}
or download some of the excellent free documentation available via the Comprehensive
TeX Archive Network (CTAN) http://www.ctan.org---{in particular see \cite{eps}}.
IOP's graphics guidelines, \gguide, provide further information on preparing EPS files---a copy
should have accompanied this document but it may be download from authors.iop.org.

\subsection{Captions}
Each figure should have a brief caption describing it and, if 
necessary, interpreting the various lines and symbols on the figure. 
As much lettering as possible should be removed from the figure itself 
and included in the caption. If a figure has parts, these should be 
labelled ($a$), ($b$), ($c$), etc and all parts should be described 
within a single caption. \Tref{blobs} gives the definitions for describing 
symbols and lines often used within figure captions (more symbols are 
available when using the optional packages loading the AMS extension fonts).

\subsection{Multimedia}
All of our journals encourage authors to submit multimedia attachments to 
enhance the online versions of published research articles. Multimedia 
enhancements typically consist of video clips, animations or supplementary 
data such as data files, tables of extra information or extra figures. They can 
add to the reader's understanding and present results in attractive ways that go 
beyond what can be presented in the print version of the journal. 
The printed journal remains the archival version, and multimedia items are 
supplements which enhance a reader's understanding of the paper but are not 
essential to that understanding. For electronic-only journals, multimedia attachments 
may be used to convey essential information. Guidelines on multimedia file formats 
are contained in the document {\it Guidelines for authors} which can be accessed 
online by going to authors.iop.org.

\begin{table}[t]
\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
captions.}
\begin{indented}
\item[]\begin{tabular}{@{}lllll}
\br
Control sequence&Output&&Control sequence&Output\\
\mr
\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
\br
\end{tabular}
\end{indented}
\end{table}

\clearpage

\appendix
\section{List of macros for formatting text, figures and tables}

\begin{table}[hb]
\caption{Macros available for use in text. Parameters in square brackets are optional.}
\footnotesize\rm
\begin{tabular}{@{}*{7}{l}}
\br
Macro name&Purpose\\
\mr
\verb"\title[#1]{#2}"&Title of article and short title (optional)\\
\verb"\paper[#1]{#2}"&Title of paper and short title (optional)\\
\verb"\letter{#1}"&Title of Letter to the Editor\\
\verb"\comment[#1]{#2}"&Title of Comment and short title (optional)\\
\verb"\topical[#1]{#2}"&Title of Topical Review and short title 
(optional)\\
\verb"\review[#1]{#2}"&Title of review article and short title (optional)\\
\verb"\note[#1]{#2}"&Title of Note and short title (optional)\\
\verb"\prelim[#1]{#2}"&Title of Preliminary Communication \& short title\\
\verb"\author{#1}"&List of all authors\\
\verb"\article[#1]{#2}{#3}"&Type and title of other articles and 
short title (optional)\\
\verb"\address{#1}"&Address of author\\
\verb"\pacs{#1}"&PACS classification codes\\
\verb"\pacno{#1}"&Single PACS classification code\\
\verb"\ams{#1}"&Mathematics Classification Scheme\\
\verb"\submitto{#1}"&`Submitted to' message\\
\verb"\maketitle"&Creates title page\\
\verb"\begin{abstract}"&Start of abstract\\
\verb"\end{abstract}"&End of abstract\\
\verb"\nosections"&Inserts space before text when no sections\\
\verb"\section{#1}"&Section heading\\
\verb"\subsection{#1}"&Subsection heading\\
\verb"\subsubsection{#1}"&Subsubsection heading\\
\verb"\appendix"&Start of appendixes\\
\verb"\ack"&Acknowledgments heading\\
\verb"\References"&Heading for reference list\\
\verb"\begin{harvard}"&Start of alphabetic reference list\\
\verb"\end{harvard}"&End of alphabetic reference list\\
\verb"\begin{thebibliography}{#1}"&Start of numeric reference list\\
\verb"\end{thebibliography}"&End of numeric reference list\\
\verb"\etal"&\etal for text and reference lists\\
\verb"\nonum"&Unnumbered entry in numerical reference list\\
\br
\end{tabular}
\end{table}

\begin{table}
\caption{Macros defined within {\tt iopart.cls}
for use with figures and tables.}
\begin{indented}
\item[]\begin{tabular}{@{}l*{15}{l}}
\br
Macro name&Purpose\\
\mr
\verb"\Figures"&Heading for list of figure captions\\
\verb"\Figure{#1}"&Figure caption\\
\verb"\Tables"&Heading for tables and table captions\\
\verb"\Table{#1}"&Table caption\\
\verb"\fulltable{#1}"&Table caption for full width table\\
\verb"\endTable"&End of table created with \verb"\Table"\\
\verb"\endfulltab"&End of table created with \verb"\fulltable"\\
\verb"\endtab"&End of table\\
\verb"\br"&Bold rule for tables\\
\verb"\mr"&Medium rule for tables\\
\verb"\ns"&Small negative space for use in table\\
\verb"\centre{#1}{#2}"&Centre heading over columns\\
\verb"\crule{#1}"&Centre rule over columns\\
\verb"\lineup"&Set macros for alignment in columns\\
\verb"\m"&Space equal to width of minus sign\\
\verb"\-"&Left overhanging minus sign\\
\verb"\0"&Space equal to width of a digit\\
\br
\end{tabular}
\end{indented}
\end{table}

\clearpage
\section{Control sequences for journal
abbreviations}
\label{jlabs}
\begin{table}[hb]
\caption{\label{jlab1}Abbreviations for the IOP journals.}
\begin{indented}
\item[]
\begin{tabular}{@{}lll}
\br
Macro name&{\rm Short form of journal title}&Years relevant\\
\mr
{\it Current journals}\\
\mr
\verb"\CQG"&Class. Quantum Grav.\\
\verb"\EJP"&Eur. J. Phys.\\
\verb"\IP"&Inverse Problems\\
\verb"\JHEP"&J. High Energy Phys.&1999 and onwards\\
\verb"\JMM"&J. of Michromech. and Microeng.\\
\verb"\JNE"&J. Neural Eng.\\
\verb"\JOA"&J. Opt. A: Pure and Applied Opt.&1998 and onwards\\
\verb"\JOB"&J. Opt. B: Quantum and Semiclass. Opt.&1999 and onwards\\
\verb"\JPA"&J. Phys. A: Math. Gen.\\
\verb"\jpb"&J. Phys. B: At. Mol. Opt. Phys.&1988 and onwards\\
\verb"\JPCM"&J. Phys: Condens. Matter&1989 and onwards\\
\verb"\JPD"&J. Phys. D: Appl. Phys.\\
\verb"\jpg"&J. Phys. G: Nucl. Part. Phys.&1989 and onwards\\
\verb"\MSMSE"&Modelling Simul. Mater. Sci. Eng.\\
\verb"\MST"&Meas. Sci. Technol.&1990 and onwards\\
\verb"\NJP"&New J. Phys.&1999 and onwards\\
\verb"\NL"&Nonlinearity\\
\verb"\NT"&Nanotechnology\\
\verb"\PB"&Phys. Biol.\\
\verb"\PM"&Physiol. Meas.\\
\verb"\PMB"&Phys. Med. Biol.\\
\verb"\PPCF"&Plasma Physics and Controlled Fusion\\
\verb"\PSST"&Plasma Sources Sci. Technol.\\
\verb"\RPP"&Rep. Prog. Phys.\\
\verb"\SST"&Semicond. Sci. Technol.\\
\verb"\SMS"&Smart Mater. Struct.\\
\verb"\SUST"&Supercond. Sci. Technol.\\
\mr
{\it No Longer Published}\\
\mr
\verb"\JPB"&J. Phys. B: At. Mol. Phys.&1968--1987\\
\verb"\JPC"&J. Phys. C: Solid State Phys.&1968--1988\\
\verb"\JPE"&J. Phys. E: Sci. Instrum.&1968--1989\\
\verb"\JPF"&J. Phys. F: Met. Phys.&1971--1988\\
\verb"\JPG"&J. Phys. G: Nucl. Phys.&1975--1988\\
\verb"\PAO"&Pure and Applied Opt.&1992--1998\\
\verb"\QO"&Quantum Opt.&1989--1994\\
\verb"\QSO"&Quantum and Semiclass. Opt.&1995--1998\\
\br
\end{tabular}
\end{indented}
\end{table}

\begin{table}

\caption{\label{jlab2}Abbreviations for some more 
common non-IOP journals.}
\begin{indented}
\item[]\begin{tabular}{@{}ll}
\br
Macro name&{\rm Short form of journal}\\
\mr
\verb"\AC"&Acta Crystallogr.\\
\verb"\AM"&Acta Metall.\\
\verb"\AP"&Ann. Phys., Lpz\\
\verb"\APNY"&Ann. Phys., NY\\
\verb"\APP"&Ann. Phys., Paris\\
\verb"\CJP"&Can. J. Phys.\\
\verb"\GRG"&Gen. Rel. Grav.\\
\verb"\JAP"&J. Appl. Phys.\\
\verb"\JCP"&J. Chem. Phys.\\
\verb"\JJAP"&Japan. J. Appl. Phys.\\
\verb"\JMMM"&J. Magn. Magn. Mater.\\
\verb"\JMP"&J. Math. Phys.\\
\verb"\JOSA"&J. Opt. Soc. Am.\\
\verb"\JP"&J. Physique\\
\verb"\JPhCh"&J. Phys. Chem.\\
\verb"\JPSJ"&J. Phys. Soc. Japan\\
\verb"\JQSRT"&J. Quant. Spectrosc. Radiat. Transfer\\
\verb"\NC"&Nuovo Cimento\\
\verb"\NIM"&Nucl. Instrum. Methods\\
\verb"\NP"&Nucl. Phys.\\
\verb"\PF"&Phys. Fluids\\
\verb"\PL"&Phys. Lett.\\
\verb"\PR"&Phys. Rev.\\
\verb"\PRL"&Phys. Rev. Lett.\\
\verb"\PRS"&Proc. R. Soc.\\
\verb"\PS"&Phys. Scr.\\
\verb"\PSS"&Phys. Status Solidi\\
\verb"\PTRS"&Phil. Trans. R. Soc.\\
\verb"\RMP"&Rev. Mod. Phys.\\
\verb"\RSI"&Rev. Sci. Instrum.\\
\verb"\SSC"&Solid State Commun.\\
\verb"\SPJ"&Sov. Phys.--JETP\\
\verb"\ZP"&Z. Phys.\\
\br
\end{tabular}
\end{indented}
\end{table}

\section*{References}
\begin{thebibliography}{10}
\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
(Reading, MA: Addison-Wesley)
\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
\end{thebibliography}

\end{document}

### 2010-04-14 ltx/BrainIDE.tex
UKF algorithm

--- 2010-04-13 ltx/BrainIDE.tex
@@
 \begin{equation*}
-\hat{\mathbf x}_0=\mathbb E[\mathbf x_0]
+\hat{\mathbf x}_0, \mathbf P_0
+\end{equation*}
+\State Forward iteration
+For $t \in \left\lbrace 0,\cdots, N\right\rbrace $,
+\begin{equation*}
+\mathcal X_t^f=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^{f}-\gamma\sqrt{\mathbf P_t^f}]
+\end{equation*}
+Propogate the sigma points through the dynamic model
+\begin{equation}
+\mathcal X_{i,t+1|t}^{f*}=Q(\mathcal X_t^f,u_t)
+\end{equation}
+\begin{equation*}
+ \hat{\mathbf x}_{k +t}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f*}
 \end{equation*}
 \begin{equation*}
-\mathbf P_0=\mathbb E[(\mathbf x_0-\hat{\mathbf x}_0)(\mathbf x_0-\hat{\mathbf x}_0)^\top]
-\end{equation*}
-\State Form the sigma vectors 
-\begin{equation*}
-\mathcal X_k=[\hat{\mathbf x}_k \quad \hat{\mathbf x}_k+\gamma\sqrt{\mathbf P_k} \quad \hat{\mathbf x}_k-\gamma\sqrt{\mathbf P_k}]
-\end{equation*}
-\State Update the sigma vectors by propogating them through state transition equation and compute the predicted state and the predicted state covariance
-\begin{equation*}
- \hat{\mathbf x}_{k +1|k}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,k+1|k}
+ \mathbf P_{t +1}^-=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e
 \end{equation*}
 \begin{equation*}
- \mathbf P_{k +1|k}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,k+1|k}-\hat{\mathbf x}_{k +1|k})(\mathcal X_{i,k+1|k}-\hat{\mathbf x}_{k +1|k})^\top+\boldsymbol \Sigma_w
+\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_v)^{-1}
 \end{equation*}
-\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
-\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
-\State find local maxima of $h_k(n)$
-\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
-\While { $x_{0,k}(n)$ is not monotonic }
-    \State $k=k+1$
-    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
-    \State repeats steps 3 to 7 to approximate parameters
-\EndWhile
-
+\begin{equation*}
+\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})
+\end{equation*}
+\begin{equation*}
+ \mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}
+\end{equation*}
+\State Backward iteration
+\State initialisation
+\begin{equation}
+ \mathbf P_T^s= \mathbf P_T^f
+\end{equation}
+\begin{equation}
+\hat{\mathbf x}^s_T= \hat{\mathbf x}^f_T
+\end{equation}
+For $t \in \left\lbrace N-1, \cdots, 0 \right\rbrace $
+\begin{equation*}
+\mathcal X_t^s=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}]
+\end{equation*}
 \end{algorithmic}

### 2010-04-14 ltx/Journal of Neuroengineering/IOPLaTeXGuidelines.tex
switching to different sty for journal

@@
 
-\title[Author guidelines for IOP journals in  \LaTeXe]{How to prepare and submit an article for 
-publication in an IOP journal using \LaTeXe}
-
-\author{Author's name}
-
-\address{Institute of Physics 
-Publishing, Dirac
-House, Temple Back, Bristol BS1 6BE, UK}
-\ead{custserv@iop.org}
+\title[State and Parameter Estimation for a Spatio-temporal Neural Fields]{State and Parameter Estimation for a Spatio-temporal Neural Field Model}
+
+\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
+
+\address{$^1$ Department
+of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
+Vic, 3010 Australia}
+\address{$^2$ Department
+of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
+S1 3JD, UK}
+\address{$^3$ Mike's}
+\address{$^4$ Ken's}
+\ead{dfreestone@bionicear.org}
 \begin{abstract}

### 2010-04-14 src/Python 2.6/ODE_ex.py
switching to different sty for journal part 2

@@ -7,7 +7,7 @@ def ex_1():
 	#-------------field--------------------
 	field_width=40
 	dimension=2
-	spacestep=4
+	spacestep=0.5
 	f_space=pb.arange(-(field_width)/2.,(field_width)/2+spacestep,spacestep)# the step size should in a way that we have (0,0) in our kernel as the center
 	spatial_location_num=(len(f_space))**2
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added article in template for JoNE

--- 2010-04-14 ltx/BrainIDE.tex
@@
-%% bare_jrnl.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-\documentclass[onecolumn,draftcls]{IEEEtran}
-%this is shit
-% \usepackage{graphicx}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    INSTITUTE OF PHYSICS PUBLISHING                                   %
+%                                                                      %
+%   `Preparing an article for publication in an Institute of Physics   %
+%    Publishing journal using LaTeX'                                   %
+%                                                                      %
+%    LaTeX source code `ioplau2e.tex' used to generate `author         %
+%    guidelines', the documentation explaining and demonstrating use   %
+%    of the Institute of Physics Publishing LaTeX preprint files       %
+%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
+%                                                                      %
+%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
+%                                                                      %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+% First we have a character check
+%
+% ! exclamation mark    " double quote  
+% # hash                ` opening quote (grave)
+% & ampersand           ' closing quote (acute)
+% $ dollar              % percent       
+% ( open parenthesis    ) close paren.  
+% - hyphen              = equals sign
+% | vertical bar        ~ tilde         
+% @ at sign             _ underscore
+% { open curly brace    } close curly   
+% [ open square         ] close square bracket
+% + plus sign           ; semi-colon    
+% * asterisk            : colon
+% < open angle bracket  > close angle   
+% , comma               . full stop
+% ? question mark       / forward slash 
+% \ backslash           ^ circumflex
+%
+% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
+% abcdefghijklmnopqrstuvwxyz 
+% 1234567890
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\documentclass[12pt]{iopart}
 \usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
-\usepackage{color}                    % For creating coloured text and background
-\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-% TODO environment
+\usepackage{color}  
+\usepackage{iopams,setstack}                  % For creating coloured text and background
+% \usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
+% \newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
+%Uncomment next line if AMS fonts required
 
@@
 
-\title{Estimation of Intracortical Connectivity in a Dynamical Neural Field Model}
+\title[State and Parameter Estimation for a Spatio-temporal Neural Fields]{State and Parameter Estimation for a Spatio-temporal Neural Fields}
 
-\author{Dean~R.~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
-        Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
-        Michael~Dewar}
-        Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
-		David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
-        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space% <-this % stops a space
+\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
 
-\thanks{D. Freestone is with the Department
+\address{$^1$ Department
 of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
-Vic, 3010 Australia {\tt\small dfreestone@bionicear.org}.}% <-this % stops a space
-\thanks{P. Aram is with Sheffield...}
-\thanks{M. Dewar is with Edinburgh...}
-\thanks{K. Scerri is with Malta...}
-\thanks{V. Kadirkamanathan is with Sheffield...}
+Vic, 3010 Australia}
+\address{$^2$ Department
+of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
+S1 3JD, UK}
+\address{$^3$ Mike's}
+\address{$^4$ Ken's}
+\ead{dfreestone@bionicear.org}
+\begin{abstract}
+Will do the abstract towards the end.
+\end{abstract}
 
-\thanks{Manuscript received Month Day, Year; revised Month Day, Year.}
-
-% The paper headers
-\markboth{Journal of \"{U}ber C\~{o}\~{o}l Engineering,~Vol.~1, No.~1, Christmas~2009}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-
+%Uncomment for PACS numbers title message
+%\pacs{00.00, 20.00, 42.10}
+% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
+%\vspace{2pc}
+%\noindent{\it Keywords}: Article preparation, IOP journals
+% Uncomment for Submitted to journal title message
+%\submitto{\JPA}
+% Comment out if separate title page not required
 \maketitle
 
-\begin{abstract}
-Will save this for last.
-\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Integro-Difference Equation (IDE), Neural Field Model, Cortical Connectivity.
-\end{IEEEkeywords}
-
-\IEEEpeerreviewmaketitle
-
 \section{Introduction}
-\IEEEPARstart{T}{he} human brain is arguably the world's most complex system.
+The human brain is arguably the world's most complex system.
 Approximately 100 billion neurons and 60 trillion synapses operate in concert to process information, resulting in the cognition that determines our behavior.
@@
 Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
-An estimation frame work for neural field models known as dynamical causal modeling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
+An estimation frame work for neural field models known as dynamical causal modelling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
-The interconnected brain regions are modeled by the Jansen and Ritt equations.
+The interconnected brain regions are modelled by the Jansen and Ritt equations.
 The approach has proven very useful in understanding specific hierarchical networks of neural information processing.
@@
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions (three in the paper) is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria (AIC or BIC).
+Modelling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions (three in the paper) is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria (AIC or BIC).
 In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
-This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.
+This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
 %Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-% \begin{eqnarray}\label{Connectivity Kernel}
-% 	w\left(r,r'\right) =&& \\
-% &&\boldsymbol{\theta}_1\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_1^2}\right)}+\boldsymbol{\theta}_2\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_2^2}\right)}+\boldsymbol{\theta}_3\exp{\left(-\frac{(r-r')^\top(r-r')}{\sigma_3^2}\right)}\nonumber
-% \end{eqnarray}
-% where $\sigma_i$ is the scale parameter.
-% % where
-% % \begin{equation}
-% % 	\boldsymbol{\theta}=\begin{bmatrix} \boldsymbol{\theta}_{1}\\\boldsymbol{\theta}_{2}\\\boldsymbol{\theta}_{3}\end{bmatrix},\quad 		\Sigma_w=\begin{bmatrix}\Sigma_{w1}\\\Sigma_{w2}\\ \Sigma_{w3}\end{bmatrix}.
-% % \end{equation}
-% \begin{todo}
-% 	{Parham ... how are you writing this? DF: I have tried to make it better, but Parham can you check.Parham: I have changed it but I think it's better to include it in the simulation section}
-% \end{todo}
+
 The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function
@@
 \end{equation}
-% The rearrange the model into an integro-differential we take the Laplace transform of~\ref{FullDoubleIntModel} giving
-% \begin{equation}
-% 	V(s) = H(s)G(s).
-% \end{equation}
-% Since $H(s) = (s+\alpha)^{-1}$ we can write
-% \begin{equation}
-% 	(s+\alpha)V(s) = G(s).
-% \end{equation}
 To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
@@
 where $T$ is the time step, $\lambda = 1-\alpha T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
-\begin{equation}\label{eq:FieldCovariance}
- cov(\mathbf{e}_t,\mathbf{e}_{t+\tau})=
-\begin{cases}
+\begin{equation}
+    cov(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ \begin{array}{*{20}{c}}
     \gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
-0 & \mathrm{otherwise}.
-\end{cases}
+    0 & \mathrm{otherwise}. \\
+    \end{array} \right.
 \end{equation}
@@
 \end{equation}
-
-% \section{Generating Data}
-% To generate iEEG/LFP data we proceeded with the assumption of spatial homogeneity for the connectivity and activation function parameters, implying $w(\mathbf{r},\mathbf{r}') = w\left(\mathbf{r}-\mathbf{r}'\right)$, $\nu_0(\mathbf{r}) = \nu_0$ and $v_0(\mathbf{r}) = v_0$.
-In addition we assume the synaptic transmission delay is negligible.
-The model was discretized in time   and a stochastic
-% 
-% The IDE formulation in Eq.~\ref{DiscreteTimeModel} was solved using a numerical method described in Appendix~\ref{Space Discretization}. 
-% All the model parameters are described in Table 1.
-% 
-% \begin{tabular}{|c|c|c|}
-% \hline
-% Parameter & Value & Reference\\
-% \hline
-% $\alpha$ & $100$ s$^{-1}$ &\\
-% \hline
-% $\nu_0$ & $1$ s$^{-1}$ &\\
-% \hline
-% $v_0$ & $6$ mV &\\
-% \hline
-% $\beta$ & $0.56$ spikes/mV$^{-1}$ & \\
-% \hline
-% $T$ & $1\times10^{-4}$ s &\\
-% \hline
-% $\Delta$ & $1$ &\\
-% \hline
-% $\mathbf{\theta}_1$ &  &\\
-% \hline
-% $\mathbf{\theta}_2$ &  &\\
-% \hline
-% $\mathbf{\theta}_3$ &  &\\
-% \hline
-% $\sigma_{w1}$ &  &\\
-% \hline
-% $\sigma_{w2}$ &  &\\
-% \hline
-% $\sigma_{w3}$ &  &\\
-% \hline
-% $\sigma_m$ &  &\\
-% \hline
-% \end{tabular}
 
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 \begin{equation}
-\mathbf C=\begin{bmatrix}\int_{\Omega}m(\mathbf r_1 - \mathbf
-r')\boldsymbol \phi_1(\mathbf r')d\mathbf r'&\int_{\Omega}m(\mathbf r_1
-- \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r'& \hdots
+\mathbf{C} = \left[\begin{array}{{cccc}}
+\int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
 &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
@@
 r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
-\phi_2(\mathbf r')d\mathbf r'& \hdots &\int_{\Omega}m(\mathbf r_2 -
+\phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
 \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
@@
 r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
-\phi_2(\mathbf r')d\mathbf r'& \hdots &\int_{\Omega}m(\mathbf r_{n_y} -
+\phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
 \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
-\end{bmatrix},
+\end{array}\right],
 \end{equation}
 and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-
 \section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
-
 Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
@@
 Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-
 \section{State and Parameter Estimation}
@@
 \section{Conclusion}
-
-\appendices
-
-% \section{Discrete Time Model}\label{Time Discretization}
+\appendix
 \section{Discrete Time Model}\label{Time Discretization}
@@
 where $\lambda = 1 - T \alpha$.
-
  \section{Numerical Simulation of IDE Model}\label{Space Discretization}
@@
 where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$.
-%  and $\tilde{w}(r_{ij}-r_{ij}'|)$ discretized connectivity kernel described by
-% \begin{equation}\label{Discrete Connectivity Kernel}
-% 	\tilde{w}(r_{ij},r_{ij}') = \boldsymbol{\theta}^{\top} e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
-% \end{equation}
-% The observation equation and kernel were discretized in the same way by
-% \begin{equation}\label{Discrete Observation Equation}
-%     y_k\left(r_{i_n j_n}\right) = \Delta^2\sum_{i=1}^{i=I}\sum_{j=1}^{j=J} \tilde{m}( |r_{i_n j_n}-r_{ij}'| ) v_k\left(r_{ij}'\right)  + \varepsilon_k( r_{i_n j_n})
-% \end{equation}
-% where
-% \begin{equation}\label{Discrete Observation Kernel}
-% 	\tilde{m}(|r_{ij}-r_{ij}'|) = e^{\frac{\left(\left(r_i'-r_i\right)\Delta\right)^2}{(2\sigma)^2} + \frac{\left(\left(r_j'-r_j\right)\Delta\right)^2}{(2\sigma)^2}}.
-% \end{equation}
-We have used periodic boundary conditions to alleviate problems associated with edge effects.
-
+We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects.
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
+Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
+\begin{eqnarray}\label{Poo}
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+\end{eqnarray}
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+\begin{eqnarray}\label{Homogeneous SS Model}
+	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+\end{eqnarray}
 \section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
@@
 \begin{equation}
-\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{equation}
@@
 \end{lemma}
-\begin{IEEEproof}
+\begin{proof}
  Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
@@
 \end{eqnarray}
-\end{IEEEproof}
-\section{Parameter estimation using LS}
-\begin{equation}
- \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
-\label{eq:statespacemodel}
-\end{equation}
-where the matrix $\mathbf Q_{n_x \times n_{\boldsymbol{\theta}}}(\mathbf x_t)$ is defined as
-\begin{equation}
- Q_{n_x \times n_{\boldsymbol{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
-\end{equation}
-and $T_s$ is the sampling period. Least Square method can be used as (\ref{eq:statespacemodel}) is linear in parameters. At each time instant we have
+\end{proof}
+\section*{References}
+\begin{thebibliography}{10}
+\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
+(Reading, MA: Addison-Wesley)
+\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
+\end{thebibliography}
 
-\begin{eqnarray}
- \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
- \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
-&\vdots& \nonumber\\
- \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
-\end{eqnarray}
-in matrix form
-\begin{equation}
- \begin{bmatrix} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{bmatrix}-\begin{bmatrix} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{bmatrix}=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix}\begin{bmatrix} \boldsymbol{\theta} \\ \alpha\end{bmatrix}+T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
-\end{equation}
-or in compact form we have
-\begin{equation}
- \mathbf Z=\mathbf X \mathbf W+\boldsymbol \xi
-\end{equation}
-where
-\begin{equation}
- \mathbf Z=\begin{bmatrix} \mathbf x_{1}-\mathbf x_{0}\\\mathbf x_{2}-\mathbf x_{1}\\\vdots\\\mathbf x_{n}-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf X=T_s\begin{bmatrix}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{bmatrix},\quad \mathbf W=\begin{bmatrix} \boldsymbol{\theta} \\ \alpha\end{bmatrix} \text{and}\quad \boldsymbol \xi=T_s\begin{bmatrix}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{bmatrix}
-\end{equation}
-using the method of Least Square $ \mathbf W$ can be estimated
-\begin{equation}
- \mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z
-\end{equation}
-% use section* for acknowledgement
-
-\section{clarification for the derivation} 
-I ignore noise here. From equation (\ref{SpikesToPotential}) we can say $h$ is the foundamental solution to the equation
-\begin{equation}
- Lv(r,t)=g(r,t)
-\label{eq:LV}
-\end{equation}
-where $L$ is a temporal differential operator, since $h(t)$ is the foundamental solution to (\ref{eq:LV}) it can be written as a Green's function
-\begin{equation}
- Lh(t)=\delta(t)
-\end{equation}
-where $L=1+\tau\frac{d}{dt}$ therefore equation (\ref{eq:LV}) becomes:
-\begin{equation}
-\tau\frac{dv(r,t)}{dt}+ v(r,t)=g(r,t)
-\end{equation}
-substituting (\ref{RateBasedInteractions}) for $g(r,t)$ gives
-\begin{equation}
-\frac{dv\left( {r,t} \right)}{dt} + \frac{1}{\tau} v\left( r,t \right) = \frac{1}{\tau}\int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',\bar t \right)} \right)dr'} 
-\end{equation}
-
-% \section{Ken's Discretization}
-% Spatio-temporal interactions can be described by the continuous space continuous time stochastic differential equation
-% \begin{equation}\label{differential eq}	
-% \tau dv\left( r,t \right) = \left( -v\left( r,t \right) + \int_\Omega  {w\left( r,r' \right)f\left( {v\left( r',t \right)} \right)dr'} \right) dt  + d e\left( r,t \right).
-% \end{equation}
-% where $e\left( r,t \right)$ is a zero mean temporal Wiener process with incremental covariance $\Sigma_e(r)dt$.
-(not too sure about this noise since it needs to be white temporally but coloured spatially - which in continuous space-time I have never seen written ...
-has anyone?)
-% To simplify the notation, but without loss of generality, \ref{differential eq} can be rewritten as
-% \begin{equation}\label{differential simplified}
-% 	dv\left( r,t \right) = q\left(v(r,t) \right) dt  + d e\left( r,t \right)
-% \end{equation}
-% Had $q\left(v(r,t) \right)$ been a linear function in $v$, then \ref{differential simplified} could be rewritten as
-% \begin{equation}\label{differential linear}
-% 	dv\left( r,t \right) = Av(r,t)dt  + d e\left( r,t \right)
-% \end{equation}
-% Considering temporal sampling instances $\delta$ apart given by $\{t_k = 0,~1,~2, \ldots$ \}, then a solution to \ref{differential linear} at each sampling time is given by
-% \begin{equation}\label{linear solution}
-% 	v(r,t_k+\delta) = \exp\{A(\delta)\}x(t) + \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
-% \end{equation}
-% Let the discrete time random variable $e'(r,t_k)$ be
-% \begin{equation}\label{discrete noise}
-% 	e'(r,t_k) = \int_{t_k}^{t_k+\delta}\exp\{A(t_k+\delta-\tau)\}de(r,\tau)
-% \end{equation}
-% then, $e'(r,t_k)$ is a zero mean, temporally white noise term with covariance
-% \begin{equation}\label{covariance of noise}
-% 	E\left[e'(r,t_k),e'^\top(r,t_k) \right] = \int_t^{t+\delta}\exp\{A(t_k+\delta-\tau)\} \Sigma_e(r) \exp\{A(t+\delta-\tau)\} d\tau
-% \end{equation}
-% 
-% But we are not so luck as to be able to go from \ref{differential simplified} to \ref{differential linear} and thus I doubt if we can obtain an exact solution to \ref{differential simplified} without an approximation.
-Agreed?
-% 
-% A possible approximate solution is the one you have already used. Thus, interpreting the difference equation \ref{differential simplified} as an integral equation gives
-% \begin{equation}\label{euler}
-% 	v\left(r,t\right) =  v(r,t_0) + \int_{t_0}^{t} q\left(v(r,\tau) \right) d\tau  + \int_{t_0}^{t} d e\left(r,\tau\right)
-% \end{equation}
-% Using an Euler approximation, \ref{euler} can be approximated at each sampling time by
-% \begin{equation}\label{euler approx 1}
-% 	v\left(r,t_{k+1} \right) =  v(r,t_k) + q\left(v(r,t_k)\right) (t_{k+1} - t_k) + (e(r,t_{k+1}) - e(r,t_k))
-% \end{equation}
-% which can be rewritten as
-% \begin{equation}\label{euler approx 2}
-% 	v\left(r,t_k + \delta \right) =  v(r,t_k) + \delta q\left(v(r,t_k)\right) + e'(r,t_k)
-% \end{equation}
-% where $e'(r,t_k)$ is a zero mean Gaussian random variable with covariance $\delta\Sigma_e$.
-(Note that, because of the way the noise is defined in \ref{differential eq} it is not $\delta^2$ but $\delta$)
-
-\section*{Acknowledgment}
-The authors would like to thank...
-
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% references section
-
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,BrainIDE}
-
-% biography section
-%
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}{Dean R. Freestone}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiography}{Parham Aram}
-Biography text here.
-\end{IEEEbiography}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiography}{Michael Dewar}
-Biography text here.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}{Kenneth Scerri}
-Biography text here.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}{Visakan Kadirkamanathani}
-Biography text here.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}{Other Bosses}
-Biography text here.
-\end{IEEEbiography}
-
-% that's all folks
 \end{document}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to artical

@@
 \begin{equation}
-\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{equation}
@@
 \end{lemma}
-\begin{proof}
+\subsection{proof}
  Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
@@
 \mathbf{\Sigma}_e&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top} e_t\left(\mathbf{r}'\right)d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+&=&\mathbf{\Gamma}^{-1}\int\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{eqnarray}
-\end{proof}
+% \end{proof}
+\section{Parameter estimation using LS}
+\begin{equation}
+ \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+\label{eq:statespacemodel}
+\end{equation}
+where the matrix $\mathbf Q_{n_x \times n_{\boldsymbol{\theta}}}(\mathbf x_t)$ is defined as
+\begin{equation}
+ Q_{n_x \times n_{\boldsymbol{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
+\end{equation}
+and $T_s$ is the sampling period. Least Square method can be used as (\ref{eq:statespacemodel}) is linear in parameters. At each time instant we have
+\begin{eqnarray}
+ \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+ \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+&\vdots& \nonumber\\
+ \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
+\end{eqnarray}
+in matrix form
+\begin{equation}
+ \left[\begin{array}{{cccc}} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{array}\right]
+	-\left[\begin{array}{cccc} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{array}\right]
+	=T_s\left[\begin{array}{cc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
+	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right]+T_s
+		\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
+\end{equation}
+or in compact form we have
+\begin{equation}
+ \mathbf Z=\mathbf X \mathbf W+\boldsymbol \xi
+\end{equation}
+where
+\begin{equation}
+ \mathbf Z=\left[\begin{array}{cccc} \mathbf x_{1}-\mathbf x_{0}\\
+\mathbf x_{2}-\mathbf x_{1}\\\vdots\\
+\mathbf x_{n}-\mathbf x_{n-1}\end{array}\right],\quad \mathbf X=T_s\left[\begin{array}{cccc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\
+\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
+,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
+\end{equation}
+using the method of Least Square $ \mathbf W$ can be estimated
+\begin{equation}
+ \mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z
+\end{equation}
 \section*{References}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to artical, added bib to JoNE folder
update to JoNE template, so we can check the two column format

@@
 %
-\documentclass[12pt]{iopart}
+% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+\documentclass[12pt]{iopart}		%<-comment out this for checking equations
 \usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
 \usepackage{color}  
-\usepackage{iopams,setstack}                  % For creating coloured text and background
-% \usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
+\usepackage{iopams,setstack}                  %<-comment out this for checking equations
+% \usepackage{anysize}							%<-use this for checking equation length
+% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+% \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
 % \newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
-%Uncomment next line if AMS fonts required
 
@@
 
-\title[State and Parameter Estimation for a Spatio-temporal Neural Fields]{State and Parameter Estimation for a Spatio-temporal Neural Fields}
-
-\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
-
-\address{$^1$ Department
-of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
-Vic, 3010 Australia}
-\address{$^2$ Department
-of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
-S1 3JD, UK}
-\address{$^3$ Mike's}
-\address{$^4$ Ken's}
-\ead{dfreestone@bionicear.org}
+\title[State and Parameter Estimation for a Spatio-Temporal Neural Fields]{State and Parameter Estimation for a Spatio-Temporal Neural Fields}
+% 
+% \author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
+% 
+% \address{$^1$ Department
+% of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
+% Vic, 3010 Australia}
+% \address{$^2$ Department
+% of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
+% S1 3JD, UK}
+% \address{$^3$ Mike's}
+% \address{$^4$ Ken's}
+% \ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 \section*{References}
-\begin{thebibliography}{10}
-\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
-(Reading, MA: Addison-Wesley)
-\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
-\end{thebibliography}
+\bibliographystyle{unsrt}
+\bibliography{BrainIDE}
+
+% \begin{thebibliography}{10}
+% \bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
+% (Reading, MA: Addison-Wesley)
+% \bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
+% \end{thebibliography}
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
state parameter estimation

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \section{State and Parameter Estimation}
-The Unscented Rauch Tung Striebel Smoother (URTSS) was used for the state estimation \cite{Sarkka2010}, where the Unscented Kalman filter is used for the forward iteration \cite{Julier1997}.
-This method is appropriate for state estimation of stochastic nonlinear dynamical systems.
-Alternatives to this approach are the Extended Kalman Filter (EKF) \cite{Haykin2001}  and sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
+The estimation process is a two part iterative algorithm that yields the estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
+In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
+In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\lambda$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence.
+The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} along with a separate backward smoothing path to compute the smooth estimations.
+The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
+Alternatives to the UKF are the Extended Kalman Filter (EKF) \cite{Haykin2001}  and Sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
 The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time step.
@@
 The sigma points describe the mean and covariance of the state estimate.
+The number of sigma points needed is $2n_x+1$ where $n_x$ is the dimension of the stae space.
+The set of sigma points and their corresponding weights used in the UKF can be calculated as
+
  The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution.

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added parameter list

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}		%<-comment out this for checking equations
+\documentclass[12pt]{iopart}		%<-comment out this for checking equations (author list too)
 \usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
@@
 \title[State and Parameter Estimation for a Spatio-Temporal Neural Fields]{State and Parameter Estimation for a Spatio-Temporal Neural Fields}
-% 
-% \author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
-% 
-% \address{$^1$ Department
-% of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
-% Vic, 3010 Australia}
-% \address{$^2$ Department
-% of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
-% S1 3JD, UK}
-% \address{$^3$ Mike's}
-% \address{$^4$ Ken's}
-% \ead{dfreestone@bionicear.org}
+
+\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
+
+\address{$^1$ Department
+of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
+Vic, 3010 Australia}
+\address{$^2$ Department
+of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
+S1 3JD, UK}
+\address{$^3$ Mike's}
+\address{$^4$ Ken's}
+\ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 \begin{equation}\label{ActivationFunction}
-	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{\nu _0\left(\mathbf{r}\right)}{1 + \exp \left( \beta \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
+	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \beta \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 \end{algorithm}
-\section{Comparison of Estimated Parameters and True Parameters}
+\section{Results}
+
+\subsection{Frequency Analysis}
+
+\subsection{State and Parameter Estimates}
 
 \section{Discussion}
+
 \begin{itemize}
@@
 \end{equation}
+\section{Parameters}
+
+\begin{tabular} {c|c} 
+	\hline\hline
+	Symbol & Description \\ \hline
+	$v(\mathbf{r},t)$ & mean membrane potential \\
+	$g(\mathbf{r},t)$ & average action potential rate \\
+	$\mathbf{r}$ & spatial location \\
+	$t$ & time (s) \\
+	$h(t)$ & post-synaptic response kernel \\
+	$\eta(t)$ & Heaviside function \\
+	$\alpha$ & inverse synaptic time constant \\
+	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
+	$f(\mathbf{r},t)$ & firing function rate \\
+	$u(\mathbf{r},t)$ & external input \\
+	$\Omega$ & spatial domain \\
+	$f_{max}$ & maximal firing rate \\
+	$\beta$ & slope of sigmoidal activation function \\
+	$v_0$ & firing threshold \\
+	$\delta(t)$ & Dirac-delta function \\
+	$L$ & temporal differential operator \\
+	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
+	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
+	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
+	$y(\mathbf{r}_n,t)$ & obseration \\
+	$n$ & sensor index $n=1,..,N$ \\
+	$T$ & time step \\
+	$\lambda$ & time constant parameter \\
+	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
+	$\mathbf{x}_t$ & state vector at time $t$ \\
+	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
+	$\theta$ & vector of connectivity kernel parameters \\
+	$\Gamma$ & inner product of field basis functions \\
+	$q()$ & state function \\
+	$k()$ & maps into to discrete state of input function \\
+	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\
+	$\mathbf{C}$ & observation matrix \\
+	$V(\nu)$ & Spectrum of the dynamic field \\ 
+	$\nu$ & Spatial frequency \\
+	$\nu_c$ & Spatial cut-off frequency \\
+\end{tabular}
+
+\begin{tabular}{c|c}
+	\hline\hline
+	Symbol & Description \\ \hline
+	$\Delta_s$ & Distance between adjacent sensors \\
+	$\rho$ & Over-sampling parameter \\	
+	$\Delta_b$ & Distance between field basis functions \\	
+	$\sigma_{nu}^2$ & Variance of FT of Gaussian basis function \\
+	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
+	$\hat{\mathbf{x}}$ & State estimate \\
+	$\chi$ & Matrix of sigma vectors \\
+	$\hat{\mathbf{x}}_t^{f-}$ & Forward \emph{a priori} estimate \\
+	$\hat{\mathbf{x}}_t^f$ & Forward \emph{a posteriori} estimate \\
+	$\hat{\mathbf{x}}_t^{b-}$ & Backward \emph{a priori} estimate \\
+	$\hat{\mathbf{x}}_t^{b}$ & Backward \emph{a posteriori} estimate \\
+	$P^f_t$ & Forward \emph{a posteriori} covariance matrix \\
+	$P^{f-}_t$ & Forward \emph{a priori} covariance matrix \\	
+\end{tabular}
 \section*{References}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updated parameter list

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \end{equation}
+\section{Parameters}
+
+\begin{tabular} {c|c} 
+	\hline\hline
+	Symbol & Description \\ \hline
+	$v(\mathbf{r},t)$ & mean membrane potential \\
+	$g(\mathbf{r},t)$ & average action potential rate \\
+	$\mathbf{r}$ & spatial location \\
+	$t$ & time (s) \\
+	$h(t)$ & post-synaptic response kernel \\
+	$\eta(t)$ & Heaviside function \\
+	$\alpha$ & inverse synaptic time constant \\
+	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
+	$f(\mathbf{r},t)$ & firing function rate \\
+	$u(\mathbf{r},t)$ & external input \\
+	$\Omega$ & spatial domain \\
+	$f_{max}$ & maximal firing rate \\
+	$\beta$ & slope of sigmoidal activation function \\
+	$v_0$ & firing threshold \\
+	$\delta(t)$ & Dirac-delta function \\
+	$L$ & temporal differential operator \\
+	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
+	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
+	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
+	$y(\mathbf{r}_n,t)$ & obseration \\
+	$n$ & sensor index $n=1,...,N$ \\
+	$T$ & time step \\
+	$\lambda$ & time constant parameter \\
+	$\boldsymbol{\phi(r)}$ & vector of Gaussian basis functions \\
+	$\mathbf{x}_t$ & state vector at time $t$ \\
+	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions \\
+	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters \\
+	$\boldsymbol{\Gamma}$ & inner product of field basis functions \\
+	$q(.)$ & state transition function \\
+	$k(.)$ & maps into to discrete state of input function $u(\mathbf{r},t)$ \\
+	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\
+	$\mathbf{C}$ & observation matrix \\
+	$V(\nu)$ & Spectrum of the dynamic field \\ 
+	$\nu$ & Spatial frequency \\
+	$\nu_c$ & Spatial cut-off frequency \\
+\end{tabular}
+
+\begin{tabular}{c|c}
+	\hline\hline
+	Symbol & Description \\ \hline
+	$\Delta_s$ & Distance between adjacent sensors \\
+	$\rho$ & Over-sampling parameter \\	
+	$\Delta_b$ & Distance between field basis functions \\	
+	$\sigma_{nu}^2$ & Variance of FT of Gaussian basis function \\
+	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
+	$\hat{\mathbf{x}}$ & State estimate \\
+	$\boldsymbol{\chi}$ & Matrix of sigma vectors \\
+	$\hat{\mathbf{x}}_t^{f-}$ & Forward \emph{a priori} estimate \\
+	$\hat{\mathbf{x}}_t^f$ & Forward \emph{a posteriori} estimate \\
+	$\hat{\mathbf{x}}_t^{b-}$ & Backward \emph{a priori} estimate \\
+	$\hat{\mathbf{x}}_t^{b}$ & Backward \emph{a posteriori} estimate \\
+	$\mathbf{P}^f_t$ & Forward \emph{a posteriori} covariance matrix \\
+	$\mathbf{P}^{f-}_t$ & Forward \emph{a priori} covariance matrix \\	
+\end{tabular}
 \section*{References}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
state parameter estimation update

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 The sigma points describe the mean and covariance of the state estimate.
-The number of sigma points needed is $2n_x+1$ where $n_x$ is the dimension of the stae space.
-The set of sigma points and their corresponding weights used in the UKF can be calculated as
+The number of sigma points needed is $2\mathbf L+1$ where $\mathbf L$ is the dimension of the stae space.
+The  columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
+\begin{equation}
+ \mathcal X_{0}=\bar x
+\end{equation}
+\begin{equation}
+ \mathcal X_{i}=\bar x+(\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i \quad i=1, \dots, \mathbf L
+\end{equation}
+\begin{equation}
+ \mathcal X_{i}=\bar x-(\sqrt{(\mathbf L + \lambda)\mathbf P_x})_{i-\mathbf L} \quad i=\mathbf L+1, \dots, 2\mathbf L
+\end{equation}
+\begin{equation}
+ \mathbf W_0^{(m)}=\frac{\lambda}{\mathbf L+\lambda}
+\end{equation}
+\begin{equation}
+ \mathbf W_0^{(c)}=\frac{\lambda}{\mathbf L+\lambda}+(1-\alpha^2+\beta)
+\end{equation}
+\begin{equation}
+ \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2(\mathbf L+\lambda)} \quad i=1, \dots, \mathbf 2L
+\end{equation}
+where the sacling parameter $\lambda$ is defined as
+\begin{equation}
+\lambda=\alpha^2(\mathbf L+\kappa)-\mathbf L 
+\end{equation}
+parameters $\alpha$, $\beta$ and $\kappa$ can be used to tune the filtering process \cite{Haykin2001}
+
+% For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}.
+$ (\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i$ is the ith column of the matrix square root (e.g., lower-triangular Cholesky factorization).
+These sigma points propogated through the nonlinear function
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changing some parameter names so we can use UKF literature if we need to cut it back

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \begin{equation}\label{SynapticRespKernel}
-	h(t) = \eta(t)\exp{\left(-\alpha t\right)}.
+	h(t) = \eta(t)\exp{\left(-\zeta t\right)}.
 \end{equation}
-where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
+where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
 \begin{equation}\label{RateBasedInteractions}
@@
 \begin{equation}\label{ActivationFunction}
-	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \beta \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
+	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 \end{equation}
-\todo{Is the above right? I can't think of any way to make $\frac{d}{dt} h(t) + \alpha h(t)$ equal to $\delta(t)$}
-where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $L=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}\label{FinalFormContinuous}
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \alpha v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
 \end{equation} 
-where $T$ is the time step, $\lambda = 1-\alpha T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
+where $T$ is the time step, $\xi = 1-\zeta T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
 \begin{equation}
@@
 \begin{equation}\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
-In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\lambda$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence.
+In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence.
 The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} along with a separate backward smoothing path to compute the smooth estimations.
@@
 \begin{eqnarray}
-	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{eqnarray}
-where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
+where $\boldsymbol{\theta}$ and $\xi$ are the systems parameters.
 In forwards iteration since the observation equation is linear in parameters we only need to use Unsented transformation in prediction step.
@@
 \begin{equation}\label{Euler Approximation}	
-\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T} =   -\alpha v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
+\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T} =   -\zeta v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \alpha v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
+v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \zeta v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right),
 \end{equation}
-where $\lambda = 1 - T \alpha$.
+where $\xi = 1 - T \zeta$.
  \section{Numerical Simulation of IDE Model}\label{Space Discretization}
@@
 \begin{equation}\label{discrete space}
-	v_{t+1}\left(\mathbf{r}_{ij}\right) = \lambda v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
+	v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
 \end{equation}
@@
 \begin{eqnarray}\label{Poo}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
+	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{equation}
-\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{equation}
@@
 \end{lemma}
-\subsection{proof}
+\subsection*{Proof}
  Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
@@
 \begin{equation}
- \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+ \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\zeta T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
 \label{eq:statespacemodel}
@@
 \begin{eqnarray}
- \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
- \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+ \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+ \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
 &\vdots& \nonumber\\
- \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
+ \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
 \end{eqnarray}
@@
 	=T_s\left[\begin{array}{cc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
-	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right]+T_s
+	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \zeta\end{array}\right]+T_s
 		\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
@@
 \mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
-,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
+,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \zeta\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
 \end{equation}
@@
 	$\eta(t)$ & Heaviside function \\
-	$\alpha$ & inverse synaptic time constant \\
+	$\zeta$ & inverse synaptic time constant \\
 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
@@
 	$f_{max}$ & maximal firing rate \\
-	$\beta$ & slope of sigmoidal activation function \\
+	$\varsigma$ & slope of sigmoidal activation function \\
 	$v_0$ & firing threshold \\
@@
 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
-	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
+	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
 	$y(\mathbf{r}_n,t)$ & obseration \\
@@
 	$T$ & time step \\
-	$\lambda$ & time constant parameter \\
+	$\xi$ & time constant parameter \\
 	$\boldsymbol{\phi(r)}$ & vector of Gaussian basis functions \\

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates and edits to paper

@@
 
-\title[State and Parameter Estimation for a Spatio-Temporal Neural Fields]{State and Parameter Estimation for a Spatio-Temporal Neural Fields}
+\title[State and Parameter Estimation for Spatio-Temporal Neural Fields]{State and Parameter Estimation for Spatio-Temporal Neural Fields}
 
@@
 \begin{equation}\label{GreensFuncDef}
-	Lh\left( t \right) = \delta \left( t \right),
+	Dh\left( t \right) = \delta \left( t \right),
 \end{equation}
-where $L=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}\label{FinalFormContinuous}
@@
 \end{equation} 
-where $T$ is the time step, $\xi = 1-\zeta T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
+where $T$ is the time step, $\xi = 1-\zeta T$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma{\varepsilon}\right)$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma{\varepsilon}\right)$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 \begin{equation}\label{ObservationEquation}
-    \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t \\
+    \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
 \end{equation}
@@
 \begin{equation}
-\mathbf{C} = \left[\begin{array}{{cccc}}
-\int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
-&\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
-r')d\mathbf r' \\
-\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
-r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
-\phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
-\mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
-\vdots&\vdots&\ddots&\vdots\\
-\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
-r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
-\phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
-\mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
-\end{array}\right],
+	\mathbf{C} = \left[\begin{array}{{ccc}}
+	c_{1,1} & \dots & c_{1,L} \\
+	\vdots & \ddots & \vdots \\
+	c_{n_y,L} & \dots & c_{n_y,L} \end{array}\right]
 \end{equation}
-and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
+where $L$ is the number of basis functions and
+\begin{equation}
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')d\mathbf{r}'.
+\end{equation}
+% \begin{equation}
+% \mathbf{C} = \left[\begin{array}{{cccc}}
+% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
+% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
+% r')d\mathbf r' \\
+% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
+% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
+% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
+% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
+% \vdots&\vdots&\ddots&\vdots\\
+% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
+% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
+% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
+% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
+% \end{array}\right],
+% \end{equation}
+% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
 \section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ (\todo{can this be $V_t(\boldsymbol{\nu})$}), multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
 In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
-Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
+Thus the spectral response $V_t(\boldsymbol{\nu})$ is usually band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
@@
 where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
-Satisfying this condition is required for the hidden dynamic field $w_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
+Satisfying this condition is required for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
 If the condition is not satisfied, spatial aliasing will occur.
@@
 This is further illustrated our results.
-$\mathcal{W}$
+
 Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
@@
 The dynamic field must be spatially oversampled by using a larger number of sensor then imposed by frequency considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
-Following this, the distance between basis functions is usually larger then the distance between sensors.
-\todo{However this is not the case with this work.} For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
+Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
+For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates and edits to paper
I am getting mad(state parameter estimation algorithm

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \begin{equation}\label{SynapticRespKernel}
-	h(t) = \eta(t)\exp{\left(-\zeta t\right)}.
+	h(t) = \eta(t)\exp{\left(-\alpha t\right)}.
 \end{equation}
-where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
+where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
 \begin{equation}\label{RateBasedInteractions}
@@
 \begin{equation}\label{ActivationFunction}
-	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
+	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \beta \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 \end{equation}
-where $L=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+\todo{Is the above right? I can't think of any way to make $\frac{d}{dt} h(t) + \alpha h(t)$ equal to $\delta(t)$}
+where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}\label{FinalFormContinuous}
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \alpha v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
 \end{equation} 
-where $T$ is the time step, $\xi = 1-\zeta T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
+where $T$ is the time step, $\lambda = 1-\alpha T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
 \begin{equation}
@@
 \begin{equation}\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \lambda\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
-In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence.
-The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} along with a separate backward smoothing path to compute the smooth estimations.
+In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\lambda$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence .
+The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} to calculate a forward posterior estimate $\hat{\mathbf x}_t^{f} $ along with a separate backward smoothing path to compute the smooth estimations $\hat{\mathbf x}_t^{b} $.
 The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
@@
 The sigma points describe the mean and covariance of the state estimate.
-The number of sigma points needed is $2n_x+1$ where $n_x$ is the dimension of the stae space.
-The set of sigma points and their corresponding weights used in the UKF can be calculated as
+The number of sigma points needed is $2L+1$ where $ L$ is the dimension of the stae space.
+The  columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
+\begin{equation}
+ \mathcal X_{0}=\bar x
+\end{equation}
+\begin{equation}
+ \mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots,  L
+\end{equation}
+\begin{equation}
+ \mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L
+\end{equation}
+\begin{equation}
+ \mathbf W_0^{(m)}=\frac{\lambda}{ L+\lambda}
+\end{equation}
+\begin{equation}
+ \mathbf W_0^{(c)}=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta)
+\end{equation}
+\begin{equation}
+ \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L
+\end{equation}
+where the sacling parameter $\lambda$ is defined as
+\begin{equation}
+\lambda=\alpha^2( L+\kappa)- L 
+\end{equation}
+and parameters $\alpha$, $\beta$ and $\kappa$ are used to tune the filtering process \cite{Haykin2001}.
+It should be noted that $\bar x$ is $ \hat{\mathbf x}_t^{f} $ and $ \hat{\mathbf x}_t^{b} $ with their corresponding covariance matrices in filtering and smoothing iterations respectively.
+
+% For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}.
+$ (\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i$ is the ith column of the matrix square root (e.g., lower-triangular Cholesky factorization).
+These sigma points propogated through the nonlinear function
 
@@
 \begin{eqnarray}
-	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{eqnarray}
-where $\boldsymbol{\theta}$ and $\xi$ are the systems parameters.
+where $\boldsymbol{\theta}$ and $\lambda$ are the systems parameters.
 In forwards iteration since the observation equation is linear in parameters we only need to use Unsented transformation in prediction step.
@@
 \end{equation*}
-Propogate the sigma points through the dynamic model
+Propogate the sigma points through the state equation
 \begin{equation}
@@
 \end{equation}
-For $t \in \left\lbrace N-1, \cdots, 0 \right\rbrace $
+For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $
 \begin{equation*}
@@
 \end{equation*}
+\State Propogate the sigma points through the state equation similar to the forward step and compute
+
 \end{algorithmic}
@@
 \begin{equation}\label{Euler Approximation}	
-\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T} =   -\zeta v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
+\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T} =   -\alpha v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \zeta v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
+v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \alpha v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right),
 \end{equation}
-where $\xi = 1 - T \zeta$.
+where $\lambda = 1 - T \alpha$.
  \section{Numerical Simulation of IDE Model}\label{Space Discretization}
@@
 \begin{equation}\label{discrete space}
-	v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
+	v_{t+1}\left(\mathbf{r}_{ij}\right) = \lambda v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
 \end{equation}
@@
 \begin{eqnarray}\label{Poo}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{equation}
-\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{equation}
@@
 \end{lemma}
-\subsection*{Proof}
+\subsection{proof}
  Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
@@
 \begin{equation}
- \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\zeta T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
+ \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
 \label{eq:statespacemodel}
@@
 \begin{eqnarray}
- \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
- \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+ \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+ \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
 &\vdots& \nonumber\\
- \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
+ \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
 \end{eqnarray}
@@
 	=T_s\left[\begin{array}{cc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
-	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \zeta\end{array}\right]+T_s
+	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right]+T_s
 		\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
@@
 \mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
-,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \zeta\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
+,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
 \end{equation}
@@
 	$\eta(t)$ & Heaviside function \\
-	$\zeta$ & inverse synaptic time constant \\
+	$\alpha$ & inverse synaptic time constant \\
 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
@@
 	$f_{max}$ & maximal firing rate \\
-	$\varsigma$ & slope of sigmoidal activation function \\
+	$\beta$ & slope of sigmoidal activation function \\
 	$v_0$ & firing threshold \\
@@
 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
+	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
 	$y(\mathbf{r}_n,t)$ & obseration \\
-	$n$ & sensor index $n=1,...,N$ \\
+	$n$ & sensor index $n=1,..,N$ \\
 	$T$ & time step \\
-	$\xi$ & time constant parameter \\
-	$\boldsymbol{\phi(r)}$ & vector of Gaussian basis functions \\
+	$\lambda$ & time constant parameter \\
+	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
 	$\mathbf{x}_t$ & state vector at time $t$ \\
-	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions \\
-	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters \\
-	$\boldsymbol{\Gamma}$ & inner product of field basis functions \\
-	$q(.)$ & state transition function \\
-	$k(.)$ & maps into to discrete state of input function $u(\mathbf{r},t)$ \\
+	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
+	$\theta$ & vector of connectivity kernel parameters \\
+	$\Gamma$ & inner product of field basis functions \\
+	$q()$ & state function \\
+	$k()$ & maps into to discrete state of input function \\
 	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\
@@
 	$\hat{\mathbf{x}}$ & State estimate \\
-	$\boldsymbol{\chi}$ & Matrix of sigma vectors \\
+	$\chi$ & Matrix of sigma vectors \\
 	$\hat{\mathbf{x}}_t^{f-}$ & Forward \emph{a priori} estimate \\
@@
 	$\hat{\mathbf{x}}_t^{b}$ & Backward \emph{a posteriori} estimate \\
-	$\mathbf{P}^f_t$ & Forward \emph{a posteriori} covariance matrix \\
-	$\mathbf{P}^{f-}_t$ & Forward \emph{a priori} covariance matrix \\	
+	$P^f_t$ & Forward \emph{a posteriori} covariance matrix \\
+	$P^{f-}_t$ & Forward \emph{a priori} covariance matrix \\	
 \end{tabular}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 \begin{equation}\label{GreensFuncDef}
-	Lh\left( t \right) = \delta \left( t \right),
+	Dh\left( t \right) = \delta \left( t \right),
 \end{equation}
-\todo{Is the above right? I can't think of any way to make $\frac{d}{dt} h(t) + \alpha h(t)$ equal to $\delta(t)$}
+where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
@@
 \end{equation} 
-where $T$ is the time step, $\lambda = 1-\alpha T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
+where $T$ is the time step, $\xi = 1-\zeta T$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
 \begin{equation}
@@
 	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
 	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper updates

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $L=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}\label{FinalFormContinuous}
@@
 	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
 	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
@@
 
-Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
+Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition.
 The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
@@
 In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
-In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence.
-The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} along with a separate backward smoothing path to compute the smooth estimations.
+In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence .
+The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} to calculate a forward posterior estimate $\hat{\mathbf x}_t^{f} $ along with a separate backward smoothing path to compute the smooth estimations $\hat{\mathbf x}_t^{b} $.
 The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
@@
 The sigma points describe the mean and covariance of the state estimate.
-The number of sigma points needed is $2\mathbf L+1$ where $\mathbf L$ is the dimension of the stae space.
+The number of sigma points needed is $2L+1$ where $ L$ is the dimension of the state space.
 The  columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
@@
 \begin{equation}
- \mathcal X_{i}=\bar x+(\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i \quad i=1, \dots, \mathbf L
+ \mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots,  L
 \end{equation}
 \begin{equation}
- \mathcal X_{i}=\bar x-(\sqrt{(\mathbf L + \lambda)\mathbf P_x})_{i-\mathbf L} \quad i=\mathbf L+1, \dots, 2\mathbf L
+ \mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L
 \end{equation}
 \begin{equation}
- \mathbf W_0^{(m)}=\frac{\lambda}{\mathbf L+\lambda}
+ \mathbf W_0^{(m)}=\frac{\lambda}{ L+\lambda}
 \end{equation}
 \begin{equation}
- \mathbf W_0^{(c)}=\frac{\lambda}{\mathbf L+\lambda}+(1-\alpha^2+\beta)
+ \mathbf W_0^{(c)}=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta)
 \end{equation}
 \begin{equation}
- \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2(\mathbf L+\lambda)} \quad i=1, \dots, \mathbf 2L
+ \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L
 \end{equation}
-where the sacling parameter $\lambda$ is defined as
+where the scaling parameter $\lambda$ is defined as
 \begin{equation}
-\lambda=\alpha^2(\mathbf L+\kappa)-\mathbf L 
+\lambda=\alpha^2( L+\kappa)- L 
 \end{equation}
-parameters $\alpha$, $\beta$ and $\kappa$ can be used to tune the filtering process \cite{Haykin2001}
+and parameters $\alpha$, $\beta$ and $\kappa$ are used to tune the filtering process \cite{Haykin2001}.
+It should be noted that $\bar x$ is $ \hat{\mathbf x}_t^{f} $ and $ \hat{\mathbf x}_t^{b} $ with their corresponding covariance matrices in filtering and smoothing iterations respectively.
 
@@
 Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}\label{Poo}
+\begin{eqnarray}\label{ReducingState}
 	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
@@
 Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}\label{Poo}
+\begin{eqnarray}\label{StartofReduction}
 	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
@@
 \end{eqnarray}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
 \begin{eqnarray}\label{Homogeneous SS Model}
@@
 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
+	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
 	$y(\mathbf{r}_n,t)$ & obseration \\
-	$n$ & sensor index $n=1,...,N$ \\
+	$n$ & sensor index $n=1,..,N$ \\
 	$T$ & time step \\
 	$\xi$ & time constant parameter \\
-	$\boldsymbol{\phi(r)}$ & vector of Gaussian basis functions \\
+	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
 	$\mathbf{x}_t$ & state vector at time $t$ \\
-	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions \\
-	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters \\
-	$\boldsymbol{\Gamma}$ & inner product of field basis functions \\
-	$q(.)$ & state transition function \\
-	$k(.)$ & maps into to discrete state of input function $u(\mathbf{r},t)$ \\
+	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
+	$\theta$ & vector of connectivity kernel parameters \\
+	$\Gamma$ & inner product of field basis functions \\
+	$q()$ & state function \\
+	$k()$ & maps into to discrete state of input function \\
 	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
trying to solve the conflict
working on estimation section
general updates to paper

@@
 \begin{equation*}
- \hat{\mathbf x}_{k +t}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f*}
+ \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f*}
 \end{equation*}
 \begin{equation*}
- \mathbf P_{t +1}^-=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e
+ \mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e
 \end{equation*}
@@
 \end{equation*}
-\State Propogate the sigma points through the state equation similar to the forward step and compute
+\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1|t}^{b*}$ similar to the forward step and compute
 
@@
 \section{Results}
+We simulated a neural field to the generate data used in the state and parameter estimation.
+An example of the simulated field can be seen in Figure~\ref{}.
+The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.
 
@@
 \end{lemma}
-\subsection{proof}
+\section*{Proof}
  Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
@@
 &=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-&=&\mathbf{\Gamma}^{-1}\int\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{eqnarray}
@@
 \section{Parameters}
-
 \begin{tabular} {c|c} 
@@
 	$\delta(t)$ & Dirac-delta function \\
-	$L$ & temporal differential operator \\
+	$D$ & Temporal differential operator \\
+	$L$ & number of basis function and dimension of state vector \\
 	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
working on the state estimation part

@@
 \begin{equation}
-\mathcal X_{i,t+1|t}^{f*}=Q(\mathcal X_t^f,u_t)
+\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_t^f,u_t)
 \end{equation}
 \begin{equation*}
- \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f*}
+ \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-}
 \end{equation*}
@@
 \begin{equation}
- \mathbf P_T^s= \mathbf P_T^f
+ \mathbf P_T^b= \mathbf P_T^f
 \end{equation}
 \begin{equation}
-\hat{\mathbf x}^s_T= \hat{\mathbf x}^f_T
+\hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T
 \end{equation}
@@
 \begin{equation*}
-\mathcal X_t^s=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}]
+\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}]
 \end{equation*}
-\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1|t}^{b*}$ similar to the forward step and compute
+\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1}^{b-}$ similar to the forward step and compute
+\begin{equation*}
+ \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}
+\end{equation*}
+\begin{equation*}
+ \mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{f})^\top+\boldsymbol \Sigma_e
+\end{equation*}
+\begin{equation*}
+ \mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{f})^\top
+\end{equation*}
+\State compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
+\begin{equation*}
+\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1}
+\end{equation*}
+\begin{equation*}
+ \hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
+\end{equation*}
+\begin{equation*}
+ \mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
+\end{equation*}
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updating results section of paper

@@
 \begin{equation*}
- \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-}
+ \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f-}
 \end{equation*}
@@
 \end{equation*}
-\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1}^{b-}$ similar to the forward step and compute
+\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1|t}^{b-}$ similar to the forward step and compute
 \begin{equation*}
- \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}
+ \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{b-}
 \end{equation*}
@@
 \end{equation*}
-\State compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
-\begin{equation*}
-\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1}
-\end{equation*}
-\begin{equation*}
- \hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
-\end{equation*}
-\begin{equation*}
- \mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
-\end{equation*}
-
 \end{algorithmic}
@@
 We simulated a neural field to the generate data used in the state and parameter estimation.
-An example of the simulated field can be seen in Figure~\ref{}.
+All parameters for the model are given in Table~\ref{}.
+An example of the simulated field can be seen in Figure~\ref{} A.
 The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.
+This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
+Figure~\ref{} B.
+shows example data from the sensors of the model, and Figure~\ref{} C.
+shows the power spectral density of on of the simulated time-series.
+The PSD shows the typical $1/f$ characteristics of intracranial EEG.
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
update result section of paper
resolve the conflict

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \documentclass[12pt]{iopart}		%<-comment out this for checking equations (author list too)
-\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
+\usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig}
 \usepackage{color}  
@@
 \section{Results}
-We simulated a neural field to the generate data used in the state and parameter estimation.
+The neural field model was used to the generate data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{}.
-An example of the simulated field can be seen in Figure~\ref{} A.
+An example of the simulated field can be seen in Figure~\ref{}~A.
 The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.
 This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
-Figure~\ref{} B.
-shows example data from the sensors of the model, and Figure~\ref{} C.
+Figure~\ref{}~B.
+shows example data from the sensors of the model, and Figure~\ref{}~C.
 shows the power spectral density of on of the simulated time-series.
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
+% \begin{figure}
+% 	\centering
+% 		\includegraphics[scale=1]{file.eps}
+% 	\caption{Example of experimental design and model output.
+\textbf{A}.
+Example of the neural field with sensors.
+The centres of the sensors are shown by crossed and the width ($1/2$ height of Gaussian) are shown by the circles.
+\textbf{B} Example of data generated by the model through the observations.
+\textbf{C}.
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
+% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
+% \end{figure}
 
-\subsection{Frequency Analysis}
+\subsection{Spatial Frequency Analysis}
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 \begin{equation*}
- \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f-}
+ \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-}
 \end{equation*}
@@
 \end{equation*}
-\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1|t}^{b-}$ similar to the forward step and compute
+\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1}^{b-}$ similar to the forward step and compute
 \begin{equation*}
- \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{b-}
+ \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}
 \end{equation*}
@@
 \end{equation*}
+\State compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
+\begin{equation*}
+\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1}
+\end{equation*}
+\begin{equation*}
+ \hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
+\end{equation*}
+\begin{equation*}
+ \mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
+\end{equation*}
+
 \end{algorithmic}

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
adding to resutls

@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
-Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ need to be spatially band-limited.
+Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and the spatially coloured covariance functions \todo{~cite\{some EEG literature here\}}.
 In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
@@
 The sigma points describe the mean and covariance of the state estimate.
-The number of sigma points needed is $2L+1$ where $ L$ is the dimension of the state space.
+The number of sigma points needed is $2L+1$ where $L$ is the dimension of the state space.
 The columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
@@
 The neural field model was used to the generate data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{}.
-An example of the simulated field can be seen in Figure~\ref{}~A.
+All parameters for the model are given in table~\ref{}.
+An example of the simulated field can be seen in figure~\ref{}~A.
 The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.
@@
 Figure~\ref{}~B.
-shows example data from the sensors of the model, and Figure~\ref{}~C.
+shows example data from the sensors of the model, and figure~\ref{}~C.
 shows the power spectral density of on of the simulated time-series.
@@
 \subsection{Spatial Frequency Analysis}
+The spatial frequency of the observations is shown in figure~\ref{}.
+The cut-off frequency was taken to correspond to half the peak amplitude in dB and the oversampling parameter $\rho=3$.
+From equation~\ref{}, this gives a minimum distance between basis functions of \todo{??} and width of \todo{??} to satisfy Shannon's sampling criterion.
+Following this, the distance between basis function, $\Delta_b$, was set to \todo{??} and the basis function width, $\sigma$ was set to \todo{??}.
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added to results

@@
 
-\section{Neural Field Model}
+\section{Neural Field Model}\label{NeuralModelSection}
 In this section, we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
@@
 \end{equation}
-For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
+For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
 The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by
 \begin{equation}
-\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}.
+\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}.
 \end{equation}
-Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
+The relationship between the Fourier transform and the basis function width is
+\begin{equation}
+	1234
+\end{equation}
+Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
 
@@
 \section{Results}
-The neural field model was used to the generate data for state and parameter estimation.
+The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
 All parameters for the model are given in table~\ref{}.
 An example of the simulated field can be seen in figure~\ref{}~A.
-The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.
+The Figure demonstrates the experimental design where the sensors were placed in the centre of the field (full width at half maximum).
 This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
@@
 The spatial frequency of the observations is shown in figure~\ref{}.
-The cut-off frequency was taken to correspond to half the peak amplitude in dB and the oversampling parameter $\rho=3$.
-From equation~\ref{}, this gives a minimum distance between basis functions of \todo{??} and width of \todo{??} to satisfy Shannon's sampling criterion.
-Following this, the distance between basis function, $\Delta_b$, was set to \todo{??} and the basis function width, $\sigma$ was set to \todo{??}.
-
+The peak power of the fft of the observation was approximately $30$ dB.
+The cut-off frequency was taken to correspond to half the peak amplitude which was approximately $15$~dB.
+This provided a conservative The oversampling parameter $\rho=2$.
+From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion.
+\todo{maybe from Parham's derivation...
+From equation~\ref{} the width was calculated to be...
+or...}.
+The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
+Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6.
 \subsection{State and Parameter Estimates}
+To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
+Each realisation consisted of 300 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabalise.
+The initial state and parameters were unknown to the estimator.
+The state estimates were evaluated by comparing the field reconstruction to the true field using the mean RMSE and standard deviation of the RMSE.
+The distribution of the state estimates are shown in figure~\ref{}.
 
@@
 \begin{itemize}
-
+	\item 
+	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.
 	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. 
@@
 	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing.
-
 	\item The flexibility of the approach
-
 	\item Combining this method with other to incorporate longer range hetrogeneous connectivity.	
-
 	\item The need for activity to perform estimation.

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
lots of little, mostly compressive, edits to sections 1 and 2 of the paper.

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}		%<-comment out this for checking equations (author list too)
-\usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig}
+\documentclass[12pt]{iopart}
+\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
 \usepackage{color}  
-\usepackage{iopams,setstack}                  %<-comment out this for checking equations
-% \usepackage{anysize}							%<-use this for checking equation length
-% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
-% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-% \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
+\usepackage{iopams,setstack}                  % For creating coloured text and background
+% \usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
 % \newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
+\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+
+%Uncomment next line if AMS fonts required
 
@@
 
-\title[State and Parameter Estimation for Spatio-Temporal Neural Fields]{State and Parameter Estimation for Spatio-Temporal Neural Fields}
+\title[State and Parameter Estimation for a Spatio-temporal Neural Fields]{State and Parameter Estimation for a Spatio-temporal Neural Fields}
 
@@
 \section{Introduction}
-The human brain is arguably the world's most complex system.
-Approximately 100 billion neurons and 60 trillion synapses operate in concert to process information, resulting in the cognition that determines our behavior.
-The brain's efficiency, robustness, and adaptability are unparalleled by any man-made device and, despite decades of concerted research, our understanding of its complex dynamics remains modest.
-This has led researchers to study different scales of dynamics: starting from individual proteins, synapses, and neurons; moving through to neuronal networks and ensembles of neuronal networks.
+The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert.
+Despite decades of research, our understanding of neural dynamics remains modest.
+Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
 While our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
@@
 
-To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at the meso/macroscopic scale.
-Mathematical neural field  models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} \cite{Schiff2009} that would be impossible to gain from experimental data alone.
-Unfortunately, to date the use of these models in the clinic has been limited, since the neural field model are constructed for a general brain dynamics and pathologies almost always have unique underlying patient specific causes.
-Data from EEG and functional magnetic resonance imaging (fMRI) offers the patient specific link to macro-scale cortical dynamics, making these tools readily applicable to the clinic.
-However the underlying system properties, or system states, are hidden from EEG and fMRI data, making predictions of the underlying physiology inherently difficult.
+There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
+Mathematical neural field  models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008} \cite{David2003} for recent reviews).
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003}, \cite{Suffczynski2004} and \cite{Wendling2005} and insights into other pathologies \cite{Moran2008} \cite{Schiff2009} that would be difficult to gain from experimental data alone.
+
+Unfortunately, the use of these models in the clinic has been limited, since the neural field model are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient specific causes.
+Patient specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
+However the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
 
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to use a general neural field model, like the Wilson and Cohen~\cite{Wilson1973} model or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, and fit it to a patients EEG data.
+A possible approach to achieve this would be to fit a general neural field model, like the Wilson and Cohen (WC) \cite{Wilson1973} model or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
 Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
-An estimation frame work for neural field models known as dynamical causal modelling (DCM)~\cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
+
+An estimation framework for neural field models known as dynamical causal modelling (DCM) \cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
 The interconnected brain regions are modelled by the Jansen and Ritt equations.
-The approach has proven very useful in understanding specific hierarchical networks of neural information processing.
-Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the Wilson-Cowan neural field equations~\cite{schiff2008kalman}.
+Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the Wilson-Cowan neural field equations \cite{schiff2008kalman}.
 This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
@@
 That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neurodynamics and information about their particular pathologies.
-Given access to an accurate model, the application of control theory in these circumstances would allow for robust therapeutic stimulations.
-The work from Schiff and Sauer~\cite{schiff2008kalman} successfully demonstrated  it is possible to estimate parameters from the WC equations.
+Given access to an accurate model, the application of optimal control theory in these circumstances would allow for robust therapeutic stimulations.
+
+The work from Schiff and Sauer \cite{schiff2008kalman} successfully demonstrated  it is possible to estimate parameters \wtf{what kind of parameters?} from the WC equations.
 This motivates the question, what parameters are the most important?
@@
 In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modeling of the human neocortex.
+\wtf{not sure about rhetorical questions as a narrative mechanism in general, also not sure how this paper addresses these particular questions}
 
 \section{The Importance of Cortical Structure}
-Neural field models use statistics of the cortex to relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
-Each neural population represents a functional cortical processing unit referred to as a column.
-The columnar organization of the cortex is not discrete, but is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range corticocortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
-Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition~\cite{Braitenberg1998}.
-For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
 
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture the essential patient specific neurodynamics that lead to various oscillatory states.
-Estimating functional cortical connectivity via EEG measures is currently a highly active area of research.
-There is a lot of interest in understanding the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG, or fMRI times series.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}.
+Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+Each neural population represents a functional cortical processing unit, referred to as a column.
+The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
+In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range corticocortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
+Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
+
+Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
+
+Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
 Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
@@
 Until now, estimation of local intracortical connectivity structure has not been attempted.
-Recently, it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
-The key development in this work was to define a state-space model with an order independent of the number of observations (or ECoG recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modelling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions (three in the paper) is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria (AIC or BIC).
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
+Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
+The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (ECoG recording electrodes in this case).
+In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
+Modelling the neural dynamics within this framework has the distinct advantage over multivariate AR models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model \cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
-%Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
+%Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
 
 \section{Neural Field Model}
-In this section, we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
+In this section, we describe a variant of the  Wilson and Cowan neural field model \cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
 This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
@@
 The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
+
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
@@
 \end{equation}
-The post-synaptic response kernel $h(t)$ is described by
+The post-synaptic response kernel $h(t)$ is described by \todo{citation needed}
 \begin{equation}\label{SynapticRespKernel}
-	h(t) = \eta(t)\exp{\left(-\zeta t\right)}.
+	h(t) = \eta(t)\exp{\left(-\alpha t\right)}.
 \end{equation}
-where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
+where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	
 \begin{equation}\label{RateBasedInteractions}
@@
 \begin{equation}\label{ActivationFunction}
-	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
+	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{\nu _0\left(\mathbf{r}\right)}{1 + \exp \left( \beta \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 \begin{equation}\label{GreensFuncDef}
-	Dh\left( t \right) = \delta \left( t \right),
+	Lh\left( t \right) = \delta \left( t \right),
 \end{equation}
-where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-where $L=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $L=\frac{d}{dt} + \alpha$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}\label{FinalFormContinuous}
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \alpha v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \lambda v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
 \end{equation} 
-where $T$ is the time step, $\xi = 1-\zeta T$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
+where $T$ is the time step, $\lambda = 1-\alpha T$ and is an iid spatially colored, temporally white disturbance term with the covariance 
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma{\varepsilon}\right)$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\varepsilon_t \sim \mathcal{N}\left(0,\Sigma{\varepsilon}\right)$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
+	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \lambda\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
@@
 \begin{equation} 
-\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int\limits_{\Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 \begin{equation}\label{ObservationEquation}
-    \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
+    \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t \\
 \end{equation}
@@
 \begin{equation}
-	\mathbf{C} = \left[\begin{array}{{ccc}}
-	c_{1,1} & \dots & c_{1,L} \\
-	\vdots & \ddots & \vdots \\
-	c_{n_y,L} & \dots & c_{n_y,L} \end{array}\right]
+\mathbf{C} = \left[\begin{array}{{cccc}}
+\int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
+&\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
+r')d\mathbf r' \\
+\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
+r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
+\phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
+\mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
+\vdots&\vdots&\ddots&\vdots\\
+\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
+r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
+\phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
+\mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
+\end{array}\right],
 \end{equation}
-where $L$ is the number of basis functions and
-\begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')d\mathbf{r}'.
-\end{equation}
-% \begin{equation}
-% \mathbf{C} = \left[\begin{array}{{cccc}}
-% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
-% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
-% r')d\mathbf r' \\
-% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
-% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
-% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
-% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
-% \vdots&\vdots&\ddots&\vdots\\
-% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
-% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
-% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
-% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
-% \end{array}\right],
-% \end{equation}
-% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
+and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
 \section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
-Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
-Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
+Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations \cite{Sanner1992,Scerri2009}.
+Based on the higher dimension extensions of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
 
@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ (\todo{can this be $V_t(\boldsymbol{\nu})$}), multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited.
 Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}.
 In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
-Thus the spectral response $V_t(\boldsymbol{\nu})$ is usually band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
+Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
 Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
@@
 where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
-Satisfying this condition is required for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
+Satisfying this condition is required for the hidden dynamic field $w_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
 If the condition is not satisfied, spatial aliasing will occur.
@@
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation \cite{Sanner1992}.
 This is further illustrated our results.
-
-Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition.
+$\mathcal{W}$
+Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions.
 The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
@@
 The dynamic field must be spatially oversampled by using a larger number of sensor then imposed by frequency considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
-Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
+Following this, the distance between basis functions is usually larger then the distance between sensors.
+\todo{However this is not the case with this work.} For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
@@
 \section{State and Parameter Estimation}
-The estimation process is a two part iterative algorithm that yields the estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
-In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
-In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence .
-The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} to calculate a forward posterior estimate $\hat{\mathbf x}_t^{f} $ along with a separate backward smoothing path to compute the smooth estimations $\hat{\mathbf x}_t^{b} $.
-The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
-Alternatives to the UKF are the Extended Kalman Filter (EKF) \cite{Haykin2001}  and Sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
+The Unscented Rauch Tung Striebel Smoother (URTSS) was used for the state estimation \cite{Sarkka2010}, where the Unscented Kalman filter is used for the forward iteration \cite{Julier1997}.
+This method is appropriate for state estimation of stochastic nonlinear dynamical systems.
+Alternatives to this approach are the Extended Kalman Filter (EKF) \cite{Haykin2001}  and sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
 The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time step.
@@
 The sigma points describe the mean and covariance of the state estimate.
-The number of sigma points needed is $2L+1$ where $ L$ is the dimension of the state space.
-The  columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
-\begin{equation}
- \mathcal X_{0}=\bar x
-\end{equation}
-\begin{equation}
- \mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots,  L
-\end{equation}
-\begin{equation}
- \mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L
-\end{equation}
-\begin{equation}
- \mathbf W_0^{(m)}=\frac{\lambda}{ L+\lambda}
-\end{equation}
-\begin{equation}
- \mathbf W_0^{(c)}=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta)
-\end{equation}
-\begin{equation}
- \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L
-\end{equation}
-where the scaling parameter $\lambda$ is defined as
-\begin{equation}
-\lambda=\alpha^2( L+\kappa)- L 
-\end{equation}
-and parameters $\alpha$, $\beta$ and $\kappa$ are used to tune the filtering process \cite{Haykin2001}.
-It should be noted that $\bar x$ is $ \hat{\mathbf x}_t^{f} $ and $ \hat{\mathbf x}_t^{b} $ with their corresponding covariance matrices in filtering and smoothing iterations respectively.
-
-% For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}.
-$ (\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i$ is the ith column of the matrix square root (e.g., lower-triangular Cholesky factorization).
-These sigma points propogated through the nonlinear function
-
 The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution.
@@
 \end{equation*}
-Propogate the sigma points through the state equation
+Propogate the sigma points through the dynamic model
 \begin{equation}
-\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_t^f,u_t)
+\mathcal X_{i,t+1|t}^{f*}=Q(\mathcal X_t^f,u_t)
 \end{equation}
 \begin{equation*}
- \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-}
+ \hat{\mathbf x}_{k +t}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f*}
 \end{equation*}
 \begin{equation*}
- \mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e
+ \mathbf P_{t +1}^-=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e
 \end{equation*}
@@
 \begin{equation}
- \mathbf P_T^b= \mathbf P_T^f
+ \mathbf P_T^s= \mathbf P_T^f
 \end{equation}
 \begin{equation}
-\hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T
+\hat{\mathbf x}^s_T= \hat{\mathbf x}^f_T
 \end{equation}
-For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $
+For $t \in \left\lbrace N-1, \cdots, 0 \right\rbrace $
 \begin{equation*}
-\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}]
+\mathcal X_t^s=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}]
 \end{equation*}
-\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1}^{b-}$ similar to the forward step and compute
-\begin{equation*}
- \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}
-\end{equation*}
-\begin{equation*}
- \mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{f})^\top+\boldsymbol \Sigma_e
-\end{equation*}
-\begin{equation*}
- \mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{f})^\top
-\end{equation*}
-\State compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
-\begin{equation*}
-\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1}
-\end{equation*}
-\begin{equation*}
- \hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
-\end{equation*}
-\begin{equation*}
- \mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
-\end{equation*}
-
 \end{algorithmic}
 \end{algorithm}
-\section{Results}
-The neural field model was used to the generate data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{}.
-An example of the simulated field can be seen in Figure~\ref{}~A.
-The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.
-This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
-Figure~\ref{}~B.
-shows example data from the sensors of the model, and Figure~\ref{}~C.
-shows the power spectral density of on of the simulated time-series.
-The PSD shows the typical $1/f$ characteristics of intracranial EEG.
-% \begin{figure}
-% 	\centering
-% 		\includegraphics[scale=1]{file.eps}
-% 	\caption{Example of experimental design and model output.
-\textbf{A}.
-Example of the neural field with sensors.
-The centres of the sensors are shown by crossed and the width ($1/2$ height of Gaussian) are shown by the circles.
-\textbf{B} Example of data generated by the model through the observations.
-\textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
-% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
-% \end{figure}
-
-\subsection{Spatial Frequency Analysis}
-
-\subsection{State and Parameter Estimates}
+\section{Comparison of Estimated Parameters and True Parameters}
 
 \section{Discussion}
-
 \begin{itemize}
@@
 Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}\label{ReducingState}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+\begin{eqnarray}\label{Poo}
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}\label{StartofReduction}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+\begin{eqnarray}\label{Poo}
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \lambda\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
 \end{eqnarray}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \lambda \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \end{lemma}
-\section*{Proof}
+\subsection{proof}
  Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
@@
 &=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+&=&\mathbf{\Gamma}^{-1}\int\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
 \end{eqnarray}
@@
 \end{equation}
-\section{Parameters}
-\begin{tabular} {c|c} 
-	\hline\hline
-	Symbol & Description \\ \hline
-	$v(\mathbf{r},t)$ & mean membrane potential \\
-	$g(\mathbf{r},t)$ & average action potential rate \\
-	$\mathbf{r}$ & spatial location \\
-	$t$ & time (s) \\
-	$h(t)$ & post-synaptic response kernel \\
-	$\eta(t)$ & Heaviside function \\
-	$\zeta$ & inverse synaptic time constant \\
-	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
-	$f(\mathbf{r},t)$ & firing function rate \\
-	$u(\mathbf{r},t)$ & external input \\
-	$\Omega$ & spatial domain \\
-	$f_{max}$ & maximal firing rate \\
-	$\varsigma$ & slope of sigmoidal activation function \\
-	$v_0$ & firing threshold \\
-	$\delta(t)$ & Dirac-delta function \\
-	$D$ & Temporal differential operator \\
-	$L$ & number of basis function and dimension of state vector \\
-	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
-	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
-	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
-	$y(\mathbf{r}_n,t)$ & obseration \\
-	$n$ & sensor index $n=1,..,N$ \\
-	$T$ & time step \\
-	$\xi$ & time constant parameter \\
-	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
-	$\mathbf{x}_t$ & state vector at time $t$ \\
-	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
-	$\theta$ & vector of connectivity kernel parameters \\
-	$\Gamma$ & inner product of field basis functions \\
-	$q()$ & state function \\
-	$k()$ & maps into to discrete state of input function \\
-	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\
-	$\mathbf{C}$ & observation matrix \\
-	$V(\nu)$ & Spectrum of the dynamic field \\ 
-	$\nu$ & Spatial frequency \\
-	$\nu_c$ & Spatial cut-off frequency \\
-\end{tabular}
-
-\begin{tabular}{c|c}
-	\hline\hline
-	Symbol & Description \\ \hline
-	$\Delta_s$ & Distance between adjacent sensors \\
-	$\rho$ & Over-sampling parameter \\	
-	$\Delta_b$ & Distance between field basis functions \\	
-	$\sigma_{nu}^2$ & Variance of FT of Gaussian basis function \\
-	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
-	$\hat{\mathbf{x}}$ & State estimate \\
-	$\chi$ & Matrix of sigma vectors \\
-	$\hat{\mathbf{x}}_t^{f-}$ & Forward \emph{a priori} estimate \\
-	$\hat{\mathbf{x}}_t^f$ & Forward \emph{a posteriori} estimate \\
-	$\hat{\mathbf{x}}_t^{b-}$ & Backward \emph{a priori} estimate \\
-	$\hat{\mathbf{x}}_t^{b}$ & Backward \emph{a posteriori} estimate \\
-	$P^f_t$ & Forward \emph{a posteriori} covariance matrix \\
-	$P^{f-}_t$ & Forward \emph{a priori} covariance matrix \\	
-\end{tabular}
 \section*{References}
-\bibliographystyle{unsrt}
-\bibliography{BrainIDE}
-
-% \begin{thebibliography}{10}
-% \bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
-% (Reading, MA: Addison-Wesley)
-% \bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
-% \end{thebibliography}
+\begin{thebibliography}{10}
+\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
+(Reading, MA: Addison-Wesley)
+\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
+\end{thebibliography}
 

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
just found loads of merge things that i've gone through and cleaned up properly I hope. What a pain!

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
+\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
 
@@
 Until now, estimation of local intracortical connectivity structure has not been attempted.
-Recently, it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}.
-The key development in this work was to define a state-space model with an order independent of the number of observations (or ECoG recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modelling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions (three in the paper) is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria (AIC or BIC).
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}.
+Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
+The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (ECoG recording electrodes in this case).
+In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
+Modelling the neural dynamics within this framework has the distinct advantage over multivariate AR models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model \cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
-%Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..
+%Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
 
 \section{Neural Field Model}\label{NeuralModelSection}
-In this section, we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
+
+In this section, we describe a variant of the  Wilson and Cowan neural field model \cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
 This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
@@
 \end{equation}
-The post-synaptic response kernel $h(t)$ is described by
+The post-synaptic response kernel $h(t)$ is described by \todo{citation needed}
 \begin{equation}\label{SynapticRespKernel}
@@
 \end{equation}
+
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving
-where $L=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+
 \begin{equation}\label{FinalFormContinuous}
@@
 \section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
-Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
-Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
+Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations \cite{Sanner1992,Scerri2009}.
+Based on the higher dimension extensions of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
 

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
sync repositories with everyone

--- 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \documentclass[12pt]{iopart}		%<-comment out this for checking equations (author list too)
+\usepackage{iopams,setstack}                  %<-comment out this for checking equations
 \usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig}
 \usepackage{color}  
-\usepackage{iopams,setstack}                  %<-comment out this for checking equations
 % \usepackage{anysize}							%<-use this for checking equation length
@@
 % \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
-% \newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
@@
 \end{equation*}
-
 \end{algorithmic}
@@
 Example of the neural field with sensors.
-The centres of the sensors are shown by crossed and the width ($1/2$ height of Gaussian) are shown by the circles.
+The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
 \textbf{B} Example of data generated by the model through the observations.
@@
 To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
-Each realisation consisted of 300 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabalise.
+Each realisation consisted of 300 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
 The initial state and parameters were unknown to the estimator.
-The state estimates were evaluated by comparing the field reconstruction to the true field using the mean RMSE and standard deviation of the RMSE.
+The state estimates were evaluated by comparing the field reconstruction to the true field using the mean over time of the RMSE and standard deviation of the RMSE.
 The distribution of the state estimates are shown in figure~\ref{}.

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to results in prep for meeting with VK

@@
 \newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
-
+\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}  
 \begin{document}
@@
 \section{Introduction}
+This paper presents a framework for creating patient specific macroscopic neural field continuum mathematical models.
 The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert.
@@
 Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
-While our understanding of the function of neurons is well developed, the overall behavior of the brain's meso and macro-scale dynamics remains largely a mystery.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a mystery.
 Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
@@
 Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the Wilson-Cowan neural field equations \cite{schiff2008kalman}.
-This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
@@
 How patient specific do the assumed parameters have to be for the model to be useful?
-In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modeling of the human neocortex.
-\wtf{not sure about rhetorical questions as a narrative mechanism in general, also not sure how this paper addresses these particular questions}
+In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modelling of the human neocortex.
+\wtf{not sure about rhetorical questions as a narrative mechanism in general, also not sure how this paper addresses these particular questions.} \omg{Maybe the next section addresses that the connectivity is important.
+Needs sharpening.}
 
 \section{The Importance of Cortical Structure}
-
 Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
@@
 The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range corticocortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
+In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
 Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
-For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
 
@@
 Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
+Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
 Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
@@
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
+
+The sensor were model such that they were spaced in a regular square grid where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
+This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
+Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field.
+\omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
 % \begin{figure}
@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
-Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6.
+Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
+Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.
+
 \subsection{State and Parameter Estimates}
@@
 \begin{itemize}
-	\item 
+	\item the width of the connectivity basis functions here is known exactly. In practice we don't 
 	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to results in prep for meeting with VK

@@
 
-The sensor were model such that they were spaced in a regular square grid where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
+The sensors were modelled such that they were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits

@@
 Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}
-The estimation process is a two part iterative algorithm that yields the estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
-In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection}
+In this section we describe the procedure for estimating the states that scale the field basis functions, the connectivity kernel parameters and the synaptic time constant.
+The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+The two step estimation algorithm exploits the fact the parameters are linear with respect to the state estimate.
+Therefore, the parameter estimation step utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
 In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence .
@@
 % \end{proof}
-\section{Parameter estimation using LS}
+\section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix}
 \begin{equation}

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits

--- 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}
-The estimation process is a two part iterative algorithm that yields the estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
-In the parameter estimation step, Least Squares (LS) method is used which minimizes the sum of the squares of the errors on each state equation (see Appendix).
-In the state estimation step, given an estimate of $\boldsymbol \theta$ and $\xi$ the Unscented Rauch Tung Striebel Smoother (URTSS) \cite{Sarkka2010} was used to determine the posterior state sequence .
-The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration \cite{Julier1997} to calculate a forward posterior estimate $\hat{\mathbf x}_t^{f} $ along with a separate backward smoothing path to compute the smooth estimations $\hat{\mathbf x}_t^{b} $.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection}
+In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step at each time instance.
+Although the system is nonlinear, the parameters of the system are linear with respect to the state.
+This is exploited by our procedure where the parameter estimation utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
+
+The state estimation step utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} to determine the posterior state sequence.
+The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration~\cite{Julier1997} to calculate a forward posterior state estimate, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimations $\hat{\mathbf x}_t^{b}$.
 The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
@@
 \end{equation*}
-Propogate the sigma points through the state equation
+Propagate the sigma points through the state equation
 \begin{equation}

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small updates

@@
 The state estimation step utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} to determine the posterior state sequence.
-The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration~\cite{Julier1997} to calculate a forward posterior state estimate, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimations $\hat{\mathbf x}_t^{b}$.
-The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
-Alternatives to the UKF are the Extended Kalman Filter (EKF) \cite{Haykin2001}  and Sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
-The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time step.
-The linearization maintains the Gaussianality in the model.
+Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and Sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
+The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time instance.
+The linearisation maintains the Gaussianality of the model.
 The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
@@
 SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
-However, currently this method is not appropriate for our problem, due to computation demands.
+However, currently this method is not appropriate for our problem, due to computation demands.The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration~\cite{Julier1997} to calculate a forward posterior state estimate, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimations $\hat{\mathbf x}_t^{b}$.
+The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
 

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added graphics guidelines

@@
 
-The state estimation step utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} to determine the posterior state sequence.
-Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and Sequential Monte Carlo (SMC) filtering \cite{doucet2001}.
-The extended Kalman filter approximates the state transition equation by linearizing about the fixed points (by calculating the Jacobian) at each time instance.
+The state estimation technique utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
+The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration~\cite{Julier1997} to calculate a forward posterior state estimate, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimations, $\hat{\mathbf x}_t^{b}$.
+Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
+The EKF approximates the state transition equation by linearizing about the current state estimates (by calculating the Jacobian) at each time instance.
 The linearisation maintains the Gaussianality of the model.
@@
 SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
-However, currently this method is not appropriate for our problem, due to computation demands.The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration~\cite{Julier1997} to calculate a forward posterior state estimate, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimations $\hat{\mathbf x}_t^{b}$.
-The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
+However, currently this method is not appropriate for our problem, due to computation demands.The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
 

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
figurs for frequency analysys

--- 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-% \begin{figure}
-% 	\centering
-% 		\includegraphics[scale=1]{file.eps}
-% 	\caption{Example of experimental design and model output.
+ \begin{figure}
+ 	\begin{center}
+ 		\includegraphics[scale=0.2]{./Graph/kernel.pdf}
+		\includegraphics[scale=0.2]{./Graph/field.pdf}
+		\includegraphics[scale=0.2]{./Graph/filtered.pdf}
+	\end{center}
+ 	\caption{Example of experimental design and model output.
 \textbf{A}.
@@
 Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
-% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
-% \end{figure}
+ 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
+ \end{figure}
 

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
subfigs
editing estimation section

--- 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \usepackage{iopams,setstack}                  %<-comment out this for checking equations
-\usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig}
+\usepackage{algorithm, algorithmicx, algpseudocode,epsfig}
+\usepackage{subfigure}[]
+\usepackage{graphicx}
 \usepackage{color}  
+\usepackage[ansinew]{inputenc}
 % \usepackage{anysize}							%<-use this for checking equation length
@@
 The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step at each time instance.
-Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
 
 The state estimation technique utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The (URTSS) uses the Unscented Kalman Filter (UKF) in the forward iteration~\cite{Julier1997} to calculate a forward posterior state estimate, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimations, $\hat{\mathbf x}_t^{b}$.
-Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
-The EKF approximates the state transition equation by linearizing about the current state estimates (by calculating the Jacobian) at each time instance.
-The linearisation maintains the Gaussianality of the model.
-The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
-This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
-In addition, the computation of the Jacobian used in the
-EKF can be problematic.
-SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
-However, currently this method is not appropriate for our problem, due to computation demands.The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
-
-The approximation of the state density is made by propagating the so called sigma points through the state-space model.
-The sigma points describe the mean and covariance of the state estimate.
-The number of sigma points needed is $2L+1$ where $L$ is the dimension of the state space.
-The columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+An approximation of the state density is made by propagating the so-called sigma points through the state-space model.
+The sigma points describe the mean and covariance of the state estimate and are calculated using the unscented transform.
+The sigma vectors $\mathcal X_i$ are calculated by
 \begin{equation}
@@
 \end{equation}
+where $L$ is the dimension of the state space, the number of sigma points required is $2L+1$. The scaling parameter $\lambda$ is defined as a scaling parameter
+\begin{equation}
+\lambda=\alpha^2( L+\kappa)- L 
+\end{equation}
+where $\alpha$, $\beta$ and $\kappa$ are constants (see ~\cite{Haykin2001} for more details).
+It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing respectively.
+The sigma vectors are propagated through the nonlinear function The weights of the columns of the sigma point matrix and their corresponding weights used in the UKF are calculated by
+
 \begin{equation}
@@
 \end{equation}
-where the scaling parameter $\lambda$ is defined as
-\begin{equation}
-\lambda=\alpha^2( L+\kappa)- L 
-\end{equation}
-and parameters $\alpha$, $\beta$ and $\kappa$ are used to tune the filtering process \cite{Haykin2001}.
-It should be noted that $\bar x$ is $ \hat{\mathbf x}_t^{f} $ and $ \hat{\mathbf x}_t^{b} $ with their corresponding covariance matrices in filtering and smoothing iterations respectively.
-
 % For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}.
@@
  The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution.
+
 To explain the operation of the UKF we begin by deriving the traditional Kalman filter with the state-space model
@@
 The update step equations remains the same as the standard Kalman filtering formulations.
-In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filterin step, however the predicted cross-covariance of the states need to be calculated.
+In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filtering step, however the predicted cross-covariance of the states need to be calculated.
 A summary of the algorithm is given in Algorithm
@@
 \end{algorithm}
+
+Although the system is nonlinear, the parameters of the system are linear with respect to the state.
+This is exploited by our procedure where the parameter estimation utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
+
+Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
+The EKF approximates the state transition equation by linearizing about the current state estimates (by calculating the Jacobian) at each time instance.
+The linearisation maintains the Gaussianality of the model.
+The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
+This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
+In addition, the computation of the Jacobian used in the
+EKF can be problematic.
+SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
+However, currently this method is not appropriate for our problem, due to computation demands.
+The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
+
 \section{Results}

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 \usepackage{iopams,setstack}                  %<-comment out this for checking equations
-\usepackage{algorithm, algorithmicx, algpseudocode,epsfig}
-\usepackage{subfigure}[]
-\usepackage{graphicx}
+
+\usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig}
 \usepackage{color} 
-\usepackage[ansinew]{inputenc}
+ \usepackage[tight,footnotesize]{subfigure}
 % \usepackage{anysize}							%<-use this for checking equation length
@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-% \begin{figure}
-% 	\centering
-% 		\includegraphics[scale=1]{file.eps}
-% 	\caption{Example of experimental design and model output.
+ \begin{figure}
+ 	\begin{center}
+ 		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/kernel.pdf}}
+		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/field.pdf}}
+		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/filtered.pdf}}
+	\end{center}
+ 	\caption{Example of experimental design and model output.
 \textbf{A}.

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
subfigs
updated estimation section

@@
 It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing respectively.
-The sigma vectors are propagated through the nonlinear function The weights of the columns of the sigma point matrix and their corresponding weights used in the UKF are calculated by
-
+The sigma vectors are propagated through the system equations and weighted to form the posterior mean and covariance.
+The weights are calculated by
 \begin{equation}
@@
 \begin{equation}
- \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L
+ \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L.
 \end{equation}
@@
 
- The accuracy of the approximation is linked to the time step used in the temporal discretization of the system, where the state transition appears more linear with a finer resolution.
-
-To explain the operation of the UKF we begin by deriving the traditional Kalman filter with the state-space model
-\begin{eqnarray}
-	\mathbf{x}_t = q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
-\end{eqnarray}
-where $\boldsymbol{\theta}$ and $\xi$ are the systems parameters.
-In forwards iteration since the observation equation is linear in parameters we only need to use Unsented transformation in prediction step.
-The update step equations remains the same as the standard Kalman filtering formulations.
-In backward smoothing path, estimation from the forward filtering is used to form the new set of sigma points in a similar way to the filtering step, however the predicted cross-covariance of the states need to be calculated.
-A summary of the algorithm is given in Algorithm
+The update step equations are the same as the standard Kalman filtering formulations.
+The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
+However, the predicted cross-covariance of the states needs to be calculated.
+A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
 \begin{algorithm}
-\caption{The Unscented Kalman Filter}\label{CPTEMDAlgorithm}
+\caption{The Unscented Kalman Filter}\label{UKFAlgorithm}
 \begin{algorithmic}[1]
@@
 \State Forward iteration
-For $t \in \left\lbrace 0,\cdots, N\right\rbrace $,
+For $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
 \begin{equation*}
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see~\ref{LeastSquaresAppendix}).
+
+% The accuracy of the approximation is linked to the time step used in the temporal discretisation of the system, where the state transition appears more linear with a finer resolution.
 
@@
 However, currently this method is not appropriate for our problem, due to computation demands.
-The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
+%The method is appropriate for state estimation of stochastic nonlinear dynamical systems.
 

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
general paper updates

@@
 \usepackage{color} 
- \usepackage[tight,footnotesize]{subfigure}
+ \usepackage[tight,scriptsize]{subfigure}
+%\renewcommand{\subcapsize}{\small}
 % \usepackage{anysize}							%<-use this for checking equation length
@@
 \end{equation}
-
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-
 \begin{equation}\label{FinalFormContinuous}
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see Appendix~\ref{Time Discretization}) giving
+To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see~\ref{Time Discretization}) giving
 \begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
 \end{equation} 
-where $T$ is the time step, $\xi = 1-\zeta T$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
 \begin{equation}
@@
 \begin{equation}\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \end{equation}
-and manipulating the model (see Appendix~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model
+and manipulating the model (see~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model
 \begin{eqnarray}\label{Homogeneous SS Model}
@@
 	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
-	q\left(\mathbf{x}_t\right) &=& T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
-	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
+	q\left(\mathbf{x}_t\right) &=& T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
+	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
 	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}},
 \end{eqnarray}
-where $\mathbf{e}_t$ is a zero-mean normal white noise term with the covariance (see Appendix \ref{ColoredNoise})
+where $\mathbf{e}_t$ is a zero-mean normal white noise term with the covariance (see~\ref{ColoredNoise})
 \begin{equation} 
@@
 \end{equation}
-where $L$ is the dimension of the state space, the number of sigma points required is $2L+1$. The scaling parameter $\lambda$ is defined as a scaling parameter
+where $L$ is the dimension of the state space and the number of sigma points is $2L+1$. The scaling parameter $\lambda$ is defined as
 \begin{equation}
@@
 \begin{algorithmic}[1]
-\State Initialise
+\State Forward initialisation
 \begin{equation*}
@@
 \end{equation*}
-\State Backward iteration
-\State initialisation
+\State Backward initialisation
 \begin{equation}
@@
 \end{equation}
+\State Backward iteration
 For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $
@@
 \end{equation*}
-\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1}^{b-}$ similar to the forward step and compute
+\State Calculate sigma points for the smoother $\mathcal X_{i,t+1}^{b-}$ and compute
 \begin{equation*}
@@
 \end{equation*}
-\State compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
+\State Compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
 \begin{equation*}
@@
 \begin{equation}\label{Euler Approximation}	
-\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T} =   -\zeta v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
+\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =   -\zeta v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
 \end{equation}
@@
 \begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T \zeta v_t\left( \mathbf{r}\right) + T \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T u_t\left(\mathbf{r}\right).
+v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
 \end{eqnarray}
@@
 \begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T u_t\left(\mathbf{r}\right),
+	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right),
 \end{equation}
@@
 \begin{equation}\label{discrete space}
-	v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
+	v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T_s \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
 \end{equation}
@@
 \begin{eqnarray}\label{ReducingState}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
-	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
 \end{eqnarray}
@@
 \begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
-	+ \boldsymbol{\Gamma}^{-1}T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+	\mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
 \end{eqnarray}
@@
 \begin{eqnarray}\label{StartofReduction}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
-	+ T \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}.
 \end{eqnarray}

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper updates

@@
 	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
-	q\left(\mathbf{x}_t\right) &=& T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
+	\mathbf{Q}\left(\mathbf{x}_t\right) &=& T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
@@
 \section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
-Spectral analysis has been utilized to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations \cite{Sanner1992,Scerri2009}.
-Based on the higher dimension extensions of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required.
+Spectral analysis was utilised to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
+Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
 
-The spectral characteristics of the field are governed by the the shape of the connectivity kernel or the coloring of the covariance of the field disturbance.
-If the bandwidth of the disturbance covariance was greater than the bandwidth of the connectivity kernel than the disturbance governs the bandwidth of the system.
+The spectral characteristics of the field are governed by the shape of the connectivity kernel or the covariance of the field disturbance.
+If the bandwidth of the field disturbance covariance was wider than the bandwidth of the connectivity kernel, then the disturbance governs the bandwidth of the system.
 Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth.
@@
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ need to be spatially band-limited.
+Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
 Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and the spatially coloured covariance functions \todo{~cite\{some EEG literature here\}}.
-In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the effective bandwidth of the field.
 Thus the spectral response $V_t(\boldsymbol{\nu})$ is usually band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
@@
 Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
-\begin{equation}
-\Delta_s = \frac{1}{2\rho\nu_c},
+\begin{equation}\label{eq:MinimumSensorDistance}
+\Delta_s < \frac{1}{2\rho\nu_c},
 \end{equation}
@@
 There are two options available to alleviate problems with aliasing.
-The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filters.
-The first option is more desirable, since more information is retained.
-However, if sensors are modelled as having a Gaussian pickup range than the effective filter will not have a sharp cut-off and high frequency components will still remain and mild aliasing will still occur.
+The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors).
+The second is to use wider sensors, which act like an anti-aliasing filters.
+This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field.
 In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
-It may be estimated using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques.
+However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques.
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
@@
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
-
-Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
+% 
+% Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
 \section{State and Parameter Estimation}\label{StateAndParameterEstimationSection}
@@
 	\begin{center}
+		\includegraphics[scale=0.2]{./Graph/kernel.pdf}
+	\end{center}
+	\caption{Example of experimental design and model output.
+\textbf{A}.
+Example of the neural field with sensors.
+The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
+\textbf{B} Example of data generated by the model through the observations.
+\textbf{C}.
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
+
+\subsection{Spatial Frequency Analysis}
+In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+Figure~\ref{} shows the spatial frequency of the field.
+The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power.
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}.
+This confirms our separation was enough to prevent problems associated with aliasing.
+
+The spatial frequency of the observations is shown in figure~\ref{}.
+The peak power of the spatial frequency of the observations was approximately $30$~dB.
+The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB.
+This provided a conservative The oversampling parameter $\rho=2$.
+From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion.
+\todo{maybe from Parham's derivation...
+From equation~\ref{} the width was calculated to be...
+or...}.
+The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
+	\label{fig:FrequencyAnalysis}
+\end{figure}
+ \begin{figure}
+ 	\begin{center}
  		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/kernel.pdf}}
@@
  \end{figure}
-
-\subsection{Spatial Frequency Analysis}
-The spatial frequency of the observations is shown in figure~\ref{}.
-The peak power of the fft of the observation was approximately $30$ dB.
-The cut-off frequency was taken to correspond to half the peak amplitude which was approximately $15$~dB.
-This provided a conservative The oversampling parameter $\rho=2$.
-From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion.
-\todo{maybe from Parham's derivation...
-From equation~\ref{} the width was calculated to be...
-or...}.
-The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
 Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
@@
 \begin{itemize}
+	\item alternatives to frequency analysis are model selection.
 	\item the width of the connectivity basis functions here is known exactly. In practice we don't 

### 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper updates

@@
 \begin{itemize}
-	\item alternatives to frequency analysis are model selection.
+	\item if we don't know the frequency analysis or the system is marginally sampled or under-sampled, the best we can do is have the basis functions the same as the sensor kernel.
+	\item alternatives to frequency analysis are model selection...
 	\item the width of the connectivity basis functions here is known exactly. In practice we don't 

### 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added mike's affiliation
* made a bunch of comments in the discussion section * made some minor text changes * changed section 5 from "Spec Anal. and Decomp." to "Spec Anal. and Model Selection" as the decomposition was all performed in the preceeding section

@@
 % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}		%<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack}                  %<-comment out this for checking equations
+\documentclass[12pt]{iopart}
 
+%<-comment out this for checking equations (author list too)
+\usepackage{iopams,setstack}
+
+%<-comment out this for checking equations
 \usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig} 
@@
 \usepackage[tight,scriptsize]{subfigure}
+
 %\renewcommand{\subcapsize}{\small}
@@
 \newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}  
-\begin{document}
+\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}
 
@@
 
-\address{$^1$ Department
-of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
-Vic, 3010 Australia}
-\address{$^2$ Department
-of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
-S1 3JD, UK}
-\address{$^3$ Mike's}
-\address{$^4$ Ken's}
-\ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 
-\section{Introduction}
-This paper presents a framework for creating patient specific macroscopic neural field continuum mathematical models.
-The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert.
-Despite decades of research, our understanding of neural dynamics remains modest.
+\section{Introduction} This paper presents a framework for creating patient specific macroscopic neural field continuum mathematical models.
+\todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph.
+Otherwise this first sentence looks a little out of place.}
+
+The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
 Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
@@
 
-\section{The Importance of Cortical Structure}
-Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+\section{The Importance of Cortical Structure} Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
 Each neural population represents a functional cortical processing unit, referred to as a column.
@@
 Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
+
 %Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
-
 Until now, estimation of local intracortical connectivity structure has not been attempted.
@@
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
+
 %Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
-
 \section{Neural Field Model}\label{NeuralModelSection}
@@
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
-\begin{equation}\label{SpikesToPotential}
-	v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}.
+\begin{equation}
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}. 
 \end{equation}
 The post-synaptic response kernel $h(t)$ is described by \todo{citation needed} 
-\begin{equation}\label{SynapticRespKernel}
-	h(t) = \eta(t)\exp{\left(-\zeta t\right)}.
+\begin{equation}
+	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}. 
 \end{equation}
 where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by 
-\begin{equation}\label{RateBasedInteractions}
-	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right),
+\begin{equation}
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right),
 \end{equation}
 where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
-The term $u\left(\mathbf{r},t\right)$ represents a known external input.
+The term $u\left(\mathbf{r},t\right)$ represents a known external input \wtf{Do we actually use the input in this paper, or is it just dragged around the derivation to be discarded in the conclusion?}.
 The connectivity kernel is typically a ``Mexican hat'' function \todo{which describes strong local activation, weak mid-range repression and weak long-range activation \cite{}}.
@@
 The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
-\begin{equation}\label{ActivationFunction}
-	f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
+\begin{equation}
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
+
 %Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. 
 By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model 
-\begin{equation}\label{FullDoubleIntModel}
-	v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega   w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'.
+\begin{equation}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'.
 \end{equation}
 To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function 
-\begin{equation}\label{GreensFuncDef}
-	Dh\left( t \right) = \delta \left( t \right),
+\begin{equation}
+	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
 \end{equation}
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{equation}\label{FinalFormContinuous}
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
+\begin{equation}
+	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
 \end{equation}
 To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see~\ref{Time Discretization}) giving 
-\begin{equation}\label{DiscreteTimeModel}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+\begin{equation}
+	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
 \end{equation}
@@
 \begin{equation}
-    cov(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ \begin{array}{*{20}{c}}
-    \gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
+	cov(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ 
+	\begin{array}{*{20}
+		{c}} \gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
 		0 & \mathrm{otherwise}. \\
-    \end{array} \right.
+	\end{array}
+	\right. 
 \end{equation}
@@
 
-\section{Derivation of Finite Dimensional State-Space Model}
-In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions.
+\section{Derivation of Finite Dimensional State-Space Model} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions.
 Decomposition allows a continuous field to be represented by a finite dimensional state vector.
@@
 The field decomposition is described by
-\begin{equation}\label{DefFieldDecomp}
-	v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t,
+\begin{equation}
+	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
 \end{equation}
@@
 The connectivity kernel can also be considered a decomposition into a set of basis functions in
-\begin{equation}\label{DefKernelDecomp}
-	w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right).
+\begin{equation}
+	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right). 
 \end{equation}
 We will assume we know the parametric form of the connectivity basis functions, where the parameter $\boldsymbol{\theta}$ is unknown.
-Each connectivity basis function can be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
+Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
 Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{equation}\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\boldsymbol{\theta}^{\top}\int_\Omega  {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'}  - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+\begin{equation}
+	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\boldsymbol{\theta}^{\top}\int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'} - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
 By defining the term 
-\begin{equation}\label{DefGamma}
-	\boldsymbol{\Gamma}  = \int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}
+\begin{equation}
+	\label{DefGamma} \boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}} 
 \end{equation}
 and manipulating the model (see~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
-\begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+\begin{eqnarray}
+	\label{Homogeneous SS Model} \mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
 	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
@@
 The observation equation of the reduced model is 
-\begin{equation}\label{ObservationEquation}
-    \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
+\begin{equation}
+	\label{ObservationEquation} \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t 
 \end{equation}
@@
 \begin{equation}
-	\mathbf{C} = \left[\begin{array}{{ccc}}
+	\mathbf{C} = \left[
+	\begin{array}{{ccc}} 
 		c_{1,1} & \dots & c_{1,L} \\
 		\vdots & \ddots & \vdots \\
-	c_{n_y,L} & \dots & c_{n_y,L} \end{array}\right]
+		c_{n_y,L} & \dots & c_{n_y,L} 
+	\end{array}
+	\right] 
 \end{equation}
@@
 \end{equation}
+
 % \begin{equation}
@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}
-Spectral analysis was utilised to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was utilised to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
 Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
@@
 Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
-\begin{equation}\label{eq:MinimumSensorDistance}
-\Delta_s < \frac{1}{2\rho\nu_c},
+\begin{equation}
+	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho\nu_c}, 
 \end{equation}
@@
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
+
 % 
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection}
-In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
 The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step at each time instance.
@@
 \end{equation}
+
 % For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}.
@@
 These sigma points propogated through the nonlinear function
-
 The update step equations are the same as the standard Kalman filtering formulations.
@@
 		\end{equation*}
-\State Forward iteration
-For $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
+		\State Forward iteration For $t \in \left\lbrace 0,\cdots, T\right\rbrace $, 
 		\begin{equation*}
@@
 		\end{equation}
-\State Backward iteration
-For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $
+		\State Backward iteration For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ 
 		\begin{equation*}
@@
 % The accuracy of the approximation is linked to the time step used in the temporal discretisation of the system, where the state transition appears more linear with a finer resolution. 
-
 Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
@@
 This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
-In addition, the computation of the Jacobian used in the
-EKF can be problematic.
+In addition, the computation of the Jacobian used in the EKF can be problematic.
 SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
 However, currently this method is not appropriate for our problem, due to computation demands.
+
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-
-\section{Results}
-The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
+\section{Results} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
 All parameters for the model are given in table~\ref{}.
@@
 \textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
+\end{figure}
 
-\subsection{Spatial Frequency Analysis}
-In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
 Figure~\ref{} shows the spatial frequency of the field.
@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
-	\label{fig:FrequencyAnalysis}
-\end{figure}
 \begin{figure}
 	\begin{center}
- 		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/kernel.pdf}}
-		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/field.pdf}}
-		\subfigure[][]{\includegraphics[scale=0.2]{./Graph/filtered.pdf}}
+		\subfigure[][]{
+		\includegraphics[scale=0.2]{./Graph/kernel.pdf}} \subfigure[][]{
+		\includegraphics[scale=0.2]{./Graph/field.pdf}} \subfigure[][]{
+		\includegraphics[scale=0.2]{./Graph/filtered.pdf}} 
 	\end{center}
@@
 \textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
- 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:ExampleFieldAndSensorsDataAndPSD}
 \end{figure}
@@
 
-\subsection{State and Parameter Estimates}
-To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
+\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
 Each realisation consisted of 300 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
@@
 \section{Discussion}
-
 \begin{itemize}
 	\item if we don't know the frequency analysis or the system is marginally sampled or under-sampled, the best we can do is have the basis functions the same as the sensor kernel.
+\wtf{why wouldn't it be better to have, say, twice as many basis functions as we have sensors, at half the width?}
 	\item alternatives to frequency analysis are model selection...
-	\item the width of the connectivity basis functions here is known exactly. In practice we don't 
+\wtf{This frequency analysis \emph{is} model selection.
+Maybe what's meant here is that other model selection approaches could be applied?
+Some sort of IC optimisation?}
+	\item the width of the connectivity basis functions \wtf{do you mean width of the kernel?
+I'm not sure about this - as the parameters increase the kernel width increases right?
+So maybe you mean the basis functions, but don't we estimate these widths from the frequency analysis?} here is known exactly.
+In practice we don't
 	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.
-	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. 
-	\item The size of the dentritic arbour is consistent in the cortex.
+\wtf{Unless you are going to specify the computational complexity, in terms of the number of basis functions, it might be better to say something like ``there is a relationship between the number of basis functions that represent the field and the computational complexity of the estimation algorithm - the more basis functions the longer it takes to estimate''}
+	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. \omg{hell yes. This should be front and centre!} 
+	\item The size of the dentritic arbour is consistent in the cortex. \omg{?} 
 	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing. 
 	\item The flexibility of the approach 
-	\item Combining this method with other to incorporate longer range hetrogeneous connectivity.	
-	\item The need for activity to perform estimation.
+	\item Combining this method with other to incorporate longer range hetrogeneous connectivity. \omg{awesome} 
+	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
 \end{itemize}
@@
 \appendix 
-\section{Discrete Time Model}\label{Time Discretization}
-To form the IDE neural field model a time discretization must be perform. We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by
-\begin{equation}\label{Euler Approximation}	
-\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =   -\zeta v\left( \mathbf{r},t \right) + \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
+\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretization must be perform.
+We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by
+\begin{equation}
+	\label{Euler Approximation} \frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} = -\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
 \end{equation}
 For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging Eq.~\ref{Euler Approximation} we get 
-\begin{eqnarray}\label{Euler Approximation}	
-v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
+\begin{eqnarray}
+	\label{Euler Approximation} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
 \end{eqnarray}
 The discrete time form of the model is 
-\begin{equation}\label{Discrete Time Model1}
-	v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right),
+\begin{equation}
+	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right),
 \end{equation}
 where $\xi = 1 - T \zeta$. 
- \section{Numerical Simulation of IDE Model}\label{Space Discretization}
-To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
-\begin{equation}\label{discrete space}
-	v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T_s \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
+\section{Numerical Simulation of IDE Model}\label{Space Discretization} To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
+\begin{equation}
+	\label{discrete space} v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T_s \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
 \end{equation}
-where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$.
-We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects.
-\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
-Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}\label{ReducingState}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
+\begin{eqnarray}
+	\label{ReducingState} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
@@
 Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+\begin{eqnarray}
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
 \end{eqnarray}
-\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition}
-Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}\label{StartofReduction}
-	\int_\Omega  {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega  {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega  {\boldsymbol{\psi}  \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
+\begin{eqnarray}
+	\label{StartofReduction} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
 	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
@@
 Substituting Eq.~\ref{DefGamma} into Eq.~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{eqnarray}\label{Homogeneous SS Model}
-	\mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+\begin{eqnarray}
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 	\begin{equation}
- \mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega  {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}
-\label{eq:AppendixWt}
+		\mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} \label{eq:AppendixWt} 
 	\end{equation}
@@
 \end{lemma}
-\section*{Proof}
- Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
+\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
 \begin{eqnarray}
@@
 \end{eqnarray}
+
 % \end{proof}
@@
 \begin{equation}
- \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\zeta T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
-\label{eq:statespacemodel}
+	\mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\zeta T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r \label{eq:statespacemodel}
 \end{equation}
@@
 \begin{equation}
- \left[\begin{array}{{cccc}} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{array}\right]
-	-\left[\begin{array}{cccc} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{array}\right]
-	=T_s\left[\begin{array}{cc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
-	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \zeta\end{array}\right]+T_s
-		\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
+	\left[
+	\begin{array}{cccc}
+		\mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}
+	\end{array}
+	\right] -\left[
+	\begin{array}{cccc}
+		\mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}
+	\end{array}
+	\right] =T_s\left[
+	\begin{array}{cc}
+		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
+		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
+	\end{array}
+	\right] \left[
+	\begin{array}{cc}
+		\boldsymbol{\theta} \\
+		\zeta
+	\end{array}
+	\right]+T_s \left[
+	\begin{array}{cccc}
+		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
+	\end{array}
+	\right] 
 \end{equation}
@@
 \begin{equation}
- \mathbf Z=\left[\begin{array}{cccc} \mathbf x_{1}-\mathbf x_{0}\\
+	\mathbf Z=\left[
+	\begin{array}{cccc}
+		\mathbf x_{1}-\mathbf x_{0}\\
 		\mathbf x_{2}-\mathbf x_{1}\\\vdots\\
-\mathbf x_{n}-\mathbf x_{n-1}\end{array}\right],\quad \mathbf X=T_s\left[\begin{array}{cccc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\
-\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
-,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \zeta\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
+		\mathbf x_{n}-\mathbf x_{n-1}
+	\end{array}
+	\right],\quad \mathbf X=T_s\left[
+	\begin{array}{cccc}
+		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\
+		\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
+		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
+	\end{array}
+	\right] ,\quad \mathbf W=\left[
+	\begin{array}{cc}
+		\boldsymbol{\theta} \\
+		\zeta
+	\end{array}
+	\right],\quad \boldsymbol \xi=T_s\left[
+	\begin{array}{cccc}
+		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
+	\end{array}
+	\right] 
 \end{equation}
@@
 \section{Parameters} 
-\begin{tabular} {c|c} 
-	\hline\hline
-	Symbol & Description \\ \hline
-	$v(\mathbf{r},t)$ & mean membrane potential \\
+\begin{tabular}
+	{c|c} \hline\hline Symbol & Description \\
+	\hline $v(\mathbf{r},t)$ & mean membrane potential \\
 	$g(\mathbf{r},t)$ & average action potential rate \\
@@
 \end{tabular}
-
-\begin{tabular}{c|c}
-	\hline\hline
-	Symbol & Description \\ \hline
-	$\Delta_s$ & Distance between adjacent sensors \\
+\begin{tabular}
+	{c|c} \hline\hline Symbol & Description \\
+	\hline $\Delta_s$ & Distance between adjacent sensors \\
 	$\rho$ & Over-sampling parameter \\
@@
 % \end{thebibliography}
-
 \end{document}

### 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes 'utilised' to 'used' in the spec anal section. And everywhere else I fucking see it. Will commit, individually, every change of "utilise" to "use" when it's used inappropriately. And will swear a lot while doing it. Utilise means to use an object in a role it was not intended. "She utilised a biro to damage the hands of her collaborators every time they misused the word 'utilise' because they thought it sounded more engineering-y". We "use" frequency analysis to find out stuff about our system, just like everyone else!

@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was utilised to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
 Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.

### 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
making a few compressive changes to the spectral section. Got to line 246 before having to stop.

@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}.
-Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
+\section{Spectral Analysis and Model Selection}
+\label{SpectralAnalysisSection}
 
-The spectral characteristics of the field are governed by the shape of the connectivity kernel or the covariance of the field disturbance.
-If the bandwidth of the field disturbance covariance was wider than the bandwidth of the connectivity kernel, then the disturbance governs the bandwidth of the system.
-Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth.
-Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.
+Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}.
+Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
 
-Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
-Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and the spatially coloured covariance functions \todo{~cite\{some EEG literature here\}}.
-Thus the spectral response $V_t(\boldsymbol{\nu})$ is usually band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
-Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
+The spectral characteristics of the field are governed by the shape of the connectivity kernel and the covariance of the field disturbance.
+If the bandwidth of the field disturbance covariance is wider than the bandwidth of the connectivity kernel, then the disturbance covariance governs the bandwidth of the system.
+Conversely, a wider kernel bandwidth will govern the system bandwidth.
+\wtf{this bit incites trouble: Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.}
+
+Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
+Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}}.
+Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
+Note that for the 3-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
 Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy

### 2010-04-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added figure for experimental design and some small paper edits

@@
 
-Unfortunately, the use of these models in the clinic has been limited, since the neural field model are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient specific causes.
+Unfortunately, the use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient specific causes.
 Patient specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
@@
 The interconnected brain regions are modelled by the Jansen and Ritt equations.
-Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the Wilson-Cowan neural field equations \cite{schiff2008kalman}.
-This work takes a more system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
+This work takes a system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
 Generating patient specific models allows the application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
-Currently available epileptic seizure prediction and control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
+Currently available epileptic seizure  control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
 That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neurodynamics and information about their particular pathologies.
@@
 %Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
-\section{Neural Field Model}\label{NeuralModelSection}
-
-In this section, we describe a variant of the Wilson and Cowan neural field model \cite{Wilson1973} that will be used to create our intracortical connectivity estimator.
+\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
 This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
@@
 \end{equation}
-The post-synaptic response kernel $h(t)$ is described by \todo{citation needed} 
+The post-synaptic response kernel $h(t)$ is described by \todo{citation needed} \omg{this is about the most vanilla bit} 
 \begin{equation}
@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}
-\label{SpectralAnalysisSection}
-
-Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}.
 Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
@@
 	\begin{center}
-		\includegraphics[scale=0.2]{./Graph/kernel.pdf} 
+		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.jpg} 
 	\end{center}

### 2010-04-17 src/ODE_ex.py

@@ -48,7 +48,7 @@ symmetricobslocation_units = nonsymmetric_obs_location_units + offset + observat
 
 observation_locs_mm = symmetricobslocation_units*spacestep - field_width/2.
 print observation_locs_mm
-ny= len(observation_locs_mm);
+ny = len(observation_locs_mm)**2;
 
 Sensorwidth =0.9**2 #1.2**2 #equals to 1.5mm
 S_obs= observation_locs_mm
@@ -68,6 +68,7 @@ Ts = 1/Fs   #sampling period, second
 t_end = .2 # seconds
 NSamples = t_end*Fs;
 T = pb.linspace(0,t_end,NSamples);
+
 #--------------model and simulation------------------
 model=IDE(k,f_space,EEG_signals,act_func,alpha,field_noise_variance,beta_variance,obs_noise_covariance,spacestep,Ts)
 model.gen_ssmodel()

### 2010-04-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Frequency analysis derivation

--- 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
-The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by
-\begin{equation}
+The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
+\begin{equation}\label{eq:GaussianFT}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{equation}
+where 
+\begin{equation}\label{eq:GaussianFTWidth}
 	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
 \end{equation}
-The relationship between the Fourier transform and the basis function width is 
-\begin{equation}
-	1234 
+width $\sigma^2_{\nu}$ should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_c$ giving
+\begin{equation}\label{eq:WidthFrequencyRelationship}
+ \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
 \end{equation}
-Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $. Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in Appendix
+% Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
 

### 2010-04-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
adding field basis function definition and the appendix for frequency analysis

@@
 
-\section{Derivation of Finite Dimensional State-Space Model} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions.
+\section{Derivation of Finite Dimensional State-Space Model} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
+\begin{equation}\label{eq:FieldBasisFunction}
+	\phi\left(\mathbf{r}-\mathbf{r}'\right) =
+\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
+\end{equation}
  Decomposition allows a continuous field to be represented by a finite dimensional state vector.
@@
 \end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $. Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in Appendix
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $.
+Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in \ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
@@
 \end{eqnarray}
+\section{Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} }\label{ap:FrequencyAnalysis}
+Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to an \textit{n}-dimensional Gaussian centered at the origin yields
+\begin{eqnarray}
+ G(\boldsymbol \nu)&=&\int_{\mathcal R^n}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r \nonumber \\
+&=&\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
+&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right)
+\end{eqnarray}
+and 
+\begin{equation}\label{eq:IntegralOfGaussian}
+\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}
+\end{equation}
+which gives another scaled  Gaussian 
+\begin{equation}
+   \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right)
+\end{equation}
+substituting $\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}$ gives 
+\begin{equation}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{equation}
+and hence completing the proof. For 3 dB attenuation at $\boldsymbol\nu_c$ we need to set
+\begin{eqnarray}
+ |\boldsymbol\Phi(\boldsymbol\nu_c)|^2&=&\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{n}\mathrm{exp}\left(-\frac{2}{\sigma_{\nu}^2}\boldsymbol\nu_c^\top \boldsymbol\nu_c\right)\\
+&=&\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
+\end{eqnarray}
+solving for $\sigma_{\nu}^2$ we get
+\begin{equation}
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2 }.
+\end{equation}
 
-% \end{proof}
 \section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix} 

### 2010-04-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
more figures for freq analysis
updates to figures

@@
 %<-comment out this for checking equations
-\usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig} 
+\usepackage{graphicx,epsfig}
+\usepackage{algorithm, algorithmicx, algpseudocode} 
 \usepackage{color} 
@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.jpg} 
-	\end{center}
-	\caption{Example of experimental design and model output.
+% \begin{figure}
+% 	\begin{center}
+		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
+% 	\end{center}
+% 	\caption{Example of experimental design and model output.
 \textbf{A}.
@@
 Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
-\end{figure}
+% \end{figure}
 
@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
+
 \begin{figure}
 	\begin{center}
-		\subfigure[][]{
-		\includegraphics[scale=0.2]{./Graph/kernel.pdf}} \subfigure[][]{
-		\includegraphics[scale=0.2]{./Graph/field.pdf}} \subfigure[][]{
-		\includegraphics[scale=0.2]{./Graph/filtered.pdf}} 
+		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
 	\end{center}
-	\caption{Example of experimental design and model output.
-\textbf{A}.
-Example of the neural field with sensors.
-The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
-\textbf{B} Example of data generated by the model through the observations.
-\textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:ExampleFieldAndSensorsDataAndPSD}
+	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:ExampleFieldAndSensorsDataAndPSD} 
 \end{figure}

### 2010-04-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to figures

@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
-
-\begin{figure}
+\begin{figure*}
 	\begin{center}
@@
 	\end{center}
-	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:ExampleFieldAndSensorsDataAndPSD} 
-\end{figure}
+	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
+\end{figure*}
 Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.

### 2010-04-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to figures
making sure I am up to date

@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-% \begin{figure}
-% 	\begin{center}
+\begin{figure}
+	\begin{center}
 		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
-% 	\end{center}
-% 	\caption{Example of experimental design and model output.
+	\end{center}
+	\caption{Example of experimental design and model output.
 \textbf{A}.
@@
 Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
-% \end{figure}
+\end{figure}
 
@@
 \end{eqnarray}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{Poo} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{ } and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
 \begin{eqnarray}

### 2010-04-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
equation 17 correction adding t+1
equation 15 correction multiplying zeta by sampling time
equation 17 correction multiplying zeta by sampling time
paper updates

@@
 \usepackage{iopams,setstack} 
-
 %<-comment out this for checking equations
@@
 \usepackage[tight,scriptsize]{subfigure}
-
+\usepackage{pstool}
 %\renewcommand{\subcapsize}{\small}
@@
 
-\section{Introduction} This paper presents a framework for creating patient specific macroscopic neural field continuum mathematical models.
-\todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph.
+\section{Introduction} This paper presents a theoretical framework for estimating patient specific macroscopic neural field continuum mathematical models from data.
+The ability to estimate such models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
+For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
+In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+
+In addition, parameter estimation may have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms \omg{(ref, Frank Marten)}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+\omg{I extended this bit I am not sure how to connect it with the rest.} \todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph.
 Otherwise this first sentence looks a little out of place.}
@@
 \begin{equation}
-	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right). 
+	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right)^{\top} \boldsymbol{\theta}
 \end{equation}
@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
-\begin{figure*}
-	\begin{center}
-		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
-	\end{center}
-	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
-\end{figure*}
+
+\psfragfig{./Graph/FreqAnalysis}
+
+% \begin{figure*}
+% 	\begin{center}
+% 		\include{FreqAnalysis.tex}
+% 		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
+% 	\end{center}
+% 	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
+% \end{figure*}
 Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.

### 2010-04-27 src/ODE_ex.py

@@ -9,7 +9,7 @@ from scipy import io
 field_width=40;                        # -20 to 20 mm, twice the estimated field, # must be EVEN!!!
 observedfieldwidth = field_width/2;    # mm, -field_width/4 to field_width/4 
 dimension=2;
-spacestep=0.5;
+spacestep=1;
 steps_in_field = field_width/spacestep + 1;
 
 Delta = 1./spacestep;
@@ -69,7 +69,7 @@ pb.show()
 # -------Sampling properties-------------
 Fs = 1e3   #sampling rate                                       
 Ts = 1/Fs   #sampling period, second
-t_end = .2 # seconds
+t_end = .5 # seconds
 NSamples = t_end*Fs;
 T = pb.linspace(0,t_end,NSamples);
 

### 2010-04-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
change equation 14 and 15, excluded Ts from 19, got rid of extera Appendix C and change notation to Least square method and made a bit tidy

--- 2010-04-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
-\begin{equation}
+\begin{equation}\label{eq:FieldCovarianceFunction}
 	cov(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ 
@@
 The connectivity kernel can also be considered a decomposition into a set of basis functions in
-\begin{equation}
-	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right). 
+\begin{equation}\label{DefKernelDecomp}
+	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right)^\top \boldsymbol{\theta}.
 \end{equation}
@@
 \begin{equation}
-	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\boldsymbol{\theta}^{\top}\int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'} - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\int_\Omega { f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right)^\top d\mathbf{r}'}\boldsymbol{\theta} - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
 \end{equation}
@@
 \begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
-	\mathbf{Q}\left(\mathbf{x}_t\right) &=& T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t 
+\end{eqnarray}
+\begin{eqnarray}\label{eq:QMatrix}
+	\mathbf{Q}\left(\mathbf{x}_t\right) &=& \boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
@@
 \begin{eqnarray}
-	\label{ReducingState} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
-	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
-\end{eqnarray}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{ } and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
-	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
-\end{eqnarray}
-\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
-\begin{eqnarray}
 	\label{StartofReduction} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
@@
 \begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{lemma}
-	Consider the zero-mean process $e_t\left(\mathbf r\right)$ with covariance as defined by (\ref{eq:FieldCovariance}) then 
+	Consider the zero-mean process $e_t\left(\mathbf r\right)$ with covariance as defined by \ref{eq:FieldCovarianceFunction} then 
 	\begin{equation}
@@
 \section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix} 
-\begin{equation}
-	\mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\zeta T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r \label{eq:statespacemodel}
-\end{equation}
-where the matrix $\mathbf Q_{n_x \times n_{\boldsymbol{\theta}}}(\mathbf x_t)$ is defined as 
-\begin{equation}
-	Q_{n_x \times n_{\boldsymbol{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
-\end{equation}
-and $T_s$ is the sampling period. Least Square method can be used as (\ref{eq:statespacemodel}) is linear in parameters. At each time instant we have 
+The state equation given in \ref{Homogeneous SS Model} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters.
+Using  \ref{Homogeneous SS Model} and \ref{eq:QMatrix} by substituting  $\xi = 1-\zeta T_s$ at each time instant we can write
 \begin{eqnarray}
-	\mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
-	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
+	\mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+\mathbf e_0 \nonumber \\
+	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+\mathbf e_1\nonumber\\
 	&\vdots& \nonumber\\
-	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1} 
+	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+\mathbf e_{n-1} 
 \end{eqnarray}
@@
 	\end{array}
-	\right]+T_s \left[
+	\right]+\left[
 	\begin{array}{cccc}
@@
 	\end{array}
-	\right] ,\quad \mathbf W=\left[
+	\right] 
+\end{equation}
+and
+\begin{equation}
+\quad \mathbf W=\left[
 	\begin{array}{cc}
@@
 	\end{array}
-	\right],\quad \boldsymbol \xi=T_s\left[
+	\right],\quad \boldsymbol \xi=\left[
 	\begin{array}{cccc}
@@
 \end{equation}
-using the method of Least Square $ \mathbf W$ can be estimated 
+using the LS method $ \mathbf W$ can be estimated 
 \begin{equation}

### 2010-04-28 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
its just a check
paper updates

--- 2010-04-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \usepackage[tight,scriptsize]{subfigure}
-\usepackage{pstool}
-%\renewcommand{\subcapsize}{\small}
+% \usepackage{pstool}
+\renewcommand{\subcapsize}{\small}
 % \usepackage{anysize}							%<-use this for checking equation length
@@
 % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-% \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
+\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
@@
 
-The work from Schiff and Sauer \cite{schiff2008kalman} successfully demonstrated it is possible to estimate parameters \wtf{what kind of parameters?} from the WC equations.
+The work from Schiff and Sauer \cite{schiff2008kalman} successfully demonstrated it is possible to perform state estimation of modified WC equations.
 This motivates the question, what parameters are the most important?
@@
 \end{equation}
-
 %Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. 
 By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model 
-\begin{equation}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'.
-\end{equation}
+\begin{eqnarray}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =  \int_{-\infty}^t h\left(t - t'\right) \\
+	\times\left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'. 
+\end{eqnarray}
 To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function 
@@
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{equation}
-	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
-\end{equation}
+\begin{eqnarray}
+	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \\
+	\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right). 
+\end{eqnarray}
 To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see~\ref{Time Discretization}) giving 
-\begin{equation}
-	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
-\end{equation}
+\begin{eqnarray}
+	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \\
+	+ T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right), 
+\end{eqnarray}
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
@@
 Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{equation}
-	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\boldsymbol{\theta}^{\top}\int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'} - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
-\end{equation}
+\begin{eqnarray}
+	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\int_\Omega { f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right)^{\top}d\mathbf{r}'}\boldsymbol{\theta} \\
+	- \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right). 
+\end{eqnarray}
 By defining the term 
@@
 \begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& T_sq(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	&=& T_sQ\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
 	\mathbf{Q}\left(\mathbf{x}_t\right) &=& T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
@@
 
-\psfragfig{./Graph/FreqAnalysis}
+% \psfragfig{./Graph/FreqAnalysis}
 

### 2010-04-28 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-04-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}
+
+% \begin{document}
 
@@
 Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{equation}
-	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\int_\Omega { f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right)^\top d\mathbf{r}'}\boldsymbol{\theta} - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
-\end{equation}
+\begin{eqnarray}
+	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\int_\Omega { f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right)^{\top}d\mathbf{r}'}\boldsymbol{\theta} \\
+	- \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right). 
+\end{eqnarray}
 By defining the term 

### 2010-04-28 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
sharpned up the intro of the paper

@@
 Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations, marking a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
@@
 
-The work from Schiff and Sauer \cite{schiff2008kalman} successfully demonstrated it is possible to perform state estimation of modified WC equations.
-This motivates the question, what parameters are the most important?
-How patient specific do the assumed parameters have to be for the model to be useful?
-In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modelling of the human neocortex.
-\wtf{not sure about rhetorical questions as a narrative mechanism in general, also not sure how this paper addresses these particular questions.} \omg{Maybe the next section addresses that the connectivity is important.
-Needs sharpening.}
-
-\section{The Importance of Cortical Structure} Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
-Each neural population represents a functional cortical processing unit, referred to as a column.
-The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
-Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
-
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
-
-Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
-Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
-
-%Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
+This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher dimensional systems utilising a systematic model reduction procedure.
+In addition, a method is presented for estimating the the connectivity structure and the synaptic time constant.
 Until now, estimation of local intracortical connectivity structure has not been attempted.
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (ECoG recording electrodes in this case).
+The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modelling the neural dynamics within this framework has the distinct advantage over multivariate AR models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
+Modelling the neural dynamics within this framework has the distinct advantage over multivariate auto-regressive (AR) models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
 
-%Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
+The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
+Next, a reduced finite dimensional neural field model is derived in Section~\ref{ReducedModelSection}.
+The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
+Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominate dynamics of the neural field can be represented by the reduced model.
+Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
+The results for the spatial frequency analysis and parameter estimation are then presented in Section~\ref{ResultsSection}.
+The implications and limitations of this framework are discussed in Section~\ref{DiscussionSection} along with planned future developments.
+Finally, we provide concluding remarks in Section~\ref{ConclusionSection}.
+
 \section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
-This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
+Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
+They are popular due to being parsimonious yet having a strong link with the underlying physiology.
+Each neural population represents a functional cortical processing unit, such as a column.
+The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
+Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
 \begin{todo}
@@
 \end{todo}
-The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
 
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 
-\section{Derivation of Finite Dimensional State-Space Model} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
+\section{Derivation of Finite Dimensional State-Space Model}\label{ReducedModelSection} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
+\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
 All parameters for the model are given in table~\ref{}.
@@
 
-\section{Discussion}
+\section{Discussion}\label{DiscussionSection}
 \begin{itemize}
@@
 	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
+	\item Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
+	\item Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
+Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
+	\item Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not estimated using DTI
 \end{itemize}
 
-\section{Conclusion} 
+\section{Conclusion}\label{ConclusionSection}
 \appendix 

### 2010-04-28 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
general paper edits

@@
 %<-comment out this for checking equations
-\usepackage{graphicx,epsfig}
+\usepackage{graphicx}
 \usepackage{algorithm, algorithmicx, algpseudocode} 
@@
 
-\section{Introduction} This paper presents a theoretical framework for estimating patient specific macroscopic neural field continuum mathematical models from data.
+\section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field  mathematical models from patient specific data.
 The ability to estimate such models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 
-In addition, parameter estimation may have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms \omg{(ref, Frank Marten)}.
+Parameter estimation may have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{marten2009derivation}.
 These very different mechanisms would require very different medications for successful treatment.
@@
 Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-\omg{I extended this bit I am not sure how to connect it with the rest.} \todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph.
-Otherwise this first sentence looks a little out of place.}
-
-The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
+\omg{I extended this bit I am not sure how to connect it with the rest.
+Maybe the next paragraph can go.}
+% 
+% The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
 Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
-While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a mystery.
-Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a theoretical.
+Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008} \cite{David2003} for recent reviews).
@@
 The interconnected brain regions are modelled by the Jansen and Ritt equations.
-Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
+Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
 This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations, marking a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
-Generating patient specific models allows the application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
 Currently available epileptic seizure  control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
-That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neurodynamics and information about their particular pathologies.
+That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neuro-dynamics and information about their particular pathologies.
 Given access to an accurate model, the application of optimal control theory in these circumstances would allow for robust therapeutic stimulations.
@@
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
+The key development in that work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observations (recording electrodes in this case).
+In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
 Modelling the neural dynamics within this framework has the distinct advantage over multivariate auto-regressive (AR) models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
@@
 \end{equation}
-%Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. 
+The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations.
+The parameter $\varsigma$ governs the slope of the sigmoid.
 By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
@@
 \end{eqnarray}
-To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
 \begin{eqnarray}
@@
 \end{equation}
-This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
+This term was added to account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
 \begin{equation}
@@
 \section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
-All parameters for the model are given in table~\ref{}.
-An example of the simulated field can be seen in figure~\ref{}~A.
+All parameters for the model are given in Table~\ref{tab:Model Parameters}.
+An example of the simulated field can be seen in figure~\ref{fig:experimental design}~A.
 The Figure demonstrates the experimental design where the sensors were placed in the centre of the field (full width at half maximum).
 This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
-Figure~\ref{}~B.
-shows example data from the sensors of the model, and figure~\ref{}~C.
+Figure~\ref{fig:experimental design}~B.
+shows example data from the sensors of the model, and figure~\ref{fig:experimental design}~C.
 shows the power spectral density of on of the simulated time-series.
@@
 
-The sensors were modelled such that they were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
+\begin{center}
+\begin{tabular}{c|c|c}	
+	\hline\hline Symbol & Value & Units \\
+	\hline\hline
+	$\zeta$ & 0.01 & ms$^{-1}$\\
+	$f_{max}$ & 20 & spikes/s \\
+	$\varsigma$ & 0.8 & spike/mV\\
+	$v_0$ & 2 & mV\\
+	\hline\hline
+\end{tabular}\label{tab:Model Parameters}
+\end{center}
+
+The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
-Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field.
+Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field.
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
-	\end{center}
-	\caption{Example of experimental design and model output.
+% \begin{figure}\label{fig:experimental design}
+% 	\begin{center}
+% 		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
+% 	\end{center}
+% 	\caption{Example of experimental design and model output.
 \textbf{A}.
@@
 
-% \begin{figure*}
-% 	\begin{center}
-% 		\include{FreqAnalysis.tex}
-% 		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
-% 	\end{center}
-% 	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
-% \end{figure*}
+\begin{figure*}
+	\begin{center}
+		\includegraphics[scale=0.5, angle=-90]{./Graph/FreqAnalysis.pdf}
+	\end{center}
+	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
+\end{figure*}
 Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
@@
 \begin{eqnarray}
-	\label{Euler Approximation} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
+	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
 \end{eqnarray}

### 2010-04-28 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to figures

@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-% \begin{figure}\label{fig:experimental design}
-% 	\begin{center}
-% 		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
-% 	\end{center}
-% 	\caption{Example of experimental design and model output.
+\begin{figure}\label{fig:experimental design}
+	\begin{center}
+		\includegraphics[scale=0.6]{./Graph/ExperimentFigure.pdf} 
+	\end{center}
+	\caption{Example of experimental design and model output.
 \textbf{A}.

### 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
the state estimationsection is clarified

@@
 The state estimation technique utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 An approximation of the state density is made by propagating the so-called sigma points through the state-space model.
@@
 The sigma vectors $\mathcal X_i$ are calculated by
-\begin{equation}
+\begin{equation}\label{eq:sigmapoints1}
 	\mathcal X_{0}=\bar x 
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{eq:sigmapoints2}
 	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L 
 \end{equation}
-where $L$ is the dimension of the state space and the number of sigma points is $2L+1$. The scaling parameter $\lambda$ is defined as 
-\begin{equation}
+where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the ith column of the weighted matrix squre root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
+The total number of sigma points is $2L+1$.
+The scaling parameter $\lambda$ is defined as
+\begin{equation}\label{eq:sigmapoints3}
 	\lambda=\alpha^2( L+\kappa)- L 
@@
 These sigma points propogated through the nonlinear function
-The update step equations are the same as the standard Kalman filtering formulations.
+Since the observation equation \ref{ObservationEquation} is linear the update step equations are simplified to the standard Kalman filtering formulations.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
@@
 A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
+It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used.
+This reduces the dimension and the number of sigma points used in the algorithm.
 \begin{algorithm}
@@
 		\State Forward iteration For $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		\begin{equation*}
-			\mathcal X_t^f=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^{f}-\gamma\sqrt{\mathbf P_t^f}] 
-		\end{equation*}
-		Propagate the sigma points through the state equation 
+
+		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
+% 		\begin{equation*}
+% 			\mathcal X_t^f=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^{f}-\gamma\sqrt{\mathbf P_t^f}] 
+% 		\end{equation*}
+
+% 		propagate the sigma points through the state equation 
 		\begin{equation}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_t^f,u_t) 
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f,u_t) 
 		\end{equation}
+
+		calculate the predicted mean and the predicted covariance matrix
 		\begin{equation*}
@@
 		\end{equation*}
+
+		compute the filter gain, the update mean and the update covariance matrix using the standard kalman filter formulations
 		\begin{equation*}
@@
 		\State Backward iteration For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $
-		\begin{equation*}
-			\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}] 
-		\end{equation*}
-		\State Calculate sigma points for the smoother $\mathcal X_{i,t+1}^{b-}$ and compute 
+
+calculate the sigma points $\mathcal X_{i,t}^b$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
+		\begin{equation}
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b,u_t) 
+		\end{equation}
+% 		\begin{equation*}
+% 			\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}] 
+% 		\end{equation*}
+		\State compute the predicted mean, the predicted covariance matrix and the cross-covariance matrix
 		\begin{equation*}

### 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
minor tweaks

--- 2010-04-28 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \usepackage{iopams,setstack}
+
 %<-comment out this for checking equations
-\usepackage{graphicx}
+\usepackage{graphicx,epsfig}
 \usepackage{algorithm, algorithmicx, algpseudocode} 
@@
 \usepackage[tight,scriptsize]{subfigure}
-% \usepackage{pstool}
-\renewcommand{\subcapsize}{\small}
+
+%\renewcommand{\subcapsize}{\small}
 % \usepackage{anysize}							%<-use this for checking equation length
@@
 % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
+% \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
 \newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
@@
 \newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}
-
-% \begin{document}
 
@@
 
-\section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field  mathematical models from patient specific data.
-The ability to estimate such models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+\section{Introduction} This paper presents a framework for creating patient specific macroscopic neural field continuum mathematical models.
+\todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph.
+Otherwise this first sentence looks a little out of place.}
 
-Parameter estimation may have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{marten2009derivation}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-\omg{I extended this bit I am not sure how to connect it with the rest.
-Maybe the next paragraph can go.}
-% 
-% The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
+The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
 Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a mystery.
+Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
-While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a theoretical.
-Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008} \cite{David2003} for recent reviews).
@@
 The interconnected brain regions are modelled by the Jansen and Ritt equations.
-Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations, marking a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+Another recent publication describing a parameter estimation method with a neural field model used an Unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
+This work takes a system theoretic approach to the neural estimation problem and marks a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
+Generating patient specific models allows the application of a range of techniques from control systems theory, where tailored electrical stimulation could be used therapeutically in a closed loop fashion.
 Currently available epileptic seizure  control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
-That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neuro-dynamics and information about their particular pathologies.
+That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neurodynamics and information about their particular pathologies.
 Given access to an accurate model, the application of optimal control theory in these circumstances would allow for robust therapeutic stimulations.
 
-This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher dimensional systems utilising a systematic model reduction procedure.
-In addition, a method is presented for estimating the the connectivity structure and the synaptic time constant.
+The work from Schiff and Sauer \cite{schiff2008kalman} successfully demonstrated it is possible to estimate parameters \wtf{what kind of parameters?} from the WC equations.
+This motivates the question, what parameters are the most important?
+How patient specific do the assumed parameters have to be for the model to be useful?
+In this paper, we address both of these questions and provide a theoretical platform to perform patient-specific grey-box modelling of the human neocortex.
+\wtf{not sure about rhetorical questions as a narrative mechanism in general, also not sure how this paper addresses these particular questions.} \omg{Maybe the next section addresses that the connectivity is important.
+Needs sharpening.}
+
+\subsection{The Importance of Cortical Structure}
+
+Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+Each neural population represents a functional cortical processing unit, referred to as a column.
+The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
+In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
+Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
+
+Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
+
+Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
+Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
+
+%Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
 Until now, estimation of local intracortical connectivity structure has not been attempted.
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development in that work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observations (recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
-Modelling the neural dynamics within this framework has the distinct advantage over multivariate auto-regressive (AR) models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
+The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (ECoG recording electrodes in this case).
+In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
+Modelling the neural dynamics within this framework has the distinct advantage over multivariate AR models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
 
-The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Next, a reduced finite dimensional neural field model is derived in Section~\ref{ReducedModelSection}.
-The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominate dynamics of the neural field can be represented by the reduced model.
-Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
-The results for the spatial frequency analysis and parameter estimation are then presented in Section~\ref{ResultsSection}.
-The implications and limitations of this framework are discussed in Section~\ref{DiscussionSection} along with planned future developments.
-Finally, we provide concluding remarks in Section~\ref{ConclusionSection}.
+%Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
+\section{Neural Field Model}
+\label{NeuralModelSection}
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
-Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
-They are popular due to being parsimonious yet having a strong link with the underlying physiology.
-Each neural population represents a functional cortical processing unit, such as a column.
-The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
-Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
+In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
+This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
 \begin{todo}
@@
 \end{todo}
+The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.
 
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
+\subsection{Derivation of the Integro-difference Equation Representation}
+
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 \end{equation}
-The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations.
-The parameter $\varsigma$ governs the slope of the sigmoid.
+
+%Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. 
 By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model 
-\begin{eqnarray}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =  \int_{-\infty}^t h\left(t - t'\right) \\
-	\times\left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'. 
-\end{eqnarray}
+\begin{equation}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) = \int_{-\infty}^t h\left(t - t'\right) \left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'.
+\end{equation}
 To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function 
@@
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{eqnarray}
-	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \\
-	\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right). 
-\end{eqnarray}
-To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
-\begin{eqnarray}
-	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \\
-	+ T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right), 
-\end{eqnarray}
+\begin{equation}
+	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right).
+\end{equation}
+To arrive at the integro-difference equation (IDE) form of the model we discretize time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+\begin{equation}
+	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right),
+\end{equation}
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
-\begin{equation}\label{eq:FieldCovarianceFunction}
+\begin{equation}
 	cov(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ 
@@
 \end{equation}
-This term was added to account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
+This term was added to drive the system and account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
 \begin{equation}
@@
 
-\section{Derivation of Finite Dimensional State-Space Model}\label{ReducedModelSection} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
+\subsection{Derivation of Finite Dimensional State-Space Model}
+
+In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 The connectivity kernel can also be considered a decomposition into a set of basis functions in
-\begin{equation}\label{DefKernelDecomp}
-	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right)^\top \boldsymbol{\theta}.
+\begin{equation}
+	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right). 
 \end{equation}
@@
 Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{eqnarray}
-	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\int_\Omega { f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right)^{\top}d\mathbf{r}'}\boldsymbol{\theta} \\
-	- \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right). 
-\end{eqnarray}
+\begin{equation}
+	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\boldsymbol{\theta}^{\top}\int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)d\mathbf{r}'} - \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right).
+\end{equation}
 By defining the term 
@@
 \begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t 
-\end{eqnarray}
-\begin{eqnarray}\label{eq:QMatrix}
-	\mathbf{Q}\left(\mathbf{x}_t\right) &=& \boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
+	\label{Homogeneous SS Model} \mathbf{x}_t &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t \\
+	\mathbf{Q}\left(\mathbf{x}_t\right) &=& T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-An example of the simulated field can be seen in figure~\ref{fig:experimental design}~A.
+\section{Results} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
+All parameters for the model are given in table~\ref{}.
+An example of the simulated field can be seen in figure~\ref{}~A.
 The Figure demonstrates the experimental design where the sensors were placed in the centre of the field (full width at half maximum).
 This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
-Figure~\ref{fig:experimental design}~B.
-shows example data from the sensors of the model, and figure~\ref{fig:experimental design}~C.
+Figure~\ref{}~B.
+shows example data from the sensors of the model, and figure~\ref{}~C.
 shows the power spectral density of on of the simulated time-series.
@@
 
-\begin{center}
-\begin{tabular}{c|c|c}	
-	\hline\hline Symbol & Value & Units \\
-	\hline\hline
-	$\zeta$ & 0.01 & ms$^{-1}$\\
-	$f_{max}$ & 20 & spikes/s \\
-	$\varsigma$ & 0.8 & spike/mV\\
-	$v_0$ & 2 & mV\\
-	\hline\hline
-\end{tabular}\label{tab:Model Parameters}
-\end{center}
-
-The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
+The sensors were modelled such that they were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
-Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field.
+Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field.
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-% \begin{figure}\label{fig:experimental design}
+% \begin{figure}
 % 	\begin{center}
-% 		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
+		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
 % 	\end{center}
@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
-
-% \psfragfig{./Graph/FreqAnalysis}
-
 \begin{figure*}
 	\begin{center}
-		\includegraphics[scale=0.5, angle=-90]{./Graph/FreqAnalysis.pdf}
+		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
 	\end{center}
@@
 
-\section{Discussion}\label{DiscussionSection}
+\section{Discussion}
 \begin{itemize}
@@
 	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
-	\item Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
-	\item Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
-Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
-	\item Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not estimated using DTI
 \end{itemize}
 
-\section{Conclusion}\label{ConclusionSection}
+\section{Conclusion} 
 \appendix 
@@
 \begin{eqnarray}
-	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
+	\label{Euler Approximation} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
 \end{eqnarray}
@@
 \begin{eqnarray}
+	\label{ReducingState} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
+	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+\end{eqnarray}
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{ } and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+\begin{eqnarray}
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+\end{eqnarray}
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
+\begin{eqnarray}
 	\label{StartofReduction} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
@@
 \begin{eqnarray}
-	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
 	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
@@
 \begin{lemma}
-	Consider the zero-mean process $e_t\left(\mathbf r\right)$ with covariance as defined by \ref{eq:FieldCovarianceFunction} then 
+	Consider the zero-mean process $e_t\left(\mathbf r\right)$ with covariance as defined by (\ref{eq:FieldCovariance}) then 
 	\begin{equation}
@@
 \section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix} 
-The state equation given in \ref{Homogeneous SS Model} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters.
-Using  \ref{Homogeneous SS Model} and \ref{eq:QMatrix} by substituting  $\xi = 1-\zeta T_s$ at each time instant we can write
+\begin{equation}
+	\mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\zeta T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r \label{eq:statespacemodel}
+\end{equation}
+where the matrix $\mathbf Q_{n_x \times n_{\boldsymbol{\theta}}}(\mathbf x_t)$ is defined as 
+\begin{equation}
+	Q_{n_x \times n_{\boldsymbol{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
+\end{equation}
+and $T_s$ is the sampling period. Least Square method can be used as (\ref{eq:statespacemodel}) is linear in parameters. At each time instant we have 
 \begin{eqnarray}
-	\mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+\mathbf e_0 \nonumber \\
-	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+\mathbf e_1\nonumber\\
+	\mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
+	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
 	&\vdots& \nonumber\\
-	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+\mathbf e_{n-1} 
+	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1} 
 \end{eqnarray}
@@
 	\end{array}
-	\right]+\left[
+	\right]+T_s \left[
 	\begin{array}{cccc}
@@
 	\end{array}
-	\right] 
-\end{equation}
-and
-\begin{equation}
-\quad \mathbf W=\left[
+	\right] ,\quad \mathbf W=\left[
 	\begin{array}{cc}
@@
 	\end{array}
-	\right],\quad \boldsymbol \xi=\left[
+	\right],\quad \boldsymbol \xi=T_s\left[
 	\begin{array}{cccc}
@@
 \end{equation}
-using the LS method $ \mathbf W$ can be estimated 
+using the method of Least Square $ \mathbf W$ can be estimated 
 \begin{equation}

### 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Next, a reduced finite dimensional neural field model is derived in Section~\ref{ReducedModelSection}.
-The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominate dynamics of the neural field can be represented by the reduced model.
-Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
-The results for the spatial frequency analysis and parameter estimation are then presented in Section~\ref{ResultsSection}.
-The implications and limitations of this framework are discussed in Section~\ref{DiscussionSection} along with planned future developments.
-Finally, we provide concluding remarks in Section~\ref{ConclusionSection}.
+\subsection{The Importance of Cortical Structure}
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
-Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
-They are popular due to being parsimonious yet having a strong link with the underlying physiology.
-Each neural population represents a functional cortical processing unit, such as a column.
-The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
+Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
+Each neural population represents a functional cortical processing unit, referred to as a column.
+The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
+In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
 Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
+
+Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
+
+Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
+Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
+
+%Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
+Until now, estimation of local intracortical connectivity structure has not been attempted.
+Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
+The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (ECoG recording electrodes in this case).
+In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
+Modelling the neural dynamics within this framework has the distinct advantage over multivariate AR models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
+This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
+
+%Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
+\section{Neural Field Model}
+\label{NeuralModelSection}
+
+In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
+This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
 \begin{todo}
@@
 
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
+\subsection{Derivation of the Integro-difference Equation Representation}
+
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by

### 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
the state estimationsection is clarified

@@
 
-		calculate the predicted mean and the predicted covariance matrix
+		calculate the predicted state and the predicted covariance matrix
 		\begin{equation*}
@@
 
-		compute the filter gain, the update mean and the update covariance matrix using the standard kalman filter formulations
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard kalman filter formulations
 		\begin{equation*}
@@
 % 		\end{equation*}
-		\State compute the predicted mean, the predicted covariance matrix and the cross-covariance matrix
+		\State compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
 		\begin{equation*}

### 2010-05-01 src/ODE_ex.py
Figures with python

@@ -9,7 +9,7 @@ from scipy import io
 field_width=40;                        # -20 to 20 mm, twice the estimated field, # must be EVEN!!!
 observedfieldwidth = field_width/2;    # mm, -field_width/4 to field_width/4 
 dimension=2;
-spacestep=1;
+spacestep=0.5;
 steps_in_field = field_width/spacestep + 1;
 
 Delta = 1./spacestep;
@@ -54,7 +54,7 @@ print observation_locs_mm
 
 ny= (len(observation_locs_mm))**2;
 
-Sensorwidth =0.8**2 #1.2**2 #equals to 1.5mm
+Sensorwidth =0.9**2 #1.2**2 #equals to 1.5mm
 S_obs= observation_locs_mm
 
 obs_locns=gen_spatial_lattice(S_obs)

### 2010-05-01 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Figures with python
changes to paper

--- 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-\subsection{The Importance of Cortical Structure}
+The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
+Next, a reduced finite dimensional neural field model is derived in Section~\ref{ReducedModelSection}.
+The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
+Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominate dynamics of the neural field can be represented by the reduced model.
+Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
+The results for the spatial frequency analysis and parameter estimation are then presented in Section~\ref{ResultsSection}.
+The implications and limitations of this framework are discussed in Section~\ref{DiscussionSection} along with planned future developments.
+Finally, we provide concluding remarks in Section~\ref{ConclusionSection}.
 
-Neural field models relate mean firing rates of pre-synaptic neural populations to post-synaptic mean membrane potentials.
-Each neural population represents a functional cortical processing unit, referred to as a column.
-The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \cite{Jirsa2009} \cite{Qubbaj2007}.
+\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
+Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
+They are popular due to being parsimonious yet having a strong link with the underlying physiology.
+Each neural population represents a functional cortical processing unit, such as a column.
+The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
 Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \cite{Sullivan2006}.
-
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
-
-Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
-Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
-
-%Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).
-Until now, estimation of local intracortical connectivity structure has not been attempted.
-Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development in this work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of sensors (ECoG recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of this technique to neural fields.
-Modelling the neural dynamics within this framework has the distinct advantage over multivariate AR models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
-This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
-
-%Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not..
-\section{Neural Field Model}
-\label{NeuralModelSection}
-
-In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
-This model is descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
 \begin{todo}
@@
 
-\subsection{Derivation of the Integro-difference Equation Representation}
-
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 
-\subsection{Derivation of Finite Dimensional State-Space Model}
-
-In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
+\section{Derivation of Finite Dimensional State-Space Model}\label{ReducedModelSection} In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 The state estimation technique utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 An approximation of the state density is made by propagating the so-called sigma points through the state-space model.
@@
 The sigma vectors $\mathcal X_i$ are calculated by
-\begin{equation}\label{eq:sigmapoints1}
+\begin{equation}
 	\mathcal X_{0}=\bar x 
@@
 \end{equation}
-\begin{equation}\label{eq:sigmapoints2}
+\begin{equation}
 	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L 
 \end{equation}
-where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the ith column of the weighted matrix squre root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
-The total number of sigma points is $2L+1$.
-The scaling parameter $\lambda$ is defined as
-\begin{equation}\label{eq:sigmapoints3}
+where $L$ is the dimension of the state space and the number of sigma points is $2L+1$. The scaling parameter $\lambda$ is defined as 
+\begin{equation}
 	\lambda=\alpha^2( L+\kappa)- L 
@@
 These sigma points propogated through the nonlinear function
-Since the observation equation \ref{ObservationEquation} is linear the update step equations are simplified to the standard Kalman filtering formulations.
+The update step equations are the same as the standard Kalman filtering formulations.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
@@
 A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
-It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used.
-This reduces the dimension and the number of sigma points used in the algorithm.
 \begin{algorithm}
@@
 		\State Forward iteration For $t \in \left\lbrace 0,\cdots, T\right\rbrace $, 
-
-		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
-% 		\begin{equation*}
-% 			\mathcal X_t^f=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^{f}-\gamma\sqrt{\mathbf P_t^f}] 
-% 		\end{equation*}
-
-% 		propagate the sigma points through the state equation 
+		\begin{equation*}
+			\mathcal X_t^f=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^{f}-\gamma\sqrt{\mathbf P_t^f}] 
+		\end{equation*}
+		Propagate the sigma points through the state equation 
 		\begin{equation}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f,u_t) 
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_t^f,u_t) 
 		\end{equation}
-
-		calculate the predicted mean and the predicted covariance matrix
 		\begin{equation*}
@@
 		\end{equation*}
-
-		compute the filter gain, the update mean and the update covariance matrix using the standard kalman filter formulations
 		\begin{equation*}
@@
 		\State Backward iteration For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ 
-
-calculate the sigma points $\mathcal X_{i,t}^b$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
-		\begin{equation}
-			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b,u_t) 
-		\end{equation}
-% 		\begin{equation*}
-% 			\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}] 
-% 		\end{equation*}
-		\State compute the predicted mean, the predicted covariance matrix and the cross-covariance matrix
+		\begin{equation*}
+			\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}] 
+		\end{equation*}
+		\State Calculate sigma points for the smoother $\mathcal X_{i,t+1}^{b-}$ and compute 
 		\begin{equation*}
@@
 The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
-
-% \psfragfig{./Graph/FreqAnalysis}
 

### 2010-05-01 src/UKF.py

@@ -1,6 +1,6 @@
 import pylab as pb
 import numpy as np
-import matplotlib.axes3d
+# import matplotlib
 import time,warnings
 import os
 from scipy import signal

### 2010-05-01 src/UKF_ex.py

@@ -51,7 +51,7 @@ act_func=ActivationFunction(threshold,nu,beta)
 #----------observations--------------------------
 l1=[circle(cent,2*pb.sqrt(pb.log(2),)*pb.sqrt(Sensorwidth)/2,'b') for cent in obs_locns]
 l2=[circle(cent,2*pb.sqrt(pb.log(2),)*pb.sqrt(f_widths[0][0,0])/2,'r') for cent in f_centers]
-pb.legend((l1, l2), ('r:field basis functions', 'b:Sensors'), loc='best')
+# pb.legend((l1, l2), ('r:field basis functions', 'b:Sensors'), loc='best')
 pb.axis([-field_width/2.,field_width/2.,-field_width/2,field_width/2])
 pb.show()
 ny=len(obs_locns)
@@ -74,7 +74,9 @@ Y=quickio.read('Y')
 Y=Y['var0']
 t0=time.time()
 ps_estimate=para_state_estimation(model)
-ps_estimate.itr_est(Y[4:],5)
+UKF_iterations = 10;
+start_sample = 4;
+ps_estimate.itr_est(Y[start_sample:],UKF_iterations)
 print 'elapsed time is', time.time()-t0
 #Saving Kernel and 1/synaptic time constant in mat format
 alpha_mat={}

### 2010-05-01 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to paper

--- 2010-04-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
 % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+\usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
-
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+% \author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
+% 
+% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-\begin{figure}\label{fig:experimental design}
-	\begin{center}
-		\includegraphics[scale=0.6]{./Graph/ExperimentFigure.pdf} 
-	\end{center}
+% \begin{figure}\label{fig:experimental design}
+% 	\begin{center}
+% 		\includegraphics[scale=0.6]{./Graph/ExperimentFigure.pdf} 
+% 	\end{center}
+% 	\caption{Example of experimental design and model output.
+\textbf{A}.
+Example of the neural field with sensors.
+The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
+\textbf{B} Example of data generated by the model through the observations.
+\textbf{C}.
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
+% \end{figure}
+\begin{figure}[!hb] 
+% \renewcommand*{\thesubfigure}{}
+\centering
+\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigurePy.pdf}}\\
+% \hspace{2.5mm}
+\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
+% \hspace{2.5mm}
+\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigurePSDPy.pdf}}
 \caption{Example of experimental design and model output.

### 2010-05-01 src/UKF_ex.py

@@ -24,7 +24,7 @@ obs_noise_covariance=parameters['obs_noise_covariance']
 Fs=parameters['Fs']
 t_end=parameters['t_end']
 #-------------field--------------------
-field_basis_width=2.5#3.6
+field_basis_width=2.0#3.6
 spacestep=1
 S=pb.linspace(-10,10,11)
 f_centers=gen_spatial_lattice(S)

### 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Two column format
align some of the equations for the two columns format

@@
 \renewcommand{\subcapsize}{\small}
-% \usepackage{anysize}							%<-use this for checking equation length
-% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
-% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+ \usepackage{anysize}							%<-use this for checking equation length
+ \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
 \usepackage{amsmath}
@@
 \begin{eqnarray}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =  \int_{-\infty}^t h\left(t - t'\right) \\
-	\times\left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'. 
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) &=&  \int_{-\infty}^t h\left(t - t'\right) \\
+	&\times&\left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'. \nonumber
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \\
-	\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right). 
+	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
+	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right). \nonumber
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \\
-	+ T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right), 
+	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
+	&+& T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right), 
 \end{eqnarray}
@@
 \begin{equation}\label{DefKernelDecomp}
-	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right)^\top \boldsymbol{\theta}.
+	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta}.
 \end{equation}
@@
 \begin{eqnarray}
-	\label{reduced continuous model} \boldsymbol{\phi}^{\top}\left( \mathbf{r} \right) \mathbf{x}_{t+1} = T_s\int_\Omega { f\left( \boldsymbol{\phi} ^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t \right)\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right)^{\top}d\mathbf{r}'}\boldsymbol{\theta} \\
-	- \xi\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)x_t + T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right). 
+	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}&=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}\nonumber \\
+	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + T_s u_t(\mathbf{r})+ e_t(\mathbf{r}). 
 \end{eqnarray}
@@
 \begin{eqnarray}\label{eq:QMatrix}
-	\mathbf{Q}\left(\mathbf{x}_t\right) &=& \boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \\
+	\lefteqn {\mathbf{Q}(\mathbf{x}_t)=} \\
+&&\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}}\nonumber
+\end{eqnarray}
+\begin{eqnarray}
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
-	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}, 
+	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, 
 \end{eqnarray}
@@
 The sigma vectors $\mathcal X_i$ are calculated by
-\begin{equation}\label{eq:sigmapoints1}
-	\mathcal X_{0}=\bar x 
-\end{equation}
-\begin{equation}
-	\mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots, L 
-\end{equation}
-\begin{equation}\label{eq:sigmapoints2}
-	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L 
-\end{equation}
+\begin{eqnarray}\label{eq:sigmapoints1}
+	\mathcal X_{0}&=&\bar x \\
+	\mathcal X_{i}&=&\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots, L \\
+\label{eq:sigmapoints2}
+	\mathcal X_{i}&=&\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L \nonumber \\
+\end{eqnarray}
 where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the ith column of the weighted matrix squre root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
@@
 \begin{algorithm}
-	\caption{The Unscented Kalman Filter}\label{UKFAlgorithm} 
+	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
 	\begin{algorithmic}[1] 
-		\State Forward initialisation 
+		\State Forward initialisation \quad $\hat{\mathbf x}_0, \mathbf P_0 $
+		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
+		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
 		\begin{equation*}
-			\hat{\mathbf x}_0, \mathbf P_0 
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f,u_t) 
 		\end{equation*}
-		\State Forward iteration For $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-
-		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
-% 		\begin{equation*}
-% 			\mathcal X_t^f=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^{f}-\gamma\sqrt{\mathbf P_t^f}] 
-% 		\end{equation*}
-
-% 		propagate the sigma points through the state equation 
-		\begin{equation}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f,u_t) 
-		\end{equation}
-
 		calculate the predicted state and the predicted covariance matrix
@@
 		\end{equation*}
-
-		compute the filter gain, the filtered state and the filtered covariance matrix using the standard kalman filter formulations
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter 
 		\begin{equation*}
@@
 		\State Backward initialisation 
-		\begin{equation}
-			\mathbf P_T^b= \mathbf P_T^f 
-		\end{equation}
-		\begin{equation}
-			\hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
-		\end{equation}
-		\State Backward iteration For $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $
-
-calculate the sigma points $\mathcal X_{i,t}^b$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
-		\begin{equation}
+		\begin{equation*}
+			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
+		\end{equation*}
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
+		\begin{equation*}
 			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b,u_t) 
-		\end{equation}
-% 		\begin{equation*}
-% 			\mathcal X_t^b=[\hat{\mathbf x}_t^f \quad \hat{\mathbf x}_t^f+\gamma\sqrt{\mathbf P_t^f} \quad \hat{\mathbf x}_t^f-\gamma\sqrt{\mathbf P_t^f}] 
-% 		\end{equation*}
+		\end{equation*}
 		\State compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
@@
 		\end{equation*}
-		\State Compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $ 
+		\State Compute the smoother gain, the smoothed state and the smoothed covariance matrix
 		\begin{equation*}
@@
 % \end{figure}
+
 \begin{figure}[!hb] 
@@
 \centering
-\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigurePy.pdf}}\\
+\subfigure{\includegraphics[width=3in]{./Graph/ExperimentFigurePy.pdf}}\\
 % \hspace{2.5mm}
-\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
+\subfigure{\includegraphics[width=3in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
 % \hspace{2.5mm}
-\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigurePSDPy.pdf}}
+\subfigure{\includegraphics[width=3in]{./Graph/ExperimentFigurePSDPy.pdf}}
 \caption{Example of experimental design and model output.
@@
 We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by
-\begin{equation}
-	\label{Euler Approximation} \frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} = -\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).
-\end{equation}
+\begin{eqnarray}
+	\label{Euler Approximation} \lefteqn{\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =}\nonumber\\
+& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).\nonumber \\ 
+\end{eqnarray}
 For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging Eq.~\ref{Euler Approximation} we get 
 \begin{eqnarray}
-	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).
+	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right)\nonumber \\
+&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).\nonumber \\ 
 \end{eqnarray}
@@
 \section{Numerical Simulation of IDE Model}\label{Space Discretization} To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
-\begin{equation}
-	\label{discrete space} v_{t+1}\left(\mathbf{r}_{ij}\right) = \xi v_t\left(\mathbf{r}_{ij}\right) + T_s \Delta^2 \sum_{i=1}^{i=I}{ \sum_{j=1}^{j=J}{ w\left( \mathbf{r}-\mathbf{r}_{ij}' \right)f\left( v_t\left( \mathbf{r}_{ij}'\right) \right)} } + T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}),
-\end{equation}
+\begin{eqnarray}
+	\label{discrete space} \lefteqn{v_{t+1}\left(\mathbf{r}_{ij}\right)=}\nonumber\\
+&&\xi v_t\left(\mathbf{r}_{ij}\right)+T_s \Delta^2\sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{w\left(\mathbf{r}-\mathbf{r}_{ij}'\right)f\left( v_t\left( \mathbf{r}_{ij}'\right)\right)}}\nonumber\\
+&+& T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}), 
+\end{eqnarray}
 where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
@@
 \begin{eqnarray}
-	\label{StartofReduction} \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} - \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \\
-	+ T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
+ &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
+&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}}\nonumber\\
+&+&\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
 \end{eqnarray}
@@
 \begin{eqnarray}
-	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}\left(\mathbf{r}\right) \int_\Omega {f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right)\mathbf{x}_t\right) \boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta} - \xi \mathbf{x}_t \\
-	+ \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}}.
+	 \lefteqn{\mathbf{x}_{t+1} \nonumber= T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+&-&\xi\mathbf{x}_t+\boldsymbol{\Gamma}^{-1}T_s\int_\Omega{\boldsymbol{\phi}(\mathbf{r}) u_t(\mathbf{r})d\mathbf{r}}\nonumber+\boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\
 \end{eqnarray}
@@
 \end{eqnarray}
-in matrix form 
-\begin{equation}
-	\left[
-	\begin{array}{cccc}
-		\mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}
-	\end{array}
-	\right] -\left[
-	\begin{array}{cccc}
-		\mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}
-	\end{array}
-	\right] =T_s\left[
-	\begin{array}{cc}
-		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
-		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
-	\end{array}
-	\right] \left[
-	\begin{array}{cc}
-		\boldsymbol{\theta} \\
-		\zeta
-	\end{array}
-	\right]+\left[
-	\begin{array}{cccc}
-		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
-	\end{array}
-	\right] 
-\end{equation}
-or in compact form we have 
+% in matrix form 
+% \begin{equation}
+% 	\left[
+% 	\begin{array}{cccc}
+% 		\mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}
+% 	\end{array}
+% 	\right] -\left[
+% 	\begin{array}{cccc}
+% 		\mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}
+% 	\end{array}
+% 	\right] =T_s\left[
+% 	\begin{array}{cc}
+% 		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
+% 		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
+% 	\end{array}
+% 	\right] \left[
+% 	\begin{array}{cc}
+% 		\boldsymbol{\theta} \\
+% 		\zeta
+% 	\end{array}
+% 	\right]+\left[
+% 	\begin{array}{cccc}
+% 		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
+% 	\end{array}
+% 	\right] 
+% \end{equation}
+ in compact form we have 
 \begin{equation}
@@
 where 
-\begin{equation}
+\begin{equation*}
 	\mathbf Z=\left[
@@
 	\right] 
-\end{equation}
+\end{equation*}
 and
-\begin{equation}
+\begin{equation*}
 \quad \mathbf W=\left[
@@
 	\right] 
-\end{equation}
+\end{equation*}
 using the LS method $ \mathbf W$ can be estimated 

### 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
rearranged and aligned equations for the two column format

@@
 \end{eqnarray}
-\begin{eqnarray}\label{eq:QMatrix}
-	\lefteqn {\mathbf{Q}(\mathbf{x}_t)=} \\
-&&\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}}\nonumber
-\end{eqnarray}
+where
 \begin{eqnarray}
+Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right)&=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right)\label{eq:QmatrixForSigmapoints}\\
 	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
-	\mathbf{e}_t &=& \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, 
+	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, 
 \end{eqnarray}
@@
 \begin{algorithm}
+	\begin{small}
 	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
 	\begin{algorithmic}[1] 
-		\State Forward initialisation \quad $\hat{\mathbf x}_0, \mathbf P_0 $
+		\State Forward initialisation 
+		\begin{equation*}
+		 \hat{\mathbf x}_0, \mathbf P_0 
+		\end{equation*}
 		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
+		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through equation \ref{eq:QmatrixForSigmapoints}
+% 		\begin{small}
 		\begin{equation*}
@@
 		\end{equation*}
+% 		\end{small}
 		calculate the predicted state and the predicted covariance matrix
@@
 		\end{equation*}
-		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through the state equation
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propogate them through equation \ref{eq:QmatrixForSigmapoints}
 		\begin{equation*}
@@
 		\end{equation*}
-		\State compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
+		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
 		\begin{equation*}
@@
 		\end{equation*}
-		\State Compute the smoother gain, the smoothed state and the smoothed covariance matrix
+		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
 		\begin{equation*}
@@
 	\end{algorithmic}
+\end{small}
 \end{algorithm}
@@
 \centering
-\subfigure{\includegraphics[width=3in]{./Graph/ExperimentFigurePy.pdf}}\\
+\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePy.pdf}}\\
 % \hspace{2.5mm}
-\subfigure{\includegraphics[width=3in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
+\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
 % \hspace{2.5mm}
-\subfigure{\includegraphics[width=3in]{./Graph/ExperimentFigurePSDPy.pdf}}
+\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePSDPy.pdf}}
 \caption{Example of experimental design and model output.
@@
 Substituting Eq.~\ref{DefGamma} into Eq.~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{eqnarray}
+\begin{eqnarray}\label{eq:ReducedForm}
 	 \lefteqn{\mathbf{x}_{t+1} \nonumber= T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
@@
 \begin{eqnarray}
-	\mathbf{\Sigma}_e&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top} e_t\left(\mathbf{r}'\right)d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
+	\lefteqn{\mathbf{\Sigma}_e} \nonumber \\ 
+&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top} 
 \end{eqnarray}
@@
 Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to an \textit{n}-dimensional Gaussian centered at the origin yields
-\begin{eqnarray}
- G(\boldsymbol \nu)&=&\int_{\mathcal R^n}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r \nonumber \\
-&=&\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
-&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right)
+\begin{eqnarray}\label{eq:GaussianFT}
+ \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathcal R^n}\mathrm{exp}({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r})\mathrm{exp}(-2\pi i\boldsymbol\nu^\top\mathbf r)d\mathbf r} \nonumber \\
+&=&\int_{\mathcal R^n}\mathrm{exp}(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right])d\mathbf r \nonumber \\
+&\times& \mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu)
 \end{eqnarray}
-and 
-\begin{equation}\label{eq:IntegralOfGaussian}
-\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}
-\end{equation}
-which gives another scaled  Gaussian 
+where 
+\begin{align}\label{eq:IntegralOfGaussian}
+\int_{\mathcal R^n}\mathrm{exp}(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right])d\mathbf r&& \nonumber \\
+=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}&&
+\end{align}
+substituting \ref{eq:IntegralOfGaussian} in \ref{eq:GaussianFT} gives another scaled  Gaussian 
 \begin{equation}
-   \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right)
+   \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu)
 \end{equation}
@@
 \begin{equation}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
+\boldsymbol\Phi(\boldsymbol \nu)=(\frac{1}{\pi\sigma_{\nu}^2})^{\frac{n}{2}}\mathrm{exp}(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu).
 \end{equation}
@@
 \begin{eqnarray}
- |\boldsymbol\Phi(\boldsymbol\nu_c)|^2&=&\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{n}\mathrm{exp}\left(-\frac{2}{\sigma_{\nu}^2}\boldsymbol\nu_c^\top \boldsymbol\nu_c\right)\\
-&=&\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
+ |\boldsymbol\Phi(\boldsymbol\nu_c)|^2=\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
 \end{eqnarray}
+%\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{n}\mathrm{exp}\left(-\frac{2}{\sigma_{\nu}^2}\boldsymbol\nu_c^\top \boldsymbol\nu_c\right)\\
 solving for $\sigma_{\nu}^2$ we get
@@
 \section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix} 
-The state equation given in \ref{Homogeneous SS Model} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters.
-Using  \ref{Homogeneous SS Model} and \ref{eq:QMatrix} by substituting  $\xi = 1-\zeta T_s$ at each time instant we can write
+The finite state space model  given in \ref{eq:ReducedForm} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters.
+We define $n_x \times n_{\theta}$ matrix
+\begin{eqnarray}\label{eq:QMatrix}
+	\lefteqn {\mathbf{Q}(\mathbf{x}_t)=} \\
+&&\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}}\nonumber
+\end{eqnarray}
+by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} with zero input and using $\xi = 1-\zeta T_s$ at each time instant we can write
 \begin{eqnarray}
@@
 	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+\mathbf e_1\nonumber\\
-	&\vdots& \nonumber\\
-	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+\mathbf e_{n-1} 
+	&\vdots& \\
+	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+\mathbf e_{n-1} \nonumber
 \end{eqnarray}
@@
 where 
+\begin{small}
 \begin{equation*}
@@
 \end{equation*}
+\end{small}
 and
+\begin{small}
 \begin{equation*}
@@
 \end{equation*}
+\end{small}
 using the LS method $ \mathbf W$ can be estimated 

### 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
parameter distribution graphs added to the paper
restored Dean's intro structure from an old commit.

@@
 The sigma vectors $\mathcal X_i$ are calculated by
-\begin{eqnarray}\label{eq:sigmapoints1}
-	\mathcal X_{0}&=&\bar x \\
-	\mathcal X_{i}&=&\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots, L \\
-\label{eq:sigmapoints2}
-	\mathcal X_{i}&=&\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L \nonumber \\
-\end{eqnarray}
+\begin{equation}\label{eq:sigmapoints1}
+	\mathcal X_{0}=\bar x 
+\end{equation}
+\begin{equation}
+	\mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots, L 
+\end{equation}
+\begin{equation}\label{eq:sigmapoints2}
+	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L 
+\end{equation}
 where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the ith column of the weighted matrix squre root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.

### 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to figure 1

--- 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation.
+\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
@@
 shows example data from the sensors of the model, and figure~\ref{fig:experimental design}~C.
-shows the power spectral density of on of the simulated time-series.
+shows the power spectral density of the simulated time-series.
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
@@
 \begin{figure}[!hb]
-% \renewcommand*{\thesubfigure}{}
 \centering
-\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePy.pdf}}\\
+\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy.pdf}}\\
 % \hspace{2.5mm}
-\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
+\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}}\\
 % \hspace{2.5mm}
-\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePSDPy.pdf}}
+\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}}
 \caption{Example of experimental design and model output.
@@
 \textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:experimental design}
 \end{figure}
-
+\begin{figure}[th]
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}\\
+\caption{Distribution of the parameters estimates over 272
+runs.}
+\label{fig:Parameters}
+\end{figure}
 \subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
@@
 \section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretization must be perform.
-We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by
+We used a one-step Euler method where Eq.~\ref{FinalFormContinuous} can be approximated by
 \begin{eqnarray}

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added some figurs

@@
 \subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
-Each realisation consisted of 300 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
+Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
 The initial state and parameters were unknown to the estimator.
 The state estimates were evaluated by comparing the field reconstruction to the true field using the mean over time of the RMSE and standard deviation of the RMSE.
-The distribution of the state estimates are shown in figure~\ref{}.
+The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate.pdf}
+\caption{Mean kernel estimates over 272 runs ;  true and estimated kernels are shown by solid
+and dashed line respectively, the red area shows 95\% confedence interval.}
+\label{fig:KernelEstimates}
+\end{figure}
 

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small changes to paper and code

--- 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-% \documentclass[12pt]{iopart}
+% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+\documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-% \usepackage{iopams,setstack} 
+\usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  \usepackage{anysize}							%<-use this for checking equation length
- \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-\usepackage{amsmath}
+% \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-% \author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
-% 
-% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
+
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 \end{figure}
-
+\begin{figure}[th]
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}\\
+\caption{Distribution of the parameters estimates over 272
+runs.}
+\label{fig:Parameters}
+\end{figure}
 \subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
@@
 where 
-\begin{align}\label{eq:IntegralOfGaussian}
+\begin{eqnarray}\label{eq:IntegralOfGaussian}
 \int_{\mathcal R^n}\mathrm{exp}(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right])d\mathbf r&& \nonumber \\
 =(\pi\sigma_{\phi}^2)^{\frac{n}{2}}&&
-\end{align}
+\end{eqnarray}
 substituting \ref{eq:IntegralOfGaussian} in \ref{eq:GaussianFT} gives another scaled  Gaussian 

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
whole bunch of tiny edits. Like s&r for utilise because I no longer believe that it can be used properply in science and engineering

--- 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+\documentclass[twocolumn,10pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-% \usepackage{amsmath}
+\usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
-Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008} \cite{David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003}, \cite{Suffczynski2004} and \cite{Wendling2005} and insights into other pathologies \cite{Moran2008} \cite{Schiff2009} that would be difficult to gain from experimental data alone.
+Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews).
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999,RENNIE2000}, epileptic seizure generation \cite{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \cite{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.
 
@@
 
-An estimation framework for neural field models known as dynamical causal modelling (DCM) \cite{David2003} \cite{David2006} has recently been proposed for studying evoked potential dynamics.
-Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set.
-The interconnected brain regions are modelled by the Jansen and Ritt equations.
+An estimation framework for neural field models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has recently been proposed for studying evoked potential dynamics.
+Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set under the Jansen and Ritt equations.
 Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
@@
 
-Currently available epileptic seizure  control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
+%Currently available epileptic seizure  control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
 That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neuro-dynamics and information about their particular pathologies.
@@
 This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher dimensional systems utilising a systematic model reduction procedure.
-In addition, a method is presented for estimating the the connectivity structure and the synaptic time constant.
+In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
 Until now, estimation of local intracortical connectivity structure has not been attempted.
@@
 In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
-Modelling the neural dynamics within this framework has the distinct advantage over multivariate auto-regressive (AR) models, that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+
+Modelling the neural dynamics within this framework has the distinct advantage over the more standard multivariate auto-regressive (AR) models: that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+
 In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
@@
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominate dynamics of the neural field can be represented by the reduced model.
+Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
 Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
@@
 \end{eqnarray}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an iid spatially coloured, temporally white disturbance term with the covariance 
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an i.i.d. spatially coloured, temporally white disturbance term with the covariance 
 \begin{equation}\label{eq:FieldCovarianceFunction}
-	cov(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ 
+	\mathrm{cov}(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ 
 	\begin{array}{*{20}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma{\varepsilon}\right)$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
@@
 \end{equation}
-and manipulating the model (see~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
+and manipulating the model (see Appendix~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
 \begin{eqnarray}
@@
 
-The state estimation technique utilises the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward path to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The state estimation technique uses the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 An approximation of the state density is made by propagating the so-called sigma points through the state-space model.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation utilises a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see~\ref{LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
 
@@
 The EKF approximates the state transition equation by linearizing about the current state estimates (by calculating the Jacobian) at each time instance.
-The linearisation maintains the Gaussianality of the model.
-The unscented Kalman filter approximates the \emph{a posteriori} state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
+The linearisation maintains the Gaussianity of the model.
+The unscented Kalman filter approximates the posterior state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
 This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
 In addition, the computation of the Jacobian used in the EKF can be problematic.
-SMC filtering can theoretically provide an exact \emph{a posteriori} state density for nonlinear systems.
+SMC filtering can theoretically provide an exact posterior state density for nonlinear systems.
 However, currently this method is not appropriate for our problem, due to computation demands.
@@
 where 
-\begin{eqnarray}\label{eq:IntegralOfGaussian}
+\begin{align}\label{eq:IntegralOfGaussian}
 \int_{\mathcal R^n}\mathrm{exp}(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right])d\mathbf r&& \nonumber \\
 =(\pi\sigma_{\phi}^2)^{\frac{n}{2}}&&
-\end{eqnarray}
+\end{align}
 substituting \ref{eq:IntegralOfGaussian} in \ref{eq:GaussianFT} gives another scaled  Gaussian 
@@
 \begin{tabular}
-	{c|c} \hline\hline Symbol & Description \\
-	\hline $v(\mathbf{r},t)$ & mean membrane potential \\
+	{c|c} Symbol & Description \\
+	\hline
+	\\ & \textbf{Domain and indicies} \\
+	\hline
+	$\Omega$ & spatial domain \\
+	$t$ & time (seconds) \\
+	$\mathbf{r}$ & spatial location \\
+	$n$ & sensor index $n=1,..,N$ \\
+	$T$ & time step \\
+	\\ & \textbf{Spatiotemporal Signals} \\
+	\hline
+	$y(\mathbf{r}_n,t)$ & observation \\
+	$v(\mathbf{r},t)$ & mean membrane potential \\
 	$g(\mathbf{r},t)$ & average action potential rate \\
-	$\mathbf{r}$ & spatial location \\
-	$t$ & time (s) \\
+	$f(\mathbf{r},t)$ & firing function rate \\
+	$u(\mathbf{r},t)$ & external input \\
+	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
+	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
+	\\ & \textbf{Model} \\
+	\hline
 	$h(t)$ & post-synaptic response kernel \\
+	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
 	$\eta(t)$ & Heaviside function \\
@@
 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
-	$f(\mathbf{r},t)$ & firing function rate \\
-	$u(\mathbf{r},t)$ & external input \\
-	$\Omega$ & spatial domain \\
 	$f_{max}$ & maximal firing rate \\
@@
 	$D$ & Temporal differential operator \\
-	$L$ & number of basis function and dimension of state vector \\
-	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
-	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
-	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
-	$y(\mathbf{r}_n,t)$ & obseration \\
-	$n$ & sensor index $n=1,..,N$ \\
-	$T$ & time step \\
 	$\xi$ & time constant parameter \\
+	\\ & \textbf{Decomposition} \\
+	\hline
+	$L$ & number of field basis functions  \\
 	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
@@
 	$\mathbf{C}$ & observation matrix \\
+	\\ & \textbf{Frequency Analysis} \\
+	\hline
 	$V(\nu)$ & Spectrum of the dynamic field \\
@@
 	$\nu_c$ & Spatial cut-off frequency \\
-\end{tabular}
-\begin{tabular}
-	{c|c} \hline\hline Symbol & Description \\
-	\hline $\Delta_s$ & Distance between adjacent sensors \\
+	$\Delta_s$ & Distance between adjacent sensors \\
 	$\rho$ & Over-sampling parameter \\
@@
 	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
+	\\ & \textbf{State Estimation} \\
+	\hline
 	$\hat{\mathbf{x}}$ & State estimate \\
 	$\chi$ & Matrix of sigma vectors \\
-	$\hat{\mathbf{x}}_t^{f-}$ & Forward \emph{a priori} estimate \\
-	$\hat{\mathbf{x}}_t^f$ & Forward \emph{a posteriori} estimate \\
-	$\hat{\mathbf{x}}_t^{b-}$ & Backward \emph{a priori} estimate \\
-	$\hat{\mathbf{x}}_t^{b}$ & Backward \emph{a posteriori} estimate \\
-	$P^f_t$ & Forward \emph{a posteriori} covariance matrix \\
-	$P^{f-}_t$ & Forward \emph{a priori} covariance matrix \\
+	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
+	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
+	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
+	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
+	$P^f_t$ & Forward posterior covariance matrix \\
+	$P^{f-}_t$ & Forward prior covariance matrix \\
 \end{tabular}

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 %
-\documentclass[twocolumn,10pt,a4paper]{article}		%<-use this for checking equation length
-% \documentclass[12pt]{iopart}
+% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+\documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-% \usepackage{iopams,setstack} 
+\usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
 \textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:experimental design}
 \end{figure}

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the distributions of the parameters ratio

--- 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
+Although a wide distribution can be seen over the parameters the ratio between them remains almost constant as shown in figure~\ref{}.
 \begin{figure}
@@
 \end{figure}
-
+\begin{figure}[th]
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta1_ratio.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta2_ratio.pdf}}\\
+\caption{Distribution of the parameters ratios over 272 runs.}
+\label{fig:ParametersRatio}
+\end{figure}
 \section{Discussion}\label{DiscussionSection}

### 2010-05-03 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added kernel frequency response

@@
 %
-% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+ \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
- \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-% \usepackage{amsmath}
+%  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+ \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate.pdf}
+\includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate_KernelFreqResponse.pdf}
 \caption{Mean kernel estimates over 272 runs ;  true and estimated kernels are shown by solid
-and dashed line respectively, the red area shows 95\% confedence interval.}
+and dashed line respectively, the red area shows 95\% confedence interval; top: spatial domain; bottom: frequency domain}
 \label{fig:KernelEstimates}
@@
 Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to an \textit{n}-dimensional Gaussian centered at the origin yields
-\begin{eqnarray}\label{eq:GaussianFT}
+\begin{eqnarray}\label{eq:AppendixGaussianFT}
  \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathcal R^n}\mathrm{exp}({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r})\mathrm{exp}(-2\pi i\boldsymbol\nu^\top\mathbf r)d\mathbf r} \nonumber \\
@@
 \end{eqnarray}
-substituting \ref{eq:IntegralOfGaussian} in \ref{eq:GaussianFT} gives another scaled  Gaussian 
+substituting \ref{eq:IntegralOfGaussian} in \ref{eq:AppendixGaussianFT} gives another scaled  Gaussian 
 \begin{equation}

### 2010-05-04 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
change to the experimental figure now it is plotted directly with subplot in Python to avoid spacing between plots in latex I must say it is a piece of art
change to the experimental graph again

@@
 This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $.
-Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in \ref{ap:FrequencyAnalysis}.
+Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in Appendix~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
@@
 These sigma points propogated through the nonlinear function
-Since the observation equation \ref{ObservationEquation} is linear the update step equations are simplified to the standard Kalman filtering formulations.
+Since the observation equation \ref{ObservationEquation} is linear the standard Kalman filter can be used to update the state equations.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
-However, the predicted cross-covariance of the states needs to be calculated.
+In order to compute the smoother gain the predicted cross-covariance matrix of the states needs to be calculated.
 A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-% \begin{figure}\label{fig:experimental design}
-% 	\begin{center}
-% 		\includegraphics[scale=0.6]{./Graph/ExperimentFigure.pdf} 
-% 	\end{center}
-% 	\caption{Example of experimental design and model output.
+  \begin{figure}\label{fig:experimental design}
+  	\begin{center}
+  		\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy_1.pdf} 
+  	\end{center}
+  	\caption{Example of experimental design and model output.
 \textbf{A}.
@@
 Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
-% \end{figure}
+  \end{figure}
 
-\begin{figure}[!hb]
-\centering
-\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy.pdf}}\\
-% \hspace{2.5mm}
-\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}}\\
-% \hspace{2.5mm}
-\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}}
-\caption{Example of experimental design and model output.
-\textbf{A}.
-Example of the neural field with sensors.
-The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
-\textbf{B} Example of data generated by the model through the observations.
-\textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:experimental design}
-\end{figure}
 \begin{figure}[th]

### 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
its just a check

@@
 \usepackage{color} 
+%This is to decrease the space in subfigure command
 \usepackage[tight,scriptsize]{subfigure}
+\makeatletter
+\renewcommand{\subfigtopskip}{1\p@}
+\renewcommand{\subfigcapskip}{0\p@}
+\renewcommand{\subfigcaptopadj}{1\p@}
+\renewcommand{\subfigbottomskip}{1\p@}
+\renewcommand{\subfiglabelskip}{0.05em plus 0.02em minus 0.01em}
+\makeatother
 % \usepackage{pstool}
@@
    	\caption{Example of experimental design and model output.
-\textbf{A}.
+\textbf{a}.
 Example of the neural field with sensors.
 The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
-\textbf{B} Example of data generated by the model through the observations.
-\textbf{C}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
+\textbf{b} Example of data generated by the model through the observations.
+\textbf{c}.
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
    \end{figure}
-
+% \begin{figure}[th]\label{fig:experimental design}
+% \begin{center}
+% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigurePy.pdf}}\\
+% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}}\\
+% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}}
+% \end{center}
+% \caption{Example of experimental design and model output.
+\textbf{a}.
+Example of the neural field with sensors.
+The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
+\textbf{b} Example of data generated by the model through the observations.
+\textbf{c}.
+Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
+% \end{figure}
 \begin{figure}[th]
@@
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}\\
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}
 \caption{Distribution of the parameters estimates over 272

### 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some corrections to the state parameter estimation

@@
 \section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
-The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step at each time instance.
+The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters is used to generate a new state sequence for the next iteration.
+The procedure stops when the algorithm converges.
+The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
 
@@
 The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
-An approximation of the state density is made by propagating the so-called sigma points through the state-space model.
-The sigma points describe the mean and covariance of the state estimate and are calculated using the unscented transform.
-The sigma vectors $\mathcal X_i$ are calculated by
+The first and the second order moments of the predicted state is captured by propagating the so-called sigma points through the state equation.
+The sigma points $\mathcal X_i$ are calculated using the unscented transform as follows
 \begin{equation}\label{eq:sigmapoints1}
@@
 It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing respectively.
-The sigma vectors are propagated through the system equations and weighted to form the posterior mean and covariance.
+The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance.
 The weights are calculated by
@@
 \end{equation}
-
-% For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}.
-$ (\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i$ is the ith column of the matrix square root (e.g., lower-triangular Cholesky factorization).
-These sigma points propogated through the nonlinear function
-Since the observation equation \ref{ObservationEquation} is linear the standard Kalman filter can be used to update the state equations.
+Since the observation equation \ref{ObservationEquation} is linear the standard Kalman filter can be used to update the predicted states.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
@@
 A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
-It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used.
-This reduces the dimension and the number of sigma points used in the algorithm.
+It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used , otherwise the state vector should be augmented with the noise terms.
+Using the additive form reduces the dimension and the number of sigma points used in the algorithm.
 \begin{algorithm}

### 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some little typos in the state and paramter estimation bit

@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+\section{State and Parameter Estimation}
+\label{StateAndParameterEstimationSection}
+
+In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
 The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
-At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters is used to generate a new state sequence for the next iteration.
+At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters are used to generate a new state sequence for the next iteration.
 The procedure stops when the algorithm converges.
@@
 The state estimation technique uses the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and the second order moments of the predicted state is captured by propagating the so-called sigma points through the state equation.
@@
 \end{equation}
-where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the ith column of the weighted matrix squre root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
+where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i$th column of the weighted matrix square root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
-It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used , otherwise the state vector should be augmented with the noise terms.
+It should be noted that as the disturbance $e_t\left(\mathbf{r}\right)$ and the measurement noise $\boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used , otherwise the state vector should be augmented with the noise terms.
 Using the additive form reduces the dimension and the number of sigma points used in the algorithm.

### 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
general edition

--- 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \end{eqnarray}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t\left(\mathbf{r}\right)$ is an i.i.d. spatially coloured, temporally white disturbance term with the covariance 
-\begin{equation}\label{eq:FieldCovarianceFunction}
-	\mathrm{cov}(\mathbf{e}_t,\mathbf{e}_{t+\tau}) = \left\{ 
-	\begin{array}{*{20}
-		{c}} \gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\
-		0 & \mathrm{otherwise}. \\
-	\end{array}
-	\right. 
-\end{equation}
-This term was added to account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t$ is i.i.d.
+such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
+This term was added to account for uncertainty in the model.
+To generate iEEG/LFP data we used the output function
 \begin{equation}
@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe  estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
 The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
-At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters is used to generate a new state sequence for the next iteration.
+At each iteration, a sequence of estimated states is used to calculate the parameter set and the resulting parameters is used to generate a new sequence of states for the next iteration.
 The procedure stops when the algorithm converges.
@@
 where $\alpha$, $\beta$ and $\kappa$ are constants (see ~\cite{Haykin2001} for more details).
-It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing respectively.
+It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing.
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance.
@@
 \end{equation}
-Since the observation equation \ref{ObservationEquation} is linear the standard Kalman filter can be used to update the predicted states.
+Since the observation equation \ref{ObservationEquation} is linear the standard Kalman Filter update equations can be used to update the predicted states.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
@@
 		\end{equation*}
-		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter 
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
 		\begin{equation*}
@@
 \end{equation}
-where $\xi = 1 - T \zeta$. 
+where $\xi = 1 - T_s \zeta$. 
 \section{Numerical Simulation of IDE Model}\label{Space Discretization} To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving

### 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
+\label{StateAndParameterEstimationSection}
+
+In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters are used to generate a new state sequence for the next iteration.
+The procedure stops when the algorithm converges.
+The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
 
 The state estimation technique uses the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997,Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and the second order moments of the predicted state is captured by propagating the so-called sigma points through the state equation.

### 2010-05-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Field estimation plot added to the paper

@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-   \begin{figure}\label{fig:experimental design}
+   \begin{figure}[th]\label{fig:experimental design}
    	\begin{center}
@@
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
-Although a wide distribution can be seen over the parameters the ratio between them remains almost constant as shown in figure~\ref{}.
+Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
+One snapshot for the original and the field estimate and the corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
 \begin{figure}
@@
 \end{figure}
+\begin{figure*}[!th] 
+\subfigure[][]{\includegraphics[width=2in]{./Graph/TrueField90.pdf}}
+\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimatedField90.pdf}}
+\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimationError90.pdf}}\\
+\caption{One snapshot of the spatial field; a: True field; b: Estimated field; c: The absolute error.}
+\label{fig:FieldEstimate}
+\end{figure*}
 \section{Discussion}\label{DiscussionSection}

### 2010-05-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
the plot of MRMSE is added

@@
 The initial state and parameters were unknown to the estimator.
-The state estimates were evaluated by comparing the field reconstruction to the true field using the mean over time of the RMSE and standard deviation of the RMSE.
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
 Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-One snapshot for the original and the field estimate and the corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
+The state estimates for one realization were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
+The mean of RMSE over time is also shown in figure~\ref{fig:MRMSE} One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
 \begin{figure}
 \includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate_KernelFreqResponse.pdf}
-\caption{Mean kernel estimates over 272 runs ;  true and estimated kernels are shown by solid
+\caption{Mean kernel estimates over 200 runs ;  true and estimated kernels are shown by solid
 and dashed line respectively, the red area shows 95\% confedence interval; top: spatial domain; bottom: frequency domain}
@@
 \end{figure}
+  \begin{figure}\label{fig:MRMSE}
+   	\begin{center}
+   		\includegraphics[width=0.5\textwidth]{./Graph/MRMSE.pdf} 
+   	\end{center}
+   	\caption{The mean of RMSE over time.} 
+   \end{figure}
+
 \begin{figure*}[!th] 
@@
 \begin{lemma}
-	Consider the zero-mean process $e_t\left(\mathbf r\right)$ with covariance as defined by \ref{eq:FieldCovarianceFunction} then 
+	Consider the i.i.d. noise term $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ then 
 	\begin{equation}

### 2010-05-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
no comments

@@
 The state estimates for one realization were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
-The mean of RMSE over time is also shown in figure~\ref{fig:MRMSE} One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
+The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE} One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
 \begin{figure}
@@
 \end{figure}
-  \begin{figure}\label{fig:MRMSE}
+  \begin{figure}\label{fig:RMSE}
    	\begin{center}
@@
    	\end{center}
-   	\caption{The mean of RMSE over time.} 
+   	\caption{The RMSE of the estimated field over time.} 
    \end{figure}

### 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small format change to paper

--- 2010-05-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
  \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
-%  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+ \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
  \usepackage{amsmath}
@@
 \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
-   \begin{figure}[th]\label{fig:experimental design}
+   \begin{figure}\label{fig:experimental design}
    	\begin{center}
@@
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
-Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-One snapshot for the original and the field estimate and the corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
+Although a wide distribution can be seen over the parameters the ratio between them remains almost constant as shown in figure~\ref{}.
 \begin{figure}
@@
 \end{figure}
-\begin{figure*}[!th] 
-\subfigure[][]{\includegraphics[width=2in]{./Graph/TrueField90.pdf}}
-\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimatedField90.pdf}}
-\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimationError90.pdf}}\\
-\caption{One snapshot of the spatial field; a: True field; b: Estimated field; c: The absolute error.}
-\label{fig:FieldEstimate}
-\end{figure*}
 \section{Discussion}\label{DiscussionSection}

### 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
FFT of the true and estimated field plots

--- 2010-05-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 The state estimates for one realization were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
-The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE} One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
+The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE}.
+One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
 \begin{figure}
@@
 \caption{Distribution of the parameters ratios over 272 runs.}
+\end{figure}
 \label{fig:ParametersRatio}
+\begin{figure}[th]
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTTrueField.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTEstimatedField.pdf}}\\
+\caption{The average FFT of the hidden field; a: True field; b: Estimated field.}
+\label{fig:FFTTrueEstimate}
 \end{figure}
-  \begin{figure}\label{fig:RMSE}
+
+  \begin{figure}
    	\begin{center}
@@
    	\caption{The RMSE of the estimated field over time.} 
+\label{fig:RMSE}
    \end{figure}

### 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Frequency analysis plots are added to the paper
updated required references and some paper edits to intro

@@
 \section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field mathematical models from patient specific data.
-The ability to estimate such models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
-
-Parameter estimation may have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{marten2009derivation}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-\omg{I extended this bit I am not sure how to connect it with the rest.
-Maybe the next paragraph can go.}
-% 
-% The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
-Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
-
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
@@
 Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations, marking a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations.
+This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
@@
 
-This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher dimensional systems utilising a systematic model reduction procedure.
+This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher order systems via a systematic model reduction procedure.
 In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
@@
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Next, a reduced finite dimensional neural field model is derived in Section~\ref{ReducedModelSection}.
+Next, a reduced finite dimensional neural field model is derived.
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
+Section~\ref{SpectralAnalysisSection} establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
 Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
@@
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
+\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC or Amari style neural field model \cite{Wilson1973,Amari1977} that was used to create our intracortical connectivity estimator.
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
 Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
-\begin{todo}
-	{Really need to add some citations here.} 
-\end{todo}
-It is also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations. 
-\begin{todo}
-	{Same here.} 
-\end{todo}
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
+Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}
 
@@
 \section{Discussion}\label{DiscussionSection}
+
+Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
+For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
+In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+
+Parameter estimation may have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+
 \begin{itemize}

### 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editting paper, removing u(r,t) and adding references

@@
 Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}
+Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
 
@@
 
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 \end{equation}
-The post-synaptic response kernel $h(t)$ is described by \todo{citation needed} \omg{this is about the most vanilla bit} 
+The post-synaptic response kernel $h(t)$ is described by 
 \begin{equation}
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right),
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
 \end{equation}
 where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
-The term $u\left(\mathbf{r},t\right)$ represents a known external input \wtf{Do we actually use the input in this paper, or is it just dragged around the derivation to be discarded in the conclusion?}.
-The connectivity kernel is typically a ``Mexican hat'' function \todo{which describes strong local activation, weak mid-range repression and weak long-range activation \cite{}}.
+The connectivity kernel is typically a ``Mexican hat'' function which describes strong local activation, weak mid-range repression and weak long-range activation.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
@@
 The parameter $\varsigma$ governs the slope of the sigmoid.
-By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
+By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
 \begin{eqnarray}
 	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) &=&  \int_{-\infty}^t h\left(t - t'\right) \\
-	&\times&\left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'. \nonumber
+	&\times&\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}'dt'. \nonumber
 \end{eqnarray}
@@
 	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
-	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right). \nonumber
+	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'}. \nonumber
 \end{eqnarray}
-To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see Appendix~\ref{Time Discretization}) giving 
 \begin{eqnarray}
 	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
-	&+& T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right), 
+	&+& e_t\left(\mathbf{r}\right), 
 \end{eqnarray}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t$ is i.i.d.
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is i.i.d.
 such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
@@
 \subsection{Derivation of Finite Dimensional State-Space Model} 
-
 In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
@@
  Decomposition allows a continuous field to be represented by a finite dimensional state vector.
-This allows for the application of standard nonlinear, non-Gaussian state estimation methods such as the unscented Kalman filter.
+This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
 The field decomposition is described by
@@
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
-Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
+Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
 \begin{eqnarray}
 	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}&=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}\nonumber \\
-	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + T_s u_t(\mathbf{r})+ e_t(\mathbf{r}). 
+	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t 
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t\right) + \mathbf{e}_t 
 \end{eqnarray}
@@
 \begin{eqnarray}
-Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right)&=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right)\label{eq:QmatrixForSigmapoints}\\
-	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
+Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
 	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, 
@@
 	\begin{center}
-		\includegraphics[scale=0.5, angle=-90]{./Graph/FreqAnalysis.pdf}
+\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/BasisChar.pdf}}
+\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/SensorChar.pdf}}
+\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ObservationFrequencyResponse.pdf}}
 	\end{center}
-	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
+	\caption{a:Field basis function frequency response; b:Sensor frequency response ; c: The average FFT of the observed field.} 
+\label{fig:FreqAnalysis} 
 \end{figure*}

### 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
finished edit on spatial freq analysis section

@@
 \section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}.
-Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
+Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
 
@@
 Conversely, a wider kernel bandwidth will govern the system bandwidth.
-\wtf{this bit incites trouble: Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.}
 
@@
 Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
-Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}}.
+Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something.
+These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function.
+Can we remove the sentence ``Such a condition is usually satisfied...'' }.
 Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
-Note that for the 3-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
-Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+Note that for the 2-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
 \begin{equation}
-	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho\nu_c}, 
+	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
 \end{equation}
-where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
-Satisfying this condition is required for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
+where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
+This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
 If the condition is not satisfied, spatial aliasing will occur.
@@
 The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors).
-The second is to use wider sensors, which act like an anti-aliasing filters.
+The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter.
 This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field.
-In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques.
+In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
+However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
@@
 Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition.
-The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
+The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field.
 Thus, the minimum distance between basis must satisfy
 \begin{equation}
-	\Delta_b < \frac{1}{2\nu_c}. 
+	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
 \end{equation}
-For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
+where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observation.
+For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
 The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
 \begin{equation}\label{eq:GaussianFT}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
 \end{equation}
@@
 \end{equation}
-width $\sigma^2_{\nu}$ should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_c$ giving
+The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
 \begin{equation}\label{eq:WidthFrequencyRelationship}
@@
 \end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $.
-Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in Appendix~\ref{ap:FrequencyAnalysis}.
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co} $.
+Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in Appendix~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.

### 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edited parameter and state estimation section

@@
 
-The dynamic field must be spatially oversampled by using a larger number of sensor then imposed by frequency considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
+The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
 Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
+For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe  estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
-The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
-At each iteration, a sequence of estimated states is used to calculate the parameter set and the resulting parameters is used to generate a new sequence of states for the next iteration.
-The procedure stops when the algorithm converges.
-The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
-\label{StateAndParameterEstimationSection}
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, that scale the field basis functions and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+At each iteration, the sequence of estimated states is used to update the parameter set, then resulting parameters are used to estimate a new state vector for the next iteration.
+The procedure stops when the parameters converge.
+The algorithm is initialised using a bounded random state sequence which guarantees the initial estimated parameter set forms a stable kernel.
 
-In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
-The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
-At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters are used to generate a new state sequence for the next iteration.
-The procedure stops when the algorithm converges.
-The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
-
-The state estimation technique uses the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
-The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
-The first and the second order moments of the predicted state is captured by propagating the so-called sigma points through the state equation.
-The sigma points $\mathcal X_i$ are calculated using the unscented transform as follows
+The Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The URTSS uses the unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
+The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows
 \begin{equation}\label{eq:sigmapoints1}
@@
 \end{equation}
-where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i$th column of the weighted matrix square root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i$th column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 where $\alpha$, $\beta$ and $\kappa$ are constants (see ~\cite{Haykin2001} for more details).
-It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing.
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance.
@@
 \end{equation}
-Since the observation equation \ref{ObservationEquation} is linear the standard Kalman Filter update equations can be used to update the predicted states.
+Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are  used to correct the predicted states.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
-In order to compute the smoother gain the predicted cross-covariance matrix of the states needs to be calculated.
-A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
+To compute the smoother gain, the predicted cross-covariance matrix of the states is also calculated.
+A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
 It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used , otherwise the state vector should be augmented with the noise terms.
@@
 Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
-The EKF approximates the state transition equation by linearizing about the current state estimates (by calculating the Jacobian) at each time instance.
-The linearisation maintains the Gaussianity of the model.
+The EKF approximates the state transition equation by linearising about the current state estimates (by calculating the Jacobian) at each time instance.
+The linearisation maintains the Gaussianality of the model.
 The unscented Kalman filter approximates the posterior state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+\section{Results}\label{ResultsSection} The neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
started working on the discussion

@@
 \end{figure*}
+
 \section{Discussion}\label{DiscussionSection}
-
 Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 
+Testing if this estimation framework can 
+We have presented a novel framework for model reduction to make estimation of neural field practical.
+This systematic model reduction allows for the choice a complexity.
+The level of detail of the field is related to the number and width of the field basis functions, thereby providing a flexible approach where detail and computational complexity can be tradeoff..
+For certain application it might be sufficient to capture only low (spatial) frequency dynamics.
+
+Here we assumed knowledge of the width of the kernel basis functions. If a future work we plan to extend this work to unknown widths.
+
+In future work, we aim to show how heterogeneous can be modelled within this formulation.
+We will still assume a isotropic connectivity kernel however heterogenaities can be modelled by placing basis function c
+
 \begin{itemize}
@@
 Some sort of IC optimisation?}
-	\item the width of the connectivity basis functions \wtf{do you mean width of the kernel?
-I'm not sure about this - as the parameters increase the kernel width increases right?
-So maybe you mean the basis functions, but don't we estimate these widths from the frequency analysis?} here is known exactly.
-In practice we don't
+
 	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
periodic commit. making changes to discussion

--- 2010-05-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
-	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'}. \nonumber
+	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. \nonumber
 \end{eqnarray}
@@
 \end{figure*}
+
 \section{Discussion}\label{DiscussionSection}
+This paper presents a novel framework for model reduction to make estimation of neural field practical.
+This systematic model reduction allows for the choice a complexity.
+The level of detail of the field is related to the number and width of the field basis functions, thereby providing a flexible approach where detail and computational complexity can be tradeoff.
+For certain application it might be sufficient to capture only low (spatial) frequency dynamics.
+
+The frequency analysis and model selection tools presented in this paper specifies the sensor and field basis function arrangement required to form a state-space model to capture and model dominant cortical dynamics.
+These tools can be used to better design experiments and recording techniques to advance model based neural parameter estimation and avoid spatial aliasing.
+In addition, the assumption homogeneity can be relaxed where heterogeneity can be model by careful placement of field basis functions.
+For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
+In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
+
+To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
+This is important as the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the fine spatial scale and the high degree of crossing of fibres\omg{ref}.
+In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
+The model based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
+An advantage of these auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
+The AR methods are complementary to the proposed model based framework and by combining these methods a more realistic model can be estimated.
+A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
+
+Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not estimated using DTI
 
@@
 
+This estimation framework also has theoretical implications.
+This estimation framework has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
+For example, it has been hypothesised that so called bump solutions are a possible mechanism for short term memory formation~\cite{Coombes2005}.
+Using this framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
+Therefore, this framework has the potential to validate models and test theoretically derived hypotheses.
+Associating regions of state-space and parameter sets to cognitive can potentially validate theoretical findings.
+For example, sleep, wake, memory,
+
+Here we assumed knowledge of the width of the kernel basis functions. If a future work we plan to extend this work to unknown widths.
+
+In future work, we aim to show how heterogeneous can be modelled within this formulation.
+We will still assume a isotropic connectivity kernel however heterogeneities can be modelled by placing basis function c
+
 \begin{itemize}
@@
 Some sort of IC optimisation?}
-	\item the width of the connectivity basis functions \wtf{do you mean width of the kernel?
-I'm not sure about this - as the parameters increase the kernel width increases right?
-So maybe you mean the basis functions, but don't we estimate these widths from the frequency analysis?} here is known exactly.
-In practice we don't
-	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.
-\wtf{Unless you are going to specify the computational complexity, in terms of the number of basis functions, it might be better to say something like ``there is a relationship between the number of basis functions that represent the field and the computational complexity of the estimation algorithm - the more basis functions the longer it takes to estimate''}
-	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. \omg{hell yes. This should be front and centre!} 
+
 	\item The size of the dentritic arbour is consistent in the cortex. \omg{?}
-	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing. 
-	\item The flexibility of the approach 
-	\item Combining this method with other to incorporate longer range hetrogeneous connectivity. \omg{awesome} 
+
 	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
@@
 This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
-	\item Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
-Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
-Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
-Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
-	\item Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not estimated using DTI
 \end{itemize}
@@
 	\label{Euler Approximation} \lefteqn{\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =}\nonumber\\
-& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).\nonumber \\ 
+& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.\nonumber \\ 
 \end{eqnarray}
@@
 	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right)\nonumber \\
-&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).\nonumber \\ 
+&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.\nonumber \\ 
 \end{eqnarray}
@@
 \begin{equation}
-	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right),
+	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
 \end{equation}
@@
 &&\xi v_t\left(\mathbf{r}_{ij}\right)+T_s \Delta^2\sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{w\left(\mathbf{r}-\mathbf{r}_{ij}'\right)f\left( v_t\left( \mathbf{r}_{ij}'\right)\right)}}\nonumber\\
-&+& T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}), 
+&+& e_t(\mathbf{r}_{i,j}), 
 \end{eqnarray}
@@
  &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
-&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}}\nonumber\\
-&+&\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
 \end{eqnarray}
-Substituting Eq.~\ref{DefGamma} into Eq.~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+Substituting equation~\ref{DefGamma} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
 \begin{eqnarray}\label{eq:ReducedForm}
-	 \lefteqn{\mathbf{x}_{t+1} \nonumber= T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&-&\xi\mathbf{x}_t+\boldsymbol{\Gamma}^{-1}T_s\int_\Omega{\boldsymbol{\phi}(\mathbf{r}) u_t(\mathbf{r})d\mathbf{r}}\nonumber+\boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\
+	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+&-&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
 \end{eqnarray}

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
periodic commit. almost completed rough draft of discussion

@@
 \section{Discussion}\label{DiscussionSection}
-This paper presents a novel framework for model reduction to make estimation of neural field practical.
-This systematic model reduction allows for the choice a complexity.
-The level of detail of the field is related to the number and width of the field basis functions, thereby providing a flexible approach where detail and computational complexity can be tradeoff.
-For certain application it might be sufficient to capture only low (spatial) frequency dynamics.
+This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
+The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
 
-The frequency analysis and model selection tools presented in this paper specifies the sensor and field basis function arrangement required to form a state-space model to capture and model dominant cortical dynamics.
-These tools can be used to better design experiments and recording techniques to advance model based neural parameter estimation and avoid spatial aliasing.
-In addition, the assumption homogeneity can be relaxed where heterogeneity can be model by careful placement of field basis functions.
+The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model to capture and model dominant cortical dynamics.
+These tools can be used to better design electrophysiological recording techniques to advance model-based neural parameter estimation to avoid spatial aliasing.
+In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
 For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
@@
 To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-This is important as the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the fine spatial scale and the high degree of crossing of fibres\omg{ref}.
+The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the isotropic diffusion or water in grey matter, the fine spatial scale and the high degree of crossing of fibres~\cite{Assaf2008}.
 In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
 The model based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
-An advantage of these auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-The AR methods are complementary to the proposed model based framework and by combining these methods a more realistic model can be estimated.
+An advantage of the auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
+The AR and the proposed model-based methods are complementary, where they estimating connectivity at different spatial scales.
+Therefore, by combining these methods a more realistic model can be estimated.
 A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
-
-Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not estimated using DTI
 
@@
 For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
+Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hoft bifurcation occurs~\cite{Hutt2005}, and types of oscillations that can be generated~\cite{Schmidt2009}.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
 In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
@@
 For example, it has been hypothesised that so called bump solutions are a possible mechanism for short term memory formation~\cite{Coombes2005}.
-Using this framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
-Therefore, this framework has the potential to validate models and test theoretically derived hypotheses.
-Associating regions of state-space and parameter sets to cognitive can potentially validate theoretical findings.
-For example, sleep, wake, memory,
-
-Here we assumed knowledge of the width of the kernel basis functions. If a future work we plan to extend this work to unknown widths.
-
-In future work, we aim to show how heterogeneous can be modelled within this formulation.
-We will still assume a isotropic connectivity kernel however heterogeneities can be modelled by placing basis function c
+Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
+In addition exploration of parameters and the state-space can be explored during other cognitive tasks and states of arousal such as sleep and anaesthesia.
 
 \begin{itemize}
-	\item if we don't know the frequency analysis or the system is marginally sampled or under-sampled, the best we can do is have the basis functions the same as the sensor kernel.
-\wtf{why wouldn't it be better to have, say, twice as many basis functions as we have sensors, at half the width?}
-	\item alternatives to frequency analysis are model selection...
-\wtf{This frequency analysis \emph{is} model selection.
-Maybe what's meant here is that other model selection approaches could be applied?
-Some sort of IC optimisation?}
-
-	\item The size of the dentritic arbour is consistent in the cortex. \omg{?}
-
+	\item Here we assumed knowledge of the width of the kernel basis functions. If a future work we plan to extend this work to unknown widths. 
+	\item The size of the dentritic arbour is consistent in the cortex. This implies global isotropy. Heterogeneity is less consistent. 
 	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
-	\item Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
 \end{itemize}

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
periodic commit. still adding bits to the discussion

@@
 The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field.
-Thus, the minimum distance between basis must satisfy
-\begin{equation}
+Thus, the minimum distance between basis functions must satisfy
+\begin{equation}\label{eq:BasisFunctionSeparation}
 	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
@@
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
-
 \begin{center}
@@
 \end{center}
-
-The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm.
+The sensors were spaced in a regular square \omg{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \omg{1.44} which equals \omg{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \omg{$2.22$}~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
-Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field.
-\omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
+Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
    \begin{figure}[th]\label{fig:experimental design}
@@
 \subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{} shows the spatial frequency of the field.
-The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power.
+Figure~\ref{fig:FieldFFT} (part a.) shows the spatial frequency of the field.
+The cut-off frequency, $\nu_c$, was taken to be \omg{??} ($-3$~dB point).
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}.
-This confirms our separation was enough to prevent problems associated with aliasing.
+This confirms our separation of \omg{??} was enough to prevent problems associated with aliasing.
 
-The spatial frequency of the observations is shown in figure~\ref{}.
-The peak power of the spatial frequency of the observations was approximately $30$~dB.
-The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB.
-This provided a conservative The oversampling parameter $\rho=2$.
-From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion.
+The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis} (part c.).
+The peak power of the spatial frequency of the observations was approximately \omg{$??$}~dB.
+The cut-off frequency (-3~dB point) was taken to correspond to  approximately \omg{$??$}~dB.
+This provided a conservative estimate of the spatial bandwidth.
+The oversampling parameter $\rho_b$ was set to $??$ giving a minimum distance between basis functions of $??$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 \todo{maybe from Parham's derivation...
@@
 \subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
-Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
+Each realisation consisted of 200~ms of data and the estimation was applied to the final 195~ms, allowing the model filter the initial conditions.
 The initial state and parameters were unknown to the estimator.
@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTTrueField.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTEstimatedField.pdf}}\\
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTTrueField.pdf}}\label{fig:FieldFFT}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
 \caption{The average FFT of the hidden field; a: True field; b: Estimated field.}
@@
 The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
+The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}.
 
-The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model to capture and model dominant cortical dynamics.
-These tools can be used to better design electrophysiological recording techniques to advance model-based neural parameter estimation to avoid spatial aliasing.
-In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
-For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
-In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
+The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
+These tools can be also used to better design electrophysiological recording techniques to advance model-based neural parameter estimation in order to avoid spatial aliasing.
+The effect of the basis function decomposition will restrict the frequency content of the estimated field.
+This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT}.
+Since the frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel some information will be lost due the decomposition.
+The implication of this loss of information is the high spatial frequency content of the connectivity kernel.
+This is demonstrated in Figure~\ref{fig:KernelEstimates} of the results where the frequency content of the estimated connectivity kernel is less than the true kernel.
+
+Even though the high frequency content of the connectivity kernel is lost though the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
+This is illustrated in~\ref{fig:FieldEstimate}.
+In addition, the ratio of the kernel parameters falls into a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
+This indicates that the ratio of excitation to inhibition can be tracked with this approach.
 
 To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the isotropic diffusion or water in grey matter, the fine spatial scale and the high degree of crossing of fibres~\cite{Assaf2008}.
+The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion or water in grey matter, the fine spatial scale and the high degree of crossing of fibres~\cite{Assaf2008}.
 In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
@@
 
+In this paper the widths of the connectivity kernel basis functions are assumed to be known.
+In a future work we plan to extend this work to unknown widths.
+We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting estimation procedure take care of the weights.
+In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
+For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
+In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
+
 \begin{itemize}
-	\item Here we assumed knowledge of the width of the kernel basis functions. If a future work we plan to extend this work to unknown widths. 
-	\item The size of the dentritic arbour is consistent in the cortex. This implies global isotropy. Heterogeneity is less consistent. 
-	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
+	\item What about the transient! The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
 \end{itemize}

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
periodic commit. added more to discussion. still need to discuss results more

@@
 	$v_0$ & 2 & mV\\
+	$\boldsymbol{\theta}$ & $\left[\begin{array}{ccc}
+	10 &-8 &0.5
+	\end{array}
+	\right]^{\top}$ & synaptic strength\\
+	$\sigma_{\psi,1}$ & 1.8 & inner connectivity kernel width\\
+	$\sigma_{\psi,2}$ & 2.4 & middle connectivity kernel width\\
+	$\sigma_{\psi,3}$ & 6 & outer connectivity kernel width\\
 	\hline\hline
@@
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT}.
-Since the frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel some information will be lost due the decomposition.
+This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field field is spatially band-limited.
+The frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition.
 The implication of this loss of information is the high spatial frequency content of the connectivity kernel.

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
figures updated to the final results

--- 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field  mathematical models from patient specific data.
+The ability to estimate such models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
+For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
+In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+
+Parameter estimation may have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{marten2009derivation}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+\omg{I extended this bit I am not sure how to connect it with the rest.
+Maybe the next paragraph can go.}
+% 
+% The human brain is composed of approximately 100 billion neurons and 60 trillion synapses operating in concert and, despite decades of research, our understanding of neural dynamics remains modest.
+Hence research has focused on different scales of dynamics: from individual proteins, synapses, and neurons; to neuronal networks and ensembles of neuronal networks.
+
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
@@
 Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations.
-This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations, marking a first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
@@
 
-This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher order systems via a systematic model reduction procedure.
+This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher dimensional systems utilising a systematic model reduction procedure.
 In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
@@
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Next, a reduced finite dimensional neural field model is derived.
+Next, a reduced finite dimensional neural field model is derived in Section~\ref{ReducedModelSection}.
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
+Section~\ref{SpectralAnalysisSection} then establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
 Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
@@
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC or Amari style neural field model \cite{Wilson1973,Amari1977} that was used to create our intracortical connectivity estimator.
+\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model \cite{Wilson1973} that was used to create our intracortical connectivity estimator.
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009}~\cite{Qubbaj2007}.
 Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour.
+\begin{todo}
+	{Really need to add some citations here.} 
+\end{todo}
+It is also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations. 
+\begin{todo}
+	{Same here.} 
+\end{todo}
 
@@
 
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $r$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 \end{equation}
-The post-synaptic response kernel $h(t)$ is described by 
+The post-synaptic response kernel $h(t)$ is described by \todo{citation needed} \omg{this is about the most vanilla bit} 
 \begin{equation}
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right),
 \end{equation}
 where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
-The connectivity kernel is typically a ``Mexican hat'' function which describes strong local activation, weak mid-range repression and weak long-range activation.
+The term $u\left(\mathbf{r},t\right)$ represents a known external input \wtf{Do we actually use the input in this paper, or is it just dragged around the derivation to be discarded in the conclusion?}.
+The connectivity kernel is typically a ``Mexican hat'' function \todo{which describes strong local activation, weak mid-range repression and weak long-range activation \cite{}}.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
@@
 The parameter $\varsigma$ governs the slope of the sigmoid.
-By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
+By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
 \begin{eqnarray}
 	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) &=&  \int_{-\infty}^t h\left(t - t'\right) \\
-	&\times&\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}'dt'. \nonumber
+	&\times&\left(\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}' + u(\mathbf{r},t) \right)dt'. \nonumber
 \end{eqnarray}
@@
 	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
-	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. \nonumber
+	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)dr'} + u\left(\mathbf{r},t\right). \nonumber
 \end{eqnarray}
-To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see Appendix~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
 \begin{eqnarray}
 	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
-	&+& e_t\left(\mathbf{r}\right), 
+	&+& T_s u_t\left(\mathbf{r}\right) + e_t\left(\mathbf{r}\right), 
 \end{eqnarray}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is i.i.d.
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t$ is i.i.d.
 such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
@@
 \subsection{Derivation of Finite Dimensional State-Space Model}
+
 In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
@@
  Decomposition allows a continuous field to be represented by a finite dimensional state vector.
-This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
+This allows for the application of standard nonlinear, non-Gaussian state estimation methods such as the unscented Kalman filter.
 The field decomposition is described by
@@
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
-Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
+Making substitutions of~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
 \begin{eqnarray}
 	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}&=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}\nonumber \\
-	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + T_s u_t(\mathbf{r})+ e_t(\mathbf{r}). 
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t\right) + \mathbf{e}_t 
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right) + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right) + \mathbf{e}_t 
 \end{eqnarray}
@@
 \begin{eqnarray}
-Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
+Q\left(\mathbf{x}_t,u_t(\mathbf{r})\right)&=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + k\left(u_t\left(\mathbf{r}\right)\right)\label{eq:QmatrixForSigmapoints}\\
+	k(u_t(\mathbf{r})) &=& \boldsymbol{\Gamma}^{-1}T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}} \\
 	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, 
@@
 \section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}.
-Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
+Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.
 
@@
 Conversely, a wider kernel bandwidth will govern the system bandwidth.
+\wtf{this bit incites trouble: Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.}
 
@@
 Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
-Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something.
-These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function.
-Can we remove the sentence ``Such a condition is usually satisfied...'' }.
+Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}}.
 Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
-Note that for the 2-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
-Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+Note that for the 3-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$.
+Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
 \begin{equation}
-	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
+	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho\nu_c}, 
 \end{equation}
-where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
+where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter.
+Satisfying this condition is required for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$.
 If the condition is not satisfied, spatial aliasing will occur.
@@
 The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors).
-The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter.
+The second is to use wider sensors, which act like an anti-aliasing filters.
 This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field.
-In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations.
+However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques.
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
@@
 Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition.
-The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field.
+The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem.
 Thus, the minimum distance between basis must satisfy
 \begin{equation}
-	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
+	\Delta_b < \frac{1}{2\nu_c}. 
 \end{equation}
-where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observation.
-For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
+For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
 The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
 \begin{equation}\label{eq:GaussianFT}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
 \end{equation}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
+width $\sigma^2_{\nu}$ should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_c$ giving
 \begin{equation}\label{eq:WidthFrequencyRelationship}
@@
 \end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co} $.
-Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in Appendix~\ref{ap:FrequencyAnalysis}.
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $.
+Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in Appendix~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
 
-The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
+The dynamic field must be spatially oversampled by using a larger number of sensor then imposed by frequency considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
 Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+For a spatially homogeneous isotropic field the basis functions can be placed on a regular square grid.
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, that scale the field basis functions and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
-The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
-At each iteration, the sequence of estimated states is used to update the parameter set, then resulting parameters are used to estimate a new state vector for the next iteration.
-The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state sequence which guarantees the initial estimated parameter set forms a stable kernel.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe  estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+At each iteration, a sequence of estimated states is used to calculate the parameter set and the resulting parameters is used to generate a new sequence of states for the next iteration.
+The procedure stops when the algorithm converges.
+The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
+\label{StateAndParameterEstimationSection}
 
-The Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
-The URTSS uses the unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
-The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
-The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows
+In this section we describe the procedure for estimating the states that scale the field basis functions, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process consists of a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+At each iteration, the state estimate sequence is used to calculate the parameter set and the resulting parameters are used to generate a new state sequence for the next iteration.
+The procedure stops when the algorithm converges.
+The algorithm is initialized using a bounded random state sequence which guarantees the initial parameter set forms a stable kernel.
+
+The state estimation technique uses the Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010}.
+The URTSS uses the Unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in the forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The first and the second order moments of the predicted state is captured by propagating the so-called sigma points through the state equation.
+The sigma points $\mathcal X_i$ are calculated using the unscented transform as follows
 \begin{equation}\label{eq:sigmapoints1}
@@
 \end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i$th column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+where $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i$th column of the weighted matrix square root of  $\mathbf P_x$ and  $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 where $\alpha$, $\beta$ and $\kappa$ are constants (see ~\cite{Haykin2001} for more details).
+It should be noted that $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$ and $\mathbf{P}_x$ represents the corresponding covariance matrix from the filtering or smoothing.
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance.
@@
 \end{equation}
-Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are  used to correct the predicted states.
+Since the observation equation \ref{ObservationEquation} is linear the standard Kalman Filter update equations can be used to update the predicted states.
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the predicted cross-covariance matrix of the states is also calculated.
-A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
+In order to compute the smoother gain the predicted cross-covariance matrix of the states needs to be calculated.
+A summary of the URTSS procedure is given in algorithm~\ref{UKFAlgorithm}.
 It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used , otherwise the state vector should be augmented with the noise terms.
@@
 Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
-The EKF approximates the state transition equation by linearising about the current state estimates (by calculating the Jacobian) at each time instance.
-The linearisation maintains the Gaussianality of the model.
+The EKF approximates the state transition equation by linearizing about the current state estimates (by calculating the Jacobian) at each time instance.
+The linearisation maintains the Gaussianity of the model.
 The unscented Kalman filter approximates the posterior state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
@@
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}
-\caption{Distribution of the parameters estimates over 272
+\caption{Distribution of the parameters estimates over 250
 runs.}
@@
 
-\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
+\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
 Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
@@
 \includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate_KernelFreqResponse.pdf}
-\caption{Mean kernel estimates over 200 runs ;  true and estimated kernels are shown by solid
-and dashed line respectively, the red area shows 95\% confedence interval; top: spatial domain; bottom: frequency domain}
+\caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
+and dashed line respectively, the gray area shows 95\% confedence interval; top: spatial domain; bottom: frequency domain}
 \label{fig:KernelEstimates}
@@
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{Distribution of the parameters ratios over 272 runs.}
+\caption{Distribution of the parameters ratios over 250 runs.}
 \end{figure}
@@
 \end{figure*}
-
 \section{Discussion}\label{DiscussionSection}
-This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
-The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
-
-The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model to capture and model dominant cortical dynamics.
-These tools can be used to better design electrophysiological recording techniques to advance model-based neural parameter estimation to avoid spatial aliasing.
-In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
-For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
-In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
-
-To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the isotropic diffusion or water in grey matter, the fine spatial scale and the high degree of crossing of fibres~\cite{Assaf2008}.
-In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
-The model based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
-An advantage of the auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-The AR and the proposed model-based methods are complementary, where they estimating connectivity at different spatial scales.
-Therefore, by combining these methods a more realistic model can be estimated.
-A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
-
-Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hoft bifurcation occurs~\cite{Hutt2005}, and types of oscillations that can be generated~\cite{Schmidt2009}.
+\begin{itemize}
+	\item if we don't know the frequency analysis or the system is marginally sampled or under-sampled, the best we can do is have the basis functions the same as the sensor kernel.
+\wtf{why wouldn't it be better to have, say, twice as many basis functions as we have sensors, at half the width?}
+	\item alternatives to frequency analysis are model selection...
+\wtf{This frequency analysis \emph{is} model selection.
+Maybe what's meant here is that other model selection approaches could be applied?
+Some sort of IC optimisation?}
+	\item the width of the connectivity basis functions \wtf{do you mean width of the kernel?
+I'm not sure about this - as the parameters increase the kernel width increases right?
+So maybe you mean the basis functions, but don't we estimate these widths from the frequency analysis?} here is known exactly.
+In practice we don't
+	\item the number of basis functions could be set higher to get a better representation of the field, however this is limited by computation complexity.
+\wtf{Unless you are going to specify the computational complexity, in terms of the number of basis functions, it might be better to say something like ``there is a relationship between the number of basis functions that represent the field and the computational complexity of the estimation algorithm - the more basis functions the longer it takes to estimate''}
+	\item Discuss the novelty of using the reduced model (BrainIDE) for creating patient specific models. \omg{hell yes. This should be front and centre!} 
+	\item The size of the dentritic arbour is consistent in the cortex. \omg{?} 
+	\item Spatial frequency of field and the relationship to the required density of electrodes/sensors required for estimation or to capture the required information without aliasing. 
+	\item The flexibility of the approach 
+	\item Combining this method with other to incorporate longer range hetrogeneous connectivity. \omg{awesome} 
+	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
+	\item Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs the bifurcation points of the system \cite{Hutt2005} and types of oscillations that can be generated \cite{Schmidt2009}.
 This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
-In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
-
-Parameter estimation may have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-
-This estimation framework also has theoretical implications.
-This estimation framework has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
-For example, it has been hypothesised that so called bump solutions are a possible mechanism for short term memory formation~\cite{Coombes2005}.
-Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
-In addition exploration of parameters and the state-space can be explored during other cognitive tasks and states of arousal such as sleep and anaesthesia.
-
-\begin{itemize}
-	\item Here we assumed knowledge of the width of the kernel basis functions. If a future work we plan to extend this work to unknown widths. 
-	\item The size of the dentritic arbour is consistent in the cortex. This implies global isotropy. Heterogeneity is less consistent. 
-	\item The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
+	\item Estimating functional cortical connectivity via EEG promises to shed light on the hierarchy of brain regions that are involved in specific tasks, motivating the use of techniques like DCM.
+Other comparable methods are based on auto-regressive (AR) modelling of the EEG, MEG, or fMRI times series \todo{[refs!]}.
+Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999}.
+Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data.
+	\item Long range connectivity can be estimated using DTI \cite{Knock2009}, however this short range connectivity can not estimated using DTI
 \end{itemize}
@@
 	\label{Euler Approximation} \lefteqn{\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =}\nonumber\\
-& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.\nonumber \\ 
+& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'} + u\left(\mathbf{r},t\right).\nonumber \\ 
 \end{eqnarray}
@@
 	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right)\nonumber \\
-&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.\nonumber \\ 
+&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right).\nonumber \\ 
 \end{eqnarray}
@@
 \begin{equation}
-	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
+	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} + T_s u_t\left(\mathbf{r}\right),
 \end{equation}
@@
 &&\xi v_t\left(\mathbf{r}_{ij}\right)+T_s \Delta^2\sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{w\left(\mathbf{r}-\mathbf{r}_{ij}'\right)f\left( v_t\left( \mathbf{r}_{ij}'\right)\right)}}\nonumber\\
-&+& e_t(\mathbf{r}_{i,j}), 
+&+& T_s u_t\left(\mathbf{r}\right) + e_t(\mathbf{r}_{i,j}), 
 \end{eqnarray}
@@
  &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
-&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+T_s \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) u_t\left(\mathbf{r}\right)d\mathbf{r}}\nonumber\\
+&+&\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
 \end{eqnarray}
-Substituting equation~\ref{DefGamma} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+Substituting Eq.~\ref{DefGamma} into Eq.~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
 \begin{eqnarray}\label{eq:ReducedForm}
-	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&-&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
+	 \lefteqn{\mathbf{x}_{t+1} \nonumber= T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+&-&\xi\mathbf{x}_t+\boldsymbol{\Gamma}^{-1}T_s\int_\Omega{\boldsymbol{\phi}(\mathbf{r}) u_t(\mathbf{r})d\mathbf{r}}\nonumber+\boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\
 \end{eqnarray}

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $200$ realisations of the data were generated.
-Each realisation consisted of 200~ms of data and the estimation was applied to the final 195~ms, allowing the model filter the initial conditions.
+\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
+Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
 The initial state and parameters were unknown to the estimator.

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some formating
commiting to merge

--- 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
- \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-% \documentclass[12pt]{iopart}
+ % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+\documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-% \usepackage{iopams,setstack} 
+\usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  \usepackage{anysize}							%<-use this for checking equation length
- \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
- \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
- \usepackage{amsmath}
+ % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+ % \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
-\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} 
+Starting from equation~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
 \begin{eqnarray}

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \begin{figure*}[!th]
+\centering 
 \subfigure[][]{\includegraphics[width=2in]{./Graph/TrueField90.pdf}}

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
EDITS TO DISCUSSION. ADDED DESCRIPTIONS OF PARAGRAPHS

@@
 \section{Discussion}\label{DiscussionSection}
+
+\omg{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FROM EDITING.}
+
+\omg{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
 This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
@@
 
+\omg{DISCUSS RESULTS: FREQ ANALYSIS. USE THIS TO JUSTIFY KERNEL ERRORS.}
 The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
@@
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field field is spatially band-limited.
-The frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition.
+This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
+The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition.
 The implication of this loss of information is the high spatial frequency content of the connectivity kernel.
@@
 
+\omg{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
 Even though the high frequency content of the connectivity kernel is lost though the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
 This is illustrated in~\ref{fig:FieldEstimate}.
-In addition, the ratio of the kernel parameters falls into a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
+In addition, the ratio of the kernel parameters follows a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
 This indicates that the ratio of excitation to inhibition can be tracked with this approach.
 
+\omg{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT}
+
+\omg{DISCUSS THE IMPLICATION OF ESTIMATING INTRACORTICAL CONNECTIVITY AND WHERE WE FIT WITHIN OTHER FUNCTIONAL CONNECTIVITY RESEARCH AREAS}
 To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion or water in grey matter, the fine spatial scale and the high degree of crossing of fibres~\cite{Assaf2008}.
+The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion or water in grey matter~\cite{Assaf2008}.
 In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
-The model based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
+The model-based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
 An advantage of the auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-The AR and the proposed model-based methods are complementary, where they estimating connectivity at different spatial scales.
-Therefore, by combining these methods a more realistic model can be estimated.
+It should be noted, however, that the AR and the proposed model-based methods are complementary, where connectivity is estimated at different spatial scales.
+Therefore, we envisage by combining these methods a more realistic model can be acquired.
 A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
 
+\omg{DISCUSS A BIG PICTURE. WHERE THIS WORK SHOULD GO AND WHERE IT SHOULD BE APPLIED ON THE FUTURE}
 Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hoft bifurcation occurs~\cite{Hutt2005}, and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to hyper-synchronous oscillatory states such as Turing patterns.
 In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
 
-Parameter estimation may have significant impact on the treatment of disease.
+Parameter estimation may also have significant impact on the treatment of disease.
 For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
@@
 
-This estimation framework also has theoretical implications.
-This estimation framework has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
+\omg{DISCUSS HOW IT CAN LINK THEORETICAL MODELLING STUDIES TO DATA.}
+This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
 For example, it has been hypothesised that so called bump solutions are a possible mechanism for short term memory formation~\cite{Coombes2005}.
@@
 
+\omg{DISCUSS SHORT-COMINGS AND FUTURE WORK}
 In this paper the widths of the connectivity kernel basis functions are assumed to be known.
@@
 \appendix 
-\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretization must be perform.
+\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be perform.
 We used a one-step Euler method where Eq.~\ref{FinalFormContinuous} can be approximated by

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to discussion. added more to first paragraph

@@
 
-% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 \begin{abstract}
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
+The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}.
 The width and positioning of the basis function can be determined by spectral analysis explain in detail in Section~\ref{SpectralAnalysisSection}.
@@
 
-The Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
 The URTSS uses the unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
+A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
 The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
-The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}.
+By forming a state-space model, the unscented Rauch Tung Striebel Smoother was implemented for state estimation.
+Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
 
@@
 
-\omg{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT}
+\omg{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT }
 

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added a conclusion draft

@@
 We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting estimation procedure take care of the weights.
-In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
+In addition, we plan to show in future work how the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
 For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
 In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
+This is a topic for future research.
+Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
 
@@
 \section{Conclusion}\label{ConclusionSection}
+This paper presented a novel model-based framework for patient-specific state and parameter estimation of neural fields.
+This framework enables a fundamental link between patient-specific physiologic data and theoretical neural field models.
+This link has the potential to lead to advances in our basic understanding of the dynamics of the brain at the macro/mesoscopic scale.
+Forming a greater understanding neural dynamics at this scale may lead to new and improved treatment options for diseases such as epilepsy.
+
 \appendix 

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small general edits to paper

@@
 
-\section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field mathematical models from patient specific data.
+\section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field mathematical models from patient-specific data.
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
@@
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to fit a general neural field model, like the Wilson and Cohen (WC) \cite{Wilson1973} model or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC) or Amari~\cite{Wilson1973,Amari1977} style model or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
 Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
@@
 \subsection{Derivation of the Integro-difference Equation Representation}
-
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added abstract to paper

@@
 \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+
 \begin{abstract}
-	Will do the abstract towards the end. 
+	This paper presents a framework for creating patient specific neural field models from electrophysiological data.
+A basis function decomposition of the Wilson and Cowen or Amari style neural field equations is used to form a state space model.
+Spatial frequency analysis methods are used for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field with the reduced finite dimensional model.
+Using the neural field model equation with modelled sensors, we generate data used to illustrate the state and parameter estimation framework.
+This framework provides a link between patient specific neurophysiological data and theoretical neural fields models.
+This link may lead to greater understanding of cortical dynamics at the meso and macroscopic scale where diseases such as epilepsy are manifested.
 \end{abstract}

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some changes to the plots

--- 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
- % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+ \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
- % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
- % \usepackage{amsmath}
+ \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+ \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}.
 The width and positioning of the basis function can be determined by spectral analysis explain in detail in Section~\ref{SpectralAnalysisSection}.
@@
 
-The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The Unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
 The URTSS uses the unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
 
@@
 \section{Discussion}\label{DiscussionSection}
+This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
+The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
+The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}.
 
-\omg{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FROM EDITING.}
-
-\omg{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
-This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
-A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
-The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
-By forming a state-space model, the unscented Rauch Tung Striebel Smoother was implemented for state estimation.
-Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
-
-\omg{DISCUSS RESULTS: FREQ ANALYSIS. USE THIS TO JUSTIFY KERNEL ERRORS.}
 The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
@@
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
-The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition.
+This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field field is spatially band-limited.
+The frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition.
 The implication of this loss of information is the high spatial frequency content of the connectivity kernel.
@@
 
-\omg{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
 Even though the high frequency content of the connectivity kernel is lost though the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
 This is illustrated in~\ref{fig:FieldEstimate}.
-In addition, the ratio of the kernel parameters follows a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
+In addition, the ratio of the kernel parameters falls into a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
 This indicates that the ratio of excitation to inhibition can be tracked with this approach.
 
-\omg{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT }
-
-\omg{DISCUSS THE IMPLICATION OF ESTIMATING INTRACORTICAL CONNECTIVITY AND WHERE WE FIT WITHIN OTHER FUNCTIONAL CONNECTIVITY RESEARCH AREAS}
 To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion or water in grey matter~\cite{Assaf2008}.
+The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion or water in grey matter, the fine spatial scale and the high degree of crossing of fibres~\cite{Assaf2008}.
 In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
-The model-based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
+The model based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
 An advantage of the auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-It should be noted, however, that the AR and the proposed model-based methods are complementary, where connectivity is estimated at different spatial scales.
-Therefore, we envisage by combining these methods a more realistic model can be acquired.
+The AR and the proposed model-based methods are complementary, where they estimating connectivity at different spatial scales.
+Therefore, by combining these methods a more realistic model can be estimated.
 A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
 
-\omg{DISCUSS A BIG PICTURE. WHERE THIS WORK SHOULD GO AND WHERE IT SHOULD BE APPLIED ON THE FUTURE}
 Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hoft bifurcation occurs~\cite{Hutt2005}, and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to hyper-synchronous oscillatory states such as Turing patterns.
+This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to various oscillatory states.
 In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
 
-Parameter estimation may also have significant impact on the treatment of disease.
+Parameter estimation may have significant impact on the treatment of disease.
 For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
@@
 
-\omg{DISCUSS HOW IT CAN LINK THEORETICAL MODELLING STUDIES TO DATA.}
-This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
+This estimation framework also has theoretical implications.
+This estimation framework has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
 For example, it has been hypothesised that so called bump solutions are a possible mechanism for short term memory formation~\cite{Coombes2005}.
@@
 
-\omg{DISCUSS SHORT-COMINGS AND FUTURE WORK}
 In this paper the widths of the connectivity kernel basis functions are assumed to be known.
@@
 We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting estimation procedure take care of the weights.
-In addition, we plan to show in future work how the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
+In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
 For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
 In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
-This is a topic for future research.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
 
@@
 \section{Conclusion}\label{ConclusionSection}
-This paper presented a novel model-based framework for patient-specific state and parameter estimation of neural fields.
-This framework enables a fundamental link between patient-specific physiologic data and theoretical neural field models.
-This link has the potential to lead to advances in our basic understanding of the dynamics of the brain at the macro/mesoscopic scale.
-Forming a greater understanding neural dynamics at this scale may lead to new and improved treatment options for diseases such as epilepsy.
-
 \appendix 
-\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be perform.
+\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretization must be perform.
 We used a one-step Euler method where Eq.~\ref{FinalFormContinuous} can be approximated by
@@
 where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
-\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} 
-Starting from equation~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
+\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} Starting from Eq.~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get
 \begin{eqnarray}

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some small paper edits and committing to merge with parham

--- 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
-Until now, estimation of local intracortical connectivity structure has not been attempted.
+Until now, estimation of local intracortical connectivity structure has not been reported (to the best of the authors knowledge).
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+In certain regoins of the cortex, each column is thought be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
@@
 \end{eqnarray}
-To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see Appendix~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
 \begin{eqnarray}
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}.
-The width and positioning of the basis function can be determined by spectral analysis explain in detail in Section~\ref{SpectralAnalysisSection}.
+The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+The width and positioning of the basis function can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
 The connectivity kernel can also be considered a decomposition into a set of basis functions in
@@
 \end{equation}
-and manipulating the model (see Appendix~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
+and manipulating the model (see~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
 \begin{eqnarray}
@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}.
-Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}.
+Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
 
@@
 Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
-Note that for the 2-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
@@
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
 This is further illustrated our results.
@@
 where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observation.
-For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}.
+For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
 The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
@@
 This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co} $.
-Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in Appendix~\ref{ap:FrequencyAnalysis}.
+Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 	$\sigma_{\psi,3}$ & 6 & outer connectivity kernel width\\
+	$\Sigma$ & & field disturbance covariance \\
+	sensor parameters & & \\
+	$\Delta$ & 0.5 & space step \\
+	$T_s$ & 1 & ms time step \\ 
 	\hline\hline
@@
 Example of the neural field with sensors.
-The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
+The centres of the sensors are shown by crosses.
 \textbf{b} Example of data generated by the model through the observations.
@@
 \caption{Distribution of the parameters estimates over 250
-runs.}
+runs.
+True parameters are $\zeta=100$, $\theta_0 = 10$, $\theta_1 = -8$, $\theta_3 = 0.5$.
+Grey bars show distributions with wider basis functions and blue bars show improved parameter distributions with narrower basis functions.}
 \label{fig:Parameters}
@@
 	\end{center}
-	\caption{a:Field basis function frequency response; b:Sensor frequency response ; c: The average FFT of the observed field.} 
+	\caption{a:Field basis function frequency response (projected to a 1D plot because it is symmetric); b:Sensor frequency response (projected to a 1D plot because it is symmetric); c: The average FFT of the observed field.}
 \label{fig:FreqAnalysis} 
@@
 \caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
-and dashed line respectively, the gray area shows 95\% confedence interval; top: spatial domain; bottom: frequency domain}
+and dashed line respectively, the grey area shows 95\% confidence interval; Top: spatial domain; Bottom: frequency domain}
 \label{fig:KernelEstimates}
@@
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
-\caption{The average FFT of the hidden field; a: True field; b: Estimated field.}
+\caption{The average FFT of the neural field; a: True field; b: Estimated field (showing the limited bandwidth).}
 \label{fig:FFTTrueEstimate}

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editing in LS for the zero input

@@
 \end{eqnarray}
-by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} with zero input and using $\xi = 1-\zeta T_s$ at each time instant we can write
+by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} and using $\xi = 1-\zeta T_s$ at each time instant we can write
 \begin{eqnarray}

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added notes for ken

@@
 This is further illustrated our results.
+\omg{Although our results are severely effected by the loss of high frequency info!
+Ken: Do you think you can word this a little better than what I have done.}
 
@@
 Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+\omg{Ken: can you please write something about what should be done in this case?} For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
 Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editted the abstract

@@
 \begin{abstract}
-	This paper presents a framework for creating patient specific neural field models from electrophysiological data.
-A basis function decomposition of the Wilson and Cowen or Amari style neural field equations is used to form a state space model.
-Spatial frequency analysis methods are used for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field with the reduced finite dimensional model.
-Using the neural field model equation with modelled sensors, we generate data used to illustrate the state and parameter estimation framework.
+	This paper presents a framework for creating patient-specific neural field models from electrophysiological data.
+The Wilson and Cowen or Amari style neural field equations are used as the parametric form of the model, where the parameters are estimated from data.
+To illustrate the estimation framework, data is generated using modelled sensors and the field model.
+We introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model to facilitate state and parameter estimation.
+Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
+The estimation process consists of a two stage algorithm, incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant.
+The results illustrate the cost of the model reduction with a loss of the high spatial frequency information.
 This framework provides a link between patient specific neurophysiological data and theoretical neural fields models.
-This link may lead to greater understanding of cortical dynamics at the meso and macroscopic scale where diseases such as epilepsy are manifested.
+This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.
 \end{abstract}

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
plot of Mean of absolute error and the std
editting paper body

@@
 The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
-The width and positioning of the basis function can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
-The connectivity kernel can also be considered a decomposition into a set of basis functions in
+The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
+The connectivity kernel can also be considered a decomposition into a set of basis functions where
 \begin{equation}\label{DefKernelDecomp}
@@
 The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter.
-This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field.
+This option is a compromise between alleviating issues with aliasing and losing high frequency information contained in the field.
 In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
@@
 \end{equation}
-where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observation.
+where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observations.
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editting paper body

@@
 The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
-At each iteration, the sequence of estimated states is used to update the parameter set, then resulting parameters are used to estimate a new state vector for the next iteration.
+At each iteration, the sequence of estimated states is used to update the parameter set, then the resulting parameters are used to estimate a new state vector for the next iteration.
 The procedure stops when the parameters converge.
 The algorithm is initialised using a bounded random state sequence which guarantees the initial estimated parameter set forms a stable kernel.
+\omg{Parham: can you please add to this to include the initialisation of the field?}
 

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
plot of mean of absolute error added again
editting paper body, merge again with Parham

@@
 The estimation process consists of a two stage algorithm, incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
-The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant.
+The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
 The results illustrate the cost of the model reduction with a loss of the high spatial frequency information.

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
fixed some typos in paper

@@
 \end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co} $.
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co}$.
 Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
-
 The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
@@
 \begin{equation}\label{eq:sigmapoints3}
-	\lambda=\alpha^2( L+\kappa)- L 
+	\lambda=\alpha^2( L+\kappa) - L 
 \end{equation}
-where $\alpha$, $\beta$ and $\kappa$ are constants (see ~\cite{Haykin2001} for more details).
+where $\alpha$ (determines spread of sigma points), $\beta$ (incorporate prior knowledge of the distribution of $\mathbf{x}$) and $\kappa$ (scaling parameter) are constants (see ~\cite{Haykin2001} for more details).
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance.
@@
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
-It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive the additive form of the URTS can be used , otherwise the state vector should be augmented with the noise terms.
-Using the additive form reduces the dimension and the number of sigma points used in the algorithm.
+It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive, therefore the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms.
+The additive form reduces the dimension and the number of sigma points used in the algorithm.
 \begin{algorithm}
@@
 
+  \begin{figure}
+   	\begin{center}
+   		\includegraphics[width=0.5\textwidth]{./Graph/MAE.pdf} 
+   	\end{center}
+   	\caption{The mean of the absolute error over time, gray area shows $\pm$STD.} 
+\label{fig:MAE}
+   \end{figure}
 \begin{figure*}[!th]

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
plots of the parameters convergence
kernel plots

@@
 %
- % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+  \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
- % \usepackage{amsmath}
+ \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 
@@
 \end{figure}
+\begin{figure}[th]
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/ZetaConvergence.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0Convergence.pdf}}\\
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1Convergence.pdf}}
+\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2Convergence.pdf}}
+\caption{Convergence of the parameters: averaged over 250 runs.}
+\label{fig:ParametersConvergence}
+\end{figure}
+
 \subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
@@
 One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{./Graph/KernelEstimate_KernelFreqResponse.pdf}
+\begin{figure*}
+\subfigure[][]{\includegraphics{./Graph/KernelEstimate_skinny.pdf}}
+\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_skinny.pdf}}\\
+\subfigure[][]{\includegraphics{./Graph/KernelEstimate_wide.pdf}}
+\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_wide.pdf}}\\
+
 \caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
-and dashed line respectively, the grey area shows 95\% confidence interval; Top: spatial domain; Bottom: frequency domain}
+and dashed line respectively, the grey area shows 95\% confidence interval; Left: spatial domain; Right: frequency domain; a, b: wider basis functions; c,d: narrower basis functions.}
 \label{fig:KernelEstimates}
-\end{figure}
+\end{figure*}
 \begin{figure}[th]

### 2010-05-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to plots

@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}
+\subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
+\subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
+\subfigure[][]{\includegraphics{./Graph/theta1.pdf}}
+\subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
 \caption{Distribution of the parameters estimates over 250
@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/ZetaConvergence.pdf}}
+\subfigure[][]{\includegraphics[width=1.5in]{./Graph/ZetaConvergence.pdf}}
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0Convergence.pdf}}\\
@@
 	\begin{center}
-\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/BasisChar.pdf}}
-\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/SensorChar.pdf}}
-\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ObservationFrequencyResponse.pdf}}
+\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
+\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
+\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
 	\end{center}
@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta1_ratio.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta2_ratio.pdf}}\\
+\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
+\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
 \caption{Distribution of the parameters ratios over 250 runs.}
@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTTrueField.pdf}}\label{fig:FieldFFT}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
+\centering
+\subfigure[][]{\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}\label{fig:FieldFFT}
+\subfigure[][]{\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
 \caption{The average FFT of the neural field; a: True field; b: Estimated field (showing the limited bandwidth).}
@@
    	\begin{center}
-   		\includegraphics[width=0.5\textwidth]{./Graph/MRMSE.pdf} 
+   		\includegraphics{./Graph/MRMSE.pdf} 
    	\end{center}
-   	\caption{The RMSE of the estimated field over time.} 
+   	\caption{The mean of RMSE of the estimated field over 250 runs.} 
 \label{fig:RMSE}
-   \end{figure}
-
-  \begin{figure}
-   	\begin{center}
-   		\includegraphics[width=0.5\textwidth]{./Graph/MAE.pdf} 
-   	\end{center}
-   	\caption{The mean of the absolute error over time, gray area shows $\pm$STD.} 
-\label{fig:MAE}
    \end{figure}

### 2010-05-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to plots

@@
 \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_wide.pdf}}\\
+\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_skinny_db.pdf}}
 
 \caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
-and dashed line respectively, the grey area shows 95\% confidence interval; Left: spatial domain; Right: frequency domain; a, b: wider basis functions; c,d: narrower basis functions.}
+and dashed line respectively, the grey area shows 95\% confidence interval; Left: spatial domain; Right: frequency domain; a, b: wider basis functions; c,d: narrower basis functions.**************************Guys the bottom left figure is the power in db for skinny basis functions}
 \label{fig:KernelEstimates}

### 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits

@@
 %
-  \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-% \documentclass[12pt]{iopart}
+  % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+\documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-% \usepackage{iopams,setstack} 
+\usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ % \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
  %  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
- \usepackage{amsmath}
+ % \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
 
@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-The estimation process consists of a two stage algorithm, incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+We use the reduced model for the estimation that consists of a two stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
 The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
@@
 \end{equation}
-The observation equation of the reduced model is 
+The observation equation of the reduced model is \omg{Should this be $\mathbf{y}_t \approx \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t$}
 \begin{equation}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
+The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving
 \begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
+ \sigma^2_{\nu}=\frac{2\boldsymbol\nu_{co}^\top \boldsymbol\nu_{co}}{\ln 2}.
 \end{equation}
@@
 A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
-The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
+The level of detail of the estimated field is related to the basis functions decomposition, thereby flexible framework is provided where a trade-off can be made between physiological detail and computational complexity.
 By forming a state-space model, the unscented Rauch Tung Striebel Smoother was implemented for state estimation.

### 2010-05-12 src/ODE_ex.py

@@ -40,7 +40,7 @@ beta_variance=1.3**2
 alpha=100
 threshold=2
 nu=20
-beta=.8
+beta=30
 act_func=ActivationFunction(threshold,nu,beta)
 #----------observations--------------------------
 Delta_s = 1.5	# mm

### 2010-05-12 src/ODE_ex.py
paper edits - fixed typo in eq 14

@@ -69,7 +69,7 @@ pb.show()
 # -------Sampling properties-------------
 Fs = 1e3   #sampling rate                                       
 Ts = 1/Fs   #sampling period, second
-t_end = .08 # seconds
+t_end = 1 # seconds
 NSamples = t_end*Fs;
 T = pb.linspace(0,t_end,NSamples);
 

### 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits - fixed typo in eq 14
paper edits - freq analysis section

@@
 
+\omg{show figure with the Mexican hat here.}
+
 The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
@@
 	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}&=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}\nonumber \\
-	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
 \end{eqnarray}
@@
 Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
+% 
+% Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
 Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something.
@@
 Can we remove the sentence ``Such a condition is usually satisfied...'' }.
-Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
-Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$,
+% 
+% Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
@@
 \end{equation}
-where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
+where $\boldsymbol{\nu}_c$ the cut-off frequency, $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
 This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
@@
  &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
-&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
 \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
@@
 	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&-&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
+&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
 \end{eqnarray}

### 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits - freq analysis section

@@
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
+The Fourier transform of an \textit{n}-dimensional Gaussian
+\begin{equation}\label{eq:nDimensionalGaussian}
+	\phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
+\end{equation}
+ is another Gaussian given by
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving
+The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving \omg{need to rewrite eq~\ref{eq:WidthFrequencyRelationship} in terms of $\sigma_{\phi}$.
+At the mo it is writen in terms of $\sigma_{nu}$}
 \begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu}=\frac{2\boldsymbol\nu_{co}^\top \boldsymbol\nu_{co}}{\ln 2}.
+ \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{co}}^2},
+\end{equation}
+where
+\begin{equation}\label{eq:WidthFrequencyRelationship}
+ \sigma^2_{\nu_{co}}= \frac{2\boldsymbol\nu_{co}^\top \boldsymbol\nu_{co}}{\ln 2}.
 \end{equation}

### 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Changes to section 3  Please enter the commit message for your changes. Lines starting

--- 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-  % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+  \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
  % \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
- % \usepackage{amsmath}
+ \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 \newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}
+\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
+\newcommand{\haq}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
+\begin{document}
 
@@
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Deaprtment of Systems and Control Engeineering, University of Malta, Msida, MSD 1333, Malta} \ead{dfreestone@bionicear.org}
 
@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model for the estimation that consists of a two stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+The estimation process consists of a two stage algorithm, incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
 The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
@@
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
-While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a theoretical.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a theoretical one.
 Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regoins of the cortex, each column is thought be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
+\haq{Risky comment if we don't get better estimates.}
 
@@
 such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
-This term was added to account for uncertainty in the model.
-To generate iEEG/LFP data we used the output function
+\haq{Can we remove noise form 8 and introduce only discretization there; then introduce noise in another equation.} This term was added to account for uncertainty in the model.
+To represent the iEEG/LFP data collection precedure we used the output function
 \begin{equation}
@@
 \end{equation}
-and manipulating the model (see~\ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
+and manipulating equation \ref{reduced continuous model} (see Appendix \ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
 \begin{eqnarray}
@@
 \end{equation}
-The observation equation of the reduced model is \omg{Should this be $\mathbf{y}_t \approx \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t$}
+The observation equation of the reduced model is 
 \begin{equation}
@@
 
-The spectral characteristics of the field are governed by the shape of the connectivity kernel and the covariance of the field disturbance.
-If the bandwidth of the field disturbance covariance is wider than the bandwidth of the connectivity kernel, then the disturbance covariance governs the bandwidth of the system.
-Conversely, a wider kernel bandwidth will govern the system bandwidth.
-
 Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
-Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something.
-These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function.
-Can we remove the sentence ``Such a condition is usually satisfied...'' }.
-Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
-Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
-Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+Then, based on Shannon's sampling Theorem, for an accurate representation of this field by spatially discrete observations, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency with  $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Given such a band-limited field, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
 \begin{equation}
@@
 where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
-If the condition is not satisfied, spatial aliasing will occur.
+This condition must be satisfied to avoid spectral aliasing effects in the representation of the hidden dynamic field $v_t(\mathbf{r})$ by the sampled observations, $\mathbf{y}_t$.
 
-There are two options available to alleviate problems with aliasing.
-The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors).
-The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter.
-This option is a compromise between alleviating issues with aliasing and losing high frequency information contained in the field.
-In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
-This is further illustrated our results.
-\omg{Although our results are severely effected by the loss of high frequency info!
-Ken: Do you think you can word this a little better than what I have done.}
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to \ref{eq:MinimumSensorDistance}.
+However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics.
+Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-alaising filtering.
+Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$.
+Aliasing can then be avoided by positioning the sensors according to \ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
+
+Although such sensors avoid errors due to alaising, they attentuate the high frequency variations in the observations.
+Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel.
+Such a remark motivates the use of sensors with wider bandwidths.
+Nevertheless, this choice would require an excessive number or sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response and therefore the accurate of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
 
@@
 \end{equation}
-where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observations.
+where $\rho_b$ is an over-sampling parameter to determine the basis function separation.
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
@@
 \end{equation}
-The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving
+The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
 \begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu}=\frac{2\boldsymbol\nu_{co}^\top \boldsymbol\nu_{co}}{\ln 2}.
+ \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
 \end{equation}
@@
 Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
-% Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
-The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
-Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-\omg{Ken: can you please write something about what should be done in this case?} For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
-Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
+
+Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.
 
@@
 A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
-The level of detail of the estimated field is related to the basis functions decomposition, thereby flexible framework is provided where a trade-off can be made between physiological detail and computational complexity.
+The level of detail of the estimated field is related to the basis functions decomposition, thereby providing a flexible approach where a trade-off can be made between physiological detail and computational complexity.
 By forming a state-space model, the unscented Rauch Tung Striebel Smoother was implemented for state estimation.

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
loads of little edits and typos, up to line 285. Dinner time!

--- 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
-While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a theoretical.
-Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
+Understanding the brain at this level is extremely important since it is this scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews).
@@
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC) or Amari~\cite{Wilson1973,Amari1977} style model or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC) or Amari~\cite{Wilson1973,Amari1977}  models or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
 Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
@@
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development in that work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observations (recording electrodes in this case).
+The key development here was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observation locations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
 
-Modelling the neural dynamics within this framework has the distinct advantage over the more standard multivariate auto-regressive (AR) models: that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (AR) models: that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
 
@@
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC or Amari style neural field model \cite{Wilson1973,Amari1977} that was used to create our intracortical connectivity estimator.
+\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model that was used to create our intracortical connectivity estimator.
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
-This term was added to account for uncertainty in the model.
-To generate iEEG/LFP data we used the output function
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{s}-\mathbf{r})$ \cite{Rasmussen2006} This term was added to account for uncertainty in the model.
+The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors, $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ and $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate Normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
+The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
 \begin{equation}
@@
 The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
-The connectivity kernel can also be considered a decomposition into a set of basis functions where
+The connectivity kernel can also be decomposed into a set of basis functions where
 \begin{equation}\label{DefKernelDecomp}
@@
 \begin{equation}
-	\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
+	\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{-1}
 \end{equation}
@@
 		\vdots & \ddots & \vdots \\
-		c_{n_y,L} & \dots & c_{n_y,L} 
+		c_{n_y,1} & \dots & c_{n_y,L} 
 	\end{array}
@@
 \end{equation}
-where $L$ is the number of basis functions and 
+where $L$ is the number of basis functions used to decompose the voltage field and 
 \begin{equation}
@@
 
-Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
+Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$. Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
 % 
@@
 In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+However, we envisage it may be possible the estimate the bandwidth of the cortex using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
@@
 \begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
+	\Delta_b < \frac{1}{2\rho_b\nu_{co}}
 \end{equation}
@@
 \end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co}$.
+This ensures that the basis functions can represent a field with frequency content up to $\boldsymbol\nu_{co}$.
 Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
-The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
+The dynamic field must be spatially oversampled using a larger number of sensors than imposed by the frequency analysis, to use frequency analysis to determine the minimum distance and width of the basis functions.
 Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-\omg{Ken: can you please write something about what should be done in this case?} For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
-Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
+\omg{Ken: can you please write something about what should be done in this case?} For a spatially isotropic field, the basis functions can be placed on a regular grid and hence the distance between basis functions dictates the total number of basis functions required.
 
@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, that scale the field basis functions and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
-The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
 At each iteration, the sequence of estimated states is used to update the parameter set, then the resulting parameters are used to estimate a new state vector for the next iteration.
@@
 
-The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
-The URTSS uses the unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
+The URTSS incorporates an unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
finished going through the body of the paper, making loads of little edits and correcting typos as I see 'em. Got up to the end of Section 7, haven't looked at the Appendices.

@@
 \end{equation}
-where $\alpha$ (determines spread of sigma points), $\beta$ (incorporate prior knowledge of the distribution of $\mathbf{x}$) and $\kappa$ (scaling parameter) are constants (see ~\cite{Haykin2001} for more details).
-The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance.
-The weights are calculated by
+where the constants $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is a scaling parameter (see ~\cite{Haykin2001} for more details).
+
+The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
 \begin{equation}
@@
 The additive form reduces the dimension and the number of sigma points used in the algorithm.
+
 \begin{algorithm}
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see Appendix~\ref{LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see~\ref{LeastSquaresAppendix}).
 
@@
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-An example of the simulated field can be seen in figure~\ref{fig:experimental design}~A.
-The Figure demonstrates the experimental design where the sensors were placed in the centre of the field (full width at half maximum).
+An example of the simulated field can be seen in figure~\ref{fig:experimental design}(a).
+This figure demonstrates the experimental design used: the sensors were placed in the centre of the field (full width at half maximum).
 This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
-Figure~\ref{fig:experimental design}~B.
-shows example data from the sensors of the model, and figure~\ref{fig:experimental design}~C.
-shows the power spectral density of the simulated time-series.
+Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
@@
 
-\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FieldFFT} (part a.) shows the spatial frequency of the field.
+\subsection{Spatial Frequency Analysis} 
+Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+Figure~\ref{fig:FieldFFT}(a) shows the spatial frequency of the field.
 The cut-off frequency, $\nu_c$, was taken to be \omg{??} ($-3$~dB point).
@@
 
-The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis} (part c.).
+The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis}(c).
 The peak power of the spatial frequency of the observations was approximately \omg{$??$}~dB.
@@
 or...}.
-The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
+The width of the basis functions was chosen such that the basis functions had sufficient overlap to represent the dynamic field.
 
-\begin{figure*}
+\begin{figure}
+	\label{fig:FreqAnalysis} 
 	\begin{center}
@@
 	\end{center}
-	\caption{a:Field basis function frequency response (projected to a 1D plot because it is symmetric); b:Sensor frequency response (projected to a 1D plot because it is symmetric); c: The average FFT of the observed field.}
-\label{fig:FreqAnalysis} 
-\end{figure*}
+	\caption{(a) Field basis function frequency response, (b) Sensor frequency response, (c) The average FFT of the observed field.}
+
+\end{figure}
 Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
-Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.
+\wtf{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}
 
-\subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
+\subsection{State and Parameter Estimates} 
+\label{sec:state_and_param_results}
+To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
 Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
@@
 A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
-The level of detail of the estimated field is related to the basis functions decomposition, thereby flexible framework is provided where a trade-off can be made between physiological detail and computational complexity.
+The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
 By forming a state-space model, the unscented Rauch Tung Striebel Smoother was implemented for state estimation.
@@
 The implication of this loss of information is the high spatial frequency content of the connectivity kernel.
-This is demonstrated in Figure~\ref{fig:KernelEstimates} of the results where the frequency content of the estimated connectivity kernel is less than the true kernel.
+This is demonstrated in Figure~\ref{fig:KernelEstimates} where the frequency content of the estimated connectivity kernel is less than the true kernel.
 
 \omg{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
-Even though the high frequency content of the connectivity kernel is lost though the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
+Even though the high frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
 This is illustrated in~\ref{fig:FieldEstimate}.
@@
 To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion or water in grey matter~\cite{Assaf2008}.
+The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
 In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
@@
 In this paper the widths of the connectivity kernel basis functions are assumed to be known.
-In a future work we plan to extend this work to unknown widths.
-We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting estimation procedure take care of the weights.
-In addition, we plan to show in future work how the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
+In future work we plan to extend this work to unknown widths.
+We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting the estimation procedure take care of the weights.
+In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
 For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
 In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
-This is a topic for future research.
 Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits and comments added

--- 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
-While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
-Understanding the brain at this level is extremely important since it is this scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely a theoretical.
+Understanding the brain at this level is extremely important since this is the scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews).
@@
 For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC) or Amari~\cite{Wilson1973,Amari1977}  models or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC) or Amari~\cite{Wilson1973,Amari1977} style model or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
 Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
@@
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development here was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observation locations (recording electrodes in this case).
+The key development in that work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
 
-Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (AR) models: that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+Modelling the neural dynamics within this framework has the distinct advantage over the more standard multivariate auto-regressive (AR) models: that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
 
@@
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model that was used to create our intracortical connectivity estimator.
+\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC or Amari style neural field model \cite{Wilson1973,Amari1977} that was used to create our intracortical connectivity estimator.
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+In certain regoins of the cortex, each column is thought be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
@@
 \begin{equation}
-	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
 \end{equation}
@@
 \begin{eqnarray}
-	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
+	\label{DiscreteTimeModel} v_{t+T_s}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
 	&+& e_t\left(\mathbf{r}\right), 
@@
 such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{s}-\mathbf{r})$ \cite{Rasmussen2006} This term was added to account for uncertainty in the model.
-The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function
+This term was added to account for uncertainty in the model.
+To generate iEEG/LFP data we used the output function
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors, $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ and $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate Normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
+where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$.
+The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where
 \begin{equation}
@@
 The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
-The connectivity kernel can also be decomposed into a set of basis functions where
+The connectivity kernel can also be considered a decomposition into a set of basis functions where
 \begin{equation}\label{DefKernelDecomp}
@@
 \begin{equation}
-	\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{-1}
+	\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top}
 \end{equation}
@@
 		\vdots & \ddots & \vdots \\
-		c_{n_y,1} & \dots & c_{n_y,L} 
+		c_{N,1} & \dots & c_{N,L} 
 	\end{array}
@@
 \end{equation}
-where $L$ is the number of basis functions used to decompose the voltage field and 
+where $L$ is the number of basis functions and 
 \begin{equation}
@@
 
-Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$. Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
+Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$, where $\nu$ denotes spatial frequency.
+Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
 % 
@@
 In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible the estimate the bandwidth of the cortex using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse \omg{problem} and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
 This is further illustrated our results.
@@
 \begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_b < \frac{1}{2\rho_b\nu_{co}}
+	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
 \end{equation}
@@
 \end{equation}
-This ensures that the basis functions can represent a field with frequency content up to $\boldsymbol\nu_{co}$.
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co}$.
 Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 % Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
-The dynamic field must be spatially oversampled using a larger number of sensors than imposed by the frequency analysis, to use frequency analysis to determine the minimum distance and width of the basis functions.
+The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions.
 Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-\omg{Ken: can you please write something about what should be done in this case?} For a spatially isotropic field, the basis functions can be placed on a regular grid and hence the distance between basis functions dictates the total number of basis functions required.
+\omg{Ken: can you please write something about what should be done in this case?} For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
 
@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
-The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, that scale the field basis functions and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step.
 At each iteration, the sequence of estimated states is used to update the parameter set, then the resulting parameters are used to estimate a new state vector for the next iteration.
@@
 
-The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
-The URTSS incorporates an unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The URTSS uses the unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
@@
 		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through equation \ref{eq:QmatrixForSigmapoints}
+		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
 % 		\begin{small}
 		\begin{equation*}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f,u_t) 
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) 
 		\end{equation*}
@@
 \subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
-Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
-The initial state and parameters were unknown to the estimator.
+Each realisation consisted of 200 ms of data and the estimation was applied to the final 195 ms, allowing the model to stabilise.
+\omg{transient!} The initial state and parameters were unknown to the estimator.
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
 Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-The state estimates for one realization were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
+The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
 The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE}.
@@
 \omg{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FROM EDITING.}
+
+POSSIBLE SOURCES OF THE ERROR
+\begin{itemize}
+	\item slope of nonlinearity interacting with tails of Gaussian basis functions
+	\item loss of high frequency info from basis function decomposition
+	\item distortions of the spectral content of the basis function from the nonlinearity
+	\item disturbance covariance to narrow
+	\item disturbance variance to low (no exciting the kernel enough)
+	\item boundary conditions
+	\item
+\end{itemize}
 
@@
 \end{eqnarray}
+\omg{DEFINE q HERE!!!!!}
 \section{}\label{ColoredNoise} 

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
-Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
-The initial state and parameters were unknown to the estimator.
+Each realisation consisted of 200 ms of data and the estimation was applied to the final 195 ms, allowing the model to stabilise.\omg{transient!} The initial state and parameters were unknown to the estimator.
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
 Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-The state estimates for one realization were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
+The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
 The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE}.
 One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
+
 \begin{figure*}

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
figure formatting

--- 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-\omg{show figure with the Mexican hat here.}
-
 The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
 \begin{equation}
-	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 \begin{eqnarray}
-	\label{DiscreteTimeModel} v_{t+T_s}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
+	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
 	&+& e_t\left(\mathbf{r}\right), 
@@
 	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}&=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}\nonumber \\
-	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
 \end{eqnarray}
@@
 		\vdots & \ddots & \vdots \\
-		c_{N,1} & \dots & c_{N,L} 
+		c_{n_y,L} & \dots & c_{n_y,L} 
 	\end{array}
@@
 
-Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$, where $\nu$ denotes spatial frequency.
-Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
-% 
-% Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
+Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
 Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something.
@@
 Can we remove the sentence ``Such a condition is usually satisfied...'' }.
-Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$,
-% 
-% Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency.
+Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
@@
 \end{equation}
-where $\boldsymbol{\nu}_c$ the cut-off frequency, $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
+where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
 This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
@@
 In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse \omg{problem} and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
+However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
 This is further illustrated our results.
@@
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-The Fourier transform of an \textit{n}-dimensional Gaussian
-\begin{equation}\label{eq:nDimensionalGaussian}
-	\phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
-\end{equation}
- is another Gaussian given by
+The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving \omg{need to rewrite eq~\ref{eq:WidthFrequencyRelationship} in terms of $\sigma_{\phi}$.
-At the mo it is writen in terms of $\sigma_{nu}$}
+The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
 \begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{co}}^2},
-\end{equation}
-where
-\begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu_{co}}= \frac{2\boldsymbol\nu_{co}^\top \boldsymbol\nu_{co}}{\ln 2}.
+ \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
 \end{equation}
@@
 		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
+		calculate the sigma points $\mathcal X_{i,t}^f$ using \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propogate them through equation \ref{eq:QmatrixForSigmapoints}
 % 		\begin{small}
 		\begin{equation*}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) 
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f,u_t) 
 		\end{equation*}
@@
 \subsection{State and Parameter Estimates} To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
-Each realisation consisted of 200 ms of data and the estimation was applied to the final 195 ms, allowing the model to stabilise.
-\omg{transient!} The initial state and parameters were unknown to the estimator.
+Each realisation consisted of 200 ms of data and the estimation was applied to the final 200 ms, allowing the model to stabilise.
+The initial state and parameters were unknown to the estimator.
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
 Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
+The state estimates for one realization were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
 The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE}.
@@
 \centering 
-\subfigure[][]{\includegraphics[width=2in]{./Graph/TrueField90.pdf}}
-\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimatedField90.pdf}}
-\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimationError90.pdf}}\\
+\subfigure[][]{\includegraphics[scale=0.8]{./Graph/TrueField90.pdf}}
+\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimatedField90.pdf}}
+\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimationError90.pdf}}\\
 \caption{One snapshot of the spatial field; a: True field; b: Estimated field; c: The absolute error.}
@@
 
-POSSIBLE SOURCES OF THE ERROR
-\begin{itemize}
-	\item slope of nonlinearity interacting with tails of Gaussian basis functions
-	\item loss of high frequency info from basis function decomposition
-	\item distortions of the spectral content of the basis function from the nonlinearity
-	\item disturbance covariance to narrow
-	\item disturbance variance to low (no exciting the kernel enough)
-	\item boundary conditions
-	\item
-\end{itemize}
-
 \omg{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
@@
  &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
-&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
 \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
@@
 	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
+&-&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
 \end{eqnarray}
-\omg{DEFINE q HERE!!!!!}
 \section{}\label{ColoredNoise} 

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Deaprtment of Systems and Control Engeineering, University of Malta, Msida, MSD 1333, Malta} \ead{dfreestone@bionicear.org}
 
@@
 \begin{equation}
-	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}.
 \end{equation}
@@
 
-The spectral characteristics of the field are governed by the shape of the connectivity kernel and the covariance of the field disturbance.
-If the bandwidth of the field disturbance covariance is wider than the bandwidth of the connectivity kernel, then the disturbance covariance governs the bandwidth of the system.
-Conversely, a wider kernel bandwidth will govern the system bandwidth.
-
-Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$, where $\nu$ denotes spatial frequency.
-Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
-% 
-% Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
-Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something.
-These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function.
-Can we remove the sentence ``Such a condition is usually satisfied...'' }.
-Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$,
-% 
-% Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
-Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
+Then, based on Shannon's sampling Theorem, for an accurate representation of this field by spatially discrete observations, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency with  $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Given such a band-limited field, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
 \begin{equation}
@@
 \end{equation}
-where $\boldsymbol{\nu}_c$ the cut-off frequency, $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
-If the condition is not satisfied, spatial aliasing will occur.
+where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
+This condition must be satisfied to avoid spectral aliasing effects in the representation of the hidden dynamic field $v_t(\mathbf{r})$ by the sampled observations, $\mathbf{y}_t$.
 
-There are two options available to alleviate problems with aliasing.
-The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors).
-The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter.
-This option is a compromise between alleviating issues with aliasing and losing high frequency information contained in the field.
-In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to \ref{eq:MinimumSensorDistance}.
 However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse \omg{problem} and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
-This is further illustrated our results.
-\omg{Although our results are severely effected by the loss of high frequency info!
-Ken: Do you think you can word this a little better than what I have done.}
+Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics.
+Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-alaising filtering.
+Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$.
+Aliasing can then be avoided by positioning the sensors according to \ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
+
+Although such sensors avoid errors due to alaising, they attentuate the high frequency variations in the observations.
+Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel.
+Such a remark motivates the use of sensors with wider bandwidths.
+Nevertheless, this choice would require an excessive number or sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response and therefore the accurate of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
 
@@
 \end{equation}
-where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observations.
+where $\rho_b$ is an over-sampling parameter to determine the basis function separation.
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-The Fourier transform of an \textit{n}-dimensional Gaussian
-\begin{equation}\label{eq:nDimensionalGaussian}
-	\phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
-\end{equation}
- is another Gaussian given by
+The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
+
 \begin{equation}\label{eq:GaussianFT}
@@
 \omg{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FROM EDITING.}
-
-POSSIBLE SOURCES OF THE ERROR
-\begin{itemize}
-	\item slope of nonlinearity interacting with tails of Gaussian basis functions
-	\item loss of high frequency info from basis function decomposition
-	\item distortions of the spectral content of the basis function from the nonlinearity
-	\item disturbance covariance to narrow
-	\item disturbance variance to low (no exciting the kernel enough)
-	\item boundary conditions
-	\item
-\end{itemize}
 
@@
 \end{eqnarray}
-\omg{DEFINE q HERE!!!!!}
 \section{}\label{ColoredNoise} 

### 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-05-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \end{equation}
-where $\boldsymbol{\nu}_c$ the cut-off frequency, $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$.
-If the condition is not satisfied, spatial aliasing will occur.
+where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
+This condition must be satisfied to avoid spectral aliasing effects in the representation of the hidden dynamic field $v_t(\mathbf{r})$ by the sampled observations, $\mathbf{y}_t$.
 
-There are two options available to alleviate problems with aliasing.
-The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors).
-The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter.
-This option is a compromise between alleviating issues with aliasing and losing high frequency information contained in the field.
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations.
-However, we envisage it may be possible the estimate the bandwidth of the cortex using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics.
-However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}.
-This is further illustrated our results.
-\omg{Although our results are severely effected by the loss of high frequency info!
-Ken: Do you think you can word this a little better than what I have done.}
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to \ref{eq:MinimumSensorDistance}.
+However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics.
+Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-alaising filtering.
+Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$.
+Aliasing can then be avoided by positioning the sensors according to \ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
+
+Although such sensors avoid errors due to alaising, they attentuate the high frequency variations in the observations.
+Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel.
+Such a remark motivates the use of sensors with wider bandwidths.
+Nevertheless, this choice would require an excessive number or sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response and therefore the accurate of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
 
@@
 \end{equation}
-This ensures that the basis functions can represent a field with frequency content up to $\boldsymbol\nu_{co}$.
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co}$.
 Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
-% Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
-The dynamic field must be spatially oversampled using a larger number of sensors than imposed by the frequency analysis, to use frequency analysis to determine the minimum distance and width of the basis functions.
-Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework.
-\omg{Ken: can you please write something about what should be done in this case?} For a spatially isotropic field, the basis functions can be placed on a regular grid and hence the distance between basis functions dictates the total number of basis functions required.
+
+Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.
 

### 2010-05-14 src/ODE_ex.py
check if I am uptodate

@@ -39,8 +39,8 @@ beta_variance=1.3**2
 #-------Brain----------------
 alpha=100
 threshold=2
-nu=5
-beta=10
+nu=10
+beta=0.8
 act_func=ActivationFunction(threshold,nu,beta)
 #----------observations--------------------------
 Delta_s = 1.5	# mm
@@ -69,7 +69,7 @@ pb.show()
 # -------Sampling properties-------------
 Fs = 1e3   #sampling rate                                       
 Ts = 1/Fs   #sampling period, second
-t_end = 0.5 # seconds
+t_end = 0.2 # seconds
 NSamples = t_end*Fs;
 T = pb.linspace(0,t_end,NSamples);
 
@@ -104,13 +104,13 @@ parameters['Fs']=Fs
 parameters['t_end']=t_end
 quickio.writed('parameters','w',parameters)
 #---------------save results in mat format---------------
-V_matrix_dic={}
-V_filtered_dic={}
-Y_dic={}
-V_matrix_dic['V_matrix']=V_matrix
-V_filtered_dic['V_filtered']=V_filtered
-Y_dic['Y']=Y
-io.savemat('V_filtered',V_filtered_dic)
-io.savemat('Y',Y_dic)
-io.savemat('V_matrix',V_matrix_dic)
+#V_matrix_dic={}
+#V_filtered_dic={}
+#Y_dic={}
+#V_matrix_dic['V_matrix']=V_matrix
+#V_filtered_dic['V_filtered']=V_filtered
+#Y_dic['Y']=Y
+#io.savemat('V_filtered',V_filtered_dic)
+#io.savemat('Y',Y_dic)
+#io.savemat('V_matrix',V_matrix_dic)
 

### 2010-05-14 src/UKF_ex.py

@@ -24,9 +24,9 @@ obs_noise_covariance=parameters['obs_noise_covariance']
 Fs=parameters['Fs']
 t_end=parameters['t_end']
 #-------------field--------------------
-field_basis_width=2.2#3.6
-spacestep=1
-S=pb.linspace(-10,10,11)
+field_basis_width=2.5#3.6
+spacestep=0.5
+S=pb.linspace(-10,10,9)
 f_centers=gen_spatial_lattice(S)
 nx=len(f_centers)
 f_widths=[pb.matrix([[field_basis_width,0],[0,field_basis_width]])]*nx
@@ -77,18 +77,18 @@ ps_estimate=para_state_estimation(model)
 UKF_iterations = 15;
 start_sample = 4;
 ps_estimate.itr_est(Y[start_sample:],UKF_iterations)
-print 'elapsed time is', time.time()-t0
+#print 'elapsed time is', time.time()-t0
 #Saving Kernel and 1/synaptic time constant in mat format
-alpha_mat={}
-kernel_mat={}
-alpha_mat['alpha']=ps_estimate.alpha_est 
-kernel_mat['kernel']= pb.squeeze(ps_estimate.kernel_weights_est)
-io.savemat('alpha',alpha_mat)
-io.savemat('kernel',kernel_mat)
+#alpha_mat={}
+#kernel_mat={}
+#alpha_mat['alpha']=ps_estimate.alpha_est 
+#kernel_mat['kernel']= pb.squeeze(ps_estimate.kernel_weights_est)
+#io.savemat('alpha',alpha_mat)
+#io.savemat('kernel',kernel_mat)
 #Saving filtered states in mat format
-X_f={}
-X_f['X_f']= pb.squeeze(ps_estimate.Xhat).T  #each column is a state vector
-io.savemat('X_f',X_f)
+#X_f={}
+#X_f['X_f']= pb.squeeze(ps_estimate.Xhat).T  #each column is a state vector
+#io.savemat('X_f',X_f)
 #Uncomment if you use smoother otherwise it gives error
 #saving smooth state in mat format
 #X_b={}

### 2010-05-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics.
-Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-alaising filtering.
+Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
 Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$.
@@
 
-Although such sensors avoid errors due to alaising, they attentuate the high frequency variations in the observations.
+Although such sensors avoid errors due to aliasing, they attenuate the high frequency variations in the observations.
 Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel.

### 2010-05-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
-\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
-\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
-\newcommand{\haq}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
+\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
+\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
+\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
 \begin{document}
@@
 
-\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
+\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^{1,5}$, and Visakan Kadirkamanathan$^2$}
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Deaprtment of Systems and Control Engeineering, University of Malta, Msida, MSD 1333, Malta} \ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002
+ Australia} \ead{dfreestone@bionicear.org}
 
@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model for the estimation that consists of a two stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+We use the reduced model for the estimation that consists of a two-stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
 The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
 The results illustrate the cost of the model reduction with a loss of the high spatial frequency information.
-This framework provides a link between patient specific neurophysiological data and theoretical neural fields models.
+This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models.
 This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.
@@
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
-Understanding the brain at this level is extremely important since it is this scale where pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+Understanding the brain at this level is extremely important since it is this scale at which pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews).
@@
 
-For models to be clinically viable they must be patient specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC) or Amari~\cite{Wilson1973,Amari1977}  models or a neural mass model like the Jansen and Ritt model \cite{Jansen1995}, to patient specific EEG data.
-Fitting the neural models to individuals is a highly non-trivial task, and until very recently this has not been reported in the literature.
+For models to be clinically viable they must be patient-specific.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific EEG data.
+Fitting the neural models to individuals is a highly non-trivial task, and, until very recently, this has not been reported in the literature.
 
@@
 Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating it is possible to perform state estimation of modified WC equations.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation of modified WC equations.
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
@@
 In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
-This work provides a fundamental link between the theoretical advances in neural field modelling and patient specific data.
+This work provides a fundamental link between the theoretical advances in neural field modelling and patient-specific data.
 
@@
 Section~\ref{SpectralAnalysisSection} establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
-Following this, the state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
+The state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
 The results for the spatial frequency analysis and parameter estimation are then presented in Section~\ref{ResultsSection}.
@@
 Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
 
@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\haq{Risky comment if we don't get better estimates.}
+\ken{Risky comment if we don't get better estimates.}
 
-\omg{show figure with the Mexican hat here.}
+\dean{show figure with the Mexican hat here.}
 
@@
 \end{eqnarray}
-To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function 
+To arrive at the final form of the model we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
@@
 \end{eqnarray}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is i.i.d.
-such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{s}-\mathbf{r})$ \cite{Rasmussen2006} This term was added to account for uncertainty in the model.
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an i.i.d.
+disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}.
+This term is added to account for uncertainty in the model.
 The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function
@@
 \subsection{Derivation of Finite Dimensional State-Space Model} 
-In order to implement standard estimation techniques we use a decomposition of the field using a set of Gaussian basis functions defined by
+In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions defined by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 \end{equation}
-We will assume we know the parametric form of the connectivity basis functions, where the parameter $\boldsymbol{\theta}$ is unknown.
+We will assume that we know the parametric form of the connectivity basis functions, where the parameter $\boldsymbol{\theta}$ is unknown.
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
@@
 \end{equation}
-and manipulating equation \ref{reduced continuous model} (see Appendix \ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
+and manipulating equation \ref{reduced continuous model} (see \ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
 \begin{eqnarray}
@@
 \end{equation}
-The observation equation of the reduced model is \omg{Should this be $\mathbf{y}_t \approx \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t$}
+Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is
 \begin{equation}
@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to \ref{eq:MinimumSensorDistance}.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to equation~\ref{eq:MinimumSensorDistance}.
 However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics.
+Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
 Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
 Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$.
-Aliasing can then be avoided by positioning the sensors according to \ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
+Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
 
@@
 Such a remark motivates the use of sensors with wider bandwidths.
-Nevertheless, this choice would require an excessive number or sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
-Therefore, a compromise needs to be found between the bandwidth of the sensor response and therefore the accurate of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
+Nevertheless, this choice would require an excessive number of sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
 
-Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition.
+Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
 The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field.
@@
 \end{equation}
-The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving \omg{need to rewrite eq~\ref{eq:WidthFrequencyRelationship} in terms of $\sigma_{\phi}$.
+The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving \dean{need to rewrite eq~\ref{eq:WidthFrequencyRelationship} in terms of $\sigma_{\phi}$.
 At the mo it is writen in terms of $\sigma_{nu}$}
-\begin{equation}\label{eq:WidthFrequencyRelationship}
+\begin{equation}\label{eq:WidthCutOffRelationship}
  \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{co}}^2},
@@
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
-At each iteration, the sequence of estimated states is used to update the parameter set, then the resulting parameters are used to estimate a new state vector for the next iteration.
+At each iteration, the sequence of estimated states is used to update the parameter set.
+Then the resulting parameters are used to estimate a new state vector for the next iteration.
 The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state sequence which guarantees the initial estimated parameter set forms a stable kernel.
-\omg{Parham: can you please add to this to include the initialisation of the field?}
+The algorithm is initialised using a bounded random state sequence that guarantees the initial estimated parameter set forms a stable kernel.
 
@@
 The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
-The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows
+The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
 \begin{equation}\label{eq:sigmapoints1}
@@
 \begin{equation}
-	\mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i \quad i=1, \dots, L 
+	\mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i, \quad i=1, \dots, L 
 \end{equation}
 \begin{equation}\label{eq:sigmapoints2}
-	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L} \quad i= L+1, \dots, 2 L 
+	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L}, \quad i= L+1, \dots, 2 L 
 \end{equation}
@@
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
-It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise $ \boldsymbol{\varepsilon}_t$ are additive, therefore the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms.
+It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
+Therefore, the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms.
 The additive form reduces the dimension and the number of sigma points used in the algorithm.
@@
 The linearisation maintains the Gaussianality of the model.
-The unscented Kalman filter approximates the posterior state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, whilst maintaining the nonlinearity in the system.
-This has been shown to give superior performance over the EKF in state estimation, as the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
+The unscented Kalman filter approximates the posterior state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, while maintaining the nonlinearity in the system.
+This has been shown to give superior performance over the EKF in state estimation, since the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
 In addition, the computation of the Jacobian used in the EKF can be problematic.
 SMC filtering can theoretically provide an exact posterior state density for nonlinear systems.
-However, currently this method is not appropriate for our problem, due to computation demands.
+However, currently this method is not appropriate for our problem, due to high computation demands.
 
@@
 \end{center}
-The sensors were spaced in a regular square \omg{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \omg{1.44} which equals \omg{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \omg{$2.22$}~mm.
+The sensors were spaced in a regular square \dean{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \dean{1.44} which equals \dean{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \dean{$2.22$}~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
-Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
+Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
 \begin{figure}[th]\label{fig:experimental design}
@@
 Figure~\ref{fig:FieldFFT}(a) shows the spatial frequency of the field.
-The cut-off frequency, $\nu_c$, was taken to be \omg{??} ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}.
-This confirms our separation of \omg{??} was enough to prevent problems associated with aliasing.
+The cut-off frequency, $\nu_c$, was taken to be \dean{??} ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \dean{??}.
+This confirms our separation of \dean{??} was enough to prevent problems associated with aliasing.
 
 The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis}(c).
-The peak power of the spatial frequency of the observations was approximately \omg{$??$}~dB.
-The cut-off frequency (-3~dB point) was taken to correspond to  approximately \omg{$??$}~dB.
+The peak power of the spatial frequency of the observations was approximately \dean{$??$}~dB.
+The cut-off frequency (-3~dB point) was taken to correspond to  approximately \dean{$??$}~dB.
 This provided a conservative estimate of the spatial bandwidth.
-The oversampling parameter $\rho_b$ was set to $??$ giving a minimum distance between basis functions of $??$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-\todo{maybe from Parham's derivation...
-From equation~\ref{} the width was calculated to be...
-or...}.
+The oversampling parameter $\rho_b$ was set to \dean{??} giving a minimum distance between basis functions of \dean{??} to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The width of the basis functions was chosen such that the basis functions had sufficient overlap to represent the dynamic field.
+Equation~\ref{eq:WidthCutOffRelationship} (where $sigma_{\phi}^2 = $ \dean{??}) was used to confirm the width of the basis functions was sufficiently small to capture the characteristics of the field.
 
@@
 Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
-\wtf{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}
+\mike{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}
 
@@
 To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
-Each realisation consisted of 200 ms of data and the estimation was applied to the final 195 ms, allowing the model to stabilise.\omg{transient!} The initial state and parameters were unknown to the estimator.
-The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates} respectively.
-Although a wide distribution can be seen over the parameter estimates the ratio between them remans in a narrow range as shown in figure~\ref{fig:ParametersRatio}.
+Each realisation consisted of 200~ms of data and the estimation was applied to the final 195~ms, allowing the model to stabilise.\dean{transient!} The initial state and parameters were unknown to the estimator.
+The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates}, respectively.
+Although a wide distribution can be seen over the parameter estimates, the ratio between them remains within a narrow range as shown in figure~\ref{fig:ParametersRatio}.
 The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
 The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE}.
-One snapshot for the original and the field estimate and their corresponding error are illustrated in figure~\ref{fig:FieldEstimate}.
+A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}.
 
@@
 
-\omg{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FROM EDITING.}
+\dean{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FOR EDITING.}
 
@@
 	\item distortions of the spectral content of the basis function from the nonlinearity
-	\item disturbance covariance to narrow
-	\item disturbance variance to low (no exciting the kernel enough)
+	\item disturbance covariance too narrow
+	\item disturbance variance too low (not exciting the kernel enough)
 	\item boundary conditions
@@
 
-\omg{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
+\dean{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
 This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
@@
 
-\omg{DISCUSS RESULTS: FREQ ANALYSIS. USE THIS TO JUSTIFY KERNEL ERRORS.}
+\dean{DISCUSS RESULTS: FREQ ANALYSIS. USE THIS TO JUSTIFY KERNEL ERRORS.}
 The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
@@
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
-The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition.
+This is evident in when comparing figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
+The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel.
+Therefore some information will be lost due to the field decomposition.
 The implication of this loss of information is the high spatial frequency content of the connectivity kernel.
-This is demonstrated in Figure~\ref{fig:KernelEstimates} where the frequency content of the estimated connectivity kernel is less than the true kernel.
+This is demonstrated in figure~\ref{fig:KernelEstimates} where the frequency content of the estimated connectivity kernel is less than the true kernel.
 
-\omg{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
+\dean{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
 Even though the high frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
-This is illustrated in~\ref{fig:FieldEstimate}.
-In addition, the ratio of the kernel parameters follows a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
+This is illustrated in figure~\ref{fig:FieldEstimate}.
+In addition, the ratio of the kernel parameters follows a tight distribution as seen in figure~\ref{fig:ParametersRatio}.
 This indicates that the ratio of excitation to inhibition can be tracked with this approach.
 
-\omg{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT }
+\dean{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT }
 
-\omg{DISCUSS THE IMPLICATION OF ESTIMATING INTRACORTICAL CONNECTIVITY AND WHERE WE FIT WITHIN OTHER FUNCTIONAL CONNECTIVITY RESEARCH AREAS}
-To the authors best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of this can be illustrated by considering the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-In addition, other non-model based techniques for estimating functional connectivity such as Granger causality \cite{Hesse2003}, the direct transfer function \cite{Kaminski1991}, and partial directed coherence \cite{Sameshima1999} are restricted to the spatial scales of the recording electrodes.
+\dean{DISCUSS THE IMPLICATION OF ESTIMATING INTRACORTICAL CONNECTIVITY AND WHERE WE FIT WITHIN OTHER FUNCTIONAL CONNECTIVITY RESEARCH AREAS}
+To the authors' best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
+In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
 The model-based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
-An advantage of the auto-regressive (AR) based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
+An advantage of the auto-regressive (AR) methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
 It should be noted, however, that the AR and the proposed model-based methods are complementary, where connectivity is estimated at different spatial scales.
-Therefore, we envisage by combining these methods a more realistic model can be acquired.
+Therefore, we envisage that by combining these methods a more realistic model can be acquired.
 A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
 
-\omg{DISCUSS A BIG PICTURE. WHERE THIS WORK SHOULD GO AND WHERE IT SHOULD BE APPLIED ON THE FUTURE}
+\dean{DISCUSS A BIG PICTURE. WHERE THIS WORK SHOULD GO AND WHERE IT SHOULD BE APPLIED IN THE FUTURE}
 Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hoft bifurcation occurs~\cite{Hutt2005}, and types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we could estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to hyper-synchronous oscillatory states such as Turing patterns.
+Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hopf bifurcation occurs~\cite{Hutt2005}, and the types of oscillations that can be generated~\cite{Schmidt2009}.
+This implies that if we can estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to hyper-synchronous oscillatory states such as Turing patterns.
 In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
@@
 
-\omg{DISCUSS HOW IT CAN LINK THEORETICAL MODELLING STUDIES TO DATA.}
-This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing hypotheses that have been generated in theoretical studies and to validate neural field models.
-For example, it has been hypothesised that so called bump solutions are a possible mechanism for short term memory formation~\cite{Coombes2005}.
+\dean{DISCUSS HOW IT CAN LINK THEORETICAL MODELLING STUDIES TO DATA.}
+This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
+For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}.
 Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
-In addition exploration of parameters and the state-space can be explored during other cognitive tasks and states of arousal such as sleep and anaesthesia.
+In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and under anaesthesia.
 
-\omg{DISCUSS SHORT-COMINGS AND FUTURE WORK}
-In this paper the widths of the connectivity kernel basis functions are assumed to be known.
-In future work we plan to extend this work to unknown widths.
-We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting the estimation procedure take care of the weights.
+\dean{DISCUSS SHORT-COMINGS AND FUTURE WORK}
+In this paper, the widths of the connectivity kernel basis functions are assumed to be known.
+In future work, we plan to extend this work to estimate the connectivity structure width unknown kernel basis function widths.
+We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure take care of the weights.
 In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
@@
 \begin{itemize}
-	\item What about the transient! The need for activity to perform estimation. \omg{To Learn You Must Perturb!} 
+	\item What about the transient! The need for activity to perform estimation. \dean{To Learn You Must Perturb!} 
 \end{itemize}
@@
 \end{eqnarray}
-\omg{DEFINE q HERE!!!!!}
+\dean{DEFINE q HERE!!!!!}
 \section{}\label{ColoredNoise} 

### 2010-05-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to abstract in intro of paper, added kernel figure

@@
 	This paper presents a framework for creating patient-specific neural field models from electrophysiological data.
-The Wilson and Cowen or Amari style neural field equations are used as the parametric form of the model, where the parameters are estimated from data.
-To illustrate the estimation framework, data is generated using modelled sensors and the field model.
-We introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model to facilitate state and parameter estimation.
+The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
+To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
+To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model.
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model for the estimation that consists of a two-stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+We use the reduced model to estimate the state and parameters of the non-reduced model.
+The estimation procedure consists of a two-stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
 The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
-The results illustrate the cost of the model reduction with a loss of the high spatial frequency information.
+The results also illustrate the cost of the model reduction with a loss of the high spatial frequency information.
 This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models.
@@
 
-\section{Introduction} This paper presents a theoretical framework for generating macroscopic neural field mathematical models from patient-specific data.
+\section{Introduction} This paper presents a theoretical framework for generating patient-specific macroscopic neural field mathematical models from data.
 There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
@@
 Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
-The key development here was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observation locations (recording electrodes in this case).
+The key development from this recent paper was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation locations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
@@
 
-\dean{show figure with the Mexican hat here.}
+\begin{figure}[th]\label{fig:experimental design}
+   	\begin{center}
+   		\includegraphics[width=0.3\textwidth]{./Graph/2D_kernel.pdf} 
+   	\end{center}
+   	\caption{Kernel centred at zero as a function of space.} 
+   \end{figure}
 

### 2010-05-18 src/ODE_ex.py

@@ -12,8 +12,8 @@ dimension=2;
 spacestep=0.5;
 steps_in_field = field_width/spacestep + 1;
 
-Delta = 1./spacestep;
-Nspacestep_in_observed_field = Delta*observedfieldwidth+1	
+inv_spacestep = 1./spacestep;						
+Nspacestep_in_observed_field = inv_spacestep*observedfieldwidth+1	
 
 observation_offest = field_width/4;     # mm
 observation_offset_units = observation_offest / spacestep -1;

### 2010-05-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits of model derivation

@@
 \ken{Risky comment if we don't get better estimates.}
-
-\begin{figure}[th]\label{fig:experimental design}
+\begin{figure}[ th]\label{fig:2d_kernel}
    	\begin{center}
-   		\includegraphics[width=0.3\textwidth]{./Graph/2D_kernel.pdf} 
+   		\includegraphics[angle = 90, scale=0.5]{./Graph/2D_kernel.pdf} 
    	\end{center}
@@
    \end{figure}
-
 The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
@@
 This term is added to account for uncertainty in the model.
+To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
 The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function
@@
 \subsection{Derivation of Finite Dimensional State-Space Model} 
-In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions defined by
+In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
-The connectivity kernel can also be decomposed into a set of basis functions where
+The connectivity kernel can also be decomposed as
 \begin{equation}\label{DefKernelDecomp}
-	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta}.
+	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta},
 \end{equation}
-We will assume that we know the parametric form of the connectivity basis functions, where the parameter $\boldsymbol{\theta}$ is unknown.
+where $\boldsymbol{\psi}(r-r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
@@
 \end{eqnarray}
-By defining the term 
-\begin{equation}
-	\label{DefGamma} \boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}} 
-\end{equation}
-and manipulating equation \ref{reduced continuous model} (see \ref{Simplifying Decomposition}) we isolate the state vector to form a state-space model 
+This reduced model can be manipulated into a standard state-space model in the form (see \ref{Simplifying Decomposition})
 \begin{eqnarray}
@@
 Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
-	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, 
+	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, \\
+	\boldsymbol{\Gamma} &=& \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, \label{DefGamma} 
 \end{eqnarray}
@@
 \begin{equation}
-	\label{ObservationEquation} \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t 
+	\label{ObservationEquation} \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{equation}
@@
 \end{equation}
-where $L$ is the number of basis functions used to decompose the voltage field and 
+where $L$ is the number of basis functions used to decompose the neural field and 
 \begin{equation}
@@
 Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-Then, based on Shannon's sampling Theorem, for an accurate representation of this field by spatially discrete observations, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+Based on Shannon's sampling theorem, for an accurate representation of this field by spatially discrete observations, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
 Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency with  $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
@@
 Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$.
+Such sensors therefore band-limit the field to a known bandwidth, denoted by $\nu_{co}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
@@
 Although such sensors avoid errors due to aliasing, they attenuate the high frequency variations in the observations.
-Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel.
+Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations will underestimate the high frequency component in both the field and the kernel.
 Such a remark motivates the use of sensors with wider bandwidths.
@@
 \begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_b < \frac{1}{2\rho_b\nu_{co}}
+	\Delta_{\phi} < \frac{1}{2\rho_{\phi}\nu_{co}}
 \end{equation}
-where $\rho_b$ is an over-sampling parameter to determine the basis function separation.
+where $\rho_{phi}$ is an over-sampling parameter to determine the basis function separation.
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
 The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
-
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving \dean{need to rewrite eq~\ref{eq:WidthFrequencyRelationship} in terms of $\sigma_{\phi}$.
-At the mo it is writen in terms of $\sigma_{nu}$}
+The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving
 \begin{equation}\label{eq:WidthCutOffRelationship}

### 2010-05-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to freq analysis and state estimation

@@
 \begin{eqnarray}
-	\label{DiscreteTimeModel} v_{t+T_s}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
+	\label{DiscreteTimeModel} v_{t+T_s}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
 	&+& e_t\left(\mathbf{r}\right), 
@@
 \begin{equation}\label{DefKernelDecomp}
-	 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta},
+	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
 \end{equation}
-where $\boldsymbol{\psi}(r-r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+By assuming a Gaussian isotropic connectivity structure the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 Based on Shannon's sampling theorem, for an accurate representation of this field by spatially discrete observations, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
-Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency with  $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
-Given such a band-limited field, the distance between adjacent sensors, $\Delta_s$, needs to satisfy
+Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, needs to satisfy
 \begin{equation}
-	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
+	\label{eq:MinimumSensorDistance} \Delta_y < \frac{1}{2\rho_y\nu_{c}}, 
 \end{equation}
-where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter.
+where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
 This condition must be satisfied to avoid spectral aliasing effects in the representation of the hidden dynamic field $v_t(\mathbf{r})$ by the sampled observations, $\mathbf{y}_t$.
@@
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
-At each iteration, the sequence of estimated states is used to update the parameter set.
-Then the resulting parameters are used to estimate a new state vector for the next iteration.
+At each iteration, the sequence of estimated state vectors is used to update the parameter set.
+The resulting parameters are then used to estimate a new state vector sequence for the next iteration.
 The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state sequence that guarantees the initial estimated parameter set forms a stable kernel.
+The algorithm is initialised using a bounded random state vector sequence that guarantees the initial estimated parameter set forms a stable kernel.
 
-The unscented Rauch Tung Striebel Smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
+The unscented Rauch Tung Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
 The URTSS incorporates an unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 The total number of sigma points is $2L+1$.
-The scaling parameter $\lambda$ is defined as
+The scaling parameter, $\lambda$, is defined as
 \begin{equation}\label{eq:sigmapoints3}
@@
 \end{equation}
-where the constants $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is a scaling parameter (see ~\cite{Haykin2001} for more details).
+where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is a scaling parameter (see ~\cite{Haykin2001} for more details).
 
@@
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the predicted cross-covariance matrix of the states is also calculated.
+To compute the smoother gain, the predicted cross-covariance matrix of the states is used with the covariance matrix.
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
-It should be noted that as the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
+It should be noted that  the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
 Therefore, the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms.
-The additive form reduces the dimension and the number of sigma points used in the algorithm.
-
+The additive disturbance form reduces the dimension and the number of sigma points used in the algorithm.
 \begin{algorithm}
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state estimate (see~\ref{LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{LeastSquaresAppendix}).
 

### 2010-05-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updating figure captions

@@
 An example of the simulated field can be seen in figure~\ref{fig:experimental design}(a).
-This figure demonstrates the experimental design used: the sensors were placed in the centre of the field (full width at half maximum).
+This figure demonstrates the experimental design used where the sensor array was placed in the centre of the field (sensor centres marked by crosses).
 This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
@@
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
-\begin{center}
+\begin{table}
+
+\centering
 \begin{tabular}{c|c|c}
@@
 \end{tabular}\label{tab:Model Parameters}
-\end{center}
+\caption{Parameters for neural field model used to generate data to demonstrate the estimation framework.}
+\end{table}
 The sensors were spaced in a regular square \dean{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \dean{1.44} which equals \dean{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \dean{$2.22$}~mm.
@@
 The centres of the sensors are shown by crosses.
-\textbf{b} Example of data generated by the model through the observations.
+\textbf{b} Example of data generated by the model through a subset of the observations.
 \textbf{c}.
@@
 \caption{Distribution of the parameters estimates over 250
-runs.
-True parameters are $\zeta=100$, $\theta_0 = 10$, $\theta_1 = -8$, $\theta_3 = 0.5$.
-Grey bars show distributions with wider basis functions and blue bars show improved parameter distributions with narrower basis functions.}
+realisations.
+Grey bars show distributions with wider basis functions ($\sigma_{\phi} = ?$) and blue bars show improved parameter distributions with narrower basis functions ($\sigma_{\phi} = ?$).
+\textbf{a.} The distribution of the synaptic time constant estimates (true parameter: $\zeta=100$).
+\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameters estimates (true parameter: $\theta_0 = 10$).
+\textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
 \label{fig:Parameters}
@@
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2Convergence.pdf}}
-\caption{Convergence of the parameters: averaged over 250 runs.}
+\caption{Convergence of the parameters averaged over 250 runs. }
 \label{fig:ParametersConvergence}
 \end{figure}
-
 \subsection{Spatial Frequency Analysis} 
@@
 	\end{center}
-	\caption{(a) Field basis function frequency response, (b) Sensor frequency response, (c) The average FFT of the observed field.}
-
+	\caption{Frequency analysis of the.
+\textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project.
+The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics.
+The dashed line shows the cut-off frequency (-3 dB point).
+\textbf{b} The spatial frequency response of a 1-dimensional model sensor.
+The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
+\textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 200 time steps) of the observed field.}
 \end{figure}
-Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
+Following this, the distance between basis function, $\Delta_{phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
 \mike{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}

### 2010-05-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small edits to the discussion

@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics[width=1.5in]{./Graph/ZetaConvergence.pdf}}
+\subfigure[$\zeta$ convergence]{\includegraphics[width=1.5in]{./Graph/ZetaConvergence.pdf}}
 \subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0Convergence.pdf}}\\
@@
 
-\caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
-and dashed line respectively, the grey area shows 95\% confidence interval; Left: spatial domain; Right: frequency domain; a, b: wider basis functions; c,d: narrower basis functions.**************************Guys the bottom left figure is the power in db for skinny basis functions}
+\caption{Results for connectivity estimate.
+In all the subplots the true kernel is show by the solid line, the mean kernel estimate (over 250 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region.
+\textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain.
+\textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain.
+\dean{Note: needs to be changed to absolute values if we include it.} \textbf{c.} Same as part a., except narrower wider (in space) basis functions where used in the model reduction.
+\textbf{d.} Same as part b., except narrower wider (in space) basis functions where used in the model reduction.
+\textbf{e.} Frequency domain (power dB) representation of the true kernel and the estimated kernel (using the narrower basis functions).
+\dean{Note: Power and dB needs to be non-italicised.}}
 \label{fig:KernelEstimates}
@@
 \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{Distribution of the parameters ratios over 250 runs.}
+\caption{Distribution of the connectivity kernel basis function parameter ratios over 250 realisations.
+\textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
+\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).}
 \end{figure}
@@
 \centering
-\subfigure[][]{\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}\label{fig:FieldFFT}
-\subfigure[][]{\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
-\caption{The average FFT of the neural field; a: True field; b: Estimated field (showing the limited bandwidth).}
+\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}
+\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\\
+\caption{Spatial frequency of the neural fields.
+\textbf{a.} The average (over time) spatial frequency of the neural field.
+\textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
+As a result of the band limiting properties of the sensors and basis functions the reconstructed shows a narrower bandwidth.}
 \label{fig:FFTTrueEstimate}
@@
    	\end{center}
-   	\caption{The mean of RMSE of the estimated field over 250 runs.} 
+   	\caption{The mean of average RMSE of the estimated field over 250 realisations (solid line) and the 95~\% confidence interval (grey region).
+\dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros.
+Also, it might be good to show the data points along the line, so we can see the number of iterations it takes to stabilise.}}
 \label{fig:RMSE}
@@
 \subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimationError90.pdf}}\\
-\caption{One snapshot of the spatial field; a: True field; b: Estimated field; c: The absolute error.}
+\caption{Examples of the neural fields.
+\textbf{a.} The true field from the non-reduced model the was used to generate data.
+\textbf{b.} The reconstructed estimated field of the reduced model.
+\textbf{c.} The absolute error between the true and reconstructed fields.}
 \label{fig:FieldEstimate}
@@
 \dean{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
-This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of neural fields.
+This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of spatio-temporal neural fields.
 A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
 The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
-By forming a state-space model, the unscented Rauch Tung Striebel Smoother was implemented for state estimation.
+Using the state-space model, the unscented Rauch Tung Striebel Smoother was applied for state estimation.
 Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
@@
 The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
-These tools can be also used to better design electrophysiological recording techniques to advance model-based neural parameter estimation in order to avoid spatial aliasing.
+In addition to providing conditions to ensure the reduced model can capture the significant spectral properties of the field, these tools can be used to better design electrophysiological recording techniques avoid spatial aliasing.
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
@@
 \dean{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
-Even though the high frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
+Even though the some high spatial frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
 This is illustrated in figure~\ref{fig:FieldEstimate}.
@@
 In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
-The model-based technique proposed in this paper estimates the connectivity structure independently of the recording electrode geometry.
+The model-based technique proposed in this paper estimates the connectivity structure of the number of sensors.
 An advantage of the auto-regressive (AR) methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
@@
 \end{itemize}
-
-\section{Conclusion}\label{ConclusionSection}
-This paper presented a novel model-based framework for patient-specific state and parameter estimation of neural fields.
+% 
+% \section{Conclusion}\label{ConclusionSection}
+% This paper presented a novel model-based framework for patient-specific state and parameter estimation of neural fields.
 This framework enables a fundamental link between patient-specific physiologic data and theoretical neural field models.

### 2010-05-24 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 		\end{equation*}
-		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propogate them through equation \ref{eq:QmatrixForSigmapoints}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b,u_t) 
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) 
 		\end{equation*}

### 2010-05-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits, switching conv

@@
 \end{eqnarray}
-Substituting equation~\ref{DefGamma} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+Now defining
+\begin{equation}\label{eq:DefGamma2}
+	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
+\end{equation}
+and substituting equation~\ref{eq:DefGamma2} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
 \begin{eqnarray}\label{eq:ReducedForm}
 	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
-\end{eqnarray}
+&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{eqnarray}
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
+\begin{equation}
+	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+\end{equation}
+To make the simplification we first define
+\begin{equation}\label{eq:DefPsi}
+	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+\end{equation}
+which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+\begin{equation}
+	\mathbf{x}_{t+1} \nonumber = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{equation}
 \dean{DEFINE q HERE!!!!!}
@@
 	&\vdots& \\
-	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+\mathbf e_{n-1} \nonumber
+	\mathbf x_{T}&=&\mathbf x_{T-1}+T_s \mathbf Q(\mathbf x_{T-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{T-1}+\mathbf e_{n-1} \nonumber
 \end{eqnarray}
@@
 		\mathbf x_{2}-\mathbf x_{1}\\\vdots\\
-		\mathbf x_{n}-\mathbf x_{n-1}
+		\mathbf x_{T}-\mathbf x_{T-1}
 	\end{array}
@@
 		\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
-		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
+		\mathbf Q(\mathbf x_{T-1})&-\mathbf x_{T-1}
 	\end{array}

### 2010-05-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editted reduced model derivation and the least squares appendix

@@
 \end{eqnarray}
-This reduced model can be manipulated into a standard state-space model in the form (see \ref{Simplifying Decomposition})
-\begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t\right) + \mathbf{e}_t 
-\end{eqnarray}
-where
-\begin{eqnarray}
-Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
-	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, \\
-	\boldsymbol{\Gamma} &=& \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, \label{DefGamma} 
-\end{eqnarray}
-where $\mathbf{e}_t$ is a zero-mean normal white noise term with the covariance (see~\ref{ColoredNoise}) 
-\begin{equation}
-	\boldsymbol{\Sigma}_e=\boldsymbol{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{-1}
+Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
+\begin{eqnarray}
+	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
+ &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
+&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+\end{eqnarray}
+Now defining
+\begin{equation}\label{eq:DefGamma}
+	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
+\end{equation}
+and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+\begin{eqnarray}\label{eq:ReducedForm}
+	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{eqnarray}
+This can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
+\begin{equation}
+	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+\end{equation}
+To make the simplification we first define
+\begin{equation}\label{eq:DefPsi}
+	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+\end{equation}
+which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+\begin{equation}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{equation}
+Now we define the state disturbance as
+\begin{equation}\label{eq:AppendixWt} 
+	\mathbf{e}_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
+\end{equation}
+which is a zero mean normally distributed white noise process with covariance (see~\ref{ColoredNoise})
+\begin{equation}
+	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
 \end{equation}
 Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is
-\begin{equation}
-	\label{ObservationEquation} \mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+\begin{equation}\label{ObservationEquation} 
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{equation}
@@
 \end{equation}
+Now we have the final form of the state-space model where
+\begin{equation}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t +\mathbf{e}_t.
+\end{equation}
+\begin{equation} 
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+\end{equation}
+
+This reduced model can be manipulated into a standard state-space model in the form (see \ref{Simplifying Decomposition})
+\begin{eqnarray}
+	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + \mathbf{e}_t \\
+	&=& Q\left(\mathbf{x}_t\right) + \mathbf{e}_t 
+\end{eqnarray}
+where
+\begin{eqnarray}
+Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
+	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, \\
+	\boldsymbol{\Gamma} &=& \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, \label{DefGamma} 
+\end{eqnarray}
 
@@
 where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
-\section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} 
-Starting from equation~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
-\begin{eqnarray}
-	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
- &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
-&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
-\end{eqnarray}
-Now defining
-\begin{equation}\label{eq:DefGamma2}
-	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
-\end{equation}
-and substituting equation~\ref{eq:DefGamma2} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{eqnarray}\label{eq:ReducedForm}
-	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{eqnarray}
-Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
-\begin{equation}
-	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
-\end{equation}
-To make the simplification we first define
-\begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
-\end{equation}
-which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-\begin{equation}
-	\mathbf{x}_{t+1} \nonumber = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{equation}
-\dean{DEFINE q HERE!!!!!}
+% \section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} 
+% Starting from equation~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
+% \begin{eqnarray}
+% 	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
+%  &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
+% &+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+% \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+% \end{eqnarray}
+% Now defining
+% \begin{equation}\label{eq:DefGamma2}
+% 	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
+% \end{equation}
+% and substituting equation~\ref{eq:DefGamma2} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+% \begin{eqnarray}\label{eq:ReducedForm}
+% 	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+% &+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+% \end{eqnarray}
+% Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
+% \begin{equation}
+% 	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+% \end{equation}
+% To make the simplification we first define
+% \begin{equation}\label{eq:DefPsi}
+% 	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+% \end{equation}
+% which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+% \begin{equation}
+% 	\mathbf{x}_{t+1} \nonumber = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+% \end{equation}
+% \dean{DEFINE q HERE!!!!!}
 \section{}\label{ColoredNoise} 
@@
 \begin{lemma}
-	Consider the i.i.d. noise term $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ then 
-	\begin{equation}
-		\mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} \label{eq:AppendixWt} 
+	Consider the i.i.d. noise term $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r'}))$ then 
+	\begin{equation}\label{eq:AppendixWt} 
+		\mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
 	\end{equation}
@@
 The finite state space model  given in \ref{eq:ReducedForm} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters.
-We define $n_x \times n_{\theta}$ matrix
+We define $L \times n_{\theta}$ matrix
 \begin{eqnarray}\label{eq:QMatrix}
@@
 	&\vdots& \\
-	\mathbf x_{T}&=&\mathbf x_{T-1}+T_s \mathbf Q(\mathbf x_{T-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{T-1}+\mathbf e_{n-1} \nonumber
+	\mathbf x_{T}&=&\mathbf x_{T-1}+T_s \mathbf Q(\mathbf x_{T-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{T-1}+\mathbf e_{T-1} \nonumber
 \end{eqnarray}
@@
 	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z 
+\end{equation}
+
+\section{Parameter Estimation Using Least Squares - Dean}\label{App:LeastSquaresAppendix} 
+The finite state space model given in \ref{eq:ReducedForm} is linear with respect to parameters.
+Therefore a least square (LS) method can be applied to estimate the unknown parameters.
+We define $L \times n_{\theta}$ matrix
+\begin{equation}
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta}
+\end{equation}
+Given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write
+\begin{eqnarray}
+	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \nonumber \\
+	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1 \nonumber \\
+	&\vdots& \\
+	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. \nonumber \\
+\end{eqnarray}
+This can be written in the compact form
+\begin{equation}
+	\mathbf Z=\mathbf X \mathbf W+\mathbf{e} 
+\end{equation}
+where
+\begin{small}
+\begin{equation*}
+	\mathbf Z=\left[
+	\begin{array}{cccc}
+		\mathbf x_{1}\\
+		\mathbf x_{2}\\
+		\vdots\\
+		\mathbf x_{T}
+	\end{array}
+	\right],\quad \mathbf X=\left[
+	\begin{array}{cccc}
+		\mathbf q(\mathbf x_0)& \mathbf x_{0}\\
+		\mathbf q(\mathbf x_1)& \mathbf x_{1}\\
+		\vdots & \vdots\\
+		\mathbf q(\mathbf x_{T-1})& \mathbf x_{T-1}
+	\end{array}
+	\right] 
+\end{equation*}
+\end{small}
+and
+\begin{small}
+\begin{equation*}
+\quad \mathbf W=\left[
+	\begin{array}{cc}
+		\boldsymbol{\theta} \\
+		\xi
+	\end{array}
+	\right],\quad \boldsymbol \xi=\left[
+	\begin{array}{cccc}
+		\mathbf e_0\\
+		\mathbf e_1\\
+		\vdots\\
+		\mathbf e_{T-1}
+	\end{array}
+	\right].
+\end{equation*}
+\end{small}
+Following this, the parameters, $ \mathbf W$, can be estimated by
+\begin{equation}
+	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
 \end{equation}

### 2010-05-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
repaired typos

@@
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an i.i.d.
-disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}.
+disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 This term is added to account for uncertainty in the model.
@@
 \begin{equation}
-	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t +\mathbf{e}_t.
+	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t.
 \end{equation}
@@
 \end{equation}
-
-This reduced model can be manipulated into a standard state-space model in the form (see \ref{Simplifying Decomposition})
-\begin{eqnarray}
-	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + \mathbf{e}_t \\
-	&=& Q\left(\mathbf{x}_t\right) + \mathbf{e}_t 
-\end{eqnarray}
 where 
-\begin{eqnarray}
-Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
-	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, \\
-	\boldsymbol{\Gamma} &=& \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, \label{DefGamma} 
-\end{eqnarray}
+\begin{equation}\label{eq:QmatrixForSigmapoints}
+	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
+\end{equation}
 
@@
 Therefore a least square (LS) method can be applied to estimate the unknown parameters.
-We define $L \times n_{\theta}$ matrix
-\begin{equation}
-	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta}
-\end{equation}
-Given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write
+The create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
+\begin{equation}
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta}.
+\end{equation}
+Now given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write
 \begin{eqnarray}
@@
 	\end{array}
-	\right],\quad \boldsymbol \xi=\left[
+	\right],\quad \mathbf{e}=\left[
 	\begin{array}{cccc}

### 2010-05-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits

@@
 For models to be clinically viable they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific EEG data.
-Fitting the neural models to individuals is a highly non-trivial task, and, until very recently, this has not been reported in the literature.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific EEG data.
+Fitting the neural models to individuals is a highly non-trivial task and until very recently, has not been reported in the literature.
 
@@
 
-This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher order systems via a systematic model reduction procedure.
+This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
 In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
@@
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} establishes conditions using spatial frequency analysis for both sensor and basis function spacing and geometry, such that the dominant dynamics of the neural field can be represented by the reduced model.
+Section~\ref{SpectralAnalysisSection} establishes conditions using spatial frequency analysis for both sensor and basis function spacing and width, such that the dominant dynamics of the neural field can be represented by the reduced model.
 The state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
@@
 The implications and limitations of this framework are discussed in Section~\ref{DiscussionSection} along with planned future developments.
-Finally, we provide concluding remarks in Section~\ref{ConclusionSection}.
 

### 2010-06-04 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small paper edits
some editing
fixed typo in LS algorithm
change to obseravtion noise covariance notation in the filter algorithm
commiting for merge
Connectivity Kernel Plot

@@
 %
-  % \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
 %<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
+% \usepackage{iopams,setstack} 
 %<-comment out this for checking equations
@@
  %  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
- % \usepackage{amsmath}
+  \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002
- Australia} \ead{dfreestone@bionicear.org}
+% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002
+%  Australia} \ead{dfreestone@bionicear.org}
 
@@
 
-\subsection{Derivation of the Integro-difference Equation Representation}
+\subsection{Derivation of the Integro-Difference Equation Representation}
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
@@
    	\begin{center}
-   		\includegraphics[angle = 90, scale=0.5]{./Graph/2D_kernel.pdf} 
+   		\includegraphics{./Graph/Cross_section_kernel.pdf} 
    	\end{center}
@@
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
 \end{equation}
@@
 \end{equation}
+where the superscripts $m$ and $c$ stand for mean and covariance.
 Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are  used to correct the predicted states.
@@
 		\begin{equation*}
-			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_v)^{-1} 
+			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
 		\end{equation*}
@@
 		\begin{equation*}
-			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{f})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{f})^\top 
+			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
 		\end{equation*}
@@
 \begin{equation}
-	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta}.
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
 \end{equation}

### 2010-06-04 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
kernel estimates plot

@@
 \begin{figure*}
-\subfigure[][]{\includegraphics{./Graph/KernelEstimate_skinny.pdf}}
-\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_skinny.pdf}}\\
-\subfigure[][]{\includegraphics{./Graph/KernelEstimate_wide.pdf}}
-\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_wide.pdf}}\\
-\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT_skinny_db.pdf}}
-
+\subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
+\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
 \caption{Results for connectivity estimate.
-In all the subplots the true kernel is show by the solid line, the mean kernel estimate (over 250 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region.
+In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region.
 \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain.
 \textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain.
-\dean{Note: needs to be changed to absolute values if we include it.} \textbf{c.} Same as part a., except narrower wider (in space) basis functions where used in the model reduction.
-\textbf{d.} Same as part b., except narrower wider (in space) basis functions where used in the model reduction.
-\textbf{e.} Frequency domain (power dB) representation of the true kernel and the estimated kernel (using the narrower basis functions).
-\dean{Note: Power and dB needs to be non-italicised.}}
+\dean{Note: needs to be changed to absolute values if we include it.} \dean{Note: Power and dB needs to be non-italicised.}}
 \label{fig:KernelEstimates}

### 2010-06-04 src/Matlab/Create_C.m
add Matlab code for filter and model to src/Matlab

@@ -1,0 +1,15 @@
+% create C matrix for getting observations in the reduced model
+
+
+% define analytic inner product of sensors and basis functions
+a = pi / ( (sigma_phi^2+sigma_y^2)/(sigma_phi^2*sigma_y^2) );
+b = 1/(sigma_phi^2+sigma_y^2);
+
+% now define the observation matrix
+C = zeros(NSensors_xy^2,NBasisFunctions_xy^2 );
+for n=1:NSensors_xy^2
+    for nn=1:NBasisFunctions_xy^2
+        mu_phi_minus_mu_y = mu_y(:,n)-mu_phi(:,nn);
+        C(n,nn) = a*exp(-b*(mu_phi_minus_mu_y)'*mu_phi_minus_mu_y);
+    end
+end

### 2010-06-04 src/Matlab/Create_Psi.m

@@ -1,0 +1,29 @@
+
+
+% now form the matrix
+% these are the coefficients for the convolution of psi and phi
+psi_phi_coefficient(1) = pi*sigma_psi(1)^2*sigma_phi^2 / (sigma_psi(1)^2+sigma_phi^2);
+psi_phi_coefficient(2) = pi*sigma_psi(2)^2*sigma_phi^2 / (sigma_psi(2)^2+sigma_phi^2);
+psi_phi_coefficient(3) = pi*sigma_psi(3)^2*sigma_phi^2 / (sigma_psi(3)^2+sigma_phi^2);
+
+% compute the convolution between phi and psi
+for n=1:L 
+    for m=1:length(theta)
+        % these guys here are used with the LS algorithm for estimating
+        % theta and xi
+        psi_phi = psi_phi_coefficient(m)*...
+            Define2DGaussian(mu_phi(1,n), mu_phi(2,n), sigma_psi(m)^2+sigma_phi^2, 0,NPoints,SpaceMin,SpaceMax);
+
+        psi_phi_basis(m,n,:) = psi_phi(:);  
+        theta_psi_phi_basis(m,n,:) = theta(m)*psi_phi_basis(m,n,:);
+        
+    end
+end
+
+Ts_invGamma_theta_phi_psi = Ts*(Gamma\squeeze(theta_psi_phi_basis(1,:,:) ...
+    + theta_psi_phi_basis(2,:,:) ...
+    + theta_psi_phi_basis(3,:,:)));
+
+Ts_invGamma_phi_psi(1,:,:) = Ts*(Gamma\squeeze(psi_phi_basis(1,:,:)));
+Ts_invGamma_phi_psi(2,:,:) = Ts*(Gamma\squeeze(psi_phi_basis(2,:,:)));
+Ts_invGamma_phi_psi(3,:,:) = Ts*(Gamma\squeeze(psi_phi_basis(3,:,:)));

### 2010-06-04 src/Matlab/GenerateData.m

@@ -1,0 +1,62 @@
+
+% implementation of the neural field model to generate data
+
+% if we are running a batch than we dont want to clear things
+if exist('RunningBatch') == 0
+    clear
+    close all
+    clc
+    load Parameters
+end
+
+% run the script that sets all the parameters
+Set_Parameters
+
+% create the observation disturbance
+varepsilon = mvnrnd(zeros(1,NSensors),Sigma_varepsilon,T);
+
+% DisturbanceFileName = ['e_' num2str(T) '_' num2str(100*Delta) '_' num2str(100*SpaceMax) '_' ...
+%     num2str(100*sigma_gamma) '_' num2str(100*gamma_weight) '.mat'];
+
+% if exist(DisturbanceFileName) == 2
+%     load(DisturbanceFileName)
+% else
+
+e = mvnrnd(zeros(1,NPoints^2),Sigma_gamma,T);
+%     save(DisturbanceFileName,'e')
+% end
+
+% initialize field
+v = zeros(T,NPoints,NPoints);
+v(1,:,:) = Define2DGaussian(0,0, sigma_phi^2, 0,NPoints,SpaceMin,SpaceMax);
+
+% generate data
+y = zeros(T,NSensors_xy^2);         % initialise obseravation for speed
+for t=1:T-1
+    
+    f = f_max./(1+exp(varsigma*(v_0-squeeze(v(t,:,:)))));           % calc firing rate using sigmoid
+    F = fft2(f);                                                                                % take FFT of firing for conv with kernel
+    g = ifftshift(ifft2(F.*Ts_W,'symmetric'))*Delta_squared;            % conv kernel with firing rate 
+    v(t+1,:,:) = g + xi*squeeze(v(t,:,:)) + reshape(e(t,:,:),NPoints,NPoints);  % update field
+    
+%     imagesc(r,r,squeeze(v(t+1,:,:)))                          % plot field to check things are working
+%     axis xy
+%     axis square
+%     colorbar
+%     drawnow
+    
+    V = fft2(squeeze(v(t+1,:,:)));                                                  % take FFT of field for conv with sensor
+    m_conv_v = ifftshift(ifft2(M.*V,'symmetric'))*Delta_squared;    % conv with sensor 
+    
+    y_temp = m_conv_v(sensor_indexes,sensor_indexes) ...
+        + reshape(varepsilon(t+1,:,:),NSensors_xy,NSensors_xy);     % take indexes of field conv with sensor for observations
[…]

### 2010-06-04 src/Matlab/GetFilteredStateAndCovariance.m

@@ -1,0 +1,5 @@
+function [x_plus P_plus] = GetFilteredStateAndCovariance(P_minus,C,Sigma_y,x_minus,y_t_plus_1)
+
+K = P_minus*C'/(C*P_minus*C'+Sigma_y);
+x_plus = x_minus + K*(y_t_plus_1 - C*x_minus);
+P_plus = (eye(size(P_minus))-K*C)*P_minus;

### 2010-06-04 src/Matlab/GetSigmaMatrix.m

@@ -1,0 +1,16 @@
+% generate Sigma matrix
+
+function X = GetSigmaMatrix(x,P,sqrt_L_plus_lambda)
+
+    L = size(x,1);                      % number of states
+    X = zeros(L,2*L+1);             % initialise for speed
+
+    sqrt_P = chol(P,'lower');       % take the matrix sqrt of covariance
+    sqrt_L_plus_lambda_times_sqrt_P = sqrt_L_plus_lambda*sqrt_P;
+
+    X(:,1) = x;                                       % this is either the initial or filtered state
+    x_mat = repmat(X(:,1),1,L);                 % make x bigger for subtraction and addition
+    X(:,2:L+1) = x_mat + sqrt_L_plus_lambda_times_sqrt_P;
+    X(:,L+2:2*L+1) = x_mat - sqrt_L_plus_lambda_times_sqrt_P;
+
+end

### 2010-06-04 src/Matlab/LSEstimator.m

@@ -1,0 +1,40 @@
+function [theta_est xi_est] = LSEstimator(x,phi_unwrapped,Delta,varsigma,f_max,v_0,Ts_invGamma_phi_psi)
+
+if size(x,1) > size(x,2)
+    x = x';
+end
+
+L = size(x,1);                      % size of state vector
+T = size(x,2);                      % number of time points
+Delta_squared = Delta^2;    % initialise
+
+
+for t=1:T       % for all time points
+    
+    % find v_approx = phi^T(r)x_t
+    v_approx = phi_unwrapped'*x(:,t);
+    
+    % find the firing rate using sigmoid function
+    f = f_max./(1+exp(varsigma*(v_0-v_approx)))*Delta^2;
+    
+    % find inner product with Psi
+    for n=1:size(Ts_invGamma_phi_psi,1)
+        q(:,t,n) = squeeze(Ts_invGamma_phi_psi(n,:,:))*f;
+    end
+end
+
+% form the block matrices to find LS solution
+X = [];
+Z = [];
+for t=1:T-1
+    X = [X ; [squeeze(q(:,t,:)) squeeze(x(:,t))]];
+    Z = [Z ; squeeze(x(:,t+1))]; 
+end
+
+% get parameter estimate
+parameters_est = (X'*X)\X'*Z;
+theta_est(1) = parameters_est(1);
+theta_est(2) = parameters_est(2);
+theta_est(3) = parameters_est(3);
+xi_est = parameters_est(4);
+% zeta_est = -(parameters_est(4)-1)/Ts

### 2010-06-04 src/Matlab/PredictStateAndCovariance.m

@@ -1,0 +1,11 @@
+% calculate predicted state and covariance
+
+function [x_minus P_minus] = PredictStateAndCovariance(Wm,Wc,Q_X,Sigma_e)
+
+x_minus = Q_X*Wm;
+temp = Q_X - repmat(x_minus,1,size(Q_X,2));
+temp2 = zeros(size(Q_X,2),size(Q_X,1),size(Q_X,1));
+for n=1:size(Q_X,2)
+    temp2(n,:,:) = Wc(n)*temp(:,n)*temp(:,n)';
+end
+P_minus  =squeeze(sum(temp2,1)) + Sigma_e;

### 2010-06-04 src/Matlab/Q.m

@@ -1,0 +1,32 @@
+function Q_X = Q(X,phi_unwrapped,Ts_invGamma_theta_phi_psi,Delta_squared,f_max,varsigma,v_0,xi)
+
+% compute the approximated field
+% phi^T(r)x_t
+v_approx = X'*phi_unwrapped;
+
+% for checking - to be removed later
+% for n=1:size(X,2)
+%     v_approx2(n,:) = X(:,n)'*phi_unwrapped;
+% end
+% figure
+% imagesc(v_approx-v_approx2)
+
+f = f_max./(1+exp(varsigma*(v_0-v_approx)))*Delta_squared;
+% Ts_invGamma_theta_phi_psi = *Ts_invGamma_theta_phi_psi;
+
+temp = zeros(size(X));
+for n=1:size(f,1)
+    temp(:,n) = Ts_invGamma_theta_phi_psi*f(n,:)';
+end
+
+% this part is also used for testing
+% for n=1:163
+%     for nn=1:81
+%         temp2(nn,:) = f(n,:).*Psi_with_theta(nn,:);
+%     end
+%     out(n,:) = sum(temp2,2);
+% end
+% figure
+% imagesc(temp'-out)   
+
+Q_X = temp + xi*X;

### 2010-06-04 src/Matlab/RunBatch.m

@@ -1,0 +1,15 @@
+% Run batch job
+clc
+clear
+close all
+
+RunningBatch = 1;
+NRealisations = 80;
+for Realisation=1:NRealisations
+    tic
+    disp(['Running realisation: ' num2str(Realisation) ' of ' num2str(NRealisations)])
+    disp('generating data')
+    GenerateData
+    RunFilter
+    t_realisation = toc
+end

### 2010-06-04 src/Matlab/RunFilter.m

@@ -1,0 +1,78 @@
+
+% if we are running a batch than we dont want to clear things
+if exist('RunningBatch') == 0
+    clear
+    close all
+    clc
+    load Parameters
+end
+
+% first create all the constants that we can do analytically
+Create_phi
+Create_Gamma
+Create_Psi
+Create_C
+Create_Sigma_e
+
+% initialize state sequence
+P  = 2*Sigma_e;
+x = (mvnrnd(zeros(1,L),Sigma_e,T))';
+
+% use initial state sequence to get parameter estimate
+[theta xi] = LSEstimator(x,phi_unwrapped,Delta,varsigma,f_max,v_0,Ts_invGamma_phi_psi);
+disp(['Iteration 0, theta = ' num2str(theta) ', xi = ' num2str(xi)])          
+
+% use estiamted parameters to create the Psi matrix
+Create_Psi
+
+% set filter parameters
+alpha   = 1e-3;
+kappa = 3-L;
+beta = 2;
+lambda = alpha^2*(L+kappa)-L;
+
+% calculate the weigths
+Wm = [lambda/(L+lambda) ; 1/(2*(L+lambda))*ones(2*L,1)];
+Wc = [(lambda/(L+lambda)) + (1-alpha^2+beta) ; 1/(2*(L+lambda))*ones(2*L,1)];
+
+% for calculating the sigma matrix
+sqrt_L_plus_lambda = sqrt(L+lambda);
+
+tic
+NIterations = 3;
+for Iteration = 1:NIterations
+    for t=1:T-1
+
+        % create the matrix of sigma vectors
+        X = GetSigmaMatrix(x(:,t),P,sqrt_L_plus_lambda);
+
+        % propagate the sigma matrix through Q
+        Q_X = Q(X,phi_unwrapped,Ts_invGamma_theta_phi_psi,Delta_squared,f_max,varsigma,v_0,xi);
+
+        % propagate the sigma matrix through the state equation, weigth and
+        % get the predicted state and covariance
+        [x_minus P_minus] = PredictStateAndCovariance(Wm,Wc,Q_X,Sigma_e);
+
+        % use observation to correct the state and covariance prediction
+        y_t_plus_1 = y(t+1,:)';
+        [x(:,t) P] = GetFilteredStateAndCovariance(P_minus,C,Sigma_varepsilon,x_minus,y_t_plus_1);
+      
[…]

### 2010-06-04 src/Matlab/Set_Parameters.m

@@ -1,0 +1,101 @@
+% set all the parameters for the model and the estimator
+
+% if we are running a batch than we dont want to clear things
+if exist('RunningBatch') == 0
+    clear
+    close all
+    clc
+end
+
+% spatial parameters
+Delta = 0.5;                          % space step for the spatial discretisation
+Delta_squared = Delta^2;
+SpaceMax = 10;                    % maximum space in mm
+SpaceMin = -SpaceMax;         % minimum space in mm
+NPoints = (SpaceMax-SpaceMin)/Delta+1;
+r = linspace(SpaceMin,SpaceMax,NPoints);      % define space
+
+% temporal parameter
+Ts = 1e-3;          % sampling period
+T = 300;            % maximum time (ms)
+
+% kernel parameters
+theta(1) = 10;     % local kernel amplitude
+theta(2) = -8;     % surround kernel amplitude
+theta(3) = 0.5;       % lateral kernel amplitude
+sigma_psi(1) = 1.8;     % local kernel width
+sigma_psi(2) = 2.4;     % surround kernel width
+sigma_psi(3) = 6;       % lateral kernel width
+psi_0 = Define2DGaussian(0,0, sigma_psi(1)^2, 0,NPoints,SpaceMin,SpaceMax);
+psi_1 = Define2DGaussian(0,0, sigma_psi(2)^2, 0,NPoints,SpaceMin,SpaceMax);
+psi_2 = Define2DGaussian(0,0, sigma_psi(3)^2, 0,NPoints,SpaceMin,SpaceMax);
+w = theta(1)*psi_0 + theta(2)*psi_1 + theta(3)*psi_2;       % the kernel
+W = fft2(w);                                                                       % the fft of the kernel
+Ts_W = W*Ts;                        % FFT of kernel times the time step
+
+% field basis function parameters
+NBasisFunctions_xy = 9;
+L = NBasisFunctions_xy^2;                   % number of states and the number of basis functions
+mu_phi_xy = linspace(-10,10,NBasisFunctions_xy);
+sigma_phi = sqrt(2.5);
+
+mu_phi = zeros(2,L);     % initialize for speed
+m=1;
+for n=1:NBasisFunctions_xy
+    for nn=1:NBasisFunctions_xy
+        mu_phi(:,m) = [mu_phi_xy(n) ; mu_phi_xy(nn)];
+        m=m+1;
+    end
+end
+
+% sensor parameters
+NSensors_xy = 9;%14;
[…]

### 2010-06-04 src/Matlab/Q.m
updated matlab code

@@ -4,29 +4,12 @@ function Q_X = Q(X,phi_unwrapped,Ts_invGamma_theta_phi_psi,Delta_squared,f_max,v
 % phi^T(r)x_t
 v_approx = X'*phi_unwrapped;
 
-% for checking - to be removed later
-% for n=1:size(X,2)
-%     v_approx2(n,:) = X(:,n)'*phi_unwrapped;
-% end
-% figure
-% imagesc(v_approx-v_approx2)
-
 f = f_max./(1+exp(varsigma*(v_0-v_approx)))*Delta_squared;
-% Ts_invGamma_theta_phi_psi = *Ts_invGamma_theta_phi_psi;
 
+% loop through sigma vector
 temp = zeros(size(X));
 for n=1:size(f,1)
     temp(:,n) = Ts_invGamma_theta_phi_psi*f(n,:)';
 end
-
-% this part is also used for testing
-% for n=1:163
-%     for nn=1:81
-%         temp2(nn,:) = f(n,:).*Psi_with_theta(nn,:);
-%     end
-%     out(n,:) = sum(temp2,2);
-% end
-% figure
-% imagesc(temp'-out)   
 
 Q_X = temp + xi*X;

### 2010-06-04 src/Matlab/Set_Parameters.m

@@ -49,11 +49,11 @@ for n=1:NBasisFunctions_xy
 end
 
 % sensor parameters
-NSensors_xy = 9;%14;
+NSensors_xy = 11;%14;
 NSensors = NSensors_xy^2;
 mu_y_xy = linspace(-10,10,NSensors_xy);%linspace(-9.75,9.75,NSensors_xy);               % sensor centers
 sensor_indexes = (mu_y_xy+SpaceMax)/Delta +1;             % so we can easily get the observations from the filed filtered by the sensors
-sigma_y = 0.9;                                                         % sensor width
+sigma_y = 0.6;                                                         % sensor width
 m = Define2DGaussian(0,0, sigma_y^2, 0,NPoints,SpaceMin,SpaceMax);
 M = fft2(m);                                            % fft of sensor kernel to get observations quickly
 % define all sensor centers
@@ -71,7 +71,7 @@ sigma_varepsilon = 0.0001;
 Sigma_varepsilon = sigma_varepsilon*eye(NSensors);        % observation covariance matrix
 
 % sigmoid parameters
-f_max = 20;             % maximum firing rate
+f_max = 10;             % maximum firing rate
 varsigma = 0.8;         % sigmoid slope
 v_0 = 2;                    % firing threshold
 

### 2010-06-04 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
add Matlab code for filter and model to src/Matlab
updated matlab code
analytic sensor and basis charactristics  plot

@@
 
-\begin{figure}
+\begin{figure*}
 	\label{fig:FreqAnalysis} 
@@
 \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 200 time steps) of the observed field.}
-\end{figure}
+\end{figure*}
 Following this, the distance between basis function, $\Delta_{phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updating figurs

@@
 \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
-\caption{Distribution of the parameters estimates over 250
+\caption{\parham{caption should be changed}Distribution of the parameters estimates over 100
 realisations.
@@
 \begin{figure}[th]
-\subfigure[$\zeta$ convergence]{\includegraphics[width=1.5in]{./Graph/ZetaConvergence.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0Convergence.pdf}}\\
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1Convergence.pdf}}
-\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2Convergence.pdf}}
+\subfigure[]{\includegraphics[scale=0.7]{./Graph/ZetaConvergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta0Convergence.pdf}}\\
+\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta1Convergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta2Convergence.pdf}}
 \caption{Convergence of the parameters averaged over 250 runs. }
@@
 \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{Distribution of the connectivity kernel basis function parameter ratios over 250 realisations.
+\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
@@
    	\end{center}
-   	\caption{The mean of average RMSE of the estimated field over 250 realisations (solid line) and the 95~\% confidence interval (grey region).
+   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).
 \dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros.

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updated field estimations plot

@@
 \subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta2Convergence.pdf}}
-\caption{Convergence of the parameters averaged over 250 runs. }
+\caption{Convergence of the parameters averaged over 100 runs. }
 \label{fig:ParametersConvergence}
@@
 The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
-\textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 200 time steps) of the observed field.}
+\textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.}
 \end{figure*}
@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the parameter and state estimation, $250$ realisations of the data were generated.
-Each realisation consisted of 200~ms of data and the estimation was applied to the final 195~ms, allowing the model to stabilise.\dean{transient!} The initial state and parameters were unknown to the estimator.
+To demonstrate the performance of the parameter and state estimation, $100$ realisations of the data were generated.
+Each realisation consisted of 500~ms of data and the estimation was applied to the final 400~ms, allowing the model to stabilise.\dean{transient!} The initial state and parameters were unknown to the estimator.
 The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates}, respectively.

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small edit to paper
make things pretty
got rid of the old version of the LS

@@
 \end{figure}
-\begin{figure}[th]
-\subfigure[]{\includegraphics[scale=0.7]{./Graph/ZetaConvergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta0Convergence.pdf}}\\
-\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta1Convergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta2Convergence.pdf}}
+\begin{figure*}[th]
+\subfigure[]{\includegraphics[scale=0.5]{./Graph/ZetaConvergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta0Convergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta1Convergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta2Convergence.pdf}}
 \caption{Convergence of the parameters averaged over 100 runs. }
 \label{fig:ParametersConvergence}
-\end{figure}
+\end{figure*}
 \subsection{Spatial Frequency Analysis} 
@@
 
-\section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix} 
-The finite state space model  given in \ref{eq:ReducedForm} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters.
-We define $L \times n_{\theta}$ matrix
-\begin{eqnarray}\label{eq:QMatrix}
-	\lefteqn {\mathbf{Q}(\mathbf{x}_t)=} \\
-&&\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}}\nonumber
-\end{eqnarray}
-by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} and using $\xi = 1-\zeta T_s$ at each time instant we can write
-\begin{eqnarray}
-	\mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+\mathbf e_0 \nonumber \\
-	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+\mathbf e_1\nonumber\\
-	&\vdots& \\
-	\mathbf x_{T}&=&\mathbf x_{T-1}+T_s \mathbf Q(\mathbf x_{T-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{T-1}+\mathbf e_{T-1} \nonumber
-\end{eqnarray}
-% in matrix form 
-% \begin{equation}
-% 	\left[
-% 	\begin{array}{cccc}
-% 		\mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}
-% 	\end{array}
-% 	\right] -\left[
-% 	\begin{array}{cccc}
-% 		\mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}
-% 	\end{array}
-% 	\right] =T_s\left[
-% 	\begin{array}{cc}
-% 		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
-% 		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
-% 	\end{array}
-% 	\right] \left[
-% 	\begin{array}{cc}
-% 		\boldsymbol{\theta} \\
-% 		\zeta
-% 	\end{array}
-% 	\right]+\left[
-% 	\begin{array}{cccc}
-% 		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
-% 	\end{array}
-% 	\right] 
-% \end{equation}
- in compact form we have 
-\begin{equation}
-	\mathbf Z=\mathbf X \mathbf W+\boldsymbol \xi 
-\end{equation}
-where 
-\begin{small}
-\begin{equation*}
-	\mathbf Z=\left[
-	\begin{array}{cccc}
-		\mathbf x_{1}-\mathbf x_{0}\\
-		\mathbf x_{2}-\mathbf x_{1}\\\vdots\\
-		\mathbf x_{T}-\mathbf x_{T-1}
-	\end{array}
-	\right],\quad \mathbf X=T_s\left[
-	\begin{array}{cccc}
-		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\
-		\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
-		\mathbf Q(\mathbf x_{T-1})&-\mathbf x_{T-1}
-	\end{array}
-	\right] 
-\end{equation*}
-\end{small}
-and
-\begin{small}
-\begin{equation*}
-\quad \mathbf W=\left[
-	\begin{array}{cc}
-		\boldsymbol{\theta} \\
-		\zeta
-	\end{array}
-	\right],\quad \boldsymbol \xi=\left[
-	\begin{array}{cccc}
-		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
-	\end{array}
-	\right] 
-\end{equation*}
-\end{small}
-using the LS method $ \mathbf W$ can be estimated 
-\begin{equation}
-	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z 
-\end{equation}
-
-\section{Parameter Estimation Using Least Squares - Dean}\label{App:LeastSquaresAppendix} 
+\section{Parameter Estimation Using Least Squares}\label{App:LeastSquaresAppendix} 
 The finite state space model given in \ref{eq:ReducedForm} is linear with respect to parameters.

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the table of parameters
changed the margin

@@
  \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
- %  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+  \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+   \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
   \usepackage{amsmath}
@@
 The PSD shows the typical $1/f$ characteristics of intracranial EEG.
-\begin{table}
+\begin{table*}
 
@@
 	$\zeta$ & 0.01 & ms$^{-1}$\\
-	$f_{max}$ & 20 & spikes/s \\
+	$f_{max}$ & 10 & spikes/s \\
 	$\varsigma$ & 0.8 & spike/mV\\
@@
 \caption{Parameters for neural field model used to generate data to demonstrate the estimation framework.}
-\end{table}
+\end{table*}
 The sensors were spaced in a regular square \dean{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \dean{1.44} which equals \dean{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \dean{$2.22$}~mm.
@@
    	\begin{center}
-   		\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy_1.pdf} 
+   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}} \\
+   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}} \\
    	\end{center}
    	\caption{Example of experimental design and model output.
-\textbf{a}.
-Example of the neural field with sensors.
-The centres of the sensors are shown by crosses.
-\textbf{b} Example of data generated by the model through a subset of the observations.
-\textbf{c}.
+\textbf{a} Example of data generated by the model through a subset of the observations.
+\textbf{b}.
 Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
@@
 \end{figure}
-\begin{figure*}[th]
-\subfigure[]{\includegraphics[scale=0.5]{./Graph/ZetaConvergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta0Convergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta1Convergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta2Convergence.pdf}}
+\begin{figure}[th]
+\subfigure[]{\includegraphics[scale=0.55]{./Graph/ZetaConvergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta0Convergence.pdf}}\\
+\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta1Convergence.pdf}}
+\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta2Convergence.pdf}}
 \caption{Convergence of the parameters averaged over 100 runs. }
 \label{fig:ParametersConvergence}
-\end{figure*}
+\end{figure}
 \subsection{Spatial Frequency Analysis} 

### 2010-06-06 src/Bases.py
Analytic implementation of the code

@@ -1,0 +1,263 @@
+from __future__ import division
+import pylab as pb
+import numpy as np
+
+class basis():
+	'''This is a class to define Gaussian basis functions'''
+
+	def __init__(self,center,width,dimension,constant=1):
+		'''
+		Arguments
+		---------
+			center: matrix dimension X 1
+				center of the gaussian	
+			width: covariance of the gaussian sigma^2
+				float
+			dimension: int
+					
+			constant: float
+				must be one, this is just to calculate the covariance of two gaussian basis functions'''
+
+		self.center=pb.matrix(center)
+		self.width=width
+		self.dimension=dimension
+		self.constant=constant
+		assert type(self.center) is pb.matrix, 'center must be a matrix'
+		assert self.center.shape==(self.dimension,1), 'center shape mismatch'
+		assert type(width) is float,'width must be float type'
+
+	def __call__(self,s):
+
+		assert type(s) is pb.matrix, 'input must be a matrix'
+		assert s.shape==(self.dimension,1), 'input shape mismatch'
+		return float(self.constant*pb.exp(-1/(self.width)*(s-self.center).T*(s-self.center)))
+
+	def __repr__(self):
+		return 'Gaussian basis function;'+'center='+str(self.center) +',width='+str(self.width) 
+
+	def conv(self,In):
+
+		'''calculates the convolution of two gaussian basis functions
+			Argument
+			--------
+			In: gaussian basis function
+			Returns
+			--------
+			convolution of two gaussian basis functions'''
+
+		assert In.__class__ is basis, 'The input must be a Gaussian basis function'
+		
+		convolution_weight=((pb.pi*self.width*In.width)/(self.width+In.width))**(self.dimension*0.5)
+		convolution_width=self.width+In.width
+		convolution_center=self.center+In.center
+		return basis(convolution_center,convolution_width,self.dimension,constant=convolution_weight)
+
+	def FT(self):
+
[…]

### 2010-06-06 src/Data_generator.py

@@ -1,0 +1,413 @@
+#Built-in modules
+from __future__ import division
+import pylab as pb
+import numpy as np
+import time
+import os
+from scipy import signal
+import scipy as sp
+from Bases import basis
+
+
+class ODE():
+
+	"""class defining a non-linear, Integro-Difference, discrete-time state space model.
+
+	Arguments
+	----------
+	kernel: 
+		IDE kernel.
+	field : 
+		spatial field.
+	act_fun : 
+		Sigmoidal activation function.
+	alpha : Integer
+		alpha = 1/tau, post-synaptic time constant, (Wendling, 2002, 100 for excitatory, 500 for inhibitory), Schiff = 3
+
+	beta : field covariance function
+
+	field_noise_variance: float
+		The process noise variance, which drives the dynamic system
+	obs_noise_covariance: matrix
+		Observation noise covariance
+	Sensorwidth: float
+		Sensor diameter in mm
+	obs_locns: List of matrix
+		Sensors locations
+	spacestep: float
+		Spatial step size for descritization in mm
+	Ts: float
+		sampling time, seconds
+	Attributes
+	----------
+	"""
+
+	def __init__(self,kernel,sensor_kernel,Sensor_vector,obs_locns,observation_locs_mm,gamma,gamma_weight,Sigma_varepsilon,act_fun,zeta,Ts,simulation_field_space,simulation_field_spacestep):
+
+		self.kernel = kernel
+		self.sensor_kernel=sensor_kernel
+		self.Sensor_vector=Sensor_vector
+		self.obs_locns=obs_locns
+		self.observation_locs_mm=observation_locs_mm
+		self.gamma=gamma
+		self.gamma_weight=gamma_weight
+		self.Sigma_varepsilon=Sigma_varepsilon
+		self.act_fun = act_fun
+		self.zeta=zeta
+		self.Ts=Ts
+		self.simulation_field_spacestep=simulation_field_spacestep
+		self.simulation_field_space=simulation_field_space
+		self.ny=len(self.obs_locns)
+		self.xi=1-(self.Ts*self.zeta)
+
+	def gen_ssmodel(self):
+
+		"""
+		generates nonlinear IDE
+		Arguments
+		---------
+		if sim=1 it generates K (sum of kernels which is used in simulation), the reason is finding K is faster
[…]

### 2010-06-06 src/IDE_Analytic.py

@@ -1,0 +1,1108 @@
+#Built-in modules
+from __future__ import division
+import pylab as pb
+import numpy as np
+import matplotlib.axes3d
+import time
+import os
+from scipy import signal
+import scipy as sp
+
+
+class IDE():
+
+	"""class defining a non-linear, Integro-Difference, discrete-time state space model.
+
+	Arguments
+	----------
+	kernel: 
+		IDE kernel.
+	field : 
+		spatial field.
+	act_fun : 
+		Sigmoidal activation function.
+	alpha : Integer
+		alpha = 1/tau, post-synaptic time constant, (Wendling, 2002, 100 for excitatory, 500 for inhibitory), Schiff = 3
+
+	beta : field covariance function
+
+	field_noise_variance: float
+		The process noise variance, which drives the dynamic system
+	obs_noise_covariance: matrix
+		Observation noise covariance
+	Sensorwidth: float
+		Sensor diameter in mm
+	obs_locns: List of matrix
+		Sensors locations
+	spacestep: float
+		Spatial step size for descritization in mm
+	Ts: float
+		sampling time, seconds
+	Attributes
+	----------
+	"""
+
+	def __init__(self,kernel,field,sensor_kernel,obs_locns,gamma,gamma_weight,Sigma_varepsilon,act_fun,x0,P0,zeta,Ts,field_space,spacestep):
+
+		self.kernel = kernel
+		self.field = field
+		self.sensor_kernel=sensor_kernel
+		self.obs_locns=obs_locns
+		self.gamma=gamma
+		self.gamma_weight=gamma_weight
+		self.Sigma_varepsilon=Sigma_varepsilon
+		self.act_fun = act_fun
+		self.x0=x0
+		self.P0=P0
+		self.zeta=zeta
+		self.Ts=Ts
+		self.spacestep=spacestep
+		self.field_space=field_space
+		self.nx=len(self.field.Phi)
+		self.ny=len(self.obs_locns)
+		self.xi=1-(self.Ts*self.zeta)
+
+	def gen_ssmodel(self):
+
+
+	
+		# unpack the kernel
[…]

### 2010-06-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Analytic implementation of the code
changing the RMSE value in the text

@@
 Although a wide distribution can be seen over the parameter estimates, the ratio between them remains within a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.19\pm 0.01$.
-The RMSE of the field estimate over time is also shown in figure~\ref{fig:RMSE}.
+The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.5\pm 0.02$.
+The RMSE of the field estimates over time for 100 realizations is also shown in figure~\ref{fig:RMSE}.
 A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}.
@@
 \subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
-\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
+% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
 \caption{Results for connectivity estimate.
@@
 Therefore a least square (LS) method can be applied to estimate the unknown parameters.
-The create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
+To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
 \begin{equation}

### 2010-06-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to the parameter convergence plot
changes to the field estimation plot
editing the results and frequency analysis

@@
 \end{table*}
-The sensors were spaced in a regular square \dean{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \dean{1.44} which equals \dean{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \dean{$2.22$}~mm.
+The sensors were spaced in a regular square \parham{14 $\times$ 14} grid, the sensor width $\sigma^2_m$ was \parham{0.81} which equals \parham{$1.5$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \parham{$1.5$}~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
@@
 \begin{figure}[th]
-\subfigure[]{\includegraphics[scale=0.55]{./Graph/ZetaConvergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta0Convergence.pdf}}\\
-\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta1Convergence.pdf}}
-\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta2Convergence.pdf}}
+\subfigure[]{\includegraphics[scale=1]{./Graph/ZetaConvergence.pdf}}
+\subfigure[][]{\includegraphics[scale=1]{./Graph/theta0Convergence.pdf}}\\
+\subfigure[][]{\includegraphics[scale=1]{./Graph/theta1Convergence.pdf}}
+\subfigure[][]{\includegraphics[scale=1]{./Graph/theta2Convergence.pdf}}
 \caption{Convergence of the parameters averaged over 100 runs. }
@@
 Figure~\ref{fig:FieldFFT}(a) shows the spatial frequency of the field.
-The cut-off frequency, $\nu_c$, was taken to be \dean{??} ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \dean{??}.
-This confirms our separation of \dean{??} was enough to prevent problems associated with aliasing.
+The cut-off frequency, $\nu_c$, was taken to be \parham{0.24} ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \parham{2.05}mm.
+This confirms our separation of \parham{1.5}mm was enough to prevent problems associated with aliasing.
 
 The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis}(c).
-The peak power of the spatial frequency of the observations was approximately \dean{$??$}~dB.
-The cut-off frequency (-3~dB point) was taken to correspond to  approximately \dean{$??$}~dB.
-This provided a conservative estimate of the spatial bandwidth.
-The oversampling parameter $\rho_b$ was set to \dean{??} giving a minimum distance between basis functions of \dean{??} to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+The peak power of the spatial frequency of the observations was approximately \parham{$30.62$}~dB.
+The cut-off frequency (-3~dB point) was taken to correspond to  approximately \parham{$26.47$}~dB.
+This provided a conservative estimate of the spatial bandwidth equals to \parham{0.19} Hz.
+The oversampling parameter $\rho_b$ was set to \parham{1} giving a minimum distance between basis functions of \parham{2.63} to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The width of the basis functions was chosen such that the basis functions had sufficient overlap to represent the dynamic field.
-Equation~\ref{eq:WidthCutOffRelationship} (where $sigma_{\phi}^2 = $ \dean{??}) was used to confirm the width of the basis functions was sufficiently small to capture the characteristics of the field.
+Equation~\ref{eq:WidthCutOffRelationship} (where $\sigma_{\phi}^2 = $ \parham{2.5}) was used to confirm the width of the basis functions was sufficiently small to capture the characteristics of the field.
 
@@
 \end{figure*}
-Following this, the distance between basis function, $\Delta_{phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum.
-\mike{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}
+Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum.
+\mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}
 
@@
 \centering 
-\subfigure[][]{\includegraphics[scale=0.8]{./Graph/TrueField90.pdf}}
-\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimatedField90.pdf}}
-\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimationError90.pdf}}\\
+\subfigure[][]{\includegraphics[scale=0.9]{./Graph/TrueField90.pdf}}
+\subfigure[][]{\includegraphics[scale=0.9]{./Graph/EstimatedField90.pdf}}
+\subfigure[][]{\includegraphics[scale=0.9]{./Graph/EstimationError90.pdf}}\\
 \caption{Examples of the neural fields.

### 2010-06-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
correcting some typo
suggestion for spatial frequency analysis discussion

@@
 \end{equation}
-where $\rho_{phi}$ is an over-sampling parameter to determine the basis function separation.
+where $\rho_{\phi}$ is an oversampling parameter to determine the basis function separation.
 For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
@@
 Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum.
-\mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}
+\mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}
 

### 2010-06-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some edition to the smoother
fixed the reference to the Appendix E

@@
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the predicted cross-covariance matrix of the states is used with the covariance matrix.
+To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, needs to be computed.
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{App:LeastSquaresAppendix}).
 

### 2010-06-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the experimental data figure
changed the equations for exchanging the convolution and inner product
changed the notation in Appendix D to be compatible with the main text
adding the convegence to the state and parameter estimation

@@
 	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
- &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
+ &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta} \nonumber\\
 &+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
+\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}. 
 \end{eqnarray}
@@
 \begin{eqnarray}\label{eq:ReducedForm}
-	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
 &+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
@@
 which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-\begin{equation}
-	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{equation}
+\begin{eqnarray}
+	\lefteqn{\mathbf{x}_{t+1} \nonumber= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t}\nonumber \\
+& +& \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{eqnarray}
 Now we define the state disturbance as
@@
    	\begin{center}
-   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}} \\
+   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
    		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}} \\
@@
 The RMSE of the field estimates over time for 100 realizations is also shown in figure~\ref{fig:RMSE}.
-A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}.
+A snapshot of the true field, the estimated field and their corresponding error is illustrated in figure~\ref{fig:FieldEstimate}.
+The convergence of the parameter estimation is shown in figure~\ref{fig:ParametersConvergence}.
 
@@
 \begin{eqnarray}
- |\boldsymbol\Phi(\boldsymbol\nu_c)|^2=\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
-\end{eqnarray}
-%\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{n}\mathrm{exp}\left(-\frac{2}{\sigma_{\nu}^2}\boldsymbol\nu_c^\top \boldsymbol\nu_c\right)\\
+ |\boldsymbol\Phi(\boldsymbol\nu_{c})|^2=\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
+\end{eqnarray}
 solving for $\sigma_{\nu}^2$ we get
 \begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2 }.
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
 \end{equation}

### 2010-06-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed parameter distribution caption

@@
 \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
-\caption{\parham{caption should be changed}Distribution of the parameters estimates over 100
+\caption{Distribution of the parameters estimates over 100
 realisations.
-Grey bars show distributions with wider basis functions ($\sigma_{\phi} = ?$) and blue bars show improved parameter distributions with narrower basis functions ($\sigma_{\phi} = ?$).
 \textbf{a.} The distribution of the synaptic time constant estimates (true parameter: $\zeta=100$).

### 2010-06-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some edition in the appendix
added the range of i in the URTSS algorithm for clarity
edidtion to frequency respnse analysis

@@
 Now we have the final form of the state-space model where
-\begin{equation}
+\begin{equation}\label{eq:finalformstatespacemodel}
 	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t.
@@
 		\begin{equation*}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) 
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
 		\end{equation*}
@@
 		\begin{equation*}
-			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) 
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
 		\end{equation*}
@@
 Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum.
-\mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}
+\mike{Analysis said 1 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}
 
@@
 \section{Parameter Estimation Using Least Squares}\label{App:LeastSquaresAppendix} 
-The finite state space model given in \ref{eq:ReducedForm} is linear with respect to parameters.
+The finite state space model given in \ref{eq:finalformstatespacemodel} is linear with respect to parameters.
 Therefore a least square (LS) method can be applied to estimate the unknown parameters.

### 2010-06-09 ltx/BrainIDE.tex
switching to different sty for journal part 2
made some little typo changes. Also what's going on with the document class?

@@
         Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
-        Michael~Dewar}
+        Michael~Dewar,
         Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
 		David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
-        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space% <-this % stops a space
+        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}}% <-this % stops a space% <-this % stops a space
 
@@
 and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-
+\begin{equation}
+\begin{pmatrix}\alpha & \beta\\
+	\gamma & \delta
+\end{pmatrix}
+\end{equation}
 \section{Spectral Analysis and Decomposition}\label{SpectralAnalysisSection}

### 2010-06-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
made some little typo changes. Also what's going on with the document class?

--- 2010-06-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-% \documentclass[12pt]{iopart}
+\documentclass[twocolumn,10pt,a4paper]{article}		%<-use this for checking equation length
+%\documentclass[12pt]{iopart}
 
@@
 
-\title[State and Parameter Estimation for Spatio-Temporal Neural Fields]{State and Parameter Estimation for Spatio-Temporal Neural Fields}
-
-\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^{1,5}$, and Visakan Kadirkamanathan$^2$}
+\title{State and Parameter Estimation for Spatio-Temporal Neural Fields}
+
+\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^{1,5}$,\\ and Visakan Kadirkamanathan$^2$}
 
@@
 	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
- &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta} \nonumber\\
+ &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
 &+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}. 
+\int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
 \end{eqnarray}
@@
 \begin{eqnarray}\label{eq:ReducedForm}
-	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
+	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
 &+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
@@
 which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-\begin{eqnarray}
-	\lefteqn{\mathbf{x}_{t+1} \nonumber= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t}\nonumber \\
-& +& \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{eqnarray}
+\begin{equation}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{equation}
 Now we define the state disturbance as
@@
 The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, needs to be computed.
+To compute the smoother gain, the predicted cross-covariance matrix of the states is used with the covariance matrix.
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{App:LeastSquaresAppendix}).
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{LeastSquaresAppendix}).
 
@@
    	\begin{center}
-   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
+   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}} \\
    		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}} \\
@@
 Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum.
-\mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}
+\mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}
 
@@
 The RMSE of the field estimates over time for 100 realizations is also shown in figure~\ref{fig:RMSE}.
-A snapshot of the true field, the estimated field and their corresponding error is illustrated in figure~\ref{fig:FieldEstimate}.
-The convergence of the parameter estimation is shown in figure~\ref{fig:ParametersConvergence}.
+A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}.
 
@@
 \begin{eqnarray}
- |\boldsymbol\Phi(\boldsymbol\nu_{c})|^2=\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
-\end{eqnarray}
+ |\boldsymbol\Phi(\boldsymbol\nu_c)|^2=\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
+\end{eqnarray}
+%\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{n}\mathrm{exp}\left(-\frac{2}{\sigma_{\nu}^2}\boldsymbol\nu_c^\top \boldsymbol\nu_c\right)\\
 solving for $\sigma_{\nu}^2$ we get
 \begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2 }.
 \end{equation}

### 2010-06-09 src/bases.py

@@ -1,97 +1,263 @@
-import numpy as np
+from __future__ import division
 import pylab as pb
-from ideBase import ideBase
-'''Each basis that is to be used in the integrodifference equation 
-model should be defined here. 
-
-Each basis needs to have __mul__ and __conv__ oeprators that define
-inner products and convolutions, respectively.'''
+import numpy as np
 
 class basis():
-	"""class defining common aspects of every basis"""
-	def isbasis(self):
-		return True
+	'''This is a class to define Gaussian basis functions'''
 
-class gaussianBasis(basis):
-	"""class defining a Gaussian basis function
-	Arguments
-	---------
-	dimension : int
-		The dimension of the basis functions
-	center : matrix
-		The center of the basis function
-	width: matrix
-		The covariance of the basis function
-	attributes
-	----------
-	dimension : int
-		The dimension of the basis functions
-	center : matrix
-		The center of the basis function
-	width: matrix
-		The covariance of the basis function
-	constant: float
-		The convolution coefficient
-	
-	
-	"""
-	
-	def __init__(self,dimension,centre,width,constant = 1.0):
-		assert type(dimension) is int
-		self.dimension = dimension
-		self.centre = np.matrix(centre)
-		self.centre.shape = (self.dimension,1)
-		self.width = np.matrix(width)
-		# constant - The convolution coefficient
-		self.constant = float(constant)
-		# evaluate
-		#self.evaluate = lambda s: self.constant * np.exp(-(s-self.centre).T*self.width.I*(s-self.centre))
-		self.evaluate = lambda s: self.constant * np.exp(-(s-self.centre).T*self.width.I*(s-self.centre))
+	def __init__(self,center,width,dimension,constant=1):
+		'''
+		Arguments
+		---------
+			center: matrix dimension X 1
+				center of the gaussian	
+			width: covariance of the gaussian sigma^2
+				float
+			dimension: int
+					
+			constant: float
[…]

### 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the format of all plots

--- 2010-06-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \begin{figure}[th]
-\subfigure[]{\includegraphics[scale=1]{./Graph/ZetaConvergence.pdf}}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/theta0Convergence.pdf}}\\
-\subfigure[][]{\includegraphics[scale=1]{./Graph/theta1Convergence.pdf}}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/theta2Convergence.pdf}}
+\includegraphics[scale=1]{./Graph/convergence.pdf}
 \caption{Convergence of the parameters averaged over 100 runs. }
@@
 	\begin{center}
-\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
-\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
-\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
+\subfigure[][]{\includegraphics[scale=1]{./Graph/BasisChar.pdf}}
+\subfigure[][]{\includegraphics[scale=1]{./Graph/SensorChar.pdf}}
+\subfigure[][]{\includegraphics[scale=1]{./Graph/ObservationFrequencyResponse.pdf}}\\
 	\end{center}
@@
 \subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
-% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
+ \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
 \caption{Results for connectivity estimate.
@@
 \centering
-\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}
-\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\\
+\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=1]{./Graph/FFTTrueField.pdf}}
+\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=1]{./Graph/FFTEstimatedField.pdf}}\\
 \caption{Spatial frequency of the neural fields.
@@
 \centering 
-\subfigure[][]{\includegraphics[scale=0.9]{./Graph/TrueField90.pdf}}
-\subfigure[][]{\includegraphics[scale=0.9]{./Graph/EstimatedField90.pdf}}
-\subfigure[][]{\includegraphics[scale=0.9]{./Graph/EstimationError90.pdf}}\\
+\subfigure[][]{\includegraphics[scale=1]{./Graph/TrueField90.pdf}}
+\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimatedField90.pdf}}
+\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimationError90.pdf}}\\
 \caption{Examples of the neural fields.

### 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to temporal freq figure

--- 2010-06-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 %
-\documentclass[twocolumn,10pt,a4paper]{article}		%<-use this for checking equation length
-%\documentclass[12pt]{iopart}
+\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
+% \documentclass[12pt]{iopart}
 
@@
 
-\title{State and Parameter Estimation for Spatio-Temporal Neural Fields}
-
-\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^{1,5}$,\\ and Visakan Kadirkamanathan$^2$}
+\title[State and Parameter Estimation for Spatio-Temporal Neural Fields]{State and Parameter Estimation for Spatio-Temporal Neural Fields}
+
+\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^{1,5}$, and Visakan Kadirkamanathan$^2$}
 
@@
    	\begin{center}
-   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
-   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}} \\
+   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGpy.pdf}} \\
+   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSD.pdf}} \\
    	\end{center}

### 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits and added PSD figure

--- 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\ken{Risky comment if we don't get better estimates.}
 \begin{figure}[ th]\label{fig:2d_kernel}
@@
 disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 This term is added to account for uncertainty in the model.
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
 The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
@@
 \begin{eqnarray}\label{eq:ReducedForm}
-	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega \boldsymbol{\phi}(\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
+	\times d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
 \end{eqnarray}
@@
 \subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
- \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
+ % \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
 \caption{Results for connectivity estimate.

### 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits
paper edits. Model and Freq analysis

@@
 The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function
-\begin{equation}
+\begin{equation}\label{eq:ObservationEquation}
 	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t, 
@@
 \begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
 \end{equation}
@@
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
 \end{equation}
@@
 \begin{eqnarray}
-	\lefteqn{\mathbf{x}_{t+1} \nonumber= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t}\nonumber \\
-& +& \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t\nonumber \\
++ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
 \end{eqnarray}
@@
 \begin{equation}\label{eq:AppendixWt} 
-	\mathbf{e}_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
 \end{equation}
@@
 \end{equation}
-Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is
+Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{ObservationEquation} giving
+\begin{equation}\label{eq:ReducedObservationEquation}
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_td\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+\end{equation}
+The observation equation is linear and can be written in the more compact form
 \begin{equation}\label{ObservationEquation} 
@@
 Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-Based on Shannon's sampling theorem, for an accurate representation of this field by spatially discrete observations, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited.
+According to Shannon's sampling theorem the field must be spatially band-limited, for an accurate reconstruction using spatially discrete observations.
 Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
-Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, needs to satisfy
+Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
 \begin{equation}
@@
 where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied to avoid spectral aliasing effects in the representation of the hidden dynamic field $v_t(\mathbf{r})$ by the sampled observations, $\mathbf{y}_t$.
-
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to equation~\ref{eq:MinimumSensorDistance}.
+This condition must be satisfied to avoid spectral aliasing effects when reconstructing the hidden dynamic field $v_t(\mathbf{r})$ using the sampled observations, $\mathbf{y}_t$.
+
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, thus allowing the positioning of sensor in accordance to equation~\ref{eq:MinimumSensorDistance}.
 However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
-Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore band-limit the field to a known bandwidth, denoted by $\nu_{co}$.
-Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.
-
-Although such sensors avoid errors due to aliasing, they attenuate the high frequency variations in the observations.
-Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations will underestimate the high frequency component in both the field and the kernel.
-Such a remark motivates the use of sensors with wider bandwidths.
-Nevertheless, this choice would require an excessive number of sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
-Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
+Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
+Using spatially extended sensors results in spectral low-pass action, thus providing spatial anti-aliasing filtering.
+Such sensors therefore band-limit the field to a known bandwidth, denoted by $\nu_{cy}$.
+Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{cy}$ replacing $\nu_c$.
+
+Although such sensors avoid errors due to aliasing, they attenuate the high spatial frequency variations in the observations.
+Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations has the potential to underestimate the high spatial frequency components of both the field and the connectivity kernel.
+Such a remark motivates the use of sensors with wider bandwidths (narrower in space).
+Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and thus the computational demands of estimation procedure when designed experiments.
 
@@
 \begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_{\phi} < \frac{1}{2\rho_{\phi}\nu_{co}}
+	\Delta_{\phi} < \frac{1}{2\rho_{\phi}\nu_{cy}}
 \end{equation}
 where $\rho_{\phi}$ is an oversampling parameter to determine the basis function separation.
-For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
+
+The width parameter of the Gaussian basis functions can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
+To demonstrate this we begin with the 2-dimensional Gaussian basis function defined as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
+\end{equation}
+with the corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
 \end{equation}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{co}$ giving
+The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{cy}$ giving
 \begin{equation}\label{eq:WidthCutOffRelationship}
- \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{co}}^2},
+ \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2},
 \end{equation}
@@
 \begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu_{co}}= \frac{2\boldsymbol\nu_{co}^\top \boldsymbol\nu_{co}}{\ln 2}.
-\end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co}$.
+ \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln 2}.
+\end{equation}
+This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{cy}$.
 Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
@@
 At each iteration, the sequence of estimated state vectors is used to update the parameter set.
-The resulting parameters are then used to estimate a new state vector sequence for the next iteration.
+The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
 The procedure stops when the parameters converge.
@@
 \end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i$th column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 \end{equation}
-where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is a scaling parameter (see ~\cite{Haykin2001} for more details).
+where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is a scaling parameter (see~\cite{Haykin2001} for more details).
 
@@
 % The accuracy of the approximation is linked to the time step used in the temporal discretisation of the system, where the state transition appears more linear with a finer resolution. 
-Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
+% Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
 The EKF approximates the state transition equation by linearising about the current state estimates (by calculating the Jacobian) at each time instance.
@@
 \subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
- % \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
+\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
 \caption{Results for connectivity estimate.

### 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added psd plot

@@
    	\begin{center}
-   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGpy.pdf}} \\
-   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSD.pdf}} \\
+    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
+   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePSDPy.pdf}} \\
    	\end{center}

### 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some edition for plots caption

--- 2010-06-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
    	\end{center}
-   	\caption{Kernel centred at zero as a function of space.} 
+   	\caption{A mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$ used in this paper.
+The function $w(.)$ is rotationally symetric (isotropic) about zero, hence a cross section captures the important aspect of the connectivity kernel's shape.
+The kernel decays asymptotically to zero.}
    \end{figure}
@@
    	\begin{center}
-   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGpy.pdf}} \\
-   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSD.pdf}} \\
+    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
+   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePSDPy.pdf}} \\
    	\end{center}
    	\caption{Example of experimental design and model output.
-\textbf{a} Example of data generated by the model through a subset of the observations.
+\textbf{a} Example of data generated by the non-reduced model through a subset of the observations.
+The sensors were spaced in a regular square $14 \times 14$ grid.
 \textbf{b}.
@@
    \end{figure}
-% \begin{figure}[th]\label{fig:experimental design}
-% \begin{center}
-% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigurePy.pdf}}\\
-% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}}\\
-% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}}
-% \end{center}
-% \caption{Example of experimental design and model output.
-\textbf{a}.
-Example of the neural field with sensors.
-The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles.
-\textbf{b} Example of data generated by the model through the observations.
-\textbf{c}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
-% \end{figure}
+
 \begin{figure}[th]
@@
 realisations.
-\textbf{a.} The distribution of the synaptic time constant estimates (true parameter: $\zeta=100$).
+\textbf{a.} The distribution of $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the synaptic time constant (true parameter: $\xi=0.9$).
 \textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameters estimates (true parameter: $\theta_0 = 10$).
 \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).
+The dotted line shows the location of the true parameter in each case.}
 \label{fig:Parameters}
@@
 \includegraphics[scale=1]{./Graph/convergence.pdf}
-\caption{Convergence of the parameters averaged over 100 runs. }
+\caption{The absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations. The errors fall below $10^{-4}$ after six iterations. }
 \label{fig:ParametersConvergence}
@@
 \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
-\caption{Results for connectivity estimate.
+\caption{Results for connectivity kernel estimate.
 In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region.
@@
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
-\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).}
+\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
+The dotted line shows the location of the true ratio in each case.}
 \end{figure}
@@
 \textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
-As a result of the band limiting properties of the sensors and basis functions the reconstructed shows a narrower bandwidth.}
+As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
 \label{fig:FFTTrueEstimate}
@@
    	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).
+The error remains consitent over time.
 \dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros.
@@
 \caption{Examples of the neural fields.
-\textbf{a.} The true field from the non-reduced model the was used to generate data.
-\textbf{b.} The reconstructed estimated field of the reduced model.
-\textbf{c.} The absolute error between the true and reconstructed fields.}
+\textbf{a.} The true field from the non-reduced model which was used to generate data.
+\textbf{b.} The reconstructed estimated field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+\textbf{c.} The absolute error between the true and reconstructed fields, the error shows high frequency behaviour.}
 \label{fig:FieldEstimate}

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editted results section - freq analysis

@@
  \usepackage{anysize}							%<-use this for checking equation length
- \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
-  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-  \usepackage{amsmath}
+ % \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
+ %  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
+  % \usepackage{amsmath}
 \usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
@@
 
-% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002
-%  Australia} \ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002
+ Australia} \ead{dfreestone@bionicear.org}
 
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+\section{Results}\label{ResultsSection} The non-reduced neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-An example of the simulated field can be seen in figure~\ref{fig:experimental design}(a).
-This figure demonstrates the experimental design used where the sensor array was placed in the centre of the field (sensor centres marked by crosses).
-This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions.
 Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
@@
 \begin{table*}
-
 \centering
@@
 \end{table*}
-The sensors were spaced in a regular square \parham{14 $\times$ 14} grid, the sensor width $\sigma^2_m$ was \parham{0.81} which equals \parham{$1.5$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \parham{$1.5$}~mm.
+The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was 0.81 which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
-Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
+%Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
 \begin{figure}[th]\label{fig:experimental design}
@@
 Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FieldFFT}(a) shows the spatial frequency of the field.
-The cut-off frequency, $\nu_c$, was taken to be \parham{0.24} ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \parham{2.05}mm.
-This confirms our separation of \parham{1.5}mm was enough to prevent problems associated with aliasing.
-
-The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis}(c).
-The peak power of the spatial frequency of the observations was approximately \parham{$30.62$}~dB.
-The cut-off frequency (-3~dB point) was taken to correspond to  approximately \parham{$26.47$}~dB.
-This provided a conservative estimate of the spatial bandwidth equals to \parham{0.19} Hz.
-The oversampling parameter $\rho_b$ was set to \parham{1} giving a minimum distance between basis functions of \parham{2.63} to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The width of the basis functions was chosen such that the basis functions had sufficient overlap to represent the dynamic field.
-Equation~\ref{eq:WidthCutOffRelationship} (where $\sigma_{\phi}^2 = $ \parham{2.5}) was used to confirm the width of the basis functions was sufficiently small to capture the characteristics of the field.
-
+Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
+The cut-off frequency, $\nu_c$, was taken to be 0.24~Hz ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
+This confirms our separation, $\Delta_{y}$ of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
+\begin{figure}[th]
+\centering
+\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=1]{./Graph/FFTTrueField.pdf}}
+\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=1]{./Graph/FFTEstimatedField.pdf}}\\
+\caption{Spatial frequency of the neural fields.
+\textbf{a.} The average (over time) spatial frequency of the neural field.
+\textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
+As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
+\label{fig:FFTTrueEstimate}
+\end{figure}
+The spatial frequency from the observations is shown in Figure~\ref{fig:ObservationFreqAnal}.
+The cut-off frequency, $\nu_{cy}$, was taken to be $0.19$~Hz ($-3$~dB point).
+The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
+The spatial frequency response of the sensors can be seen in figure~\ref{fig:SensorFunctionFreqResponse}.
+Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
+Following this, the distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.
+The basis function width, $\sigma_{\phi}^2$, was set above the calculated width to $2.5$ as a design choice.
+This was a result of a trade-off that ensured that the lower spatial frequency components of the field were well represented at the expense of higher spatial frequency components.
+The spatial frequency response of the basis function can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
 \begin{figure*} 
-	\label{fig:FreqAnalysis} 
 	\begin{center}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/BasisChar.pdf}}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/SensorChar.pdf}}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/ObservationFrequencyResponse.pdf}}\\
+		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics[scale=1]{./Graph/ObservationFrequencyResponse.pdf}}\\	
+		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics[scale=1]{./Graph/SensorChar.pdf}}
+		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics[scale=1]{./Graph/BasisChar.pdf}}
 	\end{center}
-	\caption{Frequency analysis of the.
-\textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project.
+	\caption{Spatial frequency analysis.
+\textbf{a.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.
+project.
 The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics.
@@
 The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
-\textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.}
+\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.}
 \end{figure*}
-Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum.
-\mike{Analysis said 1 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}
-
 \subsection{State and Parameter Estimates} 
@@
 The convergence of the parameter estimation is shown in figure~\ref{fig:ParametersConvergence}.
-
 \begin{figure*}
@@
 \label{fig:ParametersRatio}
-\begin{figure}[th]
-\centering
-\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=1]{./Graph/FFTTrueField.pdf}}
-\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=1]{./Graph/FFTEstimatedField.pdf}}\\
-\caption{Spatial frequency of the neural fields.
-\textbf{a.} The average (over time) spatial frequency of the neural field.
-\textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
-As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
-\label{fig:FFTTrueEstimate}
-\end{figure}
 
@@
 \centering 
-\subfigure[][]{\includegraphics[scale=1]{./Graph/TrueField90.pdf}}
+\subfigure[][]{\label{fig:TrueField}\includegraphics[scale=1]{./Graph/TrueField90.pdf}}
 \subfigure[][]{\includegraphics[scale=1]{./Graph/EstimatedField90.pdf}}

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to the results section of the paper

@@
 Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
-The PSD shows the typical $1/f$ characteristics of intracranial EEG.
+The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
 \begin{table*}
@@
 \textbf{a} Example of data generated by the non-reduced model through a subset of the observations.
-The sensors were spaced in a regular square $14 \times 14$ grid.
 \textbf{b}.
-Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
+Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
    \end{figure}
-
+\subsection{Spatial Frequency Analysis} 
+Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
+The cut-off frequency, $\nu_c$, was taken to be 0.24~Hz ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
+This confirms the separation, $\Delta_{y}$, of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
+\begin{figure}[th]
+\centering
+\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=1]{./Graph/FFTTrueField.pdf}}
+\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=1]{./Graph/FFTEstimatedField.pdf}}\\
+\caption{Spatial frequency of the neural fields.
+\textbf{a.} The average (over time) spatial frequency of the neural field.
+\textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
+As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
+\label{fig:FFTTrueEstimate}
+\end{figure}
+The spatial frequency from the observations is shown in Figure~\ref{fig:ObservationFreqAnal}.
+The cut-off frequency, $\nu_{cy}$, was taken to be $0.19$~Hz ($-3$~dB point).
+The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
+Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
+The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.
+The basis function width, $\sigma_{\phi}^2$, was set above the calculated width to $2.5$, which reflected a design choice.
+This was a result of a trade-off that ensured that the lower spatial frequency components of the field were better represented at the expense of higher spatial frequency components.
+The spatial frequency response of the basis function can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
+\begin{figure*} 
+	\begin{center}
+		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics[scale=1]{./Graph/ObservationFrequencyResponse.pdf}}\\	
+		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics[scale=1]{./Graph/SensorChar.pdf}}
+		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics[scale=1]{./Graph/BasisChar.pdf}}
+	\end{center}
+	\caption{Spatial frequency analysis.
+\textbf{a.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.
+The symmetry of the sensors and field basis functions allow for the 1-dimensional representation of the spectral characteristics.
+The dashed line shows the cut-off frequency (-3 dB point).
+\textbf{b.} The spatial frequency response of a 1-dimensional model sensor.
+The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
+\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.}
+\end{figure*}
+\subsection{State and Parameter Estimates} 
+\label{sec:state_and_param_results}
+To demonstrate the performance of the parameter and state estimation a Monte Carlo approach was employed where $100$ realisations of the data were generated.
+Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model to stabilise and transients to die out from the initial conditions.
+The initial state and parameters were unknown to the estimator.
+The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
+The distribution of the parameters estimates are centred about the true values indicating good results.
+Although the distributions are quite wide, the ratio of the estimates for each realisation falls into relatively tight distributions, as seen in Figure~\ref{fig:ParametersRatio}, This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
+The reconstructed connectivity kernel from the estimated parameters can be seen in Figure~\ref{fig:KernelEstimates}.
+This Figure verifies the expected net shape of the connectivity kernel is in good accordance to the true kernel.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence for parameter estimates.
 \begin{figure}[th]
@@
 \begin{figure}[th]
-\includegraphics[scale=1]{./Graph/convergence.pdf}
-\caption{The absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations. The errors fall below $10^{-4}$ after six iterations. }
-\label{fig:ParametersConvergence}
+\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
+\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
+\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+\textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
+\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
+The dotted line shows the location of the true ratio in each case.}
 \end{figure}
-\subsection{Spatial Frequency Analysis} 
-Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
-The cut-off frequency, $\nu_c$, was taken to be 0.24~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
-This confirms our separation, $\Delta_{y}$ of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
-\begin{figure}[th]
-\centering
-\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=1]{./Graph/FFTTrueField.pdf}}
-\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=1]{./Graph/FFTEstimatedField.pdf}}\\
-\caption{Spatial frequency of the neural fields.
-\textbf{a.} The average (over time) spatial frequency of the neural field.
-\textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
-As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
-\label{fig:FFTTrueEstimate}
-\end{figure}
-The spatial frequency from the observations is shown in Figure~\ref{fig:ObservationFreqAnal}.
-The cut-off frequency, $\nu_{cy}$, was taken to be $0.19$~Hz ($-3$~dB point).
-The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
-Following this, the distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.
-The basis function width, $\sigma_{\phi}^2$, was set above the calculated width to $2.5$ as a design choice.
-This was a result of a trade-off that ensured that the lower spatial frequency components of the field were well represented at the expense of higher spatial frequency components.
-The spatial frequency response of the basis function can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
-\begin{figure*} 
-	\begin{center}
-		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics[scale=1]{./Graph/ObservationFrequencyResponse.pdf}}\\	
-		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics[scale=1]{./Graph/SensorChar.pdf}}
-		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics[scale=1]{./Graph/BasisChar.pdf}}
-	\end{center}
-	\caption{Spatial frequency analysis.
-\textbf{a.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.
-project.
-The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics.
-The dashed line shows the cut-off frequency (-3 dB point).
-\textbf{b} The spatial frequency response of a 1-dimensional model sensor.
-The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
-\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.}
-\end{figure*}
-\subsection{State and Parameter Estimates} 
-\label{sec:state_and_param_results}
-To demonstrate the performance of the parameter and state estimation, $100$ realisations of the data were generated.
-Each realisation consisted of 500~ms of data and the estimation was applied to the final 400~ms, allowing the model to stabilise.\dean{transient!} The initial state and parameters were unknown to the estimator.
-The distribution of the parameters and the resulting kernel are shown in figure~\ref{fig:Parameters} and figure~\ref{fig:KernelEstimates}, respectively.
-Although a wide distribution can be seen over the parameter estimates, the ratio between them remains within a narrow range as shown in figure~\ref{fig:ParametersRatio}.
-The state estimates for one realisation were evaluated by comparing the field reconstruction to the true field using the mean over time of the Root Mean Square Error (RMSE) and standard deviation of the RMSE giving $0.5\pm 0.02$.
-The RMSE of the field estimates over time for 100 realizations is also shown in figure~\ref{fig:RMSE}.
-A snapshot of the true field, the estimated field and their corresponding error is illustrated in figure~\ref{fig:FieldEstimate}.
-The convergence of the parameter estimation is shown in figure~\ref{fig:ParametersConvergence}.
+\label{fig:ParametersRatio}
 \begin{figure*}
@@
 \begin{figure}[th]
-\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
-\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
-\textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
-\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
-The dotted line shows the location of the true ratio in each case.}
+\includegraphics[scale=1]{./Graph/convergence.pdf}
+\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
+All parameters converge after six iterations.
+\dean{Parham: is this true?
+the distribution of the estimates of $\xi$ show a bias $>0.01$!} The errors fall below $10^{-4}$ after 6 iterations.
+}
+\label{fig:ParametersConvergence}
 \end{figure}
-\label{fig:ParametersRatio}
-
+
+The accuracy for state estimates were evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space) and standard deviation of the RMSE.
+The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}.
+A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}.
+This figure highlights the loss of the high spatial frequency information in the basis function decomposition.
   \begin{figure}
@@
    	\end{center}
-   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).
-The error remains consitent over time.
-\dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros.
-Also, it might be good to show the data points along the line, so we can see the number of iterations it takes to stabilise.}}
+   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). The error remains consistent over time.} 
 \label{fig:RMSE}
@@
 \textbf{a.} The true field from the non-reduced model which was used to generate data.
-\textbf{b.} The reconstructed estimated field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+\textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
 \textbf{c.} The absolute error between the true and reconstructed fields, the error shows high frequency behaviour.}

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
moved LS appendix to the main body

@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{App:LeastSquaresAppendix}).
-
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate.
+To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
+\begin{equation}
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+\end{equation}
+Now given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write
+\begin{eqnarray}
+	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \nonumber \\
+	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1 \nonumber \\
+	&\vdots& \\
+	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. \nonumber \\
+\end{eqnarray}
+This can be written in the compact form
+\begin{equation}
+	\mathbf Z=\mathbf X \mathbf W+\mathbf{e} 
+\end{equation}
+where
+\begin{small}
+\begin{equation*}
+	\mathbf Z=\left[
+	\begin{array}{cccc}
+		\mathbf x_{1}\\
+		\mathbf x_{2}\\
+		\vdots\\
+		\mathbf x_{T}
+	\end{array}
+	\right],\quad \mathbf X=\left[
+	\begin{array}{cccc}
+		\mathbf q(\mathbf x_0)& \mathbf x_{0}\\
+		\mathbf q(\mathbf x_1)& \mathbf x_{1}\\
+		\vdots & \vdots\\
+		\mathbf q(\mathbf x_{T-1})& \mathbf x_{T-1}
+	\end{array}
+	\right] 
+\end{equation*}
+\end{small}
+and
+\begin{small}
+\begin{equation*}
+\quad \mathbf W=\left[
+	\begin{array}{cc}
+		\boldsymbol{\theta} \\
+		\xi
+	\end{array}
+	\right],\quad \mathbf{e}=\left[
+	\begin{array}{cccc}
+		\mathbf e_0\\
+		\mathbf e_1\\
+		\vdots\\
+		\mathbf e_{T-1}
+	\end{array}
+	\right].
+\end{equation*}
+\end{small}
+Following this, the parameters, $ \mathbf W$, can be estimated by
+\begin{equation}
+	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+\end{equation}
 % The accuracy of the approximation is linked to the time step used in the temporal discretisation of the system, where the state transition appears more linear with a finer resolution. 
@@
 
-\section{Parameter Estimation Using Least Squares}\label{App:LeastSquaresAppendix} 
-The finite state space model given in \ref{eq:finalformstatespacemodel} is linear with respect to parameters.
-Therefore a least square (LS) method can be applied to estimate the unknown parameters.
-To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
-\begin{equation}
-	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
-\end{equation}
-Now given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write
-\begin{eqnarray}
-	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \nonumber \\
-	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1 \nonumber \\
-	&\vdots& \\
-	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. \nonumber \\
-\end{eqnarray}
-This can be written in the compact form
-\begin{equation}
-	\mathbf Z=\mathbf X \mathbf W+\mathbf{e} 
-\end{equation}
-where
-\begin{small}
-\begin{equation*}
-	\mathbf Z=\left[
-	\begin{array}{cccc}
-		\mathbf x_{1}\\
-		\mathbf x_{2}\\
-		\vdots\\
-		\mathbf x_{T}
-	\end{array}
-	\right],\quad \mathbf X=\left[
-	\begin{array}{cccc}
-		\mathbf q(\mathbf x_0)& \mathbf x_{0}\\
-		\mathbf q(\mathbf x_1)& \mathbf x_{1}\\
-		\vdots & \vdots\\
-		\mathbf q(\mathbf x_{T-1})& \mathbf x_{T-1}
-	\end{array}
-	\right] 
-\end{equation*}
-\end{small}
-and
-\begin{small}
-\begin{equation*}
-\quad \mathbf W=\left[
-	\begin{array}{cc}
-		\boldsymbol{\theta} \\
-		\xi
-	\end{array}
-	\right],\quad \mathbf{e}=\left[
-	\begin{array}{cccc}
-		\mathbf e_0\\
-		\mathbf e_1\\
-		\vdots\\
-		\mathbf e_{T-1}
-	\end{array}
-	\right].
-\end{equation*}
-\end{small}
-Following this, the parameters, $ \mathbf W$, can be estimated by
-\begin{equation}
-	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
-\end{equation}
 \section{Parameters} 

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to the discussion

@@
 \end{equation}
-Now given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write
+Now given a state estimate sequence from the URTSS, we can write
 \begin{eqnarray}
@@
 	\item boundary conditions
-	\item
+	\item more...
 \end{itemize}
 
-\dean{FIRST DESCRIBE AN OVER ALL SUMMARY OF WHAT WE HAVE DONE AND WHAT IS NOVEL}
 This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of spatio-temporal neural fields.
@@
 The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
-Using the state-space model, the unscented Rauch Tung Striebel Smoother was applied for state estimation.
+Using the state-space model, the unscented Rauch Tung Striebel smoother was applied for state estimation.
 Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
-
-\dean{DISCUSS RESULTS: FREQ ANALYSIS. USE THIS TO JUSTIFY KERNEL ERRORS.}
+Though our novel procedure, we have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic time constant.
+
 The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
-In addition to providing conditions to ensure the reduced model can capture the significant spectral properties of the field, these tools can be used to better design electrophysiological recording techniques avoid spatial aliasing.
+In addition to providing conditions to ensure the reduced model can capture the significant spectral properties of the field, these new tools can be used to better design electrophysiological recording techniques avoid spatial aliasing.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
+This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
 The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel.
-Therefore some information will be lost due to the field decomposition.
-The implication of this loss of information is the high spatial frequency content of the connectivity kernel.
-This is demonstrated in figure~\ref{fig:KernelEstimates} where the frequency content of the estimated connectivity kernel is less than the true kernel.
-
-\dean{DISCUSS THAT EVEN THOUGH THE KERNEL ESTIMATE IS NOT EXACT, IT IS USEFUL TO KNOW THE RATIO OF EXCITATION TO INHIBITION AND THAT RELATIVE MEASURES CAN BE ACCURATELY TRACKED}
-Even though the some high spatial frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
+% 
+% In practice Even though the some high spatial frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
 This is illustrated in figure~\ref{fig:FieldEstimate}.
@@
 
-\dean{NEED TO ADD SOMETHING ABOUT THE TIME CONSTANT }
-
-\dean{DISCUSS THE IMPLICATION OF ESTIMATING INTRACORTICAL CONNECTIVITY AND WHERE WE FIT WITHIN OTHER FUNCTIONAL CONNECTIVITY RESEARCH AREAS}
 To the authors' best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
@@
 
-\dean{DISCUSS A BIG PICTURE. WHERE THIS WORK SHOULD GO AND WHERE IT SHOULD BE APPLIED IN THE FUTURE}
 Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 
-\dean{DISCUSS HOW IT CAN LINK THEORETICAL MODELLING STUDIES TO DATA.}
 This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
@@
 
-\dean{DISCUSS SHORT-COMINGS AND FUTURE WORK}
 In this paper, the widths of the connectivity kernel basis functions are assumed to be known.
@@
 
-\begin{itemize}
-	\item What about the transient! The need for activity to perform estimation. \dean{To Learn You Must Perturb!} 
-\end{itemize}
 % 

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some editions

@@
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
+Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 	\hline\hline
-\end{tabular}\label{tab:Model Parameters}
+\end{tabular}
 \caption{Parameters for neural field model used to generate data to demonstrate the estimation framework.}
+\label{tab:Model Parameters}
 \end{table*}
@@
 %Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
-\begin{figure}[th]\label{fig:experimental design}
+\begin{figure}[th]
    	\begin{center}
@@
 Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
+\label{fig:experimental design}
 \end{figure}
@@
 The dotted line shows the location of the true ratio in each case.}
+\label{fig:ParametersRatio}
 \end{figure}
-\label{fig:ParametersRatio}
 \begin{figure*}

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
corrected some little typos. Re did the symbol table as a bunch of little symbol tables as I think it looks a bit nicer...

@@
 
-% \begin{document}
-
 \title[State and Parameter Estimation for Spatio-Temporal Neural Fields]{State and Parameter Estimation for Spatio-Temporal Neural Fields}
@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\begin{figure}[ th]\label{fig:2d_kernel}
+\begin{figure}[th]\label{fig:2d_kernel}
    	\begin{center}
@@
    	\caption{A mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$ used in this paper.
-The function $w(.)$ is rotationally symetric (isotropic) about zero, hence a cross section captures the important aspect of the connectivity kernel's shape.
-The kernel decays asymptotically to zero.}
+The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross section captures the important aspect of the connectivity kernel's shape.
+The kernel decays asymptotically to zero with space.}
    \end{figure}
@@
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
+Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 \end{tabular}
-\caption{Parameters for neural field model used to generate data to demonstrate the estimation framework.}
+\caption{Parameters for the neural field model, which are used to generate synthetic data.}
 \label{tab:Model Parameters}
@@
    	\end{center}
-   	\caption{Example of experimental design and model output.
-\textbf{a} Example of data generated by the non-reduced model through a subset of the observations.
-\textbf{b}.
-Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
+   	\caption{\textbf{a.} Example of data generated by the non-reduced model.
+\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
 \label{fig:experimental design}
@@
 This confirms the separation, $\Delta_{y}$, of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
-\begin{figure}[th]
+\begin{figure}
 \centering
@@
 \textbf{a.} The average (over time) spatial frequency of the neural field.
-\textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition.
+\textbf{b.} The average (over time) spatial frequency of the estimated neural field.
 As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
@@
 \begin{figure}[th]
+    \centering
     \subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
@@
     \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
-\caption{Distribution of the parameters estimates over 100
+\caption{Distribution of the parameter estimates over 100
 realisations.
@@
 % In practice Even though the some high spatial frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
-This is illustrated in figure~\ref{fig:FieldEstimate}.
-In addition, the ratio of the kernel parameters follows a tight distribution as seen in figure~\ref{fig:ParametersRatio}.
+This is illustrated in Figure~\ref{fig:FieldEstimate}.
+In addition, the ratio of the kernel parameters follows a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
 This indicates that the ratio of excitation to inhibition can be tracked with this approach.
@@
 
-\section{Parameters} 
-\begin{tabular}
-	{c|c} Symbol & Description \\
-	\hline
-	\\ & \textbf{Domain and indicies} \\
-	\hline
+\section{Notation}
+
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular}{cl}
         $\Omega$ & spatial domain \\
@@
 	    $n$ & sensor index $n=1,..,N$ \\
-	$T$ & time step \\
-	\\ & \textbf{Spatiotemporal Signals} \\
-	\hline
+    	$T$ & time step
+    \end{tabular}
+    \caption{Domain and indices}
+\end{table}
+
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular}{cl}
         $y(\mathbf{r}_n,t)$ & observation \\
@@
     	$f(\mathbf{r},t)$ & firing function rate \\
-	$u(\mathbf{r},t)$ & external input \\
     	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
-	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance $\Sigma_\epsilon$ \\
-	\\ & \textbf{Model} \\
-	\hline
+    	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance$\Sigma_\epsilon$ \\
+    \end{tabular}
+    \caption{Spatiotemporal Signals}
+\end{table}
+
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular}{cl}
         	$h(t)$ & post-synaptic response kernel \\
-	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, variance $\sigma_m^2$ \\
+	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
 	$\eta(t)$ & Heaviside function \\
@@
 	$D$ & Temporal differential operator \\
-	$\xi$ & time constant parameter \\
-	\\ & \textbf{Decomposition} \\
-	\hline
+	$\xi$ & time constant parameter
+    \end{tabular}
+    \caption{Model}
+\end{table}
+
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular}{cl}
         $L$ & number of field basis functions  \\
@@
     	$\mathbf{C}$ & observation matrix \\
-	\\ & \textbf{Frequency Analysis} \\
-	\hline
+    \end{tabular}
+    \caption{Decomposition}
+\end{table}
+
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular}{cl}
         $V(\nu)$ & Spectrum of the dynamic field \\
@@
 	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
-	\\ & \textbf{State Estimation} \\
-	\hline
+    \end{tabular}
+    \caption{Frequency Analysis}
+\end{table}
+
+\begin{table}[h!]\footnotesize
+    \centering
+    \begin{tabular}{cl}
         $\hat{\mathbf{x}}$ & State estimate \\
@@
     	$P^f_t$ & Forward posterior covariance matrix \\
-	$P^{f-}_t$ & Forward prior covariance matrix \\
+    	$P^{f-}_t$ & Forward prior covariance matrix
     \end{tabular}
+    \caption{State Estimation}
+\end{table}
+
+\newpage
+
 \section*{References} 

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the table size
paper edits, typos

@@
 In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
-The model-based technique proposed in this paper estimates the connectivity structure of the number of sensors.
+The model-based technique proposed in this paper estimates the connectivity structure independently of the number of sensors.
 An advantage of the auto-regressive (AR) methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
@@
 In this paper, the widths of the connectivity kernel basis functions are assumed to be known.
-In future work, we plan to extend this work to estimate the connectivity structure width unknown kernel basis function widths.
+In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths.
 We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure take care of the weights.

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edited the abstract

--- 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model to estimate the state and parameters of the non-reduced model.
-The estimation procedure consists of a two-stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+We use the reduced model to estimate the state and parameters of the full neural field model.
+The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
 The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
-The results also illustrate the cost of the model reduction with a loss of the high spatial frequency information.
+The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
 This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models.
@@
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
-\begin{table*}
+\begin{table*}\footnotesize
 \centering

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed non-reduced model to full neural field model in the paper

@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The non-reduced neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+\section{Results}\label{ResultsSection} The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
@@
    	\end{center}
-   	\caption{\textbf{a.} Example of data generated by the non-reduced model.
+   	\caption{\textbf{a.} Example of data generated by the full neural field model.
 \textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
@@
 \caption{Examples of the neural fields.
-\textbf{a.} The true field from the non-reduced model which was used to generate data.
+\textbf{a.} The true field from the full neural field model which was used to generate data.
 \textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
fixed some typos in paper

@@
 \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain.
-\textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain.
-\dean{Note: needs to be changed to absolute values if we include it.} \dean{Note: Power and dB needs to be non-italicised.}}
+\textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain.}
 \label{fig:KernelEstimates}
@@
 All parameters converge after six iterations.
-\dean{Parham: is this true?
-the distribution of the estimates of $\xi$ show a bias $>0.01$!} The errors fall below $10^{-4}$ after 6 iterations.
+The mean difference between errors in consecutive iterations falls below $10^{-4}$ after 6 iterations.
 }

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
general paper edits

@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model to estimate the state and parameters of the full neural field model.
+We use the reduced model to estimate the parameters of the full neural field model.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
@@
 Patient specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
+Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
 However the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
@@
 An estimation framework for neural field models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has recently been proposed for studying evoked potential dynamics.
-Via a Bayesian inference scheme, DCM estimates the long range connectivity structure between the specific isolated brain regions that best explains a given data set under the Jansen and Ritt equations.
-Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations \cite{schiff2008kalman}.
+Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations.
+Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations~\cite{schiff2008kalman}.
 This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation of modified WC equations.
@@
 Until now, estimation of local intracortical connectivity structure has not been reported (to the best of the authors knowledge).
-Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}.
+Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
 The key development from this recent paper was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation locations (recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.
+In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
 
@@
 
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model \cite{Wilson1973}.
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient-specific data.
@@
 \end{eqnarray}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an i.i.d.
-disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors, $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ and $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate Normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors, $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ and $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
@@
 \end{equation}
-which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+which is constant and can be defined analytically. Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
 \begin{eqnarray}
@@
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field.
+The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture \dean{should this be `represent' instead of `capture'?} the dominant spectral information of the field.
 Thus, the minimum distance between basis functions must satisfy
@@
 This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{cy}$.
-Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
+Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 
@@
 The unscented Rauch Tung Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
-The URTSS incorporates an unscented Kalman Filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
@@
 It should be noted that  the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
-Therefore, the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms.
+Therefore, the additive form of the URTSS is used, otherwise the state vector should be augmented with the noise terms.
 The additive disturbance form reduces the dimension and the number of sigma points used in the algorithm.
@@
    	\end{center}
-   	\caption{\textbf{a.} Example of data generated by the full neural field model.
+   	\caption{\textbf{a.} Example of data generated by the full neural field model from the first 5 sensors.
 \textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
@@
 
-\dean{NOTE: I HAVE ADDED A SENTENCE DESCRIBING SIMPLY WHAT I WANT TO SAY IN EACH PARAGRAPH. PLEASE USE THIS AS A GUIDE FOR EDITING.}
-
 POSSIBLE SOURCES OF THE ERROR
@@
 where $\xi = 1 - T_s \zeta$. 
-\section{Numerical Simulation of IDE Model}\label{Space Discretization} To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
-\begin{eqnarray}
-	\label{discrete space} \lefteqn{v_{t+1}\left(\mathbf{r}_{ij}\right)=}\nonumber\\
-&&\xi v_t\left(\mathbf{r}_{ij}\right)+T_s \Delta^2\sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{w\left(\mathbf{r}-\mathbf{r}_{ij}'\right)f\left( v_t\left( \mathbf{r}_{ij}'\right)\right)}}\nonumber\\
-&+& e_t(\mathbf{r}_{i,j}), 
-\end{eqnarray}
-where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
+% \section{Numerical Simulation of IDE Model}\label{Space Discretization} To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
+% \begin{eqnarray}
+% 	\label{discrete space} \lefteqn{v_{t+1}\left(\mathbf{r}_{ij}\right)=}\nonumber\\
+% &&\xi v_t\left(\mathbf{r}_{ij}\right)+T_s \Delta^2\sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{w\left(\mathbf{r}-\mathbf{r}_{ij}'\right)f\left( v_t\left( \mathbf{r}_{ij}'\right)\right)}}\nonumber\\
+% &+& e_t(\mathbf{r}_{i,j}), 
+% \end{eqnarray}
+% where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
 % \section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} 
@@
 \end{eqnarray}
-\section{Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} }\label{ap:FrequencyAnalysis}
+\section{Derivation for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} }\label{ap:FrequencyAnalysis}
 Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to an \textit{n}-dimensional Gaussian centered at the origin yields

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
discussion edits

@@
 The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
+The effect of the basis function decomposition will restrict the frequency content of the estimated field.
+This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
+The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel.
 Using the state-space model, the unscented Rauch Tung Striebel smoother was applied for state estimation.
@@
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
-The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel.
+
 % 
@@
 Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
-In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and under anaesthesia.
+In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.
 

### 2010-06-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed table1
changed the units in Table 1 - only one left to do is
made a large number of smallish changes. Please run a diff to check between versions and see what you thinkcd Dropbox/Projects/BrainIDE/cd Dropbox/Projects/BrainIDE/

@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model to estimate the parameters of the full neural field model.
+We use the reduced model to estimate the parameters of the full neural field model \mike{not sure what this last sentence meant?}.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
@@
 
-\section{Introduction} This paper presents a theoretical framework for generating patient-specific macroscopic neural field mathematical models from data.
-There has been much interest in generating physiologically plausible neural field models to study brain dynamics at the meso/macroscopic scale.
+\section{Introduction}
+
+Generating physiologically plausible neural field models are of great importance in order to study brain dynamics at the meso/macroscopic scale.
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
 Understanding the brain at this level is extremely important since it is this scale at which pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews).
@@
 
-This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
+We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
 In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
-Until now, estimation of local intracortical connectivity structure has not been reported (to the best of the authors knowledge).
-Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
-The key development from this recent paper was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation locations (recording electrodes in this case).
+Until now, estimation of local intracortical connectivity structure has not been reported (to the best of the authors' knowledge).
+Our work builds on recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
+The key development here was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation locations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
 
-Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (AR) models: that the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
-
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the Wilson and Cowan neural field model~\cite{Wilson1973}.
+Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (AR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+
+In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient-specific data.
@@
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Next, a reduced finite dimensional neural field model is derived.
+Next, a finite dimensional neural field model is derived.
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
@@
 
-\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC neural field model that was used to create our intracortical connectivity estimator.
+\section{Neural Field Model}\label{NeuralModelSection}
+
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\begin{figure}[th]\label{fig:2d_kernel}
+\begin{figure}\label{fig:2d_kernel}
    	\begin{center}
@@
 The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross section captures the important aspect of the connectivity kernel's shape.
-The kernel decays asymptotically to zero with space.}
+The kernel decays asymptotically to zero.}
    \end{figure}
@@
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 This term is added to account for uncertainty in the model.
 To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
+
 The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function 
-\begin{equation}\label{eq:ObservationEquation}
+\begin{equation}
+    \label{eq:ObservationEquation}
 	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t, 
@@
 \end{equation}
-Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{ObservationEquation} giving
+Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
@@
 
-Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
+Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
 According to Shannon's sampling theorem the field must be spatially band-limited, for an accurate reconstruction using spatially discrete observations.
@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, thus allowing the positioning of sensor in accordance to equation~\ref{eq:MinimumSensorDistance}.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, stopping us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
 However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
-Using spatially extended sensors results in spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore band-limit the field to a known bandwidth, denoted by $\nu_{cy}$.
+The spatial extent of the sensors results in spectral low-pass action, thus providing spatial anti-aliasing filtering.
+Such sensors therefore can only sense the field up to a known bandwidth, denoted by $\nu_{cy}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{cy}$ replacing $\nu_c$.
@@
 Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
-Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and thus the computational demands of estimation procedure when designed experiments.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and the computational demands of the estimation procedure when designing experiments.
 
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture \dean{should this be `represent' instead of `capture'?} the dominant spectral information of the field.
-Thus, the minimum distance between basis functions must satisfy
+Again applying Shannon's Sampling Theorem, the minimum distance between basis functions must satisfy
 \begin{equation}\label{eq:BasisFunctionSeparation}
@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
@@
 Now given a state estimate sequence from the URTSS, we can write
-\begin{eqnarray}
-	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \nonumber \\
-	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1 \nonumber \\
+\begin{eqnarray*}
+	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
+	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
 	&\vdots& \\
-	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. \nonumber \\
-\end{eqnarray}
+	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
+\end{eqnarray*}
 This can be written in the compact form
@@
 \end{small}
-Following this, the parameters, $ \mathbf W$, can be estimated by
+Following this, the parameters, $ \mathbf W$, can be estimated using
 \begin{equation}
@@
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
-\begin{table*}\footnotesize
-\centering
-\begin{tabular}{c|c|c}
+\begin{table}\footnotesize
+\centering
+\begin{tabular}{ccl}
 	\hline\hline Symbol & Value & Units \\
 	\hline\hline
-	$\zeta$ & 0.01 & ms$^{-1}$\\
+	$\tau$ & 0.01 & ms$^{-1}$\\
 	$f_{max}$ & 10 & spikes/s \\
@@
 	\end{array}
-	\right]^{\top}$ & synaptic strength\\
-	$\sigma_{\psi,1}$ & 1.8 & inner connectivity kernel width\\
-	$\sigma_{\psi,2}$ & 2.4 & middle connectivity kernel width\\
-	$\sigma_{\psi,3}$ & 6 & outer connectivity kernel width\\
-	$\Sigma$ & & field disturbance covariance \\
-	sensor parameters & & \\
-	$\Delta$ & 0.5 & space step \\
-	$T_s$ & 1 & ms time step \\ 
-	\hline\hline
+	\right]^{\top}$ & mV/spike\\
+	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & 1.8, 2.4, 6 & mm\\
+	$\sigma_{m},\Delta_{y}$&0.9, 1.5&mm\\
+	$\Sigma_{\epsilon}$ &$0.1 \times I_{N} $& mm$^2$ \\
+	$\sigma_{\gamma}$&1.3&mm\\
+	$\Delta$ & 0.5 & mm \\
+	$T_s$ & 1 & ms \\ 
 \end{tabular}
@@
 \label{tab:Model Parameters}
-\end{table*}
+\end{table}
 The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was 0.81 which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
@@
 %Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
-\begin{figure}[th]
+\begin{figure}
    	\begin{center}
@@
 \centering
-\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=1]{./Graph/FFTTrueField.pdf}}
-\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=1]{./Graph/FFTEstimatedField.pdf}}\\
+\subfigure[][]{\label{fig:FieldFFT}\includegraphics{./Graph/FFTTrueField.pdf}}
+\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
 \caption{Spatial frequency of the neural fields.
@@
 The basis function width, $\sigma_{\phi}^2$, was set above the calculated width to $2.5$, which reflected a design choice.
-This was a result of a trade-off that ensured that the lower spatial frequency components of the field were better represented at the expense of higher spatial frequency components.
+This was a result of a trade-off that ensured that the lower spatial frequency components of the field were better represented at the expense of higher spatial frequency components \mike{I don't know why there's a tradeoff between estimating low and high frequency components of the kernel, and I'm not sure I've been convinced by this section}.
 The spatial frequency response of the basis function can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
-\begin{figure*} 
+\begin{figure} 
 	\begin{center}
-		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics[scale=1]{./Graph/ObservationFrequencyResponse.pdf}}\\	
-		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics[scale=1]{./Graph/SensorChar.pdf}}
-		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics[scale=1]{./Graph/BasisChar.pdf}}
+		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
+		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
+		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
 	\end{center}
@@
 \textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.}
-\end{figure*}
+\end{figure}
+
 \subsection{State and Parameter Estimates} 
@@
 To demonstrate the performance of the parameter and state estimation a Monte Carlo approach was employed where $100$ realisations of the data were generated.
-Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model to stabilise and transients to die out from the initial conditions.
+Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-The distribution of the parameters estimates are centred about the true values indicating good results.
+The distribution of the parameters estimates are centred about the true values indicating good results, except for $\xi$, which suffers from a small bias.
 Although the distributions are quite wide, the ratio of the estimates for each realisation falls into relatively tight distributions, as seen in Figure~\ref{fig:ParametersRatio}, This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
@@
 Figure~\ref{fig:ParametersConvergence} shows the rate of convergence for parameter estimates.
-\begin{figure}[th]
+\begin{figure}
     \centering
@@
 \textbf{a.} The distribution of $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the synaptic time constant (true parameter: $\xi=0.9$).
-\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameters estimates (true parameter: $\theta_0 = 10$).
+\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates (true parameter: $\theta_0 = 10$).
 \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
@@
 \end{figure}
-\begin{figure}[th]
+\begin{figure}
+    \centering
 \subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
@@
 \end{figure}
-\begin{figure*}
+\begin{figure}
+    \centering
 \subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
@@
 \label{fig:KernelEstimates}
-\end{figure*}
-\begin{figure}[th]
-\includegraphics[scale=1]{./Graph/convergence.pdf}
+\end{figure}
+\begin{figure}
+        \centering
+\includegraphics{./Graph/convergence.pdf}
 \caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
@@
    \end{figure}
-\begin{figure*}[!th]
-\centering 
-\subfigure[][]{\label{fig:TrueField}\includegraphics[scale=1]{./Graph/TrueField90.pdf}}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimatedField90.pdf}}
-\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimationError90.pdf}}\\
+
+\begin{figure}
+\centering 
+\subfigure[][]{\label{fig:TrueField}\includegraphics{./Graph/TrueField90.pdf}}
+\subfigure[][]{\includegraphics{./Graph/EstimatedField90.pdf}}
+\subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
 \caption{Examples of the neural fields.
@@
 \label{fig:FieldEstimate}
-\end{figure*}
+\end{figure}
 
@@
 
-POSSIBLE SOURCES OF THE ERROR
-\begin{itemize}
-	\item slope of nonlinearity interacting with tails of Gaussian basis functions
-	\item loss of high frequency info from basis function decomposition
-	\item distortions of the spectral content of the basis function from the nonlinearity
-	\item disturbance covariance too narrow
-	\item disturbance variance too low (not exciting the kernel enough)
-	\item boundary conditions
-	\item more...
-\end{itemize}
-
-This paper presents a novel framework for model reduction to facilitate practical state and parameter estimation of spatio-temporal neural fields.
-A basis function decomposition reduces the infinite dimensional neural field (continuous space), to a finite dimensional state-space model.
+To the authors' best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
+In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
+The model-based technique proposed in this paper estimates the connectivity structure independently of the number of sensors.
+
+The closest competitor to the integrodifference equation based approach is perhaps the multivariate auto-regressive (AR) model.
+An advantage of the AR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
+It should be noted, however, that the AR and the proposed model-based methods are complementary, where connectivity is estimated at different spatial scales \mike{really?
+Why can't we use AR models?}.
+Therefore, we envisage that by combining these methods a more realistic model can be acquired.
+A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
+
+Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a patient-specific state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
+For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
+In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+
+Parameter estimation may also have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+
+This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
+For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}.
+Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
+In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.
+
+\section{Conclusion}
+
+This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields.
+A basis function decomposition reduces the infinite dimensional neural field (continuous space) to a finite dimensional state-space model.
 The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
@@
 Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
-Though our novel procedure, we have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic time constant.
+We have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic time constant.
 
@@
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-% 
-% In practice Even though the some high spatial frequency content of the connectivity kernel is lost through the basis function decomposition, the dominant dynamics are still captured with the estimated reduced model.
-This is illustrated in Figure~\ref{fig:FieldEstimate}.
-In addition, the ratio of the kernel parameters follows a tight distribution as seen in Figure~\ref{fig:ParametersRatio}.
-This indicates that the ratio of excitation to inhibition can be tracked with this approach.
-
-To the authors' best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
-The model-based technique proposed in this paper estimates the connectivity structure independently of the number of sensors.
-An advantage of the auto-regressive (AR) methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-It should be noted, however, that the AR and the proposed model-based methods are complementary, where connectivity is estimated at different spatial scales.
-Therefore, we envisage that by combining these methods a more realistic model can be acquired.
-A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
-
-Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-Recent studies using neural field models have demonstrated the theoretical implications of specific connectivity structure of the cortical columns in neural field models, where the connectivity kernel governs where a Turing-Hopf bifurcation occurs~\cite{Hutt2005}, and the types of oscillations that can be generated~\cite{Schmidt2009}.
-This implies that if we can estimate the connectivity structure for an individual, then we could capture patient specific neurodynamics that lead to hyper-synchronous oscillatory states such as Turing patterns.
-In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
-
-Parameter estimation may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-
-This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
-For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}.
-Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
-In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.
 
@@
 Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
-
-% 
-% \section{Conclusion}\label{ConclusionSection}
-% This paper presented a novel model-based framework for patient-specific state and parameter estimation of neural fields.
-This framework enables a fundamental link between patient-specific physiologic data and theoretical neural field models.
-This link has the potential to lead to advances in our basic understanding of the dynamics of the brain at the macro/mesoscopic scale.
-Forming a greater understanding neural dynamics at this scale may lead to new and improved treatment options for diseases such as epilepsy.
 

### 2010-06-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
made some rather brutal simplifications of the latex in the wake of knowledge we'll be submitting to PLOS. Got rid of ALL the iopart junk, and joined up some horribly split equations

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%    INSTITUTE OF PHYSICS PUBLISHING                                   %
-%                                                                      %
-%   `Preparing an article for publication in an Institute of Physics   %
-%    Publishing journal using LaTeX'                                   %
-%                                                                      %
-%    LaTeX source code `ioplau2e.tex' used to generate `author         %
-%    guidelines', the documentation explaining and demonstrating use   %
-%    of the Institute of Physics Publishing LaTeX preprint files       %
-%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
-%                                                                      %
-%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
-%                                                                      %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-% First we have a character check
-%
-% ! exclamation mark    " double quote  
-% # hash                ` opening quote (grave)
-% & ampersand           ' closing quote (acute)
-% $ dollar              % percent       
-% ( open parenthesis    ) close paren.  
-% - hyphen              = equals sign
-% | vertical bar        ~ tilde         
-% @ at sign             _ underscore
-% { open curly brace    } close curly   
-% [ open square         ] close square bracket
-% + plus sign           ; semi-colon    
-% * asterisk            : colon
-% < open angle bracket  > close angle   
-% , comma               . full stop
-% ? question mark       / forward slash 
-% \ backslash           ^ circumflex
-%
-% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
-% abcdefghijklmnopqrstuvwxyz 
-% 1234567890
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
-\documentclass[12pt]{iopart}
+\documentclass[10pt,a4paper]{article}
+% \documentclass[12pt]{iopart} 
+% \usepackage{iopams,setstack}
 
-%<-comment out this for checking equations (author list too)
-\usepackage{iopams,setstack} 
-%<-comment out this for checking equations
 \usepackage{graphicx}
@@
 \makeatother
-% \usepackage{pstool}
 \renewcommand{\subcapsize}{\small}
- \usepackage{anysize}							%<-use this for checking equation length
- % \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
- %  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
-  % \usepackage{amsmath}
-\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
+
+% maths
+\usepackage{amssymb,amsfonts,amsmath}
+% notes
 \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
@@
 \newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
+
 \begin{document}
 
-\title[State and Parameter Estimation for Spatio-Temporal Neural Fields]{State and Parameter Estimation for Spatio-Temporal Neural Fields}
+\title{State and Parameter Estimation for Spatio-Temporal Neural Fields}
 
-\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^{1,5}$, and Visakan Kadirkamanathan$^2$}
+\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, \\David B. Grayden$^{1,5}$, and Visakan Kadirkamanathan$^2$}
 
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002
- Australia} \ead{dfreestone@bionicear.org}
+%\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002Australia} \ead{dfreestone@bionicear.org}
+
+\maketitle
 
@@
 \end{abstract}
-
-%Uncomment for PACS numbers title message
-%\pacs{00.00, 20.00, 42.10}
-% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
-%\vspace{2pc}
-%\noindent{\it Keywords}: Article preparation, IOP journals
-% Uncomment for Submitted to journal title message
-%\submitto{\JPA}
-% Comment out if separate title page not required
-\maketitle
 
@@
 By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
-\begin{eqnarray}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) &=&  \int_{-\infty}^t h\left(t - t'\right) \\
-	&\times&\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}'dt'. \nonumber
-\end{eqnarray}
+\begin{equation}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
+	\int_{-\infty}^t 
+	h\left(t - t'\right) \int_\Omega
+	w\left(\mathbf{r},\mathbf{r}'\right) 
+	f\left( v\left( \mathbf{r}',t \right)\right)
+	d\mathbf{r}'dt'.
+\end{equation}
 To arrive at the final form of the model we shall express the synaptic response kernel as a Green's function 
@@
 where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{eqnarray}
-	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
-	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. \nonumber
-\end{eqnarray}
+\begin{equation}
+	\label{FinalFormContinuous} 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
+\end{equation}
 To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
-\begin{eqnarray}
-	\label{DiscreteTimeModel} v_{t+T_s}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\
-	&+& e_t\left(\mathbf{r}\right), 
-\end{eqnarray}
+\begin{equation}
+	\label{DiscreteTimeModel} 
+	v_{t+T_s}\left(\mathbf{r}\right) = 
+	\xi v_t\left(\mathbf{r}\right) + 
+	T_s \int_\Omega { 
+	    w\left(\mathbf{r},\mathbf{r}'\right)
+	    f\left(v_t\left(\mathbf{r}'\right)\right) 
+	d\mathbf{r}'} 
+	+ e_t\left(\mathbf{r}\right), 
+\end{equation}
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
@@
     \label{eq:ObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t, 
+	\mathbf{y}_t =
+	\int_{\Omega}{
+	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
+	d\mathbf{r}'} + 
+	\boldsymbol{\varepsilon}_t, 
 \end{equation}
@@
 Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{eqnarray}
-	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}&=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}\nonumber \\
-	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
-\end{eqnarray}
+\begin{equation}
+	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}
+	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+\end{equation}
 Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
-\begin{eqnarray}
-	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
- &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta} \nonumber\\
-&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+\begin{equation}
+    \begin{split}
+	\label{StartofReduction}
+	\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \\
+ &T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta}  \\ & + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
 \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}. 
-\end{eqnarray}
+\end{split}
+\end{equation}
 Now defining
@@
 and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{eqnarray}\label{eq:ReducedForm}
-	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega \boldsymbol{\phi}(\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
-	\times d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{eqnarray}
+\begin{equation}
+    \label{eq:ReducedForm}
+    \begin{split}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta} \\ 
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}.
+	 \end{split}
+\end{equation}
 This can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where

### 2010-06-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
made some tiny changes to the notation tables. The notation tables suck, I think.

@@
 \begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular}{cl}
+    \begin{tabular}{ll}
         $\Omega$ & spatial domain \\
@@
 \begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular}{cl}
+    \begin{tabular}{ll}
         $y(\mathbf{r}_n,t)$ & observation \\
@@
 \begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular}{cl}
+    \begin{tabular}{ll}
         	$h(t)$ & post-synaptic response kernel \\
@@
 \begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular}{cl}
+    \begin{tabular}{ll}
         $L$ & number of field basis functions  \\
@@
 \begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular}{cl}
+    \begin{tabular}{rl}
         $V(\nu)$ & Spectrum of the dynamic field \\
@@
 \begin{table}[h!]\footnotesize
-    \centering
-    \begin{tabular}{cl}
+    \begin{tabular}{ll}
         $\hat{\mathbf{x}}$ & State estimate \\
@@
 
-\newpage
-
-\section*{References} 
 \bibliographystyle{unsrt} 

### 2010-06-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits

--- 2010-06-13 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-We use the reduced model to estimate the parameters of the full neural field model \mike{not sure what this last sentence meant?}.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, stopping us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
 However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
@@
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
+Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
+This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
+The Mexican hat connectivity kernel is typically comprised of 2 Gaussian basis functions.
 Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
@@
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
-%Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field.
 \begin{figure}
@@
 
-The closest competitor to the integrodifference equation based approach is perhaps the multivariate auto-regressive (AR) model.
-An advantage of the AR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-It should be noted, however, that the AR and the proposed model-based methods are complementary, where connectivity is estimated at different spatial scales \mike{really?
-Why can't we use AR models?}.
-Therefore, we envisage that by combining these methods a more realistic model can be acquired.
+The closest competitor to the integrodifference equation based approach is perhaps the multivariate auto-regressive (MVAR) model.
+An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
 A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
+A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
 
@@
 Parameter estimation may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
 These very different mechanisms would require very different medications for successful treatment.

### 2010-06-15 src/Matlab/RunFilter.m
added smoother to the matlab implementation

@@ -1,10 +1,10 @@
 
 % if we are running a batch than we dont want to clear things
-if exist('RunningBatch') == 0
-    clear
-    close all
-    clc
-    load Parameters
+if exist('RunningBatch','var') == 0
+%     clear
+%     close all
+%     clc
+%     load Parameters
 end
 
 % first create all the constants that we can do analytically
@@ -15,11 +15,12 @@ Create_C
 Create_Sigma_e
 
 % initialize state sequence
-P  = 2*Sigma_e;
-x = (mvnrnd(zeros(1,L),Sigma_e,T))';
+P_f = zeros(L,L,T);
+x_f = 20*mvnrnd(zeros(1,L),Sigma_e,T)';
+P_f(:,:,1)  = cov(x_f');
 
 % use initial state sequence to get parameter estimate
-[theta xi] = LSEstimator(x,phi_unwrapped,Delta,varsigma,f_max,v_0,Ts_invGamma_phi_psi);
+[theta xi] = LSEstimator(x_f,phi_unwrapped,Delta,varsigma,f_max,v_0,Ts_invGamma_phi_psi);
 disp(['Iteration 0, theta = ' num2str(theta) ', xi = ' num2str(xi)])          
 
 % use estiamted parameters to create the Psi matrix
@@ -41,26 +42,54 @@ sqrt_L_plus_lambda = sqrt(L+lambda);
 tic
 NIterations = 5;
 for Iteration = 1:NIterations
+    
+    disp('running the forward iteration (filtering)')
     for t=1:T-1
 
         % create the matrix of sigma vectors
-        X = GetSigmaMatrix(x(:,t),P,sqrt_L_plus_lambda);
+        X_f_t = GetSigmaMatrix(x_f(:,t),P_f(:,:,t),sqrt_L_plus_lambda);
 
         % propagate the sigma matrix through Q
-        Q_X = Q(X,phi_unwrapped,Ts_invGamma_theta_phi_psi,Delta_squared,f_max,varsigma,v_0,xi);
+        X_f_minus_t_plus_1 = Q(X_f_t, phi_unwrapped, Ts_invGamma_theta_phi_psi, ...
+            Delta_squared, f_max, varsigma, v_0, xi);
 
         % propagate the sigma matrix through the state equation, weigth and
         % get the predicted state and covariance
[…]

### 2010-06-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
solving conflict
corrected the typo in table1
added smoother to the matlab implementation
Visakan comments on conclusion, last paragraph

@@
 
-%\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002Australia} \ead{dfreestone@bionicear.org}
+% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002Australia} \ead{dfreestone@bionicear.org}
 
@@
 This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-The Mexican hat connectivity kernel is typically comprised of 2 Gaussian basis functions.
 Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
@@
 	\hline\hline
-	$\tau$ & 0.01 & ms$^{-1}$\\
+	$\tau$ & 0.01 & s$^{-1}$\\
 	$f_{max}$ & 10 & spikes/s \\
@@
 
-In this paper, the widths of the connectivity kernel basis functions are assumed to be known.
+In this paper,\parham{In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel.
+In future work, we plan to extent this work to relax this assumption.
+We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
+Visakan: width estimation is totally different process} the widths of the connectivity kernel basis functions are assumed to be known.
 In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths.
@@
 In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
-For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
+For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas \parham{Visakan: heteroginity is about the process not presentation, and it should be addressed by using a kernel which is different at different spatial locations}.
 In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.

### 2010-06-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some suggestions for spatial frequency analysis

@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
+Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).\parham{In order to achieve a smooth representation of the field and alleviate the effect of the disturbance we set the cut-off frequency of the basis functions lower than the observation cut-off frequency to 0.12.
+It should be noted that the smooth characteristic of Gaussian low pass filter allows  passing frequencies higher than the cut-off frequency.
+From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $2.5$.The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.} From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
 The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to paper following meeting with David, to frequency analysis method

--- 2010-06-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
-To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model.
-Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
-The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
+To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite-dimensional state-space model.
+Spatial frequency analysis methods are introduced for model selection by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
+The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation and a least squares algorithm for parameter estimation.
+The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
 The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
@@
 
-Generating physiologically plausible neural field models are of great importance in order to study brain dynamics at the meso/macroscopic scale.
+Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the meso/macroscopic scale.
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
-Understanding the brain at this level is extremely important since it is this scale at which pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+Understanding the brain at this level is extremely important since it is at this scale that pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 
@@
 
-Unfortunately, the use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient specific causes.
-Patient specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
+Unfortunately, the use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient-specific causes.
+Patient-specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
 Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
-However the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
+However, the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
 
-For models to be clinically viable they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific EEG data.
-Fitting the neural models to individuals is a highly non-trivial task and until very recently, has not been reported in the literature.
+For models to be clinically viable, they must be patient-specific.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific EEG data.
+Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
 
@@
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Next, a finite dimensional neural field model is derived.
+Then a finite dimensional neural field model is derived.
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
@@
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
-They are popular due to being parsimonious yet having a strong link with the underlying physiology.
+They are popular as they are parsimonious yet have a strong link with the underlying physiology.
 Each neural population represents a functional cortical processing unit, such as a column.
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
+Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
 
 \subsection{Derivation of the Integro-Difference Equation Representation}
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 \end{equation}
-where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by 
+where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Non-local interactions between cortical populations are described by 
 \begin{equation}
@@
 \end{equation}
-where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
-The connectivity kernel is typically a ``Mexican hat'' function which describes strong local activation, weak mid-range repression and weak long-range activation.
+where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
+The connectivity kernel is typically a ``Mexican hat'' function, which describes strong local activation, weak mid-range repression and weak long-range activation.
+An example of the connectivity kernel  used in this paper can be seen in Figure~\ref{fig:2d_kernel}.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
@@
    	\end{center}
-   	\caption{A mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$ used in this paper.
-The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross section captures the important aspect of the connectivity kernel's shape.
+   	\caption{A Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
+The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.}
@@
 \end{equation}
-To arrive at the final form of the model we shall express the synaptic response kernel as a Green's function 
+To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors, $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ and $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$, $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
@@
 \end{equation}
-Decomposition allows a continuous field to be represented by a finite dimensional state vector.
+Decomposition allows a continuous field to be represented by a finite-dimensional state vector.
 This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
@@
 where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By assuming a Gaussian isotropic connectivity structure the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
+By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 \end{equation}
-To make the simplification we first define
+To make the simplification, we first define
 \begin{equation}\label{eq:DefPsi}
@@
 \end{equation}
-Under the assumption the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
+Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}.
 Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
@@
 Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-According to Shannon's sampling theorem the field must be spatially band-limited, for an accurate reconstruction using spatially discrete observations.
-Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+According to Shannon's sampling theorem the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
+Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
@@
 To demonstrate the performance of the parameter and state estimation a Monte Carlo approach was employed where $100$ realisations of the data were generated.
-Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
+Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-The distribution of the parameters estimates are centred about the true values indicating good results, except for $\xi$, which suffers from a small bias.
-Although the distributions are quite wide, the ratio of the estimates for each realisation falls into relatively tight distributions, as seen in Figure~\ref{fig:ParametersRatio}, This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
+
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the  reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of ??
+\%).
+The distribution of the  estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) are centred about the true values, with standard deviation \dean{??}.
+\dean{ for discussion: indicating good results}.
+The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.
+The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter, though indicate a bias...
+This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
+
 The reconstructed connectivity kernel from the estimated parameters can be seen in Figure~\ref{fig:KernelEstimates}.
-This Figure verifies the expected net shape of the connectivity kernel is in good accordance to the true kernel.
+This Figure verifies the expected net shape of the estimated connectivity kernel is in good accordance to the true kernel.
+The shape is generally well preserved.
+
 Figure~\ref{fig:ParametersConvergence} shows the rate of convergence for parameter estimates.
@@
 \section{Discussion}\label{DiscussionSection}
+
+One thing that is shown is that noise has a large impact in the estimation results. To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits from David up to results

@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors according to equation~\ref{eq:MinimumSensorDistance}.
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution, such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
 The spatial extent of the sensors results in spectral low-pass action, thus providing spatial anti-aliasing filtering.
@@
 Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations has the potential to underestimate the high spatial frequency components of both the field and the connectivity kernel.
-Such a remark motivates the use of sensors with wider bandwidths (narrower in space).
+This motivates the use of sensors with wider bandwidths (narrower in space).
 Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
@@
 \end{equation}
-where $\rho_{\phi}$ is an oversampling parameter to determine the basis function separation.
+where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation.
 
 The width parameter of the Gaussian basis functions can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-To demonstrate this we begin with the 2-dimensional Gaussian basis function defined as
+To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
 \begin{equation}
@@
 \end{equation}
-This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{cy}$.
+This ensures that the basis functions can represent the field with frequency content up to $\boldsymbol\nu_{cy}$.
 Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 
-Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
-Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.
+Note that for spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
 
@@
 \begin{equation}
-	\mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i, \quad i=1, \dots, L 
+	\mathcal X_{i}=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L 
 \end{equation}
 \begin{equation}\label{eq:sigmapoints2}
-	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L}, \quad i= L+1, \dots, 2 L 
+	\mathcal X_{i}=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2 L 
 \end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 \begin{equation}\label{eq:sigmapoints3}
-	\lambda=\alpha^2( L+\kappa) - L 
+	\lambda=\alpha^2( L+\kappa) - L, 
 \end{equation}
@@
 \begin{equation}
-	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L. 
+	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
 \end{equation}
@@
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
-It should be noted that  the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
+It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
 Therefore, the additive form of the URTSS is used, otherwise the state vector should be augmented with the noise terms.
@@
 This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate.
-To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
+To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
 \begin{equation}
@@
 \begin{equation}
-	\mathbf Z=\mathbf X \mathbf W+\mathbf{e} 
+	\mathbf Z=\mathbf X \mathbf W+\mathbf{e}, 
 \end{equation}
@@
 \end{small}
-Following this, the parameters, $ \mathbf W$, can be estimated using
+Following this, the parameter estimates, $ \mathbf{\hat{W}}$, are
 \begin{equation}
-	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+	\mathbf{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
 \end{equation}
@@
 Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
-This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
+This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
+Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 \end{tabular}
-\caption{Parameters for the neural field model, which are used to generate synthetic data.}
+\caption{Parameters for the neural field model that are used to generate synthetic data.}
 \label{tab:Model Parameters}
 \end{table}
-The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was 0.81 which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
+
+The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was $0.81$, which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
@@
    	\caption{\textbf{a.} Example of data generated by the full neural field model from the first 5 sensors.
-\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
+\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
 \label{fig:experimental design}
@@
 \subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
-\caption{Spatial frequency of the neural fields.
-\textbf{a.} The average (over time) spatial frequency of the neural field.
-\textbf{b.} The average (over time) spatial frequency of the estimated neural field.
-As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
+\caption{Power in dB as a function of spatial frequency of the neural field.
+\textbf{a.} The average (over time) power of the spatial frequency of the neural field.
+\textbf{b.} The average (over time) power of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
 \label{fig:FFTTrueEstimate}
@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).\parham{In order to achieve a smooth representation of the field and alleviate the effect of the disturbance we set the cut-off frequency of the basis functions lower than the observation cut-off frequency to 0.12.
+Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).\parham{In order to achieve a smooth representation of the field and alleviate the effect of the disturbance we set the cut-off frequency of the basis functions lower than the observation cut-off frequency to 0.12.
 It should be noted that the smooth characteristic of Gaussian low pass filter allows  passing frequencies higher than the cut-off frequency.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edited the spatial frequency results

@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).\parham{In order to achieve a smooth representation of the field and alleviate the effect of the disturbance we set the cut-off frequency of the basis functions lower than the observation cut-off frequency to 0.12.
-It should be noted that the smooth characteristic of Gaussian low pass filter allows  passing frequencies higher than the cut-off frequency.
-From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $2.5$.The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.} From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
+Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.
-The basis function width, $\sigma_{\phi}^2$, was set above the calculated width to $2.5$, which reflected a design choice.
-This was a result of a trade-off that ensured that the lower spatial frequency components of the field were better represented at the expense of higher spatial frequency components \mike{I don't know why there's a tradeoff between estimating low and high frequency components of the kernel, and I'm not sure I've been convinced by this section}.
-The spatial frequency response of the basis function can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
+
+Given the basis function separation, the basis function width was set to $\sigma_{\phi}^2=2.5$.
+This facilitated a smooth representation of the field by the basis function decomposition given the basis function separation and provided further low-pass spatial filtering of the disturbance.
+From equation~\ref{eq:WidthCutOffRelationship}, this allowed the basis function decomposition to represent spatial frequencies up to approximately $0.12$~Hz.
+The spatial frequency response of the basis functions can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
 \begin{figure} 
@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the parameter and state estimation a Monte Carlo approach was employed where $100$ realisations of the data were generated.
+To demonstrate the performance of the parameter and state estimation, a Monte Carlo approach was employed where $100$ realisations of the data were generated.
 Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edited the spatial frequency results, and spatial freq method to further justify the basis function width

@@
 The width parameter of the Gaussian basis functions can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
+Alternatively, the upper spatial frequency content of the neural field modelled by the basis function decomposition can be determined, given the basis function width.
+Since Shannon's sampling theorem is derived for perfect point sensors, this is particularly useful when considering spatially distributed basis functions.
 To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
@@
 
-Given the basis function separation, the basis function width was set to $\sigma_{\phi}^2=2.5$.
-This facilitated a smooth representation of the field by the basis function decomposition given the basis function separation and provided further low-pass spatial filtering of the disturbance.
+Given the basis function separation, the basis function width was set to $\sigma_{\phi}^2=2.5$~mm.
+This facilitated a smooth representation of the field by the basis function decomposition given the basis function separation and provided low-pass spatial filtering of the field.
 From equation~\ref{eq:WidthCutOffRelationship}, this allowed the basis function decomposition to represent spatial frequencies up to approximately $0.12$~Hz.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Changes to section 3 on spectral analysis and model selection

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
-To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite-dimensional state-space model.
-Spatial frequency analysis methods are introduced for model selection by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation and a least squares algorithm for parameter estimation.
-The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
+To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model.
+Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
+The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation.
+The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework.
 The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
@@
 
-Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the meso/macroscopic scale.
+Generating physiologically plausible neural field models are of great importance in order to study brain dynamics at the meso/macroscopic scale.
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
-Understanding the brain at this level is extremely important since it is at this scale that pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
+Understanding the brain at this level is extremely important since it is this scale at which pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
 
@@
 
-Unfortunately, the use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient-specific causes.
-Patient-specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
+Unfortunately, the use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient specific causes.
+Patient specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
 Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
-However, the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
+However the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
 
-For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific EEG data.
-Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
+For models to be clinically viable they must be patient-specific.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific EEG data.
+Fitting the neural models to individuals is a highly non-trivial task and until very recently, has not been reported in the literature.
 
@@
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Then a finite dimensional neural field model is derived.
+Next, a finite dimensional neural field model is derived.
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
@@
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
-They are popular as they are parsimonious yet have a strong link with the underlying physiology.
+They are popular due to being parsimonious yet having a strong link with the underlying physiology.
 Each neural population represents a functional cortical processing unit, such as a column.
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \cite{Braitenberg1998}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
+Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
 
 \subsection{Derivation of the Integro-Difference Equation Representation}
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
@@
 \end{equation}
-where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Non-local interactions between cortical populations are described by 
+where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by 
 \begin{equation}
@@
 \end{equation}
-where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
-The connectivity kernel is typically a ``Mexican hat'' function, which describes strong local activation, weak mid-range repression and weak long-range activation.
-An example of the connectivity kernel  used in this paper can be seen in Figure~\ref{fig:2d_kernel}.
+where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface.
+The connectivity kernel is typically a ``Mexican hat'' function which describes strong local activation, weak mid-range repression and weak long-range activation.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
@@
    	\end{center}
-   	\caption{A Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
-The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+   	\caption{A mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$ used in this paper.
+The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.}
@@
 \end{equation}
-To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
+To arrive at the final form of the model we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$, $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors, $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ and $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
@@
 \end{equation}
-Decomposition allows a continuous field to be represented by a finite-dimensional state vector.
+Decomposition allows a continuous field to be represented by a finite dimensional state vector.
 This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
@@
 where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
+By assuming a Gaussian isotropic connectivity structure the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 \end{equation}
-To make the simplification, we first define
+To make the simplification we first define
 \begin{equation}\label{eq:DefPsi}
@@
 \end{equation}
-Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
+Using the same neural field basis function approximation, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}.
 Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
@@
 Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-According to Shannon's sampling theorem the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
-Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+According to Shannon's sampling theorem the field must be spatially band-limited, for an accurate reconstruction using spatially discrete observations.
+Nevertheless, an approximate reconstruction can still be obtained if the field is approximately bandlimited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors according to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution, such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
-The spatial extent of the sensors results in spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore can only sense the field up to a known bandwidth, denoted by $\nu_{cy}$.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
+However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
+The spatial response of all sensors result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
+Such sensors therefore bandlimit the field up to a known bandwidth, denoted by $\nu_{cy}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{cy}$ replacing $\nu_c$.
@@
 Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations has the potential to underestimate the high spatial frequency components of both the field and the connectivity kernel.
-This motivates the use of sensors with wider bandwidths (narrower in space).
+Such a remark motivates the use of sensors with wider bandwidths (narrower in space).
 Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
@@
 \end{equation}
-where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation.
+where $\rho_{\phi}$ is an oversampling parameter to determine the basis function separation.
 
-The width parameter of the Gaussian basis functions can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
-\begin{equation}
- \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
-\end{equation}
-with the corresponding Fourier transform
+Such spectral considerations also facilitate the choice of the basis function width parameter~\cite{Sanner1992,Scerri2009}.
+To ensure that the basis functions can represent fields with frequency content up to $\boldsymbol\nu_{cy}$, they should be chosen to poses a spectral bandwidth of at least $\boldsymbol\nu_{cy}$.
+Such a condition is satisfied by setting the width parameter such that the spectral response of the basis functions results in an attenuation of not more than 3dBs at $\boldsymbol\nu_{cy}$.
+
+To demonstrate this we begin with the 2-dimensional Gaussian basis function defined in equation \ref{eq:FieldBasisFunction}, with the corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{cy}$ giving
+Thus to obtain a 3dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
 \begin{equation}\label{eq:WidthCutOffRelationship}
@@
 \end{equation}
-This ensures that the basis functions can represent the field with frequency content up to $\boldsymbol\nu_{cy}$.
 Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 
-Note that for spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
-Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
+Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.
 
@@
 \begin{equation}
-	\mathcal X_{i}=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L 
+	\mathcal X_{i}=\bar x+(\sqrt{( L + \lambda)\mathbf P_x})_i, \quad i=1, \dots, L 
 \end{equation}
 \begin{equation}\label{eq:sigmapoints2}
-	\mathcal X_{i}=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2 L 
+	\mathcal X_{i}=\bar x-(\sqrt{( L + \lambda)\mathbf P_x})_{i- L}, \quad i= L+1, \dots, 2 L 
 \end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $(\sqrt{( L + \lambda)\mathbf P_x})_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 \begin{equation}\label{eq:sigmapoints3}
-	\lambda=\alpha^2( L+\kappa) - L, 
+	\lambda=\alpha^2( L+\kappa) - L 
 \end{equation}
@@
 \begin{equation}
-	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
+	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L. 
 \end{equation}
@@
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
-It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
+It should be noted that  the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
 Therefore, the additive form of the URTSS is used, otherwise the state vector should be augmented with the noise terms.
@@
 This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate.
-To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
+To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
 \begin{equation}
@@
 \begin{equation}
-	\mathbf Z=\mathbf X \mathbf W+\mathbf{e}, 
+	\mathbf Z=\mathbf X \mathbf W+\mathbf{e} 
 \end{equation}
@@
 \end{small}
-Following this, the parameter estimates, $ \mathbf{\hat{W}}$, are
+Following this, the parameters, $ \mathbf W$, can be estimated using
 \begin{equation}
-	\mathbf{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
 \end{equation}
@@
 Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
-This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
+This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
+The Mexican hat connectivity kernel is typically comprised of 2 Gaussian basis functions.
+Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 	\hline\hline
-	$\tau$ & 0.01 & s$^{-1}$\\
+	$\tau$ & 0.01 & ms$^{-1}$\\
 	$f_{max}$ & 10 & spikes/s \\
@@
 \end{tabular}
-\caption{Parameters for the neural field model that are used to generate synthetic data.}
+\caption{Parameters for the neural field model, which are used to generate synthetic data.}
 \label{tab:Model Parameters}
 \end{table}
-
-The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was $0.81$, which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
+The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was 0.81 which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
@@
    	\caption{\textbf{a.} Example of data generated by the full neural field model from the first 5 sensors.
-\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
+\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.}
 \label{fig:experimental design}
@@
 \subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
-\caption{Power in dB as a function of spatial frequency of the neural field.
-\textbf{a.} The average (over time) power of the spatial frequency of the neural field.
-\textbf{b.} The average (over time) power of the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
+\caption{Spatial frequency of the neural fields.
+\textbf{a.} The average (over time) spatial frequency of the neural field.
+\textbf{b.} The average (over time) spatial frequency of the estimated neural field.
+As a result of the band limiting properties of the sensors and basis functions the reconstructed field shows a narrower bandwidth.}
 \label{fig:FFTTrueEstimate}
@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).\parham{In order to achieve a smooth representation of the field and alleviate the effect of the disturbance we set the cut-off frequency of the basis functions lower than the observation cut-off frequency to 0.12.
-It should be noted that the smooth characteristic of Gaussian low pass filter allows  passing frequencies higher than the cut-off frequency.
-From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $2.5$.The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.} From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
+Using an oversampling parameter, $\rho_{\phi}$, of $1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+From equation~\ref{eq:WidthCutOffRelationship} the required basis function width to represent the dominant spatial frequencies was calculated to be $1$.
 The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.
@@
 To demonstrate the performance of the parameter and state estimation a Monte Carlo approach was employed where $100$ realisations of the data were generated.
-Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
+Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the  reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of ??
-\%).
-The distribution of the  estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) are centred about the true values, with standard deviation \dean{??}.
-\dean{ for discussion: indicating good results}.
-The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.
-The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter, though indicate a bias...
-This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
-
+The distribution of the parameters estimates are centred about the true values indicating good results, except for $\xi$, which suffers from a small bias.
+Although the distributions are quite wide, the ratio of the estimates for each realisation falls into relatively tight distributions, as seen in Figure~\ref{fig:ParametersRatio}, This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
 The reconstructed connectivity kernel from the estimated parameters can be seen in Figure~\ref{fig:KernelEstimates}.
-This Figure verifies the expected net shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The shape is generally well preserved.
-
+This Figure verifies the expected net shape of the connectivity kernel is in good accordance to the true kernel.
 Figure~\ref{fig:ParametersConvergence} shows the rate of convergence for parameter estimates.
@@
 
-One thing that is shown is that noise has a large impact in the estimation results. To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
-
 To the authors' best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
@@
 
-In this paper,\parham{In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel.
-In future work, we plan to extent this work to relax this assumption.
-We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
-Visakan: width estimation is totally different process} the widths of the connectivity kernel basis functions are assumed to be known.
+In this paper, the widths of the connectivity kernel basis functions are assumed to be known.
 In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths.
@@
 In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
-For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas \parham{Visakan: heteroginity is about the process not presentation, and it should be addressed by using a kernel which is different at different spatial locations}.
+For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas.
 In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
more paper edits

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \begin{equation} 
-	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
 \end{equation}
-where 
+and 
 \begin{equation}\label{eq:QmatrixForSigmapoints}
@@
 \end{equation}
-This ensures that the basis functions can represent the field with frequency content up to $\boldsymbol\nu_{cy}$.
+This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
 Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 
-Note that for spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid.
 Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
@@
 
-The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was $0.81$, which equals $1.5$~mm full width at half maximum, with spacing $\Delta_y$ equal to $1.5$~mm.
+The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was $0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y=1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
@@
 	\caption{Spatial frequency analysis.
-\textbf{a.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.
+\textbf{a.} Two-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.
 The symmetry of the sensors and field basis functions allow for the 1-dimensional representation of the spectral characteristics.
-The dashed line shows the cut-off frequency (-3 dB point).
 \textbf{b.} The spatial frequency response of a 1-dimensional model sensor.
 The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
-\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.}
+\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.
+The dashed line shows the cut-off frequency (-3 dB point).}
 \end{figure}
@@
 The initial state and parameters were unknown to the estimator.
+Six iterations of the estimation algorithm were required for the parameters to converge.
+
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the  reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of ??
-\%).
-The distribution of the  estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) are centred about the true values, with standard deviation \dean{??}.
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of \dean{??~\%}).
+The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviation \dean{??}.
 \dean{ for discussion: indicating good results}.
@@
 realisations.
+The dotted line shows the location of the true parameter in each case.
 \textbf{a.} The distribution of $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the synaptic time constant (true parameter: $\xi=0.9$).
@@
 \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).
-The dotted line shows the location of the true parameter in each case.}
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
 \label{fig:Parameters}
@@
 \caption{Results for connectivity kernel estimate.
-In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region.
+In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.
 \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain.
@@
 For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}.
-Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond the the theoretically derived parameters where these bump solutions can exist.
+Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond to the theoretically derived parameters where these bump solutions can exist.
 In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.
@@
 \section{Conclusion}
-
 This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields.
@@
 The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
+This is evident when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
 The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel.
@@
 The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
-In addition to providing conditions to ensure the reduced model can capture the significant spectral properties of the field, these new tools can be used to better design electrophysiological recording techniques avoid spatial aliasing.
+In addition to providing conditions to ensure the reduced model can capture the significant spectral properties of the field, these new tools can be used to better design electrophysiological recording techniques to avoid spatial aliasing.
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
@@
 In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths.
-We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure take care of the weights.
+We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure to take care of the weights.
 In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
@@
 \appendix 
-\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be perform.
-We used a one-step Euler method where Eq.~\ref{FinalFormContinuous} can be approximated by
+\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be performed.
+We used a one-step Euler method where equation~\ref{FinalFormContinuous} can be approximated by
 \begin{eqnarray}

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to distribution plots

@@
 \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).
+The solid line shows the location of the true parameter and the dashed line shows the location of the estimated parameter  in each case.}
 \label{fig:Parameters}
@@
 \textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
-The dotted line shows the location of the true ratio in each case.}
+The solid line shows the location of the true ratio and the dashed line shows the location of the estimation ratio  in each case.}
 \label{fig:ParametersRatio}

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
more paper edits
adding standard deviations of the parameters

@@
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of \dean{??~\%}).
-The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviation \dean{??}.
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of 2.5~\%).
+The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviations 2.88, 1.99 and 0.08\parham{(0.0829)} respectively.
 \dean{ for discussion: indicating good results}.
 The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.
-The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter, though indicate a bias...
+The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias...
 This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
merge changes

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 	\caption{Spatial frequency analysis.
-\textbf{a.} Two-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.
+\textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
 The symmetry of the sensors and field basis functions allow for the 1-dimensional representation of the spectral characteristics.
@@
 The initial state and parameters were unknown to the estimator.
-Six iterations of the estimation algorithm were required for the parameters to converge.
+Six iterations of the estimation algorithm was sufficient to allow the parameters to converge.
 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).
-The solid line shows the location of the true parameter and the dashed line shows the location of the estimated parameter  in each case.}
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
 \label{fig:Parameters}
@@
 \textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
-The solid line shows the location of the true ratio and the dashed line shows the location of the estimation ratio  in each case.}
+The dotted line shows the location of the true ratio in each case.}
 \label{fig:ParametersRatio}

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added table for estimates in resutls
editted table with estimates
for merge with Parham

@@
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of 2.5~\%).
-The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviations 2.88, 1.99 and 0.08\parham{(0.0829)} respectively.
-\dean{ for discussion: indicating good results}.
+The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}.
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%).
+The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.
+The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138,  \dean{ for discussion: indicating good results}.
 The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.
@@
 This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
+
+\begin{table}
+\centering
+\begin{tabular}{cccc}
+	\hline\hline Parameter & Actual Value & Mean Estimate & Standard Deviation \\
+	\hline\hline
+ 	$\xi$ & 0.9 & 0.925 & 0.004 \\
+	$\theta_0$ & 10 & 10.295 & 2.879 \\
+	$\theta_1$ & -8 & -8.571 & 1.996 \\
+	$\theta_2$ & 0.5 & 0.551 & 0.083 \\
+\end{tabular}
+\caption{Actual parameter values and mean parameter estimates and standard deviation.}
+\label{tab:Parameters estimates}
+\end{table}
 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updated results section for parameter estimates

@@
 The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.
-The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138,  \dean{ for discussion: indicating good results}.
+The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively.
 The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Changes to section 3, regarding spectral analysis and model selection

@@
 
-The width parameter of the Gaussian basis functions can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-Alternatively, the upper spatial frequency content of the neural field modelled by the basis function decomposition can be determined, given the basis function width.
-Since Shannon's sampling theorem is derived for perfect point sensors, this is particularly useful when considering spatially distributed basis functions.
-To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
-\begin{equation}
- \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
-\end{equation}
-with the corresponding Fourier transform
+Such spectral considerations also facilitate the choice of the basis function width parameter~\cite{Sanner1992,Scerri2009}.
+To ensure that the basis functions can represent fields with frequency content up to $\boldsymbol\nu_{cy}$, they should be chosen to poses a spectral bandwidth of at least $\boldsymbol\nu_{cy}$.
+This condition is satisfied by setting the width parameter such that the spectral response of the basis functions results in an attenuation of not more than 3dBs at $\boldsymbol\nu_{cy}$.
+
+To demonstrate this we begin with the 2-dimensional Gaussian basis function defined in equation \ref{eq:FieldBasisFunction}, with the corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
 Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
 
-Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid.
-Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
+Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.
 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 \end{equation}
-Using the same neural field basis function approximation, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
+Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
@@
 
-Note that for a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid.
-Thus, the knowledge of the distance between basis functions directly implies the total number of basis functions required to represent a known spatial region.
+Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Some minor changes throughout the paper

@@
 Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-According to Shannon's sampling theorem the field must be spatially band-limited, for an accurate reconstruction using spatially discrete observations.
+According to Shannon's sampling theorem, the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
 Nevertheless, an approximate reconstruction can still be obtained if the field is approximately bandlimited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
@@
 
-To demonstrate this we begin with the 2-dimensional Gaussian basis function defined in equation \ref{eq:FieldBasisFunction}, with the corresponding Fourier transform
+To ensure this, consider the 2-dimensional Gaussian basis function defined in equation \ref{eq:FieldBasisFunction}, with the corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
@@
 The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state vector sequence that guarantees the initial estimated parameter set forms a stable kernel.
+The algorithm is initialised using a bounded random state vector sequence guaranteeing that the initial estimated parameter set forms a stable kernel.
 
@@
 Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
-The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above.
+The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
 To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, needs to be computed.
@@
 It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
-Therefore, the additive form of the URTSS is used, otherwise the state vector should be augmented with the noise terms.
-The additive disturbance form reduces the dimension and the number of sigma points used in the algorithm.
+Therefore, the additive form of the URTSS is used, instead of augmenting the state vector with the noise terms with the added benefit of reducing the dimension and the number of sigma points required in the algorithm.
 \begin{algorithm}
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate.
+This feature is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
@@
 \end{small}
-Following this, the parameter estimates, $ \mathbf{\hat{W}}$, are
+Following this, the LS parameter estimates, $ \mathbf{\hat{W}}$, are
 \begin{equation}

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Minor changes in sections 5 and 5.1

@@
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
+Note that, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
 This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
@@
 
-The sensors were spaced in a regular square 14 $\times$ 14 grid, the sensor width $\sigma^2_m$ was $0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y=1.5$~mm.
-This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings.
+The sensors were spaced on a regular square 14 $\times$ 14 grid, the sensor width parameter $\sigma^2_m$ was $0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y=1.5$~mm.
+This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
 \begin{figure}
@@
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
-This confirms the separation, $\Delta_{y}$, of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
+This confirms that a separation, $\Delta_{y}$, of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
 \begin{figure}
@@
 \end{figure}
-The spatial frequency from the observations is shown in Figure~\ref{fig:ObservationFreqAnal}.
+The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
 The cut-off frequency, $\nu_{cy}$, was taken to be $0.19$~Hz ($-3$~dB point).
@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$ to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$, which is sufficient to capture the significant dynamics according to our criteria.
-
-Given the basis function separation, the basis function width was set to $\sigma_{\phi}^2=2.5$~mm.
-This facilitated a smooth representation of the field by the basis function decomposition given the basis function separation and provided low-pass spatial filtering of the field.
-From equation~\ref{eq:WidthCutOffRelationship}, this allowed the basis function decomposition to represent spatial frequencies up to approximately $0.12$~Hz.
-The spatial frequency response of the basis functions can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
+Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
+
+Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
+This allowed a smooth representation of the field by the basis function reconstruction up to a spatial frequency as given by equation~\ref{eq:WidthCutOffRelationship} of approximately $0.12$~Hz.
+This is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
 \begin{figure} 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updated results section for parameter estimates

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-According to Shannon's sampling theorem the field must be spatially band-limited, for an accurate reconstruction using spatially discrete observations.
-Nevertheless, an approximate reconstruction can still be obtained if the field is approximately bandlimited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+According to Shannon's sampling theorem the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
+Such a condition ensures that $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
-The spatial response of all sensors result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore bandlimit the field up to a known bandwidth, denoted by $\nu_{cy}$.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors according to equation~\ref{eq:MinimumSensorDistance}.
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution, such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
+The spatial extent of the sensors results in spectral low-pass action, thus providing spatial anti-aliasing filtering.
+Such sensors therefore can only sense the field up to a known bandwidth, denoted by $\nu_{cy}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{cy}$ replacing $\nu_c$.
@@
 
-Such spectral considerations also facilitate the choice of the basis function width parameter~\cite{Sanner1992,Scerri2009}.
-To ensure that the basis functions can represent fields with frequency content up to $\boldsymbol\nu_{cy}$, they should be chosen to poses a spectral bandwidth of at least $\boldsymbol\nu_{cy}$.
-This condition is satisfied by setting the width parameter such that the spectral response of the basis functions results in an attenuation of not more than 3dBs at $\boldsymbol\nu_{cy}$.
-
-To demonstrate this we begin with the 2-dimensional Gaussian basis function defined in equation \ref{eq:FieldBasisFunction}, with the corresponding Fourier transform
+The width parameter of the Gaussian basis functions can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
+Alternatively, the upper spatial frequency content of the neural field modelled by the basis function decomposition can be determined, given the basis function width.
+Since Shannon's sampling theorem is derived for perfect point sensors, this is particularly useful when considering spatially distributed basis functions.
+To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
+\end{equation}
+with the corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-Thus to obtain a 3dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
+The basis function width, $\sigma^2_{\phi}$, should be chosen to give at least 3~dB attenuation at $\boldsymbol\nu_{cy}$ giving
 \begin{equation}\label{eq:WidthCutOffRelationship}
@@
 \end{equation}
+This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
 Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
@@
 The initial state and parameters were unknown to the estimator.
-Six iterations of the estimation algorithm was sufficient to allow the parameters to converge.
+Eleven iterations of the estimation algorithm were used to ensure the parameters to converge.
 

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
mean bias of xi

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%).
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.7~\%).
 The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
mean bias of xi and theta0

@@
 The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.7~\%).
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.778~\%).
 The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.
-The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively.
+The mean parameter estimates are in good accordance with the actual values, with biases of 2.95, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively.
 The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed table 2
edits to freq analysis and results sections

--- 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 According to Shannon's sampling theorem, the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
-Nevertheless, an approximate reconstruction can still be obtained if the field is approximately bandlimited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Nevertheless, an approximate reconstruction can be obtained if the field is approximately band-limited with
+\begin{equation}
+	V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c,
+\end{equation}
+where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
 Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
@@
 where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied to avoid spectral aliasing effects when reconstructing the hidden dynamic field $v_t(\mathbf{r})$ using the sampled observations, $\mathbf{y}_t$.
+This condition must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
 
 In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors spectral characteristics.
-The spatial response of all sensors result in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore bandlimit the field up to a known bandwidth, denoted by $\nu_{cy}$.
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
+The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
+Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\nu_{cy}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{cy}$ replacing $\nu_c$.
@@
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-Again applying Shannon's Sampling Theorem, the minimum distance between basis functions must satisfy
+Again applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
 \begin{equation}\label{eq:BasisFunctionSeparation}
@@
 
-Such spectral considerations also facilitate the choice of the basis function width parameter~\cite{Sanner1992,Scerri2009}.
-To ensure that the basis functions can represent fields with frequency content up to $\boldsymbol\nu_{cy}$, they should be chosen to poses a spectral bandwidth of at least $\boldsymbol\nu_{cy}$.
-This condition is satisfied by setting the width parameter such that the spectral response of the basis functions results in an attenuation of not more than 3dBs at $\boldsymbol\nu_{cy}$.
-
-To ensure this, consider the 2-dimensional Gaussian basis function defined in equation \ref{eq:FieldBasisFunction}, with the corresponding Fourier transform
+The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
+To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
+\end{equation}
+with the corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
@@
 \end{equation}
-Thus to obtain a 3dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
+To obtain a 3~dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
 \begin{equation}\label{eq:WidthCutOffRelationship}
@@
 \end{equation}
+This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
 Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
+
+Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
+This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
+To calculate the cut-off frequency imposed by the basis function, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
+\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
+	\boldsymbol{\nu}_{c\phi}=\sqrt{\frac{\ln(2)}{2\pi^2\sigma_{\phi}^2}}.
+\end{equation}
 
@@
 \subsection{Spatial Frequency Analysis} 
-Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
 Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
-The cut-off frequency, $\nu_c$, was taken to be 0.24~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
-This confirms that a separation, $\Delta_{y}$, of 1.5~mm was sufficient to prevent problems associated with spatial aliasing.
+The cut-off frequency of the neural was taken to be $\nu_c \approx 0.24$~Hz ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.
+This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
 \begin{figure}
@@
 \subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
-\caption{Power in dB as a function of spatial frequency of the neural field.
-\textbf{a.} The average (over time) power of the spatial frequency of the neural field.
-\textbf{b.} The average (over time) power of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+\caption{Spatial frequency analysis of the neural field.
+\textbf{a.} The average (over time) power in dB of the spatial frequency of the neural field.
+\textbf{b.} The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
 The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
@@
 \end{figure}
+
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
-The cut-off frequency, $\nu_{cy}$, was taken to be $0.19$~Hz ($-3$~dB point).
+The cut-off frequency was taken to be $\nu_{cy} \approx 0.19$~Hz ($-3$~dB point) \dean{the Figure~\ref{fig:SensorFunctionFreqResponse} has the cut-off as $\approx 0.2$~Hz!}.
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter, $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
@@
 Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
-This allowed a smooth representation of the field by the basis function reconstruction up to a spatial frequency as given by equation~\ref{eq:WidthCutOffRelationship} of approximately $0.12$~Hz.
-This is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
+This allowed a smooth representation of the field by the basis function reconstruction up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
 \begin{figure} 
@@
 	\end{center}
-	\caption{Spatial frequency analysis.
+	\caption{\dean{Can we use $\nu_{cy}$ and $\nu_{c\phi}$ in the labels on the graphs?} Spatial frequency analysis.
+The dashed line shows the cut-off frequency (-3 dB point).
 \textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
@@
 \textbf{b.} The spatial frequency response of a 1-dimensional model sensor.
-The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function.
-\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function.
-The dashed line shows the cut-off frequency (-3 dB point).}
+\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
 \end{figure}
@@
 The initial state and parameters were unknown to the estimator.
-Six iterations of the estimation algorithm was sufficient to allow the parameters to converge.
+Eleven iterations of the estimation algorithm were used to ensure the parameters  converge.
 
@@
 The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.7~\%).
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%).
 The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.
@@
 \begin{tabular}{cccc}
-	\hline\hline Parameter & Actual Value & Mean Estimate & Standard Deviation \\
+	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Standard Deviation \\
 	\hline\hline
- 	$\xi$ & 0.9 & 0.925 & 0.004 \\
-	$\theta_0$ & 10 & 10.295 & 2.879 \\
-	$\theta_1$ & -8 & -8.571 & 1.996 \\
-	$\theta_2$ & 0.5 & 0.551 & 0.083 \\
+ 	$\xi$ & 0.9 & 0.925 $\pm$ 0.004 \\
+	$\theta_0$ & 10 & 10.295 $\pm$ 2.879 \\
+	$\theta_1$ & -8 & -8.571 $\pm$ 1.996 \\
+	$\theta_2$ & 0.5 & 0.551 $\pm$ 0.083 \\
 \end{tabular}
@@
 One thing that is shown is that noise has a large impact in the estimation results. To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
+
+The main contribution of this paper is the methodology for...
 

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%).
+The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.778~\%).
 The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.
-The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively.
+The mean parameter estimates are in good accordance with the actual values, with biases of 2.95, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively.
 The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.
@@
 	\hline\hline
- 	$\xi$ & 0.9 & 0.925 $\pm$ 0.004 \\
-	$\theta_0$ & 10 & 10.295 $\pm$ 2.879 \\
-	$\theta_1$ & -8 & -8.571 $\pm$ 1.996 \\
-	$\theta_2$ & 0.5 & 0.551 $\pm$ 0.083 \\
+ 	$\xi$ & $0.9$ & $0.925\pm 0.004$ \\
+	$\theta_0$ & $10$ & $10.295\pm2.879$\\
+	$\theta_1$ & $-8$ & $-8.571\pm1.996$ \\
+	$\theta_2$ & $0.5$ & $0.551\pm0.083$ \\
+\hline\hline
 \end{tabular}
-\caption{Actual parameter values and mean parameter estimates and standard deviation.}
+\caption{Actual parameter values and parameter estimates. Plus-minus figures are mean $\pm$ standard deviation.}
 \label{tab:Parameters estimates}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to results section

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
-This allowed a smooth representation of the field by the basis function reconstruction up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
+This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
@@
 Eleven iterations of the estimation algorithm were used to ensure the parameters  converge.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, demonstrating the parameters converged at six iterations of the estimation algorithm.
+\begin{figure}
+        \centering
+\includegraphics{./Graph/convergence.pdf}
+\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
+All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
+\label{fig:ParametersConvergence}
+\end{figure}
 
 The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}.
-The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%).
-The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian.
-The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively.
-The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}.
-The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias...
-This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
-
+The estimates of the parameters form distributions that are approximately Gaussian.
+The mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
+Although the distributions are quite wide, the mean estimates are in good concordance with the actual values.
+It should be noted that when the excitatory  bases of the connectivity are under (over) estimated, the inhibitory basis is typically under (over) estimated as well.
+This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates.
 \begin{table}
@@
 \begin{tabular}{cccc}
-	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Standard Deviation \\
+	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
 	\hline\hline
- 	$\xi$ & 0.9 & 0.925 $\pm$ 0.004 \\
-	$\theta_0$ & 10 & 10.295 $\pm$ 2.879 \\
-	$\theta_1$ & -8 & -8.571 $\pm$ 1.996 \\
-	$\theta_2$ & 0.5 & 0.551 $\pm$ 0.083 \\
+ 	$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
+	$\theta_0$ & $10$ & $10.295\pm2.879$ & $2.95$\\
+	$\theta_1$ & $-8$ & $-8.571\pm1.996$ & $-7.137$\\
+	$\theta_2$ & $0.5$ & $0.551\pm0.083$ & $10.2$\\
+	$\hat\theta_0/\hat\theta_1$ & $1.25$ & $?\pm0.0812$ &\\
+	$\hat\theta_0/\hat\theta_2$ & $20$ & $?\pm3.757$ & \\
+\hline\hline
 \end{tabular}
-\caption{Actual parameter values and mean parameter estimates and standard deviation.}
+\caption{Actual parameter values compared to parameter estimates.}
 \label{tab:Parameters estimates}
 \end{table}
-
-The reconstructed connectivity kernel from the estimated parameters can be seen in Figure~\ref{fig:KernelEstimates}.
-This Figure verifies the expected net shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The shape is generally well preserved.
-
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence for parameter estimates.
 \begin{figure}
@@
 realisations.
-The dotted line shows the location of the true parameter in each case.
-\textbf{a.} The distribution of $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the synaptic time constant (true parameter: $\xi=0.9$).
-\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates (true parameter: $\theta_0 = 10$).
-\textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$).
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
+The dotted line shows the actual value of the parameters and the solid line shows the mean of the estimated parameters.
+\textbf{a.} The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+\textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
 \label{fig:Parameters}
@@
 \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+\caption{\dean{need to put $\left| \right|$ around $\hat\theta_0/\hat\theta_1$ in xlabel in \textbf{a.}} Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
@@
 \end{figure}
+The reconstructed connectivity kernel from the estimated parameters can be seen in Figure~\ref{fig:KernelEstimates} with the $95\%$ confidence interval.
+This Figure verifies the expected net shape of the estimated connectivity kernel is in good accordance to the true kernel.
 \begin{figure}
     \centering
-\subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
-\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
-\caption{Results for connectivity kernel estimate.
-In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.
-\textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain.
-\textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain.}
+% \subfigure[][]{
+\includegraphics{./Graph/KernelEstimate.pdf}%}
+% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
+\caption{Connectivity kernel estimate.
+The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
 \label{fig:KernelEstimates}
 \end{figure}
-\begin{figure}
-        \centering
-\includegraphics{./Graph/convergence.pdf}
-\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
-All parameters converge after six iterations.
-The mean difference between errors in consecutive iterations falls below $10^{-4}$ after 6 iterations.
-}
-\label{fig:ParametersConvergence}
-\end{figure}
-
 The accuracy for state estimates were evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space) and standard deviation of the RMSE.
@@
 \subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
-\caption{Examples of the neural fields.
-\textbf{a.} The true field from the full neural field model which was used to generate data.
+\caption{Examples of the actual and estimated neural fields.
+\textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data.
 \textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-\textbf{c.} The absolute error between the true and reconstructed fields, the error shows high frequency behaviour.}
+\textbf{c.} The absolute error between the true and reconstructed fields.
+The error shows high frequency behaviour.}
 \label{fig:FieldEstimate}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updated results on estimates

@@
 
-\title{State and Parameter Estimation for Spatio-Temporal Neural Fields}
+\title{`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
 
@@
 The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
-
 Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
@@
 	\end{center}
-	\caption{\dean{Can we use $\nu_{cy}$ and $\nu_{c\phi}$ in the labels on the graphs?} Spatial frequency analysis.
+	\caption{\dean{Note: we use $\nu_{cy}$ and $\nu_{c\phi}$ in the labels on the graphs.} Spatial frequency analysis.
 The dashed line shows the cut-off frequency (-3 dB point).
@@
 Eleven iterations of the estimation algorithm were used to ensure the parameters  converge.
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, demonstrating the parameters converged at six iterations of the estimation algorithm.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
 \begin{figure}
@@
 
-The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}.
-The estimates of the parameters form distributions that are approximately Gaussian.
-The mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
-Although the distributions are quite wide, the mean estimates are in good concordance with the actual values.
-It should be noted that when the excitatory  bases of the connectivity are under (over) estimated, the inhibitory basis is typically under (over) estimated as well.
+Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}.
+The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
+The biases show the percentage differences between the actual values and the mean parameter estimates.
+The mean estimates are in good concordance with the actual values.
+% It should be noted that when the excitatory connectivity parameters, $\hat\theta_0$ and $\hat\theta_2$, were under (or over) estimated, the inhibitory connectivity parameter, $\hat\theta_1$, tended to be over (or under) estimated.
 This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates.
@@
 	$\theta_2$ & $0.5$ & $0.551\pm0.083$ & $10.2$\\
-	$\hat\theta_0/\hat\theta_1$ & $1.25$ & $?\pm0.0812$ &\\
-	$\hat\theta_0/\hat\theta_2$ & $20$ & $?\pm3.757$ & \\
+	% $\hat\theta_0/\hat\theta_1$ & $1.25$ & $?\pm0.0812$ &\\
+	% $\hat\theta_0/\hat\theta_2$ & $20$ & $?\pm3.757$ & \\
 \hline\hline
@@
     \subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
-    \subfigure[][]{\includegraphics{./Graph/theta1.pdf}}
+    \subfigure[][]{\label{fig:theta1dis}\includegraphics{./Graph/theta1.pdf}}
     \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
@@
 \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{\dean{need to put $\left| \right|$ around $\hat\theta_0/\hat\theta_1$ in xlabel in \textbf{a.}} Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+\caption{\dean{Note: need to put $\left| \right|$ around $\hat\theta_0/\hat\theta_1$ in xlabel in \textbf{a.}} Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
@@
 \end{figure}
-The reconstructed connectivity kernel from the estimated parameters can be seen in Figure~\ref{fig:KernelEstimates} with the $95\%$ confidence interval.
-This Figure verifies the expected net shape of the estimated connectivity kernel is in good accordance to the true kernel.
+
+The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a solid line and the range indicated by the shaded region, which is  the $95\%$ confidence interval.
+The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
+The mean estimated kernel in more negative than the actual kernel due to the bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
 \begin{figure}
@@
 \end{figure}
+
 The accuracy for state estimates were evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space) and standard deviation of the RMSE.
 The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}.
-A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}.
+A snapshot at a single time instant of the true field, the estimated field and their corresponding error is shown in Figure~\ref{fig:FieldEstimate}.
 This figure highlights the loss of the high spatial frequency information in the basis function decomposition.
@@
 \subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
-\caption{Examples of the actual and estimated neural fields.
+\caption{Examples of the actual and estimated neural fields and the error.
 \textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data.
@@
 
+This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from intracranial EEG / LFP data.
+The results indicate a good estimation performance, where the mean parameter estimates are in close accordance to the actual values.
+The distributions for the estimates of the connectivity kernel parameters also show a significant spread.
+This is expected, considering the disturbance  the system is driven by noise and the This that the estimation methodolgy
+
 One thing that is shown is that noise has a large impact in the estimation results. To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
@@
 In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
-The model-based technique proposed in this paper estimates the connectivity structure independently of the number of sensors.
+The model-based technique proposed in this paper estimates the connectivity structure independently of the number of sensors (assuming the field is sufficiently sampled).
 
@@
 A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
+In addition to estimating connectivity independently of the number of observations  The advantage of the methodology presented in this paper, is that
 
@@
 \section{Conclusion}
-This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields.
+This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields to create patient specific models.
 A basis function decomposition reduces the infinite dimensional neural field (continuous space) to a finite dimensional state-space model.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
results section edits to state parameter estimation section

@@
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The mean estimated kernel in more negative than the actual kernel due to the bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
 \begin{figure}
@@
 
-The accuracy for state estimates were evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space) and standard deviation of the RMSE.
-The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}.
-A snapshot at a single time instant of the true field, the estimated field and their corresponding error is shown in Figure~\ref{fig:FieldEstimate}.
-This figure highlights the loss of the high spatial frequency information in the basis function decomposition.
+The accuracy of the state estimates was evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space).
+The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the 95~\% confidence interval.
+The error is consistently around 0.5 over time, which approximately \dean{??}~\% of the voltages, which range over \dean{(??,??)}.
+The error in the reconstructed field is mostly due to the loss high spatial frequency information due to the basis function decomposition; this is illustrated in Figure~\ref{fig:FieldEstimate}, which shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
+It can be seen in Fig 10b that the estimated field contains the basic structure of the true field (fig10a), but is missing the higher-frequency detail.
   \begin{figure}
@@
    	\end{center}
-   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). The error remains consistent over time.} 
+   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). } 
 \label{fig:RMSE}
@@
 \section{Discussion}\label{DiscussionSection}
-
 This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from intracranial EEG / LFP data.
-The results indicate a good estimation performance, where the mean parameter estimates are in close accordance to the actual values.
-The distributions for the estimates of the connectivity kernel parameters also show a significant spread.
-This is expected, considering the disturbance  the system is driven by noise and the This that the estimation methodolgy
-
-One thing that is shown is that noise has a large impact in the estimation results. To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
+The results indicate good estimation performance, where the mean parameter estimates are close to the actual values.
+The distributions of the estimates of the connectivity kernel parameters show a relatively wide spreads, which is expected considering the large disturbances in the system that is driven by noise.
+In addition the observations contain a large amount of noise.
+
+To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
 

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small edits

@@
 \caption{Connectivity kernel estimate.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
+The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
 \label{fig:KernelEstimates}
@@
 
-The accuracy of the state estimates was evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space).
-The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the 95~\% confidence interval.
+The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over time) of the root mean square error (MRMSE) (over space).
+The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
 The error is consistently around 0.5 over time, which approximately \dean{??}~\% of the voltages, which range over \dean{(??,??)}.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed figure 2

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
    	\begin{center}
+    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePy.pdf}} \\
     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
@@
    	\end{center}
-   	\caption{\textbf{a.} Example of data generated by the full neural field model from the first 5 sensors.
-\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
+   	\caption{\textbf{a.} Example of the neural feld.
+\textbf{b.} Example of data generated by the full neural field model from the first 5 sensors.
+\textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
 \label{fig:experimental design}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added absolute value to fig7a caption

@@
 \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{\dean{Note: need to put $\left| \right|$ around $\hat\theta_0/\hat\theta_1$ in xlabel in \textbf{a.}} Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+\caption{\textbf{a.} Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the cut off frequency formula
edition to result section reference to fig2a

@@
 \begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln 2}.
+ \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
 \end{equation}
@@
 \begin{equation}\label{eq:CutoffFromBasisFuncWidth}
-	\boldsymbol{\nu}_{c\phi}=\sqrt{\frac{\ln(2)}{2\pi^2\sigma_{\phi}^2}}.
+	\boldsymbol{\nu}_{c\phi}=\sqrt{\frac{\ln2}{2}}\frac{1}{\pi\sigma_{\phi}}.
 \end{equation}
@@
 This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series.
+An example of the simulated field can
+be seen in Figure~\ref{fig:experimental design}(a).
+Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
-The cut-off frequency of the neural was taken to be $\nu_c \approx 0.24$~Hz ($-3$~dB point).
+The cut-off frequency of the neural field was taken to be $\nu_c \approx 0.24$~Hz ($-3$~dB point).
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed table1 layout
changed the text in fig4b and fig4c
for merge

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-The sensors were spaced on a regular square 14 $\times$ 14 grid, the sensor width parameter $\sigma^2_m$ was $0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y=1.5$~mm.
+The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width parameter $\sigma^2_m$ was set to $0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y=1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
@@
    	\begin{center}
-    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePy.pdf}} \\
     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
@@
    	\end{center}
-   	\caption{\textbf{a.} Example of the neural feld.
-\textbf{b.} Example of data generated by the full neural field model from the first 5 sensors.
-\textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
+   	\caption{\textbf{a.} Example of data generated by the full neural field model from the first 5 sensors.
+\textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
 \label{fig:experimental design}
@@
 \end{figure}
-
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
@@
 \textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
-The symmetry of the sensors and field basis functions allow for the 1-dimensional representation of the spectral characteristics.
-\textbf{b.} The spatial frequency response of a 1-dimensional model sensor.
-\textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
+The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
+\textbf{b.} The spatial frequency response of a one-dimensional model sensor.
+\textbf{c.} The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
 \end{figure}
@@
 \end{figure}
-
 The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a solid line and the range indicated by the shaded region, which is  the $95\%$ confidence interval.
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
+
 \begin{figure}
@@
 \end{figure}
-
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over time) of the root mean square error (MRMSE) (over space).

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 	$T_s$ & 1 & ms \\ 
+\hline\hline
 \end{tabular}
@@
 	\end{center}
-	\caption{\dean{Note: we use $\nu_{cy}$ and $\nu_{c\phi}$ in the labels on the graphs.} Spatial frequency analysis.
+	\caption{Spatial frequency analysis.
 The dashed line shows the cut-off frequency (-3 dB point).

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the distance equations to leq
changed the vcy value in spatial frequency analysis

@@
 \begin{equation}
-	\label{eq:MinimumSensorDistance} \Delta_y < \frac{1}{2\rho_y\nu_{c}}, 
+	\label{eq:MinimumSensorDistance} \Delta_y \leq \frac{1}{2\rho_y\nu_{c}}, 
 \end{equation}
@@
 \begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_{\phi} < \frac{1}{2\rho_{\phi}\nu_{cy}}
+	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\nu_{cy}}
 \end{equation}
@@
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
-The cut-off frequency was taken to be $\nu_{cy} \approx 0.19$~Hz ($-3$~dB point) \dean{the Figure~\ref{fig:SensorFunctionFreqResponse} has the cut-off as $\approx 0.2$~Hz!}.
+The cut-off frequency was taken to be $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.63$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the percentage of MRMSE
changes to discussion

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 \section{Discussion}\label{DiscussionSection}
-This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from intracranial EEG / LFP data.
-The results indicate good estimation performance, where the mean parameter estimates are close to the actual values.
-The distributions of the estimates of the connectivity kernel parameters show a relatively wide spreads, which is expected considering the large disturbances in the system that is driven by noise.
+This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+The results indicate good estimation performance, where the mean parameter estimates are in accordance to the actual values.
+The distributions of the estimates of the connectivity kernel parameters show a relatively broad, which is expected considering the large disturbances in the system that is driven by noise.
 In addition the observations contain a large amount of noise.
 
-To reduce the effect of noise, an evoked response paradigm should be considered when using real data.
-
-The main contribution of this paper is the methodology for...
+To overcome the effect of noise, an evoked response paradigm should be considered when using real data.
+Following such a paradigm, data can be epoched into a sufficient number of realisations such that the a distribution of the estimates can be formed.
 
@@
 
-The closest competitor to the integrodifference equation based approach is perhaps the multivariate auto-regressive (MVAR) model.
+The closest competitor to the integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model.
 An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
@@
 A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
-In addition to estimating connectivity independently of the number of observations  The advantage of the methodology presented in this paper, is that
+In addition to estimating connectivity independently of the number of observations, the advantage of the methodology presented in this paper, is that the number of parameters required to model the system is considerably less, and the parameter have physical meaning.
 

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

@@
 The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-The error is consistently around 0.5 over time, which approximately \dean{??}~\% of the voltages, which range over \dean{(??,??)}.
+The error is consistently around 0.5 over time, which approximately $7.1$~\% of the voltages, which range over $(-3.29,3.77)$.
 The error in the reconstructed field is mostly due to the loss high spatial frequency information due to the basis function decomposition; this is illustrated in Figure~\ref{fig:FieldEstimate}, which shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed table 2

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 	$\theta_2$ & $0.5$ & $0.551\pm0.083$ & $10.2$\\
-	% $\hat\theta_0/\hat\theta_1$ & $1.25$ & $?\pm0.0812$ &\\
-	% $\hat\theta_0/\hat\theta_2$ & $20$ & $?\pm3.757$ & \\
+	$\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &4.83\\
+	$\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &7.165 \\
 \hline\hline
@@
    	\end{center}
-   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). } 
+   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
 \label{fig:RMSE}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed table 2
small editions

--- 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
  	$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
-	$\theta_0$ & $10$ & $10.295\pm2.879$ & $2.95$\\
-	$\theta_1$ & $-8$ & $-8.571\pm1.996$ & $-7.137$\\
-	$\theta_2$ & $0.5$ & $0.551\pm0.083$ & $10.2$\\
-	% $\hat\theta_0/\hat\theta_1$ & $1.25$ & $?\pm0.0812$ &\\
-	% $\hat\theta_0/\hat\theta_2$ & $20$ & $?\pm3.757$ & \\
+	$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
+	$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
+	$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
+	$\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
+	$\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
 \hline\hline
@@
 The error is consistently around 0.5 over time, which approximately $7.1$~\% of the voltages, which range over $(-3.29,3.77)$.
-The error in the reconstructed field is mostly due to the loss high spatial frequency information due to the basis function decomposition; this is illustrated in Figure~\ref{fig:FieldEstimate}, which shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition; this is illustrated in Figure~\ref{fig:FieldEstimate}, which shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
 It can be seen in Fig 10b that the estimated field contains the basic structure of the true field (fig10a), but is missing the higher-frequency detail.

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small editions

@@
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition; this is illustrated in Figure~\ref{fig:FieldEstimate}, which shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Fig 10b that the estimated field contains the basic structure of the true field (fig10a), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:FieldEstimate}(b) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(a)), but is missing the higher-frequency detail.
   \begin{figure}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
corrected fig7 caption

@@
 \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{\textbf{a.} Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
 \textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
-The dotted line shows the location of the true ratio in each case.}
+In each case, the solid and dotted lines show the locations of the true and estimated ratios respectively.}
 \label{fig:ParametersRatio}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
corrected fig8 caption
random typo correction

@@
 \end{figure}
-The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a solid line and the range indicated by the shaded region, which is  the $95\%$ confidence interval.
+The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the range indicated by the shaded region, which is  the $95\%$ confidence interval.
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
@@
 % \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
-\caption{Connectivity kernel estimate.
+\caption{Cross-section of connectivity kernel estimate.
 The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
@@
 A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
-In addition to estimating connectivity independently of the number of observations, the advantage of the methodology presented in this paper, is that the number of parameters required to model the system is considerably less, and the parameter have physical meaning.
+In addition to estimating connectivity independently of the number of observations, the advantage of the methodology presented in this paper, is that the number of parameters required to model the system is considerably less, and the parameters have physical meaning.
 

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
random typo correction

@@
 	$\nu_c$ & Spatial cut-off frequency \\
-	$\Delta_s$ & Distance between adjacent sensors \\
+	$\Delta_y$ & Distance between adjacent sensors \\
 	$\rho$ & Over-sampling parameter \\
-	$\Delta_b$ & Distance between field basis functions \\
-	$\sigma_{nu}^2$ & Variance of FT of Gaussian basis function \\
-	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
+	$\Delta_{\phi}$ & Distance between field basis functions \\
+	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
+	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
     \end{tabular}
@@
     	$P^f_t$ & Forward posterior covariance matrix \\
-    	$P^{f-}_t$ & Forward prior covariance matrix
+    	$P^{f-}_t$ & Forward prior covariance matrix \\
+    	$P^b_t$ & Backward posterior covariance matrix \\
+    	$P^{b-}_t$ & Backward prior covariance matrix \\
+	$\mathcal K_{t} $& Filter gain\\
+	$M_t$& Cross-covariance matrix\\
+	$S_t$& Smoother gain
     \end{tabular}

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
completed table8

@@
 	$\chi$ & Matrix of sigma vectors \\
+	$\lambda$& Scaling parameter\\
+	$\alpha$& Determines the spread of sigma points\\
+	$\beta$& Priro knowledge of the sigma points distribution\\
+	$\kappa$& Scaling parameter\\
+	$W$& Sigma vecors weights\\
     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
completed table8

@@
     	$q()$ & state function \\
-    	$k()$ & maps into to discrete state of input function \\
-    	$\mathbf{e}_t$ & state disturbance, covariance $\Sigma_e$ \\
+    	$Q()$ & state function \\
+	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
+    	$\mathbf{e}_t$ & state disturbance \\
+	$\Sigma_e$ &state disturbance covariance matrix\\
+	$\mathbf{\epsilon}_t$ & observation noise \\
+	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
     	$\mathbf{C}$ & observation matrix \\
+	$c_{ij}$& elements of observation matrix
     \end{tabular}

### 2010-06-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the notation in LS to avoid conflict with sigma vector weights
changes to discussion

@@
 % Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$.
+\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
@@
 \begin{equation}
-	\mathbf Z=\mathbf X \mathbf W+\mathbf{e}, 
+	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
 \end{equation}
@@
 \begin{equation*}
-\quad \mathbf W=\left[
+\quad \mathcal W=\left[
 	\begin{array}{cc}
@@
 \end{small}
-Following this, the LS parameter estimates, $ \mathbf{\hat{W}}$, are
-\begin{equation}
-	\mathbf{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+Following this, the LS parameter estimates, $ \mathcal{\hat{W}}$, are
+\begin{equation}
+	\mathcal{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
 \end{equation}
@@
 %The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+\section{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the methods described above.
+The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Model Parameters}.
@@
 be seen in Figure~\ref{fig:experimental design}(a).
-Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
+Figure~\ref{fig:experimental design}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 
-The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width parameter $\sigma^2_m$ was set to $0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y=1.5$~mm.
+The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
@@
 Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
-The cut-off frequency of the neural field was taken to be $\nu_c \approx 0.24$~Hz ($-3$~dB point).
+The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point).
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.
@@
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
-The cut-off frequency was taken to be $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
+The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The distance between basis functions, $\Delta_{\phi}$, was set to $2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
+Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
 Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
@@
 The initial state and parameters were unknown to the estimator.
-Eleven iterations of the estimation algorithm were used to ensure the parameters  converge.
+Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
 Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
@@
 \end{figure}
-The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the range indicated by the shaded region, which is  the $95\%$ confidence interval.
+The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
@@
 The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-The error is consistently around 0.5 over time, which approximately $7.1$~\% of the voltages, which range over $(-3.29,3.77)$.
-The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition; this is illustrated in Figure~\ref{fig:FieldEstimate}, which shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
+At each time point the error is consistently around 0.5, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV.
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
+The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
 It can be seen in Figure~\ref{fig:FieldEstimate}(b) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(a)), but is missing the higher-frequency detail.
@@
 \section{Discussion}\label{DiscussionSection}
-This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-The results indicate good estimation performance, where the mean parameter estimates are in accordance to the actual values.
-The distributions of the estimates of the connectivity kernel parameters show a relatively broad, which is expected considering the large disturbances in the system that is driven by noise.
-In addition the observations contain a large amount of noise.
-
-To overcome the effect of noise, an evoked response paradigm should be considered when using real data.
-Following such a paradigm, data can be epoched into a sufficient number of realisations such that the a distribution of the estimates can be formed.
+This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+The results indicate good estimation performance, where the mean parameter estimates are in good accordance to the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by a random disturbance and the observations are corrupted by noise.
+To overcome the effect of noise, an evoked-response paradigm should be considered when using electrophysiological recordings.
+Following such a paradigm, data can be epoched into a sufficient number of realisations such that a distribution of the estimates can be formed.
+
+The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
+Importantly, these new tools can also be used to better design electrophysiological recording techniques to avoid spatial aliasing.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
+
+The accuracy of the estimation is limited by many factors.
 
@@
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-In addition, other non-model-based techniques for estimating functional connectivity, such as Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}, are restricted to the spatial scales of the recording electrodes.
-The model-based technique proposed in this paper estimates the connectivity structure independently of the number of sensors (assuming the field is sufficiently sampled).
-
-The closest competitor to the integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model.
-An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres.
-A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain.
+
+The closest competitor to the our `grey-box' integro-difference equation (IDE) based approach is perhaps the `black-box' multivariate auto-regressive (MVAR) model.
+Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
+A distinct advantage of the IDE-based technique proposed in this paper, is the estimates the connectivity structure are made independently of the number of sensors (assuming the field is sufficiently sampled).
+In addition, the number of parameters required to model the system is considerably less than a typical MVAR model.
+Furthermore, by using the neural field equations as a parametric form of the model, the parameters have physical meaning and therefore, can be clinically relevant.
+An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
+A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of a multi-scale connectivity structure in generating the characteristic rhythms of the brain.
 A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
-In addition to estimating connectivity independently of the number of observations, the advantage of the methodology presented in this paper, is that the number of parameters required to model the system is considerably less, and the parameters have physical meaning.
 
@@
 
+In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel.
+In future work, we plan to extent this work to relax this assumption.
+We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
+In addition, we have assumed the neural field is isotropic and homogeneous.
+It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
+However, the assumption of homogeneity is quite strong.
+Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
+Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
+
 \section{Conclusion}
@@
 A basis function decomposition reduces the infinite dimensional neural field (continuous space) to a finite dimensional state-space model.
+The frequency analysis methods presented in this paper provide a systematic procedure for specifying the sensor and basis function arrangement required to describe the significant neuro-dynamics by the reduced neural field model.
 The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
-The effect of the basis function decomposition will restrict the frequency content of the estimated field.
-This is evident when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field is spatially band-limited.
-The spatial frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel.
 Using the state-space model, the unscented Rauch Tung Striebel smoother was applied for state estimation.
 Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
-We have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic time constant.
-
-The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
-In addition to providing conditions to ensure the reduced model can capture the significant spectral properties of the field, these new tools can be used to better design electrophysiological recording techniques to avoid spatial aliasing.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-In this paper,\parham{In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel.
-In future work, we plan to extent this work to relax this assumption.
-We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
-Visakan: width estimation is totally different process} the widths of the connectivity kernel basis functions are assumed to be known.
-In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths.
-We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure to take care of the weights.
-In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions.
-For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas \parham{Visakan: heteroginity is about the process not presentation, and it should be addressed by using a kernel which is different at different spatial locations}.
-In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
+We have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic dynamics using the proposed methodology.
 

### 2010-06-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
minor edits

@@
 The results indicate good estimation performance, where the mean parameter estimates are in good accordance to the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by a random disturbance and the observations are corrupted by noise.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance and the observations are corrupted by noise.
 To overcome the effect of noise, an evoked-response paradigm should be considered when using electrophysiological recordings.
@@
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-The accuracy of the estimation is limited by many factors.
 
@@
 
-In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel.
-In future work, we plan to extent this work to relax this assumption.
+In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
+In future work, we plan to relax this assumption.
 We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
@@
 Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
+Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, distant dependant propagation times into the parametric neural field equations.
 

### 2010-06-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
rearranged equation 38
corrected figure6 caption change the solid and dotted line
minor edits

@@
 \begin{equation}\label{eq:CutoffFromBasisFuncWidth}
-	\boldsymbol{\nu}_{c\phi}=\sqrt{\frac{\ln2}{2}}\frac{1}{\pi\sigma_{\phi}}.
+	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
 \end{equation}
@@
 realisations.
-The dotted line shows the actual value of the parameters and the solid line shows the mean of the estimated parameters.
+The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
 \textbf{a.} The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
@@
 
-The closest competitor to the our `grey-box' integro-difference equation (IDE) based approach is perhaps the `black-box' multivariate auto-regressive (MVAR) model.
+The closest competitor to our `grey-box' integro-difference equation (IDE) based approach is perhaps the `black-box' multivariate auto-regressive (MVAR) model.
 Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.

### 2010-06-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
minor edits

@@
 Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
-A distinct advantage of the IDE-based technique proposed in this paper, is the estimates the connectivity structure are made independently of the number of sensors (assuming the field is sufficiently sampled).
+A distinct advantage of the IDE-based technique proposed in this paper, is that the estimates of the connectivity structure are made independently of the number of sensors (assuming the field is sufficiently sampled).
 In addition, the number of parameters required to model the system is considerably less than a typical MVAR model.

### 2010-06-19 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits mainly to model derivation and formation of IDE sections

@@
 Our work builds on recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
-The key development here was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation locations (recording electrodes in this case).
+The key development of this previous work was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
 
-Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (AR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (MVAR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
 
@@
 This work provides a fundamental link between the theoretical advances in neural field modelling and patient-specific data.
-
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
@@
 where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
-The connectivity kernel is typically a ``Mexican hat'' function, which describes strong local activation, weak mid-range repression and weak long-range activation.
-An example of the connectivity kernel  used in this paper can be seen in Figure~\ref{fig:2d_kernel}.
+The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
+To demonstrate flexibility in estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
+An example of the connectivity kernel is shown in in Figure~\ref{fig:2d_kernel}.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
@@
    	\end{center}
-   	\caption{A Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
+   	\caption{Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
 The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
@@
 \end{equation}
-The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations.
+The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations respectively.
 The parameter $\varsigma$ governs the slope of the sigmoid.
@@
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
-This term is added to account for uncertainty in the model.
+This term is added to account for uncertainty and unmodelled inputs.
 To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
 
-The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function 
+The mapping between the membrane voltage and the electrophysiological data (iEEG/LFP) is modelled using the observation function 
 \begin{equation}
@@
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
-Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model, representing short range excitation, surround inhibition and mid-range excitation.
+Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
+Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition.
+To demonstrate the flexibility in the estimation framework a third basis function is incorporated, corresponding to weaker mid-range excitation.
 Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
@@
 \end{equation}
-which is constant and can be defined analytically. Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+which is constant $L \times n_{\theta}$ matrix that can be defined analytically, where $n_{\theta}$ is the number of connectivity basis functions.
+Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
 \begin{eqnarray}
@@
 \end{eqnarray}
+This simplification has transformed the description of the spatial coupling from a convolution, to an inner product.
+This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
 Now we define the state disturbance as
@@
 
-The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$, which provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm.
+The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$.
+This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
@@
 In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+\dean{can expand a bit}
 

### 2010-06-19 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the convolution and inner product of two Gaussian

@@
 substituting \ref{eq:IntegralOfGaussian} in \ref{eq:AppendixGaussianFT} gives another scaled  Gaussian 
-\begin{equation}
+\begin{equation}\label{eq:FTofGaussian}
    \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu)
@@
 \end{equation}
-
+\section{Convolution and inner product of two $n$-dimensional Gaussian basis functions}\label{ap:ConvandIn}
+Consider two Gaussian basis functions
+\begin{equation}
+ \phi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+\begin{equation}
+\phi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right)
+\end{equation}
+First we derive the convolution of two Gaussian basis functions assuming $\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$.
+Convolution theorem states that the Fourier transform of a convolution is the product of Fourier transforms.
+Using equation \ref{eq:FTofGaussian} we have
+\begin{eqnarray}
+\boldsymbol\Phi_i(\boldsymbol\nu)\boldsymbol\Phi_j(\boldsymbol\nu)&=&\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{eqnarray}
+taking the inverse Fourier transform we can write the convolution as
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
+\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
+ (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
+\end{equation}
+where $\boldsymbol\mu=\mu_i+\mu_j$.
+
+The inner product of two Gaussian basis functions is defined as
+\begin{equation}\label{eq:InofGaussianDefinition}
+\phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r
+\end{equation}
+A Gaussian basis function is symmetric with respect to its center, therefore
+\begin{equation}\label{eq:GaussianSymmetry}
+ \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r)
+\end{equation}
+A direct consequence of equation \ref{eq:GaussianSymmetry} is
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
+ \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r)
+\end{equation}
+substituting equation \ref{eq:ConsequenceofGaussianSymmetry} in equation \ref{eq:InofGaussianDefinition} we have 
+\begin{eqnarray}
+\phi_i\otimes\phi_j&=&\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
+&=&\int_{\mathcal R^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
+&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i)
+\end{eqnarray}
+from equation \ref{eq:ConvoftwoGaussianNonzeroMean} we have
+\begin{equation}
+ \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
+\end{equation}
 \section{Notation}

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the convolution and inner product of two Gaussian
minor edits
edits to the discussion

@@
 
-This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
+The development of an estimation framework also has theoretical implications.
+The procedure has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
 For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}.
@@
 \end{equation}
-and hence completing the proof. For 3 dB attenuation at $\boldsymbol\nu_c$ we need to set
+and hence completing the derivation. For 3 dB attenuation at $\boldsymbol\nu_c$ we need to set
 \begin{eqnarray}
@@
 \end{equation}
-where $\boldsymbol\mu=\mu_i+\mu_j$.
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
 
@@
 \end{eqnarray}
-from equation \ref{eq:ConvoftwoGaussianNonzeroMean} we have
+evaluation equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
 \begin{equation}

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to discussion, added bit on basis func decomp

@@
 This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-An example of the simulated field can
-be seen in Figure~\ref{fig:experimental design}(a).
+When generating the simulated data we assumed free boundary conditions for the neural field.
+An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(a).
 Figure~\ref{fig:experimental design}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
@@
 	$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
-	$\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
-	$\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
+	% $\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
+	% $\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
 \hline\hline
@@
 \end{figure}
-\begin{figure}
-    \centering
-\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
-\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+% \begin{figure}
+%     \centering
+% \subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
+% \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
+% \caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
 \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
@@
 In each case, the solid and dotted lines show the locations of the true and estimated ratios respectively.}
-\label{fig:ParametersRatio}
-\end{figure}
+% \label{fig:ParametersRatio}
+% \end{figure}
 The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
@@
 
-The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics.
+A significant contribution of this paper is the derivation of the basis function decomposition of the neural field.
+Through the derivation, a finite-dimensional state-space model is formed that describes a continuous neural field.
+Previous work from Schiff and Sauer~\ref{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter for state-estimation of a discrete (in space and time) nonlinear spatial-temporal systems.
+Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
+Therefore, a limitation of this framework lies in an increase in dimensionality with increases in spatial resolution and in the physical size of the neural field.
+Increases in dimensionality lead to increases in the uncertainty the estimated state, and problems associated with computational complexity.
+This paper builds on this previous study, where the estimator is constructed to describe a continuous field.
+The dimensionality of the state vector is independent of the resolution of a spatial discretisation and is governed by the inherent spatial properties of the field.
+The frequency analysis methods provide a rigorous framework for the placement and the number of the basis functions required for the decomposition.
+This enables estimation of a larger field, with a lower dimensional state vector.
+The basis function decomposition also enabled the coupling to be described by an inner product rather than a spatial convolution.
+This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
+
+The frequency analysis and model selection tools presented in this paper specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
 Importantly, these new tools can also be used to better design electrophysiological recording techniques to avoid spatial aliasing.
@@
 The development of an estimation framework also has theoretical implications.
-The procedure has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models.
-For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}.
-Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond to the theoretically derived parameters where these bump solutions can exist.
-In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.
+The the ability to estimate parameters will allow testing of hypotheses that have been generated in theoretical studies.
+This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
+For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters and check if they correspond to the theoretically derived parameters where certain solutions can exist.
+In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
 
@@
 \end{eqnarray}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging Eq.~\ref{Euler Approximation} we get 
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation} we get 
 \begin{eqnarray}
@@
 \end{eqnarray}
-evaluation equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
+evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
 \begin{equation}

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to the appendices

@@
 Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition.
-To demonstrate the flexibility in the estimation framework a third basis function is incorporated, corresponding to weaker mid-range excitation.
+To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
 Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
@@
 \end{equation}
-Now defining
+Now defining the matrix
 \begin{equation}\label{eq:DefGamma}
@@
 \end{equation}
-This can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
+The analytic derivation of the inner product of the \emph{n}-dimensional Gaussians is provided in~\ref{ap:ConvandIn}.
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
 \begin{equation}
@@
 To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
-\begin{equation}
+\begin{equation}\label{eq:BasisFunctionAtOrigin}
  \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
@@
 \section{Derivation for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} }\label{ap:FrequencyAnalysis}
-Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to an \textit{n}-dimensional Gaussian centered at the origin yields
+Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centered at the origin (see equation~\ref{eq:BasisFunctionAtOrigin}) yields
 \begin{eqnarray}\label{eq:AppendixGaussianFT}
- \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathcal R^n}\mathrm{exp}({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r})\mathrm{exp}(-2\pi i\boldsymbol\nu^\top\mathbf r)d\mathbf r} \nonumber \\
-&=&\int_{\mathcal R^n}\mathrm{exp}(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right])d\mathbf r \nonumber \\
-&\times& \mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu)
+ \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathcal R^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
+&=&\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
+&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right)
 \end{eqnarray}
@@
 \begin{eqnarray}\label{eq:IntegralOfGaussian}
-\int_{\mathcal R^n}\mathrm{exp}(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right])d\mathbf r&& \nonumber \\
-=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}&&
+\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}&&
 \end{eqnarray}
@@
 \begin{equation}
-\boldsymbol\Phi(\boldsymbol \nu)=(\frac{1}{\pi\sigma_{\nu}^2})^{\frac{n}{2}}\mathrm{exp}(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu).
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
 \end{equation}
@@
 \begin{eqnarray}
- |\boldsymbol\Phi(\boldsymbol\nu_{c})|^2=\frac{1}{2}|\boldsymbol\Phi(\mathbf 0)|^2
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2
 \end{eqnarray}
@@
 \section{Convolution and inner product of two $n$-dimensional Gaussian basis functions}\label{ap:ConvandIn}
+In this appendix we provide derivations for the convolution and the inner product of Gaussian basis functions.
+These derivations are used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$.
 Consider two Gaussian basis functions

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to appendix

@@
 \end{eqnarray}
-\section{Derivation for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} }\label{ap:FrequencyAnalysis}
-Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centered at the origin (see equation~\ref{eq:BasisFunctionAtOrigin}) yields
+\section{Calculation of Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
+This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
+Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (see equation~\ref{eq:BasisFunctionAtOrigin}) yields
 \begin{eqnarray}\label{eq:AppendixGaussianFT}
@@
 &=&\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
-&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right)
+&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right),
 \end{eqnarray}
@@
 \int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}&&
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
 \end{eqnarray}
-substituting \ref{eq:IntegralOfGaussian} in \ref{eq:AppendixGaussianFT} gives another scaled  Gaussian 
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian 
 \begin{equation}\label{eq:FTofGaussian}
-   \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu)
-\end{equation}
-substituting $\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}$ gives 
+   \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu).
+\end{equation}
+Substituting $\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}$ gives 
 \begin{equation}
@@
 These derivations are used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$.
-Consider two Gaussian basis functions
-\begin{equation}
- \phi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-\begin{equation}
-\phi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right)
-\end{equation}
-First we derive the convolution of two Gaussian basis functions assuming $\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$.
-Convolution theorem states that the Fourier transform of a convolution is the product of Fourier transforms.
-Using equation \ref{eq:FTofGaussian} we have
+Consider the field Gaussian basis function
+\begin{equation}
+ \phi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and the connectivity kernel basis function
+\begin{equation}
+\psi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\psi_j}^2} \mathbf{r}^\top\mathbf{r}}\right)
+\end{equation}
+We will proceed in the derivation of the convolution assuming the field basis function is positioned at the origin ($\boldsymbol\mu_i=\mathbf 0$).
+The convolution theorem states that the Fourier transform of a convolution is the product of Fourier transforms.
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
 \begin{eqnarray}
-\boldsymbol\Phi_i(\boldsymbol\nu)\boldsymbol\Phi_j(\boldsymbol\nu)&=&\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\mathcal{F}\left(\phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r})\right) &=& \left(\pi\sigma_{\phi}^2\sigma_{\psi_j}^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times& (\pi(\sigma_{\phi}^2+\sigma_{\psi_j}^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_{\phi}^2+\sigma_{\psi_j}^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
 \end{eqnarray}
-taking the inverse Fourier transform we can write the convolution as
+where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution is
 \begin{equation}\label{eq:ConvoftwoGaussian}
- (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
+ \phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r}) = \left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
 \begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
-\end{equation}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+ (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).
+\end{equation}
 
@@
 \end{equation}
-A Gaussian basis function is symmetric with respect to its center, therefore
+A Gaussian basis function is symmetric with respect to its centre, therefore
 \begin{equation}\label{eq:GaussianSymmetry}

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
more appendix changes

@@
 \end{equation}
-\section{Convolution and inner product of two $n$-dimensional Gaussian basis functions}\label{ap:ConvandIn}
+\section{Convolution of two $n$-dimensional Gaussian basis functions}\label{ap:ConvandIn}
 In this appendix we provide derivations for the convolution and the inner product of Gaussian basis functions.
@@
 \begin{equation}
-\psi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\psi_j}^2} \mathbf{r}^\top\mathbf{r}}\right)
-\end{equation}
-We will proceed in the derivation of the convolution assuming the field basis function is positioned at the origin ($\boldsymbol\mu_i=\mathbf 0$).
+\psi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\psi_j}^2} \mathbf{r}^\top\mathbf{r}}\right).
+\end{equation}
+The derivation proceeds by assuming the field basis function is positioned at the origin ($\boldsymbol\mu_i=\mathbf 0$).
 The convolution theorem states that the Fourier transform of a convolution is the product of Fourier transforms.
@@
 \begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- (\phi_i*\phi_j)(\mathbf r)=\left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).
-\end{equation}
-
-The inner product of two Gaussian basis functions is defined as
+ \phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r}) = \left( \frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2} {\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).
+\end{equation}
+
+\section{Inner Product Bit}
+The matrix $\Gamma$ is defined as the inner product of the field basis function vector as
+\begin{equation}
+	\boldsymbol\Gamma = \left[
+	\begin{array}{{ccc}} 
+		\Gamma_{1,1} & \dots & \Gamma_{1,L} \\
+		\vdots & \ddots & \vdots \\
+		\Gamma_{L,1} & \dots & \Gamma_{L,L} 
+	\end{array}
+	\right],
+\end{equation}
+where
 \begin{equation}\label{eq:InofGaussianDefinition}
-\phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r
+\Gamma_{1,1} = \phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
 \end{equation}

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
correction to the appendix
more appendix changes
corrected some mistakes in the appendix

@@
 \begin{eqnarray}
-\mathcal{F}\left(\phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r})\right) &=& \left(\pi\sigma_{\phi}^2\sigma_{\psi_j}^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \nonumber \\
+\mathcal{F}\left(\phi_i*\psi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_{\phi}^2\sigma_{\psi_j}^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \nonumber \\
 &\times& (\pi(\sigma_{\phi}^2+\sigma_{\psi_j}^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_{\phi}^2+\sigma_{\psi_j}^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
@@
 \begin{equation}\label{eq:ConvoftwoGaussian}
- \phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r}) = \left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} \mathbf r^\top\mathbf r}\right).
+ \left(\phi_i*\psi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} \mathbf r^\top\mathbf r}\right).
 \end{equation}
@@
 \begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r}) = \left( \frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2} {\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).
-\end{equation}
-
+ \left(\phi_i*\psi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2} {\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).
+\end{equation}
+The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
 \section{Inner Product Bit}
@@
 \begin{equation}\label{eq:InofGaussianDefinition}
-\Gamma_{1,1} = \phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
+\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\Omega}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
 \end{equation}
@@
 \begin{equation}\label{eq:GaussianSymmetry}
- \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r)
-\end{equation}
-A direct consequence of equation \ref{eq:GaussianSymmetry} is
+ \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
 \begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r)
-\end{equation}
-substituting equation \ref{eq:ConsequenceofGaussianSymmetry} in equation \ref{eq:InofGaussianDefinition} we have 
+ \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
 \begin{eqnarray}
-\phi_i\otimes\phi_j&=&\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&\int_{\mathcal R^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i)
+\phi_i\otimes\phi_j&=&\int_{\Omega}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
+&=&\int_{\Omega}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
+&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i).
 \end{eqnarray}
-evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
+Evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
 \begin{equation}

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to paper linking appendices to text

@@
 \end{equation}
-The analytic derivation of the inner product of the \emph{n}-dimensional Gaussians is provided in~\ref{ap:ConvandIn}.
+The analytic derivation of the inner product of the \emph{n}-dimensional Gaussians is provided in~\ref{ap:InnerProdOfGaussians}.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
@@
 \end{equation}
-which is constant $L \times n_{\theta}$ matrix that can be defined analytically, where $n_{\theta}$ is the number of connectivity basis functions.
+which is constant $L \times n_{\theta}$ matrix that can be defined analytically (see~\ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), where $n_{\theta}$ is the number of connectivity basis functions.
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 To overcome the effect of noise, an evoked-response paradigm should be considered when using electrophysiological recordings.
-Following such a paradigm, data can be epoched into a sufficient number of realisations such that a distribution of the estimates can be formed.
-
-A significant contribution of this paper is the derivation of the basis function decomposition of the neural field.
+Following such a paradigm, data can be epoched into a sufficient number of realisations, where each realisation is a response to a stimuli, such that a distribution of the parameter estimates can be formed.
+
+A significant contribution of this paper is the derivation of the basis function decomposition of the neural field model.
 Through the derivation, a finite-dimensional state-space model is formed that describes a continuous neural field.
@@
 Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-Therefore, a limitation of this framework lies in an increase in dimensionality with increases in spatial resolution and in the physical size of the neural field.
+Therefore, a limitation of this framework lies in an increase in dimensionality with increases in  the spatial resolution and in the physical size of the neural field.
 Increases in dimensionality lead to increases in the uncertainty the estimated state, and problems associated with computational complexity.
@@
 \end{equation}
-\section{Convolution of two $n$-dimensional Gaussian basis functions}\label{ap:ConvandIn}
+\section{Convolution of two $n$-dimensional Gaussian basis functions}\label{ap:ConvOfGaussians}
 In this appendix we provide derivations for the convolution and the inner product of Gaussian basis functions.
@@
 The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
-\section{Inner Product Bit}
+\section{Inner Product Bit}\label{ap:InnerProdOfGaussians}
 The matrix $\Gamma$ is defined as the inner product of the field basis function vector as

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added some clarification to the appendix and fixed some notation
general paper edits

@@
 \end{equation}
-The analytic derivation of the inner product of the \emph{n}-dimensional Gaussians is provided in~\ref{ap:InnerProdOfGaussians}.
+An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in~\ref{ap:InnerProdOfGaussians}.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
@@
 \end{equation}
-which is constant $L \times n_{\theta}$ matrix that can be defined analytically (see~\ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), where $n_{\theta}$ is the number of connectivity basis functions.
+which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see~\ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 \end{equation}
-where $L$ is the number of basis functions used to decompose the neural field and 
+and 
 \begin{equation}
@@
 % and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}.
+\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
 Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
@@
 This motivates the use of sensors with wider bandwidths (narrower in space).
-Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region.
+Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
 Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and the computational demands of the estimation procedure when designing experiments.
@@
 This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
-To calculate the cut-off frequency imposed by the basis function, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
+To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
 \begin{equation}\label{eq:CutoffFromBasisFuncWidth}
@@
 
-The unscented Rauch Tung Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
+The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
 The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 \end{equation}
-where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is a scaling parameter (see~\cite{Haykin2001} for more details).
+where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
 
@@
 The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, needs to be computed.
+To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, is also computed.
 A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This feature is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate.
+This feature is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
@@
 \end{equation}
-Now given a state estimate sequence from the URTSS, we can write
+Now given a state estimate sequence from an iteration of the URTSS, we can write
 \begin{eqnarray*}
@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the parameter and state estimation, a Monte Carlo approach was employed where $100$ realisations of the data were generated.
+To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where $100$ realisations of the data were generated.
 Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
@@
 \end{figure}
-The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over time) of the root mean square error (MRMSE) (over space).
+The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space).
 The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
@@
 This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters and check if they correspond to the theoretically derived parameters where certain solutions can exist.
+For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters and check if they correspond to theoretically derived parameters where certain solutions can exist.
 In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
 
-In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
+In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
 In future work, we plan to relax this assumption.
@@
 Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, distant dependant propagation times into the parametric neural field equations.
+Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, and distant dependant propagation times into the parametric neural field equations.
 
@@
 This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
-Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (see equation~\ref{eq:BasisFunctionAtOrigin}) yields
+Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (defined in equation~\ref{eq:BasisFunctionAtOrigin}) yields
 \begin{eqnarray}\label{eq:AppendixGaussianFT}
- \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathcal R^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
-&=&\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
+ \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathbb{R}^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
+&=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
 &\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right),
@@
 \begin{eqnarray}\label{eq:IntegralOfGaussian}
-\int_{\mathcal R^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
 =\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
@@
 \end{equation}
-and hence completing the derivation. For 3 dB attenuation at $\boldsymbol\nu_c$ we need to set
+For $3$~dB attenuation at $\boldsymbol\nu_c$ we need to set
 \begin{eqnarray}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
 \end{eqnarray}
-solving for $\sigma_{\nu}^2$ we get
+since the maximum of Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Now solving for $\sigma_{\nu}^2$ we get
 \begin{equation}
@@
 \begin{equation}\label{eq:InofGaussianDefinition}
-\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\Omega}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
+\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
 \end{equation}
@@
 \begin{eqnarray}
-\phi_i\otimes\phi_j&=&\int_{\Omega}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&\int_{\Omega}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
+\phi_i\otimes\phi_j&=&\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
+&=&\int_{\mathbb{R}^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
 &=&(\phi_i*\phi_j)(2\boldsymbol \mu_i).

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
correction to the appendix
added field decomposition plot

@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\begin{figure}\label{fig:2d_kernel}
+\begin{figure}
    	\begin{center}
@@
 The kernel decays asymptotically to zero.}
+ 	\label{fig:2d_kernel}
    \end{figure}
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+An example of the field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+\begin{figure}
+   	\begin{center}
+   		\includegraphics{./Graph/FieldDecomposition.pdf} 
+   	\end{center}
+   	\caption{An example of continuous field decompposed by a finite number of basis functions scaled by the state vector. } 
+	\label{fig:FieldDecomposition}
+   \end{figure}
 The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
@@
 	\begin{equation}\label{eq:AppendixWt} 
-		\mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
+		\mathbf e_t(\mathbf r)=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
 	\end{equation}
@@
 \end{lemma}
-\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
+\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed.
+The expected value of $\mathbf e_t(\mathbf r)$ is given by
 \begin{eqnarray}
-	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
+	\mathbf E\left[ \mathbf e_t(\mathbf r)\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
 	&=&\mathbf 0 
 \end{eqnarray}
-The covariance of $\mathbf{e}_t$ is 
+The covariance of $\mathbf{e}_t(\mathbf r)$ is 
 \begin{eqnarray}
-	\lefteqn{\mathbf{\Sigma}_e} \nonumber \\ 
+	\lefteqn{\mathbf E\left[ \mathbf e_t(\mathbf r) \mathbf e_t^\top(\mathbf r')\right]} \nonumber \\ 
 &=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\

### 2010-06-21 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed appendix D

@@
 \section{Convolution of two $n$-dimensional Gaussian basis functions}\label{ap:ConvOfGaussians}
-In this appendix we provide derivations for the convolution and the inner product of Gaussian basis functions.
-These derivations are used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$.
-Consider the field Gaussian basis function
-\begin{equation}
- \phi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and the connectivity kernel basis function
-\begin{equation}
-\psi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\psi_j}^2} \mathbf{r}^\top\mathbf{r}}\right).
-\end{equation}
-The derivation proceeds by assuming the field basis function is positioned at the origin ($\boldsymbol\mu_i=\mathbf 0$).
-The convolution theorem states that the Fourier transform of a convolution is the product of Fourier transforms.
+In this appendix we provide derivation for the convolution of Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
+Consider two Gaussian basis functions
+\begin{equation}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
 Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
 \begin{eqnarray}
-\mathcal{F}\left(\phi_i*\psi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_{\phi}^2\sigma_{\psi_j}^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times& (\pi(\sigma_{\phi}^2+\sigma_{\psi_j}^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_{\phi}^2+\sigma_{\psi_j}^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
 \end{eqnarray}
@@
 \begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\phi_i*\psi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
 \begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\phi_i*\psi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2} {\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).
-\end{equation}
-The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
+\end{equation}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$. 
+% The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
 \section{Inner Product Bit}\label{ap:InnerProdOfGaussians}

### 2010-06-21 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed appendix B

@@
 Now we define the state disturbance as
-\begin{equation}\label{eq:AppendixWt} 
+\begin{equation}\label{eq:Wt} 
 	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
@@
 % \dean{DEFINE q HERE!!!!!}
-\section{}\label{ColoredNoise} 
-\newtheorem{lemma}{Lemma} 
-\begin{lemma}
-	Consider the i.i.d. noise term $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r'}))$ then 
-	\begin{equation}\label{eq:AppendixWt} 
-		\mathbf e_t(\mathbf r)=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
-	\end{equation}
-	is a vector valued, zero mean normally distributed white noise process with covariance 
-	\begin{equation}
-		\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}
-	\end{equation}
-	\label{lemma:FieldCovariance} 
-\end{lemma}
-\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed.
-The expected value of $\mathbf e_t(\mathbf r)$ is given by
+\section{Mean and covariance of the state disturbance }\label{ColoredNoise} 
+State disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
 \begin{eqnarray}
-	\mathbf E\left[ \mathbf e_t(\mathbf r)\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
+	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
 	&=&\mathbf 0 
 \end{eqnarray}
-The covariance of $\mathbf{e}_t(\mathbf r)$ is 
+The covariance of $\mathbf{e}_t$ is 
 \begin{eqnarray}
-	\lefteqn{\mathbf E\left[ \mathbf e_t(\mathbf r) \mathbf e_t^\top(\mathbf r')\right]} \nonumber \\ 
+	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
 &=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\

### 2010-06-21 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
minor edits, commiting for merge

--- 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
 
-\subsection{Derivation of Finite Dimensional State-Space Model} 
+\subsection{Derivation of Finite Dimensional State-Space Model}\section{Sect:ReducedModelDerivation}
 In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
@@
    	\end{center}
-   	\caption{An example of continuous field decompposed by a finite number of basis functions scaled by the state vector. } 
+   	\caption{An example of continuous field decomposed by a finite number of basis functions scaled by the state vector. } 
 	\label{fig:FieldDecomposition}
@@
 This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-The results indicate good estimation performance, where the mean parameter estimates are in good accordance to the actual values.
+The results indicate good estimation performance, where the mean parameter estimates are in good agreement to the actual values.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance and the observations are corrupted by noise.
@@
 
-A significant contribution of this paper is the derivation of the basis function decomposition of the neural field model.
+A significant contribution of this paper is the derivation of the basis function decomposition of the neural field model, as described in Section~\ref{Sect:ReducedModelDerivation}.
 Through the derivation, a finite-dimensional state-space model is formed that describes a continuous neural field.
@@
 
-The frequency analysis and model selection tools presented in this paper specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
+The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specifies the sensor arrangement that is required for capturing the dominant cortical dynamics.
 Importantly, these new tools can also be used to better design electrophysiological recording techniques to avoid spatial aliasing.
@@
 
-To the authors' best knowledge, this is the first paper to propose an estimation framework for intracortical connectivity from electrophysiological data.
+To the authors' best knowledge, this is the first paper to propose a model-based estimation framework for intracortical connectivity from electrophysiological data.
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
general paper edits, to word things more clearly

@@
 Spatial frequency analysis methods are introduced for model selection by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
-The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation and a least squares algorithm for parameter estimation.
+The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
 The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
@@
 
-\subsection{Derivation of Finite Dimensional State-Space Model}\section{Sect:ReducedModelDerivation}
+\subsection{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
 In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space).
-The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-At each time point the error is consistently around 0.5, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV.
+The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
+At each time point the error is consistently around 0.5~mV, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV.
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
@@
 This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-The results indicate good estimation performance, where the mean parameter estimates are in good agreement to the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance and the observations are corrupted by noise.
-To overcome the effect of noise, an evoked-response paradigm should be considered when using electrophysiological recordings.
-Following such a paradigm, data can be epoched into a sufficient number of realisations, where each realisation is a response to a stimuli, such that a distribution of the parameter estimates can be formed.
+The results indicate good estimation performance, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, that is modelled as a random disturbance, and the observations are corrupted by noise.
+To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
+Following such a paradigm, data can be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
 
 A significant contribution of this paper is the derivation of the basis function decomposition of the neural field model, as described in Section~\ref{Sect:ReducedModelDerivation}.
-Through the derivation, a finite-dimensional state-space model is formed that describes a continuous neural field.
-Previous work from Schiff and Sauer~\ref{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter for state-estimation of a discrete (in space and time) nonlinear spatial-temporal systems.
+Through the derivation, a finite-dimensional state-space model is formed that approximates a continuous neural field.
+Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
 Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-Therefore, a limitation of this framework lies in an increase in dimensionality with increases in  the spatial resolution and in the physical size of the neural field.
-Increases in dimensionality lead to increases in the uncertainty the estimated state, and problems associated with computational complexity.
-This paper builds on this previous study, where the estimator is constructed to describe a continuous field.
-The dimensionality of the state vector is independent of the resolution of a spatial discretisation and is governed by the inherent spatial properties of the field.
-The frequency analysis methods provide a rigorous framework for the placement and the number of the basis functions required for the decomposition.
+A limitation of this framework lies in an increase in dimensionality with increases in  the spatial resolution and in the physical size of the neural field.
+Increases in dimensionality lead to increases in uncertainty of the estimated state and problems associated with computational complexity.
+This paper builds on this previous study, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of a spatial discretisation and is governed by the inherent spatial properties of the field.
+The frequency analysis methods presented in Section~\ref{SpectralAnalysisSection} provide a rigorous framework for the placement and the number of the basis functions required for the decomposition.
 This enables estimation of a larger field, with a lower dimensional state vector.
@@
 
-The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specifies the sensor arrangement that is required for capturing the dominant cortical dynamics.
-Importantly, these new tools can also be used to better design electrophysiological recording techniques to avoid spatial aliasing.
+The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
+Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
 
-To the authors' best knowledge, this is the first paper to propose a model-based estimation framework for intracortical connectivity from electrophysiological data.
+To the authors' best knowledge, this is the first paper derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
@@
 The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
-Using the state-space model, the unscented Rauch Tung Striebel smoother was applied for state estimation.
+Using the state-space model, the unscented Rauch-Tung-Striebel smoother was applied for state estimation.
 Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some more general edits

@@
 This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-The results indicate good estimation performance, where the mean parameter estimates are in good agreement with the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, that is modelled as a random disturbance, and the observations are corrupted by noise.
+As seen in the Section~\ref{sec:state_and_param_results} the results indicate good estimation performance, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance, and the observations are corrupted by noise.
 To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
@@
 
-A significant contribution of this paper is the derivation of the basis function decomposition of the neural field model, as described in Section~\ref{Sect:ReducedModelDerivation}.
-Through the derivation, a finite-dimensional state-space model is formed that approximates a continuous neural field.
-Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
+Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
 Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
@@
 \section{Mean and covariance of the state disturbance }\label{ColoredNoise} 
-State disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
+The state disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$, therefore $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
 \begin{eqnarray}
 	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
-	&=&\mathbf 0 
+	&=&\mathbf 0.
 \end{eqnarray}
@@
 	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top} 
+	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
 \end{eqnarray}
@@
 &=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
-&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right),
+&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
 \end{eqnarray}
-where 
+Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
 \begin{eqnarray}\label{eq:IntegralOfGaussian}
@@
 \begin{equation}\label{eq:FTofGaussian}
-   \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu).
-\end{equation}
-Substituting $\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}$ gives 
-\begin{equation}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{equation}
-For $3$~dB attenuation at $\boldsymbol\nu_c$ we need to set
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation} 
+% 
+% \begin{equation}
+%    \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu).
+% \end{equation}
+where 
+\begin{equation}
+	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+
+For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
 \begin{eqnarray}

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to appendices

@@
 \end{eqnarray}
-\section{Calculation of Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
+\section{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
 This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
@@
 \end{equation}
-\section{Convolution of two $n$-dimensional Gaussian basis functions}\label{ap:ConvOfGaussians}
+\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
 In this appendix we provide derivation for the convolution of Gaussian basis functions.
@@
 % The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
-\section{Inner Product Bit}\label{ap:InnerProdOfGaussians}
+\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
 The matrix $\Gamma$ is defined as the inner product of the field basis function vector as

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
minor edits to the paper

@@
 Unfortunately, the use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies almost always have unique underlying patient-specific causes.
-Patient-specific data from EEG is readily available in the clinical setting, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
+Patient-specific data from electrophysiological recordings is readily available in the clinical setting, particularly from epilepsy surgery patients, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
 Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
@@
 We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
-In addition, a method is presented for estimating the connectivity structure and the synaptic time constant.
-Until now, estimation of local intracortical connectivity structure has not been reported (to the best of the authors' knowledge).
-Our work builds on recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
-The key development of this previous work was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observation (recording electrodes in this case).
+In addition, a method is presented for estimating the connectivity structure and the synaptic time dynamics.
+Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
+Our work builds on recent work which shows that it is possible to estimate local coupling of spatio-temporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
+The key development of this previous work was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
@@
 \section{Neural Field Model}\label{NeuralModelSection} 
-
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 \end{equation}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
@@
 The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\nu_{cy}$.
-Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\nu_{cy}$ replacing $\nu_c$.
+Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
+Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\boldsymbol{\nu}_{cy}$ replacing $\boldsymbol{\nu}_c$.
 
@@
 \begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\nu_{cy}}
+	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{cy}}
 \end{equation}

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
fixed a couple of typos in captions
updated appendix

@@
    	\end{center}
-   	\caption{An example of continuous field decomposed by a finite number of basis functions scaled by the state vector. } 
+   	\caption{An example of a continuous one-dimensional continuous field decomposed by a finite number of basis functions scaled by the state vector.} 
 	\label{fig:FieldDecomposition}
@@
 Consider two Gaussian basis functions
-\begin{equation}
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
  \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
@@
 and 
-\begin{equation}
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
 \varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
@@
 where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$. 
-% The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
+The analytic definition of the observation matrix, $C$, and the matrix $\boldsymbol\Psi(\mathbf{r})$ are formulated using this derivation.  
 \section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
-The matrix $\Gamma$ is defined as the inner product of the field basis function vector as
-\begin{equation}
-	\boldsymbol\Gamma = \left[
-	\begin{array}{{ccc}} 
-		\Gamma_{1,1} & \dots & \Gamma_{1,L} \\
-		\vdots & \ddots & \vdots \\
-		\Gamma_{L,1} & \dots & \Gamma_{L,L} 
-	\end{array}
-	\right],
-\end{equation}
-where
+The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
 \begin{equation}\label{eq:InofGaussianDefinition}
-\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
+\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
 \end{equation}
@@
 \begin{equation}\label{eq:GaussianSymmetry}
- \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r).
+ \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
 \end{equation}
@@
 \begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r).
+ \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
 \end{equation}
@@
 \begin{eqnarray}
-\phi_i\otimes\phi_j&=&\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&\int_{\mathbb{R}^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i).
+\varphi_i\otimes\varphi_j&=&\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
+&=&\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
+&=&(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
 \end{eqnarray}
-Evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}
- \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
+Evaluating equation~\ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
+\begin{equation}
+ \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
 \end{equation}

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
added PLoS template and bst and started converting our paper, yay!

--- 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
@@
-\documentclass[10pt,a4paper]{article}
-% \documentclass[12pt]{iopart} 
-% \usepackage{iopams,setstack}
+% Template for PLoS
+% Version 1.0 January 2009
+%
+% To compile to pdf, run:
+% latex plos.template
+% bibtex plos.template
+% latex plos.template
+% latex plos.template
+% dvipdf plos.template
 
+\documentclass[10pt]{article}
+
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
+
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
 \usepackage{graphicx}
-\usepackage{algorithm, algorithmicx, algpseudocode} 
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
 \usepackage{color}
-%This is to decrease the space in subfigure command
-\usepackage[tight,scriptsize]{subfigure}
+
+% Use doublespacing - comment out for single spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\topmargin 0.0cm
+\oddsidemargin 0.5cm
+\evensidemargin 0.5cm
+\textwidth 16cm 
+\textheight 21cm
+
+% Bold the 'Figure #' in the caption and separate it with a period
+% Captions will be left justified
+\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
+
+% Use the PLoS provided bibtex style
+\bibliographystyle{plos2009}
+
+% Remove brackets from numbering in List of References
 \makeatletter
-\renewcommand{\subfigtopskip}{1\p@}
-\renewcommand{\subfigcapskip}{0\p@}
-\renewcommand{\subfigcaptopadj}{1\p@}
-\renewcommand{\subfigbottomskip}{1\p@}
-\renewcommand{\subfiglabelskip}{0.05em plus 0.02em minus 0.01em}
+\renewcommand{\@biblabel}[1]{\quad#1.}
 \makeatother
-\renewcommand{\subcapsize}{\small}
 
-% maths
-\usepackage{amssymb,amsfonts,amsmath}
-% notes
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
-\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
-\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
+% Leave date blank
+\date{}
+
+\pagestyle{myheadings}
+%% ** EDIT HERE **
+
+%% ** EDIT HERE **
+%% PLEASE INCLUDE ALL MACROS BELOW
+
+%% END MACROS SECTION
 
@@
 
-\title{`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
+% Title must be 150 characters or less
+\begin{flushleft}
+{\Large
+\textbf{A Data Driven Framework for Patient-Specific Neural Field Modelling}
+}
+% Insert Author names, affiliations and corresponding author email.
+\\
+Dean R. Freestone$^{1,2,3}$, 
+Parham Aram$^{4}$, 
+Michael Dewar$^{5,\ast}$,
+Kenneth Scerri$^{6,\ast}$,
+David B. Grayden$^{1,\ast}$,
+Visakan Kadirkamanathan$^{4}$
+\\
+\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
+\\
+\bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
+\\
+\bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
+\\
+\bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
+\\
+\bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
+\\
+\bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta
+\\
+$\ast$ E-mail: dfreestone@bionicear.org
+\end{flushleft}
 
-\author{Dean R. Freestone$^{1,5}$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, \\David B. Grayden$^{1,5}$, and Visakan Kadirkamanathan$^2$}
-
-% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002Australia} \ead{dfreestone@bionicear.org}
-
-\maketitle
-
-\begin{abstract}
+% Please keep the abstract between 250 and 300 words
+\section*{Abstract}
 This paper presents a framework for creating patient-specific neural field models from electrophysiological data.
@@
 This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.
-\end{abstract}
 
-\section{Introduction}
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLoS ONE authors please skip this step. 
+% Author Summary not valid for PLoS ONE submissions.   
+\section*{Author Summary}
 
+\section*{Introduction}
 Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the meso/macroscopic scale.
@@
 
-%Currently available epileptic seizure control devices (i.e., the vagal nerve stimulator) are implemented in an ``open loop".
-That is, the therapeutic electrical stimulation waveforms are adjusted for each patient by trial and error, disregarding the patient's neuro-dynamics and information about their particular pathologies.
-Given access to an accurate model, the application of optimal control theory in these circumstances would allow for robust therapeutic stimulations.
-
 We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
@@
 
-\section{Neural Field Model}\label{NeuralModelSection} 
-Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
-They are popular as they are parsimonious yet have a strong link with the underlying physiology.
-Each neural population represents a functional cortical processing unit, such as a column.
-The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+% Results and Discussion can be combined.
+\section*{Results}
 
-\subsection{Derivation of the Integro-Difference Equation Representation}
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
-\begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}. 
-\end{equation}
-The post-synaptic response kernel $h(t)$ is described by 
-\begin{equation}
-	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}. 
-\end{equation}
-where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Non-local interactions between cortical populations are described by 
-\begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
-\end{equation}
-where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
-The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
-To demonstrate flexibility in estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
-An example of the connectivity kernel is shown in in Figure~\ref{fig:2d_kernel}.
-The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\begin{figure}
-   	\begin{center}
-   		\includegraphics{./Graph/Cross_section_kernel.pdf} 
-   	\end{center}
-   	\caption{Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
-The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
-The kernel decays asymptotically to zero.}
- 	\label{fig:2d_kernel}
-   \end{figure}
-The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
-\begin{equation}
-	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
-\end{equation}
-The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations respectively.
-The parameter $\varsigma$ governs the slope of the sigmoid.
-By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
-\begin{equation}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
-	\int_{-\infty}^t 
-	h\left(t - t'\right) \int_\Omega
-	w\left(\mathbf{r},\mathbf{r}'\right) 
-	f\left( v\left( \mathbf{r}',t \right)\right)
-	d\mathbf{r}'dt'.
-\end{equation}
-To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
-\begin{equation}
-	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
-\end{equation}
-where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{equation}
-	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
-\end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
-\begin{equation}
-	\label{DiscreteTimeModel} 
-	v_{t+T_s}\left(\mathbf{r}\right) = 
-	\xi v_t\left(\mathbf{r}\right) + 
-	T_s \int_\Omega { 
-	    w\left(\mathbf{r},\mathbf{r}'\right)
-	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	d\mathbf{r}'} 
-	+ e_t\left(\mathbf{r}\right), 
-\end{equation}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
-This term is added to account for uncertainty and unmodelled inputs.
-To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
+\subsection*{Subsection 1}
 
-The mapping between the membrane voltage and the electrophysiological data (iEEG/LFP) is modelled using the observation function 
-\begin{equation}
-    \label{eq:ObservationEquation}
-	\mathbf{y}_t =
-	\int_{\Omega}{
-	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	d\mathbf{r}'} + 
-	\boldsymbol{\varepsilon}_t, 
-\end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$, $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
-\begin{equation}
-	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)}. 
-\end{equation}
+\subsection*{Subsection 2}
 
-\subsection{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
-In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
-\begin{equation}\label{eq:FieldBasisFunction}
-	\phi\left(\mathbf{r}-\mathbf{r}'\right) =
-\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
-\end{equation}
-Decomposition allows a continuous field to be represented by a finite-dimensional state vector.
-This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
-The field decomposition is described by
-\begin{equation}
-	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
-\end{equation}
-where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-An example of the field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
-\begin{figure}
-   	\begin{center}
-   		\includegraphics{./Graph/FieldDecomposition.pdf} 
-   	\end{center}
-   	\caption{An example of continuous field decomposed by a finite number of basis functions scaled by the state vector. } 
-	\label{fig:FieldDecomposition}
-   \end{figure}
-The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
-The connectivity kernel can also be decomposed as
-\begin{equation}\label{DefKernelDecomp}
-	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
-\end{equation}
-where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
-We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
-Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
-Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition.
-To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
-Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{equation}
-	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}
-	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
-\end{equation}
-Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
-\begin{equation}
-    \begin{split}
-	\label{StartofReduction}
-	\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \\
- &T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta}  \\ & + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}. 
-\end{split}
-\end{equation}
-Now defining the matrix
-\begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
-\end{equation}
-and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{equation}
-    \label{eq:ReducedForm}
-    \begin{split}
-	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
-	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta} \\ 
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}.
-	 \end{split}
-\end{equation}
-An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in~\ref{ap:InnerProdOfGaussians}.
-Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
-\begin{equation}
-	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
-\end{equation}
-To make the simplification, we first define
-\begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
-\end{equation}
-which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see~\ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
-Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-\begin{eqnarray}
-	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t\nonumber \\
-+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{eqnarray}
-This simplification has transformed the description of the spatial coupling from a convolution, to an inner product.
-This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
-Now we define the state disturbance as
-\begin{equation}\label{eq:Wt} 
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
-\end{equation}
-which is a zero mean normally distributed white noise process with covariance (see~\ref{ColoredNoise})
-\begin{equation}
-	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
-\end{equation}
-Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
-\begin{equation}\label{eq:ReducedObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_td\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
-\end{equation}
-The observation equation is linear and can be written in the more compact form
-\begin{equation}\label{ObservationEquation} 
-	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
-\end{equation}
-where the observation matrix is 
-\begin{equation}
-	\mathbf{C} = \left[
-	\begin{array}{{ccc}} 
-		c_{1,1} & \dots & c_{1,L} \\
-		\vdots & \ddots & \vdots \\
-		c_{N,1} & \dots & c_{N,L} 
-	\end{array}
-	\right] 
-\end{equation}
-and 
-\begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')d\mathbf{r}'. 
-\end{equation}
-Now we have the final form of the state-space model where
-\begin{equation}\label{eq:finalformstatespacemodel}
-	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t.
-\end{equation}
-\begin{equation} 
-	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
-\end{equation}
-and 
-\begin{equation}\label{eq:QmatrixForSigmapoints}
-	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
-\end{equation}
+\section*{Discussion}
 
-% \begin{equation}
-% \mathbf{C} = \left[\begin{array}{{cccc}}
-% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
-% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
-% r')d\mathbf r' \\
-% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
-% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
-% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
-% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
-% \vdots&\vdots&\ddots&\vdots\\
-% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
-% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
-% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
-% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
-% \end{array}\right],
-% \end{equation}
-% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
-\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
-Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
+% You may title this section "Methods" or "Models". 
+% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
+% authors may use "Analysis" 
+\section*{Materials and Methods}
 
-Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
-According to Shannon's sampling theorem, the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
-Nevertheless, an approximate reconstruction can be obtained if the field is approximately band-limited with
-\begin{equation}
-	V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c,
-\end{equation}
-where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
-Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
-\begin{equation}
-	\label{eq:MinimumSensorDistance} \Delta_y \leq \frac{1}{2\rho_y\nu_{c}}, 
-\end{equation}
-where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
-This condition must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
+% Do NOT remove this, even if you are not including acknowledgments
+\section*{Acknowledgments}
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
-The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
-Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\boldsymbol{\nu}_{cy}$ replacing $\boldsymbol{\nu}_c$.
+%\section*{References}
+% The bibtex filename
+\bibliography{template}
 
-Although such sensors avoid errors due to aliasing, they attenuate the high spatial frequency variations in the observations.
-Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations has the potential to underestimate the high spatial frequency components of both the field and the connectivity kernel.
-This motivates the use of sensors with wider bandwidths (narrower in space).
-Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
-Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and the computational demands of the estimation procedure when designing experiments.
+\section*{Figure Legends}
+%\begin{figure}[!ht]
+%\begin{center}
+%%\includegraphics[width=4in]{figure_name.2.eps}
+%\end{center}
+%\caption{
+%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
+%should be left justified, as specified by the options to the caption 
+%package.
+%}
+%\label{Figure_label}
+%\end{figure}
 
-Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-Again applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
-\begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{cy}}
-\end{equation}
-where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation.
+\section*{Tables}
+%\begin{table}[!ht]
+%\caption{
+%\bf{Table title}}
+%\begin{tabular}{|c|c|c|}
+%table information
+%\end{tabular}
+%\begin{flushleft}Table caption
+%\end{flushleft}
+%\label{tab:label}
+% \end{table}
 
-The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
-\begin{equation}\label{eq:BasisFunctionAtOrigin}
- \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
-\end{equation}
-with the corresponding Fourier transform
-\begin{equation}\label{eq:GaussianFT}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation}
-where 
-\begin{equation}\label{eq:GaussianFTWidth}
-	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-To obtain a 3~dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
-\begin{equation}\label{eq:WidthCutOffRelationship}
- \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2},
-\end{equation}
-where
-\begin{equation}\label{eq:WidthFrequencyRelationship}
- \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
-\end{equation}
-This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
-Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
-
-Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
-This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
-To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
-\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
-	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
-\end{equation}
-
-Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid.
-Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
-
-% 
-% Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
-\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
-The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
-At each iteration, the sequence of estimated state vectors is used to update the parameter set.
-The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
-The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state vector sequence guaranteeing that the initial estimated parameter set forms a stable kernel.
-
-The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
-The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
-The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
-The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
-\begin{equation}\label{eq:sigmapoints1}
-	\mathcal X_{0}=\bar x 
-\end{equation}
-\begin{equation}
-	\mathcal X_{i}=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L 
-\end{equation}
-\begin{equation}\label{eq:sigmapoints2}
-	\mathcal X_{i}=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2 L 
-\end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
-The total number of sigma points is $2L+1$.
-The scaling parameter, $\lambda$, is defined as
-\begin{equation}\label{eq:sigmapoints3}
-	\lambda=\alpha^2( L+\kappa) - L, 
-\end{equation}
-where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
-
-The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
-\begin{equation}
-	\mathbf W_0^{(m)}=\frac{\lambda}{ L+\lambda} 
-\end{equation}
-\begin{equation}
-	\mathbf W_0^{(c)}=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) 
-\end{equation}
-\begin{equation}
-	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
-\end{equation}
-where the superscripts $m$ and $c$ stand for mean and covariance.
-Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
-The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, is also computed.
-A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
-It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
-Therefore, the additive form of the URTSS is used, instead of augmenting the state vector with the noise terms with the added benefit of reducing the dimension and the number of sigma points required in the algorithm.
-\begin{algorithm}
-	\begin{small}
-	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
-	\begin{algorithmic}[1] 
-		\State Forward initialisation 
-		\begin{equation*}
-		 \hat{\mathbf x}_0, \mathbf P_0 
-		\end{equation*}
-		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
-% 		\begin{small}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
-		\end{equation*}
-% 		\end{small}
-		calculate the predicted state and the predicted covariance matrix
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
-		\begin{equation*}
-			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
-		\end{equation*}
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
-		\end{equation*}
-		\State Backward initialisation 
-		\begin{equation*}
-			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
-		\end{equation*}
-		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
-		\end{equation*}
-		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
-		\end{equation*}
-		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
-		\begin{equation*}
-			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
-		\end{equation*}
-		\begin{equation*}
-			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
-		\end{equation*}
-	\end{algorithmic}
-\end{small}
-\end{algorithm}
-
-Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This feature is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
-To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
-\begin{equation}
-	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
-\end{equation}
-Now given a state estimate sequence from an iteration of the URTSS, we can write
-\begin{eqnarray*}
-	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
-	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
-	&\vdots& \\
-	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
-\end{eqnarray*}
-This can be written in the compact form
-\begin{equation}
-	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
-\end{equation}
-where
-\begin{small}
-\begin{equation*}
-	\mathbf Z=\left[
-	\begin{array}{cccc}
-		\mathbf x_{1}\\
-		\mathbf x_{2}\\
-		\vdots\\
-		\mathbf x_{T}
-	\end{array}
-	\right],\quad \mathbf X=\left[
-	\begin{array}{cccc}
-		\mathbf q(\mathbf x_0)& \mathbf x_{0}\\
-		\mathbf q(\mathbf x_1)& \mathbf x_{1}\\
-		\vdots & \vdots\\
-		\mathbf q(\mathbf x_{T-1})& \mathbf x_{T-1}
-	\end{array}
-	\right] 
-\end{equation*}
-\end{small}
-and
-\begin{small}
-\begin{equation*}
-\quad \mathcal W=\left[
-	\begin{array}{cc}
-		\boldsymbol{\theta} \\
-		\xi
-	\end{array}
-	\right],\quad \mathbf{e}=\left[
-	\begin{array}{cccc}
-		\mathbf e_0\\
-		\mathbf e_1\\
-		\vdots\\
-		\mathbf e_{T-1}
-	\end{array}
-	\right].
-\end{equation*}
-\end{small}
-Following this, the LS parameter estimates, $ \mathcal{\hat{W}}$, are
-\begin{equation}
-	\mathcal{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
-\end{equation}
-% The accuracy of the approximation is linked to the time step used in the temporal discretisation of the system, where the state transition appears more linear with a finer resolution. 
-% Alternatives to the UKF are the Extended Kalman Filter (EKF)~\cite{Haykin2001} and the Sequential Monte Carlo (SMC) filter~\cite{doucet2001}.
-The EKF approximates the state transition equation by linearising about the current state estimates (by calculating the Jacobian) at each time instance.
-The linearisation maintains the Gaussianality of the model.
-The unscented Kalman filter approximates the posterior state density by a Gaussian distribution using a minimal set of carefully chosen sigma points, while maintaining the nonlinearity in the system.
-This has been shown to give superior performance over the EKF in state estimation, since the EKF maintains a first order approximation where the UKF provides an approximation accurate at least to the second order.
-In addition, the computation of the Jacobian used in the EKF can be problematic.
-SMC filtering can theoretically provide an exact posterior state density for nonlinear systems.
-However, currently this method is not appropriate for our problem, due to high computation demands.
-
-%The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
-\section{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the methods described above.
-The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{tab:Model Parameters}.
-Note that, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
-This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-When generating the simulated data we assumed free boundary conditions for the neural field.
-An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(a).
-Figure~\ref{fig:experimental design}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
-The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
-\begin{table}\footnotesize
-\centering
-\begin{tabular}{ccl}
-	\hline\hline Symbol & Value & Units \\
-	\hline\hline
-	$\tau$ & 0.01 & s$^{-1}$\\
-	$f_{max}$ & 10 & spikes/s \\
-	$\varsigma$ & 0.8 & spike/mV\\
-	$v_0$ & 2 & mV\\
-	$\boldsymbol{\theta}$ & $\left[\begin{array}{ccc}
-	10 &-8 &0.5
-	\end{array}
-	\right]^{\top}$ & mV/spike\\
-	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & 1.8, 2.4, 6 & mm\\
-	$\sigma_{m},\Delta_{y}$&0.9, 1.5&mm\\
-	$\Sigma_{\epsilon}$ &$0.1 \times I_{N} $& mm$^2$ \\
-	$\sigma_{\gamma}$&1.3&mm\\
-	$\Delta$ & 0.5 & mm \\
-	$T_s$ & 1 & ms \\ 
-\hline\hline
-\end{tabular}
-\caption{Parameters for the neural field model that are used to generate synthetic data.}
-\label{tab:Model Parameters}
-\end{table}
-
-The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$.
-This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm.
-This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
-\begin{figure}
-   	\begin{center}
-    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePy.pdf}} \\
-    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
-   		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePSDPy.pdf}} \\
-   	\end{center}
-   	\caption{\textbf{a.} Example of the neural feld.
-\textbf{b.} Example of data generated by the full neural field model from the first 5 sensors.
-\textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
-\label{fig:experimental design}
-\end{figure}
-\subsection{Spatial Frequency Analysis} 
-Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
-The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.
-This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
-\begin{figure}
-\centering
-\subfigure[][]{\label{fig:FieldFFT}\includegraphics{./Graph/FFTTrueField.pdf}}
-\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
-\caption{Spatial frequency analysis of the neural field.
-\textbf{a.} The average (over time) power in dB of the spatial frequency of the neural field.
-\textbf{b.} The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
-\label{fig:FFTTrueEstimate}
-\end{figure}
-The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
-The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
-The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
-Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
-Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
-This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
-\begin{figure} 
-	\begin{center}
-		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
-		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
-		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
-	\end{center}
-	\caption{Spatial frequency analysis.
-The dashed line shows the cut-off frequency (-3 dB point).
-\textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
-The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-\textbf{b.} The spatial frequency response of a one-dimensional model sensor.
-\textbf{c.} The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
-\end{figure}
-
-\subsection{State and Parameter Estimates} 
-\label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where $100$ realisations of the data were generated.
-Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
-The initial state and parameters were unknown to the estimator.
-Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
-\begin{figure}
-        \centering
-\includegraphics{./Graph/convergence.pdf}
-\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
-All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
-\label{fig:ParametersConvergence}
-\end{figure}
-
-Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}.
-The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
-The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good concordance with the actual values.
-% It should be noted that when the excitatory connectivity parameters, $\hat\theta_0$ and $\hat\theta_2$, were under (or over) estimated, the inhibitory connectivity parameter, $\hat\theta_1$, tended to be over (or under) estimated.
-This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates.
-\begin{table}
-\centering
-\begin{tabular}{cccc}
-	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
-	\hline\hline
- 	$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
-	$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
-	$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
-	$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
-	% $\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
-	% $\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
-\hline\hline
-\end{tabular}
-\caption{Actual parameter values compared to parameter estimates.}
-\label{tab:Parameters estimates}
-\end{table}
-\begin{figure}
-    \centering
-    \subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
-    \subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
-    \subfigure[][]{\label{fig:theta1dis}\includegraphics{./Graph/theta1.pdf}}
-    \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
-\caption{Distribution of the parameter estimates over 100
-realisations.
-The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
-\textbf{a.} The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
-\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-\textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
-\label{fig:Parameters}
-\end{figure}
-% \begin{figure}
-%     \centering
-% \subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
-% \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-% \caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
-\textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
-\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
-In each case, the solid and dotted lines show the locations of the true and estimated ratios respectively.}
-% \label{fig:ParametersRatio}
-% \end{figure}
-The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
-The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
-
-\begin{figure}
-    \centering
-% \subfigure[][]{
-\includegraphics{./Graph/KernelEstimate.pdf}%}
-% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
-\caption{Cross-section of connectivity kernel estimate.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
-\label{fig:KernelEstimates}
-\end{figure}
-The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space).
-The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-At each time point the error is consistently around 0.5~mV, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV.
-The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
-The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:FieldEstimate}(b) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(a)), but is missing the higher-frequency detail.
-  \begin{figure}
-   	\begin{center}
-   		\includegraphics{./Graph/MRMSE.pdf} 
-   	\end{center}
-   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
-\label{fig:RMSE}
-   \end{figure}
-
-\begin{figure}
-\centering 
-\subfigure[][]{\label{fig:TrueField}\includegraphics{./Graph/TrueField90.pdf}}
-\subfigure[][]{\includegraphics{./Graph/EstimatedField90.pdf}}
-\subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
-\caption{Examples of the actual and estimated neural fields and the error.
-\textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data.
-\textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-\textbf{c.} The absolute error between the true and reconstructed fields.
-The error shows high frequency behaviour.}
-\label{fig:FieldEstimate}
-\end{figure}
-
-\section{Discussion}\label{DiscussionSection}
-This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-As seen in the Section~\ref{sec:state_and_param_results} the results indicate good estimation performance, where the mean parameter estimates are in good agreement with the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance, and the observations are corrupted by noise.
-To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
-Following such a paradigm, data can be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
-
-Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
-Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-A limitation of this framework lies in an increase in dimensionality with increases in the spatial resolution and in the physical size of the neural field.
-Increases in dimensionality lead to increases in uncertainty of the estimated state and problems associated with computational complexity.
-This paper builds on this previous study, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of a spatial discretisation and is governed by the inherent spatial properties of the field.
-The frequency analysis methods presented in Section~\ref{SpectralAnalysisSection} provide a rigorous framework for the placement and the number of the basis functions required for the decomposition.
-This enables estimation of a larger field, with a lower dimensional state vector.
-The basis function decomposition also enabled the coupling to be described by an inner product rather than a spatial convolution.
-This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
-
-The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
-Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-To the authors' best knowledge, this is the first paper derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-
-The closest competitor to our `grey-box' integro-difference equation (IDE) based approach is perhaps the `black-box' multivariate auto-regressive (MVAR) model.
-Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
-A distinct advantage of the IDE-based technique proposed in this paper, is that the estimates of the connectivity structure are made independently of the number of sensors (assuming the field is sufficiently sampled).
-In addition, the number of parameters required to model the system is considerably less than a typical MVAR model.
-Furthermore, by using the neural field equations as a parametric form of the model, the parameters have physical meaning and therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
-A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of a multi-scale connectivity structure in generating the characteristic rhythms of the brain.
-A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
-
-Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a patient-specific state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
-\dean{can expand a bit}
-
-Parameter estimation may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-
-The development of an estimation framework also has theoretical implications.
-The the ability to estimate parameters will allow testing of hypotheses that have been generated in theoretical studies.
-This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters and check if they correspond to theoretically derived parameters where certain solutions can exist.
-In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
-
-In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
-In future work, we plan to relax this assumption.
-We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
-In addition, we have assumed the neural field is isotropic and homogeneous.
-It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
-However, the assumption of homogeneity is quite strong.
-Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, and distant dependant propagation times into the parametric neural field equations.
-
-\section{Conclusion}
-This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields to create patient specific models.
-A basis function decomposition reduces the infinite dimensional neural field (continuous space) to a finite dimensional state-space model.
-The frequency analysis methods presented in this paper provide a systematic procedure for specifying the sensor and basis function arrangement required to describe the significant neuro-dynamics by the reduced neural field model.
-The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
-Using the state-space model, the unscented Rauch-Tung-Striebel smoother was applied for state estimation.
-Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
-We have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic dynamics using the proposed methodology.
-
-\appendix 
-\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be performed.
-We used a one-step Euler method where equation~\ref{FinalFormContinuous} can be approximated by
-\begin{eqnarray}
-	\label{Euler Approximation} \lefteqn{\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =}\nonumber\\
-& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.\nonumber \\ 
-\end{eqnarray}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation} we get 
-\begin{eqnarray}
-	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right)\nonumber \\
-&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.\nonumber \\ 
-\end{eqnarray}
-The discrete time form of the model is 
-\begin{equation}
-	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
-\end{equation}
-where $\xi = 1 - T_s \zeta$. 
-% \section{Numerical Simulation of IDE Model}\label{Space Discretization} To solve the intregro-difference equation in Eq.~\ref{Discrete Time Model1} we define the spatial aspect of the model on a regular square $i,j$ grid of neural masses, where the spatial step size $\Delta \mathbf{r}_i = \Delta \mathbf{r}_j = \Delta $ giving
-% \begin{eqnarray}
-% 	\label{discrete space} \lefteqn{v_{t+1}\left(\mathbf{r}_{ij}\right)=}\nonumber\\
-% &&\xi v_t\left(\mathbf{r}_{ij}\right)+T_s \Delta^2\sum_{i=1}^{i=I}{\sum_{j=1}^{j=J}{w\left(\mathbf{r}-\mathbf{r}_{ij}'\right)f\left( v_t\left( \mathbf{r}_{ij}'\right)\right)}}\nonumber\\
-% &+& e_t(\mathbf{r}_{i,j}), 
-% \end{eqnarray}
-% where $e_t(\mathbf{r}_{i,j}) \sim \mathcal{N}\left(0,\Sigma\right)$. We have used free boundary conditions and extended the spatial domain to alleviate problems associated with edge effects. 
-% \section{Reduction to Finite State-Space Model}\label{Simplifying Decomposition} 
-% Starting from equation~\ref{reduced continuous model} we multiply throughout by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
-% \begin{eqnarray}
-% 	\label{StartofReduction}\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \nonumber\\
-%  &&T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \boldsymbol{\theta}^{\top} \int_\Omega {\boldsymbol{\psi} \left(\mathbf{r}-\mathbf{r}'\right) f\left(\boldsymbol{\phi}^{\top}\left(\mathbf{r}'\right) \mathbf{x}_t \right)d\mathbf{r}'}d\mathbf{r}} \nonumber\\
-% &+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-% \int_\Omega{\boldsymbol{\phi} \left(\mathbf{r}\right) e_t\left(\mathbf{r}\right)d\mathbf{r}}. 
-% \end{eqnarray}
-% Now defining
-% \begin{equation}\label{eq:DefGamma2}
-% 	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
-% \end{equation}
-% and substituting equation~\ref{eq:DefGamma2} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-% \begin{eqnarray}\label{eq:ReducedForm}
-% 	 \lefteqn{\mathbf{x}_{t+1} \nonumber = T_s\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')d\mathbf{r}'} d\mathbf{r}} \boldsymbol{\theta}} \nonumber\\
-% &+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-% \end{eqnarray}
-% Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
-% \begin{equation}
-% 	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
-% \end{equation}
-% To make the simplification we first define
-% \begin{equation}\label{eq:DefPsi}
-% 	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
-% \end{equation}
-% which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-% \begin{equation}
-% 	\mathbf{x}_{t+1} \nonumber = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-% \end{equation}
-% \dean{DEFINE q HERE!!!!!}
-\section{Mean and covariance of the state disturbance }\label{ColoredNoise} 
-The state disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$, therefore $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
-\begin{eqnarray}
-	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
-	&=&\mathbf 0.
-\end{eqnarray}
-The covariance of $\mathbf{e}_t$ is 
-\begin{eqnarray}
-	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{eqnarray}
-\section{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
-This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
-Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (defined in equation~\ref{eq:BasisFunctionAtOrigin}) yields
-\begin{eqnarray}\label{eq:AppendixGaussianFT}
- \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathbb{R}^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
-&=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
-&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{eqnarray}
-Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{eqnarray}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
-\end{eqnarray}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation} 
-% 
-% \begin{equation}
-%    \boldsymbol\Phi(\boldsymbol\nu)=(\pi\sigma_{\phi}^2)^{\frac{n}{2}}\mathrm{exp}(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu).
-% \end{equation}
-where 
-\begin{equation}
-	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-
-For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{eqnarray}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{eqnarray}
-since the maximum of Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Now solving for $\sigma_{\nu}^2$ we get
-\begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
-\end{equation}
-\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this appendix we provide derivation for the convolution of Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
-\begin{eqnarray}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{eqnarray}
-where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution is
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
-\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
-\end{equation}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$. 
-% The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
-\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
-The matrix $\Gamma$ is defined as the inner product of the field basis function vector as
-\begin{equation}
-	\boldsymbol\Gamma = \left[
-	\begin{array}{{ccc}} 
-		\Gamma_{1,1} & \dots & \Gamma_{1,L} \\
-		\vdots & \ddots & \vdots \\
-		\Gamma_{L,1} & \dots & \Gamma_{L,L} 
-	\end{array}
-	\right],
-\end{equation}
-where
-\begin{equation}\label{eq:InofGaussianDefinition}
-\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
-\end{equation}
-A Gaussian basis function is symmetric with respect to its centre, therefore
-\begin{equation}\label{eq:GaussianSymmetry}
- \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
-\begin{eqnarray}
-\phi_i\otimes\phi_j&=&\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&\int_{\mathbb{R}^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
-&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i).
-\end{eqnarray}
-Evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}
- \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
-\end{equation}
-\section{Notation}
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        $\Omega$ & spatial domain \\
-	    $t$ & time (seconds) \\
-    	$\mathbf{r}$ & spatial location \\
-	    $n$ & sensor index $n=1,..,N$ \\
-    	$T$ & time step
-    \end{tabular}
-    \caption{Domain and indices}
-\end{table}
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        $y(\mathbf{r}_n,t)$ & observation \\
-	    $v(\mathbf{r},t)$ & mean membrane potential \\
-    	$g(\mathbf{r},t)$ & average action potential rate \\
-    	$f(\mathbf{r},t)$ & firing function rate \\
-    	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
-	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance$\Sigma_\epsilon$ \\
-    \end{tabular}
-    \caption{Spatiotemporal Signals}
-\end{table}
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        	$h(t)$ & post-synaptic response kernel \\
-	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
-	$\eta(t)$ & Heaviside function \\
-	$\zeta$ & inverse synaptic time constant \\
-	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
-	$f_{max}$ & maximal firing rate \\
-	$\varsigma$ & slope of sigmoidal activation function \\
-	$v_0$ & firing threshold \\
-	$\delta(t)$ & Dirac-delta function \\
-	$D$ & Temporal differential operator \\
-	$\xi$ & time constant parameter
-    \end{tabular}
-    \caption{Model}
-\end{table}
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        $L$ & number of field basis functions  \\
-    	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
-    	$\mathbf{x}_t$ & state vector at time $t$ \\
-    	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
-    	$\theta$ & vector of connectivity kernel parameters \\
-    	$\Gamma$ & inner product of field basis functions \\
-    	$q()$ & state function \\
-    	$Q()$ & state function \\
-	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
-    	$\mathbf{e}_t$ & state disturbance \\
-	$\Sigma_e$ &state disturbance covariance matrix\\
-	$\mathbf{\epsilon}_t$ & observation noise \\
-	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
-    	$\mathbf{C}$ & observation matrix \\
-	$c_{ij}$& elements of observation matrix
-    \end{tabular}
-    \caption{Decomposition}
-\end{table}
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{rl}
-        $V(\nu)$ & Spectrum of the dynamic field \\
-	$\nu$ & Spatial frequency \\
-	$\nu_c$ & Spatial cut-off frequency \\
-	$\Delta_y$ & Distance between adjacent sensors \\
-	$\rho$ & Over-sampling parameter \\
-	$\Delta_{\phi}$ & Distance between field basis functions \\
-	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
-	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
-    \end{tabular}
-    \caption{Frequency Analysis}
-\end{table}
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        $\hat{\mathbf{x}}$ & State estimate \\
-	$\chi$ & Matrix of sigma vectors \\
-	$\lambda$& Scaling parameter\\
-	$\alpha$& Determines the spread of sigma points\\
-	$\beta$& Priro knowledge of the sigma points distribution\\
-	$\kappa$& Scaling parameter\\
-	$W$& Sigma vecors weights\\
-    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
-    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
-    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
-    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
-    	$P^f_t$ & Forward posterior covariance matrix \\
-    	$P^{f-}_t$ & Forward prior covariance matrix \\
-    	$P^b_t$ & Backward posterior covariance matrix \\
-    	$P^{b-}_t$ & Backward prior covariance matrix \\
-	$\mathcal K_{t} $& Filter gain\\
-	$M_t$& Cross-covariance matrix\\
-	$S_t$& Smoother gain
-    \end{tabular}
-    \caption{State Estimation}
-\end{table}
-
-\bibliographystyle{unsrt} 
-\bibliography{BrainIDE}
-
-% \begin{thebibliography}{10}
-% \bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
-% (Reading, MA: Addison-Wesley)
-% \bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
-% \end{thebibliography}
 \end{document}

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
moved bib file to PLoS folder
added graphs folder to PLoS

@@
 %\doublespacing
+
+% put this in temporarily
+\usepackage{algorithm, algorithmicx, algpseudocode}
 
@@
 
+% You may title this section "Methods" or "Models". 
+% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
+% authors may use "Analysis" 
+\section*{Methods}
+
+\subsection{Neural Field Model}\label{NeuralModelSection} 
+Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
+They are popular as they are parsimonious yet have a strong link with the underlying physiology.
+Each neural population represents a functional cortical processing unit, such as a column.
+The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \cite{Braitenberg1998}.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
+Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+
+\subsection{Derivation of the Integro-Difference Equation Representation}
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
+The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
+\begin{equation}
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}. 
+\end{equation}
+The post-synaptic response kernel $h(t)$ is described by 
+\begin{equation}
+	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}. 
+\end{equation}
+where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Non-local interactions between cortical populations are described by 
+\begin{equation}
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
+\end{equation}
+where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
+The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
+To demonstrate flexibility in estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
+An example of the connectivity kernel is shown in in Figure~\ref{fig:2d_kernel}.
+The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
+\begin{figure}
+   	\begin{center}
+   		\includegraphics{./Graph/Cross_section_kernel.pdf} 
+   	\end{center}
+   	\caption{Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
+The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+The kernel decays asymptotically to zero.}
+ 	\label{fig:2d_kernel}
+   \end{figure}
+The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
+\begin{equation}
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
+\end{equation}
+The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations respectively.
+The parameter $\varsigma$ governs the slope of the sigmoid.
+By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
+\begin{equation}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
+	\int_{-\infty}^t 
+	h\left(t - t'\right) \int_\Omega
+	w\left(\mathbf{r},\mathbf{r}'\right) 
+	f\left( v\left( \mathbf{r}',t \right)\right)
+	d\mathbf{r}'dt'.
+\end{equation}
+To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
+\begin{equation}
+	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
+\end{equation}
+where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+\begin{equation}
+	\label{FinalFormContinuous} 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
+\end{equation}
+To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+\begin{equation}
+	\label{DiscreteTimeModel} 
+	v_{t+T_s}\left(\mathbf{r}\right) = 
+	\xi v_t\left(\mathbf{r}\right) + 
+	T_s \int_\Omega { 
+	    w\left(\mathbf{r},\mathbf{r}'\right)
+	    f\left(v_t\left(\mathbf{r}'\right)\right) 
+	d\mathbf{r}'} 
+	+ e_t\left(\mathbf{r}\right), 
+\end{equation}
+where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+This term is added to account for uncertainty and unmodelled inputs.
+To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
+
+The mapping between the membrane voltage and the electrophysiological data (iEEG/LFP) is modelled using the observation function 
+\begin{equation}
+    \label{eq:ObservationEquation}
+	\mathbf{y}_t =
+	\int_{\Omega}{
+	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
+	d\mathbf{r}'} + 
+	\boldsymbol{\varepsilon}_t, 
+\end{equation}
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$, $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
+The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
+\begin{equation}
+	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)}. 
+\end{equation}
+
+\subsection{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
+In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
+\begin{equation}\label{eq:FieldBasisFunction}
+	\phi\left(\mathbf{r}-\mathbf{r}'\right) =
+\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
+\end{equation}
+Decomposition allows a continuous field to be represented by a finite-dimensional state vector.
+This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
+The field decomposition is described by
+\begin{equation}
+	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
+\end{equation}
+where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
+An example of the field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+\begin{figure}
+   	\begin{center}
+   		\includegraphics{./Graph/FieldDecomposition.pdf} 
+   	\end{center}
+   	\caption{An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.} 
+	\label{fig:FieldDecomposition}
+   \end{figure}
+The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
+The connectivity kernel can also be decomposed as
+\begin{equation}\label{DefKernelDecomp}
+	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
+\end{equation}
+where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
+We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
+Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
+Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition.
+To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
+Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
+\begin{equation}
+	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}
+	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+\end{equation}
+Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
+\begin{equation}
+    \begin{split}
+	\label{StartofReduction}
+	\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \\
+ &T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta}  \\ & + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
+\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}. 
+\end{split}
+\end{equation}
+Now defining the matrix
+\begin{equation}\label{eq:DefGamma}
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
+\end{equation}
+and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
+\begin{equation}
+    \label{eq:ReducedForm}
+    \begin{split}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta} \\ 
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}.
+	 \end{split}
+\end{equation}
+An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in~\ref{ap:InnerProdOfGaussians}.
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
+\begin{equation}
+	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+\end{equation}
+To make the simplification, we first define
+\begin{equation}\label{eq:DefPsi}
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+\end{equation}
+which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see~\ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
+Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+\begin{eqnarray}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t\nonumber \\
++ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
+\end{eqnarray}
+This simplification has transformed the description of the spatial coupling from a convolution, to an inner product.
+This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
+Now we define the state disturbance as
+\begin{equation}\label{eq:Wt} 
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
+\end{equation}
+which is a zero mean normally distributed white noise process with covariance (see~\ref{ColoredNoise})
+\begin{equation}
+	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+\end{equation}
+Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
+\begin{equation}\label{eq:ReducedObservationEquation}
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_td\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+\end{equation}
+The observation equation is linear and can be written in the more compact form
+\begin{equation}\label{ObservationEquation} 
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+\end{equation}
+where the observation matrix is 
+\begin{equation}
+	\mathbf{C} = \left[
+	\begin{array}{{ccc}} 
+		c_{1,1} & \dots & c_{1,L} \\
+		\vdots & \ddots & \vdots \\
+		c_{N,1} & \dots & c_{N,L} 
+	\end{array}
+	\right] 
+\end{equation}
+and 
+\begin{equation}
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')d\mathbf{r}'. 
+\end{equation}
+Now we have the final form of the state-space model where
+\begin{equation}\label{eq:finalformstatespacemodel}
+	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t.
+\end{equation}
+\begin{equation} 
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
+\end{equation}
+and 
+\begin{equation}\label{eq:QmatrixForSigmapoints}
+	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
+\end{equation}
+
+\subsection{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
+Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
+
+Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
+According to Shannon's sampling theorem, the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
+Nevertheless, an approximate reconstruction can be obtained if the field is approximately band-limited with
+\begin{equation}
+	V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c,
+\end{equation}
+where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy
+\begin{equation}
+	\label{eq:MinimumSensorDistance} \Delta_y \leq \frac{1}{2\rho_y\nu_{c}}, 
+\end{equation}
+where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
+This condition must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
+
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
+The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
+Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
+Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\boldsymbol{\nu}_{cy}$ replacing $\boldsymbol{\nu}_c$.
+
+Although such sensors avoid errors due to aliasing, they attenuate the high spatial frequency variations in the observations.
+Therefore, any procedure applied to estimate the original field or the underlying connectivity structure from these band-limited observations has the potential to underestimate the high spatial frequency components of both the field and the connectivity kernel.
+This motivates the use of sensors with wider bandwidths (narrower in space).
+Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and the computational demands of the estimation procedure when designing experiments.
+
+Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
+Again applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
+\begin{equation}\label{eq:BasisFunctionSeparation}
+	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{cy}}
+\end{equation}
+where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation.
+
+The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
+To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
+\begin{equation}\label{eq:BasisFunctionAtOrigin}
+ \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
+\end{equation}
+with the corresponding Fourier transform
+\begin{equation}\label{eq:GaussianFT}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation}
+where 
+\begin{equation}\label{eq:GaussianFTWidth}
+	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+To obtain a 3~dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
+\begin{equation}\label{eq:WidthCutOffRelationship}
+ \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2},
+\end{equation}
+where
+\begin{equation}\label{eq:WidthFrequencyRelationship}
+ \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
+\end{equation}
+This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
+Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
+
+Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
+This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
+To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
+\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
+	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
+\end{equation}
+
+Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid.
+Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
+
+\subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
+The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
+At each iteration, the sequence of estimated state vectors is used to update the parameter set.
+The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
+The procedure stops when the parameters converge.
+The algorithm is initialised using a bounded random state vector sequence guaranteeing that the initial estimated parameter set forms a stable kernel.
+
+The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
+The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
+The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
+\begin{equation}\label{eq:sigmapoints1}
+	\mathcal X_{0}=\bar x 
+\end{equation}
+\begin{equation}
+	\mathcal X_{i}=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L 
+\end{equation}
+\begin{equation}\label{eq:sigmapoints2}
+	\mathcal X_{i}=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2 L 
+\end{equation}
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+The total number of sigma points is $2L+1$.
+The scaling parameter, $\lambda$, is defined as
+\begin{equation}\label{eq:sigmapoints3}
+	\lambda=\alpha^2( L+\kappa) - L, 
+\end{equation}
+where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
+
+The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
+\begin{equation}
+	\mathbf W_0^{(m)}=\frac{\lambda}{ L+\lambda} 
+\end{equation}
+\begin{equation}
+	\mathbf W_0^{(c)}=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) 
+\end{equation}
+\begin{equation}
+	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
+\end{equation}
+where the superscripts $m$ and $c$ stand for mean and covariance.
+Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
+The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
+To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, is also computed.
+A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
+It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
+Therefore, the additive form of the URTSS is used, instead of augmenting the state vector with the noise terms with the added benefit of reducing the dimension and the number of sigma points required in the algorithm.
+\begin{algorithm}
+	\begin{small}
+	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
+	\begin{algorithmic}[1] 
+		\State Forward initialisation 
+		\begin{equation*}
+		 \hat{\mathbf x}_0, \mathbf P_0 
+		\end{equation*}
+		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
+		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
+% 		\begin{small}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
+		\end{equation*}
+% 		\end{small}
+		calculate the predicted state and the predicted covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
+		\begin{equation*}
+			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
+		\end{equation*}
+		\State Backward initialisation 
+		\begin{equation*}
+			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
+		\end{equation*}
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
+		\end{equation*}
+		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
+		\end{equation*}
+		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
+		\begin{equation*}
+			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
+		\end{equation*}
+	\end{algorithmic}
+\end{small}
+\end{algorithm}
+
+Although the system is nonlinear, the parameters of the system are linear with respect to the state.
+This feature is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
+To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
+\begin{equation}
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+\end{equation}
+Now given a state estimate sequence from an iteration of the URTSS, we can write
+\begin{eqnarray*}
+	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
+	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
+	&\vdots& \\
+	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
+\end{eqnarray*}
+This can be written in the compact form
+\begin{equation}
+	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
+\end{equation}
+where
+\begin{small}
+\begin{equation*}
+	\mathbf Z=\left[
+	\begin{array}{cccc}
+		\mathbf x_{1}\\
+		\mathbf x_{2}\\
+		\vdots\\
+		\mathbf x_{T}
+	\end{array}
+	\right],\quad \mathbf X=\left[
+	\begin{array}{cccc}
+		\mathbf q(\mathbf x_0)& \mathbf x_{0}\\
+		\mathbf q(\mathbf x_1)& \mathbf x_{1}\\
+		\vdots & \vdots\\
+		\mathbf q(\mathbf x_{T-1})& \mathbf x_{T-1}
+	\end{array}
+	\right] 
+\end{equation*}
+\end{small}
+and
+\begin{small}
+\begin{equation*}
+\quad \mathcal W=\left[
+	\begin{array}{cc}
+		\boldsymbol{\theta} \\
+		\xi
+	\end{array}
+	\right],\quad \mathbf{e}=\left[
+	\begin{array}{cccc}
+		\mathbf e_0\\
+		\mathbf e_1\\
+		\vdots\\
+		\mathbf e_{T-1}
+	\end{array}
+	\right].
+\end{equation*}
+\end{small}
+Following this, the LS parameter estimates, $ \mathcal{\hat{W}}$, are
+\begin{equation}
+	\mathcal{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+\end{equation}
+
 % Results and Discussion can be combined.
@@
 
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Materials and Methods}
-
 % Do NOT remove this, even if you are not including acknowledgments
@@
 
-%\section*{References}
+% \section*{References}
 % The bibtex filename
-\bibliography{template}
+\bibliography{BrainIDE}
 

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added PLoS template and bst and started converting our paper, yay!
trying to add algorithm as a table

@@
    	\end{center}
-   	\caption{An example of a continuous one-dimensional continuous field decomposed by a finite number of basis functions scaled by the state vector.} 
+   	\caption{An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.} 
 	\label{fig:FieldDecomposition}
@@
 	$\alpha$& Determines the spread of sigma points\\
-	$\beta$& Priro knowledge of the sigma points distribution\\
+	$\beta$& Prior knowledge of the sigma points distribution\\
 	$\kappa$& Scaling parameter\\

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
trying to add algorithm as a table

@@
 
-Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see \cite{Deco2008,David2003} for recent reviews).
+Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008,David2003} for recent reviews).
 These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999,RENNIE2000}, epileptic seizure generation \cite{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \cite{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.
@@
 \end{equation}
-where $\boldsymbol{\psi}(r,r')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
 By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
@@
 % Results and Discussion can be combined.
-\section*{Results}
+\section*{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the methods described above.
+The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+All parameters for the model are given in Table~\ref{tab:Model Parameters}.
+Note that, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
+This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
+When generating the simulated data we assumed free boundary conditions for the neural field.
+An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(a).
+Figure~\ref{fig:experimental design}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
+The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
+\begin{table}\footnotesize
+\centering
+\begin{tabular}{ccl}
+	\hline\hline Symbol & Value & Units \\
+	\hline\hline
+	$\tau$ & 0.01 & s$^{-1}$\\
+	$f_{max}$ & 10 & spikes/s \\
+	$\varsigma$ & 0.8 & spike/mV\\
+	$v_0$ & 2 & mV\\
+	$\boldsymbol{\theta}$ & $\left[\begin{array}{ccc}
+	10 &-8 &0.5
+	\end{array}
+	\right]^{\top}$ & mV/spike\\
+	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & 1.8, 2.4, 6 & mm\\
+	$\sigma_{m},\Delta_{y}$&0.9, 1.5&mm\\
+	$\Sigma_{\epsilon}$ &$0.1 \times I_{N} $& mm$^2$ \\
+	$\sigma_{\gamma}$&1.3&mm\\
+	$\Delta$ & 0.5 & mm \\
+	$T_s$ & 1 & ms \\ 
+\hline\hline
+\end{tabular}
+\caption{Parameters for the neural field model that are used to generate synthetic data.}
+\label{tab:Model Parameters}
+\end{table}
+
+The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$.
+This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm.
+This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
+% \begin{figure}
+%    	\begin{center}
+%     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePy.pdf}} \\
+%     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
+%    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePSDPy.pdf}} \\
+%    	\end{center}
+%    	\caption{\textbf{a.} Example of the neural feld.
+\textbf{b.} Example of data generated by the full neural field model from the first 5 sensors.
+\textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
+% \label{fig:experimental design}
+% \end{figure}
+\subsection*{Spatial Frequency Analysis} 
+Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
+The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.
+This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
+% \begin{figure}
+% \centering
+% \subfigure[][]{\label{fig:FieldFFT}\includegraphics{./Graph/FFTTrueField.pdf}}
+% \subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
+% \caption{Spatial frequency analysis of the neural field.
+\textbf{a.} The average (over time) power in dB of the spatial frequency of the neural field.
+\textbf{b.} The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
+% \label{fig:FFTTrueEstimate}
+% \end{figure}
+The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
+The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
+The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
+Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
+Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
+This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
+% \begin{figure} 
+% 	\begin{center}
+% 		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
+% 		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
+% 		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
+% 	\end{center}
+% 	\caption{Spatial frequency analysis.
+The dashed line shows the cut-off frequency (-3 dB point).
+\textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
+The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
+\textbf{b.} The spatial frequency response of a one-dimensional model sensor.
+\textbf{c.} The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
+% \end{figure}
+
+\subsection*{State and Parameter Estimates} 
+\label{sec:state_and_param_results}
+To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where $100$ realisations of the data were generated.
+Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
+The initial state and parameters were unknown to the estimator.
+Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
+\begin{figure}
+        \centering
+\includegraphics{./Graph/convergence.pdf}
+\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
+All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
+\label{fig:ParametersConvergence}
+\end{figure}
+
+Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}.
+The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
+The biases show the percentage differences between the actual values and the mean parameter estimates.
+The mean estimates are in good concordance with the actual values.
+% It should be noted that when the excitatory connectivity parameters, $\hat\theta_0$ and $\hat\theta_2$, were under (or over) estimated, the inhibitory connectivity parameter, $\hat\theta_1$, tended to be over (or under) estimated.
+This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates.
+\begin{table}
+\centering
+\begin{tabular}{cccc}
+	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
+	\hline\hline
+ 	$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
+	$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
+	$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
+	$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
+	% $\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
+	% $\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
+\hline\hline
+\end{tabular}
+\caption{Actual parameter values compared to parameter estimates.}
+\label{tab:Parameters estimates}
+\end{table}
+% \begin{figure}
+%     \centering
+%     \subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
+%     \subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
+%     \subfigure[][]{\label{fig:theta1dis}\includegraphics{./Graph/theta1.pdf}}
+%     \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
+% \caption{Distribution of the parameter estimates over 100
+% realisations.
+The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
+\textbf{a.} The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+\textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
+% \label{fig:Parameters}
+% \end{figure}
+% \begin{figure}
+%     \centering
+% \subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
+% \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
+% \caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
+\textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
+\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
+In each case, the solid and dotted lines show the locations of the true and estimated ratios respectively.}
+% \label{fig:ParametersRatio}
+% \end{figure}
+The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
+The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
+
+\begin{figure}
+    \centering
+% \subfigure[][]{
+\includegraphics{./Graph/KernelEstimate.pdf}%}
+% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
+\caption{Cross-section of connectivity kernel estimate.
+The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
+\label{fig:KernelEstimates}
+\end{figure}
+The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space).
+The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
+At each time point the error is consistently around 0.5~mV, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV.
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
+The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
+It can be seen in Figure~\ref{fig:FieldEstimate}(b) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(a)), but is missing the higher-frequency detail.
+  \begin{figure}
+   	\begin{center}
+   		\includegraphics{./Graph/MRMSE.pdf} 
+   	\end{center}
+   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
+\label{fig:RMSE}
+   \end{figure}
+
+% \begin{figure}
+% \centering 
+% \subfigure[][]{\label{fig:TrueField}\includegraphics{./Graph/TrueField90.pdf}}
+% \subfigure[][]{\includegraphics{./Graph/EstimatedField90.pdf}}
+% \subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
+% \caption{Examples of the actual and estimated neural fields and the error.
+\textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data.
+\textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+\textbf{c.} The absolute error between the true and reconstructed fields.
+The error shows high frequency behaviour.}
+% \label{fig:FieldEstimate}
+% \end{figure}
 
@@
 
+\begin{table}[!ht]
+\caption{
+\bf{The Unscented RTS Smoother}}
+\begin{tabular}{|c|}
+\multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\
+$\hat{\mathbf x}_0, \mathbf P_0$ \\
+\multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
+$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$ \\
+\multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\end{tabular}
+\begin{flushleft}Table caption
+\end{flushleft}
+\label{tab:label}
+\end{table}
+
+\begin{algorithm}
+	\begin{small}
+	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
+	\begin{algorithmic}[1] 
+		\State Forward initialisation 
+		\begin{equation*}
+		 \hat{\mathbf x}_0, \mathbf P_0 
+		\end{equation*}
+		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
+		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
+% 		\begin{small}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
+		\end{equation*}
+% 		\end{small}
+		calculate the predicted state and the predicted covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
+		\begin{equation*}
+			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
+		\end{equation*}
+		\State Backward initialisation 
+		\begin{equation*}
+			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
+		\end{equation*}
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
+		\end{equation*}
+		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
+		\end{equation*}
+		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
+		\begin{equation*}
+			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
+		\end{equation*}
+	\end{algorithmic}
+\end{small}
+\end{algorithm}
+
 \end{document}

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
added discussion to new template

@@
 
-\subsection*{Subsection 1}
+\section*{Discussion}\label{DiscussionSection}
+This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+As seen in the Section~\ref{sec:state_and_param_results} the results indicate good estimation performance, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance, and the observations are corrupted by noise.
+To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
+Following such a paradigm, data can be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
 
-\subsection*{Subsection 2}
+Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
+Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
+A limitation of this framework lies in an increase in dimensionality with increases in the spatial resolution and in the physical size of the neural field.
+Increases in dimensionality lead to increases in uncertainty of the estimated state and problems associated with computational complexity.
+This paper builds on this previous study, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of a spatial discretisation and is governed by the inherent spatial properties of the field.
+The frequency analysis methods presented in Section~\ref{SpectralAnalysisSection} provide a rigorous framework for the placement and the number of the basis functions required for the decomposition.
+This enables estimation of a larger field, with a lower dimensional state vector.
+The basis function decomposition also enabled the coupling to be described by an inner product rather than a spatial convolution.
+This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
 
-\section*{Discussion}
+The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
+Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
+
+To the authors' best knowledge, this is the first paper derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
+
+The closest competitor to our `grey-box' integro-difference equation (IDE) based approach is perhaps the `black-box' multivariate auto-regressive (MVAR) model.
+Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
+A distinct advantage of the IDE-based technique proposed in this paper, is that the estimates of the connectivity structure are made independently of the number of sensors (assuming the field is sufficiently sampled).
+In addition, the number of parameters required to model the system is considerably less than a typical MVAR model.
+Furthermore, by using the neural field equations as a parametric form of the model, the parameters have physical meaning and therefore, can be clinically relevant.
+An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
+A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of a multi-scale connectivity structure in generating the characteristic rhythms of the brain.
+A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
+
+Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a patient-specific state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
+For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
+In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+
+Parameter estimation may also have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+
+The development of an estimation framework also has theoretical implications.
+The the ability to estimate parameters will allow testing of hypotheses that have been generated in theoretical studies.
+This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
+For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters and check if they correspond to theoretically derived parameters where certain solutions can exist.
+In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
+
+In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
+In future work, we plan to relax this assumption.
+We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
+In addition, we have assumed the neural field is isotropic and homogeneous.
+It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
+However, the assumption of homogeneity is quite strong.
+Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
+Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, and distant dependant propagation times into the parametric neural field equations.
+
+% This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields to create patient specific models.
+A basis function decomposition reduces the infinite dimensional neural field (continuous space) to a finite dimensional state-space model.
+The frequency analysis methods presented in this paper provide a systematic procedure for specifying the sensor and basis function arrangement required to describe the significant neuro-dynamics by the reduced neural field model.
+The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
+Using the state-space model, the unscented Rauch-Tung-Striebel smoother was applied for state estimation.
+Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
+We have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic dynamics using the proposed methodology.
 
@@
 \multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
-$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$ \\
+	$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
 \multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
@@
 $\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$
 \end{tabular}
@@
 		\end{equation*}
-		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations
 		\begin{equation*}

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
added appendices at the end of the results

@@
 	\mathcal{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+\end{equation}
+
+\subsection*{From Appendix: Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be performed.
+We used a one-step Euler method where equation~\ref{FinalFormContinuous} can be approximated by
+\begin{eqnarray}
+	\label{Euler Approximation} \lefteqn{\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =}\nonumber\\
+& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.\nonumber \\ 
+\end{eqnarray}
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation} we get 
+\begin{eqnarray}
+	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right)\nonumber \\
+&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.\nonumber \\ 
+\end{eqnarray}
+The discrete time form of the model is 
+\begin{equation}
+	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
+\end{equation}
+where $\xi = 1 - T_s \zeta$.
+
+\subsection{From Appendix: Mean and covariance of the state disturbance }\label{ColoredNoise} 
+The state disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$, therefore $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
+\begin{eqnarray}
+	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
+	&=&\mathbf 0.
+\end{eqnarray}
+The covariance of $\mathbf{e}_t$ is 
+\begin{eqnarray}
+	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
+&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
+\end{eqnarray}
+
+\subsection*{From Appendix: Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
+This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
+Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (defined in equation~\ref{eq:BasisFunctionAtOrigin}) yields
+\begin{eqnarray}\label{eq:AppendixGaussianFT}
+ \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathbb{R}^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
+&=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
+&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{eqnarray}
+Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+\begin{eqnarray}\label{eq:IntegralOfGaussian}
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
+\end{eqnarray}
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation} 
+where 
+\begin{equation}
+	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+
+For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
+\begin{eqnarray}
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
+\end{eqnarray}
+since the maximum of Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Now solving for $\sigma_{\nu}^2$ we get
+\begin{equation}
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
+\end{equation}
+
+\subsection*{From Appendix: Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
+In this appendix we provide derivation for the convolution of Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
+Consider two Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
+\begin{eqnarray}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{eqnarray}
+where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution is
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
+\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
+\end{equation}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$. 
+The analytic definition of the observation matrix, $C$, and the matrix $\boldsymbol\Psi(\mathbf{r})$ are formulated using this derivation.
+
+\section*{From Appendix: Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
+The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
+\begin{equation}\label{eq:InofGaussianDefinition}
+\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
+\end{equation}
+A Gaussian basis function is symmetric with respect to its centre, therefore
+\begin{equation}\label{eq:GaussianSymmetry}
+ \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
+ \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
+\begin{eqnarray}
+\varphi_i\otimes\varphi_j&=&\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
+&=&\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
+&=&(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
+\end{eqnarray}
+Evaluating equation~\ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
+\begin{equation}
+ \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
 \end{equation}

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
editing algorithm table

@@
 \begin{equation}
-	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
+	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \mathbf{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
 \end{equation}
@@
 \bf{The Unscented RTS Smoother}}
-\begin{tabular}{|c|}
+\begin{tabular}{|c|}\hline
 \multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\ 
+\\
 $\hat{\mathbf x}_0, \mathbf P_0$ \\
+\\
 \multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
+\\
 	$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
+	\\
 \multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
+\\
 $\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+\\
 $\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\\
 \multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$
+\\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$\\
+\\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
+\\
+$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
+\\\hline
+\multicolumn{1}{|p{16cm}|}{2. Backward initialisation}\\
+\\
+$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
+\\
+
 \end{tabular}

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
added experimental figure
edits

@@
 This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
-% \begin{figure}
-%    	\begin{center}
-%     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePy.pdf}} \\
-%     		\subfigure[][]{\includegraphics{./Graph/ExperimentFigureEEGPy.pdf}} \\
-%    		\subfigure[][]{\includegraphics{./Graph/ExperimentFigurePSDPy.pdf}} \\
-%    	\end{center}
-%    	\caption{\textbf{a.} Example of the neural feld.
+ \begin{figure}
+    	\begin{center}
+     		\includegraphics[scale=1]{./Graph/ExperimentalFigure.pdf}
+    	\end{center}
+    	\caption{\textbf{a.} Example of the neural feld.
 \textbf{b.} Example of data generated by the full neural field model from the first 5 sensors.
 \textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
-% \label{fig:experimental design}
-% \end{figure}
+ \label{fig:experimental design}
+ \end{figure}
 \subsection*{Spatial Frequency Analysis} 
@@
 \caption{
-\bf{The Unscented RTS Smoother}}
+\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
 \begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\ 
-\\
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
 $\hat{\mathbf x}_0, \mathbf P_0$ \\
-\\
-\multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
-\\
+\\ \hline
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
 $\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
 \\
-\multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
+\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
 \\
@@
 \multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-\\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$\\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
 \\
@@
 \\\hline
-\multicolumn{1}{|p{16cm}|}{2. Backward initialisation}\\
-\\
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
 $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
-\\
-
+\\\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
+$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
+\\
+\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
+\\
+$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
+\\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
+\\
+$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
+\\
+\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
+\\
+$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
+\\
+$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
+\\
+$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\\hline
 \end{tabular}
-\begin{flushleft}Table caption
+\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Smoothers smoother.
+The steps are iterated 11 times for our state estimation procedure and the least squares algorithm is run at the after each iteration.
 \end{flushleft}

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
edits to the tables

@@
 %\doublespacing
-
-% put this in temporarily
-\usepackage{algorithm, algorithmicx, algpseudocode}
 
@@
 To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, is also computed.
-A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
+A summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
 It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
 Therefore, the additive form of the URTSS is used, instead of augmenting the state vector with the noise terms with the added benefit of reducing the dimension and the number of sigma points required in the algorithm.
-\begin{algorithm}
-	\begin{small}
-	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
-	\begin{algorithmic}[1] 
-		\State Forward initialisation 
-		\begin{equation*}
-		 \hat{\mathbf x}_0, \mathbf P_0 
-		\end{equation*}
-		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
-% 		\begin{small}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
-		\end{equation*}
-% 		\end{small}
-		calculate the predicted state and the predicted covariance matrix
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
-		\begin{equation*}
-			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
-		\end{equation*}
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
-		\end{equation*}
-		\State Backward initialisation 
-		\begin{equation*}
-			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
-		\end{equation*}
-		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
-		\end{equation*}
-		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
-		\end{equation*}
-		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
-		\begin{equation*}
-			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
-		\end{equation*}
-		\begin{equation*}
-			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
-		\end{equation*}
-	\end{algorithmic}
-\end{small}
-\end{algorithm}
 
@@
 \caption{
+\bf{Notation and Parameters}}
+\begin{tabular}{|c|c|}
+	\hline
+\multicolumn{2}{|c|}{\textbf{Domain and indices}}\\
+\hline
+$\Omega$ & spatial domain \\
+$t$ & time (seconds) \\
+$\mathbf{r}$ & spatial location \\
+$n$ & sensor index $n=1,..,N$ \\
+$T$ & time step
+\end{tabular}
+\begin{flushleft}Table caption
+\end{flushleft}
+\label{tab:label}
+\end{table}
+
+% ~~~~~~~~~~~~~~~~~~~~
+\begin{table}[h!]\footnotesize
+    \begin{tabular}{ll}
+        $\Omega$ & spatial domain \\
+	    $t$ & time (seconds) \\
+    	$\mathbf{r}$ & spatial location \\
+	    $n$ & sensor index $n=1,..,N$ \\
+    	$T$ & time step
+    \end{tabular}
+    \caption{Domain and indices}
+\end{table}
+
+% \begin{table}[h!]\footnotesize
+%     \begin{tabular}{ll}
+%         $y(\mathbf{r}_n,t)$ & observation \\
+% 	    $v(\mathbf{r},t)$ & mean membrane potential \\
+%     	$g(\mathbf{r},t)$ & average action potential rate \\
+%     	$f(\mathbf{r},t)$ & firing function rate \\
+%     	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
+% 	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance$\Sigma_\epsilon$ \\
+%     \end{tabular}
+%     \caption{Spatiotemporal Signals}
+% \end{table}
+% 
+% \begin{table}[h!]\footnotesize
+%     \begin{tabular}{ll}
+%         	$h(t)$ & post-synaptic response kernel \\
+% 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
+% 	$\eta(t)$ & Heaviside function \\
+% 	$\zeta$ & inverse synaptic time constant \\
+% 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
+% 	$f_{max}$ & maximal firing rate \\
+% 	$\varsigma$ & slope of sigmoidal activation function \\
+% 	$v_0$ & firing threshold \\
+% 	$\delta(t)$ & Dirac-delta function \\
+% 	$D$ & Temporal differential operator \\
+% 	$\xi$ & time constant parameter
+%     \end{tabular}
+%     \caption{Model}
+% \end{table}
+% 
+% \begin{table}[h!]\footnotesize
+%     \begin{tabular}{ll}
+%         $L$ & number of field basis functions  \\
+%     	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
+%     	$\mathbf{x}_t$ & state vector at time $t$ \\
+%     	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
+%     	$\theta$ & vector of connectivity kernel parameters \\
+%     	$\Gamma$ & inner product of field basis functions \\
+%     	$q()$ & state function \\
+%     	$Q()$ & state function \\
+% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
+%     	$\mathbf{e}_t$ & state disturbance \\
+% 	$\Sigma_e$ &state disturbance covariance matrix\\
+% 	$\mathbf{\epsilon}_t$ & observation noise \\
+% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
+%     	$\mathbf{C}$ & observation matrix \\
+% 	$c_{ij}$& elements of observation matrix
+%     \end{tabular}
+%     \caption{Decomposition}
+% \end{table}
+% 
+% \begin{table}[h!]\footnotesize
+%     \begin{tabular}{rl}
+%         $V(\nu)$ & Spectrum of the dynamic field \\
+% 	$\nu$ & Spatial frequency \\
+% 	$\nu_c$ & Spatial cut-off frequency \\
+% 	$\Delta_y$ & Distance between adjacent sensors \\
+% 	$\rho$ & Over-sampling parameter \\
+% 	$\Delta_{\phi}$ & Distance between field basis functions \\
+% 	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
+% 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
+%     \end{tabular}
+%     \caption{Frequency Analysis}
+% \end{table}
+% 
+% \begin{table}[h!]\footnotesize
+%     \begin{tabular}{ll}
+%         $\hat{\mathbf{x}}$ & State estimate \\
+% 	$\chi$ & Matrix of sigma vectors \\
+% 	$\lambda$& Scaling parameter\\
+% 	$\alpha$& Determines the spread of sigma points\\
+% 	$\beta$& Prior knowledge of the sigma points distribution\\
+% 	$\kappa$& Scaling parameter\\
+% 	$W$& Sigma vecors weights\\
+%     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
+%     	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
+%     	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
+%     	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
+%     	$P^f_t$ & Forward posterior covariance matrix \\
+%     	$P^{f-}_t$ & Forward prior covariance matrix \\
+%     	$P^b_t$ & Backward posterior covariance matrix \\
+%     	$P^{b-}_t$ & Backward prior covariance matrix \\
+% 	$\mathcal K_{t} $& Filter gain\\
+% 	$M_t$& Cross-covariance matrix\\
+% 	$S_t$& Smoother gain
+%     \end{tabular}
+%     \caption{State Estimation}
+% \end{table}
+
+% ~~~~~~~~~~~~~~~~~~~
+\begin{table}[!ht]
+\caption{
 \bf{Steps in the Algorithm for the Unscented RTS Smoother}}
@@
 \end{tabular}
-\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Smoothers smoother.
-The steps are iterated 11 times for our state estimation procedure and the least squares algorithm is run at the after each iteration.
+\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
+The steps are iterated 11 times for our state estimation procedure.
+The least squares algorithm is run after each iteration to update the parameter estimates.
 \end{flushleft}
-\label{tab:label}
+\label{tab:UKFAlgorithm}
 \end{table}
 
-\begin{algorithm}
-	\begin{small}
-	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
-	\begin{algorithmic}[1] 
-		\State Forward initialisation 
-		\begin{equation*}
-		 \hat{\mathbf x}_0, \mathbf P_0 
-		\end{equation*}
-		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
-		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
-% 		\begin{small}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
-		\end{equation*}
-% 		\end{small}
-		calculate the predicted state and the predicted covariance matrix
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations
-		\begin{equation*}
-			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
-		\end{equation*}
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
-		\end{equation*}
-		\State Backward initialisation 
-		\begin{equation*}
-			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
-		\end{equation*}
-		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
-		\begin{equation*}
-			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
-		\end{equation*}
-		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
-		\begin{equation*}
-			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
-		\end{equation*}
-		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
-		\begin{equation*}
-			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
-		\end{equation*}
-		\begin{equation*}
-			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
-		\end{equation*}
-		\begin{equation*}
-			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
-		\end{equation*}
-	\end{algorithmic}
-\end{small}
-\end{algorithm}
-
 \end{document}

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
edits to the tables

@@
 \bf{Notation and Parameters}}
-\begin{tabular}{|c|c|}
+\begin{tabular}{|c|c|c|c|}
 	\hline
-\multicolumn{2}{|c|}{\textbf{Domain and indices}}\\
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
 	\hline
-$\Omega$ & spatial domain \\
-$t$ & time (seconds) \\
-$\mathbf{r}$ & spatial location \\
-$n$ & sensor index $n=1,..,N$ \\
-$T$ & time step
+\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
+\hline
+$\Omega$ & spatial domain & &\\
+$t$ & time & & seconds\\
+$\mathbf{r}$ & spatial location & &\\
+$n$ & sensor index $n=1,..,N$ & &\\
+$T_s$ & time step & $0.001$ & seconds\\
+$T$ & number of time steps & 0.4 & seconds\\
+\hline
+\multicolumn{4}{|c|}{\emph{Spatiotemporal signals}}\\
+\hline
+    $y(\mathbf{r}_n,t)$ & observation & & mV\\
+    $v(\mathbf{r},t)$ & mean membrane potential & & mV \\
+	$g(\mathbf{r},t)$ & weighted firing rate function & & \\
+	$f(\mathbf{r},t)$ & firing rate function & & spikes.s$^{-1}$\\
+	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
+	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\epsilon$) & &\\
 \end{tabular}
@@
 % ~~~~~~~~~~~~~~~~~~~~
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        $\Omega$ & spatial domain \\
-	    $t$ & time (seconds) \\
-    	$\mathbf{r}$ & spatial location \\
-	    $n$ & sensor index $n=1,..,N$ \\
-    	$T$ & time step
-    \end{tabular}
-    \caption{Domain and indices}
-\end{table}
-
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         $y(\mathbf{r}_n,t)$ & observation \\
-% 	    $v(\mathbf{r},t)$ & mean membrane potential \\
-%     	$g(\mathbf{r},t)$ & average action potential rate \\
-%     	$f(\mathbf{r},t)$ & firing function rate \\
-%     	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
-% 	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance$\Sigma_\epsilon$ \\
-%     \end{tabular}
-%     \caption{Spatiotemporal Signals}
-% \end{table}
+
 % 

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
updated tables

@@
 \bf{Notation and Parameters}}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|l|c|c|}
 	\hline
@@
 	$\Omega$ & spatial domain & &\\
-$t$ & time & & seconds\\
+	$\Delta$ & spatial discretisation step & 0.5 & mm \\
+	$t$ & time & & s\\
 	$\mathbf{r}$ & spatial location & &\\
 	$n$ & sensor index $n=1,..,N$ & &\\
-$T_s$ & time step & $0.001$ & seconds\\
-$T$ & number of time steps & 0.4 & seconds\\
+	$T_s$ & time step & $0.001$ & s\\
+	$T$ & number of time steps & 0.4 & s\\
 	\hline
@@
 	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\epsilon$) & &\\
+	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\varepsilon$) & &\\
+	\hline 
+\multicolumn{4}{|c|}{\emph{Model}}\\
+	\hline
+	$h(t)$ & post-synaptic response kernel & & mV\\
+	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
+	$\zeta$ & inverse synaptic time constant & & s$^{-1}$\\
+	$\xi$ & time constant parameter & & \\
+	$\eta(t)$ & Heaviside step function & & \\
+	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel (width $\sigma_m^2$) & & \\
+	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & & \\
+	$f_{max}$ & maximal firing rate & & spikes.s$^{-1}$\\
+	$\varsigma$ & slope of sigmoidal activation function & & \\
+	$v_0$ & firing threshold & & mV \\
+	$\delta(t)$ & Dirac-delta function & & \\
+	$D$ & Temporal differential operator & &\\
+	$\boldsymbol{\theta}$ & & $\left[\begin{array}{ccc}
+	10 &-8 &0.5
+	\end{array}
+	\right]^{\top}$ & mV/spike\\
+	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & & 1.8, 2.4, 6 & mm\\
+	$\sigma_{m},\Delta_{y}$& & 0.9, 1.5 & mm\\
+	$\Sigma_{\varepsilon}$ & & $0.1 \times I_{N}$ & mm$^2$ \\
+	$\sigma_{\gamma}$& & 1.3 & mm\\
+	\hline
 \end{tabular}
@@
 
+% 	\hline
+% 	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
+% 	\hline
+%     $L$ & number of field basis functions & 81 & \\
+%    	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
+%    	$\mathbf{x}_t$ & state vector at time $t$ & & \\
+%    	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
+%    	$\theta$ & vector of connectivity kernel parameters & & \\
+%    	$\Gamma$ & inner product of field basis functions & &\\
+%    	$q()$ & state function & &\\
+%    	$Q()$ & state function & &\\
+% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
+%    	$\mathbf{e}_t$ & state disturbance & &\\
+% 	$\Sigma_e$ &state disturbance covariance matrix& &\\
+% 	$\mathbf{\epsilon}_t$ & observation noise & &\\
+% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix& &\\
+%    	$\mathbf{C}$ & observation matrix& & \\
+% 	$c_{ij}$& elements of observation matrix & & \\
+% 	\hline
+% \end{tabular}
+% \begin{flushleft}Table caption
+% \end{flushleft}
+% \label{tab:label}
+% \end{table}
+
+\begin{table}[!ht]
+\caption{
+\bf{Notation and Parameters - Part 2}}
+\begin{tabular}{|c|l|c|c|}
+	\hline
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
+	\hline
+	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
+	\hline
+    $L$ & number of field basis functions & 81 & \\
+   	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
+   	$\mathbf{x}_t$ & state vector at time $t$ & & \\
+   	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
+   	$\theta$ & vector of connectivity kernel parameters & & \\
+   	$\Gamma$ & inner product of field basis functions & &\\
+   	$q()$ & state function & &\\
+   	$Q()$ & state function & &\\
+	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
+   	$\mathbf{e}_t$ & state disturbance & &\\
+	$\Sigma_e$ &state disturbance covariance matrix& &\\
+	$\mathbf{\varepsilon}_t$ & observation noise & &\\
+	$\Sigma_{\varepsilon}$ &observation noise covariance matrix& &\\
+   	$\mathbf{C}$ & observation matrix& & \\
+	$c_{ij}$& elements of observation matrix & & \\
+	\hline
+	\multicolumn{4}{|c|}{\emph{Frequency Analysis}} \\
+	\hline
+    $V(\nu)$ & Spectrum of the dynamic field & &\\
+	$\nu$ & Spatial frequency & &\\
+	$\nu_c$ & Spatial cut-off frequency & &\\
+	$\Delta_y$ & Distance between adjacent sensors & &\\
+	$\rho$ & Over-sampling parameter & &\\
+	$\Delta_{\phi}$ & Distance between field basis functions & &\\
+	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function & &\\
+	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & &\\
+	\hline
+	\multicolumn{4}{|c|}{\emph{State Estimation}} \\
+	\hline
+	$\chi$ & Matrix of sigma vectors & &\\
+	$\lambda$& Scaling parameter & &\\
+	$\alpha$& Determines the spread of sigma points & &\\
+	$\beta$& Prior knowledge of the sigma points distribution & &\\
+	$\kappa$& Scaling parameter & & \\
+	$W$& Sigma vecors weights & & \\
+   	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate & & \\
+   	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate & & \\
+   	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate & & \\
+   	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate & & \\
+   	$P^f_t$ & Forward posterior covariance matrix & & \\
+   	$P^{f-}_t$ & Forward prior covariance matrix & & \\
+   	$P^b_t$ & Backward posterior covariance matrix & & \\
+   	$P^{b-}_t$ & Backward prior covariance matrix & & \\
+	$\mathcal K_{t} $& Filter gain & & \\
+	$M_t$& Cross-covariance matrix & & \\
+	$S_t$& Smoother gain & & \\	
+	\hline
+\end{tabular}
+\begin{flushleft}Table caption
+\end{flushleft}
+\label{tab:label}
+\end{table}
+
 % ~~~~~~~~~~~~~~~~~~~~
 
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         	$h(t)$ & post-synaptic response kernel \\
-% 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
-% 	$\eta(t)$ & Heaviside function \\
-% 	$\zeta$ & inverse synaptic time constant \\
-% 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
-% 	$f_{max}$ & maximal firing rate \\
-% 	$\varsigma$ & slope of sigmoidal activation function \\
-% 	$v_0$ & firing threshold \\
-% 	$\delta(t)$ & Dirac-delta function \\
-% 	$D$ & Temporal differential operator \\
-% 	$\xi$ & time constant parameter
-%     \end{tabular}
-%     \caption{Model}
-% \end{table}
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         $L$ & number of field basis functions  \\
-%     	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
-%     	$\mathbf{x}_t$ & state vector at time $t$ \\
-%     	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
-%     	$\theta$ & vector of connectivity kernel parameters \\
-%     	$\Gamma$ & inner product of field basis functions \\
-%     	$q()$ & state function \\
-%     	$Q()$ & state function \\
-% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
-%     	$\mathbf{e}_t$ & state disturbance \\
-% 	$\Sigma_e$ &state disturbance covariance matrix\\
-% 	$\mathbf{\epsilon}_t$ & observation noise \\
-% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
-%     	$\mathbf{C}$ & observation matrix \\
-% 	$c_{ij}$& elements of observation matrix
-%     \end{tabular}
-%     \caption{Decomposition}
-% \end{table}
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{rl}
-%         $V(\nu)$ & Spectrum of the dynamic field \\
-% 	$\nu$ & Spatial frequency \\
-% 	$\nu_c$ & Spatial cut-off frequency \\
-% 	$\Delta_y$ & Distance between adjacent sensors \\
-% 	$\rho$ & Over-sampling parameter \\
-% 	$\Delta_{\phi}$ & Distance between field basis functions \\
-% 	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
-% 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
-%     \end{tabular}
-%     \caption{Frequency Analysis}
-% \end{table}
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         $\hat{\mathbf{x}}$ & State estimate \\
-% 	$\chi$ & Matrix of sigma vectors \\
-% 	$\lambda$& Scaling parameter\\
-% 	$\alpha$& Determines the spread of sigma points\\
-% 	$\beta$& Prior knowledge of the sigma points distribution\\
-% 	$\kappa$& Scaling parameter\\
-% 	$W$& Sigma vecors weights\\
-%     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
-%     	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
-%     	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
-%     	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
-%     	$P^f_t$ & Forward posterior covariance matrix \\
-%     	$P^{f-}_t$ & Forward prior covariance matrix \\
-%     	$P^b_t$ & Backward posterior covariance matrix \\
-%     	$P^{b-}_t$ & Backward prior covariance matrix \\
-% 	$\mathcal K_{t} $& Filter gain\\
-% 	$M_t$& Cross-covariance matrix\\
-% 	$S_t$& Smoother gain
-%     \end{tabular}
-%     \caption{State Estimation}
-% \end{table}
+\begin{table}[h!]\footnotesize
+    \begin{tabular}{ll}
+        $\hat{\mathbf{x}}$ & State estimate \\
+	$\chi$ & Matrix of sigma vectors \\
+	$\lambda$& Scaling parameter\\
+	$\alpha$& Determines the spread of sigma points\\
+	$\beta$& Prior knowledge of the sigma points distribution\\
+	$\kappa$& Scaling parameter\\
+	$W$& Sigma vecors weights\\
+    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
+    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
+    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
+    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
+    	$P^f_t$ & Forward posterior covariance matrix \\
+    	$P^{f-}_t$ & Forward prior covariance matrix \\
+    	$P^b_t$ & Backward posterior covariance matrix \\
+    	$P^{b-}_t$ & Backward prior covariance matrix \\
+	$\mathcal K_{t} $& Filter gain\\
+	$M_t$& Cross-covariance matrix\\
+	$S_t$& Smoother gain
+    \end{tabular}
+    \caption{State Estimation}
+\end{table}
 

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
changes to the table

@@
 	\hline
+	$\hat{\mathbf{x}}$ & State estimate & & \\
     $L$ & number of field basis functions & 81 & \\
@@
 
-% ~~~~~~~~~~~~~~~~~~~~
-
-\begin{table}[h!]\footnotesize
-    \begin{tabular}{ll}
-        $\hat{\mathbf{x}}$ & State estimate \\
-	$\chi$ & Matrix of sigma vectors \\
-	$\lambda$& Scaling parameter\\
-	$\alpha$& Determines the spread of sigma points\\
-	$\beta$& Prior knowledge of the sigma points distribution\\
-	$\kappa$& Scaling parameter\\
-	$W$& Sigma vecors weights\\
-    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
-    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
-    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
-    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
-    	$P^f_t$ & Forward posterior covariance matrix \\
-    	$P^{f-}_t$ & Forward prior covariance matrix \\
-    	$P^b_t$ & Backward posterior covariance matrix \\
-    	$P^{b-}_t$ & Backward prior covariance matrix \\
-	$\mathcal K_{t} $& Filter gain\\
-	$M_t$& Cross-covariance matrix\\
-	$S_t$& Smoother gain
-    \end{tabular}
-    \caption{State Estimation}
-\end{table}
-
-% ~~~~~~~~~~~~~~~~~~~
 \begin{table}[!ht]

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
added pdf plots in the required format

--- 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
@@
 To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, is also computed.
-A summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
+A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}.
 It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
 Therefore, the additive form of the URTSS is used, instead of augmenting the state vector with the noise terms with the added benefit of reducing the dimension and the number of sigma points required in the algorithm.
+\begin{algorithm}
+	\begin{small}
+	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
+	\begin{algorithmic}[1] 
+		\State Forward initialisation 
+		\begin{equation*}
+		 \hat{\mathbf x}_0, \mathbf P_0 
+		\end{equation*}
+		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
+		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
+% 		\begin{small}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
+		\end{equation*}
+% 		\end{small}
+		calculate the predicted state and the predicted covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman Filter update equations
+		\begin{equation*}
+			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
+		\end{equation*}
+		\State Backward initialisation 
+		\begin{equation*}
+			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
+		\end{equation*}
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
+		\end{equation*}
+		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
+		\end{equation*}
+		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
+		\begin{equation*}
+			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
+		\end{equation*}
+	\end{algorithmic}
+\end{small}
+\end{algorithm}
 
@@
     	\begin{center}
-     		\includegraphics[scale=1]{./Graph/ExperimentalFigure.pdf}
+     		\includegraphics{./Graph/ExperimentalFigure.pdf}
     	\end{center}
@@
 This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
-% \begin{figure}
-% \centering
-% \subfigure[][]{\label{fig:FieldFFT}\includegraphics{./Graph/FFTTrueField.pdf}}
-% \subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics{./Graph/FFTEstimatedField.pdf}}\\
-% \caption{Spatial frequency analysis of the neural field.
+\begin{figure}
+\centering
+\label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
+\caption{Spatial frequency analysis of the neural field.
 \textbf{a.} The average (over time) power in dB of the spatial frequency of the neural field.
@@
 The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
-% \label{fig:FFTTrueEstimate}
-% \end{figure}
+\label{fig:FFTTrueEstimate}
+\end{figure}
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
@@
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
-% \begin{figure} 
-% 	\begin{center}
-% 		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
-% 		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
-% 		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
-% 	\end{center}
-% 	\caption{Spatial frequency analysis.
+\begin{figure} 
+	\begin{center}
+		\label{fig:ObservationFreqAnal}\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
+	\end{center}
+	\caption{Spatial frequency analysis.
 The dashed line shows the cut-off frequency (-3 dB point).
@@
 \textbf{c.} The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
-% \end{figure}
+\end{figure}
 
@@
 \end{table}
-% \begin{figure}
-%     \centering
-%     \subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
-%     \subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
-%     \subfigure[][]{\label{fig:theta1dis}\includegraphics{./Graph/theta1.pdf}}
-%     \subfigure[][]{\includegraphics{./Graph/theta2.pdf}}
-% \caption{Distribution of the parameter estimates over 100
-% realisations.
+\begin{figure}
+    \centering
+    \includegraphics{./Graph/ParametesDistributions.pdf}
+  \caption{Distribution of the parameter estimates over 100
+realisations.
 The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
@@
 \textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
-% \label{fig:Parameters}
-% \end{figure}
+\label{fig:Parameters}
+\end{figure}
 % \begin{figure}
@@
 
-% \begin{figure}
-% \centering 
-% \subfigure[][]{\label{fig:TrueField}\includegraphics{./Graph/TrueField90.pdf}}
-% \subfigure[][]{\includegraphics{./Graph/EstimatedField90.pdf}}
-% \subfigure[][]{\includegraphics{./Graph/EstimationError90.pdf}}\\
-% \caption{Examples of the actual and estimated neural fields and the error.
+\begin{figure}
+\centering 
+\label{fig:TrueField}\includegraphics{./Graph/FieldTrueEstimationError.pdf}
+\caption{Examples of the actual and estimated neural fields and the error.
 \textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data.
@@
 The error shows high frequency behaviour.}
-% \label{fig:FieldEstimate}
-% \end{figure}
+\label{fig:FieldEstimate}
+\end{figure}
 
@@
 \caption{
-\bf{Notation and Parameters}}
-\begin{tabular}{|c|c|c|c|}
-	\hline
-	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
-	\hline
-\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
-\hline
-$\Omega$ & spatial domain & &\\
-$t$ & time & & seconds\\
-$\mathbf{r}$ & spatial location & &\\
-$n$ & sensor index $n=1,..,N$ & &\\
-$T_s$ & time step & $0.001$ & seconds\\
-$T$ & number of time steps & 0.4 & seconds\\
-\hline
-\multicolumn{4}{|c|}{\emph{Spatiotemporal signals}}\\
-\hline
-    $y(\mathbf{r}_n,t)$ & observation & & mV\\
-    $v(\mathbf{r},t)$ & mean membrane potential & & mV \\
-	$g(\mathbf{r},t)$ & weighted firing rate function & & \\
-	$f(\mathbf{r},t)$ & firing rate function & & spikes.s$^{-1}$\\
-	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\epsilon$) & &\\
+\bf{The Unscented RTS Smoother}}
+\begin{tabular}{|c|}\hline
+\multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\ 
+\\
+$\hat{\mathbf x}_0, \mathbf P_0$ \\
+\\
+\multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
+\\
+	$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
+	\\
+\multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
+\\
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+\\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\\
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
+\\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$\\
+\\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
+\\
+$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
+\\\hline
+\multicolumn{1}{|p{16cm}|}{2. Backward initialisation}\\
+\\
+$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
+\\
+
 \end{tabular}
@@
 
-% ~~~~~~~~~~~~~~~~~~~~
-
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         	$h(t)$ & post-synaptic response kernel \\
-% 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
-% 	$\eta(t)$ & Heaviside function \\
-% 	$\zeta$ & inverse synaptic time constant \\
-% 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
-% 	$f_{max}$ & maximal firing rate \\
-% 	$\varsigma$ & slope of sigmoidal activation function \\
-% 	$v_0$ & firing threshold \\
-% 	$\delta(t)$ & Dirac-delta function \\
-% 	$D$ & Temporal differential operator \\
-% 	$\xi$ & time constant parameter
-%     \end{tabular}
-%     \caption{Model}
-% \end{table}
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         $L$ & number of field basis functions  \\
-%     	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
-%     	$\mathbf{x}_t$ & state vector at time $t$ \\
-%     	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
-%     	$\theta$ & vector of connectivity kernel parameters \\
-%     	$\Gamma$ & inner product of field basis functions \\
-%     	$q()$ & state function \\
-%     	$Q()$ & state function \\
-% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
-%     	$\mathbf{e}_t$ & state disturbance \\
-% 	$\Sigma_e$ &state disturbance covariance matrix\\
-% 	$\mathbf{\epsilon}_t$ & observation noise \\
-% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
-%     	$\mathbf{C}$ & observation matrix \\
-% 	$c_{ij}$& elements of observation matrix
-%     \end{tabular}
-%     \caption{Decomposition}
-% \end{table}
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{rl}
-%         $V(\nu)$ & Spectrum of the dynamic field \\
-% 	$\nu$ & Spatial frequency \\
-% 	$\nu_c$ & Spatial cut-off frequency \\
-% 	$\Delta_y$ & Distance between adjacent sensors \\
-% 	$\rho$ & Over-sampling parameter \\
-% 	$\Delta_{\phi}$ & Distance between field basis functions \\
-% 	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
-% 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
-%     \end{tabular}
-%     \caption{Frequency Analysis}
-% \end{table}
-% 
-% \begin{table}[h!]\footnotesize
-%     \begin{tabular}{ll}
-%         $\hat{\mathbf{x}}$ & State estimate \\
-% 	$\chi$ & Matrix of sigma vectors \\
-% 	$\lambda$& Scaling parameter\\
-% 	$\alpha$& Determines the spread of sigma points\\
-% 	$\beta$& Prior knowledge of the sigma points distribution\\
-% 	$\kappa$& Scaling parameter\\
-% 	$W$& Sigma vecors weights\\
-%     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
-%     	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
-%     	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
-%     	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
-%     	$P^f_t$ & Forward posterior covariance matrix \\
-%     	$P^{f-}_t$ & Forward prior covariance matrix \\
-%     	$P^b_t$ & Backward posterior covariance matrix \\
-%     	$P^{b-}_t$ & Backward prior covariance matrix \\
-% 	$\mathcal K_{t} $& Filter gain\\
-% 	$M_t$& Cross-covariance matrix\\
-% 	$S_t$& Smoother gain
-%     \end{tabular}
-%     \caption{State Estimation}
-% \end{table}
-
-% ~~~~~~~~~~~~~~~~~~~
-\begin{table}[!ht]
-\caption{
-\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
-\begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
-$\hat{\mathbf x}_0, \mathbf P_0$ \\
-\\ \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
-$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
-\\
-\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
-\\
-$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-\\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
-\\
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
-\\
-$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
-\\
-$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
-\\\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
-$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
-\\\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
-$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
-\\
-\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
-\\
-$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
-\\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
-\\
-$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
-\\
-\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
-\\
-$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
-\\
-$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
-\\
-$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\\hline
-\end{tabular}
-\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
-The steps are iterated 11 times for our state estimation procedure.
-The least squares algorithm is run after each iteration to update the parameter estimates.
-\end{flushleft}
-\label{tab:UKFAlgorithm}
-\end{table}
+\begin{algorithm}
+	\begin{small}
+	\caption{The Unscented RTS Smoother}\label{UKFAlgorithm} 
+	\begin{algorithmic}[1] 
+		\State Forward initialisation 
+		\begin{equation*}
+		 \hat{\mathbf x}_0, \mathbf P_0 
+		\end{equation*}
+		\State Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $,
+		calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}
+% 		\begin{small}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L
+		\end{equation*}
+% 		\end{small}
+		calculate the predicted state and the predicted covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations
+		\begin{equation*}
+			\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} 
+		\end{equation*}
+		\State Backward initialisation 
+		\begin{equation*}
+			\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T 
+		\end{equation*}
+		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}
+		\begin{equation*}
+			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L
+		\end{equation*}
+		 compute the predicted state, the predicted covariance matrix and the cross-covariance matrix
+		\begin{equation*}
+			\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-} 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top 
+		\end{equation*}
+		 Compute the smoother gain, the smoothed state and the smoothed covariance matrix
+		\begin{equation*}
+			\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} 
+		\end{equation*}
+		\begin{equation*}
+			\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
+		\end{equation*}
+		\begin{equation*}
+			\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 
+		\end{equation*}
+	\end{algorithmic}
+\end{small}
+\end{algorithm}
 

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
made the first line in captions bold

@@
    	\end{center}
-   	\caption{Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper.
+   	\caption{{\bf Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper}.
 The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
@@
    	\end{center}
-   	\caption{An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.} 
+   	\caption{{\bf An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector}.} 
 	\label{fig:FieldDecomposition}
@@
     	\end{center}
-    	\caption{\textbf{a.} Example of the neural feld.
-\textbf{b.} Example of data generated by the full neural field model from the first 5 sensors.
-\textbf{c.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
+    	\caption{{\bf \textbf{(A)} Example of the neural feld}.
+(\textbf{B}) Example of data generated by the full neural field model from the first 5 sensors.
+(\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
  \label{fig:experimental design}
@@
 \label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
-\caption{Spatial frequency analysis of the neural field.
-\textbf{a.} The average (over time) power in dB of the spatial frequency of the neural field.
-\textbf{b.} The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+\caption{{\bf Spatial frequency analysis of the neural field}.
+(\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
+(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
 The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
@@
 	\end{center}
-	\caption{Spatial frequency analysis.
+	\caption{{\bf Spatial frequency analysis}.
 The dashed line shows the cut-off frequency (-3 dB point).
-\textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
+(\textbf{A}) Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
 The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-\textbf{b.} The spatial frequency response of a one-dimensional model sensor.
-\textbf{c.} The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
+(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
+(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
 \end{figure}
@@
 \includegraphics{./Graph/convergence.pdf}
-\caption{The mean of the absolute error between true and estimated parameters averaged over 100 runs.
+\caption{{\bf The mean of the absolute error between true and estimated parameters averaged over 100 runs}.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
@@
     \includegraphics{./Graph/ParametesDistributions.pdf}
-  \caption{Distribution of the parameter estimates over 100
-realisations.
+  \caption{{\bf Distribution of the parameter estimates over 100
+realisations}.
 The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
-\textbf{a.} The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
-\textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-\textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+(\textbf{A}) The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+(\textbf{B}) The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(\textbf{C}) The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
 \textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
@@
 \includegraphics{./Graph/KernelEstimate.pdf}%}
-% \subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
-\caption{Cross-section of connectivity kernel estimate.
+\caption{{\bf Cross-section of connectivity kernel estimate}.
 The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
@@
    	\end{center}
-   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
+   	\caption{{\bf The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).}} 
 \label{fig:RMSE}
@@
 \label{fig:TrueField}\includegraphics{./Graph/FieldTrueEstimationError.pdf}
-\caption{Examples of the actual and estimated neural fields and the error.
-\textbf{a.} The actual field at a single time instant from the full neural field model that was used to generate data.
-\textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-\textbf{c.} The absolute error between the true and reconstructed fields.
+\caption{{\bf Examples of the actual and estimated neural fields and the error}.
+(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate data.
+(\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+(\textbf{C}) The absolute error between the true and reconstructed fields.
 The error shows high frequency behaviour.}

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
minor correction
minor paper edits and updated tables

@@
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations.
-Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with the WC neural field equations~\cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation of modified WC equations.
+Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with modified WC neural field equations~\cite{schiff2008kalman}.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatio-temporal neural fields.
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
@@
 The parameter $\varsigma$ governs the slope of the sigmoid.
-By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model
+By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatio-temporal model
 \begin{equation}
@@
 \begin{equation}\label{eq:FieldBasisFunction}
-	\phi\left(\mathbf{r}-\mathbf{r}'\right) =
+	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
 \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
@@
 \begin{equation}
-	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \mathbf{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
+	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
 \end{equation}
@@
 \end{eqnarray}
-This simplification has transformed the description of the spatial coupling from a convolution, to an inner product.
+This simplification has transformed the description of the spatial coupling from a convolution to an inner product.
 This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
@@
 Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
-Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, with $\boldsymbol{\nu}_{cy}$ replacing $\boldsymbol{\nu}_c$.
+Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, replacing $\boldsymbol{\nu}_c$ with $\boldsymbol{\nu}_{cy}$.
 
@@
 \end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix from the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 \end{equation}
-where the superscripts $m$ and $c$ stand for mean and covariance.
+where the superscripts $m$ and $c$ denote mean and covariance.
 Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
 The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
-To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, is also computed.
+The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain.
 A summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
 It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
-Therefore, the additive form of the URTSS is used, instead of augmenting the state vector with the noise terms with the added benefit of reducing the dimension and the number of sigma points required in the algorithm.
+Therefore, the additive form of the URTSS is used.
 
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This feature is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
@@
 % Results and Discussion can be combined.
-\section*{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the methods described above.
-The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{tab:Model Parameters}.
+\section*{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the new methods that are described above.
+The full neural field model described in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+All parameters for the model are given in Table~\ref{tab:Parameters}.
 Note that, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
@@
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
-\begin{table}\footnotesize
-\centering
-\begin{tabular}{ccl}
-	\hline\hline Symbol & Value & Units \\
-	\hline\hline
-	$\tau$ & 0.01 & s$^{-1}$\\
-	$f_{max}$ & 10 & spikes/s \\
-	$\varsigma$ & 0.8 & spike/mV\\
-	$v_0$ & 2 & mV\\
-	$\boldsymbol{\theta}$ & $\left[\begin{array}{ccc}
-	10 &-8 &0.5
-	\end{array}
-	\right]^{\top}$ & mV/spike\\
-	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & 1.8, 2.4, 6 & mm\\
-	$\sigma_{m},\Delta_{y}$&0.9, 1.5&mm\\
-	$\Sigma_{\epsilon}$ &$0.1 \times I_{N} $& mm$^2$ \\
-	$\sigma_{\gamma}$&1.3&mm\\
-	$\Delta$ & 0.5 & mm \\
-	$T_s$ & 1 & ms \\ 
-\hline\hline
-\end{tabular}
-\caption{Parameters for the neural field model that are used to generate synthetic data.}
-\label{tab:Model Parameters}
-\end{table}
 
@@
 This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates.
-\begin{table}
-\centering
-\begin{tabular}{cccc}
-	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
-	\hline\hline
- 	$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
-	$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
-	$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
-	$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
-	% $\mid\theta_0/\theta_1\mid$ &$1.25 $ & $1.189\pm 0.0812$ &$4.88$\\
-	% $\theta_0/\theta_2$ &$20$ & $18.567\pm3.757$ &$7.165$ \\
-\hline\hline
-\end{tabular}
-\caption{Actual parameter values compared to parameter estimates.}
-\label{tab:Parameters estimates}
-\end{table}
 \begin{figure}
@@
 (\textbf{C}) The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-\textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
+(\textbf{D}) The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
 \label{fig:Parameters}
@@
 % \end{figure}
-The reconstructed connectivity kernels from the estimated parameters are illustrated in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
+
+The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the $100$ realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
@@
 The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-At each time point the error is consistently around 0.5~mV, which approximately $7.1$~\% of the field voltage range, which is $(-3.29,3.77)$~mV.
-The error in the reconstructed field is mostly due to the loss of high spatial frequency information due to the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
+At each time point the error is consistently around 0.5~mV, which is approximately $7.1$~\% of the field voltage range ($[-3.29,3.77]$~mV).
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
@@
 Increases in dimensionality lead to increases in uncertainty of the estimated state and problems associated with computational complexity.
-This paper builds on this previous study, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of a spatial discretisation and is governed by the inherent spatial properties of the field.
-The frequency analysis methods presented in Section~\ref{SpectralAnalysisSection} provide a rigorous framework for the placement and the number of the basis functions required for the decomposition.
+This paper builds on this previous study, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of a spatial discretisation.
+and is governed by the .
+The frequency analysis methods presented in Section~\ref{SpectralAnalysisSection} provide a rigorous framework determining the dimensionality of the system using inherent spatial properties of the field.
 This enables estimation of a larger field, with a lower dimensional state vector.
@@
 
-To the authors' best knowledge, this is the first paper derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
+This is the first paper derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
@@
 This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters and check if they correspond to theoretically derived parameters where certain solutions can exist.
+For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions can exist.
 In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
@@
 \section*{Tables}
-%\begin{table}[!ht]
-%\caption{
-%\bf{Table title}}
-%\begin{tabular}{|c|c|c|}
-%table information
-%\end{tabular}
-%\begin{flushleft}Table caption
-%\end{flushleft}
-%\label{tab:label}
-% \end{table}
 
@@
 \caption{
-\bf{Notation and Parameters}}
+\bf{Parameters}}
 \begin{tabular}{|c|l|c|c|}
@@
 	\hline
-	$\Omega$ & spatial domain & &\\
 	$\Delta$ & spatial discretisation step & 0.5 & mm \\
-	$t$ & time & & s\\
-	$\mathbf{r}$ & spatial location & &\\
-	$n$ & sensor index $n=1,..,N$ & &\\
 	$T_s$ & time step & $0.001$ & s\\
-	$T$ & number of time steps & 0.4 & s\\
-	\hline
-	\multicolumn{4}{|c|}{\emph{Spatiotemporal signals}}\\
-	\hline
-    $y(\mathbf{r}_n,t)$ & observation & & mV\\
-    $v(\mathbf{r},t)$ & mean membrane potential & & mV \\
-	$g(\mathbf{r},t)$ & weighted firing rate function & & \\
-	$f(\mathbf{r},t)$ & firing rate function & & spikes.s$^{-1}$\\
-	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\varepsilon$) & &\\
+	$T$ & number of time steps used in estimation & 0.4 & s\\
 	\hline 
@@
 	\hline
-	$h(t)$ & post-synaptic response kernel & & mV\\
 	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
-	$\zeta$ & inverse synaptic time constant & & s$^{-1}$\\
-	$\xi$ & time constant parameter & & \\
-	$\eta(t)$ & Heaviside step function & & \\
-	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel (width $\sigma_m^2$) & & \\
-	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & & \\
-	$f_{max}$ & maximal firing rate & & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & & \\
-	$v_0$ & firing threshold & & mV \\
-	$\delta(t)$ & Dirac-delta function & & \\
-	$D$ & Temporal differential operator & &\\
-	$\boldsymbol{\theta}$ & & $\left[\begin{array}{ccc}
+	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
+	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\
+	$v_0$ & firing threshold & 2 & mV \\
+	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
 	10 &-8 &0.5
 	\end{array}
-	\right]^{\top}$ & mV/spike\\
-	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & & 1.8, 2.4, 6 & mm\\
-	$\sigma_{m},\Delta_{y}$& & 0.9, 1.5 & mm\\
-	$\Sigma_{\varepsilon}$ & & $0.1 \times I_{N}$ & mm$^2$ \\
-	$\sigma_{\gamma}$& & 1.3 & mm\\
+	\right]^{\top}$ & mV.spike$^{-1}$\\
+	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
+	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
+	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
+	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{N}$ & mm$^2$ \\
+	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
+	$\sigma_{\gamma,t}$ & disturbance temporal variance & 0.1 & mV$^2$ \\
+	\hline 
+	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
+	\hline
+	$\Delta_{\phi}$ & Distance between field basis functions & 2.5 & mm \\
+	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
+	\hline 
+	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
+	\hline
+	$\rho_y$ & Sensor over-sampling parameter & 1 & n.a.\\
+	$\rho_\phi$ & Field basis function over-sampling parameter & 1 & n.a.\\
+	\hline 
+	\multicolumn{4}{|c|}{\emph{Estimation}}\\
+	\hline
+	$\alpha$& Determines the spread of sigma points & 0.001 & n.a.\\
+	$\beta$& Prior knowledge of the sigma points distribution & 2 & n.a.\\
+	$\kappa$& Scaling parameter & $3-L$ & n.a.\\
 	\hline
 \end{tabular}
-\begin{flushleft}Table caption
+\begin{flushleft}Parameters for the neural field model, the model reduction, the frequency analysis and the estimation procedure.
 \end{flushleft}
-\label{tab:label}
+\label{tab:Parameters}
 \end{table}
-
-% 	\hline
-% 	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
-% 	\hline
-%     $L$ & number of field basis functions & 81 & \\
-%    	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
-%    	$\mathbf{x}_t$ & state vector at time $t$ & & \\
-%    	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
-%    	$\theta$ & vector of connectivity kernel parameters & & \\
-%    	$\Gamma$ & inner product of field basis functions & &\\
-%    	$q()$ & state function & &\\
-%    	$Q()$ & state function & &\\
-% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
-%    	$\mathbf{e}_t$ & state disturbance & &\\
-% 	$\Sigma_e$ &state disturbance covariance matrix& &\\
-% 	$\mathbf{\epsilon}_t$ & observation noise & &\\
-% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix& &\\
-%    	$\mathbf{C}$ & observation matrix& & \\
-% 	$c_{ij}$& elements of observation matrix & & \\
-% 	\hline
-% \end{tabular}
-% \begin{flushleft}Table caption
-% \end{flushleft}
-% \label{tab:label}
-% \end{table}
 
@@
 \caption{
-\bf{Notation and Parameters - Part 2}}
-\begin{tabular}{|c|l|c|c|}
-	\hline
-	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
-	\hline
-	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
-	\hline
-	$\hat{\mathbf{x}}$ & State estimate & & \\
-    $L$ & number of field basis functions & 81 & \\
-   	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
-   	$\mathbf{x}_t$ & state vector at time $t$ & & \\
-   	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
-   	$\theta$ & vector of connectivity kernel parameters & & \\
-   	$\Gamma$ & inner product of field basis functions & &\\
-   	$q()$ & state function & &\\
-   	$Q()$ & state function & &\\
-	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
-   	$\mathbf{e}_t$ & state disturbance & &\\
-	$\Sigma_e$ &state disturbance covariance matrix& &\\
-	$\mathbf{\varepsilon}_t$ & observation noise & &\\
-	$\Sigma_{\varepsilon}$ &observation noise covariance matrix& &\\
-   	$\mathbf{C}$ & observation matrix& & \\
-	$c_{ij}$& elements of observation matrix & & \\
-	\hline
-	\multicolumn{4}{|c|}{\emph{Frequency Analysis}} \\
-	\hline
-    $V(\nu)$ & Spectrum of the dynamic field & &\\
-	$\nu$ & Spatial frequency & &\\
-	$\nu_c$ & Spatial cut-off frequency & &\\
-	$\Delta_y$ & Distance between adjacent sensors & &\\
-	$\rho$ & Over-sampling parameter & &\\
-	$\Delta_{\phi}$ & Distance between field basis functions & &\\
-	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function & &\\
-	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & &\\
-	\hline
-	\multicolumn{4}{|c|}{\emph{State Estimation}} \\
-	\hline
-	$\chi$ & Matrix of sigma vectors & &\\
-	$\lambda$& Scaling parameter & &\\
-	$\alpha$& Determines the spread of sigma points & &\\
-	$\beta$& Prior knowledge of the sigma points distribution & &\\
-	$\kappa$& Scaling parameter & & \\
-	$W$& Sigma vecors weights & & \\
-   	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate & & \\
-   	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate & & \\
-   	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate & & \\
-   	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate & & \\
-   	$P^f_t$ & Forward posterior covariance matrix & & \\
-   	$P^{f-}_t$ & Forward prior covariance matrix & & \\
-   	$P^b_t$ & Backward posterior covariance matrix & & \\
-   	$P^{b-}_t$ & Backward prior covariance matrix & & \\
-	$\mathcal K_{t} $& Filter gain & & \\
-	$M_t$& Cross-covariance matrix & & \\
-	$S_t$& Smoother gain & & \\	
+\bf{Notation}}
+\begin{tabular}{|c|l|c|}
+	\hline
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
+	\hline
+	$\Omega$ & spatial domain &\\
+	$\mathbf{r}$ & spatial location & [mm, mm]\\
+	$t$ & time & s\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Model}}\\
+	\hline
+    $y(\mathbf{r}_n,t)$ & observation & mV\\
+    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
+	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
+	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
+	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
+	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
+	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
+	$h(t)$ & post-synaptic response kernel & mV\\
+	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
+	$\xi$ & time constant parameter & n.a.\\
+	$\eta(t)$ & Heaviside step function & n.a.\\
+	$\delta(t)$ & Dirac-delta function & n.a.\\
+	$D$ & temporal differential operator & n.a.\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
+	\hline
+   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
+   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
+   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
+   	$\Gamma$ & inner product of field basis functions & n.a.\\
+   	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
+   	$Q()$ & state transition function &\\
+   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
+   	$\mathbf{C}$ & observation matrix & n.a. \\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
+	\hline
+    $V(\nu)$ & Fourier transform of the neural field & Hz\\
+	$\nu$ & Spatial frequency & Hz \\
+	$\nu_c$ & Field spatial cut-off frequency & Hz\\
+	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Estimation}} \\
+	\hline
+	$\mathcal{X}$ & matrix of sigma vectors & mV\\
+	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
+   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
+   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
+ 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
+   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
+	$M_t$& cross-covariance matrix & mV$^2$\\
+	$\mathcal K_{t} $ & filter gain & n.a.\\
+	$S_t$ & smoother gain & n.a.\\	
 	\hline
 \end{tabular}
-\begin{flushleft}Table caption
+\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper.
+The second column provides a brief description of the quantity, and the third column provide the relevant SI unit where appropriate.
 \end{flushleft}
@@
 
+\begin{table}[!ht]
+\caption{
+\bf{Estimation Results}}
+\begin{tabular}{|c|ccc|}	
+\hline\hline 
+Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
+\hline\hline
+$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
+$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
+$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
+$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
+\hline
+\end{tabular}
+\begin{flushleft}Actual parameter values compared to mean parameter estimates.
+\end{flushleft}
+\label{tab:Parameters estimates}
+\end{table}
+
 \end{document}

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
some table edits
some general edits

@@
 % Leave date blank
-\date{}
+% \date{}
 
@@
    	\end{center}
-   	\caption{{\bf Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$, used in this paper}.
+   	\caption{{\bf Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$}.
 The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
@@
    	\end{center}
-   	\caption{{\bf An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector}.} 
+   	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.} 
 	\label{fig:FieldDecomposition}
@@
 
-\subsection*{From Appendix: Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretisation must be performed.
-We used a one-step Euler method where equation~\ref{FinalFormContinuous} can be approximated by
-\begin{eqnarray}
-	\label{Euler Approximation} \lefteqn{\frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =}\nonumber\\
-& -&\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.\nonumber \\ 
-\end{eqnarray}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation} we get 
-\begin{eqnarray}
-	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) &=& v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right)\nonumber \\
-&+& T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.\nonumber \\ 
-\end{eqnarray}
-The discrete time form of the model is 
-\begin{equation}
-	\label{Discrete Time Model1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
-\end{equation}
-where $\xi = 1 - T_s \zeta$.
-
-\subsection{From Appendix: Mean and covariance of the state disturbance }\label{ColoredNoise} 
-The state disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$, therefore $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
-\begin{eqnarray}
-	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
-	&=&\mathbf 0.
-\end{eqnarray}
-The covariance of $\mathbf{e}_t$ is 
-\begin{eqnarray}
-	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{eqnarray}
-
-\subsection*{From Appendix: Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
-This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
-Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (defined in equation~\ref{eq:BasisFunctionAtOrigin}) yields
-\begin{eqnarray}\label{eq:AppendixGaussianFT}
- \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathbb{R}^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
-&=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
-&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{eqnarray}
-Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{eqnarray}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
-\end{eqnarray}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation} 
-where 
-\begin{equation}
-	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-
-For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{eqnarray}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{eqnarray}
-since the maximum of Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Now solving for $\sigma_{\nu}^2$ we get
-\begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
-\end{equation}
-
-\subsection*{From Appendix: Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this appendix we provide derivation for the convolution of Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
-\begin{eqnarray}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{eqnarray}
-where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution is
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
-\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
-\end{equation}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$. 
-The analytic definition of the observation matrix, $C$, and the matrix $\boldsymbol\Psi(\mathbf{r})$ are formulated using this derivation.
-
-\section*{From Appendix: Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
-The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
-\begin{equation}\label{eq:InofGaussianDefinition}
-\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
-\end{equation}
-A Gaussian basis function is symmetric with respect to its centre, therefore
-\begin{equation}\label{eq:GaussianSymmetry}
- \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
-\begin{eqnarray}
-\varphi_i\otimes\varphi_j&=&\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
-&=&\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
-&=&(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
-\end{eqnarray}
-Evaluating equation~\ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}
- \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
-\end{equation}
-
 % Results and Discussion can be combined.
@@
     	\end{center}
-    	\caption{{\bf \textbf{(A)} Example of the neural feld}.
+    	\caption{{\bf \textbf{(A)} Example of the neural field}.
 (\textbf{B}) Example of data generated by the full neural field model from the first 5 sensors.
@@
 \bf{Parameters}}
-\begin{tabular}{|c|l|c|c|}
+\begin{tabular}{|c|l|c|l|}
 	\hline
@@
 \bf{Notation}}
-\begin{tabular}{|c|l|c|}
+\begin{tabular}{|c|l|l|}
 	\hline
@@
 	\hline
-	$\Omega$ & spatial domain &\\
+	$\Omega$ & spatial domain & n.a.\\
 	$\mathbf{r}$ & spatial location & [mm, mm]\\
@@
 
+\renewcommand{\arraystretch}{1.8}
 \begin{table}[!ht]
@@
 $\hat{\mathbf x}_0, \mathbf P_0$ \\
-\\ \hline
+\hline
 \multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
 $\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
-\\
 \multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
-\\
 $\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-\\
 $\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
-\\
 \multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
 $\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
-\\
 $\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
-\\
 $\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
-\\\hline
+\hline
 \multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
 $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
-\\\hline
+\hline
 \multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
 $\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
-\\
 \multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
-\\
 $\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
-\\
 $\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
-\\
 $\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
-\\
 \multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
-\\
 $\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
-\\
 $\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
-\\
-$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\\hline
+$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
+\hline
 \end{tabular}
@@
 
+\renewcommand{\arraystretch}{1}
 \begin{table}[!ht]

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
edits to figure captions

@@
 \\
-Dean R. Freestone$^{1,2,3}$, 
+Dean R. Freestone$^{1,2,3,\ast}$, 
 Parham Aram$^{4}$, 
-Michael Dewar$^{5,\ast}$,
-Kenneth Scerri$^{6,\ast}$,
-David B. Grayden$^{1,\ast}$,
+Michael Dewar$^{5}$,
+Kenneth Scerri$^{6}$,
+David B. Grayden$^{1}$,
 Visakan Kadirkamanathan$^{4}$
@@
     	\end{center}
-    	\caption{{\bf \textbf{(A)} Example of the neural field}.
+    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} Example of the neural field at a single time instant.
 (\textbf{B}) Example of data generated by the full neural field model from the first 5 sensors.
@@
 Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FieldFFT} shows the spatial frequency of the neural field.
+Figure~\ref{fig:FFTTrueEstimate}(a) shows the spatial frequency of the neural field.
 The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point).
@@
 \end{figure}
-The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}.
+The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(c).
 The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:SensorFunctionFreqResponse}.
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(a).
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
-\begin{figure} 
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(b).
+The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(b).
+This figure illustrates the band-limiting effect of the basis function decomposition.
+\begin{figure}[!ht] 
 	\begin{center}
-		\label{fig:ObservationFreqAnal}\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
+		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
 	\end{center}
@@
 (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
+	\label{fig:ObservationFreqAnal}
 \end{figure}
+
+%\begin{figure}[!ht]
+%\begin{center}
+%%\includegraphics[width=4in]{figure_name.2.eps}
+%\end{center}
+%\caption{
+%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
+%should be left justified, as specified by the options to the caption 
+%package.
+%}
+%\label{Figure_label}
+%\end{figure}
 
@@
 \includegraphics{./Graph/convergence.pdf}
-\caption{{\bf The mean of the absolute error between true and estimated parameters averaged over 100 runs}.
+\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 100 runs.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
edits to figure captions

@@
    	\end{center}
-   	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.} 
+   	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
+The dashed line depicts the field and the solid lines show the Gaussian basis functions.}
 	\label{fig:FieldDecomposition}
@@
 When generating the simulated data we assumed free boundary conditions for the neural field.
-An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(a).
-Figure~\ref{fig:experimental design}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series.
+An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(A).
+Figure~\ref{fig:experimental design}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(C) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FFTTrueEstimate}(a) shows the spatial frequency of the neural field.
+Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field.
 The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point).
@@
 \end{figure}
-The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(c).
+The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C).
 The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(a).
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A).
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(b).
-The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(b).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B).
+The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B).
 This figure illustrates the band-limiting effect of the basis function decomposition.
@@
     \includegraphics{./Graph/ParametesDistributions.pdf}
-  \caption{{\bf Distribution of the parameter estimates over 100
+  \caption{{\bf Histograms of the parameter estimates over 100
 realisations}.
 The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
-(\textbf{A}) The distribution of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
-(\textbf{B}) The distribution of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(\textbf{C}) The distribution of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-(\textbf{D}) The distribution of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
+(\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+(\textbf{B}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(\textbf{C}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+(\textbf{D}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
 \label{fig:Parameters}
@@
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:theta1dis}.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
 
@@
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:FieldEstimate}(b) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(a)), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
   \begin{figure}

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
small edits to paper

@@
 \end{figure}
+
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C).
@@
    	\end{center}
-   	\caption{{\bf The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).}} 
+   	\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
 \label{fig:RMSE}
@@
 \bf{Notation}}
-\begin{tabular}{|c|l|l|}
+\begin{tabular}{|l|l|l|}
 	\hline
@@
 	\hline
-    $V(\nu)$ & Fourier transform of the neural field & Hz\\
+    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
 	$\nu$ & Spatial frequency & Hz \\
@@
 
-\renewcommand{\arraystretch}{1.8}
+\renewcommand{\arraystretch}{1.7}
 \begin{table}[!ht]

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
added LS notation to table

@@
    	$\Gamma$ & inner product of field basis functions & n.a.\\
-   	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
    	$Q()$ & state transition function &\\
@@
     % $V(\nu)$ & Fourier transform of the neural field & Hz\\
-	$\nu$ & Spatial frequency & Hz \\
-	$\nu_c$ & Field spatial cut-off frequency & Hz\\
+	$\nu$, $\nu_c$ & spatial frequency and spatial cut-off frequency & Hz \\
 	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
@@
 	$S_t$ & smoother gain & n.a.\\
+	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
+   	$\mathcal{\hat{W}}$& vector of parameter estimates (used in LS estimator) & n.a.\\	
 	\hline
@@
 \begin{flushleft}The first column of the table gives the symbols for all the notation used the paper.
-The second column provides a brief description of the quantity, and the third column provide the relevant SI unit where appropriate.
+The second column provides a brief description of the quantity, and the third column provide the relevant SI units.
 \end{flushleft}

### 2010-06-24 ltx/PLoS/SupportingInformation.tex
added support information document

%
%  untitled
%
%  Created by Dean Freestone on 2010-06-24.
%  Copyright (c) 2010 . All rights reserved.
%
\documentclass[]{article}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}

% Setup for fullpage use
\usepackage{fullpage}

% Uncomment some of the following if you use the features
%
% Running Headers and footers
%\usepackage{fancyhdr}

% Multipart figures
%\usepackage{subfigure}

% More symbols
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{latexsym}

% Surround parts of graphics with box
\usepackage{boxedminipage}

% Package for including code in the document
\usepackage{listings}

% If you want to generate a toc for each chapter (use with book)
\usepackage{minitoc}

% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\title{S1: Extended Derivations}
\author{Dean R. Freestone$^{1,2,3}$, 
Parham Aram$^{4}$, 
Michael Dewar$^{5,\ast}$,\\
Kenneth Scerri$^{6,\ast}$,
David B. Grayden$^{1,\ast}$,
Visakan Kadirkamanathan$^{4}$}

\begin{document}

\ifpdf
\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
\else
\DeclareGraphicsExtensions{.eps, .jpg}
\fi

\maketitle

\begin{flushleft}

\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
\\
\bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
\\
\bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
\\
\bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
\\
\bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
\\
\bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta
\\
$\ast$ E-mail: dfreestone@bionicear.org
\end{flushleft}

\section*{Time Discretisation of Neural Field Model}\label{Time Discretization} To form the IDE neural field model a 
time discretisation must be performed. We used a one-step Euler method where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{equation}
	\label{Euler Approximation}\tag{S1.1} \frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =-\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{equation}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation} we get 
\begin{equation}
	\label{Euler Approximation2}\tag{S1.2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
The discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}\tag{S1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.

\section*{Mean and Covariance of the State Disturbance }\label{ColoredNoise} 
The state disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$, therefore $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
\begin{eqnarray}
	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
	&=&\mathbf 0.
\end{eqnarray}
The covariance of $\mathbf{e}_t$ is 
\begin{eqnarray}
	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
\end{eqnarray}

\section*{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text). Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (defined in equation~\ref{eq:BasisFunctionAtOrigin}) yields
\begin{eqnarray}\label{eq:AppendixGaussianFT}
 \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathbb{R}^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
&=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
\end{eqnarray}
Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
\begin{eqnarray}\label{eq:IntegralOfGaussian}
\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
\end{eqnarray}
Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
\begin{equation}\label{eq:FTofGaussian}
\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
\end{equation} 
where 
\begin{equation}
	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
\end{equation}

For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
\begin{eqnarray}
 \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
\end{eqnarray}
since the maximum of Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Now solving for $\sigma_{\nu}^2$ we get
\begin{equation}
 \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
\end{equation}

\section*{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
In this appendix we provide derivation for the convolution of Gaussian basis functions. This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$. Consider two Gaussian basis functions
\begin{equation}\label{eq:n_dimensional_Gaussian1}
 \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
\end{equation}
and 
\begin{equation}\label{eq:n_dimensional_Gaussian2}
\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
\end{equation}
The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$). The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms. Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
\begin{eqnarray}
\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
\end{eqnarray}
where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution is
\begin{equation}\label{eq:ConvoftwoGaussian}
 \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
\end{equation}
In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
 \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
\end{equation}
where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$. 
The analytic definition of the observation matrix, $C$, and the matrix $\boldsymbol\Psi(\mathbf{r})$ are formulated using this derivation.

\section*{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
\begin{equation}\label{eq:InofGaussianDefinition}
\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
\end{equation}
A Gaussian basis function is symmetric with respect to its centre, therefore
\begin{equation}\label{eq:GaussianSymmetry}
 \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
\end{equation}
Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
 \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
\end{equation}
Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
\begin{eqnarray}
\varphi_i\otimes\varphi_j&=&\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
&=&(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
\end{eqnarray}
Evaluating equation~\ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
\begin{equation}
 \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
\end{equation}

\bibliographystyle{plain}
\bibliography{}
\end{document}

### 2010-06-24 ltx/PLoS/SupportingInformation.tex
edits to support material

@@
 \end{equation}
-The discrete time form of the model is 
+Now making simplifications, the discrete time form of the model is 
 \begin{equation}
-	\label{Discrete Time Model1}\tag{S1} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
+	\label{Discrete Time Model1}\tag{S1.3} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
 \end{equation}
@@
 \section*{Mean and Covariance of the State Disturbance }\label{ColoredNoise} 
-The state disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$, therefore $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 
-\begin{eqnarray}
-	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\
-	&=&\mathbf 0.
-\end{eqnarray}
+In this section we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(0,\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
+Therefore, $\mathbf{e}_t$ is also normally distributed.
+From equation~\ref{} the state disturbance vector is defined as
+\begin{equation} \tag{S1.4}
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
+\end{equation}
+The expected value of $\mathbf e_t$ is given by 
+\begin{equation}\tag{S1.5}
+	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
+\end{equation}
 The covariance of $\mathbf{e}_t$ is 
-\begin{eqnarray}
-	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=&\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{eqnarray}
+\begin{align}
+	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
+&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.\tag{S1.6}
+\end{align}
 

### 2010-06-24 ltx/PLoS/SupportingInformation.tex
further edits to support material

@@
 \section*{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
-This Appendix provides the derivation of the field basis function cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
-Applying the \textit{n}-dimensional Fourier transform \cite{Arsac1966} to a \textit{n}-dimensional Gaussian centred at the origin (defined in equation~\ref{eq:BasisFunctionAtOrigin}) yields
-\begin{eqnarray}\label{eq:AppendixGaussianFT}
- \lefteqn{\boldsymbol\Phi(\boldsymbol \nu)=\int_{\mathbb{R}^n}{\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r}} \nonumber \\
-&=&\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\
-&\times& \mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{eqnarray}
-Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{eqnarray}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r&& \nonumber \\
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.&&
-\end{eqnarray}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
+This section gives the derivation for the field basis function spatial cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
+For we define an \textit{n}-dimensional Gaussian  centred at the origin as
+\begin{equation}\tag{S1.7}
+ \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma^2}\mathbf r^\top\mathbf r\right).
+\end{equation}
+Now applying the \textit{n}-dimensional Fourier transform~\cite{Arsac1966} yields
+\begin{align}\label{eq:AppendixGaussianFT}
+ \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).\tag{S1.8}
+\end{align}
+Now evaluating the integral on the RHS of equation~S1.8 gives 
+\begin{equation}\label{eq:IntegralOfGaussian}\tag{S1.9}
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
+\end{equation}
+Substituting equation~S1.9 into equation~S1.8 gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}\tag{S1.10}
 \boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
@@
 where 
-\begin{equation}
+\begin{equation}\tag{S1.11}
 	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
 \end{equation}
-
 For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{eqnarray}
+\begin{equation}\tag{S1.12}
  \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{eqnarray}
-since the maximum of Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Now solving for $\sigma_{\nu}^2$ we get
-\begin{equation}
+\end{equation}
+since the maximum of Gaussian described in equation~S1.10 is at the origin. Now solving for $\sigma_{\nu}^2$ we get
+\begin{equation}\tag{S1.13}
  \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.

### 2010-06-24 ltx/PLoS/SupportingInformation.tex
more edit to supporting material (just need to add equation numbers from main text)

@@
 \section*{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this appendix we provide derivation for the convolution of Gaussian basis functions.
+In this section we provide derivation for the convolution of two $n$-dimensional Gaussian basis functions.
 This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
 Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
+\begin{equation}\label{eq:n_dimensional_Gaussian1}\tag{S1.14}
  \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
@@
 and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\begin{equation}\label{eq:n_dimensional_Gaussian2}\tag{S1.15}
 \varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
@@
 The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of \ref{ap:FrequencyAnalysis} we have
-\begin{eqnarray}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times& (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{eqnarray}
-where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution is
-\begin{equation}\label{eq:ConvoftwoGaussian}
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section we have
+\begin{equation}\tag{S1.16}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}\tag{S1.17}
  \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
 \end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation \ref{eq:ConvoftwoGaussian} becomes
-\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right).
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation~S1.17 becomes
+\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}\tag{S1.18}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
 \end{equation}
 where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
-The analytic definition of the observation matrix, $C$, and the matrix $\boldsymbol\Psi(\mathbf{r})$ are formulated using this derivation.
 
 \section*{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
+The derivation in this section was used for calculating the matrix $\Gamma$, from equation~\ref{} in the main text.
 The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
-\begin{equation}\label{eq:InofGaussianDefinition}
+\begin{equation}\label{eq:InofGaussianDefinition}\tag{S1.18}
 \varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
@@
 A Gaussian basis function is symmetric with respect to its centre, therefore
-\begin{equation}\label{eq:GaussianSymmetry}
+\begin{equation}\label{eq:GaussianSymmetry}\tag{S1.19}
  \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
 \end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~S1.19 becomes
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}\tag{S1.20}
  \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
 \end{equation}
-Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
-\begin{eqnarray}
-\varphi_i\otimes\varphi_j&=&\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
-&=&\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
-&=&(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
-\end{eqnarray}
-Evaluating equation~\ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}
+Now substituting equation~S1.20 into equation~S1.18 gives 
+\begin{align}
+\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).\tag{S1.21}
+\end{align}
+Evaluating derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
+\begin{equation}\tag{S1.22}
  \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
 \end{equation}
-
+This completes the derivation.
 \bibliographystyle{plain}

### 2010-06-24 ltx/PLoS/SupportingInformation.tex
maybe finished supporting material (i hope)

@@
 \fi
-\title{S1: Extended Derivations}
+\title{S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
 \author{Dean R. Freestone$^{1,2,3}$, 
@@
 \section*{Time Discretisation of Neural Field Model}\label{Time Discretization} To form the IDE neural field model a 
-time discretisation must be performed. We used a one-step Euler method where equation~\ref{FinalFormContinuous} can be approximated by 
+time discretisation must be performed. To do this we used a one-step Euler method, where equation~7 of the main text can be approximated by 
 \begin{equation}
@@
 \end{equation}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation} we get 
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1 we get 
 \begin{equation}
@@
 Therefore, $\mathbf{e}_t$ is also normally distributed.
-From equation~\ref{} the state disturbance vector is defined as
+From equation~21 of the main text, the state disturbance vector is defined as
 \begin{equation} \tag{S1.4}
@@
 \section*{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
-This section gives the derivation for the field basis function spatial cut-off frequency as a function of the basis function width (equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} in the main text).
+This section gives the derivation for the field basis function spatial cut-off frequency as a function of the basis function width (equations~34 and~37 in the main text).
 For we define an \textit{n}-dimensional Gaussian  centred at the origin as
@@
 \end{equation}
-Now applying the \textit{n}-dimensional Fourier transform~\cite{Arsac1966} yields
+Now applying the \textit{n}-dimensional Fourier transform yields
 \begin{align}\label{eq:AppendixGaussianFT}
@@
 \section*{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\Gamma$, from equation~\ref{} in the main text.
-The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
+The derivation in this section was used for calculating the matrix $\Gamma$, from equation~16 in the main text.
+The inner product of the two \emph{n}-dimensional Gaussians (from equations~S1.14 and~S1.15) is defined as
 \begin{equation}\label{eq:InofGaussianDefinition}\tag{S1.18}

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
added bits for checking equation length
made comments to paragraph 1 in the dicussion

@@
 
+% TO DELETE
+\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+
+%  \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
  \documentclass[10pt]{article}
@@
 %% PLEASE INCLUDE ALL MACROS BELOW
-
+% \usepackage{anysize} 									%<-use this for checking equation length
+% \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm} 				%<-use this for checking equation length
+% \setlength{\columnsep}{0.5cm}							%<-use this for checking equation length
 %% END MACROS SECTION
@@
    	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
-The dashed line depicts the field and the solid lines show the Gaussian basis functions.}
+The dashed line depicts the field and the solid lines shows the Gaussian basis functions.}
 	\label{fig:FieldDecomposition}
@@
 This figure illustrates the band-limiting effect of the basis function decomposition.
-\begin{figure}[!ht] 
+\begin{figure*}[!ht] 
 	\begin{center}
@@
 	\label{fig:ObservationFreqAnal}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering 
@@
 \label{fig:FieldEstimate}
-\end{figure}
+\end{figure*}
 
@@
 Following such a paradigm, data can be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+
+\mike{The previous paragraph seems to say this: we get good estimates, but with wide variance.
+We could shrink those aspects of the variance to do with observation noise by including an input.
+Then, in a practical setting, do multiple runs to get a distribution of parameters.
+It seems to me there are two messages here.
+1: we could reduce the variance using an input.
+2: we could deal with the fact that we get a wide range of parameter estimates in practice by conducting multiple trials.
+I think these messages could be made a bit more clearly, and turned on their heads a bit.
+I've had a go at this paragraph again.}
+
+\mike{This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+As seen in  Section~\ref{sec:state_and_param_results}, the results indicate ubiased estimation, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.}
+
+\mike{To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
+Given knowledge of the input, it is expected that the variance of the parameter estimates will decrease.}
+
+\mike{Even with an evoked potential, our results imply that we should only expect to learn distributions of parameters, rather than hope to uncover a `true' parameter set.
+By designing an input signal carefully, data could be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.}
 

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
made a lot of comments about the 2nd and 3rd paras, and made loads of little changes

@@
 Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-A limitation of this framework lies in an increase in dimensionality with increases in the spatial resolution and in the physical size of the neural field.
-Increases in dimensionality lead to increases in uncertainty of the estimated state and problems associated with computational complexity.
-This paper builds on this previous study, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of a spatial discretisation.
-and is governed by the .
-The frequency analysis methods presented in Section~\ref{SpectralAnalysisSection} provide a rigorous framework determining the dimensionality of the system using inherent spatial properties of the field.
-This enables estimation of a larger field, with a lower dimensional state vector.
+A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will results in an increased state dimension.
+
+Due to the relationship between the number of states in the model and the number of model parameters, increases in dimensionality lead to increases in uncertainty of the estimates.
+In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
+
+This paper builds on \cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process.
+Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
+These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
+This enables estimation of a larger field, with a lower dimensional state vector than would be possible otherwise.
 The basis function decomposition also enabled the coupling to be described by an inner product rather than a spatial convolution.
@@
 
+\mike{The last part of this paragraph seems to be unrelated to the first part.
+So it reads like: hey we totally pick the dimension of our model based on the data, and we do it carefully.
+Oh and we can do some funky manipulation deep in the middle of our derivation that lets us speed up life immensely.
+Maybe the bit about the convolution should come at some other point?}
+
+\mike{In addition, I think the argument associated with this inner product thing should go as follows.
+`The fact that the connectivity kernel used is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+This simplifies.....' Do we talk about this in the body of the paper because it's a really subtle point.}
+
 The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
 Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-This is the first paper derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}, \mike{ and highlights the relationship between the spatial width of the sensors and the noise in the data}.
+
+This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
@@
 
+\mike{again, this paragraph seems to have multiple messages.
+At the top is hey there are other techniques, and our is better than them.
+Then there's a repeat of the ``our state dimension is indie of observations'' argument which we already made above, then there's something about multi-resolution models and how two frameworks could be combined to give anisotropy.
+I quite like the bit about other models, but do we really need to speculate about multi-res and anisotropy?
+I don't think the relationship is particularly clear...}
+
 Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 
-Parameter estimation may also have significant impact on the treatment of disease.
+Kernel parameter estimation may also have significant impact on the treatment of disease.
 For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
@@
 Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, and distant dependant propagation times into the parametric neural field equations.
+Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times, and finite, distant dependant propagation times into the parametric neural field equations.
 

### 2010-06-25 ltx/PLoS/LaTeX_Manuscript.tex
edits to author summary
added author summary

@@
 \section*{Author Summary}
+With recent advances in medical imaging techniques and computing power we are entering a new age of neuroscientific research, where the amount of patient specific information is becoming incredibly detailed.
+In order to make the best use of this information, patient specific mathematical models should should be formed.
+This is particularly poignant where considering poorly understood complex systems such as large scale dynamics of the human brain.
+In terms of brain dynamics, there currently exists a library of neural field models that provide a theoretical explanation of various phenomena associated with various cognitive states and disease.
+In this paper we have created a platform for creating a patient specific neural field model.
+Within this platform, we propose rules for designing experiments in order to acquire the data with sufficient information and the mathematical formula to create such a model.
 

### 2010-06-25 ltx/PLoS/SupportingInformation.tex
made the convolution bit more clear and changed the first paragraph of cutoff frequency and changed tags into equation numbers

@@
 \end{flushleft}
-
+\renewcommand{\theequation}{S1.\arabic{equation}}
 \section*{Time Discretisation of Neural Field Model}\label{Time Discretization} To form the IDE neural field model a 
@@
 \begin{equation}
-	\label{Euler Approximation}\tag{S1.1} \frac{v\left( \mathbf{r},t+T \right) - v\left( \mathbf{r},t\right)}{T_s} =-\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.
+	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} =-\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.
 \end{equation}
@@
 \begin{equation}
-	\label{Euler Approximation2}\tag{S1.2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.
+	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.
 \end{equation}
@@
 \begin{equation}
-	\label{Discrete Time Model1}\tag{S1.3} v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
+	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
 \end{equation}
@@
 \section*{Mean and Covariance of the State Disturbance }\label{ColoredNoise} 
-In this section we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(0,\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+In this section we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
 We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
@@
 From equation~21 of the main text, the state disturbance vector is defined as
-\begin{equation} \tag{S1.4}
+\begin{equation}
 	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
@@
 The expected value of $\mathbf e_t$ is given by 
-\begin{equation}\tag{S1.5}
+\begin{equation}
 	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
@@
 	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.\tag{S1.6}
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
 \end{align}
@@
 \section*{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
-This section gives the derivation for the field basis function spatial cut-off frequency as a function of the basis function width (equations~34 and~37 in the main text).
-For we define an \textit{n}-dimensional Gaussian  centred at the origin as
-\begin{equation}\tag{S1.7}
- \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma^2}\mathbf r^\top\mathbf r\right).
+This section gives the derivation for the width of the Fourier transform of  the field basis function in terms of its spatial cut-off frequency (equations~34 and~37 in the main text).
+We define an \textit{n}-dimensional Gaussian  centred at the origin as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
 \end{equation}
@@
  \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
-&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).\tag{S1.8}
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
 \end{align}
-Now evaluating the integral on the RHS of equation~S1.8 gives 
-\begin{equation}\label{eq:IntegralOfGaussian}\tag{S1.9}
+Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+\begin{equation}\label{eq:IntegralOfGaussian}
 \int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
@@
 \end{equation}
-Substituting equation~S1.9 into equation~S1.8 gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}\tag{S1.10}
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}
 \boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
@@
 where 
-\begin{equation}\tag{S1.11}
+\begin{equation}
 	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
@@
 For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{equation}\tag{S1.12}
+\begin{equation}
  \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
@@
 since the maximum of Gaussian described in equation~S1.10 is at the origin. Now solving for $\sigma_{\nu}^2$ we get
-\begin{equation}\tag{S1.13}
+\begin{equation}
  \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
@@
 Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}\tag{S1.14}
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
  \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
@@
 and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}\tag{S1.15}
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
 \varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
@@
 Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section we have
-\begin{equation}\tag{S1.16}
+\begin{equation}\label{eq:FTTwoGaussianMultiplication}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform.
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$ equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+\begin{equation}
 \mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
 \end{equation}
-where $\mathcal{F}$ denotes the Fourier transform. Taking the inverse Fourier transform, the convolution becomes
-\begin{equation}\label{eq:ConvoftwoGaussian}\tag{S1.17}
+ Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}
  \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
 \end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation~S1.17 becomes
-\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}\tag{S1.18}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation~\ref{eq:ConvoftwoGaussian} becomes
+\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
  \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
@@
 The derivation in this section was used for calculating the matrix $\Gamma$, from equation~16 in the main text.
-The inner product of the two \emph{n}-dimensional Gaussians (from equations~S1.14 and~S1.15) is defined as
-\begin{equation}\label{eq:InofGaussianDefinition}\tag{S1.18}
+The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
+\begin{equation}\label{eq:InofGaussianDefinition}
 \varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
@@
 A Gaussian basis function is symmetric with respect to its centre, therefore
-\begin{equation}\label{eq:GaussianSymmetry}\tag{S1.19}
+\begin{equation}\label{eq:GaussianSymmetry}
  \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
 \end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~S1.19 becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}\tag{S1.20}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
  \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
 \end{equation}
-Now substituting equation~S1.20 into equation~S1.18 gives 
+Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
 \begin{align}
@@
 &=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).\tag{S1.21}
+&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
 \end{align}
 Evaluating derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}\tag{S1.22}
+\begin{equation}
  \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
fixed section numbers
editing discussion, including mikes edits

@@
 \newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
 
@@
 %\doublespacing
+
+%Set the section counter to one
+\setcounter{section}{1}
 
@@
 \begin{document}
-
 % Title must be 150 characters or less
@@
 To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
-To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite-dimensional state-space model.
+To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model.
 Spatial frequency analysis methods are introduced for model selection by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
-The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
+The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
 The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
 This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models.
-This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.
+This link may lead to greater understanding of cortical dynamics at the meso and macroscopic scale where diseases such as epilepsy are manifested.
 
@@
 \section*{Introduction}
-Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the meso/macroscopic scale.
+Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the meso and macroscopic scale.
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
@@
 This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-As seen in the Section~\ref{sec:state_and_param_results} the results indicate good estimation performance, where the mean parameter estimates are in good agreement with the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance, and the observations are corrupted by noise.
-To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
-Following such a paradigm, data can be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
-
-\mike{The previous paragraph seems to say this: we get good estimates, but with wide variance.
-We could shrink those aspects of the variance to do with observation noise by including an input.
-Then, in a practical setting, do multiple runs to get a distribution of parameters.
-It seems to me there are two messages here.
-1: we could reduce the variance using an input.
-2: we could deal with the fact that we get a wide range of parameter estimates in practice by conducting multiple trials.
-I think these messages could be made a bit more clearly, and turned on their heads a bit.
-I've had a go at this paragraph again.}
-
-\mike{This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-As seen in  Section~\ref{sec:state_and_param_results}, the results indicate ubiased estimation, where the mean parameter estimates are in good agreement with the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.}
-
-\mike{To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings.
-Given knowledge of the input, it is expected that the variance of the parameter estimates will decrease.}
-
-\mike{Even with an evoked potential, our results imply that we should only expect to learn distributions of parameters, rather than hope to uncover a `true' parameter set.
-By designing an input signal carefully, data could be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.}
+As seen in Section~\ref{sec:state_and_param_results}, the results indicate unbiased estimation, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
+
+\dean{I just realised one thing that was not clear.
+An evoked-potential paradigm has many (100s) of trials.
+This is standard.
+It is never just one stimulus.
+So, I kinda just had one point.
+However Mike's 2 points are far clearer than what I wrote.}
+
+To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
+Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
+
+Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
+By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, data could be epoched into (averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
 
@@
 
-This paper builds on \cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process.
+The current study builds on \cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
@@
 This enables estimation of a larger field, with a lower dimensional state vector than would be possible otherwise.
-The basis function decomposition also enabled the coupling to be described by an inner product rather than a spatial convolution.
+
+\dean{Just need to link this to the previous bit.} The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
 
-\mike{The last part of this paragraph seems to be unrelated to the first part.
-So it reads like: hey we totally pick the dimension of our model based on the data, and we do it carefully.
-Oh and we can do some funky manipulation deep in the middle of our derivation that lets us speed up life immensely.
-Maybe the bit about the convolution should come at some other point?}
-
-\mike{In addition, I think the argument associated with this inner product thing should go as follows.
-`The fact that the connectivity kernel used is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
-This simplifies.....' Do we talk about this in the body of the paper because it's a really subtle point.}
+\dean{Nice one Mike! Yup, we do talk a little about the inner product convolution exchange in the derivation.}
 
@@
 Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}, \mike{ and highlights the relationship between the spatial width of the sensors and the noise in the data}.
+In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the \dean{noise} in the data.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009},
 

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
editted discussion

@@
 Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
-By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, data could be epoched into (averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
 
@@
 
-The current study builds on \cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process.
+The current study builds on \cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
further editted discussion, around the MVAR part

@@
 Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
-In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the \dean{noise} in the data.
+In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009},
@@
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-
-The closest competitor to our `grey-box' integro-difference equation (IDE) based approach is perhaps the `black-box' multivariate auto-regressive (MVAR) model.
+The closest competitor to our `grey-box' integro-difference equation (IDE) based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
 Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
-A distinct advantage of the IDE-based technique proposed in this paper, is that the estimates of the connectivity structure are made independently of the number of sensors (assuming the field is sufficiently sampled).
-In addition, the number of parameters required to model the system is considerably less than a typical MVAR model.
-Furthermore, by using the neural field equations as a parametric form of the model, the parameters have physical meaning and therefore, can be clinically relevant.
+A distinct advantage of the IDE-based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
+Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
 An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
-A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of a multi-scale connectivity structure in generating the characteristic rhythms of the brain.
+% A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of a multi-scale connectivity structure in generating the characteristic rhythms of the brain.
 A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
@@
 
-Generating patient specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+\dean{There is definitely no repeat now. Also, I have commented out the speculative part about how to include anisotropy.}
+
+Generating patient-specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
 Specifically, the development of a patient-specific state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
small edits to discussion and added acknowledgement

@@
 In this paper we have created a platform for creating a patient specific neural field model.
-Within this platform, we propose rules for designing experiments in order to acquire the data with sufficient information and the mathematical formula to create such a model.
+Within this platform, we propose rules for designing experiments and derive mathematical formula to create such a model.
 
@@
 This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-As seen in Section~\ref{sec:state_and_param_results}, the results indicate unbiased estimation, where the mean parameter estimates are in good agreement with the actual values.
+As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
@@
 Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
-
 Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
@@
 
-The current study builds on \cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
+The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
@@
 
-\dean{Just need to link this to the previous bit.} The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
-
-\dean{Nice one Mike! Yup, we do talk a little about the inner product convolution exchange in the derivation.}
 
@@
 
-\mike{again, this paragraph seems to have multiple messages.
-At the top is hey there are other techniques, and our is better than them.
-Then there's a repeat of the ``our state dimension is indie of observations'' argument which we already made above, then there's something about multi-resolution models and how two frameworks could be combined to give anisotropy.
-I quite like the bit about other models, but do we really need to speculate about multi-res and anisotropy?
-I don't think the relationship is particularly clear...}
-
-\dean{There is definitely no repeat now. Also, I have commented out the speculative part about how to include anisotropy.}
-
 Generating patient-specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
 Specifically, the development of a patient-specific state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures.
-In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.
+For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
+In addition, a patient-specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation, thereby possibly preventing seizure onset or abating seizure activity.
 
@@
 
-The development of an estimation framework also has theoretical implications.
-The the ability to estimate parameters will allow testing of hypotheses that have been generated in theoretical studies.
+The development of an estimation framework also has theoretical implications, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
 This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions can exist.
+For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions can exist.
 In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
@@
 We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
-In addition, we have assumed the neural field is isotropic and homogeneous.
+In addition, we have assumed that the neural field is isotropic and homogeneous.
 It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
 However, the assumption of homogeneity is quite strong.
-Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed.
-Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times, and finite, distant dependant propagation times into the parametric neural field equations.
-
-% This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields to create patient specific models.
-A basis function decomposition reduces the infinite dimensional neural field (continuous space) to a finite dimensional state-space model.
+Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
+Future work should also include a more realistic synaptic response kernel, with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
+
+% This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields to create patient-specific models.
+A basis function decomposition reduces the infinite-dimensional neural field (continuous space) to a finite-dimensional state-space model.
 The frequency analysis methods presented in this paper provide a systematic procedure for specifying the sensor and basis function arrangement required to describe the significant neuro-dynamics by the reduced neural field model.
@@
 \section*{Acknowledgments}
+This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
+Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
+In addition, Dean Freestone would like to thank Dr.
+Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
 

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
comment on kernel isotropy in discussion

@@
 \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
-
+\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
  % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
@@
 
-The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic about the origin \parham{it's true for isotropic kernel in general not only about origin} means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
comment on kernel isotropy in discussion

--- 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
@@
 
-The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic about the origin \parham{it's true for isotropic kernels in general not only about the origin} means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
minor edit in discussion about the isotropy of the kernel

--- 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
@@
 
-The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
tidy up a letex file

@@
 \end{figure*}
-
-%\begin{figure}[!ht]
-%\begin{center}
-%%\includegraphics[width=4in]{figure_name.2.eps}
-%\end{center}
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
-%should be left justified, as specified by the options to the caption 
-%package.
-%}
-%\label{Figure_label}
-%\end{figure}
-
 \subsection*{State and Parameter Estimates} 
@@
 The mean estimates are in good concordance with the actual values.
-% It should be noted that when the excitatory connectivity parameters, $\hat\theta_0$ and $\hat\theta_2$, were under (or over) estimated, the inhibitory connectivity parameter, $\hat\theta_1$, tended to be over (or under) estimated.
-This is demonstrated in Figure~\ref{fig:ParametersRatio} where we show the distribution of the ratios of the parameter estimates.
 \begin{figure}
@@
 \end{figure}
-% \begin{figure}
-%     \centering
-% \subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
-% \subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
-% \caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations.
-\textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25).
-\textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).
-In each case, the solid and dotted lines show the locations of the true and estimated ratios respectively.}
-% \label{fig:ParametersRatio}
-% \end{figure}
-
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the $100$ realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
@@
 The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
-
 \begin{figure}

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
general paper edits

--- 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
@@
 \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
+
  % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
@@
 Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
-However, the meso/macroscopic neural dynamic state is not directly observable in EEG data, making predictions of the underlying physiology inherently difficult.
+However, the meso and macroscopic neural dynamic state is not directly observable in neurophysiological data, making predictions of the underlying physiology inherently difficult.
 
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific EEG data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific EEG data.
 Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
@@
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ can be described by
+The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
 \begin{equation}
@@
    	\caption{{\bf Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$}.
-The function $w(.)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.}
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
+To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see the S1 for derivation) giving 
 \begin{equation}
@@
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian Process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 This term is added to account for uncertainty and unmodelled inputs.
@@
 
-The mapping between the membrane voltage and the electrophysiological data (iEEG/LFP) is modelled using the observation function 
+The mapping between the membrane voltage and the electrophysiological data (iEEG/LFP) is modelled using the observation function that incorporates sensors with a spatial extent by
 \begin{equation}
@@
 where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$, $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry where
-\begin{equation}
-	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)}. 
-\end{equation}
+The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by
+\begin{equation}
+	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)},
+\end{equation}
+where $\sigma_m$ sets the sensor width.
 
@@
    	\end{center}
-   	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
-The dashed line depicts the field and the solid lines shows the Gaussian basis functions.}
+   	\caption{{\bf Example of a one-dimensional field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
+The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
 	\label{fig:FieldDecomposition}
@@
 
-\dean{I just realised one thing that was not clear.
-An evoked-potential paradigm has many (100s) of trials.
-This is standard.
-It is never just one stimulus.
-So, I kinda just had one point.
-However Mike's 2 points are far clearer than what I wrote.}
-
 To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
@@
 
-The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
more general edits

@@
 \end{equation}
-Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(r)$ and integrate over the spatial domain $\Omega$ to get 
+Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain $\Omega$ to get 
 \begin{equation}
@@
 \end{equation}
-An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in~\ref{ap:InnerProdOfGaussians}.
+An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see~\ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
+which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 \end{equation}
-which is a zero mean normally distributed white noise process with covariance (see~\ref{ColoredNoise})
+which is a zero mean normally distributed white noise process with covariance (see the Supporting Information, S1, for the derivation)
 \begin{equation}
@@
 The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-To demonstrate this, we begin with the two-dimensional Gaussian basis function defined as
+To demonstrate this, we begin with the two-dimensional Gaussian basis function located at the origin defined as
 \begin{equation}\label{eq:BasisFunctionAtOrigin}
- \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right)
+ \phi(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2} \mathbf r^\top\mathbf r}\right).
 \end{equation}
-with the corresponding Fourier transform
+The corresponding Fourier transform
 \begin{equation}\label{eq:GaussianFT}
@@
 This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
-Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
+Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in the Supporting Information, S1.
 
@@
 where the superscripts $m$ and $c$ denote mean and covariance.
-Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
+Since the observation equation is linear, (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
 The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
@@
 All parameters for the model are given in Table~\ref{tab:Parameters}.
-Note that, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
+Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
 This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
@@
 
-The sensors were spaced on a regular square $14 \times 14$ grid, the sensor width was set to $\sigma^2_m = 0.81$.
-This provides a width of $1.5$~mm at half the maximum amplitude of the basis function, with spacing $\Delta_y = 1.5$~mm.
+The sensors were spaced on a regular square $14 \times 14$ grid and the sensor width was set to $\sigma^2_m = 0.81$.
+This provides a width of $1.5$~mm at half the maximum amplitude of the sensor kernel.
+The distance between sensors was set to $\Delta_y = 1.5$~mm.
 This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
@@
 Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field.
-The cut-off frequency of the neural field is $\nu_c \approx 0.24$~Hz ($-3$~dB point).
+The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.
@@
 The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C).
-The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point).
+The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A).
-Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
 Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
-This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
+This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B).
 The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B).
-This figure illustrates the band-limiting effect of the basis function decomposition.
+This figure illustrates the band-limiting effect of the basis function decomposition when compared to Figure~\ref{fig:FFTTrueEstimate}(A).
 \begin{figure*}[!ht] 
@@
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-This enables estimation of a larger field, with a lower dimensional state vector than would be possible otherwise.
+This enables estimation of a larger field with a lower dimensional state vector than would be possible otherwise.
 
-The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
@@
 The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-The closest competitor to our `grey-box' integro-difference equation (IDE) based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
+The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
 Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
-A distinct advantage of the IDE-based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
+A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
 Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
@@
 \section*{Tables}
+
+\renewcommand{\arraystretch}{1.7}
+\begin{table}[!ht]
+\caption{
+\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
+\begin{tabular}{|c|}\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
+$\hat{\mathbf x}_0, \mathbf P_0$ \\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
+$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
+\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
+$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
+$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
+$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
+\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
+$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
+$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
+\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
+$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
+$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
+$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
+\hline
+\end{tabular}
+\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
+The steps are iterated 11 times for our state estimation procedure.
+The least squares algorithm is run after each iteration to update the parameter estimates.
+\end{flushleft}
+\label{tab:UKFAlgorithm}
+\end{table}
 
@@
    	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
-   	$\Gamma$ & inner product of field basis functions & n.a.\\
+   	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\
    	$Q()$ & state transition function &\\
@@
     % $V(\nu)$ & Fourier transform of the neural field & Hz\\
-	$\nu$, $\nu_c$ & spatial frequency and spatial cut-off frequency & Hz \\
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
 	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
@@
 \begin{flushleft}The first column of the table gives the symbols for all the notation used the paper.
-The second column provides a brief description of the quantity, and the third column provide the relevant SI units.
+The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.
 \end{flushleft}
 \label{tab:label}
-\end{table}
-
-\renewcommand{\arraystretch}{1.7}
-\begin{table}[!ht]
-\caption{
-\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
-\begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
-$\hat{\mathbf x}_0, \mathbf P_0$ \\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
-$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
-\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
-$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
-$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
-$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
-$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
-$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
-\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
-$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
-$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
-\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
-$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
-$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
-$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
-\hline
-\end{tabular}
-\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
-The steps are iterated 11 times for our state estimation procedure.
-The least squares algorithm is run after each iteration to update the parameter estimates.
-\end{flushleft}
-\label{tab:UKFAlgorithm}
 \end{table}

### 2010-06-27 ltx/PLoS/LaTeX_Manuscript.tex
fixed a problem with bib file
minor general edits to the paper

@@
 With recent advances in medical imaging techniques and computing power we are entering a new age of neuroscientific research, where the amount of patient specific information is becoming incredibly detailed.
-In order to make the best use of this information, patient specific mathematical models should should be formed.
+In order to make the best use of this information, patient specific mathematical models should be formed.
 This is particularly poignant where considering poorly understood complex systems such as large scale dynamics of the human brain.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific EEG data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data.
 Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
@@
 where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian Process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 This term is added to account for uncertainty and unmodelled inputs.
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$, $\mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\Sigma_{\varepsilon}$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$, $\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by
@@
    	\end{center}
-   	\caption{{\bf Example of a one-dimensional field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
+   	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
 The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\psi(\mathbf{r}-\mathbf{r}')$.
+By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 \begin{equation}
-	V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c,
+	V_t(\boldsymbol{\nu}) \approx 0 ~ \ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c,
 \end{equation}
@@
 \begin{equation}
-	\label{eq:MinimumSensorDistance} \Delta_y \leq \frac{1}{2\rho_y\nu_{c}}, 
+	\label{eq:MinimumSensorDistance} \Delta_y \leq \frac{1}{2\rho_y\boldsymbol{\nu}_{c}}, 
 \end{equation}
@@
 Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
-Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors used and the computational demands of the estimation procedure when designing experiments.
+Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors and the computational demands of the estimation procedure when designing experiments.
 
@@
     	\end{center}
-    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} Example of the neural field at a single time instant.
-(\textbf{B}) Example of data generated by the full neural field model from the first 5 sensors.
+    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant.
+(\textbf{B}) Data generated by the full neural field model from the first 5 sensors.
 (\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
@@
 \end{table}
+\renewcommand{\arraystretch}{1}
 
@@
 
-\renewcommand{\arraystretch}{1}
 \begin{table}[!ht]

### 2010-06-27 ltx/PLoS/LaTeX_Manuscript.tex
small edits to paper

@@
 The sensors were spaced on a regular square $14 \times 14$ grid and the sensor width was set to $\sigma^2_m = 0.81$.
-This provides a width of $1.5$~mm at half the maximum amplitude of the sensor kernel.
+This provides a width of 1.5~mm at half the maximum amplitude of the sensor kernel.
 The distance between sensors was set to $\Delta_y = 1.5$~mm.
@@
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of $2.05$~mm.
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
 This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where $100$ realisations of the data were generated.
-Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out.
+To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated.
+Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
@@
 \end{figure}
-The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the $100$ realisations is shown as a dotted line and the $95\%$ confidence interval is indicated by the grey shaded region.
+The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
@@
 \caption{{\bf Cross-section of connectivity kernel estimate}.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the $95~\%$ confidence interval is shown by the shaded grey region.}
+The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
 \label{fig:KernelEstimates}
@@
 The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-At each time point the error is consistently around 0.5~mV, which is approximately $7.1$~\% of the field voltage range ($[-3.29,3.77]$~mV).
+At each time point the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
@@
 \section*{Acknowledgments}
-This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
+Dean Freestone would like to thank Dr. Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
+
+% This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
 The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
 Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
-In addition, Dean Freestone would like to thank Dr.
-Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
 

### 2010-06-28 ltx/PLoS/SubmissionLetter.tex
adding the submission letter

%
%  untitled
%
%  Created by Dean Freestone on 2010-06-28.
%  Copyright (c) 2010 . All rights reserved.
%
\documentclass[]{article}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}

% Setup for fullpage use
\usepackage{fullpage}

% Uncomment some of the following if you use the features
%
% Running Headers and footers
%\usepackage{fancyhdr}

% Multipart figures
%\usepackage{subfigure}

% More symbols
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{latexsym}

% Surround parts of graphics with box
\usepackage{boxedminipage}

% Package for including code in the document
\usepackage{listings}

% If you want to generate a toc for each chapter (use with book)
\usepackage{minitoc}

% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\title{The letter}
\author{  }

\date{2010-06-28}

\begin{document}

\ifpdf
\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
\else
\DeclareGraphicsExtensions{.eps, .jpg}
\fi

\maketitle

\section{Letter}
\emph{Please explain why this manuscript is suitable for publication in PLoS Computational Biology; why will your paper inspire the other members of your field, and how will it drive research forward?}

To the editor/reviewer,

We hope that this work will inspire both theoreticians and experimentalists by providing a framework for linking continuum neural field models to patient-specific data. Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques. In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems. This work provides an essential link, bridging the data driven and theoretically driven areas of research. We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.

The novel aspects of this paper include:
\begin{itemize}
	\item the representation of a continuum neural field model as reduced finite-dimensional state-space model,
	\item derivations for the conditions for placement and geometry of sensors/electrodes to sufficiently sample a neural field to capture significant cortical dynamics,
	\item conditions for the model reduction to represent the neural field as a finite-dimensional state-space model,
	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation,
	\item a derivation for an algorithm for estimating intracortical connectivity and synaptic dynamics using the neural field equations.
\end{itemize}

Please contact us if you have any questions regarding any aspects of this paper.

Best Regards,

Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.
\bibliographystyle{plain}
\bibliography{}
\end{document}

### 2010-06-28 ltx/PLoS/LaTeX_Manuscript.tex
added to acknowledgements
commiting to merge

@@
 \section*{Author Summary}
-With recent advances in medical imaging techniques and computing power we are entering a new age of neuroscientific research, where the amount of patient specific information is becoming incredibly detailed.
-In order to make the best use of this information, patient specific mathematical models should be formed.
-This is particularly poignant where considering poorly understood complex systems such as large scale dynamics of the human brain.
-In terms of brain dynamics, there currently exists a library of neural field models that provide a theoretical explanation of various phenomena associated with various cognitive states and disease.
-In this paper we have created a platform for creating a patient specific neural field model.
-Within this platform, we propose rules for designing experiments and derive mathematical formula to create such a model.
+With recent advances in medical imaging techniques and computing power we are entering a new age of neuroscientific research, where patient-specific information is becoming incredibly detailed.
+In order to make the best use of this information, patient-specific mathematical models should be formed.
+This is particularly poignant where considering poorly understood complex systems such as large-scale dynamics of the human brain.
+There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and disease.
+In this paper, we have created a framework for creating a patient specific mathematical model, forming a bridge between theory and electrophysiological data.
+Within this framework, we propose rules for designing experiments and we derive the mathematical formula to create the model.
+To demonstrate the utility of this framework, we provide an example using synthetic data that shows a comparison between true and estimated model characteristics.
+The ability to create patient-specific models of large-scale brain dynamics has the potential to revolutionise the treatment of diseases such as epilepsy, where techniques from engineering may be used to prevent abnormal neural oscillations.
 
@@
    	\end{center}
-   	\caption{{\bf Mexican-hat connectivity kernel, $w(\mathbf{r},\mathbf{r'})$}.
-The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+   	\caption{{\bf Mexican-hat connectivity kernel.} The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.}
@@
 In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009},
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
 
@@
 \section*{Acknowledgments}
-Dean Freestone would like to thank Dr. Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
+Dean Freestone would like to thank Dr.
+Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
+Authors would also like to thank Andrew Hills for useful discussions and help with some code and the generation of figures.
 

### 2010-06-28 ltx/PLoS/SupportingInformation.tex
editing discussion, including mikes edits

@@
 \fi
-\title{S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
-\author{Dean R. Freestone$^{1,2,3}$, 
-Parham Aram$^{4}$, 
-Michael Dewar$^{5,\ast}$,\\
-Kenneth Scerri$^{6,\ast}$,
-David B. Grayden$^{1,\ast}$,
-Visakan Kadirkamanathan$^{4}$}
+% \title{S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
+% \author{Dean R. Freestone$^{1,2,3,\ast}$, 
+% Parham Aram$^{4}$, 
+% Michael Dewar$^{5}$,\\
+% Kenneth Scerri$^{6}$,
+% David B. Grayden$^{1}$,
+% Visakan Kadirkamanathan$^{4}$}
 
@@
 
-\ifpdf
-\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
-\else
-\DeclareGraphicsExtensions{.eps, .jpg}
-\fi
-
-\maketitle
-
 	\begin{flushleft}
-
+	{\Large
+	\textbf{S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
+	}
+	% Insert Author names, affiliations and corresponding author email.
+	\\
+	Dean R. Freestone$^{1,2,3,\ast}$, 
+	Parham Aram$^{4}$, 
+	Michael Dewar$^{5}$,
+	Kenneth Scerri$^{6}$,
+	David B. Grayden$^{1}$,
+	Visakan Kadirkamanathan$^{4}$
+	\\
 	\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
@@
 	\end{flushleft}
+
+\ifpdf
+\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
+\else
+\DeclareGraphicsExtensions{.eps, .jpg}
+\fi
+
+% \maketitle
+% 
+% \begin{flushleft}
+% 
+% \bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
+% \\
+% \bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
+% \\
+% \bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
+% \\
+% \bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
+% \\
+% \bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
+% \\
+% \bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta
+% \\
+% $\ast$ E-mail: dfreestone@bionicear.org
+% \end{flushleft}
 \renewcommand{\theequation}{S1.\arabic{equation}}

### 2010-06-28 ltx/PLoS/LaTeX_Manuscript.tex
restructured the discussion along the lines of 1: patient specific models, 2: implications for experiment design, 3: dealing with complexity. It's very rough, and may not make sense.

@@
 Parham Aram$^{4}$, 
-Michael Dewar$^{5}$,
+Michael Dewar$^{3,5}$,
 Kenneth Scerri$^{6}$,
@@
 
-\section*{Discussion}\label{DiscussionSection}
-This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
+\section*{Discussion}
+\label{DiscussionSection}
 
-To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
-Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
-Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
-By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+This paper has presented a method for extracting patient-specific models of synaptic dynamics from electrophysiological data.
+In so doing, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
+The mathematical formulation we have presented scales well with the number of sensors, and we have derived a finite-order model which allows us to perform inference efficiently.
 
-Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
-Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will results in an increased state dimension.
-
-Due to the relationship between the number of states in the model and the number of model parameters, increases in dimensionality lead to increases in uncertainty of the estimates.
-In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
-
-The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
-Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
-These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-This enables estimation of a larger field with a lower dimensional state vector than would be possible otherwise.
-
-The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
-This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
-
-The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
-Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
-In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
-Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
-A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
-Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
-% A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of a multi-scale connectivity structure in generating the characteristic rhythms of the brain.
-A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper.
+\subsection*{Patient Specific Modelling}
 
@@
 
+\subsection*{Implications for Experiment Design}
+
+This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
+
+To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
+Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
+Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
+By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+
+The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
+Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
+In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
+
+\subsection*{Computational Complexity}
+
+This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
+The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
+Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
+A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
+Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
+An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
+
+Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
+Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
+A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will results in an increased state dimension.
+
+Due to the relationship between the number of states in the model and the number of model parameters, increases in dimensionality lead to increases in uncertainty of the estimates.
+In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
+
+The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
+Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
+These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
+This enables estimation of a larger field with a lower dimensional state vector than would be possible otherwise.
+
+The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
+This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
+
+\subsection*{Future Work}
+
 In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
@@
 Future work should also include a more realistic synaptic response kernel, with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
-
-% This paper presents a novel framework for state and parameter estimation of spatio-temporal neural fields to create patient-specific models.
-A basis function decomposition reduces the infinite-dimensional neural field (continuous space) to a finite-dimensional state-space model.
-The frequency analysis methods presented in this paper provide a systematic procedure for specifying the sensor and basis function arrangement required to describe the significant neuro-dynamics by the reduced neural field model.
-The level of detail of the estimated field is related to the basis functions decomposition, providing a flexible framework where a trade-off can be made between physiological detail and computational complexity.
-Using the state-space model, the unscented Rauch-Tung-Striebel smoother was applied for state estimation.
-Using the sequence of state estimates, a least squares algorithm was implemented for parameter estimation.
-We have demonstrated that it is theoretically possible to estimate intracortical connectivity and the synaptic dynamics using the proposed methodology.
 

### 2010-06-29 ltx/PLoS/SubmissionLetter.tex

@@
 
+This paper brings several new techniques to Computational Biology.
+We have developed a data-driven framework for generating patient-specific neural field models.
+This paper is timely and draws together several cutting-edge technologies:
+\begin{itemize}
+	\item Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques.
+	\item In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems. 
+	\item In addition, recent advances in computing power and nonlinear systems theory have made possible state estimation from nonlinear spatio-temporal systems.
+\end{itemize}
+
 We hope that this work will inspire both theoreticians and experimentalists by providing a framework for linking continuum neural field models to patient-specific data.
-Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques.
-In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems.
 This work provides an essential link, bridging the data driven and theoretically driven areas of research.
@@
 
+Since this primarily a methods paper, we have taken the option of preceding the results by the methods section.
+
 Please contact us if you have any questions regarding any aspects of this paper.
@@
 
-Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.
+The authors.
+
+(Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.)
 \bibliographystyle{plain}

### 2010-06-29 ltx/PLoS/SubmissionLetter.tex
edits to letter

@@
 %
-\documentclass[]{article}
+\documentclass[a4paper,10pt]{letter}
+\usepackage{anysize} 									%<-use this for checking equation length
 
-% Use utf-8 encoding for foreign characters
-\usepackage[utf8]{inputenc}
+\marginsize {1.7cm}{1.5cm}{2cm}{2cm} 				%<-use this for checking equation length
 
-% Setup for fullpage use
-\usepackage{fullpage}
-
-% Uncomment some of the following if you use the features
-%
-% Running Headers and footers
-%\usepackage{fancyhdr}
-
-% Multipart figures
-%\usepackage{subfigure}
-
-% More symbols
-%\usepackage{amsmath}
-%\usepackage{amssymb}
-%\usepackage{latexsym}
-
-% Surround parts of graphics with box
-\usepackage{boxedminipage}
-
-% Package for including code in the document
-\usepackage{listings}
-
-% If you want to generate a toc for each chapter (use with book)
-\usepackage{minitoc}
-
-% This is now the recommended way for checking for PDFLaTeX:
-\usepackage{ifpdf}
-
-%\newif\ifpdf
-%\ifx\pdfoutput\undefined
-%\pdffalse % we are not running PDFLaTeX
-%\else
-%\pdfoutput=1 % we are running PDFLaTeX
-%\pdftrue
-%\fi
-
-\ifpdf
-\usepackage[pdftex]{graphicx}
-\else
-\usepackage{graphicx}
-\fi
-\title{The letter}
-\author{  }
-
-\date{2010-06-28}
+\signature{Dean R. Freestone}
+\address{Department of Electrical \\
+and Electronic Engineering \\ The University of Melbourne \\ Parkville \\ Victoria, 3010 \\ Australia}
 
@@
 
-\ifpdf
-\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
-\else
-\DeclareGraphicsExtensions{.eps, .jpg}
-\fi
+\begin{letter}{Editor/Reviewer \\ PloS Computational Biology}
 
-\maketitle
+\opening{Dear Sir or Madam,}
 
-\section{Letter}
-\emph{Please explain why this manuscript is suitable for publication in PLoS Computational Biology; why will your paper inspire the other members of your field, and how will it drive research forward?}
+% \emph{Please explain why this manuscript is suitable for publication in PLoS Computational Biology; why will your paper inspire the other members of your field, and how will it drive research forward?}
 
-To the editor/reviewer,
+I am writing to seek publication of our research article titled `A Data Driven Framework for Patient-Specific Neural Field Modelling' in PLoS Computational Biology.
 
-This paper brings several new techniques to Computational Biology.
-We have developed a data-driven framework for generating patient-specific neural field models.
-This paper is timely and draws together several cutting-edge technologies:
+This paper brings several new techniques to Computational Biology, where as the title suggests, we have developed a data-driven framework for generating patient-specific neural field models.
+This paper is timely as it draws together several areas of cutting-edge technologies including:
 \begin{itemize}
@@
 
-We hope that this work will inspire both theoreticians and experimentalists by providing a framework for linking continuum neural field models to patient-specific data.
 This work provides an essential link, bridging the data driven and theoretically driven areas of research.
@@
 
+Thank you for your time and consideration in reviewing this article.
 Please contact us if you have any questions regarding any aspects of this paper.
+I look forward to hearing the outcome of the review soon.
 
-Best Regards,
+\closing{Best Regards,}
 
-The authors.
-
-(Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.)
-\bibliographystyle{plain}
-\bibliography{}
+% The authors.
+% 
+% (Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.)
+\end{letter}
 \end{document}

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex

@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
 \end{equation}
@@
 	f\left( v\left( \mathbf{r}',t \right)\right)
-	d\mathbf{r}'dt'.
+	\textrm{d}\mathbf{r}'dt'.
 \end{equation}
@@
 	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}.
 \end{equation}
@@
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	d\mathbf{r}'} 
+	\textrm{d}\mathbf{r}'} 
 	+ e_t\left(\mathbf{r}\right), 
@@
 	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	d\mathbf{r}'} + 
+	\textrm{d}\mathbf{r}'} + 
 	\boldsymbol{\varepsilon}_t, 
@@
 \begin{equation}
-	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')d\mathbf{r}'}\boldsymbol{\theta}
+	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta}
 	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
@@
 	\label{StartofReduction}
-	\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1}=} \\
- &T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) d\mathbf{r}'}d\mathbf{r}}\boldsymbol{\theta}  \\ & + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}. 
+	\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1}=} \\
+ &T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}}\boldsymbol{\theta}  + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t+
+\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}. 
 \end{split}
@@
 \begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)\textrm{d}\mathbf{r}}, 
 \end{equation}
@@
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta} \\ 
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})d\mathbf{r}}.
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
 	 \end{split}
@@
 An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1.
-Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel
+\mike{This doesn't seem to be the isotropy of the kernel, it's the isotropy of the kernel's basis functions.
+The whole thing holds for the kernel itself or, if they're isostropic, the basis functions.
+You just can't say one and write the other!
+You could put something like ``..
+by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it''}
 \begin{equation}
@@
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
 \end{equation}
@@
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-\begin{eqnarray}
-	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t\nonumber \\
-+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.
-\end{eqnarray}
+\begin{equation}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t 
++ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
+\end{equation}
 This simplification has transformed the description of the spatial coupling from a convolution to an inner product.
-This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
+\mike{This is a bit deceptive.
+What you've actually done is move the convolution of the kernel basis functions with the nonlinearly transformed field to the convolution of field basis functions with the kernel basis functions.
+To see this, you could've done the same trick by just calling $\int \psi(r-r')f(\phi^Tx_t)dr' = A(r)$ and the saying hey!
+We now have the inner product $\int \phi(r) A(r) dr$.
+The point is that you can do the convolution $\phi * \psi$ analytically whereas you have to do the inner product $\Psi f(\phi^Tx_t)$ numerically.
+I wouldn't make a big deal about this except a fuss is made (rightly so) about this in the Discussion section.} This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
 Now we define the state disturbance as
 \begin{equation}\label{eq:Wt} 
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )\textrm{d}\mathbf{r}} 
 \end{equation}
@@
 \begin{equation}\label{eq:ReducedObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_td\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t\textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
 \end{equation}
@@
 \begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')d\mathbf{r}'. 
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
 \end{equation}
@@
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
+	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
 \end{equation}
@@
 \begin{equation}
-	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}'.
 \end{equation}
@@
 In so doing, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-The mathematical formulation we have presented scales well with the number of sensors, and we have derived a finite-order model which allows us to perform inference efficiently.
+The mathematical formulation we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation which allows us to perform inference efficiently.
 
@@
 
-In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
-In future work, we plan to relax this assumption.
-We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions.
+In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption.
+
 In addition, we have assumed that the neural field is isotropic and homogeneous.
@@
 Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
-Authors would also like to thank Andrew Hills for useful discussions and help with some code and the generation of figures.
+Parham Aram would also like to thank Andrew Hills for useful discussions and help with some code and the generation of figures.
 

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
added changes the decomposition section that mike suggested. Mikes comments are still there but commented

@@
 An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1.
-Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel
-\mike{This doesn't seem to be the isotropy of the kernel, it's the isotropy of the kernel's basis functions.
-The whole thing holds for the kernel itself or, if they're isostropic, the basis functions.
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
+% \mike{This doesn't seem to be the isotropy of the kernel, it's the isotropy of the kernel's basis functions.
+The whole thing holds for the kernel itself or, if they're isotropic, the basis functions.
 You just can't say one and write the other!
@@
 by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it''}
+% \dean{nice point Mike. I have changed it like you suggested.}
 \begin{equation}
@@
 \end{equation}
-This simplification has transformed the description of the spatial coupling from a convolution to an inner product.
-\mike{This is a bit deceptive.
+This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the of the connectivity kernel basis functions with the field basis functions.
+This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant an can be pre-defined analytically.
+This is of great importance considering the computational demands of the estimation algorithm.
+
+% \dean{Cheers Mike, I think it is better now.}
+% \mike{This is a bit deceptive.
 What you've actually done is move the convolution of the kernel basis functions with the nonlinearly transformed field to the convolution of field basis functions with the kernel basis functions.
@@
 The point is that you can do the convolution $\phi * \psi$ analytically whereas you have to do the inner product $\Psi f(\phi^Tx_t)$ numerically.
-I wouldn't make a big deal about this except a fuss is made (rightly so) about this in the Discussion section.} This transformation provides a dramatic increase in simulation speed, which is of great importance considering the computational demands of the estimation algorithm.
+I wouldn't make a big deal about this except a fuss is made (rightly so) about this in the Discussion section.}
+
 Now we define the state disturbance as
@@
 \end{equation}
-The corresponding Fourier transform
+The corresponding Fourier transform is
 \begin{equation}\label{eq:GaussianFT}
@@
 
-The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C).
+The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(A).
 The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A).
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(B).
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C).
 The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B).
@@
 
-\subsection*{Patient Specific Modelling}
+\subsection*{Patient-Specific Modelling}
 

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
added edits from David

@@
 Kenneth Scerri$^{6}$,
-David B. Grayden$^{1}$,
+David B. Grayden$^{1,2}$,
 Visakan Kadirkamanathan$^{4}$
@@
 The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
-This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models.
-This link may lead to greater understanding of cortical dynamics at the meso and macroscopic scale where diseases such as epilepsy are manifested.
+This framework provides a link between patient-specific neurophysiological data and theoretical neural field models.
+This link may lead to greater understanding of cortical dynamics at the mesoscopic and macroscopic scales where diseases such as epilepsy are manifested.
 
@@
 \section*{Author Summary}
-With recent advances in medical imaging techniques and computing power we are entering a new age of neuroscientific research, where patient-specific information is becoming incredibly detailed.
+With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information is becoming incredibly detailed.
 In order to make the best use of this information, patient-specific mathematical models should be formed.
@@
 There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and disease.
-In this paper, we have created a framework for creating a patient specific mathematical model, forming a bridge between theory and electrophysiological data.
+In this paper, we have created a framework for creating a patient-specific mathematical model, forming a bridge between theory and electrophysiological data.
 Within this framework, we propose rules for designing experiments and we derive the mathematical formula to create the model.
@@
 \section*{Introduction}
-Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the meso and macroscopic scale.
-While our understanding of the function of neurons is well developed, the overall behaviour of the brain's meso and macro-scale dynamics remains largely theoretical.
+Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the mesoscopic and macroscopic scale.
+While our understanding of the function of neurons is well developed, the overall behaviour of the brain's mesoscopic and macroscopic scale dynamics remains largely theoretical.
 Understanding the brain at this level is extremely important since it is at this scale that pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.
@@
 Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
-However, the meso and macroscopic neural dynamic state is not directly observable in neurophysiological data, making predictions of the underlying physiology inherently difficult.
+However, the mesoscopic and macroscopic neural dynamic state is not directly observable in neurophysiological data, making predictions of the underlying physiology inherently difficult.
 
@@
 An estimation framework for neural field models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has recently been proposed for studying evoked potential dynamics.
-Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations.
+Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
 Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with modified WC neural field equations~\cite{schiff2008kalman}.
@@
 \begin{equation}
-	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}. 
+	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}, 
 \end{equation}
@@
 The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
-To demonstrate flexibility in estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
 An example of the connectivity kernel is shown in in Figure~\ref{fig:2d_kernel}.
+To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$, $\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$.
+$\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
 The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-An example of the field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+An example of a one-dimensional field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
 \begin{figure}
@@
    	\end{center}
-   	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
+   	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
 The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
@@
 \begin{equation}\label{eq:Wt} 
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )\textrm{d}\mathbf{r}} 
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )\textrm{d}\mathbf{r}},
 \end{equation}
@@
 \begin{equation}\label{eq:finalformstatespacemodel}
-	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t.
+	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t
 \end{equation}
@@
 In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
 The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors therefore can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
+Such sensors, therefore, can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, replacing $\boldsymbol{\nu}_c$ with $\boldsymbol{\nu}_{cy}$.
@@
 
-\subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
+\subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
@@
 The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
-The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward iteration to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward iteration to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
-The first and the second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
+The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
 The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
-\begin{equation}\label{eq:sigmapoints1}
-	\mathcal X_{0}=\bar x 
-\end{equation}
-\begin{equation}
-	\mathcal X_{i}=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L 
-\end{equation}
-\begin{equation}\label{eq:sigmapoints2}
-	\mathcal X_{i}=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2 L 
-\end{equation}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the weighted matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+\begin{align}\label{eq:sigmapoints1}
+	\mathcal X_{0}&=\bar x \\
+	\mathcal X_{i}&=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L \\
+	\mathcal X_{i}&=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2L 
+\end{align}
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
-\begin{equation}
-	\mathbf W_0^{(m)}=\frac{\lambda}{ L+\lambda} 
-\end{equation}
-\begin{equation}
-	\mathbf W_0^{(c)}=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) 
-\end{equation}
-\begin{equation}
-	\mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
-\end{equation}
+\begin{align}
+	\mathbf W_0^{(m)}&=\frac{\lambda}{ L+\lambda} \\
+	\mathbf W_0^{(c)}&=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) \\
+	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
+\end{align}
 where the superscripts $m$ and $c$ denote mean and covariance.
-Since the observation equation is linear, (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are used to correct the predicted states.
+Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
 The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
@@
 A summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
-It should be noted that the disturbance, $\mathbf{e}_t$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
+It should be noted that the disturbance, $\mathbf{e}_t$, and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
 Therefore, the additive form of the URTSS is used.
@@
 Now given a state estimate sequence from an iteration of the URTSS, we can write
-\begin{eqnarray*}
-	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
-	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
+\begin{align*}
+	\mathbf x_{1} &= \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
+	\mathbf x_{2} &= \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
 	&\vdots& \\
-	\mathbf x_{T}&=&\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
-\end{eqnarray*}
+	\mathbf x_{T}&=\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
+\end{align*}
 This can be written in the compact form
@@
 % Results and Discussion can be combined.
-\section*{Results}\label{ResultsSection} In this section we provide a demonstration of the estimation procedure using the new methods that are described above.
+\section*{Results}\label{ResultsSection} In this section, we provide a demonstration of the estimation procedure using the new methods that are described above.
 The full neural field model described in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
@@
 This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
-When generating the simulated data we assumed free boundary conditions for the neural field.
+When generating the simulated data, we assumed free boundary conditions for the neural field.
 An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(A).
@@
 The dashed line shows the cut-off frequency (-3 dB point).
-(\textbf{A}) Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field.
+(\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
+(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
 The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
 (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
@@
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good concordance with the actual values.
+The mean estimates are in good agreement with the actual values.
 \begin{figure}
@@
 \end{figure}
+
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
-The figure verifies that the shape of the estimated connectivity kernel is in good accordance to the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias on the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
+The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
 \begin{figure}
@@
 \end{figure}
-The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) (over space).
+The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
 The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
commiting for merge
editted summary to make it data driven rather than patient specific

@@
 {\Large
-\textbf{A Data Driven Framework for Patient-Specific Neural Field Modelling}
+\textbf{A Data Driven Framework for Neural Field Modelling}
 }
@@
 \section*{Abstract}
-This paper presents a framework for creating patient-specific neural field models from electrophysiological data.
+This paper presents a framework for creating neural field models from electrophysiological data.
 The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
@@
 \section*{Author Summary}
-With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information is becoming incredibly detailed.
-In order to make the best use of this information, patient-specific mathematical models should be formed.
+With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information and experimental data is becoming incredibly detailed.
+In order to make the best use of this information, mathematical models should be formed.
 This is particularly poignant where considering poorly understood complex systems such as large-scale dynamics of the human brain.
 There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and disease.
-In this paper, we have created a framework for creating a patient-specific mathematical model, forming a bridge between theory and electrophysiological data.
+In this paper, we have created a framework for creating a data-driven mathematical model, forming a bridge between theory and electrophysiological data.
 Within this framework, we propose rules for designing experiments and we derive the mathematical formula to create the model.
@@
     \centering
-% \subfigure[][]{
 \includegraphics{./Graph/KernelEstimate.pdf}%}

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
editted abstract
adjusted abstract with patient-specific bits

@@
 \section*{Abstract}
-This paper presents a framework for creating neural field models from electrophysiological data.
+This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data.
 The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
@@
 The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
-This framework provides a link between patient-specific neurophysiological data and theoretical neural field models.
+This framework provides a link between neurophysiological data and theoretical neural field models.
 This link may lead to greater understanding of cortical dynamics at the mesoscopic and macroscopic scales where diseases such as epilepsy are manifested.

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex

@@
 In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
-This work provides a fundamental link between the theoretical advances in neural field modelling and patient-specific data.
+This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
 The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
@@
 
-This paper has presented a method for extracting patient-specific models of synaptic dynamics from electrophysiological data.
+This paper has presented a method for creating neural field models from electrophysiological data.
 In so doing, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
@@
 
-Generating patient-specific neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a patient-specific state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
+Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a data-driven state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
 For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
@@
 For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions can exist.
-In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as during sleep and anaesthesia.
+In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
 
@@
 \subsection*{Computational Complexity}
-
 This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
Corrected some typos and added some comments to discuss

@@
 \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
+\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
+
  % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
@@
 In order to make the best use of this information, mathematical models should be formed.
-This is particularly poignant where considering poorly understood complex systems such as large-scale dynamics of the human brain.
-There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and disease.
+This is particularly poignant where considering poorly understood complex systems such as the large-scale dynamics of the human brain.
+There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and diseases.
 In this paper, we have created a framework for creating a data-driven mathematical model, forming a bridge between theory and electrophysiological data.
@@
 \section*{Introduction}
-Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the mesoscopic and macroscopic scale.
+Generating physiologically plausible neural field models is of great importance for studying brain dynamics at the mesoscopic and macroscopic scale.
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's mesoscopic and macroscopic scale dynamics remains largely theoretical.
@@
 The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
-An example of the connectivity kernel is shown in in Figure~\ref{fig:2d_kernel}.
+An example of the connectivity kernel is shown in Figure~\ref{fig:2d_kernel}.
 To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
@@
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
-This term is added to account for uncertainty and unmodelled inputs.
+This term is added to account for model uncertainty and unmodelled inputs.
 To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
@@
 \end{equation}
-An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1.
+An analytic derivation of the inner product of Equation~\ref{eq:DefGamma} of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
+which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 \end{equation}
-This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the of the connectivity kernel basis functions with the field basis functions.
-This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant an can be pre-defined analytically.
+This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the connectivity kernel basis functions with the field basis functions.
+This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically.
 This is of great importance considering the computational demands of the estimation algorithm.
@@
 
-\subsection{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
+\subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
+\ken{Guys, changed the name for this section cause it only contains spectral analysis and no real model selection.
+I can understand the argument that the spectral analysis leads to a model choice, but no model selection follows it.
+Thus I'd rather use this revised name.}
+Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
 Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
@@
 
+\ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
 Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
@@
 \end{align}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
 The total number of sigma points is $2L+1$.
@@
 \subsection*{Spatial Frequency Analysis} 
-Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+The spectral analysis described in Section~\ref{SpectralAnalysisSection} was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
 Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field.
@@
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
-This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
+This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
 \begin{figure}
@@
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
-Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
+The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
+Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
@@
 The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.}
+(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
+\ken{This is not correct!} }
 	\label{fig:ObservationFreqAnal}
@@
 This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions can exist.
+For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist.
 In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
Minor change to Future Work section

@@
 Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
-Future work should also include a more realistic synaptic response kernel, with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
+Future work should also include a synaptic response kernel with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
 

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
corrected fig5 caption

@@
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
-(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
-The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
-\ken{This is not correct!} }
+(\textbf{B}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
+(\textbf{C}) The spatial frequency response of a one-dimensional model sensor.
+The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.}
 	\label{fig:ObservationFreqAnal}

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
changes to paper suggested by David and edits from David

@@
 {\Large
-\textbf{A Data Driven Framework for Neural Field Modelling}
+\textbf{A Data-Driven Framework for Neural Field Modelling}
 }
@@
 realisations}.
-The solid line shows the actual value of the parameters and the dotted line shows the mean of the estimated parameters.
+The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
 (\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
@@
 The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-At each time point the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
+At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
   \begin{figure}
@@
 \caption{{\bf Examples of the actual and estimated neural fields and the error}.
-(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate data.
+(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to the generate data.
 (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
@@
 
-This paper has presented a method for creating neural field models from electrophysiological data.
+This paper has presented a method for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In so doing, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-The mathematical formulation we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation which allows us to perform inference efficiently.
-
-\subsection*{Patient-Specific Modelling}
-
-Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a data-driven state-space model will allow for the application of techniques from engineering to be applied to neuro-dynamics.
-For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
-In addition, a patient-specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation, thereby possibly preventing seizure onset or abating seizure activity.
-
-Kernel parameter estimation may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-
-The development of an estimation framework also has theoretical implications, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
-This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist.
-In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
+The mathematical formulation that we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation that allows us to perform inference efficiently.
 
@@
 
-This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
@@
 
-The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the sensor arrangement that is required for capturing the dominant cortical dynamics.
+The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
 Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
@@
 This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale can not be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale cannot be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
 The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
@@
 Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will results in an increased state dimension.
+A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will result in an increased state dimension.
 
@@
 
+\subsection*{Patient-Specific Modelling}
+
+Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, the development of a data-driven state-space model will allow for the application of techniques from engineering to be applied to neurodynamics.
+For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
+In addition, a patient-specific state-space model will allow application of electrical stimulation to robustly prevent the neurodynamics entering pathological regions of state-space, thereby possibly preventing seizure onset or abating seizure activity.
+
+Kernel parameter estimation may also have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+
+The development of an estimation framework also has implications for theoretical neuroscience, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
+This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
+For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist.
+In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
+
 \subsection*{Future Work}
 
-In this paper, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption.
+In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption.
 
@@
 Dean Freestone would like to thank Dr.
-Mark van Rossum for hosting him whilst visiting the University of Edinburgh where this work was undertaken.
-Parham Aram would also like to thank Andrew Hills for useful discussions and help with some code and the generation of figures.
+Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken.
+Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
 
@@
 \caption{
-\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
+\bf{Algorithm for the Unscented RTS Smoother}}
 \begin{tabular}{|c|}\hline
@@
 	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
-	$\sigma_{\gamma,t}$ & disturbance temporal variance & 0.1 & mV$^2$ \\
+	$\sigma_{\gamma,t}$ & disturbance temporal variance & 0.1 & mV \\
 	\hline 
@@
 \bf{Estimation Results}}
-\begin{tabular}{|c|ccc|}	
-\hline\hline 
+\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2.5cm}|p{1.5cm}|}
+
+\hline
 Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
-\hline\hline
+\hline
 $\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
@@
 \end{tabular}
-\begin{flushleft}Actual parameter values compared to mean parameter estimates.
+\begin{flushleft}Actual parameter values compared to mean parameter estimates obtained from the 100 Monte Carlo simulations.
 \end{flushleft}

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
edits to S1 from David

@@
 \ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
-Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
+
+Alternatively, the basis function width given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
 This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.

### 2010-06-30 ltx/PLoS/SubmissionLetter.tex
edits to S1 from David

@@
 
-I am writing to seek publication of our research article titled `A Data Driven Framework for Patient-Specific Neural Field Modelling' in PLoS Computational Biology.
+I am writing to seek publication of our research article titled `A Data-Driven Framework for Neural Field Modelling' in PLoS Computational Biology.
 
-This paper brings several new techniques to Computational Biology, where as the title suggests, we have developed a data-driven framework for generating patient-specific neural field models.
+This paper brings several new techniques to Computational Biology, where as the title suggests, we have developed a data-driven framework for generating neural field models.
 This paper is timely as it draws together several areas of cutting-edge technologies including:
 \begin{itemize}
-	\item Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques.
-	\item In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems. 
-	\item In addition, recent advances in computing power and nonlinear systems theory have made possible state estimation from nonlinear spatio-temporal systems.
+	\item increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities that have led to significant advances in neurophysiological recording techniques,
+	\item developments in neural field theory that have led to valuable insights into the mass action of cortical systems,
+	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from nonlinear spatio-temporal systems.
 \end{itemize}
 
-This work provides an essential link, bridging the data driven and theoretically driven areas of research.
+This work provides an essential link, bridging the data-driven and theoretically-driven areas of research.
 We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.
@@
 
-Since this primarily a methods paper, we have taken the option of preceding the results by the methods section.
+Due to the novel aspects of the model reduction and estimation procedure, we have taken the option of preceding the results by the methods section.
 

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
edits to letter, and minor edits to paper

--- 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
@@
 With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information and experimental data is becoming incredibly detailed.
-In order to make the best use of this information, mathematical models should be formed.
+In order to make the best use of this information, data-driven mathematical models should be formed.
 This is particularly poignant where considering poorly understood complex systems such as the large-scale dynamics of the human brain.
@@
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
+Note, Table~\ref{tab:Notation} provides a description of the notation used in this study.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
@@
 \subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
-\ken{Guys, changed the name for this section cause it only contains spectral analysis and no real model selection.
+% \ken{Guys, changed the name for this section cause it only contains spectral analysis and no real model selection.
 I can understand the argument that the spectral analysis leads to a model choice, but no model selection follows it.
@@
 
-\ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
-Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
+% \ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
+
+Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field.
+Following this, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
 This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
@@
 
-The sensors were spaced on a regular square $14 \times 14$ grid and the sensor width was set to $\sigma^2_m = 0.81$.
+The sensors were spaced on a $14 \times 14$ square grid and the sensor width was set to $\sigma^2_m = 0.81$.
 This provides a width of 1.5~mm at half the maximum amplitude of the sensor kernel.
@@
 	\caption{{\bf Spatial frequency analysis}.
-The dashed line shows the cut-off frequency (-3 dB point).
+\dean{Parham, (B) and (C) need switching as we mention the sensor first.} The dashed line shows the cut-off frequency (-3 dB point).
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
@@
 Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, the development of a data-driven state-space model will allow for the application of techniques from engineering to be applied to neurodynamics.
+Specifically, these subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems.
 For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
@@
 \section*{Tables}
+
+\begin{table}[!ht]
+\caption{
+\bf{Notation}}
+\begin{tabular}{|l|l|l|}
+	\hline
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
+	\hline
+	$\Omega$ & spatial domain & n.a.\\
+	$\mathbf{r}$ & spatial location & [mm, mm]\\
+	$t$ & time & s\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Model}}\\
+	\hline
+    $y(\mathbf{r}_n,t)$ & observation & mV\\
+    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
+	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
+	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
+	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
+	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
+	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
+	$h(t)$ & post-synaptic response kernel & mV\\
+	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
+	$\xi$ & time constant parameter & n.a.\\
+	$\eta(t)$ & Heaviside step function & n.a.\\
+	$\delta(t)$ & Dirac-delta function & n.a.\\
+	$D$ & temporal differential operator & n.a.\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
+	\hline
+   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
+   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
+   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
+   	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\
+   	$Q()$ & state transition function &\\
+   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
+   	$\mathbf{C}$ & observation matrix & n.a. \\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
+	\hline
+    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
+	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Estimation}} \\
+	\hline
+	$\mathcal{X}$ & matrix of sigma vectors & mV\\
+	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
+   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
+   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
+ 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
+   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
+	$M_t$& cross-covariance matrix & mV$^2$\\
+	$\mathcal K_{t} $ & filter gain & n.a.\\
+	$S_t$ & smoother gain & n.a.\\
+	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
+   	$\mathcal{\hat{W}}$& vector of parameter estimates (used in LS estimator) & n.a.\\	
+	\hline
+\end{tabular}
+\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper.
+The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.
+\end{flushleft}
+\label{tab:Notation}
+\end{table}
 
@@
 \caption{
-\bf{Notation}}
-\begin{tabular}{|l|l|l|}
-	\hline
-	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
-	\hline
-	$\Omega$ & spatial domain & n.a.\\
-	$\mathbf{r}$ & spatial location & [mm, mm]\\
-	$t$ & time & s\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Model}}\\
-	\hline
-    $y(\mathbf{r}_n,t)$ & observation & mV\\
-    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
-	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
-	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
-	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
-	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
-	$h(t)$ & post-synaptic response kernel & mV\\
-	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
-	$\xi$ & time constant parameter & n.a.\\
-	$\eta(t)$ & Heaviside step function & n.a.\\
-	$\delta(t)$ & Dirac-delta function & n.a.\\
-	$D$ & temporal differential operator & n.a.\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
-	\hline
-   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
-   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
-   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
-   	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\
-   	$Q()$ & state transition function &\\
-   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
-   	$\mathbf{C}$ & observation matrix & n.a. \\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
-	\hline
-    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
-	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
-	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Estimation}} \\
-	\hline
-	$\mathcal{X}$ & matrix of sigma vectors & mV\\
-	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
-   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
-   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
- 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
-   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
-	$M_t$& cross-covariance matrix & mV$^2$\\
-	$\mathcal K_{t} $ & filter gain & n.a.\\
-	$S_t$ & smoother gain & n.a.\\
-	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
-   	$\mathcal{\hat{W}}$& vector of parameter estimates (used in LS estimator) & n.a.\\	
-	\hline
-\end{tabular}
-\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper.
-The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.
-\end{flushleft}
-\label{tab:label}
-\end{table}
-
-\begin{table}[!ht]
-\caption{
 \bf{Estimation Results}}

### 2010-06-30 ltx/PLoS/SubmissionLetter.tex
edits to letter, and minor edits to paper

@@
 
-\marginsize {1.7cm}{1.5cm}{2cm}{2cm} 				%<-use this for checking equation length
+\marginsize {1.7cm}{1.5cm}{1cm}{1cm} 				%<-use this for checking equation length
 
@@
 \address{Department of Electrical \\
-and Electronic Engineering \\ The University of Melbourne \\ Parkville \\ Victoria, 3010 \\ Australia}
+and Electronic Engineering \\ The University of Melbourne \\ Victoria, 3010 \\ Australia}
 
 \begin{document}
-
-\begin{letter}{Editor/Reviewer \\ PloS Computational Biology}
+\vspace{-1cm}
+\begin{letter}{Editor/Reviewer \\ PLoS Computational Biology}
 
@@
 
-This paper brings several new techniques to Computational Biology, where as the title suggests, we have developed a data-driven framework for generating neural field models.
-This paper is timely as it draws together several areas of cutting-edge technologies including:
+This paper brings several new techniques to the field of computational biology, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model.
+Our aim in this work is to model the intracortical connectivity and synaptic dynamics of an individual patient or experimental subject.
+These subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems, with application to epilepsy and other neurological disorders, and to brain-computer interfaces.
+
+This paper is timely as it draws together and is built upon several cutting-edge technologies including:
 \begin{itemize}
-	\item increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities that have led to significant advances in neurophysiological recording techniques,
+	\item increases in bandwidths in data acquisition systems, higher electrode technology and data storage capabilities that have led to significant advances in neurophysiological recording techniques, 
 	\item developments in neural field theory that have led to valuable insights into the mass action of cortical systems,
-	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from nonlinear spatio-temporal systems.
+	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from large-scale nonlinear spatio-temporal systems.
 \end{itemize}
 
-This work provides an essential link, bridging the data-driven and theoretically-driven areas of research.
-We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.
+This work provides an essential link between data-driven and theoretically-driven areas of research.
+We hope that this work will help to bring together the experimental and theoretical communities by providing a framework upon which both new and existing hypotheses in computational neuroscience may be tested.
 
@@
 \begin{itemize}
-	\item the representation of a continuum neural field model as reduced finite-dimensional state-space model,
-	\item derivations for the conditions for placement and geometry of sensors/electrodes to sufficiently sample a neural field to capture significant cortical dynamics,
-	\item conditions for the model reduction to represent the neural field as a finite-dimensional state-space model,
-	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation,
-	\item a derivation for an algorithm for estimating intracortical connectivity and synaptic dynamics using the neural field equations.
+	\item the representation of a continuum neural field model as a reduced finite-dimensional state-space model and the necessary conditions for representing the neural field by a basis function decomposition;
+	\item derivations of the necessary conditions for placement and geometry of sensors/electrodes to sufficiently sample a neural field in order to capture the significant cortical dynamics;
+	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation;
+	\item a derivation of an algorithm for estimating intracortical connectivity and synaptic dynamics using the neural field equations.
 \end{itemize}
 
-Due to the novel aspects of the model reduction and estimation procedure, we have taken the option of preceding the results by the methods section.
+Due to the novel aspects of the model reduction and estimation procedure, we have chosen to precede the Results section with the Methods section.
 
-Thank you for your time and consideration in reviewing this article.
-Please contact us if you have any questions regarding any aspects of this paper.
-I look forward to hearing the outcome of the review soon.
+Thank you for your time and consideration in reviewing this article. We look forward to hearing the outcome of the review.
 

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
small edits to discussion and a rearrangement

@@
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
-
 To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
@@
 \subsection*{Computational Complexity}
-This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale cannot be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
 The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
@@
 \subsection*{Patient-Specific Modelling}
+This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale cannot be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
 
@@
 
-In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption.
-
+In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
+In future work, we plan to relax this assumption.
 In addition, we have assumed that the neural field is isotropic and homogeneous.

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
Comment and minor changes in the spectral analysis section

@@
 Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field.
-Following this, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
-This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
+The spatial cut-off frequency of this smoothed field represented by the decomposition can be determined from spectral analysis.
+\ken{What is the rationale for the following sentence?} This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
 To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
One change to the spectral analysis section

--- 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
@@
 
-Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field.
-Following this, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis.
-This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors.
+Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the field spatial bandwidth.
+This has the added advantage of allowing an approximate representation by a low order model thus reducing the computational demands of the estimation process.
+The spatial cut-off frequency of this smoothed field is thus a user choice and the extend of its effect can be determined from spectral analysis.
 To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
changed fig2 and fig5

--- 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
@@
 	\caption{{\bf Spatial frequency analysis}.
-\dean{Parham, (B) and (C) need switching as we mention the sensor first.} The dashed line shows the cut-off frequency (-3 dB point).
+The dashed line shows the cut-off frequency (-3 dB point).
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
-(\textbf{B}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
-(\textbf{C}) The spatial frequency response of a one-dimensional model sensor.
-The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.}
+(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
+The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
+(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
+}
 	\label{fig:ObservationFreqAnal}

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
minor corrections

@@
 	w\left(\mathbf{r},\mathbf{r}'\right) 
-	f\left( v\left( \mathbf{r}',t \right)\right)
+	f\left( v\left( \mathbf{r}',t' \right)\right)
 	\textrm{d}\mathbf{r}'dt'.
@@
 \end{equation}
-where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 \begin{equation}\label{eq:ReducedObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t\textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
 \end{equation}
@@
 \caption{{\bf Examples of the actual and estimated neural fields and the error}.
-(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to the generate data.
+(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
 (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
@@
 
-The frequency analysis and model selection tools presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
+The frequency analysis presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
 Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
added some comments

@@
 This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data.
-The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
+The Wilson and Cowen \parham{shouldn't be Cowan?} or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
 To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
 To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model.
-Spatial frequency analysis methods are introduced for model selection by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
+Spatial frequency analysis methods are introduced for model selection \parham{ model selection bit should be removed} by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen \parham{Shouldn't be Cowan?} (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data.
 Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
changes to tables

@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions.
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
 Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the connectivity kernel basis functions with the field basis functions.
-This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically.
+This transformation provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically.
 This is of great importance considering the computational demands of the estimation algorithm.
@@
 	\hline
-    $y(\mathbf{r}_n,t)$ & observation & mV\\
+    $y_t$ & observation & mV\\
     $v(\mathbf{r},t)$ & mean membrane potential & mV \\
@@
 	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
-	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
 	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
@@
    	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
+	$n_{\theta}$ & number of connectivity kernel basis functions & n.a.\\
+   	$\boldsymbol{\Psi}(\mathbf{r}')$ & scaled convolution of the connectivity kernel basis functions with the field basis functions& n.a.\\
    	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\
-   	$Q()$ & state transition function &\\
+   	$Q()$ & state transition function & n.a.\\
    	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
@@
 	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
-	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
+	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\
 	\hline
@@
 	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
+	$N$ & number of sensors & 196 & n.a.\\ 
 	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
@@
 	\hline
-	$\Delta_{\phi}$ & Distance between field basis functions & 2.5 & mm \\
+	$L$ & number of basis functions& 81 & n.a.\\
+	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
@@
 	\hline
-	$\rho_y$ & Sensor over-sampling parameter & 1 & n.a.\\
-	$\rho_\phi$ & Field basis function over-sampling parameter & 1 & n.a.\\
+	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
+	$\rho_\phi$ & field basis function over-sampling parameter & 1 & n.a.\\
 	\hline 
@@
 	\hline
-	$\alpha$& Determines the spread of sigma points & 0.001 & n.a.\\
-	$\beta$& Prior knowledge of the sigma points distribution & 2 & n.a.\\
-	$\kappa$& Scaling parameter & $3-L$ & n.a.\\
+	$\alpha$& determines the spread of sigma points & 0.001 & n.a.\\
+	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
+	$\kappa$& scaling parameter $(3-L)$& -78 & n.a.\\
+	$\lambda$& scaling parameter & -80.99 & n.a.\\
 	\hline

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
for merge with Parham

@@
 This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data.
-The Wilson and Cowen \parham{shouldn't be Cowan?} or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
+The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
 To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
 To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model.
-Spatial frequency analysis methods are introduced for model selection \parham{ model selection bit should be removed} by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
+Spatial frequency analysis methods are introduced that systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen \parham{Shouldn't be Cowan?} (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data.
 Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
@@
 
-Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the field spatial bandwidth.
-This has the added advantage of allowing an approximate representation by a low order model thus reducing the computational demands of the estimation process.
-The spatial cut-off frequency of this smoothed field is thus a user choice and the extend of its effect can be determined from spectral analysis.
+Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the fields spatial bandwidth.
+This allows an approximate representation by a lower order model (fewer basis functions), thus reducing the computational demands of the estimation process.
+The spatial cut-off frequency of this smoothed field becomes a user choice and can be determined using spectral analysis.
 To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
minor corrections
small change to paper

@@
 \end{equation}
-where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point) with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$.
+where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point). %with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$. 
 Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy 
@@
 
-Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the fields spatial bandwidth.
+Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the spatial bandwidth of the approximated field.
 This allows an approximate representation by a lower order model (fewer basis functions), thus reducing the computational demands of the estimation process.
@@
 Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameter errors falling to less than $10^{-4}$ after six iterations.
 \begin{figure}
@@
 This paper has presented a method for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-In so doing, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
+In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
 The mathematical formulation that we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation that allows us to perform inference efficiently.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
restored parhams changes after I stuffed up the merge
moved figure to the end of document

@@
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
-\begin{figure}
-   	\begin{center}
-   		\includegraphics{./Graph/Cross_section_kernel.pdf} 
-   	\end{center}
-   	\caption{{\bf Mexican-hat connectivity kernel.} The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
-The kernel decays asymptotically to zero.}
- 	\label{fig:2d_kernel}
-   \end{figure}
+
 The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
@@
 An example of a one-dimensional field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
-\begin{figure}
-   	\begin{center}
-   		\includegraphics{./Graph/FieldDecomposition.pdf} 
-   	\end{center}
-   	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
-The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
-	\label{fig:FieldDecomposition}
-   \end{figure}
+
 The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
@@
 \subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
-% \ken{Guys, changed the name for this section cause it only contains spectral analysis and no real model selection.
-I can understand the argument that the spectral analysis leads to a model choice, but no model selection follows it.
-Thus I'd rather use this revised name.}
 Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
@@
 \end{equation}
-where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point). %with $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$. 
-Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy 
+where $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point). Given such a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy 
 \begin{equation}
@@
 
-% \ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
-
 Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the spatial bandwidth of the approximated field.
@@
 \begin{equation}\label{eq:CutoffFromBasisFuncWidth}
-	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
+	\nu_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
 \end{equation}
@@
 This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
+
+\subsection*{Spatial Frequency Analysis} 
+The spectral analysis described in Section~\ref{SpectralAnalysisSection} was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field.
+The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
+This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
+
+The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(A).
+The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
+The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(B).
+Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
+
+Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
+This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C).
+The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B).
+This figure illustrates the band-limiting effect of the basis function decomposition when compared to Figure~\ref{fig:FFTTrueEstimate}(A).
+
+\subsection*{State and Parameter Estimates} 
+\label{sec:state_and_param_results}
+To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated.
+Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
+The initial state and parameters were unknown to the estimator.
+Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameter errors falling to less than $10^{-4}$ after six iterations.
+
+Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}.
+The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
+The biases show the percentage differences between the actual values and the mean parameter estimates.
+The mean estimates are in good agreement with the actual values.
+
+The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
+The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
+
+The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
+The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
+At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
+The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
+It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
+
+\section*{Discussion}\label{DiscussionSection}
+This paper has presented a method for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
+The mathematical formulation that we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation that allows us to perform inference efficiently.
+
+\subsection*{Implications for Experiment Design}
+As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
+To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
+Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
+Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
+By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+
+The frequency analysis presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
+Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
+In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
+
+\subsection*{Computational Complexity}
+The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
+Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
+A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
+Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
+An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
+
+Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
+Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
+A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will result in an increased state dimension.
+
+Due to the relationship between the number of states in the model and the number of model parameters, increases in dimensionality lead to increases in uncertainty of the estimates.
+In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
+
+The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
+Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
+These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
+This enables estimation of a larger field with a lower dimensional state vector than would be possible otherwise.
+
+The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
+This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
+
+\subsection*{Patient-Specific Modelling}
+This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
+The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale cannot be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
+
+Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
+Specifically, these subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems.
+For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
+In addition, a patient-specific state-space model will allow application of electrical stimulation to robustly prevent the neurodynamics entering pathological regions of state-space, thereby possibly preventing seizure onset or abating seizure activity.
+
+Kernel parameter estimation may also have significant impact on the treatment of disease.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+These very different mechanisms would require very different medications for successful treatment.
+However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
+Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
+
+The development of an estimation framework also has implications for theoretical neuroscience, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
+This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
+For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist.
+In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
+
+\subsection*{Future Work}
+
+In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
+In future work, we plan to relax this assumption.
+In addition, we have assumed that the neural field is isotropic and homogeneous.
+It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
+However, the assumption of homogeneity is quite strong.
+Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
+Future work should also include a synaptic response kernel with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
+
+% Do NOT remove this, even if you are not including acknowledgments
+\section*{Acknowledgments}
+Dean Freestone would like to thank Dr.
+Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken.
+Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
+
+% This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
+Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
+
+% \section*{References}
+% The bibtex filename
+\bibliography{BrainIDE}
+
+\section*{Figure Legends}
+%\begin{figure}[!ht]
+%\begin{center}
+%%\includegraphics[width=4in]{figure_name.2.eps}
+%\end{center}
+%\caption{
+%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
+%should be left justified, as specified by the options to the caption 
+%package.
+%}
+%\label{Figure_label}
+%\end{figure}
+
+\begin{figure}
+   	\begin{center}
+   		\includegraphics{./Graph/Cross_section_kernel.pdf} 
+   	\end{center}
+   	\caption{{\bf Mexican-hat connectivity kernel.} The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+The kernel decays asymptotically to zero.}
+ 	\label{fig:2d_kernel}
+   \end{figure}
+
+\begin{figure}
+   	\begin{center}
+   		\includegraphics{./Graph/FieldDecomposition.pdf} 
+   	\end{center}
+   	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
+The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
+	\label{fig:FieldDecomposition}
+   \end{figure}
+
  \begin{figure}
@@
  \end{figure}
-\subsection*{Spatial Frequency Analysis} 
-The spectral analysis described in Section~\ref{SpectralAnalysisSection} was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field.
-The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
-This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
+
 \begin{figure}
@@
 
-The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(A).
-The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
-The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(B).
-Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
-Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
-This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C).
-The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B).
-This figure illustrates the band-limiting effect of the basis function decomposition when compared to Figure~\ref{fig:FFTTrueEstimate}(A).
 \begin{figure*}[!ht] 
@@
 \end{figure*}
-\subsection*{State and Parameter Estimates} 
-\label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated.
-Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
-The initial state and parameters were unknown to the estimator.
-Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameter errors falling to less than $10^{-4}$ after six iterations.
+
 \begin{figure}
@@
 
-Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}.
-The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
-The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good agreement with the actual values.
 \begin{figure}
@@
 
-The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
-The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
 \begin{figure}
@@
 \end{figure}
-The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
-At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
-The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
-The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
+
   \begin{figure}
@@
 
-\section*{Discussion}
-\label{DiscussionSection}
-
-This paper has presented a method for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-The mathematical formulation that we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation that allows us to perform inference efficiently.
-
-\subsection*{Implications for Experiment Design}
-
-As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
-To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
-Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
-Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
-By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
-
-The frequency analysis presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
-Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
-In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
-
-\subsection*{Computational Complexity}
-The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
-Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
-A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
-Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
-
-Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
-Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will result in an increased state dimension.
-
-Due to the relationship between the number of states in the model and the number of model parameters, increases in dimensionality lead to increases in uncertainty of the estimates.
-In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
-
-The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
-Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
-These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-This enables estimation of a larger field with a lower dimensional state vector than would be possible otherwise.
-
-The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
-This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
-
-\subsection*{Patient-Specific Modelling}
-This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale cannot be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
-
-Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
-Specifically, these subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems.
-For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
-In addition, a patient-specific state-space model will allow application of electrical stimulation to robustly prevent the neurodynamics entering pathological regions of state-space, thereby possibly preventing seizure onset or abating seizure activity.
-
-Kernel parameter estimation may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
-These very different mechanisms would require very different medications for successful treatment.
-However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting.
-Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies.
-
-The development of an estimation framework also has implications for theoretical neuroscience, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
-This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
-For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist.
-In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
-
-\subsection*{Future Work}
-
-In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
-In future work, we plan to relax this assumption.
-In addition, we have assumed that the neural field is isotropic and homogeneous.
-It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
-However, the assumption of homogeneity is quite strong.
-Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
-Future work should also include a synaptic response kernel with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
-
-% Do NOT remove this, even if you are not including acknowledgments
-\section*{Acknowledgments}
-Dean Freestone would like to thank Dr.
-Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken.
-Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
-
-% This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
-The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
-Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
-
-% \section*{References}
-% The bibtex filename
-\bibliography{BrainIDE}
-
-\section*{Figure Legends}
-%\begin{figure}[!ht]
-%\begin{center}
-%%\includegraphics[width=4in]{figure_name.2.eps}
-%\end{center}
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
-%should be left justified, as specified by the options to the caption 
-%package.
-%}
-%\label{Figure_label}
-%\end{figure}
-
 \section*{Tables}
@@
 	$h(t)$ & post-synaptic response kernel & mV\\
-	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
-	$\xi$ & time constant parameter & n.a.\\
+	$\zeta$, $\xi$ & inverse synaptic time constant \& time constant parameter & s$^{-1}$, n.a.\\
 	$\eta(t)$ & Heaviside step function & n.a.\\
@@
    	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
-   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
-	$n_{\theta}$ & number of connectivity kernel basis functions & n.a.\\
-   	$\boldsymbol{\Psi}(\mathbf{r}')$ & scaled convolution of the connectivity kernel basis functions with the field basis functions& n.a.\\
+   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of $n_{\theta}$ connectivity kernel basis functions & n.a.\\
+   	$\boldsymbol{\Psi}(\mathbf{r}')$ & decomposition connectivity matrix & n.a.\\
    	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
final edit of text

@@
 To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model.
-Spatial frequency analysis methods are introduced that systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field.
+Spatial frequency analysis methods are introduced that systematically specify the basis function configuration required to capture the dominant characteristics of the neural field.
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
@@
 This is particularly poignant where considering poorly understood complex systems such as the large-scale dynamics of the human brain.
-There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and diseases.
+There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of interesting phenomena associated with various cognitive states and diseases.
 In this paper, we have created a framework for creating a data-driven mathematical model, forming a bridge between theory and electrophysiological data.
@@
 
-An estimation framework for neural field models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has recently been proposed for studying evoked potential dynamics.
+An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has recently been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
 Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with modified WC neural field equations~\cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatio-temporal neural fields.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatiotemporal neural fields.
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
@@
 We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
-In addition, a method is presented for estimating the connectivity structure and the synaptic time dynamics.
+In addition, a method is presented for estimating the connectivity structure and the synaptic dynamics.
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
-Our work builds on recent work which shows that it is possible to estimate local coupling of spatio-temporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
-The key development of this previous work was to represent the spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
+Our study builds on recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
+The key development of this previous work was to represent a spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
@@
 The parameter $\varsigma$ governs the slope of the sigmoid.
-By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatio-temporal model
+By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model
 \begin{equation}
@@
 
-The mapping between the membrane voltage and the electrophysiological data (iEEG/LFP) is modelled using the observation function that incorporates sensors with a spatial extent by
+The mapping between the membrane voltage and the electrophysiological data is modelled using the observation function that incorporates sensors with a spatial extent by
 \begin{equation}
@@
 \end{equation}
-An analytic derivation of the inner product of Equation~\ref{eq:DefGamma} of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\Gamma$, is provided in the Supporting Information, S1.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
-% \mike{This doesn't seem to be the isotropy of the kernel, it's the isotropy of the kernel's basis functions.
-The whole thing holds for the kernel itself or, if they're isotropic, the basis functions.
-You just can't say one and write the other!
-You could put something like ``..
-by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it''}
-% \dean{nice point Mike. I have changed it like you suggested.}
+
 \begin{equation}
@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
-Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
 \begin{equation}
@@
 This is of great importance considering the computational demands of the estimation algorithm.
-
-% \dean{Cheers Mike, I think it is better now.}
-% \mike{This is a bit deceptive.
-What you've actually done is move the convolution of the kernel basis functions with the nonlinearly transformed field to the convolution of field basis functions with the kernel basis functions.
-To see this, you could've done the same trick by just calling $\int \psi(r-r')f(\phi^Tx_t)dr' = A(r)$ and the saying hey!
-We now have the inner product $\int \phi(r) A(r) dr$.
-The point is that you can do the convolution $\phi * \psi$ analytically whereas you have to do the inner product $\Psi f(\phi^Tx_t)$ numerically.
-I wouldn't make a big deal about this except a fuss is made (rightly so) about this in the Discussion section.}
 
@@
 
-In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing us from positioning sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
+In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing placement of sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
 However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
@@
 The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
-To demonstrate this, we begin with the two-dimensional Gaussian basis function located at the origin defined as
+To demonstrate this, we begin with a two-dimensional Gaussian basis function located at the origin, defined as
 \begin{equation}\label{eq:BasisFunctionAtOrigin}
@@
 
-Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the spatial bandwidth of the approximated field.
-This allows an approximate representation by a lower order model (fewer basis functions), thus reducing the computational demands of the estimation process.
-The spatial cut-off frequency of this smoothed field becomes a user choice and can be determined using spectral analysis.
+Alternatively, the basis function width can be set to provide a desired level of smoothness in the approximated field by reducing the spatial bandwidth.
+This allows for an approximate representation by a lower order model (fewer basis functions), thus reducing the computational demands of the estimation process.
+The spatial cut-off frequency of this smoothed field becomes a design choice.
 To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
@@
 The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state vector sequence guaranteeing that the initial estimated parameter set forms a stable kernel.
+The algorithm is initialised using a bounded random state vector sequence, guaranteeing that the initial estimated parameter set forms a stable kernel.
 
@@
 Therefore, the additive form of the URTSS is used.
+This has a significant computational advantage over using the alternative multiplicative form of the filter.
 
@@
 \end{equation}
-Now given a state estimate sequence from an iteration of the URTSS, we can write
+Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
 \begin{align*}
@@
 The spectral analysis described in Section~\ref{SpectralAnalysisSection} was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field.
+Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:FFTTrueEstimate}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
@@
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C).
-The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B).
-This figure illustrates the band-limiting effect of the basis function decomposition when compared to Figure~\ref{fig:FFTTrueEstimate}(A).
+The band-limiting effect of the basis function decomposition can seen when comparing Figure~\ref{fig:FFTTrueEstimate}(A) to Figure~\ref{fig:FFTTrueEstimate}(B).
 
@@
 Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameter errors falling to less than $10^{-4}$ after six iterations.
+Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
 
@@
 \section*{Discussion}\label{DiscussionSection}
-This paper has presented a method for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+This paper has presented a framework for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
@@
 In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density recordings~\cite{Brinkmann2009}.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.
 
@@
 
-Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation for discrete (in space and time) nonlinear spatio-temporal systems.
+Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
 Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
@@
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-This enables estimation of a larger field with a lower dimensional state vector than would be possible otherwise.
+This enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
 
-The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
+The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel with the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
@@
 
-Kernel parameter estimation may also have significant impact on the treatment of disease.
+Connectivity kernel parameter estimation may also have significant impact on the treatment of disease.
 For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
@@
 The development of an estimation framework also has implications for theoretical neuroscience, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
-This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics.
+This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of mesoscopic and macroscopic neurodynamics.
 For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist.
@@
 It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
-However, the assumption of homogeneity is quite strong.
+However, the assumption of homogeneity is quite strong as the size of the neural field becomes larger.
 Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
-Future work should also include a synaptic response kernel with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
+Future work should also include a synaptic response kernel with finite rise and decay times, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.
 
@@
 Dean Freestone would like to thank Dr.
-Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken.
+Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Matt.
 Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
@@
 	$S_t$ & smoother gain & n.a.\\
-	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
+	$q()$ & nonlinear state function (used in LS estimator) & n.a.\\
    	$\mathcal{\hat{W}}$& vector of parameter estimates (used in LS estimator) & n.a.\\	

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
final, final edit before removing the cross-referncing

@@
 Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
-Future work should also include a synaptic response kernel with finite rise and decay times, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.
+In addition, natural extensions of this framework are the inclusion of a post-synaptic response kernel with a finite rise and decay time, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.
 
@@
 Dean Freestone would like to thank Dr.
-Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Matt.
+Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Dr.
+Matthias Hennig for useful discussions and feedback.
 Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
removed cross-refernces

@@
 This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
-The paper proceeds by first deriving the continuum neural field equations in Section~\ref{NeuralModelSection}.
-Then a finite dimensional neural field model is derived.
+The paper proceeds by first deriving the continuum neural field equations.
+Then a finite-dimensional neural field model is derived.
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-Section~\ref{SpectralAnalysisSection} establishes conditions using spatial frequency analysis for both sensor and basis function spacing and width, such that the dominant dynamics of the neural field can be represented by the reduced model.
-The state and parameter estimation procedure is described in Section~\ref{StateAndParameterEstimationSection}.
-The results for the spatial frequency analysis and parameter estimation are then presented in Section~\ref{ResultsSection}.
-The implications and limitations of this framework are discussed in Section~\ref{DiscussionSection} along with planned future developments.
+The next section establishes conditions using spatial frequency analysis for both sensor and basis function spacing and width, such that the dominant dynamics of the neural field can be represented by the reduced model.
+The state and parameter estimation procedure is described in the following section.
+The results for the spatial frequency analysis and parameter estimation are then presented.
+Finally, the implications and limitations of this framework are discussed along with planned future developments.
 
@@
 
-\subsection{Neural Field Model}\label{NeuralModelSection} 
+\subsection*{Neural Field Model}\label{NeuralModelSection} 
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 
-\subsection{Derivation of the Integro-Difference Equation Representation}
+\subsection*{Derivation of the Integro-Difference Equation Representation}
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
@@
 
-\subsection{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
+\subsection*{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
 In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
@@
 
-The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}).
-The connectivity kernel can also be decomposed as
+The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in the following section). The connectivity kernel can also be decomposed as 
 \begin{equation}\label{DefKernelDecomp}
@@
 
-\subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
+\subsection*{Spectral Analysis}\label{SpectralAnalysisSection} 
 Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
@@
 
-\subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
+\subsection*{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
@@
 \section*{Results}\label{ResultsSection} In this section, we provide a demonstration of the estimation procedure using the new methods that are described above.
-The full neural field model described in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation.
+The full neural field model was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Parameters}.
@@
 The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
-Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis methods presented in Section~\ref{SpectralAnalysisSection}.
+Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in Methods section.
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
@@
 	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
-	$\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
 	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\

### 2010-07-01 ltx/PLoS/SubmissionLetter.tex
small chage to submission letter
small edits to letter

@@
 
-This paper brings several new techniques to the field of computational biology, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model.
+This paper brings several new techniques to the field of computational biology, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model from electrophysiological data.
 Our aim in this work is to model the intracortical connectivity and synaptic dynamics of an individual patient or experimental subject.
-These subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems, with application to epilepsy and other neurological disorders, and to brain-computer interfaces.
+These subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems, particularly to epilepsy and other neurological disorders, and to brain-computer interfaces.
 
@@
 	\item developments in neural field theory that have led to valuable insights into the mass action of cortical systems,
-	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from large-scale nonlinear spatio-temporal systems.
+	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from large-scale nonlinear spatiotemporal systems.
 \end{itemize}
@@
 	\item derivations of the necessary conditions for placement and geometry of sensors/electrodes to sufficiently sample a neural field in order to capture the significant cortical dynamics;
-	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation;
+	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation of a spatiotemporal neural system;
 	\item a derivation of an algorithm for estimating intracortical connectivity and synaptic dynamics using the neural field equations.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
removed some labels from the figures, as a few of them had more than 1 for some weird reason
couple of very minor edits

@@
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-Note, Table~\ref{tab:Notation} provides a description of the notation used in this study.
+Table~\ref{tab:Notation} provides a description of the notation used in this study.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
@@
 
-The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function 
 \begin{equation}
@@
 \end{equation}
-To make the simplification, we first define
+To make the simplification, we define
 \begin{equation}\label{eq:DefPsi}
@@
 The spatial cut-off frequency of this smoothed field becomes a design choice.
-To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
+To calculate the cut-off frequency imposed by the basis function width, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
 \begin{equation}\label{eq:CutoffFromBasisFuncWidth}
@@
 \subsection*{Spatial Frequency Analysis} 
-The spectral analysis described in Section~\ref{SpectralAnalysisSection} was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
+The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
 Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:FFTTrueEstimate}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
@@
 
-\begin{figure}
+\begin{figure}[!ht]
 \begin{center}
@@
 
- \begin{figure}
+\begin{figure}[!ht]
 \begin{center}
@@
 
-\begin{figure}
-\centering
-\label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Graph/FFTField.pdf}
+\end{center}
 \caption{{\bf Spatial frequency analysis of the neural field}.
@@
 
-\begin{figure}
-        \centering
+\begin{figure}[!ht]
+\begin{center}
 \includegraphics{./Graph/convergence.pdf}
+\end{center}
 \caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 100 runs.
@@
 
-\begin{figure}
-    \centering
+\begin{figure}[!ht]
+\begin{center}
 \includegraphics{./Graph/ParametesDistributions.pdf}
+\end{center}
 \caption{{\bf Histograms of the parameter estimates over 100
@@
 
-\begin{figure}
-    \centering
-\includegraphics{./Graph/KernelEstimate.pdf}%}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Graph/KernelEstimate.pdf}
+\end{center}
 \caption{{\bf Cross-section of connectivity kernel estimate}.
@@
 
-  \begin{figure}
+\begin{figure}[!ht]
 \begin{center}
@@
 
-\begin{figure*}
-\centering 
-\label{fig:TrueField}\includegraphics{./Graph/FieldTrueEstimationError.pdf}
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/FieldTrueEstimationError.pdf}
+\end{center}
 \caption{{\bf Examples of the actual and estimated neural fields and the error}.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
missed a couple of cross-refs that need removal

@@
 \subsection*{Implications for Experiment Design}
-As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
+As seen in Figure~\ref{fig:Parameters}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
@@
 
-The frequency analysis presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
+The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
 Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
changed the description of the convolution swapping bit.

@@
 \begin{equation}
-	\label{reduced continuous model}\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta}
+	\label{reduced continuous model}
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta}
 	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
@@
 	\label{StartofReduction}
-	\lefteqn{ \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1}=} \\
- &T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}}\boldsymbol{\theta}  + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t+
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1}= &
+ T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}}\boldsymbol{\theta}  \\
+& + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t +
 \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}. 
@@
 \end{equation}
-This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the connectivity kernel basis functions with the field basis functions.
-This transformation provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically.
-This is of great importance considering the computational demands of the estimation algorithm.
+This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in \ref{reduced continuous model}, which is computationally demanding, with the convolution in \ref{eq:DefPsi}.
+This provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ can be calculated analytically.
+This is of great importance as it lowers the computational demands of the estimation algorithm.
 

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
added new figures
changed figure names in the tex file

@@
 The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
-An example of the connectivity kernel is shown in Figure~\ref{fig:2d_kernel}.
+An example of the connectivity kernel is shown in Figure~\ref{fig:Figure1}.
 To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
@@
 where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-An example of a one-dimensional field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
 
@@
 When generating the simulated data, we assumed free boundary conditions for the neural field.
-An example of the simulated field can be seen in Figure~\ref{fig:experimental design}(A).
-Figure~\ref{fig:experimental design}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:experimental design}(C) shows the power spectral density (PSD) of the simulated time-series.
+An example of the simulated field can be seen in Figure~\ref{fig:Figure3}(A).
+Figure~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
 The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:FFTTrueEstimate}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
+Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
@@
 
-The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(A).
+The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(A).
 The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(B).
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C).
-The band-limiting effect of the basis function decomposition can seen when comparing Figure~\ref{fig:FFTTrueEstimate}(A) to Figure~\ref{fig:FFTTrueEstimate}(B).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
+The band-limiting effect of the basis function decomposition can seen when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
 
@@
 Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
-Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
+Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
 
-Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Parameters}.
+Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Figure7}.
 The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
@@
 
-The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:KernelEstimates}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
+The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
 The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Parameters}(C).
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
 
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}, with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
 At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
-The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:FieldEstimate}.
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:FieldEstimate}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:FieldEstimate}(A)), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.
 
@@
 \subsection*{Implications for Experiment Design}
-As seen in Figure~\ref{fig:Parameters}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
+As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
@@
 \begin{center}
-\includegraphics{./Graph/Cross_section_kernel.pdf} 
+\includegraphics{./Graph/pdf/Figure1.pdf} 
 \end{center}
@@
 The kernel decays asymptotically to zero.}
-\label{fig:2d_kernel}
+\label{fig:Figure1}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/FieldDecomposition.pdf} 
+\includegraphics{./Graph/pdf/Figure2.pdf} 
 \end{center}
@@
 The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
-\label{fig:FieldDecomposition}
+\label{fig:Figure2}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/ExperimentalFigure.pdf}
+\includegraphics{./Graph/pdf/Figure3.pdf}
 \end{center}
@@
 (\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
-\label{fig:experimental design}
+\label{fig:Figure3}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/FFTField.pdf}
+\includegraphics{./Graph/pdf/Figure4.pdf}
 \end{center}
@@
 The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
-\label{fig:FFTTrueEstimate}
+\label{fig:Figure4}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
+\includegraphics{./Graph/pdf/Figure5.pdf}	
 \end{center}
@@
 }
-\label{fig:ObservationFreqAnal}
+\label{fig:Figure5}
 \end{figure*}
@@
 \begin{center}
-\includegraphics{./Graph/convergence.pdf}
+\includegraphics{./Graph/pdf/Figure6.pdf}
 \end{center}
@@
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
-\label{fig:ParametersConvergence}
+\label{fig:Figure6}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/ParametesDistributions.pdf}
+\includegraphics{./Graph/pdf/Figure7.pdf}
 \end{center}
@@
 (\textbf{D}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
-\label{fig:Parameters}
+\label{fig:Figure7}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/KernelEstimate.pdf}
+\includegraphics{./Graph/pdf/Figure8.pdf}
 \end{center}
@@
 The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
-\label{fig:KernelEstimates}
+\label{fig:Figure8}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/MRMSE.pdf} 
+\includegraphics{./Graph/pdf/Figure9.pdf} 
 \end{center}
 \caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
-\label{fig:RMSE}
+\label{fig:Figure9}
 \end{figure}
@@
 \begin{center}
-\includegraphics{./Graph/FieldTrueEstimationError.pdf}
+\includegraphics{./Graph/pdf/Figure10.pdf}
 \end{center}
@@
 The error shows high frequency behaviour.}
-\label{fig:FieldEstimate}
+\label{fig:Figure10}
 \end{figure*}

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
edit disturbance variance in table3
nimor edit

@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
 Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
-	$\sigma_{\gamma,t}$ & disturbance temporal variance & 0.1 & mV \\
+	$\sigma_{d}$ & disturbance variance & 0.1 & mV \\
 	\hline 

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
minor correction

@@
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
-The band-limiting effect of the basis function decomposition can seen when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
+The band-limiting effect of the basis function decomposition can be seen when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
 
@@
 \end{tabular}
-\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper.
+\begin{flushleft}The first column of the table gives the symbols for all the notation used in the paper.
 The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
minor correction

@@
 $\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
+$\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
 $\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
put equation blah withmikes edits

--- 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
@@
 \end{equation}
-This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in \ref{reduced continuous model}, which is computationally demanding, with the convolution in \ref{eq:DefPsi}.
+This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}.
 This provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ can be calculated analytically.

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
minor correction
minor correction in table3

@@
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm.
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.08~mm.
 This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
@@
 \end{figure*}
-
 \section*{Tables}
@@
 	$T_s$ & time step & $0.001$ & s\\
-	$T$ & number of time steps used in estimation & 0.4 & s\\
+	$T$ & number of time steps used in estimation & 400 & n.a.\\
 	\hline 

### 2010-07-06 ltx/first_order_framework/LaTeX_Manuscript.tex
still restructuring

--- 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
@@
 \section*{Abstract}
+Since the mid 1970s there has been significant developments in generating neural field models that provide theoretical insights into macroscopic neurodynamics, which have previously been impossible to gain from experimental data alone.
+In parallel to these developments, technological advances have led to significant increases into the spatiotemporal resolution of data acquired in electrophysiological recording systems.
+In order to make the best of these developments, a method is required for relating data to the mathematical models.
+
 This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data.
@@
 The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
-The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure.
-This framework provides a link between neurophysiological data and theoretical neural field models.
+The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
+
+This framework provides a link between electrophysiological data and theoretical neural field models.
 This link may lead to greater understanding of cortical dynamics at the mesoscopic and macroscopic scales where diseases such as epilepsy are manifested.
-
 % Please keep the Author Summary between 150 and 200 words
@@
 \end{center}
-\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant.
+\caption{{\bf Example of the spatiotemporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant.
 (\textbf{B}) Data generated by the full neural field model from the first 5 sensors.

### 2010-07-06 ltx/first_order_framework/SupportingInformation.tex
still restructuring

--- 2010-06-28 ltx/PLoS/SupportingInformation.tex
@@
 	Kenneth Scerri$^{6}$,
-	David B. Grayden$^{1}$,
+	David B. Grayden$^{1,2}$,
 	Visakan Kadirkamanathan$^{4}$
@@
 \renewcommand{\theequation}{S1.\arabic{equation}}
-\section*{Time Discretisation of Neural Field Model}\label{Time Discretization} To form the IDE neural field model a 
-time discretisation must be performed. To do this we used a one-step Euler method, where equation~7 of the main text can be approximated by 
+\section*{Time Discretisation of Neural Field Model}\label{Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
+To do this, we used a one-step Euler method, where equation~7 of the main text can be approximated by
 \begin{equation}
@@
 \end{equation}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1 we get 
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1, we get 
 \begin{equation}
@@
 \section*{Mean and Covariance of the State Disturbance }\label{ColoredNoise} 
-In this section we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
 We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
@@
 \end{align}
-Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
 \begin{equation}\label{eq:IntegralOfGaussian}
@@
 \section*{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this section we provide derivation for the convolution of two $n$-dimensional Gaussian basis functions.
+In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
 This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
@@
 The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section we have
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section, we have
 \begin{equation}\label{eq:FTTwoGaussianMultiplication}
@@
 \begin{equation}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
 \end{equation}
@@
 \end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation~\ref{eq:ConvoftwoGaussian} becomes
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
 \begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
@@
 \section*{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\Gamma$, from equation~16 in the main text.
+The derivation in this section was used for calculating the matrix $\Gamma$ from equation~16 in the main text.
 The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
@@
 \end{equation}
-A Gaussian basis function is symmetric with respect to its centre, therefore
+A Gaussian basis function is symmetric with respect to its centre so
 \begin{equation}\label{eq:GaussianSymmetry}
@@
 \end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$, equation~\ref{eq:GaussianSymmetry} becomes
 \begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
@@
 \end{align}
-Evaluating derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
+Using the derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
 \begin{equation}

### 2010-07-07 ltx/second_order_framework/second_order_manuscript.tex
model derivation for second order framework

\documentclass[a4paper,10pt]{article}
\usepackage[utf8x]{inputenc}
% *** CITATION PACKAGE ***
\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
\usepackage[pdftex]{graphicx}
% *** MATH PACKAGES ***
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
%Appendix
\usepackage{appendix}
\usepackage{color}

%to delete
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
%opening
\title{Non-linear Spatio-temporal modelling using the Integro-Difference Equation}
\author{Parham Aram*,
        Dean~R.~Freestone,Kenneth Scerri, Michael Dewar,\\ Andrew Zammit Mangion and Visakan Kadirkamanathan}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
\section{State space Representation of the Spatio-temporal Non-linear IDE}
We define the $p$th order non-linear, stochastic, spatio-temporal homogenous IDE as
 \begin{equation}\label{eq:IDEModel}
  \rho_t(\mathbf r)=\int_{\Omega}w(\mathbf r-\mathbf r')f(v_{t-p}(\mathbf r'))d\mathbf r'+\mathbf e_{t-p}(\mathbf r) 
 \end{equation}
where $\rho_t(\mathbf r)$ is a lag polynomial defined as
\begin{equation}\label{eq:LagPolynomial}
 \rho_t(\mathbf r)=(1+\sum_{i=1}^{p}\varphi_i L_i)v_{t}\left(\mathbf r\right)
\end{equation}

where $v_t(\mathbf r)$ denotes the spatial field at time $t$ and at spatial location $\mathbf r$, $f(.)$ is some nonlinear map, and $w(.)$ is the spatial kernel. The disturbance $\mathbf e_{t-p}(\mathbf r)$ is a zero-mean normally distributed noise process, spatially
coloured but temporally independent, with covariance
\begin{equation}
cov\left(e_{t}\left(\mathbf{r}\right),e_{t+\tau}\left(\mathbf{r'}\right)\right)=
\gamma\left(\mathbf{r}-\mathbf{r'}\right)\delta(t-\tau)
\label{eq:FieldCovariance}
\end{equation}
where $\delta(.)$ is the Dirac-delta function.
 The spatial field is observed by
\begin{equation}
    \label{eq:ObservationEquation}
	\mathbf{y}_t =
	\int_{\Omega}{
	    m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	d\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_t, 
\end{equation}
where the observation vector $\mathbf{y}_{t}$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise ${\boldsymbol\varepsilon}_t\sim \mathcal{N}\left(\mathbf{0},\boldsymbol\Sigma_{\varepsilon}\right)$ with $\mathbf{\Sigma}_{\boldsymbol\varepsilon}=\sigma_{\varepsilon}^2\mathbf I_{n_y} $. It is assumed here that $\boldsymbol\Sigma_{\varepsilon}$ and $\gamma\left(\mathbf r-\mathbf r' \right)$ are known. The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by 
\begin{equation}\label{eq:SensorKernel}
	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)},
\end{equation}
where $\sigma_m$ sets the sensor width. The superscript $\top$ denotes the transpose operator. We proceed by writing the spatio-temporal IDE model in a parameterized state space form which allows the application of standard estimation
techniques. We use a decomposition of the filed and the spatial kernel using a set of Gaussian basis functions
 \begin{equation}
	\label{eq:FieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t
\end{equation}
\begin{equation}\label{eq:KernelDecomp}
	 w\left(\mathbf{r}-\mathbf{r}'\right) \approx\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta}
\end{equation}
where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ and $\mathbf{\boldsymbol{\psi}}(\mathbf{r})$ are  vectors of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$ and the scaling parameter vector $\boldsymbol\theta$ respectively. Substituting \eqref{eq:LagPolynomial} in \eqref{eq:IDEModel} and using the above decomposition we have
\begin{equation}\label{eq:DecompModel}
\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t=\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\mathbf e_{t-p}(\mathbf r)
 \end{equation}
multiplying \eqref{eq:DecompModel} by $\boldsymbol \phi(\mathbf r)$ and integrate over the spatial domain $\Omega$ we get
\begin{equation}\label{eq:GammaDecompModel}
 \boldsymbol \Gamma (1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t=\int_{\Omega}\boldsymbol \phi(\mathbf r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf e_{t-p}(\mathbf r)d\mathbf r
\end{equation}
where 
\begin{equation}\label{eq:DefGamma}
	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}} 
\end{equation}
cross-multiplying \eqref{eq:GammaDecompModel} by $\boldsymbol{\Gamma}^{-1}$ gives
\begin{equation}\label{eq:InvGammaDecompModel}
 (1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t=\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf e_{t-p}(\mathbf r)d\mathbf r
\end{equation}
This can be further simplified by assuming isotropic structure for the spatial kernel
\begin{equation}
	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (2c+\mathbf{r}'-\mathbf{r}).
\end{equation}
where $c$ is the center of the kernel. To make the simplification, we first define
\begin{equation}\label{eq:DefPsi}
	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (2c+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
\end{equation}
which is a constant $n_x \times n_{\theta}$ matrix and can be computed analytically. Now substituting \eqref{eq:DefPsi} into \eqref{eq:InvGammaDecompModel} we get
\begin{equation}
(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta}
+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_{t-p}(\mathbf{r})\textrm{d}\mathbf{r}}.
\end{equation}
Now we define the state disturbance as
\begin{equation}\label{eq:Wt} 
	\mathbf{e}_{t-p} \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_{t-p}( \mathbf{r} )\textrm{d}\mathbf{r}},
\end{equation}
which is a zero mean normally distributed white noise process with covariance
\begin{equation}
	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
\end{equation}
the observation equation of the reduced model is found by substituting \eqref{eq:FieldDecomp} into \eqref{eq:ObservationEquation} giving
\begin{equation}\label{ObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where the observation matrix is 
\begin{equation}
	\mathbf{C} = \left[
	\begin{array}{{ccc}} 
		c_{1,1} & \dots & c_{1,L} \\
		\vdots & \ddots & \vdots \\
		c_{N,1} & \dots & c_{N,L} 
	\end{array}
	\right] 
\end{equation}
and 
\begin{equation}
	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
\end{equation}
Now we have the final form of the state-space model where
\begin{equation}\label{eq:finalformstatespacemodel}
	(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_{t-p}) \textrm{d}\mathbf{r}' \boldsymbol{\theta}
 +\mathbf{e}_{t-p}
\end{equation}
\begin{equation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t
\end{equation}

Here we consider the case where $p=1$, therefore we have
\begin{equation}
x_t+\varphi_{1} x_{t-1}=\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-1})d\mathbf r'\boldsymbol{\theta}+\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf e_{t-1}(\mathbf r)d\mathbf r
\end{equation}
\section{Deterministic second order neural field model}
\begin{equation}\label{SpikesToPotential}
	v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}
\end{equation}
The post-synaptic response kernel $h(t)$ is described by
\begin{equation}\label{SynapticRespKernel}
	h(t) = \eta(t)At\exp{\left(-\zeta t\right)}.
\end{equation}
where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. $A$ determines the maximal amplitude of the post-synaptic potentials.
Nonlocal interactions between cortical populations are described by	
\begin{equation}\label{RateBasedInteractions}
	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} 
\end{equation}
where $f(.)$ is the firing rate function, $w(.)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain.
\subsection*{Deriving  Integro-differential Equation}
we can write
\begin{eqnarray}\label{SynapticRespKernelderivation}
 \frac{dh(t)}{dt}&=&A[\delta(t)t\mathrm{exp}(-\zeta t)+\eta(t)\frac{d}{dt}(t\mathrm{exp}(-\zeta t))] \nonumber\\
&=& A[0+\eta(t)[\mathrm{exp}(-\zeta t)-\zeta t\mathrm{exp}(-\zeta t) ]\nonumber \\
&=&A\eta(t)\mathrm{exp}(-\zeta t)-\zeta h(t)
\end{eqnarray}
and taking derivative from \ref{SynapticRespKernelderivation} we have
\begin{eqnarray}\label{SynapticRespKernelSecondderivation}
 \frac{d^2h(t)}{dt^2}&=&A[\delta(t)\mathrm{exp}(-\zeta t)-\zeta\eta(t)\mathrm{exp}(-\zeta t)]-\zeta \frac{dh(t)}{dt} \nonumber\\
&=& A\delta(t)-\zeta A \eta(t)\mathrm{exp}(-\zeta t)-\zeta \frac{dh(t)}{dt} \nonumber \\
&=&A\delta(t)-2\zeta A \eta(t)\mathrm{exp}(-\zeta t)+\zeta^2h(t)
\end{eqnarray}
We define the operator $D$ as $D=\frac{d^2}{dt^2}+2\zeta \frac{d}{dt}+\zeta^2 $, applying $D$ on $h$ and using the result from (\ref{SynapticRespKernelSecondderivation}) it is clear that 
\begin{equation}
 Dh=A\delta(t)
\end{equation}
by applying $D$ on (\ref{SpikesToPotential}) we have
\begin{eqnarray}
 Dv&=&D(h*g) \nonumber \\
&=&(Dh*g) \nonumber\\
&=& A(\delta(t)*g)\nonumber \\
&=&Ag
\end{eqnarray}
therefore we have
\begin{equation}\label{eq:finalcontinouosmodel}
\begin{split}
 \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf r,t)}{dt}+\zeta^2v(\mathbf r,t)&=Ag\left( \mathbf{r},t \right)\\
&=A\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} \\
\end{split}
\end{equation}
\subsection*{Discritization}
The above second order differential equation can be split into two, coupled first order ODEs.\\
\begin{equation}\label{eq:systemofode}
\begin{cases}
\tilde{v}=\frac{dv}{dt} \\
\frac{d\tilde{v}}{dt}+2\zeta\tilde{v}+\zeta^2v=Ag\left( \mathbf{r},t \right)
\end{cases}
\end{equation}
Now we approximate the two first-order ode by Euler's method
\begin{equation}\label{eq:discritizedsystemofode}
\begin{cases}
v_{t+1}=T_s\tilde{v_t}+v_t\\
\tilde{v}_{t+1}=(1-2\zeta T_s)\tilde{v}_t-\zeta^2T_sv_t+AT_sg_t\left( \mathbf{r}\right)
\end{cases}
\end{equation}
in matrix format we have
\begin{equation}
 \begin{bmatrix}v_{t+1} \\ \tilde{v}_{t+1}\end{bmatrix}= \begin{bmatrix} T_s &1\\ 1-2\zeta T_s & -\zeta^2T_s\end{bmatrix}\begin{bmatrix}v_{t} \\ \tilde{v}_{t}\end{bmatrix}+AT_sg_t\left( \mathbf{r}\right)
\end{equation}
or alternatively we can write (\ref{eq:discritizedsystemofode}) as
\begin{equation}\label{eq:DifferenceModel}
 v_{t+2}-2(1-\zeta T_s)v_{t+1}+(1-2\zeta T_s+\zeta^2T_s^2)v_t=AT_s^2g_t\left( \mathbf{r}\right)
\end{equation}
\subsection*{From Difference equation to state space model}
We define
\begin{equation}\label{eq:tildev}
v_{t+1}-v_t=T_s\tilde{v_t}
\end{equation}
expanding \eqref{eq:DifferenceModel} we get
\begin{equation}\label{eq:rearrangedDifferenceModel}
 v_{t+2}-2v_{t+1}+2\zeta T_S v_{t+1}+v_t-2\zeta T_sv_t+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
\end{equation}
rearranging \eqref{eq:rearrangedDifferenceModel} we have
\begin{equation}
(v_{t+2}-v_{t+1})-(v_{t+1}-v_t)+2\zeta T_s(v_{t+1}-v_t)+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
\end{equation}
therefore
\begin{equation}
(v_{t+2}-v_{t+1})-(1-2\zeta T_s)(v_{t+1}-v_t)+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
\end{equation}
substituting \eqref{eq:tildev} in the above equation and multiplying by $1/T_s$ we get the state space model
\begin{equation}\label{eq:StateSpaceModel}
\begin{cases}
v_{t+1}=T_s\tilde{v_t}+v_t\\
\tilde{v}_{t+1}=(1-2\zeta T_s)\tilde{v}_t-\zeta^2T_sv_t+AT_sg_t\left( \mathbf{r}\right)
\end{cases}
\end{equation}

\section{First order stochastic Neural Field Model}
The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$. The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by 
\begin{equation}
	\label{eq:SpikesToPotential} v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)h(t)+\int_0^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'} 
\end{equation}
The post-synaptic response kernel $h(t)$ is described by 
\begin{equation}
	\label{eq:SynapticRespKernel} h(t) = \exp{\left(-\zeta t\right)} 
\end{equation}
where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant.
Let $W(\mathbf r,t)$ be a spatio-temporal Wiener process. Then, for $\sigma \in \mathbb R^{+}$, the non-local interactions $g\left( {\mathbf{r},t} \right)$ between cortical populations can be divided into a predominantly deterministic part $g'\left( {\mathbf{r},t} \right) $ and  the random component $W(\mathbf r,t)$,
\begin{equation}\label{eq:ActPotComponents}
  g\left( {\mathbf{r},t} \right)dt=g'\left( {\mathbf{r},t} \right)dt+\sigma d W(r,t)
\end{equation}
As a result, the post-synaptic membrane voltage $v(\mathbf r, t)$ is itself a stochastic process. The deterministic part $g'(\mathbf r, t)$ is usually modelled as an integral equation with exogenous deterministic input , $ u(\mathbf r,t)$, of the form \cite{Atay2005}
\begin{equation}
	\label{DeterministicRateBasedInteractions} g'\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}+u(\mathbf r,t)
\end{equation}
where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface. Substituting \eqref{eq:ActPotComponents} in \eqref{eq:SpikesToPotential} we get
\begin{equation}\label{eq:NeuralModelDeterStoch}
v\left( {\mathbf{r},t} \right)=v_0h(t)+\int_0^t {h\left( {t - t'} \right)g'\left( {\mathbf{r},t'} \right)dt'}+ \int_0^t h\left( {t - t'} \right)\sigma d W(r,t')
\end{equation}
Here we assume that $v_0$ is generated by a known distribution $p_0(v)$ and is independent of the the random component $W(\mathbf r,t)$. We stress that $\sigma$ does not depend on the field $v(\mathbf r, t)$
and hence the noise in \eqref{eq:NeuralModelDeterStoch} is strictly additive. It can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the following initial value problem (see Appendix \ref{app:InitialValueProblemProof})
\begin{equation}
 dv(\mathbf r, t) + \zeta v(\mathbf r, t)dt = g'(\mathbf r, t)dt + dW(\mathbf r, t) \quad t\ge0, v(\mathbf r, 0) = v_0
\end{equation}
applying the Euler-Maruyama method the integro-difference equation (IDE) model takes the form of
\begin{equation}\label{eq:Euler-MaruyamaDiscrit}
 v_{t+T_s}(\mathbf r)- v_{t}(\mathbf r)+ T_s\zeta v_t(\mathbf r)= T_sg'(\mathbf r, t) + (W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
\end{equation}
where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf r)$ is normally distributed with mean zero and covariance function $T_s\gamma(\mathbf r-\mathbf r')$. We rewrite \eqref{eq:Euler-MaruyamaDiscrit} as
\begin{equation}
	\label{DiscreteTimeModel} 
	v_{t+T_s}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r}'\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\textrm{d}\mathbf{r}'}+T_su_t(\mathbf r)
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
 where $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $T_s\gamma(\mathbf{r}-\mathbf{r}')$. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper. 
\section{Second order stochastic Neural Field Model}
The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$. The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by 
\begin{equation}
	\label{eq:SecondOrderSpikesToPotential} v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)(t+1)e^{-\zeta t}+v'(\mathbf r,0)te^{-\zeta t}+\int_0^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'} 
\end{equation}
The post-synaptic response kernel $h(t)$ is described by 
\begin{equation}
	\label{eq:SecondOrderSynapticRespKernel} h(t) = At\exp{\left(-\zeta t\right)} 
\end{equation}
where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant.  $A$ determines the maximal amplitude of the post-synaptic potentials.
Let $W(\mathbf r,t)$ be a spatio-temporal Wiener process. Then, for $\sigma \in \mathbb R^{+}$, the non-local interactions $g\left( {\mathbf{r},t} \right)$ between cortical populations can be divided into a predominantly deterministic part $g'\left( {\mathbf{r},t} \right) $ and  the random component $W(\mathbf r,t)$,
\begin{equation}\label{eq:SecondOrderActPotComponents}
  g\left( {\mathbf{r},t} \right)dt=g'\left( {\mathbf{r},t} \right)dt+\sigma d W(r,t)
\end{equation}
As a result, the post-synaptic membrane voltage $v(\mathbf r, t)$ is itself a stochastic process. The deterministic part $g'(\mathbf r, t)$ is usually modelled as an integral equation with exogenous deterministic input , $ u(\mathbf r,t)$, of the form \cite{Atay2005}
\begin{equation}
	\label{DeterministicRateBasedInteractions} g'\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}+u(\mathbf r,t)
\end{equation}
where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface. Substituting \eqref{eq:SecondOrderActPotComponents} in \eqref{eq:SecondOrderSpikesToPotential} we get
\begin{equation}\label{eq:SecondOrderNeuralModelDeterStoch}
v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)(t+1)e^{-\zeta t}+v'(\mathbf r,0)te^{-\zeta t}+\int_0^t {h\left( {t - t'} \right)g'\left( {\mathbf{r},t'} \right)dt'}+ \int_0^t h\left( {t - t'} \right)\sigma d W(r,t')
\end{equation}
It can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the following initial value problem \parham{Andrew do you know how?}
\begin{equation*}
\left\lbrace \begin{array}{lc}
dv(\mathbf r,t)=\tilde{v}(\mathbf r,t)d_t & \\
d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v_tdt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)
\end{array}\right.
\end{equation*}
the linear second order SDE can be written in matrix notation as
\begin{equation}
 d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ \zeta^2 & 2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)
\end{equation}

\section{Estimation of the Non-linear Spatio-temporal IDE Model}

\subsection{Unscented Kalman Filter}
\subsection{Unscented RTS Smoother}
\subsection{Parameter Estimation}
\subsection{Computational Complexity}
\section{Example}
\section{Conclusion}

\appendices
\section{}\label{app:InitialValueProblemProof}
%Appendix one text goes here.
Here we show that the post-synaptic potential $v(\mathbf r, t)$ is a solution to the initial value problem 
\begin{equation}
 dv(\mathbf r, t) + \zeta v(\mathbf r, t)dt = g'(\mathbf r, t) + dW(\mathbf r, t) \quad t\ge0, v(\mathbf r, 0) = v_0
\end{equation}
Consider the function $\kappa(v(\mathbf r, t), t) \in C_{1,2}$ defined as
\begin{equation}
\kappa(v(\mathbf r, t), t) = v(\mathbf r, t)e^{\zeta t}
\end{equation}
 applying Ito's formula we get
\begin{equation}\label{eq:kappafunction}
 d\kappa = e^{\zeta t}g'(\mathbf r, t)dt + e^{\zeta t}\sigma dW(\mathbf r, t)
\end{equation}
Integrating \eqref{eq:kappafunction} over $[0, t]$ gives 
\begin{equation}\label{eq:kappafunctionInteration}
 v(\mathbf r, t)e^{\zeta t}-v_0 = \int_0^te^{\zeta t'}g'(\mathbf r, t')dt' +\int_0^te^{\zeta t'}\sigma dW(\mathbf r, t')
\end{equation}
and multiplying throughout by $e^{-\zeta t}$ gives 
\begin{eqnarray}
\begin{split}
 v(\mathbf r, t) &=&v_0e^{-\zeta t}+ \int_0^te^{-\zeta(t-t')}g'(\mathbf r, t')dt' +\int_0^te^{-\zeta (t-t')}\sigma dW(\mathbf r, t')\\
&=&v_0e^{-\zeta t}+ \int_0^t h(t-t')g'(\mathbf r, t')dt' +\int_0^th(t-t')\sigma dW(\mathbf r, t')
\end{split}
\end{eqnarray}
% Now attach the bibliography
\bibliographystyle{plainnat}
\bibliography{STIDE}
\end{document}

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
minor correction to second order mo0del derivation and added discritization

@@
 It can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the following initial value problem \parham{Andrew do you know how?}
-\begin{equation*}
+\begin{equation*}\label{eq:SecondOrderInitialValueProblem}
 \left\lbrace \begin{array}{lc}
 dv(\mathbf r,t)=\tilde{v}(\mathbf r,t)d_t & \\
-d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v_tdt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)
+d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v(\mathbf r,t)dt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)
 \end{array}\right.
@@
 the linear second order SDE can be written in matrix notation as
+\begin{equation}\label{eq:SecondOrderSDEMatrix}
+ d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)
+\end{equation}
+applying the Euler-Maruyama method the integro-difference equation (IDE) model takes the form of
 \begin{equation}
- d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ \zeta^2 & 2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)
+ \begin{bmatrix} v_{t+T_s}(\mathbf r)-v_t(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)-\tilde{v}_t(\mathbf r)\end{bmatrix}=T_s\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}(W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
 \end{equation}

### 2010-07-08 ltx/data_paper/DataPaper.tex

--- 2010-06-25 ltx/PLoS/SupportingInformation.tex
@@
 %
-%  Created by Dean Freestone on 2010-06-24.
+%  Created by Dean Freestone on 2010-07-06.
 %  Copyright (c) 2010 . All rights reserved.
@@
 % More symbols
-\usepackage{amsmath}
-\usepackage{amssymb}
+%\usepackage{amsmath}
+%\usepackage{amssymb}
 %\usepackage{latexsym}
@@
 \fi
-\title{S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
-\author{Dean R. Freestone$^{1,2,3}$, 
-Parham Aram$^{4}$, 
-Michael Dewar$^{5,\ast}$,\\
-Kenneth Scerri$^{6,\ast}$,
-David B. Grayden$^{1,\ast}$,
-Visakan Kadirkamanathan$^{4}$}
+\title{Patient-Specific Neural Field Model}
+\author{Parham Aram, Dean Freestone, Kenneth Scerri, Michael Dewar,\\
+ Jacob Donoghue, Sydney Cash, David Grayden and Visakan Kadirkamanathan  }
+
+\date{2010-07-06}
 
@@
 
-\begin{flushleft}
+\begin{abstract}
+	\begin{itemize}
+		\item Background
+		\item Method
+		\item Result
+		\item Conclusion
+	\end{itemize}
+\end{abstract}
 
-\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
-\\
-\bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
-\\
-\bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
-\\
-\bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
-\\
-\bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
-\\
-\bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta
-\\
-$\ast$ E-mail: dfreestone@bionicear.org
-\end{flushleft}
-\renewcommand{\theequation}{S1.\arabic{equation}}
-\section*{Time Discretisation of Neural Field Model}\label{Time Discretization} To form the IDE neural field model a 
-time discretisation must be performed. To do this we used a one-step Euler method, where equation~7 of the main text can be approximated by 
-\begin{equation}
-	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} =-\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.
-\end{equation}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1 we get 
-\begin{equation}
-	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.
-\end{equation}
-Now making simplifications, the discrete time form of the model is 
-\begin{equation}
-	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
-\end{equation}
-where $\xi = 1 - T_s \zeta$.
+\section{Introduction}
+\begin{itemize}
+	\item Understanding of macroscopic neurodynamics
+	\item Neural field model
+	\item Improvements in electrode technology with great spatiotemporal resolution
+\end{itemize}
 
-\section*{Mean and Covariance of the State Disturbance }\label{ColoredNoise} 
-In this section we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
-We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
-Therefore, $\mathbf{e}_t$ is also normally distributed.
-From equation~21 of the main text, the state disturbance vector is defined as
-\begin{equation}
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
-\end{equation}
-The expected value of $\mathbf e_t$ is given by 
-\begin{equation}
-	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
-\end{equation}
-The covariance of $\mathbf{e}_t$ is 
-\begin{align}
-	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{align}
+\section{Method}
 
-\section*{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}
-This section gives the derivation for the width of the Fourier transform of  the field basis function in terms of its spatial cut-off frequency (equations~34 and~37 in the main text).
-We define an \textit{n}-dimensional Gaussian  centred at the origin as
-\begin{equation}
- \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
-\end{equation}
-Now applying the \textit{n}-dimensional Fourier transform yields
-\begin{align}\label{eq:AppendixGaussianFT}
- \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
-&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{align}
-Now evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{equation}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
-\end{equation}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation} 
-where 
-\begin{equation}
-	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{equation}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{equation}
-since the maximum of Gaussian described in equation~S1.10 is at the origin. Now solving for $\sigma_{\nu}^2$ we get
-\begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
-\end{equation}
+\subsection{Data Collection}
+\begin{itemize}
+	\item Show medical imaging
+	\item Show LFP Data (background, seizure, post-seizure)
+	\item Show spectral properties of LFPs
+\end{itemize}
 
-\section*{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this section we provide derivation for the convolution of two $n$-dimensional Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section we have
-\begin{equation}\label{eq:FTTwoGaussianMultiplication}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
-\end{equation}
-where $\mathcal{F}$ denotes the Fourier transform.
-Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$ equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
-\begin{equation}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{equation}
- Taking the inverse Fourier transform, the convolution becomes
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$ equation~\ref{eq:ConvoftwoGaussian} becomes
-\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
-\end{equation}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+\subsection{Frequency Analysis}
+\begin{itemize}
+	\item Create 2D FT of observations to estimate bandwidth
+\end{itemize}
 
-\section*{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\Gamma$, from equation~16 in the main text.
-The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
-\begin{equation}\label{eq:InofGaussianDefinition}
-\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
-\end{equation}
-A Gaussian basis function is symmetric with respect to its centre, therefore
-\begin{equation}\label{eq:GaussianSymmetry}
- \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
-\begin{align}
-\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
-\end{align}
-Evaluating derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}
- \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
-\end{equation}
-This completes the derivation.
+\subsection{Pre-processing}
+
+\subsection{Estimation Algorithm}
+\begin{itemize}
+	\item Model
+	\item URTSS
+\end{itemize}
+
+\section{Results}
+\begin{itemize}
+	\item Will show parameter distributions
+	\item Will show parameter changes over time through the seizure
+\end{itemize}
+
+\section{Discussion}
+\begin{itemize}
+	\item  
+\end{itemize}
+
 \bibliographystyle{plain}

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
completed discritization

@@
 applying the Euler-Maruyama method the integro-difference equation (IDE) model takes the form of
-\begin{equation}
+\begin{equation}\label{eq:SecondOrderEulerMaruyamaDis}
  \begin{bmatrix} v_{t+T_s}(\mathbf r)-v_t(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)-\tilde{v}_t(\mathbf r)\end{bmatrix}=T_s\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}(W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
 \end{equation}
-
+where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf r)$ is normally distributed with mean zero and covariance function $T_s\gamma(\mathbf r-\mathbf r')$.
+We rewrite \eqref{eq:SecondOrderEulerMaruyamaDis} as
+\begin{equation}
+ \begin{bmatrix} v_{t+T_s}(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)\end{bmatrix}=\begin{bmatrix}1 & T_s \\ -\zeta^2 T_s & 1-2\zeta T_s \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}e_t(\mathbf r)
+\end{equation}
+ where $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$.
+Here $\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $T_s\gamma(\mathbf{r}-\mathbf{r}')$.
+To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
 \section{Estimation of the Non-linear Spatio-temporal IDE Model}

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
some small edits to 2nd order paper and fixed typo in DataPaper data viewing script

@@
 %opening
-\title{Non-linear Spatio-temporal modelling using the Integro-Difference Equation}
+\title{Nonlinear Spatio-Temporal Modelling using the Integro-Difference Equation}
 \author{Parham Aram*,
@@
 \section{Introduction}
-\section{State space Representation of the Spatio-temporal Non-linear IDE}
-We define the $p$th order non-linear, stochastic, spatio-temporal homogenous IDE as
+\section{State-Space Representation of the Spatio-temporal Nonlinear IDE}
+The $p^{th}$-order nonlinear, stochastic, spatio-temporal homogenous IDE model is defined as
  \begin{equation}\label{eq:IDEModel}
-  \rho_t(\mathbf r)=\int_{\Omega}w(\mathbf r-\mathbf r')f(v_{t-p}(\mathbf r'))d\mathbf r'+\mathbf e_{t-p}(\mathbf r) 
+  \rho_t(\mathbf r)=\int_{\Omega}w(\mathbf r-\mathbf r')f(v_{t-p}(\mathbf r'))d\mathbf r'+\mathbf e_{t-p}(\mathbf r). 
  \end{equation}
-where $\rho_t(\mathbf r)$ is a lag polynomial defined as
+The quantity $\rho_t(\mathbf r)$ is a lag polynomial defined as
 \begin{equation}\label{eq:LagPolynomial}
- \rho_t(\mathbf r)=(1+\sum_{i=1}^{p}\varphi_i L_i)v_{t}\left(\mathbf r\right)
+ \rho_t(\mathbf r)=(1+\sum_{i=1}^{p}\varphi_i L_i)v_{t}\left(\mathbf r\right),
 \end{equation}
-
-where $v_t(\mathbf r)$ denotes the spatial field at time $t$ and at spatial location $\mathbf r$, $f(.)$ is some nonlinear map, and $w(.)$ is the spatial kernel.
-The disturbance $\mathbf e_{t-p}(\mathbf r)$ is a zero-mean normally distributed noise process, spatially
-coloured but temporally independent, with covariance
+where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at spatial location $\mathbf r$, $f(.)$ is a nonlinear map, and $w(.)$ is a spatial mixing kernel.
+The disturbance, $\mathbf e_{t-p}(\mathbf r)$, is a zero-mean normally distributed noise process that is spatially
+coloured and temporally white, with covariance
 \begin{equation}
@@
 \end{equation}
-where $\delta(.)$ is the Dirac-delta function.
- The spatial field is observed by
+and $\delta(.)$ is the Dirac-delta function.
+Observations from the spatio-temporal field are described by the measurement function
 \begin{equation}
@@
 \end{equation}
-where the observation vector $\mathbf{y}_{t}$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise ${\boldsymbol\varepsilon}_t\sim \mathcal{N}\left(\mathbf{0},\boldsymbol\Sigma_{\varepsilon}\right)$ with $\mathbf{\Sigma}_{\boldsymbol\varepsilon}=\sigma_{\varepsilon}^2\mathbf I_{n_y} $.
+where the observation vector, $\mathbf{y}_{t}$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise ${\boldsymbol\varepsilon}_t\sim \mathcal{N}\left(\mathbf{0},\boldsymbol\Sigma_{\varepsilon}\right)$ with $\mathbf{\Sigma}_{\boldsymbol\varepsilon}=\sigma_{\varepsilon}^2\mathbf I_{n_y} $.
 It is assumed here that $\boldsymbol\Sigma_{\varepsilon}$ and $\gamma\left(\mathbf r-\mathbf r' \right)$ are known.
@@
 The superscript $\top$ denotes the transpose operator.
-We proceed by writing the spatio-temporal IDE model in a parameterized state space form which allows the application of standard estimation
-techniques. We use a decomposition of the filed and the spatial kernel using a set of Gaussian basis functions
+We proceed by writing the spatio-temporal IDE model in a parameterized state space form which allows the application of standard estimation techniques.
+We use a decomposition of the field and the spatial mixing kernel using a set of Gaussian basis functions
  \begin{equation}
@@
 \end{equation}
-\subsection*{Discritization}
+\subsection*{Discretization}
 The above second order differential equation can be split into two, coupled first order ODEs.\\
@@
 \end{equation}
-\subsection*{From Difference equation to state space model}
+\subsection*{From Difference Equation to State-Space Model}
 We define
@@
 \left\lbrace \begin{array}{lc}
-dv(\mathbf r,t)=\tilde{v}(\mathbf r,t)d_t & \\
+dv(\mathbf r,t)=\tilde{v}(\mathbf r,t)dt & \\
 d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v(\mathbf r,t)dt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)

### 2010-07-08 src/DataPaper/ReadAndPlotData.m

@@ -63,7 +63,7 @@ end
 % ~~~~~~~~~~~~~~~~~~
 PlotOffset  = 200;                          % this just puts some space between channels
 OffsetMatrix = PlotOffset*(1:100);
-OffsetMatrix = repmat(OffsetMatrix,size(Data,1),1);
+OffsetMatrix = repmat(OffsetMatrix,size(CARData,1),1);
 OffsetData = OffsetMatrix+CARData;
 figure('units','normalized','position',[0 0 1 1])
 % WindowSize = 50000;

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
added the aims to the 2nd order paper

@@
 \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{yellow}{#1}}}}}
+
 %opening
@@
 \begin{abstract}
+The aim of this paper is to 	
+\begin{enumerate}
+	\item Derive the temporally second order model
+	\item Apply the EM algorithm on test data generated by the model above
+	\item Extend the EM algorithm to estimate also the model covariances
+	\item Apply method above to measured data
+\end{enumerate}
 
@@
 \section{Introduction}
+\begin{enumerate}
+	\item General background and motivation
+	\item Aims and hypotheses
+	\item Specific background
+	\item Point out specific things we are doing and why they are important
+	\item Paper layout
+\end{enumerate}
 \section{State-Space Representation of the Spatio-temporal Nonlinear IDE}
@@
 \end{equation}
-where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at spatial location $\mathbf r$, $f(.)$ is a nonlinear map, and $w(.)$ is a spatial mixing kernel.
+where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at spatial location $\mathbf r$, $f(\cdot)$ is a nonlinear map, and $w(\cdot)$ is a spatial mixing kernel.
 The disturbance, $\mathbf e_{t-p}(\mathbf r)$, is a zero-mean normally distributed noise process that is spatially
@@
 \end{equation}
-and $\delta(.)$ is the Dirac-delta function.
+and $\delta(\cdot)$ is the Dirac-delta function.
 Observations from the spatio-temporal field are described by the measurement function
@@
 \end{equation}
-where $c$ is the center of the kernel. To make the simplification, we first define
+where $c$ is the center of the kernel. \dean{Can't use c as it is used in the observation matrix.} To make the simplification, we first define
 \begin{equation}\label{eq:DefPsi}
@@
 \end{equation}
-\section{Deterministic second order neural field model}
+\section{Deterministic Second-Order Neural Field Model}
 \begin{equation}\label{SpikesToPotential}
@@
 \subsection*{Discretization}
-The above second order differential equation can be split into two, coupled first order ODEs.\\
+The above second-order differential equation can be split into two, coupled first order ODEs.\\
 \begin{equation}\label{eq:systemofode}
@@
 \end{equation}
-Now we approximate the two first-order ode by Euler's method
+Now we approximate the two first-order ODE by Euler's method
 \begin{equation}\label{eq:discritizedsystemofode}

### 2010-07-10 src/DataPaper/ReadAndPlotData.m
added spatial freq figure

@@ -1,10 +1,23 @@
 clc
 clear
 close all
+FS = 10;
+TwoColumnWidth = 17.35;     % PLoS figure width cm
+Fs = 30e3;          % sampling rate in Hz
+FsDec = 5e3;
+TsDec = 1/FsDec;
+DecimationFactor = Fs/FsDec;
+
+ElectrodeSpacing = 0.4;     % mm
+SpatialFreqMax = 1/ElectrodeSpacing;
+SpatialFreq = linspace(0,SpatialFreqMax,10);
+
+SzStart = 8;        % seconds
+SzEnd = 34;         % seconds
 
 % read in neuroport data from .mat file
-DataFile = '/Users/dean/Dropbox/iEEG Data Boston/MG29_Seizure22_LFP_Clip_Dean.mat';
-Data = open('/Users/dean/Dropbox/iEEG Data Boston/MG29_Seizure22_LFP_Clip_Dean.mat');
+DataFileLocation = '/Users/dean/Dropbox/iEEG Data Boston/MG29_Seizure22_LFP_Clip_Dean.mat';
+Data = open(DataFileLocation);
 Data = Data.whole_data';
 
 % map the rows of the data matrix to the channels
@@ -42,30 +55,88 @@ CAR = repmat(mean(MappedData,2),1,100);
 CARData = MappedData-CAR;                       % CAR = common average reference
 clear MappedData
 
-% here reshape the data so each time point is 10x10 matrix
-MatrixData = zeros(size(CARData,1),10,10);
-for n=1:size(CARData,1)
-    MatrixData(n,:,:) = reshape(CARData(n,:),10,10);
+% re-assign the bad channels and the corners to nans so we can interpolate
+ZeroChannels = [1 10 13 15 19 24 26 35 42 46 47 54 56  57 67 81 85 87 91 100];
+% get ride of the noisey guys
+for n=1:length(ZeroChannels)
+    CARData(:,ZeroChannels(n)) = nan(size(CARData,1),1);
 end
+
+% low-pass filter data
+Fc = 100;           % Cut-off frequency in Hz
+Wn = Fc/(Fs/2);
+FilterOrder = 2;
+[b a] = butter(FilterOrder,Wn);
+FiltData = filter(b,a,CARData);
+clear CARData
+
+% downsample to 1 kHz
+FiltData = downsample(FiltData,DecimationFactor);
[…]

### 2010-07-11 ltx/data_paper/DataPaper.tex
added spatial freq figure
added LFP figure and some pre-processing steps

@@
 \usepackage{ifpdf}
+
+\usepackage{amsmath,amssymb,amsfonts,epsfig} % Typical maths resource packages
 
@@
 \end{itemize}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/LFPs.eps}
+\end{center}
+\caption{{\bf Local Field Potentials}. Data recorded from the first five channels of the array. The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
+\label{fig:SpatialFreqObservation}
+\end{figure}
 
@@
 
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/SpatialFreq.eps}
+\end{center}
+\caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+\label{fig:SpatialFreqObservation}
+\end{figure}
+
 \subsection{Pre-processing}
-
+\begin{itemize}
+	\item Identification and removal of bad channels
+	\item Common average reference (CAR) montage 
+	\item Low-pass filter data, with cut-off at 100~Hz
+	\item Decimate data from 30~kHz to 5~kHz temporal sampling
+	\item Spatially interpolate missing data to facilitate spatial frequency analysis
+\end{itemize}
 \subsection{Estimation Algorithm}

### 2010-07-11 src/DataPaper/ReadAndPlotData.m

@@ -2,6 +2,8 @@ clc
 clear
 close all
 FS = 10;
+FS2 = 12;
+
 TwoColumnWidth = 17.35;     % PLoS figure width cm
 Fs = 30e3;          % sampling rate in Hz
 FsDec = 5e3;
@@ -98,6 +100,7 @@ Pos = get(CB,'position');
 set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 xlabel('Hz','fontsize',FS,'fontname','arial')
 ylabel('Hz','fontsize',FS,'fontname','arial')
+title('\bf A','fontsize',FS2,'fontname','arial','position',[-0.5 2.8])
 
 subplot(132),imagesc( SpatialFreq,SpatialFreq,squeeze( mean( DataFFT(SzStart*FsDec+1:SzEnd*FsDec,:,:),1)) )
 axis square
@@ -107,6 +110,7 @@ Pos = get(CB,'position');
 set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 xlabel('Hz','fontsize',FS,'fontname','arial')
 ylabel('Hz','fontsize',FS,'fontname','arial')
+title('\bf B','fontsize',FS2,'fontname','arial','position',[-0.5 2.8])
 
 subplot(133),imagesc( SpatialFreq,SpatialFreq,squeeze( mean( DataFFT(SzEnd*FsDec+1:end,:,:),1)) )
 axis square
@@ -116,6 +120,7 @@ Pos = get(CB,'position');
 set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 xlabel('Hz','fontsize',FS,'fontname','arial')
 ylabel('Hz','fontsize',FS,'fontname','arial')
+title('\bf C','fontsize',FS2,'fontname','arial','position',[-0.5 2.8])
 
 % this bit plot the observed field
 % ~~~~~~~~~~~~~~~~~~
@@ -131,7 +136,7 @@ ylabel('Hz','fontsize',FS,'fontname','arial')
 
 % plot channels as a time series
 % ~~~~~~~~~~~~~~~~~~
-PlotOffset  = 200;                          % this just puts some space between channels
+PlotOffset  = 500;                          % this just puts some space between channels
[…]

### 2010-07-11 src/DataPaper/ReadAndPlotData.m
added temporal freq figure

@@ -76,6 +76,52 @@ clear CARData
 FiltData = downsample(FiltData,DecimationFactor);
 t = TsDec*(0:size(FiltData,1)-1);
 
+% get indexes for good channels
+m=1;
+for n=1:size(FiltData,2)
+    if ~ismember(n,ZeroChannels)
+        GoodChannels(m) = n;
+        m=m+1;
+    end
+end
+
+NFFTPoints = 10*1024;
+YMax = 105;
+FMax = 100;
+figure('units','centimeters','position',[2,2,TwoColumnWidth,6])
+TemporalFFT1 = 20*log10(abs(fft(FiltData(1:SzStart*FsDec,GoodChannels),NFFTPoints,1)));
+TemporalFFT2 = 20*log10(abs(fft(FiltData(SzStart*FsDec+1:SzEnd*FsDec,GoodChannels),NFFTPoints,1)));
+TemporalFFT3 = 20*log10(abs(fft(FiltData(SzEnd*FsDec+1:end,GoodChannels),NFFTPoints,1)));
+
+f = linspace(0,FsDec,NFFTPoints);
+subplot(131),semilogx(f,mean(TemporalFFT1,2))
+xlim([0 FMax])
+ylim([60 YMax])
+axis square
+set(gca,'fontsize',FS,'fontname','arial')
+xlabel('Frequency (Hz)','fontsize',FS,'fontname','arial')
+ylabel('Power (dB)','fontsize',FS,'fontname','arial')
+title('\bf A','fontsize',FS2,'fontname','arial','position',[0.2 100 17])
+
+subplot(132),semilogx(f,mean(TemporalFFT2,2))
+xlim([0 FMax])
+ylim([60 YMax])
+axis square
+set(gca,'fontsize',FS,'fontname','arial')
+xlabel('Frequency (Hz)','fontsize',FS,'fontname','arial')
+ylabel('Power (dB)','fontsize',FS,'fontname','arial')
+title('\bf B','fontsize',FS2,'fontname','arial','position',[0.2 100 17])
+
+subplot(133),semilogx(f,mean(TemporalFFT3,2))
+xlim([0 FMax])
+ylim([60 YMax])
+axis square
+set(gca,'fontsize',FS,'fontname','arial')
+xlabel('Frequency (Hz)','fontsize',FS,'fontname','arial')
+ylabel('Power (dB)','fontsize',FS,'fontname','arial')
[…]

### 2010-07-12 ltx/data_paper/DataPaper.tex
added temporal freq figure
added spatial freq cross-section and field observation figures

@@
 \begin{abstract}
+
 	\begin{itemize}
@@
 \end{itemize}
+
 \begin{figure}[!ht]
@@
 \caption{{\bf Local Field Potentials}. Data recorded from the first five channels of the array. The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
-\label{fig:SpatialFreqObservation}
+\label{fig:TimeSeries}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/FieldObservations.eps}
+\end{center}
+\caption{{\bf Snap-shots of the spatial aspects of the observed field}. The snap-shots are ordered from A to I forming a consecutive sequence spaced 2.5~ms apart starting at 34.024s}
+\label{fig:FieldObserations}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/TemporalFreq.eps}
+\end{center}
+\caption{{\bf Spectra from local field potential recordings}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+\label{fig:TemporalFreqObservation}
 \end{figure}
@@
 \caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+\label{fig:SpatialFreqObservation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/SpatialFreqCrossSection.eps}
+\end{center}
+\caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
 \label{fig:SpatialFreqObservation}

### 2010-07-12 src/DataPaper/ReadAndPlotData.m

@@ -1,3 +1,6 @@
+% this script reads in the micro data and plot the times series and the
+% temporal and spatial frequency properties.
+
 clc
 clear
 close all
@@ -5,14 +8,13 @@ FS = 10;
 FS2 = 12;
 
 TwoColumnWidth = 17.35;     % PLoS figure width cm
-Fs = 30e3;          % sampling rate in Hz
-FsDec = 5e3;
-TsDec = 1/FsDec;
+Fs = 30e3;                              % sampling rate in Hz
+FsDec = 5e3;                          % this is the sampling rate that we will use
+TsDec = 1/FsDec;                    % the decimated sampling period
 DecimationFactor = Fs/FsDec;
 
 ElectrodeSpacing = 0.4;     % mm
 SpatialFreqMax = 1/ElectrodeSpacing;
-SpatialFreq = linspace(0,SpatialFreqMax,10);
 
 SzStart = 8;        % seconds
 SzEnd = 34;         % seconds
@@ -44,19 +46,21 @@ for n=1:100
 end
 clear Data      % save some RAM
 
+%%
 % these are the channels that have loads of noise and will be useless
 BadChannels = [13 15 19 24 26 35 42 46 47 54 56  57 67 81 85 87];
 % get ride of the noisey guys
 for n=1:length(BadChannels)
     MappedData(:,BadChannels(n)) = zeros(size(MappedData,1),1);
 end
-
+%%
 % now need to re-reference the data
 % ~~~~~~~~~~~~~~~~~~~~~
 CAR = repmat(mean(MappedData,2),1,100);
 CARData = MappedData-CAR;                       % CAR = common average reference
 clear MappedData
 
+%%
 % re-assign the bad channels and the corners to nans so we can interpolate
 ZeroChannels = [1 10 13 15 19 24 26 35 42 46 47 54 56  57 67 81 85 87 91 100];
 % get ride of the noisey guys
@@ -64,6 +68,7 @@ for n=1:length(ZeroChannels)
     CARData(:,ZeroChannels(n)) = nan(size(CARData,1),1);
 end
 
+%%
 % low-pass filter data
 Fc = 100;           % Cut-off frequency in Hz
 Wn = Fc/(Fs/2);
[…]

### 2010-07-13 ltx/data_paper/DataPaper.tex
added the Mstep to the data paper

@@
 \subsection{Estimation Algorithm}
-\begin{itemize}
-	\item Model
-	\item URTSS
-\end{itemize}
+The state space model is given by
+\begin{equation}
+ \mathbf x_{t+1}=\boldsymbol\Theta q(\mathbf x_t)+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)
+\end{equation}
+\begin{equation}
+ \mathbf y_t=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t
+\end{equation}
+where $\boldsymbol\Theta$ is an $n_x \times n_x$ block matrix where each block matrix is of dimension $ 1\times n_{\theta}$ defined as
+\begin{equation}
+\boldsymbol \Theta_{i,j}=\left\lbrace  \begin{array}{cc}
+\boldsymbol \theta^\top &i=j \\
+\mathbf 0_{1 \times n_{\theta}}& i\neq j  
+ \end{array}\right. 
+\end{equation}
+and the non-linear map $q(.)$ is defined as
+\begin{equation}\label{eq:QmatrixForSigmapoints}
+	q(\mathbf{x}_t) \triangleq T_s\boldsymbol{\Gamma}^{-1} \int_\Omega \boldsymbol{\Lambda}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+\end{equation}
+where $\boldsymbol{\Lambda}(\mathbf{r}')  $ is an $n_x \times 1$ block vector with each block of dimension $n_{\theta} \times 1 $
+\begin{equation}\label{eq:DefPsi}
+\boldsymbol{\Lambda}(\mathbf{r}')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r')\\\boldsymbol \lambda_2(\mathbf r')\\ \vdots \\ \boldsymbol \lambda_{n_{x}}(\mathbf r') \end{bmatrix}_{n_x \times 1}
+\end{equation}
+and where
+\begin{equation}
+\boldsymbol \lambda_i(\mathbf r') =\begin{bmatrix} \phi_i\ast \psi_1(\mathbf r') \\ \phi_i\ast \psi_2 (\mathbf r') \\ \vdots \\ \phi_i\ast \psi_{n_{\theta}}(\mathbf r') \end{bmatrix}_{n_{\theta} \times 1}
+\end{equation}
+As a result $q(\mathbf x_t)$ is an $n_x \times 1$ block vector and each block is $n_{\theta} \times 1$. It should be noted that $\boldsymbol\Theta q(\mathbf x_t)$ is an $n_x \times 1$ vector.
+$ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.
+\subsection*{$\mathcal Q$-function}
+Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
+\begin{equation}
+ p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0)
+\label{eq:jointdistribution}
+\end{equation}
+The $\mathcal Q$-function can be written in terms of its component as shown in (\ref{eq:jointdistribution})
+\begin{eqnarray}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\mathbf E_{\boldsymbol (\theta',\xi')}[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)]\nonumber\\
+&=&\mathbf E_{\boldsymbol (\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta)+\sum_{t=1}^{T}\ln p(\mathbf x_0)]
+\end{eqnarray}
+$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter therefore $\mathcal Q$-function can be rewritten as
+\begin{equation}
+\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)]+\textrm{const}
+\end{equation}
+The Gaussian distribution of the disturbance, $e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ results into the following conditional distribution of the state at $t+1$
+\begin{equation}
+ p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=ce^{-(\mathbf x_{t+1}-\boldsymbol\Theta q(\mathbf  x_t)-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\boldsymbol\Theta q( \mathbf x_t)-\xi \mathbf  x_t)}
+\end{equation}
+where c is the normalising constant. Taking $\log$ we get
+\begin{equation}
+ \ln p(\mathbf x_{t+1} |\mathbf x_t;\boldsymbol\theta,\xi)=\ln c -(\mathbf x_{t+1}^\top-q^\top(\mathbf x_t)\boldsymbol\Theta^\top -\xi  \mathbf x_t^\top)\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\boldsymbol\Theta q(\mathbf x_t)-\xi \mathbf x_t)
+\end{equation}
+\begin{eqnarray}
+ \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta, \xi)&=&\ln c-[\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t \nonumber \\
+&&- q^\top(\mathbf x_t)\boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+q^\top(\mathbf x_t)\boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)+\xi q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\mathbf x_t \nonumber\\
+&&-\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+\xi  \mathbf  x_t^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)+\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t]
+\end{eqnarray}
+\begin{eqnarray}\label{eq:Qfunctioninter}
+  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q( \mathbf x_t)+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
+&&-q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t
+\end{eqnarray}
+taking trace and using invariant cyclic permutations property of the trace this distribution can be written as 
+ \begin{eqnarray}
+   \ln p(x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2 tr \left\lbrace  \boldsymbol\Theta q( \mathbf x_t)\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace  +2 \xi tr\left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber\\
+ &&-tr \left\lbrace \boldsymbol\Theta q(\mathbf x_t)q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\right\rbrace  -2\xi tr \left\lbrace \boldsymbol\Theta q(\mathbf x_t)  \mathbf x_t^\top\boldsymbol\Sigma_e^{-1} \right\rbrace -\xi^2 tr \left\lbrace\mathbf x_t\mathbf x_t^\top\boldsymbol\Sigma_w^{-1} \right\rbrace  \nonumber
+ \end{eqnarray} 
+taking the expected value is leading to the following  $\mathcal Q$-function
+\begin{eqnarray}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2 tr\left\lbrace \boldsymbol\Theta\Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
+&-&tr \left\lbrace\boldsymbol\Theta\Xi_4 \boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\right\rbrace -2\xi tr \left\lbrace \boldsymbol\Theta\Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
+&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber
+\end{eqnarray}
+where  $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi)}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to the parameters and will disapear by differentiation and
+\begin{equation}
+ \Xi_0=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_{t+1}^\top] \quad \Xi_1=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_t^\top]
+\end{equation}
+Other terms can be approximated by linearising $q(\mathbf x)$ and taking the first-order truncated  Taylor-series expansion around the mean of the state at each time instant, i.e. 
+\begin{equation}\label{eq:qTaylor}
+ q(\mathbf x_t)=q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)
+\end{equation}
+where
+\begin{equation}
+\nabla q=\begin{bmatrix}\frac{\delta q}{\delta x_1} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t} &\frac{\delta q}{\delta x_2} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}& \dots &\frac{\delta q}{\delta x_n} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}\end{bmatrix}^\top
+\end{equation}
+therefore
+\begin{equation}
+ \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
+\end{equation}
+\begin{equation}
+ \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
+\end{equation}
+\begin{equation}
+ \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ]=q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
+\end{equation}
+we rewrite the $\mathcal Q$-function as
+\begin{eqnarray}\label{eq:rewrittenQ}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2  \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_2]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i} +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
+&-& \sum_{i,j,k,l=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_4]_{j,k}[ \boldsymbol\Theta^\top]_{k,l}[\boldsymbol\Sigma_e^{-1}]_{l,i} -2\xi \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_3]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i}  \nonumber \\
+&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  
+\end{eqnarray}
+we can simplify \eqref{eq:rewrittenQ} by noting that $[\boldsymbol \Theta]_{i,j}=\mathbf 0 \quad i \neq j$
+
+\begin{equation}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\beta +2\xi r_0 -\xi^2 r_1 +2 \boldsymbol\theta^\top \mathbf r_2-2\xi \boldsymbol\theta^\top \mathbf r_3  -\boldsymbol\theta^\top\mathbf R_4\boldsymbol\theta
+\end{equation}
+where 
+\begin{equation}
+ r_0=tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace   \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace \quad
+ \mathbf r_2=tr\left\lbrace \Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace \quad  \mathbf r_3= tr \left\lbrace \Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace \quad \mathbf R_4= tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber
+\end{equation}
+
+differentiate with respect to $\boldsymbol\theta$ and equating to zero we have
+\begin{eqnarray}
+\frac{\delta \mathcal Q}{\delta \boldsymbol \theta}=2\mathbf r_2^\top-2\xi \mathbf r_3^\top-2\boldsymbol \theta^\top\mathbf R_4^\top=0
+\end{eqnarray}
+therefore
+\begin{equation}\label{eq:thetasolution}
+ \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2-\xi\mathbf r_3)
+\end{equation}
+differentiate with respect to $\xi$ we have
+\begin{equation}
+ \frac{\delta \mathcal Q}{\delta \xi}=+2r_0-2\xi r_1-2\boldsymbol\theta^\top\mathbf r_3=0
+\end{equation}
+and we get
+\begin{equation}\label{eq:xisolution}
+ \xi=\frac{1}{r_1}(r_0- \boldsymbol \theta^\top \mathbf r_3)
+\end{equation}
+substituting \eqref{eq:thetasolution} in \eqref{eq:xisolution} we get
+\begin{eqnarray}
+\xi=\frac{r_0-r'_0}{r_1-r'_1}
+\end{eqnarray}
+where
+\begin{equation}
+ r'_0=\mathbf r_2^\top \mathbf R_4^{-\top}\mathbf r_3 \quad r'_1=\mathbf r_3^\top \mathbf R_4^{-\top}\mathbf r_3
+\end{equation}
+and subsequently
+\begin{equation}
+ \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2+\frac{r'_0-r_0}{r_1-r'_1} \mathbf r_3)
+\end{equation}
+\subsection*{Discussion}
+The second derivative of the $\mathcal Q$-function with respect to $\xi$ is given by
+\begin{equation}
+ \frac{\delta^2 \mathcal Q}{\delta \xi^2}=-2 r_1 \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace
+\end{equation}
+$\Xi_1 $ is positive definite if the state vector is persistently excited and the covariance matrix $\boldsymbol\Sigma_w^{-1}$ is also positive definite therefore the trace of $\Xi_1\boldsymbol\Sigma_w^{-1}$ is guaranteed to be positive so the second derivative is negative and represents a maximum of $\mathcal Q$-function.\\
+The second derivative of the $\mathcal Q$-function with respect to $\boldsymbol \theta$ is given by
+\begin{equation}
+ \frac{\delta^2 \mathcal Q}{\delta \boldsymbol\theta^2}=-2\mathbf R_4 \quad \mathbf R_4= tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace
+\end{equation}
+$\mathbf R_4$ is positive definite and invertible and the second derivative is negative definite and represents a maximum of $\mathcal Q$- function.
+\subsection*{Summary of the M-step}
+\begin{eqnarray}
+\xi=\frac{r_0-r'_0}{r_1-r'_1}
+ \quad  \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2+\frac{r'_0-r_0}{r_1-r'_1} \mathbf r_3)
+\end{eqnarray}
+where
+\begin{eqnarray}
+ r_0&=&tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber \\
+r'_0&=&\mathbf r_2^\top \mathbf R_4^{-\top}\mathbf r_3  \quad r'_1=\mathbf r_3^\top \mathbf R_4^{-\top}\mathbf r_3 \nonumber \\
+\nonumber \\
+ \mathbf r_2&=&tr\left\lbrace \Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace \quad \mathbf r_3= tr \left\lbrace \Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\ 
+ \mathbf R_4&=& tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber 
+\end{eqnarray}
+
+\begin{equation}
+ \Xi_0=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_{t+1}^\top] \quad \Xi_1=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_t^\top]
+\end{equation}
+\begin{equation}
+ \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
+\end{equation}
+\begin{equation}
+ \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
+\end{equation}
+\begin{equation}
+ \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ]=q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
+\end{equation}
 

### 2010-07-15 src/DataPaper/ReadAndPlotData.m
added cross correlation figure for determining support of kernel

@@ -20,7 +20,8 @@ if strcmp(User,'Dean')
     SpatialFreqCrossSectFig = '/Users/dean/Projects/BrainIDE/ltx/data_paper/Figures/SpatialFreqCrossSection.eps';
     FieldObservationsFig = '/Users/dean/Projects/BrainIDE/ltx/data_paper/Figures/FieldObservations.eps';
     LFPsFig = '/Users/dean/Projects/BrainIDE/ltx/data_paper/Figures/LFPs.eps';
-    
+    CrossCorrFig2D = '/Users/dean/Projects/BrainIDE/ltx/data_paper/Figures/CrossCorr2D.eps';
+    CrossCorrFig1D = '/Users/dean/Projects/BrainIDE/ltx/data_paper/Figures/CrossCorr1D.eps';
 elseif strcmp(User,'Parham')
     DataFileLocation = '';                  % file location
     TemporalFreqFig = '';                   % figure save location from here down.
@@ -94,6 +95,7 @@ BadChannels = [13 15 19 24 26 35 42 46 47 54 56  57 67 81 85 87];
 for n=1:length(BadChannels)
     MappedData(:,BadChannels(n)) = zeros(size(MappedData,1),1);
 end
+
 %%
 % now need to re-reference the data
 % ~~~~~~~~~~~~~~~~~~~~~
@@ -134,42 +136,42 @@ for n=1:size(FiltData,2)
 end
 
 %%
-NFFTPoints = 150*1024;
-YMax = 122;
-FMax = 100;
-figure('units','centimeters','position',[2,2,TwoColumnWidth,6],...
-    'filename',TemporalFreqFig)
-TemporalFFT1 = 20*log10(abs(fft(FiltData(1:SzStart*FsDec,GoodChannels),NFFTPoints,1)));
-TemporalFFT2 = 20*log10(abs(fft(FiltData(SzStart*FsDec+1:SzEnd*FsDec,GoodChannels),NFFTPoints,1)));
-TemporalFFT3 = 20*log10(abs(fft(FiltData(SzEnd*FsDec+1:end,GoodChannels),NFFTPoints,1)));
-
-f = linspace(0,FsDec,NFFTPoints);
-subplot(131),semilogx(f,mean(TemporalFFT1,2))
-xlim([0 FMax])
-ylim([60 YMax])
-axis square
-set(gca,'fontsize',FS,'fontname','arial')
[…]

### 2010-07-15 src/Matlab/GenerateData.m

@@ -36,6 +36,7 @@ v(1,:,:) = Define2DGaussian(0,0, sigma_phi^2, 0,NPoints,SpaceMin,SpaceMax);
 
 % generate data
 y = zeros(T,NSensors_xy^2);         % initialise obseravation for speed
+y_matrix = zeros(T,NSensors_xy,NSensors_xy);
 for t=1:T-1
     
     f = f_max./(1+exp(varsigma*(v_0-squeeze(v(t,:,:)))));           % calc firing rate using sigmoid
@@ -46,8 +47,9 @@ for t=1:T-1
     V = fft2(squeeze(v(t+1,:,:)));                                                  % take FFT of field for conv with sensor
     m_conv_v = ifftshift(ifft2(M.*V,'symmetric'))*Delta_squared;    % conv with sensor 
     
-    y_temp = m_conv_v(sensor_indexes,sensor_indexes) ...
+    y_matrix(t+1,:,:) = m_conv_v(sensor_indexes,sensor_indexes) ...
         + reshape(varepsilon(t+1,:,:),NSensors_xy,NSensors_xy);     % take indexes of field conv with sensor for observations
+    y_temp = squeeze(y_matrix(t+1,:,:));
     y(t+1,:) = y_temp(:);                                                                 % observations as a vector
     
 end

### 2010-07-15 src/Matlab/Set_Parameters.m

@@ -11,7 +11,7 @@ end
 % ~~~~~~~~~~~
 Delta = 0.5;                          % space step for the spatial discretisation
 Delta_squared = Delta^2;
-SpaceMax = 10;                    % maximum space in mm
+SpaceMax = 20;                    % maximum space in mm
 SpaceMin = -SpaceMax;         % minimum space in mm
 NPoints = (SpaceMax-SpaceMin)/Delta+1;
 r = linspace(SpaceMin,SpaceMax,NPoints);      % define space
@@ -56,7 +56,7 @@ end
 
 % sensor parameters
 % ~~~~~~~~~~~~
-NSensors_xy = 9;%21;%14;
+NSensors_xy = 11;%21;%14;
 NSensors = NSensors_xy^2;
 % mu_y_xy = linspace(-15,15,NSensors_xy);
 mu_y_xy = linspace(-10,10,NSensors_xy);               % sensor centers

### 2010-07-15 ltx/data_paper/DataPaper.tex
added cross correlation figure for determining support of kernel
minor correction to EM
added derivetive of q to the data paper

@@
 
+\subsection{Estimating Support For Connectivity Kernel}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[angle=-90]{./Figures/CrossCorr2D.eps}
+\end{center}
+\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}.
+Note: The correlations are normalised such that the maximum value is one.
+A.
+Pre-seizure observation correlations.
+B.
+Seizure observation correlations.
+C.
+Post-seizure observation correlations.}
+\label{fig:SpatialFreqObservation}
+\end{figure}
+
 \subsection{Pre-processing}
@@
 \begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t)=q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)
+ q(\mathbf x_t)\approx q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)
 \end{equation}
@@
 \end{equation}
+and
+\begin{equation}
+\frac{\delta q}{\delta x_i}= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\phi_i(\mathbf r') f'(\phi^\top(\mathbf{r}'){x}_t) d\mathbf{r}'\\
+\end{equation}
+
 therefore
 \begin{equation}
- \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
+ \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
 \end{equation}
 \begin{equation}
- \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
+ \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
 \end{equation}
 \begin{equation}
- \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ]=q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
+ \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ] \approx q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
 \end{equation}

### 2010-07-17 ltx/second_order_framework/second_order_manuscript.tex

@@
 
+\usepackage{anysize} 									%<-use this for checking equation length
+\marginsize {1.7cm}{1.5cm}{1cm}{1cm} 				%<-use this for checking equation length
+
 %to delete
 \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{yellow}{#1}}}}}
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
 
@@
 \section{Introduction}
+\dean{Hi Parham: I have added some headings.
+Hope they are ok.
+I was going to cut and paste the derivation in, but I thought I would let you do it, because it goes back and forth a little.
+When we get a structure (doesn't have to be how I laid it out) it will be easier for me to work on it too.}
 \begin{enumerate}
@@
 \end{enumerate}
+
+\section{Method}
+\subsection{Derivation of the Integro-Difference Equation Neural Field Model}
+
+\subsection{Model-Reduction: Derivation of Finite Dimensional State-Space Model}
+
+\subsection{Frequency Analysis: Determining Basis Function Width and Spacing}
+Need something about the method of placement of basis functions and sampling of the field. \dean{Are we going to go for a triangular grid of basis functions?}
+
+\subsection{Determining Connectivity Kernel Width}
+
+\subsection{Estimation: Expectation Maximization Algorithm}
+
+\section{Results}
+
+\subsection{Frequency Analysis}
+Confirmation of field sampling by sensors and show spatial frequency constraints on the approximated field.
+
+\subsection{Connectivity Kernel Width}
+
+\subsection{State and Parameters Estimation}
+Need to show the parameter distributions
+
+\section{Discussion and Conclusion}
+
 \section{State-Space Representation of the Spatio-temporal Nonlinear IDE}
@@
 To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
-\section{Second order stochastic Neural Field Model}
+\section{Second-Order Stochastic Neural Field Model}
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.

### 2010-07-18 ltx/data_paper/DataPaper.tex
added derivetive of q to the data paper
added to the methods section of the paper and added figure to check the assumption of homogeneity

@@
 % More symbols
-%\usepackage{amsmath}
-%\usepackage{amssymb}
+
 %\usepackage{latexsym}
@@
 \fi
+\usepackage{color}
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+
 \title{Patient-Specific Neural Field Model}
-\author{Parham Aram, Dean Freestone, Kenneth Scerri, Michael Dewar,\\
+\author{In no specific order: Parham Aram, Dean Freestone, Kenneth Scerri, Michael Dewar,\\
  Jacob Donoghue, Sydney Cash, David Grayden and Visakan Kadirkamanathan  }
@@
 
-\subsection{Data Collection}
+\subsection{Data Collection and Pre-processing}
 \begin{itemize}
@@
 
+Data was collected from a patient undergoing work-up for surgical resection of epileptic brain tissue.
+The standard procedure for the resective surgery involves implantation of subdural electrodes for intracranial EEG monitoring (iEEG).
+Data from these electrodes provide information for mapping functional and pathological tissue to define the surgical margins.
+In addition to standard iEEG electrodes, data was collected in parallel from a Neuroport system (Blackrock microsystems, Utah, USA) incorporating a micro-electrode array.
+This data was collected with informed consent from the patient under ethics approval from the MGH human research ethics committee..??
+Figure~\ref{MRI_CT} shows the position of the iEEGs electrodes and the micro-electrode array.
+The iEEG electrode covers the temporal lobe, and the micro-electrode placement was targeted at..
+The micro-electrode array consisted of square grid of 96 (10 by 10 with the corner electrodes missing).
+The x,y electrode spacing was 400~$\mu m$, yielding a coverage of 4 by 4~mm.
+Data from the Neuroport system was acquired with a sampling rate of 30~kHz, with hardware filters in the range of~\dean{??}.
+
+During the time-course of the iEEG monitoring several seizures were recorded. This study focuses on the local field potential (LFP) data recorded with the micro-electrode during a seizure.
+
+The pre-processing steps consisted of:
+\begin{itemize}
+	\item Identification and removal (set to nan) of severely noise corrupted channels (16 of 96 channels);
+	\item Implementation of a common average reference (CAR) montage; 
+	\item Low-pass filter data, with cut-off at 100~Hz;
+	\item Decimate data from 30~kHz to 5~kHz temporal sampling;
+	\item Spatially interpolate missing data to facilitate spatial frequency analysis.
+\end{itemize}
+
+\subsection{Spatio-temporal Analysis}
+The first 5 channels of the LFP time series from the seizure is shown in Figure~\ref{fig:TimeSeries}.
+For the analysis, the time series was segmented into three periods; the pre-seizure period, seizure period and post-seizure period.
+The seizure onset is marked by the red dotted line and the seizure end is marked by the blue dashed line.
+An example to illustrate the spatial aspects of the observed neural field is shown in Figure~\ref{fig:FieldObserations}.
+Each subplot in the figure shows the observaed field at a sample of the pre-processed data, with each plot separated in time by 2.5~ms.
+The figure shows spatially correlated activity.
+
 \begin{figure}[!ht]
@@
 \end{center}
-\caption{{\bf Local Field Potentials}. Data recorded from the first five channels of the array. The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
+\caption{{\bf Local field potentials from the micro-electrode array}.
+Data recorded from the first five channels of the array.
+The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
 \label{fig:TimeSeries}
@@
 \end{figure}
+
+To confirm the applicability of the model spatio-temporal analysis were performed.
+The spectral properties of the recorded time series for each of the time segments are shown in Figure~\ref{fig:TemporalFreqObservation}.
 
@@
 \caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:SpatialFreqObservation}
+\label{fig:DiagSpatialFreqObservation}
 \end{figure}
@@
 \begin{center}
-\includegraphics[angle=-90]{./Figures/CrossCorr2D.eps}
+\includegraphics{./Figures/CrossCorr2D.eps}
 \end{center}
@@
 Post-seizure observation correlations.}
-\label{fig:SpatialFreqObservation}
+\label{fig:SpatialCrossCorrelation}
 \end{figure}
 
-\subsection{Pre-processing}
-\begin{itemize}
-	\item Identification and removal of bad channels
-	\item Common average reference (CAR) montage 
-	\item Low-pass filter data, with cut-off at 100~Hz
-	\item Decimate data from 30~kHz to 5~kHz temporal sampling
-	\item Spatially interpolate missing data to facilitate spatial frequency analysis
-\end{itemize}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/HomoTestCrossCorr.eps}
+\end{center}
+\caption{{\bf Mean cross-correlations between subsets of the consecutive observations of the neural field}.}
+\label{fig:HomogeneityTest}
+\end{figure}
+
 \subsection{Estimation Algorithm}
@@
 \begin{equation}
-\nabla q=\begin{bmatrix}\frac{\delta q}{\delta x_1} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t} &\frac{\delta q}{\delta x_2} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}& \dots &\frac{\delta q}{\delta x_n} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}\end{bmatrix}^\top
+\nabla q=\begin{bmatrix}\frac{\delta q}{\delta x_{t,1}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t} &\frac{\delta q}{\delta x_{t,2}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}& \dots &\frac{\delta q}{\delta x_{t,n}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}\end{bmatrix}^\top
 \end{equation}
@@
 \begin{equation}
-\frac{\delta q}{\delta x_i}= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\phi_i(\mathbf r') f'(\phi^\top(\mathbf{r}'){x}_t) d\mathbf{r}'\\
+\frac{\delta q}{\delta x_{t,i}}= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\phi_i(\mathbf r') f'(\phi^\top(\mathbf{r}'){x}_t) d\mathbf{r}'\\
 \end{equation}

### 2010-07-18 src/DataPaper/ReadAndPlotData.m

@@ -192,22 +192,28 @@ for n=1:size(FiltData,1)
 %     DataFFT(n,:,:) = 20*log10(abs(fft2(MatrixDataTemp-MeanObservation,NPoints2DFFT,NPoints2DFFT )));
 end
 
-% plot the 2D cross-correlation
+%%
+% calc and plot the 2D cross-correlation
 disp('finding cross correlations')
 CrossCor = zeros(size(MatrixData,1),2*size(MatrixData,2)-1,2*size(MatrixData,2)-1);
 for n=1:size(MatrixData,1)-1   
-    CrossCor(n,:,:) = xcorr2(squeeze(MatrixData(n+1,:,:)),squeeze(MatrixData(n,:,:)));
+    CrossCor(n,:,:) = normxcorr2(squeeze(MatrixData(n+1,:,:)),squeeze(MatrixData(n,:,:)));
 end
 CrossCorrMeanPreSeizure = squeeze(mean(CrossCor(1:SzStart*FsDec,:,:),1)); 
-CrossCorrMeanPreSeizure=CrossCorrMeanPreSeizure/max(max(CrossCorrMeanPreSeizure));
+% CrossCorrMeanPreSeizure=CrossCorrMeanPreSeizure/max(max(CrossCorrMeanPreSeizure));
 CrossCorrMeanSeizure = squeeze(mean(CrossCor(SzStart*FsDec+1:SzEnd*FsDec,:,:),1)); 
-CrossCorrMeanSeizure=CrossCorrMeanSeizure/max(max(CrossCorrMeanSeizure));
+% CrossCorrMeanSeizure=CrossCorrMeanSeizure/max(max(CrossCorrMeanSeizure));
 CrossCorrMeanPostSeizure = squeeze(mean(CrossCor(SzEnd*FsDec:end,:,:),1)); 
-CrossCorrMeanPostSeizure=CrossCorrMeanPostSeizure/max(max(CrossCorrMeanPostSeizure));
+% CrossCorrMeanPostSeizure=CrossCorrMeanPostSeizure/max(max(CrossCorrMeanPostSeizure));
 
+%% 
+% the plots for the xcorrs
 SpactialLocation = linspace(-2,2,size(CrossCorrMeanPreSeizure,1));
 HeightOffset = 1;
 HeigthScale = 0.5;
+figure('units','centimeters','position',[2,2,TwoColumnWidth,6],'renderer','painters',...
[…]

### 2010-07-19 ltx/data_paper/DataPaper.tex
began to add a model derivation to the paper and updated figures

@@
 \end{itemize}
-
+The aim of this paper is to great a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.
 \section{Method}
 
+\subsection{Neural Field Model}
+The neural field equations used as the parametric form of the model are based on the influential papers from Wilson and Cowan~\cite{Wilson1973}, and Amari~\cite{Amari1977}.
+This class of model describes a continuous cortical sheet or surface, relating mean firing rates of pre and post-synaptic neural populations.
+The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the temporal convolution
+\begin{equation}
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}, 
+\end{equation}   
+where $h(\cdot)$ is the synaptic response kernel and $g(\cdot)$ describes the mean firing rate. The firing rate is described by spatial convolution
+\begin{equation}
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
+\end{equation}
+where $f(\cdot)$ relates mean post-synaptic potentials to mean firing rates, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing the cortical sheet or surface.
+The firing rate function is the sigmoidal activation function described by
+\begin{equation}
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{1}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}, 
+\end{equation}
+where $v_0$ and $\varsigma$ describe the firing threshold the slope of the sigmoid respectively.
+By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model
+\begin{equation}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
+	\int_{-\infty}^t 
+	h\left(t - t'\right) \int_\Omega
+	w\left(\mathbf{r},\mathbf{r}'\right) 
+	f\left( v\left( \mathbf{r}',t' \right)\right)
+	\textrm{d}\mathbf{r}'dt'.
+\end{equation}
+To arrive at the general intergral-differential equation form of the model, we shall express the synaptic response kernel as a Green's function 
+\begin{equation}
+	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
+\end{equation}
+where $D$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+\begin{equation}
+	\label{FinalFormContinuous} 
+	Dv\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}. 
+\end{equation}
 \subsection{Data Collection and Pre-processing}
@@
 
-\subsection{Spatio-temporal Analysis}
+\subsection{Spatiotemporal Data Analysis}
 The first 5 channels of the LFP time series from the seizure is shown in Figure~\ref{fig:TimeSeries}.
@@
 The seizure onset is marked by the red dotted line and the seizure end is marked by the blue dashed line.
-An example to illustrate the spatial aspects of the observed neural field is shown in Figure~\ref{fig:FieldObserations}.
-Each subplot in the figure shows the observaed field at a sample of the pre-processed data, with each plot separated in time by 2.5~ms.
-The figure shows spatially correlated activity.
 
@@
 
+An example to illustrate the spatial aspects of the observed neural field is shown in Figure~\ref{fig:FieldObserations}.
+Each subplot in the figure shows the observed field at a sample of the pre-processed data, with each plot separated in time by 2.5~ms.
+The figure shows spatially correlated activity.
+
 \begin{figure}[!ht]
@@
 
-To confirm the applicability of the model spatio-temporal analysis were performed.
 The spectral properties of the recorded time series for each of the time segments are shown in Figure~\ref{fig:TemporalFreqObservation}.
+Each plot shows an averaged (across channels) spectrum the data.
+The pre-seizure period shows a decay in power at a typical $1/f^2$ rate.
+The seizure period has higher power at low and high ends of the spectrum.
+In addition, there is a peak in the power of the LFPs at ~51~Hz during the seizure.
+This peak would be difficult to observe in European and Asian countries due to the 50~Hz mains power frequency.
+The post-seizure period shows a large increase in lower frequency power...
 
@@
 
-\subsection{Frequency Analysis}
-\begin{itemize}
-	\item Create 2D FT of observations to estimate bandwidth
-\end{itemize}
+Figure~\ref{fig:SpatialFreqObservation} shows the results of spatial frequency analysis of the observed neural field.
+Throughout this paper the spatial frequency shall be denoted by $\nu$.
+Each subplot is an average (across time) spatial frequency during either the pre-seizure, seizure or post-seizure periods.
+The spatial frequency of the neural field is governed by disturbances (inputs from outside the field) and the underlying connectivity structure.
+The symmetry in the plots provides some evidence for homogeneous and isotropic connectivity.
 
@@
 \end{figure}
+
+Figure~\ref{fig:DiagSpatialFreqObservation} shows diagonal cross-sections of the spatial frequency plots.
+From this figure we can see that the spatial cut-off frequency (-3~dB point) is $\nu_c \approx 0.26$~Hz.
+The profile of the diagonal cross-section indicates that the field is adequately sampled from the micro-electrode array, where the power drops by ~25~dB at the maximum observable spatial frequency (according to Shannon's sampling theorem) indicating spatial aliasing will have an insignificant effect.
+The spatial cut-off frequency provides information on the complexity of the model required to represent the neural field.
+Considering the field is band-limited, we can represent the continuous field by a finite set of continuous basis functions.
+According the Shannon's sampling theorem, the minimum spacing between basis functions, $\Delta_{\phi}$, to describe the field is
+\begin{equation}\label{eq:BasisFunctionSeparation}
+	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{c}}
+\end{equation}
+where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation.
 
@@
 \bibliographystyle{plain}
-\bibliography{}
+\bibliography{BrainIDE}
 \end{document}

### 2010-07-19 src/DataPaper/ReadAndPlotData.m

@@ -527,7 +527,7 @@ figure('units','centimeters','position',[0 0 2 30],'renderer','opengl')
 figure('units','centimeters','position',[2,2,TwoColumnWidth,6],...
     'filename',LFPsFig)
 StartChannel = 2;
-EndChannel = 100;
+EndChannel = 9;
 plot(t,OffsetData(:,StartChannel:EndChannel),'k','linewidth',0.5)
 axis tight
 axis off

### 2010-07-19 ltx/data_paper/DataPaper.tex
continued to add model derivation up to Euler method

@@
 \end{equation}   
-where $h(\cdot)$ is the synaptic response kernel and $g(\cdot)$ describes the mean firing rate. The firing rate is described by spatial convolution
+where $h(\cdot)$ is the synaptic response kernel and $g(\cdot)$ describes the mean firing rate.
+Assuming an infinite propagation velocity for action potentials within the field, the incoming firing rate the position $\mathbf{r}$ is described by spatial convolution
 \begin{equation}
@@
 \end{equation}
-where $f(\cdot)$ relates mean post-synaptic potentials to mean firing rates, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing the cortical sheet or surface.
-The firing rate function is the sigmoidal activation function described by
+where $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing the cortical sheet or surface.
+The function $f(\cdot)$ relates mean post-synaptic potentials to mean firing rates and follows a sigmoid described by
 \begin{equation}
@@
 \end{equation}
-To arrive at the general intergral-differential equation form of the model, we shall express the synaptic response kernel as a Green's function 
+To arrive at the general integral-differential equation form of the model, we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
@@
 \end{equation}
+By assuming the synaptic response kernel has the form 
+\begin{equation}
+	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}, 
+\end{equation}
+where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function, the operator $D$ is
+\begin{equation}
+	D=\frac{d}{dt} + \zeta,
+\end{equation}
+yielding
+\begin{equation}
+	\label{FinalFormContinuous} 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}.
+\end{equation}
+The neural field equations must be written as a discrete-time finite-dimensional model in order to relate it to patient-specific data.
+The discrete time model is found applying the a first-order Euler method giving
+\begin{equation}\label{EulerMethod}
+	\frac{v\left( \mathbf{r},t+T_s \right)-v\left( \mathbf{r},t \right)}{T_s} + \zeta v\left(\mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right) f\left( {v\left( \mathbf{r}',t \right)}\right)\textrm{d}\mathbf{r}'},
+\end{equation}
+where $T_s$ is the time step or sampling period. Rearranging equation~\ref{EulerMethod} gives the integro-difference equation
+\begin{equation}
+	\label{DiscreteTimeModel} 
+	v_{t+T_s}\left(\mathbf{r}\right) = 
+	\xi v_t\left(\mathbf{r}\right) + 
+	T_s \int_\Omega { 
+	    w\left(\mathbf{r},\mathbf{r}'\right)
+	    f\left(v_t\left(\mathbf{r}'\right)\right) 
+	\textrm{d}\mathbf{r}'}, 
+\end{equation}
+where $\xi = 1-T_s\zeta$.
+
 \subsection{Data Collection and Pre-processing}

### 2010-07-19 ltx/data_paper/DataPaper.tex
added the model reduction part to the paper

@@
 \end{equation}
-By assuming the synaptic response kernel has the form 
+By assuming the synaptic response kernel is of first order has the form of
 \begin{equation}
@@
 The neural field equations must be written as a discrete-time finite-dimensional model in order to relate it to patient-specific data.
-The discrete time model is found applying the a first-order Euler method giving
+The discrete-time model is found applying the a first-order Euler method giving
 \begin{equation}\label{EulerMethod}
@@
 \end{equation}
-where $T_s$ is the time step or sampling period. Rearranging equation~\ref{EulerMethod} gives the integro-difference equation
+where $T_s$ is the time step or sampling period. Rearranging equation~\ref{EulerMethod} gives the integro-difference equation (IDE) form
 \begin{equation}
@@
 \end{equation}
-where $\xi = 1-T_s\zeta$.
-
+where $\xi = 1-T_s\zeta$. Finally, a disturbance term is added, to account for uncertainty and unmodelled inputs, to the IDE form giving
+\begin{equation}
+	\label{NoisyDiscreteTimeModel} 
+	v_{t+T_s}\left(\mathbf{r}\right) = 
+	\xi v_t\left(\mathbf{r}\right) + 
+	T_s \int_\Omega { 
+	    w\left(\mathbf{r},\mathbf{r}'\right)
+	    f\left(v_t\left(\mathbf{r}'\right)\right) 
+	\textrm{d}\mathbf{r}'} 
+	+ e_t\left(\mathbf{r}\right), 
+\end{equation}
+where $e_t(\mathbf{r})$ is $i.i.d.$ such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+To reduce the model to a finite dimensional system the neural field is approximated by a basis function decomposition where
+\begin{equation}
+	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
+\end{equation}
+where $\mathbf{x}_t$ is a state vector that weights another vector of two-dimension Gaussian basis functions, $\boldsymbol{\phi}(\mathbf{r})$, described by
+\begin{equation}\label{eq:FieldBasisFunction}
+	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
+\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
+\end{equation}
+The parameter $\sigma_{\phi}$ controls the basis function width and is inferred by frequency analysis.
+Substituting equation~\ref{DefFieldDecomp} into~\ref{NoisyDiscreteTimeModel} gives to approximate model
+\begin{equation}
+	\label{eq:reduced continuous model}
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )w(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}
+	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+\end{equation}
+Next we multiply equation~\ref{eq:reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
+\begin{equation}
+	\label{StartofReduction}
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {w(\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}} + \xi\int_\Omega{\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t + \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
+\end{equation}
+Now by defining the matrix
+\begin{equation}\label{eq:DefGamma}
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)\textrm{d}\mathbf{r}} 
+\end{equation}
+enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken such that the state vector can is isolated on the left-hand-side as
+\begin{equation}\label{eq:ReducedForm}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega w(\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} 
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
+\end{equation}
 \subsection{Data Collection and Pre-processing}

### 2010-07-19 ltx/data_paper/DataPaper.tex
added to the model derivation and the pre-processing steps

@@
 \end{equation}
-where $T_s$ is the time step or sampling period. Rearranging equation~\ref{EulerMethod} gives the integro-difference equation (IDE) form
+where $T_s$ is the time step or sampling period.
+To simplify the notation, the sample at the the current time step shall be indexed by $t$ and the future time step by $t+1$ for the rest of the paper.
+Rearranging equation~\ref{EulerMethod} gives the integro-difference equation (IDE) form
 \begin{equation}
 	\label{DiscreteTimeModel} 
-	v_{t+T_s}\left(\mathbf{r}\right) = 
+	v_{t+1}\left(\mathbf{r}\right) = 
 	\xi v_t\left(\mathbf{r}\right) + 
@@
 	\label{NoisyDiscreteTimeModel} 
-	v_{t+T_s}\left(\mathbf{r}\right) = 
+	v_{t+1}\left(\mathbf{r}\right) = 
 	\xi v_t\left(\mathbf{r}\right) + 
@@
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
-To reduce the model to a finite dimensional system the neural field is approximated by a basis function decomposition where
+To reduce the model to a finite-dimensional system the neural field is approximated by a basis function decomposition where
 \begin{equation}
-	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
+	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t 
 \end{equation}
-where $\mathbf{x}_t$ is a state vector that weights another vector of two-dimension Gaussian basis functions, $\boldsymbol{\phi}(\mathbf{r})$, described by
+and $\mathbf{x}_t$ is a state vector that weights a vector of two-dimension Gaussian basis functions, $\boldsymbol{\phi}(\mathbf{r})$, described by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 	\label{eq:reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )w(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )w(\mathbf{r},\mathbf{r}')\textrm{d}\mathbf{r}'}
 	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
@@
 	\label{StartofReduction}
- 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {w(\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}} + \xi\int_\Omega{\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t + \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {w(\mathbf{r},\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}} + \xi\int_\Omega{\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t + \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
 \end{equation}
@@
 \end{equation}
-enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken such that the state vector can is isolated on the left-hand-side as
+enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken, such that the state vector can is isolated on the left-hand-side as
 \begin{equation}\label{eq:ReducedForm}
@@
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega w(\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} 
+	 \int_\Omega w(\mathbf{r},\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} 
 	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
 \end{equation}
+A property of the Gaussian basis function decomposition it that the Gaussianality of the disturbance term is maintained. The decomposition disturbance term is defined as
+\begin{equation}\label{eq:Wt} 
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )\textrm{d}\mathbf{r}},
+\end{equation}
+where $\mathbf{e}_t \sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$. The covariance matrix is defined as (see the Supporting Information, S1, for the derivation)
+\begin{equation}
+	\boldsymbol\Sigma_e \triangleq \mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+\end{equation}
+
 \subsection{Data Collection and Pre-processing}
-\begin{itemize}
-	\item Show medical imaging
-	\item Show LFP Data (background, seizure, post-seizure)
-	\item Show spectral properties of LFPs
-\end{itemize}
 
@@
 
-The pre-processing steps consisted of:
-\begin{itemize}
-	\item Identification and removal (set to nan) of severely noise corrupted channels (16 of 96 channels);
-	\item Implementation of a common average reference (CAR) montage; 
-	\item Low-pass filter data, with cut-off at 100~Hz;
-	\item Decimate data from 30~kHz to 5~kHz temporal sampling;
-	\item Spatially interpolate missing data to facilitate spatial frequency analysis.
-\end{itemize}
+The first pre-processing step was to identify channels that had very poor signal quality.
+These channels were set to the $nan$ data type.
+Following this, the data was re-referenced to a common average montage to remove common mode artifact and the effect of the reference electrode.
+Next the data was low-pass filtered with a cut-off frequency of 100~Hz.
+The data was then resampled from 30~kHz to 5~kHz.
+To enable spatial visualisation and spatial frequency analysis, the corrupted channels, set to $nan$, were interpolated using all neighbouring channels.
 
 \subsection{Spatiotemporal Data Analysis}
-The first 5 channels of the LFP time series from the seizure is shown in Figure~\ref{fig:TimeSeries}.
+The first 8 channels of the LFP time series from the seizure is shown in Figure~\ref{fig:TimeSeries}.
 For the analysis, the time series was segmented into three periods; the pre-seizure period, seizure period and post-seizure period.
@@
 \caption{{\bf Local field potentials from the micro-electrode array}.
-Data recorded from the first five channels of the array.
+Data recorded from the first 8 channels of the array.
 The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}

### 2010-07-19 ltx/data_paper/DataPaper.tex
minor edit to paper and added bib file

@@
 
-\title{Patient-Specific Neural Field Model}
-\author{In no specific order: Parham Aram, Dean Freestone, Kenneth Scerri, Michael Dewar,\\
- Jacob Donoghue, Sydney Cash, David Grayden and Visakan Kadirkamanathan  }
+\title{Patient-Specific Neural Field Modeling from Mirco-Electrode Data}
+\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
+ Jacob A. Donoghue, Sydney S. Cash, David B. Grayden and Visakan Kadirkamanathan  }
 
@@
 \subsection{Estimating Support For Connectivity Kernel}
+The support for the connectivity kernel can be inferred...
+
 \begin{figure}[!ht]
@@
 \end{center}
-\caption{{\bf Mean cross-correlations between subsets of the consecutive observations of the neural field}.}
+\caption{{\bf Mean cross-correlations between consecutive samples using subsets of observations of the neural field}.
+Each subplot shows correlations corresponding to a subset electrodes.
+Indexing the electrodes in a (x,y) grid, where index ranges from 1 to 10.
+Subplot A shows the mean correlation between electrode indexes (1-6, 5-10), subplot B shows correlations from indexes (5-10,5-10), subplot C shows indexes (1-6, 1-6) and subplot D shows indexes (5-10, 5-10).}
 \label{fig:HomogeneityTest}

### 2010-07-19 ltx/data_paper/DataPaper.tex
added note to paper about the connectivity kernel decomp

@@
 \end{equation}
-A property of the Gaussian basis function decomposition it that the Gaussianality of the disturbance term is maintained. The decomposition disturbance term is defined as
+A property of the basis function decomposition it the preservation of the Gaussianality of the disturbance term. The decomposition disturbance term is defined as
 \begin{equation}\label{eq:Wt} 
@@
 \end{equation}
+
+\dean{I will do the connectivity kernel decomposition bit after the correlation analysis, because we can use it to say something about heterogeneity and isotropy.}
 

### 2010-07-19 ltx/data_paper/DataPaper.tex
cmmiting for merge
changed the estimation algorithm

--- 2010-07-19 ltx/data_paper/DataPaper.tex
@@
 
-\subsection{Estimation Algorithm}
+\section{Estimation Algorithm}
+\subsection{state-space model}
 The state space model is given by
 \begin{equation}
- \mathbf x_{t+1}=\boldsymbol\Theta q(\mathbf x_t)+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)
+ \mathbf x_{t+1}=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)
 \end{equation}
@@
 \end{equation}
-where $\boldsymbol\Theta$ is an $n_x \times n_x$ block matrix where each block matrix is of dimension $ 1\times n_{\theta}$ defined as
-\begin{equation}
-\boldsymbol \Theta_{i,j}=\left\lbrace  \begin{array}{cc}
-\boldsymbol \theta^\top &i=j \\
-\mathbf 0_{1 \times n_{\theta}}& i\neq j  
- \end{array}\right. 
-\end{equation}
 and the non-linear map $q(.)$ is defined as
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	q(\mathbf{x}_t) \triangleq T_s\boldsymbol{\Gamma}^{-1} \int_\Omega \boldsymbol{\Lambda}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
 \end{equation}
-where $\boldsymbol{\Lambda}(\mathbf{r}')  $ is an $n_x \times 1$ block vector with each block of dimension $n_{\theta} \times 1 $
+where
 \begin{equation}\label{eq:DefPsi}
-\boldsymbol{\Lambda}(\mathbf{r}')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r')\\\boldsymbol \lambda_2(\mathbf r')\\ \vdots \\ \boldsymbol \lambda_{n_{x}}(\mathbf r') \end{bmatrix}_{n_x \times 1}
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
 \end{equation}
-and where
-\begin{equation}
-\boldsymbol \lambda_i(\mathbf r') =\begin{bmatrix} \phi_i\ast \psi_1(\mathbf r') \\ \phi_i\ast \psi_2 (\mathbf r') \\ \vdots \\ \phi_i\ast \psi_{n_{\theta}}(\mathbf r') \end{bmatrix}_{n_{\theta} \times 1}
-\end{equation}
-As a result $q(\mathbf x_t)$ is an $n_x \times 1$ block vector and each block is $n_{\theta} \times 1$. It should be noted that $\boldsymbol\Theta q(\mathbf x_t)$ is an $n_x \times 1$ vector.
 $ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.
-\subsection*{$\mathcal Q$-function}
-Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
+\subsection{$\mathcal Q$-function}
+Given a joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over observed variables $\mathbf Y$ and hidden variables $\mathbf X$ governed by parameters $\boldsymbol \theta$ and $\xi$, the goal is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$.
+It is often difficult to maximize the likelihood  $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly, however by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute
+a sequence of parameter estimates  that converges on the maximum likelihood parameter estimate. Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
 \begin{equation}
@@
 \end{equation}
-The $\mathcal Q$-function can be written in terms of its component as shown in (\ref{eq:jointdistribution})
+The $\mathcal Q$-function can be written in terms of joint distribution components as
 \begin{eqnarray}
@@
 \end{eqnarray}
-$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter therefore $\mathcal Q$-function can be rewritten as
+where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
+It should be noted that
+$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter set and therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}
-\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)]+\textrm{const}
+\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)]+\mathrm{const}
 \end{equation}
+the constant term can be ignored since it is not affecting the drivative with respect to the parameters. 
 The Gaussian distribution of the disturbance, $e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ results into the following conditional distribution of the state at $t+1$
 \begin{equation}
- p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=ce^{-(\mathbf x_{t+1}-\boldsymbol\Theta q(\mathbf  x_t)-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\boldsymbol\Theta q( \mathbf x_t)-\xi \mathbf  x_t)}
+ p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=\alpha e^{-(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
 \end{equation}
-where c is the normalising constant. Taking $\log$ we get
+where $\alpha$ is the normalising constant. Taking $\log$ we get
+\begin{eqnarray}\label{eq:Qfunction}
+  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
+&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t
+\end{eqnarray}
+taking trace and using invariant cyclic permutations property of the trace this distribution can be written
+as
+\begin{eqnarray}\label{eq:Qfunctionintrace}
+  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
+&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace
+\end{eqnarray}
+we first linearise $q(\mathbf x_t)$ by taking the first-order truncated  Taylor-series expansion around the mean of the state at each time instant for the sigmoidal activation function, i.e.
 \begin{equation}
- \ln p(\mathbf x_{t+1} |\mathbf x_t;\boldsymbol\theta,\xi)=\ln c -(\mathbf x_{t+1}^\top-q^\top(\mathbf x_t)\boldsymbol\Theta^\top -\xi  \mathbf x_t^\top)\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\boldsymbol\Theta q(\mathbf x_t)-\xi \mathbf x_t)
+ f(\boldsymbol \phi^\top(\mathbf r')\mathbf x_t) \approx f(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)+  \boldsymbol \phi^\top(\mathbf r')(\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)
 \end{equation}
+where we can approximate $q(\mathbf x_t)$ as
+\begin{equation}\label{eq:qTaylor}
+ q(\mathbf x_t) \approx q(\mathbf {\hat x}_t)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'
+\end{equation}
+By substituting \eqref{eq:qTaylor} in \eqref{eq:Qfunctionintrace}  and taking the expectation leads to the following  $\mathcal Q$-function
 \begin{eqnarray}
- \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta, \xi)&=&\ln c-[\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t \nonumber \\
-&&- q^\top(\mathbf x_t)\boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+q^\top(\mathbf x_t)\boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)+\xi q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\mathbf x_t \nonumber\\
-&&-\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+\xi  \mathbf  x_t^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)+\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t]
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2\Xi_0\boldsymbol\theta+
+2\xi tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
+&-&\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace\nonumber
 \end{eqnarray}
-\begin{eqnarray}\label{eq:Qfunctioninter}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q( \mathbf x_t)+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
-&&-q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t
-\end{eqnarray}
-taking trace and using invariant cyclic permutations property of the trace this distribution can be written as 
- \begin{eqnarray}
-   \ln p(x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2 tr \left\lbrace  \boldsymbol\Theta q( \mathbf x_t)\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace  +2 \xi tr\left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber\\
- &&-tr \left\lbrace \boldsymbol\Theta q(\mathbf x_t)q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\right\rbrace  -2\xi tr \left\lbrace \boldsymbol\Theta q(\mathbf x_t)  \mathbf x_t^\top\boldsymbol\Sigma_e^{-1} \right\rbrace -\xi^2 tr \left\lbrace\mathbf x_t\mathbf x_t^\top\boldsymbol\Sigma_w^{-1} \right\rbrace  \nonumber
- \end{eqnarray} 
-taking the expected value is leading to the following  $\mathcal Q$-function
-\begin{eqnarray}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2 tr\left\lbrace \boldsymbol\Theta\Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
-&-&tr \left\lbrace\boldsymbol\Theta\Xi_4 \boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\right\rbrace -2\xi tr \left\lbrace \boldsymbol\Theta\Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
-&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber
-\end{eqnarray}
-where  $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi)}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to the parameters and will disapear by differentiation and
+where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and
+\begin{equation}\label{eq:Xi0}
+ \Xi_0=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+\end{equation}
+\begin{equation}\label{eq:Xi1}
+ \Xi_1=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] 
+\end{equation}
 \begin{equation}
- \Xi_0=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_{t+1}^\top] \quad \Xi_1=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_t^\top]
-\end{equation}
-Other terms can be approximated by linearising $q(\mathbf x)$ and taking the first-order truncated  Taylor-series expansion around the mean of the state at each time instant, i.e. 
-\begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t)\approx q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)
+ \Xi_2=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t\tilde{\Lambda}_t(\mathbf r')
 \end{equation}
@@
 \begin{equation}
-\nabla q=\begin{bmatrix}\frac{\delta q}{\delta x_{t,1}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t} &\frac{\delta q}{\delta x_{t,2}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}& \dots &\frac{\delta q}{\delta x_{t,n}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}\end{bmatrix}^\top
+ \Lambda(\mathbf r')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \quad \text{and} \quad \tilde{\Lambda}(\mathbf r')=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix}
+\end{equation}
+and where
+\begin{equation}
+ \boldsymbol\lambda_i(\mathbf r')=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
 \end{equation}
@@
 \begin{equation}
-\frac{\delta q}{\delta x_{t,i}}= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\phi_i(\mathbf r') f'(\phi^\top(\mathbf{r}'){x}_t) d\mathbf{r}'\\
+ \tilde{\boldsymbol \lambda}_i(\mathbf r')=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
 \end{equation}
-
-therefore
+and 
 \begin{equation}
- \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
+ \Xi_3=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
 \end{equation}
 \begin{equation}
- \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
+ \Xi_4=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top]
 \end{equation}
+differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating to zero we get
 \begin{equation}
- \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ] \approx q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
+ \boldsymbol \theta=\Xi_2^{-\top}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
 \end{equation}
-we rewrite the $\mathcal Q$-function as
-\begin{eqnarray}\label{eq:rewrittenQ}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2  \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_2]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i} +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
-&-& \sum_{i,j,k,l=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_4]_{j,k}[ \boldsymbol\Theta^\top]_{k,l}[\boldsymbol\Sigma_e^{-1}]_{l,i} -2\xi \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_3]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i}  \nonumber \\
-&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  
-\end{eqnarray}
-we can simplify \eqref{eq:rewrittenQ} by noting that $[\boldsymbol \Theta]_{i,j}=\mathbf 0 \quad i \neq j$
-
+and
 \begin{equation}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\beta +2\xi r_0 -\xi^2 r_1 +2 \boldsymbol\theta^\top \mathbf r_2-2\xi \boldsymbol\theta^\top \mathbf r_3  -\boldsymbol\theta^\top\mathbf R_4\boldsymbol\theta
+ \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}
 \end{equation}
-where 
-\begin{equation}
- r_0=tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace   \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace \quad
- \mathbf r_2=tr\left\lbrace \Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace \quad  \mathbf r_3= tr \left\lbrace \Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace \quad \mathbf R_4= tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber
-\end{equation}
-
-differentiate with respect to $\boldsymbol\theta$ and equating to zero we have
-\begin{eqnarray}
-\frac{\delta \mathcal Q}{\delta \boldsymbol \theta}=2\mathbf r_2^\top-2\xi \mathbf r_3^\top-2\boldsymbol \theta^\top\mathbf R_4^\top=0
-\end{eqnarray}
-therefore
-\begin{equation}\label{eq:thetasolution}
- \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2-\xi\mathbf r_3)
-\end{equation}
-differentiate with respect to $\xi$ we have
-\begin{equation}
- \frac{\delta \mathcal Q}{\delta \xi}=+2r_0-2\xi r_1-2\boldsymbol\theta^\top\mathbf r_3=0
-\end{equation}
-and we get
-\begin{equation}\label{eq:xisolution}
- \xi=\frac{1}{r_1}(r_0- \boldsymbol \theta^\top \mathbf r_3)
-\end{equation}
-substituting \eqref{eq:thetasolution} in \eqref{eq:xisolution} we get
-\begin{eqnarray}
-\xi=\frac{r_0-r'_0}{r_1-r'_1}
-\end{eqnarray}
-where
-\begin{equation}
- r'_0=\mathbf r_2^\top \mathbf R_4^{-\top}\mathbf r_3 \quad r'_1=\mathbf r_3^\top \mathbf R_4^{-\top}\mathbf r_3
-\end{equation}
-and subsequently
-\begin{equation}
- \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2+\frac{r'_0-r_0}{r_1-r'_1} \mathbf r_3)
-\end{equation}
-\subsection*{Discussion}
+\subsection{Discussion}
 The second derivative of the $\mathcal Q$-function with respect to $\xi$ is given by
 \begin{equation}
- \frac{\delta^2 \mathcal Q}{\delta \xi^2}=-2 r_1 \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace
+ \frac{\delta^2 \mathcal Q}{\delta \xi^2}=-2 tr \left\lbrace\Xi_1\boldsymbol\Sigma_e^{-1} \right\rbrace
 \end{equation}
-$\Xi_1 $ is positive definite if the state vector is persistently excited and the covariance matrix $\boldsymbol\Sigma_w^{-1}$ is also positive definite therefore the trace of $\Xi_1\boldsymbol\Sigma_w^{-1}$ is guaranteed to be positive so the second derivative is negative and represents a maximum of $\mathcal Q$-function.\\
+$\Xi_1 $ is positive definite if the state vector is persistently excited and the covariance matrix $\boldsymbol\Sigma_e^{-1}$ is also positive definite therefore the trace of $\Xi_1\boldsymbol\Sigma_w^{-1}$ is guaranteed to be positive so the second derivative is negative and represents a maximum of $\mathcal Q$-function.\\
 The second derivative of the $\mathcal Q$-function with respect to $\boldsymbol \theta$ is given by
 \begin{equation}
- \frac{\delta^2 \mathcal Q}{\delta \boldsymbol\theta^2}=-2\mathbf R_4 \quad \mathbf R_4= tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace
+ \frac{\delta^2 \mathcal Q}{\delta \boldsymbol\theta^2}=-2 \Xi_2 
 \end{equation}
-$\mathbf R_4$ is positive definite and invertible and the second derivative is negative definite and represents a maximum of $\mathcal Q$- function.
-\subsection*{Summary of the M-step}
-\begin{eqnarray}
-\xi=\frac{r_0-r'_0}{r_1-r'_1}
- \quad  \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2+\frac{r'_0-r_0}{r_1-r'_1} \mathbf r_3)
-\end{eqnarray}
-where
-\begin{eqnarray}
- r_0&=&tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber \\
-r'_0&=&\mathbf r_2^\top \mathbf R_4^{-\top}\mathbf r_3  \quad r'_1=\mathbf r_3^\top \mathbf R_4^{-\top}\mathbf r_3 \nonumber \\
-\nonumber \\
- \mathbf r_2&=&tr\left\lbrace \Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace \quad \mathbf r_3= tr \left\lbrace \Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\ 
- \mathbf R_4&=& tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber 
-\end{eqnarray}
-
-\begin{equation}
- \Xi_0=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_{t+1}^\top] \quad \Xi_1=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_t^\top]
-\end{equation}
-\begin{equation}
- \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
-\end{equation}
-\begin{equation}
- \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
-\end{equation}
-\begin{equation}
- \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ]=q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
-\end{equation}
+$\Xi_2$ is positive definite and invertible and the second derivative is negative definite and represents a maximum of $\mathcal Q$- function.
 

### 2010-07-19 ltx/data_paper/DataPaper.tex
minor correction to the estimation algorithm

@@
 \end{eqnarray}
-where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and
+where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and
 \begin{equation}\label{eq:Xi0}

### 2010-07-20 ltx/data_paper/DataPaper.tex
small edit to paper

--- 2010-07-19 ltx/data_paper/DataPaper.tex
@@
 From this figure we can see that the spatial cut-off frequency (-3~dB point) is $\nu_c \approx 0.26$~Hz.
-The profile of the diagonal cross-section indicates that the field is adequately sampled from the micro-electrode array, where the power drops by ~25~dB at the maximum observable spatial frequency (according to Shannon's sampling theorem) indicating spatial aliasing will have an insignificant effect.
+The profile of the diagonal cross-section indicates that the field is adequately sampled from the micro-electrode array, where the power drops by approximately 25~dB at the maximum observable spatial frequency (according to Shannon's sampling theorem) indicating spatial aliasing will have an insignificant effect.
 The spatial cut-off frequency provides information on the complexity of the model required to represent the neural field.
@@
 
-\section{Estimation Algorithm}
-\subsection{state-space model}
+\subsection{Estimation Algorithm}
 The state space model is given by
 \begin{equation}
- \mathbf x_{t+1}=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)
+ \mathbf x_{t+1}=\boldsymbol\Theta q(\mathbf x_t)+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)
 \end{equation}
@@
 \end{equation}
+where $\boldsymbol\Theta$ is an $n_x \times n_x$ block matrix where each block matrix is of dimension $ 1\times n_{\theta}$ defined as
+\begin{equation}
+\boldsymbol \Theta_{i,j}=\left\lbrace  \begin{array}{cc}
+\boldsymbol \theta^\top &i=j \\
+\mathbf 0_{1 \times n_{\theta}}& i\neq j  
+ \end{array}\right. 
+\end{equation}
 and the non-linear map $q(.)$ is defined as
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+	q(\mathbf{x}_t) \triangleq T_s\boldsymbol{\Gamma}^{-1} \int_\Omega \boldsymbol{\Lambda}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
 \end{equation}
-where
+where $\boldsymbol{\Lambda}(\mathbf{r}')  $ is an $n_x \times 1$ block vector with each block of dimension $n_{\theta} \times 1 $
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
+\boldsymbol{\Lambda}(\mathbf{r}')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r')\\\boldsymbol \lambda_2(\mathbf r')\\ \vdots \\ \boldsymbol \lambda_{n_{x}}(\mathbf r') \end{bmatrix}_{n_x \times 1}
 \end{equation}
+and where
+\begin{equation}
+\boldsymbol \lambda_i(\mathbf r') =\begin{bmatrix} \phi_i\ast \psi_1(\mathbf r') \\ \phi_i\ast \psi_2 (\mathbf r') \\ \vdots \\ \phi_i\ast \psi_{n_{\theta}}(\mathbf r') \end{bmatrix}_{n_{\theta} \times 1}
+\end{equation}
+As a result $q(\mathbf x_t)$ is an $n_x \times 1$ block vector and each block is $n_{\theta} \times 1$. It should be noted that $\boldsymbol\Theta q(\mathbf x_t)$ is an $n_x \times 1$ vector.
 $ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.
-\subsection{$\mathcal Q$-function}
-Given a joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over observed variables $\mathbf Y$ and hidden variables $\mathbf X$ governed by parameters $\boldsymbol \theta$ and $\xi$, the goal is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$.
-It is often difficult to maximize the likelihood  $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly, however by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute
-a sequence of parameter estimates  that converges on the maximum likelihood parameter estimate. Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
+\subsection*{$\mathcal Q$-function}
+Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
 \begin{equation}
@@
 \end{equation}
-The $\mathcal Q$-function can be written in terms of joint distribution components as
+The $\mathcal Q$-function can be written in terms of its component as shown in (\ref{eq:jointdistribution})
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
-It should be noted that
-$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter set and therefore $\mathcal Q$-function can be rewritten as
+$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}
-\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)]+\mathrm{const}
+\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)]+\textrm{const}
 \end{equation}
-the constant term can be ignored since it is not affecting the drivative with respect to the parameters. 
 The Gaussian distribution of the disturbance, $e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ results into the following conditional distribution of the state at $t+1$
 \begin{equation}
- p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=\alpha e^{-(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
+ p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=ce^{-(\mathbf x_{t+1}-\boldsymbol\Theta q(\mathbf  x_t)-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\boldsymbol\Theta q( \mathbf x_t)-\xi \mathbf  x_t)}
 \end{equation}
-where $\alpha$ is the normalising constant. Taking $\log$ we get
-\begin{eqnarray}\label{eq:Qfunction}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
-&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t
+where c is the normalising constant. Taking $\log$ we get
+\begin{equation}
+ \ln p(\mathbf x_{t+1} |\mathbf x_t;\boldsymbol\theta,\xi)=\ln c -(\mathbf x_{t+1}^\top-q^\top(\mathbf x_t)\boldsymbol\Theta^\top -\xi  \mathbf x_t^\top)\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\boldsymbol\Theta q(\mathbf x_t)-\xi \mathbf x_t)
+\end{equation}
+\begin{eqnarray}
+ \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta, \xi)&=&\ln c-[\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t \nonumber \\
+&&- q^\top(\mathbf x_t)\boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+q^\top(\mathbf x_t)\boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)+\xi q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\mathbf x_t \nonumber\\
+&&-\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+\xi  \mathbf  x_t^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)+\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t]
 \end{eqnarray}
-taking trace and using invariant cyclic permutations property of the trace this distribution can be written
-as
-\begin{eqnarray}\label{eq:Qfunctionintrace}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace
+\begin{eqnarray}\label{eq:Qfunctioninter}
+  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q( \mathbf x_t)+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
+&&-q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\boldsymbol\Theta q(\mathbf x_t)-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t
 \end{eqnarray}
-we first linearise $q(\mathbf x_t)$ by taking the first-order truncated  Taylor-series expansion around the mean of the state at each time instant for the sigmoidal activation function, i.e.
+taking trace and using invariant cyclic permutations property of the trace this distribution can be written as 
+ \begin{eqnarray}
+   \ln p(x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2 tr \left\lbrace  \boldsymbol\Theta q( \mathbf x_t)\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace  +2 \xi tr\left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber\\
+ &&-tr \left\lbrace \boldsymbol\Theta q(\mathbf x_t)q^\top(\mathbf x_t)\boldsymbol\Theta^\top \boldsymbol\Sigma_e^{-1}\right\rbrace  -2\xi tr \left\lbrace \boldsymbol\Theta q(\mathbf x_t)  \mathbf x_t^\top\boldsymbol\Sigma_e^{-1} \right\rbrace -\xi^2 tr \left\lbrace\mathbf x_t\mathbf x_t^\top\boldsymbol\Sigma_w^{-1} \right\rbrace  \nonumber
+ \end{eqnarray} 
+taking the expected value is leading to the following  $\mathcal Q$-function
+\begin{eqnarray}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2 tr\left\lbrace \boldsymbol\Theta\Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
+&-&tr \left\lbrace\boldsymbol\Theta\Xi_4 \boldsymbol\Theta^\top\boldsymbol\Sigma_e^{-1}\right\rbrace -2\xi tr \left\lbrace \boldsymbol\Theta\Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
+&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber
+\end{eqnarray}
+where  $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi)}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to the parameters and will disapear by differentiation and
 \begin{equation}
- f(\boldsymbol \phi^\top(\mathbf r')\mathbf x_t) \approx f(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)+  \boldsymbol \phi^\top(\mathbf r')(\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)
+ \Xi_0=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_{t+1}^\top] \quad \Xi_1=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_t^\top]
 \end{equation}
-where we can approximate $q(\mathbf x_t)$ as
+Other terms can be approximated by linearising $q(\mathbf x)$ and taking the first-order truncated  Taylor-series expansion around the mean of the state at each time instant, i.e. 
 \begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t) \approx q(\mathbf {\hat x}_t)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'
-\end{equation}
-By substituting \eqref{eq:qTaylor} in \eqref{eq:Qfunctionintrace}  and taking the expectation leads to the following  $\mathcal Q$-function
-\begin{eqnarray}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2\Xi_0\boldsymbol\theta+
-2\xi tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&-&\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace\nonumber
-\end{eqnarray}
-where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and
-\begin{equation}\label{eq:Xi0}
- \Xi_0=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
-\end{equation}
-\begin{equation}\label{eq:Xi1}
- \Xi_1=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] 
-\end{equation}
-\begin{equation}
- \Xi_2=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t\tilde{\Lambda}_t(\mathbf r')
+ q(\mathbf x_t)\approx q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)
 \end{equation}
@@
 \begin{equation}
- \Lambda(\mathbf r')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \quad \text{and} \quad \tilde{\Lambda}(\mathbf r')=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix}
-\end{equation}
-and where
-\begin{equation}
- \boldsymbol\lambda_i(\mathbf r')=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
+\nabla q=\begin{bmatrix}\frac{\delta q}{\delta x_{t,1}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t} &\frac{\delta q}{\delta x_{t,2}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}& \dots &\frac{\delta q}{\delta x_{t,n}} \mid_{{\mathbf x}_t=\mathbf{\hat x}_t}\end{bmatrix}^\top
 \end{equation}
@@
 \begin{equation}
- \tilde{\boldsymbol \lambda}_i(\mathbf r')=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
+\frac{\delta q}{\delta x_{t,i}}= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\phi_i(\mathbf r') f'(\phi^\top(\mathbf{r}'){x}_t) d\mathbf{r}'\\
 \end{equation}
-and 
+
+therefore
 \begin{equation}
- \Xi_3=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+ \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
 \end{equation}
 \begin{equation}
- \Xi_4=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top]
+ \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
 \end{equation}
-differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating to zero we get
 \begin{equation}
- \boldsymbol \theta=\Xi_2^{-\top}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
+ \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ] \approx q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
 \end{equation}
-and
+we rewrite the $\mathcal Q$-function as
+\begin{eqnarray}\label{eq:rewrittenQ}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2  \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_2]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i} +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
+&-& \sum_{i,j,k,l=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_4]_{j,k}[ \boldsymbol\Theta^\top]_{k,l}[\boldsymbol\Sigma_e^{-1}]_{l,i} -2\xi \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_3]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i}  \nonumber \\
+&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  
+\end{eqnarray}
+we can simplify \eqref{eq:rewrittenQ} by noting that $[\boldsymbol \Theta]_{i,j}=\mathbf 0 \quad i \neq j$
+
 \begin{equation}
- \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\beta +2\xi r_0 -\xi^2 r_1 +2 \boldsymbol\theta^\top \mathbf r_2-2\xi \boldsymbol\theta^\top \mathbf r_3  -\boldsymbol\theta^\top\mathbf R_4\boldsymbol\theta
 \end{equation}
-\subsection{Discussion}
+where 
+\begin{equation}
+ r_0=tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace   \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace \quad
+ \mathbf r_2=tr\left\lbrace \Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace \quad  \mathbf r_3= tr \left\lbrace \Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace \quad \mathbf R_4= tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber
+\end{equation}
+
+differentiate with respect to $\boldsymbol\theta$ and equating to zero we have
+\begin{eqnarray}
+\frac{\delta \mathcal Q}{\delta \boldsymbol \theta}=2\mathbf r_2^\top-2\xi \mathbf r_3^\top-2\boldsymbol \theta^\top\mathbf R_4^\top=0
+\end{eqnarray}
+therefore
+\begin{equation}\label{eq:thetasolution}
+ \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2-\xi\mathbf r_3)
+\end{equation}
+differentiate with respect to $\xi$ we have
+\begin{equation}
+ \frac{\delta \mathcal Q}{\delta \xi}=+2r_0-2\xi r_1-2\boldsymbol\theta^\top\mathbf r_3=0
+\end{equation}
+and we get
+\begin{equation}\label{eq:xisolution}
+ \xi=\frac{1}{r_1}(r_0- \boldsymbol \theta^\top \mathbf r_3)
+\end{equation}
+substituting \eqref{eq:thetasolution} in \eqref{eq:xisolution} we get
+\begin{eqnarray}
+\xi=\frac{r_0-r'_0}{r_1-r'_1}
+\end{eqnarray}
+where
+\begin{equation}
+ r'_0=\mathbf r_2^\top \mathbf R_4^{-\top}\mathbf r_3 \quad r'_1=\mathbf r_3^\top \mathbf R_4^{-\top}\mathbf r_3
+\end{equation}
+and subsequently
+\begin{equation}
+ \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2+\frac{r'_0-r_0}{r_1-r'_1} \mathbf r_3)
+\end{equation}
+\subsection*{Discussion}
 The second derivative of the $\mathcal Q$-function with respect to $\xi$ is given by
 \begin{equation}
- \frac{\delta^2 \mathcal Q}{\delta \xi^2}=-2 tr \left\lbrace\Xi_1\boldsymbol\Sigma_e^{-1} \right\rbrace
+ \frac{\delta^2 \mathcal Q}{\delta \xi^2}=-2 r_1 \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace
 \end{equation}
-$\Xi_1 $ is positive definite if the state vector is persistently excited and the covariance matrix $\boldsymbol\Sigma_e^{-1}$ is also positive definite therefore the trace of $\Xi_1\boldsymbol\Sigma_w^{-1}$ is guaranteed to be positive so the second derivative is negative and represents a maximum of $\mathcal Q$-function.\\
+$\Xi_1 $ is positive definite if the state vector is persistently excited and the covariance matrix $\boldsymbol\Sigma_w^{-1}$ is also positive definite therefore the trace of $\Xi_1\boldsymbol\Sigma_w^{-1}$ is guaranteed to be positive so the second derivative is negative and represents a maximum of $\mathcal Q$-function.\\
 The second derivative of the $\mathcal Q$-function with respect to $\boldsymbol \theta$ is given by
 \begin{equation}
- \frac{\delta^2 \mathcal Q}{\delta \boldsymbol\theta^2}=-2 \Xi_2 
+ \frac{\delta^2 \mathcal Q}{\delta \boldsymbol\theta^2}=-2\mathbf R_4 \quad \mathbf R_4= tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace
 \end{equation}
-$\Xi_2$ is positive definite and invertible and the second derivative is negative definite and represents a maximum of $\mathcal Q$- function.
+$\mathbf R_4$ is positive definite and invertible and the second derivative is negative definite and represents a maximum of $\mathcal Q$- function.
+\subsection*{Summary of the M-step}
+\begin{eqnarray}
+\xi=\frac{r_0-r'_0}{r_1-r'_1}
+ \quad  \boldsymbol \theta=\mathbf R_4^{-1}(\mathbf r_2+\frac{r'_0-r_0}{r_1-r'_1} \mathbf r_3)
+\end{eqnarray}
+where
+\begin{eqnarray}
+ r_0&=&tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace \quad r_1=tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber \\
+r'_0&=&\mathbf r_2^\top \mathbf R_4^{-\top}\mathbf r_3  \quad r'_1=\mathbf r_3^\top \mathbf R_4^{-\top}\mathbf r_3 \nonumber \\
+\nonumber \\
+ \mathbf r_2&=&tr\left\lbrace \Xi_2\boldsymbol\Sigma_e^{-1}\right\rbrace \quad \mathbf r_3= tr \left\lbrace \Xi_3\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\ 
+ \mathbf R_4&=& tr \left\lbrace\Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace\nonumber 
+\end{eqnarray}
+
+\begin{equation}
+ \Xi_0=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_{t+1}^\top] \quad \Xi_1=\sum_{t=1}^T\mathbf E_{(\theta',\xi')}[\mathbf x_t\mathbf x_t^\top]
+\end{equation}
+\begin{equation}
+ \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
+\end{equation}
+\begin{equation}
+ \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
+\end{equation}
+\begin{equation}
+ \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ]=q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
+\end{equation}
 

### 2010-07-20 src/DataPaper/ReadAndPlotData.m

@@ -54,7 +54,7 @@ FS2 = 12;
 
 TwoColumnWidth = 17.35;     % PLoS figure width cm
 OneColumnWidth = 8.3; % cm
-Fs = 30e3;                              % sampling rate in Hz
+Fs = 30e3;                              % sampling rate in Hz of the raw data
 FsDec = 5e3;                          % this is the sampling rate that we will use
 TsDec = 1/FsDec;                    % the decimated sampling period
 DecimationFactor = Fs/FsDec;
@@ -86,7 +86,7 @@ for n=1:100
     if n==1 || n==10 || n==91 || n==100
         MappedData(:,n) = zeros(size(Data,1),1);
     else
-        MappedData(:,n) = Data(:,DataMap(n)) - mean(Data(:,DataMap(n)));
+        MappedData(:,n) = Data(:,DataMap(n));
     end
 end
 clear Data      % save some RAM
@@ -144,6 +144,9 @@ end
 % FMax = 100;
 % figure('units','centimeters','position',[2,2,TwoColumnWidth,6],...
 %     'filename',TemporalFreqFig)
+
+% need to remove the mean here!!!
+
 % TemporalFFT1 = 20*log10(abs(fft(FiltData(1:SzStart*FsDec,GoodChannels),NFFTPoints,1)));
 % TemporalFFT2 = 20*log10(abs(fft(FiltData(SzStart*FsDec+1:SzEnd*FsDec,GoodChannels),NFFTPoints,1)));
 % TemporalFFT3 = 20*log10(abs(fft(FiltData(SzEnd*FsDec+1:end,GoodChannels),NFFTPoints,1)));
@@ -196,8 +199,11 @@ end
 % calc and plot the 2D cross-correlation
 disp('finding cross correlations')
 CrossCor = zeros(size(MatrixData,1),2*size(MatrixData,2)-1,2*size(MatrixData,2)-1);
+v0 = 2;
+varsigma = 0.56;
 for n=1:size(MatrixData,1)-1   
-    CrossCor(n,:,:) = normxcorr2(squeeze(MatrixData(n+1,:,:)),squeeze(MatrixData(n,:,:)));
+    f = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,:,:)))));
[…]

### 2010-07-20 ltx/data_paper/DataPaper.tex
commiting for merge

@@
 
+To relate the model to the data the electrodes are also modelled.
+The electrodes have a pick-up range (for LFPs) of approximately 400~$\mu$m.
+Therefore, we model the electrodes as a spatial convolution of a Gaussian shaped sensor kernel (using a width parameters of 400~$\mu$m) with the neural field.
+The observation equation is
+\begin{equation}
+    \label{eq:ObservationEquation}
+	\mathbf{y}_t =
+	\int_{\Omega}{
+	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
+	\textrm{d}\mathbf{r}'} + 
+	\boldsymbol{\varepsilon}_t, 
+\end{equation}
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$.
+$\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+The sensor kernel, $m(\mathbf{r}-\mathbf{r}')$, is defined by
+\begin{equation}
+	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)},
+\end{equation}
+where $\sigma_m$ sets the sensor width.
+Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
+\begin{equation}\label{eq:ReducedObservationEquation}
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+\end{equation}
+The observation equation is linear with respect to the state and can be written in the more compact form
+\begin{equation}\label{ObservationEquation} 
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+\end{equation}
+where the observation matrix is 
+\begin{equation}
+	\mathbf{C} = \left[
+	\begin{array}{{ccc}} 
+		c_{1,1} & \dots & c_{1,L} \\
+		\vdots & \ddots & \vdots \\
+		c_{N,1} & \dots & c_{N,L} 
+	\end{array}
+	\right] 
+\end{equation}
+and 
+\begin{equation}
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
+\end{equation}
+
 \dean{I will do the connectivity kernel decomposition bit after the correlation analysis, because we can use it to say something about heterogeneity and isotropy.}
@@
 \subsection{Estimating Support For Connectivity Kernel}
-The support for the connectivity kernel can be inferred...
+The support for the connectivity kernel can be inferred by studying the correlation between consecutive observations of the neural field. 
+\begin{itemize}
+	\item it is difficult to tell what correlations are from the cross-talk due the the sensor kernel
+	\item it is difficult because of the nonlinear function
+	\item 
+\end{itemize}
 
@@
 \section{Estimation Algorithm}
-\subsection{state-space model}
-The state space model is given by
+\subsection{State-Space Model}
+The state-space model is given by
 \begin{equation}

### 2010-07-21 ltx/data_paper/DataPaper.tex
change to scaling in plots

@@
 \author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
- Jacob A. Donoghue, Sydney S. Cash, David B. Grayden and Visakan Kadirkamanathan  }
+ Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
+ David B. Grayden and Visakan Kadirkamanathan  }
 
@@
 The state-space model is given by
-\begin{equation}
- \mathbf x_{t+1}=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)
-\end{equation}
-\begin{equation}
- \mathbf y_t=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t
-\end{equation}
-and the non-linear map $q(.)$ is defined as
+\begin{align}
+ \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \\
+ \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t
+\end{align}
+and the nonlinear function, $q(\cdot)$, is defined as
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
+	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}',
 \end{equation}
@@
 $ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.
+
 \subsection{$\mathcal Q$-function}
-Given a joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over observed variables $\mathbf Y$ and hidden variables $\mathbf X$ governed by parameters $\boldsymbol \theta$ and $\xi$, the goal is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$.
-It is often difficult to maximize the likelihood  $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly, however by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute
-a sequence of parameter estimates  that converges on the maximum likelihood parameter estimate. Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
-\begin{equation}
- p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0)
-\label{eq:jointdistribution}
+The goal of the M-step is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol \theta$ and $\xi$.
+Unfortunately, it is often difficult to maximize the likelihood $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly.
+However, by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.
+
+Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
+\begin{equation}\label{eq:jointdistribution}
+ p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0).
 \end{equation}
-The $\mathcal Q$-function can be written in terms of joint distribution components as
+The $\mathcal Q$-function, or lower bound on the likelihood, can be written in terms of joint distribution components as
 \begin{eqnarray}

### 2010-07-21 src/DataPaper/ReadAndPlotData.m

@@ -217,10 +217,11 @@ CrossCorrMeanPostSeizure = squeeze(mean(CrossCor(SzEnd*FsDec:end,:,:),1));
 SpactialLocation = linspace(-2,2,size(CrossCorrMeanPreSeizure,1));
 HeightOffset = 1;
 HeigthScale = 0.5;
+ColorbarLims = [-1 1];
 figure('units','centimeters','position',[2,2,TwoColumnWidth,6],'renderer','painters',...
     'filename',CrossCorrFig2D)
 subplot(131)
-imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanPreSeizure)
+imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanPreSeizure,ColorbarLims)
 xlabel('Space (mm)','fontsize',FS,'fontname','arial')
 ylabel('Space (mm)','fontsize',FS,'fontname','arial')
 title('\bf A','fontsize',FS2,'fontname','arial','position',[-2.5 2.8])
@@ -231,7 +232,7 @@ set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 set(gca,'fontsize',FS,'YDir','normal','fontname','arial')
 
 subplot(132)
-imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanSeizure)
+imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanSeizure,ColorbarLims)
 xlabel('Space (mm)','fontsize',FS,'fontname','arial')
 ylabel('Space (mm)','fontsize',FS,'fontname','arial')
 title('\bf B','fontsize',FS2,'fontname','arial','position',[-2.5 2.8])
@@ -242,7 +243,7 @@ set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 set(gca,'fontsize',FS,'YDir','normal','fontname','arial')
 
 subplot(133)
-imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanPostSeizure)
+imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanPostSeizure,ColorbarLims)
 xlabel('Space (mm)','fontsize',FS,'fontname','arial')
 ylabel('Space (mm)','fontsize',FS,'fontname','arial')
 title('\bf C','fontsize',FS2,'fontname','arial','position',[-2.5 2.8])

### 2010-07-22 ltx/data_paper/DataPaper.tex
moved figures to end of paper, started to edit M-step and add E-step

@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/LFPs.eps}
-\end{center}
-\caption{{\bf Local field potentials from the micro-electrode array}.
-Data recorded from the first 8 channels of the array.
-The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
-\label{fig:TimeSeries}
-\end{figure}
-
 An example to illustrate the spatial aspects of the observed neural field is shown in Figure~\ref{fig:FieldObserations}.
@@
 The figure shows spatially correlated activity.
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/FieldObservations.eps}
-\end{center}
-\caption{{\bf Snap-shots of the spatial aspects of the observed field}. The snap-shots are ordered from A to I forming a consecutive sequence spaced 2.5~ms apart starting at 34.024s}
-\label{fig:FieldObserations}
-\end{figure}
 
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/TemporalFreq.eps}
-\end{center}
-\caption{{\bf Spectra from local field potential recordings}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:TemporalFreqObservation}
-\end{figure}
-
 Figure~\ref{fig:SpatialFreqObservation} shows the results of spatial frequency analysis of the observed neural field.
@@
 The symmetry in the plots provides some evidence for homogeneous and isotropic connectivity.
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/SpatialFreq.eps}
-\end{center}
-\caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:SpatialFreqObservation}
-\end{figure}
 
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/SpatialFreqCrossSection.eps}
-\end{center}
-\caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:DiagSpatialFreqObservation}
-\end{figure}
-
 \subsection{Estimating Support For Connectivity Kernel}
-The support for the connectivity kernel can be inferred by studying the correlation between consecutive observations of the neural field. 
+The support for the connectivity kernel can be inferred by studying the cross-correlation between consecutive observations of the neural field. 
 \begin{itemize}
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/CrossCorr2D.eps}
-\end{center}
-\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}.
-Note: The correlations are normalised such that the maximum value is one.
-A.
-Pre-seizure observation correlations.
-B.
-Seizure observation correlations.
-C.
-Post-seizure observation correlations.}
-\label{fig:SpatialCrossCorrelation}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/HomoTestCrossCorr.eps}
-\end{center}
-\caption{{\bf Mean cross-correlations between consecutive samples using subsets of observations of the neural field}.
-Each subplot shows correlations corresponding to a subset electrodes.
-Indexing the electrodes in a (x,y) grid, where index ranges from 1 to 10.
-Subplot A shows the mean correlation between electrode indexes (1-6, 5-10), subplot B shows correlations from indexes (5-10,5-10), subplot C shows indexes (1-6, 1-6) and subplot D shows indexes (5-10, 5-10).}
-\label{fig:HomogeneityTest}
-\end{figure}
-
 \section{Estimation Algorithm}
-\subsection{State-Space Model}
 The state-space model is given by
@@
  \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \\
- \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t
+ \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t,
 \end{align}
-and the nonlinear function, $q(\cdot)$, is defined as
+where the nonlinear function, $q(\cdot)$, is defined as
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}',
+	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'
 \end{equation}
-where
+and
 \begin{equation}\label{eq:DefPsi}
@@
 
-\subsection{$\mathcal Q$-function}
-The goal of the M-step is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol \theta$ and $\xi$.
-Unfortunately, it is often difficult to maximize the likelihood $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly.
-However, by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.
+\subsection{E-Step}
+The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
+An additional element to the URTSS algorithm was created to approximate $q(\mathbf{x}_t)$, which is required for the M-step.
 
-Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
-\begin{equation}\label{eq:jointdistribution}
- p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0).
-\end{equation}
-The $\mathcal Q$-function, or lower bound on the likelihood, can be written in terms of joint distribution components as
-\begin{eqnarray}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\mathbf E_{\boldsymbol (\theta',\xi')}[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)]\nonumber\\
-&=&\mathbf E_{\boldsymbol (\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta)+\sum_{t=1}^{T}\ln p(\mathbf x_0)]
-\end{eqnarray}
-where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
-It should be noted that
-$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter set and therefore $\mathcal Q$-function can be rewritten as
-\begin{equation}
-\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)]+\mathrm{const}
-\end{equation}
-the constant term can be ignored since it is not affecting the drivative with respect to the parameters. 
-The Gaussian distribution of the disturbance, $e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ results into the following conditional distribution of the state at $t+1$
-\begin{equation}
- p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=\alpha e^{-(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
-\end{equation}
-where $\alpha$ is the normalising constant. Taking $\log$ we get
-\begin{eqnarray}\label{eq:Qfunction}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
-&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t
-\end{eqnarray}
-taking trace and using invariant cyclic permutations property of the trace this distribution can be written
-as
-\begin{eqnarray}\label{eq:Qfunctionintrace}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace
-\end{eqnarray}
-we first linearise $q(\mathbf x_t)$ by taking the first-order truncated  Taylor-series expansion around the mean of the state at each time instant for the sigmoidal activation function, i.e.
+This is accomplished by taking the first-order truncated Taylor-series expansion of $q(\mathbf x_t)$ around the mean of the state at each time instant for the sigmoidal activation function, i.e.
 \begin{equation}
@@
 \end{equation}
-By substituting \eqref{eq:qTaylor} in \eqref{eq:Qfunctionintrace}  and taking the expectation leads to the following  $\mathcal Q$-function
-\begin{eqnarray}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2\Xi_0\boldsymbol\theta+
+
+The algorithm for the modified URTSS can be seen in Figure~\ref{tab:URTSSAlgorithm}.
+
+\subsection{M-Step}
+
+\subsection{$\mathcal Q$-function}
+The goal of the M-step is to maximise the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol \theta$ and $\xi$.
+Unfortunately, it is often not possible to maximise the likelihood $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly.
+However, by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.
+
+Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
+\begin{equation}\label{eq:jointdistribution}
+ p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0).
+\end{equation}
+The $\mathcal Q$-function, or lower-bound on the likelihood, can be written in terms of joint distribution components as
+\begin{align}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right]\nonumber\\
+&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],
+\end{align}
+where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
+It should be noted that
+$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter set and therefore $\mathcal Q$-function can be rewritten as
+\begin{equation}
+\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)\right]+\mathrm{const}
+\end{equation}
+the constant term can be ignored since it is not affecting the derivative with respect to the parameters. 
+The Gaussian distribution of the disturbance, $e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ results into the following conditional distribution of the state at $t+1$
+\begin{equation}
+ p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=\alpha e^{-(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
+\end{equation}
+where $\alpha$ is the normalising constant. By expanding the exponent and taking $\log$ we get
+\begin{eqnarray}\label{eq:Qfunction}
+  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
+&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.
+\end{eqnarray}
+Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\begin{eqnarray}\label{eq:Qfunctionintrace}
+  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
+&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
+\end{eqnarray}
+Now taking the expectation of the log likelihood function gives the $\mathcal Q$-function, which is the lower-bound that needs to be maximised to gain optimal parameter estimates.
+The $\mathcal Q$-function is written as
+\begin{align}
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\beta+2\Xi_0\boldsymbol\theta+
 2\xi tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&-&\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace\nonumber
-\end{eqnarray}
-where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and
+&-\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace \tag{Voldermont}
+\end{align}
+where 
+\begin{align}
+	\beta &= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \\
+\Xi_0&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_1&=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] \\
+\Xi_2&=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r')
+\end{align}
+is constant with respect to $\boldsymbol \theta$ and will disappear by differentiation, and
 \begin{equation}\label{eq:Xi0}
@@
 
+% all figures here
+% ~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/LFPs.eps}
+\end{center}
+\caption{{\bf Local field potentials from the micro-electrode array}.
+Data recorded from the first 8 channels of the array.
+The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
+\label{fig:TimeSeries}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/FieldObservations.eps}
+\end{center}
+\caption{{\bf Snap-shots of the spatial aspects of the observed field}. The snap-shots are ordered from A to I forming a consecutive sequence spaced 2.5~ms apart starting at 34.024s}
+\label{fig:FieldObserations}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/TemporalFreq.eps}
+\end{center}
+\caption{{\bf Spectra from local field potential recordings}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+\label{fig:TemporalFreqObservation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/SpatialFreq.eps}
+\end{center}
+\caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+\label{fig:SpatialFreqObservation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/SpatialFreqCrossSection.eps}
+\end{center}
+\caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+\label{fig:DiagSpatialFreqObservation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/CrossCorr2D.eps}
+\end{center}
+\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}.
+Note: The correlations are normalised such that the maximum value is one.
+A.
+Pre-seizure observation correlations.
+B.
+Seizure observation correlations.
+C.
+Post-seizure observation correlations.}
+\label{fig:SpatialCrossCorrelation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/HomoTestCrossCorr.eps}
+\end{center}
+\caption{{\bf Mean cross-correlations between consecutive samples using subsets of observations of the neural field}.
+Each subplot shows correlations corresponding to a subset electrodes.
+Indexing the electrodes in a (x,y) grid, where index ranges from 1 to 10.
+Subplot A shows the mean correlation between electrode indexes (1-6, 5-10), subplot B shows correlations from indexes (5-10,5-10), subplot C shows indexes (1-6, 1-6) and subplot D shows indexes (5-10, 5-10).}
+\label{fig:HomogeneityTest}
+\end{figure}
+
+% tables here
+% ~~~~~~~~~~~
+\renewcommand{\arraystretch}{1.7}
+\begin{table}[!ht]
+\caption{
+\bf{Algorithm for the Unscented RTS Smoother}}
+\begin{tabular}{|c|}\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
+$\hat{\mathbf x}_0, \mathbf P_0$ \\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
+$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
+\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
+$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
+$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
+$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
+\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
+$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
+$\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
+$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
+\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
+$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
+$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
+$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
+\hline
+\end{tabular}
+\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
+The steps are iterated 11 times for our state estimation procedure.
+The least squares algorithm is run after each iteration to update the parameter estimates.
+\end{flushleft}
+\label{tab:UKFAlgorithm}
+\end{table}
+\renewcommand{\arraystretch}{1}
+
 \bibliographystyle{plain}

### 2010-07-22 ltx/data_paper/DataPaper.tex
rearranged the m-step a little more in an effort to make it clearer

@@
 
-The algorithm for the modified URTSS can be seen in Figure~\ref{tab:URTSSAlgorithm}.
+The algorithm for the modified URTSS can be seen in Table~\ref{tab:URTSSAlgorithm}.
 
@@
 \begin{align}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right]\nonumber\\
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right] \\
 &=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],
 \end{align}
-where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
+\dean{there is a parameter missing here..} where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
 It should be noted that
@@
 The $\mathcal Q$-function is written as
-\begin{align}
+\begin{align}\label{eq:Voldermont}
  \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\beta+2\Xi_0\boldsymbol\theta+
@@
 \begin{align}
-	\beta &= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \\
+	\beta &= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
 \Xi_0&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] \\
-\Xi_2&=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r')
+\Xi_1&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
+\Xi_2&=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r') \\
+ \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+ \Xi_4&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]
 \end{align}
-is constant with respect to $\boldsymbol \theta$ and will disappear by differentiation, and
-\begin{equation}\label{eq:Xi0}
- \Xi_0=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
-\end{equation}
-\begin{equation}\label{eq:Xi1}
- \Xi_1=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] 
-\end{equation}
-\begin{equation}
- \Xi_2=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t\tilde{\Lambda}_t(\mathbf r')
-\end{equation}
-where
-\begin{equation}
- \Lambda(\mathbf r')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \quad \text{and} \quad \tilde{\Lambda}(\mathbf r')=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix}
-\end{equation}
-and where
-\begin{equation}
- \boldsymbol\lambda_i(\mathbf r')=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
-\end{equation}
 and
-\begin{equation}
- \tilde{\boldsymbol \lambda}_i(\mathbf r')=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
-\end{equation}
-and 
-\begin{equation}
- \Xi_3=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
-\end{equation}
-\begin{equation}
- \Xi_4=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top]
-\end{equation}
-differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating to zero we get
+\begin{align}
+	 \Lambda(\mathbf r')&=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \\
+	 \boldsymbol\lambda_i(\mathbf r')&=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'\\
+	\tilde{\Lambda}(\mathbf r')&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix} \\
+	 \tilde{\boldsymbol \lambda}_i(\mathbf r')&=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
+\end{align}
+When taking the derivative of equation~\ref{eq:Voldermont}, the first term described in equation~\ref{eq:def of beta} will will disappear.
+Also, when we differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating it to zero we get
 \begin{equation}
@@
 \begin{equation}
- \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}
+ \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}.
 \end{equation}

### 2010-07-25 ltx/second_order_framework/second_order_manuscript.tex
correction to EM algorithm

@@
 
-\usepackage{anysize} 									%<-use this for checking equation length
-\marginsize {1.7cm}{1.5cm}{1cm}{1cm} 				%<-use this for checking equation length
+\usepackage{anysize} 								
+%<-use this for checking equation length
+\marginsize {1.7cm}{1.5cm}{1cm}{1cm} 				%<-use this for
+% checking equation length
 
@@
 %opening
-\title{Nonlinear Spatio-Temporal Modelling using the Integro-Difference Equation}
+\title{Nonlinear Spatio-Temporal Modelling using the Integro-Difference
+Equation}
 \author{Parham Aram*,
-        Dean~R.~Freestone,Kenneth Scerri, Michael Dewar,\\ Andrew Zammit Mangion and Visakan Kadirkamanathan}
+        Dean~R.~Freestone,Kenneth Scerri, Michael Dewar,\\ Andrew Zammit Mangion
+and Visakan Kadirkamanathan}
 
@@
 \section{Introduction}
-\dean{Hi Parham: I have added some headings.
-Hope they are ok.
-I was going to cut and paste the derivation in, but I thought I would let you do it, because it goes back and forth a little.
-When we get a structure (doesn't have to be how I laid it out) it will be easier for me to work on it too.}
+\dean{Hi Parham: I have added some headings. Hope they are ok. I was going to
+cut and paste the derivation in, but I thought I would let you do it, because it
+goes back and forth a little. When we get a structure (doesn't have to be how I
+laid it out) it will be easier for me to work on it too.}
 \begin{enumerate}
@@
 \subsection{Frequency Analysis: Determining Basis Function Width and Spacing}
-Need something about the method of placement of basis functions and sampling of the field. \dean{Are we going to go for a triangular grid of basis functions?}
+Need something about the method of placement of basis functions and sampling of
+the field. \dean{Are we going to go for a triangular grid of basis functions?}
 
@@
 \subsection{Frequency Analysis}
-Confirmation of field sampling by sensors and show spatial frequency constraints on the approximated field.
+Confirmation of field sampling by sensors and show spatial frequency constraints
+on the approximated field.
 
@@
 \section{State-Space Representation of the Spatio-temporal Nonlinear IDE}
-The $p^{th}$-order nonlinear, stochastic, spatio-temporal homogenous IDE model is defined as
+The $p^{th}$-order nonlinear, stochastic, spatio-temporal homogenous IDE model
+is defined as
  \begin{equation}\label{eq:IDEModel}
-  \rho_t(\mathbf r)=\int_{\Omega}w(\mathbf r-\mathbf r')f(v_{t-p}(\mathbf r'))d\mathbf r'+\mathbf e_{t-p}(\mathbf r). 
+  \rho_t(\mathbf r)=\int_{\Omega}w(\mathbf r-\mathbf r')f(v_{t-p}(\mathbf
+r'))d\mathbf r'+\mathbf e_{t-p}(\mathbf r). 
  \end{equation}
@@
 \end{equation}
-where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at spatial location $\mathbf r$, $f(\cdot)$ is a nonlinear map, and $w(\cdot)$ is a spatial mixing kernel.
-The disturbance, $\mathbf e_{t-p}(\mathbf r)$, is a zero-mean normally distributed noise process that is spatially
+where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at
+spatial location $\mathbf r$, $f(\cdot)$ is a nonlinear map, and $w(\cdot)$ is a
+spatial mixing kernel. The disturbance, $\mathbf e_{t-p}(\mathbf r)$, is a
+zero-mean normally distributed noise process that is spatially
 coloured and temporally white, with covariance
@@
 and $\delta(\cdot)$ is the Dirac-delta function.
-Observations from the spatio-temporal field are described by the measurement function
+Observations from the spatio-temporal field are described by the measurement
+function
 \begin{equation}
@@
 \end{equation}
-where the observation vector, $\mathbf{y}_{t}$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise ${\boldsymbol\varepsilon}_t\sim \mathcal{N}\left(\mathbf{0},\boldsymbol\Sigma_{\varepsilon}\right)$ with $\mathbf{\Sigma}_{\boldsymbol\varepsilon}=\sigma_{\varepsilon}^2\mathbf I_{n_y} $.
-It is assumed here that $\boldsymbol\Sigma_{\varepsilon}$ and $\gamma\left(\mathbf r-\mathbf r' \right)$ are known.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by
+where the observation vector, $\mathbf{y}_{t}$, compiled at $n_{y}$ spatial
+locations and at time $t$, is corrupted by an i.i.d normally distributed
+zero-mean white noise ${\boldsymbol\varepsilon}_t\sim
+\mathcal{N}\left(\mathbf{0},\boldsymbol\Sigma_{\varepsilon}\right)$ with
+$\mathbf{\Sigma}_{\boldsymbol\varepsilon}=\sigma_{\varepsilon}^2\mathbf I_{n_y}
+$. It is assumed here that $\boldsymbol\Sigma_{\varepsilon}$ and
+$\gamma\left(\mathbf r-\mathbf r' \right)$ are known. The output kernel
+$m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined
+by 
 \begin{equation}\label{eq:SensorKernel}
-	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)},
+	m\left(\mathbf{r}-\mathbf{r}'\right) =
+\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{
+\sigma_m^2}\right)},
 \end{equation}
-where $\sigma_m$ sets the sensor width.
-The superscript $\top$ denotes the transpose operator.
-We proceed by writing the spatio-temporal IDE model in a parameterized state space form which allows the application of standard estimation techniques.
-We use a decomposition of the field and the spatial mixing kernel using a set of Gaussian basis functions
+where $\sigma_m$ sets the sensor width. The superscript $\top$ denotes the
+transpose operator. We proceed by writing the spatio-temporal IDE model in a
+parameterized state space form which allows the application of standard
+estimation techniques. We use a decomposition of the field and the spatial
+mixing kernel using a set of Gaussian basis functions
  \begin{equation}
-	\label{eq:FieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t
+	\label{eq:FieldDecomp} v_t\left(\mathbf{r}\right) \approx
+\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t
 \end{equation}
 \begin{equation}\label{eq:KernelDecomp}
-	 w\left(\mathbf{r}-\mathbf{r}'\right) \approx\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta}
+	 w\left(\mathbf{r}-\mathbf{r}'\right)
+\approx\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right)
+\boldsymbol{\theta}
 \end{equation}
-where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ and $\mathbf{\boldsymbol{\psi}}(\mathbf{r})$ are  vectors of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$ and the scaling parameter vector $\boldsymbol\theta$ respectively.
-Substituting \eqref{eq:LagPolynomial} in \eqref{eq:IDEModel} and using the above decomposition we have
+where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ and
+$\mathbf{\boldsymbol{\psi}}(\mathbf{r})$ are  vectors of Gaussian basis
+functions that are scaled by the state vector, $\mathbf{x}_t$ and the scaling
+parameter vector $\boldsymbol\theta$ respectively. Substituting
+\eqref{eq:LagPolynomial} in \eqref{eq:IDEModel} and using the above
+decomposition we have
 \begin{equation}\label{eq:DecompModel}
-\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t=\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\mathbf e_{t-p}(\mathbf r)
+\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)(1+\sum_{i=1}^{p}\varphi_i L_i)
+\mathbf{x}_t=\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}
+'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right)
+\mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\mathbf e_{t-p}(\mathbf r)
  \end{equation}
-multiplying \eqref{eq:DecompModel} by $\boldsymbol \phi(\mathbf r)$ and integrate over the spatial domain $\Omega$ we get
+multiplying \eqref{eq:DecompModel} by $\boldsymbol \phi(\mathbf r)$ and
+integrate over the spatial domain $\Omega$ we get
 \begin{equation}\label{eq:GammaDecompModel}
- \boldsymbol \Gamma (1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t=\int_{\Omega}\boldsymbol \phi(\mathbf r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf e_{t-p}(\mathbf r)d\mathbf r
+ \boldsymbol \Gamma (1+\sum_{i=1}^{p}\varphi_i L_i)
+\mathbf{x}_t=\int_{\Omega}\boldsymbol \phi(\mathbf
+r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right)
+f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf
+r'\boldsymbol{\theta}+\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf
+e_{t-p}(\mathbf r)d\mathbf r
 \end{equation}
@@
 \begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}} 
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi}
+\left(\mathbf{r}\right)\boldsymbol{\phi}
+^{\top}\left(\mathbf{r}\right)d\mathbf{r}} 
 \end{equation}
-cross-multiplying \eqref{eq:GammaDecompModel} by $\boldsymbol{\Gamma}^{-1}$ gives
+cross-multiplying \eqref{eq:GammaDecompModel} by $\boldsymbol{\Gamma}^{-1}$
+gives
 \begin{equation}\label{eq:InvGammaDecompModel}
- (1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t=\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf r'\boldsymbol{\theta}+\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf e_{t-p}(\mathbf r)d\mathbf r
+ (1+\sum_{i=1}^{p}\varphi_i L_i)
+\mathbf{x}_t=\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf
+r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right)
+f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-p})d\mathbf
+r'\boldsymbol{\theta}+\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol\phi(\mathbf
+r)\mathbf e_{t-p}(\mathbf r)d\mathbf r
 \end{equation}
-This can be further simplified by assuming isotropic structure for the spatial kernel
+This can be further simplified by assuming isotropic structure for the spatial
+kernel
 \begin{equation}
-	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (2c+\mathbf{r}'-\mathbf{r}).
+	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi}
+(2c+\mathbf{r}'-\mathbf{r}).
 \end{equation}
-where $c$ is the center of the kernel. \dean{Can't use c as it is used in the observation matrix.} To make the simplification, we first define
+where $c$ is the center of the kernel. \dean{Can't use c as it is used in the
+observation matrix.} To make the simplification, we first define
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (2c+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq
+T_s\boldsymbol{\Gamma}^{-1}\int_\Omega
+{\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top}
+(2c+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
 \end{equation}
-which is a constant $n_x \times n_{\theta}$ matrix and can be computed analytically. Now substituting \eqref{eq:DefPsi} into \eqref{eq:InvGammaDecompModel} we get
+which is a constant $n_x \times n_{\theta}$ matrix and can be computed
+analytically. Now substituting \eqref{eq:DefPsi} into
+\eqref{eq:InvGammaDecompModel} we get
 \begin{equation}
-(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta}
-+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_{t-p}(\mathbf{r})\textrm{d}\mathbf{r}}.
+(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t = \int_\Omega
+\boldsymbol{\Psi}(\mathbf{r}')
+f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}'
+\boldsymbol{\theta}
++ \boldsymbol{\Gamma}^{-1}
+\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_{t-p}(\mathbf{r})\textrm{d}\mathbf{r}
+}.
 \end{equation}
@@
 \begin{equation}\label{eq:Wt} 
-	\mathbf{e}_{t-p} \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_{t-p}( \mathbf{r} )\textrm{d}\mathbf{r}},
+	\mathbf{e}_{t-p} \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega
+{\boldsymbol{\phi} ( \mathbf{r} )e_{t-p}( \mathbf{r} )\textrm{d}\mathbf{r}},
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+	\boldsymbol\Sigma_e
+=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf
+r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf
+r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
 \end{equation}
-the observation equation of the reduced model is found by substituting \eqref{eq:FieldDecomp} into \eqref{eq:ObservationEquation} giving
+the observation equation of the reduced model is found by substituting
+\eqref{eq:FieldDecomp} into \eqref{eq:ObservationEquation} giving
 \begin{equation}\label{ObservationEquation} 
@@
 \begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i -
+\mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
 \end{equation}
@@
 \begin{equation}\label{eq:finalformstatespacemodel}
-	(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_{t-p}) \textrm{d}\mathbf{r}' \boldsymbol{\theta}
+	(1+\sum_{i=1}^{p}\varphi_i L_i) \mathbf{x}_t = \int_\Omega
+\boldsymbol{\Psi}(\mathbf{r}')
+f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_{t-p}) \textrm{d}\mathbf{r}'
+\boldsymbol{\theta}
  +\mathbf{e}_{t-p}
@@
 \begin{equation}
-x_t+\varphi_{1} x_{t-1}=\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol \phi(\mathbf r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-1})d\mathbf r'\boldsymbol{\theta}+\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol\phi(\mathbf r)\mathbf e_{t-1}(\mathbf r)d\mathbf r
+x_t+\varphi_{1} x_{t-1}=\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol
+\phi(\mathbf
+r)\int_{\Omega}\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right)
+f(\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_{t-1})d\mathbf
+r'\boldsymbol{\theta}+\boldsymbol\Gamma^{-1}\int_{\Omega}\boldsymbol\phi(\mathbf
+r)\mathbf e_{t-1}(\mathbf r)d\mathbf r
 \end{equation}
@@
 \begin{equation}\label{SpikesToPotential}
-	v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}
+	v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'}
+\right)g\left( {\mathbf{r},t'} \right)dt'}
 \end{equation}
@@
 \end{equation}
-where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. $A$ determines the maximal amplitude of the post-synaptic potentials.
+where $\zeta=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$
+is the Heaviside step function. $A$ determines the maximal amplitude of the
+post-synaptic potentials.
 Nonlocal interactions between cortical populations are described by	
 \begin{equation}\label{RateBasedInteractions}
-	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} 
+	g\left( \mathbf{r},t \right) = \int_\Omega  {w\left(
+\mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right)
+\right)d\mathbf{r}'} 
 \end{equation}
-where $f(.)$ is the firing rate function, $w(.)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain.
+where $f(.)$ is the firing rate function, $w(.)$ is the spatial connectivity
+kernel, and $\Omega$ is the spatial domain.
 \subsection*{Deriving Integro-differential Equation}
@@
 \begin{eqnarray}\label{SynapticRespKernelderivation}
- \frac{dh(t)}{dt}&=&A[\delta(t)t\mathrm{exp}(-\zeta t)+\eta(t)\frac{d}{dt}(t\mathrm{exp}(-\zeta t))] \nonumber\\
-&=& A[0+\eta(t)[\mathrm{exp}(-\zeta t)-\zeta t\mathrm{exp}(-\zeta t) ]\nonumber \\
+ \frac{dh(t)}{dt}&=&A[\delta(t)t\mathrm{exp}(-\zeta
+t)+\eta(t)\frac{d}{dt}(t\mathrm{exp}(-\zeta t))] \nonumber\\
+&=& A[0+\eta(t)[\mathrm{exp}(-\zeta t)-\zeta t\mathrm{exp}(-\zeta t) ]\nonumber
+\\
 &=&A\eta(t)\mathrm{exp}(-\zeta t)-\zeta h(t)
@@
 \begin{eqnarray}\label{SynapticRespKernelSecondderivation}
- \frac{d^2h(t)}{dt^2}&=&A[\delta(t)\mathrm{exp}(-\zeta t)-\zeta\eta(t)\mathrm{exp}(-\zeta t)]-\zeta \frac{dh(t)}{dt} \nonumber\\
-&=& A\delta(t)-\zeta A \eta(t)\mathrm{exp}(-\zeta t)-\zeta \frac{dh(t)}{dt} \nonumber \\
+ \frac{d^2h(t)}{dt^2}&=&A[\delta(t)\mathrm{exp}(-\zeta
+t)-\zeta\eta(t)\mathrm{exp}(-\zeta t)]-\zeta \frac{dh(t)}{dt} \nonumber\\
+&=& A\delta(t)-\zeta A \eta(t)\mathrm{exp}(-\zeta t)-\zeta \frac{dh(t)}{dt}
+\nonumber \\
 &=&A\delta(t)-2\zeta A \eta(t)\mathrm{exp}(-\zeta t)+\zeta^2h(t)
 \end{eqnarray}
-We define the operator $D$ as $D=\frac{d^2}{dt^2}+2\zeta \frac{d}{dt}+\zeta^2 $, applying $D$ on $h$ and using the result from (\ref{SynapticRespKernelSecondderivation}) it is clear that 
+We define the operator $D$ as $D=\frac{d^2}{dt^2}+2\zeta \frac{d}{dt}+\zeta^2 $,
+applying $D$ on $h$ and using the result from
+(\ref{SynapticRespKernelSecondderivation}) it is clear that 
 \begin{equation}
@@
 \begin{split}
- \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf r,t)}{dt}+\zeta^2v(\mathbf r,t)&=Ag\left( \mathbf{r},t \right)\\
-&=A\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'} \\
+ \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf
+r,t)}{dt}+\zeta^2v(\mathbf r,t)&=Ag\left( \mathbf{r},t \right)\\
+&=A\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
+\mathbf{r}',t \right) \right)d\mathbf{r}'} \\
 \end{split}
@@
 \subsection*{Discretization}
-The above second-order differential equation can be split into two, coupled first order ODEs.\\
+The above second-order differential equation can be split into two, coupled
+first order ODEs.\\
 \begin{equation}\label{eq:systemofode}
@@
 v_{t+1}=T_s\tilde{v_t}+v_t\\
-\tilde{v}_{t+1}=(1-2\zeta T_s)\tilde{v}_t-\zeta^2T_sv_t+AT_sg_t\left( \mathbf{r}\right)
+\tilde{v}_{t+1}=(1-2\zeta T_s)\tilde{v}_t-\zeta^2T_sv_t+AT_sg_t\left(
+\mathbf{r}\right)
 \end{cases}
@@
 \begin{equation}
- \begin{bmatrix}v_{t+1} \\ \tilde{v}_{t+1}\end{bmatrix}= \begin{bmatrix} T_s &1\\ 1-2\zeta T_s & -\zeta^2T_s\end{bmatrix}\begin{bmatrix}v_{t} \\ \tilde{v}_{t}\end{bmatrix}+AT_sg_t\left( \mathbf{r}\right)
+ \begin{bmatrix}v_{t+1} \\ \tilde{v}_{t+1}\end{bmatrix}= \begin{bmatrix} T_s
+&1\\ 1-2\zeta T_s & -\zeta^2T_s\end{bmatrix}\begin{bmatrix}v_{t} \\
+\tilde{v}_{t}\end{bmatrix}+AT_sg_t\left( \mathbf{r}\right)
 \end{equation}
@@
 \begin{equation}\label{eq:DifferenceModel}
- v_{t+2}-2(1-\zeta T_s)v_{t+1}+(1-2\zeta T_s+\zeta^2T_s^2)v_t=AT_s^2g_t\left( \mathbf{r}\right)
+ v_{t+2}-2(1-\zeta T_s)v_{t+1}+(1-2\zeta T_s+\zeta^2T_s^2)v_t=AT_s^2g_t\left(
+\mathbf{r}\right)
 \end{equation}
@@
 \begin{equation}\label{eq:rearrangedDifferenceModel}
- v_{t+2}-2v_{t+1}+2\zeta T_S v_{t+1}+v_t-2\zeta T_sv_t+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
+ v_{t+2}-2v_{t+1}+2\zeta T_S v_{t+1}+v_t-2\zeta
+T_sv_t+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
 \end{equation}
@@
 \begin{equation}
-(v_{t+2}-v_{t+1})-(v_{t+1}-v_t)+2\zeta T_s(v_{t+1}-v_t)+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
+(v_{t+2}-v_{t+1})-(v_{t+1}-v_t)+2\zeta
+T_s(v_{t+1}-v_t)+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
 \end{equation}
@@
 \begin{equation}
-(v_{t+2}-v_{t+1})-(1-2\zeta T_s)(v_{t+1}-v_t)+\zeta^2T_s^2v_t=AT_s^2g_t\left( \mathbf{r}\right)
+(v_{t+2}-v_{t+1})-(1-2\zeta T_s)(v_{t+1}-v_t)+\zeta^2T_s^2v_t=AT_s^2g_t\left(
+\mathbf{r}\right)
 \end{equation}
-substituting \eqref{eq:tildev} in the above equation and multiplying by $1/T_s$ we get the state space model
+substituting \eqref{eq:tildev} in the above equation and multiplying by $1/T_s$
+we get the state space model
 \begin{equation}\label{eq:StateSpaceModel}
@@
 \section{First order stochastic Neural Field Model}
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
+The model relates the average number of action potentials $g(\mathbf{r},t)$
+arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local
+post-synaptic membrane voltage $v(\mathbf{r},t)$. The post-synaptic potentials
+generated at a neuronal population at location $\mathbf{r}$ by action potentials
+arriving from all other connected populations at locations $\mathbf{r}'$ is
+described by 
 \begin{equation}
-	\label{eq:SpikesToPotential} v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)h(t)+\int_0^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'} 
+	\label{eq:SpikesToPotential} v\left( {\mathbf{r},t} \right)=v(\mathbf r,
+0)h(t)+\int_0^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'} 
 \end{equation}
@@
 where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant.
-Let $W(\mathbf r,t)$ be a spatio-temporal Wiener process.
-Then, for $\sigma \in \mathbb R^{+}$, the non-local interactions $g\left( {\mathbf{r},t} \right)$ between cortical populations can be divided into a predominantly deterministic part $g'\left( {\mathbf{r},t} \right) $ and  the random component $W(\mathbf r,t)$,
+Let $W(\mathbf r,t)$ be a spatio-temporal Wiener process. Then, for $\sigma \in
+\mathbb R^{+}$, the non-local interactions $g\left( {\mathbf{r},t} \right)$
+between cortical populations can be divided into a predominantly deterministic
+part $g'\left( {\mathbf{r},t} \right) $ and  the random component $W(\mathbf
+r,t)$,
 \begin{equation}\label{eq:ActPotComponents}
-  g\left( {\mathbf{r},t} \right)dt=g'\left( {\mathbf{r},t} \right)dt+\sigma d W(r,t)
+  g\left( {\mathbf{r},t} \right)dt=g'\left( {\mathbf{r},t} \right)dt+\sigma d
+W(r,t)
 \end{equation}
-As a result, the post-synaptic membrane voltage $v(\mathbf r, t)$ is itself a stochastic process.
-The deterministic part $g'(\mathbf r, t)$ is usually modelled as an integral equation with exogenous deterministic input , $ u(\mathbf r,t)$, of the form \cite{Atay2005}
+As a result, the post-synaptic membrane voltage $v(\mathbf r, t)$ is itself a
+stochastic process. The deterministic part $g'(\mathbf r, t)$ is usually
+modelled as an integral equation with exogenous deterministic input , $
+u(\mathbf r,t)$, of the form \cite{Atay2005}
 \begin{equation}
-	\label{DeterministicRateBasedInteractions} g'\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}+u(\mathbf r,t)
+	\label{DeterministicRateBasedInteractions} g'\left( \mathbf{r},t \right)
+= \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
+\mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}+u(\mathbf r,t)
 \end{equation}
-where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
-Substituting \eqref{eq:ActPotComponents} in \eqref{eq:SpikesToPotential} we get
+where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial
+connectivity kernel and $\Omega$ is the spatial domain representing a cortical
+sheet or surface. Substituting \eqref{eq:ActPotComponents} in
+\eqref{eq:SpikesToPotential} we get
 \begin{equation}\label{eq:NeuralModelDeterStoch}
-v\left( {\mathbf{r},t} \right)=v_0h(t)+\int_0^t {h\left( {t - t'} \right)g'\left( {\mathbf{r},t'} \right)dt'}+ \int_0^t h\left( {t - t'} \right)\sigma d W(r,t')
+v\left( {\mathbf{r},t} \right)=v_0h(t)+\int_0^t {h\left( {t - t'}
+\right)g'\left( {\mathbf{r},t'} \right)dt'}+ \int_0^t h\left( {t - t'}
+\right)\sigma d W(r,t')
 \end{equation}
-Here we assume that $v_0$ is generated by a known distribution $p_0(v)$ and is independent of the the random component $W(\mathbf r,t)$.
-We stress that $\sigma$ does not depend on the field $v(\mathbf r, t)$
-and hence the noise in \eqref{eq:NeuralModelDeterStoch} is strictly additive.
-It can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the following initial value problem (see Appendix \ref{app:InitialValueProblemProof})
+Here we assume that $v_0$ is generated by a known distribution $p_0(v)$ and is
+independent of the the random component $W(\mathbf r,t)$. We stress that
+$\sigma$ does not depend on the field $v(\mathbf r, t)$
+and hence the noise in \eqref{eq:NeuralModelDeterStoch} is strictly additive. It
+can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the
+following initial value problem (see Appendix
+\ref{app:InitialValueProblemProof})
 \begin{equation}
- dv(\mathbf r, t) + \zeta v(\mathbf r, t)dt = g'(\mathbf r, t)dt + dW(\mathbf r, t) \quad t\ge0, v(\mathbf r, 0) = v_0
+ dv(\mathbf r, t) + \zeta v(\mathbf r, t)dt = g'(\mathbf r, t)dt + dW(\mathbf r,
+t) \quad t\ge0, v(\mathbf r, 0) = v_0
 \end{equation}
-applying the Euler-Maruyama method the integro-difference equation (IDE) model takes the form of
+applying the Euler-Maruyama method the integro-difference equation (IDE) model
+takes the form of
 \begin{equation}\label{eq:Euler-MaruyamaDiscrit}
- v_{t+T_s}(\mathbf r)- v_{t}(\mathbf r)+ T_s\zeta v_t(\mathbf r)= T_sg'(\mathbf r, t) + (W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
+ v_{t+T_s}(\mathbf r)- v_{t}(\mathbf r)+ T_s\zeta v_t(\mathbf r)= T_sg'(\mathbf
+r, t) + (W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
 \end{equation}
-where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf r)$ is normally distributed with mean zero and covariance function $T_s\gamma(\mathbf r-\mathbf r')$.
-We rewrite \eqref{eq:Euler-MaruyamaDiscrit} as
+where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf
+r)$ is normally distributed with mean zero and covariance function
+$T_s\gamma(\mathbf r-\mathbf r')$. We rewrite \eqref{eq:Euler-MaruyamaDiscrit}
+as
 \begin{equation}
@@
 \end{equation}
- where $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $T_s\gamma(\mathbf{r}-\mathbf{r}')$.
-To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
+ where $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such
+that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf
+0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf
+0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian
+process with covariance function $T_s\gamma(\mathbf{r}-\mathbf{r}')$. To
+simplify the notation, the index of the future time sample, $t+T_s$, shall be
+referred to as $t+1$ throughout the rest of the paper. 
 \section{Second-Order Stochastic Neural Field Model}
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
+The model relates the average number of action potentials $g(\mathbf{r},t)$
+arriving at time $t \in \mathbb R^{+}$ and at position $\mathbf{r}$ to the local
+post-synaptic membrane voltage $v(\mathbf{r},t)$. The post-synaptic potentials
+generated at a neuronal population at location $\mathbf{r}$ by action potentials
+arriving from all other connected populations at locations $\mathbf{r}'$ is
+described by 
 \begin{equation}
-	\label{eq:SecondOrderSpikesToPotential} v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)(t+1)e^{-\zeta t}+v'(\mathbf r,0)te^{-\zeta t}+\int_0^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}
+	\label{eq:SecondOrderSpikesToPotential} v\left( {\mathbf{r},t}
+\right)=v(\mathbf r, 0)(t+1)e^{-\zeta t}+v'(\mathbf r,0)te^{-\zeta t}+\int_0^t
+{h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'} 
 \end{equation}
@@
 \begin{equation}
-	\label{eq:SecondOrderSynapticRespKernel} h(t) = At\exp{\left(-\zeta t\right)} 
+	\label{eq:SecondOrderSynapticRespKernel} h(t) = At\exp{\left(-\zeta
+t\right)} 
 \end{equation}
-where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant.  $A$ determines the maximal amplitude of the post-synaptic potentials.
-Let $W(\mathbf r,t)$ be a spatio-temporal Wiener process.
-Then, for $\sigma \in \mathbb R^{+}$, the non-local interactions $g\left( {\mathbf{r},t} \right)$ between cortical populations can be divided into a predominantly deterministic part $g'\left( {\mathbf{r},t} \right) $ and  the random component $W(\mathbf r,t)$,
+where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant.  $A$ determines
+the maximal amplitude of the post-synaptic potentials.
+Let $W(\mathbf r,t)$ be a spatio-temporal Wiener process. Then, for $\sigma \in
+\mathbb R^{+}$, the non-local interactions $g\left( {\mathbf{r},t} \right)$
+between cortical populations can be divided into a predominantly deterministic
+part $g'\left( {\mathbf{r},t} \right) $ and  the random component $W(\mathbf
+r,t)$,
 \begin{equation}\label{eq:SecondOrderActPotComponents}
-  g\left( {\mathbf{r},t} \right)dt=g'\left( {\mathbf{r},t} \right)dt+\sigma d W(r,t)
+  g\left( {\mathbf{r},t} \right)dt=g'\left( {\mathbf{r},t} \right)dt+\sigma d
+W(r,t)
 \end{equation}
-As a result, the post-synaptic membrane voltage $v(\mathbf r, t)$ is itself a stochastic process.
-The deterministic part $g'(\mathbf r, t)$ is usually modelled as an integral equation with exogenous deterministic input , $ u(\mathbf r,t)$, of the form \cite{Atay2005}
+As a result, the post-synaptic membrane voltage $v(\mathbf r, t)$ is itself a
+stochastic process. The deterministic part $g'(\mathbf r, t)$ is usually
+modelled as an integral equation with exogenous deterministic input , $
+u(\mathbf r,t)$, of the form \cite{Atay2005}
 \begin{equation}
-	\label{DeterministicRateBasedInteractions} g'\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}+u(\mathbf r,t)
+	\label{DeterministicRateBasedInteractions} g'\left( \mathbf{r},t \right)
+= \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
+\mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}+u(\mathbf r,t)
 \end{equation}
-where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
-Substituting \eqref{eq:SecondOrderActPotComponents} in \eqref{eq:SecondOrderSpikesToPotential} we get
+where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial
+connectivity kernel and $\Omega$ is the spatial domain representing a cortical
+sheet or surface. Substituting \eqref{eq:SecondOrderActPotComponents} in
+\eqref{eq:SecondOrderSpikesToPotential} we get
 \begin{equation}\label{eq:SecondOrderNeuralModelDeterStoch}
-v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)(t+1)e^{-\zeta t}+v'(\mathbf r,0)te^{-\zeta t}+\int_0^t {h\left( {t - t'} \right)g'\left( {\mathbf{r},t'} \right)dt'}+ \int_0^t h\left( {t - t'} \right)\sigma d W(r,t')
+v\left( {\mathbf{r},t} \right)=v(\mathbf r, 0)(t+1)e^{-\zeta t}+v'(\mathbf
+r,0)te^{-\zeta t}+\int_0^t {h\left( {t - t'} \right)g'\left( {\mathbf{r},t'}
+\right)dt'}+ \int_0^t h\left( {t - t'} \right)\sigma d W(r,t')
 \end{equation}
-It can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the following initial value problem \parham{Andrew do you know how?}
+It can be shown that the post-synaptic potential $v(\mathbf r, t)$ solves the
+following initial value problem \parham{Andrew do you know how?}
 \begin{equation*}\label{eq:SecondOrderInitialValueProblem}
@@
 dv(\mathbf r,t)=\tilde{v}(\mathbf r,t)dt & \\
-d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v(\mathbf r,t)dt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)
+d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v(\mathbf
+r,t)dt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)
 \end{array}\right.
@@
 \begin{equation}\label{eq:SecondOrderSDEMatrix}
- d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)
+ d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r
+,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta
+\end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r
+,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r,
+t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)
 \end{equation}
-applying the Euler-Maruyama method the integro-difference equation (IDE) model takes the form of
+applying the Euler-Maruyama method the integro-difference equation (IDE) model
+takes the form of
 \begin{equation}\label{eq:SecondOrderEulerMaruyamaDis}
- \begin{bmatrix} v_{t+T_s}(\mathbf r)-v_t(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)-\tilde{v}_t(\mathbf r)\end{bmatrix}=T_s\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}(W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
+ \begin{bmatrix} v_{t+T_s}(\mathbf r)-v_t(\mathbf r) \\
+\tilde{v}_{t+T_s}(\mathbf r)-\tilde{v}_t(\mathbf
+r)\end{bmatrix}=T_s\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta
+\end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf
+r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r,
+t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}(W_{t+T_s}(\mathbf
+r)-W_t(\mathbf r))
 \end{equation}
-where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf r)$ is normally distributed with mean zero and covariance function $T_s\gamma(\mathbf r-\mathbf r')$.
-We rewrite \eqref{eq:SecondOrderEulerMaruyamaDis} as
+where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf
+r)$ is normally distributed with mean zero and covariance function
+$T_s\gamma(\mathbf r-\mathbf r')$. We rewrite
+\eqref{eq:SecondOrderEulerMaruyamaDis} as
 \begin{equation}
- \begin{bmatrix} v_{t+T_s}(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)\end{bmatrix}=\begin{bmatrix}1 & T_s \\ -\zeta^2 T_s & 1-2\zeta T_s \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}e_t(\mathbf r)
+ \begin{bmatrix} v_{t+T_s}(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf
+r)\end{bmatrix}=\begin{bmatrix}1 & T_s \\ -\zeta^2 T_s & 1-2\zeta T_s
+\end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf
+r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r,
+t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}e_t(\mathbf r)
 \end{equation}
- where $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $T_s\gamma(\mathbf{r}-\mathbf{r}')$.
-To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
+ where $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that
+$e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$.
+Here $\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero
+mean spatial Gaussian process with covariance function
+$T_s\gamma(\mathbf{r}-\mathbf{r}')$. To simplify the notation, the index of the
+future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest
+of the paper. 
 \section{Estimation of the Non-linear Spatio-temporal IDE Model}
@@
 %Appendix one text goes here.
-Here we show that the post-synaptic potential $v(\mathbf r, t)$ is a solution to the initial value problem 
+Here we show that the post-synaptic potential $v(\mathbf r, t)$ is a solution to
+the initial value problem 
 \begin{equation}
- dv(\mathbf r, t) + \zeta v(\mathbf r, t)dt = g'(\mathbf r, t) + dW(\mathbf r, t) \quad t\ge0, v(\mathbf r, 0) = v_0
+ dv(\mathbf r, t) + \zeta v(\mathbf r, t)dt = g'(\mathbf r, t) + dW(\mathbf r,
+t) \quad t\ge0, v(\mathbf r, 0) = v_0
 \end{equation}
@@
 \begin{equation}\label{eq:kappafunctionInteration}
- v(\mathbf r, t)e^{\zeta t}-v_0 = \int_0^te^{\zeta t'}g'(\mathbf r, t')dt' +\int_0^te^{\zeta t'}\sigma dW(\mathbf r, t')
+ v(\mathbf r, t)e^{\zeta t}-v_0 = \int_0^te^{\zeta t'}g'(\mathbf r, t')dt'
++\int_0^te^{\zeta t'}\sigma dW(\mathbf r, t')
 \end{equation}
@@
 \begin{split}
- v(\mathbf r, t) &=&v_0e^{-\zeta t}+ \int_0^te^{-\zeta(t-t')}g'(\mathbf r, t')dt' +\int_0^te^{-\zeta (t-t')}\sigma dW(\mathbf r, t')\\
-&=&v_0e^{-\zeta t}+ \int_0^t h(t-t')g'(\mathbf r, t')dt' +\int_0^th(t-t')\sigma dW(\mathbf r, t')
+ v(\mathbf r, t) &=&v_0e^{-\zeta t}+ \int_0^te^{-\zeta(t-t')}g'(\mathbf r,
+t')dt' +\int_0^te^{-\zeta (t-t')}\sigma dW(\mathbf r, t')\\
+&=&v_0e^{-\zeta t}+ \int_0^t h(t-t')g'(\mathbf r, t')dt' +\int_0^th(t-t')\sigma
+dW(\mathbf r, t')
 \end{split}

### 2010-07-26 ltx/data_paper/DataPaper.tex
added andrew to data paper
committing for merge
correction to EM algorithm
added to section on estimating support for kernel

@@
 
-\title{Patient-Specific Neural Field Modeling from Mirco-Electrode Data}
+\title{Patient-Specific Neural Field Modeling from Micro-Electrode Data}
 \author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
- Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
+ Andrew Zammit Mangion, Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
  David B. Grayden and Visakan Kadirkamanathan  }
@@
 
-During the time-course of the iEEG monitoring several seizures were recorded. This study focuses on the local field potential (LFP) data recorded with the micro-electrode during a seizure.
+During the time-course of the iEEG monitoring period, several seizures were recorded. This study focuses on the local field potential (LFP) data recorded with the micro-electrode during a seizure.
 
@@
 The data was then resampled from 30~kHz to 5~kHz.
-To enable spatial visualisation and spatial frequency analysis, the corrupted channels, set to $nan$, were interpolated using all neighbouring channels.
+To enable spatial visualisation and spatial frequency analysis, the corrupted channels that were set to $nan$, were interpolated using data from all neighbouring channels.
 
@@
 The spectral properties of the recorded time series for each of the time segments are shown in Figure~\ref{fig:TemporalFreqObservation}.
-Each plot shows an averaged (across channels) spectrum the data.
+Each plot shows the averaged (across channels) spectrum of the data.
 The pre-seizure period shows a decay in power at a typical $1/f^2$ rate.
@@
 In addition, there is a peak in the power of the LFPs at ~51~Hz during the seizure.
-This peak would be difficult to observe in European and Asian countries due to the 50~Hz mains power frequency.
+This peak would be difficult to observe in European, Asian and other countries due to the 50~Hz mains power frequency.
 The post-seizure period shows a large increase in lower frequency power...
@@
 Throughout this paper the spatial frequency shall be denoted by $\nu$.
-Each subplot is an average (across time) spatial frequency during either the pre-seizure, seizure or post-seizure periods.
+Each subplot is the average (across time) spatial frequency during either the pre-seizure, seizure or post-seizure periods.
 The spatial frequency of the neural field is governed by disturbances (inputs from outside the field) and the underlying connectivity structure.
@@
 From this figure we can see that the spatial cut-off frequency (-3~dB point) is $\nu_c \approx 0.26$~Hz.
-The profile of the diagonal cross-section indicates that the field is adequately sampled from the micro-electrode array, where the power drops by approximately 25~dB at the maximum observable spatial frequency (according to Shannon's sampling theorem) indicating spatial aliasing will have an insignificant effect.
+The profile of the diagonal cross-section indicates that the field is adequately sampled from the micro-electrode array, where the power drops by approximately 25~dB at the maximum observable spatial frequency (according to Shannon's sampling theorem) indicating spatial aliasing will have an insignificant effect on the sampled data.
 The spatial cut-off frequency provides information on the complexity of the model required to represent the neural field.
-Considering the field is band-limited, we can represent the continuous field by a finite set of continuous basis functions.
+Considering the field is band-limited, we can represent it by a finite set of continuous basis functions.
 According the Shannon's sampling theorem, the minimum spacing between basis functions, $\Delta_{\phi}$, to describe the field is
@@
 \subsection{Estimating Support For Connectivity Kernel}
-The support for the connectivity kernel can be inferred by studying the cross-correlation between consecutive observations of the neural field. 
+Under the assumption that the sensors are not spatially band-limiting the spectral content of the field, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations of the neural field.
+The deterministic component of the spatial mapping between consecutive fields is determined by the connectivity kernel convolved with the firing rates.
+Although the relationship between the field and the firing rate is nonlinear, the cross-correlation analysis still extracts meaningful results.
+This can be seen by considering the three operating regions of the sigmoid.
+When the sigmoid is mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed.
+Therefore, this will not contribute to the results.
+Within the active region the sigmoid can be approximated by a linear function between consecutive samples, given a sufficiently high sampling rate.
+Therefore, linear cross-correlation analysis is appropriate.
+When the sigmoid is in the saturated region, the correlation coefficients will be higher.
+Therefore, we can not estimate the gain for the kernel, but the spatial extent can still be inferred.
+The gain for the kernel will be inferred using the EM algorithm described below.
+
+Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression.
+By averaging over time, the effect of the disturbance on the analysis is reduced.
+The figure shows that the connectivity kernel has a local excitation with surround inhibition structure.
+can be approximated by a local as a two-dimensional Gaussian.
+The wi
 \begin{itemize}
@@
 \Xi_1&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
-\Xi_2&=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r') \\
+\Xi_2&=\sum_{t=1}^T\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r')\right] \\
  \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
@@
 \section{Discussion}
+
 \begin{itemize}

### 2010-07-26 src/DataPaper/ReadAndPlotData.m

@@ -217,11 +217,11 @@ CrossCorrMeanPostSeizure = squeeze(mean(CrossCor(SzEnd*FsDec:end,:,:),1));
 SpactialLocation = linspace(-2,2,size(CrossCorrMeanPreSeizure,1));
 HeightOffset = 1;
 HeigthScale = 0.5;
-ColorbarLims = [-0.5 1];
+ColorbarLims = [-0.1 0.3];
 figure('units','centimeters','position',[2,2,TwoColumnWidth,6],'renderer','painters',...
     'filename',CrossCorrFig2D)
 subplot(131)
-imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanPreSeizure,ColorbarLims)
+imagesc(SpactialLocation,SpactialLocation,log10(1+CrossCorrMeanPreSeizure),ColorbarLims)
 xlabel('Space (mm)','fontsize',FS,'fontname','arial')
 ylabel('Space (mm)','fontsize',FS,'fontname','arial')
 title('\bf A','fontsize',FS2,'fontname','arial','position',[-2.5 2.8])
@@ -232,7 +232,7 @@ set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 set(gca,'fontsize',FS,'YDir','normal','fontname','arial')
 
 subplot(132)
-imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanSeizure,ColorbarLims)
+imagesc(SpactialLocation,SpactialLocation,log10(1+CrossCorrMeanSeizure),ColorbarLims)
 xlabel('Space (mm)','fontsize',FS,'fontname','arial')
 ylabel('Space (mm)','fontsize',FS,'fontname','arial')
 title('\bf B','fontsize',FS2,'fontname','arial','position',[-2.5 2.8])
@@ -243,7 +243,7 @@ set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 set(gca,'fontsize',FS,'YDir','normal','fontname','arial')
 
 subplot(133)
-imagesc(SpactialLocation,SpactialLocation,CrossCorrMeanPostSeizure,ColorbarLims)
+imagesc(SpactialLocation,SpactialLocation,log10(1+CrossCorrMeanPostSeizure),ColorbarLims)
 xlabel('Space (mm)','fontsize',FS,'fontname','arial')
[…]

### 2010-07-26 ltx/data_paper/DataPaper.tex
added missing paramater in EM (Dean comment)

@@
  \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right] \\
-&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],
+&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],
 \end{align}
-\dean{there is a parameter missing here..} where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
+where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
 It should be noted that

### 2010-07-26 ltx/data_paper/DataPaper.tex
changed notation in EM
added parameters on expectation for Xi1 and Xi4

@@
   \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
-&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.
+&&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.
 \end{eqnarray}
@@
   \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
+&&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
 \end{eqnarray}
-Now taking the expectation of the log likelihood function gives the $\mathcal Q$-function, which is the lower-bound that needs to be maximised to gain optimal parameter estimates.
+Now taking the expectation of the log likelihood function for all time instants gives the $\mathcal Q$-function, which is the lower-bound that needs to be maximised to gain optimal parameter estimates.
 The $\mathcal Q$-function is written as
@@
 \Xi_0&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
+\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
 \Xi_2&=\sum_{t=1}^T\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r')\right] \\
  \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
- \Xi_4&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]
+ \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]
 \end{align}

### 2010-07-26 ltx/data_paper/DataPaper.tex
added firing rate derivative to the text
changed notations for lambda
edits to kernel support section

--- 2010-07-26 ltx/data_paper/DataPaper.tex
@@
 \subsection{Estimating Support For Connectivity Kernel}
-Under the assumption that the sensors are not spatially band-limiting the spectral content of the field, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations of the neural field.
-The deterministic component of the spatial mapping between consecutive fields is determined by the connectivity kernel convolved with the firing rates.
+Under the assumption that the sensors are not spatially band-limiting the spectral content of the field and the connectivity kernel is homogeneous, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations.
+The deterministic component of the spatial mapping between consecutive fields is due to the convolution of the connectivity kernel with the firing rates.
 Although the relationship between the field and the firing rate is nonlinear, the cross-correlation analysis still extracts meaningful results.
 This can be seen by considering the three operating regions of the sigmoid.
-When the sigmoid is mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed.
+When the mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed.
 Therefore, this will not contribute to the results.
@@
 Therefore, linear cross-correlation analysis is appropriate.
-When the sigmoid is in the saturated region, the correlation coefficients will be higher.
-Therefore, we can not estimate the gain for the kernel, but the spatial extent can still be inferred.
+When the sigmoid is in the saturated region, the correlation coefficients will be higher, but not provide a meaningful measure of the kernel weight or gain.
+Therefore, we can not estimate the gain for the kernel using cross-correlation analysis, but the spatial extent can still be inferred.
 The gain for the kernel will be inferred using the EM algorithm described below.
@@
 Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression.
-By averaging over time, the effect of the disturbance on the analysis is reduced.
-The figure shows that the connectivity kernel has a local excitation with surround inhibition structure.
-can be approximated by a local as a two-dimensional Gaussian.
-The wi
+By averaging over time, the effect of the disturbance is reduced.
+The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition.
+The plot indicate the support for excitatory aspect of the kernel centred at the origin is -2 mm to 2 mm in the x direction and slightly wider in the y direction.
+
+The assumption of homgeneity can be tested by performing the correlation analysis 
 \begin{itemize}

### 2010-07-26 ltx/data_paper/DataPaper.tex

--- 2010-07-26 ltx/data_paper/DataPaper.tex
@@
 This is accomplished by taking the first-order truncated Taylor-series expansion of $q(\mathbf x_t)$ around the mean of the state at each time instant for the sigmoidal activation function, i.e.
-\begin{equation}
+\begin{equation}\label{eq:SigmoidTaylor}
  f(\boldsymbol \phi^\top(\mathbf r')\mathbf x_t) \approx f(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)+  \boldsymbol \phi^\top(\mathbf r')(\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)
 \end{equation}
-where we can approximate $q(\mathbf x_t)$ as
+where 
+\begin{equation}\label{eq:SigmoidDerivative}
+ f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)=\varsigma f(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)\left( 1-\frac{f( \boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)}{f_{max}}\right)
+\end{equation}
+substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ as
 \begin{equation}\label{eq:qTaylor}
@@
 \Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
-\Xi_2&=\sum_{t=1}^T\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r')\right] \\
+\Xi_2&=\sum_{t=1}^T\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
  \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
@@
 \begin{align}
-	 \Lambda(\mathbf r')&=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \\
-	 \boldsymbol\lambda_i(\mathbf r')&=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'\\
-	\tilde{\Lambda}(\mathbf r')&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix} \\
-	 \tilde{\boldsymbol \lambda}_i(\mathbf r')&=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
+	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \\
+	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\\
+	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \\
+	 \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
 \end{align}

### 2010-07-26 ltx/data_paper/DataPaper.tex
completed X1 and X4 formulation

@@
 \subsection{Estimating Support For Connectivity Kernel}
-Under the assumption that the sensors are not spatially band-limiting the spectral content of the field and the connectivity kernel is homogeneous, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations.
-The deterministic component of the spatial mapping between consecutive fields is due to the convolution of the connectivity kernel with the firing rates.
+Under the assumption that the sensors are not spatially band-limiting the spectral content of the field, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations of the neural field.
+The deterministic component of the spatial mapping between consecutive fields is determined by the connectivity kernel convolved with the firing rates.
 Although the relationship between the field and the firing rate is nonlinear, the cross-correlation analysis still extracts meaningful results.
 This can be seen by considering the three operating regions of the sigmoid.
-When the mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed.
+When the sigmoid is mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed.
 Therefore, this will not contribute to the results.
@@
 Therefore, linear cross-correlation analysis is appropriate.
-When the sigmoid is in the saturated region, the correlation coefficients will be higher, but not provide a meaningful measure of the kernel weight or gain.
-Therefore, we can not estimate the gain for the kernel using cross-correlation analysis, but the spatial extent can still be inferred.
+When the sigmoid is in the saturated region, the correlation coefficients will be higher.
+Therefore, we can not estimate the gain for the kernel, but the spatial extent can still be inferred.
 The gain for the kernel will be inferred using the EM algorithm described below.
@@
 Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression.
-By averaging over time, the effect of the disturbance is reduced.
-The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition.
-The plot indicate the support for excitatory aspect of the kernel centred at the origin is -2 mm to 2 mm in the x direction and slightly wider in the y direction.
-
-The assumption of homgeneity can be tested by performing the correlation analysis 
+By averaging over time, the effect of the disturbance on the analysis is reduced.
+The figure shows that the connectivity kernel has a local excitation with surround inhibition structure.
+can be approximated by a local as a two-dimensional Gaussian.
+The wi
 \begin{itemize}
@@
 \Xi_0&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
+\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=1}^T\left(\mathbf M_t+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
 \Xi_2&=\sum_{t=1}^T\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
  \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
- \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]
+ \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=1}^T\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
 \end{align}

### 2010-07-26 ltx/data_paper/DataPaper.tex
edits to kernel support section the homogeniety test bit

--- 2010-07-26 ltx/data_paper/DataPaper.tex
@@
 
-Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression.
-By averaging over time, the effect of the disturbance is reduced.
+Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods of the seizure progression.
+By averaging over time, the effect of the disturbance is reduced allowing for the support of the kernel to be seen.
 The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition.
-The plot indicate the support for excitatory aspect of the kernel centred at the origin is -2 mm to 2 mm in the x direction and slightly wider in the y direction.
+The plots indicate the support for excitatory aspect of the kernel centred at the origin is -2~mm to 2~mm in the $x$ direction and slightly wider in the $y$ direction.
 
-The assumption of homgeneity can be tested by performing the correlation analysis 
-\begin{itemize}
-	\item it is difficult to tell what correlations are from the cross-talk due the the sensor kernel
-	\item it is difficult because of the nonlinear function
-	\item 
-\end{itemize}
+The assumption of homogeneity was tested by performing the cross-correlation analysis on 4 equal sized subsections of the field observations.
+The subsections consisted $6\times6$ electrode grids, such that they overlapped by one electrode row and column.
+The overlap was required so the subsections where large enough for the support of the kernel to be seen in the cross-correlation analysis.
+The results of the analysis can be seen in Figure~\ref{fig:HomogeneityTest}.
+The results indicate that...
 

### 2010-07-26 src/DataPaper/ReadAndPlotData.m

@@ -254,23 +254,31 @@ set(CB, 'position', [Pos(1) Pos(2)+HeightOffset Pos(3) HeigthScale*Pos(4)] )
 set(gca,'fontsize',FS,'YDir','normal','fontname','arial')
 
 %%
-% check for homogeneity
+% check for homogeneity 
 disp('finding cross correlations to test for homogeniety')
 NElectrodes = 6;
-HomoCrossCor1 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
-HomoCrossCor2 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
-HomoCrossCor3 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
-HomoCrossCor4 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
+% HomoCrossCor1 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
+% HomoCrossCor2 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
+% HomoCrossCor3 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
+% HomoCrossCor4 = zeros(size(MatrixData,1), 2*NElectrodes-1, 2*NElectrodes-1);
+HomoCrossCor1 = zeros(size(MatrixData,1), 15, 15);
+HomoCrossCor2 = zeros(size(MatrixData,1), 15, 15);
+HomoCrossCor3 = zeros(size(MatrixData,1), 15,15);
+HomoCrossCor4 = zeros(size(MatrixData,1), 15,15);
 
-for n=1:size(MatrixData,1)-1  
-    f1 = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,1:NElectrodes,1:NElectrodes)))));
-    f2 = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,end-NElectrodes+1:end,end-NElectrodes+1:end)))));
-    f3 = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,1:NElectrodes,end-NElectrodes+1:end)))));
-    f4 = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,end-NElectrodes+1:end,1:NElectrodes)))));
[…]

### 2010-07-27 ltx/data_paper/DataPaper.tex
added connectivity kernel decomp outline

@@
 The plots indicate the support for excitatory aspect of the kernel centred at the origin is -2~mm to 2~mm in the $x$ direction and slightly wider in the $y$ direction.
+Although the kernel is not isotropic, we will approximate it as being isotropic.
+This is for computation reasons.
 
@@
 The results of the analysis can be seen in Figure~\ref{fig:HomogeneityTest}.
-The results indicate that...
+The results show that each subsection of the field has similar cross-correlations, with each subplot showing local excitation with surround inhibition.
+From this analysis, we will approximate the connectivity kernel as being homogeneous.
 
+\subsection{Parametrisation of Connectivity Kernel}
+The connectivity kernel can be decomposed as 
+\begin{equation}\label{eq:DefKernelDecomp}
+	 w\left(\mathbf{r},\mathbf{r}'\right) \approx \boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
+\end{equation}
+where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
+We will assume that we know the parametric form of the connectivity basis functions from the correlation analysis, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
+Substituting equation~\ref{eq:DefKernelDecomp} into equation\ref{eq:ReducedForm} gives
+\begin{equation}\label{eq:KernelDecompForm}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega \boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta} f(\boldsymbol{\phi}^{\top} (\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} 
+	 + \xi\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+The connectivity kernel weights can be shifted outside the integral giving
+\begin{equation}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
+	 + \xi\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+Now taking the basis function vector inside the inner integrand gives
+\begin{equation}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \int_\Omega \boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}
+	 + \xi\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
+\begin{equation}
+	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+\end{equation}
+To make the simplification, we define
+\begin{equation}\label{eq:DefPsi}
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+\end{equation}
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+\begin{equation}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t 
++ \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}.
+This provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ can be calculated analytically.
+This is of great importance as it lowers the computational demands of the estimation algorithm.
 \section{Estimation Algorithm}

### 2010-07-27 ltx/data_paper/DataPaper.tex
edits to connectivity kernel decomp

--- 2010-07-26 ltx/data_paper/DataPaper.tex
@@
 \begin{equation}
-	\label{FinalFormContinuous} 
+	\label{eq:ContinuousWithOperator} 
 	Dv\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}. 
@@
 The results of the analysis can be seen in Figure~\ref{fig:HomogeneityTest}.
-The results indicate that...
+The results show that each subsection of the field has similar cross-correlations, with each subplot showing local excitation with surround inhibition.
+From this analysis, we will approximate the connectivity kernel as being homogeneous.
 
-\section{Estimation Algorithm}
-The state-space model is given by
+\subsection{Parametrisation of Connectivity Kernel}
+The connectivity kernel can be decomposed as 
+\begin{equation}\label{eq:DefKernelDecomp}
+	 w\left(\mathbf{r},\mathbf{r}'\right) \approx \boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
+\end{equation}
+where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
+By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
+We will assume that we know the parametric form of the connectivity basis functions from the correlation analysis, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
+Substituting equation~\ref{eq:DefKernelDecomp} into equation\ref{eq:ReducedForm} gives
+\begin{equation}\label{eq:KernelDecompForm}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega \boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta} f(\boldsymbol{\phi}^{\top} (\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} 
+	 + \xi\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+The connectivity kernel weights can be shifted outside the integral giving
+\begin{equation}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
+	 + \xi\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+Now taking the basis function vector inside the inner integrand gives
+\begin{equation}\label{eq:ReucedFormWithKernelDecomp}
+	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+	 \int_\Omega \int_\Omega \boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}
+	 + \xi\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+This equation can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
+\begin{equation}
+	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+\end{equation}
+To make the simplification, we define
+\begin{equation}\label{eq:DefPsi}
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+\end{equation}
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReucedFormWithKernelDecomp} gives
+\begin{equation}
+	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t 
++ \mathbf{e}_t(\mathbf{r}).
+\end{equation}
+This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{eq:ReucedFormWithKernelDecomp}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}.
+This provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ can be calculated analytically.
+This is of great importance as it lowers the computational demands of the estimation algorithm.
+
+As a result of the model reduction via the basis function decomposition and the decomposition of the connectivity kernel the state space model is formed
 \begin{align}
@@
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'
+	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
 \end{equation}
-and
-\begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
-\end{equation}
-$ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.
+\section{Estimation Algorithm}
 

### 2010-07-27 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to connectivity kernel decomp

@@
 	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta}
-	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
+	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
 \end{equation}
@@
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
-
 \begin{equation}

### 2010-07-28 ltx/data_paper/DataPaper.tex
added the smoothed cross covariance matrix to the table and corrected the time index

@@
 \begin{equation}\label{eq:jointdistribution}
- p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0).
+ p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)p(\mathbf x_0).
 \end{equation}
@@
  \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right] \\
-&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],
+&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=0}^{T-1}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=0}^{T-1}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}\ln p(\mathbf x_0)\right],
 \end{align}
@@
 \begin{equation}
-\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)\right]+\mathrm{const}
+\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)\right]+\mathrm{const}
 \end{equation}
@@
 \begin{align}
-	\beta &= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
-\Xi_0&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=1}^T\left(\mathbf M_t+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
-\Xi_2&=\sum_{t=1}^T\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
- \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
- \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=1}^T\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
+	\beta &= \sum_{t=0}^{T-1}\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
+\Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_t+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
+\Xi_2&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+ \Xi_3&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+ \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
 \end{align}
@@
 $\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
-$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
+$\mathbf M_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
 \multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
-$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
+$\mathbf S_t=\mathbf M_{t +1}^{b-}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
 $\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
 $\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
+\multicolumn{1}{|p{16cm}|}{Additional step to calculate the smoothed cross covariance matrix}\\
+$\mathbf M_{t +1}^{b}=\mathbf S_t\mathbf P_{t+1}^{b}$\\
 \hline

### 2010-07-30 src/DataPaper/ReadAndPlotData.m
minor changes and commiting to merge

@@ -202,7 +202,8 @@ CrossCor = zeros(size(MatrixData,1),2*size(MatrixData,2)-1,2*size(MatrixData,2)-
 v0 = 2;
 varsigma = 0.56;
 for n=1:size(MatrixData,1)-1   
-    f = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,:,:)))));
+%     f = 1./(1+exp(varsigma*(v0-squeeze(MatrixData(n,:,:)))));
+    f = squeeze(MatrixData(n+1,:,:));
     CrossCor(n,:,:) = normxcorr2(squeeze(MatrixData(n+1,:,:)),f);
 end
 CrossCorrMeanPreSeizure = squeeze(mean(CrossCor(1:SzStart*FsDec,:,:),1)); 
@@ -266,15 +267,22 @@ HomoCrossCor2 = zeros(size(MatrixData,1), 15, 15);
 HomoCrossCor3 = zeros(size(MatrixData,1), 15,15);
 HomoCrossCor4 = zeros(size(MatrixData,1), 15,15);
 
-for n=1:2%size(MatrixData,1)-1  
-    f1 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,1:NElectrodes,1:NElectrodes)))));
-    f2 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,end-NElectrodes+1:end,end-NElectrodes+1:end)))));
-    f3 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,1:NElectrodes,end-NElectrodes+1:end)))));
-    f4 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,end-NElectrodes+1:end,1:NElectrodes)))));
+for n=1:size(MatrixData,1)-1  
+%     f1 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,1:NElectrodes,1:NElectrodes)))));
+%     f2 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,end-NElectrodes+1:end,end-NElectrodes+1:end)))));
+%     f3 = 1./(1+exp(varsigma*(v0 - squeeze(MatrixData(n,1:NElectrodes,end-NElectrodes+1:end)))));
[…]

### 2010-07-30 ltx/data_paper/DataPaper.tex
corrected the time index
correction to beta in Q function
minor changes and commiting to merge
added derivation of Xi variables to suplimentary information

@@
 The aim of this paper is to great a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.
+
+Instead of extracting features we aim to extract meaningful parameters...
+
 \section{Method}
@@
 The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
-An additional element to the URTSS algorithm was created to approximate $q(\mathbf{x}_t)$, which is required for the M-step.
+An additional step is required in the $\mathbf E$-step to calculate the cross-covariance matrix $\mathbf M_{t+1}=\textrm{cov}(\mathbf x_t,\mathbf x_{t+1})$.
+An additional element to the URTSS algorithm was also created to approximate $q(\mathbf{x}_t)$, which is required for the M-step.
 
@@
 \end{eqnarray}
-Now taking the expectation of the log likelihood function for all time instants gives the $\mathcal Q$-function, which is the lower-bound that needs to be maximised to gain optimal parameter estimates.
-The $\mathcal Q$-function is written as
+Substituting \ref{eq:qTaylor} in \ref{eq:Qfunctionintrace} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
+Therefore $\mathcal Q$-function can be approximated as
 \begin{align}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\beta+2\Xi_0\boldsymbol\theta+
+ \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&\approx\beta+2\Xi_0\boldsymbol\theta+
 2\xi tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
@@
 \begin{align}
-	\beta &= \sum_{t=0}^{T-1}\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
-\Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_t+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
+	\beta &= \sum_{t=0}^{T-1}\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
+\Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
 \Xi_2&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
@@
 \end{align}
-When taking the derivative of equation~\ref{eq:Voldermont}, the first term described in equation~\ref{eq:def of beta} will will disappear.
-Also, when we differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating it to zero we get
+Given the state estimates, $\mathbf {\hat x^{b}}_t$ the state covariance $\mathbf P_t^b$ and cross-covariance $\mathbf M_t^b$ , the $\Xi$-variables can be computed directly.
+
+When taking the derivative of equation~\ref{eq:Voldermont}, the first term described in equation~\ref{eq:def of beta} will disappear. Differntiating with respect to $\boldsymbol\theta$ we have
+\begin{equation}\label{eq:Qpartialtheta}
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=2\Xi_0-\boldsymbol\theta^\top(\Xi_2^\top+\Xi_2)-2\xi\Xi_3
+\end{equation}
+nothing that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
+\begin{equation}\label{eq:theta}
+ \boldsymbol \theta=\Xi_2^{-1}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
+\end{equation}
+similarly differentiating with respect to $\xi$ we have
+\begin{equation}\label{eq:Qpartialxi}
+ \frac{\partial \mathcal Q}{\partial \xi}=2tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace -2 \Xi_3 \boldsymbol\theta - 2\xi tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace
+\end{equation}
+substituting \ref{eq:theta} in \ref{eq:Qpartialxi} and equating to zero we get
 \begin{equation}
- \boldsymbol \theta=\Xi_2^{-\top}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
-\end{equation}
-and
-\begin{equation}
- \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}.
+ \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_3^\top}
 \end{equation}
@@
 \begin{equation}
- \frac{\delta^2 \mathcal Q}{\delta \xi^2}=-2 tr \left\lbrace\Xi_1\boldsymbol\Sigma_e^{-1} \right\rbrace
+ \frac{\partial^2 \mathcal Q}{\partial \xi^2}=-2 tr \left\lbrace\Xi_1\boldsymbol\Sigma_e^{-1} \right\rbrace
 \end{equation}
@@
 \begin{equation}
- \frac{\delta^2 \mathcal Q}{\delta \boldsymbol\theta^2}=-2 \Xi_2 
+ \frac{\partial^2 \mathcal Q}{\partial \boldsymbol\theta^2}=-2 \Xi_2 
 \end{equation}

### 2010-08-01 ltx/data_paper/DataPaper.tex
deleted fmax from sigmoid definition
added reference for cross covariance matrix calculation in the table

@@
 \begin{equation}\label{eq:SigmoidDerivative}
- f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)=\varsigma f(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)\left( 1-\frac{f( \boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)}{f_{max}}\right)
+ f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)=\varsigma f(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)\left( 1-f( \boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)\right)
 \end{equation}
@@
 $\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
-\multicolumn{1}{|p{16cm}|}{Additional step to calculate the smoothed cross covariance matrix}\\
+\multicolumn{1}{|p{16cm}|}{Additional step to calculate the smoothed cross covariance matrix \cite{Sarkka2008}} \\
 $\mathbf M_{t +1}^{b}=\mathbf S_t\mathbf P_{t+1}^{b}$\\

### 2010-08-03 ltx/data_paper/DataPaper.tex
minor correction
Addition of stochastic method to Datapaper.tex. Note changes in noise covariance matrix.

@@
 \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
 
@@
 This class of model describes a continuous cortical sheet or surface, relating mean firing rates of pre and post-synaptic neural populations.
-The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the temporal convolution
+The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the \red{(temporal convolution - I'd rather say integral equation	)} integral equation
 \begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}, 
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = e^{-\zeta t}v\left( {\mathbf{r},0} \right) + \int_{0}^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)\textrm{d}t'}, 
 \end{equation}   
-where $h(\cdot)$ is the synaptic response kernel and $g(\cdot)$ describes the mean firing rate.
-Assuming an infinite propagation velocity for action potentials within the field, the incoming firing rate the position $\mathbf{r}$ is described by spatial convolution
+where $v\left( {\mathbf{r},0} \right)$ is the membrane voltage at the initial time $t = 0$, $h(\cdot)$ is the synaptic response kernel assumed to be first order and of the form 
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
+	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}, 
+\end{equation}
+$\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function \blue{(you can keep it here if you wish as it doesn't change the integral equation because of the upper limit.
+I would remove it)}.
+$g(\cdot)$ describes the mean firing rate.
+In practice, the firing rate can rarely be considered as a purely determinstic process because \red{(can someone write down why?)}.
+We thus choose to introduce a spatially coloured space-time Wiener process $W(\mathbf{r},t)$ to model the flactuations in the mean firing rate and decompose $g(\cdot)$ as
+\begin{equation}\label{DecompositionOfg}
+g(\mathbf{r},t)\textrm{d}t = \tilde{g}(\mathbf{r},t)\textrm{d}t + \sigma_W \textrm{d}W(\mathbf{r},t) 
+\end{equation}
+where $\sigma_W \ge 0$ is a measure of the introduced space-time randomness.
+For $\sigma_W = 0$ a pure deterministic process is recovered.
+As a result of the random component component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process.
+Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \red{citation?}
+\begin{equation}
+	\label{RateBasedInteractions} \tilde{g}\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
 \end{equation}
@@
 where $v_0$ and $\varsigma$ describe the firing threshold the slope of the sigmoid respectively. 
-By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model
+By substituting equation~\ref{DecompositionOfg} into equation~\ref{SpikesToPotential} we obtain the stochastic integral equation model 
 \begin{equation}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
-	\int_{-\infty}^t 
-	h\left(t - t'\right) \int_\Omega
-	w\left(\mathbf{r},\mathbf{r}'\right) 
-	f\left( v\left( \mathbf{r}',t' \right)\right)
-	\textrm{d}\mathbf{r}'dt'.
+	\label{StochasticModel} v\left(\mathbf{r},t\right) = e^{-\zeta t}v\left( {\mathbf{r},0} \right) +
+	\int_{0}^t h\left(t - t'\right)\tilde{g}\left(\mathbf{r},t'\right) \textrm{d}t'+ \sigma_W\int_{0}^t h\left(t - t'\right)\textrm{d}W\left(\mathbf{r},t'\right).
 \end{equation}
-To arrive at the general integral-differential equation form of the model, we shall express the synaptic response kernel as a Green's function 
+ Here we assume that $v\left( {\mathbf{r}},0 \right)$ is independent of the disturbance on the action potentials and assumed to be generated by a known distribution.
+We stress that $\sigma_W$ does not depend on the field $v({\mathbf{r}},t)$ and hence the noise in equation \ref{StochasticModel} is strictly additive.
+The general integral-differential equation is given by
+\begin{equation} \label{DifferentialEquationContTime}
+ \textrm{d}v(\mathbf{r},t) + \zeta v(\mathbf{r},t)\textrm{d}t = \tilde{g}(\mathbf{r},t)\textrm{d}t + \textrm{d}W(\mathbf{r},t)  ~~~~ t \ge 0, v(\mathbf{r},0) = \red{GP?}
+\end{equation}
+To show that this is indeed the case consider the function $\kappa(v(\mathbf{r},t),t) = v(\mathbf{r},t)e^{\zeta t}$.
+We note that $\kappa(v(\mathbf{r},t),t)$ is twice differentiable so that we can apply It\hat{o}'s formula to obtain
 \begin{equation}
-	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
+ \textrm{d}\kappa = e^{\zeta t}g(\mathbf{r},t)\textrm{d}t + e^{\zeta t}\sigma \textrm{d}W(\mathbf{r},t)
 \end{equation}
-where $D$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
-\begin{equation}
-	\label{eq:ContinuousWithOperator} 
-	Dv\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}. 
-\end{equation}
-By assuming the synaptic response kernel is of first order has the form of
-\begin{equation}
-	\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}, 
-\end{equation}
-where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function, the operator $D$ is
-\begin{equation}
-	D=\frac{d}{dt} + \zeta,
-\end{equation}
-yielding
-\begin{equation}
-	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}.
-\end{equation}
+\noindent Integrating over $[0,t]$ and multiplying throughout by $e^{-\zeta t}$ gives the required result.
 The neural field equations must be written as a discrete-time finite-dimensional model in order to relate it to patient-specific data.
-The discrete-time model is found applying the a first-order Euler method giving
+The discrete-time model is found applying the a first-order Euler-Maruyama method on equation \ref{DifferentialEquationContTime} giving
 \begin{equation}\label{EulerMethod}
-	\frac{v\left( \mathbf{r},t+T_s \right)-v\left( \mathbf{r},t \right)}{T_s} + \zeta v\left(\mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right) f\left( {v\left( \mathbf{r}',t \right)}\right)\textrm{d}\mathbf{r}'},
+	v\left( \mathbf{r},t+T_s \right)-v\left( \mathbf{r},t \right) + \zeta T_sv\left(\mathbf{r},t \right) = T_s\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right) f\left( {v\left( \mathbf{r}',t \right)}\right)\textrm{d}\mathbf{r}'} + 	\sigma_W[W\left( \mathbf{r},t+T_s \right)-W\left( \mathbf{r},t \right)],
 \end{equation}
@@
 Rearranging equation~\ref{EulerMethod} gives the integro-difference equation (IDE) form
-\begin{equation}
-	\label{DiscreteTimeModel} 
-	v_{t+1}\left(\mathbf{r}\right) = 
-	\xi v_t\left(\mathbf{r}\right) + 
-	T_s \int_\Omega { 
-	    w\left(\mathbf{r},\mathbf{r}'\right)
-	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	\textrm{d}\mathbf{r}'}, 
-\end{equation}
-where $\xi = 1-T_s\zeta$. Finally, a disturbance term is added, to account for uncertainty and unmodelled inputs, to the IDE form giving
 \begin{equation}
@@
 \end{equation}
-where $e_t(\mathbf{r})$ is $i.i.d.$ such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+where $e_t(\mathbf{r}) = \sigma_W[W\left( \mathbf{r},t+T_s \right)-W\left( \mathbf{r},t \right)]$ is the increment of a space-time Wiener process, $i.i.d.$ with zero spatial mean such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\sigma_W^2\gamma(\mathbf{r}-\mathbf{r}'))$.
+Here $\mathcal{GP}(\mathbf 0,T_s\sigma_W^2\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 To reduce the model to a finite-dimensional system the neural field is approximated by a basis function decomposition where
@@
 \begin{equation}
-	\boldsymbol\Sigma_e \triangleq \mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+	\boldsymbol\Sigma_e \triangleq T_s\sigma_W^2\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
 \end{equation}
@@
 \end{equation}
-nothing that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
+noting that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
 \begin{equation}\label{eq:theta}

### 2010-08-18 ltx/data_paper/DataPaper.tex
corrected the latex file
Fixed error in previous upload
added observation noise estimation

@@
 To show that this is indeed the case consider the function $\kappa(v(\mathbf{r},t),t) = v(\mathbf{r},t)e^{\zeta t}$.
-We note that $\kappa(v(\mathbf{r},t),t)$ is twice differentiable so that we can apply It\hat{o}'s formula to obtain
+We note that $\kappa(v(\mathbf{r},t),t)$ is twice differentiable so that we can apply Ito's formula to obtain
 \begin{equation}
@@
 \subsection{$\mathcal Q$-function}
-The goal of the M-step is to maximise the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol \theta$ and $\xi$.
-Unfortunately, it is often not possible to maximise the likelihood $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly.
-However, by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.
+The goal of the M-step is to maximise the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol\Sigma_{\epsilon}$, $\boldsymbol \theta$ and $\xi$.
+Unfortunately, it is often not possible to maximise the likelihood $p(\mathbf Y;\boldsymbol\Theta)$ directly.
+However, by using the relationship between $p(\mathbf Y;\boldsymbol \Theta)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.
 
-Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
+Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ we have
 \begin{equation}\label{eq:jointdistribution}
- p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)p(\mathbf x_0).
+ p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)p(\mathbf x_0).
 \end{equation}
@@
 \begin{align}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right] \\
-&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=0}^{T-1}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=0}^{T-1}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}\ln p(\mathbf x_0)\right],
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right] \\
+&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
 \end{align}
-where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates.
+where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ where $\boldsymbol \Theta'$ is the current parameter estimate.
 It should be noted that
-$p(\mathbf y_t|\mathbf x_t)$ and $p(\mathbf x_0)$ are not functions of parameter set and therefore $\mathcal Q$-function can be rewritten as
+ $p(\mathbf x_0)$ is not function of parameter set and therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}
-\mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta ,\xi)\right]+\mathrm{const}
+\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\xi)\right]+\mathrm{const}
 \end{equation}
 the constant term can be ignored since it is not affecting the derivative with respect to the parameters.
-The Gaussian distribution of the disturbance, $e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ results into the following conditional distribution of the state at $t+1$
-\begin{equation}
- p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)=\alpha e^{-(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
-\end{equation}
-where $\alpha$ is the normalising constant. By expanding the exponent and taking $\log$ we get
+Under the Gaussian assumption and ignoring constant normalising terms, the joint distribution at $t+1$ can be written as
+\begin{eqnarray}
+ p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}} \times  e^{-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) } \nonumber \\
+&+& e^{-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
+\end{eqnarray}
+by expanding the exponent and taking $2\log$ we get
 \begin{eqnarray}\label{eq:Qfunction}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
-&&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.
+2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)&=&-\ln \boldsymbol\Sigma_{\epsilon}- (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\nonumber \\
+&-&\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
+&-&\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.
 \end{eqnarray}
@@
 \begin{eqnarray}\label{eq:Qfunctionintrace}
-  \ln p(\mathbf x_{t+1} | \mathbf x_t;\boldsymbol\theta,\xi)&=&\ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
+  \ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& -\ln \boldsymbol\Sigma_{\epsilon}-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace   \nonumber \\
+&-&\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
 &&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
@@
 Therefore $\mathcal Q$-function can be approximated as
-\begin{align}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&\approx\beta+2\Xi_0\boldsymbol\theta+
-2\xi tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&-\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace \tag{Voldermont}
-\end{align}
+\begin{eqnarray}\label{eq:Voldermont}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)\ln \boldsymbol\Sigma_{\epsilon}-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&+&\beta+2\Xi_0\boldsymbol\theta+
+2\xi \mathrm{tr}\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
+&-&\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 \mathrm{tr} \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace 
+\end{eqnarray}
 where 
 \begin{align}
-	\beta &= \sum_{t=0}^{T-1}\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
+	\beta &= \sum_{t=0}^{T-1}\mathbf E_{\Theta'}\left[-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
 \Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
+\Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
 \Xi_2&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
  \Xi_3&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
- \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
+ \Xi_4&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
 \end{align}
@@
 \end{align}
+It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_t \mathbf{\hat{x}}_t^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right] $.
 Given the state estimates, $\mathbf {\hat x^{b}}_t$ the state covariance $\mathbf P_t^b$ and cross-covariance $\mathbf M_t^b$ , the $\Xi$-variables can be computed directly.
 
-When taking the derivative of equation~\ref{eq:Voldermont}, the first term described in equation~\ref{eq:def of beta} will disappear. Differntiating with respect to $\boldsymbol\theta$ we have
+When taking the derivative of equation~\ref{eq:Voldermont}, the constant $\beta$ described in equation~\ref{eq:def of beta} will disappear. Differntiating with respect to $\boldsymbol\theta$ we have
 \begin{equation}\label{eq:Qpartialtheta}
@@
 \end{equation}
+differentiating equation~\ref{eq:Voldermont} with respect to $\boldsymbol\Sigma_{\epsilon}$ we get
+\begin{equation}
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\Sigma_{\epsilon}}= (T-1)\boldsymbol\Sigma_{\epsilon}-\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right]=\mathbf 0
+\end{equation}
+therefore we have
+\begin{equation}
+ \boldsymbol\Sigma_{\epsilon}=\frac{1}{T-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right]
+\end{equation}
+
 \subsection{Discussion}

### 2010-08-18 src/DataPaper/ReadAndPlotData.m

@@ -8,8 +8,8 @@ close all
 % hi guys, when you use this uncomment your name. You also need to add
 % where you have saved the data and where you want to save the figures
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-User = 'Dean';                   
-% User = 'Parham';
+%User = 'Dean';                   
+ User = 'Parham';
 % User = 'Mike';
 % User = 'Ken';
 
@@ -25,12 +25,12 @@ if strcmp(User,'Dean')
     HomoCrossCorrFig = '/Users/dean/Projects/BrainIDE/ltx/data_paper/Figures/HomoTestCrossCorr.eps';
     
 elseif strcmp(User,'Parham')
-    DataFileLocation = '';                  % file location
-    TemporalFreqFig = '';                   % figure save location from here down.
-    SpatialFreqFig = '';
-    SpatialFreqCrossSectFig = '';
-    FieldObservationsFig = '';
-    LFPsFig = '';
+    DataFileLocation = '/home/parham/Dropbox/iEEG Data Boston/MG29_Seizure22_LFP_Clip_Dean.mat';                  % file location
+    TemporalFreqFig = '/home/parham/Desktop/Figures/TemporalFreq.eps';                   % figure save location from here down.
+    SpatialFreqFig = '/home/parham/Desktop/SpatialFreq.eps';
+    SpatialFreqCrossSectFig = '/home/parham/Desktop/SpatialFreqCrossSection.eps';
+    FieldObservationsFig = '/home/parham/Desktop/FieldObservations.eps';
+    LFPsFig = '/home/parham/Desktop/Figures/LFPs.eps';
     
 elseif strcmp(User,'Ken')   
     DataFileLocation = '';
@@ -104,488 +104,488 @@ end
 % ~~~~~~~~~~~~~~~~~~~~~
 CAR = repmat(mean(MappedData,2),1,100);
 CARData = MappedData-CAR;                       % CAR = common average reference
-clear MappedData
+ clear MappedData
 
-%%
-% re-assign the bad channels and the corners to nans so we can interpolate
[…]

### 2010-08-18 src/python/PLoS/Data_generation_and_estimation.py

@@ -112,9 +112,9 @@ NF_model=NF(NF_Connectivity_kernel,sensor_kernel,obs_locns,observation_locs_mm,g
 IDE_model=IDE(IDE_Connectivity_kernel,IDE_field,sensor_kernel,obs_locns,gamma,gamma_weight,Sigma_varepsilon,act_fun,x0,P0,zeta,Ts,field_space,spacestep)
 #generate the Neural Field model
 NF_model.gen_ssmodel()
-V,Y=NF_model.simulate(T)
+#V,Y=NF_model.simulate(T)
 #generate the reduced model (state space model)
 IDE_model.gen_ssmodel()
 #estimate the states, the connectivity kernel parameters and the synaptic dynamics
-ps_estimate=para_state_estimation(IDE_model)
-ps_estimate.itrerative_state_parameter_estimation(Y[First_n_observations:],number_of_iterations)
+#ps_estimate=para_state_estimation(IDE_model)
+#ps_estimate.itrerative_state_parameter_estimation(Y[First_n_observations:],number_of_iterations)

### 2010-09-18 ltx/first_order_framework/LaTeX_Manuscript.tex
tried to narrow claims

@@
 \section*{Abstract}
-Since the mid 1970s there has been significant developments in generating neural field models that provide theoretical insights into macroscopic neurodynamics, which have previously been impossible to gain from experimental data alone.
-In parallel to these developments, technological advances have led to significant increases into the spatiotemporal resolution of data acquired in electrophysiological recording systems.
-In order to make the best of these developments, a method is required for relating data to the mathematical models.
 
-This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data.
+This paper presents a framework for creating neural field models from electrophysiological data.
 The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
 To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
-To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model.
+To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite-dimensional state-space model.
 Spatial frequency analysis methods are introduced that systematically specify the basis function configuration required to capture the dominant characteristics of the neural field.
@@
 
-This framework provides a link between electrophysiological data and theoretical neural field models.
-This link may lead to greater understanding of cortical dynamics at the mesoscopic and macroscopic scales where diseases such as epilepsy are manifested.
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLoS ONE authors please skip this step. 
-% Author Summary not valid for PLoS ONE submissions.   
-\section*{Author Summary}
-With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information and experimental data is becoming incredibly detailed.
-In order to make the best use of this information, data-driven mathematical models should be formed.
-This is particularly poignant where considering poorly understood complex systems such as the large-scale dynamics of the human brain.
-There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of interesting phenomena associated with various cognitive states and diseases.
-In this paper, we have created a framework for creating a data-driven mathematical model, forming a bridge between theory and electrophysiological data.
-Within this framework, we propose rules for designing experiments and we derive the mathematical formula to create the model.
-To demonstrate the utility of this framework, we provide an example using synthetic data that shows a comparison between true and estimated model characteristics.
-The ability to create patient-specific models of large-scale brain dynamics has the potential to revolutionise the treatment of diseases such as epilepsy, where techniques from engineering may be used to prevent abnormal neural oscillations.
-
 \section*{Introduction}
-Generating physiologically plausible neural field models is of great importance for studying brain dynamics at the mesoscopic and macroscopic scale.
+Generating physiologically plausible neural field models is of great importance for studying brain dynamics at the mesoscopic and macroscopic scales.
 While our understanding of the function of neurons is well developed, the overall behaviour of the brain's mesoscopic and macroscopic scale dynamics remains largely theoretical.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data.
-Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models, or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific data.
+Fitting the neural models to individuals is a highly non-trivial task.
+Recently, however, this taks has been approached from a number of standpoints.
 
-An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has recently been proposed for studying evoked potential dynamics.
+An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
-Another recent publication describing a parameter estimation method with a neural field model used an unscented Kalman filter with modified WC neural field equations~\cite{schiff2008kalman}.
+Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}.
 This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatiotemporal neural fields.
@@
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
-Our study builds on recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
+Our study extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
 The key development of this previous work was to represent a spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
+This paper extends the linear framework of \cite{Dewar2009,Scerri2009} to the nonlinear case required by the WC model.
 
@@
 
-Due to the relationship between the number of states in the model and the number of model parameters, increases in dimensionality lead to increases in uncertainty of the estimates.
+This, in turn, will lead to increases in uncertainty of the estimates.
 In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
 
-The current study builds on this previous work~\cite{schiff2008kalman}, where the estimator is constructed to approximate a continuous field and the dimensionality of the state vector is independent of the resolution of the observation process and spatial resolution of the model.
+The current study builds on Schiff and Sauer's approach ~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in Methods section.
@@
 
-The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel with the firing rates as a convolution of the kernel with the membrane voltage field basis functions.
+That the connectivity kernel is isotropic means the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
 
+\section*{Future Work}
+
 \subsection*{Patient-Specific Modelling}
-This is the first paper to derive a continuum neural field model-based estimation framework for intracortical connectivity from electrophysiological data.
-The importance of the estimation framework can be illustrated by considering that the connectivity structure at this scale cannot be estimated using diffusion tensor imaging due to the near isotropic diffusion of water in grey matter~\cite{Assaf2008}.
 
@@
 
-\subsection*{Future Work}
+\subsection*{Extensions to the framework}
 

### 2010-09-22 ltx/data_paper/DataPaper.tex
changes to the kernel basis functions to show that we can switch the inner product and the convolution

@@
 \end{equation}
-This equation can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
+This equation can be simplified by exploiting the isotropy of the basis functions used to represent the kernel, and hence,
 \begin{equation}
-	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
+	\psi_i (\mathbf{r}-\mathbf{r}') = \psi_i (2c_i+\mathbf{r}'-\mathbf{r}).
 \end{equation}
-To make the simplification, we define
+where $c_i$ is the center of the $i^{th}$ basis function of the kernel decomposition. To make the simplification, we define
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+	\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}  \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2c_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that is defined analytically, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a constant $L \times n_{\theta}$ matrix that is defined analytically, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
 Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReucedFormWithKernelDecomp} gives

### 2010-10-11 ltx/first_order_framework/LaTeX_Manuscript.tex
small paper edits

@@
 
+\dean{Need to add extra references between here}
 An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics.
@@
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+\dean{and here}
 
@@
 where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface.
-The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition.
-An example of the connectivity kernel is shown in Figure~\ref{fig:Figure1}.
+The connectivity kernel is typically a ``Mexican hat'' or ``wizard hat'' function, which describes local excitation and surround inhibition.
+An example of the Mexican hat connectivity kernel used in this paper is shown in Figure~\ref{fig:Figure1}.
 To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
@@
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
-This term is added to account for model uncertainty and unmodelled inputs.
+The disturbance is added to account for model uncertainty and unmodelled inputs.
 To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
@@
 \subsection*{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
-In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions that are defined by
-\begin{equation}\label{eq:FieldBasisFunction}
-	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
-\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
-\end{equation}
+In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions.
 Decomposition allows a continuous field to be represented by a finite-dimensional state vector.
@@
 \end{equation}
-where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$.
-An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
+where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$. The field basis functions are described by
+\begin{equation}\label{eq:FieldBasisFunction}
+	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
+\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
+\end{equation}
+An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.
 

### 2010-10-11 src/Matlab/Set_Parameters.m

@@ -11,7 +11,7 @@ end
 % ~~~~~~~~~~~
 Delta = 0.5;                          % space step for the spatial discretisation
 Delta_squared = Delta^2;
-SpaceMax = 20;                    % maximum space in mm
+SpaceMax = 10;                    % maximum space in mm
 SpaceMin = -SpaceMax;         % minimum space in mm
 NPoints = (SpaceMax-SpaceMin)/Delta+1;
 r = linspace(SpaceMin,SpaceMax,NPoints);      % define space
@@ -124,3 +124,6 @@ hold on
 plot(r,k0+k1+k2,'k','linewidth',4)
 legend('continuous kernel','discrete kernel')
 drawnow
+
+figure
+plot(r_continuous,k0_continuous)

### 2010-10-25 ltx/BrainIDEPoster/BrainIDE_Poster.tex
added poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX poster template
% Created by Nathaniel Johnston
% August 2009
% http://www.nathanieljohnston.com/index.php/2009/08/latex-poster-template/
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[final]{beamer}
\usepackage[scale=1.24]{beamerposter}
\usepackage{graphicx}			% allows us to import images
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{relsize}
\usepackage{epsfig}
%-----------------------------------------------------------
% Define the column width and poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% The separation I chose is 0.024 and I want 4 columns
% Then set onecolwid to be (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be 2*onecolwid + sepwid = 0.464
%-----------------------------------------------------------

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in}
\setlength{\paperheight}{36in}
\setlength{\sepwid}{0.024\paperwidth}
\setlength{\onecolwid}{0.22\paperwidth}
\setlength{\twocolwid}{0.464\paperwidth}
\setlength{\threecolwid}{0.708\paperwidth}
\setlength{\topmargin}{-0.5in}
\usetheme{confposter}

%-----------------------------------------------------------
% Define colours (see beamerthemeconfposter.sty to change these colour definitions)
%-----------------------------------------------------------

\setbeamercolor{block title}{fg=ngreen,bg=white}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70}
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10}

%-----------------------------------------------------------
% Name and authors of poster/paper/research
%-----------------------------------------------------------

\title{A Data-Driven Framework for Neural Field Modelling}
\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$ and Visakan Kadirkamanathan$^2$}

\institute{1. Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia \\
% 2. The Bionic Ear Institute, East Melbourne, VIC, Australia \\
% 3. Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK \\
2. Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK \\
3. Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA \\
4. Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta }

%-----------------------------------------------------------
% Start the poster itself
%-----------------------------------------------------------
% The \rmfamily command is used frequently throughout the poster to force a serif font to be used for the body text
% Serif font is better for small text, sans-serif font is better for headers (for readability reasons)
%-----------------------------------------------------------
\begin{document}
\begin{frame}[t]
  \begin{columns}[t]												% the [t] option aligns the column's content at the top
    \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{\onecolwid}
      \begin{block}{Introduction}
        \rmfamily{Neural field models provide insights into the physics and dynamics of electroencephalography (EEG) (see~\cite{Deco2008} for a recent review). The use of these models in the clinic has been limited, since they are constructed for ``general'' brain dynamics whereas pathologies are patient-specific. Here we develop a framework for creating patient-specific neural field models.}
      \end{block}

      \vskip2ex

      \begin{block}{Neural Field Model}
        \rmfamily{The model's temporal dynamics are described by 
		\begin{equation}
			\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}, 
		\end{equation}
		where the post-synaptic response kernel $h(t)$ is described by 
		\begin{equation}
			\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}, 
		\end{equation}
		and $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Spatial interactions between cortical populations are described by 
		\begin{equation}
			\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
		\end{equation}
		where $f(\cdot)$ is a sigmoidal firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface. Substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} gives the spatiotemporal model 
		\begin{equation}
			\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
			\int_{-\infty}^t 
			h\left(t - t'\right) \int_\Omega
			w\left(\mathbf{r},\mathbf{r}'\right) 
			f\left( v\left( \mathbf{r}',t' \right)\right)
			\textrm{d}\mathbf{r}'dt'.
		\end{equation}		
The model can be discretised in time and written as an integro-difference equation in the form
% \begin{alertblock}{Neural Field IDE}
\begin{equation}
	\label{DiscreteTimeModel} 
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r}'\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\textrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
% \end{alertblock}
where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$.

The mapping between the membrane voltage and the electrophysiological data is
	\begin{equation}
	    \label{eq:ObservationEquation}
		\mathbf{y}_t =
		\int_{\Omega}{
		    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
		\textrm{d}\mathbf{r}'} + 
		\boldsymbol{\varepsilon}_t, 
	\end{equation}
	where $\mathbf{r}_n$ defines the electrode positions, $n=1,...,N$ indexes the electrodes and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$. $\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$. The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by 
	\begin{equation}
		m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)},
	\end{equation}
	where $\sigma_m$ sets the sensor width.}
    \end{block}

	\begin{figure}
	\begin{center}
	\includegraphics[width=8in, scale = 10]{FieldModel.eps}
	\end{center}
	\caption{{\bf Diagram of neural mass.} Pictorial representation of the rate-to-voltage and voltage-to-rate equations.} 
	\label{fig:Figure1}
	\end{figure}

    \end{column}

    \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}

		% \setbeamercolor{block title}{fg=red,bg=white}%frame color
        \setbeamercolor{block body}{fg=black,bg=white}%body color

\begin{block}{State-Space Model}
	\begin{figure}	
	\begin{center}
	  \includegraphics[width=7in, scale = 10]{Figure2.eps}
	\end{center}
	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector. The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.} 
	\label{fig:Figure2}	
	\end{figure}
	\rmfamily{To implement standard estimation techniques, we use a set of Gaussian basis functions to decompose the field \cite{Dewar2009}. The field decomposition is described by 
	\begin{equation}
		\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
	\end{equation}
	where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$. The field basis functions are described by
	\begin{equation}\label{eq:FieldBasisFunction}
		\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
	\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
	\end{equation}
	The connectivity kernel can also be decomposed as 
	\begin{equation}\label{DefKernelDecomp}
		 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
	\end{equation}
	where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. Now defining the matrices
	\begin{align}
		\boldsymbol{\Gamma} &\triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)\textrm{d}\mathbf{r}} \label{eq:DefGamma} \\ 
		\boldsymbol{\Psi}(\mathbf{r}') &\triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top}\label{eq:DefPsi} (\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
	\end{align}
	where $\Gamma$ is a $L\times L$ matrix and $\Psi$ is $L \times n_{\theta}$ matrix, where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions. The state disturbance is defined as
	\begin{equation}\label{eq:Wt} 
		\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )\textrm{d}\mathbf{r}},
	\end{equation}
	which is a zero mean normally distributed white noise process with covariance
	\begin{equation}
		\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
	\end{equation}
	By rearranging Eq.~\ref{DiscreteTimeModel} and substituting in Eqs. \ref{DefFieldDecomp}, \ref{eq:FieldBasisFunction}, \ref{eq:DefGamma}, \ref{eq:DefPsi} and \ref{eq:Wt} we get the following state-space model
	% \begin{alertblock}{State-Space Model}
	\begin{align}
		\mathbf{x}_{t+1} &= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \mathbf{e}_t \\
		\mathbf{y}_t &= \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t.
		\end{align} 	
	% \end{alertblock}
	where the observation matrix is 
	\begin{equation}
			\mathbf{C} = \left[
			\begin{array}{{ccc}} 
				c_{1,1} & \dots & c_{1,L} \\
				\vdots & \ddots & \vdots \\
				c_{N,1} & \dots & c_{N,L} 
			\end{array}
			\right] 
		\end{equation}
		and 
		\begin{equation}
			c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
		\end{equation}
	}
\end{block}

    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column
	\begin{column}{\onecolwid}

      \begin{block}{Frequency Analysis}
		\begin{figure}
		\begin{center}
		\includegraphics[width=7in, scale = 10]{Figure4.eps}
		\end{center}
		\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
		\label{fig:Figure4}
		\end{figure}
		\rmfamily{Given a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy 
		\begin{equation}
			\label{eq:MinimumSensorDistance} \Delta_y \leq \frac{1}{2\rho_y\boldsymbol{\nu}_{c}}, 
		\end{equation}
		where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter and $\boldsymbol{\nu}_c$ is a cutoff frequency (typically taken as the -3~dB point). This condition must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.

		In the same manner the minimum distance between basis functions must satisfy 
		\begin{equation}\label{eq:BasisFunctionSeparation}
			\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{cy}}
		\end{equation}
		where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation and $\boldsymbol{\nu}_{cy}$ is the cut-off frequency of the observed field.
		The field basis function widths can also be inferred using spectral considerations~\cite{Scerri2009}. The basis function width, $\sigma^2_{\phi}$, should be chosen to be
		\begin{equation}\label{eq:WidthCutOffRelationship}
		 \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2},
		\end{equation}
		where
		\begin{equation}\label{eq:WidthFrequencyRelationship}
		 \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
		\end{equation}}
	\end{block}
	% \vskip2ex
	\begin{block}{Estimation}
		\rmfamily{The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.} 
	\end{block}	
	\begin{block}{References}
        \small{\rmfamily{\begin{thebibliography}{99}
\bibitem{Deco2008} G. Deco, V. Jirsa, P. Robinson, M. Breakspear, K. Friston. PLoS Computational Biology. \textbf{4} (2008).
\bibitem{Dewar2009} M. Dewar, K. Scerri, V. Kadirkamanathan. IEEE Transactions on Signal Processing. \textbf{57} (2009) 83-91.
\bibitem{Scerri2009} K. Scerri, M. Dewar, V. Kadirkamanathan. IEEE Trans. on Signal Processing. \textbf{57} (2009) 482-492.
        \end{thebibliography}}}	\end{block}
\end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column
	\begin{column}{\onecolwid}

      \begin{block}{Results}
		\begin{figure}	
		\begin{center}
		  \includegraphics[width=7in, scale = 10]{Figure7.eps}
		\end{center}
		\caption{{\bf Histograms of the parameter estimates over 100
		realisations}. Solid lines show the actual values of the parameters and the dotted lines show the means of estimated parameters. (\textbf{A}) The synaptic time constant estimates. (\textbf{B}) The central excitatory connectivity basis function parameter estimates. (\textbf{C}) The surround inhibition connectivity basis function parameter estimates. (\textbf{D}) The longer range excitatory connectivity basis function parameter estimates.} 
		\label{fig:Figure7}	
		\end{figure}
		\begin{figure}
		\begin{center}
		\includegraphics[width=7in, scale = 10]{Figure8.eps}
		\end{center}
		\caption{{\bf Cross-section of connectivity kernel estimate}. The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
		\label{fig:Figure8}
		\end{figure}

		\begin{figure}
		\begin{center}
		\includegraphics[width=10.5in, scale = 10]{FieldComparison.eps}
		\end{center}
		\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.}
		\label{fig:Figure10}
		\end{figure}

	\end{block}
\end{column}

	\begin{column}{\sepwid}\end{column}			% empty spacer column

 \end{columns}
\end{frame}
\end{document}

### 2010-10-25 ltx/first_order_framework/LaTeX_Manuscript.tex
added poster

@@
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this taks has been approached from a number of standpoints.
+Recently, however, this task has been approached from a number of standpoints.
 
 \dean{Need to add extra references between here}
+
 An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics.

### 2010-10-26 ltx/BrainIDEPoster/BrainIDE_Poster.tex
edits to the poster

@@
       \vskip2ex
-
+% \begin{block}{Notation}
+% 	\rmfamily{
+% 	
+% 	}
+% \end{block}
       \begin{block}{Neural Field Model}
-        \rmfamily{The model's temporal dynamics are described by 
-		\begin{equation}
-			\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}, 
-		\end{equation}
-		where the post-synaptic response kernel $h(t)$ is described by 
-		\begin{equation}
-			\label{SynapticRespKernel} h(t) = \eta(t)\exp{\left(-\zeta t\right)}, 
-		\end{equation}
-		and $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Spatial interactions between cortical populations are described by 
+        \rmfamily{The model's temporal synaptic dynamics are described by 
+		\begin{align}
+			\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) &= \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'} \\ 
+			h(t) &= \eta(t)\exp{\left(-\zeta t\right)}, 
+		\end{align}
+		where $g(\mathbf{r},t)$ is the input firing rate, $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function.
+Interactions between cortical populations are described by
 		\begin{equation}
@@
 		\end{equation}
-The model can be discretised in time and written as an integro-difference equation in the form
-% \begin{alertblock}{Neural Field IDE}
+The discrete time integro-difference equation form of the model is
+\begin{alertblock}{Neural Field IDE}
 \begin{equation}
@@
 \end{equation}
-% \end{alertblock}
-where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$.
+\end{alertblock}
+where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
 
-The mapping between the membrane voltage and the electrophysiological data is
+The mapping between the neural field and the electrophysiological data is
 	\begin{equation}
@@
 	where $\mathbf{r}_n$ defines the electrode positions, $n=1,...,N$ indexes the electrodes and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$.
-$\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by
+The output kernel, $m(\mathbf{r}-\mathbf{r}')$, governs the sensor pick-up geometry and is defined by
 	\begin{equation}
@@
 	\begin{center}
-	  \includegraphics[width=7in, scale = 10]{Figure2.eps}
+	  \includegraphics[width=8in, scale = 10]{Figure2.eps}
 	\end{center}
-	\caption{{\bf Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
-The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
+	\caption{{\bf Example of a one-dimensional field decomposition.} The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
 	\label{fig:Figure2}	
@@
 	\end{equation}
-	where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$. The field basis functions are described by
-	\begin{equation}\label{eq:FieldBasisFunction}
-		\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
-	\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
-	\end{equation}
+	where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$. 
 	The connectivity kernel can also be decomposed as 
@@
 \ref{DefFieldDecomp}, \ref{eq:FieldBasisFunction}, \ref{eq:DefGamma}, \ref{eq:DefPsi} and \ref{eq:Wt} we get the following state-space model
-	% \begin{alertblock}{State-Space Model}
+	\begin{alertblock}{State-Space Model}
 	\begin{align}
@@
 		\end{align} 	
-	% \end{alertblock}
+	\end{alertblock}
 	where the observation matrix is 
@@
 		\begin{center}
-		\includegraphics[width=7in, scale = 10]{Figure4.eps}
+		\includegraphics[width=8in, scale = 10]{Figure4.eps}
 		\end{center}
@@
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
-(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
+(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.}
 		\label{fig:Figure4}
@@
 		\begin{center}
-		  \includegraphics[width=7in, scale = 10]{Figure7.eps}
+		  \includegraphics[width=8in, scale = 10]{Figure7.eps}
 		\end{center}
@@
 		realisations}.
-Solid lines show the actual values of the parameters and the dotted lines show the means of estimated parameters.
-(\textbf{A}) The synaptic time constant estimates.
-(\textbf{B}) The central excitatory connectivity basis function parameter estimates.
-(\textbf{C}) The surround inhibition connectivity basis function parameter estimates.
-(\textbf{D}) The longer range excitatory connectivity basis function parameter estimates.}
+Solid lines show the actual parameters and the dotted lines show the means of estimated parameters.
+(\textbf{A}) The synaptic time constant.
+(\textbf{B}) The central excitatory connectivity parameter.
+(\textbf{C}) The surround inhibition connectivity parameter.
+(\textbf{D}) The longer range excitatory connectivity parameter.}
 		\label{fig:Figure7}	
@@
 		\begin{center}
-		\includegraphics[width=7in, scale = 10]{Figure8.eps}
+		\includegraphics[width=8in, scale = 10]{Figure8.eps}
 		\end{center}

### 2010-10-26 ltx/BrainIDEPoster/BrainIDE_Poster.tex
edits to poster, making it clearer and graphics bigger

@@
 
-\institute{1. Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia \\
+\institute{1. Department of Electrical and Electronic Engineering, University of Melbourne, Australia \\
 % 2. The Bionic Ear Institute, East Melbourne, VIC, Australia \\
 % 3. Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK \\
-2. Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK \\
-3. Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA \\
-4. Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta }
+2. Department of Automatic Control and Systems Engineering, University of Sheffield, UK \\
+3. Department of Applied Physics and Applied Mathematics, Columbia University, USA \\
+4. Department of Systems and Control Engineering, University of Malta, Malta }
 
@@
 		\begin{equation}
-			\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
+			\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \left|\mathbf{r}-\mathbf{r}'\right| \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
 		\end{equation}
@@
 	\begin{center}
-	\includegraphics[width=8in, scale = 10]{FieldModel.eps}
+	\includegraphics[width=10in, scale = 10]{FieldModel.eps}
 	\end{center}
@@
 	\begin{center}
-	  \includegraphics[width=8in, scale = 10]{Figure2.eps}
+	  \includegraphics[width=9in, scale = 10]{Figure2.eps}
 	\end{center}
@@
 		\begin{center}
-		\includegraphics[width=8in, scale = 10]{Figure4.eps}
+		\includegraphics[width=9in, scale = 10]{Figure4.eps}
 		\end{center}
@@
 		\begin{center}
-		  \includegraphics[width=8in, scale = 10]{Figure7.eps}
+		  \includegraphics[width=9in, scale = 10]{Figure7.eps}
 		\end{center}
@@
 		\begin{center}
-		\includegraphics[width=8in, scale = 10]{Figure8.eps}
+		\includegraphics[width=9in, scale = 10]{Figure8.eps}
 		\end{center}
@@
 		\end{center}
-		\caption{{\bf Examples of the actual and estimated neural fields and the error}.
-(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
-(\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.}
+		\caption{{\bf The actual and estimated neural fields}. (\textbf{A}) The actual field at a single time instant. (\textbf{B}) The reconstructed field of the reduced model.}
 		\label{fig:Figure10}

### 2010-10-26 ltx/BrainIDEPoster/BrainIDE_Poster.tex
fixed the integral in the poster
simplified poster, bigger pictures

@@
 \usetheme{confposter}
-
+\usepackage{exscale}
 %-----------------------------------------------------------
@@
 		\begin{equation}
-			\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \left|\mathbf{r}-\mathbf{r}'\right| \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
+			\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
 		\end{equation}
@@
 			h\left(t - t'\right) \int_\Omega
-			w\left(\mathbf{r},\mathbf{r}'\right) 
+			w\left(\mathbf{r}-\mathbf{r}'\right) 
 			f\left( v\left( \mathbf{r}',t' \right)\right)
@@
 	T_s \int_\Omega { 
-	    w\left(\mathbf{r},\mathbf{r}'\right)
+	    w\left(\mathbf{r}-\mathbf{r}'\right)
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
@@
 	\begin{equation}\label{DefKernelDecomp}
-		 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
+		 w\left(\mathbf{r}-\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r}-\mathbf{r}'\right) \boldsymbol{\theta},
 	\end{equation}
-	where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. Now defining the matrices
+	where $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. Now defining the matrices
 	\begin{align}
@@
 	where the observation matrix is 
-	\begin{equation}
-			\mathbf{C} = \left[
+	\begin{align}
+		\mathbf{C} &= \left[
 		\begin{array}{{ccc}} 
@@
 		\end{array}
-			\right] 
-		\end{equation}
-		and 
-		\begin{equation}
-			c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
-		\end{equation}
+		\right], \ \	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
+		\end{align}
 	}
@@
 		\end{figure}
-		\rmfamily{Given a band-limited field, the distance between adjacent sensors, $\Delta_y$, must satisfy 
+		\rmfamily{Given a band-limited field, the distance between electrodes, $\Delta_y$, must satisfy 
 		\begin{equation}
@@
 		The field basis function widths can also be inferred using spectral considerations~\cite{Scerri2009}. The basis function width, $\sigma^2_{\phi}$, should be chosen to be
-		\begin{equation}\label{eq:WidthCutOffRelationship}
-		 \sigma^2_{\phi}= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2},
-		\end{equation}
-		where
-		\begin{equation}\label{eq:WidthFrequencyRelationship}
-		 \sigma^2_{\nu_{cy}}= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
-		\end{equation}}
+		\begin{align}\label{eq:WidthCutOffRelationship}
+		 \sigma^2_{\phi} &= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2} \\
+		 \sigma^2_{\nu_{cy}} &= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
+		\end{align}}
 	\end{block}

### 2010-10-27 ltx/BrainIDEPoster/BrainIDE_Poster.tex
added estimation figure

@@
 \usepackage{epsfig}
+
 %-----------------------------------------------------------
@@
 \usepackage{exscale}
+
 %-----------------------------------------------------------
@@
   \begin{columns}[t]												% the [t] option aligns the column's content at the top
+	  \setbeamercolor{block title}{fg=red,bg=white}%frame color
+
     \begin{column}{\sepwid}\end{column}			% empty spacer column
@@
 The discrete time integro-difference equation form of the model is
-\begin{alertblock}{Neural Field IDE}
+\vskip2ex
+\begin{alertblock}{Neural Field IDE \\}
 \begin{equation}
@@
 \end{alertblock}
+\vskip2ex
 where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
+
+\vskip2ex
 
@@
     \end{block}
-
+\vskip2ex
 	\begin{figure}
@@
 	where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$.
+
 	The connectivity kernel can also be decomposed as 
@@
 	\end{equation}
+	\vskip2ex
 	By rearranging Eq.~\ref{DiscreteTimeModel} and substituting in Eqs.
-\ref{DefFieldDecomp}, \ref{eq:FieldBasisFunction}, \ref{eq:DefGamma}, \ref{eq:DefPsi} and \ref{eq:Wt} we get the following state-space model
-	\begin{alertblock}{State-Space Model}
+\ref{DefFieldDecomp}, \ref{DefKernelDecomp}, \ref{eq:DefGamma}, \ref{eq:DefPsi} and \ref{eq:Wt} we get the following state-space model
+	\vskip2ex
+	\begin{alertblock}{State-Space Model \\}
 	\begin{align}
@@
 	\end{alertblock}
+	% \vskip2ex
 	where the observation matrix is 
@@
 		\end{array}
-		\right], \ \	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
+		\right], \\	
+		c_{i,j} &= \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
 		\end{align}
@@
 		\caption{{\bf Spatial frequency analysis of the neural field}.
-(\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
-(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.}
+Both plots show an average (over time) power in dB of the spatial frequency.
+(\textbf{A}) The actual field.
+(\textbf{B}) The reconstructed field from the basis function decomposition.}
 		\label{fig:Figure4}
@@
 
-		In the same manner the minimum distance between basis functions must satisfy 
+		The minimum distance between basis functions must also satisfy 
 		\begin{equation}\label{eq:BasisFunctionSeparation}
@@
 	\begin{block}{Estimation}
-		\rmfamily{The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.}
+		\rmfamily{The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother (URTSS) for state estimation and a least squares (LS) algorithm for parameter estimation.}
+		\begin{figure}	
+		\begin{center}
+		  \includegraphics[width=10in, scale = 10]{EstimationAlgorithm.eps}
+		\end{center}
+		\caption{{\bf Estimation algorithm}. Flow chart describing steps in algorithm.} 
+		\label{fig:Estimation Algorithm}	
+		\end{figure} 
 	\end{block}	
@@
         \small{\rmfamily{\begin{thebibliography}{99}
-\bibitem{Deco2008} G. Deco, V. Jirsa, P. Robinson, M. Breakspear, K. Friston. PLoS Computational Biology. \textbf{4} (2008).
-\bibitem{Dewar2009} M. Dewar, K. Scerri, V. Kadirkamanathan. IEEE Transactions on Signal Processing. \textbf{57} (2009) 83-91.
-\bibitem{Scerri2009} K. Scerri, M. Dewar, V. Kadirkamanathan. IEEE Trans. on Signal Processing. \textbf{57} (2009) 482-492.
+\bibitem{Deco2008} G. Deco, et al. PLoS Computational Biology. \textbf{4} (2008).
+\bibitem{Dewar2009} M. Dewar, et al. IEEE Trans. on Signal Processing. \textbf{57} (2009) 83-91.
+\bibitem{Scerri2009} K. Scerri, et al. IEEE Trans. on Signal Processing. \textbf{57} (2009) 482-492.
         \end{thebibliography}}}	\end{block}
@@
 		\end{figure}				
-
 		\begin{figure}
 		\begin{center}
-		\includegraphics[width=10.5in, scale = 10]{FieldComparison.eps}
+		\includegraphics[width=11in, scale = 10]{FieldComparison.eps}
 		\end{center}

### 2010-10-27 ltx/first_order_framework/LaTeX_Manuscript.tex
added hinton diagrams for sensors parameters

@@
 \end{figure*}
+
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure11.pdf}
+\end{center}
+\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
+Log of the RMSE of the kernel for different values of $\nu_{cm}$ and $\Delta_y$.
+Mean kernel estimates are obtained over 50 realisations in each case.}
+\label{fig:Figure11}
+\end{figure*}
+
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure12.pdf}
+\end{center}
+\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
+Log of the RMSE of the kernel for different values of firing thereshold, $v_0$ and the slope of the sigmoid, $\varsigma$.
+Mean kernel estimates are obtained over 50 realisations in each case.
+red crosses indicate cases where the kernel can not be estimated due to numerical issues.}
+\label{fig:Figure12}
+\end{figure*}
+
 \section*{Tables}

### 2010-10-28 ltx/first_order_framework/LaTeX_Manuscript.tex
commiting to pull, no real changes
converting paper to IOP compatible format

@@
  % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
- \documentclass[10pt]{article}
-
+ % \documentclass{article}
+\documentclass[12pt]{iopart} 
+\usepackage{iopams}
 % amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
+% \usepackage{amsmath}
 % amssymb package, useful for mathematical symbols
@@
 
-\dean{Need to add extra references between here}
+% \dean{Need to add extra references between here}
 
@@
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
-\dean{and here}
+% \dean{and here}
 
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\textrm{d}\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\rm{d}\mathbf{r}'}, 
 \end{equation}
@@
 By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model
-\begin{equation}
-	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
-	\int_{-\infty}^t 
-	h\left(t - t'\right) \int_\Omega
-	w\left(\mathbf{r},\mathbf{r}'\right) 
-	f\left( v\left( \mathbf{r}',t' \right)\right)
-	\textrm{d}\mathbf{r}'dt'.
-\end{equation}
+% \begin{equation}
+% 	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
+% 	\int_{-\infty}^t 
+% 	h\left(t - t'\right) \int_\Omega
+% 	w\left(\mathbf{r},\mathbf{r}'\right) 
+% 	f\left( v\left( \mathbf{r}',t' \right)\right)
+% 	\textrm{d}\mathbf{r}'dt'.
+% \end{equation}
 To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
@@
 	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}.
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textnormal{d}\mathbf{r}'}.
 \end{equation}
@@
 
-The mapping between the membrane voltage and the electrophysiological data is modelled using the observation function that incorporates sensors with a spatial extent by
+The mapping between the membrane voltage and $\textrm{d}$ the electrophysiological data is modelled using the observation function that incorporates sensors with a spatial extent by
 \begin{equation}
@@
 Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain $\Omega$ to get 
-\begin{equation}
-    \begin{split}
+\begin{eqnarray}
 	\label{StartofReduction}
- 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1}= &
- T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {\boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}}\boldsymbol{\theta}  \\
-& + \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t +
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} &=&
+ T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
+&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'\textrm{d}\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
+&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
 \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}. 
-\end{split}
-\end{equation}
+\end{eqnarray}
 Now defining the matrix
@@
 \end{equation}
-and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 
-\begin{equation}
+and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives \dean{here}
+\begin{eqnarray}
     \label{eq:ReducedForm}
-    \begin{split}
-	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
+    % \begin{split}
+	 \mathbf{x}_{t+1} &=& T_s\boldsymbol{\Gamma}^{-1}
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
+	&\times& \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
 	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
-	 \end{split}
-\end{equation}
+	 % \end{split}
+\end{eqnarray}
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\Gamma$, is provided in the Supporting Information, S1.
@@
 The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
-\begin{align}\label{eq:sigmapoints1}
-	\mathcal X_{0}&=\bar x \\
-	\mathcal X_{i}&=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L \\
-	\mathcal X_{i}&=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2L 
-\end{align}
+\begin{eqnarray}\label{eq:sigmapoints1}
+	\mathcal X_{0}&=&\bar x \\
+	\mathcal X_{i}&=&\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L \\
+	\mathcal X_{i}&=&\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2L 
+\end{eqnarray}
 where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
@@
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
-\begin{align}
-	\mathbf W_0^{(m)}&=\frac{\lambda}{ L+\lambda} \\
-	\mathbf W_0^{(c)}&=\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) \\
-	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
-\end{align}
+\begin{eqnarray}
+	\mathbf W_0^{(m)}&=&\frac{\lambda}{ L+\lambda} \\
+	\mathbf W_0^{(c)}&=&\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) \\
+	\mathbf W_i^{(m)}&=&\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
+\end{eqnarray}
 where the superscripts $m$ and $c$ denote mean and covariance.
@@
 Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
-\begin{align*}
-	\mathbf x_{1} &= \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
-	\mathbf x_{2} &= \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
+\begin{eqnarray*}
+	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
+	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
 	&\vdots& \\
-	\mathbf x_{T}&=\mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
-\end{align*}
+	\mathbf x_{T}&=& \mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
+\end{eqnarray*}
 This can be written in the compact form

### 2010-10-28 ltx/first_order_framework/LaTeX_Manuscript.tex
more changes to paper converting it to JoNE

@@
 %Set the section counter to one
-\setcounter{section}{1}
+% \setcounter{section}{1}
 
@@
 
-\pagestyle{myheadings}
+% \pagestyle{myheadings}
 %% ** EDIT HERE **
@@
 % Title must be 150 characters or less
-\begin{flushleft}
-{\Large
-\textbf{A Data-Driven Framework for Neural Field Modelling}
-}
-% Insert Author names, affiliations and corresponding author email.
-\\
-Dean R. Freestone$^{1,2,3,\ast}$, 
+\title[A Data-Driven Framework for Neural Field Modelling]{A Data-Driven Framework for Neural Field Modelling}
+
+\author{Dean R. Freestone$^{1,2,3}$, 
 Parham Aram$^{4}$, 
@@
 David B. Grayden$^{1,2}$,
-Visakan Kadirkamanathan$^{4}$
-\\
-\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
+Visakan Kadirkamanathan$^{4}$}
+
+\address{\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
 \\
@@
 \\
-\bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta
-\\
-$\ast$ E-mail: dfreestone@bionicear.org
-\end{flushleft}
-
-% Please keep the abstract between 250 and 300 words
-\section*{Abstract}
-
+\bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+
+\ead{dfreestone@bionicear.org}
+
+\begin{abstract}
 This paper presents a framework for creating neural field models from electrophysiological data.
@@
 The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
-
-\section*{Introduction}
+\end{abstract}
+
+\maketitle
+
+\section{Introduction}
 Generating physiologically plausible neural field models is of great importance for studying brain dynamics at the mesoscopic and macroscopic scales.
@@
 % authors may use "Analysis" 
-\section*{Methods}
-
-\subsection*{Neural Field Model}\label{NeuralModelSection} 
+\section{Methods}
+
+\subsection{Neural Field Model}\label{NeuralModelSection} 
 Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials.
@@
 
-\subsection*{Derivation of the Integro-Difference Equation Representation}
+\subsection{Derivation of the Integro-Difference Equation Representation}
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
@@
 
-\subsection*{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
+\subsection{Derivation of Finite Dimensional State-Space Model}\label{Sect:ReducedModelDerivation}
 In order to implement standard estimation techniques, we use a decomposition of the field using a set of Gaussian basis functions.
@@
 
-\subsection*{Spectral Analysis}\label{SpectralAnalysisSection} 
+\subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
 Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
@@
 
-\subsection*{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
+\subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
@@
 % Results and Discussion can be combined.
-\section*{Results}\label{ResultsSection} In this section, we provide a demonstration of the estimation procedure using the new methods that are described above.
+\section{Results}\label{ResultsSection} In this section, we provide a demonstration of the estimation procedure using the new methods that are described above.
 The full neural field model was used to generate the data for state and parameter estimation.
@@
 
-\subsection*{Spatial Frequency Analysis} 
+\subsection{Spatial Frequency Analysis} 
 The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
@@
 
-\subsection*{State and Parameter Estimates} 
+\subsection{State and Parameter Estimates} 
 \label{sec:state_and_param_results}
@@
 
-\section*{Discussion}\label{DiscussionSection}
+\section{Discussion}\label{DiscussionSection}
 This paper has presented a framework for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
@@
 
-\subsection*{Implications for Experiment Design}
+\subsection{Implications for Experiment Design}
 As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
@@
 
-\subsection*{Computational Complexity}
+\subsection{Computational Complexity}
 The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
@@
 
-\section*{Future Work}
-
-\subsection*{Patient-Specific Modelling}
+\section{Future Work}
+
+\subsection{Patient-Specific Modelling}
 
@@
 
-\subsection*{Extensions to the framework}
+\subsection{Extensions to the framework}
 
@@
 % Do NOT remove this, even if you are not including acknowledgments
-\section*{Acknowledgments}
+\section{Acknowledgments}
 Dean Freestone would like to thank Dr.

### 2010-10-28 ltx/first_order_framework/LaTeX_Manuscript.tex
more edits converting to IOP sty

@@
-% Template for PLoS
-% Version 1.0 January 2009
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-
 % TO DELETE
@@
 
- % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
- % \documentclass{article}
 \documentclass[12pt]{iopart} 
 \usepackage{iopams}
-% amsmath package, useful for mathematical formulas
+
+% % for checking equation size
+% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \documentclass[a4paper,10pt,twocolumn]{article} 
 % \usepackage{amsmath}
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
-
-% graphicx package, useful for including eps and pdf graphics
-% include graphics with the command \includegraphics
-\usepackage{graphicx}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-\usepackage{color}
-
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-%Set the section counter to one
-% \setcounter{section}{1}
-
-% Text layout
-\topmargin 0.0cm
-\oddsidemargin 0.5cm
-\evensidemargin 0.5cm
-\textwidth 16cm 
-\textheight 21cm
-
-% Bold the 'Figure #' in the caption and separate it with a period
-% Captions will be left justified
-\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
-
-% Use the PLoS provided bibtex style
-\bibliographystyle{plos2009}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-% \date{}
-
-% \pagestyle{myheadings}
-%% ** EDIT HERE **
-
-%% ** EDIT HERE **
-%% PLEASE INCLUDE ALL MACROS BELOW
 % \usepackage{anysize} %<-use this for checking equation length
@@
 % \setlength{\columnsep}{0.5cm} %<-use this for checking equation length
-%% END MACROS SECTION
+% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\usepackage{amssymb}
+\usepackage{graphicx}
+% \usepackage{cite}
+\usepackage{color}
 
@@
 
-\address{\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
-\\
-\bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
-\\
-\bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
-\\
-\bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
-\\
-\bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
-\\
-\bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
-
-\ead{dfreestone@bionicear.org}
+% \address{\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
+% \\
+% \bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
+% \\
+% \bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
+% \\
+% \bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
+% \\
+% \bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
+% \\
+% \bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+% 
+% \ead{dfreestone@bionicear.org}
 
@@
 
-% \dean{Need to add extra references between here}
+\dean{Need to add extra references between here}
 
@@
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
-% \dean{and here}
+\dean{and here}
 
@@
 
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
 \section{Methods}
@@
 By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model
-% \begin{equation}
-% 	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
-% 	\int_{-\infty}^t 
-% 	h\left(t - t'\right) \int_\Omega
-% 	w\left(\mathbf{r},\mathbf{r}'\right) 
-% 	f\left( v\left( \mathbf{r}',t' \right)\right)
-% 	\textrm{d}\mathbf{r}'dt'.
-% \end{equation}
+\begin{equation}
+	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
+	\int_{-\infty}^t 
+	h\left(t - t'\right) \int_\Omega
+	w\left(\mathbf{r},\mathbf{r}'\right) 
+	f\left( v\left( \mathbf{r}',t' \right)\right)
+	\textrm{d}\mathbf{r}'\textrm{d}t'.
+\end{equation}
 To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
-	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
+	\label{GreensFuncDef} \textrm{D}h\left( t \right) = \delta \left( t \right), 
 \end{equation}
-where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $\textrm{d}=\frac{d}{\textrm{d}t} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}
 	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textnormal{d}\mathbf{r}'}.
+	\frac{\textrm{d}v\left( \mathbf{r},t \right)}{\textrm{d}t} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}.
 \end{equation}

### 2010-10-28 ltx/first_order_framework/LaTeX_Manuscript.tex
added kernel estimates
updated histograms

@@
 \end{center}
-\caption{{\bf Histograms of the parameter estimates over 100
+\caption{{\bf Histograms of the parameter estimates over 150
 realisations}.
 The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
-(\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
-(\textbf{B}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(\textbf{C}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-(\textbf{D}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
+(\textbf{a}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+(\textbf{b}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(\textbf{c}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+(\textbf{d}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
 \label{fig:Figure7}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure8.pdf}
+\includegraphics{./Graph/pdf/Figure8_1.pdf}
 \end{center}

### 2010-10-28 ltx/first_order_framework/LaTeX_Manuscript.tex
got rid of fmax

@@
 \begin{equation}
-	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
+	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{1}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
 \end{equation}
-The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations respectively.
+The parameter $v_0$ describes the  firing threshold of the neural populations.
 The parameter $\varsigma$ governs the slope of the sigmoid.
@@
 	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
-	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
+% 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
 	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
formatting paper to IOP sty and making equations fit
added electrode kernel to sup material

@@
 % \usepackage{anysize} %<-use this for checking equation length
-% \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm} %<-use this for checking equation length
+% \marginsize {1.6cm}{1.6cm}{1.0cm}{1.8cm} %<-use this for checking equation length
 % \setlength{\columnsep}{0.5cm} %<-use this for checking equation length
@@
 
-% \address{\bf{1} Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
-% \\
-% \bf{2} The Bionic Ear Institute, East Melbourne, VIC, Australia
-% \\
-% \bf{3} Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
-% \\
-% \bf{4} Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
-% \\
-% \bf{5} Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
-% \\
-% \bf{6} Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
-% 
-% \ead{dfreestone@bionicear.org}
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
+\\
+$^2$ The Bionic Ear Institute, East Melbourne, VIC, Australia
+\\
+$^3$ Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
+\\
+$^4$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
+\\
+$^5$ Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
+\\
+$^6$ Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+
+\ead{dfreestone@bionicear.org}
 
@@
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$.
-$\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
-The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the sensor pick-up geometry and is defined by
+where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denoting the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+
+When considering the measurement of a point source in a homogeneous field measured by a point sensor the observation kernel will theoretically follow a Laplacian distribution, with an exponential decay in amplitude with increasing distance between the source and sensor \dean{(ref)}.
+However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes flattened and is more likened to a Gaussian shape.
+Therefore, the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
 \begin{equation}
@@
 \end{equation}
-where $\sigma_m$ sets the sensor width.
+where $\sigma_m$ sets the kernel width. An example of measured
 
@@
 Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
-\begin{equation}
+\begin{eqnarray}
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta}
-	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
-\end{equation}
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
+\end{eqnarray}
 Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain $\Omega$ to get 
@@
 Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
-\begin{equation}
-	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t 
+\begin{eqnarray}
+	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
 + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
-\end{equation}
+\end{eqnarray}
 This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}.
@@
 
-% \section*{References}
-% The bibtex filename
+\section*{References}
+\bibliographystyle{unsrt} 
 \bibliography{BrainIDE}
@@
 \multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
-$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$ \\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})$ \\
 $\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 

### 2010-10-29 ltx/first_order_framework/SupportingInformation.tex
added electrode kernel to sup material

@@
 %\fi
-
-\ifpdf
-\usepackage[pdftex]{graphicx}
-\else
-\usepackage{graphicx}
-\fi
+\usepackage{graphicx,epsfig}
+% 
+% \ifpdf
+% % \usepackage[pdftex]{graphicx}
+% \else
+% \fi
 % \title{S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'}
@@
 This completes the derivation.
+
+\section*{Observation Kernel}
+The Gaussian shape of the observation kernel was verified experimentally by moving a current dipole source across a recording electrode submerged in saline.
+A photograph of the experimental setup can be seen in Figure~\ref{fig:SensorAndSource}.
+The measurement electrode was a $5\times5$ Utah array (Blackrock Microsystems) with electrode spacing of 400~$\mu$m.
+The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
+The twisted wire electrode was manipulated in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
+The twisted wire electrode and the Utah array were co-registered by visual inspection using a microscope.
+\begin{figure}[ht]		
+	\begin{center}
+		%trim option's parameter order: left bottom right top
+	\includegraphics[scale=.1, trim = .5mm .5mm .00005mm .00005mm, clip ] {./Graph/eps/SensorAndSource.eps}
+\end{center}
+	\caption{Sensor and source. The electrode used for recording was the center electrode of the Utah array, and the source is the twisted wired electrode.}
+	\label{fig:SensorAndSource}
+\end{figure}
+
+The stimulation for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
+The recording from the central electrode was used construct the sensor kernel.
+To extract the amplitude the signal the data was first band-pass filtered with a centre frequency of 40~Hz.
+The the envelope of the signal was found by
+\begin{equation}
+	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
+\end{equation}
+where
+\begin{figure}[h]
+	\begin{center}
+	\includegraphics[scale=1]{./Graph/eps/channel3fig.eps}
+	\end{center}
+	\caption{Amplitude of the envelope of the signal recorded from an electrode at the origin as the source was moved.}
+	\label{fig:Ch3}
+\end{figure}
+
 \bibliographystyle{plain}

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure4

@@
 \caption{{\bf Spatial frequency analysis of the neural field}.
-(\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
-(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+(\textbf{a}) The average (over time) power in dB of the spatial frequency of the neural field.
+(\textbf{b}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
 The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure5

@@
 The dashed line shows the cut-off frequency (-3 dB point).
-(\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
-(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
+(\textbf{a}) The average (over time) power in dB of the spatial frequency of the observations.
+(\textbf{b}) The spatial frequency response of a one-dimensional model sensor.
 The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
+(\textbf{c}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
 }

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure6
Changed Figure9

@@
 \end{center}
-\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 100 runs.
+\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 runs.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
@@
 \end{center}
-\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
+\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).} 
 \label{fig:Figure9}

### 2010-10-29 ltx/first_order_framework/SupportingInformation.tex
commiting for merge

@@
 
-The stimulation for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
+The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
 The recording from the central electrode was used construct the sensor kernel.
 To extract the amplitude the signal the data was first band-pass filtered with a centre frequency of 40~Hz.
-The the envelope of the signal was found by
+The envelope of the signal was found by computing the mean instantaneous amplitude computed by
 \begin{equation}
@@
 \end{equation}
-where
+where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
+
 \begin{figure}[h]

### 2010-10-30 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure10

@@
 \caption{{\bf Examples of the actual and estimated neural fields and the error}.
-(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
-(\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-(\textbf{C}) The absolute error between the true and reconstructed fields.
+(\textbf{a}) The actual field at a single time instant from the full neural field model that was used to generate the data.
+(\textbf{b}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+(\textbf{c}) The absolute error between the true and reconstructed fields.
 The error shows high frequency behaviour.}

### 2010-10-31 ltx/first_order_framework/SupportingInformation.tex
update to suporting info

@@
 \section*{Observation Kernel}
-The Gaussian shape of the observation kernel was verified experimentally by moving a current dipole source across a recording electrode submerged in saline.
-A photograph of the experimental setup can be seen in Figure~\ref{fig:SensorAndSource}.
+The Gaussian shape of the observation kernel was verified experimentally by moving a dipole  across a recording electrode submerged in saline.
+A photograph of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
 The measurement electrode was a $5\times5$ Utah array (Blackrock Microsystems) with electrode spacing of 400~$\mu$m.
 The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
-The twisted wire electrode was manipulated in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
+The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
 The twisted wire electrode and the Utah array were co-registered by visual inspection using a microscope.
@@
 \end{center}
-	\caption{Sensor and source. The electrode used for recording was the center electrode of the Utah array, and the source is the twisted wired electrode.}
+	\caption{Photograph through a microscope of the Utah recording array and the twisted bipolar current source.}
 	\label{fig:SensorAndSource}
@@
 The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
-The recording from the central electrode was used construct the sensor kernel.
+The recording from the central electrode in the array was used estimate the shape of the sensor kernel.
 To extract the amplitude the signal the data was first band-pass filtered with a centre frequency of 40~Hz.
-The envelope of the signal was found by computing the mean instantaneous amplitude computed by
+The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
 \begin{equation}
@@
 where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
+Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus to distance between the twisted wire electrode and the recording electrode.
 

### 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
added cross section of the Figure12
minor corrections

@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated.
+To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 150 realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
-Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
+Ten iterations of the estimation algorithm were used to ensure the parameters  converged.
 Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
@@
 \end{figure*}
+\begin{figure*}[!ht]
+\begin{center}
 
+\includegraphics{./Graph/pdf/Figure13.pdf}
+\end{center}
+\caption{{\bf RMSE of the kernel estimates}.
+RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$.
+Mean kernel estimates are obtained over 50 realisations in each case.}
+\label{fig:Figure12}
+\end{figure*}
 \section*{Tables}
@@
 % 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\
-	$v_0$ & firing threshold & 2 & mV \\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 & mV$^{-1}$\\
+	$v_0$ & firing threshold & 1.8 & mV \\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}

### 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to state and parameter estimates

@@
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good agreement with the actual values.
-
-The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
-The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
+\parham{The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however $\xi$ is outside the estimate distribution.}
 
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
 At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
@@
 It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.
+
+\parham{To further study the ability of the proposed technique we used differents sets of connectivity basis functions parameters.
+The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where for each subset the mean over the 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.} \parham{this bit should change as well:} The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
 
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure8_1.pdf}
-\end{center}
-\caption{{\bf Cross-section of connectivity kernel estimate}.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
-\label{fig:Figure8}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
 \includegraphics{./Graph/pdf/Figure9.pdf} 
@@
 \end{figure*}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure8_1.pdf}
+\end{center}
+\caption{{\bf Cross-section of connectivity kernel estimate}.
+The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
+\label{fig:Figure8}
+\end{figure}
 

### 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to state and parameter estimates

@@
 
-\parham{To further study the ability of the proposed technique we used differents sets of connectivity basis functions parameters.
+\parham{To further study the ability of the proposed technique we used different sets of connectivity basis functions parameters.
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where for each subset the mean over the 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.} \parham{this bit should change as well:} The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
 The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
+
+\parham{variations in thereshold and slope}
+
+\parham{variations in sensor width}
 
@@
 \subsection{Implications for Experiment Design}
-As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values.
+As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation \parham{for the connectivity kernel parameters}, where the mean parameter estimates are in good agreement with the actual values.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
commiting for merge

--- 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 150 realisations of the data were generated.
+To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
-Ten iterations of the estimation algorithm were used to ensure the parameters  converged.
+Eleven iterations of the estimation algorithm were used to ensure the parameters  converged.
 Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
@@
 \end{figure*}
-\begin{figure*}[!ht]
-\begin{center}
 
-\includegraphics{./Graph/pdf/Figure13.pdf}
-\end{center}
-\caption{{\bf RMSE of the kernel estimates}.
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{./Graph/pdf/Figure13.pdf}
+% \end{center}
+% \caption{{\bf RMSE of the kernel estimates}.
 RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$.
 Mean kernel estimates are obtained over 50 realisations in each case.}
-\label{fig:Figure12}
-\end{figure*}
+% \label{fig:Figure12}
+% \end{figure*}
+
 \section*{Tables}
@@
 % 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 & mV$^{-1}$\\
-	$v_0$ & firing threshold & 1.8 & mV \\
+	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\
+	$v_0$ & firing threshold & 2 & mV \\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
added Figure13
minor correction
finished adding sensor kernel experiment to sup material and ammended paper accordingly

--- 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\rm{d}\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
 \end{equation}
@@
 	f\left( v\left( \mathbf{r}',t' \right)\right)
-	\textrm{d}\mathbf{r}'\textrm{d}t'.
+	d\mathbf{r}'dt'.
 \end{equation}
@@
 \end{equation}
-where $\textrm{d}=\frac{d}{\textrm{d}t} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $\textrm{D}=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}
 	\label{FinalFormContinuous} 
-	\frac{\textrm{d}v\left( \mathbf{r},t \right)}{\textrm{d}t} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\textrm{d}\mathbf{r}'}.
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see the S1 for derivation) giving 
+To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see the supplementary material for derivation) giving 
 \begin{equation}
@@
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	\textrm{d}\mathbf{r}'} 
+	d\mathbf{r}'} 
 	+ e_t\left(\mathbf{r}\right), 
@@
 
-The mapping between the membrane voltage and $\textrm{d}$ the electrophysiological data is modelled using the observation function that incorporates sensors with a spatial extent by
+The mapping between the membrane voltage and the electrophysiological data is modelled using the observation function that incorporates sensors with a spatial extent by
 \begin{equation}
@@
 	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	\textrm{d}\mathbf{r}'} + 
+	d\mathbf{r}'} + 
 	\boldsymbol{\varepsilon}_t, 
 \end{equation}
-where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denoting the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,N$ indexes the electrodes and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denoting the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
 
-When considering the measurement of a point source in a homogeneous field measured by a point sensor the observation kernel will theoretically follow a Laplacian distribution, with an exponential decay in amplitude with increasing distance between the source and sensor \dean{(ref)}.
-However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes flattened and is more likened to a Gaussian shape.
+When considering the measurement of a point source in a homogeneous field measured by a point sensor the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in amplitude with increasing distance between the source and sensor~\cite{Jackson1999}.
+However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more likened to a Gaussian shape~\cite{Jackson1999}.
 Therefore, the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
@@
 \end{equation}
-where $\sigma_m$ sets the kernel width. An example of measured
+where $\sigma_m$ sets the kernel width. An example of measured observation kernel is shown in the supplementary material.
 
@@
 \caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
-Log of the RMSE of the kernel for different values of firing thereshold, $v_0$ and the slope of the sigmoid, $\varsigma$.
+Log of the RMSE of the kernel for different values of firing threshold, $v_0$ and the slope of the sigmoid, $\varsigma$.
 Mean kernel estimates are obtained over 50 realisations in each case.

### 2010-11-01 ltx/first_order_framework/SupportingInformation.tex
commiting for merge
finished adding sensor kernel experiment to sup material and ammended paper accordingly

@@
 \section*{Observation Kernel}
-The Gaussian shape of the observation kernel was verified experimentally by moving a dipole  across a recording electrode submerged in saline.
-A photograph of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
-The measurement electrode was a $5\times5$ Utah array (Blackrock Microsystems) with electrode spacing of 400~$\mu$m.
+The Gaussian shape of the observation kernel was verified experimentally.
+This was achieved by moving a dipole across a recording electrode submerged in saline.
+A photograph through a microscope of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
+The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
 The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
 The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
-The twisted wire electrode and the Utah array were co-registered by visual inspection using a microscope.
+The twisted wire electrode and the Utah array were co-registered by visually using the microscope.
 \begin{figure}[ht]		
@@
 Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus to distance between the twisted wire electrode and the recording electrode.
-
+A Gaussian fitted to the amplitudes is also shown.
+The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
 \begin{figure}[h]

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to paper, some minor formatting and some edits to results with the new graphs

@@
 To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
-Making substitutions of equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} into~\ref{DiscreteTimeModel} we get
+Rearranging the order of the spatial convolution in~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
 \begin{eqnarray}
@@
 \end{equation}
-and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives \dean{here}
+and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives
 \begin{eqnarray}
@@
 \end{eqnarray}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\Gamma$, is provided in the Supporting Information, S1.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\Gamma$, is provided in the supplementary material.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
@@
 \end{equation}
-which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the supplementary material for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
 Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
@@
 \end{eqnarray}
-This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}.
-This provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ can be calculated analytically.
-This is of great importance as it lowers the computational demands of the estimation algorithm.
+This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{reduced continuous model}, which would be computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which can be calculated analytically.
+This is of great importance as it lowers the computational demands of the estimation algorithm and provides a dramatic increase in estimation speed.
 
@@
 \end{equation}
-which is a zero mean normally distributed white noise process with covariance (see the Supporting Information, S1, for the derivation)
+which is a zero mean normally distributed white noise process with covariance (see the supplementary material for the derivation)
 \begin{equation}
@@
 Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
-Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.
+Based on a two-dimensional extension of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
 
@@
 This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
-Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in the Supporting Information, S1.
+Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in the supplementary material.
 
@@
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
-At each iteration, the sequence of estimated state vectors is used to update the parameter set.
+Once initialised, at each iteration the sequence of estimated state vectors is used to update the parameter set.
 The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
@@
 \end{small}
-Following this, the LS parameter estimates, $ \mathcal{\hat{W}}$, are
+Following this, the LS parameter estimates, $ \hat{\mathcal{W}}$, are
 \begin{equation}
-	\mathcal{\hat{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
+	\hat{\mathcal{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
 \end{equation}
@@
 Figure~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
-The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
+%The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
 
@@
 The distance between sensors was set to $\Delta_y = 1.5$~mm.
-This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
+This arrangement modelled the recording as having some cross talk (from volume conduction), which is typical for neurophysiological recordings.
 
@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 150 realisations of the data were generated.
+To demonstrate the performance of the state and parameter estimation algorithm several experiments were performed.
+The results of the first experiment demonstrates the estimation performance using a Monte Carlo approach for a single set of parameters.
+The second experiment demonstrates the performance with a selection of different connectivity kernel parameters.
+The third experiment shows the dependance of the estimation accuracy on the parameters of the sigmoidal nonlinearity.
+The final experiment shows the effect of the width of the sensor kernel on the estimation performance.
+
+\subsubsection{Monte Carlo Simulation with Fixed Parameters}
+A Monte Carlo approach was employed where \dean{150} realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
@@
 
-Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Figure7}.
+Histograms of the parameter estimates obtained over the \dean{150} realisations are shown in Figure~\ref{fig:Figure7}.
 The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-\parham{The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however $\xi$ is outside the estimate distribution.}
+The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of 2.78\%).
 
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for \dean{150} realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
 At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
@@
 
-\parham{To further study the ability of the proposed technique we used different sets of connectivity basis functions parameters.
-The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where for each subset the mean over the 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.} \parham{this bit should change as well:} The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
+\subsubsection{Results for Different Connectivity Kernel Parameters}
+
+To further study the performance of the proposed framework we used different sets of connectivity basis functions parameters.
+The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
+For each subset of parameters the mean of the reconstructed kernel over \dean{50} realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
+
+Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied.
+For Part a), the kernel estimates are not in good accordance with the true kernel, as the true kernel falls outside of the confidence intervals in some areas.
+\dean{This is because???}
+\parham{this bit should change as well:} 
+The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
 The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
 
-\parham{variations in thereshold and slope}
+\subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
 
-\parham{variations in sensor width}
+\subsubsection{Results for Varying the Sensor Kernel Width}
 
@@
 \end{center}
-\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 runs.
+\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over \dean{150} realisations.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
@@
 \end{center}
-\caption{{\bf Histograms of the parameter estimates over 150
+\caption{{\bf Histograms of the parameter estimates over \dean{150}
 realisations}.
@@
 \end{center}
-\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).} 
+\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over \dean{150} realisations (solid line) and the 95~\% confidence interval (grey region).} 
 \label{fig:Figure9}
@@
 \caption{{\bf Cross-section of connectivity kernel estimate}.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
+The actual kernel is shown by the solid line, the mean kernel estimate (over \dean{50} realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
 \label{fig:Figure8}
@@
 
-% \begin{figure*}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/Figure13.pdf}
-% \end{center}
-% \caption{{\bf RMSE of the kernel estimates}.
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure13.pdf}
+\end{center}
+\caption{{\bf RMSE of the kernel estimates}.
 RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$.
 Mean kernel estimates are obtained over 50 realisations in each case.}
-% \label{fig:Figure12}
-% \end{figure*}
+\label{fig:Figure13}
+\end{figure*}
 

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to results, sigmoid parameters bit

@@
 For Part a), the kernel estimates are not in good accordance with the true kernel, as the true kernel falls outside of the confidence intervals in some areas.
-\dean{This is because???}
+\dean{This is because???
+the amplitude the central kernel is low, so noise has a greater effect (although this should just cause a wider confidence interval)?, the amplitude or the outer basis function is high (and the field is too small (boundary issues))?
+the spatial discretisation stuffs it up (the peaks of the extrema of the continuous kernel do not fall as discrete space locations)?}
+
 \parham{this bit should change as well:} 
-The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
+For parts b) and c) the figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(c).
 
 \subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
-
+To illustrate the effect of varying the 
+Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy for the connectivity kernel for various parameters of the sigmoid. 
 \subsubsection{Results for Varying the Sensor Kernel Width}

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
added bit about the varying sigmoid

@@
 \subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
-To illustrate the effect of varying the 
-Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy for the connectivity kernel for various parameters of the sigmoid. 
+Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) for the connectivity kernel for various parameters of the sigmoid, varying the slope, $\varsigma$, and the threshold, $\v_0$ .
+The size of the squares in the figure show the magnitude of the log of the error.
+The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white of the log of the error is positive (the RMSE is $>1$).
+The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations.
 \subsubsection{Results for Varying the Sensor Kernel Width}

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

@@
 \subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
-Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) for the connectivity kernel for various parameters of the sigmoid, varying the slope, $\varsigma$, and the threshold, $\v_0$ .
+Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) for the connectivity kernel for various parameters of the sigmoid, varying the slope, $\varsigma$, and the threshold, $v_0$ .
 The size of the squares in the figure show the magnitude of the log of the error.

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
added new figure to show sigmoid functions

@@
 \subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
-Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) for the connectivity kernel for various parameters of the sigmoid, varying the slope, $\varsigma$, and the threshold, $v_0$ .
+Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) of the connectivity kernel for various parameters of the sigmoid varying the slope, $\varsigma$, and the threshold, $v_0$, whilst the other parameters remain fixed.
+The kernel and time constant parameters used in this experiment were the one that gave the best results from the previous experiment.
 The size of the squares in the figure show the magnitude of the log of the error.
-The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white of the log of the error is positive (the RMSE is $>1$).
+The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$).
 The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations.
+From the figure it can be seen that the estimation accuracy depends on the characteristics of the sigmoid function.
+When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
+However as the slope is increased or the cut-off is increased, more information is being cut off by the activation function.
+This is illustrated in figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
+This appears to have a detrimental effect on the estimation accuracy.
+
 \subsubsection{Results for Varying the Sensor Kernel Width}
@@
 \begin{center}
+\includegraphics{./Graph/pdf/sigmoidfunctions.pdf}
+\end{center}
+\caption{{\bf Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.}
+\label{fig:sigmoidfunctions}
+\end{figure*}
+
+\begin{figure*}[!ht]
+\begin{center}
 \includegraphics{./Graph/pdf/Figure13.pdf}

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 \subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
+
 Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) of the connectivity kernel for various parameters of the sigmoid varying the slope, $\varsigma$, and the threshold, $v_0$, whilst the other parameters remain fixed.

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
changed the table of estimated paprameters

@@
 
-\begin{table}[!ht]
-\caption{
-\bf{Estimation Results}}
-\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2.5cm}|p{1.5cm}|}
-
-\hline
-Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
-\hline
-$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
-$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
-$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
-$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
-\hline
-\end{tabular}
-\begin{flushleft}Actual parameter values compared to mean parameter estimates obtained from the 100 Monte Carlo simulations.
-\end{flushleft}
-\label{tab:Parameters estimates}
-\end{table}
+% \begin{table}[!ht]
+% \centering
+% \caption{\bf{Estimation Results}}
+% % \begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2.5cm}|p{1.5cm}|}
+% \begin{tabular}{|c|c|c|c|}	
+% \hline
+% Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
+% \hline
+% % $\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
+% $\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
+% $\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
+% $\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
+% \hline
+% \end{tabular}
+% \begin{flushleft}Actual parameter values compared to mean parameter estimates obtained from the 100 Monte Carlo simulations.
+% \end{flushleft}
+% \label{tab:Parameters estimates}
+% \end{table}
+
+% \tiny{\begin{tabular}{lllllllllllllllllll}
+% \hline
+% & \multicolumn{6}{c|}{$\theta_0$}&\multicolumn{6}{c|}{$\theta_1$}&\multicolumn{6}{c|}{$\theta_2$}\\
+% \cline{2-19}
+%  &I&II&III&IV&V&VI&I&II&III&IV&V&VI&I&II&III&IV&V&VI\\
+% \hline\hline
+% Actual Value&$90$&$100$&$110$&$15$&$30$&$50$&$-80$&$-80$&$-80$&$0$&$0$&$0$&$5$&$5$&$5$&$0$&$0$&$0$\\
+% Mean Estimate&$103.86$&$101.75$&$98.9$&$35.67$&$40.43$&$61.43$&$-89.05$&$-81.00$&$-73.13$&$-18.16$&$-12.01$&$-15.03$&$5.23$&$4.75$&$4.37$&$0.81$&$0.35$&$0.27$\\
+% Std. Dev.&$23.14$&$21.29$&$16.57$&$14.82$&$0.73$&$0.65$\\
+% Bias (\%) &at her&\textbf{aici}& & \\
+% \hline
+% \end{tabular}}
+
+\small{\begin{tabular}{lccccccccc}
+Experiment&\multicolumn{3}{c}{I}&\multicolumn{3}{c}{II}&\multicolumn{3}{c}{III}\\
+ Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
+\hline\hline
+Actual Value&$90$&$-80$&$5$&$100$&$-80$&$5$&$110$&$-80$&$5$\\
+Mean Estimate&$103.86$&$-89.05$&$5.23$&$101.75$&$-81.00$&$4.76$&$98.90 $&$-73.13$&$4.37$\\
+Std. Dev.&$23.14$&$16.57$&$0.74$&$21.30$&$14.82$&$0.65$&$16.48$& $11.72$&$0.54$\\
+Bias (\%)& $15.4$&$11.31$&$4.6$&$1.75$&$1.25$&$4.8$&$10.1$&$ 8.58$&$12.6$  \\
+\end{tabular}}
+
+\small{\begin{tabular}{lccccccccc}
+Experiment&\multicolumn{3}{c}{IV}&\multicolumn{3}{c}{V}&\multicolumn{3}{c}{VI}\\
+ Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
+\hline\hline
+Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
+Mean Estimate&$35.68$&$-18.16$&$0.81$&$40.43$&$-12.01$&$ 0.35$&$61.46$&$-15.03$&$0.27$\\
+Std. Dev.&$16.72$&$11.77$&$0.53$&$11.47$&$7.8$&$0.36$&$11.51$&$7.56$&$0.29$\\
+Bias (\%)&$22.97$&$22.7$&$16.2$&$10.43$&$15.01$&$7$&$0.42$&$18.78$&$5.4$\\
+\end{tabular}}
 

### 2010-11-02 ltx/first_order_framework/LaTeX_Manuscript.tex
correction to the table
correction to figure referencing

@@
 When generating the simulated data, we assumed free boundary conditions for the neural field.
-An example of the simulated field can be seen in Figure~\ref{fig:Figure3}(A).
-Figure~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
+An example of the simulated field can be seen in Figure~\ref{fig:Figure3}(a).
+Figure~\ref{fig:Figure3}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(c) shows the power spectral density (PSD) of the simulated time-series.
 %The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
+Figure~\ref{fig:Figure4}(a) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(b) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
@@
 
-The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(A).
+The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(a).
 The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(b).
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
-The band-limiting effect of the basis function decomposition can be seen when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(c).
+The band-limiting effect of the basis function decomposition can be seen when comparing Figure~\ref{fig:Figure4}(a) to Figure~\ref{fig:Figure4}(b).
 
@@
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:Figure10}(b) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(a)), but is missing the higher-frequency detail.
 
@@
 Std. Dev.&$16.72$&$11.77$&$0.53$&$11.47$&$7.8$&$0.36$&$11.51$&$7.56$&$0.29$\\
-Bias (\%)&$22.97$&$22.7$&$16.2$&$10.43$&$15.01$&$7$&$0.42$&$18.78$&$5.4$\\
+Bias (\%)&$137.87$&$-$&$-$&$34.77$&$-$&$-$&$22.92$&$-$&$-$\\
 \end{tabular}}

### 2010-11-02 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

@@
 \subsubsection{Monte Carlo Simulation with Fixed Parameters}
-A Monte Carlo approach was employed where \dean{150} realisations of the data were generated.
+A Monte Carlo approach was employed where 150 realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
@@
 
-Histograms of the parameter estimates obtained over the \dean{150} realisations are shown in Figure~\ref{fig:Figure7}.
+Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
 The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for \dean{150} realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
 At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For each subset of parameters the mean of the reconstructed kernel over \dean{50} realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
+For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
 
@@
 \end{center}
-\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over \dean{150} realisations.
+\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realisations.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
@@
 \end{center}
-\caption{{\bf Histograms of the parameter estimates over \dean{150}
-realisations}.
+\caption{{\bf Histograms of the parameter estimates over 150 realisations}.
 The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
@@
 \end{center}
-\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over \dean{150} realisations (solid line) and the 95~\% confidence interval (grey region).} 
+\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).} 
 \label{fig:Figure9}
@@
 \caption{{\bf Cross-section of connectivity kernel estimate}.
-The actual kernel is shown by the solid line, the mean kernel estimate (over \dean{50} realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
+The actual kernel is shown by the solid line, the mean kernel estimate (over 50 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
 \label{fig:Figure8}

### 2010-11-02 ltx/first_order_framework/LaTeX_Manuscript.tex
committing for merge

--- 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(a)), but is missing the higher-frequency detail.
 
@@
 Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied.
-For Part a), the kernel estimates are not in good accordance with the true kernel, as the true kernel falls outside of the confidence intervals in some areas.
-\dean{This is because???
-the amplitude the central kernel is low, so noise has a greater effect (although this should just cause a wider confidence interval)?, the amplitude or the outer basis function is high (and the field is too small (boundary issues))?
-the spatial discretisation stuffs it up (the peaks of the extrema of the continuous kernel do not fall as discrete space locations)?}
+In all cases the actual kernel fell within the confidence interval of the estimated kernel.
+The mean kernel estimate for Part b) shows very good accordance with the actual kernel.
+In the other Parts a) and c) there is an over estimate and an underestimate of the kernel, respectively.
+These bias are a result
 

### 2010-11-03 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to results section

@@
 
-To further study the performance of the proposed framework we used different sets of connectivity basis functions parameters.
+To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernels.
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
+By changing the weights of the connectivity kernel we are effectivly changing gain of the system and the range of the field amplitudes.
+Therefore, we are changing were the
+
 For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.

### 2010-11-06 ltx/first_order_framework/LaTeX_Manuscript.tex
editted results with different kernels

@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-By changing the weights of the connectivity kernel we are effectivly changing gain of the system and the range of the field amplitudes.
-Therefore, we are changing were the
-
+By changing the weights of the connectivity kernel we are effectively changing gain of the system and the range of the field amplitudes.
+Since the sigmoidal nonlinearity is remaining static, we are changing the operating region on the sigmoid.
+Therefore, we expect our estimation accuracy to vary.
 For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
-
 Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied.
 In all cases the actual kernel fell within the confidence interval of the estimated kernel.
+The kernel in Part a) has the least amount of excitation and the most amount of inhibition.
+Therefore of the three Mexican hat kernels shown, this one will have the least amount of activation.
+The result is an overestimate of the central excitatory region of the kernel.
+Conversely, in Part c) of the figure the actual kernel has the most amount of excitation and the least amount of inhibition.
+Therefore
+
 The mean kernel estimate for Part b) shows very good accordance with the actual kernel.

### 2010-11-06 src/Matlab/GenerateData.m

@@ -76,3 +76,7 @@ if exist('RunningBatch') == 1
         'mu_phi_xy','NSensors_xy','mu_y_xy','sigma_y','sigma_varepsilon',...
         'f_max','varsigma','v_0','zeta','sigma_gamma','gamma_weight')
 end 
+max1 = squeeze(max(v,[],2));
+max_v_t = mean(max(max1,[],2));
+min1 = squeeze(min(v,[],2));
+min_v_t = mean(min(min1,[],2));

### 2010-11-06 src/Matlab/Set_Parameters.m

@@ -27,7 +27,7 @@ theta(1) = 10.0;     % local kernel amplitude
 theta(2) = -8;     % surround kernel amplitude
 theta(3) = 0.5;       % lateral kernel amplitude
 
-sigma_psi(1) = 1.5;     % local kernel width
+sigma_psi(1) = 1.8;     % local kernel width
 sigma_psi(2) = 2.4;     % surround kernel width
 sigma_psi(3) = 6;       % lateral kernel width
 
@@ -40,7 +40,7 @@ Ts_W = W*Ts;                        % FFT of kernel times the time step
 
 % field basis function parameters
 % ~~~~~~~~~~~~~~~~~~~
-NBasisFunctions_xy = 11;
+NBasisFunctions_xy = 9;
 L = NBasisFunctions_xy^2;                   % number of states and the number of basis functions
 mu_phi_xy = linspace(-10,10,NBasisFunctions_xy);
 sigma_phi = sqrt(2);
@@ -62,7 +62,7 @@ NSensors = NSensors_xy^2;
 mu_y_xy = linspace(-10,10,NSensors_xy);               % sensor centers
 
 sensor_indexes = (mu_y_xy+SpaceMax)/Delta +1;             % so we can easily get the observations from the filed filtered by the sensors
-sigma_y = 0.7;                                                         % sensor width
+sigma_y = 0.9;                                                         % sensor width
 m = Define2DGaussian(0,0, sigma_y^2, 0,NPoints,SpaceMin,SpaceMax);
 M = fft2(m);                                            % fft of sensor kernel to get observations quickly
 % define all sensor centers
@@ -77,14 +77,14 @@ end
 
 % observation noise characteristics
 % ~~~~~~~~~~~~~~~~~~~~
-sigma_varepsilon = 0.001;                                  
+sigma_varepsilon = 0.1;                                  
 Sigma_varepsilon = sigma_varepsilon*eye(NSensors);        % observation covariance matrix
 
 % sigmoid parameters
 % ~~~~~~~~~~~~
 f_max = 10;             % maximum firing rate
-varsigma = 0.8;         % sigmoid slope
-v_0 = 2;                    % firing threshold
+varsigma = 0.56;         % sigmoid slope
+v_0 = 1.8;                    % firing threshold
 
 % synaptic kernel parameter
 % ~~~~~~~~~~~~~~~~

### 2010-11-08 ltx/first_order_framework/LaTeX_Manuscript.tex
made all the ds consistent in each integral (they now all read \, \textrm{d})
corrected table of parameters

@@
 \begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right)dt'}. 
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, \mathrm{d}t'}. 
 \end{equation}
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)d\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\, \mathrm{d}\mathbf{r}'}, 
 \end{equation}
@@
 	f\left( v\left( \mathbf{r}',t' \right)\right)
-	d\mathbf{r}'dt'.
+	\, \mathrm{d} \mathbf{r}' \mathrm{d}t'.
 \end{equation}
@@
 	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, \mathrm{d}\mathbf{r}'}.
 \end{equation}
@@
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	d\mathbf{r}'} 
+	\, \mathrm{d}\mathbf{r}'} 
 	+ e_t\left(\mathbf{r}\right), 
@@
 	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	d\mathbf{r}'} + 
+	\, \mathrm{d}\mathbf{r}'} + 
 	\boldsymbol{\varepsilon}_t, 
@@
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, \textrm{d}\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
 	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
@@
  T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
-&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'\textrm{d}\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
+&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, \textrm{d}\mathbf{r}'\textrm{d}\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
 &+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}. 
+\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}. 
 \end{eqnarray}
@@
 \begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)\textrm{d}\mathbf{r}}, 
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right) \, \textrm{d}\mathbf{r}}, 
 \end{equation}
@@
 	&\times& \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}.
 	 % \end{split}
@@
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r}) \, \textrm{d}\mathbf{r}},
 \end{equation}
@@
 \begin{eqnarray}
-	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
-+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
+	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, \textrm{d}\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
++ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}.
 \end{eqnarray}
@@
 \begin{equation}\label{eq:Wt} 
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )\textrm{d}\mathbf{r}},
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, \textrm{d}\mathbf{r}},
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, \mathrm{d}\mathbf r' \mathrm{d}\mathbf r\mathbf{\Gamma}^{- \top}.
 \end{equation}
@@
 \begin{equation}\label{eq:ReducedObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, \textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
 \end{equation}
@@
 \begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, \textrm{d}\mathbf{r}'. 
 \end{equation}
@@
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
+	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
 \end{equation}
@@
 \begin{equation}
-	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}'.
+	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \,\textrm{d}\mathbf{r}'.
 \end{equation}
@@
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
-	10 &-8 &0.5
+	100 &-80 &5
 	\end{array}

### 2010-11-08 ltx/first_order_framework/LaTeX_Manuscript.tex
added xi mean and std to the result table

@@
 
-\small{\begin{tabular}{lccccccccc}
-Experiment&\multicolumn{3}{c}{I}&\multicolumn{3}{c}{II}&\multicolumn{3}{c}{III}\\
- Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
+\tiny{\begin{tabular}{lcccccccccccc}
+Experiment&\multicolumn{4}{c}{I}&\multicolumn{4}{c}{II}&\multicolumn{4}{c}{III}\\
+ Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
 \hline\hline
-Actual Value&$90$&$-80$&$5$&$100$&$-80$&$5$&$110$&$-80$&$5$\\
-Mean Estimate&$103.86$&$-89.05$&$5.23$&$101.75$&$-81.00$&$4.76$&$98.90 $&$-73.13$&$4.37$\\
-Std. Dev.&$23.14$&$16.57$&$0.74$&$21.30$&$14.82$&$0.65$&$16.48$& $11.72$&$0.54$\\
-Bias (\%)& $15.4$&$11.31$&$4.6$&$1.75$&$1.25$&$4.8$&$10.1$&$ 8.58$&$12.6$  \\
+Actual Value&$90$&$-80$&$5$&$0.9$&$100$&$-80$&$5$&$0.9$&$110$&$-80$&$5$&$0.9$\\
+Mean Estimate&$103.86$&$-89.05$&$5.23$&$0.923$&$101.75$&$-81.00$&$4.76$&$0.924$&$98.90 $&$-73.13$&$4.37$&$0.925$\\
+Std. Dev.&$23.14$&$16.57$&$0.74$&$0.003$&$21.30$&$14.82$&$0.65$&$0.003$&$16.48$& $11.72$&$0.54$&$0.003$\\
+Bias (\%)& $15.4$&$11.31$&$4.6$&$2.56$&$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
 \end{tabular}}
 
-\small{\begin{tabular}{lccccccccc}
-Experiment&\multicolumn{3}{c}{IV}&\multicolumn{3}{c}{V}&\multicolumn{3}{c}{VI}\\
- Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
+\tiny{\begin{tabular}{lcccccccccccc}
+Experiment&\multicolumn{4}{c}{IV}&\multicolumn{4}{c}{V}&\multicolumn{4}{c}{VI}\\
+ Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
 \hline\hline
 Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
-Mean Estimate&$35.68$&$-18.16$&$0.81$&$40.43$&$-12.01$&$ 0.35$&$61.46$&$-15.03$&$0.27$\\
-Std. Dev.&$16.72$&$11.77$&$0.53$&$11.47$&$7.8$&$0.36$&$11.51$&$7.56$&$0.29$\\
-Bias (\%)&$137.87$&$-$&$-$&$34.77$&$-$&$-$&$22.92$&$-$&$-$\\
+Mean Estimate&$35.68$&$-18.16$&$0.81$&$0.923$&$40.43$&$-12.01$&$ 0.35$&$0.924$&$61.46$&$-15.03$&$0.27$&$0.924$\\
+Std. Dev.&$16.72$&$11.77$&$0.53$&$0.002$&$11.47$&$7.8$&$0.36$&$0.003$&$11.51$&$7.56$&$0.29$&$0.003$\\
+Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
 \end{tabular}}

### 2010-11-08 ltx/first_order_framework/LaTeX_Manuscript.tex
added graph showing operating regions along sigmoid

--- 2010-11-06 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 
-To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernels.
+To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernel parameters.
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
@@
 Therefore, we expect our estimation accuracy to vary.
+
+Losing higher frequency peaks
+Losing higher frequency troughs
+
 For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
@@
 \label{fig:Figure8}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/OperatingRegions.pdf}
+\end{center}
+\caption{{\bf Operating Regions along the sigmoid}. The top graph is from the full model and the lower is from the reduced model.}
+\label{fig:OperatingRegions}
 \end{figure}

### 2010-11-08 src/Matlab/Create_C.m

@@ -6,9 +6,9 @@ a = pi / ( (sigma_phi^2+sigma_y^2)/(sigma_phi^2*sigma_y^2) );
 b = 1/(sigma_phi^2+sigma_y^2);
 
 % now define the observation matrix
-C = zeros(NSensors_xy^2,NBasisFunctions_xy^2 );
+C = zeros(NSensors_xy^2,L );
 for n=1:NSensors_xy^2
-    for nn=1:NBasisFunctions_xy^2
+    for nn=1:L
         mu_phi_minus_mu_y = mu_y(:,n)-mu_phi(:,nn);
         C(n,nn) = a*exp(-b*(mu_phi_minus_mu_y)'*mu_phi_minus_mu_y);
     end

### 2010-11-08 src/Matlab/GenerateData.m

@@ -1,82 +1,89 @@
+for ppp=1:1
+    % implementation of the neural field model to generate data
 
-% implementation of the neural field model to generate data
+    % if we are running a batch than we dont want to clear things
+    if exist('RunningBatch') == 0
+        clear
+        close all
+        clc
 
-% if we are running a batch than we dont want to clear things
-if exist('RunningBatch') == 0
-    clear
-    close all
-    clc
-    
-    % run the script that sets all the parameters
-    Set_Parameters
-    plotdata = 1;
-%     load Parameters
-else
-    plotdata = 0;
-end
-
-% create the observation disturbance
-varepsilon = mvnrnd(zeros(1,NSensors),Sigma_varepsilon,T);
-
-% DisturbanceFileName = ['e_' num2str(T) '_' num2str(100*Delta) '_' num2str(100*SpaceMax) '_' ...
-%     num2str(100*sigma_gamma) '_' num2str(100*gamma_weight) '.mat'];
-
-% if exist(DisturbanceFileName) == 2
-%     load(DisturbanceFileName)
-% else
-disp('generating disturbance signal')
-e = mvnrnd(zeros(1,NPoints^2),Sigma_gamma,T);
-%     save(DisturbanceFileName,'e')
-% end
-
-disp('generating data')
-% initialize field
-v = zeros(T,NPoints,NPoints);
-v(1,:,:) = Define2DGaussian(0,0, sigma_phi^2, 0,NPoints,SpaceMin,SpaceMax);
-
-% generate data
-y = zeros(T,NSensors_xy^2);         % initialise obseravation for speed
-y_matrix = zeros(T,NSensors_xy,NSensors_xy);
-for t=1:T-1
-    
-    f = f_max./(1+exp(varsigma*(v_0-squeeze(v(t,:,:)))));           % calc firing rate using sigmoid
-    F = fft2(f);                                                                                % take FFT of firing for conv with kernel
-    g = ifftshift(ifft2(F.*Ts_W,'symmetric'))*Delta_squared;            % conv kernel with firing rate 
-    v(t+1,:,:) = g + xi*squeeze(v(t,:,:)) + reshape(e(t,:,:),NPoints,NPoints);  % update field
-        
-    V = fft2(squeeze(v(t+1,:,:)));                                                  % take FFT of field for conv with sensor
-    m_conv_v = ifftshift(ifft2(M.*V,'symmetric'))*Delta_squared;    % conv with sensor 
-    
[…]

### 2010-11-08 src/Matlab/RunBatch.m

@@ -6,7 +6,7 @@ close all
 Set_Parameters
 
 RunningBatch = 1;               % this is a flag for the scripts
-NRealisations = 50;
+NRealisations = 3;
 for Realisation=1:NRealisations
     tic
     disp(['Running realisation: ' num2str(Realisation) ' of ' num2str(NRealisations)])

### 2010-11-08 src/Matlab/RunFilter.m

@@ -40,7 +40,7 @@ Wc = [(lambda/(L+lambda)) + (1-alpha^2+beta) ; 1/(2*(L+lambda))*ones(2*L,1)];
 sqrt_L_plus_lambda = sqrt(L+lambda);
 
 tic
-NIterations = 5;
+NIterations = 10;
 for Iteration = 1:NIterations
     
     disp('running the forward iteration (filtering)')
@@ -68,27 +68,27 @@ for Iteration = 1:NIterations
     P_b = P_f;
     
     % run the smoother
-    disp('running the backward iteration (smoothing)')
-    for n=1:T-1
-        
-        X_b_minus_t = GetSigmaMatrix(x_b(:,T-n),P_b(:,:,T-n),sqrt_L_plus_lambda);
-        
-        X_b_minus_t_plus_1 = Q(X_b_minus_t, phi_unwrapped, ...
-            Ts_invGamma_theta_phi_psi, Delta_squared, f_max,varsigma, v_0, xi);
-        
-         [x_b_minus_t_plus_1 P_b_minus_t_plus_1] = PredictStateAndCovariance(Wm, Wc, X_b_minus_t_plus_1, Sigma_e);
-         
-         % calculate cross covariance matrix
-         M_t_plus_1 = CalcCrossCovariance(Wc,X_b_minus_t, x_f(:,T-n), X_b_minus_t_plus_1, x_b_minus_t_plus_1);
-        
-         % get smoothed state and smoothed covaraince
-         [P_b(:,:,T-n) x_b(:,T-n)] = GetSmoothedStateAndCovariance(M_t_plus_1, P_b_minus_t_plus_1, ...
-             x_f(:,T-n), x_b(:,(T-n)+1), x_b_minus_t_plus_1, P_b(:,:,(T-n)+1), P_f(:,:,T-n));
-        
-    end
+%     disp('running the backward iteration (smoothing)')
+%     for n=1:T-1
+%         
+%         X_b_minus_t = GetSigmaMatrix(x_b(:,T-n),P_b(:,:,T-n),sqrt_L_plus_lambda);
+%         
+%         X_b_minus_t_plus_1 = Q(X_b_minus_t, phi_unwrapped, ...
+%             Ts_invGamma_theta_phi_psi, Delta_squared, f_max,varsigma, v_0, xi);
+%         
[…]

### 2010-11-08 src/Matlab/Set_Parameters.m

@@ -2,9 +2,9 @@
 
 % if we are running a batch than we dont want to clear things
 if exist('RunningBatch','var') == 0
-    clear
+%     clear
     close all
-    clc
+%     clc
 end
 
 % spatial parameters
@@ -16,16 +16,16 @@ SpaceMin = -SpaceMax;         % minimum space in mm
 NPoints = (SpaceMax-SpaceMin)/Delta+1;
 r = linspace(SpaceMin,SpaceMax,NPoints);      % define space
 
-% temporal parameter
-% ~~~~~~~~~~~~
+% temporal parameters
+% ~~~~~~~~~~~~~
 Ts = 1e-3;          % sampling period (s)
-T = 400;            % maximum time (ms)
+T = 500;            % maximum time (ms)
 
 % kernel parameters
 % ~~~~~~~~~~~
-theta(1) = 10.0;     % local kernel amplitude
-theta(2) = -8;     % surround kernel amplitude
-theta(3) = 0.5;       % lateral kernel amplitude
+theta(1) = 100.0;     % local kernel amplitude
+theta(2) = -80;     % surround kernel amplitude
+theta(3) = 5;       % lateral kernel amplitude
 
 sigma_psi(1) = 1.8;     % local kernel width
 sigma_psi(2) = 2.4;     % surround kernel width
@@ -38,30 +38,67 @@ w = theta(1)*psi_0 + theta(2)*psi_1 + theta(3)*psi_2;       % the kernel
 W = fft2(w);                                                                       % the fft of the kernel
 Ts_W = W*Ts;                        % FFT of kernel times the time step
 
+% ~~~~~~~~~~~~~~~~~~~~~~
+% ~~~~~~~~~~~~~~~~~~~~~~
 % field basis function parameters
 % ~~~~~~~~~~~~~~~~~~~
-NBasisFunctions_xy = 9;
-L = NBasisFunctions_xy^2;                   % number of states and the number of basis functions
-mu_phi_xy = linspace(-10,10,NBasisFunctions_xy);
-sigma_phi = sqrt(2);
+EstimationSpaceMax = 10;
+EstimationSpaceMin = -10;
+phi_x_spacing = 2.0;
+angle = 60;
+phi_y_spacing = phi_x_spacing*sin((angle/360)*2*pi);
 
[…]

### 2010-11-11 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 \label{sec:state_and_param_results}
-To demonstrate the performance of the state and parameter estimation algorithm several experiments were performed.
-The results of the first experiment demonstrates the estimation performance using a Monte Carlo approach for a single set of parameters.
-The second experiment demonstrates the performance with a selection of different connectivity kernel parameters.
+Experiments were performed to demonstrate the performance of the state and parameter estimation algorithm.
+The first experiment evaluates the estimation performance using a Monte Carlo approach for a single set of parameters.
+The second experiment evaluates the performance with a selection of different connectivity kernel parameters.
 The third experiment shows the dependance of the estimation accuracy on the parameters of the sigmoidal nonlinearity.
@@
 Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
-The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
+The actual parameter values, the mean estimates, corresponding standard deviations and biases are given with the results from the next Section in Table~\ref{tab:Parameters estimates}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
@@
 The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
-At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
+At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range \dean{([-3.29,3.77]~mV)}.
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-By changing the weights of the connectivity kernel we are effectively changing gain of the system and the range of the field amplitudes.
-Since the sigmoidal nonlinearity is remaining static, we are changing the operating region on the sigmoid.
-Therefore, we expect our estimation accuracy to vary.
-
-Losing higher frequency peaks
-Losing higher frequency troughs
-
-For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
-Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied.
-In all cases the actual kernel fell within the confidence interval of the estimated kernel.
-The kernel in Part a) has the least amount of excitation and the most amount of inhibition.
-Therefore of the three Mexican hat kernels shown, this one will have the least amount of activation.
-The result is an overestimate of the central excitatory region of the kernel.
-Conversely, in Part c) of the figure the actual kernel has the most amount of excitation and the least amount of inhibition.
-Therefore
-
-The mean kernel estimate for Part b) shows very good accordance with the actual kernel.
-In the other Parts a) and c) there is an over estimate and an underestimate of the kernel, respectively.
-These bias are a result
-
-\parham{this bit should change as well:} 
-For parts b) and c) the figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
-The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(c).
+For Parts a), b) and c) a Mexican hat connectivity kernel was used.
+For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
+In each case the actual kernel was within the 95~\% confidence of kernel estimate.
+The statistics for the kernel parameters estimates for each of the parameter sets are shown in Table~\ref{tab:Parameters estimates}.
+
+For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
+Parts d), e) and f) of Figure~\ref{fig:Figure8} show results when the kernel support in the estimator differed from the actual data.
+In these cases the data was generated using a single positive (excitatory) Gaussian kernel.
+The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples.
+Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates, for the majority of the kernel space until the amplitude is relatively low.
+Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates.
+Importantly, although the reconstructed kernel estimate is in good accord with the actual kernel, the individual kernel basis function weights are not in agreement with the actual parameters.
+This result demonstrates that unless the support of the kernel basis functions are precisely known, the exact meaning of the parameters in isolation is not clear and the net reconstructed kernel should be considered in a practical setting.
 
@@
 
-Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) of the connectivity kernel for various parameters of the sigmoid varying the slope, $\varsigma$, and the threshold, $v_0$, whilst the other parameters remain fixed.
+Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the affect of the sigmoid parameters on the parameter estimation accuracy.
+The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
 The kernel and time constant parameters used in this experiment were the one that gave the best results from the previous experiment.
@@
 The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$).
-The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations.
+The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
 From the figure it can be seen that the estimation accuracy depends on the characteristics of the sigmoid function.
 When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
-However as the slope is increased or the cut-off is increased, more information is being cut off by the activation function.
-This is illustrated in figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
+However, as the slope is increased or the threshold is increased, more information is being cut off or attenuated by the activation function.
+This is illustrated in figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
 This appears to have a detrimental effect on the estimation accuracy.
@@
 \subsubsection{Results for Varying the Sensor Kernel Width}
+The accuracy of the estimation algorithm was tested for observation kernels of different width. To test the affect of the electrode kernel parameter on the estimation
 
@@
 Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
-\end{tabular}}
+\end{tabular}\label{tab:GaussianKernelResults}}
 

### 2010-11-14 ltx/first_order_framework/LaTeX_Manuscript.tex
added alternative figure for the sigmoid RMSE graph
added alternative sensor kernel plot
added to results section, observation kernel experiemnt

@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For Parts a), b) and c) a Mexican hat connectivity kernel was used.
+For Parts a), b) and c) of the figure a Mexican hat connectivity kernel was used.
 For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
@@
 Parts d), e) and f) of Figure~\ref{fig:Figure8} show results when the kernel support in the estimator differed from the actual data.
-In these cases the data was generated using a single positive (excitatory) Gaussian kernel.
+In these cases the data was generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in the figure.
 The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples.
@@
 
-Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the affect of the sigmoid parameters on the parameter estimation accuracy.
+Figure~\ref{fig:Figure11} demonstrates the affect of the sigmoid parameters on the estimation accuracy.
 The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
 The kernel and time constant parameters used in this experiment were the one that gave the best results from the previous experiment.
-The size of the squares in the figure show the magnitude of the log of the error.
+% The size of the squares in the figure show the magnitude of the log of the error.
 The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$).
@@
 However, as the slope is increased or the threshold is increased, more information is being cut off or attenuated by the activation function.
-This is illustrated in figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
+This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
 This appears to have a detrimental effect on the estimation accuracy.
@@
 \subsubsection{Results for Varying the Sensor Kernel Width}
-The accuracy of the estimation algorithm was tested for observation kernels of different width. To test the affect of the electrode kernel parameter on the estimation
+The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter.
+Figure~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various connectivity kernel widths.
+The figure shows that there is error a desirable connectivity kernel width range.
+As the the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
+When the observation kernel is to narrow, a small amount of aliasing appears to be increasing the estimation error.
+When the observation kernel width is initially increased the error drops.
+As expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
 
@@
 \subsection{Implications for Experiment Design}
-As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation \parham{for the connectivity kernel parameters}, where the mean parameter estimates are in good agreement with the actual values.
+As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values and the true kernel lies within the 95~\% confidence intervals of the estimates.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
@@
 
-The current study builds on Schiff and Sauer's approach ~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
+The current study builds on Schiff and Sauer's approach~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in Methods section.
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/OperatingRegions.pdf}
-\end{center}
-\caption{{\bf Operating Regions along the sigmoid}. The top graph is from the full model and the lower is from the reduced model.}
-\label{fig:OperatingRegions}
-\end{figure}
-
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure11.pdf}
-\end{center}
-\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Graph/pdf/OperatingRegions.pdf}
+% \end{center}
+% \caption{{\bf Operating Regions along the sigmoid}. The top graph is from the full model and the lower is from the reduced model.}
+% \label{fig:OperatingRegions}
+% \end{figure}
+
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{./Graph/pdf/Figure11.pdf}
+% \end{center}
+% \caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
 Log of the RMSE of the kernel for different values of $\nu_{cm}$ and $\Delta_y$.
 Mean kernel estimates are obtained over 50 realisations in each case.}
-\label{fig:Figure11}
-\end{figure*}
+% \label{fig:Figure11}
+% \end{figure*}
 
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure12.pdf}
-\end{center}
-\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
+\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
+\end{center}
+\caption{{\bf RMSE of different kernel estimates}.
 Log of the RMSE of the kernel for different values of firing threshold, $v_0$ and the slope of the sigmoid, $\varsigma$.
 Mean kernel estimates are obtained over 50 realisations in each case.
-red crosses indicate cases where the kernel can not be estimated due to numerical issues.}
+White spaces indicate cases where the kernel can not be estimated due to numerical problems.}
 \label{fig:Figure12}
@@
 
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{./Graph/pdf/Figure13.pdf}
+% \end{center}
+% \caption{{\bf RMSE of the kernel estimates}.
+RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$.
+Mean kernel estimates are obtained over 50 realisations in each case.}
+% \label{fig:Figure13}
+% \end{figure*}
+
 \begin{figure*}[!ht]
 \begin{center}
-\includegraphics{./Graph/pdf/Figure13.pdf}
+\includegraphics{./Graph/pdf/RMSESensor.pdf}
 \end{center}
 \caption{{\bf RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$.
+RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$.
 Mean kernel estimates are obtained over 50 realisations in each case.}

### 2010-11-14 ltx/first_order_framework/LaTeX_Manuscript.tex
small general edits to paper, improved some of the results section

@@
 Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatiotemporal neural fields.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
@@
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
-This paper extends the linear framework of \cite{Dewar2009,Scerri2009} to the nonlinear case required by the WC model.
+This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required by the WC model.
 
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \cite{Braitenberg1998}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition~\cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
@@
 The first experiment evaluates the estimation performance using a Monte Carlo approach for a single set of parameters.
+Using this experiment we demonstrate convergence of the algorithm, show the distribution of estimated parameters and the accuracy of the state estimates for a single set of parameters.
 The second experiment evaluates the performance with a selection of different connectivity kernel parameters.
-The third experiment shows the dependance of the estimation accuracy on the parameters of the sigmoidal nonlinearity.
+In addition, results are shown where the support of the connectivity kernels differs between actual data and the estimator.
+The third experiment shows the how the estimation accuracy varies depending on the parameters of the sigmoidal nonlinearity.
 The final experiment shows the effect of the width of the sensor kernel on the estimation performance.
@@
 Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
-The actual parameter values, the mean estimates, corresponding standard deviations and biases are given with the results from the next Section in Table~\ref{tab:Parameters estimates}.
+The actual parameter values, the mean estimates, corresponding standard deviations and biases are given with the results from the next Section in Table~\ref{tab:MexicanHatKernelResults}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of 2.78\%).
+The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of 2.78\%), with a small variance in parameter estimates.
 
@@
 In each case the actual kernel was within the 95~\% confidence of kernel estimate.
-The statistics for the kernel parameters estimates for each of the parameter sets are shown in Table~\ref{tab:Parameters estimates}.
+The statistics for the kernel parameters estimates for each of the parameter sets are shown in Table~\ref{tab:MexicanHatKernelResults}.
 
 For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
-Parts d), e) and f) of Figure~\ref{fig:Figure8} show results when the kernel support in the estimator differed from the actual data.
-In these cases the data was generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in the figure.
+However, in Parts d), e) and f) of Figure~\ref{fig:Figure8} the kernel support in the estimator differed from the actual data.
+In these cases the data was generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
 The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples.
@@
 The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
-The kernel and time constant parameters used in this experiment were the one that gave the best results from the previous experiment.
+The other model parameters remained fixed and where set according the Table~\ref{tab:Parameters}.
+
 % The size of the squares in the figure show the magnitude of the log of the error.
@@
 The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
-From the figure it can be seen that the estimation accuracy depends on the characteristics of the sigmoid function.
+From the figure it can be seen that the estimation accuracy is inter-related to the properties of the sigmoid function.
 When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
@@
 Bias (\%)& $15.4$&$11.31$&$4.6$&$2.56$&$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
-\end{tabular}}
+\end{tabular}\label{tab:MexicanHatKernelResults}}
 

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
changed the derivative and integrtal operators to be nonitalicized for consistancy

@@
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this task has been approached from a number of standpoints.
-
-\dean{Need to add extra references between here}
-
-An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics.
+Recently, however, this task has been approached from a number of standpoints~\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}.
+
+Perhaps the most accepted estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
@@
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
-\dean{and here}
 
@@
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
-This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required by the WC model.
+This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required for the WC or Amari model.
 
@@
 \begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, \mathrm{d}t'}. 
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, dt'}. 
 \end{equation}
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\, \mathrm{d}\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\, d\mathbf{r}'}, 
 \end{equation}
@@
 	f\left( v\left( \mathbf{r}',t' \right)\right)
-	\, \mathrm{d} \mathbf{r}' \mathrm{d}t'.
+	\, d\mathbf{r}'dt'.
 \end{equation}
@@
 	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, \mathrm{d}\mathbf{r}'}.
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
 \end{equation}
@@
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	\, \mathrm{d}\mathbf{r}'} 
+	\, d\mathbf{r}'} 
 	+ e_t\left(\mathbf{r}\right), 
@@
 	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	\, \mathrm{d}\mathbf{r}'} + 
+	\, d\mathbf{r}'} + 
 	\boldsymbol{\varepsilon}_t, 
@@
 However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more likened to a Gaussian shape~\cite{Jackson1999}.
-Therefore, the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
+Therefore, in this study the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
 \begin{equation}
@@
 To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
-Rearranging the order of the spatial convolution in~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
+Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
 \begin{eqnarray}
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, \textrm{d}\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
 	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
@@
 	\label{StartofReduction}
- 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} &=&
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} &=&
  T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
-&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, \textrm{d}\mathbf{r}'\textrm{d}\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
-&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}. 
+&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
+&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
+\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
 \end{eqnarray}
@@
 \begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right) \, \textrm{d}\mathbf{r}}, 
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right) \, d\mathbf{r}}, 
 \end{equation}
@@
 	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
-	&\times& \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}.
+	&\times& d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
 	 % \end{split}
 \end{eqnarray}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\Gamma$, is provided in the supplementary material.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the supplementary material.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
@@
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r}) \, \textrm{d}\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r}) \, d\mathbf{r}},
 \end{equation}
 which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the supplementary material for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
-Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
+Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
 \begin{eqnarray}
-	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, \textrm{d}\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
-+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}.
+	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
++ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, d\mathbf{r}}.
 \end{eqnarray}
@@
 \begin{equation}\label{eq:Wt} 
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, \textrm{d}\mathbf{r}},
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, d\mathbf{r}},
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, \mathrm{d}\mathbf r' \mathrm{d}\mathbf r\mathbf{\Gamma}^{- \top}.
-\end{equation}
-Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
+	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+\end{equation}
+Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, \textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
 \end{equation}
@@
 \begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, \textrm{d}\mathbf{r}'. 
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'. 
 \end{equation}
@@
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
+	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
 \end{equation}

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
added reference to the work of Freeman to the discussion, spatial freq analysis

@@
 The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
-Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
+As pointed out in numerous publications by Freeman and colleagues (see \cite{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
+Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial properties can be recovered.
 In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
added alternative table

@@
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-Again applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
+Again, applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
 \begin{equation}\label{eq:BasisFunctionSeparation}
@@
 % Results and Discussion can be combined.
-\section{Results}\label{ResultsSection} In this section, we provide a demonstration of the estimation procedure using the new methods that are described above.
+\section{Results}\label{ResultsSection} In this section, we provide demonstrations of the estimation procedure using the new methods that are described above.
 The full neural field model was used to generate the data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{tab:Parameters}.
+All parameters for the model are given in Table~\ref{tab:Parameters}, unless otherwise explicitly stated for particular experiments.
 Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
@@
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.08~mm.
-This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
+This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.
 
@@
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(c).
-The band-limiting effect of the basis function decomposition can be seen when comparing Figure~\ref{fig:Figure4}(a) to Figure~\ref{fig:Figure4}(b).
+This band-limiting effect of the basis function decomposition can be observed when comparing Figure~\ref{fig:Figure4}(a) to Figure~\ref{fig:Figure4}(b).
 
@@
 Ten iterations of the estimation algorithm were used to ensure the parameters converged.
-Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
+Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after 6 iterations.
 
@@
 
-\tiny{\begin{tabular}{lcccccccccccc}
-Experiment&\multicolumn{4}{c}{I}&\multicolumn{4}{c}{II}&\multicolumn{4}{c}{III}\\
- Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
-\hline\hline
-Actual Value&$90$&$-80$&$5$&$0.9$&$100$&$-80$&$5$&$0.9$&$110$&$-80$&$5$&$0.9$\\
-Mean Estimate&$103.86$&$-89.05$&$5.23$&$0.923$&$101.75$&$-81.00$&$4.76$&$0.924$&$98.90 $&$-73.13$&$4.37$&$0.925$\\
-Std. Dev.&$23.14$&$16.57$&$0.74$&$0.003$&$21.30$&$14.82$&$0.65$&$0.003$&$16.48$& $11.72$&$0.54$&$0.003$\\
-Bias (\%)& $15.4$&$11.31$&$4.6$&$2.56$&$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
-\end{tabular}\label{tab:MexicanHatKernelResults}}
+% \tiny{\begin{tabular}{lcccccccccccc}
+% Experiment&\multicolumn{4}{c}{I}&\multicolumn{4}{c}{II}&\multicolumn{4}{c}{III}\\
+%  Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
+% \hline\hline
+% Actual Value&$90$&$-80$&$5$&$0.9$&$100$&$-80$&$5$&$0.9$&$110$&$-80$&$5$&$0.9$\\
+% Mean Estimate&$103.86$&$-89.05$&$5.23$&$0.923$& $101.75$&$-81.00$&$4.76$&$0.924$&$98.90 $&$-73.13$&$4.37$&$0.925$\\
+% Std. Dev.&$23.14$&$16.57$&$0.74$&$0.003$ & $21.30$&$14.82$&$0.65$&$0.003$&$16.48$& $11.72$&$0.54$&$0.003$\\
+% Bias (\%)& $15.4$&$11.31$&$4.6$ &$2.56$ &$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
+% \end{tabular}\label{tab:MexicanHatKernelResults}}
+
+\begin{table}[!ht]
+	\caption{
+	\bf{Results from varying the connectivity kernel parameters}}
+\begin{tabular}{c|ccccc}
+	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
+	I &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
+	& $\theta_1$ & -80 & -89.05 & 16.57 & -11.31 \\
+	& $\theta_2$ & 5 & 5.23 & 0.74 & 4.6 \\
+	& $\xi$ & 0.9 & 0.923 & 0.003 & 2.56 \\ \hline
+
+	II & $\theta_0$ & $100$ & 101.75 & $21.30$ & $1.75$ \\
+	& $\theta_1$ & -80 & -81.00 & $14.82$ & $1.25$ \\
+	& $\theta_2$ & 5 & $4.76$ & $0.65$ & $4.8$ \\
+	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
+
+	III & $\theta_0$ & $110$ & $98.90$ & $16.48$ & $10.1$ \\
+	& $\theta_1$ & -80 & $-73.13$ & $11.72$ & $ 8.58$ \\
+	& $\theta_2$ & 5 & $4.37$ & $0.54$ & $12.6$ \\
+	& $\xi$ & 0.9 & $0.925$ & $0.003$ & $2.78$ \\ \hline
+\end{tabular}\label{tab:MexicanHatKernelResults}
+\end{table}
 

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
added reference for thereshold in table3

@@
 	$\varsigma$ & slope of sigmoidal activation function & 0.56 & mV$^{-1}$\\
-	$v_0$ & firing threshold & 1.8 & mV \\
+	$v_0$ & firing threshold & 1.8 \cite{Marreiros2008}& mV  \\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to table 5

--- 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 	\caption{
-	\bf{Results from varying the connectivity kernel parameters}}
+	\bf{Results from varying the Mexican hat connectivity kernel parameters}}
 \begin{tabular}{c|ccccc}
@@
 	I &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
-	& $\theta_1$ & -80 & -89.05 & 16.57 & -11.31 \\
+	& $\theta_1$ & -80 & -89.05 & 16.57 & 11.31 \\
 	& $\theta_2$ & 5 & 5.23 & 0.74 & 4.6 \\
@@
 
-\tiny{\begin{tabular}{lcccccccccccc}
-Experiment&\multicolumn{4}{c}{IV}&\multicolumn{4}{c}{V}&\multicolumn{4}{c}{VI}\\
- Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
-\hline\hline
-Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
-Mean Estimate&$35.68$&$-18.16$&$0.81$&$0.923$&$40.43$&$-12.01$&$ 0.35$&$0.924$&$61.46$&$-15.03$&$0.27$&$0.924$\\
-Std. Dev.&$16.72$&$11.77$&$0.53$&$0.002$&$11.47$&$7.8$&$0.36$&$0.003$&$11.51$&$7.56$&$0.29$&$0.003$\\
-Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
-\end{tabular}\label{tab:GaussianKernelResults}}
+% \tiny{\begin{tabular}{lcccccccccccc}
+% Experiment&\multicolumn{4}{c}{IV}&\multicolumn{4}{c}{V}&\multicolumn{4}{c}{VI}\\
+%  Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
+% \hline\hline
+% Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
+% Mean Estimate&$35.68$&$-18.16$&$0.81$&$0.923$&   $40.43$&$-12.01$&$ 0.35$&$0.924$&        $61.46$&$-15.03$&$0.27$&$0.924$\\
+% Std. Dev.&$16.72$&$11.77$&$0.53$&$0.002$&		$11.47$&$7.8$&$0.36$&$0.003$&	$11.51$&$7.56$&$0.29$&$0.003$\\
+% Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
+% \end{tabular}\label{tab:GaussianKernelResults}}
+
+\begin{table}[!ht]
+	\caption{
+	\bf{Results from varying the Gaussian connectivity kernel parameter}}
+\begin{tabular}{c|ccccc}
+	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
+	IV &$\theta_0$ & $15$ & $35.68$ & $16.72$ & $137.87$ \\
+	& $\theta_1$ & 0 & $-18.16$ & $11.77$ & - \\
+	& $\theta_2$ & 0 & $0.81$ & $0.53$ & - \\
+	& $\xi$ & 0.9 & 0.923 & $0.002$ & 2.56 \\ \hline
+
+	V & $\theta_0$ & $30$ & $40.43$ & $11.47$ & $34.77$ \\
+	& $\theta_1$ & 0 & $-12.01$ & $7.8$ & - \\
+	& $\theta_2$ & 0 & 0.35 & $0.36$ & - \\
+	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
+
+	VI & $\theta_0$ & $50$ & $61.46$ & $11.51$ & $22.92$ \\
+	& $\theta_1$ & 0 & $-15.03$ & $7.56$ & - \\
+	& $\theta_2$ & 0 & $0.27$ & $0.29$ & - \\
+	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
+\end{tabular}\label{tab:GaussianKernelResults}
+\end{table}
 

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
changed the figure and references in the text

@@
 When generating the simulated data, we assumed free boundary conditions for the neural field.
-An example of the simulated field can be seen in Figure~\ref{fig:Figure3}(a).
-Figure~\ref{fig:Figure3}(b) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(c) shows the power spectral density (PSD) of the simulated time-series.
+An example of the simulated field can be seen in Figure~\ref{fig:Figure3}(A).
+Figure~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
 %The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:Figure4}(a) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(b) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
+Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
@@
 
-The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(a).
+The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(A).
 The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(b).
+The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
 Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(c).
-This band-limiting effect of the basis function decomposition can be observed when comparing Figure~\ref{fig:Figure4}(a) to Figure~\ref{fig:Figure4}(b).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
+This band-limiting effect of the basis function decomposition can be observed when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
 
@@
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:Figure10}(b) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(a)), but is missing the higher-frequency detail.
+It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.
 
@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For Parts a), b) and c) of the figure a Mexican hat connectivity kernel was used.
+For Parts A), B) and C) of the figure a Mexican hat connectivity kernel was used.
 For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
@@
 For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
-However, in Parts d), e) and f) of Figure~\ref{fig:Figure8} the kernel support in the estimator differed from the actual data.
+However, in Parts D), E) and F) of Figure~\ref{fig:Figure8} the kernel support in the estimator differed from the actual data.
 In these cases the data was generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
@@
 \caption{{\bf Spatial frequency analysis of the neural field}.
-(\textbf{a}) The average (over time) power in dB of the spatial frequency of the neural field.
-(\textbf{b}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+(\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
+(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
 The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
@@
 The dashed line shows the cut-off frequency (-3 dB point).
-(\textbf{a}) The average (over time) power in dB of the spatial frequency of the observations.
-(\textbf{b}) The spatial frequency response of a one-dimensional model sensor.
+(\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
+(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
 The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-(\textbf{c}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
+(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
 }
@@
 The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
-(\textbf{a}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
-(\textbf{b}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(\textbf{c}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-(\textbf{d}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
+(\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+(\textbf{B}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(\textbf{C}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+(\textbf{D}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
 \label{fig:Figure7}
@@
 \caption{{\bf Examples of the actual and estimated neural fields and the error}.
-(\textbf{a}) The actual field at a single time instant from the full neural field model that was used to generate the data.
-(\textbf{b}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-(\textbf{c}) The absolute error between the true and reconstructed fields.
+(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
+(\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+(\textbf{C}) The absolute error between the true and reconstructed fields.
 The error shows high frequency behaviour.}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
corrected the range of the field
maybe did something to the ds and forgot to commit? Who knows?

--- 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 
-\documentclass[12pt]{iopart} 
+\documentclass[justified]{iopart} 
 \usepackage{iopams}
@@
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this task has been approached from a number of standpoints~\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}.
-
-Perhaps the most accepted estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
+Recently, however, this task has been approached from a number of standpoints.
+
+\dean{Need to add extra references between here}
+
+An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
 Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
+This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatiotemporal neural fields.
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+\dean{and here}
 
@@
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
-This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required for the WC or Amari model.
+This paper extends the linear framework of \cite{Dewar2009,Scerri2009} to the nonlinear case required by the WC model.
 
@@
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition~\cite{Braitenberg1998}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \cite{Braitenberg1998}.
 For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
@@
 \begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, dt'}. 
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, \mathrm{d}t'}. 
 \end{equation}
@@
 \begin{equation}
-	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\, d\mathbf{r}'}, 
+	\label{RateBasedInteractions} g\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left( \mathbf{r}',t \right) \right)\, \mathrm{d}\mathbf{r}'}, 
 \end{equation}
@@
 	f\left( v\left( \mathbf{r}',t' \right)\right)
-	\, d\mathbf{r}'dt'.
+	\, \mathrm{d} \mathbf{r}' \mathrm{d}t'.
 \end{equation}
@@
 	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, \mathrm{d}\mathbf{r}'}.
 \end{equation}
@@
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	\, d\mathbf{r}'} 
+	\, \mathrm{d}\mathbf{r}'} 
 	+ e_t\left(\mathbf{r}\right), 
@@
 	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	\, d\mathbf{r}'} + 
+	\, \mathrm{d}\mathbf{r}'} + 
 	\boldsymbol{\varepsilon}_t, 
@@
 However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more likened to a Gaussian shape~\cite{Jackson1999}.
-Therefore, in this study the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
+Therefore, the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
 \begin{equation}
@@
 To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
-Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
+Rearranging the order of the spatial convolution in~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
 \begin{eqnarray}
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, \textrm{d}\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
 	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
@@
 	\label{StartofReduction}
- 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} &=&
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} &=&
  T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
-&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
-&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
+&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, \textrm{d}\mathbf{r}'\textrm{d}\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
+&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
+\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}. 
 \end{eqnarray}
@@
 \begin{equation}\label{eq:DefGamma}
-	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right) \, d\mathbf{r}}, 
+	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right) \, \textrm{d}\mathbf{r}}, 
 \end{equation}
@@
 	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
-	&\times& d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
+	&\times& \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} \boldsymbol{\theta}  
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}.
 	 % \end{split}
 \end{eqnarray}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the supplementary material.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\Gamma$, is provided in the supplementary material.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
@@
 \begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r}) \, d\mathbf{r}},
+	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r}) \, \textrm{d}\mathbf{r}},
 \end{equation}
 which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the supplementary material for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
-Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
+Substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
 \begin{eqnarray}
-	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
-+ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, d\mathbf{r}}.
+	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, \textrm{d}\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
++ \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, \textrm{d}\mathbf{r}}.
 \end{eqnarray}
@@
 \begin{equation}\label{eq:Wt} 
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, d\mathbf{r}},
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, \textrm{d}\mathbf{r}},
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
-\end{equation}
-Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
+	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, \mathrm{d}\mathbf r' \mathrm{d}\mathbf r\mathbf{\Gamma}^{- \top}.
+\end{equation}
+Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
-	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
+	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, \textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
 \end{equation}
@@
 \begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'. 
+	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, \textrm{d}\mathbf{r}'. 
 \end{equation}
@@
 \begin{equation}\label{eq:QmatrixForSigmapoints}
-	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
+	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, \textrm{d}\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.
 \end{equation}
@@
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-Again, applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
+Again applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
 \begin{equation}\label{eq:BasisFunctionSeparation}
@@
 % Results and Discussion can be combined.
-\section{Results}\label{ResultsSection} In this section, we provide demonstrations of the estimation procedure using the new methods that are described above.
+\section{Results}\label{ResultsSection} In this section, we provide a demonstration of the estimation procedure using the new methods that are described above.
 The full neural field model was used to generate the data for state and parameter estimation.
-All parameters for the model are given in Table~\ref{tab:Parameters}, unless otherwise explicitly stated for particular experiments.
+All parameters for the model are given in Table~\ref{tab:Parameters}.
 Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
@@
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.08~mm.
-This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.
+This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
 
@@
 The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(c).
-This band-limiting effect of the basis function decomposition can be observed when comparing Figure~\ref{fig:Figure4}(a) to Figure~\ref{fig:Figure4}(b).
+The band-limiting effect of the basis function decomposition can be seen when comparing Figure~\ref{fig:Figure4}(a) to Figure~\ref{fig:Figure4}(b).
 
@@
 \label{sec:state_and_param_results}
-Experiments were performed to demonstrate the performance of the state and parameter estimation algorithm.
-The first experiment evaluates the estimation performance using a Monte Carlo approach for a single set of parameters.
-Using this experiment we demonstrate convergence of the algorithm, show the distribution of estimated parameters and the accuracy of the state estimates for a single set of parameters.
-The second experiment evaluates the performance with a selection of different connectivity kernel parameters.
-In addition, results are shown where the support of the connectivity kernels differs between actual data and the estimator.
-The third experiment shows the how the estimation accuracy varies depending on the parameters of the sigmoidal nonlinearity.
+To demonstrate the performance of the state and parameter estimation algorithm several experiments were performed.
+The results of the first experiment demonstrates the estimation performance using a Monte Carlo approach for a single set of parameters.
+The second experiment demonstrates the performance with a selection of different connectivity kernel parameters.
+The third experiment shows the dependance of the estimation accuracy on the parameters of the sigmoidal nonlinearity.
 The final experiment shows the effect of the width of the sensor kernel on the estimation performance.
@@
 Ten iterations of the estimation algorithm were used to ensure the parameters  converged.
-Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after 6 iterations.
+Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.
 
 Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
-The actual parameter values, the mean estimates, corresponding standard deviations and biases are given with the results from the next Section in Table~\ref{tab:MexicanHatKernelResults}.
+The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of 2.78\%), with a small variance in parameter estimates.
+The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of 2.78\%).
 
@@
 The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
-At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range \dean{([-3.29,3.77]~mV)}.
+At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV).
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
@@
 
-To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernel parameters.
+To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernels.
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For Parts a), b) and c) of the figure a Mexican hat connectivity kernel was used.
-For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
-In each case the actual kernel was within the 95~\% confidence of kernel estimate.
-The statistics for the kernel parameters estimates for each of the parameter sets are shown in Table~\ref{tab:MexicanHatKernelResults}.
-
-For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
-However, in Parts d), e) and f) of Figure~\ref{fig:Figure8} the kernel support in the estimator differed from the actual data.
-In these cases the data was generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
-The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples.
-Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates, for the majority of the kernel space until the amplitude is relatively low.
-Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates.
-Importantly, although the reconstructed kernel estimate is in good accord with the actual kernel, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the support of the kernel basis functions are precisely known, the exact meaning of the parameters in isolation is not clear and the net reconstructed kernel should be considered in a practical setting.
+By changing the weights of the connectivity kernel we are effectively changing gain of the system and the range of the field amplitudes.
+Since the sigmoidal nonlinearity is remaining static, we are changing the operating region on the sigmoid.
+Therefore, we expect our estimation accuracy to vary.
+For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
+Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied.
+In all cases the actual kernel fell within the confidence interval of the estimated kernel.
+The kernel in Part a) has the least amount of excitation and the most amount of inhibition.
+Therefore of the three Mexican hat kernels shown, this one will have the least amount of activation.
+The result is an overestimate of the central excitatory region of the kernel.
+Conversely, in Part c) of the figure the actual kernel has the most amount of excitation and the least amount of inhibition.
+Therefore
+
+The mean kernel estimate for Part b) shows very good accordance with the actual kernel.
+In the other Parts a) and c) there is an over estimate and an underestimate of the kernel, respectively.
+These bias are a result
+
+\parham{this bit should change as well:} 
+For parts b) and c) the figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel.
+The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(c).
 
@@
 
-Figure~\ref{fig:Figure11} demonstrates the affect of the sigmoid parameters on the estimation accuracy.
-The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
-The other model parameters remained fixed and where set according the Table~\ref{tab:Parameters}.
-
-% The size of the squares in the figure show the magnitude of the log of the error.
+Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) of the connectivity kernel for various parameters of the sigmoid varying the slope, $\varsigma$, and the threshold, $v_0$, whilst the other parameters remain fixed.
+The kernel and time constant parameters used in this experiment were the one that gave the best results from the previous experiment.
+The size of the squares in the figure show the magnitude of the log of the error.
 The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$).
-The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
-From the figure it can be seen that the estimation accuracy is inter-related to the properties of the sigmoid function.
+The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations.
+From the figure it can be seen that the estimation accuracy depends on the characteristics of the sigmoid function.
 When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
-However, as the slope is increased or the threshold is increased, more information is being cut off or attenuated by the activation function.
-This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
+However as the slope is increased or the cut-off is increased, more information is being cut off by the activation function.
+This is illustrated in figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
 This appears to have a detrimental effect on the estimation accuracy.
@@
 \subsubsection{Results for Varying the Sensor Kernel Width}
-The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter.
-Figure~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various connectivity kernel widths.
-The figure shows that there is error a desirable connectivity kernel width range.
-As the the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
-When the observation kernel is to narrow, a small amount of aliasing appears to be increasing the estimation error.
-When the observation kernel width is initially increased the error drops.
-As expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
 
@@
 \subsection{Implications for Experiment Design}
-As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values and the true kernel lies within the 95~\% confidence intervals of the estimates.
+As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation \parham{for the connectivity kernel parameters}, where the mean parameter estimates are in good agreement with the actual values.
 The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
@@
 The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
-As pointed out in numerous publications by Freeman and colleagues (see \cite{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
-Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial properties can be recovered.
+Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing.
 In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
@@
 
-The current study builds on Schiff and Sauer's approach~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
+The current study builds on Schiff and Sauer's approach ~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in Methods section.
@@
 
-% \begin{figure}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/OperatingRegions.pdf}
-% \end{center}
-% \caption{{\bf Operating Regions along the sigmoid}. The top graph is from the full model and the lower is from the reduced model.}
-% \label{fig:OperatingRegions}
-% \end{figure}
-
-% \begin{figure*}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/Figure11.pdf}
-% \end{center}
-% \caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure11.pdf}
+\end{center}
+\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
 Log of the RMSE of the kernel for different values of $\nu_{cm}$ and $\Delta_y$.
 Mean kernel estimates are obtained over 50 realisations in each case.}
-% \label{fig:Figure11}
-% \end{figure*}
+\label{fig:Figure11}
+\end{figure*}
 
@@
 \begin{center}
-\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
-\end{center}
-\caption{{\bf RMSE of different kernel estimates}.
+\includegraphics{./Graph/pdf/Figure12.pdf}
+\end{center}
+\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
 Log of the RMSE of the kernel for different values of firing threshold, $v_0$ and the slope of the sigmoid, $\varsigma$.
 Mean kernel estimates are obtained over 50 realisations in each case.
-White spaces indicate cases where the kernel can not be estimated due to numerical problems.}
+red crosses indicate cases where the kernel can not be estimated due to numerical issues.}
 \label{fig:Figure12}
@@
 
-% \begin{figure*}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/Figure13.pdf}
-% \end{center}
-% \caption{{\bf RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$.
-Mean kernel estimates are obtained over 50 realisations in each case.}
-% \label{fig:Figure13}
-% \end{figure*}
-
 \begin{figure*}[!ht]
 \begin{center}
-\includegraphics{./Graph/pdf/RMSESensor.pdf}
+\includegraphics{./Graph/pdf/Figure13.pdf}
 \end{center}
 \caption{{\bf RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$.
+RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$.
 Mean kernel estimates are obtained over 50 realisations in each case.}
@@
 \end{figure*}
+
 \section*{Tables}
@@
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
-	100 &-80 &5
+	10 &-8 &0.5
 	\end{array}
@@
 
-% \tiny{\begin{tabular}{lcccccccccccc}
-% Experiment&\multicolumn{4}{c}{I}&\multicolumn{4}{c}{II}&\multicolumn{4}{c}{III}\\
-%  Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
-% \hline\hline
-% Actual Value&$90$&$-80$&$5$&$0.9$&$100$&$-80$&$5$&$0.9$&$110$&$-80$&$5$&$0.9$\\
-% Mean Estimate&$103.86$&$-89.05$&$5.23$&$0.923$& $101.75$&$-81.00$&$4.76$&$0.924$&$98.90 $&$-73.13$&$4.37$&$0.925$\\
-% Std. Dev.&$23.14$&$16.57$&$0.74$&$0.003$ & $21.30$&$14.82$&$0.65$&$0.003$&$16.48$& $11.72$&$0.54$&$0.003$\\
-% Bias (\%)& $15.4$&$11.31$&$4.6$ &$2.56$ &$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
-% \end{tabular}\label{tab:MexicanHatKernelResults}}
-
-\begin{table}[!ht]
-	\caption{
-	\bf{Results from varying the Mexican hat connectivity kernel parameters}}
-\begin{tabular}{c|ccccc}
-	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
-	I &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
-	& $\theta_1$ & -80 & -89.05 & 16.57 & 11.31 \\
-	& $\theta_2$ & 5 & 5.23 & 0.74 & 4.6 \\
-	& $\xi$ & 0.9 & 0.923 & 0.003 & 2.56 \\ \hline
-
-	II & $\theta_0$ & $100$ & 101.75 & $21.30$ & $1.75$ \\
-	& $\theta_1$ & -80 & -81.00 & $14.82$ & $1.25$ \\
-	& $\theta_2$ & 5 & $4.76$ & $0.65$ & $4.8$ \\
-	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
-
-	III & $\theta_0$ & $110$ & $98.90$ & $16.48$ & $10.1$ \\
-	& $\theta_1$ & -80 & $-73.13$ & $11.72$ & $ 8.58$ \\
-	& $\theta_2$ & 5 & $4.37$ & $0.54$ & $12.6$ \\
-	& $\xi$ & 0.9 & $0.925$ & $0.003$ & $2.78$ \\ \hline
-\end{tabular}\label{tab:MexicanHatKernelResults}
-\end{table}
-
-% \tiny{\begin{tabular}{lcccccccccccc}
-% Experiment&\multicolumn{4}{c}{IV}&\multicolumn{4}{c}{V}&\multicolumn{4}{c}{VI}\\
-%  Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
-% \hline\hline
-% Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
-% Mean Estimate&$35.68$&$-18.16$&$0.81$&$0.923$&   $40.43$&$-12.01$&$ 0.35$&$0.924$&        $61.46$&$-15.03$&$0.27$&$0.924$\\
-% Std. Dev.&$16.72$&$11.77$&$0.53$&$0.002$&		$11.47$&$7.8$&$0.36$&$0.003$&	$11.51$&$7.56$&$0.29$&$0.003$\\
-% Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
-% \end{tabular}\label{tab:GaussianKernelResults}}
-
-\begin{table}[!ht]
-	\caption{
-	\bf{Results from varying the Gaussian connectivity kernel parameter}}
-\begin{tabular}{c|ccccc}
-	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
-	IV &$\theta_0$ & $15$ & $35.68$ & $16.72$ & $137.87$ \\
-	& $\theta_1$ & 0 & $-18.16$ & $11.77$ & - \\
-	& $\theta_2$ & 0 & $0.81$ & $0.53$ & - \\
-	& $\xi$ & 0.9 & 0.923 & $0.002$ & 2.56 \\ \hline
-
-	V & $\theta_0$ & $30$ & $40.43$ & $11.47$ & $34.77$ \\
-	& $\theta_1$ & 0 & $-12.01$ & $7.8$ & - \\
-	& $\theta_2$ & 0 & 0.35 & $0.36$ & - \\
-	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
-
-	VI & $\theta_0$ & $50$ & $61.46$ & $11.51$ & $22.92$ \\
-	& $\theta_1$ & 0 & $-15.03$ & $7.56$ & - \\
-	& $\theta_2$ & 0 & $0.27$ & $0.29$ & - \\
-	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
-\end{tabular}\label{tab:GaussianKernelResults}
-\end{table}
+\small{\begin{tabular}{lccccccccc}
+Experiment&\multicolumn{3}{c}{I}&\multicolumn{3}{c}{II}&\multicolumn{3}{c}{III}\\
+ Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
+\hline\hline
+Actual Value&$90$&$-80$&$5$&$100$&$-80$&$5$&$110$&$-80$&$5$\\
+Mean Estimate&$103.86$&$-89.05$&$5.23$&$101.75$&$-81.00$&$4.76$&$98.90 $&$-73.13$&$4.37$\\
+Std. Dev.&$23.14$&$16.57$&$0.74$&$21.30$&$14.82$&$0.65$&$16.48$& $11.72$&$0.54$\\
+Bias (\%)& $15.4$&$11.31$&$4.6$&$1.75$&$1.25$&$4.8$&$10.1$&$ 8.58$&$12.6$  \\
+\end{tabular}}
+
+\small{\begin{tabular}{lccccccccc}
+Experiment&\multicolumn{3}{c}{IV}&\multicolumn{3}{c}{V}&\multicolumn{3}{c}{VI}\\
+ Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
+\hline\hline
+Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
+Mean Estimate&$35.68$&$-18.16$&$0.81$&$40.43$&$-12.01$&$ 0.35$&$61.46$&$-15.03$&$0.27$\\
+Std. Dev.&$16.72$&$11.77$&$0.53$&$11.47$&$7.8$&$0.36$&$11.51$&$7.56$&$0.29$\\
+Bias (\%)&$137.87$&$-$&$-$&$34.77$&$-$&$-$&$22.92$&$-$&$-$\\
+\end{tabular}}
 

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
updated figures from the parameter search experiments

--- 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
-At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range \dean{([-3.29,3.77]~mV)}.
+At each time point, the error is consistently around 0.5~mV, which is approximately 10.73~\% of the field voltage range ([-2.20,2.46]~mV).
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
@@
 \caption{{\bf RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$.
+RMSE of the kernel for different values of sensor width, $\sigma_m$, distance between adjacent sensors is $\Delta_y=1.5$.
 Mean kernel estimates are obtained over 50 realisations in each case.}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
started making changes suggested by David

@@
 The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
-To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters.
-To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite-dimensional state-space model.
+To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors so a comparison can be made between estimated and true parameters.
+To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model using a basis function decomposition to form a finite-dimensional state-space model.
 Spatial frequency analysis methods are introduced that systematically specify the basis function configuration required to capture the dominant characteristics of the neural field.
@@
 This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
-The paper proceeds by first deriving the continuum neural field equations.
+The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
 Then a finite-dimensional neural field model is derived.
@@
 \end{equation}
-where $\textrm{D}=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $\textrm{D}=d/dt + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}
@@
 \end{equation}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,N$ indexes the electrodes and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denoting the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
-
-When considering the measurement of a point source in a homogeneous field measured by a point sensor the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in amplitude with increasing distance between the source and sensor~\cite{Jackson1999}.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,N$ indexes the electrodes and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+
+When considering the measurement of a point source in a homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in amplitude with increasing distance between the source and sensor~\cite{Jackson1999}.
 However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more likened to a Gaussian shape~\cite{Jackson1999}.
@@
 \end{equation}
-where $\sigma_m$ sets the kernel width. An example of measured observation kernel is shown in the supplementary material.
+where $\sigma_m$ sets the kernel width. An example of an experimentally measured observation kernel is shown in the supplementary material.
 
@@
 \end{eqnarray}
-Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain $\Omega$ to get 
+Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
 \begin{eqnarray}
@@
 \end{eqnarray}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the supplementary material.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$ is provided in the supplementary material.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
@@
 % Results and Discussion can be combined.
-\section{Results}\label{ResultsSection} In this section, we provide demonstrations of the estimation procedure using the new methods that are described above.
+\section{Results}\label{ResultsSection} We now provide demonstrations of the estimation procedure using the new methods that are described above.
 The full neural field model was used to generate the data for state and parameter estimation.
 All parameters for the model are given in Table~\ref{tab:Parameters}, unless otherwise explicitly stated for particular experiments.
-Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
-This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation.
+Note that the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology.
+This is because the temporal aspects scale with the sampling rate and the length of the times series, and the spatial aspects scale with the size of the neural field and the spatial step size used for numerical simulation.
 When generating the simulated data, we assumed free boundary conditions for the neural field.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
edits from Davids markup to spatial freq section

@@
 When generating the simulated data, we assumed free boundary conditions for the neural field.
-An example of the simulated field can be seen in Figure~\ref{fig:Figure3}(A).
+An example of the simulated field at a single point in time can be seen in Figure~\ref{fig:Figure3}(A).
 Figure~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
@@
 The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstruct neural field from the basis function decomposition.
+Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
@@
 The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(A).
-The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point).
+The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point).
 The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
@@
 Experiments were performed to demonstrate the performance of the state and parameter estimation algorithm.
-The first experiment evaluates the estimation performance using a Monte Carlo approach for a single set of parameters.
+The first experiment evaluated the estimation performance using a Monte Carlo approach for a single set of parameters.
 Using this experiment we demonstrate convergence of the algorithm, show the distribution of estimated parameters and the accuracy of the state estimates for a single set of parameters.
-The second experiment evaluates the performance with a selection of different connectivity kernel parameters.
+The second experiment evaluated the performance with a selection of different connectivity kernel parameters.
 In addition, results are shown where the support of the connectivity kernels differs between actual data and the estimator.
-The third experiment shows the how the estimation accuracy varies depending on the parameters of the sigmoidal nonlinearity.
+The third experiment shows how the estimation accuracy depends on the parameters of the sigmoidal nonlinearity.
 The final experiment shows the effect of the width of the sensor kernel on the estimation performance.
 
-\subsubsection{Monte Carlo Simulation with Fixed Parameters}
-A Monte Carlo approach was employed where 150 realisations of the data were generated.
+\subsubsection{Experiment I: Monte Carlo Simulation with Fixed Parameters}
+A Monte Carlo approach was employed where \dean{is it 50 or 150, because of the new experiment?} 150 realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
-Ten iterations of the estimation algorithm were used to ensure the parameters converged.
-Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after 6 iterations.
-
-Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
-The actual parameter values, the mean estimates, corresponding standard deviations and biases are given with the results from the next Section in Table~\ref{tab:MexicanHatKernelResults}.
+Ten iterations of the estimation algorithm were used to ensure that the parameters converged.
+Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the parameters converged, with the changes in the parameter errors (between iterations) falling to less than $10^{-4}$ after 6 iterations.
+
+Histograms of the parameter estimates obtained over the \dean{50 or 150} realisations are shown in Figure~\ref{fig:Figure7}.
+The actual parameter values, the mean parameter estimates, corresponding standard deviations and biases are given in Table~\ref{tab:MexicanHatKernelResults} \dean{need to switch the graphs in Figure 10 so that the first one uses these parameters}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
@@
 	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
-	I &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
+	I and II-A &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
 	& $\theta_1$ & -80 & -89.05 & 16.57 & 11.31 \\
@@
 
-	II & $\theta_0$ & $100$ & 101.75 & $21.30$ & $1.75$ \\
+	II-B & $\theta_0$ & $100$ & 101.75 & $21.30$ & $1.75$ \\
 	& $\theta_1$ & -80 & -81.00 & $14.82$ & $1.25$ \\
@@
 
-	III & $\theta_0$ & $110$ & $98.90$ & $16.48$ & $10.1$ \\
+	II-C & $\theta_0$ & $110$ & $98.90$ & $16.48$ & $10.1$ \\
 	& $\theta_1$ & -80 & $-73.13$ & $11.72$ & $ 8.58$ \\
@@
 	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
-	IV &$\theta_0$ & $15$ & $35.68$ & $16.72$ & $137.87$ \\
+	II-D &$\theta_0$ & $15$ & $35.68$ & $16.72$ & $137.87$ \\
 	& $\theta_1$ & 0 & $-18.16$ & $11.77$ & - \\
@@
 
-	V & $\theta_0$ & $30$ & $40.43$ & $11.47$ & $34.77$ \\
+ 	II-E& $\theta_0$ & $30$ & $40.43$ & $11.47$ & $34.77$ \\
 	& $\theta_1$ & 0 & $-12.01$ & $7.8$ & - \\
@@
 
-	VI & $\theta_0$ & $50$ & $61.46$ & $11.51$ & $22.92$ \\
+	II-F & $\theta_0$ & $50$ & $61.46$ & $11.51$ & $22.92$ \\
 	& $\theta_1$ & 0 & $-15.03$ & $7.56$ & - \\

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
editting Monte Carlo results bit

@@
 \subsubsection{Experiment I: Monte Carlo Simulation with Fixed Parameters}
-A Monte Carlo approach was employed where \dean{is it 50 or 150, because of the new experiment?} 150 realisations of the data were generated.
+A Monte Carlo approach was employed where \dean{is it 50 or 150 with the new experiments?} 150 realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
@@
 Ten iterations of the estimation algorithm were used to ensure that the parameters converged.
-Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the parameters converged, with the changes in the parameter errors (between iterations) falling to less than $10^{-4}$ after 6 iterations.
+Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the parameters converged, with the changes in the parameter errors (between consecutive iterations) falling to less than $10^{-4}$ after 6 iterations.
 
 Histograms of the parameter estimates obtained over the \dean{50 or 150} realisations are shown in Figure~\ref{fig:Figure7}.
-The actual parameter values, the mean parameter estimates, corresponding standard deviations and biases are given in Table~\ref{tab:MexicanHatKernelResults} \dean{need to switch the graphs in Figure 10 so that the first one uses these parameters}.
+\dean{Can we show the distribution of between 0.85 and 0.95 and put it last in the sequence?} In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
+The actual parameter values, the mean parameter estimates, corresponding standard deviations and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults} with results from Experiment II.
+\dean{We need to switch the graphs in Figure 10 so that the first one uses these parameters}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of 2.78\%), with a small variance in parameter estimates.
+The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.78\%$), with a small variance in parameter estimates.
 
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
-At each time point, the error is consistently around 0.5~mV, which is approximately 10.73~\% of the field voltage range ([-2.20,2.46]~mV).
+The MRMSE of the field estimates over time for \dean{150} realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
+At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
@@
 \end{center}
-\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realisations.
+\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over \dean{150?} realisations.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
@@
 \end{center}
-\caption{{\bf Histograms of the parameter estimates over 150 realisations}.
-The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
+\caption{{\bf Histograms of the parameter estimates over \dean{150?} realisations}.
+\dean{David suggested that we switch the order of the graphs here so $\xi$ is the last one.} The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
 (\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
editting results, up to experiment III

@@
 \dean{Can we show the distribution of between 0.85 and 0.95 and put it last in the sequence?} In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
-The actual parameter values, the mean parameter estimates, corresponding standard deviations and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults} with results from Experiment II.
+The actual parameter values, the mean parameter estimates, corresponding standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults} with results from Experiment II.
 \dean{We need to switch the graphs in Figure 10 so that the first one uses these parameters}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
-The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.78\%$), with a small variance in parameter estimates.
+For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters.
+However, the time constant parameter, $\xi$, is outside the estimate distribution \dean{(with bias of $2.78\%$) - we need to check this!}, with a small variance in parameter estimates.
 
@@
 The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
-The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.
-
-\subsubsection{Results for Different Connectivity Kernel Parameters}
+The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields.
+It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail, which can be see in the error shown in Figure~\ref{fig:Figure10}(C)).
+
+\subsubsection{Experiment II: Results for Different Connectivity Kernel Parameters}
 
@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For Parts A), B) and C) of the figure a Mexican hat connectivity kernel was used.
-For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
-In each case the actual kernel was within the 95~\% confidence of kernel estimate.
-The statistics for the kernel parameters estimates for each of the parameter sets are shown in Table~\ref{tab:MexicanHatKernelResults}.
+For Figure~\ref{fig:Figure8}(A-C) Mexican hat connectivity kernels were used.
+For each subset of parameters, the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
+In each case, the actual kernel was within the 95~\% confidence interval of the kernel estimate.
+The statistics for the kernel parameter estimates for each of the parameter sets are shown in Table~\ref{tab:MexicanHatKernelResults}.
 
 For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
-However, in Parts D), E) and F) of Figure~\ref{fig:Figure8} the kernel support in the estimator differed from the actual data.
-In these cases the data was generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
+However, in Figure~\ref{fig:Figure8}(D-F) the kernel support in the estimator differed from the actual data.
+In these cases the data sets were generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
 The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples.
-Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates, for the majority of the kernel space until the amplitude is relatively low.
+Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates for the majority of the kernel space until the amplitude is relatively low.
 Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates.
-Importantly, although the reconstructed kernel estimate is in good accord with the actual kernel, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the support of the kernel basis functions are precisely known, the exact meaning of the parameters in isolation is not clear and the net reconstructed kernel should be considered in a practical setting.
-
-\subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
+Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
+This result demonstrates that unless the support of the kernel is precisely known, the exact meaning of the parameters in isolation is not clear and the net shape of the reconstructed kernel is important.
+
+\subsubsection{Experiment III: Results for Varying the Parameters of the Sigmoidal Activation Function}
 

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
up to experiment iV of results for Davids edits

@@
 
-Figure~\ref{fig:Figure11} demonstrates the affect of the sigmoid parameters on the estimation accuracy.
+Figure~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy.
 The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
-The other model parameters remained fixed and where set according the Table~\ref{tab:Parameters}.
+The other model parameters remained fixed and were set according the Table~\ref{tab:Parameters}.
 
@@
 The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
-From the figure it can be seen that the estimation accuracy is inter-related to the properties of the sigmoid function.
-When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
-However, as the slope is increased or the threshold is increased, more information is being cut off or attenuated by the activation function.
-This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted.
+From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends the parameters of the sigmoid function.
+\dean{This next bit is CRAP (help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
+However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function.
+This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted.
 This appears to have a detrimental effect on the estimation accuracy.
 
-\subsubsection{Results for Varying the Sensor Kernel Width}
+\subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
 The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter.
@@
 \caption{{\bf RMSE of different kernel estimates}.
-Log of the RMSE of the kernel for different values of firing threshold, $v_0$ and the slope of the sigmoid, $\varsigma$.
+Log of the RMSE of the kernel for different values of firing threshold, $v_0$, and the slope of the sigmoid, $\varsigma$.
 Mean kernel estimates are obtained over 50 realisations in each case.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
up to discussion for Davids edits

@@
 From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends the parameters of the sigmoid function.
-\dean{This next bit is CRAP (help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
+\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
 However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function.
@@
 \subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
-The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter.
-Figure~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various connectivity kernel widths.
-The figure shows that there is error a desirable connectivity kernel width range.
-As the the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
-When the observation kernel is to narrow, a small amount of aliasing appears to be increasing the estimation error.
-When the observation kernel width is initially increased the error drops.
-As expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
+The accuracy of the estimation algorithm was tested for different observation kernels by varying the width parameter, $\sigma_m$.
+Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
+As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter and when the observation kernel is to narrow, high spatial frequency information is present but not adequately sampled by the observation function.
+Therefore, a small amount of aliasing occurs which results in the estimation error.
+When the observation kernel width is increased, the high spatial frequency information is filtered by the observation kernel and the error decreases.
+However, as expected, when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
 
@@
 
-\subsection{Implications for Experiment Design}
+\subsection{Implications for Experimental Design}
 As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values and the true kernel lies within the 95~\% confidence intervals of the estimates.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
edits from David to discussion

@@
 \section{Discussion}\label{DiscussionSection}
-This paper has presented a framework for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-The mathematical formulation that we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation that allows us to perform inference efficiently.
+We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.
 

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
more edits from David to discussion

@@
 \subsection{Implications for Experimental Design}
-As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values and the true kernel lies within the 95~\% confidence intervals of the estimates.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.
+As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
+The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
 To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
-Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease.
-Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
-By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
-
-The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
+Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease.
+Even when using a known input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
+By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+
+The frequency analysis specifies the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
 As pointed out in numerous publications by Freeman and colleagues (see \cite{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
@@
 \subsection{Computational Complexity}
-The closest competitor to our `grey-box' integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
-Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991} and partial directed coherence~\cite{Sameshima1999}.
+The closest competitor to our `grey-box' integro-difference equation approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
+Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}.
 A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
-Furthermore, by using the neural field equations as a parametric form of a model, the parameters have physical meaning and, therefore, can be clinically relevant.
+Furthermore, by using the neural field equations as a parametric form of a model, the estimated quantities have physical meaning and, therefore, can be clinically relevant.
 An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
 
-Previous work from Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
-Within their framework, each discrete spatial location forms an element of the state vector to be estimated with the UKF.
-A limitation of this framework is that an increase in spatial resolution and/or the physical size of the neural field will result in an increased state dimension.
-
-This, in turn, will lead to increases in uncertainty of the estimates.
+Previous work by Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
+Within their framework, each discrete spatial location formed an element of the state vector to be estimated with the UKF.
+A limitation of this framework was that an increase in spatial resolution and/or the physical size of the neural field resulted in an increased state dimension.
+This, in turn, leads to increases in uncertainty in the state estimates.
 In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
@@
 The current study builds on Schiff and Sauer's approach~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
-Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in Methods section.
+Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in the Methods section.
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
@@
 
-That the connectivity kernel is isotropic means the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions.
+The isotropy of the connectivity kernel means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
@@
 
-% Do NOT remove this, even if you are not including acknowledgments
 \section{Acknowledgments}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
added to discussion

@@
 
-\section{Future Work}
-
 \subsection{Patient-Specific Modelling}
@@
 
+\section{Conclusion}
+This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology.
+\dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...
+
 \section{Acknowledgments}
@@
 Matthias Hennig for useful discussions and feedback.
+This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
+Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship for supporting this research.
 Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed the bib file

@@
 % 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 & mV$^{-1}$\\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 \cite{Wendling2005} & mV$^{-1}$\\
 	$v_0$ & firing threshold & 1.8 \cite{Marreiros2008}& mV  \\

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
Minor changes to sections 1 and 2

@@
 
-Perhaps the most accepted estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
+Perhaps the most accepted estimation framework for neural mass models is dynamical causal modelling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
 Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}.
-This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
+This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
 This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
@@
 To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
-The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.
+The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from patient specific data.
 
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see the supplementary material for derivation) giving 
+To arrive at the Integro-Difference Equation (IDE) form of the model, we discretise time using a first-order Euler method (see the supplementary material for derivation) giving 
 \begin{equation}
@@
 When considering the measurement of a point source in a homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in amplitude with increasing distance between the source and sensor~\cite{Jackson1999}.
-However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more likened to a Gaussian shape~\cite{Jackson1999}.
+However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
 Therefore, in this study the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By assuming a Gaussian isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
+By assuming an isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
-Such sensors, therefore, can only sense the field up to a known spatial bandwidth, denoted by $\boldsymbol{\nu}_{cy}$.
+Such sensors limit the spatial bandwidth of the observation to a value  denoted by $\boldsymbol{\nu}_{cy}$.
 Aliasing can then be avoided by positioning the sensors according to equation~\ref{eq:MinimumSensorDistance}, replacing $\boldsymbol{\nu}_c$ with $\boldsymbol{\nu}_{cy}$.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
+This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
changed figures and numbers in the text

@@
 \subsubsection{Experiment I: Monte Carlo Simulation with Fixed Parameters}
-A Monte Carlo approach was employed where \dean{is it 50 or 150 with the new experiments?} 150 realisations of the data were generated.
+A Monte Carlo approach was employed where 150 realisations of the data were generated.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
@@
 
-Histograms of the parameter estimates obtained over the \dean{50 or 150} realisations are shown in Figure~\ref{fig:Figure7}.
-\dean{Can we show the distribution of between 0.85 and 0.95 and put it last in the sequence?} In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
+Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
+In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
 The actual parameter values, the mean parameter estimates, corresponding standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults} with results from Experiment II.
-\dean{We need to switch the graphs in Figure 10 so that the first one uses these parameters}.
+\dean{We need to switch the graphs in Figure 10 so that the first one uses these parameters} \parham{it's in ascending order for $\theta_0$ for both rows}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
 For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters.
-However, the time constant parameter, $\xi$, is outside the estimate distribution \dean{(with bias of $2.78\%$) - we need to check this!}, with a small variance in parameter estimates.
+However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
 
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for \dean{150} realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
@@
 \end{center}
-\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over \dean{150?} realisations.
+\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realisations.
 All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
@@
 \end{center}
-\caption{{\bf Histograms of the parameter estimates over \dean{150?} realisations}.
-\dean{David suggested that we switch the order of the graphs here so $\xi$ is the last one.} The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
-(\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
-(\textbf{B}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(\textbf{C}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-(\textbf{D}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
+\caption{{\bf Histograms of the parameter estimates over 150 realisations}.
+The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
+(\textbf{A}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(\textbf{B}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+(\textbf{C}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.
+(\textbf{D}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.}
 \label{fig:Figure7}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction
changed figure 13
generalise the model for non isotropic case

@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By assuming an isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
+\parham{By exploiting the isotropy of the connectivity basis functions, the kernel basis functions can be written as
+$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.} By assuming an isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$ is provided in the supplementary material.
-Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
+Equation~\ref{eq:ReducedForm} \parham{can be simplified by exploiting the isotropy of the kernel  basis functions used to represent the kernel , and hence,
+\begin{equation}
+	\psi_i (\mathbf{r}-\mathbf{r}') = \psi_i (2c_i+\mathbf{r}'-\mathbf{r}).
+\end{equation}
+where $c_i$ is the center of the $i^{th}$ basis function of the kernel decomposition. To make the simplification, we define
+\begin{equation}\label{eq:DefPsi}
+	\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}  \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2c_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+\end{equation}
+where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the supplementary material for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.}
+
+can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
+
 \begin{equation}
@@
 The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
-From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends the parameters of the sigmoid function.
+From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
 \dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
@@
 \begin{center}
-\includegraphics{./Graph/pdf/RMSESensor.pdf}
+\includegraphics{./Graph/pdf/Figure13.pdf}
 \end{center}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
Some comments

@@
 
-In this paper, we demonstrate for the first time how intracortical connectivity can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
+In this paper, we demonstrate for the first time \ken{Is it really the first time?} how intracortical connectivity can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
@@
 This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
-The field decomposition is described by
+The field decomposition is described by \ken{$\phi$ can't be a scalar and a vector}
 \begin{equation}
@@
 To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
-Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
+\ken{Is this really the reason?} Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
 \begin{eqnarray}
@@
 \end{equation}
-Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
+Under the assumption that the basis function decomposition is accurate \ken{Do we really want to say this?}, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
Some more comments

@@
 \end{small}
-Following this, the LS parameter estimates, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates \ken{some reference for this result}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
-From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.08~mm.
+From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm.
 This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.
@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
-Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+\ken{revise} Using an oversampling parameter of $\rho_{\phi}=1$, the maximum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
 
-Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm.
+Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$.
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
started to add mikes edit

--- 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \subsection{Derivation of the Integro-Difference Equation Representation}
-The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-Table~\ref{tab:Notation} provides a description of the notation used in this study.
+The combination of modelling techniques in this paper leads to a large amount of notation so a reference of the symbols used is provided in Table~\ref{tab:Notation}.
+The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t$ and position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
 The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
 \begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, dt'}. 
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r}',t'} \right) \, dt'}. 
 \end{equation}
@@
 
-The mapping between the membrane voltage and the electrophysiological data is modelled using the observation function that incorporates sensors with a spatial extent by
+The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf y_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
 \begin{equation}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
Yet more comments
minor corrections

@@
 The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
-The other model parameters remained fixed and were set according the Table~\ref{tab:Parameters}.
+The other model parameters remained fixed and were set according to the Table~\ref{tab:Parameters}.
 
@@
 
-The isotropy of the connectivity kernel means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions.
+The isotropy of the connectivity kernel basis functions means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
@@
 (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-(\textbf{C}) The absolute error between the true and reconstructed fields.
+(\textbf{C}) The error between the true and reconstructed fields.
 The error shows high frequency behaviour.}

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
edits from meeting

--- 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
-As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter and when the observation kernel is to narrow, high spatial frequency information is present but not adequately sampled by the observation function.
+As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter and when the observation kernel is too narrow, high spatial frequency information is present but not adequately sampled by the observation function.
 Therefore, a small amount of aliasing occurs which results in the estimation error.

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex

--- 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
+\ken{say why ...
+high freq?}
 

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
edits following meeting with Ken and Parham 17112010

@@
 
-In this paper, we demonstrate for the first time \ken{Is it really the first time?} how intracortical connectivity can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
+In this paper, we demonstrate for the first time \ken{Is it really the first time?} how intracortical connectivity kernel can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
@@
 An example of the Mexican hat connectivity kernel used in this paper is shown in Figure~\ref{fig:Figure1}.
-To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
+In an attempt model longer range connectivity, To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from patient specific data.
@@
 
-When considering the measurement of a point source in a homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in amplitude with increasing distance between the source and sensor~\cite{Jackson1999}.
+When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor~\cite{Jackson1999}.
 However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
+An experiment support this was performed and the results are shown in \dean{Appendix?}.
 Therefore, in this study the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
@@
 \end{equation}
-where $\sigma_m$ sets the kernel width. An example of an experimentally measured observation kernel is shown in the supplementary material.
+where $\sigma_m$ sets the kernel width.
 
@@
 	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
-\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
-\end{equation}
-An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.
+\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}, 
+\end{equation}
+where $\sigma_{phi}$ is the basis function width parameter. An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.
 
@@
 However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
+We attribute this small bias to the disparity between the actual field and the smoother estimated field from the decomposition.
 \ken{say why ...

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
added more edits from the meeting

@@
 
-In this paper, we demonstrate for the first time \ken{Is it really the first time?} how intracortical connectivity kernel can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
+In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
@@
 \begin{equation}
-	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r}',t'} \right) \, dt'}. 
+	\label{SpikesToPotential} v\left( {\mathbf{r},t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)g\left( {\mathbf{r},t'} \right) \, dt'}. 
 \end{equation}
@@
 An example of the Mexican hat connectivity kernel used in this paper is shown in Figure~\ref{fig:Figure1}.
-In an attempt model longer range connectivity, To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation.
+In an attempt model longer range connectivity, To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
 The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from patient specific data.
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-\parham{By exploiting the isotropy of the connectivity basis functions, the kernel basis functions can be written as
-$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.} By assuming an isotropic connectivity structure, the kernel basis functions can be written as $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
+By exploiting the isotropy of the connectivity basis functions, they can be written as
+$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
 We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
@@
 Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition.
-To demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
-\ken{Is this really the reason?} Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
+In order to model larger areas of cortex and to demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
+Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
 \begin{eqnarray}
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$ is provided in the supplementary material.
-Equation~\ref{eq:ReducedForm} \parham{can be simplified by exploiting the isotropy of the kernel  basis functions used to represent the kernel , and hence,
-\begin{equation}
-	\psi_i (\mathbf{r}-\mathbf{r}') = \psi_i (2c_i+\mathbf{r}'-\mathbf{r}).
-\end{equation}
-where $c_i$ is the center of the $i^{th}$ basis function of the kernel decomposition. To make the simplification, we define
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
+\begin{equation}
+	\psi_i (\mathbf{r}-\mathbf{r}') = \psi_i (2c_i+\mathbf{r}'-\mathbf{r})
+\end{equation}
+and $c_i$ is the center of the $i^{th}$ basis function of the kernel decomposition. To make the simplification we define
 \begin{equation}\label{eq:DefPsi}
@@
 \end{equation}
-where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the supplementary material for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.}
-
-can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where
-
-\begin{equation}
-	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
-\end{equation}
-To make the simplification, we define
-\begin{equation}\label{eq:DefPsi}
-	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r}) \, d\mathbf{r}},
-\end{equation}
-which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the supplementary material for analytic convolution of two Gaussians), where $L$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a constant $L \times n_{\theta}$ matrix, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+This matrix is defined analytically (see the supplementary (\dean{Appendix}) material for analytic convolution of two Gaussians).
 Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
@@
 \end{eqnarray}
-This substitution exploits the isotropy of the connectivity kernel basis functions, allowing us to swap the convolution in equation~\ref{reduced continuous model}, which would be computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which can be calculated analytically.
+This substitution allows us to swap the convolution in equation~\ref{reduced continuous model}, which would be computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is calculated analytically.
 This is of great importance as it lowers the computational demands of the estimation algorithm and provides a dramatic increase in estimation speed.
@@
 \end{equation}
-which is a zero mean normally distributed white noise process with covariance (see the supplementary material for the derivation)
+which is a zero mean normally distributed white noise process with covariance (see the supplementary material \dean{(Appendix)} for the derivation)
 \begin{equation}
@@
 \end{equation}
-Under the assumption that the basis function decomposition is accurate \ken{Do we really want to say this?}, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
+The observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation}
@@
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
-\ken{revise} Using an oversampling parameter of $\rho_{\phi}=1$, the maximum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
+
+\ken{revise}
+
+\dean{-------new bit start ------------}
+
+Due to restrictions imposed by the computationally demanding nature of the algorithm we chose to use a $9\times9$ grid of Gaussian basis functions to decompose the field, which resulted in 81 states.
+Given the spatial domain, this yielded a basis function separation of $\Delta_{\phi}=2.5$~mm.
+The basis function width parameter was chosen such that a smooth representation of the field could be achieved with this arrangement, where $\sigma_{\phi}^2=2.5$.
+Given the basis function width, the decomposition is able to represent the field up to the spatial cutoff frequency of $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
+The result of the band-limiting effect in the field reconstruction can be observed when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
+Given the spatial cutoff frequency of the basis functions and the basis function separation the oversampling parameter $\rho_{\phi}\approx 1.67$.
+
+\dean{-------new bit end ------------}
+
+\dean{-------olde bit start ------------}
+
+Using an oversampling parameter of $\rho_{\phi}=1$, the maximum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
 The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
@@
 This band-limiting effect of the basis function decomposition can be observed when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
+
+\dean{-------olde bit end ------------}
 
@@
 \subsubsection{Experiment I: Monte Carlo Simulation with Fixed Parameters}
-A Monte Carlo approach was employed where 150 realisations of the data were generated.
+A Monte Carlo approach was employed where 150 realisations of the data were generated, such that distributions of the parameters estimates could be formed.
 Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
@@
 In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
-The actual parameter values, the mean parameter estimates, corresponding standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults} with results from Experiment II.
+The actual parameter values, the mean parameter estimates, corresponding standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries show results from Experiment II.
 \dean{We need to switch the graphs in Figure 10 so that the first one uses these parameters} \parham{it's in ascending order for $\theta_0$ for both rows}.
@@
 We attribute this small bias to the disparity between the actual field and the smoother estimated field from the decomposition.
-\ken{say why ...
-high freq?}
 
@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For Figure~\ref{fig:Figure8}(A-C) Mexican hat connectivity kernels were used.
+For Figure~\ref{fig:Figure8}(A-C) the Mexican hat connectivity kernels were used.
 For each subset of parameters, the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
@@
 Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the support of the kernel is precisely known, the exact meaning of the parameters in isolation is not clear and the net shape of the reconstructed kernel is important.
+This result demonstrates that unless the support of the kernel is precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and on the estimated parameter values individually.
 

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
more general edits

@@
 From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
-\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
+This is expected since..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
 However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function.

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
added mikes edits

@@
 \end{equation}
-where $\sigma_{phi}$ is the basis function width parameter. An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.
+where $\sigma_{\phi}$ is the basis function width parameter. An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.
 
@@
 \end{eqnarray}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$ is provided in the supplementary material.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$ is provided in the (\dean{Appendix}) supplementary material.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
@@
 \end{equation}
-where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a constant $L \times n_{\theta}$ matrix, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
-This matrix is defined analytically (see the supplementary (\dean{Appendix}) material for analytic convolution of two Gaussians).
+where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a $L \times n_{\theta}$ matrix, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+This matrix is defined analytically (see the supplementary (\dean{Appendix}) material for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
 Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
@@
 \end{equation}
-where the observation matrix is 
-\begin{equation}
-	\mathbf{C} = \left[
-	\begin{array}{{ccc}} 
-		c_{1,1} & \dots & c_{1,L} \\
-		\vdots & \ddots & \vdots \\
-		c_{N,1} & \dots & c_{N,L} 
-	\end{array}
-	\right] 
-\end{equation}
-and 
-\begin{equation}
-	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'. 
-\end{equation}
+where each element of the observation matrix is 
+\begin{equation}
+	\mathbf{C}_{ij} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
+\end{equation}
+% \begin{equation}
+% 	\mathbf{C} = \left[
+% 	\begin{array}{{ccc}} 
+% 		c_{1,1} & \dots & c_{1,L} \\
+% 		\vdots & \ddots & \vdots \\
+% 		c_{N,1} & \dots & c_{N,L} 
+% 	\end{array}
+% 	\right] 
+% \end{equation}
+% and 
+% \begin{equation}
+% 	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'. 
+% \end{equation}
 Now we have the final form of the state-space model where
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
+This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence \dean{(this should be mean (not sum) of the squared error for stochastic LS right?)}.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
general edits
added ref for LS algorithm
some small edits

@@
 \begin{equation}
-	\mathbf{C}_{ij} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
+	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
 \end{equation}
@@
 \end{small}
-Following this, the LS parameter estimates \ken{some reference for this result}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates~\cite{Kailath2000} \ken{some reference for this result}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 The result of the band-limiting effect in the field reconstruction can be observed when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
-Given the spatial cutoff frequency of the basis functions and the basis function separation the oversampling parameter $\rho_{\phi}\approx 1.67$.
+Given the spatial cutoff frequency of the basis functions and the basis function separation the oversampling parameter is $\rho_{\phi}\approx 1.67$.
 
@@
 From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
-This is expected since..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
+This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
+
+..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
 However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function.

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
added a couple of notes

@@
 This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
-
+\dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
 ..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
@@
 \dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...
+\dean{PLEASE HELP TO FILL THIS SECTION IN.
+ANYTHING WILL DO.}
 

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
Minor changes and comments

@@
 However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
-An experiment support this was performed and the results are shown in \dean{Appendix?}.
+An experiment supporting this was performed and the results are shown in \dean{Appendix?}.
 Therefore, in this study the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence \dean{(this should be mean (not sum) of the squared error for stochastic LS right?)}.
+This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence \dean{(this should be mean (not sum) of the squared error for stochastic LS right?)} \ken{why is it different?}.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
@@
 
-Due to restrictions imposed by the computationally demanding nature of the algorithm we chose to use a $9\times9$ grid of Gaussian basis functions to decompose the field, which resulted in 81 states.
+To limit the computationally demand of the estimation procedure we chose to use a $9\times9$ grid of Gaussian basis functions to decompose the field, which resulted in 81 states.
 Given the spatial domain, this yielded a basis function separation of $\Delta_{\phi}=2.5$~mm.

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
edit to UKF
correct LS notation
changed the order in figure 10
unbold phi notation

@@
 This facilitates application of standard nonlinear state estimation methods such as the unscented Kalman filter.
-The field decomposition is described by \ken{$\phi$ can't be a scalar and a vector}
+The field decomposition is described by
 \begin{equation}
@@
 \begin{equation}\label{eq:FieldBasisFunction}
-	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
+	\phi\left(\mathbf{r}-\mathbf{r}'\right) =
 \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}, 
@@
 Therefore, the additive form of the URTSS is used.
-This has a significant computational advantage over using the alternative multiplicative form of the filter.
 
@@
 \begin{eqnarray*}
-	\mathbf x_{1} &=& \mathbf{q}(\mathbf x_0) \boldsymbol{\theta}+\xi\mathbf x_0+\mathbf e_0 \\
-	\mathbf x_{2} &=& \mathbf{q}(\mathbf x_1) \boldsymbol{\theta}+\xi\mathbf x_1+\mathbf e_1  \\
+	 \hat{\mathbf x}^b_{1} &=& \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
+	\hat{\mathbf x}^b_{2} &=& \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
 	&\vdots& \\
-	\mathbf x_{T}&=& \mathbf{q}(\mathbf x_{T-1}) \boldsymbol{\theta}+\xi\mathbf x_{T-1}+\mathbf e_{T-1}. 
+	\hat{\mathbf x}^b_{T}&=& \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
 \end{eqnarray*}
@@
 	\begin{array}{cccc}
-		\mathbf x_{1}\\
-		\mathbf x_{2}\\
+		\hat{\mathbf x}^b_{1}\\
+		\hat{\mathbf x}^b_{2}\\
 		\vdots\\
-		\mathbf x_{T}
+		\hat{\mathbf x}^b_{T}
 	\end{array}
@@
 	\begin{array}{cccc}
-		\mathbf q(\mathbf x_0)& \mathbf x_{0}\\
-		\mathbf q(\mathbf x_1)& \mathbf x_{1}\\
+		\mathbf q(\hat{\mathbf x}^b_0)& \hat{\mathbf x}^b_{0}\\
+		\mathbf q(\hat{\mathbf x}^b_1)& \hat{\mathbf x}^b_{1}\\
 		\vdots & \vdots\\
-		\mathbf q(\mathbf x_{T-1})& \mathbf x_{T-1}
+		\mathbf q(\hat{\mathbf x}^b_{T-1})& \hat{\mathbf x}^b_{T-1}
 	\end{array}
@@
 The actual parameter values, the mean parameter estimates, corresponding standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries show results from Experiment II.
-\dean{We need to switch the graphs in Figure 10 so that the first one uses these parameters} \parham{it's in ascending order for $\theta_0$ for both rows}.
 The biases show the percentage differences between the actual values and the mean parameter estimates.

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
deleted Dean comment on the sum of the error in LS

@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence \dean{(this should be mean (not sum) of the squared error for stochastic LS right?)} \ken{why is it different?}.
+This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
 To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edit
defined the transpose

@@
 \end{equation}
-where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$. The field basis functions are described by
+where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$.
+The superscript $\top$ denotes the transpose operator.
+The field basis functions are described by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 \end{small}
-Following this, the LS parameter estimates~\cite{Kailath2000} \ken{some reference for this result}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates~\cite{Kailath2000}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point).
+The cut-off frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz.
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm.
@@
 The initial state and parameters were unknown to the estimator.
-Ten iterations of the estimation algorithm were used to ensure that the parameters converged.
+Ten iterations of the estimation algorithm were used to ensure that the parameter estimates converged.
 Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the parameters converged, with the changes in the parameter errors (between consecutive iterations) falling to less than $10^{-4}$ after 6 iterations.

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edit in abstract

@@
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
-The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework.
+The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity \parham{kernel} and synaptic dynamics with the proposed framework.
 The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
@@
 
-Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
+Let the spectral representation of the post-synaptic membrane voltage field at time $t$ \parham{and at spatial frequency $\boldsymbol\nu$} be denoted by $V_t(\boldsymbol{\nu})$.
 According to Shannon's sampling theorem, the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
@@
 \end{equation}
-where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
+where the constant $\alpha$ determines the spread of the sigma points and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
 
@@
 \end{eqnarray}
-where the superscripts $m$ and $c$ denote mean and covariance.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
made changes from Mikes comments

@@
 \end{equation}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,N$ indexes the electrodes and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
 
@@
 \end{equation}
-where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a $L \times n_{\theta}$ matrix, where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a $n_x \times n_{\theta}$ matrix, where $n_x$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
 This matrix is defined analytically (see the supplementary (\dean{Appendix}) material for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
@@
 % 	\begin{array}{{ccc}} 
-% 		c_{1,1} & \dots & c_{1,L} \\
+% 		c_{1,1} & \dots & c_{1,n_x} \\
 % 		\vdots & \ddots & \vdots \\
-% 		c_{N,1} & \dots & c_{N,L} 
+% 		c_{n_y,1} & \dots & c_{n_y,n_x} 
 % 	\end{array}
@@
 
-Let the spectral representation of the post-synaptic membrane voltage field at time $t$ \parham{and at spatial frequency $\boldsymbol\nu$} be denoted by $V_t(\boldsymbol{\nu})$.
+Let the spectral representation of the post-synaptic membrane voltage field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$, where $\boldsymbol\nu$ is the spatial frequency.
 According to Shannon's sampling theorem, the field must be spatially band-limited for an accurate reconstruction using spatially discrete observations.
-Nevertheless, an approximate reconstruction can be obtained if the field is approximately band-limited with
+However, an approximate reconstruction can be obtained if the field is approximately band-limited with
 \begin{equation}
@@
 However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
-Nevertheless, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
+Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
 The spatial extent of the sensors results in a spectral low-pass action, thus providing spatial anti-aliasing filtering.
@@
 This motivates the use of sensors with wider bandwidths (narrower in space).
-Nevertheless, this choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
+This choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
 Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors and the computational demands of the estimation procedure when designing experiments.
@@
 	\mathcal X_{0}&=&\bar x \\
-	\mathcal X_{i}&=&\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L \\
-	\mathcal X_{i}&=&\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2L 
+	\mathcal X_{i}&=&\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
+	\mathcal X_{i}&=&\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
 \end{eqnarray}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space.
-The total number of sigma points is $2L+1$.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $n_x$ is the dimension of the state space.
+The total number of sigma points is $2n_x+1$.
 The scaling parameter, $\lambda$, is defined as
 \begin{equation}\label{eq:sigmapoints3}
-	\lambda=\alpha^2( L+\kappa) - L, 
+	\lambda=\alpha^2( n_x+\kappa) - n_x, 
 \end{equation}
@@
 \begin{eqnarray}
-	\mathbf W_0^{(m)}&=&\frac{\lambda}{ L+\lambda} \\
-	\mathbf W_0^{(c)}&=&\frac{\lambda}{ L+\lambda}+(1-\alpha^2+\beta) \\
-	\mathbf W_i^{(m)}&=&\mathbf W_i^{(c)}=\frac{1}{2( L+\lambda)} \quad i=1, \dots, 2L, 
+	\mathbf W_0^{(m)}&=&\frac{\lambda}{ n_x+\lambda} \\
+	\mathbf W_0^{(c)}&=&\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
+	\mathbf W_i^{(m)}&=&\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
 \end{eqnarray}
@@
 The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
-The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain.
-A summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
+The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
 It should be noted that the disturbance, $\mathbf{e}_t$, and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
@@
 This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
-To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
+To create the least squares parameter estimator, we first define the $n_x \times n_{\theta}$ matrix
 \begin{equation}
@@
 \section{Results}\label{ResultsSection} We now provide demonstrations of the estimation procedure using the new methods that are described above.
-The full neural field model was used to generate the data for state and parameter estimation.
+Data was generated using the neural field model, described in Section~\ref{NeuralModelSection}, to demonstrate the state and parameter estimation framework.
 All parameters for the model are given in Table~\ref{tab:Parameters}, unless otherwise explicitly stated for particular experiments.
@@
 	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
+	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m^2$) & n.a. \\
 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
@@
 	\hline
-   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
+   	$\boldsymbol\phi(\mathbf{r})$ & vector of $n_x$ Gaussian basis functions & n.a.\\
    	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
@@
 \multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
-$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
+$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2n_x$\\
 \multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
-$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
 \multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
@@
 \multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
-$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
+$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2n_x$\\
 \multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
-$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
-$\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
-$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
+$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
+$\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
+$\mathbf M_{t +1}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
 \multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
@@
 	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
-	$N$ & number of sensors & 196 & n.a.\\ 
+	$n_y$ & number of sensors & 196 & n.a.\\ 
 	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
 	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
-	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{N}$ & mm$^2$ \\
+	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
 	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
@@
 	\hline
-	$L$ & number of basis functions& 81 & n.a.\\
+	$n_x$ & number of basis functions& 81 & n.a.\\
 	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
@@
 	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
-	$\kappa$& scaling parameter $(3-L)$& -78 & n.a.\\
+	$\kappa$& scaling parameter $(3-n_x)$& -78 & n.a.\\
 	$\lambda$& scaling parameter & -80.99 & n.a.\\

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
small edits, committing to pull

@@
 The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity \parham{kernel} and synaptic dynamics with the proposed framework.
-The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
+%The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
 \end{abstract}
@@
 We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
-In addition, a method is presented for estimating the connectivity structure and the synaptic dynamics.
+In addition, a new method is presented for estimating the connectivity structure and the synaptic dynamics.
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
@@
 In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
-This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required for the WC or Amari model.
+This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required for the neural field equations.
 
@@
 The model is reduced by approximating the neural field using a set of continuous basis functions, weighted by a finite dimensional state vector.
-The next section establishes conditions using spatial frequency analysis for both sensor and basis function spacing and width, such that the dominant dynamics of the neural field can be represented by the reduced model.
+The next section establishes conditions, using spatial frequency analysis, for both sensor and basis function spacing and width, such that the dominant dynamics of the neural field can be represented by the reduced model.
 The state and parameter estimation procedure is described in the following section.
@@
 
-\subsection{Derivation of the Integro-Difference Equation Representation}
-The combination of modelling techniques in this paper leads to a large amount of notation so a reference of the symbols used is provided in Table~\ref{tab:Notation}.
+\subsection{Integro-Difference Equation Neural Field Model}
+The combination of modelling techniques in this paper leads to a large amount of notation, so a reference of the symbols used is provided in Table~\ref{tab:Notation}.
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t$ and position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
-The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations at locations $\mathbf{r}'$ is described by
+The post-synaptic potentials generated at a neuronal population at location $\mathbf{r}$ by action potentials arriving from all other connected populations is described by
 \begin{equation}
@@
 \end{equation}
-where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Non-local interactions between cortical populations are described by 
+where $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function.
+Non-local interactions between cortical populations at positions $\mathbf{r}$ and $\mathbf{r}'$ are described by
 \begin{equation}
@@
 In an attempt model longer range connectivity, To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
-The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from patient specific data.
+The exact shape of this kernel is assumed to vary across subjects, and hence needs to be inferred from subject-specific data.
 
@@
 \end{equation}
-The parameter $v_0$ describes the  firing threshold of the neural populations.
-The parameter $\varsigma$ governs the slope of the sigmoid.
+The parameter $v_0$ describes the firing threshold of the neural populations and $\varsigma$ governs the slope of the sigmoid.
 By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model
@@
 \end{equation}
-To arrive at the Integro-Difference Equation (IDE) form of the model, we discretise time using a first-order Euler method (see the supplementary material for derivation) giving 
+To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see the supplementary (\dean{Appendix}) material for derivation) giving 
 \begin{equation}
@@
 
-When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like distribution, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor~\cite{Jackson1999}.
-However, when considering a source or sensor with a spatial extent the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
+When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor~\cite{Jackson1999}.
+However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
 An experiment supporting this was performed and the results are shown in \dean{Appendix?}.
-Therefore, in this study the observation kernel $m(\mathbf{r}-\mathbf{r}')$ that governs the sensor pick-up geometry and is defined by
+Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry and is defined by
 \begin{equation}
@@
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
-Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition.
-In order to model larger areas of cortex and to demonstrate the flexibility of the estimation framework, a third basis function is incorporated, corresponding to weaker mid-range excitation.
+Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition, but in order to model larger areas of cortex a third basis function is incorporated corresponding to weaker mid-range excitation.
 Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
@@
 \end{eqnarray}
-Next we multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
+Next we cross-multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
 \begin{eqnarray}
@@
 \end{eqnarray}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$ is provided in the (\dean{Appendix}) supplementary material.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the (\dean{Appendix}) supplementary material.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
 \begin{equation}
-	\psi_i (\mathbf{r}-\mathbf{r}') = \psi_i (2c_i+\mathbf{r}'-\mathbf{r})
-\end{equation}
-and $c_i$ is the center of the $i^{th}$ basis function of the kernel decomposition. To make the simplification we define
+	\psi_i (\mathbf{r}-\mathbf{r}') = \psi_i (2\mathbf{c}_i+\mathbf{r}'-\mathbf{r})
+\end{equation}
+and $\mathbf{c}_i$ is the center of the $i^{th}$ basis function of the kernel decomposition. To make the simplification we define
 \begin{equation}\label{eq:DefPsi}
-	\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}  \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2c_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+	\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}  \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2\mathbf{c}_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
 \end{equation}
@@
 \end{eqnarray}
-This substitution allows us to swap the convolution in equation~\ref{reduced continuous model}, which would be computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is calculated analytically.
+This substitution allows us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is pre-defined analytically.
 This is of great importance as it lowers the computational demands of the estimation algorithm and provides a dramatic increase in estimation speed.
@@
 This choice would require more sensors in order to satisfy Shannon's sampling theorem for a given spatial region.
-Therefore, a compromise needs to be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors and the computational demands of the estimation procedure when designing experiments.
+Therefore, a compromise should be found between the bandwidth of the sensor response, the accuracy of the estimation results, the number of sensors and the computational demands of the estimation procedure when designing experiments.
 
@@
 This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
-Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in the supplementary material.
+Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in the supplementary material (\dean{Appendix}).
 
@@
 This allows for an approximate representation by a lower order model (fewer basis functions), thus reducing the computational demands of the estimation process.
-The spatial cut-off frequency of this smoothed field becomes a design choice.
-To calculate the cut-off frequency imposed by the basis function width, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
+The spatial cutoff frequency of this smoothed field becomes a design choice.
+To calculate the cutoff frequency imposed by the basis function width, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
 \begin{equation}\label{eq:CutoffFromBasisFuncWidth}
@@
 
-Note that for a spatially homogeneous isotropic field, the basis functions can be placed on a regular grid.
+Note that for a spatially homogeneous and isotropic field, the basis functions can be placed on a regular grid.
 Thus, the knowledge of the distance between basis functions can be used to determine the total number of basis functions required to represent a known spatial region.
@@
 \end{eqnarray}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $n_x$ is the dimension of the state space.
+where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space.
 The total number of sigma points is $2n_x+1$.
@@
 \end{eqnarray}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
 To create the least squares parameter estimator, we first define the $n_x \times n_{\theta}$ matrix
@@
 Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The cut-off frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz.
+The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz.
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm.
@@
 The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(A).
-The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point).
-The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors.
+The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point).
+The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors.
 The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
@@
 
-To limit the computationally demand of the estimation procedure we chose to use a $9\times9$ grid of Gaussian basis functions to decompose the field, which resulted in 81 states.
+Due to the limitations imposed by the computationally demanding estimation procedure we chose to use a $9\times9$ grid of Gaussian basis functions to decompose the field, which resulted in $81$ states.
 Given the spatial domain, this yielded a basis function separation of $\Delta_{\phi}=2.5$~mm.
@@
 \label{sec:state_and_param_results}
-Experiments were performed to demonstrate the performance of the state and parameter estimation algorithm.
+Several experiments were performed to demonstrate the performance of the state and parameter estimation algorithm.
 The first experiment evaluated the estimation performance using a Monte Carlo approach for a single set of parameters.
@@
 The third experiment shows how the estimation accuracy depends on the parameters of the sigmoidal nonlinearity.
-The final experiment shows the effect of the width of the sensor kernel on the estimation performance.
+The final experiment shows the effect of the width of the observation kernel on the estimation performance.
 
@@
 Ten iterations of the estimation algorithm were used to ensure that the parameter estimates converged.
-Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the parameters converged, with the changes in the parameter errors (between consecutive iterations) falling to less than $10^{-4}$ after 6 iterations.
+Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the algorithm converged to steady parameter values, with the changes in the parameter errors (between consecutive iterations) falling to less than $10^{-4}$ after 6 iterations.
 
@@
 In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
-The actual parameter values, the mean parameter estimates, corresponding standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries show results from Experiment II.
+The actual parameter values, the mean parameter estimates, standard deviations, and biases for this parameter combination are given as the first entry in Table~\ref{tab:MexicanHatKernelResults}, where other entries in the table show results from Experiment II.
 The biases show the percentage differences between the actual values and the mean parameter estimates.
@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9} with the $95~\%$ confidence interval.
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
@@
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail, which can be see in the error shown in Figure~\ref{fig:Figure10}(C)).
+It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field, shown in Figure~\ref{fig:Figure10}(A), but is missing the higher-frequency detail, which can be see in the error shown in Figure~\ref{fig:Figure10}(C).
 
@@
 
-To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernel parameters.
+To study the robustness of the estimation algorithm, the performance was evaluated for various connectivity kernel parameters.
 The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
@@
 The estimation algorithm was constructed allowing for the Mexican hat connectivity of the previous examples.
-Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates for the majority of the kernel space until the amplitude is relatively low.
+Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates for the majority of the kernel space, until the amplitude is relatively low.
 Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates.
 Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the support of the kernel is precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and on the estimated parameter values individually.
+This result demonstrates that unless the support of the kernel is precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
 
@@
 Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
-As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter and when the observation kernel is too narrow, high spatial frequency information is present but not adequately sampled by the observation function.
+As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
+When the observation kernel is too narrow, a small amount of high spatial frequency information is still present but not adequately sampled by the observation function, since the field is not exactly band-limited.
 Therefore, a small amount of aliasing occurs which results in the estimation error.
-When the observation kernel width is increased, the high spatial frequency information is filtered by the observation kernel and the error decreases.
-However, as expected, when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
+When the observation kernel width is increased, the high spatial frequency information that is not adequately sampled is filtered more strongly by the observation kernel and the error decreases.
+However, as expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
 
 \section{Discussion}\label{DiscussionSection}
-This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.
 
 \subsection{Implications for Experimental Design}
-As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
-The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
-To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings.
-Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease.
+As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
+The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
+To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings, where given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease.
 Even when using a known input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
@@
 As pointed out in numerous publications by Freeman and colleagues (see \cite{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
-Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial properties can be recovered.
+Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
 In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
@@
 Furthermore, by using the neural field equations as a parametric form of a model, the estimated quantities have physical meaning and, therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
+An advantage of the MVAR-based methods is that they allow for inhomogeneous and anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
 
@@
 Specifically, these subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems.
-For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space may indicate intent of movement or imminent seizures, respectively.
+For example, state tracking could be used in brain-computer interfaces or epileptic seizure prediction, where specific regions of the state-space or certain parameter combinations may indicate intent of movement or imminent seizures, respectively.
 In addition, a patient-specific state-space model will allow application of electrical stimulation to robustly prevent the neurodynamics entering pathological regions of state-space, thereby possibly preventing seizure onset or abating seizure activity.
 
-Connectivity kernel parameter estimation may also have significant impact on the treatment of disease.
+Estimation of the connectivity structure or the synaptic time constant may also have significant impact on the treatment of disease.
 For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
@@
 
-The development of an estimation framework also has implications for theoretical neuroscience, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies.
+The development of the estimation framework also has implications for theoretical neuroscience, where the ability to estimate subject-specific properties will allow testing of hypotheses that have been generated in computational modelling studies.
 This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of mesoscopic and macroscopic neurodynamics.
@@
 \section{Conclusion}
-This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology.
-\dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...
-\dean{PLEASE HELP TO FILL THIS SECTION IN.
-ANYTHING WILL DO.}
+\dean{I MOVED THIS FROM THE START OF THE DISCUSSION.
+ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
+We have derived a finite-order state-space representation of the continuum neural field equations that allows inference to be performed efficiently.
+Importantly, the mathematical formulation that we have presented scales well with the number of sensors.
+The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
 
@@
 Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
+The authors would also like to thank Dr.
+John Terry for insightful discussions and feedback.
 
@@
 \caption{{\bf Spatial frequency analysis}.
-The dashed line shows the cut-off frequency (-3 dB point).
+The dashed line shows the cutoff frequency (-3 dB point).
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
@@
     % $V(\nu)$ & Fourier transform of the neural field & Hz\\
-	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & Hz \\
 	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Changes to section 3.1

@@
 
-\ken{revise}
+\ken{revised new bit}
+
+To reduce the computational demand of the estimation procedure, the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
+Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen.
+Therefore for an equally spaced grid of basis functions over the full spatial domain being considered, a $9\times9$ grid was required to decompose the field, which resulted in $81$ states.
+The other parameter of the basis functions, $\sigma_{\phi}^2$, is set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.
+
+\ken{how's that?}
 

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Changes in section 3.2.1. to better justify eliminating the high frequency components in the field reconstruction.

@@
 However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
-We attribute this small bias to the disparity between the actual field and the smoother estimated field from the decomposition.
+We attribute this small bias to the loss of the high frequency components in the smoother estimated field with respect to the actual field.
+These results thus indicate that choosing to limit the frequency content of the reconstructed neural field has only minor effects on the accuracy of the estimated kernel while allowing for significant gains in the computational demand.
 

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
final commit before moving to different neuroimage cls

--- 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 An example of the Mexican hat connectivity kernel used in this paper is shown in Figure~\ref{fig:Figure1}.
-In an attempt model longer range connectivity, To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
+To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
 The exact shape of this kernel is assumed to vary across subjects, and hence needs to be inferred from subject-specific data.
@@
 \end{equation}
-To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
+Now we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
@@
 \end{equation}
-where $\textrm{D}=d/dt + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
+where $\textrm{D}=d/dt + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This gives the standard form of the model
 \begin{equation}
@@
 An experiment supporting this was performed and the results are shown in \dean{Appendix?}.
-Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry and is defined by
+Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry is defined by
 \begin{equation}

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edit to the abstract

@@
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
-The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity \parham{kernel} and synaptic dynamics with the proposed framework.
+The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity structure and synaptic dynamics with the proposed framework.
 %The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Response of the help request of section 3.2.3

--- 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 An example of the Mexican hat connectivity kernel used in this paper is shown in Figure~\ref{fig:Figure1}.
-To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
+In an attempt model longer range connectivity, To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
 The exact shape of this kernel is assumed to vary across subjects, and hence needs to be inferred from subject-specific data.
@@
 \end{equation}
-Now we shall express the synaptic response kernel as a Green's function 
+To arrive at the final form of the model, we shall express the synaptic response kernel as a Green's function 
 \begin{equation}
@@
 \end{equation}
-where $\textrm{D}=d/dt + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This gives the standard form of the model
+where $\textrm{D}=d/dt + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
 \begin{equation}
@@
 An experiment supporting this was performed and the results are shown in \dean{Appendix?}.
-Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry is defined by
+Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry and is defined by
 \begin{equation}
@@
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
-The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
+The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields.
@@
 Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the support of the kernel is precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
+This result demonstrates that unless the widths of the Gaussians forming the kernel are precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
 
@@
 From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
-This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
+This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
+
+\ken{what I would write}
+
+For example, when the sigmoid slope is very gentle, most of the neural activity falls in the central, nearly linear region of the sigmoid, thus having minor effects on the estimation procedure.
+On the other hand, sharp slopes result in most of the activity falling in the saturation region of the sigmoid with adverse effects on the estimation.
+Similar arguments can be made for variations to the sigmoid threshold.
+
+\ken{what do you think?}
+
 \dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
changed to Neuroimage cls file and added appendices, still need to fix long equations and cross referencing

--- 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 
-\documentclass[12pt]{iopart} 
-\usepackage{iopams}
+\documentclass[5p]{elsarticle}
+% \documentclass[12pt]{iopart} 
+% \usepackage{iopams}
 
@@
 % % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\usepackage{amsmath}
 
@@
 
+\journal{Neuroimage}
+
 \begin{document}
+
+	\begin{frontmatter}
 % Title must be 150 characters or less
-\title[A Data-Driven Framework for Neural Field Modelling]{A Data-Driven Framework for Neural Field Modelling}
-
-\author{Dean R. Freestone$^{1,2,3}$, 
-Parham Aram$^{4}$, 
-Michael Dewar$^{3,5}$,
-Kenneth Scerri$^{6}$,
-David B. Grayden$^{1,2}$,
-Visakan Kadirkamanathan$^{4}$}
-
-\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
-\\
-$^2$ The Bionic Ear Institute, East Melbourne, VIC, Australia
-\\
-$^3$ Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
-\\
-$^4$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
-\\
-$^5$ Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
-\\
-$^6$ Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
-
+\title{A Data-Driven Framework for Neural Field Modelling}
+
+\author[DEEE,BEI,UE]{D. R. Freestone\corref{cor1}}
 \ead{dfreestone@bionicear.org}
+\author[US]{P. Aram} 
+\author[UE,CU]{M. Dewar}
+\author[UM]{K. Scerri}
+\author[DEEE,BEI]{D. B. Grayden}
+\author[US]{V. Kadirkamanathan}
+
+\address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
+\address[BEI]{The Bionic Ear Institute, East Melbourne, VIC, Australia}
+\address[UE]{Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK}
+\address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
+\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
+\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
 
@@
 The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation.
-The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity structure and synaptic dynamics with the proposed framework.
+The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity \parham{kernel} and synaptic dynamics with the proposed framework.
 %The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
@@
 
-\maketitle
+\begin{keyword}
+	keyword1 \sep keyword2
+%% keywords here, in the form: keyword \sep keyword
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-% This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
-The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
-Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
-
-\section*{References}
+\appendix
+\section{Time Discretisation of Neural Field Model}
+\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
+To do this, we used a one-step Euler method, where equation~7 of the main text can be approximated by
+\begin{equation}
+	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} =-\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.
+\end{equation}
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1, we get 
+\begin{equation}
+	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.
+\end{equation}
+Now making simplifications, the discrete time form of the model is 
+\begin{equation}
+	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
+\end{equation}
+where $\xi = 1 - T_s \zeta$.
+
+\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
+In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
+Therefore, $\mathbf{e}_t$ is also normally distributed.
+From equation~21 of the main text, the state disturbance vector is defined as
+\begin{equation}
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
+\end{equation}
+The expected value of $\mathbf e_t$ is given by 
+\begin{equation}
+	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
+\end{equation}
+The covariance of $\mathbf{e}_t$ is 
+\begin{align}
+	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
+&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
+\end{align}
+
+\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
+This section gives the derivation for the width of the Fourier transform of  the field basis function in terms of its spatial cut-off frequency (equations~34 and~37 in the main text).
+We define an \textit{n}-dimensional Gaussian  centred at the origin as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
+\end{equation}
+Now applying the \textit{n}-dimensional Fourier transform yields
+\begin{align}\label{eq:AppendixGaussianFT}
+ \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{align}
+Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+\begin{equation}\label{eq:IntegralOfGaussian}
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
+\end{equation}
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation} 
+where 
+\begin{equation}
+	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
+\begin{equation}
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
+\end{equation}
+since the maximum of the Gaussian described in equation~S1.10 is at the origin. Solving for $\sigma_{\nu}^2$, we get
+\begin{equation}
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
+\end{equation}
+
+\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
+In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
+Consider two Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section, we have
+\begin{equation}\label{eq:FTTwoGaussianMultiplication}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform.
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+\begin{equation}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{equation}
+Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
+\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
+\end{equation}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+
+\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
+The derivation in this section was used for calculating the matrix $\Gamma$ from equation~16 in the main text.
+The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
+\begin{equation}\label{eq:InofGaussianDefinition}
+\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
+\end{equation}
+A Gaussian basis function is symmetric with respect to its centre so
+\begin{equation}\label{eq:GaussianSymmetry}
+ \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$, equation~\ref{eq:GaussianSymmetry} becomes
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
+ \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
+\begin{align}
+\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
+\end{align}
+Using the derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
+\begin{equation}
+ \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
+\end{equation}
+This completes the derivation.
+
+\section{Observation Kernel}
+The Gaussian shape of the observation kernel was verified experimentally.
+This was achieved by moving a dipole across a recording electrode submerged in saline.
+A photograph through a microscope of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
+The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
+The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
+The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
+The twisted wire electrode and the Utah array were co-registered visually using the microscope.
+% \begin{figure}[ht]		
+% 	\begin{center}
+% 		%trim option's parameter order: left bottom right top
+% 	\includegraphics[scale=.1, trim = .5mm .5mm .00005mm .00005mm, clip ] {./Graph/eps/SensorAndSource.eps}
+% \end{center}
+% 	\caption{Photograph through a microscope of the Utah recording array and the twisted bipolar current source.}
+% 	\label{fig:SensorAndSource}
+% \end{figure}
+The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
+The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
+To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
+The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
+\begin{equation}
+	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
+\end{equation}
+where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
+Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
+A Gaussian fitted to the amplitudes is also shown.
+The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
+% \begin{figure}[h]
+% 	\begin{center}
+% 	\includegraphics[scale=1]{./Graph/eps/channel3fig.eps}
+% 	\end{center}
+% 	\caption{Amplitude of the envelope of the signal recorded from an electrode at the origin as the source was moved.}
+% 	\label{fig:Ch3}
+% \end{figure}
+
 \bibliographystyle{unsrt} 

### 2010-11-18 ltx/first_order_framework/SupportingInformation.tex
changed to Neuroimage cls file and added appendices, still need to fix long equations and cross referencing

@@
 \end{equation}
-since the maximum of Gaussian described in equation~S1.10 is at the origin. Now solving for $\sigma_{\nu}^2$ we get
+since the maximum of the Gaussian described in equation~S1.10 is at the origin. Solving for $\sigma_{\nu}^2$, we get
 \begin{equation}
@@
 \begin{equation}\label{eq:FTTwoGaussianMultiplication}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
 \end{equation}
 where $\mathcal{F}$ denotes the Fourier transform.
-Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$ equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
 \begin{equation}
@@
 The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
-The twisted wire electrode and the Utah array were co-registered by visually using the microscope.
+The twisted wire electrode and the Utah array were co-registered visually using the microscope.
 \begin{figure}[ht]		
@@
 The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
-The recording from the central electrode in the array was used estimate the shape of the sensor kernel.
-To extract the amplitude the signal the data was first band-pass filtered with a centre frequency of 40~Hz.
+The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
+To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
 The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
@@
 where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
-Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus to distance between the twisted wire electrode and the recording electrode.
+Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
 A Gaussian fitted to the amplitudes is also shown.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed the equations length

@@
 Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
-\begin{eqnarray}
+\begin{align}
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
-	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
-\end{eqnarray}
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
+\end{align}
 Next we cross-multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
-\begin{eqnarray}
+\begin{align}
 	\label{StartofReduction}
- 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} &=&
- T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
-&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
-&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
+ 	\int_\Omega \boldsymbol{\phi} &\left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)d\mathbf{r} \mathbf{x}_{t+1}  \nonumber \\
+ &=T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') 
+ f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}\boldsymbol{\theta} \nonumber \\ 
+&+ \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t + 
 \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
-\end{eqnarray}
+\end{align}
 Now defining the matrix
@@
 and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives
-\begin{eqnarray}
+\begin{align}
     \label{eq:ReducedForm}
-    % \begin{split}
-	 \mathbf{x}_{t+1} &=& T_s\boldsymbol{\Gamma}^{-1}
+	 \mathbf{x}_{t+1} &= T_s\boldsymbol{\Gamma}^{-1}
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
 	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
-	&\times& d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
+	&\times d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
 	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
-	 % \end{split}
-\end{eqnarray}
+\end{align}
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the (\dean{Appendix}) supplementary material.
@@
 Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
-\begin{eqnarray}
-	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
+\begin{align}
+	\mathbf{x}_{t+1} &= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+ \xi\mathbf{x}_t 
 + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, d\mathbf{r}}.
-\end{eqnarray}
+\end{align}
 This substitution allows us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is pre-defined analytically.
@@
 The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
-\begin{eqnarray}\label{eq:sigmapoints1}
-	\mathcal X_{0}&=&\bar x \\
-	\mathcal X_{i}&=&\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
-	\mathcal X_{i}&=&\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
-\end{eqnarray}
+\begin{align}\label{eq:sigmapoints1}
+	\mathcal X_{0}&=\bar x \\
+	\mathcal X_{i}&=\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
+	\mathcal X_{i}&=\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
+\end{align}
 where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space.
@@
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
-\begin{eqnarray}
-	\mathbf W_0^{(m)}&=&\frac{\lambda}{ n_x+\lambda} \\
-	\mathbf W_0^{(c)}&=&\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
-	\mathbf W_i^{(m)}&=&\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
-\end{eqnarray}
+\begin{align}
+	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
+	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
+	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
+\end{align}
 where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$.
@@
 Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
-\begin{eqnarray*}
-	 \hat{\mathbf x}^b_{1} &=& \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
-	\hat{\mathbf x}^b_{2} &=& \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
+\begin{align*}
+	 \hat{\mathbf x}^b_{1} &= \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
+	\hat{\mathbf x}^b_{2} &= \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
 	&\vdots& \\
-	\hat{\mathbf x}^b_{T}&=& \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
-\end{eqnarray*}
+	\hat{\mathbf x}^b_{T}&= \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
+\end{align*}
 This can be written in the compact form
@@
 To do this, we used a one-step Euler method, where equation~7 of the main text can be approximated by
-\begin{equation}
-	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} =-\zeta v\left( \mathbf{r},t \right) + \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}.
-\end{equation}
+\begin{align}
+	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
+&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
+\end{align}
 For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1, we get 
@@
  \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
-&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
 \end{align}
@@
 Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
-\begin{equation}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
-\end{equation}
+\begin{align}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
+ &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{align}
 Taking the inverse Fourier transform, the convolution becomes
@@
 In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
-\begin{equation}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
-\end{equation}
+\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
+\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
+\end{align}
 where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
@@
 Using the derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{equation}
- \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
-\end{equation}
+\begin{align}
+ \varphi_i\otimes\varphi_j&=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
+\end{align}
 This completes the derivation.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Changes to section 3.2.4

@@
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
-	&\times d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  \nonumber \\
+	& + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
 \end{align}
@@
 As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
+
+\ken{tried to make it a little more straight forward}
+
+When the observation kernel is too narrow, high frequency components in the neural field are sampled.
+These high frequency components result in aliasing errors in the estimated field thus affecting the kernel estimation accuracy.
+On the other hand, for the very wide kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the high frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
+Thus, as indicated in Figure~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
+
+\ken{that ok?}
+
 When the observation kernel is too narrow, a small amount of high spatial frequency information is still present but not adequately sampled by the observation function, since the field is not exactly band-limited.
@@
 \label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
-To do this, we used a one-step Euler method, where equation~7 of the main text can be approximated by
+To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} of the main text can be approximated by
 \begin{align}
@@
 \end{align}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~S1.1, we get 
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
 \begin{equation}

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Minor change

@@
 \dean{I MOVED THIS FROM THE START OF THE DISCUSSION.
-ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+ANY OBJECTIONS?} \ken{None} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed cross referencing in appendix

@@
 \label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
-To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} of the main text can be approximated by
+To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by
 \begin{align}
@@
 Therefore, $\mathbf{e}_t$ is also normally distributed.
-From equation~21 of the main text, the state disturbance vector is defined as
+From equation~\ref{eq:Wt}, the state disturbance vector is defined as
 \begin{equation}
@@
 \section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
-This section gives the derivation for the width of the Fourier transform of  the field basis function in terms of its spatial cut-off frequency (equations~34 and~37 in the main text).
+This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
 We define an \textit{n}-dimensional Gaussian  centred at the origin as
@@
 \end{equation}
-since the maximum of the Gaussian described in equation~S1.10 is at the origin. Solving for $\sigma_{\nu}^2$, we get
+since the maximum of the Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Solving for $\sigma_{\nu}^2$, we get
 \begin{equation}
@@
 The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section, we have
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
 \begin{equation}\label{eq:FTTwoGaussianMultiplication}
@@
 \section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\Gamma$ from equation~16 in the main text.
+The derivation in this section was used for calculating the matrix $\Gamma$ from equation~\ref{eq:DefGamma}.
 The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edits from proof read of entire paper

--- 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 
-\documentclass[5p]{elsarticle}
-% \documentclass[12pt]{iopart} 
-% \usepackage{iopams}
+\documentclass[12pt]{iopart} 
+\usepackage{iopams}
 
@@
 % % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\usepackage{amsmath}
 
@@
 
-\journal{Neuroimage}
-
 \begin{document}
-
-	\begin{frontmatter}
 % Title must be 150 characters or less
-\title{A Data-Driven Framework for Neural Field Modelling}
-
-\author[DEEE,BEI,UE]{D. R. Freestone\corref{cor1}}
+\title[A Data-Driven Framework for Neural Field Modelling]{A Data-Driven Framework for Neural Field Modelling}
+
+\author{Dean R. Freestone$^{1,2,3}$, 
+Parham Aram$^{4}$, 
+Michael Dewar$^{3,5}$,
+Kenneth Scerri$^{6}$,
+David B. Grayden$^{1,2}$,
+Visakan Kadirkamanathan$^{4}$}
+
+\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia
+\\
+$^2$ The Bionic Ear Institute, East Melbourne, VIC, Australia
+\\
+$^3$ Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK
+\\
+$^4$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK
+\\
+$^5$ Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA
+\\
+$^6$ Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+
 \ead{dfreestone@bionicear.org}
-\author[US]{P. Aram} 
-\author[UE,CU]{M. Dewar}
-\author[UM]{K. Scerri}
-\author[DEEE,BEI]{D. B. Grayden}
-\author[US]{V. Kadirkamanathan}
-
-\address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
-\address[BEI]{The Bionic Ear Institute, East Melbourne, VIC, Australia}
-\address[UE]{Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK}
-\address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
-\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
-\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
 
@@
 
-\begin{keyword}
-	keyword1 \sep keyword2
-%% keywords here, in the form: keyword \sep keyword
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
+\maketitle
 
@@
 Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
-\begin{align}
+\begin{eqnarray}
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
-	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
-\end{align}
+	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &=& T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
+\end{eqnarray}
 Next we cross-multiply equation~\ref{reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
-\begin{align}
+\begin{eqnarray}
 	\label{StartofReduction}
- 	\int_\Omega \boldsymbol{\phi} &\left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)d\mathbf{r} \mathbf{x}_{t+1}  \nonumber \\
- &=T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') 
- f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}\boldsymbol{\theta} \nonumber \\ 
-&+ \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t + 
+ 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) d\mathbf{r}} \mathbf{x}_{t+1} &=&
+ T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') \nonumber \\
+&\times& { f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}}\boldsymbol{\theta} \nonumber \\ 
+&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t \nonumber \\ &+& 
 \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
-\end{align}
+\end{eqnarray}
 Now defining the matrix
@@
 and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives
-\begin{align}
+\begin{eqnarray}
     \label{eq:ReducedForm}
-	 \mathbf{x}_{t+1} &= T_s\boldsymbol{\Gamma}^{-1}
+    % \begin{split}
+	 \mathbf{x}_{t+1} &=& T_s\boldsymbol{\Gamma}^{-1}
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  \nonumber \\
-	& + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
-\end{align}
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
+	&\times& d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
+	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
+	 % \end{split}
+\end{eqnarray}
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the (\dean{Appendix}) supplementary material.
@@
 Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
-\begin{align}
-	\mathbf{x}_{t+1} &= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+ \xi\mathbf{x}_t 
+\begin{eqnarray}
+	\mathbf{x}_{t+1} &=& \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \, d\mathbf{r}' \boldsymbol{\theta} \nonumber \\ &+& \xi\mathbf{x}_t 
 + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r}) \, d\mathbf{r}}.
-\end{align}
+\end{eqnarray}
 This substitution allows us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is pre-defined analytically.
@@
 The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
-\begin{align}\label{eq:sigmapoints1}
-	\mathcal X_{0}&=\bar x \\
-	\mathcal X_{i}&=\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
-	\mathcal X_{i}&=\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
-\end{align}
+\begin{eqnarray}\label{eq:sigmapoints1}
+	\mathcal X_{0}&=&\bar x \\
+	\mathcal X_{i}&=&\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
+	\mathcal X_{i}&=&\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
+\end{eqnarray}
 where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space.
@@
 The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
-\begin{align}
-	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
-	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
-	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
-\end{align}
+\begin{eqnarray}
+	\mathbf W_0^{(m)}&=&\frac{\lambda}{ n_x+\lambda} \\
+	\mathbf W_0^{(c)}&=&\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
+	\mathbf W_i^{(m)}&=&\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
+\end{eqnarray}
 where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$.
@@
 Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
-\begin{align*}
-	 \hat{\mathbf x}^b_{1} &= \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
-	\hat{\mathbf x}^b_{2} &= \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
+\begin{eqnarray*}
+	 \hat{\mathbf x}^b_{1} &=& \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
+	\hat{\mathbf x}^b_{2} &=& \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
 	&\vdots& \\
-	\hat{\mathbf x}^b_{T}&= \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
-\end{align*}
+	\hat{\mathbf x}^b_{T}&=& \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
+\end{eqnarray*}
 This can be written in the compact form
@@
 
-\ken{revised new bit}
-
-To reduce the computational demand of the estimation procedure, the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
-Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen.
-Therefore for an equally spaced grid of basis functions over the full spatial domain being considered, a $9\times9$ grid was required to decompose the field, which resulted in $81$ states.
-The other parameter of the basis functions, $\sigma_{\phi}^2$, is set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.
-
-\ken{how's that?}
+\ken{revise}
 
@@
 However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
-We attribute this small bias to the loss of the high frequency components in the smoother estimated field with respect to the actual field.
-These results thus indicate that choosing to limit the frequency content of the reconstructed neural field has only minor effects on the accuracy of the estimated kernel while allowing for significant gains in the computational demand.
+We attribute this small bias to the disparity between the actual field and the smoother estimated field from the decomposition.
 
@@
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
-The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
+The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields.
@@
 Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the widths of the Gaussians forming the kernel are precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
+This result demonstrates that unless the support of the kernel is precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
 
@@
 From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
-This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
-
-\ken{what I would write}
-
-For example, when the sigmoid slope is very gentle, most of the neural activity falls in the central, nearly linear region of the sigmoid, thus having minor effects on the estimation procedure.
-On the other hand, sharp slopes result in most of the activity falling in the saturation region of the sigmoid with adverse effects on the estimation.
-Similar arguments can be made for variations to the sigmoid threshold.
-
-\ken{what do you think?}
-
+This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
 \dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
@@
 As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
-
-\ken{tried to make it a little more straight forward}
-
-When the observation kernel is too narrow, high frequency components in the neural field are sampled.
-These high frequency components result in aliasing errors in the estimated field thus affecting the kernel estimation accuracy.
-On the other hand, for the very wide kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the high frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
-Thus, as indicated in Figure~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
-
-\ken{that ok?}
-
 When the observation kernel is too narrow, a small amount of high spatial frequency information is still present but not adequately sampled by the observation function, since the field is not exactly band-limited.
@@
 \section{Discussion}\label{DiscussionSection}
+This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
+We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.
 
@@
 \section{Conclusion}
-\dean{I MOVED THIS FROM THE START OF THE DISCUSSION.
-ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-We have derived a finite-order state-space representation of the continuum neural field equations that allows inference to be performed efficiently.
-Importantly, the mathematical formulation that we have presented scales well with the number of sensors.
-The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
+This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology.
+\dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...
+\dean{PLEASE HELP TO FILL THIS SECTION IN.
+ANYTHING WILL DO.}
 
@@
 Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
-The authors would also like to thank Dr.
-John Terry for insightful discussions and feedback.
-
-\appendix
-\section{Time Discretisation of Neural Field Model}
-\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
-To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} of the main text can be approximated by
-\begin{align}
-	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
-&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
-\end{align}
-For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
-\begin{equation}
-	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.
-\end{equation}
-Now making simplifications, the discrete time form of the model is 
-\begin{equation}
-	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
-\end{equation}
-where $\xi = 1 - T_s \zeta$.
-
-\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
-In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
-We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
-Therefore, $\mathbf{e}_t$ is also normally distributed.
-From equation~21 of the main text, the state disturbance vector is defined as
-\begin{equation}
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
-\end{equation}
-The expected value of $\mathbf e_t$ is given by 
-\begin{equation}
-	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
-\end{equation}
-The covariance of $\mathbf{e}_t$ is 
-\begin{align}
-	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{align}
-
-\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
-This section gives the derivation for the width of the Fourier transform of  the field basis function in terms of its spatial cut-off frequency (equations~34 and~37 in the main text).
-We define an \textit{n}-dimensional Gaussian  centred at the origin as
-\begin{equation}
- \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
-\end{equation}
-Now applying the \textit{n}-dimensional Fourier transform yields
-\begin{align}\label{eq:AppendixGaussianFT}
- \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
-&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{align}
-Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{equation}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
-\end{equation}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation} 
-where 
-\begin{equation}
-	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{equation}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{equation}
-since the maximum of the Gaussian described in equation~S1.10 is at the origin. Solving for $\sigma_{\nu}^2$, we get
-\begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
-\end{equation}
-
-\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~S1.10 of the previous section, we have
-\begin{equation}\label{eq:FTTwoGaussianMultiplication}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{equation}
-where $\mathcal{F}$ denotes the Fourier transform.
-Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
-\begin{align}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
- &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
-\end{align}
-Taking the inverse Fourier transform, the convolution becomes
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
-\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
-\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
-\end{align}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
-
-\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\Gamma$ from equation~16 in the main text.
-The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
-\begin{equation}\label{eq:InofGaussianDefinition}
-\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
-\end{equation}
-A Gaussian basis function is symmetric with respect to its centre so
-\begin{equation}\label{eq:GaussianSymmetry}
- \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$, equation~\ref{eq:GaussianSymmetry} becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
-\begin{align}
-\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
-\end{align}
-Using the derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{align}
- \varphi_i\otimes\varphi_j&=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
-\end{align}
-This completes the derivation.
-
-\section{Observation Kernel}
-The Gaussian shape of the observation kernel was verified experimentally.
-This was achieved by moving a dipole across a recording electrode submerged in saline.
-A photograph through a microscope of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
-The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
-The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
-The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
-The twisted wire electrode and the Utah array were co-registered visually using the microscope.
-% \begin{figure}[ht]		
-% 	\begin{center}
-% 		%trim option's parameter order: left bottom right top
-% 	\includegraphics[scale=.1, trim = .5mm .5mm .00005mm .00005mm, clip ] {./Graph/eps/SensorAndSource.eps}
-% \end{center}
-% 	\caption{Photograph through a microscope of the Utah recording array and the twisted bipolar current source.}
-% 	\label{fig:SensorAndSource}
-% \end{figure}
-The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
-The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
-To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
-The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
-\begin{equation}
-	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
-\end{equation}
-where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
-Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
-A Gaussian fitted to the amplitudes is also shown.
-The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
-% \begin{figure}[h]
-% 	\begin{center}
-% 	\includegraphics[scale=1]{./Graph/eps/channel3fig.eps}
-% 	\end{center}
-% 	\caption{Amplitude of the envelope of the signal recorded from an electrode at the origin as the source was moved.}
-% 	\label{fig:Ch3}
-% \end{figure}
-
+
+% This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
+Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
+
+\section*{References}
 \bibliographystyle{unsrt} 

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
added note about conclusion

@@
 \section{Discussion}\label{DiscussionSection}
-This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+\dean{I MIGHT MOVE THIS BIT TO THE CONCLUSION.
+ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
added a bit to the conclusion

@@
 \section{Discussion}\label{DiscussionSection}
-\dean{I MIGHT MOVE THIS BIT TO THE CONCLUSION.
-ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
-In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.
 
@@
 \section{Conclusion}
-This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology.
-\dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...
-\dean{PLEASE HELP TO FILL THIS SECTION IN.
-ANYTHING WILL DO.}
+\dean{I MOVED THIS FROM THE START OF THE DISCUSSION.
+ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
+We have derived a finite-order state-space representation of the neural field equations that allows inference to be performed efficiently.
+In addition, the mathematical formulation that we have presented scales well with the number of sensors.
+The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
 

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
some formatting for the graph and tables

@@
 and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives
-\begin{eqnarray}
+\begin{align}
     \label{eq:ReducedForm}
-    % \begin{split}
-	 \mathbf{x}_{t+1} &=& T_s\boldsymbol{\Gamma}^{-1}
+	 \mathbf{x}_{t+1} &= T_s\boldsymbol{\Gamma}^{-1}
 	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
-	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \nonumber \\
-	&\times& d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  
-	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
-	 % \end{split}
-\end{eqnarray}
+	 \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)d\mathbf{r}' d\mathbf{r} \boldsymbol{\theta}  \nonumber \\
+	& + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}.
+\end{align}
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the (\dean{Appendix}) supplementary material.
@@
 \dean{I MOVED THIS FROM THE START OF THE DISCUSSION.
-ANY OBJECTIONS?} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+ANY OBJECTIONS?} \ken{None} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
-We have derived a finite-order state-space representation of the neural field equations that allows inference to be performed efficiently.
-In addition, the mathematical formulation that we have presented scales well with the number of sensors.
+We have derived a finite-order state-space representation of the continuum neural field equations that allows inference to be performed efficiently.
+Importantly, the mathematical formulation that we have presented scales well with the number of sensors.
 The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
@@
 Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
-
-% This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
-The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
-Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship and supporting this research.
-
-\section*{References}
+The authors would also like to thank Dr.
+John Terry for insightful discussions and feedback.
+
 \bibliographystyle{unsrt} 
@@
 
-\section*{Figure Legends}
-%\begin{figure}[!ht]
-%\begin{center}
-%%\includegraphics[width=4in]{figure_name.2.eps}
-%\end{center}
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
-%should be left justified, as specified by the options to the caption 
-%package.
-%}
-%\label{Figure_label}
-%\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure1.pdf} 
-\end{center}
-\caption{{\bf Mexican-hat connectivity kernel.} The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
-The kernel decays asymptotically to zero.}
-\label{fig:Figure1}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure2.pdf} 
-\end{center}
-\caption{{\bf Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
-The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.}
-\label{fig:Figure2}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure3.pdf}
-\end{center}
-\caption{{\bf Example of the spatiotemporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant.
-(\textbf{B}) Data generated by the full neural field model from the first 5 sensors.
-(\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.}
-\label{fig:Figure3}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure4.pdf}
-\end{center}
-\caption{{\bf Spatial frequency analysis of the neural field}.
-(\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
-(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
-\label{fig:Figure4}
-\end{figure}
-
-\begin{figure*}[!ht] 
-\begin{center}
-\includegraphics{./Graph/pdf/Figure5.pdf}	
-\end{center}
-\caption{{\bf Spatial frequency analysis}.
-The dashed line shows the cutoff frequency (-3 dB point).
-(\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
-(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
-The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
-(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
-}
-\label{fig:Figure5}
-\end{figure*}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure6.pdf}
-\end{center}
-\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realisations.
-All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
-\label{fig:Figure6}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure7.pdf}
-\end{center}
-\caption{{\bf Histograms of the parameter estimates over 150 realisations}.
-The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
-(\textbf{A}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(\textbf{B}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-(\textbf{C}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.
-(\textbf{D}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.}
-\label{fig:Figure7}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure9.pdf} 
-\end{center}
-\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).} 
-\label{fig:Figure9}
-\end{figure}
-
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure10.pdf}
-\end{center}
-\caption{{\bf Examples of the actual and estimated neural fields and the error}.
-(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
-(\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
-(\textbf{C}) The error between the true and reconstructed fields.
-The error shows high frequency behaviour.}
-\label{fig:Figure10}
-\end{figure*}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure8_1.pdf}
-\end{center}
-\caption{{\bf Cross-section of connectivity kernel estimate}.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 50 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
-\label{fig:Figure8}
-\end{figure}
-
-% \begin{figure}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/OperatingRegions.pdf}
-% \end{center}
-% \caption{{\bf Operating Regions along the sigmoid}. The top graph is from the full model and the lower is from the reduced model.}
-% \label{fig:OperatingRegions}
-% \end{figure}
-
-% \begin{figure*}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/Figure11.pdf}
-% \end{center}
-% \caption{{\bf Hinton diagram of the RMSE of the kernel estimates}.
-Log of the RMSE of the kernel for different values of $\nu_{cm}$ and $\Delta_y$.
-Mean kernel estimates are obtained over 50 realisations in each case.}
-% \label{fig:Figure11}
-% \end{figure*}
-
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
-\end{center}
-\caption{{\bf RMSE of different kernel estimates}.
-Log of the RMSE of the kernel for different values of firing threshold, $v_0$, and the slope of the sigmoid, $\varsigma$.
-Mean kernel estimates are obtained over 50 realisations in each case.
-White spaces indicate cases where the kernel can not be estimated due to numerical problems.}
-\label{fig:Figure12}
-\end{figure*}
-
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/sigmoidfunctions.pdf}
-\end{center}
-\caption{{\bf Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.}
-\label{fig:sigmoidfunctions}
-\end{figure*}
-
-% \begin{figure*}[!ht]
-% \begin{center}
-% \includegraphics{./Graph/pdf/Figure13.pdf}
-% \end{center}
-% \caption{{\bf RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma^2_m$, distance between adjacent sensors is $\Delta_y=1.5$.
-Mean kernel estimates are obtained over 50 realisations in each case.}
-% \label{fig:Figure13}
-% \end{figure*}
-
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/Figure13.pdf}
-\end{center}
-\caption{{\bf RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma_m$, distance between adjacent sensors is $\Delta_y=1.5$.
-Mean kernel estimates are obtained over 50 realisations in each case.}
-\label{fig:Figure13}
-\end{figure*}
 \section*{Tables}
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{
@@
 \label{tab:Notation}
-\end{table}
-
+\end{table*}
+\clearpage
+\newpage
 \renewcommand{\arraystretch}{1.7}
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{
@@
 \label{tab:UKFAlgorithm}
-\end{table}
+\end{table*}
+\clearpage
+\newpage
 \renewcommand{\arraystretch}{1}
-
-\begin{table}[!ht]
+\begin{table*}[!ht]
 \caption{
@@
 \label{tab:Parameters}
-\end{table}
-
-% \begin{table}[!ht]
-% \centering
-% \caption{\bf{Estimation Results}}
-% % \begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2.5cm}|p{1.5cm}|}
-% \begin{tabular}{|c|c|c|c|}	
-% \hline
-% Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
-% \hline
-% % $\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
-% $\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
-% $\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
-% $\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
-% \hline
-% \end{tabular}
-% \begin{flushleft}Actual parameter values compared to mean parameter estimates obtained from the 100 Monte Carlo simulations.
-% \end{flushleft}
-% \label{tab:Parameters estimates}
-% \end{table}
-
-% \tiny{\begin{tabular}{lllllllllllllllllll}
-% \hline
-% & \multicolumn{6}{c|}{$\theta_0$}&\multicolumn{6}{c|}{$\theta_1$}&\multicolumn{6}{c|}{$\theta_2$}\\
-% \cline{2-19}
-%  &I&II&III&IV&V&VI&I&II&III&IV&V&VI&I&II&III&IV&V&VI\\
-% \hline\hline
-% Actual Value&$90$&$100$&$110$&$15$&$30$&$50$&$-80$&$-80$&$-80$&$0$&$0$&$0$&$5$&$5$&$5$&$0$&$0$&$0$\\
-% Mean Estimate&$103.86$&$101.75$&$98.9$&$35.67$&$40.43$&$61.43$&$-89.05$&$-81.00$&$-73.13$&$-18.16$&$-12.01$&$-15.03$&$5.23$&$4.75$&$4.37$&$0.81$&$0.35$&$0.27$\\
-% Std. Dev.&$23.14$&$21.29$&$16.57$&$14.82$&$0.73$&$0.65$\\
-% Bias (\%) &at her&\textbf{aici}& & \\
-% \hline
-% \end{tabular}}
-
-% \tiny{\begin{tabular}{lcccccccccccc}
-% Experiment&\multicolumn{4}{c}{I}&\multicolumn{4}{c}{II}&\multicolumn{4}{c}{III}\\
-%  Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
-% \hline\hline
-% Actual Value&$90$&$-80$&$5$&$0.9$&$100$&$-80$&$5$&$0.9$&$110$&$-80$&$5$&$0.9$\\
-% Mean Estimate&$103.86$&$-89.05$&$5.23$&$0.923$& $101.75$&$-81.00$&$4.76$&$0.924$&$98.90 $&$-73.13$&$4.37$&$0.925$\\
-% Std. Dev.&$23.14$&$16.57$&$0.74$&$0.003$ & $21.30$&$14.82$&$0.65$&$0.003$&$16.48$& $11.72$&$0.54$&$0.003$\\
-% Bias (\%)& $15.4$&$11.31$&$4.6$ &$2.56$ &$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
-% \end{tabular}\label{tab:MexicanHatKernelResults}}
-
-\begin{table}[!ht]
+\end{table*}
+\clearpage
+\newpage
+\begin{table*}[!ht]
 	\caption{
@@
 \end{tabular}\label{tab:MexicanHatKernelResults}
-\end{table}
-
-% \tiny{\begin{tabular}{lcccccccccccc}
-% Experiment&\multicolumn{4}{c}{IV}&\multicolumn{4}{c}{V}&\multicolumn{4}{c}{VI}\\
-%  Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
-% \hline\hline
-% Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
-% Mean Estimate&$35.68$&$-18.16$&$0.81$&$0.923$&   $40.43$&$-12.01$&$ 0.35$&$0.924$&        $61.46$&$-15.03$&$0.27$&$0.924$\\
-% Std. Dev.&$16.72$&$11.77$&$0.53$&$0.002$&		$11.47$&$7.8$&$0.36$&$0.003$&	$11.51$&$7.56$&$0.29$&$0.003$\\
-% Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
-% \end{tabular}\label{tab:GaussianKernelResults}}
-
-\begin{table}[!ht]
+\end{table*}
+\clearpage
+\newpage
+\begin{table*}[!ht]
 	\caption{
@@
 \end{tabular}\label{tab:GaussianKernelResults}
-\end{table}
-
+\end{table*}
+
+\newpage
+\clearpage
+\section*{Figure Legends}
+{\bf Figure 1.
+Mexican-hat connectivity kernel.} The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+The kernel decays asymptotically to zero.
+
+{\bf Figure 2.
+Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
+The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.
+
+{\bf Figure 3.
+Example of the spatiotemporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant.
+(\textbf{B}) Data generated by the full neural field model from the first 5 sensors.
+(\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.
+
+{\bf Figure 4.
+Spatial frequency analysis of the neural field}.
+(\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
+(\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition.
+The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.
+
+{\bf Figure 5.
+Spatial frequency analysis}.
+The dashed line shows the cutoff frequency (-3 dB point).
+(\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
+(\textbf{B}) The spatial frequency response of a one-dimensional model sensor.
+The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics.
+(\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.
+
+{\bf Figure 6.
+Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realisations.
+All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.
+
+{\bf Figure 7.
+Histograms of the parameter estimates over 150 realisations}.
+The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
+(\textbf{A}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(\textbf{B}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+(\textbf{C}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.
+(\textbf{D}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant.
+
+{\bf Figure 8. Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).
+
+{\bf Figure 9.
+Examples of the actual and estimated neural fields and the error}.
+(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
+(\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
+(\textbf{C}) The error between the true and reconstructed fields.
+The error shows high frequency behaviour.
+
+{\bf Figure 10.
+Cross-section of connectivity kernel estimate}.
+The actual kernel is shown by the solid line, the mean kernel estimate (over 50 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.
+
+{\bf Figure 11.
+RMSE of different kernel estimates}.
+Log of the RMSE of the kernel for different values of firing threshold, $v_0$, and the slope of the sigmoid, $\varsigma$.
+Mean kernel estimates are obtained over 50 realisations in each case.
+White spaces indicate cases where the kernel can not be estimated due to numerical problems.
+
+{\bf Figure 12. Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.
+
+{\bf Figure 13.
+RMSE of the kernel estimates}.
+RMSE of the kernel for different values of sensor width, $\sigma_m$, distance between adjacent sensors is $\Delta_y=1.5$.
+Mean kernel estimates are obtained over 50 realisations in each case.
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure1.pdf} 
+\end{center}
+\caption{{\bf Fig. 1}}
+\label{fig:Figure1}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure2.pdf} 
+\end{center}
+\caption{{\bf Fig. 2}}
+\label{fig:Figure2}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure3.pdf}
+\end{center}
+\caption{{\bf Fig. 3}} 
+\label{fig:Figure3}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure4.pdf}
+\end{center}
+\caption{{\bf Fig. 4}}
+\label{fig:Figure4}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht] 
+\begin{center}
+\includegraphics{./Graph/pdf/Figure5.pdf}	
+\end{center}
+\caption{{\bf Fig. 5}}
+\label{fig:Figure5}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure6.pdf}
+\end{center}
+\caption{{\bf Fig. 6}}
+\label{fig:Figure6}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure7.pdf}
+\end{center}
+\caption{{\bf Fig. 7}} 
+\label{fig:Figure7}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure9.pdf} 
+\end{center}
+\caption{{\bf Fig. 8}} 
+\label{fig:Figure9}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure10.pdf}
+\end{center}
+\caption{{\bf Fig. 9}}
+\label{fig:Figure10}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure8_1.pdf}
+\end{center}
+\caption{{\bf Fig. 10}}
+\label{fig:Figure8}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
+\end{center}
+\caption{{\bf Fig. 11}}
+\label{fig:Figure12}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/sigmoidfunctions.pdf}
+\end{center}
+\caption{{\bf Fig. 12}}
+\label{fig:sigmoidfunctions}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/Figure13.pdf}
+\end{center}
+\caption{{\bf Fig. 12}}
+\label{fig:Figure13}
+\end{figure*}
+\clearpage
+\newpage
+\appendix
+\section{Time Discretisation of Neural Field Model}
+\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
+To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by
+\begin{align}
+	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
+&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
+\end{align}
+For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
+\begin{equation}
+	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}.
+\end{equation}
+Now making simplifications, the discrete time form of the model is 
+\begin{equation}
+	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'},
+\end{equation}
+where $\xi = 1 - T_s \zeta$.
+
+\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
+In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
+Therefore, $\mathbf{e}_t$ is also normally distributed.
+From equation~\ref{eq:Wt}, the state disturbance vector is defined as
+\begin{equation}
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
+\end{equation}
+The expected value of $\mathbf e_t$ is given by 
+\begin{equation}
+	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
+\end{equation}
+The covariance of $\mathbf{e}_t$ is 
+\begin{align}
+	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
+&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
+\end{align}
+
+\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
+This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
+We define an \textit{n}-dimensional Gaussian  centred at the origin as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
+\end{equation}
+Now applying the \textit{n}-dimensional Fourier transform yields
+\begin{align}\label{eq:AppendixGaussianFT}
+ \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{align}
+Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+\begin{equation}\label{eq:IntegralOfGaussian}
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
+\end{equation}
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation} 
+where 
+\begin{equation}
+	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
+\begin{equation}
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
+\end{equation}
+since the maximum of the Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Solving for $\sigma_{\nu}^2$, we get
+\begin{equation}
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
+\end{equation}
+
+\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
+In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
+Consider two Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
+\begin{equation}\label{eq:FTTwoGaussianMultiplication}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform.
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+\begin{align}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
+ &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{align}
+Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
+\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
+\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
+\end{align}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+
+\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
+The derivation in this section was used for calculating the matrix $\Gamma$ from equation~\ref{eq:DefGamma}.
+The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
+\begin{equation}\label{eq:InofGaussianDefinition}
+\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
+\end{equation}
+A Gaussian basis function is symmetric with respect to its centre so
+\begin{equation}\label{eq:GaussianSymmetry}
+ \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$, equation~\ref{eq:GaussianSymmetry} becomes
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
+ \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
+\begin{align}
+\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
+\end{align}
+Using the derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
+\begin{align}
+ \varphi_i\otimes\varphi_j&=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
+\end{align}
+This completes the derivation.
+
+\section{Observation Kernel}
+The Gaussian shape of the observation kernel was verified experimentally.
+This was achieved by moving a dipole across a recording electrode submerged in saline.
+A photograph through a microscope of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
+The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
+The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
+The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
+The twisted wire electrode and the Utah array were co-registered visually using the microscope.
+The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
+The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
+To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
+The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
+\begin{equation}
+	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
+\end{equation}
+where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
+Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
+A Gaussian fitted to the amplitudes is also shown.
+The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
 \end{document}

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
deleted all the figures
changed figure to Fig

@@
 The connectivity kernel is typically a ``Mexican hat'' or ``wizard hat'' function, which describes local excitation and surround inhibition.
-An example of the Mexican hat connectivity kernel used in this paper is shown in Figure~\ref{fig:Figure1}.
+An example of the Mexican hat connectivity kernel used in this paper is shown in Fig.~\ref{fig:Figure1}.
 To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
@@
 \end{equation}
-where $\sigma_{\phi}$ is the basis function width parameter. An example of a one-dimensional field decomposition is given in Figure~\ref{fig:Figure2}.
+where $\sigma_{\phi}$ is the basis function width parameter. An example of a one-dimensional field decomposition is given in Fig.~\ref{fig:Figure2}.
 
@@
 When generating the simulated data, we assumed free boundary conditions for the neural field.
-An example of the simulated field at a single point in time can be seen in Figure~\ref{fig:Figure3}(A).
-Figure~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Figure~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
+An example of the simulated field at a single point in time can be seen in Fig.~\ref{fig:Figure3}(A).
+Fig.~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Fig.~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
 %The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field.
-Figure~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Figure~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
+Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
 The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz.
@@
 
-The spatial frequency of the observed field is shown in Figure~\ref{fig:Figure5}(A).
+The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A).
 The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point).
 The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors.
-The spatial frequency response of the sensors can be seen in Figure~\ref{fig:Figure5}(B).
+The spatial frequency response of the sensors can be seen in Fig.~\ref{fig:Figure5}(B).
 
@@
 Given the basis function width, the decomposition is able to represent the field up to the spatial cutoff frequency of $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
-The result of the band-limiting effect in the field reconstruction can be observed when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C).
+The result of the band-limiting effect in the field reconstruction can be observed when comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
 Given the spatial cutoff frequency of the basis functions and the basis function separation the oversampling parameter is $\rho_{\phi}\approx 1.67$.
@@
 This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:Figure5}(C).
-This band-limiting effect of the basis function decomposition can be observed when comparing Figure~\ref{fig:Figure4}(A) to Figure~\ref{fig:Figure4}(B).
+The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C).
+This band-limiting effect of the basis function decomposition can be observed when comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
 
@@
 Ten iterations of the estimation algorithm were used to ensure that the parameter estimates converged.
-Figure~\ref{fig:Figure6} shows the rate of convergence, confirming that the algorithm converged to steady parameter values, with the changes in the parameter errors (between consecutive iterations) falling to less than $10^{-4}$ after 6 iterations.
-
-Histograms of the parameter estimates obtained over the 150 realisations are shown in Figure~\ref{fig:Figure7}.
+Fig.~\ref{fig:Figure6} shows the rate of convergence, confirming that the algorithm converged to steady parameter values, with the changes in the parameter errors (between consecutive iterations) falling to less than $10^{-4}$ after 6 iterations.
+
+Histograms of the parameter estimates obtained over the 150 realisations are shown in Fig.~\ref{fig:Figure7}.
 In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9} with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Fig.~\ref{fig:Figure9} with the $95~\%$ confidence interval.
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
-The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}.
+The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Fig.~\ref{fig:Figure10}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field, shown in Figure~\ref{fig:Figure10}(A), but is missing the higher-frequency detail, which can be see in the error shown in Figure~\ref{fig:Figure10}(C).
+It can be seen in Fig.~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field, shown in Fig.~\ref{fig:Figure10}(A), but is missing the higher-frequency detail, which can be see in the error shown in Fig.~\ref{fig:Figure10}(C).
 
@@
 To study the robustness of the estimation algorithm, the performance was evaluated for various connectivity kernel parameters.
-The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}.
-For Figure~\ref{fig:Figure8}(A-C) the Mexican hat connectivity kernels were used.
+The reconstructed connectivity kernels from the estimated parameters are shown in Fig.~\ref{fig:Figure8}.
+For Fig.~\ref{fig:Figure8}(A-C) the Mexican hat connectivity kernels were used.
 For each subset of parameters, the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
@@
 For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
-However, in Figure~\ref{fig:Figure8}(D-F) the kernel support in the estimator differed from the actual data.
+However, in Fig.~\ref{fig:Figure8}(D-F) the kernel support in the estimator differed from the actual data.
 In these cases the data sets were generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
@@
 
-Figure~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy.
+Fig.~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy.
 The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
@@
 The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
-From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
+From Fig.~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
 This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
@@
 However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function.
-This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted.
+This is illustrated in Fig.~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Fig.~\ref{fig:sigmoidfunctions} are plotted.
 This appears to have a detrimental effect on the estimation accuracy.
@@
 The accuracy of the estimation algorithm was tested for different observation kernels by varying the width parameter, $\sigma_m$.
-Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
+Fig.~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
 As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
@@
 On the other hand, for the very wide kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the high frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
-Thus, as indicated in Figure~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
+Thus, as indicated in Fig.~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
 
@@
 \subsection{Implications for Experimental Design}
-As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
+As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
 The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
@@
 \bibliography{BrainIDE}
-
 \section*{Tables}
-
 \begin{table*}[!ht]
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure1.pdf} 
+\includegraphics{./Graph/pdf/fig1.pdf} 
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure2.pdf} 
+\includegraphics{./Graph/pdf/fig2.pdf} 
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure3.pdf}
+\includegraphics{./Graph/pdf/fig3.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure4.pdf}
+\includegraphics{./Graph/pdf/fig4.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure5.pdf}	
+\includegraphics{./Graph/pdf/fig5.pdf}	
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure6.pdf}
+\includegraphics{./Graph/pdf/fig6.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure7.pdf}
+\includegraphics{./Graph/pdf/fig7.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure9.pdf} 
+\includegraphics{./Graph/pdf/fig8.pdf} 
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure10.pdf}
+\includegraphics{./Graph/pdf/fig9.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure8_1.pdf}
+\includegraphics{./Graph/pdf/fig10.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
+\includegraphics{./Graph/pdf/fig11.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/sigmoidfunctions.pdf}
+\includegraphics{./Graph/pdf/fig12.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/Figure13.pdf}
+\includegraphics{./Graph/pdf/fig13.pdf}
 \end{center}
-\caption{{\bf Fig. 12}}
+\caption{{\bf Fig. 13}}
 \label{fig:Figure13}
@@
 This was achieved by moving a dipole across a recording electrode submerged in saline.
-A photograph through a microscope of the submerged electrodes can be seen in Figure~\ref{fig:SensorAndSource}.
+A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}.
 The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
@@
 where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
-Figure~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
+Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
 A Gaussian fitted to the amplitudes is also shown.

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
minor changes

@@
 
-The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation.
+\parham{The additive form of the unscented Rauch-Tung-Striebel smoother} (URTSS)~\cite{Sarkka2010} is used for the state estimation.
 The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
-It should be noted that the disturbance, $\mathbf{e}_t$, and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive.
-Therefore, the additive form of the URTSS is used.
 
@@
 \end{center}
-\caption{{\bf Fig. 1}}
+\caption{}
 \label{fig:Figure1}
@@
 \end{center}
-\caption{{\bf Fig. 2}}
+\caption{}
 \label{fig:Figure2}
@@
 \end{center}
-\caption{{\bf Fig. 3}} 
+\caption{} 
 \label{fig:Figure3}
@@
 \end{center}
-\caption{{\bf Fig. 4}}
+\caption{}
 \label{fig:Figure4}
@@
 \end{center}
-\caption{{\bf Fig. 5}}
+\caption{}
 \label{fig:Figure5}
@@
 \end{center}
-\caption{{\bf Fig. 6}}
+\caption{}
 \label{fig:Figure6}
@@
 \end{center}
-\caption{{\bf Fig. 7}} 
+\caption{} 
 \label{fig:Figure7}
@@
 \end{center}
-\caption{{\bf Fig. 8}} 
+\caption{} 
 \label{fig:Figure9}
@@
 \end{center}
-\caption{{\bf Fig. 9}}
+\caption{}
 \label{fig:Figure10}
@@
 \end{center}
-\caption{{\bf Fig. 10}}
+\caption{}
 \label{fig:Figure8}
@@
 \end{center}
-\caption{{\bf Fig. 11}}
+\caption{}
 \label{fig:Figure12}
@@
 \end{center}
-\caption{{\bf Fig. 12}}
+\caption{}
 \label{fig:sigmoidfunctions}
@@
 \end{center}
-\caption{{\bf Fig. 13}}
+\caption{}
 \label{fig:Figure13}

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
slightly editted kens bit on the freq analysis basis function bit

@@
 
-\documentclass[5p]{elsarticle}
+\documentclass[5p,authoryear]{elsarticle}
 % \documentclass[12pt]{iopart} 
@@
 
-\parham{The additive form of the unscented Rauch-Tung-Striebel smoother} (URTSS)~\cite{Sarkka2010} is used for the state estimation.
+The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
 The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 
-\ken{revised new bit}
-
-To reduce the computational demand of the estimation procedure, the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
+As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen the account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure.
+In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
+The result of the band-limiting effect in the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
+This effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C).
 Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen.
-Therefore for an equally spaced grid of basis functions over the full spatial domain being considered, a $9\times9$ grid was required to decompose the field, which resulted in $81$ states.
-The other parameter of the basis functions, $\sigma_{\phi}^2$, is set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.
-
-\ken{how's that?}
-
-\dean{-------new bit start ------------}
-
-Due to the limitations imposed by the computationally demanding estimation procedure we chose to use a $9\times9$ grid of Gaussian basis functions to decompose the field, which resulted in $81$ states.
-Given the spatial domain, this yielded a basis function separation of $\Delta_{\phi}=2.5$~mm.
-The basis function width parameter was chosen such that a smooth representation of the field could be achieved with this arrangement, where $\sigma_{\phi}^2=2.5$.
-Given the basis function width, the decomposition is able to represent the field up to the spatial cutoff frequency of $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C).
-The result of the band-limiting effect in the field reconstruction can be observed when comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
-Given the spatial cutoff frequency of the basis functions and the basis function separation the oversampling parameter is $\rho_{\phi}\approx 1.67$.
-
-\dean{-------new bit end ------------}
-
-\dean{-------olde bit start ------------}
-
-Using an oversampling parameter of $\rho_{\phi}=1$, the maximum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}).
-The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
-
-Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$.
-This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}.
-The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C).
-This band-limiting effect of the basis function decomposition can be observed when comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
-
-\dean{-------olde bit end ------------}
+Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain, an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.
+%The other parameter of the basis functions, $\sigma_{\phi}^2$, was set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.
 
@@
 
-\bibliographystyle{unsrt} 
+\bibliographystyle{elsarticle-harv} 
 \bibliography{BrainIDE}

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
added cross refs to appendix

@@
 The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
-To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors so a comparison can be made between estimated and true parameters.
+To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors enabling a comparison between the estimated and true parameters.
 To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model using a basis function decomposition to form a finite-dimensional state-space model.
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see the supplementary (\dean{Appendix}) material for derivation) giving 
+To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
 \begin{equation}
@@
 where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 The disturbance is added to account for model uncertainty and unmodelled inputs.
@@
 However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
-An experiment supporting this was performed and the results are shown in \dean{Appendix?}.
-Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry is defined by
+An experiment supporting this was performed and the results are shown in \ref{App:ObsKernelExperiment}.
+Therefore, in this study the observation kernel, $m(\mathbf{r}-\mathbf{r}')$, that governs the sensor pick-up geometry is defined by the Gaussian
 \begin{equation}
@@
 \end{align}
-The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in the (\dean{Appendix}) supplementary material.
+The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}.
 Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
@@
 where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a $n_x \times n_{\theta}$ matrix, where $n_x$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
-This matrix is defined analytically (see the supplementary (\dean{Appendix}) material for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
+This matrix is defined analytically (see \ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
 Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
@@
 \end{equation}
-which is a zero mean normally distributed white noise process with covariance (see the supplementary material \dean{(Appendix)} for the derivation)
+which is a zero mean normally distributed white noise process with covariance (see \ref{App:ColoredNoise} for the derivation)
 \begin{equation}
@@
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-Again, applying Shannon's sampling theorem, the minimum distance between basis functions must satisfy
+Again, applying Shannon's sampling theorem, the minimum distance between basis functions to accurately reconstruct the neural field must satisfy
 \begin{equation}\label{eq:BasisFunctionSeparation}
@@
 This ensures that the basis functions can represent the neural field with frequency content up to $\boldsymbol\nu_{cy}$.
-Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in the supplementary material (\dean{Appendix}).
+Derivations for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in \ref{App:FrequencyAnalysis}.
 
@@
 
-\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
-In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
-We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
-Therefore, $\mathbf{e}_t$ is also normally distributed.
-From equation~\ref{eq:Wt}, the state disturbance vector is defined as
-\begin{equation}
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
-\end{equation}
-The expected value of $\mathbf e_t$ is given by 
-\begin{equation}
-	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
-\end{equation}
-The covariance of $\mathbf{e}_t$ is 
-\begin{align}
-	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{align}
-
-\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
-This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
-We define an \textit{n}-dimensional Gaussian  centred at the origin as
-\begin{equation}
- \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
-\end{equation}
-Now applying the \textit{n}-dimensional Fourier transform yields
-\begin{align}\label{eq:AppendixGaussianFT}
- \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
-&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{align}
-Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{equation}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
-\end{equation}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation} 
-where 
-\begin{equation}
-	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{equation}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{equation}
-since the maximum of the Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Solving for $\sigma_{\nu}^2$, we get
-\begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
-\end{equation}
-
-\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
-\begin{equation}\label{eq:FTTwoGaussianMultiplication}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{equation}
-where $\mathcal{F}$ denotes the Fourier transform.
-Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
-\begin{align}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
- &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
-\end{align}
-Taking the inverse Fourier transform, the convolution becomes
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
-\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
-\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
-\end{align}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+\section{Observation Kernel}\label{App:ObsKernelExperiment}
+The Gaussian shape of the observation kernel was verified experimentally.
+This was achieved by moving a dipole across a recording electrode submerged in saline.
+A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}.
+The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
+The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
+The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
+The twisted wire electrode and the Utah array were co-registered visually using the microscope.
+The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
+The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
+To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
+The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
+\begin{equation}
+	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
+\end{equation}
+where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
+Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
+A Gaussian fitted to the amplitudes is also shown.
+The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
 
@@
 
-\section{Observation Kernel}
-The Gaussian shape of the observation kernel was verified experimentally.
-This was achieved by moving a dipole across a recording electrode submerged in saline.
-A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}.
-The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
-The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m.
-The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m.
-The twisted wire electrode and the Utah array were co-registered visually using the microscope.
-The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s.
-The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
-To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
-The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
-\begin{equation}
-	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
-\end{equation}
-where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
-Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
-A Gaussian fitted to the amplitudes is also shown.
-The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
+\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
+In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
+Consider two Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
+\begin{equation}\label{eq:FTTwoGaussianMultiplication}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform.
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+\begin{align}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
+ &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{align}
+Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
+\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
+\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
+\end{align}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+
+\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
+In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
+Therefore, $\mathbf{e}_t$ is also normally distributed.
+From equation~\ref{eq:Wt}, the state disturbance vector is defined as
+\begin{equation}
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
+\end{equation}
+The expected value of $\mathbf e_t$ is given by 
+\begin{equation}
+	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
+\end{equation}
+The covariance of $\mathbf{e}_t$ is 
+\begin{align}
+	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
+&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
+\end{align}
+
+\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
+This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
+We define an \textit{n}-dimensional Gaussian  centred at the origin as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
+\end{equation}
+Now applying the \textit{n}-dimensional Fourier transform yields
+\begin{align}\label{eq:AppendixGaussianFT}
+ \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{align}
+Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+\begin{equation}\label{eq:IntegralOfGaussian}
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
+\end{equation}
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation} 
+where 
+\begin{equation}
+	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
+\begin{equation}
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
+\end{equation}
+since the maximum of the Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Solving for $\sigma_{\nu}^2$, we get
+\begin{equation}
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
+\end{equation}
+
 \end{document}

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
small edits to frequency analysis results

@@
 In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
-The result of the band-limiting effect in the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
-This effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C).
-Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen.
-Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain, an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.
+The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
+This effect is due to the spatial frequency response of the basis functions, which is shown in Fig.~\ref{fig:Figure5}(C).
+Due to the slow roll-off in the frequency response of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen.
+Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.
 %The other parameter of the basis functions, $\sigma_{\phi}^2$, was set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
added elsarticle
changed the authoryear setting

@@
 
-\documentclass[5p,authoryear]{elsarticle}
+\documentclass[5p]{elsarticle}
 % \documentclass[12pt]{iopart} 
@@
 The sensors were spaced on a $14 \times 14$ square grid and the sensor width was set to $\sigma^2_m = 0.81$.
-This provides a width of 1.5~mm at half the maximum amplitude of the sensor kernel.
+This provides a width of 1.5~mm at half the maximum amplitude of the observation kernel.
 The distance between sensors was set to $\Delta_y = 1.5$~mm.
@@
 The first experiment evaluated the estimation performance using a Monte Carlo approach for a single set of parameters.
-Using this experiment we demonstrate convergence of the algorithm, show the distribution of estimated parameters and the accuracy of the state estimates for a single set of parameters.
+In this experiment we demonstrate convergence of the algorithm, show the distribution of estimated parameters and the accuracy of the state estimates for a single set of parameters.
 The second experiment evaluated the performance with a selection of different connectivity kernel parameters.
@@
 For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters.
-However, the time constant parameter, $\xi$, is outside the estimate distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
+However, the time constant parameter, $\xi$, is outside the estimated distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
 We attribute this small bias to the loss of the high frequency components in the smoother estimated field with respect to the actual field.
-These results thus indicate that choosing to limit the frequency content of the reconstructed neural field has only minor effects on the accuracy of the estimated kernel while allowing for significant gains in the computational demand.
+These results indicate that choosing to limit the frequency content of the reconstructed neural field has only minor effects on the accuracy of the estimated kernel while allowing for significant gains in the computational demand.
 
@@
 This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
-
-\ken{what I would write}
-
 For example, when the sigmoid slope is very gentle, most of the neural activity falls in the central, nearly linear region of the sigmoid, thus having minor effects on the estimation procedure.
@@
 
-\ken{what do you think?}
-
-\dean{PLEASE HELP TO FILL THIS SECTION IN. ANYTHING WILL DO.}
-..\dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function.
-However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function.
-This is illustrated in Fig.~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Fig.~\ref{fig:sigmoidfunctions} are plotted.
-This appears to have a detrimental effect on the estimation accuracy.
-
 \subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
@@
 Fig.~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
-As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter.
-
-\ken{tried to make it a little more straight forward}
-
-When the observation kernel is too narrow, high frequency components in the neural field are sampled.
-These high frequency components result in aliasing errors in the estimated field thus affecting the kernel estimation accuracy.
-On the other hand, for the very wide kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the high frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
-Thus, as indicated in Fig.~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
-
-\ken{that ok?}
-
-When the observation kernel is too narrow, a small amount of high spatial frequency information is still present but not adequately sampled by the observation function, since the field is not exactly band-limited.
-Therefore, a small amount of aliasing occurs which results in the estimation error.
-When the observation kernel width is increased, the high spatial frequency information that is not adequately sampled is filtered more strongly by the observation kernel and the error decreases.
-However, as expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.
+As the theory presented earlier in Section~\ref{SpectralAnalysisSection} states, the observation kernel acts as a spatial filter.
+
+When the observation kernel is too narrow, high frequency components in the neural field are present but under sampled.
+These high frequency components result in aliasing errors in the estimated field, thus affecting the kernel estimation accuracy.
+On the other hand, for the very wide observation kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the important frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
+As indicated in Fig.~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
 
@@
 \bibliography{BrainIDE}
+
 \section*{Tables}
@@
 	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
-	I and II-A &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
+
+	I and II-A & $\theta_0$ & $100$ & 101.75 & $21.30$ & $1.75$ \\
+	& $\theta_1$ & -80 & -81.00 & $14.82$ & $1.25$ \\
+	& $\theta_2$ & 5 & $4.76$ & $0.65$ & $4.8$ \\
+	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
+
+	II-B &	$\theta_0$ & $90$ & 103.86 & 23.14 & 15.4 \\
 	& $\theta_1$ & -80 & -89.05 & 16.57 & 11.31 \\
@@
 	& $\xi$ & 0.9 & 0.923 & 0.003 & 2.56 \\ \hline
-
-	II-B & $\theta_0$ & $100$ & 101.75 & $21.30$ & $1.75$ \\
-	& $\theta_1$ & -80 & -81.00 & $14.82$ & $1.25$ \\
-	& $\theta_2$ & 5 & $4.76$ & $0.65$ & $4.8$ \\
-	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
 

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
Americanized spelling

@@
 This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
-This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+This marks the first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
 
@@
 \end{equation}
-To arrive at the integro-difference equation (IDE) form of the model, we discretise time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
+To arrive at the integro-difference equation (IDE) form of the model, we discretize time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
 \begin{equation}
@@
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
-Once initialised, at each iteration the sequence of estimated state vectors is used to update the parameter set.
+Once initialized, at each iteration the sequence of estimated state vectors is used to update the parameter set.
 The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
 The procedure stops when the parameters converge.
-The algorithm is initialised using a bounded random state vector sequence, guaranteeing that the initial estimated parameter set forms a stable kernel.
+The algorithm is initialized using a bounded random state vector sequence, guaranteeing that the initial estimated parameter set forms a stable kernel.
 
@@
 Although the system is nonlinear, the parameters of the system are linear with respect to the state.
-This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
+This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimizes the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence.
 To create the least squares parameter estimator, we first define the $n_x \times n_{\theta}$ matrix
@@
 Even when using a known input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
-By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
+By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realisations), such that a distribution of the parameter estimates and resulting connectivity kernels can be formed.
 
@@
 Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
-In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data.
+In addition, the frequency analysis highlights the relationship between the width of the sensors and the information in the data.
 This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.
@@
 
-The isotropy of the connectivity kernel basis functions means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions.
+The isotropy of the connectivity kernel basis functions means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the field basis functions.
 This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
@@
 \section{Conclusion}
-\dean{I MOVED THIS FROM THE START OF THE DISCUSSION.
-ANY OBJECTIONS?} \ken{None} This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
+This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data.
 In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred.
@@
 \begin{equation}
-	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
-\end{equation}
-where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.
+	a = \frac{1}{T}\sum_n{\sqrt{(y_t-\mathcal{H}y_t^2}}
+\end{equation}
+where $\mathcal{H}$ denotes the Hilbert transform operator, $t$ indexes samples and $T$ is the total number of samples in the time series.
 Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
deleted sigmoid figure
corrected cross referencing

@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Fig.~\ref{fig:Figure9} with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Fig.~\ref{fig:Figure10} with the $95~\%$ confidence interval.
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
-The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Fig.~\ref{fig:Figure10}.
+The error in the reconstructed field is again mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Fig.~\ref{fig:Figure9}.
 The figure shows a snapshot at a single time instant of the true neural field, the estimated field, and the corresponding error, which is the difference between the true and estimated neural fields.
-It can be seen in Fig.~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field, shown in Fig.~\ref{fig:Figure10}(A), but is missing the higher-frequency detail, which can be see in the error shown in Fig.~\ref{fig:Figure10}(C).
+It can be seen in Fig.~\ref{fig:Figure9}(B) that the estimated field contains the basic structure of the true field, shown in Fig.~\ref{fig:Figure9}(A), but is missing the higher-frequency detail, which can be see in the error shown in Fig.~\ref{fig:Figure9}(C).
 
@@
 To study the robustness of the estimation algorithm, the performance was evaluated for various connectivity kernel parameters.
-The reconstructed connectivity kernels from the estimated parameters are shown in Fig.~\ref{fig:Figure8}.
-For Fig.~\ref{fig:Figure8}(A-C) the Mexican hat connectivity kernels were used.
+The reconstructed connectivity kernels from the estimated parameters are shown in Fig.~\ref{fig:Figure10}.
+For Fig.~\ref{fig:Figure10}(A-C) the Mexican hat connectivity kernels were used.
 For each subset of parameters, the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
@@
 For each of the Mexican hat connectivities, the support of the kernel was assumed to be known.
-However, in Fig.~\ref{fig:Figure8}(D-F) the kernel support in the estimator differed from the actual data.
+However, in Fig.~\ref{fig:Figure10}(D-F) the kernel support in the estimator differed from the actual data.
 In these cases the data sets were generated using a single positive (excitatory) Gaussian kernel, as seen by the solid line in each of the subplots of the figure.
@@
 
-Fig.~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy.
+Fig.~\ref{fig:Figure11} demonstrates the effect of the sigmoid parameters on the estimation accuracy.
 The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$.
@@
 The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
-From Fig.~\ref{fig:Figure12} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
+From Fig.~\ref{fig:Figure11} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
 This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
@@
 The accuracy of the estimation algorithm was tested for different observation kernels by varying the width parameter, $\sigma_m$.
-Fig.~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
+Fig.~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths.
 As the theory presented earlier in Section~\ref{SpectralAnalysisSection} states, the observation kernel acts as a spatial filter.
@@
 On the other hand, for the very wide observation kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the important frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
-As indicated in Fig.~\ref{fig:Figure13}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
+As indicated in Fig.~\ref{fig:Figure12}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
 
@@
 \subsection{Implications for Experimental Design}
-As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
+As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure9}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
 The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
@@
 \caption{} 
-\label{fig:Figure9}
+\label{fig:Figure8}
 \end{figure*}
@@
 \caption{}
-\label{fig:Figure10}
+\label{fig:Figure9}
 \end{figure*}
@@
 \caption{}
-\label{fig:Figure8}
+\label{fig:Figure10}
 \end{figure*}
@@
 \caption{}
-\label{fig:Figure12}
+\label{fig:Figure11}
 \end{figure*}
@@
 \caption{}
-\label{fig:sigmoidfunctions}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{./Graph/pdf/fig13.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure13}
+\label{fig:Figure12}
 \end{figure*}

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
miror corrections

@@
 \begin{keyword}
-	keyword1 \sep keyword2
+	\parham{keyword1 \sep keyword2}
 %% keywords here, in the form: keyword \sep keyword
@@
 This matrix is defined analytically (see \ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
-Substituting equation~\ref{eq:DefPsi} into equation~\ref{eq:ReducedForm} gives
+\parham{Substituting $\boldsymbol{\Psi}(\mathbf{r}')$ into equation~\ref{eq:ReducedForm} gives}
 \begin{align}
@@
 The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
-The procedure stops when the parameters converge.
+The procedure stops when the \parham{parameter estimates} converge.
 The algorithm is initialized using a bounded random state vector sequence, guaranteeing that the initial estimated parameter set forms a stable kernel.
@@
 \begin{align}\label{eq:sigmapoints1}
-	\mathcal X_{0}&=\bar x \\
-	\mathcal X_{i}&=\bar x+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
-	\mathcal X_{i}&=\bar x-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
+	\mathcal X_{0}&=\mathbf{\bar x} \\
+	\mathcal X_{i}&= \mathbf{\bar x}+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
+	\mathcal X_{i}&=\mathbf{\bar x}-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
 \end{align}
-where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space.
+where $\mathbf{\bar x}$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space.
 The total number of sigma points is $2n_x+1$.
@@
 \end{equation}
-where the constant $\alpha$ determines the spread of the sigma points and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
+where the constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$, and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
 
@@
 \end{small}
-Following this, the LS parameter estimates~\cite{Kailath2000}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates~\cite{Ljung1985}, $ \hat{\mathcal{W}}$, are
 \begin{equation}

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
miror corrections

@@
 \subsection{Implications for Experimental Design}
-As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure9}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
+As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
 The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.

### 2010-11-20 ltx/first_order_framework/LaTeX_Manuscript.tex
added research highlights

@@
 % Title must be 150 characters or less
-\title{A Data-Driven Framework for Neural Field Modelling}
+\title{A Data-Driven Framework for Neural Field Modeling}
 
@@
 \begin{keyword}
-	\parham{keyword1 \sep keyword2}
+	Neural Field Model \sep Nonlinear Estimation \sep Intracortical Connectivity \sep Nonlinear Dynamics
 %% keywords here, in the form: keyword \sep keyword
@@
 
-Perhaps the most accepted estimation framework for neural mass models is dynamical causal modelling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
+Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
@@
 
-Modelling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (MVAR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+Modeling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (MVAR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
 
 In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
-This work provides a fundamental link between the theoretical advances in neural field modelling and electrophysiological data.
+This work provides a fundamental link between the theoretical advances in neural field modeling and electrophysiological data.
 The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
@@
 \subsection{Integro-Difference Equation Neural Field Model}
-The combination of modelling techniques in this paper leads to a large amount of notation, so a reference of the symbols used is provided in Table~\ref{tab:Notation}.
+The combination of modeling techniques in this paper leads to a large amount of notation, so a reference of the symbols used is provided in Table~\ref{tab:Notation}.
 The model relates the average number of action potentials $g(\mathbf{r},t)$ arriving at time $t$ and position $\mathbf{r}$ to the local post-synaptic membrane voltage $v(\mathbf{r},t)$.
@@
 This matrix is defined analytically (see \ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
-\parham{Substituting $\boldsymbol{\Psi}(\mathbf{r}')$ into equation~\ref{eq:ReducedForm} gives}
+Substituting $\boldsymbol{\Psi}(\mathbf{r}')$ into equation~\ref{eq:ReducedForm} gives
 \begin{align}
@@
 The resulting parameters are then used when estimating the new state vector sequence for the next iteration.
-The procedure stops when the \parham{parameter estimates} converge.
+The procedure stops when the parameter estimates converge.
 The algorithm is initialized using a bounded random state vector sequence, guaranteeing that the initial estimated parameter set forms a stable kernel.
@@
 This, in turn, leads to increases in uncertainty in the state estimates.
-In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modelling assumption.
+In addition, directly linking the complexity of the underlying system to the spatial resolution of the observation process implies that the system's dynamics become increasingly more complex the closer we look, which may not be an accurate modeling assumption.
 
@@
 
-\subsection{Patient-Specific Modelling}
+\subsection{Patient-Specific Modeling}
 
@@
 
-The development of the estimation framework also has implications for theoretical neuroscience, where the ability to estimate subject-specific properties will allow testing of hypotheses that have been generated in computational modelling studies.
+The development of the estimation framework also has implications for theoretical neuroscience, where the ability to estimate subject-specific properties will allow testing of hypotheses that have been generated in computational modeling studies.
 This has the potential to validate neural field models and, in doing so, provide new insights that may lead to a greater understanding of mesoscopic and macroscopic neurodynamics.

### 2010-11-20 ltx/first_order_framework/SubmissionLetter.tex
added research highlights

--- 2010-07-01 ltx/PLoS/SubmissionLetter.tex
@@
 \vspace{-1cm}
-\begin{letter}{Editor/Reviewer \\ PLoS Computational Biology}
+\begin{letter}{Editor/Reviewer \\ Neuroimage}
 
@@
 
-I am writing to seek publication of our research article titled `A Data-Driven Framework for Neural Field Modelling' in PLoS Computational Biology.
+I am writing to seek publication of our research article titled `A Data-Driven Framework for Neural Field Modeling' in Neuroimage.
 
-This paper brings several new techniques to the field of computational biology, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model from electrophysiological data.
+This paper brings several new techniques to the fields of neuroscience and neuroimaging, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model from electrophysiological data.
 Our aim in this work is to model the intracortical connectivity and synaptic dynamics of an individual patient or experimental subject.
@@
 
-Due to the novel aspects of the model reduction and estimation procedure, we have chosen to precede the Results section with the Methods section.
-
 Thank you for your time and consideration in reviewing this article. We look forward to hearing the outcome of the review.

### 2010-11-20 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

@@
 
-Modeling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (MVAR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the required model complexity.
+Modeling the neural dynamics within this framework has a distinct advantage over the more standard multivariate auto-regressive (MVAR) models: the number of parameters to define the spatial connectivity is considerably smaller than the number of AR coefficients typically required to achieve the model complexity.
 

### 2010-11-20 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

@@
 
-\subsection{Integro-Difference Equation Neural Field Model}
+\subsection{Integro-Difference Equation Neural Field Model}\label{IntegroDifferenceEquationSection} 
 The combination of modeling techniques in this paper leads to a large amount of notation, so a reference of the symbols used is provided in Table~\ref{tab:Notation}.
@@
 \end{equation}
-where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a $n_x \times n_{\theta}$ matrix, where $n_x$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
-This matrix is defined analytically (see \ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
+where $\left[ \boldsymbol\Psi(\mathbf{r}')\right]_{:i}$ denotes the $i^{th}$ column of $\boldsymbol{\Psi}(\mathbf{r}')$ which is a $n_x \times n_{\theta}$ matrix, where $n_x$ is the number of basis functions (states) and $n_{\theta}$ is the number of connectivity kernel basis functions.
+This matrix is pre-defined analytically (see \ref{ap:ConvOfGaussians} for analytic convolution of two Gaussians), since it is constant with respect to the states and the unknown parameters.
 Substituting $\boldsymbol{\Psi}(\mathbf{r}')$ into equation~\ref{eq:ReducedForm} gives
@@
 \section{Results}\label{ResultsSection} We now provide demonstrations of the estimation procedure using the new methods that are described above.
-Data was generated using the neural field model, described in Section~\ref{NeuralModelSection}, to demonstrate the state and parameter estimation framework.
+Data was generated using the neural field model, described in Section~\ref{IntegroDifferenceEquationSection}, to demonstrate the state and parameter estimation framework.
 All parameters for the model are given in Table~\ref{tab:Parameters}, unless otherwise explicitly stated for particular experiments.
@@
 Furthermore, by using the neural field equations as a parametric form of a model, the estimated quantities have physical meaning and, therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for inhomogeneous and anisotropic connectivity, which is present in the longer range cortico-cortical fibres.
+An advantage of the MVAR-based methods is that they allow for \parham{inhomogeneous connectivity, which is present in the longer range cortico-cortical fibres.}
 

### 2010-11-20 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

@@
 
-As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen the account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure.
+As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure.
 In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
@@
 For this parameter combination the mean estimates are in good agreement (within 1 standard deviation) with the actual values of the connectivity kernel parameters.
-However, the time constant parameter, $\xi$, is outside the estimated distribution (with bias of $2.56\%$), with a small variance in parameter estimates.
+However, the time constant parameter, $\xi$, is outside the estimated distribution (with bias of $2.67\%$), with a small variance in parameter estimates.
 We attribute this small bias to the loss of the high frequency components in the smoother estimated field with respect to the actual field.
@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Fig.~\ref{fig:Figure10} with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realisations is shown in Fig.~\ref{fig:Figure8} with the $95~\%$ confidence interval.
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
@@
 Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates.
-Although the net reconstructed kernel estimates are in good accord with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
+Although the net reconstructed kernel estimates are in good accordance with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
 This result demonstrates that unless the widths of the Gaussians forming the kernel are precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
@@
 	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
-	$\rho_\phi$ & field basis function over-sampling parameter & 1 & n.a.\\
+	$\rho_\phi$ & field basis function over-sampling parameter & 1.67 & n.a.\\
 	\hline 
@@
 This was achieved by moving a dipole across a recording electrode submerged in saline.
-A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}.
+A photograph through a microscope of the submerged electrodes can be seen in \parham{Fig.~\ref{fig:SensorAndSource}}.
 The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
@@
 where $\mathcal{H}$ denotes the Hilbert transform operator, $t$ indexes samples and $T$ is the total number of samples in the time series.
-Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
+\parham{Fig.~\ref{fig:Ch3}} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
 A Gaussian fitted to the amplitudes is also shown.
 The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
-
+\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
+This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
+We define an \textit{n}-dimensional Gaussian  centred at the origin as
+\begin{equation}
+ \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
+\end{equation}
+Now applying the \textit{n}-dimensional Fourier transform yields
+\begin{align}\label{eq:AppendixGaussianFT}
+ \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
+&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
+\end{align}
+Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
+\begin{equation}\label{eq:IntegralOfGaussian}
+\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
+=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
+\end{equation}
+Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
+\begin{equation}\label{eq:FTofGaussian}
+\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
+\end{equation} 
+where 
+\begin{equation}
+	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
+\end{equation}
+For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
+\begin{equation}
+ \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
+\end{equation}
+since the maximum of the Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Solving for $\sigma_{\nu}^2$, we get
+\begin{equation}
+ \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
+\end{equation}
+\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
+In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
+Consider two Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
+Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
+\begin{equation}\label{eq:FTTwoGaussianMultiplication}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform.
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+\begin{align}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
+ &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{align}
+Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
+\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
+\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
+\end{align}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
 \section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
@@
 
-\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
-\begin{equation}\label{eq:FTTwoGaussianMultiplication}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{equation}
-where $\mathcal{F}$ denotes the Fourier transform.
-Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
-\begin{align}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
- &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
-\end{align}
-Taking the inverse Fourier transform, the convolution becomes
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
-\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
-\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
-\end{align}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
-
 \section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
@@
 
-\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
-This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
-We define an \textit{n}-dimensional Gaussian  centred at the origin as
-\begin{equation}
- \phi(\mathbf r)=\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r\right).
-\end{equation}
-Now applying the \textit{n}-dimensional Fourier transform yields
-\begin{align}\label{eq:AppendixGaussianFT}
- \boldsymbol\Phi(\boldsymbol \nu)&=\int_{\mathbb{R}^n} {\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2}\mathbf r^\top\mathbf r}\right)\mathrm{exp}\left(-2\pi i\boldsymbol\nu^\top\mathbf r\right)d\mathbf r} \nonumber \\
-&=\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r \nonumber \\ &\times\mathrm{exp}\left(-\sigma_{\phi}^2\pi^2\boldsymbol\nu^\top \boldsymbol\nu\right).
-\end{align}
-Evaluating the integral on the RHS of equation~\ref{eq:AppendixGaussianFT} gives 
-\begin{equation}\label{eq:IntegralOfGaussian}
-\int_{\mathbb{R}^n}\mathrm{exp}\left(-\frac{1}{\sigma_{\phi}^2}\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]^\top\left[\mathbf r +\sigma_{\phi}\pi i \boldsymbol\nu\right]\right)d\mathbf r
-=\left(\pi\sigma_{\phi}^2\right)^{\frac{n}{2}}.
-\end{equation}
-Substituting equation~\ref{eq:IntegralOfGaussian} into equation~\ref{eq:AppendixGaussianFT} gives the scaled Gaussian
-\begin{equation}\label{eq:FTofGaussian}
-\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
-\end{equation} 
-where 
-\begin{equation}
-	\sigma_{\nu}^2=\frac{1}{\pi^2\sigma_{\phi}^2}. 
-\end{equation}
-For $3$~dB attenuation ($1/2$ to peak power) at the cut-off frequency, $\boldsymbol\nu_c$, we need to set
-\begin{equation}
- \left|\boldsymbol\Phi(\boldsymbol\nu_{c})\right|^2=\frac{1}{2}\left|\boldsymbol\Phi(\mathbf 0)\right|^2,
-\end{equation}
-since the maximum of the Gaussian described in equation~\ref{eq:FTofGaussian} is at the origin. Solving for $\sigma_{\nu}^2$, we get
-\begin{equation}
- \sigma_{\nu}^2=\frac{2\boldsymbol\nu_{c}^\top \boldsymbol\nu_{c}}{\ln 2 }.
-\end{equation}
-
 \end{document}

### 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction
made the references in the AuthorDate format as required and fixed some Americanized spelling

@@
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008,David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999,RENNIE2000}, epileptic seizure generation \cite{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \cite{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) (\cite{Liley1999,RENNIE2000}), epileptic seizure generation (\cite{DaSilva2003,Suffczynski2004,Wendling2005}) and insights into other pathologies (\cite{Moran2008,Schiff2009}) that would be difficult to gain from experimental data alone.
 
@@
 Patient-specific data from electrophysiological recordings is readily available in the clinical setting, particularly from epilepsy surgery patients, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
-Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
+Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling (\cite{Brinkmann2009}).
 However, the mesoscopic and macroscopic neural dynamic state is not directly observable in neurophysiological data, making predictions of the underlying physiology inherently difficult.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models, or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the \cite{Wilson1973} (WC) or \cite{Amari1977} models, or a neural mass model like the \cite{Jansen1995} model, to patient-specific data.
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this task has been approached from a number of standpoints~\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}.
-
-Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
-Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
-Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}.
+Recently, however, this task has been approached from a number of standpoints (\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}).
+
+Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) (\cite{David2003,David2006}), which has been proposed for studying evoked potential dynamics.
+Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the model of \cite{Jansen1995}.
+Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations (\cite{schiff2008kalman}).
 This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
@@
 
-We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
+We present an extension to the work of \cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
 In addition, a new method is presented for estimating the connectivity structure and the synaptic dynamics.
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
-Our study extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
+Our study extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning (\cite{Dewar2009}).
 The key development of this previous work was to represent a spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
-This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required for the neural field equations.
+In addition, the appropriate model selection tools have been developed (\cite{Scerri2009}) allowing for the application of the technique to neural fields.
+This paper extends the linear framework of \cite{Dewar2009} and \cite{Scerri2009} to the nonlinear case required for the neural field equations.
 
@@
 
-In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
+In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the \cite{Wilson1973} neural field model.
 This work provides a fundamental link between the theoretical advances in neural field modeling and electrophysiological data.
@@
 The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition~\cite{Braitenberg1998}.
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
-Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) (\cite{Jirsa2009,Qubbaj2007}).
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition (\cite{Braitenberg1998}).
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field (\cite{Sullivan2006}).
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour (\cite{David2003,Bressloff2001,Breakspear2006}).
+Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and traveling oscillations (\cite{Amari1977,Coombes2005,Coombes2007}).
 
@@
 where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$ (\cite{Rasmussen2005}).
 The disturbance is added to account for model uncertainty and unmodelled inputs.
@@
 
-When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor~\cite{Jackson1999}.
-However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
+When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor (\cite{Jackson1999}).
+However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape (\cite{Jackson1999}).
 An experiment supporting this was performed and the results are shown in \ref{App:ObsKernelExperiment}.
@@
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
-Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition, but in order to model larger areas of cortex a third basis function is incorporated corresponding to weaker mid-range excitation.
 Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
@@
 \subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
-Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
-Based on a two-dimensional extension of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
+Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations (\cite{Sanner1992,Scerri2009}).
+Based on a two-dimensional extension of Shannon's sampling theorem (\cite{Peterson1962}), the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
 
@@
 In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing placement of sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}).
 Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
@@
 
-The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
+The field basis function widths can also be inferred using spectral considerations (\cite{Sanner1992,Scerri2009}).
 To demonstrate this, we begin with a two-dimensional Gaussian basis function located at the origin, defined as
@@
 
-The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
-The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS) (\cite{Sarkka2010}) was used for the state estimation.
+The URTSS incorporates an unscented Kalman filter (UKF) (\cite{Julier1997, Merwe2003}) in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
@@
 \end{small}
-Following this, the LS parameter estimates~\cite{Ljung1985}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates (\cite{Ljung1985}), $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 In addition, the frequency analysis highlights the relationship between the width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes (\cite{Brinkmann2009}).
 
@@
 The closest competitor to our `grey-box' integro-difference equation approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
-Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}.
+Examples of MVAR models for estimating functional connectivity include Granger causality (\cite{Hesse2003}), the direct transfer function (\cite{Kaminski1991}), and partial directed coherence (\cite{Sameshima1999}).
 A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
 Furthermore, by using the neural field equations as a parametric form of a model, the estimated quantities have physical meaning and, therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for \parham{inhomogeneous connectivity, which is present in the longer range cortico-cortical fibres.}
-
-Previous work by Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
+An advantage of the MVAR-based methods is that they allow for inhomogeneous connectivity, which is present in the longer range cortico-cortical fibres.
+
+Previous work by \cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
 Within their framework, each discrete spatial location formed an element of the state vector to be estimated with the UKF.
@@
 
-The current study builds on Schiff and Sauer's approach~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
+The current study builds on Schiff and Sauer's approach by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in the Methods section.
@@
 Estimation of the connectivity structure or the synaptic time constant may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms (\cite{Marten2009}).
 These very different mechanisms would require very different medications for successful treatment.
@@
 	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m^2$) & n.a. \\
+	$m(\mathbf{r}_n,\mathbf{r}')$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m$) & n.a. \\
 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
@@
 	$\delta(t)$ & Dirac-delta function & n.a.\\
-	$D$ & temporal differential operator & n.a.\\
+	$\textrm{D}$ & temporal differential operator & n.a.\\
 	\hline
@@
 \begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialization} \\ 
 $\hat{\mathbf x}_0, \mathbf P_0$ \\
@@
 \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialization}\\
 $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
@@
 $\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
-$\mathbf M_{t +1}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
+$\mathbf M_{t +1}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t}^{b}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
 \multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
@@
 \begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
-The steps are iterated 11 times for our state estimation procedure.
+The steps are iterated 10 times for our state estimation procedure.
 The least squares algorithm is run after each iteration to update the parameter estimates.
@@
 % 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 \cite{Wendling2005} & mV$^{-1}$\\
-	$v_0$ & firing threshold & 1.8 \cite{Marreiros2008}& mV  \\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 (\cite{Wendling2005}) & mV$^{-1}$\\
+	$v_0$ & firing threshold & 1.8 (\cite{Marreiros2008}) & mV  \\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
@@
 	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
-	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
+	$\sigma_{m}$ & observation kernel width parameter & 0.9 & mm \\
 	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
@@
 	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
-	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
+	$\sigma_{\phi}$ & width of field basis functions in spatial domain & 2.5 & mm$^2$\\
 	\hline 
@@
 
-{\bf Figure 12. Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.
-
-{\bf Figure 13.
+% {\bf Figure 12. Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.
+
+{\bf Figure 12.
 RMSE of the kernel estimates}.
@@
 The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
-To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
+To extract the amplitude of the signal, the data was first band-pass filtered with a center frequency of 40~Hz.
 The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
@@
 This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
-We define an \textit{n}-dimensional Gaussian  centred at the origin as
+We define an \textit{n}-dimensional Gaussian  centerd at the origin as
 \begin{equation}
@@
 \end{equation}
-A Gaussian basis function is symmetric with respect to its centre so
+A Gaussian basis function is symmetric with respect to its center so
 \begin{equation}\label{eq:GaussianSymmetry}

### 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
further general edits fixing typos

@@
 The Wilson and Cowan or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data.
-To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors enabling a comparison between the estimated and true parameters.
+To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters.
 To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model using a basis function decomposition to form a finite-dimensional state-space model.
@@
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
-Our study extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning (\cite{Dewar2009}).
+Our study also extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning (\cite{Dewar2009}).
 The key development of this previous work was to represent a spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
@@
 \end{equation}
-where $\sigma_{\phi}$ is the basis function width parameter. An example of a one-dimensional field decomposition is given in Fig.~\ref{fig:Figure2}.
-
-The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in the following section). The connectivity kernel can also be decomposed as 
+where $\sigma_{\phi}$ is the basis function width parameter.
+An example of a one-dimensional field decomposition is given in Fig.~\ref{fig:Figure2}.
+The width and positioning of the basis functions can be determined by spectral analysis (explained in detail in the following section).
+
+The connectivity kernel can also be decomposed as 
 \begin{equation}\label{DefKernelDecomp}
@@
 \end{align}
-This substitution allows us to swap the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is pre-defined analytically.
+This substitution swaps the convolution in equation~\ref{reduced continuous model}, which is computationally demanding, with the convolution in equation~\ref{eq:DefPsi}, which is pre-defined analytically.
 This is of great importance as it lowers the computational demands of the estimation algorithm and provides a dramatic increase in estimation speed.
@@
 \end{equation}
-To obtain a 3~dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen to be
+To obtain a 3~dB attenuation at $\boldsymbol\nu_{cy}$, the basis function width, $\sigma^2_{\phi}$, should be chosen such that
 \begin{equation}\label{eq:WidthCutOffRelationship}
@@
 The distance between sensors was set to $\Delta_y = 1.5$~mm.
-This arrangement modelled the recording as having some cross talk (from volume conduction), which is typical for neurophysiological recordings.
+This arrangement modeled the recording as having some cross talk (from volume conduction), which is typical for neurophysiological recordings.
 
@@
 \subsubsection{Experiment I: Monte Carlo Simulation with Fixed Parameters}
-A Monte Carlo approach was employed where 150 realisations of the data were generated, such that distributions of the parameters estimates could be formed.
-Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
+A Monte Carlo approach was employed where 150 realizations of the data were generated, such that distributions of the parameters estimates could be formed.
+Each realization consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out.
 The initial state and parameters were unknown to the estimator.
@@
 The reconstructed connectivity kernels from the estimated parameters are shown in Fig.~\ref{fig:Figure10}.
-For Fig.~\ref{fig:Figure10}(A-C) the Mexican hat connectivity kernels were used.
+For Fig.~\ref{fig:Figure10}(A-C) Mexican hat connectivity kernels were used.
 For each subset of parameters, the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
@@
 Although the net reconstructed kernel estimates are in good accordance with the actual kernels, the individual kernel basis function weights are not in agreement with the actual parameters.
-This result demonstrates that unless the widths of the Gaussians forming the kernel are precisely known, the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
+This result demonstrates that the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
 
@@
 From Fig.~\ref{fig:Figure11} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
-This is expected since by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
+This is expected since that by altering the parameters we are changing the nonlinearity and the saturation region of the sigmoid.
 For example, when the sigmoid slope is very gentle, most of the neural activity falls in the central, nearly linear region of the sigmoid, thus having minor effects on the estimation procedure.
-On the other hand, sharp slopes result in most of the activity falling in the saturation region of the sigmoid with adverse effects on the estimation.
+On the other hand, sharp slopes result in more of the activity falling in the saturation region of the sigmoid with adverse effects on the estimation.
 Similar arguments can be made for variations to the sigmoid threshold.
@@
 These high frequency components result in aliasing errors in the estimated field, thus affecting the kernel estimation accuracy.
-On the other hand, for the very wide observation kernels considered, important neural dynamics are not pick up by the estimated field due to the filtering out of the important frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
+On the other hand, for the very wide observation kernels considered, important neural dynamics are not represented in the estimated field due to the filtering out of the important frequency components by the sensors, resulting in poor accuracy in the kernel estimate.
 As indicated in Fig.~\ref{fig:Figure12}, the best results are obtained when the sensor width is chosen to minimize both sources of errors.
@@
 
-% {\bf Figure 12. Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.
-
 {\bf Figure 12.
@@
 \end{figure*}
-\clearpage
-\newpage
+
+\clearpage
+\newpage
+
 \appendix
-\section{Time Discretisation of Neural Field Model}
-\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretisation must be performed.
+\section{Time Discretization of the Neural Field Model}
+\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretization must be performed.
 To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by
@@
 The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
-\section{Spatial Cut-off Frequency of Field Basis Functions}\label{App:FrequencyAnalysis}
-This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
-We define an \textit{n}-dimensional Gaussian  centerd at the origin as
+\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
+The derivation in this section was used for calculating the matrix $\mathbf \Gamma$ from equation~\ref{eq:DefGamma}. Consider two Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+
+The inner product of the two \emph{n}-dimensional Gaussians is defined as
+\begin{equation}\label{eq:InofGaussianDefinition}
+\varphi_i\otimes\varphi_j \triangleq \int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
+\end{equation}
+A Gaussian basis function is symmetric with respect to its center, therefore
+\begin{equation}\label{eq:GaussianSymmetry}
+ \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$, equation~\ref{eq:GaussianSymmetry} becomes
+\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
+ \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
+\end{equation}
+Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
+\begin{align}
+\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
+&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
+\end{align}
+Now we solve the convolution using the formula derived in \ref{ap:ConvOfGaussians}, and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
+\begin{align}
+ \varphi_i\otimes\varphi_j&=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
+&\times\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
+\end{align}
+This completes the derivation.
+\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
+In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
+This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the elements of the observation matrix, $\mathbf C$.
+Consider the two Gaussian basis functions from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}.
+The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
+The convolution theorem states that the Fourier transform of the convolution of two functions is equal to the product of their Fourier transforms.
+Using the formula from the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} in \ref{App:FrequencyAnalysis}, we have
+\begin{equation}\label{eq:FTTwoGaussianMultiplication}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
+\end{equation}
+where $\mathcal{F}$ denotes the Fourier transform.
+Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
+\begin{align}
+\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
+ &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
+\end{align}
+Taking the inverse Fourier transform, the convolution becomes
+\begin{equation}\label{eq:ConvoftwoGaussian}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
+\end{equation}
+In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
+\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
+ \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
+\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
+\end{align}
+where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
+In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
+We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
+Therefore, $\mathbf{e}_t$ also follows a Gaussian distribution.
+From equation~\ref{eq:Wt}, the state disturbance vector is defined as
+\begin{equation}
+	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
+\end{equation}
+The expected value of $\mathbf e_t$ is given by 
+\begin{equation}
+	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
+\end{equation}
+The covariance of $\mathbf{e}_t$ is 
+\begin{align}
+	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
+&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
+	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
+\end{align}
+\section{Spatial Cut-off Frequency of the Field Basis Functions}\label{App:FrequencyAnalysis}
+This section provides a derivation for the width of the Fourier transform of the field basis functions in terms of their spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
+We define an \textit{n}-dimensional Gaussian centered at the origin as
 \begin{equation}
@@
 \end{equation}
-\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
-In this section, we provide a derivation for the convolution of two $n$-dimensional Gaussian basis functions.
-This derivation is used in the analytic calculation of $\boldsymbol\Psi(\mathbf{r})$ and the observation matrix, $\mathbf C$.
-Consider two Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-The derivation proceeds by assuming the Gaussian basis functions are positioned at the origin ($\boldsymbol\mu_i=\boldsymbol\mu_j=\mathbf 0$).
-The convolution theorem states that the Fourier transform of the convolution of two functions is the product of their Fourier transforms.
-Using the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} of the previous section, we have
-\begin{equation}\label{eq:FTTwoGaussianMultiplication}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\pi^2\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right),
-\end{equation}
-where $\mathcal{F}$ denotes the Fourier transform.
-Multiplying and dividing by $\left(\pi\left(\sigma_i^2+\sigma_j^2\right)\right)^{\frac{n}{2}}$, equation~\ref{eq:FTTwoGaussianMultiplication} can be written as
-\begin{align}
-\mathcal{F}\left(\varphi_i*\varphi_j\right)(\mathbf{r})&=\left(\pi\sigma_i^2\sigma_j^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} (\pi(\sigma_i^2+\sigma_j^2))^{\frac{n}{2}} \nonumber \\
- &\times\mathrm{exp}\left(-(\sigma_i^2+\sigma_j^2)\pi^2\boldsymbol\nu^\top\boldsymbol\nu\right).
-\end{align}
-Taking the inverse Fourier transform, the convolution becomes
-\begin{equation}\label{eq:ConvoftwoGaussian}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} \mathbf r^\top\mathbf r}\right).
-\end{equation}
-In the case where $\boldsymbol\mu_i\neq\boldsymbol\mu_j\neq\mathbf 0$, equation~\ref{eq:ConvoftwoGaussian} becomes
-\begin{align}\label{eq:ConvoftwoGaussianNonzeroMean}
- \left(\varphi_i*\varphi_j\right)(\mathbf{r}) =& \left( \frac{\pi\sigma_i^2\sigma_j^2} {\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\nonumber \\
-\times & \mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\mathbf r-\boldsymbol\mu)^\top(\mathbf r-\boldsymbol\mu)}\right),
-\end{align}
-where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
-\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\Gamma$ from equation~\ref{eq:DefGamma}.
-The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as
-\begin{equation}\label{eq:InofGaussianDefinition}
-\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.
-\end{equation}
-A Gaussian basis function is symmetric with respect to its center so
-\begin{equation}\label{eq:GaussianSymmetry}
- \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$, equation~\ref{eq:GaussianSymmetry} becomes
-\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
- \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).
-\end{equation}
-Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
-\begin{align}
-\varphi_i\otimes\varphi_j&=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r \nonumber\\
-&=(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).
-\end{align}
-Using the derivation of the convolution of two Gaussians given in the previous section and evaluating it at $\mathbf r=2\boldsymbol\mu_i $ gives
-\begin{align}
- \varphi_i\otimes\varphi_j&=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}} \nonumber \\
-&\times\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
-\end{align}
-This completes the derivation.
-
-\section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
-In this section, we show that the state disturbance vector is $\mathbf{e}_t\sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$ if $e_t(\mathbf{r})\sim\mathcal{GP}\left(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}')\right)$.
-We begin the derivation by acknowledging the state disturbance vector is a linear function of $e_t(\mathbf r)$.
-Therefore, $\mathbf{e}_t$ is also normally distributed.
-From equation~\ref{eq:Wt}, the state disturbance vector is defined as
-\begin{equation}
-	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}}.
-\end{equation}
-The expected value of $\mathbf e_t$ is given by 
-\begin{equation}
-	\mathbf E\left[ \mathbf e_t\right]= \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r}=\mathbf 0.
-\end{equation}
-The covariance of $\mathbf{e}_t$ is 
-\begin{align}
-	\boldsymbol\Sigma_e &=\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
-&=\mathbf{\Gamma}^{-1}\mathbf E[\int_{\Omega}\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r} \int_{\Omega}\boldsymbol{\phi}^{\top}(\mathbf{r}') e_t(\mathbf{r}')d\mathbf{r}']\mathbf{\Gamma}^{- \top} \nonumber \\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}(\mathbf{r}) \mathbf E[e_t(\mathbf{r})e_t(\mathbf{r}')]\boldsymbol{\phi}^{\top}(\mathbf{r}')d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
-	&=\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}(\mathbf r) \gamma(\mathbf r- \mathbf r' )\boldsymbol{\phi}^{\top}(\mathbf r')d\mathbf r' d\mathbf r\mathbf{\Gamma}^{-\top}.
-\end{align}
 

### 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
editted figure captions

@@
 \documentclass[5p,authoryear]{elsarticle}
-% \documentclass[12pt]{iopart} 
-% \usepackage{iopams}
-
-% % for checking equation size
-% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
-% \documentclass[a4paper,10pt,twocolumn]{article} 
-% \usepackage{amsmath}
-% \usepackage{anysize} %<-use this for checking equation length
-% \marginsize {1.6cm}{1.6cm}{1.0cm}{1.8cm} %<-use this for checking equation length
-% \setlength{\columnsep}{0.5cm} %<-use this for checking equation length
-% % ~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
 \usepackage{amsmath}
-
 \usepackage{amssymb}
@@
 Each neural population represents a functional cortical processing unit, such as a column.
-The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
+The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
 In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) (\cite{Jirsa2009,Qubbaj2007}).
 In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition (\cite{Braitenberg1998}).
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field (\cite{Sullivan2006}).
+For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field (\cite{Sullivan2006}).
 Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour (\cite{David2003,Bressloff2001,Breakspear2006}).
@@
 \end{equation}
-Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
+Now given a state estimate sequence from the initialization or an iteration of the URTSS, we can write
 \begin{align*}
@@
 
-Histograms of the parameter estimates obtained over the 150 realisations are shown in Fig.~\ref{fig:Figure7}.
+Histograms of the parameter estimates obtained over the 150 realizations are shown in Fig.~\ref{fig:Figure7}.
 In each of the subplots of the figure the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
@@
 The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space.
-The MRMSE of the field estimates over time for 150 realisations is shown in Fig.~\ref{fig:Figure8} with the $95~\%$ confidence interval.
+The MRMSE of the field estimates over time for 150 realizations is shown in Fig.~\ref{fig:Figure8} with the $95~\%$ confidence interval.
 At each time point, the error is consistently around $0.5$~mV, which is approximately $10.73~\%$ of the field voltage range ([-2.20, 2.46]~mV).
@@
 For Fig.~\ref{fig:Figure10}(A-C) Mexican hat connectivity kernels were used.
-For each subset of parameters, the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
+For each subset of parameters, the mean of the reconstructed kernel over 50 realizations is shown as a dotted line and the 95~\% confidence interval is indicated by the grey shaded region.
 In each case, the actual kernel was within the 95~\% confidence interval of the kernel estimate.
@@
 As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
-The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
+The estimates of the connectivity kernels show relatively broad distributions over the different realizations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
 To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings, where given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease.
 Even when using a known input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set.
-By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realisations), such that a distribution of the parameter estimates and resulting connectivity kernels can be formed.
+By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realizations), such that a distribution of the parameter estimates and resulting connectivity kernels can be formed.
 
@@
 	\hline
-	$\Delta$ & spatial discretisation step & 0.5 & mm \\
+	$\Delta$ & spatial discretization step & 0.5 & mm \\
 	$T_s$ & time step & $0.001$ & s\\
@@
 {\bf Figure 1.
-Mexican-hat connectivity kernel.} The function $w(\cdot)$ is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+Mexican-hat connectivity kernel.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.
@@
 Example of a one-dimensional field decomposition.} A continuous, one-dimensional field decomposed by a finite number of basis functions scaled by the state vector.
-The dashed line depicts the field, the black solid lines shows the Gaussian basis functions and the vertical lines show the position and amplitude of the states.
+The dashed line depicts the field, the black solid lines show the Gaussian basis functions and the vertical lines show the position and amplitude of the states.
 
@@
 Example of the spatiotemporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant.
-(\textbf{B}) Data generated by the full neural field model from the first 5 sensors.
-(\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.
+(\textbf{B}) Data generated by the full neural field model at the first 5 sensors.
+(\textbf{C}) Mean power spectral density of the data generated by the observations.
 
 {\bf Figure 4.
-Spatial frequency analysis of the neural field}.
+Spatial frequency analysis: the neural field}.
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field.
@@
 {\bf Figure 5.
-Spatial frequency analysis}.
-The dashed line shows the cutoff frequency (-3 dB point).
+Spatial frequency analysis: observations and basis functions}.
+The dashed line shows the cutoff frequency ($-3$ dB point).
 (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations.
@@
 {\bf Figure 6.
-Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realisations.
-All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.
+Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 realizations.
+All parameters converge after 6 iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.
 
 {\bf Figure 7.
-Histograms of the parameter estimates over 150 realisations}.
-The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters.
+Histograms of the parameter estimates over 150 realizations}.
+In  each of the subplots the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.
 (\textbf{A}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
@@
 
-{\bf Figure 8. Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).
+{\bf Figure 8.
+Error in the field reconstruction}.
+The mean (over iterations) of average (over space) RMSE of the estimated field over 150 realizations (solid line) and the 95~\% confidence interval (grey region).
 
@@
 Examples of the actual and estimated neural fields and the error}.
-(\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data.
+(\textbf{A}) The actual field at a single time instant from the neural field model that was used to generate the data.
 (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field.
 (\textbf{C}) The error between the true and reconstructed fields.
-The error shows high frequency behaviour.
 
 {\bf Figure 10.
-Cross-section of connectivity kernel estimate}.
-The actual kernel is shown by the solid line, the mean kernel estimate (over 50 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.
+Cross-section of connectivity kernel estimates}.
+In each of the subplots the actual kernels are shown by the solid lines, the mean kernel estimates (over 50 realizations) are shown by the dotted lines and the 95~\% confidence intervals are shown by the shaded grey regions.
 
 {\bf Figure 11.
-RMSE of different kernel estimates}.
-Log of the RMSE of the kernel for different values of firing threshold, $v_0$, and the slope of the sigmoid, $\varsigma$.
-Mean kernel estimates are obtained over 50 realisations in each case.
+RMSE of connectivity kernel estimates with various sigmoid parameters}.
+Log of the RMSE of the connectivity kernel for different values of firing threshold, $v_0$, and the slope of the sigmoid, $\varsigma$.
+Mean kernel estimates are obtained over 50 realizations in each case.
 White spaces indicate cases where the kernel can not be estimated due to numerical problems.
@@
 {\bf Figure 12.
-RMSE of the kernel estimates}.
-RMSE of the kernel for different values of sensor width, $\sigma_m$, distance between adjacent sensors is $\Delta_y=1.5$.
-Mean kernel estimates are obtained over 50 realisations in each case.
+RMSE of connectivity kernel estimates with various observation kernel widths}.
+RMSE of the connectivity kernel for different values of observation width, $\sigma_m$.
+Mean kernel estimates are obtained over 50 realizations in each case.
+
 \clearpage
@@
 \end{figure*}
-
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig13.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure12}
+\end{figure*}
 \clearpage

### 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
check if i m updated

--- 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008,David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) (\cite{Liley1999,RENNIE2000}), epileptic seizure generation (\cite{DaSilva2003,Suffczynski2004,Wendling2005}) and insights into other pathologies (\cite{Moran2008,Schiff2009}) that would be difficult to gain from experimental data alone.
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999,RENNIE2000}, epileptic seizure generation \cite{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \cite{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.
 
@@
 Patient-specific data from electrophysiological recordings is readily available in the clinical setting, particularly from epilepsy surgery patients, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
-Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling (\cite{Brinkmann2009}).
+Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling~\cite{Brinkmann2009}.
 However, the mesoscopic and macroscopic neural dynamic state is not directly observable in neurophysiological data, making predictions of the underlying physiology inherently difficult.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the \cite{Wilson1973} (WC) or \cite{Amari1977} models, or a neural mass model like the \cite{Jansen1995} model, to patient-specific data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models, or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific data.
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this task has been approached from a number of standpoints (\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}).
-
-Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) (\cite{David2003,David2006}), which has been proposed for studying evoked potential dynamics.
-Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the model of \cite{Jansen1995}.
-Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations (\cite{schiff2008kalman}).
+Recently, however, this task has been approached from a number of standpoints~\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}.
+
+Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) \cite{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
+Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}.
+Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}.
 This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
@@
 
-We present an extension to the work of \cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
+We present an extension to the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
 In addition, a new method is presented for estimating the connectivity structure and the synaptic dynamics.
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
-Our study extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning (\cite{Dewar2009}).
+Our study extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning~\cite{Dewar2009}.
 The key development of this previous work was to represent a spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed (\cite{Scerri2009}) allowing for the application of the technique to neural fields.
-This paper extends the linear framework of \cite{Dewar2009} and \cite{Scerri2009} to the nonlinear case required for the neural field equations.
+In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of the technique to neural fields.
+This paper extends the linear framework of~\cite{Dewar2009,Scerri2009} to the nonlinear case required for the neural field equations.
 
@@
 
-In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the \cite{Wilson1973} neural field model.
+In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the WC neural field model~\cite{Wilson1973}.
 This work provides a fundamental link between the theoretical advances in neural field modeling and electrophysiological data.
@@
 The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) (\cite{Jirsa2009,Qubbaj2007}).
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition (\cite{Braitenberg1998}).
-For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field (\cite{Sullivan2006}).
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour (\cite{David2003,Bressloff2001,Breakspear2006}).
-Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and traveling oscillations (\cite{Amari1977,Coombes2005,Coombes2007}).
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition~\cite{Braitenberg1998}.
+For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}.
+Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and travelling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.
 
@@
 where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$ (\cite{Rasmussen2005}).
+Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 The disturbance is added to account for model uncertainty and unmodelled inputs.
@@
 
-When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor (\cite{Jackson1999}).
-However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape (\cite{Jackson1999}).
+When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor~\cite{Jackson1999}.
+However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape~\cite{Jackson1999}.
 An experiment supporting this was performed and the results are shown in \ref{App:ObsKernelExperiment}.
@@
 Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
+Typically, the Mexican hat connectivity kernel is comprised of two basis functions representing local excitation and surround inhibition, but in order to model larger areas of cortex a third basis function is incorporated corresponding to weaker mid-range excitation.
 Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
@@
 \subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
-Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations (\cite{Sanner1992,Scerri2009}).
-Based on a two-dimensional extension of Shannon's sampling theorem (\cite{Peterson1962}), the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
+Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}.
+Based on a two-dimensional extension of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
 
@@
 In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements, possibly preventing placement of sensors in accordance to equation~\ref{eq:MinimumSensorDistance}.
-However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}).
+However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}.
 Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
@@
 
-The field basis function widths can also be inferred using spectral considerations (\cite{Sanner1992,Scerri2009}).
+The field basis function widths can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}.
 To demonstrate this, we begin with a two-dimensional Gaussian basis function located at the origin, defined as
@@
 
-The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS) (\cite{Sarkka2010}) was used for the state estimation.
-The URTSS incorporates an unscented Kalman filter (UKF) (\cite{Julier1997, Merwe2003}) in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
@@
 \end{small}
-Following this, the LS parameter estimates (\cite{Ljung1985}), $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates~\cite{Ljung1985}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 In addition, the frequency analysis highlights the relationship between the width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes (\cite{Brinkmann2009}).
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.
 
@@
 The closest competitor to our `grey-box' integro-difference equation approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
-Examples of MVAR models for estimating functional connectivity include Granger causality (\cite{Hesse2003}), the direct transfer function (\cite{Kaminski1991}), and partial directed coherence (\cite{Sameshima1999}).
+Examples of MVAR models for estimating functional connectivity include Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}.
 A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
 Furthermore, by using the neural field equations as a parametric form of a model, the estimated quantities have physical meaning and, therefore, can be clinically relevant.
-An advantage of the MVAR-based methods is that they allow for inhomogeneous connectivity, which is present in the longer range cortico-cortical fibres.
-
-Previous work by \cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
+An advantage of the MVAR-based methods is that they allow for \parham{inhomogeneous connectivity, which is present in the longer range cortico-cortical fibres.}
+
+Previous work by Schiff and Sauer~\cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
 Within their framework, each discrete spatial location formed an element of the state vector to be estimated with the UKF.
@@
 
-The current study builds on Schiff and Sauer's approach by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
+The current study builds on Schiff and Sauer's approach~\cite{schiff2008kalman} by estimating a continuous field whose complexity is independent of the resolution of the observation process and spatial resolution of the model.
 Instead, the dimensionality is governed by the expected complexity of the underlying field, which we measure using the frequency analysis presented in the Methods section.
@@
 Estimation of the connectivity structure or the synaptic time constant may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms (\cite{Marten2009}).
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms~\cite{Marten2009}.
 These very different mechanisms would require very different medications for successful treatment.
@@
 	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n,\mathbf{r}')$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m$) & n.a. \\
+	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m^2$) & n.a. \\
 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
@@
 	$\delta(t)$ & Dirac-delta function & n.a.\\
-	$\textrm{D}$ & temporal differential operator & n.a.\\
+	$D$ & temporal differential operator & n.a.\\
 	\hline
@@
 \begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialization} \\ 
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
 $\hat{\mathbf x}_0, \mathbf P_0$ \\
@@
 \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialization}\\
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
 $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
@@
 % 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 (\cite{Wendling2005}) & mV$^{-1}$\\
-	$v_0$ & firing threshold & 1.8 (\cite{Marreiros2008}) & mV  \\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 \cite{Wendling2005} & mV$^{-1}$\\
+	$v_0$ & firing threshold & 1.8 \cite{Marreiros2008}& mV  \\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
@@
 	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
-	$\sigma_{m}$ & observation kernel width parameter & 0.9 & mm \\
+	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
 	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
@@
 	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
-	$\sigma_{\phi}$ & width of field basis functions in spatial domain & 2.5 & mm$^2$\\
+	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
 	\hline 
@@
 White spaces indicate cases where the kernel can not be estimated due to numerical problems.
-
-% {\bf Figure 12. Sigmoid functions}. From bottom left corner to the right of the second second row of the previous figure.
 
@@
 The recording from the central electrode in the array was used to estimate the shape of the sensor kernel.
-To extract the amplitude of the signal, the data was first band-pass filtered with a center frequency of 40~Hz.
+To extract the amplitude of the signal, the data was first band-pass filtered with a centre frequency of 40~Hz.
 The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
@@
 This section gives the derivation for the width of the Fourier transform of the field basis function in terms of its spatial cut-off frequency (equations~\ref{eq:GaussianFT} and~\ref{eq:WidthFrequencyRelationship}).
-We define an \textit{n}-dimensional Gaussian  centerd at the origin as
+We define an \textit{n}-dimensional Gaussian  centred at the origin as
 \begin{equation}
@@
 \end{equation}
-A Gaussian basis function is symmetric with respect to its center so
+A Gaussian basis function is symmetric with respect to its centre so
 \begin{equation}\label{eq:GaussianSymmetry}

### 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
solved the conflict

--- 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \begin{table*}[!ht]
-\caption{
-\bf{Notation}}
 \begin{tabular}{|l|l|l|}
@@
 \end{tabular}
-\begin{flushleft}The first column of the table gives the symbols for all the notation used in the paper.
-The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.
-\end{flushleft}
+\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper.
+The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
 \label{tab:Notation}
@@
 \begin{table*}[!ht]
-\caption{
-\bf{Algorithm for the Unscented RTS Smoother}}
 \begin{tabular}{|c|}\hline
@@
 \end{tabular}
-\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
+\caption{\textbf{Algorithm for the Unscented RTS Smoother.} This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm.
 The steps are iterated 10 times for our state estimation procedure.
-The least squares algorithm is run after each iteration to update the parameter estimates.
-\end{flushleft}
+The least squares algorithm is run after each iteration to update the parameter estimates.}
 \label{tab:UKFAlgorithm}
@@
 \begin{table*}[!ht]
-\caption{
-\bf{Parameters}}
 \begin{tabular}{|c|l|c|l|}
@@
 \end{tabular}
-\begin{flushleft}Parameters for the neural field model, the model reduction, the frequency analysis and the estimation procedure.
-\end{flushleft}
+\caption{\textbf{Parameters.} Parameters for the neural field model, the reduced model, the frequency analysis and the estimation procedure.}
 \label{tab:Parameters}
@@
 \begin{table*}[!ht]
-	\caption{
-	\bf{Results from varying the Mexican hat connectivity kernel parameters}}
 \begin{tabular}{c|ccccc}
@@
 \end{tabular}\label{tab:MexicanHatKernelResults}
+\caption{\textbf{Results from varying the Mexican hat connectivity kernel parameters}}
 \end{table*}
@@
 \begin{table*}[!ht]
-	\caption{
-	\bf{Results from varying the Gaussian connectivity kernel parameter}}
 \begin{tabular}{c|ccccc}
@@
 \end{tabular}\label{tab:GaussianKernelResults}
+\caption{\textbf{Results from varying the Gaussian connectivity kernel parameter}}
 \end{table*}
@@
 
+{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording array and the twisted bipolar current source.
+
+{\bf Figure 14. Observation kernel experimental results}. Amplitude of the envelope of the signal recorded from the electrode at the center of the array vs. the source position.
+
 \clearpage
@@
 \caption{}
-\label{fig:Figure12}
-\end{figure*}
-\clearpage
-\newpage
-
+\label{fig:SensorAndSource}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig14.pdf}
+\end{center}
+\caption{}
+\label{fig:Ch3}
+\end{figure*}
+\clearpage
+\newpage
 \appendix
@@
 This was achieved by moving a dipole across a recording electrode submerged in saline.
-A photograph through a microscope of the submerged electrodes can be seen in \parham{Fig.~\ref{fig:SensorAndSource}}.
+A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}.
 The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m.
@@
 where $\mathcal{H}$ denotes the Hilbert transform operator, $t$ indexes samples and $T$ is the total number of samples in the time series.
-\parham{Fig.~\ref{fig:Ch3}} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
+Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode.
 A Gaussian fitted to the amplitudes is also shown.

### 2010-11-21 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction in appendixB added bracket to formula B1
minor correction in frequency analysis
minor correction in table3

@@
 Similar considerations need to be made regarding the representation of the dynamic field, $v_t(\mathbf{r})$, using the basis function decomposition.
-Again, applying Shannon's sampling theorem, the minimum distance between basis functions to accurately reconstruct the neural field must satisfy
+Again, applying Shannon's sampling theorem, the maximum distance between basis functions to accurately reconstruct the neural field must satisfy
 \begin{equation}\label{eq:BasisFunctionSeparation}
@@
 	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
-	$\sigma_{\phi}$ & width of field basis functions in spatial domain & 2.5 & mm$^2$\\
+	$\sigma_{\phi}$ & width of field basis functions in spatial domain & 1.58 & mm$^2$\\
 	\hline 
@@
 \begin{equation}
-	a = \frac{1}{T}\sum_n{\sqrt{(y_t-\mathcal{H}y_t^2}}
+	a = \frac{1}{T}\sum_n{\sqrt{(y_t-\mathcal{H}y_t^2})}
 \end{equation}

### 2010-11-22 ltx/first_order_framework/LaTeX_Manuscript.tex
added footnote to author list
added another footnote to author list
removed all of the bits that were commented out prior to submission

@@
-% TO DELETE
-\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
-\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
-
 \documentclass[5p,authoryear]{elsarticle}
@@
 \usepackage{graphicx}
-% \usepackage{cite}
 \usepackage{color}
@@
 \journal{Neuroimage}
-
 \begin{document}
-
 \begin{frontmatter}
-% Title must be 150 characters or less
 \title{A Data-Driven Framework for Neural Field Modeling}
 
-\author[DEEE,BEI,UE]{D. R. Freestone\corref{cor1}}
+\author[DEEE,BEI,UE]{D. R. Freestone \corref{cor1} \fnref{fn1}}
 \ead{dfreestone@bionicear.org}
-\author[US]{P. Aram} 
+\author[US]{P. Aram\fnref{fn1}} 
 \author[UE,CU]{M. Dewar}
@@
 \address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+
+\fntext[fn1]{Authors contributed equally to this work.}
+\cortext[cor1]{Corresponding author}
 
@@
 The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity structure and synaptic dynamics with the proposed framework.
-%The results also illustrate a systematic loss of high spatial frequency information as the cost incurred by the model reduction procedure.
 \end{abstract}
@@
 	Neural Field Model \sep Nonlinear Estimation \sep Intracortical Connectivity \sep Nonlinear Dynamics
-%% keywords here, in the form: keyword \sep keyword
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
 \end{keyword}
@@
 \end{equation}
-% \begin{equation}
-% 	\mathbf{C} = \left[
-% 	\begin{array}{{ccc}} 
-% 		c_{1,1} & \dots & c_{1,n_x} \\
-% 		\vdots & \ddots & \vdots \\
-% 		c_{n_y,1} & \dots & c_{n_y,n_x} 
-% 	\end{array}
-% 	\right] 
-% \end{equation}
-% and 
-% \begin{equation}
-% 	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'. 
-% \end{equation}
+
 Now we have the final form of the state-space model where
@@
 
-% Results and Discussion can be combined.
 \section{Results}\label{ResultsSection} We now provide demonstrations of the estimation procedure using the new methods that are described above.
@@
 Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.
-%The other parameter of the basis functions, $\sigma_{\phi}^2$, was set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.
 
@@
 \subsubsection{Experiment II: Results for Different Connectivity Kernel Parameters}
-
 To study the robustness of the estimation algorithm, the performance was evaluated for various connectivity kernel parameters.
@@
 \subsubsection{Experiment III: Results for Varying the Parameters of the Sigmoidal Activation Function}
-
 Fig.~\ref{fig:Figure11} demonstrates the effect of the sigmoid parameters on the estimation accuracy.
@@
 
-% The size of the squares in the figure show the magnitude of the log of the error.
-The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$).
-The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}).
 From Fig.~\ref{fig:Figure11} it can be seen that the estimation accuracy depends on the parameters of the sigmoid function.
@@
 \subsection{Patient-Specific Modeling}
-
 Generating data-driven neural field models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology.
@@
 \subsection{Extensions to the framework}
-
 In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
@@
 Matthias Hennig for useful discussions and feedback.
+He would also like to thank Dr.
+James Fallon for assistance wit the observation kernel experiment.
 This research was funded in part by the Australian Research Council (Linkage Project LP0560684).
@@
 	\hline
-    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
 	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & Hz \\

### 2010-11-22 src/python/NeuroImage/Data_generation_and_estimation.py
added readme file for the python files

@@ -1,6 +1,6 @@
 #Author Parham Aram
 #Date 21-11-2010
-'''This module simulates the full neural model and uses the data
+'''This module simulates the  neural model and uses the data
 in the state space model to estimate the states, 
 the connectivity kernel parameters and the synaptic dynamics'''
 

### 2010-11-22 src/python/NeuroImage/NF.py

@@ -1,7 +1,7 @@
 #Author Parham Aram
 #Date 28-06-2010
 """
-This module provides the full neural field class, which describes a non-linear
+This module provides the neural field class, which describes a non-linear
 integro-difference equation model and methods to simulate
 the model
 """

### 2010-11-22 ltx/first_order_framework/ResearchHighlights.tex
added tex files for reviewer suggestions and research highlights

%  Created by Dean Freestone on 2010-11-22.
%  Copyright (c) 2010 . All rights reserved.
%
\documentclass[]{article}

\begin{document}

\textbf{Research Highlights}
\begin{itemize}
	\item We derive a model-based, data-driven estimator of continuum neural field parameters.
	\item Systematic field decomposition enables a finite-dimensional state-space model.
	\item We show how to infer intracortical connectivity and synaptic dynamics from data.
	\item Our framework provides a new link between theoretical and experimental neuroscience.
\end{itemize}

\end{document}

### 2010-11-23 ltx/first_order_framework/LaTeX_Manuscript.tex
submission  and changes to matlab circular boundary

@@
-\documentclass[5p,authoryear]{elsarticle}
+\documentclass[review,authoryear,3p]{elsarticle}
 
@@
 \usepackage{graphicx}
-\usepackage{color}
+\usepackage{setspace}
 
@@
 \author[US]{P. Aram\fnref{fn1}} 
+\ead{p.aram@sheffield.ac.uk}
 \author[UE,CU]{M. Dewar}
+\ead{mike.dewar@columbia.edu}
 \author[UM]{K. Scerri}
+\ead{kenneth.scerri@um.edu.mt}
 \author[DEEE,BEI]{D. B. Grayden}
+\ead{grayden@unimelb.edu.au}
 \author[US]{V. Kadirkamanathan}
+\ead{visakan@sheffield.ac.uk}
 
@@
 \section{Introduction}
+
 Generating physiologically plausible neural field models is of great importance for studying brain dynamics at the mesoscopic and macroscopic scales.
@@
 
-Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008,David2003} for recent reviews).
-These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) (\cite{Liley1999,RENNIE2000}), epileptic seizure generation (\cite{DaSilva2003,Suffczynski2004,Wendling2005}) and insights into other pathologies (\cite{Moran2008,Schiff2009}) that would be difficult to gain from experimental data alone.
+Mathematical neural field models provide insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\citet{Deco2008,David2003} for recent reviews).
+These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \citep{Liley1999,RENNIE2000}, epileptic seizure generation \citep{DaSilva2003,Suffczynski2004,Wendling2005} and insights into other pathologies \citep{Moran2008,Schiff2009} that would be difficult to gain from experimental data alone.
 
@@
 Patient-specific data from electrophysiological recordings is readily available in the clinical setting, particularly from epilepsy surgery patients, suggesting an opportunity to make the patient-specific link to models of cortical dynamics.
-Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling (\cite{Brinkmann2009}).
+Furthermore, recent technological advances have driven an increased level of sophistication in recording techniques, with dramatic increases in spatial and temporal sampling \citep{Brinkmann2009}.
 However, the mesoscopic and macroscopic neural dynamic state is not directly observable in neurophysiological data, making predictions of the underlying physiology inherently difficult.
@@
 For models to be clinically viable, they must be patient-specific.
-A possible approach to achieve this would be to fit a general continuum neural field model, like the \cite{Wilson1973} (WC) or \cite{Amari1977} models, or a neural mass model like the \cite{Jansen1995} model, to patient-specific data.
+A possible approach to achieve this would be to fit a general continuum neural field model, like the \citet{Wilson1973} (WC) or \citet{Amari1977} models, or a neural mass model like the \citet{Jansen1995} model, to patient-specific data.
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this task has been approached from a number of standpoints (\cite{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}).
-
-Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) (\cite{David2003,David2006}), which has been proposed for studying evoked potential dynamics.
-Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the model of \cite{Jansen1995}.
-Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations (\cite{schiff2008kalman}).
+Recently, however, this task has been approached from a number of standpoints \citep{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}.
+
+Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) \citep{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
+Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the model of \citet{Jansen1995}.
+Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations \citep{schiff2008kalman}.
 This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
@@
 
-We present an extension to the work of \cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
+We present an extension to the work of \citet{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for larger scale (more space) systems via a systematic model reduction procedure.
 In addition, a new method is presented for estimating the connectivity structure and the synaptic dynamics.
 Until now, model-based estimation of local intracortical connectivity has not been reported in the literature (to the best of the authors' knowledge).
-Our study also extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning (\cite{Dewar2009}).
+Our study also extends recent work which shows that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \citep{Dewar2009}.
 The key development of this previous work was to represent a spatiotemporal system as a standard state-space model, with the number of states independent of the number of observations (recording electrodes in this case).
-In addition, the appropriate model selection tools have been developed (\cite{Scerri2009}) allowing for the application of the technique to neural fields.
-This paper extends the linear framework of \cite{Dewar2009} and \cite{Scerri2009} to the nonlinear case required for the neural field equations.
+In addition, the appropriate model selection tools have been developed \citep{Scerri2009} allowing for the application of the technique to neural fields.
+This paper extends the linear framework of \citet{Dewar2009} and \citet{Scerri2009} to the nonlinear case required for the neural field equations.
 
@@
 
-In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the \cite{Wilson1973} neural field model.
+In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the \citet{Wilson1973} neural field model.
 This work provides a fundamental link between the theoretical advances in neural field modeling and electrophysiological data.
@@
 The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) (\cite{Jirsa2009,Qubbaj2007}).
-In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition (\cite{Braitenberg1998}).
-For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field (\cite{Sullivan2006}).
-Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour (\cite{David2003,Bressloff2001,Breakspear2006}).
-Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and traveling oscillations (\cite{Amari1977,Coombes2005,Coombes2007}).
+In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \citep{Jirsa2009,Qubbaj2007}.
+In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \citep{Braitenberg1998}.
+For example, this structural organization is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field \citep{Sullivan2006}.
+Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behaviour \citep{David2003,Bressloff2001,Breakspear2006}.
+Field models are also capable of generating complex spatial patterns of activity such as Turing patterns, spirals and traveling oscillations \citep{Amari1977,Coombes2005,Coombes2007}.
 
@@
 Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$ (\cite{Rasmussen2005}).
-The disturbance is added to account for model uncertainty and unmodelled inputs.
+The disturbance is added to account for model uncertainty and unmodeled inputs.
 To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.
@@
 
-When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor (\cite{Jackson1999}).
-However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape (\cite{Jackson1999}).
+When considering the measurement of a point source in a conductive homogeneous field measured by a point sensor, the observation kernel will theoretically follow a Laplacian like shape, with an exponential decay in the amplitude of a measurement with an increasing distance between the source and sensor \citep{Jackson1999}.
+However, when considering a source or sensor with a spatial extent, the peak of the observation kernel becomes smoothed and is more similar to a Gaussian shape \citep{Jackson1999}.
 An experiment supporting this was performed and the results are shown in \ref{App:ObsKernelExperiment}.
@@
 \subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
-Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations (\cite{Sanner1992,Scerri2009}).
-Based on a two-dimensional extension of Shannon's sampling theorem (\cite{Peterson1962}), the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
+Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \citep{Sanner1992,Scerri2009}.
+Based on a two-dimensional extension of Shannon's sampling theorem \citep{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spatial spectral characteristics of the neural field.
 
@@
 
-The field basis function widths can also be inferred using spectral considerations (\cite{Sanner1992,Scerri2009}).
+The field basis function widths can also be inferred using spectral considerations \citep{Sanner1992,Scerri2009}.
 To demonstrate this, we begin with a two-dimensional Gaussian basis function located at the origin, defined as
@@
 
-The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS) (\cite{Sarkka2010}) was used for the state estimation.
-The URTSS incorporates an unscented Kalman filter (UKF) (\cite{Julier1997, Merwe2003}) in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS) \citep{Sarkka2010} was used for the state estimation.
+The URTSS incorporates an unscented Kalman filter (UKF) \citep{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
@@
 \end{equation}
-where the constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$, and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).
+where the constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$, and $\kappa$ is an additional scaling parameter (see~\citet{Haykin2001} for more details).
 
@@
 \end{small}
-Following this, the LS parameter estimates (\cite{Ljung1985}), $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates \citep{Ljung1985}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 Each plot shows that the actual kernel lies within the confidence intervals of the reconstructed estimates for the majority of the kernel space, until the amplitude is relatively low.
+
 Table~\ref{tab:GaussianKernelResults} shows the statistics of the parameter estimates.
@@
 The frequency analysis specifies the minimum sensor arrangement that is required to capture the dominant cortical dynamics.
-As pointed out in numerous publications by Freeman and colleagues (see \cite{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
+As pointed out in numerous publications by Freeman and colleagues (see \citet{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
 Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
 In addition, the frequency analysis highlights the relationship between the width of the sensors and the information in the data.
-This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes (\cite{Brinkmann2009}).
+This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes \citep{Brinkmann2009}.
 
@@
 The closest competitor to our `grey-box' integro-difference equation approach is perhaps the multivariate auto-regressive (MVAR) model, which is a `black-box' approach.
-Examples of MVAR models for estimating functional connectivity include Granger causality (\cite{Hesse2003}), the direct transfer function (\cite{Kaminski1991}), and partial directed coherence (\cite{Sameshima1999}).
+Examples of MVAR models for estimating functional connectivity include Granger causality \citep{Hesse2003}, the direct transfer function \citep{Kaminski1991}, and partial directed coherence \citep{Sameshima1999}.
 A distinct advantage of the integro-difference equation based technique proposed in this current study is that the number of parameters required to model the system is considerably less than a typical MVAR model.
@@
 
-Previous work by \cite{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
+Previous work by \citet{schiff2008kalman} demonstrated for the first time the applicability of the unscented Kalman filter (UKF) for state estimation of discrete (in space and time) nonlinear spatiotemporal systems.
 Within their framework, each discrete spatial location formed an element of the state vector to be estimated with the UKF.
@@
 Estimation of the connectivity structure or the synaptic time constant may also have significant impact on the treatment of disease.
-For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms (\cite{Marten2009}).
+For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from either abnormal excitatory or inhibitory mechanisms \citep{Marten2009}.
 These very different mechanisms would require very different medications for successful treatment.
@@
 
-\bibliographystyle{elsarticle-harv} 
+\bibliographystyle{model2-names} 
 \bibliography{BrainIDE}
 
+\clearpage
+\newpage
 \section*{Tables}
+
+\singlespacing
+
 \begin{table*}[!ht]
@@
 \end{table*}
-\clearpage
-\newpage
 \renewcommand{\arraystretch}{1}
+
+\clearpage
+\newpage
 \begin{table*}[!ht]
@@
 % 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 (\cite{Wendling2005}) & mV$^{-1}$\\
-	$v_0$ & firing threshold & 1.8 (\cite{Marreiros2008}) & mV  \\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$\\
+	$v_0$ & firing threshold & 1.8 \citep{Marreiros2008} & mV  \\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
@@
 
+\doublespacing
+
 \newpage
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig1.pdf} 
+\includegraphics{fig1.pdf} 
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig2.pdf} 
+\includegraphics{fig2.pdf} 
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig3.pdf}
+\includegraphics{fig3.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig4.pdf}
+\includegraphics{fig4.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig5.pdf}	
+\includegraphics{fig5.pdf}	
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig6.pdf}
+\includegraphics{fig6.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig7.pdf}
+\includegraphics{fig7.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig8.pdf} 
+\includegraphics{fig8.pdf} 
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig9.pdf}
+\includegraphics{fig9.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig10.pdf}
+\includegraphics{fig10.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig11.pdf}
+\includegraphics{fig11.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig12.pdf}
+\includegraphics{fig12.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig13.pdf}
+\includegraphics{fig13.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics{./Graph/pdf/fig14.pdf}
+\includegraphics{fig14.pdf}
 \end{center}

### 2010-11-23 src/Matlab/SphericalBoundary.m

@@ -54,11 +54,11 @@ for n=1:NPointsInField
         mm=mm+1;
         
 %         clim = [-200 -1];         % for log
-<<<<<<< HEAD
-% %<<<<<<< HEAD
-=======
 % <<<<<<< HEAD
->>>>>>> 77a47d259f23fdd63d76d9be5524cd4b75d66048
+% %<<<<<<< HEAD
+% =======
+% <<<<<<< HEAD
+% >>>>>>> 77a47d259f23fdd63d76d9be5524cd4b75d66048
 %         clim = [0 0.08];
 % 
 %         subplot(3,3,1),imagesc(topleft,clim)
@@ -93,13 +93,13 @@ for n=1:NPointsInField
 % % %         imagesc(log10(temp2))
 % %         drawnow
 % >>>>>>> 8cec59265d4c54159cbc4765871cd56ee7b9e942
-<<<<<<< HEAD
-     end
- end
-=======
+% <<<<<<< HEAD
+%      end
+%  end
+% =======
     end
 end
->>>>>>> 77a47d259f23fdd63d76d9be5524cd4b75d66048
+% >>>>>>> 77a47d259f23fdd63d76d9be5524cd4b75d66048
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@ -125,13 +125,14 @@ end
 % % surf(Sigma_gamma-Sigma_gamma','edgecolor','none'),axis square
 % % max(max(Sigma_gamma-Sigma_gamma',[],1))
 % % [T,P] = cholcov(Sigma_gamma);
-% e = mvnrnd(zeros(1,NPointsInField^2),Sigma_gamma,T);
-% for t=1:T-1
-%     e_square = reshape(e(t,:,:),NPointsInField,NPointsInField);
-%     imagesc(e_square)
-%     axis square
-%     drawnow
-%     pause
-%     
-% end
+e = mvnrnd(zeros(1,NPointsInField^2),Sigma_gamma,T);
+for t=1:T-1
+    e_square = reshape(e(t,:,:),NPointsInField,NPointsInField);
+    e_pad = padarray(e_square,size(e_square),'circular');
+    imagesc(e_pad)
+    axis square
+    drawnow
+    pause
+    
+end
     

### 2010-12-28 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed typo in appendix 2
corrected observation noise covariance estimation in dara paper
added section on correlation analysis

@@
 \usepackage{setspace} 
+\usepackage{color}
+
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
 
@@
     \label{eq:ObservationEquation}
-	\mathbf{y}_t =
+	y_t(\mathbf{r}_n) =
 	\int_{\Omega}{
@@
 	\, d\mathbf{r}'} + 
-	\boldsymbol{\varepsilon}_t, 
-\end{equation}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+	\varepsilon_t(\mathbf{r}_n), 
+\end{equation}
+\dean{(dean: I added $(\mathbf{r}_n)$ to index the observations)}
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
 
@@
 	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
-	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 
+	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}). 
 \end{align}
@@
 \end{equation}
-The observation equation is linear and can be written in the more compact form
+\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate to reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
 \begin{equation}\label{ObservationEquation} 
@@
 \end{equation}
+
+\subsection{Estimation of Connectivity Kernel Support}
+The support of the connectivity kernel can be inferred using spatial correlation analysis.
+The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}.
+To demonstrate the method for the neural field model, we first define the spatial cross-correlation function between consecutive observations as
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}_n\right)\right] \\
+	&= \mathbf{E}\left[\left(\int_{\Omega}{
+	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
+	\, d\mathbf{r}'} + 
+	\boldsymbol{\varepsilon}_t\right)\left(\int_{\Omega}{
+	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
+	\, d\mathbf{r}'} + 
+	\boldsymbol{\varepsilon}_{t+1}\right)\right] \\
+	&= \mathbf{E}\left[\int_{\Omega}{
+	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
+	\, d\mathbf{r}'}\int_{\Omega}{
+	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
+	\, d\mathbf{r}'} \right]
+\end{align}
+where $\mathbf{E}[\cdot]$ is the expected value. Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}\right) +T_s \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}+ e_t\left(\mathbf{r}\right)\right)\, d\mathbf{r}'} \right] \\
+	 &= \xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
+{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] \nonumber \\
+	&+ T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] \nonumber \\
+	&+ \mathbf{E}\left[ \int_{\Omega} { m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \,d\mathbf{r}' }\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}\right)\, d\mathbf{r}' } \right]
+	\label{eq:spatialxcorr}
+\end{align}
+
+The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
+\begin{equation}
+	\xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
+{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{y_{t},y_{t}}(\mathbf{\tau}),
+\end{equation}
+which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$.
+DOES THIS GIVE US AN ESTIMATE OF THE FIELD DISTURBANCE COVARIANCE?
+NUMERICALLY IT SEEMS TO GIVE SOMETHING VERY CLOSE.
+DEPENDS ON THE BANDWIDTH OF M.
+The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$.
+The middle term is
+\begin{equation}
+	T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] = T_s\mathbf{E}\left[y_t(\mathbf{r}_n+\boldsymbol{\tau})\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) g_t(\mathbf{r})\, d\mathbf{r}'} \right],
+\end{equation}
+where
+\begin{equation}
+	g_t\left( \mathbf{r} \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left( \mathbf{r}' \right) \right)\, d\mathbf{r}'}. 
+\end{equation}
+% Therefore we can write
+% \begin{equation}
+% 	R_{v_{t},v_{t+1}}(\mathbf{\tau}) = \xi R_{v_{t},v_{t}}(\mathbf{\tau}) + T_s R_{v_{t},g_{t}}(\mathbf{\tau})
+% \end{equation}
+% and
+% \begin{equation}\label{eq:xcorr_firing_and_field}
+% 	T_s R_{v_{t},g_{t}}(\mathbf{\tau}) = R_{v_{t},v_{t+1}}(\mathbf{\tau})-\xi R_{v_{t},v_{t}}(\mathbf{\tau}).
+% \end{equation}
+% The spatial cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$ depends on the shape of the spatial mixing kernel $w\left( \mathbf{r},\mathbf{r}' \right)$.
+Furthermore, the sign (polarity) of $R_{v_{t},g_{t}}(\mathbf{\tau})$ will be the same as the $w\left( \mathbf{r},\mathbf{r}' \right)$ for a given spatial location since the sigmoid function $f\left( v_t\left( \mathbf{r}' \right) \right) > \mathbf{0}$.
+Therefore, the support of the kernel can be inferred given the cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$.
+The right hand side of equation~\ref{eq:xcorr_firing_and_field} can be calculated from data if $\xi$ is known.
+However, since $\xi$ is a decay parameter, we know that $\xi \in (0,1)$.
+Also, if we assume that
+% \begin{equation}
+% 	\xi R_{v_{t},v_{t}}(\mathbf{\tau}) \gg T_s R_{v_{t},g_{t}}(\mathbf{\tau})
+% \end{equation}
+% and
+% \begin{equation}
+% 	R_{v_{t},g_{t}}(\mathbf{0}) > 0,
+% \end{equation}
+% which corresponds to local excitation, then we can guess $\xi$ by incrementally increasing it from zero and evaluating equation~\ref{eq:xcorr_firing_and_field} until $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$.
+The value of $\xi$ before $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$ will provide the approximation.
 
@@
 
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig1.pdf} 
-\end{center}
-\caption{}
-\label{fig:Figure1}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig2.pdf} 
-\end{center}
-\caption{}
-\label{fig:Figure2}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig3.pdf}
-\end{center}
-\caption{} 
-\label{fig:Figure3}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig4.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure4}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht] 
-\begin{center}
-\includegraphics{fig5.pdf}	
-\end{center}
-\caption{}
-\label{fig:Figure5}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig6.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure6}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig7.pdf}
-\end{center}
-\caption{} 
-\label{fig:Figure7}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig8.pdf} 
-\end{center}
-\caption{} 
-\label{fig:Figure8}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig9.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure9}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig10.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure10}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig11.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure11}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig12.pdf}
-\end{center}
-\caption{}
-\label{fig:Figure12}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig13.pdf}
-\end{center}
-\caption{}
-\label{fig:SensorAndSource}
-\end{figure*}
-\clearpage
-\newpage
-\begin{figure*}[!ht]
-\begin{center}
-\includegraphics{fig14.pdf}
-\end{center}
-\caption{}
-\label{fig:Ch3}
-\end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig1.pdf} 
+% \end{center}
+% \caption{}
+% \label{fig:Figure1}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig2.pdf} 
+% \end{center}
+% \caption{}
+% \label{fig:Figure2}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig3.pdf}
+% \end{center}
+% \caption{} 
+% \label{fig:Figure3}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig4.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Figure4}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht] 
+% \begin{center}
+% \includegraphics{fig5.pdf}	
+% \end{center}
+% \caption{}
+% \label{fig:Figure5}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig6.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Figure6}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig7.pdf}
+% \end{center}
+% \caption{} 
+% \label{fig:Figure7}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig8.pdf} 
+% \end{center}
+% \caption{} 
+% \label{fig:Figure8}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig9.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Figure9}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig10.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Figure10}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig11.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Figure11}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig12.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Figure12}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig13.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:SensorAndSource}
+% \end{figure*}
+% \clearpage
+% \newpage
+% \begin{figure*}[!ht]
+% \begin{center}
+% \includegraphics{fig14.pdf}
+% \end{center}
+% \caption{}
+% \label{fig:Ch3}
+% \end{figure*}
 \clearpage
@@
 \begin{equation}
-	a = \frac{1}{T}\sum_n{\sqrt{(y_t-\mathcal{H}y_t^2})}
+	a = \frac{1}{T}\sum_t{\sqrt{(y_t^2-\mathcal{H}y_t^2})}
 \end{equation}

### 2010-12-28 src/Matlab/SphericalBoundary.m

@@ -5,7 +5,7 @@
 
 % spatial parameters
 % ~~~~~~~~~~~
-Delta = 0.5;                          % space step for the spatial discretisation
+% Delta = 0.5;                          % space step for the spatial discretisation
 Delta_squared = Delta^2;
 SpaceMaxPeriodicField = 30;                    % maximum space in mm
 SpaceMinPeriodicField = -30;         % minimum space in mm
@@ -15,13 +15,13 @@ r = linspace(SpaceMinPeriodicField/3,SpaceMaxPeriodicField/3,NPointsInField);   
 
 % temporal parameters
 % ~~~~~~~~~~~~~
-Ts = 1e-3;          % sampling period (s)
-T = 500;            % maximum time (ms)
+% Ts = 1e-3;          % sampling period (s)
+% T = 500;            % maximum time (ms)
 
 % disturbance paramters
 % ~~~~~~~~~~~~~
-sigma_gamma = 1.3;          % parameter for covariance of disturbance
-gamma_weight = 0.1;            % variance of disturbance
+% sigma_gamma = 1.3;          % parameter for covariance of disturbance
+% gamma_weight = 0.1;            % variance of disturbance
 
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~
@@ -125,14 +125,17 @@ end
 % % surf(Sigma_gamma-Sigma_gamma','edgecolor','none'),axis square
 % % max(max(Sigma_gamma-Sigma_gamma',[],1))
 % % [T,P] = cholcov(Sigma_gamma);
-e = mvnrnd(zeros(1,NPointsInField^2),Sigma_gamma,T);
-for t=1:T-1
-    e_square = reshape(e(t,:,:),NPointsInField,NPointsInField);
-    e_pad = padarray(e_square,size(e_square),'circular');
-    imagesc(e_pad)
-    axis square
-    drawnow
-    pause
-    
-end
+
+
+
+% e = mvnrnd(zeros(1,NPointsInField^2),Sigma_gamma,T);
+% for t=1:T-1
+%     e_square = reshape(e(t,:,:),NPointsInField,NPointsInField);
+%     e_pad = padarray(e_square,size(e_square),'circular');
+%     imagesc(e_pad)
+%     axis square
+%     drawnow
+%     pause
+%     
+% end
     

### 2010-12-29 ltx/first_order_framework/LaTeX_Manuscript.tex
updated the correlation analysis for finding kernel support in first order paper

@@
 \end{equation}
-\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate to reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
+\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate the reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
 \begin{equation}\label{ObservationEquation} 
@@
 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}_n\right)\right] \\
-	&= \mathbf{E}\left[\left(\int_{\Omega}{
-	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	\, d\mathbf{r}'} + 
-	\boldsymbol{\varepsilon}_t\right)\left(\int_{\Omega}{
-	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
-	\, d\mathbf{r}'} + 
-	\boldsymbol{\varepsilon}_{t+1}\right)\right] \\
-	&= \mathbf{E}\left[\int_{\Omega}{
-	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	\, d\mathbf{r}'}\int_{\Omega}{
-	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
-	\, d\mathbf{r}'} \right]
-\end{align}
-where $\mathbf{E}[\cdot]$ is the expected value. Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}\right) +T_s \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}+ e_t\left(\mathbf{r}\right)\right)\, d\mathbf{r}'} \right] \\
-	 &= \xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
-{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] \nonumber \\
-	&+ T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] \nonumber \\
-	&+ \mathbf{E}\left[ \int_{\Omega} { m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \,d\mathbf{r}' }\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}\right)\, d\mathbf{r}' } \right]
+	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}_n\right)\right) \right], \label{eq:ObsXCorr}
+\end{align}
+where $\mathbf{E}[\cdot]$ is the expected value. Since the observation noise is temporally white and independent of the field, equation~\ref{eq:ObsXCorr} reduces to
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
+	&=\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right],
+\end{align}
+where $\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)$ is the noise-free observation.
+
+Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} + e_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'} \right] \\
+	 &= \xi\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) d\mathbf{r}'} \right] \nonumber \\
+	&+ T_s\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'} \right] \nonumber \\
+	&+ \mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}'\right)\, d\mathbf{r}' } \right]
 	\label{eq:spatialxcorr}
@@
 \begin{equation}
-	\xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
-{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{y_{t},y_{t}}(\mathbf{\tau}),
+	\xi\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{\bar{y}_{t},\bar{y}_{t}}(\boldsymbol{\tau}),
 \end{equation}
@@
 The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$.
-The middle term is
-\begin{equation}
-	T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] = T_s\mathbf{E}\left[y_t(\mathbf{r}_n+\boldsymbol{\tau})\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) g_t(\mathbf{r})\, d\mathbf{r}'} \right],
-\end{equation}
-where
-\begin{equation}
-	g_t\left( \mathbf{r} \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left( \mathbf{r}' \right) \right)\, d\mathbf{r}'}. 
-\end{equation}
+
+To understand the middle term, the sigmoid activation function, $f(\cdot)$, is approximated by the piecewise function
+\begin{equation}
+	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
+		0, & v_t(\mathbf{r}') \le v_1 \\
+		\varsigma v_t(\mathbf{r}'), &  v_1 < v_t(\mathbf{r}') < v_2 \\
+		1, & v_t(\mathbf{r}') \ge v_2 \\ 
+		\end{array}\right.
+\end{equation}
+
+Evaluating the middle term for the case where the field is in the linear region of the nonlinearity gives
+\begin{align}
+	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \\
+	&=T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) \varsigma v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \label{eq:preswap}  \\
+	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
+	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
+\end{align}
+where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.
+
+Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
+\begin{align}
+	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \\
+	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'}\right] \\
+	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
+\end{align}
+where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
+
+Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
+\end{equation}
+The autocorrelation of the noisy observations is
+\begin{equation}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
+\end{equation}
+
 % Therefore we can write
@@
 
-{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording array and the twisted bipolar current source.
+{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording yy and the twisted bipolar current source.
 

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
intialised the response to reviewers document

\documentclass{article}

\title{Response To Reviews - A Data-Driven Framework for Neural Field Modeling}
\author{D. Freestone, P. Aram, M. Dewar, K. Scerri, D. Grayden, V. Kadirkamanathan}

\begin{document}
    \maketitle

    \section{Reviewer 1}

        We first adress the reviewer's main concerns, followed by the reviewer's additional comments.

    \subsection{Main Concerns}

    \begin{itemize}
        \item Do not use real data for the validation of their approach
        \item Assume that a few kernel basis functions accurately represent the actual connectivity kernel, which might not be the case when using real data;
        \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)
    \end{itemize}

    \subsection{Additional Comments}

    \begin{itemize}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the recontructed kernels seem satisfying.
        \item The use of Euler discretisation and how this affects the system's behavior.
        \item The derivation of Equations (30) and (31) [spacing and width of basis functions] and make them more transparent for the general audience.
        \item The existing literature on inversion schemes for similar models of brain activity.
        \item In section 3, Table 6 is mentioned however there is no such table in the ms.
    \end{itemize}

    \section{Reviewer 2}

    We thank the author for their encouraging review. Each point raised is dealt with in turn.

\begin{itemize}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.
\item Although we all know the 1970s version of Wilson and Cowan's field equations, there was an intriguing stochasticization of these equations by Benayoun et al PloS Comp Biol 2010. I and others will value the authors' thoughts of how a more palatable stochasticization of these field equations might influence the future development of the data-assimilation framework presented in this paper.
\item This is NeuroImage, not the Physical Review. Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.
\item What is the relation of the substitution of the temporal and spatial basis functions as employed in this paper to Galerkin's projection? How do the two techniques differ? If this is close, the non-local case for a Galerkin projection (typically used in diffusive processes) has not, to my knowledge, been done. Certainly not in a way that is obvious for neural field theory. Perhaps this is my ignorance. This seems important to clarify for the rest of us.
\item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?
\item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes? I am concerned that it might be much higher than any of us wish to consider. One would perhaps be saved by the filter characteristics of brain (e.g. Phys. Rev. E 73, 051911 (2006)).
\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
\item I understand that the Mexican Hat bases are in this paper often a composite of $\theta_0$, $\theta_1$, and $\theta_2$, representing short range excitation, short range inhibition, and long range excitation. But many will be confused by this subtlety, and at times in the text the Mexican Hat basis is described as if it were a single function. I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.
\item A few comments on how to adapt the smoother for real time implementation would be helpful. I presume that one would perform the smoothing during a training phase. But one would also wish to adapt in real time as observation or control scenarios progressed. A few words of perspective would be invaluable to help others translate the author's wisdom on this method to other applications.
\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?
\item Page 45, Appendix D, Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.
\end{itemize}

\end{document}

### 2010-12-29 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 \dean{(dean: I added $(\mathbf{r}_n)$ to index the observations)}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$\dean{ = $\sigma_{\varepsilon}\mathbf{I}$}.
 
@@
 Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
-\begin{equation}
+\begin{equation}\label{eq:approx_xcorr}
 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
@@
 The autocorrelation of the noisy observations is
-\begin{equation}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
-\end{equation}
-
+\begin{equation}\label{eq:autocorrelation_of_y}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2,
+\end{equation}
+where $\delta(\cdot)$ is the Kronecker delta function. Rearranging equation~\ref{eq:autocorrelation_of_y} and substituting it into equation~\ref{eq:approx_xcorr} gives
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
+\end{equation}
+and
+\begin{equation}\label{eq:support_estimator}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) \approx T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
+\end{equation}
+The right hand side of equation~\ref{eq:support_estimator} will have the structure of the connectivity kernel. My intuition tells me that we should be able to simplify the RHS to
+\begin{equation}
+	T_s\varsigma \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right] = T_s \varsigma \sigma_d \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_{\Omega}{ m(\mathbf{r}'-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''}d\mathbf{r}'}.
+\end{equation}
+Following this, I also think that
+\begin{equation}
+	R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) = \sigma_d \int_{\Omega}{ m(\mathbf{r}_n-\mathbf{r}') \gamma(\mathbf{r}-\mathbf{r}') d\mathbf{r}'}.
+\end{equation}
+This would mean that
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi \sigma_d \int_{\Omega}{ m(\mathbf{r}_n-\mathbf{r}') \gamma(\mathbf{r}-\mathbf{r}')d\mathbf{r}'} = T_s \varsigma \sigma_d \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_{\Omega}{ m(\mathbf{r}'-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''} d\mathbf{r}'},
+\end{equation}
+which is nice.
 % Therefore we can write

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
started putting responses (only one)

@@
 
-    \begin{itemize}
+    \begin{enumerate}
         \item Do not use real data for the validation of their approach
@@
         \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)
-    \end{itemize}
+    \end{enumerate}
 
@@
 
-    \begin{itemize}
+    \begin{enumerate}
         \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the recontructed kernels seem satisfying.
@@
         \item In section 3, Table 6 is mentioned however there is no such table in the ms.
-    \end{itemize}
+    \end{enumerate}
 
@@
 
-\begin{itemize}
-    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8).
+\begin{enumerate}
+    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 [The nonlinear IntegroDifference Equation]).
 I do very much appreciate the spectral estimation of spatial and temporal scales.
@@
 I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model.
-But I will let the authors answer this question.
+But I will let the authors answer this question.\\
+    \emph{talk about model order}
 \item Although we all know the 1970s version of Wilson and Cowan's field equations, there was an intriguing stochasticization of these equations by Benayoun et al PloS Comp Biol 2010.
@@
 \item Page 45, Appendix D, Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.
-\end{itemize}
+\end{enumerate}
 

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
some points for the choice of the Gaussian basis functions

@@
 This seems important to clarify for the rest of us.
-\item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?
+\item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\
+\emph{Gaussians has semi-compact support but Fourier basis functions are global functions.
+Gaussian can be easily extended to higher dimension (dont know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}
 \item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
response to parameters in equation 41

@@
 \item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
+\emph{The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which can be made arbitrary small (e.g.
+$0<\alpha\le 10^{-4} $) to minimise higher order effect (cite Julier (The Scaled Unscented Transformation) and  Heiken (Kalman filtering and neural network) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$.
+cite Julier A New Approach for Filtering Nonlinear Systems}
+
 \item I understand that the Mexican Hat bases are in this paper often a composite of $\theta_0$, $\theta_1$, and $\theta_2$, representing short range excitation, short range inhibition, and long range excitation.

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex

--- 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
@@
 \item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
+\emph{The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which can be made arbitrary small (e.g.
+$0<\alpha\le 10^{-4} $) to minimise higher order effect (cite Julier (The Scaled Unscented Transformation) and  Haykin (Kalman filtering and neural network) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$.
+cite Julier A New Approach for Filtering Nonlinear Systems}
+
 \item I understand that the Mexican Hat bases are in this paper often a composite of $\theta_0$, $\theta_1$, and $\theta_2$, representing short range excitation, short range inhibition, and long range excitation.

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
added figure to review

@@
 \documentclass{article}
-
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
 \title{Response To Reviews - A Data-Driven Framework for Neural Field Modeling}
@@
 But many will be confused by this subtlety, and at times in the text the Mexican Hat basis is described as if it were a single function.
-I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.
+I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.\\
+\emph{I think we need to show each kernel basis function in Figure 1}
+ \begin{figure*}[!ht]
+ \begin{center}
+ \includegraphics{/Graph/pdf/fig1_revised.pdf} 
+ \end{center}
+ \caption{}
+ \label{fig:Figure1}
+ \end{figure*}
+
 \item A few comments on how to adapt the smoother for real time implementation would be helpful.

### 2010-12-29 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
-	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
+	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) y_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\right] \\
+	&= ????
+T_s\varsigma \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right)\bar{y}_t\left( \mathbf{r}' \right)\right]\, d\mathbf{r}'},
 \end{align}
@@
 \begin{align}
-	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \\
-	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'}\right] \\
-	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
+	middle term &= T_s \mathbf{E} \left[ \bar{y}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right) \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right) \, d\mathbf{r}''} \, d\mathbf{r}'} \right] \\
+	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
+	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right] \\
+	&= T_s a_1 a_2 \int_{\Omega}{ m\left( \mathbf{r}_n - \mathbf{r}'\right) \mathbf{E}\left[ v_t\left( \mathbf{r}\right) \right] d\mathbf{r}'} \\
+	&= T_s a_1 a_2 \int_{\Omega}{ m\left( \mathbf{r}_n - \mathbf{r}'\right) d\mathbf{r}'} \\
+	&= T_s a_1 a_2^2 ,
 \end{align}

### 2010-12-29 ltx/first_order_framework/LaTeX_Manuscript.tex
removed some mistakes from correation analyses

--- 2010-12-29 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \end{equation}
-\dean{(dean: I added $(\mathbf{r}_n)$ to index the observations)}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
 
@@
 which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$.
-DOES THIS GIVE US AN ESTIMATE OF THE FIELD DISTURBANCE COVARIANCE?
-NUMERICALLY IT SEEMS TO GIVE SOMETHING VERY CLOSE.
-DEPENDS ON THE BANDWIDTH OF M.
 The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$.
@@
 \end{equation}
-
-Evaluating the middle term for the case where the field is in the linear region of the nonlinearity gives
+Evaluating the middle term of the RHS of equation~\ref{eq:spatialxcorr} for the case where the field is in the linear region of the nonlinearity gives
 \begin{align}
@@
 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
-	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
+	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\right],
 \end{align}
 where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.
-
-Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
-\begin{align}
-	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \\
-	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'}\right] \\
-	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
-\end{align}
-where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
+% 
+% Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
+% \begin{align}
+% 	middle term &= T_s \mathbf{E} \left[ \bar{y}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right) \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right) \, d\mathbf{r}''} \, d\mathbf{r}'} \right] \\
+% 	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
+% 	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
+% \end{align}
+% where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
 
 Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
-\begin{equation}
+\begin{equation}\label{eq:approx_xcorr}
 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
@@
 The autocorrelation of the noisy observations is
-\begin{equation}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
-\end{equation}
-
+\begin{equation}\label{eq:autocorrelation_of_y}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2,
+\end{equation}
+where $\delta(\cdot)$ is the Kronecker delta function. Rearranging equation~\ref{eq:autocorrelation_of_y} and substituting it into equation~\ref{eq:approx_xcorr} gives
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
+\end{equation}
+and
+\begin{equation}\label{eq:support_estimator}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) \approx T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
+\end{equation}
+The right hand side of equation~\ref{eq:support_estimator} will have the structure of the connectivity kernel.
+
+This may hold:
+\begin{equation}
+	R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) = \sigma_d \int_{\Omega}{ m(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}')\int_{\Omega}{ m(\mathbf{r}'_n-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''} d\mathbf{r}'}.
+\end{equation}
+If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.
 % Therefore we can write

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
added revised figure1
response to the lead field

@@
         \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)
+	\emph{We interested in intracranial EEG, and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if  non-linear we need unscented transform on observation and if not the state estimation remains unchanged.)}
     \end{enumerate}
@@
  \begin{center}
- \includegraphics{/Graph/pdf/fig1_revised.pdf} 
+ \includegraphics{./Graph/pdf/fig1_revised.pdf} 
  \end{center}

### 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
response to the lead field

--- 2010-12-29 ltx/first_order_framework/response_to_reviews.tex
@@
         \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)
+	\emph{We interested in intracranial EEG, and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if  non-linear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
+considered.
+This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored.
+In fact the observation model is not
+quite realistic, without lead field and without amplifier characteristics.}
     \end{enumerate}

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex
added to reviewer comments

@@
 \usepackage{graphicx}
+\usepackage{anysize} %<-for setting margins
+\marginsize {1.6cm}{1.6cm}{2.0cm}{2cm}
+\usepackage{color}
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+
 \title{Response To Reviews - A Data-Driven Framework for Neural Field Modeling}
@@
 
-        We first adress the reviewer's main concerns, followed by the reviewer's additional comments.
+        We first address the reviewer's main concerns, followed by the reviewer's additional comments.
 
@@
         \item Do not use real data for the validation of their approach
+
+	\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data.
+However, before validating the method on real data we believe that it is important to first validate the method artificial data, where the true and estimated parameters can be compared.
+Given the space limitations on the article, it is not feasible to show examples using real data in this paper.
+Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.
+In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.}
+
         \item Assume that a few kernel basis functions accurately represent the actual connectivity kernel, which might not be the case when using real data;
+
+	\emph{The examples presented in the paper use the Mexican hat connectivity kernel.
+The framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions, parametrized by a coefficient vector $\mathbf{\theta}$.
+The mathematical formulation does not restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented.
+Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support.
+For more complex basis functions some of the analytic derivations described in the appendix may have to be performed numerically.
+We have added the above statements to the methods section to be more explicit in the subtleties of the method.}
+
         \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)
@@
     \begin{enumerate}
-        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the recontructed kernels seem satisfying.
+        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
         \item The use of Euler discretisation and how this affects the system's behavior.
@@
 \emph{Gaussians has semi-compact support but Fourier basis functions are global functions.
-Gaussian can be easily extended to higher dimension (dont know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}
+Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}
 \item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?

### 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
added to reviewer comments

@@
 This work provides a fundamental link between the theoretical advances in neural field modeling and electrophysiological data.
-The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
+\dean{Dean (for reviewer 1 comment 1) (this is copied from the abstract): To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters.} The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
 Then a finite-dimensional neural field model is derived.

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex
edits to response letter

@@
     \subsection{Main Concerns}
+    It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.
 
@@
 	\emph{The examples presented in the paper use the Mexican hat connectivity kernel.
-The framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions, parametrized by a coefficient vector $\mathbf{\theta}$.
+The framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented.
 Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support.
-For more complex basis functions some of the analytic derivations described in the appendix may have to be performed numerically.
-We have added the above statements to the methods section to be more explicit in the subtleties of the method.}
+For more complex basis functions some of the analytic derivations described in the Appendix may have to be performed numerically.
+We have added the above statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}
 
         \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)
-	\emph{We interested in intracranial EEG, and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if  non-linear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
+
+	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
+Amendments have been made to the Introduction, Method, and Discussion.
+We have primarily developed the framework for higher density intracranial measurements.
+We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.
+
+	, and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
 considered.
 This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored.
-In fact the observation model is not
-quite realistic, without lead field and without amplifier characteristics.}
+In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
     \end{enumerate}
@@
 But I will let the authors answer this question.\\
+
     \emph{talk about model order}
+
 \item Although we all know the 1970s version of Wilson and Cowan's field equations, there was an intriguing stochasticization of these equations by Benayoun et al PloS Comp Biol 2010.
@@
 \item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\
+
 \emph{Gaussians has semi-compact support but Fourier basis functions are global functions.
 Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}
+
 \item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?

### 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to response letter

@@
 By exploiting the isotropy of the connectivity basis functions, they can be written as
-$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$.
-We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown.
-Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model.
+$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
+\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
+The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented.
+Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support.}
+
+Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model.
 Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex
added more to the response to the review and editted the manuscript

@@
 	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
-Amendments have been made to the Introduction, Method, and Discussion.
+Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion.
 We have primarily developed the framework for higher density intracranial measurements.
-We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.
+We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.}
 
-	, and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
+	\emph{..., and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
 considered.

### 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
added more to the response to the review and editted the manuscript

@@
 In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the \citet{Wilson1973} neural field model.
-This work provides a fundamental link between the theoretical advances in neural field modeling and electrophysiological data.
-\dean{Dean (for reviewer 1 comment 1) (this is copied from the abstract): To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters.} The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
+This work provides a fundamental link between the theoretical advances in neural field modeling and \dean{(for reviewer 1, comment 3:) high resolution intracranial} electrophysiological data.
+\dean{(for reviewer 1 comment 1:) (this is copied from the abstract) To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters.} The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
 Then a finite-dimensional neural field model is derived.
@@
 
-The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf y_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
-\begin{equation}
-    \label{eq:ObservationEquation}
-	y_t(\mathbf{r}_n) =
-	\int_{\Omega}{
-	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
-	\, d\mathbf{r}'} + 
-	\varepsilon_t(\mathbf{r}_n), 
+The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf{y}_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
+\begin{equation}\label{eq:ObservationEquation}
+	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \varepsilon_t(\mathbf{r}_n), 
 \end{equation}
 where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
+\dean{(for reviewer 1, comment 3:) Note, since we are considering intracranial measurements recorded directly from the surface or within the cortex the lead field is not modeled by the observation equation.}
 

### 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
added the observation autocor proof

@@
 \end{equation}
-If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.
+If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.\\
+the proof of the above\\
+\begin{align}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}_n\right)\right] \\
+	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
+	&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right]\\
+	&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''}\\
+	&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''}\label{eq:ObsCorr}
+\end{align}
+
 % Therefore we can write

### 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

--- 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \end{equation}
-If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.
+If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.\\
+the proof of the above\\
+\begin{align}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}_n\right)\right] \\
+	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
+	&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right]\\
+	&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''}\\
+	&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''}\label{eq:ObsCorr}
+\end{align}
+
 % Therefore we can write

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex
deletd width from additional comments review1 number3
added proof of shannon sampling

@@
         \item The use of Euler discretisation and how this affects the system's behavior.
-        \item The derivation of Equations (30) and (31) [spacing and width of basis functions] and make them more transparent for the general audience.
+        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.\\ \\
+\emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points.
+The continuous field $v(\mathbf r)$ can be sampled using a field of Dirac-delta functions, $\delta(\mathbf r)$ located at the lattice points as
+\begin{equation}
+ v_s(\Delta J)=\sum_{J \in \mathbb Z^n}\delta(\mathbf r-\Delta J)v(\mathbf r)
+\end{equation}
+taking Fourier transfom of the sampled field $v_s(\Delta J)$ we have
+\begin{align}
+ V_s(\boldsymbol{\nu})&=\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n}\delta(\boldsymbol{\nu}-\frac{J}{\Delta})\ast V(\boldsymbol\nu)\\
+&=\frac{1}{\Delta^n}V(\boldsymbol\nu)+\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n\setminus \mathbf \{0\}}V(\boldsymbol{\nu}-\frac{J}{\Delta})
+\end{align}
+hence,$V_s(\boldsymbol{\nu})$ contains $V(\boldsymbol\nu)$ plus infinitely many copies (aliases) of  $V(\boldsymbol\nu)$ repeated on the regular lattice $\left\lbrace \frac{J}{\Delta}; J\in \mathbb Z^n\right\rbrace$.
+Given the dynamic field is band-limited with a cut-off frequency $\boldsymbol\nu_c$ in order for $V(\boldsymbol\nu)$ to be disjointed with its aliases the amount of shift $\frac{1}{\Delta}$ must be at least $2\nu_c$, therefore
+\begin{equation}\label{ap:Shannon}
+ \Delta\le\frac{1}{2\rho\nu_c}
+\end{equation}
+where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. To recover the continuous field, we first introduce a low-pass filter \begin{equation}
+F(\boldsymbol \nu)=\begin{cases}
+  \Delta^n & |\boldsymbol\nu|\le \boldsymbol\nu_c \\
+  0 & \text{otherwise}
+\end{cases} 
+\end{equation}
+if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum can be recovered using
+\begin{equation}
+ V(\boldsymbol\nu)=F(\boldsymbol \nu)V_s(\boldsymbol\nu)
+\end{equation}
+taking inverse Fourier transform we have
+\begin{align}
+v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
+&=\sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
+\end{align}
+However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the summ of weighted, spatially translated, continuous  basis functions.}
+
         \item The existing literature on inversion schemes for similar models of brain activity.

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex
minor correction

@@
 \end{equation}
-if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum can be recovered using
+if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum, $V(\boldsymbol\nu)$ can be recovered using
 \begin{equation}
@@
 \end{align}
-However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the summ of weighted, spatially translated, continuous  basis functions.}
+However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the sum of weighted, spatially translated, continuous  basis functions.}
 

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex
added to reviewer comments

@@
         \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
+
         \item The use of Euler discretisation and how this affects the system's behavior.
-        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.\\ \\
+
+		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
+		Filtering for the estimation of neural mass models from data [1-3],
+		[13]. In fact from those papers stressed the importance of carrying out
+		a high order discretization of the differential equations, which should
+		be in fact treated as stochastic. In equation (S1.1) of the extended
+		derivation, it is shown that an Euler approximation is taken which may
+		even change the dynamical properties of the system. The authors should
+		discuss this issue.''}
+
+        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.
+
 \emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points.

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
added an alternative derivation to Parhams for Shannons sampling theorem

@@
 \end{equation}
-taking Fourier transfom of the sampled field $v_s(\Delta J)$ we have
+taking Fourier transform of the sampled field $v_s(\Delta J)$ we have
 \begin{align}
@@
 	v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
-&=\sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
+	&= \sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
 \end{align}
 However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the sum of weighted, spatially translated, continuous  basis functions.}
+
+Parham: I made a copy for my edits so that we don't get conflicts.
+
+\emph{Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
+The observations can be considered samples from a continuous field that is filtered (convolved) by the observation kernel as
+\begin{equation}
+	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
+\end{equation} 
+where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
+\begin{align}
+ Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
+	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
+\end{align} 
+It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice with spacing $\frac{1}{\Delta_y}$.
+Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$.
+In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\frac{1}{\Delta_y}$ must be at least $2\boldsymbol\nu_{cy}$ (since each alias has a spectral range of
+\begin{equation}
+	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
+\end{equation}
+Therefore, to avoid aliasing the distance between observations must satisfy
+\begin{equation}\label{eq:SamplingCriteria}
+	\frac{1}{\Delta_y} \ge 2\nu_{cy}.
+\end{equation}
+Since the observation kernel is not an ideal filter an oversampling parameter should be included to further separate the aliases.
+Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
+\begin{equation}\label{ap:Shannon}
+	\Delta_y\le\frac{1}{2\rho\nu_{cy}},
+\end{equation}
+where $\rho \in \mathbb{R} \ge 1$. }
 

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
small edit to derivation for Shannons sampling

@@
 \emph{Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
-The observations can be considered samples from a continuous field that is filtered (convolved) by the observation kernel as
+The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
 \begin{equation}
@@
 \end{align} 
-It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice with spacing $\frac{1}{\Delta_y}$.
+It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice centered at $n\Delta_y^{-1}$.
 Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$.
-In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\frac{1}{\Delta_y}$ must be at least $2\boldsymbol\nu_{cy}$ (since each alias has a spectral range of
+In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
 \begin{equation}

### 2010-12-31 ltx/first_order_framework/LaTeX_Manuscript.tex
small edit to derivation for Shannons sampling

@@
 \end{equation}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=0,...,n_y-1$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
 \dean{(for reviewer 1, comment 3:) Note, since we are considering intracranial measurements recorded directly from the surface or within the cortex the lead field is not modeled by the observation equation.}

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
added comments to address comment 1 from reviewer 2

@@
 
-\emph{Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
+\emph{This appendix provides a derivation for equations ??
+and ??.
+The derivation is adapted from (Sanner et al., 1992, and Scerri et al., 2009).
+Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
 The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
@@
     \emph{talk about model order}
+
+	\emph{Indeed there will always be a mismatch between the a mathematical model and the natural phenomena it is attempting to describe.
+The model proposed in our paper is modest in terms of the temporal dynamics, where the state transition is assumed to be first-order.
+However, the development of the framework for this simple model is a significant development that can be expanded to include longer range time dependencies.
+A major benefit in using a mean field model is the freedom to lump detailed parameters, such as specific ion concentrations, into other parameters such as the connectivity kernel coefficients.
+An extension to our framework that is currently in development is to allow for time-varying kernel parameters.
+}
 

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
added laplace method to extend the Greenie bastard

@@
 
-	\emph{Indeed there will always be a mismatch between the a mathematical model and the natural phenomena it is attempting to describe.
+	\emph{Indeed, there will always be a mismatch between a mathematical model and the natural phenomena it is attempting to describe.
 The model proposed in our paper is modest in terms of the temporal dynamics, where the state transition is assumed to be first-order.
-However, the development of the framework for this simple model is a significant development that can be expanded to include longer range time dependencies.
-A major benefit in using a mean field model is the freedom to lump detailed parameters, such as specific ion concentrations, into other parameters such as the connectivity kernel coefficients.
-An extension to our framework that is currently in development is to allow for time-varying kernel parameters.
-}
+However, the development of the framework for this modest brain model is a significant development that can be expanded to include longer range time dependencies.
+A major benefit in using a mean field model is the freedom to lump detailed parameters, such as specific ion concentrations, into more general parameters such as the connectivity kernel coefficients that describe the net system gain.
+Please note, we have assumed that factors influencing excitability are stationary over the estimation period.
+This is a reasonable assumption is applying the framework to an evoked potential experiment.
+An extension to our framework, that is currently in development, is to allow for time-varying parameter estimates.
+This will allow the application of the framework to longer-term data recordings.
+The problem then can be posed in terms of convergence time and estimation accuracy vs.
+nonstationarity of the metabolic processes and other unmodeled brain dynamics.}
 
@@
 I and others will value the authors' thoughts of how a more palatable stochasticization of these field equations might influence the future development of the data-assimilation framework presented in this paper.
+
 \item This is NeuroImage, not the Physical Review.
 Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.
+
 \item What is the relation of the substitution of the temporal and spatial basis functions as employed in this paper to Galerkin's projection?

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
got rid of my version of Shannon theorem

@@
         \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.
-
-\emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points.
-The continuous field $v(\mathbf r)$ can be sampled using a field of Dirac-delta functions, $\delta(\mathbf r)$ located at the lattice points as
-\begin{equation}
- v_s(\Delta J)=\sum_{J \in \mathbb Z^n}\delta(\mathbf r-\Delta J)v(\mathbf r)
-\end{equation}
-taking Fourier transform of the sampled field $v_s(\Delta J)$ we have
-\begin{align}
- V_s(\boldsymbol{\nu})&=\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n}\delta(\boldsymbol{\nu}-\frac{J}{\Delta})\ast V(\boldsymbol\nu)\\
-&=\frac{1}{\Delta^n}V(\boldsymbol\nu)+\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n\setminus \mathbf \{0\}}V(\boldsymbol{\nu}-\frac{J}{\Delta})
-\end{align}
-hence,$V_s(\boldsymbol{\nu})$ contains $V(\boldsymbol\nu)$ plus infinitely many copies (aliases) of  $V(\boldsymbol\nu)$ repeated on the regular lattice $\left\lbrace \frac{J}{\Delta}; J\in \mathbb Z^n\right\rbrace$.
-Given the dynamic field is band-limited with a cut-off frequency $\boldsymbol\nu_c$ in order for $V(\boldsymbol\nu)$ to be disjointed with its aliases the amount of shift $\frac{1}{\Delta}$ must be at least $2\nu_c$, therefore
-\begin{equation}\label{ap:Shannon}
-	\Delta\le\frac{1}{2\rho\nu_c}
-\end{equation}
-where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. To recover the continuous field, we first introduce a low-pass filter \begin{equation}
-F(\boldsymbol \nu)=\begin{cases}
-  \Delta^n & |\boldsymbol\nu|\le \boldsymbol\nu_c \\
-0 & \text{otherwise}
-\end{cases} 
-\end{equation}
-if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum, $V(\boldsymbol\nu)$ can be recovered using
-\begin{equation}
-	V(\boldsymbol\nu)=F(\boldsymbol \nu)V_s(\boldsymbol\nu)
-\end{equation}
-taking inverse Fourier transform we have
-\begin{align}
-	v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
-	&= \sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
-\end{align}
-However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the sum of weighted, spatially translated, continuous  basis functions.}
-
-Parham: I made a copy for my edits so that we don't get conflicts.
 

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
tried to clarify the green function

@@
 \item This is NeuroImage, not the Physical Review.
-Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.
+Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.\\
+
+\emph{The synaptic response kernel can be viewed as the Green function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$ i.e., satisfying
+\begin{equation}
+	\label{GreensFuncDef} \textrm{D}h\left( t \right) = \delta \left( t \right), 
+\end{equation} 
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ on equation (5) we have
+\begin{align}
+ \textrm{D}v\left(\mathbf r,t\right)&= \textrm{D}\left(h\ast g\right)\left(\mathbf r,t\right)\\
+&=\left(\textrm{D}h\ast g\right)\left(\mathbf r,t\right)\\
+&=\left(\delta \left(t\right)\ast g\right)\left(\mathbf r,t\right)\\
+&=g\left(\mathbf r,t\right)
+\end{align}
+where $\ast$ denotes convolution operator. This gives the standard form of the model
+\begin{equation}
+	\label{FinalFormContinuous} 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
+\end{equation}}
 

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
added a comment on discretisation
deletd extra bit from lead field

@@
 
-	\emph{..., and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
-considered.
-This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored.
-In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
     \end{enumerate}
@@
 		even change the dynamical properties of the system. The authors should
-		discuss this issue.''}
+		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}
 

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex
minor correction

@@
 	\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data.
-However, before validating the method on real data we believe that it is important to first validate the method artificial data, where the true and estimated parameters can be compared.
+However, before validating the method on real data we believe that it is important to first validate the method on artificial data, where the true and estimated parameters can be compared.
 Given the space limitations on the article, it is not feasible to show examples using real data in this paper.
@@
 \end{equation} 
-where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ on equation (5) we have
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ on equation (5) from the main text we have
 \begin{align}
@@
 E 73, 051911 (2006)).
-\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
+\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\
 \emph{The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which can be made arbitrary small (e.g.
-$0<\alpha\le 10^{-4} $) to minimise higher order effect (cite Julier (The Scaled Unscented Transformation) and  Haykin (Kalman filtering and neural network) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$.
-cite Julier A New Approach for Filtering Nonlinear Systems}
+$0<\alpha\le 10^{-4} $) to minimise higher order effect (Julier et al., 2002, and Haykin, 2001) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$ (Julier et al., 1995).}
 

### 2011-01-01 ltx/first_order_framework/response_to_reviews.tex
edits to paper and review letter

@@
 	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
-Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion.
+Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion (Implications for Experimental Design).
 We have primarily developed the framework for higher density intracranial measurements.
@@
 
-\emph{This appendix provides a derivation for equations ??
-and ??.
-The derivation is adapted from (Sanner et al., 1992, and Scerri et al., 2009).
-Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
-The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
-\begin{equation}
-	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
-\end{equation} 
-where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
-\begin{align}
- Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
-	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
-\end{align} 
-It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice centered at $n\Delta_y^{-1}$.
-Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$.
-In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
-\begin{equation}
-	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
-\end{equation}
-Therefore, to avoid aliasing the distance between observations must satisfy
-\begin{equation}\label{eq:SamplingCriteria}
-	\frac{1}{\Delta_y} \ge 2\nu_{cy}.
-\end{equation}
-Since the observation kernel is not an ideal filter an oversampling parameter should be included to further separate the aliases.
-Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
-\begin{equation}\label{ap:Shannon}
-	\Delta_y\le\frac{1}{2\rho\nu_{cy}},
-\end{equation}
-where $\rho \in \mathbb{R} \ge 1$. }
+\emph{To address this point, we have added an extra appendix with a derivation of the sampling theorem with the appropriate cross-referencing to the main text.
+An effort was made to keep this derivation minimal and as clear as possible.
+We have also added the references to relevant part of the text (that should have been there before, as the reviewer has correctly pointed out).
+We felt that it was worth adding the extra appendix to provide a clear derivation that is contextually and notationally relevant to this paper, as the derivations cited papers may not be clear to the Neuroimage general audience.}
 
         \item The existing literature on inversion schemes for similar models of brain activity.
+
         \item In section 3, Table 6 is mentioned however there is no such table in the ms.
@@
 
-    \emph{talk about model order}
-
 	\emph{Indeed, there will always be a mismatch between a mathematical model and the natural phenomena it is attempting to describe.
@@
 Please note, we have assumed that factors influencing excitability are stationary over the estimation period.
-This is a reasonable assumption is applying the framework to an evoked potential experiment.
+This is a reasonable assumption is applying the framework to an evoked-potential experiment.
 An extension to our framework, that is currently in development, is to allow for time-varying parameter estimates.
 This will allow the application of the framework to longer-term data recordings.
-The problem then can be posed in terms of convergence time and estimation accuracy vs.
+The problem can then be posed in terms of convergence time and estimation accuracy vs.
 nonstationarity of the metabolic processes and other unmodeled brain dynamics.}
@@
 \item This is NeuroImage, not the Physical Review.
-Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.\\
+Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.
 
-\emph{The synaptic response kernel can be viewed as the Green function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$ i.e., satisfying
-\begin{equation}
-	\label{GreensFuncDef} \textrm{D}h\left( t \right) = \delta \left( t \right), 
-\end{equation} 
-where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ on equation (5) from the main text we have
-\begin{align}
- \textrm{D}v\left(\mathbf r,t\right)&= \textrm{D}\left(h\ast g\right)\left(\mathbf r,t\right)\\
-&=\left(\textrm{D}h\ast g\right)\left(\mathbf r,t\right)\\
-&=\left(\delta \left(t\right)\ast g\right)\left(\mathbf r,t\right)\\
-&=g\left(\mathbf r,t\right)
-\end{align}
-where $\ast$ denotes convolution operator. This gives the standard form of the model
-\begin{equation}
-	\label{FinalFormContinuous} 
-	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
-\end{equation}}
+\emph{A more detailed explanation has been added to the manuscript.}
 
@@
 This seems important to clarify for the rest of us.
+
 \item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\
@@
 E 73, 051911 (2006)).
+
 \item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\
+
 \emph{The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which can be made arbitrary small (e.g.
@@
 I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.\\
+
 \emph{I think we need to show each kernel basis function in Figure 1}
+
  \begin{figure*}[!ht]

### 2011-01-01 ltx/first_order_framework/LaTeX_Manuscript.tex
added comments to address comment 1 from reviewer 2
added laplace method to extend the Greenie bastard
edits to paper and review letter

@@
 \end{equation}
-Now we shall express the synaptic response kernel as a Green's function 
+
+\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
+A Green's function satisfies
 \begin{equation}
@@
 \end{equation} 
-where $\textrm{D}=d/dt + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This gives the standard form of the model
+where $\delta(t)$ is the Dirac-delta function. To understand this property, one can take the Laplace transform of $\textrm{D}$ and $h(t)$, giving
+\begin{align}
+	\mathcal{L}\{h(t)\} &= \frac{1}{s+\zeta} \\
+	\mathcal{L}\{\textrm{D}\} &= s+\zeta,
+\end{align}
+and then taking the inverse Laplace transform of $\mathcal{L}\{\textrm{D}\}$ applied to $\mathcal{L}\{h(t)\}$, giving
+\begin{align}
+	\mathcal{L}^{-1}\left\{\frac{s+\zeta}{s+\zeta}\right\} &= \mathcal{L}^{-1}\left\{1\right\} \\
+	&= \delta \left( t \right).
+\end{align}
+Applying the differential operator $\textrm{D}$ to equation~\ref{FullDoubleIntModel} gives
+\begin{align}
+ \textrm{D}v\left(\mathbf r,t\right)&= \textrm{D}\left(h\ast g\right)\left(\mathbf r,t\right)\\
+&=\left(\textrm{D}h\ast g\right)\left(\mathbf r,t\right)\\
+&=\left(\delta \left(t\right)\ast g\right)\left(\mathbf r,t\right)\\
+&=g\left(\mathbf r,t\right)
+\end{align}
+where $\ast$ denotes convolution operator.} This gives the standard form of the model
 \begin{equation}
@@
 \end{equation}
+
 To arrive at the integro-difference equation (IDE) form of the model, we discretize time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
@@
 	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
-	&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right]\\
-	&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''}\\
-	&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''}\label{eq:ObsCorr}
+	&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\\
+	&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\label{eq:ObsCorr}
 \end{align}
@@
 where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
+\dean{(reviewer 1, additional comment 3:) A derivation of the sampling theorem is provided in \ref{App:SamplingTheorem} that is based on the work of \citet{Sanner1992} and \citet{Scerri2009}}.
 This condition must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
@@
 As pointed out in numerous publications by Freeman and colleagues (see \citet{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
-Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
+Importantly, the spatial frequency analysis tools presented in this paper can be used to design \dean{(reviewer 1, item 3:) high density intracranial} electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
 In addition, the frequency analysis highlights the relationship between the width of the sensors and the information in the data.
@@
 In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
+
+\subsection{Real time implementation}
+\dean{(comment 1 and 9 from reviewer 2:) The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol.
+Over the time duration of an experimental paradigm the connectivity and synaptic kernel parameters are assumed to be stationary.
+However, if the method is applied to a continuous recording over a longer time duration it is unlikely that the parameters will be stationary.
+If fact, it is likely that changes in the parameter values would be of most interest.
+To implement the algorithm in a real-time scenario the we would assume that the parameters are stationary over a time period (window) where the estimation is performed.
+The parameter of the previous window can be used to initialize parameters of the next window.
+}
 
@@
 {\bf Figure 14. Observation kernel experimental results}. Amplitude of the envelope of the signal recorded from the electrode at the center of the array vs. the source position.
+
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig1.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure1}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig2.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure2}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig3.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure3}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig4.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure4}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig5.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure5}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig6.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure6}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig7.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure7}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig8.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure8}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig9.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure9}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig10.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure10}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig11.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure11}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig12.pdf}
+\end{center}
+\caption{}
+\label{fig:Figure12}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig13.pdf}
+\end{center}
+\caption{}
+\label{fig:SensorAndSource}
+\end{figure*}
+\clearpage
+\newpage
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics{./Graph/pdf/fig14.pdf}
+\end{center}
+\caption{}
+\label{fig:Ch3}
+\end{figure*}
+\clearpage
+\newpage
 
@@
 The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
+
 \section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
@@
 This completes the derivation.
+
 \section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}
@@
 where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.
+
 \section{Mean and Covariance of the State Disturbance }\label{App:ColoredNoise} 
@@
 \end{align}
+
+\section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
+\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}.
+The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}.
+Consider the cortical sheet defined on the surface $\Omega$ with sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
+The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
+\begin{equation}
+	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
+\end{equation} 
+where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
+\begin{align}
+ Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
+	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
+\end{align} 
+It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$.
+Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$.
+In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
+\begin{equation}
+	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
+\end{equation}
+Therefore, to avoid aliasing the distance between observations must satisfy
+\begin{equation}\label{eq:SamplingCriteria}
+	\frac{1}{\Delta_y} \ge 2\boldsymbol{\nu}_{cy}.
+\end{equation}
+Since the observation kernel is not an ideal filter, an oversampling parameter should be included to further separate the aliases.
+Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
+\begin{equation}\label{ap:Shannon}
+	\Delta_y\le\frac{1}{2\rho\boldsymbol{\nu}_{cy}},
+\end{equation}
+where $\rho \in \mathbb{R} \ge 1$.}
+
 \section{Spatial Cut-off Frequency of the Field Basis Functions}\label{App:FrequencyAnalysis}

### 2011-01-01 ltx/first_order_framework/LaTeX_Manuscript.tex
comment on  sampling
commit for pull

@@
 However, if the method is applied to a continuous recording over a longer time duration it is unlikely that the parameters will be stationary.
-If fact, it is likely that changes in the parameter values would be of most interest.
-To implement the algorithm in a real-time scenario the we would assume that the parameters are stationary over a time period (window) where the estimation is performed.
-The parameter of the previous window can be used to initialize parameters of the next window.
-}
+If fact, it is likely that changes in the parameter values would be of most interest.}
+
+\dean{To implement the algorithm in a real-time scenario the we would assume that the parameters are stationary over a time period (window) where the estimation is performed.
+The parameter of the previous window can be used to initialize parameters of the next window.}
 

### 2011-01-02 ltx/first_order_framework/LaTeX_Manuscript.tex
editted sampling theorem derivation

@@
 
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+% \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+\newcommand{\dean}[1]{\textcolor{red}{#1}}
+
+ \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
 
@@
 Consider the cortical sheet defined on the surface $\Omega$ with sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
-The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
+Noise-free observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
 \begin{equation}
@@
 \end{equation} 
-where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
-\begin{align}
- Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
-	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
-\end{align} 
+\parham{\begin{equation}
+	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
+\end{equation}}
+where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of \parham{$\mathbf y$~}$y(\mathbf{r}_n)$ is
+\begin{align}
+ Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{\mathbf{n}_n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
+	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu) + \frac{1}{\Delta_y^2} \sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{\mathbf{n}_n}{\Delta_y}\right),
+\end{align} 
+where $\mathbf{n}$ is a $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{n}$).
 It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$.

### 2011-01-02 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to correlation analysis

@@
 The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}.
-To demonstrate the method for the neural field model, we first define the spatial cross-correlation function between consecutive observations as
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}_n\right)\right] \\
-	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}_n\right)\right) \right], \label{eq:ObsXCorr}
+To demonstrate the method for the neural field model we assume the sensors are infinitesimally close (continuous observation).
+The spatial cross-correlation function between consecutive observations is defined as
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}\right)\right] \\
+	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}_n\right)\right) \right], \label{eq:ObsXCorr}
 \end{align}
 where $\mathbf{E}[\cdot]$ is the expected value. Since the observation noise is temporally white and independent of the field, equation~\ref{eq:ObsXCorr} reduces to
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
-	&=\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right],
-\end{align}
-where $\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)$ is the noise-free observation.
-
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right].
+\end{equation}
 Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
 \begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} + e_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'} \right] \\
-	 &= \xi\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) d\mathbf{r}'} \right] \nonumber \\
-	&+ T_s\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'} \right] \nonumber \\
-	&+ \mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}'\right)\, d\mathbf{r}' } \right]
-	\label{eq:spatialxcorr}
-\end{align}
-
-The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
-\begin{equation}
-	\xi\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{\bar{y}_{t},\bar{y}_{t}}(\boldsymbol{\tau}),
-\end{equation}
-which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$.
-The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$.
-
-To understand the middle term, the sigmoid activation function, $f(\cdot)$, is approximated by the piecewise function
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{m\left(\mathbf{r}-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} + e_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'} \right] \\
+	 &= \xi\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) d\mathbf{r}'} \right] \nonumber \\
+	&+ T_s\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega} {m\left(\mathbf{r} - \mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'} \right] \nonumber \\
+	&+ \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega} { m\left(\mathbf{r} - \mathbf{r}'\right) e_t \left(\mathbf{r}'\right)\, d\mathbf{r}' } \right]
+	\\
+	&= R_1(\boldsymbol{\tau}) + R_2(\boldsymbol{\tau}) + R_3(\boldsymbol{\tau}).\label{eq:spatialxcorr} 
+\end{align}
+The last term on the right hand side of equation~\ref{eq:spatialxcorr} is
+\begin{equation}
+	R_3(\boldsymbol{\tau}) = 0,
+\end{equation}
+since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$. Putting to other two terms back together we can write
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{m\left(\mathbf{r}-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} \right)\, d\mathbf{r}'} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}}M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) F(\boldsymbol{\nu}) \right) \right\} \right]
+\end{align}
+where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform. Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
 \begin{equation}
@@
 \end{equation}
-Evaluating the middle term of the RHS of equation~\ref{eq:spatialxcorr} for the case where the field is in the linear region of the nonlinearity gives
-\begin{align}
-	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \\
-	&=T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) \varsigma v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \label{eq:preswap}  \\
-	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
-	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\right],
-\end{align}
-where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.
+Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. From this we get the simplified cross-correlation function
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu})  \right) \right\} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r}) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right] \\
+	&= (R_{y_t,y_t} - \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2) \ast \mathbf{E}\left[\left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right]
+\end{align}
 % 
-% Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
 % \begin{align}
-% 	middle term &= T_s \mathbf{E} \left[ \bar{y}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right) \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right) \, d\mathbf{r}''} \, d\mathbf{r}'} \right] \\
-% 	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
-% 	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
+% 	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \\
+% 	&=T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) \varsigma v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \label{eq:preswap}  \\
+% 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
+% 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\right],
 % \end{align}
-% where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
-
-Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
-\begin{equation}\label{eq:approx_xcorr}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
-\end{equation}
-The autocorrelation of the noisy observations is
-\begin{equation}\label{eq:autocorrelation_of_y}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2,
-\end{equation}
-where $\delta(\cdot)$ is the Kronecker delta function. Rearranging equation~\ref{eq:autocorrelation_of_y} and substituting it into equation~\ref{eq:approx_xcorr} gives
-\begin{equation}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
-\end{equation}
-and
-\begin{equation}\label{eq:support_estimator}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) \approx T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
-\end{equation}
-The right hand side of equation~\ref{eq:support_estimator} will have the structure of the connectivity kernel.
-
-This may hold:
-\begin{equation}
-	R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) = \sigma_d \int_{\Omega}{ m(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}')\int_{\Omega}{ m(\mathbf{r}'_n-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''} d\mathbf{r}'}.
-\end{equation}
-If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.\\
-the proof of the above\\
-\begin{align}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}_n\right)\right] \\
-	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
-	&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\\
-	&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\label{eq:ObsCorr}
+% where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.
+% % 
+% % Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
+% % \begin{align}
+% % 	middle term &= T_s \mathbf{E} \left[ \bar{y}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right) \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right) \, d\mathbf{r}''} \, d\mathbf{r}'} \right] \\
+% % 	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
+% % 	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
+% % \end{align}
+% % where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
+% 
+% The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
+% \begin{equation}
+% 	R_1(\boldsymbol{\tau}) = \xi R_{\bar{y}_{t},\bar{y}_{t}}(\boldsymbol{\tau}),
+% \end{equation}
+% which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$.
+% 
+% Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
+% \begin{equation}\label{eq:approx_xcorr}
+% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
+% \end{equation}
+% The autocorrelation of the noisy observations is
+% \begin{equation}\label{eq:autocorrelation_of_y}
+% 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2,
+% \end{equation}
+% where $\delta(\cdot)$ is the Kronecker delta function. Rearranging equation~\ref{eq:autocorrelation_of_y} and substituting it into equation~\ref{eq:approx_xcorr} gives
+% \begin{equation}
+% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
+% \end{equation}
+% and
+% \begin{equation}\label{eq:support_estimator}
+% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) \approx T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
+% \end{equation}
+% The right hand side of equation~\ref{eq:support_estimator} will have the structure of the connectivity kernel. To show this let
+% \begin{align}
+% 	Z &= \mathcal{F}\left\{\bar{y}_t\left( \mathbf{r} + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r},\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right\} \\
+% 	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})\bar{Y}(\boldsymbol{\nu}) \ast W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \\
+% 	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \ast \bar{Y}(\boldsymbol{\nu}),
+% \end{align}
+% using the associativity with scalar multiplication property of convolution. Now taking the inverse Fourier transform
+% \begin{align}
+% 	z &= \mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \ast \bar{Y}(\boldsymbol{\nu})\right\} \\
+% 	&= w(\mathbf{r}+\boldsymbol{\tau}) \ast \bar{y}^2(\mathbf{r}) \\
+% 	&= \int_{\Omega}{w(\mathbf{r}+\boldsymbol{\tau},\mathbf{r}')\bar{y}^2(\mathbf{r}')d\mathbf{r}'}
+% \end{align}
+% 
+% 
+% This may hold:
+% \begin{equation}
+% 	R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) = \sigma_d \int_{\Omega}{ m(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}')\int_{\Omega}{ m(\mathbf{r}'_n-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''} d\mathbf{r}'}.
+% \end{equation}
+% If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.\\
+% the proof of the above\\
+% \begin{align}
+% 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
+% 		&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+% 		&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\\
+% 		&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\label{eq:ObsCorr}
+% \end{align}
+
+Alternative, we can write
+\begin{align}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}_n\right)\right]\\
+	&= \mathbf{E}\left[m(\mathbf{r}_n+\boldsymbol{\tau})\ast v(\mathbf{r}) \times m(\mathbf{r}_n)\ast v(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[m(\mathbf{r}_n+\boldsymbol{\tau}) \ast m(\mathbf{r}_n) \ast v^2(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
+\end{align}
+To show how we get this result, we first define
+\begin{align}
+	K(\boldsymbol{\nu}) &= \mathcal{F}\left\{m(\mathbf{r}_n+\boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}_n) \ast v(\mathbf{r})\right\} \\
+	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \\
+	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \\
+	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}).
+\end{align}
+Now taking the inverse Fourier transform we get
+\begin{align}
+	k(\mathbf{r}) = m(\mathbf{r}_n+\boldsymbol{\tau}) \ast m(\mathbf{r}_n) \ast v^2(\mathbf{r}).
 \end{align}
@@
 
-\subsection{Real time implementation}
+\subsection{Modeling Assumptions}
 \dean{(comment 1 and 9 from reviewer 2:) The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol.
@@
 \begin{equation}
-	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
+	y(\mathbf{r}_n)=\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
 \end{equation} 

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
small edit the correlation analysis
added to correlation analysis derivation

@@
 
- \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
+\newcommand{\parham}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
 	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu})  \right) \right\} \right] \\
@@
 	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r}) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right] \\
-	&= (R_{y_t,y_t} - \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2) \ast \mathbf{E}\left[\left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right]
-\end{align}
+	&= \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \label{eq:xcorr_with_autocorr}
+\end{align}
+where $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations and $\delta(\cdot)$ is the Kronecker delta function.
+
+To show how we get this result, we define the auto-correlation of the observations as
+\begin{align}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}\right)\right]\\
+	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}) \ast v(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \right\}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \right\}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[m(\mathbf{r}+\boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
+\end{align}
+
+Now to isolate the kernel, the Fourier transform is taken
+\begin{align}
+	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right\} \\
+	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{ \xi  + T_s \varsigma w(\mathbf{r}) \right\}.
+\end{align}
+Now rearranging
+\begin{equation}
+	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \xi  + T_s \varsigma w(\mathbf{r}) \right\}.
+\end{equation}
+Take inverse Fourier transform and rearrange to get an approximation of the kernel
+\begin{align}
+	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} &\approx \xi  + T_s \varsigma w(\mathbf{r}) % \\
+	 % 	(\varsigma T_s)^{-1} \mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}} {\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} - (\varsigma T_s)^{-1}\xi &\approx w(\mathbf{r})
+\end{align}
+This equation states that the support of the kernel can be estimated given knowledge of $\sigma_\varepsilon^2$.
+Furthermore, is we assume a local coupling (at $\boldsymbol\tau=0$) regime, either excitation or inhibition, than we don't even need to know $\sigma_\varepsilon^2$.
+The peak in the kernel at $\mathbf{r}=0$ will be bigger or smaller if we guess incorrectly and the kernel parameters can do the rest!
 % 
@@
 % \end{align}
-
-Alternative, we can write
-\begin{align}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}_n\right)\right]\\
-	&= \mathbf{E}\left[m(\mathbf{r}_n+\boldsymbol{\tau})\ast v(\mathbf{r}) \times m(\mathbf{r}_n)\ast v(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[m(\mathbf{r}_n+\boldsymbol{\tau}) \ast m(\mathbf{r}_n) \ast v^2(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
-\end{align}
-To show how we get this result, we first define
-\begin{align}
-	K(\boldsymbol{\nu}) &= \mathcal{F}\left\{m(\mathbf{r}_n+\boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}_n) \ast v(\mathbf{r})\right\} \\
-	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \\
-	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \\
-	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}).
-\end{align}
-Now taking the inverse Fourier transform we get
-\begin{align}
-	k(\mathbf{r}) = m(\mathbf{r}_n+\boldsymbol{\tau}) \ast m(\mathbf{r}_n) \ast v^2(\mathbf{r}).
-\end{align}
 
@@
 \end{equation} 
+where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The observations in matrix form is described by
 \parham{\begin{equation}
@@
 \end{equation}}
-where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of \parham{$\mathbf y$~}$y(\mathbf{r}_n)$ is
+The Fourier transform of $\mathbf{y}$ is
 \begin{align}

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
greenie bastard bit

@@
 \end{equation} 
-where $\delta(t)$ is the Dirac-delta function. To understand this property, one can take the Laplace transform of $\textrm{D}$ and $h(t)$, giving
-\begin{align}
-	\mathcal{L}\{h(t)\} &= \frac{1}{s+\zeta} \\
-	\mathcal{L}\{\textrm{D}\} &= s+\zeta,
-\end{align}
-and then taking the inverse Laplace transform of $\mathcal{L}\{\textrm{D}\}$ applied to $\mathcal{L}\{h(t)\}$, giving
-\begin{align}
-	\mathcal{L}^{-1}\left\{\frac{s+\zeta}{s+\zeta}\right\} &= \mathcal{L}^{-1}\left\{1\right\} \\
-	&= \delta \left( t \right).
-\end{align}
-Applying the differential operator $\textrm{D}$ to equation~\ref{FullDoubleIntModel} gives
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ to equation~\ref{FullDoubleIntModel} gives
 \begin{align}
@@
 \parham{\begin{equation}
-	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
+	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}).
 \end{equation}}
@@
 \begin{align}
- Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{\mathbf{n}_n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
-	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu) + \frac{1}{\Delta_y^2} \sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{\mathbf{n}_n}{\Delta_y}\right),
-\end{align} 
-where $\mathbf{n}$ is a $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{n}$).
+ Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{\mathbf{k}_n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
+	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu) + \frac{1}{\Delta_y^2} \sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{\mathbf{k}_n}{\Delta_y}\right),
+\end{align} 
+where $\mathbf{k}$ is a $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}$).
 It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$.

### 2011-01-03 src/Matlab/Set_Parameters.m

@@ -22,7 +22,7 @@ EstimationSpaceMin = -10;
 % temporal parameters
 % ~~~~~~~~~~~~~
 Ts = 1e-3;          % sampling period (s)
-T = 1000;            % maximum time (ms)
+T = 200;            % maximum time (ms)
 
 % kernel parameters
 % ~~~~~~~~~~~
@@ -118,7 +118,7 @@ Create_m
 
 % observation noise characteristics
 % ~~~~~~~~~~~~~~~~~~~~
-sigma_varepsilon = 0.1;                                  
+sigma_varepsilon = 0.0; %0.1                                  
 Sigma_varepsilon = sigma_varepsilon*eye(NSensors);        % observation covariance matrix
 
 % sigmoid parameters

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
edits to correlation analysis
edits to paper - modeling assumptions

@@
 	\emph{Indeed, there will always be a mismatch between a mathematical model and the natural phenomena it is attempting to describe.
-The model proposed in our paper is modest in terms of the temporal dynamics, where the state transition is assumed to be first-order.
+The model used to develop our estimator is modest in terms of the temporal dynamics, where the state transition is assumed to be first-order.
 However, the development of the framework for this modest brain model is a significant development that can be expanded to include longer range time dependencies.
@@
 Please note, we have assumed that factors influencing excitability are stationary over the estimation period.
-This is a reasonable assumption is applying the framework to an evoked-potential experiment.
+This is a reasonable assumption if applying the framework to an evoked-potential experiment.
 An extension to our framework, that is currently in development, is to allow for time-varying parameter estimates.

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to paper - modeling assumptions

@@
 	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r}) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right] \\
-	&= \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \label{eq:xcorr_with_autocorr}
-\end{align}
-where $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations and $\delta(\cdot)$ is the Kronecker delta function.
+	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r}) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \right] \\
+	&= \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \label{eq:xcorr_with_autocorr}
+\end{align}
+where $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.
 
@@
 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}\right)\right]\\
-	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}) \ast v(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \right\}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \right\}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[m(\mathbf{r}+\boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r})\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
+	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}) \ast v(\mathbf{r})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \right\}\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \right\}\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
+	&= \mathbf{E}\left[m(\mathbf{r}+\boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2
 \end{align}
@@
 \begin{align}
-	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \left(\xi  + T_s \varsigma w(\mathbf{r})\right) \right\} \\
-	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{ \xi  + T_s \varsigma w(\mathbf{r}) \right\}.
-\end{align}
-Now rearranging
-\begin{equation}
-	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \xi  + T_s \varsigma w(\mathbf{r}) \right\}.
+	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \right\} \\
+	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}) \right\}.
+\end{align}
+Now rearranging (Note: this step is wrong. The RHS should be a function of $\boldsymbol\tau$!)
+\begin{equation}
+	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}) \right\}.
 \end{equation}
@@
 \begin{align}
-	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} &\approx \xi  + T_s \varsigma w(\mathbf{r}) % \\
+	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} &\approx \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}) % \\
 	 % 	(\varsigma T_s)^{-1} \mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}} {\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} - (\varsigma T_s)^{-1}\xi &\approx w(\mathbf{r})
@@
 where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
-\dean{(reviewer 1, additional comment 3:) A derivation of the sampling theorem is provided in \ref{App:SamplingTheorem} that is based on the work of \citet{Sanner1992} and \citet{Scerri2009}}.
-This condition must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
+\dean{(reviewer 1, additional comment 3:) A derivation of the sampling theorem that is based on the work of \citet{Sanner1992} and \citet{Scerri2009} is provided in \ref{App:SamplingTheorem}}.
+The condition in equation~\ref{eq:MinimumSensorDistance} must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
 
@@
 \subsection{Modeling Assumptions}
-\dean{(comment 1 and 9 from reviewer 2:) The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol.
+\dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of cortical dynamics.
+Although models of this form are capable of describing a variety of cortical dynamics, there is without doubt, a mismatch between the cortex and the model.
+Nevertheless, there is a major benefit in using a mean field model over a more detailed model is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
+Analytic solutions...
+A goal of the framework is to create a method to assimilate ...}
+
+\dean{The framework assumes that the model parameters are stationary over the estimation period.
+This is a reasonable assumption if applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
+However, it is well known that factors that influence excitability are non-stationary over longer time periods.
+Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
+A possible way to achieve this is to use a more sophisticated model..
+Alternatively, a simpler method would be to allow for time-varying parameter estimates...
+}
+
+\dean{The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol.
 Over the time duration of an experimental paradigm the connectivity and synaptic kernel parameters are assumed to be stationary.

### 2011-01-03 src/Matlab/Set_Parameters.m

@@ -22,7 +22,7 @@ EstimationSpaceMin = -10;
 % temporal parameters
 % ~~~~~~~~~~~~~
 Ts = 1e-3;          % sampling period (s)
-T = 200;            % maximum time (ms)
+T = 1000;            % maximum time (ms)
 
 % kernel parameters
 % ~~~~~~~~~~~

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
more edits to modeling assumptions

@@
 \subsection{Modeling Assumptions}
-\dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of cortical dynamics.
+\dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of the cortical dynamics recorded from the subject.
 Although models of this form are capable of describing a variety of cortical dynamics, there is without doubt, a mismatch between the cortex and the model.
-Nevertheless, there is a major benefit in using a mean field model over a more detailed model is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
-Analytic solutions...
-A goal of the framework is to create a method to assimilate ...}
-
-\dean{The framework assumes that the model parameters are stationary over the estimation period.
+Nevertheless, there is a sufficient volume of interesting results from theoretical studies that warrants the data assimilation framework.
+}
+
+\dean{An advantage in using a mean field model over a more detailed mathematical description is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
+In this way a minimal number of assumptions are made.
+A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from neuroscience and engineering perspectives) .}
+
+\dean{The framework assumes that the parameters of the model (and brain) are stationary over the estimation period.
 This is a reasonable assumption if applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
-However, it is well known that factors that influence excitability are non-stationary over longer time periods.
+However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010} for a nice example).
 Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
-A possible way to achieve this is to use a more sophisticated model..
-Alternatively, a simpler method would be to allow for time-varying parameter estimates...
+A possible way to achieve this is to use a more sophisticated model that accounts for longer term time dependancies (higher temporal order).
+Alternatively, the parameters of the model could be considered time-varying, where changes in excitability might result in different connectivity kernel parameters.
+A possible way to achieve this would be to employ window-based estimation, where the estimation is performed on successive windows of data (possibly overlapping windows).
+The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.
+A real-time implementation can also be achieved using the UKF (without the smoother) and a real-time LS estimator (see REF for example).
 }
-
-\dean{The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol.
-Over the time duration of an experimental paradigm the connectivity and synaptic kernel parameters are assumed to be stationary.
-However, if the method is applied to a continuous recording over a longer time duration it is unlikely that the parameters will be stationary.
-If fact, it is likely that changes in the parameter values would be of most interest.}
-
-\dean{To implement the algorithm in a real-time scenario the we would assume that the parameters are stationary over a time period (window) where the estimation is performed.
-The parameter of the previous window can be used to initialize parameters of the next window.}
 

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
added to section about the palatable stochasticization of the field equations

@@
 
+\emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
+The paper he is talk about is also a nightmare to read.}
+
+\emph{We added the disturbance term to the firing rate function $g(\mathbf{r},t)$ (equation 3).
+Although we added this after we provided the model derivation and discritization, we can show holds is we add the disturbance to equation 3 and use Ito's method to form the IDE and the Euler-Maruyama method for the discretization.
+We chose the simplest method to present the model due to space considerations and the expected audience.
+}
+
+\emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences.
+Since we a talking about a large number of neurons, we expect this disturbance to be Gaussian (according to the central limit theorem).
+Furthermore, we expect the disturbance to be spatially correlated according to the covariance function $\sigma_d\gamma(\mathbf{r}-\mathbf{r}')$, since we consider the small areas of the field to be functional processing units.}
+
 \item This is NeuroImage, not the Physical Review.
@@
 
-\emph{Gaussians has semi-compact support but Fourier basis functions are global functions.
+\emph{Gaussians have semi-compact support but Fourier basis functions are global functions.
 Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
added to section about the palatable stochasticization of the field equations

@@
 In this way a minimal number of assumptions are made.
-A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from neuroscience and engineering perspectives) .}
+A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
 

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
editted response to stochastification

--- 2011-01-01 ltx/first_order_framework/response_to_reviews.tex
@@
 
-	\emph{Indeed, there will always be a mismatch between a mathematical model and the natural phenomena it is attempting to describe.
-The model proposed in our paper is modest in terms of the temporal dynamics, where the state transition is assumed to be first-order.
-However, the development of the framework for this modest brain model is a significant development that can be expanded to include longer range time dependencies.
-A major benefit in using a mean field model is the freedom to lump detailed parameters, such as specific ion concentrations, into more general parameters such as the connectivity kernel coefficients that describe the net system gain.
-Please note, we have assumed that factors influencing excitability are stationary over the estimation period.
-This is a reasonable assumption is applying the framework to an evoked-potential experiment.
-An extension to our framework, that is currently in development, is to allow for time-varying parameter estimates.
-This will allow the application of the framework to longer-term data recordings.
-The problem can then be posed in terms of convergence time and estimation accuracy vs.
-nonstationarity of the metabolic processes and other unmodeled brain dynamics.}
+	\emph{To address this point, we have added an extra section to the discussion, 'Modeling Asusumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
 
@@
 I and others will value the authors' thoughts of how a more palatable stochasticization of these field equations might influence the future development of the data-assimilation framework presented in this paper.
+
+\emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
+The paper he is talk about is also a nightmare to read.}
+
+\emph{We added the disturbance term to the firing rate function  (equation 12).
+Although we added this after we provided the model derivation and discritization, we can show this holds if we assume the disturbance is a Wiener process, add it to the firing rate $g(\mathbf{r},t)$ (equation 3), use Ito's method to form the IDE, and the Euler-Maruyama method for the discretization.
+The disturbance will then be an incremental Wiener process.
+We chose the simplest method to present the model so the paper did not get too heavy in the maths (at least in the intro) and due to space considerations.
+}
+
+\emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences.
+Since we a talking about a large number of neurons, we expect this disturbance to be Gaussian (according to the central limit theorem).
+Furthermore, we expect the disturbance to be spatially colored according to the covariance function $\sigma_d\gamma(\mathbf{r}-\mathbf{r}')$, since we consider small neighboring regions within the field to be functional processing units.}
 

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
changed fig1 caption

@@
 {\bf Figure 1.
-Mexican-hat connectivity kernel.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+Mexican-hat connectivity kernel.} \parham{(comment 8, reviewer 2) The kernel is a composite of three Gaussian basis functions (dashed lines), representing short-range excitation, mid-range inhibition and long-range excitation.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
reviewer2 comment7 about the fudge factors

--- 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \end{equation}
-where the constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$, and $\kappa$ is an additional scaling parameter (see~\citet{Haykin2001} for more details).
+\parham{(reviewer 2, comment 7:) The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which is set arbitrary small (e.g., $10^{-3}$) to minimise higher order effect \citep{Haykin2001} , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$ \citep{Julier2002a}.}
 
@@
 {\bf Figure 1.
-Mexican-hat connectivity kernel.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+Mexican-hat connectivity kernel.} \parham{(reviewer 2, comment 8:) The kernel is a composite of three Gaussian basis functions (dashed lines), representing short-range excitation, mid-range inhibition and long-range excitation.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
added fig1 connectivity kernel and its component
minor comments

@@
 
-\emph{The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which can be made arbitrary small (e.g.
-$0<\alpha\le 10^{-4} $) to minimise higher order effect (Julier et al., 2002, and Haykin, 2001) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$ (Julier et al., 1995).}
+\emph{Values for the two parameters in equation 41 along with the relevant references have been added to the manuscript.}
 
@@
 
-\emph{I think we need to show each kernel basis function in Figure 1}
+\emph{This point is clarified by adding the connectivity kernel componets superimposed by the resulting Mexican Hat basis in Figure 1. of the manuscript.}
 
@@
  \begin{center}
- \includegraphics{./Graph/pdf/fig1_revised.pdf} 
+ \includegraphics{./Graph/pdf/fig1.pdf} 
  \end{center}
@@
 A few words of perspective would be invaluable to help others translate the author's wisdom on this method to other applications.
-\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?
+\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?\\
+
+\emph{Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to ?????}
+
 \item Page 45, Appendix D, Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
minor comments

@@
 Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz.
+The cutoff frequency ($-3$~dB point) of the neural field is \parham{$\boldsymbol{\nu}_c \approx 0.24$~Hz}.
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm.
@@
 The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A).
-The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point).
+The cutoff frequency is \parham{$\boldsymbol{\nu}_{cy} \approx 0.2$~Hz} ($-3$~dB point).
 The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors.
@@
 As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure.
-In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
+In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to \parham{$\boldsymbol{\nu}_{c\phi} = 0.12$~Hz}.
 The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
@@
 	\hline
-	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & Hz \\
-	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & \parham{Hz} \\
+	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{Hz}$^2$\\
 	\hline

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
change hz to cycles/mm

--- 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz.
+The cutoff frequency ($-3$~dB point) of the neural field is \parham{$\boldsymbol{\nu}_c \approx 0.24$~cycles/mm}.
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm.
@@
 The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A).
-The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point).
+The cutoff frequency is \parham{$\boldsymbol{\nu}_{cy} \approx 0.2$~cycles/mm} ($-3$~dB point).
 The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors.
@@
 As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure.
-In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz.
+In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to \parham{$\boldsymbol{\nu}_{c\phi} = 0.12$~cycles/mm}.
 The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
@@
 	\hline
-	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & Hz \\
-	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & \parham{cycles/mm} \\
+	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{cycles/mm$^2$}\\
 	\hline

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
change hz to cycles/mm
added reference for nu_c

@@
 
+\emph{The spatial frequency content is seems to be actually lower than one might first think.
+We have added 'From the work of (Freeman et al, 2000), the expected bandwidth of the human neocortex is approximately 0.4 cycles/mm which requires a maximal sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing' to the Frequency Analysis section of the paper to clear this up.
+Note, we expect the spatial bandwidth of the cortex to be governed by the connectivity kernel, since it is equivalent to a spatial low-pass filter acting on the firing rates.
+}
+
 \item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\
 
-\emph{Values for the two parameters in equation 41 along with the relevant references have been added to the manuscript.}
+\emph{Values for the two parameters in equation 41 along with the relevant references ,that describe the rationale for parameter choice, have been added to the manuscript.}
 
@@
 
-\emph{Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to ?????}
+\emph{Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to cycles/mm.}
 

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction in table1
added reference for nu_c

@@
 \newcommand{\dean}[1]{\textcolor{red}{#1}}
-
 \newcommand{\parham}[1]{\textcolor{blue}{#1}}
@@
 However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}).
+\dean{Reviewer 2, comment 6: From the work of~\citet{Freeman2000}, the expected bandwidth of the human neocortex is approximately 0.4 cycles/mm which requires a maximal sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing.}
+
 Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
@@
 \end{align}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for Gaussian disturbance $\beta$ should be set to 2)}.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & \parham{cycles/mm} \\
-	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{cycles/mm$^2$}\\
+	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{(cycles/mm)$^2$}\\
 	\hline

### 2011-01-04 ltx/first_order_framework/response_to_reviews.tex
edited a bit the response to the 'need data' response

--- 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
@@
 	\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data.
-However, before validating the method on real data we believe that it is important to first validate the method on artificial data, where the true and estimated parameters can be compared.
-Given the space limitations on the article, it is not feasible to show examples using real data in this paper.
+However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
+In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.
 Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.
-In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.}
+WE SHOULD ADD SOMETHING IN THE CONCLUSION TO SAY WE TOTALLY NEED TO VALIDATE THIS ON REAL DATA AND IT'S NOTED AS FUTURE WORK}
 
@@
 	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
-Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion (Implications for Experimental Design).
+Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion.
 We have primarily developed the framework for higher density intracranial measurements.
@@
 
+	\emph{..., and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
+considered.
+This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored.
+In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
     \end{enumerate}
@@
 
-\emph{To address this point, we have added an extra appendix with a derivation of the sampling theorem with the appropriate cross-referencing to the main text.
-An effort was made to keep this derivation minimal and as clear as possible.
-We have also added the references to relevant part of the text (that should have been there before, as the reviewer has correctly pointed out).
-We felt that it was worth adding the extra appendix to provide a clear derivation that is contextually and notationally relevant to this paper, as the derivations cited papers may not be clear to the Neuroimage general audience.}
+\emph{This appendix provides a derivation for equations ??
+and ??.
+The derivation is adapted from (Sanner et al., 1992, and Scerri et al., 2009).
+Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$.
+The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
+\begin{equation}
+	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
+\end{equation} 
+where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
+\begin{align}
+ Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
+	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
+\end{align} 
+It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice centered at $n\Delta_y^{-1}$.
+Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$.
+In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
+\begin{equation}
+	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
+\end{equation}
+Therefore, to avoid aliasing the distance between observations must satisfy
+\begin{equation}\label{eq:SamplingCriteria}
+	\frac{1}{\Delta_y} \ge 2\nu_{cy}.
+\end{equation}
+Since the observation kernel is not an ideal filter an oversampling parameter should be included to further separate the aliases.
+Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
+\begin{equation}\label{ap:Shannon}
+	\Delta_y\le\frac{1}{2\rho\nu_{cy}},
+\end{equation}
+where $\rho \in \mathbb{R} \ge 1$. }
 
         \item The existing literature on inversion schemes for similar models of brain activity.
-
         \item In section 3, Table 6 is mentioned however there is no such table in the ms.
@@
 
-	\emph{To address this point, we have added an extra section to the discussion, 'Modeling Asusumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
+    \emph{talk about model order}
+
+	\emph{Indeed, there will always be a mismatch between a mathematical model and the natural phenomena it is attempting to describe.
+The model proposed in our paper is modest in terms of the temporal dynamics, where the state transition is assumed to be first-order.
+However, the development of the framework for this modest brain model is a significant development that can be expanded to include longer range time dependencies.
+A major benefit in using a mean field model is the freedom to lump detailed parameters, such as specific ion concentrations, into more general parameters such as the connectivity kernel coefficients that describe the net system gain.
+Please note, we have assumed that factors influencing excitability are stationary over the estimation period.
+This is a reasonable assumption is applying the framework to an evoked potential experiment.
+An extension to our framework, that is currently in development, is to allow for time-varying parameter estimates.
+This will allow the application of the framework to longer-term data recordings.
+The problem then can be posed in terms of convergence time and estimation accuracy vs.
+nonstationarity of the metabolic processes and other unmodeled brain dynamics.}
 
@@
 
-\emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
-The paper he is talk about is also a nightmare to read.}
+\item This is NeuroImage, not the Physical Review.
+Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.\\
 
-\emph{We added the disturbance term to the firing rate function  (equation 12).
-Although we added this after we provided the model derivation and discritization, we can show this holds if we assume the disturbance is a Wiener process, add it to the firing rate $g(\mathbf{r},t)$ (equation 3), use Ito's method to form the IDE, and the Euler-Maruyama method for the discretization.
-The disturbance will then be an incremental Wiener process.
-We chose the simplest method to present the model so the paper did not get too heavy in the maths (at least in the intro) and due to space considerations.
-}
-
-\emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences.
-Since we a talking about a large number of neurons, we expect this disturbance to be Gaussian (according to the central limit theorem).
-Furthermore, we expect the disturbance to be spatially colored according to the covariance function $\sigma_d\gamma(\mathbf{r}-\mathbf{r}')$, since we consider small neighboring regions within the field to be functional processing units.}
-
-\item This is NeuroImage, not the Physical Review.
-Although most of this framework involves mathematics that is reasonable to follow for typical readers of this journal, I would suggest that the authors explain and expand a bit on the introduction of Green's functions where introduced in equation 6.
-
-\emph{A more detailed explanation has been added to the manuscript.}
+\emph{The synaptic response kernel can be viewed as the Green function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$ i.e., satisfying
+\begin{equation}
+	\label{GreensFuncDef} \textrm{D}h\left( t \right) = \delta \left( t \right), 
+\end{equation} 
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ on equation (5) we have
+\begin{align}
+ \textrm{D}v\left(\mathbf r,t\right)&= \textrm{D}\left(h\ast g\right)\left(\mathbf r,t\right)\\
+&=\left(\textrm{D}h\ast g\right)\left(\mathbf r,t\right)\\
+&=\left(\delta \left(t\right)\ast g\right)\left(\mathbf r,t\right)\\
+&=g\left(\mathbf r,t\right)
+\end{align}
+where $\ast$ denotes convolution operator. This gives the standard form of the model
+\begin{equation}
+	\label{FinalFormContinuous} 
+	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
+\end{equation}}
 
@@
 This seems important to clarify for the rest of us.
-
 \item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\
 
-\emph{Gaussians have semi-compact support but Fourier basis functions are global functions.
+\emph{Gaussians has semi-compact support but Fourier basis functions are global functions.
 Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}
@@
 E 73, 051911 (2006)).
-
-\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\
-
+\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
 \emph{The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which can be made arbitrary small (e.g.
-$0<\alpha\le 10^{-4} $) to minimise higher order effect (Julier et al., 2002, and Haykin, 2001) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$ (Julier et al., 1995).}
+$0<\alpha\le 10^{-4} $) to minimise higher order effect (cite Julier (The Scaled Unscented Transformation) and  Haykin (Kalman filtering and neural network) , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$.
+cite Julier A New Approach for Filtering Nonlinear Systems}
 
@@
 I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.\\
-
 \emph{I think we need to show each kernel basis function in Figure 1}
-
  \begin{figure*}[!ht]

### 2011-01-04 ltx/first_order_framework/response_to_reviews.tex
fixed table crossreferencing reviewrone comment 5
small edits

--- 2011-01-03 ltx/first_order_framework/response_to_reviews.tex
@@
 
+	\emph{Valdes uses a Lopes Da Silva / Freeman neural mass model. }
+
         \item In section 3, Table 6 is mentioned however there is no such table in the ms.
@@
 \emph{The spatial frequency content is seems to be actually lower than one might first think.
-We have added 'From the work of (Freeman et al, 2000), the expected bandwidth of the human neocortex is approximately 0.4 cycles/mm which requires a maximal sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing' to the Frequency Analysis section of the paper to clear this up.
+We have added `From the work of (Freeman et al, 2000), the expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm which requires a sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing' to the Frequency Analysis section of the paper to clear this up.
+We have also added to the discussion.
 Note, we expect the spatial bandwidth of the cortex to be governed by the connectivity kernel, since it is equivalent to a spatial low-pass filter acting on the firing rates.
@@
 
-\emph{This point is clarified by adding the connectivity kernel componets superimposed by the resulting Mexican Hat basis in Figure 1. of the manuscript.}
+\emph{This point is clarified by adding the connectivity kernel components superimposed by the resulting Mexican Hat basis in Figure 1. of the manuscript.}
 
@@
 A few words of perspective would be invaluable to help others translate the author's wisdom on this method to other applications.
-\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?\\
+
+\emph{A few comments have been added to the Modeling Assumptions section of the discussion.}
+
+\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?
 

### 2011-01-04 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed table referencing reviewrone comment 5
small edits

--- 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}).
+\dean{(Reviewer 2, comment 6:) From the work of~\citet{Freeman2000}, the expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm.}
+
 Spectral aliasing can be avoided by a proper choice of the spatial sampling distance given the sensors' spectral characteristics.
@@
 \end{equation}
-\parham{(reviewer 2, comment 7:) The positive constant $\alpha$ determines the spread of the sigma points around $\mathbf{\bar x}$ which is set arbitrary small (e.g., $10^{-3}$) to minimise higher order effect \citep{Haykin2001} , and  $\kappa$ is an additional scaling parameter which is usually set to $3-n_x$ \citep{Julier2002a}.}
+\parham{(reviewer 2, comment 7:) The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, is typically set arbitrary small (e.g., $10^{-3}$) to minimise higher order effect \citep{Haykin2001}, and  $\kappa$ is an additional scaling parameter which was set to $3-n_x$ in accordance to \citet{Julier2002a}.}
 
@@
 \end{align}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance $\beta$ should be set to 2)}.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 
+\dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the electrode spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
+Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to humans with existing technology.}
+
 \subsection{Computational Complexity}

### 2011-01-04 ltx/first_order_framework/response_to_reviews.tex

--- 2011-01-04 ltx/first_order_framework/response_to_reviews.tex
@@
 
-        \item In section 3, Table 6 is mentioned however there is no such table in the ms.
+        \item In section 3, Table 6 is mentioned however there is no such table in the ms.\\
+\emph{The cross-referencing has been corrected.}
     \end{enumerate}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed error in  xcorr analysis
fix some errors in the xcorr derivation

@@
 \begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}\right)\right] \\
-	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}_n\right)\right) \right], \label{eq:ObsXCorr}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \\
+	&= \mathbf{E}\left[\left(m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) + \boldsymbol{\varepsilon}_t\left(\mathbf{r}\right) \right) \times \left( m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right], \label{eq:ObsXCorr}
 \end{align}
@@
 \begin{equation}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right].
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right].
 \end{equation}
@@
 \begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{m\left(\mathbf{r}-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} + e_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'} \right] \\
-	 &= \xi\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) d\mathbf{r}'} \right] \nonumber \\
-	&+ T_s\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega} {m\left(\mathbf{r} - \mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'} \right] \nonumber \\
-	&+ \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega} { m\left(\mathbf{r} - \mathbf{r}'\right) e_t \left(\mathbf{r}'\right)\, d\mathbf{r}' } \right]
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left( \xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) + e_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \\
+	 &= \xi \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \nonumber \\
+	&+ T_s\mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \nonumber \\
+	&+ \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast e_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]
 	\\
@@
 since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$. Putting to other two terms back together we can write
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{m\left(\mathbf{r}-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} \right)\, d\mathbf{r}'} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}}M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) F(\boldsymbol{\nu}) \right) \right\} \right]
-\end{align}
-where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform. Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right) \right]
+\end{equation}
+Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
 \begin{equation}
@@
 \end{equation}
-Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. From this we get the simplified cross-correlation function
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu})  \right) \right\} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r}) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \right] \\
-	&= \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \label{eq:xcorr_with_autocorr}
-\end{align}
-where $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.
-
-To show how we get this result, we define the auto-correlation of the observations as
-\begin{align}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}\right)\right]\\
-	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}) \ast v(\mathbf{r})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \right\}\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \right\}\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-	&= \mathbf{E}\left[m(\mathbf{r}+\boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2
-\end{align}
-
-Now to isolate the kernel, the Fourier transform is taken
-\begin{align}
-	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \right\} \\
-	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}) \right\}.
-\end{align}
-Now rearranging (Note: this step is wrong. The RHS should be a function of $\boldsymbol\tau$!)
-\begin{equation}
-	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}) \right\}.
+Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. 
+\begin{equation}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \varsigma v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right) \right]
+\end{equation}
+Now we take the Fourier transform of the terms inside the expectation giving
+\begin{align}
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) + T_s e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \left(\xi + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \ast \left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \\
+	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \right] \ast \mathbf{E}\left[\left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \label{eq:xcorr_pre_sub}
+\end{align}
+where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform and $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.
+
+We define the auto-correlation of the observations as
+\begin{align}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]\\
+	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2
+\end{align}
+Rearrange to get
+\begin{equation}\label{eq:autocorr_for_sub}
+	R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 = \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right].
+\end{equation}
+Now to isolate the kernel equation~\ref{eq:autocorr_for_sub} is substituted into equation~\ref{eq:xcorr_pre_sub} and the Fourier transform is taken giving
+\begin{align}
+	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \mathbf{E} \left[ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right] \right\} \\
+	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right) \sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{\mathbf{E}[ \xi \delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.
+\end{align}
+Now rearranging
+\begin{equation}
+	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \mathbf{E}[ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.
 \end{equation}
 Take inverse Fourier transform and rearrange to get an approximation of the kernel
-\begin{align}
-	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} &\approx \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}) % \\
-	 % 	(\varsigma T_s)^{-1} \mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}} {\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} - (\varsigma T_s)^{-1}\xi &\approx w(\mathbf{r})
-\end{align}
+\begin{equation}
+	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} \approx \mathbf{E}[\xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau})].
+\end{equation}
 This equation states that the support of the kernel can be estimated given knowledge of $\sigma_\varepsilon^2$.
@@
 	& $\xi$ & 0.9 & $0.925$ & $0.003$ & $2.78$ \\ \hline
-\end{tabular}\label{tab:MexicanHatKernelResults}
+\end{tabular}
 \caption{\textbf{Results from varying the Mexican hat connectivity kernel parameters}}
+\label{tab:MexicanHatKernelResults}
 \end{table*}
@@
 	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
-\end{tabular}\label{tab:GaussianKernelResults}
+\end{tabular}
 \caption{\textbf{Results from varying the Gaussian connectivity kernel parameter}}
+\label{tab:GaussianKernelResults}
 \end{table*}

### 2011-01-05 ltx/first_order_framework/response_to_reviews.tex
add background on estimation schemes suggested by reviewer 1

@@
 
+		\emph{We should add some more to the modeling assumptions section to address this one. I have begun to talk about the LL method.}
+
         \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.
@@
 
-        \item In section 3, Table 6 is mentioned however there is no such table in the ms.\\
+\emph{The existing literature has been discussed in more depth in the introduction.}
+
+        \item In section 3, Table 6 is mentioned however there is no such table in the ms.
+
 \emph{The cross-referencing has been corrected.}
+
     \end{enumerate}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
editted cor derivation
add background on estimation schemes suggested by reviewer 1

@@
 Fitting the neural models to individuals is a highly non-trivial task.
-Recently, however, this task has been approached from a number of standpoints \citep{Nunez2000,Jirsa2002,Robinson2004,Daunizeau2009}.
+Recently, however, this task has been approached from a number of standpoints.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} using an extended Kalman filter.
+This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}
 
 Perhaps the most accepted estimation framework for neural mass models is dynamical causal modeling (DCM) \citep{David2003,David2006}, which has been proposed for studying evoked potential dynamics.
+This framework can be viewed as an extension to the work of~\citet{Valdes1999} allowing for coupling of neural masses.
 Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the model of \citet{Jansen1995}.
-Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations \citep{schiff2008kalman}.
+
+\dean{(Reviewer 1, additional comment d):) Data-driven neural modeling was extended to the continuum approximation by \citet{Galka2008}, where they proposed an estimation framework based on a linear damped wave equation.
+Using a Kalman filter maximum likelihood framework, they improved on the low resolution electromagnetic tomography (LORETA) method for solving the inverse EEG problem.
+Another continuum neural field model-based estimator was developed by \citet{Daunizeau2009}, as an extension to the DCM framework.
+They argued that this approach is superior for data assimilation than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.}
+
+\dean{Another recent approach estimates the parameters of a modified WC neural field model using an unscented Kalman filter~\citep{schiff2008kalman}.
 This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
 This marks the first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
+For other valuable contributions to data-driven neural modeling see \citet{Nunez2000,Jirsa2002,Robinson2004}.}
 
@@
 \begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) + T_s e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \left(\xi + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
+	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) + T_s e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
+	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \left(\xi + T_s \varsigma e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
 	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \ast \left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \\
@@
 
-\dean{An advantage in using a mean field model over a more detailed mathematical description is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
+\dean{An advantage in using a lumped-parameter field model over a more detailed mathematical description is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
 In this way a minimal number of assumptions are made.
@@
 The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.
+If this trade-off can not be successfully achieved then the level of detail in the model must be increased.
 A real-time implementation can also be achieved using the UKF (without the smoother) and a real-time LS estimator (see REF for example).
 }
+
+\dean{We have assumed that the model can be discretized by the first order Euler method.
+This discretization may change the properties of the stochastic nonlinear system.
+An alternative is to use the LL method....}
 

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
added reference for recursive least square and change the reference for least square

@@
 \end{align}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance $\beta$ should be set to 2)}.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance $\beta$ should be set to 2 \parham{\citep{Haykin2001}})}.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 \end{small}
-Following this, the LS parameter estimates \citep{Ljung1985}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates \parham{\citep{Ljung1999}}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 If this trade-off can not be successfully achieved then the level of detail in the model must be increased.
-A real-time implementation can also be achieved using the UKF (without the smoother) and a real-time LS estimator (see REF for example).
+A real-time implementation can also be achieved using the UKF (without the smoother\parham{???}) \parham{and an online recursive LS estimator (see \citet{Ljung1999} for example)}.
 }

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
added a comment on Lopez Da Silva and Zetterberg citation

@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} using an extended Kalman filter.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think)}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
added a comment on Lopez Da Silva and Zetterberg citation

--- 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} using an extended Kalman filter.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think-maybe just say using nonlinear Kalman filtering algorithm)}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
added a comment on Lopez Da Silva and Zetterberg citation

--- 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} using an extended Kalman filter.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think-maybe just say using nonlinear Kalman filtering algorithm or maybe using Local Linearisation filter (Ozaki,1994))}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
added reference for local linearisation filter

--- 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think)}.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think-maybe just say using nonlinear Kalman filtering algorithm or maybe using Local Linearisation filter \citep{Ozaki1994}}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
very minor edit

--- 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think-maybe just say using nonlinear Kalman filtering algorithm)}.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} using an extended Kalman filter.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}
@@
 \subsection{Estimation of Connectivity Kernel Support}
-The support of the connectivity kernel can be inferred using spatial correlation analysis.
+\dean{The support of the connectivity kernel can be inferred using spatial correlation analysis.
 The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}.
@@
 where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform and $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.
-
 We define the auto-correlation of the observations as
@@
 The peak in the kernel at $\mathbf{r}=0$ will be bigger or smaller if we guess incorrectly and the kernel parameters can do the rest!
+}
 % 
@@
 \end{align}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance $\beta$ should be set to 2 \parham{\citep{Haykin2001}})}.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance $\beta$ should be set to 2)}.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 \end{small}
-Following this, the LS parameter estimates \parham{\citep{Ljung1999}}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates \citep{Ljung1985}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 If this trade-off can not be successfully achieved then the level of detail in the model must be increased.
-A real-time implementation can also be achieved using the UKF (without the smoother\parham{???}) \parham{and an online recursive LS estimator (see \citet{Ljung1999} for example)}.
+A real-time implementation can also be achieved using the UKF (without the smoother) and a real-time LS estimator (see REF for example).
 }

### 2011-01-06 ltx/first_order_framework/response_to_reviews.tex
reviewer2 comment 5

@@
 
-\emph{Gaussians have semi-compact support but Fourier basis functions are global functions.
-Gaussian can be easily extended to higher dimension (don't know about the Fourier basis functions), any orthonormal basis functions like Fourier basis functions simplify our equations, $\Gamma$ becomes identity matrix, but using Gaussian basis functions equations are in their generic form.}
+\emph{Fourier basis functions are indeed a correct alternative in the case examined in this paper.
+In fact Fourier basis functions or any other orthonormal basis functions simplify the state space representation of the model, since $\Gamma$ defined in equation (20) of the manuscript becomes Identity matrix.
+However, we have chosen Gaussian basis functions due to their semi-compact support.
+By choosing Gauassian basis functions the stat space representation of the model remains in its generic form which is also correct in the case of orthonormal basis functions.}
 

### 2011-01-06 ltx/first_order_framework/response_to_reviews.tex
added relationship to Galerkin project

--- 2011-01-05 ltx/first_order_framework/response_to_reviews.tex
@@
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented.
-Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support.
+Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.
 For more complex basis functions some of the analytic derivations described in the Appendix may have to be performed numerically.
@@
 We have primarily developed the framework for higher density intracranial measurements.
-We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.}
+This is explained in the spatial freq analysis method and discussion.}
 
@@
 
-    We thank the author for their encouraging review. Each point raised is dealt with in turn.
+    We thank the reviewer for their encouraging review. Each point raised is dealt with in turn.
 
@@
 
+\emph{The relationship to our basis function decomposition to Galerkin's projection has been added to the derivation of the state-space model. }
+
 \item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\
@@
 
-\item In equation 29, what would a reasonable $v_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
+\item In equation 29, what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
 I am concerned that it might be much higher than any of us wish to consider.

### 2011-01-06 ltx/first_order_framework/LaTeX_Manuscript.tex
added relationship to Galerkin project

--- 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented.
-Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support.}
+Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.}
 
 Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model.
-Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get
+Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get
+% \begin{align}
+% 	\label{reduced continuous model}
+% 	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+% 	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}). 
+% \end{align}
 \begin{align}
 	\label{reduced continuous model}
-	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	v_{t+1}\left(\mathbf{r}\right) &\approx T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
 	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}). 
@@
 \begin{align}
-	\label{StartofReduction}
- 	\int_\Omega \boldsymbol{\phi} &\left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)d\mathbf{r} \mathbf{x}_{t+1}  \nonumber \\
- &=T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') 
- f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}\boldsymbol{\theta} \nonumber \\ 
-&+ \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t + 
-\int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
-\end{align}
+	\label{eq:decompRHS}
+ 	\int_\Omega \boldsymbol{\phi}&\left(\mathbf{r}\right) v_{t+1}\left(\mathbf{r}\right)d\mathbf{r}  \nonumber \\
+	&\approx T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}\boldsymbol{\theta} \nonumber \\
+	&+ \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r} } \mathbf{x}_t + \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
+\end{align}
+\dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to the Galerkin projection. To show this we define the residual
+\begin{align}
+	\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) &= v_{t+1}(\mathbf{r}) - T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{align} 
+The Galerkin projection finds $\mathbf{x}_t$ such that for all basis functions, the inner product with the residual satisfies
+\begin{equation}\label{eq:GalerkinProjection}
+	G_i = \int_{\Omega}\Xi(x_t,v_t(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,
+\end{equation}
+where $n_x$ is the number of states and basis functions.
+If equation~\ref{eq:GalerkinProjection} is satisfied then the basis functions are orthogonal to the residual.
+If one was using the Galerkin projection to estimate the states, they would numerically solve the $n_x$ equations to estimate the state vector, which is a standard method in economics modeling.
+The method in this paper takes a different approach by forming the state-space model.
+To show how this is achieved we substitute the field decomposition into the right hand side of equation~\ref{eq:decompRHS} giving
+\begin{align}
+	\label{eq:StartofReduction}
+ 	\int_\Omega \boldsymbol{\phi}&\left(\mathbf{r}\right) \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right)\mathbf{x}_{t+1}d\mathbf{r}  \nonumber \\
+	&= T_s \int_\Omega \boldsymbol{\phi} (\mathbf{r}) \int_\Omega \boldsymbol{\psi}^{\top} (\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \, d\mathbf{r}'d\mathbf{r}\boldsymbol{\theta} \nonumber \\
+	&+ \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r} } \mathbf{x}_t + \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r}) \, d\mathbf{r}}. 
+\end{align}
+  }
 Now defining the matrix
@@
 \end{equation}
-and substituting this into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives
+and substituting it into equation~\ref{eq:StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives
 \begin{align}
@@
 \begin{equation}
-	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \mathbf{E}[ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.
+	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \mathbf{E}\left[ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right]\right\}.
 \end{equation}
@@
 Alternatively, the parameters of the model could be considered time-varying, where changes in excitability might result in different connectivity kernel parameters.
-A possible way to achieve this would be to employ window-based estimation, where the estimation is performed on successive windows of data (possibly overlapping windows).
+A possible way to achieve this would be to employ window-based estimation or fixed-lag, where the estimation is performed on successive windows of data (possibly overlapping windows).
 The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.
 If this trade-off can not be successfully achieved then the level of detail in the model must be increased.
-A real-time implementation can also be achieved using the UKF (without the smoother\parham{???}) \parham{and an online recursive LS estimator (see \citet{Ljung1999} for example)}.
+A real-time implementation can also be achieved using the UKF \parham{and an online recursive LS estimator (see \citet{Ljung1999} for example)}.
 }

### 2011-01-06 ltx/first_order_framework/LaTeX_Manuscript.tex
some minor edits to the relationship to galerkin

@@
 Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model.
-Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get
+Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get the approximation of the dynamic field
 % \begin{align}
@@
 \end{align} 
-The Galerkin projection finds $\mathbf{x}_t$ such that for all basis functions, the inner product with the residual satisfies
+The Galerkin projection method finds $\mathbf{x}_t$ such that for all of the basis functions the inner product with the residual satisfies
 \begin{equation}\label{eq:GalerkinProjection}
-	G_i = \int_{\Omega}\Xi(x_t,v_t(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,
+	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,
 \end{equation}
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}.
-Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
+\dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ become the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
 \begin{equation}

### 2011-01-06 ltx/first_order_framework/LaTeX_Manuscript.tex
minor chnages
minor edits

@@
 Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model.
-Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get the approximation of the dynamic field
+Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the right hand side} we get the approximation of the dynamic field
 % \begin{align}
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}.
-\dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ become the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
+\dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
 \begin{equation}

### 2011-01-06 ltx/first_order_framework/LaTeX_Manuscript.tex
edit to paper, Add appendix to describe the galerkin proection

@@
 \end{equation}
-
 \dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
@@
 \end{equation}
-
 To arrive at the integro-difference equation (IDE) form of the model, we discretize time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
@@
 \end{align}
-\dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to the Galerkin projection. To show this we define the residual
-\begin{align}
-	\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) &= v_{t+1}(\mathbf{r}) - T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
-	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
-\end{align} 
-The Galerkin projection method finds $\mathbf{x}_t$ such that for all of the basis functions the inner product with the residual satisfies
-\begin{equation}\label{eq:GalerkinProjection}
-	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,
-\end{equation}
-where $n_x$ is the number of states and basis functions.
-If equation~\ref{eq:GalerkinProjection} is satisfied then the basis functions are orthogonal to the residual.
-If one was using the Galerkin projection to estimate the states, they would numerically solve the $n_x$ equations to estimate the state vector, which is a standard method in economics modeling.
-The method in this paper takes a different approach by forming the state-space model.
-To show how this is achieved we substitute the field decomposition into the right hand side of equation~\ref{eq:decompRHS} giving
+\dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to finding a Galerkin projection, where the field basis functions would be considered the Galerkin projection functions and the states would be the amplitude coefficients.
+If the Galerkin approach was used estimate the states, $n_x$ coupled ODEs would be solved independently to estimate the state vector, which is a standard method in fluid dynamics and economics modeling.
+The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation.
+To show how this is achieved we substitute the field decomposition into the left hand side of equation~\ref{eq:decompRHS} giving
 \begin{align}
@@
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-This enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
+\dean{It should be noted that Schiff and Sauer suggest the possibility of using a Galerkin projection or similar decomposition that is used in this paper to perform efficient estimation as a direction for future work.
+Indeed,} we have show that this enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
 
@@
 
-\bibliographystyle{model2-names} 
+\bibliographystyle{./elsarticle/model2-names} 
 \bibliography{BrainIDE}
@@
 
+\section{Equivalence to Galerkin's Projection}
+To show how to solution of equation for the state vector is equivalent to the Galerkin projection we define the residual between the field and the decomposition as 
+\begin{align}
+	\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) &= v_{t+1}(\mathbf{r}) - T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+\end{align} 
+The Galerkin projection method finds $\mathbf{x}_t$, such that for all of the basis functions, the inner product with the residual satisfies
+\begin{equation}\label{eq:GalerkinProjection}
+	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,
+\end{equation}
+where $n_x$ is the number of states and basis functions.
+If the inner product between the residual and the basis functions in equation~\ref{eq:GalerkinProjection} is zero, then the basis functions are orthogonal to the residual.
+
 \section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
removed the word 'nice' from line 625. I'm worried we're getting a bit too chatty in this document!
edits to discussion

@@
 \dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to finding a Galerkin projection, where the field basis functions would be considered the Galerkin projection functions and the states would be the amplitude coefficients.
-If the Galerkin approach was used estimate the states, $n_x$ coupled ODEs would be solved independently to estimate the state vector, which is a standard method in fluid dynamics and economics modeling.
-The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation.
-To show how this is achieved we substitute the field decomposition into the left hand side of equation~\ref{eq:decompRHS} giving
+In the next step to forming the state-space model we substitute the field decomposition into the left hand side of equation~\ref{eq:decompRHS} giving}
 \begin{align}
@@
 \end{align}
-  }
 Now defining the matrix
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}.
-\dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
+\dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal, such as a Fourier basis, then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
 \begin{equation}
@@
 \end{equation}
-\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate the reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
+\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate the reduced model observation equation from the full model.} The observation equation is linear and can be written in the more compact form
 \begin{equation}\label{ObservationEquation} 
@@
 Alternatively, the parameters of the model could be considered time-varying, where changes in excitability might result in different connectivity kernel parameters.
-A possible way to achieve this would be to employ window-based estimation or fixed-lag, where the estimation is performed on successive windows of data (possibly overlapping windows).
+A possible way to achieve this would be to employ window-based or fixed-lag estimation, where the estimation is performed on successive windows of data (possibly overlapping windows).
 The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.
@@
 In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
-In future work, we plan to relax this assumption.
+In future work, we plan to relax this assumption \dean{and show how the support of the connectivity kernel can also be inferred from data}.
 In addition, we have assumed that the neural field is isotropic and homogeneous.
@@
 The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
+\dean{The validation of the estimation framework on real data is now required, and is the subject of planned future work.}
 
@@
 John Terry for insightful discussions and feedback.
+\dean{Finally, the authors would like to thanks the anonymous reviews who have provided an excellent critique that has led to valuable insights that would have gone otherwise astray.}
 
@@
 \section{Equivalence to Galerkin's Projection}
-To show how to solution of equation for the state vector is equivalent to the Galerkin projection we define the residual between the field and the decomposition as 
-\begin{align}
-	\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) &= v_{t+1}(\mathbf{r}) - T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
+\dean{To show how to solution of equation for the state vector is equivalent to the Galerkin projection we define the residual between the field and the decomposition as 
+\begin{align}\label{eq:BasisFunctionResidual}
+	\Xi(\mathbf{x}_t,v_{t+1}&(\mathbf{r})) = v_{t+1}(\mathbf{r}) \nonumber \\
+	&- T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
 	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
 \end{align} 
-The Galerkin projection method finds $\mathbf{x}_t$, such that for all of the basis functions, the inner product with the residual satisfies
+The Galerkin projection method finds $\mathbf{x}_t$, such that the inner product of the residual with all of the basis functions satisfies
 \begin{equation}\label{eq:GalerkinProjection}
-	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,
-\end{equation}
-where $n_x$ is the number of states and basis functions.
+	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0,
+\end{equation}
+where $i=0,1,\hdots,n_x-1,$ and $n_x$ is the number of states and basis functions.
 If the inner product between the residual and the basis functions in equation~\ref{eq:GalerkinProjection} is zero, then the basis functions are orthogonal to the residual.
+By substituting equation~\ref{eq:BasisFunctionResidual} into equation~\ref{eq:GalerkinProjection} and rearranging we get equation~\ref{eq:decompRHS} in the main text.
+Note, if Galerkin's method was used estimate the states, $n_x$ coupled ODEs would need to be solved independently (each $G_i$) to estimate the state vector, which is a standard method in fluid dynamics and economics modeling.
+The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation.
+}
 

### 2011-01-07 ltx/first_order_framework/response_to_reviews.tex

@@
 \usepackage{graphicx}
+\usepackage{soul}
 \usepackage{anysize} %<-for setting margins
@@
 \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
+\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
 
@@
 In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.
-Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.
-WE SHOULD ADD SOMETHING IN THE CONCLUSION TO SAY WE TOTALLY NEED TO VALIDATE THIS ON REAL DATA AND IT'S NOTED AS FUTURE WORK}
+Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.\mike{it would be worth saying something about validating the framework on real data is noted as future work in the conclusion}}
 
@@
 	\emph{The examples presented in the paper use the Mexican hat connectivity kernel.
-The framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
-The mathematical formulation does not restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented.
-Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.
+The framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
+The mathematical formulation does not \mike{place any further restrictions on the form of the spatial mixing kernel.} \st{restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented.} \mike{Does any of the rest of this answer address the question?} Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.
 For more complex basis functions some of the analytic derivations described in the Appendix may have to be performed numerically.
@@
 We have primarily developed the framework for higher density intracranial measurements.
-This is explained in the spatial freq analysis method and discussion.}
+This is explained in the spatial frequency analysis method and discussion.}
 
@@
         \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
+        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}
 
@@
 
-\emph{The existing literature has been discussed in more depth in the introduction.}
+\emph{The existing literature has been discussed in more depth in the Introduction section.}
 
@@
 
-	\emph{To address this point, we have added an extra section to the discussion, 'Modeling Asusumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
+	\emph{To address this point, we have added an extra section to the discussion, `Modeling Asusumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
+	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model.
+The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data.
+While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent.
+Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extenstion in the underlying field model or its discretisation.}}
 

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 This is a reasonable assumption if applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
-However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010} for a nice example).
+However, it is well known that factors that influence excitability are non-stationary over longer time periods (see e.g.
+\citet{Ullah2010}).
 Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
@@
 Alternatively, the parameters of the model could be considered time-varying, where changes in excitability might result in different connectivity kernel parameters.
-A possible way to achieve this would be to employ window-based or fixed-lag estimation, where the estimation is performed on successive windows of data (possibly overlapping windows).
+A possible way to achieve this would be to employ window-based estimation or fixed-lag, where the estimation is performed on successive windows of data (possibly overlapping windows).
 The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.

### 2011-01-07 ltx/first_order_framework/response_to_reviews.tex
edits to discussion

@@
 In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.
-Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.\mike{it would be worth saying something about validating the framework on real data is noted as future work in the conclusion}}
+Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.
+We have also added that validating the framework on real data is noted as future work in the conclusion.}
 
@@
 The framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
-The mathematical formulation does not \mike{place any further restrictions on the form of the spatial mixing kernel.} \st{restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented.} \mike{Does any of the rest of this answer address the question?} Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.
-For more complex basis functions some of the analytic derivations described in the Appendix may have to be performed numerically.
-We have added the above statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}
+The mathematical formulation does not place any further restrictions on the form of the spatial mixing kernel.
+We have added statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}
 
@@
 
-        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.
+        \item The derivation of Equations (30) and (31) and make them more transparent for the general audience.
 
@@
 We have also added the references to relevant part of the text (that should have been there before, as the reviewer has correctly pointed out).
-We felt that it was worth adding the extra appendix to provide a clear derivation that is contextually and notationally relevant to this paper, as the derivations cited papers may not be clear to the Neuroimage general audience.}
+We felt that it was worth adding the extra appendix to provide a clear derivation that is contextually and notationally relevant to this paper.}
 
@@
 
-	\emph{To address this point, we have added an extra section to the discussion, `Modeling Asusumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
+	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
 	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model.
@@
 While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent.
-Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extenstion in the underlying field model or its discretisation.}}
+Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}}
 
@@
 \emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
-The paper he is talk about is also a nightmare to read.}
+The paper he is talking about is also a nightmare to read.}
 
@@
 
-\emph{Fourier basis functions are indeed a correct alternative in the case examined in this paper.
-In fact Fourier basis functions or any other orthonormal basis functions simplify the state space representation of the model, since $\Gamma$ defined in equation (20) of the manuscript becomes Identity matrix.
-However, we have chosen Gaussian basis functions due to their semi-compact support.
-By choosing Gauassian basis functions the stat space representation of the model remains in its generic form which is also correct in the case of orthonormal basis functions.}
+\emph{Fourier basis functions would be a correct alternative to the case examined in this paper.
+In fact Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation (20)) of the manuscript would be the identity matrix.
+However, we have chosen Gaussian basis functions due to their semi-compact support.} %By choosing Gaussian basis functions the state-space representation of the model remains in its generic form which is also correct in the case of orthonormal basis functions.}
 
@@
 
-\emph{The spatial frequency content is seems to be actually lower than one might first think.
+\emph{The mean spatial frequency content is seems to be actually lower than one might first think.
 We have added `From the work of (Freeman et al, 2000), the expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm which requires a sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing' to the Frequency Analysis section of the paper to clear this up.
 We have also added to the discussion.
-Note, we expect the spatial bandwidth of the cortex to be governed by the connectivity kernel, since it is equivalent to a spatial low-pass filter acting on the firing rates.
-}
+Note, we expect the spatial bandwidth of the cortex to be governed by the connectivity kernel, since it is equivalent to a spatial low-pass filter acting on the firing rates.}
 
@@
 
-\emph{A few comments have been added to the Modeling Assumptions section of the discussion.}
+\emph{A few comments have been added to the `Extensions to the Framework' section of the discussion.}
 
@@
 \item Page 45, Appendix D, Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.
+
+\emph{We stand corrected. We have changed the text to `an n-dimensional'.}
+
 \end{enumerate}

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to discussion

@@
 \usepackage{setspace} 
-\usepackage{color}
+\usepackage[usenames,dvipsnames]{color}
 
@@
 \newcommand{\parham}[1]{\textcolor{blue}{#1}}
+\newcommand{\mike}[1]{\textcolor{Plum}{#1}}
 
@@
 \end{align}
-\dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to finding a Galerkin projection, where the field basis functions would be considered the Galerkin projection functions and the states would be the amplitude coefficients.
-In the next step to forming the state-space model we substitute the field decomposition into the left hand side of equation~\ref{eq:decompRHS} giving}
+\dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to finding a Galerkin projection, where the field basis functions would be considered the projection functions and the states would be the amplitude coefficients.
+See~\ref{App:Galerkin} for more information.}
+
+In the next step of forming the state-space model we substitute the field decomposition into the left hand side of equation~\ref{eq:decompRHS} giving
 \begin{align}
@@
 \end{equation}
-\parham{(reviewer 2, comment 7:) The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, is typically set arbitrary small (e.g., $10^{-3}$) to minimise higher order effect \citep{Haykin2001}, and  $\kappa$ is an additional scaling parameter which was set to $3-n_x$ in accordance to \citet{Julier2002a}.}
+\parham{(reviewer 2, comment 7:) The positive constant $\alpha$ that determines the spread of the sigma points around $\mathbf{\bar x}$ is typically set arbitrary small (e.g., $10^{-3}$) to minimise higher-order effects \citep{Haykin2001}, and  $\kappa$ is an additional scaling parameter which was set to $3-n_x$ in accordance to \citet{Julier2002a}.}
 
@@
 Although models of this form are capable of describing a variety of cortical dynamics, there is without doubt, a mismatch between the cortex and the model.
-Nevertheless, there is a sufficient volume of interesting results from theoretical studies that warrants the data assimilation framework.
+Nevertheless, there is a sufficient volume of interesting results from theoretical studies using the WC field equations that warrants the data assimilation framework.
 }
@@
 In this way a minimal number of assumptions are made.
-A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
+A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed, such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
 
@@
 \citet{Ullah2010}).
-Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
-A possible way to achieve this is to use a more sophisticated model that accounts for longer term time dependancies (higher temporal order).
+Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.}
+
+% A possible way to achieve this is to use a more sophisticated model that accounts for longer term time dependancies (higher temporal order).
 Alternatively, the parameters of the model could be considered time-varying, where changes in excitability might result in different connectivity kernel parameters.
@@
 
+\mike{The estimation framework that we have presented uses an inherently batch algorithm designed to operate after data has been collected.
+An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung99}, the incremental EM algorithm \cite{Neal98} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used.
+These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.}
+
 \section{Conclusion}
@@
 The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
-\dean{The validation of the estimation framework on real data is now required, and is the subject of planned future work.}
+\dean{A validation of the estimation framework on real data is now required.
+This is the subject of planned future work.}
 
@@
 
-\section{Equivalence to Galerkin's Projection}
-\dean{To show how to solution of equation for the state vector is equivalent to the Galerkin projection we define the residual between the field and the decomposition as 
+\section{Equivalence to Galerkin's Projection}\label{App:Galerkin}
+\dean{To show how equation~\ref{eq:decompRHS} is equivalent to the Galerkin projection, we define the residual between the field and the decomposition as 
 \begin{align}\label{eq:BasisFunctionResidual}
@@
 where $i=0,1,\hdots,n_x-1,$ and $n_x$ is the number of states and basis functions.
-If the inner product between the residual and the basis functions in equation~\ref{eq:GalerkinProjection} is zero, then the basis functions are orthogonal to the residual.
-By substituting equation~\ref{eq:BasisFunctionResidual} into equation~\ref{eq:GalerkinProjection} and rearranging we get equation~\ref{eq:decompRHS} in the main text.
+If equation~\ref{eq:GalerkinProjection} is satisfied the basis functions are orthogonal to the residual.
+By substituting equation~\ref{eq:BasisFunctionResidual} into equation~\ref{eq:GalerkinProjection} and rearranging we get equation~\ref{eq:decompRHS} of the main text.
 Note, if Galerkin's method was used estimate the states, $n_x$ coupled ODEs would need to be solved independently (each $G_i$) to estimate the state vector, which is a standard method in fluid dynamics and economics modeling.
@@
 The convolution theorem states that the Fourier transform of the convolution of two functions is equal to the product of their Fourier transforms.
-Using the formula from the derivation of the Fourier transform of a \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} in \ref{App:FrequencyAnalysis}, we have
+Using the formula from the derivation of the Fourier transform of an \emph{n}-dimensional Gaussian from equation~\ref{eq:FTofGaussian} in \ref{App:FrequencyAnalysis}, we have
 \begin{equation}\label{eq:FTTwoGaussianMultiplication}

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to discussion

@@
 \end{equation}
-\parham{(reviewer 2, comment 7:) The positive constant $\alpha$ that determines the spread of the sigma points around $\mathbf{\bar x}$ is typically set arbitrary small (e.g., $10^{-3}$) to minimise higher-order effects \citep{Haykin2001}, and  $\kappa$ is an additional scaling parameter which was set to $3-n_x$ in accordance to \citet{Julier2002a}.}
+\parham{(reviewer 2, comment 7:) The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, was set to $10^{-3}$.
+It is typically set arbitrary small to minimise higher-order effects \citep{Haykin2001}.
+The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \citet{Julier2002a}.}
 

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
replaced extended kalman filterin with local linearization filter and added references

@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think-maybe just say using nonlinear Kalman filtering algorithm or maybe using Local Linearisation filter \citep{Ozaki1994}}.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using a form of non-linear Kalman filtering called the local linearization (LL) filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
added incremental EM reference

@@
 \mike{The estimation framework that we have presented uses an inherently batch algorithm designed to operate after data has been collected.
-An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung99}, the incremental EM algorithm \cite{Neal98} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used.
+An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung99}, the incremental EM algorithm \cite{Neal1998} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used.
 These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.}

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
minor correction

--- 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \mike{The estimation framework that we have presented uses an inherently batch algorithm designed to operate after data has been collected.
-An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung99}, the incremental EM algorithm \cite{Neal98} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used.
+An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung1999}, the incremental EM algorithm \cite{Neal1998} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used.
 These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
comment on higher order model

@@
 \newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
+\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
 
@@
 While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent.
-Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}}
+Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}
+	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
+ \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf
+r,t)}{dt}+\zeta^2v(\mathbf r,t)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
+\mathbf{r}',t \right) \right)d\mathbf{r}'} 
+\end{equation}
+and in a discretized form we have
+\begin{equation}
+ v_{t+2}(\mathbf r)-2(1-\zeta T_s)v_{t+1}(\mathbf r)+(1-\zeta T_s)^2v_t(\mathbf r)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left(
+\mathbf{r}'\right) \right)d\mathbf{r}'} 
+\end{equation}}}
 

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
comment on higher order model
reviewer 1 additional comment 2

@@
 		even change the dynamical properties of the system. The authors should
-		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}
+		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\
+
+		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written as 
+		  \begin{equation}\label{vrecursive}
+		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
+		  \end{equation}
+		  where
+		  \begin{equation}
+		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
+\mathbf{r}'\right) \right)d\mathbf{r}'} 
+		  \end{equation}
+		  in a worst case scenario if we assume $f(v_t(\mathbf r))$ saturates for all $g_t$ we have
+		  \begin{align}
+		   g_{t}(\mathbf r)=&\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)d\mathbf{r}'} \nonumber \\
+				   =-a
+		  \end{align}	
+		  where $a$ is the area under the connectivity kernel. Substituting $-a$ for all $g_{t}$ in \eqref{vrecursive} we get
+		  \begin{align}\label{vrecursiveinlimit}
+		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-aT_s\sum_{i=0}^t\xi^i \nonumber\\
+				     &=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s(1-\xi^{t+1})}{1-\xi}
+		  \end{align}
+		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
+		  \begin{equation}\label{simplifiedvrecursiveinlimit}
+		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s}{1-\xi}
+		  \end{equation}
+		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit}
+		  \begin{equation}
+		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{a}{\zeta}
+		  \end{equation}
+		  by choosing sufficiently small $T_s$ the discretized model will be stable.}}
 
@@
 \begin{equation}
- v_{t+2}(\mathbf r)-2(1-\zeta T_s)v_{t+1}(\mathbf r)+(1-\zeta T_s)^2v_t(\mathbf r)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left(
+ v_{t+2}(\mathbf r)-2(1-\zeta T_s)v_{t+1}(\mathbf r)+(1-\zeta T_s)^2v_t(\mathbf r)= T_s^2\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left(
 \mathbf{r}'\right) \right)d\mathbf{r}'} 

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
reviewer 1 additional comment 2

@@
 		  \end{equation}
-		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit}
+		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
 		  \begin{equation}
@@
 		  \end{equation}
-		  by choosing sufficiently small $T_s$ the discretized model will be stable.}}
+		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}
 

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
reviewer 1 additional comment 2
changes to reviewer 1 additional comment 2

@@
 		  \end{equation}
-		  in a worst case scenario if we assume $f(v_t(\mathbf r))$ saturates for all $g_t$ we have
-		  \begin{align}
-		   g_{t}(\mathbf r)=&\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)d\mathbf{r}'} \nonumber \\
-				   =-a
-		  \end{align}	
-		  where $a$ is the area under the connectivity kernel. Substituting $-a$ for all $g_{t}$ in \eqref{vrecursive} we get
+		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
+		  if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
 		  \begin{align}\label{vrecursiveinlimit}
-		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-aT_s\sum_{i=0}^t\xi^i \nonumber\\
-				     &=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s(1-\xi^{t+1})}{1-\xi}
+		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
+				     &=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
 		  \end{align}
@@
 		  \begin{equation}\label{simplifiedvrecursiveinlimit}
-		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{aT_s}{1-\xi}
+		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s}{1-\xi}
 		  \end{equation}
@@
 		  \begin{equation}
-		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{a}{\zeta}
+		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{g_{b}}{\zeta}
 		  \end{equation}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
changes to reviewer 1 additional comment 2

@@
 		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
-		  if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
+		  in a worse case scenario if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
 		  \begin{align}\label{vrecursiveinlimit}

### 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
changes to reviewer 1 additional comment 2

@@
 
-		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written as 
+		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written in a form of 
 		  \begin{equation}\label{vrecursive}
@@
 		  \begin{align}\label{vrecursiveinlimit}
-		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)-g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
-				     &=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
+		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)+g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
+				     &=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
 		  \end{align}
@@
 		  \begin{equation}\label{simplifiedvrecursiveinlimit}
-		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)-\frac{g_{b}T_s}{1-\xi}
+		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s}{1-\xi}
 		  \end{equation}
@@
 		  \begin{equation}
-		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)-\frac{g_{b}}{\zeta}
+		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{b}}{\zeta}
 		  \end{equation}
@@
 
-		\emph{We should add some more to the modeling assumptions section to address this one. I have begun to talk about the LL method.}
+		\emph{We should add some more to the modeling assumptions section to address this one.
+I have begun to talk about the LL method.
+\parham{here he just ask about Euler method he doesn't ask about s-word.}}
 

### 2011-01-09 ltx/first_order_framework/response_to_reviews.tex
added stability proof to appendix from Parhams derivation

@@
 		  \end{equation}
-		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
+		  since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
 		  in a worse case scenario if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
@@
 		  \end{align}
-		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
+		  in a limit equation (geometric series) \eqref{vrecursiveinlimit} can be written as 
 		  \begin{equation}\label{simplifiedvrecursiveinlimit}

### 2011-01-09 ltx/first_order_framework/LaTeX_Manuscript.tex
added stability proof to appendix from Parhams derivation

@@
 
+Even though the continuous system is stable, it is not guaranteed the discrete system is stable when using Euler's method.
+Therefore, it is necessary to demonstrate the stability of the discretized IDE.
+To show this, the model is written as the series
+\begin{align}
+	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
+	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
+	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \\
+	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
+\end{align}
+where
+\begin{equation}
+	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
+\end{equation}
+Now, since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded.
+To assess the stability of the system  we assume the entire field is firing at the maximal rate.
+Therefore $g_{t}(\mathbf{r}) = c$, where $c$ is the integral of the connectivity kernel.
+Substituting this into equation~\ref{eq:fieldmodelseries} yields
+\begin{align}\label{vrecursiveinlimit}
+	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ c T_s \sum_{i=0}^t \xi^i \nonumber \\
+	&=\xi^{t+1}v_0(\mathbf r) + \frac{ c T_s(1-\xi^{t+1})}{1-\xi}.
+\end{align}
+Now considering the limit as $t$ approaches infinity, equation \eqref{vrecursiveinlimit} can be written as a geometric series
+\begin{equation}\label{simplifiedvrecursiveinlimit}
+	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{c T_s}{1-\xi}.
+\end{equation}
+Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
+\begin{equation}
+	v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{c}{\zeta}.
+\end{equation}
+From this equation it can be seen that the system is stable if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$.
+The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
+Therefore, the discretization preserved the stability properties of the system.
+
 \section{Observation Kernel}\label{App:ObsKernelExperiment}

### 2011-01-10 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to euler appendix

--- 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-By exploiting the isotropy of the connectivity basis functions, they can be written as
+\dean{A graphical demonstration of the connectivity kernel decomposition is provided in Figure~\ref{fig:Figure1}.} By exploiting the isotropy of the connectivity basis functions, they can be written as
 $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
@@
 
+Even though the continuous system is stable, there is no guarantee that the discrete system is stable when using Euler's method.
+Therefore, it is necessary to demonstrate the stability of the discretized IDE.
+To do this, the model is written as the series
+\begin{align}
+	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
+	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
+	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \nonumber \\
+	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
+\end{align}
+where
+\begin{equation}
+	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
+\end{equation}
+Now, $g_t(\mathbf r)$ is always bounded since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is finite.
+To assess the stability of the discrete time system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$.
+Substituting this into equation~\ref{eq:fieldmodelseries} yields
+\begin{align}\label{vrecursiveinlimit}
+	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ g_{max} T_s \sum_{i=0}^t \xi^i \nonumber \\
+	&=\xi^{t+1}v_0(\mathbf r) + \frac{ g_{max} T_s(1-\xi^{t+1})}{1-\xi}.
+\end{align}
+To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity and in doing so we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
+\begin{equation}\label{simplifiedvrecursiveinlimit}
+	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{max} T_s}{1-\xi}.
+\end{equation}
+Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
+\begin{equation}
+	v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta}.
+\end{equation}
+From this equation it can be seen that the system is stable if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$.
+The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
+Therefore, the discretization preserved the stability properties of the system.
+
 \section{Observation Kernel}\label{App:ObsKernelExperiment}

### 2011-01-10 ltx/first_order_framework/response_to_reviews.tex
updated response about the AR process

@@
 	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
-	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model.
+	\emph{\mike{We would like to directly address the idea of representing the error using an autoregressive model.
 The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data.
-While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent.
-Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}
+Done properly, modelling the error as an autoregressive process  will introduce additional connectivity kernels, one for each temporal lag in the AR process, i.e.
+	\begin{equation}
+	   e_t(s) = \sum_i \int_\Omega K_i(s,s')e_{t-i}(s')ds'
+	\end{equation} 
+where $K_i$ is the $i^\mathrm{th}$ connectivity kernel.
+Hence this would imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.
+Having said this, we are considering various model extensions, and that of higher order temporal dynamics is particularly intriguing due to the additional richness of signal we can represent.}
 	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}

### 2011-01-11 ltx/first_order_framework/response_to_reviews.tex
made chages from DG

--- 2011-01-08 ltx/first_order_framework/response_to_reviews.tex
@@
 \usepackage{color}
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
-\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
+\newcommand{\dean}[1]{\textcolor{red}{#1}}
+\newcommand{\mike}[1]{\textcolor{green}{#1}}
+\newcommand{\parham}[1]{\textcolor{blue}{#1}}
 
@@
         \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
-        \emph{\mike{something about the identifiability of the parameters, as many parametere sets give rise to the same kernel?}}
+
+		\emph{These results show that the system may not be identifiable in non-ideal, practical situations. Nevertheless, the net shape of the estimated kernels will be in accordance to actual data.}
 
@@
 
-		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
-		Filtering for the estimation of neural mass models from data [1-3],
-		[13]. In fact from those papers stressed the importance of carrying out
-		a high order discretization of the differential equations, which should
-		be in fact treated as stochastic. In equation (S1.1) of the extended
-		derivation, it is shown that an Euler approximation is taken which may
-		even change the dynamical properties of the system. The authors should
-		discuss this issue.'' ALL THESE PAPERS USE a method called local linearisation approach for discretisation.}\\
-
-		\emph{\parham{ discretized membrane voltage $v_{t+1}(\mathbf r)$ can be written in a form of 
-		  \begin{equation}\label{vrecursive}
-		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+T_s\sum_{i=0}^t\xi^ig_{t-i}(\mathbf r)
-		  \end{equation}
-		  where
-		  \begin{equation}
-		   g_{t}(\mathbf r)=\int_\Omega  {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( v_t\left(
-\mathbf{r}'\right) \right)d\mathbf{r}'} 
-		  \end{equation}
-		  since $0\leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is bounded, $g_t(\mathbf r)$ is always bounded,
-		  in a worse case scenario if we assume $g_t=g_b$ for all time, where $g_b$ is the upper bound on the average firing rate, we have
-		  \begin{align}\label{vrecursiveinlimit}
-		   v_{t+1}(\mathbf r)&=\xi^{t+1}v_0(\mathbf r)+g_{b}T_s\sum_{i=0}^t\xi^i \nonumber\\
-				     &=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s(1-\xi^{t+1})}{1-\xi}
-		  \end{align}
-		  in a limit equation \eqref{vrecursiveinlimit} can be written as 
-		  \begin{equation}\label{simplifiedvrecursiveinlimit}
-		   v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{b}T_s}{1-\xi}
-		  \end{equation}
-		  substituting $\xi=1-\zeta T_s$ in \eqref{simplifiedvrecursiveinlimit} we get
-		  \begin{equation}
-		   v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{b}}{\zeta}
-		  \end{equation}
-		  by choosing $0<T_s\le \frac{1}{\zeta}$ which is the case in practice the discretized system will be stable.}}
-
-		\emph{We should add some more to the modeling assumptions section to address this one.
-I have begun to talk about the LL method.
-\parham{here he just ask about Euler method he doesn't ask about s-word.}}
+		\emph{Amendments have been made to Appendix A, where the discretization is performed.
+We have commented on how the discrete-time system's properties may differ from the continuous-time system.
+In addition, we have provided a proof for the stability of the discrete-time system.}
 
@@
 
-\emph{The existing literature has been discussed in more depth in the Introduction section.}
+\emph{The existing literature has been discussed in more depth in the Introduction.}
 
@@
 I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model.
-But I will let the authors answer this question.\\
+But I will let the authors answer this question.
 
 	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
+
 	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model.
@@
 While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent.
-Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}
-	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
+Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}}
+
+	\emph{\parham{It doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
  \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf
@@
 
-\emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
+\dean{\emph{The author do not have much to add to this comment.
+We feel that adding the disturbance to the firing rate is appropriate for this model, which is what we have done.
+By the central limit theorem, we expect the disturbance to be Gaussian and due to the structural organization of the cortex, we expect the disturance to be spatially colored.
+In future work we plan to add to the framework and show how the disturbance properties can also be estimated from data.}}
+% \emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
 The paper he is talking about is also a nightmare to read.}
-
-\emph{We added the disturbance term to the firing rate function (equation 12).
+% 
+% \emph{We added the disturbance term to the firing rate function (equation 12).
 Although we added this after we provided the model derivation and discritization, we can show this holds if we assume the disturbance is a Wiener process, add it to the firing rate $g(\mathbf{r},t)$ (equation 3), use Ito's method to form the IDE, and the Euler-Maruyama method for the discretization.
@@
 }
-
-\emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences.
+% 
+% \emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences.
 Since we a talking about a large number of neurons, we expect this disturbance to be Gaussian (according to the central limit theorem).
@@
 
-\item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?\\
+\item In the isotropic and translationally invariant case examined here, would a Fourier basis for temporal and spatial structure have been a formally correct alternative?
 
@@
 
-\emph{The mean spatial frequency content is seems to be actually lower than one might first think.
+\emph{The mean spatial frequency content is actually lower than one might first expect.
 We have added `From the work of (Freeman et al, 2000), the expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm which requires a sensor spacing of approximately 1.25 mm to avoid distortions due to aliasing' to the Frequency Analysis section of the paper to clear this up.
@@
 
-\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?\\
+\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
 

### 2011-01-11 ltx/first_order_framework/LaTeX_Manuscript.tex
made chages from DG

@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using a form of non-linear Kalman filtering called the local linearization (LL) filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}}.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient-specific modeling came from~\citet{Valdes1999}, where they fit the neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} to EEG data using the local linearization filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}
@@
 Another continuum neural field model-based estimator was developed by \citet{Daunizeau2009}, as an extension to the DCM framework.
-They argued that this approach is superior for data assimilation than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.}
+They argue that using a spatially extended continuum field models is superior for explaining cortical function than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.}
 
@@
 This marks the first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
-For other valuable contributions to data-driven neural modeling see \citet{Nunez2000,Jirsa2002,Robinson2004}.}
+For other valuable contributions to data-driven neural modeling, see \citet{Nunez2000}, \citet{Jirsa2002}, and \citet{Robinson2004}.}
 
@@
 This work provides a fundamental link between the theoretical advances in neural field modeling and \dean{(for reviewer 1, comment 3:) high resolution intracranial} electrophysiological data.
-\dean{(for reviewer 1 comment 1:) (this is copied from the abstract) To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters.} The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
+\dean{(for reviewer 1 comment 1:) (this is copied from the abstract) To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison to be made between the estimated and true parameters.} The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
 Then a finite-dimensional neural field model is derived.
@@
 The columnar organization of the cortex is continuous, where pyramidal cells are members of many columns.
-In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \citep{Jirsa2009,Qubbaj2007}.
+In general, cortical structure can be modeled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity) \citep{Jirsa2009,Qubbaj2007}.
 In certain regions of the cortex, each column is thought to be connected locally via symmetric short range local excitation with surround inhibition \citep{Braitenberg1998}.
@@
 \end{align}
-where $\ast$ denotes convolution operator.} This gives the standard form of the model
+where $\ast$ denotes the convolution operator.} This gives the standard form of the model
 \begin{equation}
@@
 
-The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf{y}_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
+The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf{y}_t$, is modeled using the observation function that incorporates sensors with a spatial extent by
 \begin{equation}\label{eq:ObservationEquation}
@@
 where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=0,...,n_y-1$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
-\dean{(for reviewer 1, comment 3:) Note, since we are considering intracranial measurements recorded directly from the surface or within the cortex the lead field is not modeled by the observation equation.}
+\dean{(for reviewer 1, comment 3:) Since we are considering intracranial measurements recorded directly from the surface of the cortex or within the brain, the lead field is not modeled by the observation equation.}
 
@@
 $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
-\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
+\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented.
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}.
-\dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal, such as a Fourier basis, then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
+\dean{Alternative field basis functions may be used to form the decomposition; if the basis is orthonormal, such as a Fourier basis, then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
 \begin{equation}
@@
 where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
-\dean{(reviewer 1, additional comment 3:) A derivation of the sampling theorem that is based on the work of \citet{Sanner1992} and \citet{Scerri2009} is provided in \ref{App:SamplingTheorem}}.
+\dean{(reviewer 1, additional comment 3:) A derivation of the sampling theorem that is based on \citet{Sanner1992} and \citet{Scerri2009} is provided in \ref{App:SamplingTheorem}}.
 The condition in equation~\ref{eq:MinimumSensorDistance} must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
@@
 However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}).
-\dean{(Reviewer 2, comment 6:) From the work of~\citet{Freeman2000}, the expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm.}
+\dean{(Reviewer 2, comment 6:) The expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm~\citep{Freeman2000}.}
 
@@
 \end{align}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance $\beta$ should be set to 2 \parham{\citep{Haykin2001}})}.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance, $\beta$ should be set to 2 \parham{\citep{Haykin2001}})}.
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 An example of the simulated field at a single point in time can be seen in Fig.~\ref{fig:Figure3}(A).
-Fig.~\ref{fig:Figure3}(B) shows an example of data from the modelled sensors and Fig.~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
+Fig.~\ref{fig:Figure3}(B) shows an example of data from the modeled sensors and Fig.~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
 %The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
@@
 As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates.
-The estimates of the connectivity kernels show relatively broad distributions over the different realizations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise.
+The estimates of the connectivity kernels show relatively broad distributions over the different realizations, which can be expected considering the system's input is modeled as a random disturbance and the observations are corrupted by noise.
 To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings, where given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease.
@@
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-\dean{It should be noted that Schiff and Sauer suggest the possibility of using a Galerkin projection or similar decomposition that is used in this paper to perform efficient estimation as a direction for future work.
-Indeed,} we have show that this enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
+\dean{It should be noted that Schiff and Sauer suggest the possibility of using a Galerkin projection, or similar decomposition that is used in this paper, to perform efficient estimation as a direction for future work.
+Indeed,} we have shown that this enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
 
@@
 This is a reasonable assumption if applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
-However, it is well known that factors that influence excitability are non-stationary over longer time periods (see e.g.
-\citet{Ullah2010}).
-Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.}
-
-% A possible way to achieve this is to use a more sophisticated model that accounts for longer term time dependancies (higher temporal order).
-Alternatively, the parameters of the model could be considered time-varying, where changes in excitability might result in different connectivity kernel parameters.
-A possible way to achieve this would be to employ window-based estimation or fixed-lag, where the estimation is performed on successive windows of data (possibly overlapping windows).
+However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010}).
+Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
+A possible way to achieve this is to use a more sophisticated model that accounts for longer-term time dependancies (higher temporal order).
+Alternatively, the parameters of the model could be considered time-varying, where changes in excitability would result in different connectivity kernel parameters.}
+
+ % A possible way to achieve this would be to employ window-based estimation or fixed-lag, where the estimation is performed on successive windows of data (possibly overlapping windows).
 The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.
@@
 
-\dean{We have assumed that the model can be discretized by the first order Euler method.
-This discretization may change the properties of the stochastic nonlinear system.
-An alternative is to use the LL method....}
-
 \subsection{Extensions to the framework}
@@
 In addition, we have assumed that the neural field is isotropic and homogeneous.
-It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic.
+It is generally accepted that the intracortical connectivity structure can be accurately modeled as being isotropic.
 However, the assumption of homogeneity is quite strong as the size of the neural field becomes larger.
@@
 
-\mike{The estimation framework that we have presented uses an inherently batch algorithm designed to operate after data has been collected.
-An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung1999}, the incremental EM algorithm \cite{Neal1998} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used.
-These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.}
+\mike{A further extension of the framework is to allow for the algorithm to learn online.
+The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
+A filter that designed to be implemented in an online setting, can be used in place of the smoother.
+Doing this, while sacrificing accuracy, will increase the speed at which the state estimation can be done and decrease the amount of information that would need to be stored.
+Approaches for online state estimation include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \cite{Sato00,Cappe09} may be used.
+These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.
+Something something something estimator, something something something online, something something something complete...
+about updating parameters rather than finding brand new ones, recursive LS estimator \cite{Ljung1999},}
 
@@
 
-Even though the continuous system is stable, there is no guarantee that the discrete system is stable when using Euler's method.
-Therefore, it is necessary to demonstrate the stability of the discretized IDE.
+The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
+Observability is assumed and then verified with the estimation results.
+The stability of the discretized IDE is proven below.
 To do this, the model is written as the series
@@
 \end{align} 
-where $\mathbf{k}$ is a $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}$).
+where $\mathbf{k}$ is an $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}$).
 It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$.

### 2011-01-11 ltx/first_order_framework/response_to_reviews.tex

@@
 	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
-
-	\emph{\mike{We would like to directly address the idea of extending the error term to a higher order model.
+	\emph{\mike{We would like to directly address the idea of representing the error using an autoregressive model.
 The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data.
-While we are considering various model extensions, that of higher order temporal dynamics are particularly intriguing due to the additional richness of signal we can represent.
-Done properly though, this will introduce additional connectivity kernels (one for each temporal lag in the AR process), and would hence imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.}}
-
-	\emph{\parham{It doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
+Done properly, modelling the error as an autoregressive process  will introduce additional connectivity kernels, one for each temporal lag in the AR process, i.e.
+	\begin{equation}
+	   e_t(s) = \sum_i \int_\Omega K_i(s,s')e_{t-i}(s')ds'
+	\end{equation} 
+where $K_i$ is the $i^\mathrm{th}$ connectivity kernel.
+Hence this would imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.
+Having said this, we are considering various model extensions, and that of higher order temporal dynamics is particularly intriguing due to the additional richness of signal we can represent.}
+	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
  \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf

### 2011-01-11 ltx/first_order_framework/LaTeX_Manuscript.tex
made tiny change to the Galerkin method bit. Tiny!
more edits from DG

@@
 \dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of the cortical dynamics recorded from the subject.
-Although models of this form are capable of describing a variety of cortical dynamics, there is without doubt, a mismatch between the cortex and the model.
+Although models of this form are capable of describing a variety of cortical dynamics, there is without doubt a mismatch between the cortex and the model.
 Nevertheless, there is a sufficient volume of interesting results from theoretical studies using the WC field equations that warrants the data assimilation framework.
@@
 \dean{An advantage in using a lumped-parameter field model over a more detailed mathematical description is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
-In this way a minimal number of assumptions are made.
+In this way, a minimal number of assumptions are made.
 A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed, such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
@@
 \dean{The framework assumes that the parameters of the model (and brain) are stationary over the estimation period.
-This is a reasonable assumption if applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
+This is a reasonable assumption when applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
 However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010}).
@@
 \section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
-\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}.
+\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}, which provide conditions on distance between the sensors and the field basis functions.
 The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}.
@@
 \end{equation} 
-where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The observations in matrix form is described by
+where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The observations are described in matrix form by
 \parham{\begin{equation}

### 2011-01-11 ltx/first_order_framework/response_to_reviews.tex
deleted second order formulation

@@
 Hence this would imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.
-Having said this, we are considering various model extensions, and that of higher order temporal dynamics is particularly intriguing due to the additional richness of signal we can represent.}
-	\parham{it doesn't introduce additional connectivity kernel e.g the second order model is in a form of \begin{equation}
- \frac{d^2v(\mathbf r,t)}{dt^2}+2\zeta \frac{dv(\mathbf
-r,t)}{dt}+\zeta^2v(\mathbf r,t)=\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v\left(
-\mathbf{r}',t \right) \right)d\mathbf{r}'} 
-\end{equation}
-and in a discretized form we have
-\begin{equation}
- v_{t+2}(\mathbf r)-2(1-\zeta T_s)v_{t+1}(\mathbf r)+(1-\zeta T_s)^2v_t(\mathbf r)= T_s^2\int_\Omega  {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left(
-\mathbf{r}'\right) \right)d\mathbf{r}'} 
-\end{equation}}}
+Having said this, we are considering various model extensions, and that of higher order temporal dynamics is particularly intriguing due to the additional richness of signal we can represent.}}
 

### 2011-01-11 ltx/first_order_framework/response_to_reviews.tex
commit for pull

--- 2011-01-11 ltx/first_order_framework/response_to_reviews.tex
@@
 
-\dean{\emph{The author do not have much to add to this comment.
-We feel that adding the disturbance to the firing rate is appropriate for this model, which is what we have done.
+\dean{\emph{The authors do not have much to add to this comment.
+We feel that adding the disturbance to the firing rate is appropriate for this model, which is what we have done, and it agrees with the work by Benayoun et al PloS Comp Biol 2010.
 By the central limit theorem, we expect the disturbance to be Gaussian and due to the structural organization of the cortex, we expect the disturance to be spatially colored.
 In future work we plan to add to the framework and show how the disturbance properties can also be estimated from data.}}
-% \emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise.
-The paper he is talking about is also a nightmare to read.}
-% 
-% \emph{We added the disturbance term to the firing rate function (equation 12).
-Although we added this after we provided the model derivation and discritization, we can show this holds if we assume the disturbance is a Wiener process, add it to the firing rate $g(\mathbf{r},t)$ (equation 3), use Ito's method to form the IDE, and the Euler-Maruyama method for the discretization.
-The disturbance will then be an incremental Wiener process.
-We chose the simplest method to present the model so the paper did not get too heavy in the maths (at least in the intro) and due to space considerations.
-}
-% 
-% \emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences.
-Since we a talking about a large number of neurons, we expect this disturbance to be Gaussian (according to the central limit theorem).
-Furthermore, we expect the disturbance to be spatially colored according to the covariance function $\sigma_d\gamma(\mathbf{r}-\mathbf{r}')$, since we consider small neighboring regions within the field to be functional processing units.}
 

### 2011-01-12 ltx/data_paper/DataPaper.tex
corrected observation noise covariance estimation in dara paper

@@
 
-\title{Patient-Specific Neural Field Modeling from Micro-Electrode Data}
+\title{Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data}
 \author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
@@
 \begin{eqnarray}\label{eq:Qfunction}
-2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)&=&-\ln \boldsymbol\Sigma_{\epsilon}- (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\nonumber \\
+2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)&=&-\ln \mid\boldsymbol\Sigma_{\epsilon}\mid- (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\nonumber \\
 &-&\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
@@
 \begin{eqnarray}\label{eq:Qfunctionintrace}
-  \ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& -\ln \boldsymbol\Sigma_{\epsilon}-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace   \nonumber \\
+  \ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& -\ln \mid\boldsymbol\Sigma_{\epsilon}\mid-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace   \nonumber \\
 &-&\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
@@
 \begin{eqnarray}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)\ln \boldsymbol\Sigma_{\epsilon}-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)\ln \mid\boldsymbol\Sigma_{\epsilon}\mid-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
 &+&\beta+2\Xi_0\boldsymbol\theta+
@@
 \end{equation}
-differentiating equation~\ref{eq:Voldermont} with respect to $\boldsymbol\Sigma_{\epsilon}$ we get
+Rewrite equation~\ref{eq:Voldermont} as
 \begin{equation}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\Sigma_{\epsilon}}= (T-1)\boldsymbol\Sigma_{\epsilon}-\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right]=\mathbf 0
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')\propto-(T-1)n_y\ln\sigma^2_{\epsilon}-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
 \end{equation}
-therefore we have
+differentiating with respect to $\sigma_{\epsilon}^2$
 \begin{equation}
- \boldsymbol\Sigma_{\epsilon}=\frac{1}{T-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right]
+  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon^4}}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
+\end{equation}
+setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
+\begin{equation}
+ \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
 \end{equation}

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 
-\subsection{Extensions to the framework}
+\subsection{Extensions to the Framework}
 In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
@@
 \end{align} 
-The Galerkin projection method finds $\mathbf{x}_t$, such that the inner product of the residual with all of the basis functions satisfies
+The Galerkin projection finds $\mathbf{x}_t$, such that the inner product of the residual with all of the basis functions satisfies
 \begin{equation}\label{eq:GalerkinProjection}
@@
 \end{align} 
-where $\mathbf{k}$ is an $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}$).
-It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$.
+where $\mathbf{k}$ is an $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}_n$).
+It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $\mathbf{k}_n\Delta_y^{-1}$.
 Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$.
@@
 \begin{equation}
-	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
+	\boldsymbol\nu = \left[\frac{\mathbf{k}_n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{\mathbf{k}_n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
 \end{equation}

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
added few words and references for online algorithm

@@
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-A filter that designed to be implemented in an online setting, can be used in place of the smoother.
-Doing this, while sacrificing accuracy, will increase the speed at which the state estimation can be done and decrease the amount of information that would need to be stored.
-Approaches for online state estimation include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \cite{Sato00,Cappe09} may be used.
-These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.
-Something something something estimator, something something something online, something something something complete...
-about updating parameters rather than finding brand new ones, recursive LS estimator \cite{Ljung1999},}
+A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}
 

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
added few words and references for online algorithm

@@
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}
+\parham{A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
 

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
colored changes in the manuscript for ken

@@
 
-\mike{A further extension of the framework is to allow for the algorithm to learn online.
+\mike{(Reviewer 2, comment 9:)A further extension of the framework is to allow for the algorithm to learn online.
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
@@
 
-The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
+\parham{(Reviewer1, Additional comments 2:) The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
 Observability is assumed and then verified with the estimation results.
@@
 The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
-Therefore, the discretization preserved the stability properties of the system.
+Therefore, the discretization preserved the stability properties of the system.}
 

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to appendix A

@@
 Observability is assumed and then verified with the estimation results.
-The stability of the discretized IDE is proven below.
+Here we show that if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$,  the discretized IDE is stable.
 To do this, the model is written as the series
@@
 \end{align}
-To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity and in doing so we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
+To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity.
+Noting $0 < \xi <1$  we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
 \begin{equation}\label{simplifiedvrecursiveinlimit}
@@
 \end{equation}
-From this equation it can be seen that the system is stable if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$.
+From this equation it can be seen that if $0 < T_s < \tau$, the system is stable.
 The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.

### 2011-01-12 ltx/first_order_framework/response_to_reviews.tex
changes to appendix A and some changes for ken comments

@@
 	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
-	\emph{\mike{We would like to directly address the idea of representing the error using an autoregressive model.
-The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data.
-Done properly, modelling the error as an autoregressive process  will introduce additional connectivity kernels, one for each temporal lag in the AR process, i.e.
-	\begin{equation}
-	   e_t(s) = \sum_i \int_\Omega K_i(s,s')e_{t-i}(s')ds'
-	\end{equation} 
-where $K_i$ is the $i^\mathrm{th}$ connectivity kernel.
-Hence this would imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation.
-Having said this, we are considering various model extensions, and that of higher order temporal dynamics is particularly intriguing due to the additional richness of signal we can represent.}}
 
@@
 
-\dean{\emph{The authors do not have much to add to this comment.
+\dean{\emph{We have not added anything to the The authors do not have much to add to this comment.
 We feel that adding the disturbance to the firing rate is appropriate for this model, which is what we have done, and it agrees with the work by Benayoun et al PloS Comp Biol 2010.

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to appendix A and some changes for ken comments

@@
 Another continuum neural field model-based estimator was developed by \citet{Daunizeau2009}, as an extension to the DCM framework.
-They argue that using a spatially extended continuum field models is superior for explaining cortical function than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.}
+\parham{They argue that using a spatially extended continuum field model is superior for explaining cortical function than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.}}
 
@@
 \end{equation}
-\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
+\parham{The post-synaptic membrane potential is in fact the temporal convolution between the synaptic kernel and the average firing rate
+\begin{equation}\label{FullConvolutionModel}
+ v\left(\mathbf r,t\right)= \left(h\ast g\right)\left(\mathbf r,t\right)
+\end{equation}
+where $\ast$ denotes the convolution operator.}
+\dean{(reviewer 2, comment 3:) \parham{To obtain (To arrive at)} the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
 A Green's function satisfies
@@
 \end{equation} 
-where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ to equation~\ref{FullDoubleIntModel} gives
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ \parham{to equation~\ref{FullConvolutionModel}} gives
 \begin{align}
@@
 \end{align}
-where $\ast$ denotes the convolution operator.} This gives the standard form of the model
+} This gives the standard form of the model
 \begin{equation}
@@
 
-\parham{(Reviewer1, Additional comments 2:) The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
-Observability is assumed and then verified with the estimation results.
-Here we show that if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$,  the discretized IDE is stable.
+\parham{(Reviewer1, Additional comments 2:) The analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
+Here we only study the stability of the discretized model, we show that if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$,  the discretized IDE is stable.
 To do this, the model is written as the series
@@
 \end{equation}
-Now, $g_t(\mathbf r)$ is always bounded since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is finite.
+Since  $0 \leq f(v_t(\mathbf r)) \leq 1$ and the kernel is semi-compactly supported, $g_t(\mathbf r)$ is always bounded .
 To assess the stability of the discrete time system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$.
@@
 By substituting equation~\ref{eq:BasisFunctionResidual} into equation~\ref{eq:GalerkinProjection} and rearranging we get equation~\ref{eq:decompRHS} of the main text.
-Note, if Galerkin's method was used estimate the states, $n_x$ coupled ODEs would need to be solved independently (each $G_i$) to estimate the state vector, which is a standard method in fluid dynamics and economics modeling.
+Note, if Galerkin's method was used to estimate the states, $n_x$ coupled ODEs would need to be solved independently (each $G_i$) to estimate the state vector, which is a standard method in fluid dynamics and economics modeling.
 The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation.

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
applied ken comments
minor edits

--- 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 \end{equation}
-\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
+\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the operator $\textrm{D}=d/dt + \zeta$.
 A Green's function satisfies
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-\dean{A graphical demonstration of the connectivity kernel decomposition is provided in Figure~\ref{fig:Figure1}.} By exploiting the isotropy of the connectivity basis functions, they can be written as
+\dean{A graphical demonstration of the connectivity kernel decomposition is provided in Fig.~\ref{fig:Figure1}.} By exploiting the isotropy of the connectivity basis functions, they can be written as
 $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
@@
 \end{equation}
-
-\subsection{Estimation of Connectivity Kernel Support}
-\dean{The support of the connectivity kernel can be inferred using spatial correlation analysis.
-The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}.
-To demonstrate the method for the neural field model we assume the sensors are infinitesimally close (continuous observation).
-The spatial cross-correlation function between consecutive observations is defined as
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \\
-	&= \mathbf{E}\left[\left(m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) + \boldsymbol{\varepsilon}_t\left(\mathbf{r}\right) \right) \times \left( m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right], \label{eq:ObsXCorr}
-\end{align}
-where $\mathbf{E}[\cdot]$ is the expected value. Since the observation noise is temporally white and independent of the field, equation~\ref{eq:ObsXCorr} reduces to
-\begin{equation}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right].
-\end{equation}
-Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left( \xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) + e_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \\
-	 &= \xi \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \nonumber \\
-	&+ T_s\mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \nonumber \\
-	&+ \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast e_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]
-	\\
-	&= R_1(\boldsymbol{\tau}) + R_2(\boldsymbol{\tau}) + R_3(\boldsymbol{\tau}).\label{eq:spatialxcorr} 
-\end{align}
-The last term on the right hand side of equation~\ref{eq:spatialxcorr} is
-\begin{equation}
-	R_3(\boldsymbol{\tau}) = 0,
-\end{equation}
-since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$. Putting to other two terms back together we can write
-\begin{equation}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right) \right]
-\end{equation}
-Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
-\begin{equation}
-	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
-		0, & v_t(\mathbf{r}') \le v_1 \\
-		\varsigma v_t(\mathbf{r}'), &  v_1 < v_t(\mathbf{r}') < v_2 \\
-		1, & v_t(\mathbf{r}') \ge v_2 \\ 
-		\end{array}\right.
-\end{equation}
-Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. 
-\begin{equation}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \varsigma v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right) \right]
-\end{equation}
-Now we take the Fourier transform of the terms inside the expectation giving
-\begin{align}
-	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) + T_s e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \left(\xi + T_s \varsigma e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
-	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \ast \left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \\
-	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \right] \ast \mathbf{E}\left[\left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \label{eq:xcorr_pre_sub}
-\end{align}
-where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform and $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.
-We define the auto-correlation of the observations as
-\begin{align}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]\\
-	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2
-\end{align}
-Rearrange to get
-\begin{equation}\label{eq:autocorr_for_sub}
-	R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 = \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right].
-\end{equation}
-Now to isolate the kernel equation~\ref{eq:autocorr_for_sub} is substituted into equation~\ref{eq:xcorr_pre_sub} and the Fourier transform is taken giving
-\begin{align}
-	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \mathbf{E} \left[ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right] \right\} \\
-	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right) \sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{\mathbf{E}[ \xi \delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.
-\end{align}
-Now rearranging
-\begin{equation}
-	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \mathbf{E}\left[ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right]\right\}.
-\end{equation}
-Take inverse Fourier transform and rearrange to get an approximation of the kernel
-\begin{equation}
-	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} \approx \mathbf{E}[\xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau})].
-\end{equation}
-This equation states that the support of the kernel can be estimated given knowledge of $\sigma_\varepsilon^2$.
-Furthermore, is we assume a local coupling (at $\boldsymbol\tau=0$) regime, either excitation or inhibition, than we don't even need to know $\sigma_\varepsilon^2$.
-The peak in the kernel at $\mathbf{r}=0$ will be bigger or smaller if we guess incorrectly and the kernel parameters can do the rest!
-}
-% 
-% \begin{align}
-% 	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \\
-% 	&=T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) \varsigma v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \label{eq:preswap}  \\
-% 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
-% 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\right],
-% \end{align}
-% where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.
-% % 
-% % Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
-% % \begin{align}
-% % 	middle term &= T_s \mathbf{E} \left[ \bar{y}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right) \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right) \, d\mathbf{r}''} \, d\mathbf{r}'} \right] \\
-% % 	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
-% % 	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
-% % \end{align}
-% % where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
-% 
-% The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
-% \begin{equation}
-% 	R_1(\boldsymbol{\tau}) = \xi R_{\bar{y}_{t},\bar{y}_{t}}(\boldsymbol{\tau}),
-% \end{equation}
-% which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$.
-% 
-% Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
-% \begin{equation}\label{eq:approx_xcorr}
-% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
-% \end{equation}
-% The autocorrelation of the noisy observations is
-% \begin{equation}\label{eq:autocorrelation_of_y}
-% 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2,
-% \end{equation}
-% where $\delta(\cdot)$ is the Kronecker delta function. Rearranging equation~\ref{eq:autocorrelation_of_y} and substituting it into equation~\ref{eq:approx_xcorr} gives
-% \begin{equation}
-% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],
-% \end{equation}
-% and
-% \begin{equation}\label{eq:support_estimator}
-% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) \approx T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
-% \end{equation}
-% The right hand side of equation~\ref{eq:support_estimator} will have the structure of the connectivity kernel. To show this let
-% \begin{align}
-% 	Z &= \mathcal{F}\left\{\bar{y}_t\left( \mathbf{r} + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r},\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right\} \\
-% 	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})\bar{Y}(\boldsymbol{\nu}) \ast W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \\
-% 	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \ast \bar{Y}(\boldsymbol{\nu}),
-% \end{align}
-% using the associativity with scalar multiplication property of convolution. Now taking the inverse Fourier transform
-% \begin{align}
-% 	z &= \mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \ast \bar{Y}(\boldsymbol{\nu})\right\} \\
-% 	&= w(\mathbf{r}+\boldsymbol{\tau}) \ast \bar{y}^2(\mathbf{r}) \\
-% 	&= \int_{\Omega}{w(\mathbf{r}+\boldsymbol{\tau},\mathbf{r}')\bar{y}^2(\mathbf{r}')d\mathbf{r}'}
-% \end{align}
-% 
-% 
-% This may hold:
-% \begin{equation}
-% 	R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) = \sigma_d \int_{\Omega}{ m(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}')\int_{\Omega}{ m(\mathbf{r}'_n-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''} d\mathbf{r}'}.
-% \end{equation}
-% If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.\\
-% the proof of the above\\
-% \begin{align}
-% 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
-% 		&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
-% 		&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\\
-% 		&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\label{eq:ObsCorr}
-% \end{align}
-
-% Therefore we can write
-% \begin{equation}
-% 	R_{v_{t},v_{t+1}}(\mathbf{\tau}) = \xi R_{v_{t},v_{t}}(\mathbf{\tau}) + T_s R_{v_{t},g_{t}}(\mathbf{\tau})
-% \end{equation}
-% and
-% \begin{equation}\label{eq:xcorr_firing_and_field}
-% 	T_s R_{v_{t},g_{t}}(\mathbf{\tau}) = R_{v_{t},v_{t+1}}(\mathbf{\tau})-\xi R_{v_{t},v_{t}}(\mathbf{\tau}).
-% \end{equation}
-% The spatial cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$ depends on the shape of the spatial mixing kernel $w\left( \mathbf{r},\mathbf{r}' \right)$.
-Furthermore, the sign (polarity) of $R_{v_{t},g_{t}}(\mathbf{\tau})$ will be the same as the $w\left( \mathbf{r},\mathbf{r}' \right)$ for a given spatial location since the sigmoid function $f\left( v_t\left( \mathbf{r}' \right) \right) > \mathbf{0}$.
-Therefore, the support of the kernel can be inferred given the cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$.
-The right hand side of equation~\ref{eq:xcorr_firing_and_field} can be calculated from data if $\xi$ is known.
-However, since $\xi$ is a decay parameter, we know that $\xi \in (0,1)$.
-Also, if we assume that
-% \begin{equation}
-% 	\xi R_{v_{t},v_{t}}(\mathbf{\tau}) \gg T_s R_{v_{t},g_{t}}(\mathbf{\tau})
-% \end{equation}
-% and
-% \begin{equation}
-% 	R_{v_{t},g_{t}}(\mathbf{0}) > 0,
-% \end{equation}
-% which corresponds to local excitation, then we can guess $\xi$ by incrementally increasing it from zero and evaluating equation~\ref{eq:xcorr_firing_and_field} until $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$.
-The value of $\xi$ before $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$ will provide the approximation.
 
@@
 As the theory presented earlier in Section~\ref{SpectralAnalysisSection} states, the observation kernel acts as a spatial filter.
-
 When the observation kernel is too narrow, high frequency components in the neural field are present but under sampled.
@@
 
-\mike{(Reviewer 2, comment 9:)A further extension of the framework is to allow for the algorithm to learn online.
+\mike{A further extension of the framework is to allow for the algorithm to learn online.
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-\parham{A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
+A filter that designed to be implemented in an online setting, can be used in place of the smoother.
+Doing this, while sacrificing accuracy, will increase the speed at which the state estimation can be done and decrease the amount of information that would need to be stored.
+Approaches for online state estimation include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \cite{Sato00,Cappe09} may be used.
+These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.
+Something something something estimator, something something something online, something something something complete...
+about updating parameters rather than finding brand new ones, recursive LS estimator \cite{Ljung1999},}
 
@@
 
-\parham{(Reviewer1, Additional comments 2:) The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
+The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
 Observability is assumed and then verified with the estimation results.
@@
 The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
-Therefore, the discretization preserved the stability properties of the system.}
+Therefore, the discretization preserved the stability properties of the system.
 

### 2011-01-12 ltx/first_order_framework/response_to_reviews.tex

@@
 
-		\emph{These results show that the system may not be identifiable in non-ideal, practical situations. Nevertheless, the net shape of the estimated kernels will be in accordance to actual data.}
+		\emph{These results show that the system may not be identifiable in non-ideal, practical situations.
+Nevertheless, the net shape of the estimated kernels will be in accordance to actual data.
+\parham{These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
+Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.}}
 
@@
 
-\emph{This point is clarified by adding the connectivity kernel components superimposed by the resulting Mexican Hat basis in Figure 1. of the manuscript.}
+\emph{This point is clarified by adding the connectivity kernel components superimposed by the resulting Mexican Hat basis in Figure 1.
+of the manuscript.
+\parham{It has also been clarified throughout the paper.}}
 

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex

@@
 \end{equation}
-\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the operator $\textrm{D}=d/dt + \zeta$.
+\parham{The post-synaptic membrane potential is in fact the temporal convolution between the synaptic kernel and the average firing rate
+\begin{equation}\label{FullConvolutionModel}
+ v\left(\mathbf r,t\right)= \left(h\ast g\right)\left(\mathbf r,t\right)
+\end{equation}
+where $\ast$ denotes the convolution operator.}
+\dean{(reviewer 2, comment 3:) \parham{To obtain (To arrive at)} the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
 A Green's function satisfies
@@
 This result demonstrates that the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
+\parham{(reviewer 1, additional comments 1:) These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
+Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.}
 
@@
 
-\mike{A further extension of the framework is to allow for the algorithm to learn online.
+\mike{(Reviewer 2, comment 9:)A further extension of the framework is to allow for the algorithm to learn online.
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-A filter that designed to be implemented in an online setting, can be used in place of the smoother.
-Doing this, while sacrificing accuracy, will increase the speed at which the state estimation can be done and decrease the amount of information that would need to be stored.
-Approaches for online state estimation include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \cite{Sato00,Cappe09} may be used.
-These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.
-Something something something estimator, something something something online, something something something complete...
-about updating parameters rather than finding brand new ones, recursive LS estimator \cite{Ljung1999},}
+\parham{A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
 
@@
 
-The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization.
-Observability is assumed and then verified with the estimation results.
-The stability of the discretized IDE is proven below.
+\parham{(Reviewer1, Additional comments 2:) The analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
+Here we only study the stability of the discretized model, we show that if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$,  the discretized IDE is stable.
 To do this, the model is written as the series
@@
 \end{equation}
-From this equation it can be seen that the system is stable if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$.
+From this equation it can be seen that if $0 < T_s < \tau$, the system is stable.
 The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
-Therefore, the discretization preserved the stability properties of the system.
+Therefore, the discretization preserved the stability properties of the system.}
 

### 2011-01-13 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edits-took out line on minimal assumptions
moved assumptions section as ken and parham suggested

@@
 
+\dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of the cortical dynamics recorded from a specific subject.
+Although models of this form are capable of describing a variety of cortical dynamics, there will be without doubt a mismatch between the cortex and the model.
+Nevertheless, there is a sufficient volume of interesting results from theoretical studies using the WC field equations that warrants the data assimilation framework.
+An advantage in using a lumped-parameter field model over a more detailed mathematical description is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into parameters (connectivity kernel coefficients) that effectively describe the net system gain.
+Therefore, there are less parameters to estimate.
+A major challenge in model-based data analysis for the mass action of the brain is to make models sufficiently detailed, such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
+
 \subsection{Integro-Difference Equation Neural Field Model}\label{IntegroDifferenceEquationSection} 
@@
 \subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
+\dean{The framework assumes that the parameters of the model (and brain) are stationary over the estimation period.
+This is a reasonable assumption when applying the framework to an evoked-potential experiment over a short time period in a controlled environment.}
+
 The estimation process is a two part iterative algorithm, consisting of a state estimation step followed by a parameter estimation step.
@@
 
-\subsection{Modeling Assumptions}
-\dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of the cortical dynamics recorded from the subject.
-Although models of this form are capable of describing a variety of cortical dynamics, there is without doubt a mismatch between the cortex and the model.
-Nevertheless, there is a sufficient volume of interesting results from theoretical studies using the WC field equations that warrants the data assimilation framework.
-}
-
-\dean{An advantage in using a lumped-parameter field model over a more detailed mathematical description is that the myriad of parameters that might influence excitability, such as specific ion concentrations, are considered to be lumped into the connectivity kernel coefficients that effectively describe the net system gain.
-In this way, a minimal number of assumptions are made.
-A major challenge in data assimilation for the mass action of the brain is to make models sufficiently detailed, such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
-
-\dean{The framework assumes that the parameters of the model (and brain) are stationary over the estimation period.
-This is a reasonable assumption when applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
-However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010}).
-Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
-A possible way to achieve this is to use a more sophisticated model that accounts for longer-term time dependancies (higher temporal order).
-Alternatively, the parameters of the model could be considered time-varying, where changes in excitability would result in different connectivity kernel parameters.}
-
- % A possible way to achieve this would be to employ window-based estimation or fixed-lag, where the estimation is performed on successive windows of data (possibly overlapping windows).
-The window length will need to be sufficiently short such that the parameters are approximately stationary of the estimation duration, and sufficiently long to achieve a good estimation result.
-If this trade-off can not be successfully achieved then the level of detail in the model must be increased.
-A real-time implementation can also be achieved using the UKF \parham{and an online recursive LS estimator (see \citet{Ljung1999} for example)}.
-}
-
 \subsection{Extensions to the Framework}
@@
 Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed.
-In addition, natural extensions of this framework are the inclusion of a post-synaptic response kernel with a finite rise and decay time, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.
-
-\mike{(Reviewer 2, comment 9:)A further extension of the framework is to allow for the algorithm to learn online.
+Other natural extensions of this framework are the inclusion of a post-synaptic response kernel with a finite rise and decay time, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.
+
+\dean{The assumption was made that the parameters of the model are stationary over the estimation period.
+However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010}).
+Therefore, the estimation framework must be altered, to account for time-varying parameters, if it is to be applied to data over extended periods of time.
+A possible way to achieve this is to use a more sophisticated model that accounts for longer-term time dependancies (higher temporal order).
+Alternatively, the parameters of the model could be considered time-varying, where changes in excitability would result in different connectivity kernel parameters.}
+
+\mike{(Reviewer 2, comment 9:) A further extension of the framework is to allow for the algorithm to learn online.
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-\parham{A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
+\parham{A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}.
+Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
 
@@
 \section{Time Discretization of the Neural Field Model}
-\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretization must be performed.
-To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by
+\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE) and provides a proof for the stability of the discrete-time equations.
+To perform the discretization, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by
 \begin{align}
@@
 
-\parham{(Reviewer1, Additional comments 2:) The analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
-Here we only study the stability of the discretized model, we show that if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$,  the discretized IDE is stable.
-To do this, the model is written as the series
+\parham{(Reviewer1, Additional comments 2:) If $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$, the IDE field model is stable. To show this, the model is written as the series
 \begin{align}
@@
 Since  $0 \leq f(v_t(\mathbf r)) \leq 1$ and the kernel is semi-compactly supported, $g_t(\mathbf r)$ is always bounded .
-To assess the stability of the discrete time system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$.
+To assess the stability of the system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$.
 Substituting this into equation~\ref{eq:fieldmodelseries} yields
@@
 To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity.
-Noting $0 < \xi <1$  we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
+Since $0 < \xi <1$  we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
 \begin{equation}\label{simplifiedvrecursiveinlimit}
@@
 Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
-\begin{equation}
-	v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta}.
-\end{equation}
+\begin{align}
+	v_{t+1}(\mathbf r) &= (1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta} \\
+	&= \left(1-\frac{T_s}{\tau}\right)^{t+1}v_0(\mathbf r) + \tau g_{max}
+\end{align}
 From this equation it can be seen that if $0 < T_s < \tau$, the system is stable.
 The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
-Therefore, the discretization preserved the stability properties of the system.}
+Therefore, the discretization preserved the stability properties of the system.
+Further analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
+}
 
@@
 \section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
-The derivation in this section was used for calculating the matrix $\mathbf \Gamma$ from equation~\ref{eq:DefGamma}. Consider two Gaussian basis functions
+The derivation in this appendix was used for calculating the matrix $\mathbf \Gamma$ from equation~\ref{eq:DefGamma}. Consider two Gaussian basis functions
 \begin{equation}\label{eq:n_dimensional_Gaussian1}

### 2011-01-13 ltx/first_order_framework/response_to_reviews.tex
minor comments

@@
 The mathematical formulation does not place any further restrictions on the form of the spatial mixing kernel.
-We have added statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}
+We have added statements to the methods section \parham{(after equation~13)} to be more explicit in describing subtleties of the method.}
 
@@
 In fact Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation (20)) of the manuscript would be the identity matrix.
-However, we have chosen Gaussian basis functions due to their semi-compact support.} %By choosing Gaussian basis functions the state-space representation of the model remains in its generic form which is also correct in the case of orthonormal basis functions.}
+However, we have chosen Gaussian basis functions due to their semi-compact support.
+\parham{A comment has been added for possible alternative basis functions under equation (23) of the manuscript.}}
 

### 2011-01-13 ltx/first_order_framework/response_to_reviews.tex
minor comments on response letter

@@
 	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
-Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion (Implications for Experimental Design).
+Amendments have been made to the Introduction (last paragraph), Method \parham{(after equation 9)}, and Discussion (Implications for Experimental Design).
 We have primarily developed the framework for higher density intracranial measurements.
@@
 
-		\emph{Amendments have been made to Appendix A, where the discretization is performed.
-We have commented on how the discrete-time system's properties may differ from the continuous-time system.
-In addition, we have provided a proof for the stability of the discrete-time system.}
+		\emph{\parham{Amendments have been made to Appendix A, where the discretization is performed.
+We have provided a proof for the stability of the discrete-time system.
+In addition,  We have added reference for the further analysis of the error introduced by Euler discretization method.}}
 
@@
 
-	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
+	\emph{\parham{To address this point, we have added an extra paragrapgh to 'Neural Field Model' section of the Methods.
+There we discuss model mismatch and what we think is a good way to deal with it.}}
 
@@
 \emph{Fourier basis functions would be a correct alternative to the case examined in this paper.
-In fact Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation (20)) of the manuscript would be the identity matrix.
+In fact Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ \parham{(defined in equation (20))} of the manuscript would be the identity matrix.
 However, we have chosen Gaussian basis functions due to their semi-compact support.
@@
 
-\item In equation 29, what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
+\item In equation 29 \parham{(now equation (35))}, what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
 I am concerned that it might be much higher than any of us wish to consider.
@@
 
-\item The two covariance inflation parameters in equation 41 make me cringe. How are we best to adjust these fudge factors?
+\item The two covariance inflation parameters in equation 41 (\parham{now equation (47)}) make me cringe. How are we best to adjust these fudge factors?
 
-\emph{Values for the two parameters in equation 41 along with the relevant references ,that describe the rationale for parameter choice, have been added to the manuscript.}
+\emph{Values for the two parameters in equation 41 \parham{(now equation (47))} along with the relevant references ,that describe the rationale for parameter choice, have been added to the manuscript.}
 

### 2011-01-13 ltx/first_order_framework/LaTeX_Manuscript.tex
editted the greenie bastard

@@
 \end{equation}
-\parham{The post-synaptic membrane potential is in fact the temporal convolution between the synaptic kernel and the average firing rate
-\begin{equation}\label{FullConvolutionModel}
- v\left(\mathbf r,t\right)= \left(h\ast g\right)\left(\mathbf r,t\right)
-\end{equation}
-where $\ast$ denotes the convolution operator.}
-\dean{(reviewer 2, comment 3:) \parham{To obtain (To arrive at)} the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
+To obtain (To arrive at) the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
 A Green's function satisfies
@@
 \end{equation} 
-where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ \parham{to equation~\ref{FullConvolutionModel}} gives
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ \parham{to equation~\ref{SpikesToPotential}} gives
 \begin{align}
@@
 \end{align}
-} This gives the standard form of the model
+This gives the standard form of the model
 \begin{equation}

### 2011-01-13 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edits to green shit

@@
 \end{equation}
-To obtain (To arrive at) the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
+To obtain the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$.
 A Green's function satisfies
@@
 \end{align}
-This gives the standard form of the model
+where $\ast$ denotes the convolution operator. This gives the standard form of the model
 \begin{equation}

### 2011-01-14 ltx/first_order_framework/response_to_reviews.tex
edits to the letter and paper

@@
 
-		\emph{These results show that the system may not be identifiable in non-ideal, practical situations.
-Nevertheless, the net shape of the estimated kernels will be in accordance to actual data.
-\parham{These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
-Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.}}
+		\emph{\parham{We have added to the results section describing experiment II: `These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
+Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.'}}
 
@@
 We have provided a proof for the stability of the discrete-time system.
-In addition,  We have added reference for the further analysis of the error introduced by Euler discretization method.}}
+We have also added a reference for the further analysis of the error introduced by Euler discretization method.}}
 
@@
 
-	\emph{\parham{To address this point, we have added an extra paragrapgh to 'Neural Field Model' section of the Methods.
-There we discuss model mismatch and what we think is a good way to deal with it.}}
+	\emph{\parham{The authors believe that allowing for time-varying parameters will account for changes in excitability levels.
+In future work, we will also estimate the disturbance properties (spatial covariance and temporal variance).
+To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters.
+In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}}
 
@@
 
-\dean{\emph{We have not added anything to the The authors do not have much to add to this comment.
-We feel that adding the disturbance to the firing rate is appropriate for this model, which is what we have done, and it agrees with the work by Benayoun et al PloS Comp Biol 2010.
-By the central limit theorem, we expect the disturbance to be Gaussian and due to the structural organization of the cortex, we expect the disturance to be spatially colored.
-In future work we plan to add to the framework and show how the disturbance properties can also be estimated from data.}}
+\dean{\emph{The results of Benayoun et al.
+provide evidence that the variance in a stochastic WC model will depend on the number of neurons that are modeled (in a stochastic network), where a larger network behaves more like the deterministic WC equations.
+This work encourages the use of the WC model for data-assimilation, but provides evidence that the disturbance properties should also be estimated.
+The authors believe that estimating the noise properties is possible, and we are planning to demonstrate how the achieve this in a subsequent paper.
+We have added some comments to the Extension to the Framework section in this regard.}}
 
@@
 
-\emph{The relationship to our basis function decomposition to Galerkin's projection has been added to the derivation of the state-space model. }
+\emph{We have added an extra step in the derivation of the state-space model to highlight the relationship to our basis function decomposition and Galerkin's projection.
+We have also added an extra Appendix to further explain the relationship.}
 
@@
 
-\emph{Fourier basis functions would be a correct alternative to the case examined in this paper.
-In fact Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ \parham{(defined in equation (20))} of the manuscript would be the identity matrix.
+\emph{Yes.
+Fourier basis functions would be a correct alternative to the case examined in this paper.
+In fact, a Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ \parham{(defined in equation (20))} of the manuscript would be the identity matrix.
 However, we have chosen Gaussian basis functions due to their semi-compact support.
@@
 
-\emph{Values for the two parameters in equation 41 \parham{(now equation (47))} along with the relevant references ,that describe the rationale for parameter choice, have been added to the manuscript.}
+\emph{Values for the two parameters in equation 41 \parham{(now equation (47))} along with the relevant references, that describe the rationale for parameter choice, have been added to the manuscript.}
 
@@
 \parham{It has also been clarified throughout the paper.}}
-
- \begin{figure*}[!ht]
- \begin{center}
- \includegraphics{./Graph/pdf/fig1.pdf} 
- \end{center}
- \caption{}
- \label{fig:Figure1}
- \end{figure*}
+ % 
+ % \begin{figure*}[!ht]
+ % \begin{center}
+ % \includegraphics{./Graph/pdf/fig1.pdf} 
+ % \end{center}
+ % \caption{}
+ % \label{fig:Figure1}
+ % \end{figure*}
 
@@
 
-\emph{Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to cycles/mm.}
+\emph{Yes. Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to cycles/mm.}
 

### 2011-01-14 ltx/first_order_framework/LaTeX_Manuscript.tex
another minor edit to green shit
edits to the letter and paper

@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient-specific modeling came from~\citet{Valdes1999}, where they fit the neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} to EEG data using the local linearization filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}.
+\dean{(Reviewer 1, additional comment d):) The first paper on patient-specific modeling (to the authors' best knowledge) came from~\citet{Valdes1999}, where they fit the neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} to EEG data using the local linearization filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}.
 This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}
@@
 \end{equation} 
-where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ \parham{to equation~\ref{SpikesToPotential}} gives
+where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ to equation~\ref{SpikesToPotential} gives
 \begin{align}
@@
 A possible way to achieve this is to use a more sophisticated model that accounts for longer-term time dependancies (higher temporal order).
-Alternatively, the parameters of the model could be considered time-varying, where changes in excitability would result in different connectivity kernel parameters.}
+Alternatively, the parameters of the model could be considered time-varying, where changes in excitability would result in different connectivity kernel parameters.
+Furthermore, the model may be considered heteroscedastic, where the disturbance is also time-varying.
+This is common in spatio-temporal econometric studies, where methods have been developed to test for heteroscedasticity~\citep{Anselin1988}.
+Following this, the disturbance properties of the system will also need to be estimated.
+A simple method to allow for time-varying parameters would be to perform a window-based or fixed-lag estimation, which would assume the parameters are quasi-stationary over the duration of the window.
+}
 
@@
 John Terry for insightful discussions and feedback.
-\dean{Finally, the authors would like to thanks the anonymous reviews who have provided an excellent critique that has led to valuable insights that would have gone otherwise astray.}
+\dean{Finally, the authors would like to thanks the anonymous reviews who have provided a critique that has led to valuable insights that would have gone otherwise astray.}
 

### 2011-01-14 ltx/first_order_framework/response_to_reviews.tex
very minor corrections

@@
 \begin{enumerate}
-    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 [The nonlinear IntegroDifference Equation]).
+    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 \parham{(now equation 12)} [The nonlinear IntegroDifference Equation]).
 I do very much appreciate the spectral estimation of spatial and temporal scales.
@@
 This work encourages the use of the WC model for data-assimilation, but provides evidence that the disturbance properties should also be estimated.
-The authors believe that estimating the noise properties is possible, and we are planning to demonstrate how the achieve this in a subsequent paper.
+The authors believe that estimating the noise properties is possible, and we are planning to demonstrate how to achieve this in a subsequent paper.
 We have added some comments to the Extension to the Framework section in this regard.}}

### 2011-01-14 ltx/first_order_framework/LaTeX_Manuscript.tex
comment on spatial frequency in discussion

@@
 
-\dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the electrode spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
+\dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the \parham{electrode} spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
 Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to humans with existing technology.}

### 2011-01-15 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edits to future work

@@
 \dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the \parham{electrode} spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
-Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to humans with existing technology.}
+Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to human data with existing technology.}
 
@@
 However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010}).
-Therefore, the estimation framework must be altered, to account for time-varying parameters, if it is to be applied to data over extended periods of time.
+Therefore, the estimation framework must be altered if it is to be applied to data over extended periods of time.
 A possible way to achieve this is to use a more sophisticated model that accounts for longer-term time dependancies (higher temporal order).
@@
 Following this, the disturbance properties of the system will also need to be estimated.
-A simple method to allow for time-varying parameters would be to perform a window-based or fixed-lag estimation, which would assume the parameters are quasi-stationary over the duration of the window.
+A simple approach allowing for time-varying parameters is to perform a window-based or fixed-lag estimation, which would require the assumption that the parameters are quasi-stationary over the duration of the window.
 }
@@
 The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
-\dean{A validation of the estimation framework on real data is now required.
-This is the subject of planned future work.}
+\dean{A validation of the estimation framework on real data is now required.}
 

### 2011-01-15 ltx/first_order_framework/response_to_reviews.tex
removed colors

@@
 
-\title{Response To Reviews - A Data-Driven Framework for Neural Field Modeling}
+\title{Responses - A Data-Driven Framework for Neural Field Modeling}
 \author{D. Freestone, P. Aram, M. Dewar, K. Scerri, D. Grayden, V. Kadirkamanathan}
@@
 
+    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help improve this paper.
+Please find below the authors responses to the reviewers questions and suggestions regarding the manuscript.
+\\
+
+Best Regards,
+\\
+
+Dean Freestone.
+
     \section{Reviewer 1}
-
-        We first address the reviewer's main concerns, followed by the reviewer's additional comments.
 
@@
 The mathematical formulation does not place any further restrictions on the form of the spatial mixing kernel.
-We have added statements to the methods section \parham{(after equation~13)} to be more explicit in describing subtleties of the method.}
+We have added statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}
 
@@
 	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
-Amendments have been made to the Introduction (last paragraph), Method \parham{(after equation 9)}, and Discussion (Implications for Experimental Design).
+Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion (Implications for Experimental Design).
 We have primarily developed the framework for higher density intracranial measurements.
@@
 
-		\emph{\parham{We have added to the results section describing experiment II: `These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
-Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.'}}
+		\emph{We have added to the results section describing experiment II: `These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
+Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.'}
 
@@
 
-		\emph{\parham{Amendments have been made to Appendix A, where the discretization is performed.
+		\emph{Amendments have been made to Appendix A, where the discretization is performed.
 We have provided a proof for the stability of the discrete-time system.
-We have also added a reference for the further analysis of the error introduced by Euler discretization method.}}
+We have also added a reference for the further analysis of the error introduced by Euler discretization method.}
 
@@
 
-    We thank the reviewer for their encouraging review. Each point raised is dealt with in turn.
-
 \begin{enumerate}
-    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 \parham{(now equation 12)} [The nonlinear IntegroDifference Equation]).
+    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 (now equation 12) [The nonlinear IntegroDifference Equation]).
 I do very much appreciate the spectral estimation of spatial and temporal scales.
@@
 
-	\emph{\parham{The authors believe that allowing for time-varying parameters will account for changes in excitability levels.
+	\emph{The authors believe that allowing for time-varying parameters will account for changes in excitability levels.
 In future work, we will also estimate the disturbance properties (spatial covariance and temporal variance).
 To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters.
-In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}}
+In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}
 
@@
 
-\dean{\emph{The results of Benayoun et al.
+\emph{The results of Benayoun et al.
 provide evidence that the variance in a stochastic WC model will depend on the number of neurons that are modeled (in a stochastic network), where a larger network behaves more like the deterministic WC equations.
@@
 The authors believe that estimating the noise properties is possible, and we are planning to demonstrate how to achieve this in a subsequent paper.
-We have added some comments to the Extension to the Framework section in this regard.}}
+We have added some comments to the Extension to the Framework section in this regard.}
 
@@
 Fourier basis functions would be a correct alternative to the case examined in this paper.
-In fact, a Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ \parham{(defined in equation (20))} of the manuscript would be the identity matrix.
+In fact, a Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation (20)) of the manuscript would be the identity matrix.
 However, we have chosen Gaussian basis functions due to their semi-compact support.
-\parham{A comment has been added for possible alternative basis functions under equation (23) of the manuscript.}}
+A comment has been added for possible alternative basis functions under equation (23) of the manuscript.}
 
-\item In equation 29 \parham{(now equation (35))}, what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
+\item In equation 29 (now equation (35)), what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
 I am concerned that it might be much higher than any of us wish to consider.
@@
 
-\item The two covariance inflation parameters in equation 41 (\parham{now equation (47)}) make me cringe. How are we best to adjust these fudge factors?
+\item The two covariance inflation parameters in equation 41 (now equation (47)) make me cringe. How are we best to adjust these fudge factors?
 
-\emph{Values for the two parameters in equation 41 \parham{(now equation (47))} along with the relevant references, that describe the rationale for parameter choice, have been added to the manuscript.}
+\emph{Values for the two parameters in equation 41 (now equation (47)) along with the relevant references, that describe the rationale for parameter choice, have been added to the manuscript.}
 
@@
 But many will be confused by this subtlety, and at times in the text the Mexican Hat basis is described as if it were a single function.
-I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.\\
+I would show how the theta's sum to create the general spatial basis shape of the hat in figure 1, and go through the paper in order to clarify this issue.
 
@@
 of the manuscript.
-\parham{It has also been clarified throughout the paper.}}
+It has also been clarified throughout the paper.}
  % 

### 2011-01-15 ltx/first_order_framework/LaTeX_Manuscript.tex
removed colors

@@
 % \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
-\newcommand{\dean}[1]{\textcolor{red}{#1}}
-\newcommand{\parham}[1]{\textcolor{blue}{#1}}
-\newcommand{\mike}[1]{\textcolor{Plum}{#1}}
+% \newcommand{\dean}[1]{\textcolor{red}{#1}}
+% \newcommand{\parham}[1]{\textcolor{blue}{#1}}
+% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
 
@@
 Recently, however, this task has been approached from a number of standpoints.
-\dean{(Reviewer 1, additional comment d):) The first paper on patient-specific modeling (to the authors' best knowledge) came from~\citet{Valdes1999}, where they fit the neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} to EEG data using the local linearization filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}.
-This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}
+The first paper on patient-specific modeling (to the authors' best knowledge) came from~\citet{Valdes1999}, where they fit the neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} to EEG data using the local linearization filter \citep{Ozaki1993,Ozaki1994,Ozaki2000}.
+This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.
 
@@
 
-\dean{(Reviewer 1, additional comment d):) Data-driven neural modeling was extended to the continuum approximation by \citet{Galka2008}, where they proposed an estimation framework based on a linear damped wave equation.
+Data-driven neural modeling was extended to the continuum approximation by \citet{Galka2008}, where they proposed an estimation framework based on a linear damped wave equation.
 Using a Kalman filter maximum likelihood framework, they improved on the low resolution electromagnetic tomography (LORETA) method for solving the inverse EEG problem.
 Another continuum neural field model-based estimator was developed by \citet{Daunizeau2009}, as an extension to the DCM framework.
-\parham{They argue that using a spatially extended continuum field model is superior for explaining cortical function than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.}}
-
-\dean{Another recent approach estimates the parameters of a modified WC neural field model using an unscented Kalman filter~\citep{schiff2008kalman}.
+They argue that using a spatially extended continuum field model is superior for explaining cortical function than the neural mass DCM, since field models can explain a richer repertoire of dynamics such as traveling waves and bump solutions.
+
+Another recent approach estimates the parameters of a modified WC neural field model using an unscented Kalman filter~\citep{schiff2008kalman}.
 This work takes a systems theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation and control on spatiotemporal neural fields.
 This marks the first step in what has the potential to revolutionize the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
-For other valuable contributions to data-driven neural modeling, see \citet{Nunez2000}, \citet{Jirsa2002}, and \citet{Robinson2004}.}
+For other valuable contributions to data-driven neural modeling, see \citet{Nunez2000}, \citet{Jirsa2002}, and \citet{Robinson2004}.
 
@@
 In this paper, we demonstrate for the first time how an intracortical connectivity kernel can be inferred from data, based on a variant of the \citet{Wilson1973} neural field model.
-This work provides a fundamental link between the theoretical advances in neural field modeling and \dean{(for reviewer 1, comment 3:) high resolution intracranial} electrophysiological data.
-\dean{(for reviewer 1 comment 1:) (this is copied from the abstract) To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison to be made between the estimated and true parameters.} The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
+This work provides a fundamental link between the theoretical advances in neural field modeling and high resolution intracranial electrophysiological data.
+To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison to be made between the estimated and true parameters.
+The paper proceeds by first describing the continuum neural field equations that are used as the cortical model.
 Then a finite-dimensional neural field model is derived.
@@
 
-\dean{(comment 1 and 9 from reviewer 2:) It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of the cortical dynamics recorded from a specific subject.
+It is an implicit assumption that the neural field model (in equation~\ref{DiscreteTimeModel}) provides an apt description of the cortical dynamics recorded from a specific subject.
 Although models of this form are capable of describing a variety of cortical dynamics, there will be without doubt a mismatch between the cortex and the model.
@@
 Therefore, there are less parameters to estimate.
-A major challenge in model-based data analysis for the mass action of the brain is to make models sufficiently detailed, such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).}
+A major challenge in model-based data analysis for the mass action of the brain is to make models sufficiently detailed, such that the parameters are meaningful, but simple enough to yield clear insights that can be related to theoretical studies (from both neuroscience and engineering perspectives).
 
@@
 where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=0,...,n_y-1$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
-\dean{(for reviewer 1, comment 3:) Since we are considering intracranial measurements recorded directly from the surface of the cortex or within the brain, the lead field is not modeled by the observation equation.}
+Since we are considering intracranial measurements recorded directly from the surface of the cortex or within the brain, the lead field is not modeled by the observation equation.
 
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-\dean{A graphical demonstration of the connectivity kernel decomposition is provided in Fig.~\ref{fig:Figure1}.} By exploiting the isotropy of the connectivity basis functions, they can be written as
+A graphical demonstration of the connectivity kernel decomposition is provided in Fig.~\ref{fig:Figure1}.
+By exploiting the isotropy of the connectivity basis functions, they can be written as
 $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
-\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
+Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented.
-Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.}
+Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.
 
 Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model.
-Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the right hand side} we get the approximation of the dynamic field
-% \begin{align}
-% 	\label{reduced continuous model}
-% 	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1} &= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
-% 	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}). 
-% \end{align}
+Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} to the right hand side we get the approximation of the dynamic field
 \begin{align}
@@
 \end{align}
-\dean{The solution of this equation for $\mathbf{x}_t$ is equivalent to finding a Galerkin projection, where the field basis functions would be considered the projection functions and the states would be the amplitude coefficients.
-See~\ref{App:Galerkin} for more information.}
-
+The solution of this equation for $\mathbf{x}_t$ is equivalent to finding a Galerkin projection, where the field basis functions would be considered the projection functions and the states would be the amplitude coefficients.
+See~\ref{App:Galerkin} for more information.
 In the next step of forming the state-space model we substitute the field decomposition into the left hand side of equation~\ref{eq:decompRHS} giving
@@
 The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}.
-\dean{Alternative field basis functions may be used to form the decomposition; if the basis is orthonormal, such as a Fourier basis, then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
+Alternative field basis functions may be used to form the decomposition; if the basis is orthonormal, such as a Fourier basis, then $\Gamma$ is simply the identity matrix.
+Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
 \begin{equation}
@@
 \end{equation}
-\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate the reduced model observation equation from the full model.} The observation equation is linear and can be written in the more compact form
+Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate the reduced model observation equation from the full model.
+The observation equation is linear and can be written in the more compact form
 \begin{equation}\label{ObservationEquation} 
@@
 where $\rho_y \in \mathbb{R} \ge 1$ is an oversampling parameter.
-\dean{(reviewer 1, additional comment 3:) A derivation of the sampling theorem that is based on \citet{Sanner1992} and \citet{Scerri2009} is provided in \ref{App:SamplingTheorem}}.
+A derivation of the sampling theorem that is based on \citet{Sanner1992} and \citet{Scerri2009} is provided in \ref{App:SamplingTheorem}.
 The condition in equation~\ref{eq:MinimumSensorDistance} must be satisfied to avoid spatial spectral aliasing effects when reconstructing the hidden dynamic field, $v_t(\mathbf{r})$, using the sampled observations, $\mathbf{y}_t$.
@@
 However, we envisage it may be possible to estimate the spatial bandwidth using other modalities with higher spatial resolution such as fMRI, NIRS or other optical imaging techniques (\cite{Issa2000}).
-\dean{(Reviewer 2, comment 6:) The expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm~\citep{Freeman2000}.}
+The expected bandwidth of the human neocortex is approximately 0.1-0.4 cycles/mm~\citep{Freeman2000}.
 
@@
 \subsection{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section, we describe the procedure for estimating the states, $\mathbf{x}_t$, the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic dynamics, $\xi$.
-\dean{The framework assumes that the parameters of the model (and brain) are stationary over the estimation period.
-This is a reasonable assumption when applying the framework to an evoked-potential experiment over a short time period in a controlled environment.}
+The framework assumes that the parameters of the model (and brain) are stationary over the estimation period.
+This is a reasonable assumption when applying the framework to an evoked-potential experiment over a short time period in a controlled environment.
 
@@
 \end{equation}
-\parham{(reviewer 2, comment 7:) The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, was set to $10^{-3}$.
+The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, was set to $10^{-3}$.
 It is typically set arbitrary small to minimise higher-order effects \citep{Haykin2001}.
-The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \citet{Julier2002a}.}
+The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \citet{Julier2002a}.
 
@@
 \end{align}
-where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ \dean{(for a Gaussian disturbance, $\beta$ should be set to 2 \parham{\citep{Haykin2001}})}.
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ (for a Gaussian disturbance, $\beta$ should be set to 2 \citep{Haykin2001}).
 Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
@@
 \end{small}
-Following this, the LS parameter estimates \parham{\citep{Ljung1999}}, $ \hat{\mathcal{W}}$, are
+Following this, the LS parameter estimates \citep{Ljung1999}, $ \hat{\mathcal{W}}$, are
 \begin{equation}
@@
 Fig.~\ref{fig:Figure3}(B) shows an example of data from the modeled sensors and Fig.~\ref{fig:Figure3}(C) shows the power spectral density (PSD) of the simulated time-series.
-%The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.
 
@@
 Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition.
-The cutoff frequency ($-3$~dB point) of the neural field is \parham{$\boldsymbol{\nu}_c \approx 0.24$~cycles/mm}.
+The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~cycles/mm.
 From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm.
@@
 The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A).
-The cutoff frequency is \parham{$\boldsymbol{\nu}_{cy} \approx 0.2$~cycles/mm} ($-3$~dB point).
+The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~cycles/mm ($-3$~dB point).
 The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors.
@@
 As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure.
-In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to \parham{$\boldsymbol{\nu}_{c\phi} = 0.12$~cycles/mm}.
+In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~cycles/mm.
 The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B).
@@
 This result demonstrates that the interpretation of the results should be based on the net shape of the estimated connectivity kernel and not on the estimated parameter values individually.
-\parham{(reviewer 1, additional comments 1:) These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
-Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.}
+These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
+Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.
 
@@
 As pointed out in numerous publications by Freeman and colleagues (see \citet{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics.
-Importantly, the spatial frequency analysis tools presented in this paper can be used to design \dean{(reviewer 1, item 3:) high density intracranial} electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
+Importantly, the spatial frequency analysis tools presented in this paper can be used to design high density intracranial electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial dynamics can be observed.
 In addition, the frequency analysis highlights the relationship between the width of the sensors and the information in the data.
@@
 
-\dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the \parham{electrode} spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
-Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to human data with existing technology.}
+The work of \citet{Freeman2000} provides direct evidence that the spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
+Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to human data with existing technology.
 
@@
 These methods provide a rigorous framework for determining the dimensionality of the system using inherent spatial properties of the field.
-\dean{It should be noted that Schiff and Sauer suggest the possibility of using a Galerkin projection, or similar decomposition that is used in this paper, to perform efficient estimation as a direction for future work.
-Indeed,} we have shown that this enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
+It should be noted that Schiff and Sauer suggest the possibility of using a Galerkin projection, or similar decomposition that is used in this paper, to perform efficient estimation as a direction for future work.
+Indeed, we have shown that this enables estimation of a larger field with a lower dimensional state vector than would be otherwise possible.
 
@@
 In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel.
-In future work, we plan to relax this assumption \dean{and show how the support of the connectivity kernel can also be inferred from data}.
+In future work, we plan to relax this assumption and show how the support of the connectivity kernel can also be inferred from data.
 In addition, we have assumed that the neural field is isotropic and homogeneous.
@@
 
-\dean{The assumption was made that the parameters of the model are stationary over the estimation period.
+The assumption was made that the parameters of the model are stationary over the estimation period.
 However, it is well known that factors that influence excitability are non-stationary over longer time periods (see \citet{Ullah2010}).
@@
 A simple approach allowing for time-varying parameters is to perform a window-based or fixed-lag estimation, which would require the assumption that the parameters are quasi-stationary over the duration of the window.
-}
-
-\mike{(Reviewer 2, comment 9:) A further extension of the framework is to allow for the algorithm to learn online.
+
+A further extension of the framework is to allow for the algorithm to learn online.
 The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-\parham{A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}.
-Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
+A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}.
+Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.
 
@@
 The major contribution of this framework is to formally bridge a gap between experimental and theoretical neuroscience in order to gain a better understanding of the mesoscopic dynamics of the brain.
-\dean{A validation of the estimation framework on real data is now required.}
+A validation of the estimation framework on real data is now required.
 
@@
 John Terry for insightful discussions and feedback.
-\dean{Finally, the authors would like to thanks the anonymous reviews who have provided a critique that has led to valuable insights that would have gone otherwise astray.}
+Finally, the authors would like to thank the anonymous reviews who have provided a critique that has led to valuable insights that would have gone otherwise astray.
 
@@
 	\hline
-	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & \parham{cycles/mm} \\
-	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{(cycles/mm)$^2$}\\
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
+	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
 	\hline
@@
 {\bf Figure 1.
-Mexican-hat connectivity kernel.} \parham{(reviewer 2, comment 8:) The kernel is a composite of three Gaussian basis functions (dashed lines), representing short-range excitation, mid-range inhibition and long-range excitation.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
+Mexican-hat connectivity kernel.} The kernel is a composite of three Gaussian basis functions (dashed lines), representing short-range excitation, mid-range inhibition and long-range excitation.
+The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape.
 The kernel decays asymptotically to zero.
@@
 
-\parham{(Reviewer1, Additional comments 2:) If $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$, the IDE field model is stable. To show this, the model is written as the series
+If $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$, the IDE field model is stable. To show this, the model is written as the series
 \begin{align}
@@
 Further analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
-}
 
@@
 \section{Equivalence to Galerkin's Projection}\label{App:Galerkin}
-\dean{To show how equation~\ref{eq:decompRHS} is equivalent to the Galerkin projection, we define the residual between the field and the decomposition as 
+To show how equation~\ref{eq:decompRHS} is equivalent to the Galerkin projection, we define the residual between the field and the decomposition as 
 \begin{align}\label{eq:BasisFunctionResidual}
@@
 The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation.
-}
 
@@
 \section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
-\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}, which provide conditions on distance between the sensors and the field basis functions.
+This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}, which provide conditions on distance between the sensors and the field basis functions.
 The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}.
@@
 where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The observations are described in matrix form by
-\parham{\begin{equation}
+\begin{equation}
 	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}).
-\end{equation}}
+\end{equation}
 The Fourier transform of $\mathbf{y}$ is
@@
 \end{equation}
-where $\rho \in \mathbb{R} \ge 1$.}
+where $\rho \in \mathbb{R} \ge 1$.
 

### 2011-01-16 ltx/first_order_framework/response_to_reviews.tex
corrected the equation numbers in the response letter

@@
 Fourier basis functions would be a correct alternative to the case examined in this paper.
-In fact, a Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation (20)) of the manuscript would be the identity matrix.
+In fact, a Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation 21) of the manuscript would be the identity matrix.
 However, we have chosen Gaussian basis functions due to their semi-compact support.
-A comment has been added for possible alternative basis functions under equation (23) of the manuscript.}
+A comment has been added for possible alternative basis functions under equation 22 of the manuscript.}
 
-\item In equation 29 (now equation (35)), what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
+\item In equation 29 (now equation 34), what would a reasonable $\boldsymbol{\nu}_c$ be for a real neuronal system (mammalian) given the number of neurons and scale of electrodes?
 I am concerned that it might be much higher than any of us wish to consider.
@@
 
-\item The two covariance inflation parameters in equation 41 (now equation (47)) make me cringe. How are we best to adjust these fudge factors?
+\item The two covariance inflation parameters in equation 41 (now equation 46) make me cringe. How are we best to adjust these fudge factors?
 
-\emph{Values for the two parameters in equation 41 (now equation (47)) along with the relevant references, that describe the rationale for parameter choice, have been added to the manuscript.}
+\emph{Values for the two parameters in equation 41 (now equation 46) along with the relevant references, that describe the rationale for parameter choice, have been added to the manuscript.}
 

### 2011-01-16 ltx/first_order_framework/response_to_reviews.tex
corrected the equation numbers in the response letter

@@
 The mathematical formulation does not place any further restrictions on the form of the spatial mixing kernel.
-We have added statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}
+We have added statements to the methods section (after equation~17) to be more explicit in describing subtleties of the method.}
 
@@
 	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework.
-Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion (Implications for Experimental Design).
+Amendments have been made to the Introduction (last paragraph), Method (after equation 13), and Discussion (Implications for Experimental Design).
 We have primarily developed the framework for higher density intracranial measurements.
@@
 
-        \item The derivation of Equations (30) and (31) and make them more transparent for the general audience.
+        \item The derivation of Equations (30) and (31) (now equations (35) and (36)) and make them more transparent for the general audience.
 

### 2011-01-16 ltx/first_order_framework/LaTeX_Manuscript.tex
added edits suggested by Parham to fix typos

@@
 The connectivity kernel is typically a ``Mexican hat'' or ``wizard hat'' function, which describes local excitation and surround inhibition.
-An example of the Mexican hat connectivity kernel used in this paper is shown in Fig.~\ref{fig:Figure1}.
+An example of the Mexican hat connectivity kernel, that is a weighted sum of Gaussians, used in this paper is shown in Fig.~\ref{fig:Figure1}.
 To demonstrate flexibility in the estimation algorithm and to model larger cortical regions, a third component of the kernel is introduced describing weak longer-range excitation.
@@
 \end{equation}
-where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=0,...,n_y-1$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$.
+where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=0,...,n_y-1$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$, where $\mathbf{I}$ is the identity matrix.
 Since we are considering intracranial measurements recorded directly from the surface of the cortex or within the brain, the lead field is not modeled by the observation equation.
@@
 where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters.
-A graphical demonstration of the connectivity kernel decomposition is provided in Fig.~\ref{fig:Figure1}.
+A graphical demonstration of the connectivity kernel decomposition and the net shape is provided in Fig.~\ref{fig:Figure1}.
 By exploiting the isotropy of the connectivity basis functions, they can be written as
@@
 The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
-The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm is given in Table~\ref{tab:UKFAlgorithm}.
+The cross-covariance matrix of the states, $\mathbf M$, is also required for computing the smoother gain, as described in the summary of the steps in the URTSS algorithm given in Table~\ref{tab:UKFAlgorithm}.
 
@@
 The work of \citet{Freeman2000} provides direct evidence that the spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm.
-Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to human data with existing technology.
+Micro-electrodes systems that satisfy this requirement are now currently in use for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to human data with existing technology.
 
@@
 John Terry for insightful discussions and feedback.
-Finally, the authors would like to thank the anonymous reviews who have provided a critique that has led to valuable insights that would have gone otherwise astray.
+Finally, the authors would like to thank the anonymous reviewers who have provided a critique that has led to valuable insights that would have gone otherwise astray.
 

### 2011-01-16 ltx/first_order_framework/response_to_reviews.tex
added edits suggested by Parham to fix typos
very minor correction in the response letter

@@
 
-    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help improve this paper.
+    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help to improve this paper.
 Please find below the authors responses to the reviewers questions and suggestions regarding the manuscript.
@@
 To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters.
+We have also added to the Estimation section, stating that we are assuming the parameters are stationary of the estimation period.
 In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}

### 2011-01-17 ltx/first_order_framework/response_to_reviews.tex
very minor correction in the response letter

@@
 Fourier basis functions would be a correct alternative to the case examined in this paper.
-In fact, a Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation 21) of the manuscript would be the identity matrix.
+In fact, Fourier basis functions or any other orthonormal basis functions would simplify the state-space representation of the model, since $\Gamma$ (defined in equation 21) of the manuscript would be the identity matrix.
 However, we have chosen Gaussian basis functions due to their semi-compact support.

### 2011-01-17 ltx/first_order_framework/response_to_reviews.tex
minor correction reviewer2 comment2 in response letter
minor edits

--- 2011-01-16 ltx/first_order_framework/response_to_reviews.tex
@@
 To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters.
-In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}
+We have also added to the Estimation section, stating that we are assuming the parameters are stationary of the estimation period.
+In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.
+Model better estimation harder.}
 

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
edits to letter with suggestion from VK and Parham

--- 2011-01-17 ltx/first_order_framework/response_to_reviews.tex
@@
 In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.
-Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation.
-We have also added that validating the framework on real data is noted as future work in the conclusion.}
+We plan to validate the framework on real data in future work.
+We have added that validating the framework on real data is required in the Conclusion.}
 
@@
 The mathematical formulation does not place any further restrictions on the form of the spatial mixing kernel.
+However, more complex shapes may require more basis functions, leading to more parameters.
 We have added statements to the methods section (after equation~17) to be more explicit in describing subtleties of the method.}
@@
 We have also added to the Estimation section, stating that we are assuming the parameters are stationary of the estimation period.
-In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}
+In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.
+Model better estimation harder.}
 
@@
 
+\emph{In all honesty, the authors are not 100\% sure on what the reviewer is asking for with a more palatable stochasticization.
+We have attempted to answer assuming the reviewer is after a sensible method for choosing the disturbance parameters.}
+
 \emph{The results of Benayoun et al.
 provide evidence that the variance in a stochastic WC model will depend on the number of neurons that are modeled (in a stochastic network), where a larger network behaves more like the deterministic WC equations.
-This work encourages the use of the WC model for data-assimilation, but provides evidence that the disturbance properties should also be estimated.
-The authors believe that estimating the noise properties is possible, and we are planning to demonstrate how to achieve this in a subsequent paper.
+This work encourages the use of the WC model with an additive disturbance for data-assimilation, but provides evidence that the disturbance properties should also be estimated.
+The authors believe that estimating the noise properties is possible within an EM framework, and we are planning to demonstrate how to achieve this in a subsequent paper.
 We have added some comments to the Extension to the Framework section in this regard.}

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
corrected equation C1 for Galerkein projection
edits to letter with suggestion from VK and Parham
edits to Euler appendix

@@
 
-% \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
-% \newcommand{\dean}[1]{\textcolor{red}{#1}}
-% \newcommand{\parham}[1]{\textcolor{blue}{#1}}
+\newcommand{\dean}[1]{\textcolor{red}{#1}}
+\newcommand{\parham}[1]{\textcolor{blue}{#1}}
 % \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
@@
 The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \citet{Julier2002a}.
+\dean{Parham to add something about the sensitivity of the parameters.}
 
@@
 These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
-Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.
+Nevertheless, the net shape of the connectivity kernel can be determined reasonably accurately.
 
@@
 
-If $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$, the IDE field model is stable. To show this, the model is written as the series
-\begin{align}
-	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
-	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
-	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \nonumber \\
-	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
-\end{align}
-where
-\begin{equation}
-	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
-\end{equation}
-Since  $0 \leq f(v_t(\mathbf r)) \leq 1$ and the kernel is semi-compactly supported, $g_t(\mathbf r)$ is always bounded .
+% If $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$, the IDE field model is stable. To show this, the model is written as the series
+% \begin{align}
+% 	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
+% 	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
+% 	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \nonumber \\
+% 	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
+% \end{align}
+% where
+% \begin{equation}
+% 	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
+% \end{equation}
+% Since  $0 \leq f(v_t(\mathbf r)) \leq 1$ and the kernel is semi-compactly supported, $g_t(\mathbf r)$ is always bounded .
 To assess the stability of the system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$.
 Substituting this into equation~\ref{eq:fieldmodelseries} yields
-\begin{align}\label{vrecursiveinlimit}
-	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ g_{max} T_s \sum_{i=0}^t \xi^i \nonumber \\
-	&=\xi^{t+1}v_0(\mathbf r) + \frac{ g_{max} T_s(1-\xi^{t+1})}{1-\xi}.
-\end{align}
-To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity.
+% \begin{align}\label{vrecursiveinlimit}
+% 	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ g_{max} T_s \sum_{i=0}^t \xi^i \nonumber \\
+% 	&=\xi^{t+1}v_0(\mathbf r) + \frac{ g_{max} T_s(1-\xi^{t+1})}{1-\xi}.
+% \end{align}
+% To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity.
 Since $0 < \xi <1$  we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
-\begin{equation}\label{simplifiedvrecursiveinlimit}
-	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{max} T_s}{1-\xi}.
-\end{equation}
-Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
-\begin{align}
-	v_{t+1}(\mathbf r) &= (1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta} \\
-	&= \left(1-\frac{T_s}{\tau}\right)^{t+1}v_0(\mathbf r) + \tau g_{max}
-\end{align}
-From this equation it can be seen that if $0 < T_s < \tau$, the system is stable.
+% \begin{equation}\label{simplifiedvrecursiveinlimit}
+% 	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{max} T_s}{1-\xi}.
+% \end{equation}
+% Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
+% \begin{align}
+% 	v_{t+1}(\mathbf r) &= (1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta} \\
+% 	&= \left(1-\frac{T_s}{\tau}\right)^{t+1}v_0(\mathbf r) + \tau g_{max}
+% \end{align}
+% From this equation it can be seen that if $0 < T_s < \tau$, the system is stable.
 The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$.
 Therefore, the discretization preserved the stability properties of the system.
-Further analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
+Note, the discretization using the first Euler method has the potential to affect the system's behaviour.
+If the sampling period is too large, the difference between the continuous and discrete-time systems can be substantial.
+The sampling period of 1~ms was used in this paper, which was sufficiently small to yield good estimation results.
+An analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
+An alternative to the Euler's method is the local linearization method, which may provide improved results~\citep{Ozaki1994}.
 
@@
 	&- T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
-	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
+	&- \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t - \mathbf{e}_t(\mathbf{r}).
 \end{align} 

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
added online algorithm to the extension

@@
 
+\parham{The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
 A further extension of the framework is to allow for the algorithm to learn online.
-The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}.
-Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.
+A filter which is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived.
+A simple real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator \cite{Ljung1999}.}
+
+%  A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}.
+
+% Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.
 

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
minor edit
small edit to online estimation discussion

@@
 Following this, the disturbance properties of the system will also need to be estimated.
-A simple approach allowing for time-varying parameters is to perform a window-based or fixed-lag estimation, which would require the assumption that the parameters are quasi-stationary over the duration of the window.
-
-\parham{The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
+A possible approach allowing for time-varying parameters is to perform a window-based or fixed-lag estimation, which would require the assumption that the parameters are quasi-stationary over the duration of the window.
+
+The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
 A further extension of the framework is to allow for the algorithm to learn online.
-A filter which is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived.
-A simple real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator \cite{Ljung1999}.}
+A filter that is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived.
+A real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator \cite{Ljung1999}.
 
@@
 If the sampling period is too large, the difference between the continuous and discrete-time systems can be substantial.
-The sampling period of 1~ms was used in this paper, which was sufficiently small to yield good estimation results.
+The sampling period of 1~ms was used in this paper, which was sufficiently small to yield stable discrete-time system and good estimation results.
 An analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
edits to response in AR error bit

@@
 		\emph{We have added to the results section describing experiment II: `These results indicate that the solution to the system may not be unique in non-ideal, practical situations.
-Nevertheless, the system is identifiable in terms of the net shape of the estimated kernel.'}
+Nevertheless, the net shape of the connectivity kernel can be determined reasonably accurately.'}
 
@@
 
-	\emph{The authors believe that allowing for time-varying parameters will account for changes in excitability levels.
-In future work, we will also estimate the disturbance properties (spatial covariance and temporal variance).
+	\emph{A more sophisticated model for the error will provide a more realistic description of the cortical dynamics.
+However, this will increase the number of parameters making the estimation problem more difficult.
+Furthermore, the authors believe that is a benefit staying as close as possible to the classic WC equations, so future results can be compared to theoretical studies.
+A preferable alternative to an AR error term is to allow for time-varying parameters to account for changes in excitability levels.
+In future work, we also hope estimate the disturbance properties (spatial covariance and temporal variance).
 To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters.
 We have also added to the Estimation section, stating that we are assuming the parameters are stationary of the estimation period.
-In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.
-Model better estimation harder.}
+In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}
 

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
changed one of the references

@@
 
-\emph{A few comments have been added to the `Extensions to the Framework' section of the discussion.}
+\emph{A few comments have been added to the `Extensions to the Framework' section of the discussion:\\\\ 'The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
+A further extension of the framework is to allow for the algorithm to learn online.
+A filter that is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived.
+A real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator Ljung (1999).'}
 

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to response in AR error bit
edit the discretization appendix

@@
 Therefore, the discretization preserved the stability properties of the system.
-Note, the discretization using the first Euler method has the potential to affect the system's behaviour.
-If the sampling period is too large, the difference between the continuous and discrete-time systems can be substantial.
-The sampling period of 1~ms was used in this paper, which was sufficiently small to yield stable discrete-time system and good estimation results.
-An analysis of the error introduced by Euler discretization method can be found in \citet{Butcher2008}.
-An alternative to the Euler's method is the local linearization method, which may provide improved results~\citep{Ozaki1994}.
+
+Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can be substantial.
+The Euler method was used for its simplicity.
+The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results.
+An analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}.
+An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.
 

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed a couple of typos

@@
 
-Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can be substantial.
+Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial.
 The Euler method was used for its simplicity.

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex

@@
 
-\emph{In all honesty, the authors are not 100\% sure on what the reviewer is asking for with a more palatable stochasticization.
-We have attempted to answer assuming the reviewer is after a sensible method for choosing the disturbance parameters.}
+\emph{We have attempted to answer this assuming the reviewer is after a sensible method for choosing the disturbance parameters.}
 
@@
 provide evidence that the variance in a stochastic WC model will depend on the number of neurons that are modeled (in a stochastic network), where a larger network behaves more like the deterministic WC equations.
-This work encourages the use of the WC model with an additive disturbance for data-assimilation, but provides evidence that the disturbance properties should also be estimated.
-The authors believe that estimating the noise properties is possible within an EM framework, and we are planning to demonstrate how to achieve this in a subsequent paper.
+This work encourages the use of the WC model with an additive disturbance for data-assimilation, but suggests that the disturbance properties should also be estimated.
+The authors believe that estimating the noise properties is possible within an EM framework, and we are planning to demonstrate how to achieve this in our future work.
 We have added some comments to the Extension to the Framework section in this regard.}

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
minor changes

@@
 
-\emph{A few comments have been added to the `Extensions to the Framework' section of the discussion:\\\\ 'The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected.
-A further extension of the framework is to allow for the algorithm to learn online.
-A filter that is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived.
-A real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator Ljung (1999).'}
+\emph{A few comments have been added to the last paragraph of the `Extensions to the Framework' section of the discussion.}
 

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
got rid of colour in the filter
minor changes

@@
 The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \citet{Julier2002a}.
-\dean{Parham to add something about the sensitivity of the parameters.}
 
@@
 A further extension of the framework is to allow for the algorithm to learn online.
-A filter that is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived.
+A filter that is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameters after a new observation arrived.
 A real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator \cite{Ljung1999}.

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
changed the euler method

@@
 
-		\emph{Amendments have been made to Appendix A, where the discretization is performed.
-We have provided a proof for the stability of the discrete-time system.
-We have also added a reference for the further analysis of the error introduced by Euler discretization method.}
+		\emph{We have added some comments to  Appendix A, where the discretization is performed.
+We have also added a reference for the further analysis of the error introduced by Euler discretization method along with a reference for an alternative method.}
 

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
very minor correcion to the openning of the response letter
minor change for reviewer2 comment11

@@
 
-    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help to improve this paper.
+    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help improve this paper.
 Please find below the authors responses to the reviewers questions and suggestions regarding the manuscript.
@@
 
-\item Page 45, Appendix D, Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.
+\item Page 45, Appendix D (now Appendix E), Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.
 

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
minor change for reviewer2 comment11

@@
 
-Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial.
+Note, the discretization using the first order Euler method has the potential to affect the system's behaviour in terms of both stability and consistency, an analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}.
+The Euler method was used for its simplicity.
+The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results.
+An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.
+
+% Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial.
 The Euler method was used for its simplicity.

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
moved the transpose definition to the first place where it is introduced
minor correction

@@
 \end{equation}
-where $\sigma_m$ sets the kernel width.
+where $\sigma_m$ sets the kernel width. The superscript $\top$ denotes the transpose operator.
 
@@
 \end{equation}
-where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$.
-The superscript $\top$ denotes the transpose operator.
-The field basis functions are described by
+where $\mathbf{x}_t$ is the state vector that scales the field basis functions $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$. The field basis functions are described by
 \begin{equation}\label{eq:FieldBasisFunction}
@@
 $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
-Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$.
+Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\boldsymbol{\theta}$.
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented.

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
correction to Appendix A

--- 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
@@
 
-Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial.
-The Euler method was used for its simplicity.
-The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results.
+Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be significant.
+The sampling period of 1~ms was used in this paper which is ten times smaller than the synaptic time constant, therefore the discrepancy between the continuous and its discrete approximation is small.
+This yielded a stable discrete-time system and good estimation results.
 An analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}.

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edit the app A

@@
 \section{Time Discretization of the Neural Field Model}
-\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE) and provides a proof for the stability of the discrete-time equations.
+\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE).
 To perform the discretization, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex
edits with parham

@@
 
-	\emph{The examples presented in the paper use the Mexican hat connectivity kernel.
+	\emph{Most examples presented in the paper use the Mexican hat connectivity kernel.
 The framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
@@
 
-		\emph{We have added some comments to  Appendix A, where the discretization is performed.
-We have also added a reference for the further analysis of the error introduced by Euler discretization method along with a reference for an alternative method.}
+		\emph{We have added some comments to  Appendix A, where the discretization is performed.}
 
@@
 In future work, we also hope estimate the disturbance properties (spatial covariance and temporal variance).
-To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters.
+To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions.
 We have also added to the Estimation section, stating that we are assuming the parameters are stationary of the estimation period.

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edits with parham

@@
 $\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
-Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\boldsymbol{\theta}$.
+Note, that although most examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\boldsymbol{\theta}$.
 The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented.
@@
 
-{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording yy and the twisted bipolar current source.
+{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah array recording electrode and the twisted bipolar current source.
 

### 2011-01-20 ltx/first_order_framework/response_to_reviews.tex
editted xcorr analysis

@@
 However, this will increase the number of parameters making the estimation problem more difficult.
-Furthermore, the authors believe that is a benefit staying as close as possible to the classic WC equations, so future results can be compared to theoretical studies.
+Furthermore, the authors believe that there is a benefit staying as close as possible to the classic WC equations, so future results can be compared to theoretical studies.
 A preferable alternative to an AR error term is to allow for time-varying parameters to account for changes in excitability levels.

### 2011-02-06 ltx/data_paper/DataPaper.tex
added abit to estimation algorithm

@@
 \section{Estimation Algorithm}
-
+Here we describe the problem of estimating non-linear state-space neural field model using the expectation-maximisation (EM) technique.
+The resulting process is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
 \subsection{E-Step}
@@
 \subsection{M-Step}
-
-\subsection{$\mathcal Q$-function}
 The goal of the M-step is to maximise the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol\Sigma_{\epsilon}$, $\boldsymbol \theta$ and $\xi$.
@@
  \renewcommand{\arraystretch}{1}
-
+\newpage
 \bibliographystyle{plain}

### 2011-02-06 ltx/data_paper/DataPaper.tex
added abit to estimation algorithm

@@
 Here we describe the problem of estimating non-linear state-space neural field model using the expectation-maximisation (EM) technique.
-The resulting process is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
+The resulting estimation process is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
+At each iteration we maximise an approximate lower bound on the log likelihood function.
+The approximate lower bound can be computed by taking the first-order truncated Taylor-series expansion of the non-linear component around the smoothed state estimate at each time instant.
 \subsection{E-Step}

### 2011-02-06 ltx/data_paper/DataPaper.tex
added abit to estimation algorithm

@@
 The resulting estimation process is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
-At each iteration we maximise an approximate lower bound on the log likelihood function.
+In the E-step we estimate the states $\mathbf x_t$, of the systems and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+Using the state estimates at each iteration we maximise an approximate lower bound on the log likelihood function.
 The approximate lower bound can be computed by taking the first-order truncated Taylor-series expansion of the non-linear component around the smoothed state estimate at each time instant.

### 2011-02-06 ltx/data_paper/DataPaper.tex
added sumway to the citation

@@
 \section{Estimation Algorithm}
-Here we describe the problem of estimating non-linear state-space neural field model using the expectation-maximisation (EM) technique.
+Here we describe the problem of estimating non-linear state-space neural field model using the expectation-maximisation (EM) technique \cite{Shumway2000}.
 The resulting estimation process is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.

### 2011-02-06 ltx/data_paper/DataPaper.tex
corrected table cross referencing
edits to E step

@@
 \subsection{E-Step}
-The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
-The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
+In the E-step the additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+The URTSS incorporates an unscented Kalman filter (UKF) \cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
 The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation.
-An additional step is required in the $\mathbf E$-step to calculate the cross-covariance matrix $\mathbf M_{t+1}=\textrm{cov}(\mathbf x_t,\mathbf x_{t+1})$.
+The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
+\begin{align}\label{eq:sigmapoints1}
+	\mathcal X_{0}&=\mathbf{\bar x} \\
+	\mathcal X_{i}&= \mathbf{\bar x}+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
+	\mathcal X_{i}&=\mathbf{\bar x}-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
+\end{align}
+where $\mathbf{\bar x}$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space.
+The total number of sigma points is $2n_x+1$.
+The scaling parameter, $\lambda$, is defined as
+\begin{equation}\label{eq:sigmapoints3}
+	\lambda=\alpha^2( n_x+\kappa) - n_x, 
+\end{equation}
+The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, was set to $10^{-3}$.
+It is typically set arbitrary small to minimise higher-order effects \cite{Haykin2001}.
+The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \cite{Julier2002a}.
+
+The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
+\begin{align}
+	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
+	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
+	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
+\end{align}
+where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ (for a Gaussian disturbance, $\beta$ should be set to 2 \cite{Haykin2001}).
+Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states.
+The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above.
+The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required.
+The former is used  for computing the smoother gain and the latter is used to compute required terms in the M-step.
+The formulation of the cross-covariance matrices are also given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
 An additional element to the URTSS algorithm was also created to approximate $q(\mathbf{x}_t)$, which is required for the M-step.
-
-This is accomplished by taking the first-order truncated Taylor-series expansion of $q(\mathbf x_t)$ around the mean of the state at each time instant for the sigmoidal activation function, i.e.
+This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^{b}$ at each time instant, i.e.
 \begin{equation}\label{eq:SigmoidTaylor}
- f(\boldsymbol \phi^\top(\mathbf r')\mathbf x_t) \approx f(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)+  \boldsymbol \phi^\top(\mathbf r')(\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t)
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^{b}\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^{b}\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)
 \end{equation}
@@
 \begin{equation}\label{eq:SigmoidDerivative}
- f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)=\varsigma f(\boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)\left( 1-f( \boldsymbol \phi^\top(\mathbf r')\mathbf {x}_t)\right)
+ f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)\right)
 \end{equation}
@@
 \begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t) \approx q(\mathbf {\hat x}_t)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'
+ q(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t^{b}\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^{b}\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right) d\mathbf{r}'
 \end{equation}
-
-The algorithm for the modified URTSS can be seen in Table~\ref{tab:URTSSAlgorithm}.
 
@@
 \bf{Algorithm for the Unscented RTS Smoother}}
+\label{tab:URTSSAlgorithm}
 \begin{tabular}{|c|}\hline

### 2011-02-06 ltx/data_paper/DataPaper.tex
edits to E step

@@
 The former is used  for computing the smoother gain and the latter is used to compute required terms in the M-step.
-The formulation of the cross-covariance matrices are also given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
-An additional element to the URTSS algorithm was also created to approximate $q(\mathbf{x}_t)$, which is required for the M-step.
+The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
+
+Since the state equation is non-linear,  calculation of covariance and  cross-covariance terms required for the maximisation step is not straightforward as in the linear case.
+Therefore, an additional element to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$, which is required in the M-step.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^{b}$ at each time instant, i.e.
@@
 \end{equation}
+Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
 

### 2011-02-06 ltx/data_paper/DataPaper.tex
edits to E step

@@
 Since the state equation is non-linear,  calculation of covariance and  cross-covariance terms required for the maximisation step is not straightforward as in the linear case.
-Therefore, an additional element to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$, which is required in the M-step.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$, which is required in the M-step.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^{b}$ at each time instant, i.e.
@@
 \end{eqnarray}
-Substituting \ref{eq:qTaylor} in \ref{eq:Qfunctionintrace} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, Substituting \ref{eq:qTaylor} in \ref{eq:Qfunctionintrace} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
 Therefore $\mathcal Q$-function can be approximated as

### 2011-02-06 ltx/data_paper/DataPaper.tex
edits to E step

@@
 \end{itemize}
-The aim of this paper is to great a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.
+The aim of this paper is to create a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.
 
@@
 Since the state equation is non-linear,  calculation of covariance and  cross-covariance terms required for the maximisation step is not straightforward as in the linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$, which is required in the M-step.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is required in the M-step.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^{b}$ at each time instant, i.e.

### 2011-02-07 ltx/data_paper/DataPaper.tex
edits to E step

@@
 The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required.
-The former is used  for computing the smoother gain and the latter is used to compute required terms in the M-step.
+The former is used  for computing the smoother gain and the latter is used to compute required expected values in the M-step.
 The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
@@
 Since the state equation is non-linear,  calculation of covariance and  cross-covariance terms required for the maximisation step is not straightforward as in the linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is required in the M-step.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the M-step.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^{b}$ at each time instant, i.e.

### 2011-02-07 ltx/data_paper/DataPaper.tex
edits to estimation algorithm
edits to M step

@@
 \section{Estimation Algorithm}
-Here we describe the problem of estimating non-linear state-space neural field model using the expectation-maximisation (EM) technique \cite{Shumway2000}.
-The resulting estimation process is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
+Here we describe the problem of estimating non-linear state-space neural field model using expectation-maximisation (EM) based algorithm \cite{Shumway2000}.
+The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters.
 In the E-step we estimate the states $\mathbf x_t$, of the systems and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
-Using the state estimates at each iteration we maximise an approximate lower bound on the log likelihood function.
-The approximate lower bound can be computed by taking the first-order truncated Taylor-series expansion of the non-linear component around the smoothed state estimate at each time instant.
+Once initialized, at each iteration the sequence of smoothed state vectors is used to update the parameters by maximizing an approximate lower bound on the log likelihood function.
+The resulting parameters are then used when estimating the new
+state vector sequence for the next iteration. The procedure stops when the parameter estimates converge.
 \subsection{E-Step}
@@
 \end{equation}
-substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ as
+substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the smoothed estimate $\hat{\mathbf{x}}_t^b$ 
 \begin{equation}\label{eq:qTaylor}
@@
 \subsection{M-Step}
-The goal of the M-step is to maximise the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol\Sigma_{\epsilon}$, $\boldsymbol \theta$ and $\xi$.
-Unfortunately, it is often not possible to maximise the likelihood $p(\mathbf Y;\boldsymbol\Theta)$ directly.
-However, by using the relationship between $p(\mathbf Y;\boldsymbol \Theta)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.
-
-Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ we have
+The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+We choose to maximize  $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
+Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}.
+We proceed by expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$
 \begin{equation}\label{eq:jointdistribution}
- p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)p(\mathbf x_0).
+ p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \sigma_d)p(\mathbf x_0).
 \end{equation}
-The $\mathcal Q$-function, or lower-bound on the likelihood, can be written in terms of joint distribution components as
+The  lower-bound on the joint likelihood function is defined as   
 \begin{align}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right] \\
-&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right],
 \end{align}
-where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ where $\boldsymbol \Theta'$ is the current parameter estimate.
+where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ where $\boldsymbol \Theta'$ is the current parameter estimate.
+Re-writing $\mathcal Q$-function in terms of joint distribution components gives
+\begin{align}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
+\end{align}
  It should be noted that

### 2011-02-07 ltx/data_paper/DataPaper.tex
edits to M step

@@
 The  lower-bound on the joint likelihood function is defined as   
-\begin{align}
+\begin{align}\label{eq:QFunction}
  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right],
 \end{align}
-where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ where $\boldsymbol \Theta'$ is the current parameter estimate.
-Re-writing $\mathcal Q$-function in terms of joint distribution components gives
+where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta')$, and $\boldsymbol \Theta'$ is the current parameter estimates.
+Substituting  \ref{eq:jointdistribution} in \ref{eq:QFunction} gives
 \begin{align}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
 \end{align}
  It should be noted that
- $p(\mathbf x_0)$ is not function of parameter set and therefore $\mathcal Q$-function can be rewritten as
+ $p(\mathbf x_0)$ is not a function of parameter set and therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}
-\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\xi)\right]+\mathrm{const}
+\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)\right]+\mathrm{const}
 \end{equation}

### 2011-02-07 ltx/data_paper/DataPaper.tex
edits to M step

@@
 \end{align}
- It should be noted that
- $p(\mathbf x_0)$ is not a function of parameter set and therefore $\mathcal Q$-function can be rewritten as
-\begin{equation}
-\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)\right]+\mathrm{const}
+ It should be noted that the last term is not a function of parameter set and can be ignored therefore $\mathcal Q$-function can be rewritten as
+\begin{equation}\label{eq:QIntermsofJointDist}
+\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)\right].
 \end{equation}
-the constant term can be ignored since it is not affecting the derivative with respect to the parameters.
-Under the Gaussian assumption and ignoring constant normalising terms, the joint distribution at $t+1$ can be written as
-\begin{eqnarray}
- p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}} \times  e^{-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) } \nonumber \\
-&+& e^{-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
-\end{eqnarray}
-by expanding the exponent and taking $2\log$ we get
-\begin{eqnarray}\label{eq:Qfunction}
-2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)&=&-\ln \mid\boldsymbol\Sigma_{\epsilon}\mid- (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\nonumber \\
-&-&\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t\nonumber \\
-&-&\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.
-\end{eqnarray}
-Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
-\begin{eqnarray}\label{eq:Qfunctionintrace}
-  \ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& -\ln \mid\boldsymbol\Sigma_{\epsilon}\mid-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace   \nonumber \\
-&-&\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
-\end{eqnarray}
+Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions
+\begin{align}
+ p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}} \times  e^{-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) } \\
+p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \times e^{-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
+\end{align}
+We ignored constant terms in the normalising factor of these conditional distributions. By expanding the exponent and taking $2\log$ we get
+\begin{align}\label{eq:CondititionDist1}
+2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right]  \\
+2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
+&-\frac{1}{\sigma_e^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t.
+\label{eq:CondititionDist2}
+\end{align}
+Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
+Substituting equations \ref{eq:CondititionDist1} and \ref{eq:CondititionDist2} into \ref{eq:QIntermsofJointDist} and taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\begin{align}\label{eq:Qfunctiontrace}
+  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace    \\
+ 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
+&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
+\end{align}
 Having approximated $q\left(\mathbf x_t\right)$ in the E-step, Substituting \ref{eq:qTaylor} in \ref{eq:Qfunctionintrace} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.

### 2011-02-07 ltx/data_paper/DataPaper.tex
edits to M step

@@
 Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
-Substituting equations \ref{eq:CondititionDist1} and \ref{eq:CondititionDist2} into \ref{eq:QIntermsofJointDist} and taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
-\begin{align}\label{eq:Qfunctiontrace}
+Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\begin{align}\label{eq:Qfunctiontrace1}
   2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace    \\
- 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}q( \mathbf x_t)\boldsymbol\theta+2\xi \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace.
+ 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_s^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace.
+\label{eq:Qfunctiontrace2}
 \end{align}
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, Substituting \ref{eq:qTaylor} in \ref{eq:Qfunctionintrace} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
+Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma_e}\mid $ as it is not a function of the parameter set.
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
 Therefore $\mathcal Q$-function can be approximated as
 \begin{eqnarray}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)\ln \mid\boldsymbol\Sigma_{\epsilon}\mid-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&+&\beta+2\Xi_0\boldsymbol\theta+
-2\xi \mathrm{tr}\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace \nonumber \\
-&-&\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-2\xi \Xi_3 \boldsymbol\theta - \xi^2 \mathrm{tr} \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace 
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)n_y\ln \sigma_{\epsilon}^2-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-&(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi'_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +2\frac{1}{\sigma_d^2}\Xi_0\boldsymbol\theta+
+\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-&\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_3 \boldsymbol\theta -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_4\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
 \end{eqnarray}
@@
 \begin{align}
-	\beta &= \sum_{t=0}^{T-1}\mathbf E_{\Theta'}\left[-\mathbf x_{t+1}^\top\boldsymbol\Sigma_e^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\
-\Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+	\Xi'_0&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:def of Xi'0} \\
+\Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
 \Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
-\Xi_2&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
- \Xi_3&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_2&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+ \Xi_3&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
  \Xi_4&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
@@
 	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \\
-	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\\
+	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\tilde{\boldsymbol\Sigma}_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\\
 	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \\

### 2011-02-11 ltx/data_paper/DataPaper.tex
edits to M step
edits to supp for Xi variables
check updates

@@
 \begin{equation}\label{eq:SigmoidTaylor}
- f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^{b}\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^{b}\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)
 \end{equation}
@@
 \begin{equation}\label{eq:SigmoidDerivative}
- f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right)\right)
+ f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\right)
 \end{equation}
@@
 \begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t^{b}\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^{b}\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^{b}\right) d\mathbf{r}'
+ q(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
 \end{equation}
@@
 \begin{eqnarray}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)n_y\ln \sigma_{\epsilon}^2-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-&(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi'_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +2\frac{1}{\sigma_d^2}\Xi_0\boldsymbol\theta+
-\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
-&-&\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_2\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_3 \boldsymbol\theta -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_4\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-&(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+2\frac{1}{\sigma_d^2}\Xi_{2}\boldsymbol\theta
+ \nonumber \\
+&-&\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_{3}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_{4} \boldsymbol\theta -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_{5}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
 \end{eqnarray}
@@
 \begin{align}
-	\Xi'_0&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:def of Xi'0} \\
-\Xi_0&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
-\Xi_2&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
- \Xi_3&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
- \Xi_4&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
+	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0} \\
+\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1} \\
+\Xi_{2}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_{3}&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+ \Xi_{4}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+ \Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
 \end{align}
@@
 \begin{align}
-	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \\
-	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\tilde{\boldsymbol\Sigma}_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\\
-	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \\
-	 \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
+	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambda}\\
+	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\tilde{\boldsymbol\Sigma}_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\label{eq:lambdai}\\
+	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambdatilde}\\
+	 \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r' \label{eq:lambdatildei}
 \end{align}
-It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_t \mathbf{\hat{x}}_t^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right] $.
+It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right] $.
 Given the state estimates, $\mathbf {\hat x^{b}}_t$ the state covariance $\mathbf P_t^b$ and cross-covariance $\mathbf M_t^b$ , the $\Xi$-variables can be computed directly.
+In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
 
-When taking the derivative of equation~\ref{eq:Voldermont}, the constant $\beta$ described in equation~\ref{eq:def of beta} will disappear. Differntiating with respect to $\boldsymbol\theta$ we have
+In order to find the maximum of the $\mathcal{Q}$-function Differntiating with respect to $\boldsymbol\theta$ we have
 \begin{equation}\label{eq:Qpartialtheta}

### 2011-02-11 ltx/data_paper/DataPaper.tex
edits to maximization

@@
 
-In order to find the maximum of the $\mathcal{Q}$-function Differntiating with respect to $\boldsymbol\theta$ we have
+Consider first the maximization of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
 \begin{equation}\label{eq:Qpartialtheta}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=2\Xi_0-\boldsymbol\theta^\top(\Xi_2^\top+\Xi_2)-2\xi\Xi_3
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_2-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_3^\top+\Xi_3)-\frac{2\xi}{\sigma_d^2}\Xi_4
 \end{equation}
-noting that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
+noting that $\Xi_3$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
 \begin{equation}\label{eq:theta}
- \boldsymbol \theta=\Xi_2^{-1}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
+ \boldsymbol \theta=\Xi_3^{-1}\left(\Xi_2^\top-\xi\Xi_4^\top \right).
 \end{equation}
-similarly differentiating with respect to $\xi$ we have
-\begin{equation}\label{eq:Qpartialxi}
- \frac{\partial \mathcal Q}{\partial \xi}=2tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace -2 \Xi_3 \boldsymbol\theta - 2\xi tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace
-\end{equation}
-substituting \ref{eq:theta} in \ref{eq:Qpartialxi} and equating to zero we get
+The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
+Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
 \begin{equation}
- \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_3^\top}
-\end{equation}
-Rewrite equation~\ref{eq:Voldermont} as
-\begin{equation}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')\propto-(T-1)n_y\ln\sigma^2_{\epsilon}-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
-\end{equation}
-differentiating with respect to $\sigma_{\epsilon}^2$
-\begin{equation}
-  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon^4}}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
+  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
 \end{equation}
@@
 \end{equation}
+A second derivative test shows that this is indeed the maximum.
 

### 2011-02-11 ltx/data_paper/DataPaper.tex
edits to maximization

@@
 \end{equation}
-A second derivative test shows that this is indeed the maximum.
-
-\subsection{Discussion}
-The second derivative of the $\mathcal Q$-function with respect to $\xi$ is given by
-\begin{equation}
- \frac{\partial^2 \mathcal Q}{\partial \xi^2}=-2 tr \left\lbrace\Xi_1\boldsymbol\Sigma_e^{-1} \right\rbrace
-\end{equation}
-$\Xi_1 $ is positive definite if the state vector is persistently excited and the covariance matrix $\boldsymbol\Sigma_e^{-1}$ is also positive definite therefore the trace of $\Xi_1\boldsymbol\Sigma_w^{-1}$ is guaranteed to be positive so the second derivative is negative and represents a maximum of $\mathcal Q$-function.\\
-The second derivative of the $\mathcal Q$-function with respect to $\boldsymbol \theta$ is given by
-\begin{equation}
- \frac{\partial^2 \mathcal Q}{\partial \boldsymbol\theta^2}=-2 \Xi_2 
-\end{equation}
-$\Xi_2$ is positive definite and invertible and the second derivative is negative definite and represents a maximum of $\mathcal Q$- function.
+A second derivative test shows that this is indeed the maximum. Finally differentiating with respec to $\sigma_d^2$ we get
+\begin{eqnarray}
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&=& -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_d^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\frac{1}{\sigma_d^4}\Xi_2\boldsymbol\theta \nonumber \\
+&+&\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_4 \boldsymbol\theta +\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+\end{eqnarray}
+setting above to zero and solving for $\sigma_e^2$ we have
+\begin{eqnarray}
+\sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+2\xi\mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\Xi_2\boldsymbol\theta+\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+2\xi\Xi_4 \boldsymbol\theta +\xi^2\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace \right]
+\end{eqnarray}
+It can be also shown that the resulting solution is a maximum.
 

### 2011-02-11 ltx/data_paper/DataPaper.tex
edits to maximization

@@
 \section{Estimation Algorithm}
-Here we describe the problem of estimating non-linear state-space neural field model using expectation-maximisation (EM) based algorithm \cite{Shumway2000}.
+Here we describe the problem of estimating non-linear state-space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
 The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters.
@@
 The resulting parameters are then used when estimating the new
-state vector sequence for the next iteration. The procedure stops when the parameter estimates converge.
+state vector sequence for the next iteration. The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation.
 \subsection{E-Step}
@@
 \begin{eqnarray}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&=& -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_d^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\frac{1}{\sigma_d^4}\Xi_2\boldsymbol\theta \nonumber \\
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&=& -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\frac{1}{\sigma_d^4}\Xi_2\boldsymbol\theta \nonumber \\
 &+&\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_4 \boldsymbol\theta +\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
@@
 \end{eqnarray}
-It can be also shown that the resulting solution is a maximum.
+The second derivative test confirms this is a maximum.
 

### 2011-02-11 ltx/data_paper/DataPaper.tex
minor edit to derivation

@@
 The resulting parameters are then used when estimating the new
-state vector sequence for the next iteration. The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation.
+state vector sequence for the next iteration. The stopping criterion is when the parameter estimates converge. or the log-likelihood variation.
 \subsection{E-Step}
@@
 Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
+\dean{The difference between the linearised and nonlinear likliehood will be the error in the approximation at the state estimate that maximised the likelihood.}
 
 \subsection{M-Step}
-The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
-We choose to maximize  $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
+The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e.,
+\begin{equation}
+	\Theta = [\theta ...]
+\end{equation}
+ connectivity kernel parameters $\boldsymbol\theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
 Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}.
@@
 \end{equation}
-The  lower-bound on the joint likelihood function is defined as   
+The standard form of the lower bound of the log-likelihood or $\mathcal{Q}$ function, is defined as   
 \begin{align}\label{eq:QFunction}
@@
 where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta')$, and $\boldsymbol \Theta'$ is the current parameter estimates.
+The factor of $2$ is included to simplify the derivation in the later steps.
 Substituting  \ref{eq:jointdistribution} in \ref{eq:QFunction} gives

### 2011-02-11 ltx/data_paper/DataPaper.tex
edits to em derivation in data paper

@@
 \end{equation}
+Define
+\begin{equation}
+	e(x) = q(x) - f(x) \nonumber
+\end{equation}
+
+Then we can write f(x) = q(x) + e(x) and use this to show that the error in the estimate is proportional to e(x).
+
 Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
-\dean{The difference between the linearised and nonlinear likliehood will be the error in the approximation at the state estimate that maximised the likelihood.}
+\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
 
@@
 The factor of $2$ is included to simplify the derivation in the later steps.
-Substituting  \ref{eq:jointdistribution} in \ref{eq:QFunction} gives
+Using the chain rule of probability theory (relationship between conditional and joint) we can right
+\begin{equation}
+	... \nonumber
+\end{equation}
+ Substituting equations \ref{eq:jointdistribution} in \ref{eq:QFunction} gives
 \begin{align}
@@
 \end{equation}
-Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions
+Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions (ignoring the normalising factor of these conditional distributions)
 \begin{align}
- p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}} \times  e^{-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) } \\
+ p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \dean{exp}^{-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) } \\
 p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \times e^{-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
 \end{align}
-We ignored constant terms in the normalising factor of these conditional distributions. By expanding the exponent and taking $2\log$ we get
+Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ (\dean{$\sigma_W$ notation from 18}) where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
+By expanding the exponent and taking $2\ln$ we get
 \begin{align}\label{eq:CondititionDist1}
@@
 \end{align}
-Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
+\dean{Dean to check expansion.} Now we rearrange the equation so we can write down (or isolate (reason for doing this step is..)) the cross-covariance etc so we can use the information from the filter.
 Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
@@
 Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma_e}\mid $ as it is not a function of the parameter set.
+
 Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.

### 2011-02-12 ltx/data_paper/DataPaper.tex
edits to maximization

@@
 \end{align}
-Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma_e}\mid $ as it is not a function of the parameter set.
+Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma}_e\mid $ as it is not a function of the parameter set.
 
@@
 The second derivative test confirms this is a maximum.
+
+\section{Results}
+\begin{itemize}
+	\item Will show parameter distributions
+	\item Will show parameter changes over time through the seizure
+\end{itemize}
+\section{M-Step-II}
+\dean{Dean to check expansion.} Now we rearrange the equation so we can write down (or isolate (reason for doing this step is..)) the cross-covariance etc so we can use the information from the filter.
+Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\begin{align}\label{eq:Qfunctiontrace1}
+  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace    \\
+ 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace.
+\label{eq:Qfunctiontrace2}
+\end{align}
+Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma}_e\mid $ as it is not a function of the parameter set.
+
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
+Therefore $\mathcal Q$-function can be written as
+\begin{align}\label{eq:Voldermont}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&= -(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right]\boldsymbol\theta
+ \nonumber \\
+&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right]\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \boldsymbol\theta
+\end{align}
+It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right] $.
+For simplicity we write \ref{eq:Voldermont} in a form of
+\begin{align}\label{eq:VoldermontwitXivariables}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+ \nonumber \\
+&+\frac{2}{\sigma_d^2}\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_{5} \boldsymbol\theta
+\end{align}
+where
+\begin{align}
+	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0} \\
+\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1} \\
+\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)\\
+\Xi_{3}&=E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \\	
+\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right]\\
+ \Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right]
+ \end{align}
+Consider first the maximization of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
+\begin{equation}\label{eq:Qpartialtheta}
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_2-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_3^\top+\Xi_3)-\frac{2\xi}{\sigma_d^2}\Xi_4
+\end{equation}
+noting that $\Xi_3$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
+\begin{equation}\label{eq:theta}
+ \boldsymbol \theta=\Xi_3^{-1}\left(\Xi_2^\top-\xi\Xi_4^\top \right).
+\end{equation}
+The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
+Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+\begin{equation}
+  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
+\end{equation}
+setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
+\begin{equation}
+ \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
+\end{equation}
+A second derivative test shows that this is indeed the maximum. Finally differentiating with respec to $\sigma_d^2$ we get
+\begin{eqnarray}
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&=& -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\frac{1}{\sigma_d^4}\Xi_2\boldsymbol\theta \nonumber \\
+&+&\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_4 \boldsymbol\theta +\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+\end{eqnarray}
+setting above to zero and solving for $\sigma_e^2$ we have
+\begin{eqnarray}
+\sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+2\xi\mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\Xi_2\boldsymbol\theta+\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+2\xi\Xi_4 \boldsymbol\theta +\xi^2\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace \right]
+\end{eqnarray}
+The second derivative test confirms this is a maximum.
+where   
+\begin{align}
+	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0} \\
+\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1} \\
+\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)\\
+\Xi_{3}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_{4}&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+ \Xi_{5}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+ \end{align}
+and
+\begin{align}
+	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambda}\\
+	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\tilde{\boldsymbol\Sigma}_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\label{eq:lambdai}\\
+	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambdatilde}\\
+	 \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r' \label{eq:lambdatildei}
+\end{align}
+Given the state estimates, $\mathbf {\hat x^{b}}_t$ the state covariance $\mathbf P_t^b$ and cross-covariance $\mathbf M_t^b$ , the $\Xi$-variables can be computed directly.
+In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
 

### 2011-02-12 ltx/data_paper/DataPaper.tex
edits to maximization

@@
 
-Since the state equation is non-linear,  calculation of covariance and  cross-covariance terms required for the maximisation step is not straightforward as in the linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the M-step.
-This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^{b}$ at each time instant, i.e.
-\begin{equation}\label{eq:SigmoidTaylor}
- f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)
-\end{equation}
-where 
-\begin{equation}\label{eq:SigmoidDerivative}
- f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\right)
-\end{equation}
-substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the smoothed estimate $\hat{\mathbf{x}}_t^b$ 
-\begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
-\end{equation}
-Define
+\subsection{M-Step}
+The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
 \begin{equation}
-	e(x) = q(x) - f(x) \nonumber
-\end{equation}
-
-Then we can write f(x) = q(x) + e(x) and use this to show that the error in the estimate is proportional to e(x).
-
-Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
-\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
-
-\subsection{M-Step}
-The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e.,
-\begin{equation}
-	\Theta = [\theta ...]
-\end{equation}
- connectivity kernel parameters $\boldsymbol\theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
-We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
+	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \sigma_d, \sigma_{\epsilon}\right\rbrace 
+\end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
 Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}.
@@
 \begin{align}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta.
+\sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
 \end{align}
- It should be noted that the last term is not a function of parameter set and can be ignored therefore $\mathcal Q$-function can be rewritten as
+ It should be noted that the last term is not a function of parameter set and can be ignored, therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}\label{eq:QIntermsofJointDist}
@@
 \begin{align}
- p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \dean{exp}^{-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) } \\
-p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \times e^{-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t)}
+ p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \mathrm{exp}\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right)\\
+p\left(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d\right)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}}\mathrm{exp}\left(-\frac{1}{2}\left(\mathbf x_{t+1}-q\left(\mathbf  x_t\right)\boldsymbol\theta-\xi  \mathbf x_t\right)^\top\boldsymbol\Sigma_e^{-1}\left(\mathbf x_{t+1}-q\left( \mathbf x_t\right)\boldsymbol\theta-\xi \mathbf  x_t\right)\right)
 \end{align}
@@
 \end{align}
-\dean{Dean to check expansion.} Now we rearrange the equation so we can write down (or isolate (reason for doing this step is..)) the cross-covariance etc so we can use the information from the filter.
-Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
-\begin{align}\label{eq:Qfunctiontrace1}
-  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace    \\
- 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_s^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
-&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace.
-\label{eq:Qfunctiontrace2}
-\end{align}
-Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma}_e\mid $ as it is not a function of the parameter set.
-
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
-Therefore $\mathcal Q$-function can be approximated as
-\begin{eqnarray}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-&(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+2\frac{1}{\sigma_d^2}\Xi_{2}\boldsymbol\theta
- \nonumber \\
-&-&\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_{3}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_{4} \boldsymbol\theta -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_{5}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
-\end{eqnarray}
-where 
-\begin{align}
-	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0} \\
-\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1} \\
-\Xi_{2}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_{3}&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
- \Xi_{4}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
- \Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
-\end{align}
-and
-\begin{align}
-	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambda}\\
-	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\tilde{\boldsymbol\Sigma}_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\label{eq:lambdai}\\
-	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambdatilde}\\
-	 \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r' \label{eq:lambdatildei}
-\end{align}
-It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right] $.
-Given the state estimates, $\mathbf {\hat x^{b}}_t$ the state covariance $\mathbf P_t^b$ and cross-covariance $\mathbf M_t^b$ , the $\Xi$-variables can be computed directly.
-In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
-
-Consider first the maximization of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
-\begin{equation}\label{eq:Qpartialtheta}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_2-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_3^\top+\Xi_3)-\frac{2\xi}{\sigma_d^2}\Xi_4
-\end{equation}
-noting that $\Xi_3$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
-\begin{equation}\label{eq:theta}
- \boldsymbol \theta=\Xi_3^{-1}\left(\Xi_2^\top-\xi\Xi_4^\top \right).
-\end{equation}
-The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
-Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
-\begin{equation}
-  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
-\end{equation}
-setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
-\begin{equation}
- \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
-\end{equation}
-A second derivative test shows that this is indeed the maximum. Finally differentiating with respec to $\sigma_d^2$ we get
-\begin{eqnarray}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&=& -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\frac{1}{\sigma_d^4}\Xi_2\boldsymbol\theta \nonumber \\
-&+&\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_4 \boldsymbol\theta +\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
-\end{eqnarray}
-setting above to zero and solving for $\sigma_e^2$ we have
-\begin{eqnarray}
-\sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
-2\xi\mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\Xi_2\boldsymbol\theta+\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+2\xi\Xi_4 \boldsymbol\theta +\xi^2\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace \right]
-\end{eqnarray}
-The second derivative test confirms this is a maximum.
-
-\section{Results}
-\begin{itemize}
-	\item Will show parameter distributions
-	\item Will show parameter changes over time through the seizure
-\end{itemize}
-\section{M-Step-II}
 \dean{Dean to check expansion.} Now we rearrange the equation so we can write down (or isolate (reason for doing this step is..)) the cross-covariance etc so we can use the information from the filter.
@@
 \begin{align}
-	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0} \\
-\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1} \\
-\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)\\
-\Xi_{3}&=E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \\	
-\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right]\\
- \Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right]
+	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\label{eq:defofXi0} \\
+\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:defofXi1} \\
+\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\\
+\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \label{eq:Xi3} \\	
+\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right] \label{eq:Xi4}\\
+ \Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \label{eq:Xi5}
  \end{align}
@@
 \begin{equation}\label{eq:Qpartialtheta}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_2-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_3^\top+\Xi_3)-\frac{2\xi}{\sigma_d^2}\Xi_4
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_4^\top+\Xi_4)-\frac{2\xi}{\sigma_d^2}\Xi_5
 \end{equation}
-noting that $\Xi_3$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
+noting that $\Xi_4$ is symmetric and positive-definite by construction, equating \ref{eq:Qpartialtheta} to the zero vector we get
 \begin{equation}\label{eq:theta}
- \boldsymbol \theta=\Xi_3^{-1}\left(\Xi_2^\top-\xi\Xi_4^\top \right).
+ \boldsymbol \theta=\Xi_4^{-1}\left(\Xi_3^\top-\xi\Xi_5^\top \right).
 \end{equation}
@@
 A second derivative test shows that this is indeed the maximum. Finally differentiating with respec to $\sigma_d^2$ we get
-\begin{eqnarray}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&=& -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\frac{1}{\sigma_d^4}\Xi_2\boldsymbol\theta \nonumber \\
-&+&\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_4 \boldsymbol\theta +\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
-\end{eqnarray}
+\begin{align}
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace  \nonumber \\
+&-\frac{2}{\sigma_d^4}\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_5 \boldsymbol\theta 
+\end{align}
 setting above to zero and solving for $\sigma_e^2$ we have
-\begin{eqnarray}
+\begin{align}
 \sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
-2\xi\mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\Xi_2\boldsymbol\theta+\boldsymbol\theta^\top \Xi_3\boldsymbol\theta+2\xi\Xi_4 \boldsymbol\theta +\xi^2\mathrm{tr} \left\lbrace\Xi_5\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace \right]
-\end{eqnarray}
+2\xi\mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top \Xi_4\boldsymbol\theta+2\xi\Xi_5 \boldsymbol\theta\right]
+\end{align}
 The second derivative test confirms this is a maximum.
+
+Computing unknown variables, $\boldsymbol\Theta$, in the maximization step requires calculation of covariance and  cross-covariance terms, including both linear, $\Xi_0$, $\Xi_1$ and $\Xi_2$ and non-linear terms, $\Xi_3$, $\Xi_4$ and  $\Xi_5$.
+Finding linear $\Xi$-variables is straightforward as they can be obtained using smoother outputs, $\hat{\mathbf x}_t $, $\mathbf P_t$ and $\mathbf M_t$ using the following expressions \cite{Shumway2000} (see supporting information for details)
+\begin{align}
+	\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0}, \\
+\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1}, \\
+\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+ \end{align}
+However calculation of non-linear $\Xi$-variables required for the M-step is not straightforward as in the linear case.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\Xi_3$, $\Xi_4$ and $\Xi_5$.
+This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the estimated state, $\hat{\mathbf x}_t$ at each time instant, i.e.
+\begin{equation}\label{eq:SigmoidTaylor}
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)
+\end{equation}
 where 
+\begin{equation}\label{eq:SigmoidDerivative}
+ f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\right)
+\end{equation}
+substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the estimated state $\hat{\mathbf{x}}_t$ 
+\begin{equation}\label{eq:qTaylor}
+ q(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
+\end{equation}
+Define
+\begin{equation}
+	e(x) = q(x) - f(x) \nonumber
+\end{equation}
+
+Then we can write f(x) = q(x) + e(x) and use this to show that the error in the estimate is proportional to e(x).
+
+Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
+\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
+
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\Xi$-variables can be calculated
 \begin{align}
@@
  \end{align}
-and
+where
 \begin{align}

### 2011-02-12 ltx/data_paper/DataPaper.tex
edits to maximization

@@
 
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives an approximate to the lower-bound that needs to be maximised to gain optimal parameter estimates.
-Therefore $\mathcal Q$-function can be written as
+Substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives the lower-bound that needs to be maximised to gain optimal parameter estimates,
 \begin{align}\label{eq:Voldermont}
@@
 \end{align}
-It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right] $.
-For simplicity we write \ref{eq:Voldermont} in a form of
-\begin{align}\label{eq:VoldermontwitXivariables}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
- \nonumber \\
-&+\frac{2}{\sigma_d^2}\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_{5} \boldsymbol\theta
-\end{align}
-where
+It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right]$.
+By choosing
 \begin{align}
@@
  \end{align}
+equation \ref{eq:Voldermont} can be written as
+\begin{align}\label{eq:VoldermontwitXivariables}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+ \nonumber \\
+&+\frac{2}{\sigma_d^2}\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_{5} \boldsymbol\theta.
+\end{align}
+
 Consider first the maximization of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
 \begin{equation}\label{eq:Qpartialtheta}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_4^\top+\Xi_4)-\frac{2\xi}{\sigma_d^2}\Xi_5
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_4^\top+\Xi_4)-\frac{2\xi}{\sigma_d^2}\Xi_5,
 \end{equation}
-noting that $\Xi_4$ is symmetric and positive-definite by construction, equating \ref{eq:Qpartialtheta} to the zero vector we get
+variable $\Xi_4$ is symmetric and positive-definite by construction, equating \ref{eq:Qpartialtheta} to the zero vector yields
 \begin{equation}\label{eq:theta}
@@
 \end{equation}
-setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
+setting above to zero and solving for $\sigma_{\epsilon}^2$ gives
 \begin{equation}
@@
 
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\Xi$-variables can be calculated
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\Xi$-variables can be calculated which provides an approximate lower bound on the log-likelihood function (see supporting information),
 \begin{align}
-	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0} \\
-\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1} \\
-\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)\\
-\Xi_{3}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_{4}&=\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
- \Xi_{5}&=\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+ \Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
  \end{align}
@@
 \end{align}
-Given the state estimates, $\mathbf {\hat x^{b}}_t$ the state covariance $\mathbf P_t^b$ and cross-covariance $\mathbf M_t^b$ , the $\Xi$-variables can be computed directly.
+Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\Xi$-variables can be computed directly.
 In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.

### 2011-02-12 ltx/data_paper/DataPaper.tex
small edit

@@
 \begin{align}
- p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \mathrm{exp}\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right)\\
-p\left(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d\right)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}}\mathrm{exp}\left(-\frac{1}{2}\left(\mathbf x_{t+1}-q\left(\mathbf  x_t\right)\boldsymbol\theta-\xi  \mathbf x_t\right)^\top\boldsymbol\Sigma_e^{-1}\left(\mathbf x_{t+1}-q\left( \mathbf x_t\right)\boldsymbol\theta-\xi \mathbf  x_t\right)\right)
+ p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left(-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right) \\
+p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \exp \left(-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right)
 \end{align}
@@
 \end{align}
-It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right]$.
+It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right]$, ref(Shumway).
 By choosing
@@
 \begin{equation}\label{eq:qTaylor}
- q(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
+ q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
 \end{equation}
@@
 \begin{equation}
-	e(x) = q(x) - f(x) \nonumber
+	e(x) = q(x) - q_L(x) \nonumber
 \end{equation}
 
-Then we can write f(x) = q(x) + e(x) and use this to show that the error in the estimate is proportional to e(x).
+Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
 

### 2011-02-16 src/Matlab/SphericalBoundary.m
edits to xcorr derivation

@@ -30,7 +30,7 @@ SecondThirdEnd = 2*FirstThirdEnd+1;
 
 mm=1;
 Sigma_gamma = zeros(NPointsInField^2,NPointsInField^2);   % create disturbance covariance matrix
-figure
+% figure
 template = zeros(NPointsInField,NPointsInField);
 for n=1:NPointsInField
     for nn=1:NPointsInField

### 2011-02-16 ltx/data_paper/DataPaper.tex
edits to maximization
added note to discussion
fixed the conflict on exp for the distributions

@@
 \newcommand{\blue}{\textcolor{blue}}
+\newcommand{\cyan}{\textcolor{cyan}}
 
@@
 \end{equation}
+\cyan{small thing: are we using $\exp(x)$ or $e^x$ to represent exponential?}
 $\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function \blue{(you can keep it here if you wish as it doesn't change the integral equation because of the upper limit.
@@
 For $\sigma_W = 0$ a pure deterministic process is recovered.
-As a result of the random component component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process.
+As a result of the random component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process.
 Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \red{citation?}
@@
 \end{equation}
-where $v_0$ and $\varsigma$ describe the firing threshold the slope of the sigmoid respectively. 
+where $v_0$ and $\varsigma$ describe the firing threshold and the slope of the sigmoid respectively. 
 By substituting equation~\ref{DecompositionOfg} into equation~\ref{SpikesToPotential} we obtain the stochastic integral equation model 
@@
 \end{equation}
-enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken, such that the state vector can is isolated on the left-hand-side as
+enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken, such that the state vector is isolated on the left-hand-side as
 \begin{equation}\label{eq:ReducedForm}
@@
 \begin{align}
- p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left(-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right) \\
+ p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right),\\
 p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \exp \left(-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right)
@@
 \begin{align}\label{eq:CondititionDist1}
-2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right]  \\
+2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],  \\
 2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
@@
 \begin{itemize}
-	\item  
+	\item comment on how the e step is ukf and m step is kinda like the ekf.  
 \end{itemize}

### 2011-02-20 src/DataPaper/ReadAndPlotData.m
updated support estimation

@@ -8,8 +8,8 @@ close all
 % hi guys, when you use this uncomment your name. You also need to add
 % where you have saved the data and where you want to save the figures
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-%User = 'Dean';                   
- User = 'Parham';
+User = 'Dean';                   
+%  User = 'Parham';
 % User = 'Mike';
 % User = 'Ken';
 
@@ -55,7 +55,7 @@ FS2 = 12;
 TwoColumnWidth = 17.35;     % PLoS figure width cm
 OneColumnWidth = 8.3; % cm
 Fs = 30e3;                              % sampling rate in Hz of the raw data
-FsDec = 5e3;                          % this is the sampling rate that we will use
+FsDec = 1e3;                          % this is the sampling rate that we will use
 TsDec = 1/FsDec;                    % the decimated sampling period
 DecimationFactor = Fs/FsDec;
 
@@ -66,6 +66,7 @@ SzStart = 8;        % seconds
 SzEnd = 34;         % seconds
 
 % read in neuroport data from .mat file
+% ~~~~~~~~~~~~~~~~~~~~~~
 Data = open(DataFileLocation);
 Data = Data.whole_data';
 
@@ -104,8 +105,8 @@ end
 % ~~~~~~~~~~~~~~~~~~~~~
 CAR = repmat(mean(MappedData,2),1,100);
 CARData = MappedData-CAR;                       % CAR = common average reference
- clear MappedData
-
+clear MappedData
+clear CAR;
 %%
 % re-assign the bad channels and the corners to nans so we can interpolate
 ZeroChannels = [1 10 13 15 19 24 26 35 42 46 47 54 56  57 67 81 85 87 91 100];
@@ -121,7 +122,7 @@ Wn = Fc/(Fs/2);
 FilterOrder = 2;
 [b a] = butter(FilterOrder,Wn);
 FiltData = filter(b,a,CARData);
-%clear CARData
+clear CARData
 
 %%
 % downsample to FsDec
@@ -139,11 +140,11 @@ t = TsDec*(0:size(FiltData,1)-1);
 
 %
[…]

### 2011-02-20 src/Matlab/CorrelationOnObservations170211.m

@@ -55,7 +55,7 @@ w_tau = theta(1)*psi_0 + theta(2)*psi_1 + theta(3)*psi_2;       % the kernel
 % ~~~~~~~~~~~~
 sigma_m = 0.9;                                                         % sensor width
 m = Define2DGaussian(0,0,sigma_m^2,0,NPoints,SpaceMin,SpaceMax);        % sensor kernel
-sigma_varepsilon = 0.001;       % observation noise                            
+sigma_varepsilon = 0.1;       % observation noise                            
 
 % sigmoid parameters
 % ~~~~~~~~~~~~
@@ -113,7 +113,9 @@ for n=1:N_realizations
     InitialCondition = min_field_init + (max_field_init - min_field_init)*rand(NPoints,NPoints);
     future_field = InitialCondition;
 
+    fft_y = zeros(T,NPoints,NPoints);       % initialize for speed
     y = zeros(T,NPoints,NPoints);       % initialize for speed
+
     future_obs = squeeze(y(1,:,:));
     xcorr = zeros(T-1,81,81);           % initialize for speed
     autocorr = xcorr;                       % initialize for speed
@@ -123,8 +125,8 @@ for n=1:N_realizations
     % main loop
     for t=1:T-1
         current_field = future_field;
-        f = 1./(1+exp(varsigma*(v_0-current_field)));           % calc firing rate using sigmoid
-%         f = varsigma * current_field;
+%         f = 1./(1+exp(varsigma*(v_0-current_field)));           % calc firing rate using sigmoid
+        f = varsigma * current_field;
         if Torus == true
             f = padarray(f,size(f),'circular');                                     % pad array for toroidal boundary
         end
@@ -143,7 +145,7 @@ for n=1:N_realizations
         obs_noise =  reshape(varepsilon(t,:,:),NPoints,NPoints);
         
         future_obs = conv2(m,future_field,'same')*Delta_squared + obs_noise; 
-        y(t+1,:,:) = future_obs;
+        fft_y(t+1,:,:) = fft2(future_obs - mean(mean(future_obs,1)));
         
         autocorr(t,:,:) = xcorr2(current_obs, current_obs);
[…]

### 2011-02-22 src/DataPaper/ReadAndPlotData.m
updated kernel support paper

@@ -107,6 +107,7 @@ CAR = repmat(mean(MappedData,2),1,100);
 CARData = MappedData-CAR;                       % CAR = common average reference
 clear MappedData
 clear CAR;
+
 %%
 % re-assign the bad channels and the corners to nans so we can interpolate
 ZeroChannels = [1 10 13 15 19 24 26 35 42 46 47 54 56  57 67 81 85 87 91 100];
@@ -158,14 +159,27 @@ clear FiltData
 %%
 % calc and plot the 2D cross-correlation
 disp('finding cross correlations')
-autocorr = zeros(size(MatrixData,1),2*size(MatrixData,2)-1,2*size(MatrixData,2)-1);
+
+% EndSample = SzEnd*FsDec;
+EndSample = SzStart*FsDec;
+
+autocorr = zeros(EndSample,2*size(MatrixData,2)-1,2*size(MatrixData,2)-1);
 xcorr = autocorr;
 future_obs = zeros(size(MatrixData,2),size(MatrixData,3));
-fft_obs  = zeros(size(MatrixData,1),2*size(MatrixData,2),2*size(MatrixData,2));
-for n=1:size(MatrixData,1)-1   
+FFT_padding = 3;
+fft_obs  = zeros(EndSample,FFT_padding*size(MatrixData,2),FFT_padding*size(MatrixData,2));
+for n=1:EndSample           %size(MatrixData,1)-1   
     current_obs = future_obs;
+    mean_current_obs = mean(mean(current_obs,2),1);
     future_obs = squeeze(MatrixData(n+1,:,:));
-    fft_obs(n,:,:) = fft2(current_obs,2*size(MatrixData,2),2*size(MatrixData,3));
+    fft_obs(n,:,:) = 20*log10( abs( fft2(current_obs-mean_current_obs, ...
+        FFT_padding*size(MatrixData,2), FFT_padding*size(MatrixData,3)) ) );
+%     clims = [0 70];
+%     imagesc(squeeze(fft_obs(n,:,:)),clims)
+%     axis xy
+%     axis square
+%     drawnow
+%     pause
     autocorr(n,:,:) = xcorr2(current_obs, current_obs);
     xcorr(n,:,:) = xcorr2(future_obs, current_obs);
 end
[…]

### 2011-02-22 src/Matlab/CorrelationOnObservations170211.m

@@ -29,7 +29,7 @@ r = linspace(SpaceMin,SpaceMax,NPoints);      % define space
 % temporal parameters
 % ~~~~~~~~~~~~~
 Ts = 1e-3;          % sampling period (s)
-T = 20000;            % maximum time (ms)
+T = 10000;            % maximum time (ms)
 
 % kernel parameters
 % ~~~~~~~~~~~
@@ -55,7 +55,7 @@ w_tau = theta(1)*psi_0 + theta(2)*psi_1 + theta(3)*psi_2;       % the kernel
 % ~~~~~~~~~~~~
 sigma_m = 0.9;                                                         % sensor width
 m = Define2DGaussian(0,0,sigma_m^2,0,NPoints,SpaceMin,SpaceMax);        % sensor kernel
-sigma_varepsilon = 0.1;       % observation noise                            
+sigma_varepsilon = 0.0;       % observation noise                            
 
 % sigmoid parameters
 % ~~~~~~~~~~~~
@@ -125,8 +125,8 @@ for n=1:N_realizations
     % main loop
     for t=1:T-1
         current_field = future_field;
-%         f = 1./(1+exp(varsigma*(v_0-current_field)));           % calc firing rate using sigmoid
-        f = varsigma * current_field;
+        f = 1./(1+exp(varsigma*(v_0-current_field)));           % calc firing rate using sigmoid
+%         f = varsigma * current_field;
         if Torus == true
             f = padarray(f,size(f),'circular');                                     % pad array for toroidal boundary
         end
@@ -162,11 +162,34 @@ for n=1:N_realizations
     
     LHS = (R_yy_plus_1 - xi*(R_yy-mean_obs_noise)) ;
     
-    %%
-    R_yy_conv_mat = convmtx2(R_yy-mean_obs_noise,81,81);
-    LHS_vect = LHS(:);
-    w_vect = linsolve(full(R_yy_conv_mat)',LHS_vect);
-    w_est_linsolve = reshape(w_vect,161,161)*xi/(Ts*varsigma);
+%     %%
+%     R_yy_conv_mat = convmtx2(R_yy-mean_obs_noise,81,81);
+%     LHS_vect = LHS(:);
+%     tic
[…]

### 2011-02-22 src/Matlab/CorrelationOnObservations170211.m
added figures for debugging

@@ -125,8 +125,8 @@ for n=1:N_realizations
     % main loop
     for t=1:T-1
         current_field = future_field;
-        f = 1./(1+exp(varsigma*(v_0-current_field)));           % calc firing rate using sigmoid
-%         f = varsigma * current_field;
+%         f = 1./(1+exp(varsigma*(v_0-current_field)));           % calc firing rate using sigmoid
+        f = varsigma * current_field;
         if Torus == true
             f = padarray(f,size(f),'circular');                                     % pad array for toroidal boundary
         end
@@ -246,10 +246,16 @@ for n=1:N_realizations
     drawnow
     
     shifted_ratio = fftshift(ratio);
+    
+    figure,imagesc(abs(shifted_ratio))
+    
     NSamps = 13;
-    temp1 = shifted_ratio(41-NSamps:41+NSamps,41-NSamps:41+NSamps);
-    temp2 = zeros(size(ratio));
-    temp2(41-NSamps:41+NSamps,41-NSamps:41+NSamps) = temp1;
+%     temp1 = shifted_ratio(41-NSamps:41+NSamps,41-NSamps:41+NSamps);
+%     temp2 = zeros(size(ratio));
+%     temp2(41-NSamps:41+NSamps,41-NSamps:41+NSamps) = temp1;
+    temp1 = shifted_ratio;
+    temp1(41-NSamps:41+NSamps,41-NSamps:41+NSamps) = 0;
+    temp2 = temp1;
     ratio = ifftshift(temp2);
     
     filename = '/Users/dean/Projects/BrainIDE/ltx/EMBCCorrelationAnalysisPaper/ltx/figures/FFTKernelEstimateThreshold.pdf';

### 2011-03-11 ltx/BrainIDEPoster/BrainIDE_Poster.tex
poster edits
made a colour change in the poster
added BrainIDETalk

@@
 
-\setbeamercolor{block title}{fg=ngreen,bg=white}
+\setbeamercolor{block title}{fg=dblue,bg=white}
 \setbeamercolor{block body}{fg=black,bg=white}
@@
 \setbeamercolor{block alerted body}{fg=black,bg=dblue!10}
+%\setbeamercolor{block title}{fg=red,bg=white}
 
@@
 \institute{1. Department of Electrical and Electronic Engineering, University of Melbourne, Australia \\
-% 2. The Bionic Ear Institute, East Melbourne, VIC, Australia \\
-% 3. Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK \\
 2. Department of Automatic Control and Systems Engineering, University of Sheffield, UK \\
@@
   \begin{columns}[t]												% the [t] option aligns the column's content at the top
-	  \setbeamercolor{block title}{fg=red,bg=white}%frame color
 
@@
 		\begin{center}
-		  \includegraphics[width=10in, scale = 10]{EstimationAlgorithm.eps}
+		  \includegraphics[width=10.5in, scale = 10]{EstimationAlgorithm.eps}
 		\end{center}

### 2011-03-11 src/Matlab/CorrelationOnObservations170211.m

@@ -124,7 +124,7 @@ for n=1:N_realizations
     autocorr = xcorr;                       % initialize for speed
     obs_noise_autocorr = xcorr;
     extra_bit1 = xcorr;
-%     extra_bit2 = xcorr;
+    extra_bit2 = xcorr;
     extra_bit3 = xcorr;
 %     extra_bit4 = xcorr;
     extra_bit5 = xcorr;
@@ -173,28 +173,47 @@ for n=1:N_realizations
         
         autocorr_trim = squeeze(autocorr(t,41-20:41+20,41-20:41+20));
         
-        extra_bit1(t,:,:) = xcorr2(conv2(m,disturbance,'same')*Delta^2,current_obs);
-%         extra_bit2(t,:,:) = xcorr2(conv2(m,xi*current_field,'same')*Delta^2,current_obs);
+        extra_bit1(t,:,:) = xcorr2(conv2(m,padarray(disturbance,size(disturbance),'circular'),'same')*Delta^2,current_obs);
+        extra_bit2(t,:,:) = xcorr2(conv2(m,xi*padarray(current_field,size(current_field),'circular'),'same')*Delta^2,current_obs);
         extra_bit3(t,:,:) = xcorr2( conv2(m,padarray(g,size(g),'circular') ,'same')*Delta^2,current_obs);        
 %         extra_bit4(t,:,:) = Ts* xcorr2(conv2(m, conv2(w,f)*Delta^2,'same')*Delta^2 ,current_obs ); % should be the same as extra_bit3        
         extra_bit5(t,:,:) = Ts* xcorr2( conv2(w, conv2(m,f)*Delta^2,'same')*Delta^2,current_obs ); % should be the same as extra_bit3
 
         extra_bit6(t,:,:) = varsigma*Ts* xcorr2( conv2(w, padarray(current_obs,size(current_obs),'circular'),'same')*Delta^2, current_obs ); % should be the same as extra_bit3
-        extra_bit7(t,:,:) = varsigma*Ts*conv2(-w_tau,xcorr2(current_obs,flipud(fliplr(current_obs))),'same')*Delta^2; % should be the same as extra_bit3
-
-%         extra_bit8(t,:,:) = ifft2(fft2(w).*conj(fft2(current_obs)).*fft2(current_obs));
         
[…]

### 2011-04-26 ltx/data_paper/DataPaper.tex
added bib file to data paper folder
added xi estiamation to data paper

@@
 
-\ifpdf
-\usepackage[pdftex]{graphicx}
-\else
-\usepackage{graphicx}
-\fi
+% \ifpdf
+% \usepackage[pdftex]{graphicx}
+% \else
+% \usepackage{graphicx}
+% \fi
 \usepackage{color}
@@
 \begin{align}
-	\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\label{eq:defofXi0} \\
-\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:defofXi1} \\
-\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\\
-\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \label{eq:Xi3} \\	
-\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right] \label{eq:Xi4}\\
- \Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \label{eq:Xi5}
+	\boldsymbol\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\label{eq:defofXi0} \\
+\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:defofXi1} \\
+\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\\
+\boldsymbol\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \label{eq:Xi3} \\	
+\boldsymbol\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right] \label{eq:Xi4}\\
+ \boldsymbol\Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \label{eq:Xi5}
  \end{align}
@@
  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\boldsymbol\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
  \nonumber \\
-&+\frac{2}{\sigma_d^2}\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \Xi_{5} \boldsymbol\theta.
+&+\frac{2}{\sigma_d^2}\boldsymbol\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \boldsymbol\Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2}\boldsymbol \Xi_{5} \boldsymbol\theta.
 \end{align}
@@
 \begin{equation}\label{eq:Qpartialtheta}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_4^\top+\Xi_4)-\frac{2\xi}{\sigma_d^2}\Xi_5,
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\boldsymbol\Xi_4^\top+\boldsymbol\Xi_4)-\frac{2\xi}{\sigma_d^2}\boldsymbol\Xi_5,
 \end{equation}
-variable $\Xi_4$ is symmetric and positive-definite by construction, equating \ref{eq:Qpartialtheta} to the zero vector yields
+variable $\boldsymbol\Xi_4$ is symmetric and positive-definite by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
 \begin{equation}\label{eq:theta}
- \boldsymbol \theta=\Xi_4^{-1}\left(\Xi_3^\top-\xi\Xi_5^\top \right).
+ \boldsymbol \theta=\boldsymbol\Xi_4^{-1}\left(\boldsymbol\Xi_3^\top-\xi\boldsymbol\Xi_5^\top \right).
 \end{equation}
 The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
+In order to maximise $\mathcal{Q}$-function with respect to $\xi$ we can write
+\begin{equation}\label{eq:Qpartialxi}
+ \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5,
+\end{equation}
+setting \eqref{eq:Qpartialxi} to zero and solving for $\xi$
+\begin{equation}
+ \xi=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
+\end{equation}
+
 Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
@@
 
-% all figures here
-% ~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/LFPs.eps}
-\end{center}
-\caption{{\bf Local field potentials from the micro-electrode array}.
+% % all figures here
+% % ~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/LFPs.eps}
+% \end{center}
+% \caption{{\bf Local field potentials from the micro-electrode array}.
 Data recorded from the first 8 channels of the array.
 The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
-\label{fig:TimeSeries}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/FieldObservations.eps}
-\end{center}
-\caption{{\bf Snap-shots of the spatial aspects of the observed field}. The snap-shots are ordered from A to I forming a consecutive sequence spaced 2.5~ms apart starting at 34.024s}
-\label{fig:FieldObserations}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/TemporalFreq.eps}
-\end{center}
-\caption{{\bf Spectra from local field potential recordings}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:TemporalFreqObservation}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/SpatialFreq.eps}
-\end{center}
-\caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:SpatialFreqObservation}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/SpatialFreqCrossSection.eps}
-\end{center}
-\caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
-\label{fig:DiagSpatialFreqObservation}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/CrossCorr2D.eps}
-\end{center}
-\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}.
+% \label{fig:TimeSeries}
+% \end{figure}
+% 
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/FieldObservations.eps}
+% \end{center}
+% \caption{{\bf Snap-shots of the spatial aspects of the observed field}. The snap-shots are ordered from A to I forming a consecutive sequence spaced 2.5~ms apart starting at 34.024s}
+% \label{fig:FieldObserations}
+% \end{figure}
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/TemporalFreq.eps}
+% \end{center}
+% \caption{{\bf Spectra from local field potential recordings}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+% \label{fig:TemporalFreqObservation}
+% \end{figure}
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/SpatialFreq.eps}
+% \end{center}
+% \caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+% \label{fig:SpatialFreqObservation}
+% \end{figure}
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/SpatialFreqCrossSection.eps}
+% \end{center}
+% \caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
+% \label{fig:DiagSpatialFreqObservation}
+% \end{figure}
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/CrossCorr2D.eps}
+% \end{center}
+% \caption{{\bf Mean cross-correlations between consecutive observations of the neural field}.
 Note: The correlations are normalised such that the maximum value is one.
@@
 Post-seizure observation correlations.}
-\label{fig:SpatialCrossCorrelation}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/HomoTestCrossCorr.eps}
-\end{center}
-\caption{{\bf Mean cross-correlations between consecutive samples using subsets of observations of the neural field}.
+% \label{fig:SpatialCrossCorrelation}
+% \end{figure}
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/HomoTestCrossCorr.eps}
+% \end{center}
+% \caption{{\bf Mean cross-correlations between consecutive samples using subsets of observations of the neural field}.
 Each subplot shows correlations corresponding to a subset electrodes.
@@
 Subplot A shows the mean correlation between electrode indexes (1-6, 5-10), subplot B shows correlations from indexes (5-10,5-10), subplot C shows indexes (1-6, 1-6) and subplot D shows indexes (5-10, 5-10).}
-\label{fig:HomogeneityTest}
-\end{figure}
+% \label{fig:HomogeneityTest}
+% \end{figure}
 
@@
 \bibliographystyle{plain}
-\bibliography{BrainIDE}
+\bibliography{EMIDE}
 \end{document}

### 2011-04-26 ltx/data_paper/DataPaper.tex
made all Xi variable bold in EM paper

@@
 The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters.
-In the E-step we estimate the states $\mathbf x_t$, of the systems and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+In the E-step we estimate the states $\mathbf x_t$, of the systems and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, synaptic dynamic $\xi$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
 Once initialized, at each iteration the sequence of smoothed state vectors is used to update the parameters by maximizing an approximate lower bound on the log likelihood function.
@@
 \subsection{M-Step}
-The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
 \begin{equation}
-	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \sigma_d, \sigma_{\epsilon}\right\rbrace 
+	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma_d, \sigma_{\epsilon}\right\rbrace 
 \end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
@@
 
-Consider first the maximization of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
+Consider first the maximisation of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
 \begin{equation}\label{eq:Qpartialtheta}
- \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\boldsymbol\Xi_4^\top+\boldsymbol\Xi_4)-\frac{2\xi}{\sigma_d^2}\boldsymbol\Xi_5,
+ \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\boldsymbol\Xi_3-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\boldsymbol\Xi_4^\top+\boldsymbol\Xi_4)-\frac{2\xi}{\sigma_d^2}\boldsymbol\Xi_5,
 \end{equation}
@@
 \begin{align}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace  \nonumber \\
-&-\frac{2}{\sigma_d^4}\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \Xi_5 \boldsymbol\theta 
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace  \nonumber \\
+&-\frac{2}{\sigma_d^4}\boldsymbol\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \boldsymbol\Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \boldsymbol\Xi_5 \boldsymbol\theta 
 \end{align}
@@
 \begin{align}
-\sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
-2\xi\mathrm{tr}\left\lbrace \Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top \Xi_4\boldsymbol\theta+2\xi\Xi_5 \boldsymbol\theta\right]
+\sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right]
 \end{align}
@@
 
-Computing unknown variables, $\boldsymbol\Theta$, in the maximization step requires calculation of covariance and  cross-covariance terms, including both linear, $\Xi_0$, $\Xi_1$ and $\Xi_2$ and non-linear terms, $\Xi_3$, $\Xi_4$ and  $\Xi_5$.
-Finding linear $\Xi$-variables is straightforward as they can be obtained using smoother outputs, $\hat{\mathbf x}_t $, $\mathbf P_t$ and $\mathbf M_t$ using the following expressions \cite{Shumway2000} (see supporting information for details)
+Computing unknown variables, $\boldsymbol\Theta$, in the maximization step requires calculation of covariance and  cross-covariance terms, including both linear, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
+Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be obtained using smoother outputs, $\hat{\mathbf x}_t $, $\mathbf P_t$ and $\mathbf M_t$ using the following expressions \cite{Shumway2000} (see supporting information for details)
 \begin{align}
-	\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0}, \\
-\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1}, \\
-\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0}, \\
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1}, \\
+\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
  \end{align}
-However calculation of non-linear $\Xi$-variables required for the M-step is not straightforward as in the linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\Xi_3$, $\Xi_4$ and $\Xi_5$.
+However calculation of non-linear $\boldsymbol\Xi$-variables required for the M-step is not straightforward as in the linear case.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the estimated state, $\hat{\mathbf x}_t$ at each time instant, i.e.
@@
 
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\Xi$-variables can be calculated which provides an approximate lower bound on the log-likelihood function (see supporting information),
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which provides an approximate lower bound on the log-likelihood function (see supporting information),
 \begin{align}
-\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
- \Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+ \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
  \end{align}
@@
 \end{align}
-Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\Xi$-variables can be computed directly.
+Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.
 In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.

### 2011-04-27 ltx/data_paper/DataPaper.tex
minor edits to EM paer
added second derivative test for maximisation step in data paper

@@
 \end{align}
-Note that we ignore $\ln\mid\tilde{\boldsymbol\Sigma}_e\mid $ as it is not a function of the parameter set.
 
@@
 
-Consider first the maximisation of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
+Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, we can write
+\begin{equation}\label{eq:Qpartialxi}
+ \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5,
+\end{equation}
+setting \eqref{eq:Qpartialxi} to zero and solving for $\xi$ gives
+\begin{equation}
+ \xi=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
+\end{equation}
+In order to maximise $\mathcal{Q}$-function with respect to $\boldsymbol\theta$ we can write
 \begin{equation}\label{eq:Qpartialtheta}
@@
 \end{equation}
-The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
-In order to maximise $\mathcal{Q}$-function with respect to $\xi$ we can write
-\begin{equation}\label{eq:Qpartialxi}
- \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5,
-\end{equation}
-setting \eqref{eq:Qpartialxi} to zero and solving for $\xi$
-\begin{equation}
- \xi=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
-\end{equation}
-
-Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
 \begin{equation}
@@
 \end{align}
-The second derivative test confirms this is a maximum.
+In order to confirm calculated parameters are indeed maxima of the lower bound, the second derivative test is carried out for each parameter, giving
+\begin{alignat}{2}%(number of &)+1 divided by 2 here we have (3+1)/2
+ \frac{\partial \mathcal Q^2}{\partial^2\xi}&\biggr\rvert_{\xi=\hat{\xi}}&&=-\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \label{eq:SecondDerivativexi}\\
+ \frac{\partial \mathcal Q^2}{\partial^2\boldsymbol\theta}&\biggr\rvert_{\boldsymbol\theta=\hat{\boldsymbol\theta}}&&=-\frac{2}{\sigma_d^2}\boldsymbol\Xi_4 \label{eq:SecondDerivativetheta} \\
+ \frac{\partial \mathcal Q^2}{\partial^2\sigma_{\epsilon}^2}&\biggr\rvert_{\sigma_{\epsilon}=\hat{\sigma}_{\epsilon}}&&=-\frac{(T-1)n_y}{\hat{\sigma}_{\epsilon}^4} \label{eq:SecondDerivativenoise} \\
+ \frac{\partial \mathcal Q^2}{\partial^2\sigma_{d}^2}&\biggr\rvert_{{\sigma}_{d}=\hat{\sigma}_{d}}&&= -\frac{(T-1)n_x}{\hat{\sigma}_{d}^4} \label{eq:SecondDerivativedisturbance}
+\end{alignat}
+$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of state vectors, which is guaranteed by the disturbance, $\mathbf e$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore we have \cite{Coope1994}
+\begin{equation}
+ 0 < \mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \le \mathrm{tr}\left\lbrace \boldsymbol\Xi_2\right\rbrace \mathrm{tr}\left\lbrace\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace,
+\end{equation}
+hence \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum.
+Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
+\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativetheta} and \eqref{eq:SecondDerivativedisturbance}, disturbance estimates clearly represent maxima of the $\mathcal{Q}$-function.
 

### 2011-04-27 ltx/data_paper/DataPaper.tex
added second derivative test for maximisation step in data paper

@@
 \end{equation}
-hence \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum.
+meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum.
 Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
-\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativetheta} and \eqref{eq:SecondDerivativedisturbance}, disturbance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativetheta} and \eqref{eq:SecondDerivativedisturbance}, disturbance and noise estimates clearly represent maxima of the $\mathcal{Q}$-function.
 

### 2011-04-28 ltx/data_paper/DataPaper.tex

@@
 meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum.
-Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
-\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativetheta} and \eqref{eq:SecondDerivativedisturbance}, disturbance and noise estimates clearly represent maxima of the $\mathcal{Q}$-function.
+Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996},
+% to show this we define
+% \begin{equation}
+%  \boldsymbol\Psi(\mathbf r')=T_s\boldsymbol\Gamma^{-1}\tilde{\boldsymbol\Psi}(\mathbf r')
+% \end{equation}
+% where 
+% \begin{equation}\label{eq:DefPsitilde}
+% 	\left[ \tilde{\boldsymbol\Psi}(\mathbf{r}')\right]_{:i} =\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2c_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+% \end{equation}
+% since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
+\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
 
@@
 \end{align}
+\begin{equation}
+ \sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ji}\boldsymbol\lambda_t^{(j)}\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol\lambda_t^{(i)\top}
+\end{equation}
+
 Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.

### 2011-05-01 ltx/data_paper/DataPaper.tex
general edits to EM

@@
 The resulting parameters are then used when estimating the new
-state vector sequence for the next iteration. The stopping criterion is when the parameter estimates converge. or the log-likelihood variation.
+state vector sequence for the next iteration. The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
 \subsection{E-Step}
@@
 \begin{equation}
- 0 < \mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \le \mathrm{tr}\left\lbrace \boldsymbol\Xi_2\right\rbrace \mathrm{tr}\left\lbrace\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace,
+ \mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace >0,
 \end{equation}
@@
 \boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t(\mathbf r)\mathbf P_t \tilde{\Lambda}_t(\mathbf r)\right] \\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t\right] \\
  \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
@@
 \begin{align}
-	 \Lambda_t(\mathbf r)&=\begin{bmatrix}\boldsymbol \lambda_t^{(1)}(\mathbf r) & \boldsymbol \lambda_t^{(2)}(\mathbf r)& \dots &\boldsymbol \lambda_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambda}\\
-	 \boldsymbol\lambda_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi^\top(\mathbf r')\tilde{\boldsymbol\Sigma}_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'\label{eq:lambdai}\\
-	\tilde{\Lambda}_t(\mathbf r)&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_t^{(1)}(\mathbf r) \\ \tilde{\boldsymbol \lambda}_t^{(2)}(\mathbf r) \\ \vdots \\ \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)\end{bmatrix} \label{eq:Lambdatilde}\\
-	 \tilde{\boldsymbol \lambda}_t^{(i)}(\mathbf r)&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r' \label{eq:lambdatildei}
+	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r' \label{eq:lambdatildei}
 \end{align}
 \begin{equation}
- \sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ji}\boldsymbol\lambda_t^{(j)}\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol\lambda_t^{(i)\top}
+ \Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
 \end{equation}
@@
 	\item Will show parameter distributions
-	\item Will show parameter changes over time through the seizure
+	\item Will show lower bound
 \end{itemize}
@@
 \begin{itemize}
-	\item comment on how the e step is ukf and m step is kinda like the ekf.  
+	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate.  
 \end{itemize}

### 2011-05-04 ltx/data_paper/DataPaper.tex
edits to derivation of Xi4 in supporting informatiom
edits to product of two Gaussians derivation
added figures to data paper

@@
 where
-\begin{align}
-	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r' \label{eq:lambdatildei}
+\begin{align}\label{eq:lambdat} 
+	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
 \end{align}
+and
 \begin{equation}
- \Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
+ \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
 \end{equation}
@@
 % % ~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelWidthEstimation.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel support estimation}.}
+\label{fig:KernelWidthEstimation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelBasis.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}.}
+\label{fig:KernelBasis}
+\end{figure}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
+\end{center}
+\caption{{\bf Disturbance support estimation}.}
+\label{fig:DisturbanceWidthEstimation}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelEstimate.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
+\label{fig:KernelEstimates}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
+\end{center}
+\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
+\label{fig:KernelEstimateCrossSection}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/ConfedenceIntervel.pdf}
+\end{center}
+\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation}. An alternative figure which shows estimates outside confedence interval.}
+\label{figConfedenceIntervel}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/Histogram.pdf}
+\end{center}
+\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
+\label{fig:Histogram}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/Q.pdf}
+\end{center}
+\caption{{\bf Lower-bound of the log-likelihood}.}
+\label{fig:FieldObserations}
+\end{figure}
+
 % \begin{figure}[!ht]

### 2011-05-05 ltx/data_paper/DataPaper.tex
changed lower bound plot caption
minor edits

@@
 The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required.
-The former is used  for computing the smoother gain and the latter is used to compute required expected values in the M-step.
+The former is used  for computing the smoother gain and the latter is used to compute $\boldsymbol\Xi$ variables required  in the M-step.
 The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
@@
 \begin{equation}
- \xi=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
+ \hat{\xi}=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
 \end{equation}
@@
 \begin{equation}\label{eq:theta}
- \boldsymbol \theta=\boldsymbol\Xi_4^{-1}\left(\boldsymbol\Xi_3^\top-\xi\boldsymbol\Xi_5^\top \right).
+ \hat{\boldsymbol \theta}=\boldsymbol\Xi_4^{-1}\left(\boldsymbol\Xi_3^\top-\xi\boldsymbol\Xi_5^\top \right).
 \end{equation}
@@
 \begin{equation}
- \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
+ \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
 \end{equation}
@@
 \begin{align}
-\sigma_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+\hat{\sigma}_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
 2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right]
@@
 \end{center}
-\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}.}
+\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
 \label{fig:KernelBasis}
@@
 \end{center}
-\caption{{\bf Lower-bound of the log-likelihood}.}
+\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
 \label{fig:FieldObserations}

### 2011-05-05 ltx/data_paper/DataPaper.tex

@@
 \end{equation}
-where $e_t(\mathbf{r}) = \sigma_W[W\left( \mathbf{r},t+T_s \right)-W\left( \mathbf{r},t \right)]$ is the increment of a space-time Wiener process, $i.i.d.$ with zero spatial mean such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\sigma_W^2\gamma(\mathbf{r}-\mathbf{r}'))$.
-Here $\mathcal{GP}(\mathbf 0,T_s\sigma_W^2\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
+where $e_t(\mathbf{r}) = \sigma_W[W\left( \mathbf{r},t+T_s \right)-W\left( \mathbf{r},t \right)]$ is the increment of a space-time Wiener process, $i.i.d.$ with zero spatial mean such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\sigma_d^2\gamma(\mathbf{r}-\mathbf{r}'))$, where $\sigma_d^2=T_s\sigma_W^2$.
+Here $\mathcal{GP}(\mathbf 0,\sigma_d^2\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
 To reduce the model to a finite-dimensional system the neural field is approximated by a basis function decomposition where

### 2011-05-05 ltx/data_paper/DataPaper.tex
changed comment commands

@@
 \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\red}{\textcolor{red}}
-\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
+
+%\newcommand{\red}{\textcolor{red}}
+%\newcommand{\blue}{\textcolor{blue}}
 \newcommand{\cyan}{\textcolor{cyan}}
@@
 This class of model describes a continuous cortical sheet or surface, relating mean firing rates of pre and post-synaptic neural populations.
-The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the \red{(temporal convolution - I'd rather say integral equation	)} integral equation
+The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the \dean{(temporal convolution - I'd rather say integral equation	)} integral equation
 \begin{equation}
@@
 \cyan{small thing: are we using $\exp(x)$ or $e^x$ to represent exponential?}
-$\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function \blue{(you can keep it here if you wish as it doesn't change the integral equation because of the upper limit.
+$\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function \parham{(you can keep it here if you wish as it doesn't change the integral equation because of the upper limit.
 I would remove it)}.
 $g(\cdot)$ describes the mean firing rate.
-In practice, the firing rate can rarely be considered as a purely determinstic process because \red{(can someone write down why?)}.
+In practice, the firing rate can rarely be considered as a purely determinstic process because \dean{(can someone write down why?)}.
 We thus choose to introduce a spatially coloured space-time Wiener process $W(\mathbf{r},t)$ to model the flactuations in the mean firing rate and decompose $g(\cdot)$ as
@@
 As a result of the random component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process.
-Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \red{citation?}
+Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \dean{citation?}
 \begin{equation}
@@
 \begin{equation} \label{DifferentialEquationContTime}
- \textrm{d}v(\mathbf{r},t) + \zeta v(\mathbf{r},t)\textrm{d}t = \tilde{g}(\mathbf{r},t)\textrm{d}t + \textrm{d}W(\mathbf{r},t)  ~~~~ t \ge 0, v(\mathbf{r},0) = \red{GP?}
+ \textrm{d}v(\mathbf{r},t) + \zeta v(\mathbf{r},t)\textrm{d}t = \tilde{g}(\mathbf{r},t)\textrm{d}t + \textrm{d}W(\mathbf{r},t)  ~~~~ t \ge 0, v(\mathbf{r},0) = \cyan{GP?}
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol\Sigma_e \triangleq T_s\sigma_W^2\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+	\boldsymbol\Sigma_e \triangleq \sigma_d^2\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
 \end{equation}
@@
 \end{align}
-Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ (\dean{$\sigma_W$ notation from 18}) where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
+Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ (\dean{$\sigma_W$ notation from 18}\parham{I fixed it by defining $\sigma_d^2 =T_s\sigma^2_W$ in the model derivation}) where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
 By expanding the exponent and taking $2\ln$ we get
@@
 % since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
-\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+\parham{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
 

### 2011-05-05 ltx/data_paper/DataPaper.tex
added comment on discussion
added a comment on condition under which Xi4 is invertible

@@
 \end{equation}
-variable $\boldsymbol\Xi_4$ is symmetric and positive-definite by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
+noting that variable $\boldsymbol\Xi_4$ is symmetric by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
 \begin{equation}\label{eq:theta}
@@
 \end{equation}
-The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on.
+The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
+Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
 \begin{equation}
@@
 	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
+	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property (I guess) using EM with URTSS
 \end{itemize}

### 2011-05-05 ltx/data_paper/DataPaper.tex
added some notes on positive defeniteness of Xi4

@@
 meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum.
-Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996},
+Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
+The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is the set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}.
+(note that multiplying by $\mathbf \Gamma^{-1}$ doesnt change the rank).
+However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically making it difficult to calculate the rank of $q(\mathbf x_t)$ .
+Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration.
 % to show this we define
@@
 % since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
-\parham{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
 

### 2011-05-05 ltx/data_paper/DataPaper.tex
minor edits

@@
 The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters.
-In the E-step we estimate the states $\mathbf x_t$, of the systems and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, synaptic dynamic $\xi$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+In the E-step we estimate the states $\mathbf x_t$, of the system and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
 Once initialized, at each iteration the sequence of smoothed state vectors is used to update the parameters by maximizing an approximate lower bound on the log likelihood function.
@@
 \subsection{M-Step}
-The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma_d$ and the observation noise variance $\sigma_{\epsilon}$.
+The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
 \begin{equation}
-	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma_d, \sigma_{\epsilon}\right\rbrace 
+	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma^2_d, \sigma^2_{\epsilon}\right\rbrace 
 \end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.

### 2011-05-05 ltx/data_paper/DataPaper.tex
minor edits

@@
 Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
-The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is the set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}.
-(note that multiplying by $\mathbf \Gamma^{-1}$ doesnt change the rank).
-However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically making it difficult to calculate the rank of $q(\mathbf x_t)$ .
-Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration.
+The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}.
+(note that multiplying by $\mathbf \Gamma^{-1}$ doesn't change the rank).
+However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically, making it difficult to calculate the rank of $q(\mathbf x_t)$ .
+Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration of the E-step.
 % to show this we define

### 2011-05-07 ltx/data_paper/DataPaper.tex
changed the kernel estimate plot
added another plot for kernel support estimation
minor edit

--- 2011-05-05 ltx/data_paper/DataPaper.tex
@@
 
-\usepackage{amsmath,amssymb,amsfonts,epsfig} % Typical maths resource packages
+\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
 
-%\newif\ifpdf
-%\ifx\pdfoutput\undefined
-%\pdffalse % we are not running PDFLaTeX
-%\else
-%\pdfoutput=1 % we are running PDFLaTeX
-%\pdftrue
-%\fi
+\newif\ifpdf
+\ifx\pdfoutput\undefined
+\pdffalse % we are not running PDFLaTeX
+\else
+\pdfoutput=1 % we are running PDFLaTeX
+\pdftrue
+\fi
 
-% \ifpdf
-% \usepackage[pdftex]{graphicx}
-% \else
-% \usepackage{graphicx}
-% \fi
+\ifpdf
+\usepackage[pdftex]{graphicx}
+\else
+\usepackage{graphicx}
+\fi
 \usepackage{color}
 \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}
-
-%\newcommand{\red}{\textcolor{red}}
-%\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
 \newcommand{\cyan}{\textcolor{cyan}}
@@
 This class of model describes a continuous cortical sheet or surface, relating mean firing rates of pre and post-synaptic neural populations.
-The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the \dean{(temporal convolution - I'd rather say integral equation	)} integral equation
+The neural field, $v\left( {\mathbf{r},t} \right)$, at position $\mathbf{r}$ and time $t$, is the aggregated post-synaptic potentials described by the \red{(temporal convolution - I'd rather say integral equation	)} integral equation
 \begin{equation}
@@
 \cyan{small thing: are we using $\exp(x)$ or $e^x$ to represent exponential?}
-$\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function \parham{(you can keep it here if you wish as it doesn't change the integral equation because of the upper limit.
+$\zeta=\tau^{-1}$, $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function \blue{(you can keep it here if you wish as it doesn't change the integral equation because of the upper limit.
 I would remove it)}.
 $g(\cdot)$ describes the mean firing rate.
-In practice, the firing rate can rarely be considered as a purely determinstic process because \dean{(can someone write down why?)}.
+In practice, the firing rate can rarely be considered as a purely determinstic process because \red{(can someone write down why?)}.
 We thus choose to introduce a spatially coloured space-time Wiener process $W(\mathbf{r},t)$ to model the flactuations in the mean firing rate and decompose $g(\cdot)$ as
@@
 As a result of the random component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process.
-Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \dean{citation?}
+Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \red{citation?}
 \begin{equation}
@@
 \begin{equation} \label{DifferentialEquationContTime}
- \textrm{d}v(\mathbf{r},t) + \zeta v(\mathbf{r},t)\textrm{d}t = \tilde{g}(\mathbf{r},t)\textrm{d}t + \textrm{d}W(\mathbf{r},t)  ~~~~ t \ge 0, v(\mathbf{r},0) = \cyan{GP?}
+ \textrm{d}v(\mathbf{r},t) + \zeta v(\mathbf{r},t)\textrm{d}t = \tilde{g}(\mathbf{r},t)\textrm{d}t + \textrm{d}W(\mathbf{r},t)  ~~~~ t \ge 0, v(\mathbf{r},0) = \red{GP?}
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol\Sigma_e \triangleq \sigma_d^2\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
+	\boldsymbol\Sigma_e \triangleq T_s\sigma_W^2\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
 \end{equation}
@@
 \end{align}
-Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ (\dean{$\sigma_W$ notation from 18}\parham{I fixed it by defining $\sigma_d^2 =T_s\sigma^2_W$ in the model derivation}) where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
+Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ (\dean{$\sigma_W$ notation from 18}) where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
 By expanding the exponent and taking $2\ln$ we get
@@
 \end{equation}
-noting that variable $\boldsymbol\Xi_4$ is symmetric by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
+variable $\boldsymbol\Xi_4$ is symmetric and positive-definite by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
 \begin{equation}\label{eq:theta}
@@
 \end{equation}
-We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on.
-The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
-Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
 \begin{equation}
@@
 meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum.
-Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
-The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is the set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}.
-(note that multiplying by $\mathbf \Gamma^{-1}$ doesnt change the rank).
-However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically making it difficult to calculate the rank of $q(\mathbf x_t)$ .
-Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration.
+Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996},
 % to show this we define
@@
 % since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
-From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+\blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function.
 
@@
 	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate.  
-	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property (I guess) using EM with URTSS
 \end{itemize}

### 2011-05-07 ltx/data_paper/DataPaper.tex

--- 2011-05-05 ltx/data_paper/DataPaper.tex
@@
 
-\usepackage{amsmath,amssymb,amsfonts,epsfig} % Typical maths resource packages
+\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
 
-%\newif\ifpdf
-%\ifx\pdfoutput\undefined
-%\pdffalse % we are not running PDFLaTeX
-%\else
-%\pdfoutput=1 % we are running PDFLaTeX
-%\pdftrue
-%\fi
+\newif\ifpdf
+\ifx\pdfoutput\undefined
+\pdffalse % we are not running PDFLaTeX
+\else
+\pdfoutput=1 % we are running PDFLaTeX
+\pdftrue
+\fi
 
-% \ifpdf
-% \usepackage[pdftex]{graphicx}
-% \else
-% \usepackage{graphicx}
-% \fi
+\ifpdf
+\usepackage[pdftex]{graphicx}
+\else
+\usepackage{graphicx}
+\fi
 \usepackage{color}
@@
 \begin{center}
+\includegraphics{./Figures/KernelBasis1.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
+\label{fig:KernelBasis1}
+\end{figure}
+\begin{figure}[!ht]
+\begin{center}
 \includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
@@
 \label{fig:KernelEstimateCrossSection}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/ConfedenceIntervel.pdf}
-\end{center}
-\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation}. An alternative figure which shows estimates outside confedence interval.}
-\label{figConfedenceIntervel}
 \end{figure}

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to result section

@@
 \begin{align}
- \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \\
- \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t,
+ \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \label{eq:StateEq} \\
+ \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t,\label{eq:OutputEq}
 \end{align}
@@
 \section{Estimation Algorithm}
-Here we describe the problem of estimating non-linear state-space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
+Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
 The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters.
@@
 \section{Results}
+This section demonstrates the identification of the proposed IDE model using simulated data.
+Data is generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$  , assuming the observed field can be fully
+described by the decomposed IDE model.
+100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state.
+The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ .
+The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations.
+The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$.
+The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively.
+The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.
 \begin{itemize}

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to Result section

@@
 
-\subsection{Estimating Support For Connectivity Kernel}
+\subsection{Correlation analysis}\label{subsec:CorrAnal}
 Under the assumption that the sensors are not spatially band-limiting the spectral content of the field and the connectivity kernel is homogeneous, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations.
@@
 This section demonstrates the identification of the proposed IDE model using simulated data.
-Data is generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$  , assuming the observed field can be fully
-described by the decomposed IDE model.
+The observation noise and disturbance were unknown and no assumption were made on the shape of the kernel.
+Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state.
@@
 The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.
+
+The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function.
+In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equation () and () were set to zero in correlation analysis.
+By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, however, an approximate of their support can be still extracted.
+In fact, the estimated support for the disturbance covariance function was very accurate.
+The estimates of the connectivity kernel and disturbance support were normalised and thresholded for values less than 0.01.
+The result of the correlation analysis for the connectivity kernel is shown in Figure.\ref{fig:KernelWidthEstimation}.
+The red circle shows the estimated support which encompasses the non-zero values after thresholding.
+The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}.
+By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor,$\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
+
 \begin{itemize}
@@
 	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property (I guess) using EM with URTSS
+	\item itterative EM and correlation analysis (maybe)
 \end{itemize}
@@
 % % ~~~~~~~~~~~~~~~~
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelBasis1.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
+\label{fig:KernelWidthEstimation}
+\end{figure}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
+\end{center}
+\caption{{\bf Disturbance support estimation}.}
+\label{fig:DisturbanceWidthEstimation}
+\end{figure}
 \begin{figure}[!ht]
@@
 \caption{{\bf Connectivity kernel support estimation}.}
-\label{fig:KernelWidthEstimation}
+\label{fig:KernelWidthEstimation1}
 \end{figure}
@@
 \label{fig:KernelBasis}
-\end{figure}
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelBasis1.pdf}
-\end{center}
-\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
-\label{fig:KernelBasis1}
-\end{figure}
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
-\end{center}
-\caption{{\bf Disturbance support estimation}.}
-\label{fig:DisturbanceWidthEstimation}
 \end{figure}

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to Result section

@@
 \end{equation}
-\section{Estimation Algorithm}
+\section{Estimation Algorithm}\label{sec:EstimationAlgorithm}
 Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
@@
 The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function.
-In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equation () and () were set to zero in correlation analysis.
-By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, however, an approximate of their support can be still extracted.
+In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero in correlation analysis.
+By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
 In fact, the estimated support for the disturbance covariance function was very accurate.
@@
 The result of the correlation analysis for the connectivity kernel is shown in Figure.\ref{fig:KernelWidthEstimation}.
-The red circle shows the estimated support which encompasses the non-zero values after thresholding.
+The red circle shows the estimated support which encompasses the non-zero values (black area) after thresholding.
 The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}.
 By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor,$\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
+
+The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
+A $5 \times 5$ square grid of basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$.
+This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.
+The true and estimated connectivity kernel over 100 realisations are shown in Figure~\ref{fig:KernelEstimates}.
+Cross-sections of the estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}.
+The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+The large standard deviation is due to the high number of parameters need to be estimated.
 
@@
 \end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{figure}[!ht]
@@
 \end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelEstimate.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
+\label{fig:KernelEstimates}
+\end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
+\end{center}
+\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
+\label{fig:KernelEstimateCrossSection}
+\end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
 \begin{figure}[!ht]
@@
 \label{fig:KernelBasis}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelEstimate.pdf}
-\end{center}
-\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
-\label{fig:KernelEstimates}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
-\end{center}
-\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
-\label{fig:KernelEstimateCrossSection}
 \end{figure}
@@
  \renewcommand{\arraystretch}{1}
+\clearpage
 \newpage

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to Result section

@@
 This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.
-The true and estimated connectivity kernel over 100 realisations are shown in Figure~\ref{fig:KernelEstimates}.
-Cross-sections of the estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}.
-The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+The true and estimated connectivity kernel for 100 Monte Carlo simulations are shown in Figure~\ref{fig:KernelEstimates}.
+Cross-sections of the connectivity kernel estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}.
+The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel is inside the confidence interval.
 The large standard deviation is due to the high number of parameters need to be estimated.
+Figure~\ref{fig:Histogram} depicts the histogram of parameter estimates from 100 simulations where the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
+These histograms indicate small bias in parameter estimates with a very small standard deviation.
 
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/Histogram.pdf}
+\end{center}
+\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
+\label{fig:Histogram}
+\end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/Q.pdf}
+\end{center}
+\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
+\label{fig:FieldObserations}
+\end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@
 \label{fig:KernelBasis}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/Histogram.pdf}
-\end{center}
-\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
-\label{fig:Histogram}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/Q.pdf}
-\end{center}
-\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
-\label{fig:FieldObserations}
 \end{figure}

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to Result section
added Neural field estimates plot
commented out extra figures
minor edits to result section

@@
 The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function.
-In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero in correlation analysis.
+In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero.
 By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
@@
 The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
-A $5 \times 5$ square grid of basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$.
+A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$.
 This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.
@@
 \begin{center}
+\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
+\end{center}
+\caption{{\bf Field Estimates}. }
+\label{fig:FieldEstimates}
+\end{figure}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\begin{center}
 \includegraphics{./Figures/Q.pdf}
@@
 \caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
-\label{fig:FieldObserations}
+\label{fig:LowerBound}
 \end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelWidthEstimation.pdf}
-\end{center}
-\caption{{\bf Connectivity kernel support estimation}.}
-\label{fig:KernelWidthEstimation1}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelBasis.pdf}
-\end{center}
-\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
-\label{fig:KernelBasis}
-\end{figure}
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/KernelWidthEstimation.pdf}
+% \end{center}
+% \caption{{\bf Connectivity kernel support estimation}.}
+% \label{fig:KernelWidthEstimation1}
+% \end{figure}
+% 
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/KernelBasis.pdf}
+% \end{center}
+% \caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
+% \label{fig:KernelBasis}
+% \end{figure}
 

### 2011-05-12 ltx/data_paper/DataPaper.tex
added convergence to the results

@@
 These histograms indicate small bias in parameter estimates with a very small standard deviation.
+Examples of neural field reconstruction are given in Figure.~\ref{fig:FieldEstimates}.
+The figure shows snapshots at three time instants of the true neural field and the estimated field.
+In each subplot neural activity is plotted against spatial index in 1D to provide a comparision between true and the estimated underlying fields.
+Plot of lower bound of the log likelihood versus iterations of the EM is shown in Figure.~\ref{fig:LowerBound}.
+In general, for the non-linear dynamical systems the actual lower bound can not be claculated analytically, therefore the approximate of the lower bound obtained by URTSS is shown.
+The change in lower bound drops below 0.009 percent after 15 iterations, confirming
+that the algorithm converged to steady parameter values.
 

### 2011-05-12 ltx/data_paper/DataPaper.tex
added computational complexity

@@
 In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
+The computational complexity of the algorithm is given ib Table
+ \begin {table}
+\begin{center}
+\scalebox{1}{\begin{tabular}{lll}
+\hline \hline
+Variable &Order&Order of the approximate\\ \hline\\
+$\Xi_0, \Xi_1, \Xi_2$&$O(Tn_x^2)$&-\\
+$\Xi_3, \Xi_5$&$O(Tn_x^3)+O(Tn_x^2n_{\theta})$&$O(Tn_x^3n_r^2)+O(Tn_x^2n_{\theta}n_r^2)$ \\
+$\Xi_4$&$O(Tn_x^3n_{\theta})+O(Tn_x^2n_{\theta}^2)$&$O(Tn_x^3n_{\theta}n_r^2)+O(Tn_x^2n_{\theta}^2n_r^2)$\\
+$\hat{\boldsymbol\theta} $&$O(n_{\theta}^3)$&-\\
+$\hat{\xi}$&$O(n_x^3+n_{\theta}^3)$&-\\
+ $\hat{\sigma}_{\epsilon}^2$&$O(Tn_y^2n_x^2)$&-\\
+$\hat{\sigma}_{d}^2$&$O(Tn_x^3)+O(Tn_{\theta}^3)&-$\\
+\hline \hline
+\end{tabular}}
+ \caption {Computational complexity of EM algorithm} 
+\label{table:BsplineConvolutionandInnerproduct}
+\end{center}
+\end {table}
 
@@
 This section demonstrates the identification of the proposed IDE model using simulated data.
-The observation noise and disturbance were unknown and no assumption were made on the shape of the kernel.
+The observation noise and disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the kernel.
 Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.

### 2011-05-12 ltx/data_paper/DataPaper.tex
added computational complexity

--- 2011-05-12 ltx/data_paper/DataPaper.tex
@@
 In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
+The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
+ \begin {table}
+\begin{center}
+\scalebox{1}{\begin{tabular}{lll}
+\hline \hline
+Variable &Order&Order of the approximate\\ \hline\\
+$\Xi_0, \Xi_1, \Xi_2$&$O(Tn_x^2)$&-\\
+$\Xi_3, \Xi_5$&$O(Tn_x^3)+O(Tn_x^2n_{\theta})$&$O(Tn_x^3n_r^2)+O(Tn_x^2n_{\theta}n_r^2)$ \\
+$\Xi_4$&$O(Tn_x^3n_{\theta})+O(Tn_x^2n_{\theta}^2)$&$O(Tn_x^4n_{\theta}n_r^2)+O(Tn_x^3n_{\theta}^2n_r^2)$\\
+$\hat{\boldsymbol\theta} $&$O(n_{\theta}^3)$&-\\
+$\hat{\xi}$&$O(n_x^3+n_{\theta}^3)$&-\\
+ $\hat{\sigma}_{\epsilon}^2$&$O(Tn_y^2n_x^2)$&-\\
+$\hat{\sigma}_{d}^2$&$O(Tn_x^3)+O(Tn_{\theta}^3)$&-\\
+\hline \hline
+\end{tabular}}
+ \caption {Computational complexity of EM algorithm} 
+\label{table:ComputationalComplexity}
+\end{center}
+\end {table}
 

### 2011-05-13 ltx/data_paper/DataPaper.tex
edits to EM section

@@
 Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
-The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters.
-In the E-step we estimate the states $\mathbf x_t$, of the system and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
-Once initialized, at each iteration the sequence of smoothed state vectors is used to update the parameters by maximizing an approximate lower bound on the log likelihood function.
-The resulting parameters are then used when estimating the new
-state vector sequence for the next iteration. The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
+EM is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
+Both the E and the M steps of the EM algorithm increase a lower bound on the log-likelihood function of the parameters given the observed field.
+In the E-step we estimate the state $\mathbf x_t$, of the system given the observed field and current estimate of the model parameters to calculate expected log-likelihood.
+In the M-step we estimate the system parameters by maximising the expected log-likelihood computed in the E-step.
+The resulting parameters are then used to estimate the distribution of the state vector sequence for the next iteration.
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
 \subsection{E-Step}
-In the E-step the additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
+In state space models, E-step corresponds to solving the smoothing problem, i.e.
+estimating the states of the system, $\mathbf x_t$ given all observations and the parameters of the system.
+The smoother output is then used to calculate the expected log-likelihood function required in M-step.
+The non-linear behaviour of the state-space neural field described in \eqref{eq:StateEq} requires a non-linear smoother to be employed for state estimation in the E-step.
+% In order to caulculate the expected log-likelihood in the E-step the smoothed states of the system is required.
+An additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used to estimate the approximate state distribution in the E-step.
+% It can be shown that the maximum in the E-step occurs when the state distribution is exactly $p(\mathbf X\mid \mathbf Y;\boldsymbol \theta')$, the conditional distribution of X, given all observations and the current value of the parameter estimates which corresponds to solving the smoothing problem.
+\subsubsection{State estimation}
+The additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation.
 The URTSS incorporates an unscented Kalman filter (UKF) \cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$.
@@
 The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required.
-The former is used  for computing the smoother gain and the latter is used to compute $\boldsymbol\Xi$ variables required  in the M-step.
+The former is used  for computing the smoother gain and the latter is used to compute expected log-likelihood.
 The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
 
-\subsection{M-Step}
-The goal of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
-\begin{equation}
-	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma^2_d, \sigma^2_{\epsilon}\right\rbrace 
-\end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
-Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}.
-We proceed by expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$
-\begin{equation}\label{eq:jointdistribution}
- p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \sigma_d)p(\mathbf x_0).
-\end{equation}
-The standard form of the lower bound of the log-likelihood or $\mathcal{Q}$ function, is defined as   
+\subsubsection{Expected log-likelihood} 
+It is well known that the expected joint data log likelihood $\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$, forms a lower bound on the log-likelihood function $\ln p(\mathbf Y;\boldsymbol\Theta)$, where $\mathbf X$ and $\mathbf Y$ are set of all states and the set of all observations respectively and $\boldsymbol \Theta$ denotes the set of all system parameters.
+Therefore we can write
 \begin{align}\label{eq:QFunction}
@@
 \end{align}
-where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta')$, and $\boldsymbol \Theta'$ is the current parameter estimates.
+where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the distribution $p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$) which is marginal distribution of the state estimates conditioned on observed field and current estimate of the parameter set $\boldsymbol\Theta'$, i.e.
+smoother output.
 The factor of $2$ is included to simplify the derivation in the later steps.
-Using the chain rule of probability theory (relationship between conditional and joint) we can right
-\begin{equation}
-	... \nonumber
+We proceed by expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ as
+\begin{equation}\label{eq:jointdistribution}
+ p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi, \sigma_d)p(\mathbf x_0).
 \end{equation}
- Substituting equations \ref{eq:jointdistribution} in \ref{eq:QFunction} gives
+ Substituting equations \eqref{eq:jointdistribution} in \eqref{eq:QFunction} gives
 \begin{align}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta.
-\sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta,\xi, \sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
 \end{align}
- It should be noted that the last term is not a function of parameter set and can be ignored, therefore $\mathcal Q$-function can be rewritten as
+ It should be noted that the last term is not a function of parameter set and can be dropped, therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}\label{eq:QIntermsofJointDist}
-\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)\right].
+\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi ,\sigma_d)\right].
 \end{equation}
-Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions (ignoring the normalising factor of these conditional distributions)
+Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions, where the normalising factors are ignored 
 \begin{align}
@@
 \end{align}
-Note that $\boldsymbol\Sigma_e=\sigma_d^2\tilde{\boldsymbol\Sigma}_e$ (\dean{$\sigma_W$ notation from 18}\parham{I fixed it by defining $\sigma_d^2 =T_s\sigma^2_W$ in the model derivation}) where $\tilde{\boldsymbol\Sigma}_e$ is constant and can be calculated beforehand as the support of the disturbance covariance function is assumed to be known.
+Note that the disturbance covariance matrix can be written as a product of the unknown parameter, $\sigma_d^2$ and a constant matrix, $\tilde{\boldsymbol\Sigma}_e$ where the constant part is calculated using the estimated support from the correlation analysis.
 By expanding the exponent and taking $2\ln$ we get
@@
 \end{align}
-\dean{Dean to check expansion.} Now we rearrange the equation so we can write down (or isolate (reason for doing this step is..)) the cross-covariance etc so we can use the information from the filter.
-Taking trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\dean{Dean to check expansion.} Now we rearrange the equation so we can  use the information from the smoother.
+(or isolate (reason for doing this step is..)) the cross-covariance etc.
+Taking trace and rearranging, using the invariant cyclic permutations property of the trace, thess distributions can be written as
 \begin{align}\label{eq:Qfunctiontrace1}
@@
 \end{align}
-
-Substituting  \ref{eq:Qfunctiontrace1} and \ref{eq:Qfunctiontrace2} into \ref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives the lower-bound that needs to be maximised to gain optimal parameter estimates,
+Substituting  \eqref{eq:Qfunctiontrace1} and \eqref{eq:Qfunctiontrace2} into \eqref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives the lower-bound which is to be maximised in the M-step.
 \begin{align}\label{eq:Voldermont}
@@
 \end{align}
-It should be noted that the second term in equation \ref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation, $\mathbf E_{\boldsymbol\Theta'}\left[ .\right]$, ref(Shumway).
-By choosing
+The second term in \eqref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1}.
+By defining $\Xi$-variables as
 \begin{align}
@@
  \end{align}
-equation \ref{eq:Voldermont} can be written as
+equation \eqref{eq:Voldermont} can be written as
 \begin{align}\label{eq:VoldermontwitXivariables}
@@
 \end{align}
+Covariance and cross-covariances in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
+Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e.
+$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using the following expressions \cite{Gibsona2005} (see supporting information for details)
+\begin{align}
+	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0}, \\
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1}, \\
+\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+ \end{align}
+However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
+This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.
+\begin{equation}\label{eq:SigmoidTaylor}
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)
+\end{equation}
+where 
+\begin{equation}\label{eq:SigmoidDerivative}
+ f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\right)
+\end{equation}
+substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the estimated state $\hat{\mathbf{x}}_t$ 
+\begin{equation}\label{eq:qTaylor}
+ q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
+\end{equation}
+Define
+\begin{equation}
+	e(x) = q(x) - q_L(x) \nonumber
+\end{equation}
 
+Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
+
+Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
+\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
+
+Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which provides an approximate lower bound on the log-likelihood function (see supporting information),
+\begin{align}
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t\right] \\
+ \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+ \end{align}
+where
+\begin{align}\label{eq:lambdat} 
+	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
+\end{align}
+and
+\begin{equation}
+ \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
+\end{equation}
+
+Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.
+In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
+The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
+
+\subsection{M-Step}
+The objective of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
                                                                                                                                                                                                                                                                                                                                                                                                                                                                             Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, we can write
@@
 From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function. 
-
-Computing unknown variables, $\boldsymbol\Theta$, in the maximization step requires calculation of covariance and  cross-covariance terms, including both linear, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
-Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be obtained using smoother outputs, $\hat{\mathbf x}_t $, $\mathbf P_t$ and $\mathbf M_t$ using the following expressions \cite{Shumway2000} (see supporting information for details)
-\begin{align}
-	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0}, \\
-\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1}, \\
-\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
- \end{align}
-However calculation of non-linear $\boldsymbol\Xi$-variables required for the M-step is not straightforward as in the linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
-This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the estimated state, $\hat{\mathbf x}_t$ at each time instant, i.e.
-\begin{equation}\label{eq:SigmoidTaylor}
- f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)
-\end{equation}
-where 
-\begin{equation}\label{eq:SigmoidDerivative}
- f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\right)
-\end{equation}
-substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the estimated state $\hat{\mathbf{x}}_t$ 
-\begin{equation}\label{eq:qTaylor}
- q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
-\end{equation}
-Define
 \begin{equation}
-	e(x) = q(x) - q_L(x) \nonumber
-\end{equation}
-
-Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
-
-Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
-\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
-
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which provides an approximate lower bound on the log-likelihood function (see supporting information),
-\begin{align}
-\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t\right] \\
- \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
- \end{align}
-where
-\begin{align}\label{eq:lambdat} 
-	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
-\end{align}
-and
-\begin{equation}
- \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
-\end{equation}
-
-Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.
-In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
-The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
-In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
+	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma^2_d, \sigma^2_{\epsilon}\right\rbrace 
+\end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
+Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}.
  \begin {table}
@@
 	\item itterative EM and correlation analysis (maybe)
+	\item{comment on EM might convrge to suboptimal solution,simulated
+annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
 \end{itemize}

### 2011-05-13 ltx/data_paper/DataPaper.tex
edits to EM section

@@
 \begin{align}
-	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}+\mathbf{\hat x}_{t+1}\mathbf{\hat x}_{t+1}^\top\right)\label{eq:defofXi0}, \\
-\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:defofXi1}, \\
-\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}^b+\mathbf{\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\right)\label{eq:defofXi0}, \\
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:defofXi1}, \\
+\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).
  \end{align}
@@
 \begin{equation}\label{eq:SigmoidTaylor}
- f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^b\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)
 \end{equation}
@@
 \begin{equation}\label{eq:SigmoidDerivative}
- f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right)\right)
+ f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)\right)
 \end{equation}
-substituting \ref{eq:SigmoidTaylor} in \ref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the estimated state $\hat{\mathbf{x}}_t$ 
+substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ 
 \begin{equation}\label{eq:qTaylor}
- q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t\right) d\mathbf{r}'
-\end{equation}
-Define
-\begin{equation}
-	e(x) = q(x) - q_L(x) \nonumber
+ q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t^b\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right) d\mathbf{r}'
 \end{equation}
 
-Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
-
-Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
-\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
-
-Having approximated $q\left(\mathbf x_t\right)$ in the E-step, by substituting  \ref{eq:qTaylor} into equations \ref{eq:Xi3}-\ref{eq:Xi5} an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which provides an approximate lower bound on the log-likelihood function (see supporting information),
+Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which in turn provides an approximate lower bound on the log-likelihood function (see supporting information),
 \begin{align}
@@
 Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.
-In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
 The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
@@
 
+Define
+\begin{equation}
+	e(x) = q(x) - q_L(x) \nonumber
+\end{equation}
+
+Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
+
+Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
+\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
 \subsection{M-Step}
-The objective of the M-step is to maximize a lower bound on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
+% In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
+The objective of the M-step is to maximize the lower bound found in E-step, whcich consequenly increases the log-likelihood function $p(\mathbf Y;\boldsymbol\Theta)$.
+% on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
                                                                                                                                                                                                                                                                                                                                                                                                                                                                             Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, we can write
@@
 \end{center}
-\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
+\caption{{\bf Connectivity kernel support estimate.} The estimated support of the kernel is shown by the red circle.
+Black area shows the non-zero values of the support after thresholding.
+A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
 \label{fig:KernelWidthEstimation}

### 2011-05-13 ltx/data_paper/DataPaper.tex
got rid of extra bits

@@
 \dean{I will do the connectivity kernel decomposition bit after the correlation analysis, because we can use it to say something about heterogeneity and isotropy.}
-
-\subsection{Data Collection and Pre-processing}
-
-Data was collected from a patient undergoing work-up for surgical resection of epileptic brain tissue.
-The standard procedure for the resective surgery involves implantation of subdural electrodes for intracranial EEG monitoring (iEEG).
-Data from these electrodes provide information for mapping functional and pathological tissue to define the surgical margins.
-In addition to standard iEEG electrodes, data was collected in parallel from a Neuroport system (Blackrock microsystems, Utah, USA) incorporating a micro-electrode array.
-This data was collected with informed consent from the patient under ethics approval from the MGH human research ethics committee..??
-Figure~\ref{MRI_CT} shows the position of the iEEGs electrodes and the micro-electrode array.
-The iEEG electrode covers the temporal lobe, and the micro-electrode placement was targeted at..
-The micro-electrode array consisted of square grid of 96 (10 by 10 with the corner electrodes missing).
-The x,y electrode spacing was 400~$\mu m$, yielding a coverage of 4 by 4~mm.
-Data from the Neuroport system was acquired with a sampling rate of 30~kHz, with hardware filters in the range of~\dean{??}.
-
-During the time-course of the iEEG monitoring period, several seizures were recorded. This study focuses on the local field potential (LFP) data recorded with the micro-electrode during a seizure.
-
-The first pre-processing step was to identify channels that had very poor signal quality.
-These channels were set to the $nan$ data type.
-Following this, the data was re-referenced to a common average montage to remove common mode artifact and the effect of the reference electrode.
-Next the data was low-pass filtered with a cut-off frequency of 100~Hz.
-The data was then resampled from 30~kHz to 5~kHz.
-To enable spatial visualisation and spatial frequency analysis, the corrupted channels that were set to $nan$, were interpolated using data from all neighbouring channels.
-
-\subsection{Spatiotemporal Data Analysis}
-The first 8 channels of the LFP time series from the seizure is shown in Figure~\ref{fig:TimeSeries}.
-For the analysis, the time series was segmented into three periods; the pre-seizure period, seizure period and post-seizure period.
-The seizure onset is marked by the red dotted line and the seizure end is marked by the blue dashed line.
-
-An example to illustrate the spatial aspects of the observed neural field is shown in Figure~\ref{fig:FieldObserations}.
-Each subplot in the figure shows the observed field at a sample of the pre-processed data, with each plot separated in time by 2.5~ms.
-The figure shows spatially correlated activity.
-
-The spectral properties of the recorded time series for each of the time segments are shown in Figure~\ref{fig:TemporalFreqObservation}.
-Each plot shows the averaged (across channels) spectrum of the data.
-The pre-seizure period shows a decay in power at a typical $1/f^2$ rate.
-The seizure period has higher power at low and high ends of the spectrum.
-In addition, there is a peak in the power of the LFPs at ~51~Hz during the seizure.
-This peak would be difficult to observe in European, Asian and other countries due to the 50~Hz mains power frequency.
-The post-seizure period shows a large increase in lower frequency power...
-
-Figure~\ref{fig:SpatialFreqObservation} shows the results of spatial frequency analysis of the observed neural field.
-Throughout this paper the spatial frequency shall be denoted by $\nu$.
-Each subplot is the average (across time) spatial frequency during either the pre-seizure, seizure or post-seizure periods.
-The spatial frequency of the neural field is governed by disturbances (inputs from outside the field) and the underlying connectivity structure.
-The symmetry in the plots provides some evidence for homogeneous and isotropic connectivity.
-
-Figure~\ref{fig:DiagSpatialFreqObservation} shows diagonal cross-sections of the spatial frequency plots.
-From this figure we can see that the spatial cut-off frequency (-3~dB point) is $\nu_c \approx 0.26$~Hz.
-The profile of the diagonal cross-section indicates that the field is adequately sampled from the micro-electrode array, where the power drops by approximately 25~dB at the maximum observable spatial frequency (according to Shannon's sampling theorem) indicating spatial aliasing will have an insignificant effect on the sampled data.
-The spatial cut-off frequency provides information on the complexity of the model required to represent the neural field.
-Considering the field is band-limited, we can represent it by a finite set of continuous basis functions.
-According the Shannon's sampling theorem, the minimum spacing between basis functions, $\Delta_{\phi}$, to describe the field is
-\begin{equation}\label{eq:BasisFunctionSeparation}
-	\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{c}}
-\end{equation}
-where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation.
 

### 2011-05-13 ltx/data_paper/DataPaper.tex
edit to plot captions

@@
 \end{center}
-\caption{{\bf Connectivity kernel support estimate.} The estimated support of the kernel is shown by the red circle.
+\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle.
 Black area shows the non-zero values of the support after thresholding.
@@
 \end{center}
-\caption{{\bf Disturbance support estimation}.}
+\caption{{\bf Disturbance support approximation}. }
 \label{fig:DisturbanceWidthEstimation}
@@
 \end{center}
-\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
+\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations}
 \label{fig:KernelEstimates}
@@
 \end{center}
-\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
+\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively.
+Each of the estimate from Monte Carlo simulation is shown with black line.
+The 95\% confidence intervals are shown by shaded red area.}
 \label{fig:KernelEstimateCrossSection}

### 2011-05-13 ltx/data_paper/DataPaper.tex
edit to plot captions

@@
 \end{center}
-\caption{{\bf Synaptic dynamic parameter and hyperparameter estimates}.}
+\caption{{\bf Histograms of the parameter estimates over 100 realizations}.
+The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively.
+(A) The histogram of the synaptic dynamic parameter, $\xi$.
+(B) The histogram of the observation noise variance, $\sigma_{\epsilon}$.
+(C) The histogram of the disturbance noise variance, $\sigma_d^2$}.
 \label{fig:Histogram}

### 2011-05-14 ltx/data_paper/DataPaper.tex
edit to plot captions
changed the title

@@
 
-\title{Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data}
+\title{Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm}
 \author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
@@
 The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required.
-The former is used  for computing the smoother gain and the latter is used to compute expected log-likelihood.
+The former is used  for computing the smoother gain and the latter is used to compute expected log-likelihood function.
 The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.
@@
 \subsubsection{Expected log-likelihood} 
-It is well known that the expected joint data log likelihood $\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$, forms a lower bound on the log-likelihood function $\ln p(\mathbf Y;\boldsymbol\Theta)$, where $\mathbf X$ and $\mathbf Y$ are set of all states and the set of all observations respectively and $\boldsymbol \Theta$ denotes the set of all system parameters.
+It is well known that the expected joint data log likelihood $\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$, forms a lower bound on the log-likelihood function $\ln p(\mathbf Y;\boldsymbol\Theta)$, where $\mathbf X$ and $\mathbf Y$ are set of all states and the set of all observations respectively and $\boldsymbol \Theta$ denotes the set of all system parameters, i.e.
+\begin{equation}
+	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma_d, \sigma_{\epsilon}\right\rbrace 
+\end{equation}
  Therefore we can write
@@
 (or isolate (reason for doing this step is..)) the cross-covariance etc.
-Taking trace and rearranging, using the invariant cyclic permutations property of the trace, thess distributions can be written as
+Taking trace and rearranging, using the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
 \begin{align}\label{eq:Qfunctiontrace1}
@@
 Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e.
-$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using the following expressions \cite{Gibsona2005} (see supporting information for details)
+$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using following expressions \cite{Gibsona2005} (see supporting information for details)
 \begin{align}
@@
  \end{align}
-However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
+However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in linear case.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.
@@
 \end{equation}
-
-Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which in turn provides an approximate lower bound on the log-likelihood function (see supporting information),
+Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated (see supporting information) which in turn provides an approximate lower bound on the log-likelihood function,
 \begin{align}
@@
 \end{equation}
-
-Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.
+By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete.
+The lower bound now can be used in M-step to find a set of new parameters.
 The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
-In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
+In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found elsewhere \cite{Sarkka2010}.
 
@@
 \end{equation}
-We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on.
-The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
-Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
 \begin{equation}
@@
 \end{equation}
-A second derivative test shows that this is indeed the maximum. Finally differentiating with respec to $\sigma_d^2$ we get
+Finally differentiating with respec to $\sigma_d^2$ we get
 \begin{align}
@@
 \end{align}
-setting above to zero and solving for $\sigma_e^2$ we have
+setting above to zero and solving for $\sigma_d^2$ we have
 \begin{align}
@@
 From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function. 
-\begin{equation}
-	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma^2_d, \sigma^2_{\epsilon}\right\rbrace 
-\end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly.
-Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}.
+%  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 
  \begin {table}
@@
 \end {table}
-
 \section{Results}
@@
 	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
-	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property (I guess) using EM with URTSS
+	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property than using EM with URTSS
 	\item itterative EM and correlation analysis (maybe)
@@
 annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
+	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
 \end{itemize}
@@
 \end{center}
-\caption{{\bf Field Estimates}. }
+\caption{{\bf Neural field estimates at different time instants}. In each subplot, true (gray line) and reconstructed neural field (red dots) are plotted versus spatial index.}
 \label{fig:FieldEstimates}

### 2011-05-14 ltx/data_paper/DataPaper.tex
minor edit
minor edits

@@
 \begin{align}
-\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
-\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t\right] \\
- \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right]
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\Lambda_t\right] \\
+ \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right]
  \end{align}
@@
 \begin{align}\label{eq:lambdat} 
-	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
+	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r'
 \end{align}
@@
 \begin{equation}
- \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
+ \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
 \end{equation}
@@
 The lower bound now can be used in M-step to find a set of new parameters.
-The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+An approximate for computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+Note that computational complexity of the nonlinear terms depend on the number of points, $n_r$ used for spatial discritisation.
 In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found elsewhere \cite{Sarkka2010}.
@@
 $\Xi_0, \Xi_1, \Xi_2$&$O(Tn_x^2)$&-\\
-$\Xi_3, \Xi_5$&$O(Tn_x^3)+O(Tn_x^2n_{\theta})$&$O(Tn_x^3n_r^2)+O(Tn_x^2n_{\theta}n_r^2)$ \\
-$\Xi_4$&$O(Tn_x^3n_{\theta})+O(Tn_x^2n_{\theta}^2)$&$O(Tn_x^4n_{\theta}n_r^2)+O(Tn_x^3n_{\theta}^2n_r^2)$\\
+$\Xi_3, \Xi_5$&$O(Tn_x^2n_{\theta})$&$O(Tn_x^2n_r^2)+O(Tn_xn_{\theta}n_r^2)$ \\
+$\Xi_4$&$O(Tn_x^2n_{\theta})+O(Tn_xn_{\theta}^2)$&$O(Tn_x^4n_{\theta}n_r^2)+O(Tn_x^3n_{\theta}^2n_r^2)$\\
 $\hat{\boldsymbol\theta} $&$O(n_{\theta}^3)$&-\\

### 2011-05-14 ltx/data_paper/DataPaper.tex
minor edits

@@
 \begin{align}
-\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \\
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \\
 \boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\Lambda_t\right] \\
@@
 where
+\begin{equation}
+ \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
+\end{equation}
+and
 \begin{align}\label{eq:lambdat} 
@@
 \end{align}
-and
-\begin{equation}
- \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
-\end{equation}
 By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete.
@@
 % since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
-From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance covariance estimates clearly represent maxima of the $\mathcal{Q}$-function. 
+From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function. 
 %  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 

### 2011-05-14 ltx/data_paper/DataPaper.tex
minor edits

@@
 $\Xi_0, \Xi_1, \Xi_2$&$O(Tn_x^2)$&-\\
-$\Xi_3, \Xi_5$&$O(Tn_x^2n_{\theta})$&$O(Tn_x^2n_r^2)+O(Tn_xn_{\theta}n_r^2)$ \\
-$\Xi_4$&$O(Tn_x^2n_{\theta})+O(Tn_xn_{\theta}^2)$&$O(Tn_x^4n_{\theta}n_r^2)+O(Tn_x^3n_{\theta}^2n_r^2)$\\
+$\Xi_3, \Xi_5$&$O(Tn_x^2n_{\theta})$&$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
+$\Xi_4$&$O(Tn_x^2n_{\theta})+O(Tn_xn_{\theta}^2)$&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_xn_{\theta}n_r)$\\
 $\hat{\boldsymbol\theta} $&$O(n_{\theta}^3)$&-\\
@@
 \end{center}
-\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations}
+\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations.}
 \label{fig:KernelEstimates}
@@
 (B) The histogram of the observation noise variance, $\sigma_{\epsilon}$.
-(C) The histogram of the disturbance noise variance, $\sigma_d^2$}.
+(C) The histogram of the disturbance noise variance, $\sigma_d^2$.}
 \label{fig:Histogram}
@@
 \end{center}
-\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
+\caption{{\bf Convergence of the EM algorithm.} The mean of the lower bound of the log-likelihood function over 100 realisations.
+The change in lower bound drops below 0.009 percent after 15 iterations}
+%  $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$
 \label{fig:LowerBound}

### 2011-05-16 ltx/data_paper/DataPaper.tex
minor edits
minor edit to results

@@
 	\boldsymbol\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\label{eq:defofXi0} \\
-\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:defofXi1} \\
-\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\\
+\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:Xi1} \\
+\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\label{eq:Xi2}\\
 \boldsymbol\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \label{eq:Xi3} \\	
@@
 \begin{align}
-	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}^b+\mathbf{\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\right)\label{eq:defofXi0}, \\
-\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:defofXi1}, \\
-\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).
+	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}^b+\mathbf{\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\right)\label{eq:Xi0Gibson}, \\
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi1Gibson}, \\
+\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).\label{eq:Xi2Gibson}
  \end{align}
@@
 \begin{align}
-\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \\
-\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\Lambda_t\right] \\
- \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right]
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi3Ap}\\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\Lambda_t\right]\label{eq:Xi4Ap} \\
+ \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi5Ap}
  \end{align}
@@
 setting \eqref{eq:Qpartialxi} to zero and solving for $\xi$ gives
-\begin{equation}
+\begin{equation}\label{eq:xihat}
  \hat{\xi}=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
@@
 noting that variable $\boldsymbol\Xi_4$ is symmetric by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
-\begin{equation}\label{eq:theta}
+\begin{equation}\label{eq:thetahat}
  \hat{\boldsymbol \theta}=\boldsymbol\Xi_4^{-1}\left(\boldsymbol\Xi_3^\top-\xi\boldsymbol\Xi_5^\top \right).
@@
 setting above to zero and solving for $\sigma_{\epsilon}^2$ gives
-\begin{equation}
+\begin{equation}\label{eq:sigmaepsilonhat}
  \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
@@
 setting above to zero and solving for $\sigma_d^2$ we have
-\begin{align}
+\begin{align}\label{eq:sigmadhat}
 \hat{\sigma}_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
@@
 \hline \hline
-Variable &Order&Order of the approximate\\ \hline\\
-$\Xi_0, \Xi_1, \Xi_2$&$O(Tn_x^2)$&-\\
-$\Xi_3, \Xi_5$&$O(Tn_x^2n_{\theta})$&$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
-$\Xi_4$&$O(Tn_x^2n_{\theta})+O(Tn_xn_{\theta}^2)$&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_xn_{\theta}n_r)$\\
-$\hat{\boldsymbol\theta} $&$O(n_{\theta}^3)$&-\\
-$\hat{\xi}$&$O(n_x^3+n_{\theta}^3)$&-\\
- $\hat{\sigma}_{\epsilon}^2$&$O(Tn_y^2n_x^2)$&-\\
-$\hat{\sigma}_{d}^2$&$O(Tn_x^3)+O(Tn_{\theta}^3)$&-\\
+Variable &Equation&Order\\ \hline\\
+$\Xi_0, \Xi_1, \Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
+$\Xi_3, \Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)+O(Tn_{\theta}n_r^2)$ \\
+$\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r^2)$\\
+$\hat{\xi}$&\eqref{eq:xihat}&$O(n_x^3+n_{\theta}^3)$\\
+$\hat{\boldsymbol\theta} $&\eqref{eq:thetahat}&$O(n_{\theta}^3)$\\
+$\hat{\sigma}_{\epsilon}^2$&\eqref{eq:sigmaepsilonhat}&$O(Tn_x^2n_y)+O(Tn_xn_y^2)$\\
+$\hat{\sigma}_{d}^2$&\eqref{eq:sigmadhat}&$O(n_x^3)+O(n_{\theta}^2)$\\
 \hline \hline
@@
 In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero.
-By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
+By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as a prerequisite for the EM algorithm, however, an approximate of their support can be still extracted.
 In fact, the estimated support for the disturbance covariance function was very accurate.
@@
 that the algorithm converged to steady parameter values.
-
-\begin{itemize}
-	\item Will show parameter distributions
-	\item Will show lower bound
-      \end{itemize}
-
 \section{Discussion}

### 2011-07-07 ltx/data_paper/DataPaper.tex
edits to EM for data paper

@@
 Taking trace and rearranging, using the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
+\parham{In the next step the above equation is rearranged in order to isolate the covariance and the cross-covariance terms, enabling the use of smoother outputs.
+Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become}
 \begin{align}\label{eq:Qfunctiontrace1}

### 2011-07-10 ltx/data_paper/DataPaper.tex
edits to EM section

--- 2011-05-16 ltx/data_paper/DataPaper.tex
@@
  Substituting equations \eqref{eq:jointdistribution} in \eqref{eq:QFunction} gives
-\begin{align}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta,\xi, \sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
+\begin{align}\label{eq:EM-QwithInitialstates}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta,\xi, \sigma_d) \right.\nonumber \\
+&\left.+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
 \end{align}
- It should be noted that the last term is not a function of parameter set and can be dropped, therefore $\mathcal Q$-function can be rewritten as
+ The last term on the right-hand side of \eqref{eq:EM-QwithInitialstates} can be omitted as it does not depend on the parameter set, therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}\label{eq:QIntermsofJointDist}
@@
 \end{equation}
-Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions, where the normalising factors are ignored 
+Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions, where the normalising factors are ignored since scaling by a constant coefficient does not alter the location of the maximum with respect to the parameters.
 \begin{align}
  p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right),\\
-p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \exp \left(-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right)
+p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \nonumber \\
+&\times\exp \left(-\frac{1}{2}(\mathbf x_{t+1}-\mathbf q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\mathbf q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right).
 \end{align}
-Note that the disturbance covariance matrix can be written as a product of the unknown parameter, $\sigma_d^2$ and a constant matrix, $\tilde{\boldsymbol\Sigma}_e$ where the constant part is calculated using the estimated support from the correlation analysis.
+Note that disturbance covariance matrix, $\boldsymbol\Sigma_e$, can be written as the product of the unknown parameter, $\sigma_d^2$ with the constant matrix, $\tilde{\boldsymbol\Sigma}_e$, where the constant part can be  calculated using the estimated support for disturbance covariance function, $\gamma$ from the correlation analysis (see equation \eqref{eq:EM-MMGFourier2}).
 By expanding the exponent and taking $2\ln$ we get
 \begin{align}\label{eq:CondititionDist1}
-2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],  \\
-2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
-&-\frac{1}{\sigma_e^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t.
-\label{eq:CondititionDist2}
+2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],
 \end{align}
-\dean{Dean to check expansion.} Now we rearrange the equation so we can  use the information from the smoother.
-(or isolate (reason for doing this step is..)) the cross-covariance etc.
-Taking trace and rearranging, using the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
+\begin{align}
+2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}\nonumber \\
+&+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta 
++\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
+&-\frac{1}{\sigma_e^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta\nonumber \\
+&-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
+\end{align}
+In the next step the above equation is rearranged in order to isolate the covariance and the cross-covariance terms, enabling the use of smoother outputs.
+Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
 \begin{align}\label{eq:Qfunctiontrace1}
-  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace    \\
- 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
-&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace.
-\label{eq:Qfunctiontrace2}
+  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace
+\end{align}
+\begin{align}
+ 2 \ln &p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) =-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta \nonumber \\
+&+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta \nonumber \\
+&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace. \label{eq:Qfunctiontrace2}
 \end{align}
@@
 \begin{align}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&= -(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right]\boldsymbol\theta
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2\nonumber \\
+& -\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\right]\boldsymbol\theta
  \nonumber \\
-&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right]\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \boldsymbol\theta
+&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  \mathbf q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right]\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)  \right] \boldsymbol\theta.
 \end{align}
-The second term in \eqref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1}.
+The third term in \eqref{eq:Voldermont} is obtained using the same method in \cite{Shumway2000}, i.e.
+by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1} .
 By defining $\Xi$-variables as
@@
 	\boldsymbol\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\label{eq:defofXi0} \\
-\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:Xi1} \\
-\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\label{eq:Xi2}\\
-\boldsymbol\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \label{eq:Xi3} \\	
-\boldsymbol\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right] \label{eq:Xi4}\\
- \boldsymbol\Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \label{eq:Xi5}
+\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:defofXi1} \\
+\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\label{eq:defofXi2}\\
+\boldsymbol\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\right] \label{eq:defofXi3} \\	
+\boldsymbol\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  \mathbf q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1} \mathbf q(\mathbf x_t)\right] \label{eq:defofXi4}\\
+ \boldsymbol\Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)  \right] \label{eq:defofXi5}
  \end{align}
-equation \eqref{eq:Voldermont} can be written as
+equation \eqref{eq:Voldermont} can be written in a form of
 \begin{align}\label{eq:VoldermontwitXivariables}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\boldsymbol\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace
  \nonumber \\
-&+\frac{2}{\sigma_d^2}\boldsymbol\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \boldsymbol\Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2}\boldsymbol \Xi_{5} \boldsymbol\theta.
+&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\boldsymbol\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\boldsymbol\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \boldsymbol\Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2}\boldsymbol \Xi_{5} \boldsymbol\theta.
 \end{align}
-Covariance and cross-covariances in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
+Covariance and cross-covariance terms in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
 Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e.
-$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using following expressions \cite{Gibsona2005} (see supporting information for details)
+$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ \cite{Gibsona2005}.
+To show how it can be done, the smoothed covariance matrix at time $t+1$ can be written as
+\begin{align}
+ \mathbf P_{t+1}^b&=\mathbf E_{\Theta'}\left[(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)^{\top}\right]=\mathbf E_{\theta'}\left[\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]-\mathbf {\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\label{eq:EM-PrimeryXi0derivation1}\\
+ \mathbf M_{t+1}^b&=\mathbf E_{\Theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t^b)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)^{\top}\right]= \mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf {\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top},\label{eq:EM-PrimeryXi1derivation1}
+\end{align}
+consequently,
+\begin{align}\label{eq:EM-Xi0derivation1}
+ \mathbf E_{\Theta'}\left[\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\mathbf P_{t+1}^b+\mathbf {\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\\
+ \mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}^b+\mathbf {\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\label{eq:EM-Xi1derivation1},
+\end{align}
+substituting \eqref{eq:EM-Xi0derivation1} and \eqref{eq:EM-Xi1derivation1} in \eqref{eq:defofXi0} and \eqref{eq:defofXi1} respectively , gives the final formula for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$, i.e.
 \begin{align}
 	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}^b+\mathbf{\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\right)\label{eq:Xi0Gibson}, \\
-\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi1Gibson}, \\
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi1Gibson}.
+\end{align}
+The expression for $\boldsymbol\Xi_{2}$ can be derived in a similar manner, giving
+\begin{align}
 \boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).\label{eq:Xi2Gibson}
@@
 However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $\mathbf q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.
 \begin{equation}\label{eq:SigmoidTaylor}
- f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^b\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^b\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right),
 \end{equation}
 where 
-\begin{equation}\label{eq:SigmoidDerivative}
- f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)\right)
+\begin{align}\label{eq:SigmoidDerivative}
+ f'(\boldsymbol \phi^\top\left(\mathbf r'\right)&\hat{\mathbf x}_t^b)= \frac{\varsigma}{\left(1 + \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right)\right)^2} \times \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right) \nonumber \\
+=&\frac{\varsigma}{1 + \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right)} \times \left(1-\frac{1}{1 + \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right)}\right) \nonumber \\
+=& \varsigma f(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b)\left( 1-f(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right).
+\end{align}
+substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained
+\begin{equation}\label{eq:qTaylor}
+ \mathbf q(\mathbf x_t) \approx \mathbf q(\hat{\mathbf x}_t^b)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right) d\mathbf{r}'.
 \end{equation}
-substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ 
-\begin{equation}\label{eq:qTaylor}
- q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t^b\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right) d\mathbf{r}'
+Having approximated $\mathbf q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:defofXi3}-\ref{eq:defofXi5}) an approximation to the non-linear $\boldsymbol\Xi$-variables can be made.
+The three nonlinear variables are dealt with in turn.
+To start with, first consider equation \eqref{eq:defofXi3}, substituting in equation \eqref{eq:qTaylor} for $\mathbf q\left(\mathbf x_t\right)$, the term under the summation can be approximated by
+\begin{align}\label{eq:Xi3Derivation1}
+ \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t) &\approx \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}',
+\end{align}
+noting that $\phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)$ is a scalar, equation \eqref{eq:Xi3Derivation1} can be rewritten as 
+\begin{align}\label{eq:Xi3Derivation2}
+ \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\approx\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}',
+\end{align}
+taking expected value of \eqref{eq:Xi3Derivation2} gives
+\begin{align}\label{eq:Xi3Derivation3}
+ \mathbf E_{\boldsymbol\Theta'}\left[\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\right] &\approx \mathbf E_{\boldsymbol\Theta'}\left[\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b) \nonumber \\
+&+\int_\Omega \boldsymbol \phi^\top(\mathbf r')  \mathbf E_{\boldsymbol\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}',
+\end{align}
+Substituting for  $\mathbf E_{\boldsymbol\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\right]$ from equation \eqref{eq:EM-PrimeryXi1derivation1} and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
+\begin{equation}
+\boldsymbol\Xi_{3}\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right].
+\label{eq:Xi3Ap} \\
 \end{equation}
-Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated (see supporting information) which in turn provides an approximate lower bound on the log-likelihood function,
+To find an approximation for $\boldsymbol\Xi_4$, the same approach is applied by using \eqref{eq:qTaylor} for the nonlinear experession in equation \eqref{eq:defofXi4} giving
+\begin{align}\label{eq:Xi4derivation1}
+ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)&\approx \left[ \mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right]^\top  \times \tilde{\boldsymbol\Sigma}_e^{-1}\nonumber \\
+&\times\left[ \mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \nonumber \\
+&= \mathrm{term1} + \mathrm{term2} + \mathrm{term3} + \mathrm{term4}
+\end{align}
+where
 \begin{align}
-\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi3Ap}\\
-\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\Lambda_t\right]\label{eq:Xi4Ap} \\
- \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi5Ap}
+  \mathrm{term1}&=\mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)
+\end{align}
+\begin{align}
+\mathrm{term2}=&\mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
+ \end{align}
+\begin{align}
+\mathrm{term3}=&\int_\Omega \boldsymbol{\Psi}^\top(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)
+\end{align}
+\begin{align}\label{eq:-EMterm4}
+ \mathrm{term4} &=\int_\Omega \boldsymbol{\Psi}^\top(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}' \times \tilde{\boldsymbol  \Sigma}_e^{-1} \nonumber \\
+&\times \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}' 
+\end{align}
+It should be noted that when applying expectation, term1 is constant, and term2 and term3 disapears as $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\right]= \mathbf 0$.
+However in term4 to use the covariance estimate from the smoother the $\mathbf{x}_t$ terms should be brought together.
+To do this equation \eqref{eq:-EMterm4} can be rewritten as
+\begin{align}
+ term4 &= \int_\Omega \boldsymbol{\Psi}^\top(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) \boldsymbol \phi^\top(\mathbf r')(\mathbf x_t - \mathbf  {\hat x}_t^b)d\mathbf{r}' \times \tilde{\boldsymbol\Sigma}_e^{-1} \nonumber \\
+&\times\int_\Omega  (\mathbf x_t - \mathbf  {\hat x}_t^b)^\top\boldsymbol \phi(\mathbf r') \boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'& \nonumber \\
+&=\sum_{i,j=1}^{n_x}{\boldsymbol\Lambda}_t^{(i)\top}(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b)\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
+\end{align}
+where
+\begin{align}
+	{\boldsymbol \Lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r' \label{eq:lambdatildei}.
+\end{align}
+Now taking expectation from \eqref{eq:Xi4derivation1} gives
+\begin{align}\label{eq:Xi4derivation2}
+  \mathbf{E}_{\boldsymbol\Theta'}\left[ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right] &= \mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
+&+\sum_{i,j=1}^{n_x}{\boldsymbol\Lambda}_t^{(i)\top}\mathbf{E}_{\boldsymbol\Theta'}\left[(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b)\right] \tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
+\end{align}
+and noting $\mathbf E_{\boldsymbol\theta'}\left[(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b) \right]=\left[\mathbf{P}_t^b\right]_{i,j} $ gives
+\begin{align}
+ \mathbf{E}_{\boldsymbol\Theta'}\left[ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right]&= \mathbf q^\top(\mathbf {\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t)+\boldsymbol\varLambda_t
 \end{align}
@@
 \begin{equation}
- \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
+ \boldsymbol\varLambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\Lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
 \end{equation}
-and
-\begin{align}\label{eq:lambdat} 
-	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r'
+and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
+\begin{align}
+ \boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[\mathbf q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf \mathbf q(\mathbf{\hat x}_t^b)+\boldsymbol\varLambda_t\right]\label{eq:Xi4Ap}.
+\end{align}
+Finally, to calculate $\boldsymbol\Xi_5$, the nonlinear term can be treated in a smae way, using the expression for $\mathbf q(\mathbf x_t)$ in \eqref{eq:defofXi5} and rearranging gives
+\begin{align}\label{eq:Xi5derivation1}
+ \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\approx\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
+\end{align}
+taking expected value of \eqref{eq:Xi5derivation1} gives
+\begin{align}\label{eq:Xi5derivation2}
+\mathbf E_{\Theta'}\left[\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf q(\mathbf x_t)\right]&\approx\mathbf E_{\Theta'}\left[\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
+&+\int_\Omega \boldsymbol \phi^\top(\mathbf r') \mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
+\end{align}
+substituting for $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right] $ from equation \eqref{eq:EM-PrimeryXi0derivation1} at time $t$, and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ gives
+\begin{align}
+\boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi5Ap}
  \end{align}
@@
 In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found elsewhere \cite{Sarkka2010}.
-
-Define
-\begin{equation}
-	e(x) = q(x) - q_L(x) \nonumber
-\end{equation}
-
-Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
-
-Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
-\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
 \subsection{M-Step}
 % In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
-The objective of the M-step is to maximize the lower bound found in E-step, whcich consequenly increases the log-likelihood function $p(\mathbf Y;\boldsymbol\Theta)$.
+The objective of the M-step is to maximize the computed lower bound in E-step, whcich consequenly increases the log-likelihood function $p(\mathbf Y;\boldsymbol\Theta)$.
 % on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
@@
 \begin{equation}\label{eq:xihat}
- \hat{\xi}=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
+ \hat{\xi}=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}.
 \end{equation}
@@
 \begin{equation}
-  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
+  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace,
 \end{equation}
@@
 \begin{equation}\label{eq:sigmaepsilonhat}
- \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
+ \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace.
 \end{equation}
@@
 \begin{align}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace  \nonumber \\
-&-\frac{2}{\sigma_d^4}\boldsymbol\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \boldsymbol\Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \boldsymbol\Xi_5 \boldsymbol\theta 
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace  \nonumber \\
+&+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace-\frac{2}{\sigma_d^4}\boldsymbol\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \boldsymbol\Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \boldsymbol\Xi_5 \boldsymbol\theta,
 \end{align}
@@
 \begin{align}\label{eq:sigmadhat}
-\hat{\sigma}_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
-2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right]
+\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace\right.\nonumber \\ &\left.-2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right].
 \end{align}
@@
 (note that multiplying by $\mathbf \Gamma^{-1}$ doesn't change the rank).
-However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically, making it difficult to calculate the rank of $q(\mathbf x_t)$ .
-Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration of the E-step.
-% to show this we define
-% \begin{equation}
-%  \boldsymbol\Psi(\mathbf r')=T_s\boldsymbol\Gamma^{-1}\tilde{\boldsymbol\Psi}(\mathbf r')
-% \end{equation}
-% where 
-% \begin{equation}\label{eq:DefPsitilde}
-% 	\left[ \tilde{\boldsymbol\Psi}(\mathbf{r}')\right]_{:i} =\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2c_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
-% \end{equation}
-% since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
+However, $\mathbf q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically, making it difficult to calculate the rank of $\mathbf q(\mathbf x_t)$ .
+Therefore, we recommend to check the rank of $\mathbf q(\mathbf x_t)$ at each iteration of the E-step.
+
 From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function. 

### 2011-07-10 ltx/data_paper/DataPaper.tex
edits to correlation analysis

@@
 
-Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods of the seizure progression.
-By averaging over time, the effect of the disturbance is reduced allowing for the support of the kernel to be seen.
-The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition.
-The plots indicate the support for excitatory aspect of the kernel centred at the origin is -2~mm to 2~mm in the $x$ direction and slightly wider in the $y$ direction.
-Although the kernel is not isotropic, we will approximate it as being isotropic.
-This is for computation reasons.
-
-The assumption of homogeneity was tested by performing the cross-correlation analysis on 4 equal sized subsections of the field observations.
-The subsections consisted $6\times6$ electrode grids, such that they overlapped by one electrode row and column.
-The overlap was required so the subsections where large enough for the support of the kernel to be seen in the cross-correlation analysis.
-The results of the analysis can be seen in Figure~\ref{fig:HomogeneityTest}.
-The results show that each subsection of the field has similar cross-correlations, with each subplot showing local excitation with surround inhibition.
-From this analysis, we will approximate the connectivity kernel as being homogeneous.
-
+\subsubsection{Estimation of Connectivity Kernel Support}
+For the derivation of the spatial properties estimator of the neural field equations a more compact notation is employed to define convolution and correlation operators.
+The spatial convolution shall be denoted as
+\begin{equation}
+	\int_\Omega a(\mathbf{r}-\mathbf{r}')b(\mathbf{r}')d\mathbf{r}' = (a\ast b)(\mathbf{r}),
+\end{equation}
+and the spatial cross-correlation shall be denoted as 
+\begin{equation}
+	\int_\Omega a(\mathbf{r})b(\mathbf{r}+\boldsymbol{\iota})d\mathbf{r} = (a\star b)(\boldsymbol{\iota}),
+\end{equation} 
+where $\iota$ is the spatial shift.
+The spatial relationship between consecutive observations is governed by the shape of the connectivity kernel.
+Therefore, the spatial cross-correlation between consecutive observations is used to estimate the kernel's support and shape.
+To begin the derivation the spatial cross-correlation between consecutive observations (in time) is defined as
+\begin{equation}
+	R_{y_{t+1}y_t}(\boldsymbol{\iota}) = \left(y_{t+1}\star y_t\right)\left(\boldsymbol{\iota}\right),
+\end{equation}
+ The aim of the derivation is to make the necessary substitutions and simplifications to get an expression of the cross-correlation as a function of the connectivity kernel.
+In the next step equation~\eqref{eq:EM-ObservationEquation} is substituted for $y_{t+1}(\mathbf{r})$ and expanded to give
+\begin{equation}
+	R_{y_{t+1}y_t}\left(\boldsymbol{\iota}\right) = \left(\left(m \ast v_{t+1}\right)\star y_t\right)\left(\boldsymbol{\iota}\right) + \left(\varepsilon_{t+1} \star y_t\right)\left(\boldsymbol{\iota}\right).
+\end{equation}
+Next equation~\eqref{eq:EM-DiscreteTimeModel} is substituted for $v_{t+1}(\mathbf{r})$ giving 
+\begin{align}
+	R_{y_{t+1}y_t}(\boldsymbol{\iota}) &= (\left(m \ast \left(\xi v_t +  T_s g_t + e_t\right)\right) \star y_t)(\boldsymbol{\iota})\\
+	&= \xi\left(\left(m \ast v_t\right) \star y_t \right)(\boldsymbol{\iota}) \nonumber\\
+	&\quad+ T_s \left(\left(m\ast g_t\right)\star y_t \right)(\boldsymbol{\iota}) \nonumber\\
+	&\quad+ \left(\left(m\ast e_t\right)\star y_t \right)(\boldsymbol{\iota}) \nonumber\\
+	&\quad+ (\varepsilon_{t+1} \star y_t)(\boldsymbol{\iota}).
+\end{align}
+Now the expectation over time is taken, so that the observation noise and process disturbance terms have minimal effect on the result, giving 
+\begin{align}\label{eq:EM-ExpectationToCancelNoise}
+	\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})] &= \mathbf{E}[\xi\left(\left(m \ast v_t\right) \star y_t \right)(\boldsymbol{\iota})] + T_s \mathbf{E}[\left(\left(m\ast g_t\right)\star y_t \right)(\boldsymbol{\iota})],
+\end{align}
+since the disturbance and measurement noise are assumed to be independent of the observations and temporally white. 
+The cross-correlation is further simplified by recognizing that the first term on right hand side of equation~\eqref{eq:EM-ExpectationToCancelNoise} can be written as 
+\begin{align}
+	\mathbf{E}[\xi&\left(\left(m \ast v_t \right) \star y_t \right)(\boldsymbol{\iota})] = \mathbf{E}\left[\xi\left(\left(y_t-\varepsilon_t\right) \star y_t \right)(\boldsymbol{\iota})\right] \nonumber \\
+	&= \xi \mathbf{E}\left[ (y_t \star y_t)(\boldsymbol{\iota}) - \left(\varepsilon_t\star y_t \right)(\boldsymbol{\iota})\right] \nonumber \\
+	&= \xi\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})  - \left(\varepsilon_t \star (m\ast v_t + \varepsilon_t)\right) (\boldsymbol{\iota})] \nonumber \\
+	&=\xi\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota}) -\left(\varepsilon_t\star (m\ast v_t)\right)(\boldsymbol{\iota}) - (\varepsilon_t\star\varepsilon_t)(\boldsymbol{\iota})] \nonumber \\
+	&= \xi\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right), \label{eq:EM-FirstTermReduced}
+\end{align}
+where $\delta\left(\cdot\right)$ denotes Kronecker delta. Substituting equation~\eqref{eq:EM-FirstTermReduced} back into equation~\eqref{eq:EM-ExpectationToCancelNoise} gives
+\begin{align}\label{eq:EM-SimplifiedFirstTerm}
+	\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})] &= \xi\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)+ T_s\mathbf{E}[ \left(\left(m\ast g_t\right)\star y_t \right)(\boldsymbol{\iota})].
+\end{align}
+Next we simplify second term in equation~\eqref{eq:EM-SimplifiedFirstTerm} to get an expression involving the connectivity kernel.
+By substituting equation~\eqref{eq:EM-RateBasedInteractions} for $g_t$ we can write
+\begin{equation}\label{eq:EM-before_linearization}
+	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) = T_s((w \ast m\ast f(v_t)) \star y_t)(\boldsymbol\iota).
+\end{equation}
+The remainder of the derivation is focused on isolating the connectivity kernel. To show how this is done, the activation function is assumed to be in the linear region, i.e 
+ \begin{equation}
+	f\left(v_t(\mathbf{r})\right) \approx \varsigma v_t(\mathbf{r})
+\end{equation} 
+Substituting the linear activation function back into equation~\eqref{eq:EM-before_linearization} yields
+\begin{align}\label{eq:EM-after_linearization1}	
+	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) &\approx T_s\varsigma((w \ast m\ast v_t) \star y_t)(\boldsymbol\iota).
+\end{align}
+Now by substituting $y_t - \varepsilon_t$ in for $m\ast v_t$ equation \eqref{eq:EM-after_linearization1} can be written as 
+\begin{align}
+	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) &\approx T_s\varsigma(w\ast (y_t - \varepsilon_t)) \star y_t (\boldsymbol\iota)
+\end{align}
+To isolate the kernel, the order of the convolution and cross-correlation is reversed by recognizing that a property $(a \ast b)(\boldsymbol\iota) \star c(\boldsymbol\iota) = a(-\boldsymbol\iota)\ast(b \star c)(\boldsymbol\iota)$ \parham{(see Appendix for proof)}.
+Therefore,
+\begin{align}
+	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) &\approx T_s\varsigma w(-\boldsymbol\iota) \ast ((y_t - \varepsilon_t)) \star y_t)(\boldsymbol\iota),
+\end{align}
+Now using the identity established to get equation~\eqref{eq:EM-FirstTermReduced} gives
+\begin{equation}\label{eq:EM-second_term_reduced}
+	T_s\mathbf{E}\left[((m \ast g_t) \star y_t)(\boldsymbol\iota)\right] \approx T_s\varsigma w(-\boldsymbol\iota) \ast  (\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))
+\end{equation}
+Now substituting back equation~\eqref{eq:EM-second_term_reduced} into equation~\eqref{eq:EM-SimplifiedFirstTerm} gives
+\begin{align}\label{eq:EM-SimplifiedXcorr}
+	\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})] &= \xi\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)\nonumber \\
+&+T_s\varsigma w(-\boldsymbol\iota) \ast  (\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))
+\end{align}
+Rearranging equation~\eqref{eq:EM-SimplifiedXcorr} gives
+\begin{align}
+	 w(-\boldsymbol\iota) \ast  (\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))&=\frac{1}{T_s\varsigma}\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]-\frac{\xi}{T_s\varsigma}\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)\nonumber \\
+\end{align}
+The solution of the above equation for the connectivity kernel is a deconvolution.
+This can be approached from a number of different standpoints.
+The simplest solution is to use the convolution theorem and to solve for the kernel algebraically in the frequency domain.
+\begin{align}\label{eq:EM-XcorrFourier}
+	\mathcal{F}\{w(-\boldsymbol\iota)\} \mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\} &\approx \frac{1}{T_s\varsigma}\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\nonumber \\
+&-\frac{\xi}{T_s\varsigma}\mathcal{F} \{\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)\}.
+\end{align}
+Now rearranging \eqref{eq:EM-XcorrFourier} gives
+\begin{equation}\label{eq:EM-Fourier_TF_of_Kernel}
+	\mathcal{F}\left(w(-\boldsymbol\iota)\right) = \frac{1}{T_s\varsigma }\left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\}}-\xi\right].
+\end{equation}
+From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect estimate in the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion would be insignificant.
+The denominator in equation \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of noise free observations which is non-negative and real.
+This important result is known as Weiner-Khintchine (W-K) theorem in signal processsing which states that the power spectral density of the wide sense stationary process is the Fourier transform of it's autocorrelation function \cite{Ricker2003}.
+The numerator is also called the cross spectrum or cross spectral density.
+Since the connectivity kernel is a real function, the following relation holds \cite{Bracewell2000}
+\begin{equation}
+ \mathcal{F}\left(w(\boldsymbol\iota)\right)=\overline{\mathcal{F}\left(w(-\boldsymbol\iota)\right)},
+\end{equation}
+where over-bar denotes complex conjugate operator. Finally, an expression for the kernel is obtained by taking the inverse Fourier tranform 
+\begin{equation}\label{eq:KernelSolution}
+	w(\boldsymbol\iota) = \frac{1}{T_s\varsigma }\mathcal{F}^{-1}\overline{\left\{\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2 }-\xi\right\}}.
+\end{equation}
+Complex conjugate operator essentially reflects the connectivity kernel through the origin in the spatial domain, therefore, if the connectivity kernel is isotropic, the complex conjugate operator can be dropped.
+% Alternatively, the convolution can be written as a system of linear equations by forming the convolution (Toeplitz) matrix.
+The solution of the convolution equation for $w(\cdot)$ can then be found by either inverting the convolution matrix or directly solving the system of equations.
+% Directly solving the system is the most numerically stable and less computationally demanding then inverting the convolution matrix.
+To show this we take the spatial Fourier transform of both sides of equation~\ref{} giving
+\subsubsection{Estimation of Disturbance Covariance Support}
+The observation auto-correlation at time $t+1$ can be expressed as
+\begin{equation}
+	R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})=(y_{t+1} \star y_{t+1})(\boldsymbol\iota).
+\end{equation}
+Substituting equation~\eqref{eq:EM-ObservationEquation} in for $y_{t+1}$ and expanding gives
+\begin{align}\label{eq:EM-expanded_auto_corr}
+	R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota}) &= \xi((m \ast v_{t}) \star y_{t+1})(\boldsymbol{\iota}) +T_s((m\ast g_{t})\star y_{t+1})(\boldsymbol{\iota}) \nonumber \\
+	&+((m\ast e_{t})\star  y_{t+1})(\boldsymbol{\iota})+(\varepsilon_{t+1} \star y_{t+1})(\boldsymbol{\iota}).
+\end{align}
+By using similar arguments that were used in the derivation for the connectivity kernel support, the autocorrelation can be simplified by recognizing that
+\begin{align}\label{eq:EM-Autoterm1}
+  \mathbf{E}[\xi((m\ast v_{t})\star y_{t+1})(\boldsymbol{\iota})]&=\xi \mathbf{E}[ R_{y_ty_{t+1}}(\boldsymbol{\iota})],
+\end{align}
+and
+\begin{align}\label{eq:EM-Autoterm2}
+	T_s\mathbf{E}[((m\ast g_t) \star y_{t+1})(\boldsymbol\iota)] &\approx T_s\varsigma\mathbf{E}[((m \ast w )\star y_{t+1})(\boldsymbol\iota)] \nonumber\\
+	&= T_s\varsigma w(-\boldsymbol\iota) \ast (\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] ).
+\end{align}
+\begin{align}\label{eq:EM-Autoterm3}
+ \mathbf{E}[(\varepsilon_{t+1}\star y_{t+1})(\boldsymbol\iota)]&=\sigma_{\varepsilon}^2\delta(\boldsymbol{\iota}),
+\end{align}
+Substituting equations~\eqref{eq:EM-Autoterm1}, \eqref{eq:EM-Autoterm2}, and ~\eqref{eq:EM-Autoterm3} back into equation~\eqref{eq:EM-expanded_auto_corr} gives
+\begin{align}\label{eq:EM-Auto&CrossNoisy}
+	\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})] &= \xi \mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]+T_s\varsigma w(-\boldsymbol\iota) \ast (\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] ) \nonumber \\
+	&+\mathbf{E}[((m\ast e_t)\star y_{t+1})(\boldsymbol\iota)] +\sigma_{\epsilon}^2\delta(\boldsymbol{\iota}).
+\end{align}
+The third term in \eqref{eq:EM-Auto&CrossNoisy} can be simplified as
+\begin{align}\label{eq:EM-term3Noisy}
+\mathbf{E}[((m\ast e_t)\star y_{t+1})(\boldsymbol\iota)] &= \mathbf{E}[((m\ast e_t)\star (m\ast v_{t+1}+\varepsilon_{t+1})) (\boldsymbol\iota)] \nonumber \\
+	&= \mathbf{E}[(\left(m \ast e_t\right) \star (m \ast [\xi v_t + T_s g_t + e_t]+\varepsilon_{t+1}))(\boldsymbol\iota)] \nonumber \\
+	&=\mathbf{E}[\left(m \ast e_t\right)\star\left(m \ast e_t\right)(\boldsymbol\iota)]
+\end{align}
+A property of cross-correlation and convolution is $(a \ast b)(\boldsymbol\tau) \star (a \ast b)(\boldsymbol\tau)=(a \star a)(\boldsymbol\tau)\ast(b \star b)(\boldsymbol\tau)$ \parham{(see Appendix II for a proof)}, using the isotropy property of the observation kernel we can write
+\begin{align}\label{eq:EM-Autoterm4}
+\mathbf{E}[(\left(m \ast e_t\right)\star\left(m \ast e_t\right))(\boldsymbol\iota)]&=\mathbf{E}[(\left(m \star m\right)\ast\left(e_t \star e_t\right))(\boldsymbol\iota)] \nonumber \\
+&=(m\ast m \ast \gamma)(\boldsymbol\iota).
+\end{align}
+Substituting this back into equation~\eqref{eq:EM-Auto&CrossNoisy} gives
+\begin{align}
+	\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})] &= \xi \mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]+T_s\varsigma w(-\boldsymbol\iota) \ast (\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] ) \nonumber \\
+	&+(m\ast m \ast \gamma)(\boldsymbol\iota) +\sigma_{\epsilon}^2\delta(\boldsymbol{\iota}).
+\end{align}
+To solve for the disturbance covariance, again the convolution theorem is applied to perform the deconvolution algebraically. Taking the Fourier transform and rearranging gives
+\begin{align}
+	\mathcal{F}\{(m\ast m \ast \gamma)(\boldsymbol\iota)\} &= \mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}-\xi \mathcal{F}\{\mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]\}\nonumber \\
+	&- T_s\varsigma\mathcal{F}\{w(-\boldsymbol\iota)\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}-\sigma_{\varepsilon}^2 
+\end{align}
+Now substituting in equation~\eqref{eq:EM-Fourier_TF_of_Kernel} for $\mathcal{F}\{w(-\boldsymbol{\iota})\}$ results in
+\begin{align}
+	\mathcal{F}&\{(m\ast m \ast \gamma)(\boldsymbol\iota)\} = \mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}-\xi \mathcal{F}\{\mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]\}\nonumber \\
+	&- T_s\varsigma \times \frac{1}{T_s\varsigma }\left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\}}-\xi\right]\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\} -\sigma_{\varepsilon}^2\label{eq:EM=mmgamma}
+\end{align}
+Now simplifying gives
+\begin{align}\label{eq:EM-MMGFourier1}
+	\mathcal{F}&\{m(\boldsymbol\iota)\}\mathcal{F}\{m(\boldsymbol\iota)\}\mathcal{F}\{\gamma(\boldsymbol\iota)\} = \nonumber \\
+&\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}- \left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2}\right]-\sigma_{\varepsilon}^2 ,
+\end{align}
+rearranging and taking inverse Fourier transform gives the final result
+\begin{align}\label{eq:EM-MMGFourier2}
+	&\gamma(\boldsymbol\iota) = \nonumber \\
+&\mathcal{F}^{-1}\left\lbrace \frac{1}{\tilde{m}(\boldsymbol\iota)}\left[\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}- \left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2}\right]-\sigma_{\varepsilon}^2\right]\right\rbrace  ,
+\end{align}
+where
+\begin{equation}
+ \tilde{m}(\boldsymbol\iota)=\mathcal{F}\{m(\boldsymbol\iota)\}\mathcal{F}\{m(\boldsymbol\iota)\}.
+\end{equation}
+% from \eqref{eq:EM=mmgamma},  when considering a sensor with a spatial extent equation \eqref{eq:EM-MMGFourier2} should be used
+From \eqref{eq:EM-MMGFourier2}, to calculate the exact shape of the disturbance covariance function, observation noise variance and the sensor kernel support are required.
+Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small.
+If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} might generate numerical error.
+However, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
+\begin{equation}
+ \sigma_d^2=\sigma_{mm\gamma}^2-4\sigma_m^2.
+\end{equation}
+where $\sigma_{mm\gamma}^2$ is the width of fitted Gaussian to the estimated support of $(m\ast m\ast\gamma)(\boldsymbol\iota)$.
 \subsection{Parametrisation of Connectivity Kernel}

### 2011-07-10 ltx/data_paper/DataPaper.tex
edits to correlation analysis

@@
 The denominator in equation \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of noise free observations which is non-negative and real.
-This important result is known as Weiner-Khintchine (W-K) theorem in signal processsing which states that the power spectral density of the wide sense stationary process is the Fourier transform of it's autocorrelation function \cite{Ricker2003}.
+This important result is known as Weiner-Khintchine (W-K) theorem in signal processsing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}.
 The numerator is also called the cross spectrum or cross spectral density.

### 2011-07-10 ltx/data_paper/DataPaper.tex
added convergence plots
edits to M step

@@
 \fi
+\usepackage[font=footnotesize]{subfig}
 \usepackage{color}
@@
 % on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
-                                                                                                                                                                                                                                                                                                                                                                                                                                                                            Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, we can write
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                            Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, differentiating equation \eqref{eq:VoldermontwitXivariables} with respec to the synaptic parameter gives
 \begin{equation}\label{eq:Qpartialxi}
@@
 \end{equation}
-In order to maximise $\mathcal{Q}$-function with respect to $\boldsymbol\theta$ we can write
+In order to maximise $\mathcal{Q}$-function with respect to the connectivity kernel parameters, $\boldsymbol\theta$, differentiation is taken as follows
 \begin{equation}\label{eq:Qpartialtheta}
@@
 \end{equation}
-We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+The condition under which $\boldsymbol\Xi_4$ is invertible is discussed later in this section. Now maximising the lower bound with respect to $\sigma_{\epsilon}^2$ gives
 \begin{equation}
@@
 \end{equation}
-setting above to zero and solving for $\sigma_{\epsilon}^2$ gives
+and setting the above equation to zero and solving for $\sigma_{\epsilon}^2$ gives the result
 \begin{equation}\label{eq:sigmaepsilonhat}
@@
 \end{equation}
-Finally differentiating with respec to $\sigma_d^2$ we get
+Finally differentiating the lower bound with respec to $\sigma_d^2$ gives
 \begin{align}
@@
 \end{align}
-setting above to zero and solving for $\sigma_d^2$ we have
+setting above to zero and solving for $\sigma_d^2$ completes the maximisation step
 \begin{align}\label{eq:sigmadhat}
@@
 \end{alignat}
-$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of state vectors, which is guaranteed by the disturbance, $\mathbf e$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore we have \cite{Coope1994}
+$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of state vectors, which is guaranteed by the disturbance, $\mathbf e$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore by \cite{Coope1994}
 \begin{equation}
@@
 Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
-The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}.
-(note that multiplying by $\mathbf \Gamma^{-1}$ doesn't change the rank).
-However, $\mathbf q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically, making it difficult to calculate the rank of $\mathbf q(\mathbf x_t)$ .
-Therefore, we recommend to check the rank of $\mathbf q(\mathbf x_t)$ at each iteration of the E-step.
-
+The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004} (note that multiplying by $\mathbf \Gamma^{-1}$ has no effect on the rank).
+However, $\mathbf q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid function cannot be solved analytically, making it difficult to calculate the rank of $\mathbf q(\mathbf x_t)$ .
+Therefore, the rank of $\mathbf q(\mathbf x_t)$ at each iteration of the algorithm should be examined.
 From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function.
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{figure}[!ht]
+\centering
+% \subfloat[][]{\includegraphics[scale=1]{./Graph/EM/Q.pdf}}\\
+\subfloat[][]{\includegraphics[scale=1]{./Figures/ParameterConvergence.pdf}}\\
+\centering
+\subfloat[][]{\includegraphics[scale=1]{./Figures/KernelConvergence.pdf}}
+\caption{{\bf Convergence of parameters}.
+All parameters converge after 9 iterations.
+(\textbf a) The logarithm of the mean of synaptic parameter, observation noise variance and field disturbance variance over 100 realisations.
+(\textbf b) The mean kernel estimates at each iteration of the EM algorithm.}
+\label{fig:ParameterConvergence}
+\end{figure}
 

### 2011-07-11 ltx/data_paper/DataPaper.tex
edit to introduction

@@
 	\item Improvements in electrode technology with great spatiotemporal resolution
+
 \end{itemize}
@@
 Instead of extracting features we aim to extract meaningful parameters...
+
+Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics.
+They perform a stability analysis of the network in terms of total connectivity and time delayes in the presence of noise.
+Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.
 

### 2011-07-11 ltx/data_paper/DataPaper.tex
added appendix to the data paper

@@
 where
-\begin{align}
-	{\boldsymbol \Lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r' \label{eq:lambdatildei}.
+\begin{align}\label{eq:EM-Lambdat}
+	{\boldsymbol \Lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r'.
 \end{align}
@@
 
+\clearpage
+\newpage
+\appendix
+\section{Product of two $n$-dimensional Gaussian functions}\label{sec:GaussianProduct} 
+In this section, we provide a derivation for the product of two n-dimensional Gaussian basis functions.
+This derivation is used in the  calculation of $\boldsymbol\Lambda_t^{(i)}$  defined in equation \eqref{eq:EM-Lambdat} of the main text. Consider two
+Gaussian basis functions
+\begin{equation}\label{eq:n_dimensional_Gaussian1}
+ \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
+\end{equation}
+and 
+\begin{equation}\label{eq:n_dimensional_Gaussian2}
+\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
+\end{equation}
+the product of two Gauusian basis functions is given by
+\begin{equation}
+ \varphi_i(\mathbf r)\varphi_j(\mathbf r)=\mathrm{exp}\left(-\left[ {\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol\mu_i)+{\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol\mu_j)}}\right] \right)
+\end{equation}
+the product is expanded to give
+\begin{align} 
+ \varphi_i(\mathbf r)\varphi_j(\mathbf r)&=
+\mathrm{exp}\left(-\left[ \frac{(\sigma_i^2+\sigma_j^2)\left[\mathbf r^\top\mathbf r-2\mathbf r^\top \frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2}+\frac{(\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j)^\top(\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j)}{(\sigma_i^2+\sigma_j^2)^2}\right]}{\sigma_i^2\sigma_j^2}\right.\right.
+\nonumber\\
+&\left.\left. \frac{+\frac{\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}(\boldsymbol \mu_i-\boldsymbol\mu_j)^\top(\boldsymbol \mu_i-\boldsymbol\mu_j)}{}\right]\right) \nonumber\\
+  &=\mathrm{exp}\left(-\frac{(\sigma_i^2+\sigma_j^2)\left[(\mathbf r-\frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2})^\top(\mathbf r-\frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2})\right]  }{\sigma_i^2\sigma_j^2}\right) \nonumber \\
+   &\times\mathrm{exp}\left(-\frac{(\boldsymbol \mu_i-\boldsymbol\mu_j)^\top(\boldsymbol \mu_i-\boldsymbol\mu_j)}{\sigma_i^2+\sigma_j^2}\right),
+\end{align}
+therefore we have
+\begin{equation}
+ \varphi_i(\mathbf r)\varphi_j(\mathbf r)=c_{i,j}\times\mathrm{exp}\left({-\frac{1}{\sigma^2} (\mathbf r-\boldsymbol \mu)^\top(\mathbf r-\boldsymbol\mu)}\right)
+\end{equation}
+where
+\begin{equation}
+ c_{i,j}=\mathrm{exp}\left(-\frac{(\boldsymbol \mu_i-\boldsymbol\mu_j)^\top(\boldsymbol \mu_i-\boldsymbol\mu_j)}{\sigma_i^2+\sigma_j^2}\right) \quad \sigma^2=\frac{\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}
+\end{equation}
+and
+\begin{equation}
+ \boldsymbol\mu=\frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2}
+\end{equation}
+
+\section{Cross-correlation and convolution}\label{ap:CorrelationAnalysis}
+This appendix provide a proof for the properties of the cross-correlation and convolution used in the Correlation analysis Section of Chapter 2. To show 
+\begin{equation}\label{eq:app-ConvXcorRelation1}
+ \left(a \ast b \right)\left(\boldsymbol\iota\right)  \star c\left(\boldsymbol\iota\right)  = a\left(-\boldsymbol\iota\right)\ast\left(b \star c\right)\left(\boldsymbol\iota\right)
+\end{equation}
+and
+\begin{equation}\label{eq:app-ConvXcorRelation2}
+(a \ast b)(\boldsymbol \iota) \star (a \ast b)(\boldsymbol\iota)=(a \star a)(\boldsymbol\iota)\ast(b \star b)(\boldsymbol\iota),
+\end{equation}
+first note that cross-correlation function is related to the convolution by \cite{Yarlagadda2009}
+\begin{equation}\label{eq:app-ConvXcorRelation}
+ \left(a \star b\right)\left(\boldsymbol\iota\right)= a\left(-\boldsymbol\iota\right)\ast b\left(\boldsymbol\iota\right).
+\end{equation}
+Therefore, equation \eqref{eq:app-ConvXcorRelation1} can be wriiten as
+\begin{align}
+ \left(a \ast b\right)\left(\boldsymbol\iota\right) \star c\left(\boldsymbol\iota\right)&= \left(a \ast b\right)\left(-\boldsymbol\iota \right)\ast c\left(\boldsymbol\iota\right) \nonumber \\
+&=a\left(-\boldsymbol\iota\right)\ast \left(b\left(-\boldsymbol\iota\right) \ast c\left(\boldsymbol\iota\right)\right)\nonumber \\
+&=a\left(-\boldsymbol\iota\right)\ast\left(b\star c\right)\left(\boldsymbol\iota\right).
+\end{align}
+Similarly, equation \eqref{eq:app-ConvXcorRelation2} can be written as
+\begin{align}
+ (a \ast b)(\boldsymbol \iota) \star (a \ast b)(\boldsymbol\iota)&=(a \ast b)(-\boldsymbol\iota) \ast (a \ast b)(\boldsymbol\iota) \nonumber \\
+&=a(-\boldsymbol\iota)\ast a(\boldsymbol\iota) \ast b(-\boldsymbol\iota)\ast b(\boldsymbol\iota) \nonumber \\
+&=(a \star a)(\boldsymbol\iota)\ast(b \star b)(\boldsymbol\iota).
+\end{align}
+
 % \begin{figure}[!ht]

### 2011-07-11 ltx/data_paper/DataPaper.tex
edits to disturbance support estimation
edits to result section

@@
 	&\gamma(\boldsymbol\iota) = \nonumber \\
-&\mathcal{F}^{-1}\left\lbrace \frac{1}{\tilde{m}(\boldsymbol\iota)}\left[\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}- \left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2}\right]-\sigma_{\varepsilon}^2\right]\right\rbrace  ,
+&\mathcal{F}^{-1}\left\lbrace \frac{1}{\tilde{m}(\boldsymbol\iota)}\left[\left[\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}-\sigma_{\varepsilon}^2\right]- \left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2}\right]\right]\right\rbrace  ,
 \end{align}
@@
 Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small.
+Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively.
 If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} might generate numerical error.
@@
 This section demonstrates the identification of the proposed IDE model using simulated data.
-The observation noise and disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the kernel.
-Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
+The observation noise and the field disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
+Data was generated employing state-space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state.
-The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ .
-The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations.
-The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$.
-The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively.
-The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.
+Observation noise variance was set to 0.2.
+All other parameters for the simulation were the same as Chapter 2 (see Table 1.1).
 
 The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function.
-In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero.
-By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as a prerequisite for the EM algorithm, however, an approximate of their support can be still extracted.
+However, to compute the supports the unknown parameters, $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
+To form a more accurate initial guess of the unkown parameters and explore the effect on the estimated support several tests were performed.
+First consider equation \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
+As mentioned before the power spectral densities are non negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
+The minimum value of the power spectral density was 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit.
+This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted.
+The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and thresholded for values less than 0.01.
+By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using equation \eqref{eq:EM-AnalyticSupportCalculation}.
+Deconvolution can also be performed numerically to directly find the support as can be seen in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
+%Figure 1 here
+\begin{figure}[!ht]
+\centering
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation0.pdf}}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation01.pdf}}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation02.pdf}}\\
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation023.pdf}}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation03.pdf}}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation04.pdf}}
+\caption{{\bf Disturbance support estimates for variyng observation noise variance.} Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
+(\textbf a) $\sigma_{\varepsilon}^2$=0.
+(\textbf b) $\sigma_{\varepsilon}^2$=0.1 .
+(\textbf c) $\sigma_{\varepsilon}^2$=0.2 .
+(\textbf d) $\sigma_{\varepsilon}^2$=0.23 .
+(\textbf e) $\sigma_{\varepsilon}^2$=0.3 .
+(\textbf f) $\sigma_{\varepsilon}^2$=0.4 .}
+\label{fig:DisturbanceSupportExperiment}
+\end{figure}
+\begin{figure}[!ht]
+\begin{center}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimationBinary.pdf}}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthTrue.pdf}}
+\end{center}
+\caption{{\bf Disturbance support approximation for }$\sigma_{\varepsilon}^2<$0.23.
+Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
+(\textbf{a}) Estimated support is shown by red circle, nonzero values after thresholding are shown by the black area.
+(\textbf{b}) True support.}
+\label{fig:BinaryDisturbanceWidthEstimation}
+\end{figure}
+\begin{figure}[!ht]
+\begin{center}
+\centering
+\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimationCrossSection.pdf}
+\end{center}
+\caption{{\bf Cross-section of disturbance covariance support estimation}. The true and the estimated width are shown by solid and dashed lines respectively.}
+\label{fig:DisturbanceWidthEstimationCrossSection}
+\end{figure}
+
+ By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
 In fact, the estimated support for the disturbance covariance function was very accurate.
@@
 The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}.
-By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor,$\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
-
-The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
-A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$.
+By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
+
+The estimated supports were then employed in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
+A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated kernel support where $\sigma_{\psi}^2=3.5$.
 This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.

### 2011-07-12 ltx/data_paper/DataPaper.tex
edits to result section
edit to correlation analysis

@@
 Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively.
-If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} might generate numerical error.
-However, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
+If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} is then required.
+Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
 \begin{equation}
@@
 \end{center}
-\caption{{\bf Cross-section of disturbance covariance support estimation}. The true and the estimated width are shown by solid and dashed lines respectively.}
+\caption{{\bf Cross-section of disturbance covariance support estimation}. The normalized true and the estimated width are shown by solid and dashed lines respectively.}
 \label{fig:DisturbanceWidthEstimationCrossSection}

### 2011-07-12 ltx/data_paper/DataPaper.tex
edit to result section

@@
 However, to compute the supports the unknown parameters, $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
-To form a more accurate initial guess of the unkown parameters and explore the effect on the estimated support several tests were performed.
+To form a more accurate initial guess of the unkown parameters and explore the effect of chosen initial guess on the estimated supports several tests were performed.
 First consider equation \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
 As mentioned before the power spectral densities are non negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
-The minimum value of the power spectral density was 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit.
+The minimum value of the power spectral density was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit.
 This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted.
@@
 By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using equation \eqref{eq:EM-AnalyticSupportCalculation}.
-Deconvolution can also be performed numerically to directly find the support as can be seen in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
+Alternatively deconvolution can also be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
 %Figure 1 here

### 2011-07-13 ltx/data_paper/DataPaper.tex
added plots for kernel support experiment

@@
 \end{figure}
-
+\begin{figure}
+\begin{center}
+\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise0.pdf}}
+\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise01.pdf}}
+\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise018.pdf}}
+\end{center}
+\caption{{\bf Kernel support approximation for different values of synaptic time constant, $\tau$ and observation noise variance, $\sigma^2_{\varepsilon}$}.
+Each subplot shows normalised connectivity kernel estimate.
+(\textbf a) $\sigma_{\varepsilon}^2$=0.
+(\textbf b) $\sigma_{\varepsilon}^2$=0.1 .
+(\textbf c) $\sigma_{\varepsilon}^2$=0.18.}
+\label{fig:KernelWidthEstimationExperiment}
+\end{figure}
+The effect of the observation noise variance on the connectivity kernel support is very much like to that of disturbance covariance function where an initial guess can be made in a similar manner.
+To study how synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, influence the resultant support of the connectivity kernel different values of synaptic time constatnt, $\tau$, were considered in a physiologically plausible range while noting that its value should be also higher than the sampling time.
+In fact synaptic parameter in \eqref{eq:EM-Fourier_TF_of_Kernel}  acts like a scaling factor, dilating or shrinking the estimated support, as the subtracting a constant in a frequency domain only affects the value at the origin in the spatial domain.
+The result of the correlation analysis for the connectivity kernel is shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised  estimate for varying synaptic time constants while the observation noise was kept constant.
+Note that for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
  By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.

### 2011-07-14 ltx/data_paper/DataPaper.tex
edits to result section
edits to discussion

@@
 Variable &Equation&Order\\ \hline\\
-$\Xi_0, \Xi_1, \Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
-$\Xi_3, \Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)+O(Tn_{\theta}n_r^2)$ \\
-$\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r^2)$\\
+$\mathbf q(\mathbf{x}_t)$&\eqref{}&$O(n_xn_{\theta}n_r)$\\
+$\boldsymbol\Xi_0, \boldsymbol\Xi_1, \boldsymbol\Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
+$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
+$\boldsymbol\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r)$\\
 $\hat{\xi}$&\eqref{eq:xihat}&$O(n_x^3+n_{\theta}^3)$\\
@@
 Note that for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
+The result suggests that choosing the range of approximately $\left[-5,5 \right] $ is reasonable for the spatial extent of the connectivity kernel.
+
  By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
@@
 \section{Discussion}
+The correlation analysis specifies approximate supports for both disturbance covariance function and connectivity kernel.
+Since the analysis assumes the sigmoidal firing rate to be in the active region, the amplitudes for the kernel and the disturbance cannot be inferred this way.
+Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be chosen as described in Correlation analysis section, their values influence the exact shape of the kernel significantly, this step might be considered as an initialisation for the EM algorithm.
+Knowing the spatial extent of the kernel greatly increases the speed of the algorithm as the number of basis functions to decompose the kernel reduces significanly compared to the case in which the basis funtions are laid out across the entire spatial domain.
+This also improves the uncertainty of the parameter estimates as the number of parameters to be estimated reduces.
+On the other hand, the approximated support of the disturbance covariance function facilitates the implementation of the EM algorithm as the disturbance covariance matrix can be factorised into a constant matrix which only depends on the inferred support and an unknown scaling parameter which needs to be estimated.
+
+The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the state and observation equations about the state estimates and then applying regular Kalman filter to the linear system.
+This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of states in the presented framework.
+However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible.
+Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure.
+In addition, URTSS provides better approximation compared to the EKS and therefore the approximated lower bound will be more accurate \cite{Haykin2001}.
 
 \begin{itemize}
-	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
 	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property than using EM with URTSS

### 2011-07-14 ltx/data_paper/DataPaper.tex
added computational complexity initialisation and stopping

@@
  \end{align}
-By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete.
-The lower bound now can be used in M-step to find a set of new parameters.
-An approximate for computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
-Note that computational complexity of the nonlinear terms depend on the number of points, $n_r$ used for spatial discritisation.
-In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found elsewhere \cite{Sarkka2010}.
+By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete. The lower bound now can be used in M-step to find a set of new parameters. 
 \subsection{M-Step}
@@
 From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+\subsection{Initialisation, stopping and algorithmic complexity}
+For initialisation a bounded random state sequence is employed to ensure that the initial parameter estimates describe a stable kernel, although the quality of such initial estimate is poor, it provides an initialisation that typically ensues a satisfactory convergence of the algorithm, as illustrated numerically in Result section.
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
+Here the change in parameter estimates, $L^2$-norm in the case of connectivity kernel weights, is used to halt the excecution of the algorithm.
+Besides, the lower bound on the likelihood function is also monitored to further investigate the convergence of the EM algorithm.
+
+An approximate for computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
+Note that computational complexity of the nonlinear terms depend on the number of points, $n_r$ used for spatial discritisation.
+Calculation of the nonlinear terms $\boldsymbol\Xi$ is clearly the slowest part of the algorithm where $n_x$ is the problematic dimension, more specifically the matrix $\boldsymbol\Xi_4 $ has complexity that grows with the order of four in $n_x$.
+Although number of states  is decoupled from number of observation locations (recording electrods) , and the number of basis functions required for the connectivity kernel decomposition, it does tend to grow linearly in one dimensional space and quadratically in two dimensional space.
+This growth assumes that the basis functions are arragend regularly in space, which is not a necessary construction.
+
 %  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 

### 2011-07-14 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 
+While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm.
+However, since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be guaranteed.
+Nevertheless, the proposed framework is more stable than using EKS as the E-step due to better performance of the URTSS.
 \begin{itemize}
-	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property than using EM with URTSS
 	\item itterative EM and correlation analysis (maybe)

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 The correlation analysis specifies approximate supports for both disturbance covariance function and connectivity kernel.
-Since the analysis assumes the sigmoidal firing rate to be in the active region, the amplitudes for the kernel and the disturbance cannot be inferred this way.
-Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be chosen as described in Correlation analysis section, their values influence the exact shape of the kernel significantly, this step might be considered as an initialisation for the EM algorithm.
+Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S~\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate to be in the active region, as a result  the kernel and the disturbance amplitudes cannot be inferred only through correlation analysis.
+This step might be considered as a prerequisite for the EM algorithm described in \S~\ref{sec:EstimationAlgorithm} where approximated supports are employed to estimate the gain of the kernel and disturbance.
 Knowing the spatial extent of the kernel greatly increases the speed of the algorithm as the number of basis functions to decompose the kernel reduces significanly compared to the case in which the basis funtions are laid out across the entire spatial domain.
-This also improves the uncertainty of the parameter estimates as the number of parameters to be estimated reduces.
-On the other hand, the approximated support of the disturbance covariance function facilitates the implementation of the EM algorithm as the disturbance covariance matrix can be factorised into a constant matrix which only depends on the inferred support and an unknown scaling parameter which needs to be estimated.
+This also improves the uncertainty of the estimates because of the lower number of parameters needs to be estimated.
+On the other hand, the approximated support of the disturbance covariance function facilitates the implementation of the EM algorithm as the disturbance covariance matrix can be factorised into two components, a constant matrix depending only on the inferred support and an unknown scaling parameter.
+This way the problem of estimating the covariance matrix reduces to estimation of a single scaling parameter.
 

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 
-The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the state and observation equations about the state estimates and then applying regular Kalman filter to the linear system.
-This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of states in the presented framework.
+The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the nonlinear equations about the state estimates.
+This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of state vecors in the presented framework.
 However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible.
 Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure.
-In addition, URTSS provides better approximation compared to the EKS and therefore the approximated lower bound will be more accurate \cite{Haykin2001}.
+In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the approximated lower bound will be more accurate  resulting in better parameter estimations.
 

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm.
-However, since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be guaranteed.
-Nevertheless, the proposed framework is more stable than using EKS as the E-step due to better performance of the URTSS.
+However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured.
+Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
 \begin{itemize}

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
+
+In almost all applications a sequence of likelihood converges to some stationary values i.e.
+global (local) maximum or a saddle point.
+If the sequence of EM is trapped in a saddle point a small random purturbation diverges the EM from the saddle point \cite{McLachlan1997}.
+In general convergence of the EM algorithm to any stationary point either global (local) maxima or saddle points
+depends on the initialisation. Here a bounded sequence of state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and good parameter estimations.
 \begin{itemize}

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 depends on the initialisation. Here a bounded sequence of state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and good parameter estimations.
+
+Since the non-linearity is a sigmoid function first-order Taylor approximation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
 \begin{itemize}
 	\item itterative EM and correlation analysis (maybe)
-	\item{comment on EM might convrge to suboptimal solution,simulated
-annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
-	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
 \end{itemize}

### 2011-07-20 ltx/data_paper/DataPaper.tex
edits to discussion
committing for merge

--- 2011-07-16 ltx/data_paper/DataPaper.tex
@@
 \fi
-\usepackage[font=footnotesize]{subfig}
 \usepackage{color}
@@
 \author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
- Andrew Zammit Mangion, Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
- David B. Grayden and Visakan Kadirkamanathan  }
+ Andrew Zammit Mangion, David B. Grayden and Visakan Kadirkamanathan  }
 
@@
 	\item Improvements in electrode technology with great spatiotemporal resolution
-
 \end{itemize}
@@
 Instead of extracting features we aim to extract meaningful parameters...
-
-Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics.
-They perform a stability analysis of the network in terms of total connectivity and time delayes in the presence of noise.
-Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.
 
@@
 
-\subsubsection{Estimation of Connectivity Kernel Support}
-For the derivation of the spatial properties estimator of the neural field equations a more compact notation is employed to define convolution and correlation operators.
-The spatial convolution shall be denoted as
-\begin{equation}
-	\int_\Omega a(\mathbf{r}-\mathbf{r}')b(\mathbf{r}')d\mathbf{r}' = (a\ast b)(\mathbf{r}),
-\end{equation}
-and the spatial cross-correlation shall be denoted as 
-\begin{equation}
-	\int_\Omega a(\mathbf{r})b(\mathbf{r}+\boldsymbol{\iota})d\mathbf{r} = (a\star b)(\boldsymbol{\iota}),
-\end{equation} 
-where $\iota$ is the spatial shift.
-The spatial relationship between consecutive observations is governed by the shape of the connectivity kernel.
-Therefore, the spatial cross-correlation between consecutive observations is used to estimate the kernel's support and shape.
-To begin the derivation the spatial cross-correlation between consecutive observations (in time) is defined as
-\begin{equation}
-	R_{y_{t+1}y_t}(\boldsymbol{\iota}) = \left(y_{t+1}\star y_t\right)\left(\boldsymbol{\iota}\right),
-\end{equation}
- The aim of the derivation is to make the necessary substitutions and simplifications to get an expression of the cross-correlation as a function of the connectivity kernel.
-In the next step equation~\eqref{eq:EM-ObservationEquation} is substituted for $y_{t+1}(\mathbf{r})$ and expanded to give
-\begin{equation}
-	R_{y_{t+1}y_t}\left(\boldsymbol{\iota}\right) = \left(\left(m \ast v_{t+1}\right)\star y_t\right)\left(\boldsymbol{\iota}\right) + \left(\varepsilon_{t+1} \star y_t\right)\left(\boldsymbol{\iota}\right).
-\end{equation}
-Next equation~\eqref{eq:EM-DiscreteTimeModel} is substituted for $v_{t+1}(\mathbf{r})$ giving 
-\begin{align}
-	R_{y_{t+1}y_t}(\boldsymbol{\iota}) &= (\left(m \ast \left(\xi v_t +  T_s g_t + e_t\right)\right) \star y_t)(\boldsymbol{\iota})\\
-	&= \xi\left(\left(m \ast v_t\right) \star y_t \right)(\boldsymbol{\iota}) \nonumber\\
-	&\quad+ T_s \left(\left(m\ast g_t\right)\star y_t \right)(\boldsymbol{\iota}) \nonumber\\
-	&\quad+ \left(\left(m\ast e_t\right)\star y_t \right)(\boldsymbol{\iota}) \nonumber\\
-	&\quad+ (\varepsilon_{t+1} \star y_t)(\boldsymbol{\iota}).
-\end{align}
-Now the expectation over time is taken, so that the observation noise and process disturbance terms have minimal effect on the result, giving 
-\begin{align}\label{eq:EM-ExpectationToCancelNoise}
-	\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})] &= \mathbf{E}[\xi\left(\left(m \ast v_t\right) \star y_t \right)(\boldsymbol{\iota})] + T_s \mathbf{E}[\left(\left(m\ast g_t\right)\star y_t \right)(\boldsymbol{\iota})],
-\end{align}
-since the disturbance and measurement noise are assumed to be independent of the observations and temporally white. 
-The cross-correlation is further simplified by recognizing that the first term on right hand side of equation~\eqref{eq:EM-ExpectationToCancelNoise} can be written as 
-\begin{align}
-	\mathbf{E}[\xi&\left(\left(m \ast v_t \right) \star y_t \right)(\boldsymbol{\iota})] = \mathbf{E}\left[\xi\left(\left(y_t-\varepsilon_t\right) \star y_t \right)(\boldsymbol{\iota})\right] \nonumber \\
-	&= \xi \mathbf{E}\left[ (y_t \star y_t)(\boldsymbol{\iota}) - \left(\varepsilon_t\star y_t \right)(\boldsymbol{\iota})\right] \nonumber \\
-	&= \xi\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})  - \left(\varepsilon_t \star (m\ast v_t + \varepsilon_t)\right) (\boldsymbol{\iota})] \nonumber \\
-	&=\xi\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota}) -\left(\varepsilon_t\star (m\ast v_t)\right)(\boldsymbol{\iota}) - (\varepsilon_t\star\varepsilon_t)(\boldsymbol{\iota})] \nonumber \\
-	&= \xi\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right), \label{eq:EM-FirstTermReduced}
-\end{align}
-where $\delta\left(\cdot\right)$ denotes Kronecker delta. Substituting equation~\eqref{eq:EM-FirstTermReduced} back into equation~\eqref{eq:EM-ExpectationToCancelNoise} gives
-\begin{align}\label{eq:EM-SimplifiedFirstTerm}
-	\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})] &= \xi\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)+ T_s\mathbf{E}[ \left(\left(m\ast g_t\right)\star y_t \right)(\boldsymbol{\iota})].
-\end{align}
-Next we simplify second term in equation~\eqref{eq:EM-SimplifiedFirstTerm} to get an expression involving the connectivity kernel.
-By substituting equation~\eqref{eq:EM-RateBasedInteractions} for $g_t$ we can write
-\begin{equation}\label{eq:EM-before_linearization}
-	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) = T_s((w \ast m\ast f(v_t)) \star y_t)(\boldsymbol\iota).
-\end{equation}
-The remainder of the derivation is focused on isolating the connectivity kernel. To show how this is done, the activation function is assumed to be in the linear region, i.e 
- \begin{equation}
-	f\left(v_t(\mathbf{r})\right) \approx \varsigma v_t(\mathbf{r})
-\end{equation} 
-Substituting the linear activation function back into equation~\eqref{eq:EM-before_linearization} yields
-\begin{align}\label{eq:EM-after_linearization1}	
-	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) &\approx T_s\varsigma((w \ast m\ast v_t) \star y_t)(\boldsymbol\iota).
-\end{align}
-Now by substituting $y_t - \varepsilon_t$ in for $m\ast v_t$ equation \eqref{eq:EM-after_linearization1} can be written as 
-\begin{align}
-	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) &\approx T_s\varsigma(w\ast (y_t - \varepsilon_t)) \star y_t (\boldsymbol\iota)
-\end{align}
-To isolate the kernel, the order of the convolution and cross-correlation is reversed by recognizing that a property $(a \ast b)(\boldsymbol\iota) \star c(\boldsymbol\iota) = a(-\boldsymbol\iota)\ast(b \star c)(\boldsymbol\iota)$ \parham{(see Appendix for proof)}.
-Therefore,
-\begin{align}
-	T_s((m \ast g_t) \star y_t)(\boldsymbol\iota) &\approx T_s\varsigma w(-\boldsymbol\iota) \ast ((y_t - \varepsilon_t)) \star y_t)(\boldsymbol\iota),
-\end{align}
-Now using the identity established to get equation~\eqref{eq:EM-FirstTermReduced} gives
-\begin{equation}\label{eq:EM-second_term_reduced}
-	T_s\mathbf{E}\left[((m \ast g_t) \star y_t)(\boldsymbol\iota)\right] \approx T_s\varsigma w(-\boldsymbol\iota) \ast  (\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))
-\end{equation}
-Now substituting back equation~\eqref{eq:EM-second_term_reduced} into equation~\eqref{eq:EM-SimplifiedFirstTerm} gives
-\begin{align}\label{eq:EM-SimplifiedXcorr}
-	\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})] &= \xi\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)\nonumber \\
-&+T_s\varsigma w(-\boldsymbol\iota) \ast  (\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))
-\end{align}
-Rearranging equation~\eqref{eq:EM-SimplifiedXcorr} gives
-\begin{align}
-	 w(-\boldsymbol\iota) \ast  (\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))&=\frac{1}{T_s\varsigma}\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]-\frac{\xi}{T_s\varsigma}\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)\nonumber \\
-\end{align}
-The solution of the above equation for the connectivity kernel is a deconvolution.
-This can be approached from a number of different standpoints.
-The simplest solution is to use the convolution theorem and to solve for the kernel algebraically in the frequency domain.
-\begin{align}\label{eq:EM-XcorrFourier}
-	\mathcal{F}\{w(-\boldsymbol\iota)\} \mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\} &\approx \frac{1}{T_s\varsigma}\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\nonumber \\
-&-\frac{\xi}{T_s\varsigma}\mathcal{F} \{\left(\mathbf{E}[ R_{y_ty_t}(\boldsymbol{\iota})] - \sigma_{\varepsilon}^2 \delta(\boldsymbol{\iota})\right)\}.
-\end{align}
-Now rearranging \eqref{eq:EM-XcorrFourier} gives
-\begin{equation}\label{eq:EM-Fourier_TF_of_Kernel}
-	\mathcal{F}\left(w(-\boldsymbol\iota)\right) = \frac{1}{T_s\varsigma }\left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\}}-\xi\right].
-\end{equation}
-From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect estimate in the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion would be insignificant.
-The denominator in equation \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of noise free observations which is non-negative and real.
-This important result is known as Weiner-Khintchine (W-K) theorem in signal processsing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}.
-The numerator is also called the cross spectrum or cross spectral density.
-Since the connectivity kernel is a real function, the following relation holds \cite{Bracewell2000}
-\begin{equation}
- \mathcal{F}\left(w(\boldsymbol\iota)\right)=\overline{\mathcal{F}\left(w(-\boldsymbol\iota)\right)},
-\end{equation}
-where over-bar denotes complex conjugate operator. Finally, an expression for the kernel is obtained by taking the inverse Fourier tranform 
-\begin{equation}\label{eq:KernelSolution}
-	w(\boldsymbol\iota) = \frac{1}{T_s\varsigma }\mathcal{F}^{-1}\overline{\left\{\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2 }-\xi\right\}}.
-\end{equation}
-Complex conjugate operator essentially reflects the connectivity kernel through the origin in the spatial domain, therefore, if the connectivity kernel is isotropic, the complex conjugate operator can be dropped.
-% Alternatively, the convolution can be written as a system of linear equations by forming the convolution (Toeplitz) matrix.
-The solution of the convolution equation for $w(\cdot)$ can then be found by either inverting the convolution matrix or directly solving the system of equations.
-% Directly solving the system is the most numerically stable and less computationally demanding then inverting the convolution matrix.
-To show this we take the spatial Fourier transform of both sides of equation~\ref{} giving
-\subsubsection{Estimation of Disturbance Covariance Support}
-The observation auto-correlation at time $t+1$ can be expressed as
-\begin{equation}
-	R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})=(y_{t+1} \star y_{t+1})(\boldsymbol\iota).
-\end{equation}
-Substituting equation~\eqref{eq:EM-ObservationEquation} in for $y_{t+1}$ and expanding gives
-\begin{align}\label{eq:EM-expanded_auto_corr}
-	R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota}) &= \xi((m \ast v_{t}) \star y_{t+1})(\boldsymbol{\iota}) +T_s((m\ast g_{t})\star y_{t+1})(\boldsymbol{\iota}) \nonumber \\
-	&+((m\ast e_{t})\star  y_{t+1})(\boldsymbol{\iota})+(\varepsilon_{t+1} \star y_{t+1})(\boldsymbol{\iota}).
-\end{align}
-By using similar arguments that were used in the derivation for the connectivity kernel support, the autocorrelation can be simplified by recognizing that
-\begin{align}\label{eq:EM-Autoterm1}
-  \mathbf{E}[\xi((m\ast v_{t})\star y_{t+1})(\boldsymbol{\iota})]&=\xi \mathbf{E}[ R_{y_ty_{t+1}}(\boldsymbol{\iota})],
-\end{align}
-and
-\begin{align}\label{eq:EM-Autoterm2}
-	T_s\mathbf{E}[((m\ast g_t) \star y_{t+1})(\boldsymbol\iota)] &\approx T_s\varsigma\mathbf{E}[((m \ast w )\star y_{t+1})(\boldsymbol\iota)] \nonumber\\
-	&= T_s\varsigma w(-\boldsymbol\iota) \ast (\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] ).
-\end{align}
-\begin{align}\label{eq:EM-Autoterm3}
- \mathbf{E}[(\varepsilon_{t+1}\star y_{t+1})(\boldsymbol\iota)]&=\sigma_{\varepsilon}^2\delta(\boldsymbol{\iota}),
-\end{align}
-Substituting equations~\eqref{eq:EM-Autoterm1}, \eqref{eq:EM-Autoterm2}, and ~\eqref{eq:EM-Autoterm3} back into equation~\eqref{eq:EM-expanded_auto_corr} gives
-\begin{align}\label{eq:EM-Auto&CrossNoisy}
-	\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})] &= \xi \mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]+T_s\varsigma w(-\boldsymbol\iota) \ast (\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] ) \nonumber \\
-	&+\mathbf{E}[((m\ast e_t)\star y_{t+1})(\boldsymbol\iota)] +\sigma_{\epsilon}^2\delta(\boldsymbol{\iota}).
-\end{align}
-The third term in \eqref{eq:EM-Auto&CrossNoisy} can be simplified as
-\begin{align}\label{eq:EM-term3Noisy}
-\mathbf{E}[((m\ast e_t)\star y_{t+1})(\boldsymbol\iota)] &= \mathbf{E}[((m\ast e_t)\star (m\ast v_{t+1}+\varepsilon_{t+1})) (\boldsymbol\iota)] \nonumber \\
-	&= \mathbf{E}[(\left(m \ast e_t\right) \star (m \ast [\xi v_t + T_s g_t + e_t]+\varepsilon_{t+1}))(\boldsymbol\iota)] \nonumber \\
-	&=\mathbf{E}[\left(m \ast e_t\right)\star\left(m \ast e_t\right)(\boldsymbol\iota)]
-\end{align}
-A property of cross-correlation and convolution is $(a \ast b)(\boldsymbol\tau) \star (a \ast b)(\boldsymbol\tau)=(a \star a)(\boldsymbol\tau)\ast(b \star b)(\boldsymbol\tau)$ \parham{(see Appendix II for a proof)}, using the isotropy property of the observation kernel we can write
-\begin{align}\label{eq:EM-Autoterm4}
-\mathbf{E}[(\left(m \ast e_t\right)\star\left(m \ast e_t\right))(\boldsymbol\iota)]&=\mathbf{E}[(\left(m \star m\right)\ast\left(e_t \star e_t\right))(\boldsymbol\iota)] \nonumber \\
-&=(m\ast m \ast \gamma)(\boldsymbol\iota).
-\end{align}
-Substituting this back into equation~\eqref{eq:EM-Auto&CrossNoisy} gives
-\begin{align}
-	\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})] &= \xi \mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]+T_s\varsigma w(-\boldsymbol\iota) \ast (\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] ) \nonumber \\
-	&+(m\ast m \ast \gamma)(\boldsymbol\iota) +\sigma_{\epsilon}^2\delta(\boldsymbol{\iota}).
-\end{align}
-To solve for the disturbance covariance, again the convolution theorem is applied to perform the deconvolution algebraically. Taking the Fourier transform and rearranging gives
-\begin{align}
-	\mathcal{F}\{(m\ast m \ast \gamma)(\boldsymbol\iota)\} &= \mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}-\xi \mathcal{F}\{\mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]\}\nonumber \\
-	&- T_s\varsigma\mathcal{F}\{w(-\boldsymbol\iota)\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}-\sigma_{\varepsilon}^2 
-\end{align}
-Now substituting in equation~\eqref{eq:EM-Fourier_TF_of_Kernel} for $\mathcal{F}\{w(-\boldsymbol{\iota})\}$ results in
-\begin{align}
-	\mathcal{F}&\{(m\ast m \ast \gamma)(\boldsymbol\iota)\} = \mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}-\xi \mathcal{F}\{\mathbf{E}[R_{y_ty_{t+1}}(\boldsymbol{\iota})]\}\nonumber \\
-	&- T_s\varsigma \times \frac{1}{T_s\varsigma }\left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\}}-\xi\right]\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\} -\sigma_{\varepsilon}^2\label{eq:EM=mmgamma}
-\end{align}
-Now simplifying gives
-\begin{align}\label{eq:EM-MMGFourier1}
-	\mathcal{F}&\{m(\boldsymbol\iota)\}\mathcal{F}\{m(\boldsymbol\iota)\}\mathcal{F}\{\gamma(\boldsymbol\iota)\} = \nonumber \\
-&\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}- \left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2}\right]-\sigma_{\varepsilon}^2 ,
-\end{align}
-rearranging and taking inverse Fourier transform gives the final result
-\begin{align}\label{eq:EM-MMGFourier2}
-	&\gamma(\boldsymbol\iota) = \nonumber \\
-&\mathcal{F}^{-1}\left\lbrace \frac{1}{\tilde{m}(\boldsymbol\iota)}\left[\left[\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_{t+1}}(\boldsymbol{\iota})]\}-\sigma_{\varepsilon}^2\right]- \left[\frac{\mathcal{F}\{\mathbf{E}[R_{y_{t+1}y_t}(\boldsymbol{\iota})]\}\mathcal{F}\left\{\mathbf{E}\left[R_{y_ty_{t+1}}(\boldsymbol\iota)\right] \right\}}{\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\} - \sigma_{\varepsilon}^2}\right]\right]\right\rbrace  ,
-\end{align}
-where
-\begin{equation}
- \tilde{m}(\boldsymbol\iota)=\mathcal{F}\{m(\boldsymbol\iota)\}\mathcal{F}\{m(\boldsymbol\iota)\}.
-\end{equation}
-% from \eqref{eq:EM=mmgamma},  when considering a sensor with a spatial extent equation \eqref{eq:EM-MMGFourier2} should be used
-From \eqref{eq:EM-MMGFourier2}, to calculate the exact shape of the disturbance covariance function, observation noise variance and the sensor kernel support are required.
-Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small.
-Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively.
-If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} is then required.
-Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
-\begin{equation}
- \sigma_d^2=\sigma_{mm\gamma}^2-4\sigma_m^2.
-\end{equation}
-where $\sigma_{mm\gamma}^2$ is the width of fitted Gaussian to the estimated support of $(m\ast m\ast\gamma)(\boldsymbol\iota)$.
+Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods of the seizure progression.
+By averaging over time, the effect of the disturbance is reduced allowing for the support of the kernel to be seen.
+The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition.
+The plots indicate the support for excitatory aspect of the kernel centred at the origin is -2~mm to 2~mm in the $x$ direction and slightly wider in the $y$ direction.
+Although the kernel is not isotropic, we will approximate it as being isotropic.
+This is for computation reasons.
+
+The assumption of homogeneity was tested by performing the cross-correlation analysis on 4 equal sized subsections of the field observations.
+The subsections consisted $6\times6$ electrode grids, such that they overlapped by one electrode row and column.
+The overlap was required so the subsections where large enough for the support of the kernel to be seen in the cross-correlation analysis.
+The results of the analysis can be seen in Figure~\ref{fig:HomogeneityTest}.
+The results show that each subsection of the field has similar cross-correlations, with each subplot showing local excitation with surround inhibition.
+From this analysis, we will approximate the connectivity kernel as being homogeneous.
+
 \subsection{Parametrisation of Connectivity Kernel}
@@
  Substituting equations \eqref{eq:jointdistribution} in \eqref{eq:QFunction} gives
-\begin{align}\label{eq:EM-QwithInitialstates}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta,\xi, \sigma_d) \right.\nonumber \\
-&\left.+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
-\end{align}
- The last term on the right-hand side of \eqref{eq:EM-QwithInitialstates} can be omitted as it does not depend on the parameter set, therefore $\mathcal Q$-function can be rewritten as
+\begin{align}
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta,\xi, \sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
+\end{align}
+ It should be noted that the last term is not a function of parameter set and can be dropped, therefore $\mathcal Q$-function can be rewritten as
 \begin{equation}\label{eq:QIntermsofJointDist}
@@
 \end{equation}
-Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions, where the normalising factors are ignored since scaling by a constant coefficient does not alter the location of the maximum with respect to the parameters.
+Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions, where the normalising factors are ignored 
 \begin{align}
  p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right),\\
-p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \nonumber \\
-&\times\exp \left(-\frac{1}{2}(\mathbf x_{t+1}-\mathbf q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\mathbf q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right).
-\end{align}
-Note that disturbance covariance matrix, $\boldsymbol\Sigma_e$, can be written as the product of the unknown parameter, $\sigma_d^2$ with the constant matrix, $\tilde{\boldsymbol\Sigma}_e$, where the constant part can be  calculated using the estimated support for disturbance covariance function, $\gamma$ from the correlation analysis (see equation \eqref{eq:EM-MMGFourier2}).
+p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \exp \left(-\frac{1}{2}(\mathbf x_{t+1}-q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right)
+\end{align}
+Note that the disturbance covariance matrix can be written as a product of the unknown parameter, $\sigma_d^2$ and a constant matrix, $\tilde{\boldsymbol\Sigma}_e$ where the constant part is calculated using the estimated support from the correlation analysis.
 By expanding the exponent and taking $2\ln$ we get
 \begin{align}\label{eq:CondititionDist1}
-2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],
-\end{align}
-\begin{align}
-2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}\nonumber \\
-&+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta 
-+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
-&-\frac{1}{\sigma_e^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta\nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
-\end{align}
-In the next step the above equation is rearranged in order to isolate the covariance and the cross-covariance terms, enabling the use of smoother outputs.
-Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
+2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],  \\
+2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
+&-\frac{1}{\sigma_e^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t.
+\label{eq:CondititionDist2}
+\end{align}
+\dean{Dean to check expansion.} Now we rearrange the equation so we can  use the information from the smoother.
+(or isolate (reason for doing this step is..)) the cross-covariance etc.
+Taking trace and rearranging, using the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
 \begin{align}\label{eq:Qfunctiontrace1}
-  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace
-\end{align}
-\begin{align}
- 2 \ln &p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) =-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta \nonumber \\
-&+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta \nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace. \label{eq:Qfunctiontrace2}
+  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace    \\
+ 2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) &=-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\boldsymbol\theta+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace.
+\label{eq:Qfunctiontrace2}
 \end{align}
@@
 \begin{align}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2\nonumber \\
-& -\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\right]\boldsymbol\theta
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&= -(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
+&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right]\boldsymbol\theta
  \nonumber \\
-&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  \mathbf q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right]\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)  \right] \boldsymbol\theta.
-\end{align}
-The third term in \eqref{eq:Voldermont} is obtained using the same method in \cite{Shumway2000}, i.e.
-by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1} .
+&-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right]\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \boldsymbol\theta
+\end{align}
+The second term in \eqref{eq:Voldermont} is obtained by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1}.
 By defining $\Xi$-variables as
@@
 	\boldsymbol\Xi_{0}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\label{eq:defofXi0} \\
-\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:defofXi1} \\
-\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\label{eq:defofXi2}\\
-\boldsymbol\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\right] \label{eq:defofXi3} \\	
-\boldsymbol\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  \mathbf q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1} \mathbf q(\mathbf x_t)\right] \label{eq:defofXi4}\\
- \boldsymbol\Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)  \right] \label{eq:defofXi5}
- \end{align}
-equation \eqref{eq:Voldermont} can be written in a form of
+\boldsymbol\Xi_{1}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right]\label{eq:Xi1} \\
+\boldsymbol\Xi_{2}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right]\label{eq:Xi2}\\
+\boldsymbol\Xi_{3}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q( \mathbf x_t)\right] \label{eq:Xi3} \\	
+\boldsymbol\Xi_{4}&= \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}  q^\top(\mathbf  x_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)\right] \label{eq:Xi4}\\
+ \boldsymbol\Xi_{5}&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf x_t)  \right] \label{eq:Xi5}
+ \end{align}
+equation \eqref{eq:Voldermont} can be written as
 \begin{align}\label{eq:VoldermontwitXivariables}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+&-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -  \frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\boldsymbol\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace
  \nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr} \left\lbrace\boldsymbol\Xi_{2}\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace +\frac{2}{\sigma_d^2}\boldsymbol\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \boldsymbol\Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2}\boldsymbol \Xi_{5} \boldsymbol\theta.
-\end{align}
-Covariance and cross-covariance terms in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
+&+\frac{2}{\sigma_d^2}\boldsymbol\Xi_{3}\boldsymbol\theta-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \boldsymbol\Xi_{4}\boldsymbol\theta-\frac{2\xi}{\sigma_d^2}\boldsymbol \Xi_{5} \boldsymbol\theta.
+\end{align}
+Covariance and cross-covariances in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
 Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e.
-$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ \cite{Gibsona2005}.
-To show how it can be done, the smoothed covariance matrix at time $t+1$ can be written as
-\begin{align}
- \mathbf P_{t+1}^b&=\mathbf E_{\Theta'}\left[(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)^{\top}\right]=\mathbf E_{\theta'}\left[\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]-\mathbf {\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\label{eq:EM-PrimeryXi0derivation1}\\
- \mathbf M_{t+1}^b&=\mathbf E_{\Theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t^b)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)^{\top}\right]= \mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf {\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top},\label{eq:EM-PrimeryXi1derivation1}
-\end{align}
-consequently,
-\begin{align}\label{eq:EM-Xi0derivation1}
- \mathbf E_{\Theta'}\left[\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\mathbf P_{t+1}^b+\mathbf {\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\\
- \mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}^b+\mathbf {\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\label{eq:EM-Xi1derivation1},
-\end{align}
-substituting \eqref{eq:EM-Xi0derivation1} and \eqref{eq:EM-Xi1derivation1} in \eqref{eq:defofXi0} and \eqref{eq:defofXi1} respectively , gives the final formula for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$, i.e.
+$\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using following expressions \cite{Gibsona2005} (see supporting information for details)
 \begin{align}
 	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}^b+\mathbf{\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\right)\label{eq:Xi0Gibson}, \\
-\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi1Gibson}.
-\end{align}
-The expression for $\boldsymbol\Xi_{2}$ can be derived in a similar manner, giving
-\begin{align}
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi1Gibson}, \\
 \boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).\label{eq:Xi2Gibson}
@@
 However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $\mathbf q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
+Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.
 \begin{equation}\label{eq:SigmoidTaylor}
- f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^b\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right),
+ f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\mathbf x_t\right) \approx f\left(\boldsymbol \phi^\top(\mathbf r')\hat{\mathbf x}_t^b\right)+  \boldsymbol \phi^\top\left(\mathbf r'\right)\left(\mathbf x_t - \hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)
 \end{equation}
 where 
-\begin{align}\label{eq:SigmoidDerivative}
- f'(\boldsymbol \phi^\top\left(\mathbf r'\right)&\hat{\mathbf x}_t^b)= \frac{\varsigma}{\left(1 + \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right)\right)^2} \times \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right) \nonumber \\
-=&\frac{\varsigma}{1 + \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right)} \times \left(1-\frac{1}{1 + \exp \left( \varsigma \left( v_0 - \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b \right) \right)}\right) \nonumber \\
-=& \varsigma f(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b)\left( 1-f(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right).
-\end{align}
-substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained
+\begin{equation}\label{eq:SigmoidDerivative}
+ f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)=\varsigma f\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)\left( 1-f\left( \boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right)\right)
+\end{equation}
+substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints}  we get an approximation for $q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ 
 \begin{equation}\label{eq:qTaylor}
- \mathbf q(\mathbf x_t) \approx \mathbf q(\hat{\mathbf x}_t^b)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right) d\mathbf{r}'.
-\end{equation}
-Having approximated $\mathbf q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:defofXi3}-\ref{eq:defofXi5}) an approximation to the non-linear $\boldsymbol\Xi$-variables can be made.
-The three nonlinear variables are dealt with in turn.
-To start with, first consider equation \eqref{eq:defofXi3}, substituting in equation \eqref{eq:qTaylor} for $\mathbf q\left(\mathbf x_t\right)$, the term under the summation can be approximated by
-\begin{align}\label{eq:Xi3Derivation1}
- \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t) &\approx \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}',
-\end{align}
-noting that $\phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)$ is a scalar, equation \eqref{eq:Xi3Derivation1} can be rewritten as 
-\begin{align}\label{eq:Xi3Derivation2}
- \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\approx\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}',
-\end{align}
-taking expected value of \eqref{eq:Xi3Derivation2} gives
-\begin{align}\label{eq:Xi3Derivation3}
- \mathbf E_{\boldsymbol\Theta'}\left[\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\right] &\approx \mathbf E_{\boldsymbol\Theta'}\left[\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b) \nonumber \\
-&+\int_\Omega \boldsymbol \phi^\top(\mathbf r')  \mathbf E_{\boldsymbol\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}',
-\end{align}
-Substituting for  $\mathbf E_{\boldsymbol\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\right]$ from equation \eqref{eq:EM-PrimeryXi1derivation1} and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
-\begin{equation}
-\boldsymbol\Xi_{3}\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right].
-\label{eq:Xi3Ap} \\
-\end{equation}
-To find an approximation for $\boldsymbol\Xi_4$, the same approach is applied by using \eqref{eq:qTaylor} for the nonlinear experession in equation \eqref{eq:defofXi4} giving
-\begin{align}\label{eq:Xi4derivation1}
- \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)&\approx \left[ \mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right]^\top  \times \tilde{\boldsymbol\Sigma}_e^{-1}\nonumber \\
-&\times\left[ \mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \nonumber \\
-&= \mathrm{term1} + \mathrm{term2} + \mathrm{term3} + \mathrm{term4}
+ q_L(\mathbf x_t) \approx q\left(\hat{\mathbf x}_t^b\right)+\int_\Omega \boldsymbol{\Psi}\left(\mathbf{r}'\right)\boldsymbol \phi^\top\left(\mathbf r'\right) \left(\mathbf x_t -\hat{\mathbf x}_t^b\right)f'\left(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right) d\mathbf{r}'
+\end{equation}
+Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated (see supporting information) which in turn provides an approximate lower bound on the log-likelihood function,
+\begin{align}
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi3Ap}\\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\Lambda_t\right]\label{eq:Xi4Ap} \\
+ \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi5Ap}
  \end{align}
 where
-\begin{align}
-  \mathrm{term1}&=\mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)
-\end{align}
-\begin{align}
-\mathrm{term2}=&\mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
- \end{align}
-\begin{align}
-\mathrm{term3}=&\int_\Omega \boldsymbol{\Psi}^\top(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)
-\end{align}
-\begin{align}\label{eq:-EMterm4}
- \mathrm{term4} &=\int_\Omega \boldsymbol{\Psi}^\top(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}' \times \tilde{\boldsymbol  \Sigma}_e^{-1} \nonumber \\
-&\times \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}' 
-\end{align}
-It should be noted that when applying expectation, term1 is constant, and term2 and term3 disapears as $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\right]= \mathbf 0$.
-However in term4 to use the covariance estimate from the smoother the $\mathbf{x}_t$ terms should be brought together.
-To do this equation \eqref{eq:-EMterm4} can be rewritten as
-\begin{align}
- term4 &= \int_\Omega \boldsymbol{\Psi}^\top(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) \boldsymbol \phi^\top(\mathbf r')(\mathbf x_t - \mathbf  {\hat x}_t^b)d\mathbf{r}' \times \tilde{\boldsymbol\Sigma}_e^{-1} \nonumber \\
-&\times\int_\Omega  (\mathbf x_t - \mathbf  {\hat x}_t^b)^\top\boldsymbol \phi(\mathbf r') \boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'& \nonumber \\
-&=\sum_{i,j=1}^{n_x}{\boldsymbol\Lambda}_t^{(i)\top}(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b)\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
-\end{align}
-where
-\begin{align}\label{eq:EM-Lambdat}
-	{\boldsymbol \Lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r'.
-\end{align}
-Now taking expectation from \eqref{eq:Xi4derivation1} gives
-\begin{align}\label{eq:Xi4derivation2}
-  \mathbf{E}_{\boldsymbol\Theta'}\left[ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right] &= \mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
-&+\sum_{i,j=1}^{n_x}{\boldsymbol\Lambda}_t^{(i)\top}\mathbf{E}_{\boldsymbol\Theta'}\left[(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b)\right] \tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
-\end{align}
-and noting $\mathbf E_{\boldsymbol\theta'}\left[(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b) \right]=\left[\mathbf{P}_t^b\right]_{i,j} $ gives
-\begin{align}
- \mathbf{E}_{\boldsymbol\Theta'}\left[ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right]&= \mathbf q^\top(\mathbf {\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t)+\boldsymbol\varLambda_t
-\end{align}
-where
-\begin{equation}
- \boldsymbol\varLambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\Lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
-\end{equation}
-and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
-\begin{align}
- \boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[\mathbf q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf \mathbf q(\mathbf{\hat x}_t^b)+\boldsymbol\varLambda_t\right]\label{eq:Xi4Ap}.
-\end{align}
-Finally, to calculate $\boldsymbol\Xi_5$, the nonlinear term can be treated in a smae way, using the expression for $\mathbf q(\mathbf x_t)$ in \eqref{eq:defofXi5} and rearranging gives
-\begin{align}\label{eq:Xi5derivation1}
- \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\approx\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
-\end{align}
-taking expected value of \eqref{eq:Xi5derivation1} gives
-\begin{align}\label{eq:Xi5derivation2}
-\mathbf E_{\Theta'}\left[\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf q(\mathbf x_t)\right]&\approx\mathbf E_{\Theta'}\left[\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
-&+\int_\Omega \boldsymbol \phi^\top(\mathbf r') \mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
-\end{align}
-substituting for $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right] $ from equation \eqref{eq:EM-PrimeryXi0derivation1} at time $t$, and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ gives
-\begin{align}
-\boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \label{eq:Xi5Ap}
- \end{align}
-By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete. The lower bound now can be used in M-step to find a set of new parameters. 
+\begin{equation}
+ \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
+\end{equation}
+and
+\begin{align}\label{eq:lambdat} 
+	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r'
+\end{align}
+By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete.
+The lower bound now can be used in M-step to find a set of new parameters.
+An approximate for computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+Note that computational complexity of the nonlinear terms depend on the number of points, $n_r$ used for spatial discritisation.
+In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found elsewhere \cite{Sarkka2010}.
+
+Define
+\begin{equation}
+	e(x) = q(x) - q_L(x) \nonumber
+\end{equation}
+
+Then we can write $q(x) = q_L(x) + e(x)$ and use this to show that the error in the estimate is proportional to $e(x)$.
+
+Equation \ref{eq:qTaylor} is used to approximate the lower bound on the log-likelihood function in the M-step.
+\dean{The difference between the linearised and nonlinear likelihood will be the error in the approximation at the state estimate that maximised the likelihood.}
 \subsection{M-Step}
 % In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
-The objective of the M-step is to maximize the computed lower bound in E-step, whcich consequenly increases the log-likelihood function $p(\mathbf Y;\boldsymbol\Theta)$.
+The objective of the M-step is to maximize the lower bound found in E-step, whcich consequenly increases the log-likelihood function $p(\mathbf Y;\boldsymbol\Theta)$.
 % on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
-                                                                                                                                                                                                                                                                                                                                                                                                                                                                            Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, differentiating equation \eqref{eq:VoldermontwitXivariables} with respec to the synaptic parameter gives
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                            Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, we can write
 \begin{equation}\label{eq:Qpartialxi}
@@
 \begin{equation}\label{eq:xihat}
- \hat{\xi}=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}.
-\end{equation}
-In order to maximise $\mathcal{Q}$-function with respect to the connectivity kernel parameters, $\boldsymbol\theta$, differentiation is taken as follows
+ \hat{\xi}=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}}
+\end{equation}
+In order to maximise $\mathcal{Q}$-function with respect to $\boldsymbol\theta$ we can write
 \begin{equation}\label{eq:Qpartialtheta}
@@
 \end{equation}
-The condition under which $\boldsymbol\Xi_4$ is invertible is discussed later in this section. Now maximising the lower bound with respect to $\sigma_{\epsilon}^2$ gives
-\begin{equation}
-  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace,
-\end{equation}
-and setting the above equation to zero and solving for $\sigma_{\epsilon}^2$ gives the result
+We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
+\begin{equation}
+  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
+\end{equation}
+setting above to zero and solving for $\sigma_{\epsilon}^2$ gives
 \begin{equation}\label{eq:sigmaepsilonhat}
- \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace.
-\end{equation}
-Finally differentiating the lower bound with respec to $\sigma_d^2$ gives
+ \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
+\end{equation}
+Finally differentiating with respec to $\sigma_d^2$ we get
 \begin{align}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace  \nonumber \\
-&+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace-\frac{2}{\sigma_d^4}\boldsymbol\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \boldsymbol\Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \boldsymbol\Xi_5 \boldsymbol\theta,
-\end{align}
-setting above to zero and solving for $\sigma_d^2$ completes the maximisation step
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace  \nonumber \\
+&-\frac{2}{\sigma_d^4}\boldsymbol\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \boldsymbol\Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \boldsymbol\Xi_5 \boldsymbol\theta 
+\end{align}
+setting above to zero and solving for $\sigma_d^2$ we have
 \begin{align}\label{eq:sigmadhat}
-\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
-2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace\right.\nonumber \\ &\left.-2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right].
+\hat{\sigma}_d^2=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right]
 \end{align}
@@
 \end{alignat}
-$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of state vectors, which is guaranteed by the disturbance, $\mathbf e$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore by \cite{Coope1994}
+$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of state vectors, which is guaranteed by the disturbance, $\mathbf e$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore we have \cite{Coope1994}
 \begin{equation}
@@
 Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}.
-The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004} (note that multiplying by $\mathbf \Gamma^{-1}$ has no effect on the rank).
-However, $\mathbf q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid function cannot be solved analytically, making it difficult to calculate the rank of $\mathbf q(\mathbf x_t)$ .
-Therefore, the rank of $\mathbf q(\mathbf x_t)$ at each iteration of the algorithm should be examined.
+The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}.
+(note that multiplying by $\mathbf \Gamma^{-1}$ doesn't change the rank).
+However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically, making it difficult to calculate the rank of $q(\mathbf x_t)$ .
+Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration of the E-step.
+% to show this we define
+% \begin{equation}
+%  \boldsymbol\Psi(\mathbf r')=T_s\boldsymbol\Gamma^{-1}\tilde{\boldsymbol\Psi}(\mathbf r')
+% \end{equation}
+% where 
+% \begin{equation}\label{eq:DefPsitilde}
+% 	\left[ \tilde{\boldsymbol\Psi}(\mathbf{r}')\right]_{:i} =\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\psi_i (2c_i+\mathbf{r}'-\mathbf{r})\textrm{d}\mathbf{r}},
+% \end{equation}
+% since matrix $\boldsymbol\Gamma^{-1}$ is symmetric
 From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function. 
-\subsection{Initialisation, stopping and algorithmic complexity}
-For initialisation a bounded random state sequence is employed to ensure that the initial parameter estimates describe a stable kernel, although the quality of such initial estimate is poor, it provides an initialisation that typically ensues a satisfactory convergence of the algorithm, as illustrated numerically in Result section.
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
-Here the change in parameter estimates, $L^2$-norm in the case of connectivity kernel weights, is used to halt the excecution of the algorithm.
-Besides, the lower bound on the likelihood function is also monitored to further investigate the convergence of the EM algorithm.
-
-An approximate for computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
-In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
-Note that computational complexity of the nonlinear terms depend on the number of points, $n_r$ used for spatial discritisation.
-Calculation of the nonlinear terms $\boldsymbol\Xi$ is clearly the slowest part of the algorithm where $n_x$ is the problematic dimension, more specifically the matrix $\boldsymbol\Xi_4 $ has complexity that grows with the order of four in $n_x$.
-Although number of states  is decoupled from number of observation locations (recording electrods) , and the number of basis functions required for the connectivity kernel decomposition, it does tend to grow linearly in one dimensional space and quadratically in two dimensional space.
-This growth assumes that the basis functions are arragend regularly in space, which is not a necessary construction.
-
 %  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 
@@
 Variable &Equation&Order\\ \hline\\
-$\mathbf q(\mathbf{x}_t)$&\eqref{}&$O(n_xn_{\theta}n_r)$\\
-$\boldsymbol\Xi_0, \boldsymbol\Xi_1, \boldsymbol\Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
-$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
-$\boldsymbol\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r)$\\
+$\Xi_0, \Xi_1, \Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
+$\Xi_3, \Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)+O(Tn_{\theta}n_r^2)$ \\
+$\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r^2)$\\
 $\hat{\xi}$&\eqref{eq:xihat}&$O(n_x^3+n_{\theta}^3)$\\
@@
 This section demonstrates the identification of the proposed IDE model using simulated data.
-The observation noise and the field disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
-Data was generated employing state-space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
+The observation noise and disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the kernel.
+Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state.
-Observation noise variance was set to 0.2.
-All other parameters for the simulation were the same as Chapter 2 (see Table 1.1).
+The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ .
+The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations.
+The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$.
+The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively.
+The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.
 
 The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function.
-However, to compute the supports the unknown parameters, $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
-To form a more accurate initial guess of the unkown parameters and explore the effect of chosen initial guess on the estimated supports several tests were performed.
-First consider equation \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
-As mentioned before the power spectral densities are non negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
-The minimum value of the power spectral density was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit.
-This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted.
-The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and thresholded for values less than 0.01.
-By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using equation \eqref{eq:EM-AnalyticSupportCalculation}.
-Alternatively deconvolution can also be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
-%Figure 1 here
-\begin{figure}[!ht]
-\centering
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation0.pdf}}
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation01.pdf}}
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation02.pdf}}\\
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation023.pdf}}
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation03.pdf}}
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation04.pdf}}
-\caption{{\bf Disturbance support estimates for variyng observation noise variance.} Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
-(\textbf a) $\sigma_{\varepsilon}^2$=0.
-(\textbf b) $\sigma_{\varepsilon}^2$=0.1 .
-(\textbf c) $\sigma_{\varepsilon}^2$=0.2 .
-(\textbf d) $\sigma_{\varepsilon}^2$=0.23 .
-(\textbf e) $\sigma_{\varepsilon}^2$=0.3 .
-(\textbf f) $\sigma_{\varepsilon}^2$=0.4 .}
-\label{fig:DisturbanceSupportExperiment}
-\end{figure}
-\begin{figure}[!ht]
-\begin{center}
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimationBinary.pdf}}
-\subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthTrue.pdf}}
-\end{center}
-\caption{{\bf Disturbance support approximation for }$\sigma_{\varepsilon}^2<$0.23.
-Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
-(\textbf{a}) Estimated support is shown by red circle, nonzero values after thresholding are shown by the black area.
-(\textbf{b}) True support.}
-\label{fig:BinaryDisturbanceWidthEstimation}
-\end{figure}
-\begin{figure}[!ht]
-\begin{center}
-\centering
-\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimationCrossSection.pdf}
-\end{center}
-\caption{{\bf Cross-section of disturbance covariance support estimation}. The normalized true and the estimated width are shown by solid and dashed lines respectively.}
-\label{fig:DisturbanceWidthEstimationCrossSection}
-\end{figure}
-\begin{figure}
-\begin{center}
-\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise0.pdf}}
-\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise01.pdf}}
-\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise018.pdf}}
-\end{center}
-\caption{{\bf Kernel support approximation for different values of synaptic time constant, $\tau$ and observation noise variance, $\sigma^2_{\varepsilon}$}.
-Each subplot shows normalised connectivity kernel estimate.
-(\textbf a) $\sigma_{\varepsilon}^2$=0.
-(\textbf b) $\sigma_{\varepsilon}^2$=0.1 .
-(\textbf c) $\sigma_{\varepsilon}^2$=0.18.}
-\label{fig:KernelWidthEstimationExperiment}
-\end{figure}
-The effect of the observation noise variance on the connectivity kernel support is very much like to that of disturbance covariance function where an initial guess can be made in a similar manner.
-To study how synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, influence the resultant support of the connectivity kernel different values of synaptic time constatnt, $\tau$, were considered in a physiologically plausible range while noting that its value should be also higher than the sampling time.
-In fact synaptic parameter in \eqref{eq:EM-Fourier_TF_of_Kernel}  acts like a scaling factor, dilating or shrinking the estimated support, as the subtracting a constant in a frequency domain only affects the value at the origin in the spatial domain.
-The result of the correlation analysis for the connectivity kernel is shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised  estimate for varying synaptic time constants while the observation noise was kept constant.
-Note that for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
-The result suggests that choosing the range of approximately $\left[-5,5 \right] $ is reasonable for the spatial extent of the connectivity kernel.
-
- By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
+In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero.
+By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as a prerequisite for the EM algorithm, however, an approximate of their support can be still extracted.
 In fact, the estimated support for the disturbance covariance function was very accurate.
@@
 The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}.
-By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
-
-The estimated supports were then employed in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
-A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated kernel support where $\sigma_{\psi}^2=3.5$.
+By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor,$\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
+
+The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
+A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$.
 This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.
@@
 \section{Discussion}
-The correlation analysis specifies approximate supports for both disturbance covariance function and connectivity kernel.
-Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S~\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate to be in the active region, as a result  the kernel and the disturbance amplitudes cannot be inferred only through correlation analysis.
-This step might be considered as a prerequisite for the EM algorithm described in \S~\ref{sec:EstimationAlgorithm} where approximated supports are employed to estimate the gain of the kernel and disturbance.
-Knowing the spatial extent of the kernel greatly increases the speed of the algorithm as the number of basis functions to decompose the kernel reduces significanly compared to the case in which the basis funtions are laid out across the entire spatial domain.
-This also improves the uncertainty of the estimates because of the lower number of parameters needs to be estimated.
-On the other hand, the approximated support of the disturbance covariance function facilitates the implementation of the EM algorithm as the disturbance covariance matrix can be factorised into two components, a constant matrix depending only on the inferred support and an unknown scaling parameter.
-This way the problem of estimating the covariance matrix reduces to estimation of a single scaling parameter.
-
-The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the nonlinear equations about the state estimates.
-This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of state vecors in the presented framework.
-However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible.
-Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure.
-In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the approximated lower bound will be more accurate  resulting in better parameter estimations.
-
-While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm.
-However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured.
-Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
+
 \begin{itemize}
+	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
+	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property than using EM with URTSS
 	\item itterative EM and correlation analysis (maybe)
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\centering
-% \subfloat[][]{\includegraphics[scale=1]{./Graph/EM/Q.pdf}}\\
-\subfloat[][]{\includegraphics[scale=1]{./Figures/ParameterConvergence.pdf}}\\
-\centering
-\subfloat[][]{\includegraphics[scale=1]{./Figures/KernelConvergence.pdf}}
-\caption{{\bf Convergence of parameters}.
-All parameters converge after 9 iterations.
-(\textbf a) The logarithm of the mean of synaptic parameter, observation noise variance and field disturbance variance over 100 realisations.
-(\textbf b) The mean kernel estimates at each iteration of the EM algorithm.}
-\label{fig:ParameterConvergence}
-\end{figure}
-
-\clearpage
-\newpage
-\appendix
-\section{Product of two $n$-dimensional Gaussian functions}\label{sec:GaussianProduct} 
-In this section, we provide a derivation for the product of two n-dimensional Gaussian basis functions.
-This derivation is used in the  calculation of $\boldsymbol\Lambda_t^{(i)}$  defined in equation \eqref{eq:EM-Lambdat} of the main text. Consider two
-Gaussian basis functions
-\begin{equation}\label{eq:n_dimensional_Gaussian1}
- \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
-\end{equation}
-and 
-\begin{equation}\label{eq:n_dimensional_Gaussian2}
-\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
-\end{equation}
-the product of two Gauusian basis functions is given by
-\begin{equation}
- \varphi_i(\mathbf r)\varphi_j(\mathbf r)=\mathrm{exp}\left(-\left[ {\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol\mu_i)+{\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol\mu_j)}}\right] \right)
-\end{equation}
-the product is expanded to give
-\begin{align} 
- \varphi_i(\mathbf r)\varphi_j(\mathbf r)&=
-\mathrm{exp}\left(-\left[ \frac{(\sigma_i^2+\sigma_j^2)\left[\mathbf r^\top\mathbf r-2\mathbf r^\top \frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2}+\frac{(\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j)^\top(\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j)}{(\sigma_i^2+\sigma_j^2)^2}\right]}{\sigma_i^2\sigma_j^2}\right.\right.
-\nonumber\\
-&\left.\left. \frac{+\frac{\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}(\boldsymbol \mu_i-\boldsymbol\mu_j)^\top(\boldsymbol \mu_i-\boldsymbol\mu_j)}{}\right]\right) \nonumber\\
-  &=\mathrm{exp}\left(-\frac{(\sigma_i^2+\sigma_j^2)\left[(\mathbf r-\frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2})^\top(\mathbf r-\frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2})\right]  }{\sigma_i^2\sigma_j^2}\right) \nonumber \\
-   &\times\mathrm{exp}\left(-\frac{(\boldsymbol \mu_i-\boldsymbol\mu_j)^\top(\boldsymbol \mu_i-\boldsymbol\mu_j)}{\sigma_i^2+\sigma_j^2}\right),
-\end{align}
-therefore we have
-\begin{equation}
- \varphi_i(\mathbf r)\varphi_j(\mathbf r)=c_{i,j}\times\mathrm{exp}\left({-\frac{1}{\sigma^2} (\mathbf r-\boldsymbol \mu)^\top(\mathbf r-\boldsymbol\mu)}\right)
-\end{equation}
-where
-\begin{equation}
- c_{i,j}=\mathrm{exp}\left(-\frac{(\boldsymbol \mu_i-\boldsymbol\mu_j)^\top(\boldsymbol \mu_i-\boldsymbol\mu_j)}{\sigma_i^2+\sigma_j^2}\right) \quad \sigma^2=\frac{\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}
-\end{equation}
-and
-\begin{equation}
- \boldsymbol\mu=\frac{\sigma_j^2\boldsymbol\mu_i+\sigma_i^2\boldsymbol\mu_j}{\sigma_i^2+\sigma_j^2}
-\end{equation}
-
-\section{Cross-correlation and convolution}\label{ap:CorrelationAnalysis}
-This appendix provide a proof for the properties of the cross-correlation and convolution used in the Correlation analysis Section of Chapter 2. To show 
-\begin{equation}\label{eq:app-ConvXcorRelation1}
- \left(a \ast b \right)\left(\boldsymbol\iota\right)  \star c\left(\boldsymbol\iota\right)  = a\left(-\boldsymbol\iota\right)\ast\left(b \star c\right)\left(\boldsymbol\iota\right)
-\end{equation}
-and
-\begin{equation}\label{eq:app-ConvXcorRelation2}
-(a \ast b)(\boldsymbol \iota) \star (a \ast b)(\boldsymbol\iota)=(a \star a)(\boldsymbol\iota)\ast(b \star b)(\boldsymbol\iota),
-\end{equation}
-first note that cross-correlation function is related to the convolution by \cite{Yarlagadda2009}
-\begin{equation}\label{eq:app-ConvXcorRelation}
- \left(a \star b\right)\left(\boldsymbol\iota\right)= a\left(-\boldsymbol\iota\right)\ast b\left(\boldsymbol\iota\right).
-\end{equation}
-Therefore, equation \eqref{eq:app-ConvXcorRelation1} can be wriiten as
-\begin{align}
- \left(a \ast b\right)\left(\boldsymbol\iota\right) \star c\left(\boldsymbol\iota\right)&= \left(a \ast b\right)\left(-\boldsymbol\iota \right)\ast c\left(\boldsymbol\iota\right) \nonumber \\
-&=a\left(-\boldsymbol\iota\right)\ast \left(b\left(-\boldsymbol\iota\right) \ast c\left(\boldsymbol\iota\right)\right)\nonumber \\
-&=a\left(-\boldsymbol\iota\right)\ast\left(b\star c\right)\left(\boldsymbol\iota\right).
-\end{align}
-Similarly, equation \eqref{eq:app-ConvXcorRelation2} can be written as
-\begin{align}
- (a \ast b)(\boldsymbol \iota) \star (a \ast b)(\boldsymbol\iota)&=(a \ast b)(-\boldsymbol\iota) \ast (a \ast b)(\boldsymbol\iota) \nonumber \\
-&=a(-\boldsymbol\iota)\ast a(\boldsymbol\iota) \ast b(-\boldsymbol\iota)\ast b(\boldsymbol\iota) \nonumber \\
-&=(a \star a)(\boldsymbol\iota)\ast(b \star b)(\boldsymbol\iota).
-\end{align}
 

### 2011-07-21 ltx/data_paper/DataPaper.tex
minor edits

--- 2011-07-16 ltx/data_paper/DataPaper.tex
@@
 \section{Estimation Algorithm}\label{sec:EstimationAlgorithm}
-Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
+Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000} is described.
 EM is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
@@
 \end{itemize}
+\scetion{Conclusion}
 

### 2011-07-21 ltx/first_order_framework/LaTeX_Manuscript.tex
editted xcorr analysis

@@
 
-\newcommand{\dean}[1]{\textcolor{red}{#1}}
-\newcommand{\parham}[1]{\textcolor{blue}{#1}}
+% \newcommand{\dean}[1]{\textcolor{red}{#1}}
+% \newcommand{\parham}[1]{\textcolor{blue}{#1}}
 % \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
@@
 \bibliographystyle{./elsarticle/model2-names} 
+% \bibliographystyle{model2-names} 
 \bibliography{BrainIDE}
@@
 \singlespacing
-
 \begin{table*}[!ht]
@@
 	\hline
-	$\Delta$ & spatial discretization step & 0.5 & mm \\
+	$\Delta$ & spatial discretisation step & 0.5 & mm \\
 	$T_s$ & time step & $0.001$ & s\\
@@
 % \end{figure*}
+
 \clearpage

### 2011-07-28 ltx/data_paper/DataPaper.tex
minor edits
edits to discussion and conclusion

@@
 that the algorithm converged to steady parameter values.
-\section{Discussion}
-The correlation analysis specifies approximate supports for both disturbance covariance function and connectivity kernel.
-Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S~\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate to be in the active region, as a result  the kernel and the disturbance amplitudes cannot be inferred only through correlation analysis.
-This step might be considered as a prerequisite for the EM algorithm described in \S~\ref{sec:EstimationAlgorithm} where approximated supports are employed to estimate the gain of the kernel and disturbance.
-Knowing the spatial extent of the kernel greatly increases the speed of the algorithm as the number of basis functions to decompose the kernel reduces significanly compared to the case in which the basis funtions are laid out across the entire spatial domain.
-This also improves the uncertainty of the estimates because of the lower number of parameters needs to be estimated.
-On the other hand, the approximated support of the disturbance covariance function facilitates the implementation of the EM algorithm as the disturbance covariance matrix can be factorised into two components, a constant matrix depending only on the inferred support and an unknown scaling parameter.
-This way the problem of estimating the covariance matrix reduces to estimation of a single scaling parameter.
-
-The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the nonlinear equations about the state estimates.
-This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of state vecors in the presented framework.
-However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible.
-Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure.
-In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the approximated lower bound will be more accurate  resulting in better parameter estimations.
-
-While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm.
-However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured.
-Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
-
-In almost all applications a sequence of likelihood converges to some stationary values i.e.
+\section{Discussion}\label{sec:EM-Discussion}
+The correlation analysis specifies approximate supports for both the disturbance covariance function and connectivity kernel.
+Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate in the active region, as a result  the kernel and disturbance amplitudes cannot be inferred only through the correlation analysis.
+This step might be considered as a prerequisite for the EM algorithm described in \S\ref{subsec:EM-EMAlgorithm} where the approximated supports are used to estimate the gain of the kernel and field disturbance variance.
+Knowing the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition is significantly reduced  compared to the case where the basis functions are arranged across the entire spatial domain.
+This also improves the uncertainty of the estimates as lower number of unknown parameters need to be estimated.
+The approximated support of the disturbance covariance function facilitates the application of the EM algorithm.
+This way the disturbance covariance matrix can be decomposed into two parts: an unknown scalar and a constant matrix depending only on the inferred spatial support.
+Therefore, the estimation problem of the disturbance covariance matrix breaks down to the estimation of a single scalar parameter, improving the accuracy and the convergence property of the algorithm.
+
+The additional Taylor approximation step introduced in the E-step of the algorithm resembles the extended Kalman filtering \cite{Jazwinski1970,Chui2009}.
+EKF approximates a stationary non-linear dynamic system with a linear non-stationary one using first order Taylor expansion around the state estimates.
+This might imply that the extended Kalman smoother is a better candidate (in terms of implementation) for the state inference in the proposed algorithm.
+However, extended Kalman smoother (EKS) requires re-linearising about the backwards estimates which in turn necessitates the non-linear mapping to be uniquely invertible.
+Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation.
+In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the constructed lower bound will be more accurate, resulting in a better parameter estimation.
+
+While EKS has been  applied in the EM algorithm for learning non-linear models \cite{Ghahramani1999} this is the first work (to the best author's knowledge) where the URTSS is used in this context.
+However, as in the case of the EKS the stability of the algorithm cannot be ensured.
+This is because the use of EKS or URTSS represents an approximation to the exact E-step.
+As a result the maximisation of the approximated lower bound might not necessairly increase the log-likelihood function.
+Nevertheless, it is envisaged that the use of URTSS will provide a more stable algorithm due to its superior performance.
+
+Typically a sequence of likelihood values converge to some stationary points i.e.
 global (local) maximum or a saddle point.
-If the sequence of EM is trapped in a saddle point a small random purturbation diverges the EM from the saddle point \cite{McLachlan1997}.
-In general convergence of the EM algorithm to any stationary point either global (local) maxima or saddle points
-depends on the initialisation. Here a bounded sequence of state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and good parameter estimations.
-
-Since the non-linearity is a sigmoid function first-order Taylor approximation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
-\begin{itemize}
-	\item itterative EM and correlation analysis (maybe)
-\end{itemize}
-\scetion{Conclusion}
+If the sequence of EM is trapped in a saddle point a small random perturbation diverges the algorithm from such a stationary value \cite{McLachlan1997}.
+In general convergence of the EM algorithm to any stationary points either global (local) maxima or saddle points depends on the initialisation.
+Here a bounded sequence of the state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and parameter estimations.
+
+Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
+\section{Conclusion}
+In this chapter, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
+It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified.
+This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process.
+In addition to the connectivity kernel weights, synaptic parameter, observation noise and disturbance variances were also identified.
+The empirical distributions of the estimated non-kernel parameters showed small bias with very smalll standard deviations.
 

### 2011-07-28 ltx/data_paper/DataPaper.tex
edits to discussion and conclusion

@@
 \section{Conclusion}
-In this chapter, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
+In this paper, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
 It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified.

### 2011-07-28 ltx/data_paper/DataPaper.tex
added algorithm

@@
 \usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
-
+% Algorithms
+\usepackage{float}
+\floatstyle{ruled}
+\newfloat{algorithm}{htbp}{loa}
+\floatname{algorithm}{Algorithm}
 \newif\ifpdf
@@
 Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of rank $n_{\theta}$ \cite{Golub1996}.
-The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004} (note that multiplying by $\mathbf \Gamma^{-1}$ has no effect on the rank).
-However, $\mathbf q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid function cannot be solved analytically, making it difficult to calculate the rank of $\mathbf q(\mathbf x_t)$ .
-Therefore, the rank of $\mathbf q(\mathbf x_t)$ at each iteration of the algorithm should be examined.
-From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+However, $\mathbf q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid function cannot be found analytically \cite{MacKay1992}, making it difficult to calculate the rank of $\mathbf q(\mathbf x_t)$.
+Therefore, the rank of $\mathbf q(\mathbf x_t)$ at each iteration of the algorithm should be examined numerically.
+In the experiments of this work the problem of rank deficiency was never encountered.
+From \eqref{eq:SecondDerivativenoise} and \eqref{eq:SecondDerivativedisturbance}, the observation noise and disturbance variance estimates clearly represent maxima of the $\mathcal{Q}$-function.
+The joint state and parameter estimation algorithm is summarised in Algorithm~\ref{alg:EM-EMAlgorithm}.
+\begin{algorithm}\footnotesize
+\caption{Joint state and parameter estimation for the IDE model.}
+\label{alg:EM-EMAlgorithm}
+\begin{enumerate}
+\item  Initialise:
+Generate a bounded, random sequence of dimension $n_x$ and use as the initial state sequence estimate.
+\item Approximate $\Xi$-variables
+\begin{align}
+	\boldsymbol\Xi_{0}&=\sum_{t=0}^{T-1}\left(\mathbf P_{t+1}^b+\mathbf{\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\right)\nonumber \\
+\boldsymbol\Xi_{1}&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right)\nonumber\\
+\boldsymbol\Xi_{2}&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right)\nonumber\\
+\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1}^b \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right]  \nonumber \\
+\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[\mathbf q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\sum_{i,j=1}^{n_x}[\mathbf{P}_t^b]_{ij}{\boldsymbol\Lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)}\right]\nonumber\\
+ \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^{b\top}\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t^b \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \nonumber
+ \end{align}
+\item Calculate the parameter estimates
+\begin{align}
+ \hat{\xi}&=\frac{\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_3^\top}{\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\boldsymbol\Xi_5\boldsymbol\Xi_4^{-1}\boldsymbol\Xi_5^{\top}} \nonumber\\
+ \hat{\boldsymbol \theta}&=\boldsymbol\Xi_4^{-1}\left(\boldsymbol\Xi_3^\top-\hat{\xi}\boldsymbol\Xi_5^\top \right)\nonumber\\
+\hat{\sigma}_{\epsilon}^2&=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace \nonumber\\
+\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+2\hat{\xi}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\hat{\xi}^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace\right.\nonumber \\ &\left.-2\boldsymbol\Xi_3\hat{\boldsymbol\theta}+\hat{\boldsymbol\theta}^\top\boldsymbol \Xi_4\hat{\boldsymbol\theta}+2\hat{\xi}\boldsymbol\Xi_5 \hat{\boldsymbol\theta}\right] \nonumber
+\end{align}
+\item E step: Execute Algorithm~2.1 of chapter 2, and perform the additional step
+\begin{align}
+\mathbf M_{t +1}^{b}=\mathbf S_t\mathbf P_{t+1}^{b} \nonumber
+\end{align}
+and compute the $\Xi$-variables using step 2.
+\item M step: execute step 3.
+\item Calculate stopping criterion.
+\end{enumerate}
+\end{algorithm}
 \subsection{Initialisation, stopping and algorithmic complexity}

### 2011-07-29 ltx/data_paper/DataPaper.tex
commit for merge

--- 2011-07-28 ltx/data_paper/DataPaper.tex
@@
 \section{Estimation Algorithm}\label{sec:EstimationAlgorithm}
-Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000} is described.
+Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}.
 EM is an iterative algorithm that converges on the maximum-likelihood estimates of the parameters.
@@
 that the algorithm converged to steady parameter values.
-\section{Discussion}\label{sec:EM-Discussion}
-The correlation analysis specifies approximate supports for both the disturbance covariance function and connectivity kernel.
-Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate in the active region, as a result  the kernel and disturbance amplitudes cannot be inferred only through the correlation analysis.
-This step might be considered as a prerequisite for the EM algorithm described in \S\ref{subsec:EM-EMAlgorithm} where the approximated supports are used to estimate the gain of the kernel and field disturbance variance.
-Knowing the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition is significantly reduced  compared to the case where the basis functions are arranged across the entire spatial domain.
-This also improves the uncertainty of the estimates as lower number of unknown parameters need to be estimated.
-The approximated support of the disturbance covariance function facilitates the application of the EM algorithm.
-This way the disturbance covariance matrix can be decomposed into two parts: an unknown scalar and a constant matrix depending only on the inferred spatial support.
-Therefore, the estimation problem of the disturbance covariance matrix breaks down to the estimation of a single scalar parameter, improving the accuracy and the convergence property of the algorithm.
-
-The additional Taylor approximation step introduced in the E-step of the algorithm resembles the extended Kalman filtering \cite{Jazwinski1970,Chui2009}.
-EKF approximates a stationary non-linear dynamic system with a linear non-stationary one using first order Taylor expansion around the state estimates.
-This might imply that the extended Kalman smoother is a better candidate (in terms of implementation) for the state inference in the proposed algorithm.
-However, extended Kalman smoother (EKS) requires re-linearising about the backwards estimates which in turn necessitates the non-linear mapping to be uniquely invertible.
-Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation.
-In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the constructed lower bound will be more accurate, resulting in a better parameter estimation.
-
-While EKS has been  applied in the EM algorithm for learning non-linear models \cite{Ghahramani1999} this is the first work (to the best author's knowledge) where the URTSS is used in this context.
-However, as in the case of the EKS the stability of the algorithm cannot be ensured.
-This is because the use of EKS or URTSS represents an approximation to the exact E-step.
-As a result the maximisation of the approximated lower bound might not necessairly increase the log-likelihood function.
-Nevertheless, it is envisaged that the use of URTSS will provide a more stable algorithm due to its superior performance.
-
-Typically a sequence of likelihood values converge to some stationary points i.e.
+\section{Discussion}
+The correlation analysis specifies approximate supports for both disturbance covariance function and connectivity kernel.
+Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S~\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate to be in the active region, as a result  the kernel and the disturbance amplitudes cannot be inferred only through correlation analysis.
+This step might be considered as a prerequisite for the EM algorithm described in \S~\ref{sec:EstimationAlgorithm} where approximated supports are employed to estimate the gain of the kernel and disturbance.
+Knowing the spatial extent of the kernel greatly increases the speed of the algorithm as the number of basis functions to decompose the kernel reduces significanly compared to the case in which the basis funtions are laid out across the entire spatial domain.
+This also improves the uncertainty of the estimates because of the lower number of parameters needs to be estimated.
+On the other hand, the approximated support of the disturbance covariance function facilitates the implementation of the EM algorithm as the disturbance covariance matrix can be factorised into two components, a constant matrix depending only on the inferred support and an unknown scaling parameter.
+This way the problem of estimating the covariance matrix reduces to estimation of a single scaling parameter.
+
+The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the nonlinear equations about the state estimates.
+This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of state vecors in the presented framework.
+However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible.
+Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure.
+In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the approximated lower bound will be more accurate  resulting in better parameter estimations.
+
+While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm.
+However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured.
+Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
+
+In almost all applications a sequence of likelihood converges to some stationary values i.e.
 global (local) maximum or a saddle point.
-If the sequence of EM is trapped in a saddle point a small random perturbation diverges the algorithm from such a stationary value \cite{McLachlan1997}.
-In general convergence of the EM algorithm to any stationary points either global (local) maxima or saddle points depends on the initialisation.
-Here a bounded sequence of the state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and parameter estimations.
-
-Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
+If the sequence of EM is trapped in a saddle point a small random purturbation diverges the EM from the saddle point \cite{McLachlan1997}.
+In general convergence of the EM algorithm to any stationary point either global (local) maxima or saddle points
+depends on the initialisation. Here a bounded sequence of state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and good parameter estimations.
+
+Since the non-linearity is a sigmoid function first-order Taylor approximation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
+\begin{itemize}
+	\item itterative EM and correlation analysis (maybe)
+\end{itemize}
 \section{Conclusion}
-In this paper, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
-It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified.
-This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process.
-In addition to the connectivity kernel weights, synaptic parameter, observation noise and disturbance variances were also identified.
-The empirical distributions of the estimated non-kernel parameters showed small bias with very smalll standard deviations.
 

### 2011-07-29 ltx/data_paper/DataPaper.tex
general edits to the data paper

--- 2011-07-28 ltx/data_paper/DataPaper.tex
@@
 \end{equation}
-Gaussian distributions of the state disturbance and the observation noise results into the following conditional distributions, where the normalising factors are ignored since scaling by a constant coefficient does not alter the location of the maximum with respect to the parameters.
-\begin{align}
- p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right),\\
-p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \nonumber \\
+The distribution of the initial states is assumed to be Gaussian and known.
+Therefore, the last term on the right-hand side of \eqref{eq:EM-QwithInitialstates} can be omitted as it does not depend on the parameter set, $\mathcal Q$-function can be then rewritten as
+\begin{equation}\label{eq:QIntermsofJointDist}
+\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1}; \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi ,\sigma_d)\right].
+\end{equation}
+Gaussian distributions of the field disturbance and the observation noise result into the following conditional distributions, where the constant normalising factors are dropped as multiplying by a constant does not alter the location of the maximum.
+\begin{align}\label{eq:EM-twicelog1}
+ p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right),
+\end{align}
+\begin{align}\label{eq:EM-twicelog2}
+p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta , \xi, \sigma_d)&= \mid\boldsymbol\Sigma_{e}\mid^{-\frac{1}{2}} \nonumber \\
 &\times\exp \left(-\frac{1}{2}(\mathbf x_{t+1}-\mathbf q(\mathbf  x_t)\boldsymbol\theta-\xi  \mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}(\mathbf x_{t+1}-\mathbf q( \mathbf x_t)\boldsymbol\theta-\xi \mathbf  x_t) \right).
 \end{align}
-Note that disturbance covariance matrix, $\boldsymbol\Sigma_e$, can be written as the product of the unknown parameter, $\sigma_d^2$ with the constant matrix, $\tilde{\boldsymbol\Sigma}_e$, where the constant part can be  calculated using the estimated support for disturbance covariance function, $\gamma$ from the correlation analysis (see equation \eqref{eq:EM-MMGFourier2}).
-By expanding the exponent and taking $2\ln$ we get
+Note that the disturbance covariance matrix, $\boldsymbol\Sigma_e$, can be written as the product of the unknown parameter, $\sigma_d^2$ with a constant matrix, $\tilde{\boldsymbol\Sigma}_e$, where the constant part can be calculated (\parham{from \eqref{eq:DisturbanceCovariance}}) using the estimated support for the disturbance covariance function, $\gamma$, from the correlation analysis (see \eqref{eq:EM-MMGFourier2}).
+This simplifies the M-step significantly as the estimation of the entire covariance matrix  reduces to the estimation of the single scalar  $\sigma_d^2$.
+By expanding the exponent in \eqref{eq:EM-twicelog1} and \eqref{eq:EM-twicelog2}, twice the logarithm of the results give
 \begin{align}\label{eq:CondititionDist1}
@@
 \begin{align}
-2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}\nonumber \\
-&+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta 
-+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t \nonumber \\
-&-\frac{1}{\sigma_e^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta\nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
-\end{align}
-In the next step the above equation is rearranged in order to isolate the covariance and the cross-covariance terms, enabling the use of smoother outputs.
+2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\xi, \sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta\nonumber \\
+&+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t -\frac{1}{\sigma_e^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta\nonumber\nonumber \\
+& -\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
+% &-\franc{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
+\end{align}
+In the next step the above equations are rearranged to isolate the covariance and the cross-covariance terms, allowing the smoother outputs to be used.
+In order to permute the matrices, the scalar nature of the likelihood is exploited, this way the trace operator can be applied to express the likelihood in a more compact form.
 Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
@@
 \begin{align}
- 2 \ln &p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d) =-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta \nonumber \\
+ 2 \ln &p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi, \sigma_d) =-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta \nonumber \\
 &+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta \nonumber \\
@@
 \end{align}
-Substituting  \eqref{eq:Qfunctiontrace1} and \eqref{eq:Qfunctiontrace2} into \eqref{eq:QIntermsofJointDist} and taking the expectation of the log likelihood function for all time instants gives the lower-bound which is to be maximised in the M-step.
+Substituting  \eqref{eq:Qfunctiontrace1} and \eqref{eq:Qfunctiontrace2} back into \eqref{eq:QIntermsofJointDist} and taking the expectation of the log-likelihood function at all time instants gives the required lower-bound.
+Note that the expectation distributes over the trace sum.
 \begin{align}\label{eq:Voldermont}
  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2\nonumber \\
-& -\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+& -\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b)^\top+\mathbf C \mathbf P_{t+1}^b\mathbf C^\top\right] \right\rbrace\nonumber \\
 &-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
@@
 The third term in \eqref{eq:Voldermont} is obtained using the same method in \cite{Shumway2000}, i.e.
-by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1} \mathbf{\hat{x}}_{t+1}^\top \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1} .
+by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1}^b \mathbf{\hat{x}}_{t+1}^{b\top} \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1} and then exploiting the expression given in \eqref{eq:EM-Xi0derivation1} .
 By defining $\Xi$-variables as
@@
  \end{align}
-equation \eqref{eq:Voldermont} can be written in a form of
+equation \eqref{eq:Voldermont} can be written in a more compact form
 \begin{align}\label{eq:VoldermontwitXivariables}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b)^\top+\mathbf C \mathbf P_{t+1}^b\mathbf C^\top\right] \right\rbrace\nonumber \\
 &-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace
@@
 \end{align}
-Covariance and cross-covariance terms in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
-Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e.
+The covariance and cross-covariance terms in \eqref{eq:VoldermontwitXivariables}, consist of both the linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
+Finding the linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly from the smoother outputs, i.e.
 $\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ \cite{Gibsona2005}.
@@
 \begin{align}\label{eq:EM-Xi0derivation1}
- \mathbf E_{\Theta'}\left[\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\mathbf P_{t+1}^b+\mathbf {\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}\\
+ \mathbf E_{\Theta'}\left[\mathbf x_{t+1}\mathbf x_{t+1}^\top\right]=\mathbf P_{t+1}^b+\mathbf {\hat x}_{t+1}^b\mathbf{\hat x}_{t+1}^{b\top}
+\end{align}
+\begin{align}
  \mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}^b+\mathbf {\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\label{eq:EM-Xi1derivation1},
@@
 \end{align}
-However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in linear case.
-Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $\mathbf q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$.
-This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.
+However calculation of the non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case.
+Therefore, an additional Taylor expansion step to the URTSS algorithm is also created to linearise $\mathbf q(\mathbf{x}_t)$, enabling the  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$ using the smoother outputs.
+This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function at each time instant  around the smoothed state, $\hat{\mathbf x}_t^b$, i.e.
 \begin{equation}\label{eq:SigmoidTaylor}
@@
 where 
+% \begin{align}\label{eq:SigmoidDerivative}
+%  f'(\boldsymbol \phi^\top\left(\mathbf r'\right)&\hat{\mathbf x}_t^b)= \varsigma f(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b)\left( 1-f(\boldsymbol \phi^\top\left(\mathbf r'\right)\hat{\mathbf x}_t^b\right).
+% \end{align}
  \begin{align}\label{eq:SigmoidDerivative}
@@
  \end{align}
-substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained
+substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:EM-Stateequationnonlinearity},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained
 \begin{equation}\label{eq:qTaylor}
@@
 \end{equation}
-Having approximated $\mathbf q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:defofXi3}-\ref{eq:defofXi5}) an approximation to the non-linear $\boldsymbol\Xi$-variables can be made.
-The three nonlinear variables are dealt with in turn.
-To start with, first consider equation \eqref{eq:defofXi3}, substituting in equation \eqref{eq:qTaylor} for $\mathbf q\left(\mathbf x_t\right)$, the term under the summation can be approximated by
+Having approximated $\mathbf q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:defofXi3}-\ref{eq:defofXi5}) an approximation to each of the non-linear $\boldsymbol\Xi$-variable can be made.
+The three non-linear variables are dealt with in turn.
+To start, first consider \eqref{eq:defofXi3}, substituting in \eqref{eq:qTaylor} for $\mathbf q\left(\mathbf x_t\right)$, the term under the summation sign can be approximated by
 \begin{align}\label{eq:Xi3Derivation1}
@@
 \end{align}
-noting that $\phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)$ is a scalar, equation \eqref{eq:Xi3Derivation1} can be rewritten as 
+noting that $\phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)$ is scalar, \eqref{eq:Xi3Derivation1} can be rearranged in the form 
 \begin{align}\label{eq:Xi3Derivation2}
@@
 \end{align}
-Substituting for  $\mathbf E_{\boldsymbol\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\right]$ from equation \eqref{eq:EM-PrimeryXi1derivation1} and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
+Substituting for  $\mathbf E_{\boldsymbol\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_{t+1}^\top\right]$ from \eqref{eq:EM-PrimeryXi1derivation1} and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
 \begin{equation}
@@
 \end{equation}
-To find an approximation for $\boldsymbol\Xi_4$, the same approach is applied by using \eqref{eq:qTaylor} for the nonlinear experession in equation \eqref{eq:defofXi4} giving
+To find an approximation for $\boldsymbol\Xi_4$, a similar approach is used where the non-linear expression in \eqref{eq:defofXi4} is replaced by \eqref{eq:qTaylor}  giving
 \begin{align}\label{eq:Xi4derivation1}
@@
 &\times\left[ \mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'\right] \nonumber \\
-&= \mathrm{term1} + \mathrm{term2} + \mathrm{term3} + \mathrm{term4}
+&= \mathrm{term1} + \mathrm{term2} + \mathrm{term3} + \mathrm{term4},
 \end{align}
@@
 \end{align}
-It should be noted that when applying expectation, term1 is constant, and term2 and term3 disapears as $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\right]= \mathbf 0$.
-However in term4 to use the covariance estimate from the smoother the $\mathbf{x}_t$ terms should be brought together.
-To do this equation \eqref{eq:-EMterm4} can be rewritten as
+It should be noted that when applying expectation, term1 is constant, and term2 and term3 vanish as $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\right]= \mathbf 0$.
+However in term4 to use the covariance estimate from the smoother the $\mathbf{x}_t$ terms should be permuted.
+To do this \eqref{eq:-EMterm4} can be rewritten as
 \begin{align}
@@
 where
-\begin{align}\label{eq:EM-Lambdat}
-	{\boldsymbol \Lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r'.
+\begin{align}
+	{\boldsymbol \Lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t^b)d\mathbf r' \label{eq:lambdatildei}.
 \end{align}
@@
 \begin{align}\label{eq:Xi4derivation2}
-  \mathbf{E}_{\boldsymbol\Theta'}\left[ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right] &= \mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
+  \mathbf{E}_{\boldsymbol\Theta'}\left[ \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\right] &\approx \mathbf q^\top(\mathbf {\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
 &+\sum_{i,j=1}^{n_x}{\boldsymbol\Lambda}_t^{(i)\top}\mathbf{E}_{\boldsymbol\Theta'}\left[(\mathbf x_{i,t} - \mathbf  {\hat x}_{i,t}^b)(\mathbf x_{j,t} - \mathbf  {\hat x}_{j,t}^b)\right] \tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\Lambda}_t^{(j)},
@@
 \end{equation}
-and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
-\begin{align}
- \boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[\mathbf q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf \mathbf q(\mathbf{\hat x}_t^b)+\boldsymbol\varLambda_t\right]\label{eq:Xi4Ap}.
-\end{align}
-Finally, to calculate $\boldsymbol\Xi_5$, the nonlinear term can be treated in a smae way, using the expression for $\mathbf q(\mathbf x_t)$ in \eqref{eq:defofXi5} and rearranging gives
+summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ yields
+\begin{align}
+ \boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[\mathbf q^\top(\mathbf{\hat x}_t^b)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf{\hat x}_t^b)+\boldsymbol\varLambda_t\right]\label{eq:Xi4Ap}. 
+\end{align}
+Finally, to calculate $\boldsymbol\Xi_5$, the non-linear term can be treated in a similar way, using the expression for $\mathbf q(\mathbf x_t)$ in \eqref{eq:defofXi5} and rearranging gives
 \begin{align}\label{eq:Xi5derivation1}
- \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\approx\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
-\end{align}
-taking expected value of \eqref{eq:Xi5derivation1} gives
+ \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\approx\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)+\int_\Omega \boldsymbol \phi^\top(\mathbf r') (\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'.
+\end{align}
+Taking expected value of \eqref{eq:Xi5derivation1} yields
 \begin{align}\label{eq:Xi5derivation2}
 \mathbf E_{\Theta'}\left[\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf q(\mathbf x_t)\right]&\approx\mathbf E_{\Theta'}\left[\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf {\hat x}_t^b)\nonumber \\
-&+\int_\Omega \boldsymbol \phi^\top(\mathbf r') \mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'
-\end{align}
-substituting for $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right] $ from equation \eqref{eq:EM-PrimeryXi0derivation1} at time $t$, and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ gives
+&+\int_\Omega \boldsymbol \phi^\top(\mathbf r') \mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right]\tilde{\boldsymbol\Sigma}_e^{-1}\boldsymbol{\Psi}(\mathbf{r}')f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t^b) d\mathbf{r}'.
+\end{align}
+Substituting for $\mathbf E_{\Theta'}\left[(\mathbf x_t - \mathbf  {\hat x}_t^b)\mathbf x_t^\top\right] $ from \eqref{eq:EM-PrimeryXi0derivation1} at time $t$, and summing over $t \in \left\lbrace 0, \dots, T-1\right\rbrace $ gives
 \begin{align}
@@
  \end{align}
-By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete. The lower bound now can be used in M-step to find a set of new parameters. 
-\subsection{M-Step}
-% In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.
-The objective of the M-step is to maximize the computed lower bound in E-step, whcich consequenly increases the log-likelihood function $p(\mathbf Y;\boldsymbol\Theta)$.
-% on the joint likelihood function, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, where $\mathbf X$ is the set of all states, $\mathbf Y$ is the set of all observations, and $\boldsymbol \Theta$ denotes the set of all unknown parameters, i.e., connectivity kernel parameters $\boldsymbol\theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$.
-                                                                                                                                                                                                                                                                                                                                                                                                                                                                            Consider first the maximisation of $\mathcal{Q}$-function with respect to $\xi$, differentiating equation \eqref{eq:VoldermontwitXivariables} with respec to the synaptic parameter gives
+By computing $\boldsymbol\Xi$-variables, the approximation of the lower bound is complete. The lower bound now can be used in the M-step to find a set of new parameters. 
+\subsubsection{M-Step}
+The objective of the M-step is to maximise the computed lower bound in the E-step, which consequently increases the log-likelihood function $\ln p(\mathbf Y;\boldsymbol\Theta)$.
+Consider first the maximisation of the $\mathcal{Q}$-function with respect to $\xi$, differentiating \eqref{eq:VoldermontwitXivariables} with respect to the synaptic parameter gives
 \begin{equation}\label{eq:Qpartialxi}
@@
 \end{equation}
-In order to maximise $\mathcal{Q}$-function with respect to the connectivity kernel parameters, $\boldsymbol\theta$, differentiation is taken as follows
+In order to maximise the $\mathcal{Q}$-function with respect to the connectivity kernel parameters, $\boldsymbol\theta$, differentiation is taken as follows
 \begin{equation}\label{eq:Qpartialtheta}
@@
 \end{equation}
-noting that variable $\boldsymbol\Xi_4$ is symmetric by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
+noting that the variable $\boldsymbol\Xi_4$ is symmetric by construction, equating \eqref{eq:Qpartialtheta} to the zero vector yields
 \begin{equation}\label{eq:thetahat}
@@
 \end{equation}
-The condition under which $\boldsymbol\Xi_4$ is invertible is discussed later in this section. Now maximising the lower bound with respect to $\sigma_{\epsilon}^2$ gives
+The condition under which $\boldsymbol\Xi_4$ is invertible will be discussed later in this section (see below \eqref{eq:EM-traceinequality}).
+Now maximising the lower bound with respect to $\sigma_{\epsilon}^2$ gives
 \begin{equation}
@@
 \end{equation}
-and setting the above equation to zero and solving for $\sigma_{\epsilon}^2$ gives the result
+and setting the above equation to zero and solving for $\sigma_{\epsilon}^2$ yields
 \begin{equation}\label{eq:sigmaepsilonhat}
@@
 \end{equation}
-Finally differentiating the lower bound with respec to $\sigma_d^2$ gives
+Finally differentiating the lower bound with respect to $\sigma_d^2$ gives
 \begin{align}
@@
 \end{align}
-setting above to zero and solving for $\sigma_d^2$ completes the maximisation step
+setting the above to zero and solving for $\sigma_d^2$ completes the maximisation step.
 \begin{align}\label{eq:sigmadhat}
@@
 \end{align}
-In order to confirm calculated parameters are indeed maxima of the lower bound, the second derivative test is carried out for each parameter, giving
+In order to confirm that the calculated solutions maximise the lower bound, a second derivative test is performed for each of the parameter giving
 \begin{alignat}{2}%(number of &)+1 divided by 2 here we have (3+1)/2
@@
 \end{alignat}
-$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of state vectors, which is guaranteed by the disturbance, $\mathbf e$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore by \cite{Coope1994}
-\begin{equation}
+$\boldsymbol\Xi_2$ is positive definite under the persistent excitation condition of the state vectors, which is guaranteed by the disturbance, $\mathbf{e}_t(\mathbf r)$, and $\tilde{\boldsymbol\Sigma}_e^{-1}$ is positive definite by construction (Note that the inverse of a positive definite matrix is also positive definite \cite{Horn2005}), therefore by \cite{Coope1994}
+\begin{equation}\label{eq:EM-traceinequality}
  \mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace >0,
@@
 The joint state and parameter estimation algorithm is summarised in Algorithm~\ref{alg:EM-EMAlgorithm}.
+
+For initialisation a bounded random state sequence is employed to ensure that the initial parameter estimates describe a stable kernel, although the quality of such initial estimate is poor, it provides an initialisation that typically ensues a satisfactory convergence of the algorithm, as illustrated numerically in \S\ref{sec:EM-Results}.
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
+Here the change in parameter estimates, $L^2$-norm in the case of the connectivity kernel weights, is used to halt the execution of the algorithm.
+Besides, the lower bound on the likelihood function is also monitored to further investigate the convergence of the EM algorithm.
+
+An approximate for the computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
+In this table only the computational complexity of the variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
+Note that the computational complexity of the non-linear terms depend on the number of points, $n_r$, used for the spatial discretisation.
+Calculation of the non-linear terms is clearly the slowest part of the algorithm where $n_x$ is the critical dimension, more specifically the matrix $\boldsymbol\Xi_4 $ has the complexity that grows with the order of four in $n_x$.
+Although the number of states  is decoupled from the number of observation locations (recording electrodes in this case) , and the number of basis functions for the connectivity kernel decomposition, it  grows quadratically in two dimensional space for the equally spaced basis functions.
+%  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 
+ \begin {table}
+\begin{center}
+\scalebox{1}{\begin{tabular}{lll}
+\hline \hline
+Variable &Equation&Order\\ \hline\\
+$\mathbf q(\mathbf{x}_t)$&\eqref{eq:EM-Stateequationnonlinearity}&$O(n_xn_{\theta}n_r)$\\
+$\boldsymbol\Xi_0, \boldsymbol\Xi_1, \boldsymbol\Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
+$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
+$\boldsymbol\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r)$\\
+$\hat{\xi}$&\eqref{eq:xihat}&$O(n_x^3+n_{\theta}^3)$\\
+$\hat{\boldsymbol\theta} $&\eqref{eq:thetahat}&$O(n_{\theta}^3)$\\
+$\hat{\sigma}_{\epsilon}^2$&\eqref{eq:sigmaepsilonhat}&$O(Tn_x^2n_y)+O(Tn_xn_y^2)$\\
+$\hat{\sigma}_{d}^2$&\eqref{eq:sigmadhat}&$O(n_x^3)+O(n_{\theta}^2)$\\
+\hline \hline
+\end{tabular}}
+ \caption {Computational complexity of the EM algorithm} 
+\label{table:ComputationalComplexity}
+\end{center}
+\end {table}
 \begin{algorithm}\footnotesize
@@
 %  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 
- \begin {table}
-\begin{center}
-\scalebox{1}{\begin{tabular}{lll}
-\hline \hline
-Variable &Equation&Order\\ \hline\\
-$\mathbf q(\mathbf{x}_t)$&\eqref{}&$O(n_xn_{\theta}n_r)$\\
-$\boldsymbol\Xi_0, \boldsymbol\Xi_1, \boldsymbol\Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
-$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
-$\boldsymbol\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r)$\\
-$\hat{\xi}$&\eqref{eq:xihat}&$O(n_x^3+n_{\theta}^3)$\\
-$\hat{\boldsymbol\theta} $&\eqref{eq:thetahat}&$O(n_{\theta}^3)$\\
-$\hat{\sigma}_{\epsilon}^2$&\eqref{eq:sigmaepsilonhat}&$O(Tn_x^2n_y)+O(Tn_xn_y^2)$\\
-$\hat{\sigma}_{d}^2$&\eqref{eq:sigmadhat}&$O(n_x^3)+O(n_{\theta}^2)$\\
-\hline \hline
-\end{tabular}}
- \caption {Computational complexity of EM algorithm} 
-\label{table:ComputationalComplexity}
-\end{center}
-\end {table}
-\section{Results}
+\section{Results}\label{sec:EM-Results}
 This section demonstrates the identification of the proposed IDE model using simulated data.
 The observation noise and the field disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
-Data was generated employing state-space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
-100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state.
+Data was generated employing state-space equation (\ref{eq:finalformstatespacemodel}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
+100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach the steady state.
 Observation noise variance was set to 0.2.
-All other parameters for the simulation were the same as Chapter 2 (see Table 1.1).
-
-The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function.
-However, to compute the supports the unknown parameters, $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
-To form a more accurate initial guess of the unkown parameters and explore the effect of chosen initial guess on the estimated supports several tests were performed.
-First consider equation \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
-As mentioned before the power spectral densities are non negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
-The minimum value of the power spectral density was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit.
+All the other parameters for the simulation were chosen as that of Chapter 2 (see Table~\ref{tab:Parameters}).
+
+The correlation analysis described in \S\ref{subsec:CorrAnal} were applied to the generated data in order to approximate the unknown supports of both the connectivity kernel and disturbance covariance function.
+In doing so, the unknown parameters $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
+To form a more accurate initial guess of the unknown parameters and explore the effect of the chosen initial guess on the estimated supports several tests were performed.
+First consider  \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
+As mentioned before the power spectral densities are non-negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
+The minimum value of the power spectral density was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for varying  $\sigma^2_{\varepsilon}$ around the calculated limit.
 This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted.
-The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and thresholded for values less than 0.01.
-By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using equation \eqref{eq:EM-AnalyticSupportCalculation}.
-Alternatively deconvolution can also be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
-%Figure 1 here
+The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and threshold for values less than 0.01.
+By fitting a Gaussian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was analytically calculated  using \eqref{eq:EM-AnalyticSupportCalculation}.
+Alternatively deconvolution can be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.%Figure 1 here
 \begin{figure}[!ht]
@@
 \subfloat[][]{\includegraphics[scale=1]{./Figures/DisturbanceWidthEstimation04.pdf}}
-\caption{{\bf Disturbance support estimates for variyng observation noise variance.} Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
+\caption{{\bf Disturbance support estimates for different values of observation noise variance.} Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
 (\textbf a) $\sigma_{\varepsilon}^2$=0.
@@
 Each subplot shows the support of the disturbance covariance function convolved twice with the sensor kernel.
-(\textbf{a}) Estimated support is shown by red circle, nonzero values after thresholding are shown by the black area.
+(\textbf{a}) Estimated support is shown by red circle, non-zero values after thresholding are shown by the black area.
 (\textbf{b}) True support.}
@@
 \end{center}
-\caption{{\bf Cross-section of disturbance covariance support estimation}. The normalized true and the estimated width are shown by solid and dashed lines respectively.}
+\caption{{\bf Cross-section of normalised disturbance covariance function estimation}.
+The actual and the estimated covariance functions (obtained by numerical deconvolution via \eqref{eq:EM-MMGFourier2}) are shown by solid and dashed lines respectively.}
 \label{fig:DisturbanceWidthEstimationCrossSection}
 \end{figure}
-\begin{figure}
+\begin{figure}[!ht]
 \begin{center}
@@
 \end{center}
-\caption{{\bf Kernel support approximation for different values of synaptic time constant, $\tau$ and observation noise variance, $\sigma^2_{\varepsilon}$}.
-Each subplot shows normalised connectivity kernel estimate.
+\caption{{\bf Kernel support approximation for different values of the synaptic time constant, $\tau$ and the observation noise variance, $\sigma^2_{\varepsilon}$}.
+Each subplot shows the normalised connectivity kernel estimate.
 (\textbf a) $\sigma_{\varepsilon}^2$=0.
@@
 \end{figure}
-The effect of the observation noise variance on the connectivity kernel support is very much like to that of disturbance covariance function where an initial guess can be made in a similar manner.
-To study how synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, influence the resultant support of the connectivity kernel different values of synaptic time constatnt, $\tau$, were considered in a physiologically plausible range while noting that its value should be also higher than the sampling time.
+The effect of the observation noise variance on the connectivity kernel support is very much like to that of the disturbance covariance function where an initial guess can be made in a similar manner.
+To study the influence of the synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, on the resultant support of the connectivity kernel different values of synaptic time constant, $\tau$, in a physiologically plausible range were considered  while noting that the chosen values should be higher than the sampling time, $T_s$.
 In fact synaptic parameter in \eqref{eq:EM-Fourier_TF_of_Kernel}  acts like a scaling factor, dilating or shrinking the estimated support, as the subtracting a constant in a frequency domain only affects the value at the origin in the spatial domain.
-The result of the correlation analysis for the connectivity kernel is shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised  estimate for varying synaptic time constants while the observation noise was kept constant.
-Note that for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
-The result suggests that choosing the range of approximately $\left[-5,5 \right] $ is reasonable for the spatial extent of the connectivity kernel.
-
- By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted.
-In fact, the estimated support for the disturbance covariance function was very accurate.
-The estimates of the connectivity kernel and disturbance support were normalised and thresholded for values less than 0.01.
-The result of the correlation analysis for the connectivity kernel is shown in Figure.\ref{fig:KernelWidthEstimation}.
-The red circle shows the estimated support which encompasses the non-zero values (black area) after thresholding.
-The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}.
-By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.
-
-The estimated supports were then employed in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
+The results of the correlation analysis for the connectivity kernel are shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised  estimate for varying synaptic time constants while holding the observation noise fixed.
+Note  for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
+The result suggested that a support of approximately $\left[-5,5 \right] $ is a reasonable choice for the spatial extent of the connectivity kernel.
+
+The estimated supports were then employed in the EM algorithm described in \S\ref{subsec:EM-EMAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the parameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
 A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated kernel support where $\sigma_{\psi}^2=3.5$.
 This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.
+The depicted support was obtained by normalising and thresholding for values less than 0.01.
+The red circle shows the estimated support which encompasses the non-zero values (black area) after thresholding.
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelBasis1.pdf}
+\end{center}
+\caption{{\bf Connectivity kernel decomposition.} The approximate support of the kernel is shown by the red circle.
+Black area shows the non-zero values of the support after thresholding.
+A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
+\label{fig:KernelWidthEstimation}
+\end{figure}
  The true and estimated connectivity kernel for 100 Monte Carlo simulations are shown in Figure~\ref{fig:KernelEstimates}. 
-Cross-sections of the connectivity kernel estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}.
-The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel is inside the confidence interval.
-The large standard deviation is due to the high number of parameters need to be estimated.
-Figure~\ref{fig:Histogram} depicts the histogram of parameter estimates from 100 simulations where the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dashed line.
-These histograms indicate small bias in parameter estimates with a very small standard deviation.
-Examples of neural field reconstruction are given in Figure.~\ref{fig:FieldEstimates}.
-The figure shows snapshots at three time instants of the true neural field and the estimated field.
-In each subplot neural activity is plotted against spatial index in 1D to provide a comparision between true and the estimated underlying fields.
-Plot of lower bound of the log likelihood versus iterations of the EM is shown in Figure.~\ref{fig:LowerBound}.
-In general, for the non-linear dynamical systems the actual lower bound can not be claculated analytically, therefore the approximate of the lower bound obtained by URTSS is shown.
-The change in lower bound drops below 0.009 percent after 15 iterations, confirming
-that the algorithm converged to steady parameter values.
+\begin{figure}[!ht]
+\begin{center}
+\subfloat[][]{\includegraphics[scale=1]{./Figures/KernelEstimate.pdf}}
+\end{center}
+\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations.}
+\label{fig:KernelEstimates}
+\end{figure}
+The cross-sections of the connectivity kernel estimates for each run are also shown in Figure~\ref{fig:KernelEstimateCrossSection}.
+The mean reconstructed kernel is reasonably accurate, where the actual kernel is inside the confidence interval.
+The large standard deviation is due to the high number of unknown parameters associated with the connectivity kernel decomposition.
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
+\end{center}
+\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively.
+Each of the estimate from Monte Carlo simulation is shown with black line.
+The 95\% confidence intervals are shown by the shaded red area.}
+\label{fig:KernelEstimateCrossSection}
+\end{figure}
+Figure~\ref{fig:EM-Histogram} depicts the histogram of the non-kernel parameter estimates from 100 simulations where the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dotted line.
+These histograms indicate small bias in the parameter estimates with small standard deviations of 0.004, 0.0013 and 0.0012 for Figure~\ref{fig:EM-Histogram}(a), (b) and (c) respectively.
+\begin{figure}[!ht]
+\centering
+\subfloat[][]{\includegraphics[scale=1]{./Figures/Histogram.pdf}}
+\caption{{\bf Histograms of the non-kernel parameter estimates over 100 realizations}.
+The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively.
+(\textbf{a}) The histogram of the synaptic dynamic parameter, $\xi$.
+(\textbf{b}) The histogram of the observation noise variance, $\sigma_{\epsilon}$.
+(\textbf{c}) The histogram of the disturbance noise variance, $\sigma_d^2$.}
+\label{fig:EM-Histogram}
+\end{figure}
+Examples of the neural field reconstruction are given in Figure~\ref{fig:FieldEstimates}.
+The figure shows snapshots at three different time instants of the true and estimated neural fields.
+In each subplot neural activity is plotted against spatial index in 1-D to provide a better comparison between the true and estimated underlying fields.
+\begin{figure}[!ht]
+\centering
+\subfloat[][]{\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}}
+\caption{{\bf Neural field estimates at different time instants}. In each subplot, true (grey line) and reconstructed neural field (red dots) are plotted versus the spatial index.}
+\label{fig:FieldEstimates}
+\end{figure}
+Plot of the lower bound on the log-likelihood function versus iterations of the EM is shown in Figure~\ref{fig:LowerBound}.
+In general, for the non-linear dynamical systems the actual lower bound cannot be calculated analytically, therefore an approximate of the lower bound obtained by URTSS is shown.
+The mean change in the lower bound in consecutive iterations dropped below 0.009 percent after 15 iterations, confirming
+that the algorithm converged to a steady value.
+\begin{figure}[!ht]
+\centering
+\includegraphics{./Figures/Q.pdf}
+\caption{{\bf Convergence of the EM algorithm.} The mean of the lower bound of the log-likelihood function over 100 realisations.
+The change in lower bound drops below 0.009 percent after 15 iterations; \small{$Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$}.}
+%  $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$
+\label{fig:LowerBound}
+\end{figure}
+To further illustrate the convergence of the algorithm the parameter estimates averaged over 100 realisation is also shown in Figure~\ref{fig:EM-ParameterConvergence}, demonstrating the convergence of the parameter estimates.
+\begin{figure}[!ht]
+\centering
+\subfloat[][]{\includegraphics[scale=1]{./Figures/ParameterConvergence.pdf}}\\
+\centering
+ \subfloat[][]{\includegraphics[scale=1]{./Figures/KernelConvergence.pdf}}
+\caption{{\bf Convergence of parameters}.
+All parameters converge after 9 iterations.
+(\textbf a) The logarithm of the mean of synaptic parameter, observation noise variance, field disturbance variance and $L_2$ norm of the connectivity kernel parameter vector over 100 realisations.
+(\textbf b) The mean kernel estimates at each iteration of the EM algorithm.}
+\label{fig:EM-ParameterConvergence}
+\end{figure}
 \section{Discussion}\label{sec:EM-Discussion}
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelBasis1.pdf}
-\end{center}
-\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle.
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/KernelBasis1.pdf}
+% \end{center}
+% \caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle.
 Black area shows the non-zero values of the support after thresholding.
 A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
-\label{fig:KernelWidthEstimation}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
-\end{center}
-\caption{{\bf Disturbance support approximation}. }
-\label{fig:DisturbanceWidthEstimation}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelEstimate.pdf}
-\end{center}
-\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations.}
-\label{fig:KernelEstimates}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
-\end{center}
-\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively.
+% \label{fig:KernelWidthEstimation}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
+% \end{center}
+% \caption{{\bf Disturbance support approximation}. }
+% \label{fig:DisturbanceWidthEstimation}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/KernelEstimate.pdf}
+% \end{center}
+% \caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations.}
+% \label{fig:KernelEstimates}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/KernelEstimateCrossSection.pdf}
+% \end{center}
+% \caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively.
 Each of the estimate from Monte Carlo simulation is shown with black line.
 The 95\% confidence intervals are shown by shaded red area.}
-\label{fig:KernelEstimateCrossSection}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/Histogram.pdf}
-\end{center}
-\caption{{\bf Histograms of the parameter estimates over 100 realizations}.
+% \label{fig:KernelEstimateCrossSection}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/Histogram.pdf}
+% \end{center}
+% \caption{{\bf Histograms of the parameter estimates over 100 realizations}.
 The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively.
@@
 (C) The histogram of the disturbance noise variance, $\sigma_d^2$.}
-\label{fig:Histogram}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
-\end{center}
-\caption{{\bf Neural field estimates at different time instants}. In each subplot, true (gray line) and reconstructed neural field (red dots) are plotted versus spatial index.}
-\label{fig:FieldEstimates}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics{./Figures/Q.pdf}
-\end{center}
-\caption{{\bf Convergence of the EM algorithm.} The mean of the lower bound of the log-likelihood function over 100 realisations.
+% \label{fig:Histogram}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
+% \end{center}
+% \caption{{\bf Neural field estimates at different time instants}. In each subplot, true (gray line) and reconstructed neural field (red dots) are plotted versus spatial index.}
+% \label{fig:FieldEstimates}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \begin{center}
+% \includegraphics{./Figures/Q.pdf}
+% \end{center}
+% \caption{{\bf Convergence of the EM algorithm.} The mean of the lower bound of the log-likelihood function over 100 realisations.
 The change in lower bound drops below 0.009 percent after 15 iterations}
-%  $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$
-\label{fig:LowerBound}
-\end{figure}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{figure}[!ht]
-\centering
-% \subfloat[][]{\includegraphics[scale=1]{./Graph/EM/Q.pdf}}\\
-\subfloat[][]{\includegraphics[scale=1]{./Figures/ParameterConvergence.pdf}}\\
-\centering
-\subfloat[][]{\includegraphics[scale=1]{./Figures/KernelConvergence.pdf}}
-\caption{{\bf Convergence of parameters}.
+% %  $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$
+% \label{fig:LowerBound}
+% \end{figure}
+% %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% \begin{figure}[!ht]
+% \centering
+% % \subfloat[][]{\includegraphics[scale=1]{./Graph/EM/Q.pdf}}\\
+% \subfloat[][]{\includegraphics[scale=1]{./Figures/ParameterConvergence.pdf}}\\
+% \centering
+% \subfloat[][]{\includegraphics[scale=1]{./Figures/KernelConvergence.pdf}}
+% \caption{{\bf Convergence of parameters}.
 All parameters converge after 9 iterations.
@@
 (\textbf b) The mean kernel estimates at each iteration of the EM algorithm.}
-\label{fig:ParameterConvergence}
-\end{figure}
+% \label{fig:ParameterConvergence}
+% \end{figure}
 

### 2011-07-29 ltx/data_paper/DataPaper.tex
general edits to the data paper

@@
 \end{algorithm}
-\subsection{Initialisation, stopping and algorithmic complexity}
-For initialisation a bounded random state sequence is employed to ensure that the initial parameter estimates describe a stable kernel, although the quality of such initial estimate is poor, it provides an initialisation that typically ensues a satisfactory convergence of the algorithm, as illustrated numerically in Result section.
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
-Here the change in parameter estimates, $L^2$-norm in the case of connectivity kernel weights, is used to halt the excecution of the algorithm.
-Besides, the lower bound on the likelihood function is also monitored to further investigate the convergence of the EM algorithm.
-
-An approximate for computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}.
-In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.
-Note that computational complexity of the nonlinear terms depend on the number of points, $n_r$ used for spatial discritisation.
-Calculation of the nonlinear terms $\boldsymbol\Xi$ is clearly the slowest part of the algorithm where $n_x$ is the problematic dimension, more specifically the matrix $\boldsymbol\Xi_4 $ has complexity that grows with the order of four in $n_x$.
-Although number of states  is decoupled from number of observation locations (recording electrods) , and the number of basis functions required for the connectivity kernel decomposition, it does tend to grow linearly in one dimensional space and quadratically in two dimensional space.
-This growth assumes that the basis functions are arragend regularly in space, which is not a necessary construction.
-
 %  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 

### 2011-07-29 ltx/data_paper/DataPaper.tex
edit to correlation analysis

@@
 \end{equation}
-From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect estimate in the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion would be insignificant.
-The denominator in equation \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of noise free observations which is non-negative and real.
-This important result is known as Weiner-Khintchine (W-K) theorem in signal processsing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}.
-The numerator is also called the cross spectrum or cross spectral density.
+From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect guess of the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion becomes insignificant.
+The denominator in \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of the noise-free observations and is a non-negative and real quantity.
+This  is known as Weiner-Khintchine (W-K) theorem in signal processing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}.
+The numerator is also known as the cross-spectrum or cross-spectral density.
 Since the connectivity kernel is a real function, the following relation holds \cite{Bracewell2000}

### 2011-08-03 ltx/data_paper/DataPaper.tex
edits to introduction of paper

@@
 \end{itemize}
+
+The human brain brain is arguably the most complicated system known to man.
+The development of a complete theory for its function is one of the greatest challenges faced by scientists today.
+To address this challenge, researchers have naturally used both theoretical and experimental frameworks.
+Experimental frameworks are typically designed to uncover causal relationships between the systems properties or parameters and its function (reverse engineering the brain).
+Theoretical studies are typically used in one of two ways.
+The first is to explain data acquired in an experiment and the second is to predict system behaviour.
+
+Presently, it is almost half a century since Hodgkin and Huxley shared the Nobel prize (in 1963 with Eccles for Physiology and Medicine) for influential model that established the field of theoretical neuroscience.
+Over this time period, both experimental and theoretical methods have developed considerably.
+Experimental approaches have been able to isolate function using various forms or manipulation in greater detail.
+In parallel, theoretical/computational models have been able to explain and provide new hypotheses for an ever increasing assortment of neural phenomena.
+Through the development of these models a fundamental set a parametric equations has been established that explain neuronal responses to input a varying spatiotemporal scales from small patches of membrane to networks neural ensembles.
+
+Although the explanatory power of the theoretical models is rather vast, a limitation has been establishing a rigorous method for choosing model parameters.
+For example, over the last decade it has come to light that there is a significant variability in parameters of neural models across subjects (ref Marder 2006).
+For example, it has been shown that a target network behaviour may be achieved by continuum of parameter combinations (Tail wagging the ref).
+We expect an analogous situation in disease states and pathological activity such as epileptic seizures.
+Therefore, for models to be clinically useful they must be subject-specific.
+
+To further motivate the development of a framework for patient-specific neural models we will use intracranial EEG monitoring for planning epilepsy surgery as an example.
+During iEEG monitoring high fidelity spatiotemporal recordings of the electrical fields of the brain are undertaken.
+The goal is of the clinical work is to record the electrical activity of seizures and locate their origin.
+This information along with other behaviour and psychophyics studies enables the definition of surgical margins for the resection of pathological tissue.
+The ability to fuse the iEEG with a model will not only provide
+
 The aim of this paper is to create a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.
@@
 Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics.
-They perform a stability analysis of the network in terms of total connectivity and time delayes in the presence of noise.
+They perform a stability analysis of the network in terms of total connectivity and time delays in the presence of noise.
 Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.
@@
 $g(\cdot)$ describes the mean firing rate.
-In practice, the firing rate can rarely be considered as a purely determinstic process because \dean{(can someone write down why?)}.
-We thus choose to introduce a spatially coloured space-time Wiener process $W(\mathbf{r},t)$ to model the flactuations in the mean firing rate and decompose $g(\cdot)$ as
+In practice, the firing rate can rarely be considered as a purely deterministic process because \dean{(can someone write down why?)}.
+We thus choose to introduce a spatially coloured space-time Wiener process $W(\mathbf{r},t)$ to model the fluctuations in the mean firing rate and decompose $g(\cdot)$ as
 \begin{equation}\label{DecompositionOfg}

### 2011-08-04 ltx/data_paper/DataPaper.tex
edits to introduction of paper added epilepsy example

@@
 The development of a complete theory for its function is one of the greatest challenges faced by scientists today.
-To address this challenge, researchers have naturally used both theoretical and experimental frameworks.
+To address this challenge, researchers have naturally used both theoretical and experimental frameworks to develop and test hypotheses investigating brain function.
 Experimental frameworks are typically designed to uncover causal relationships between the systems properties or parameters and its function (reverse engineering the brain).
@@
 
-Although the explanatory power of the theoretical models is rather vast, a limitation has been establishing a rigorous method for choosing model parameters.
+Although the predictive explanatory power of the theoretical models is rather vast when they are tuned to mimic experimental conditions, a limitation has been establishing a rigorous method for choosing model parameters in more general situations.
 For example, over the last decade it has come to light that there is a significant variability in parameters of neural models across subjects (ref Marder 2006).
@@
 
-To further motivate the development of a framework for patient-specific neural models we will use intracranial EEG monitoring for planning epilepsy surgery as an example.
-During iEEG monitoring high fidelity spatiotemporal recordings of the electrical fields of the brain are undertaken.
-The goal is of the clinical work is to record the electrical activity of seizures and locate their origin.
-This information along with other behaviour and psychophyics studies enables the definition of surgical margins for the resection of pathological tissue.
-The ability to fuse the iEEG with a model will not only provide
-
-The aim of this paper is to create a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.
-
-Instead of extracting features we aim to extract meaningful parameters...
+By assimilating experimental or clinical measurements with mathematical models one can infer unmeasured or latent system properties or parameters.
+Inference of patient-specific parameters has the the potential to revolutionise the treatment of disease.
+Typically, one can measure the blood-oxygen level dependent signal through fMRI or the electromagnetic fields of the brain through EEG or MEG.
+In clinical neurology, these measurement modalities give a kind or a `where and when' indication of the presence of a pathology, but provide little information on the causative mechanisms for disease.
+A classic example of this is in epilepsy management, where the disease is diagnosed using EEG.
+If electrical seizures are recorded, a medication plan is prescribed.
+The choice of medication is not based on the data acquired from the EEG, but based on the clinician's experience with similar cases and sometimes trial and error because similar electrographic seizure can have fundamentally different mechanisms of initiation (JTs paper).
+Ideally in epilepsy monitoring we would like to image the concentration of ions, the synaptic dynamics, the connectivity strength and structure etc.
+to better inform a treatment plan by understand physiological changes that lead to seizures.
+This is also highly desirable for epileptic seizure prediction..
+
+The aim of this paper is to contribute towards to goal of being able to infer patient-specific parameters from electrophysiological data.
+
+Contributions from other groups...
 

### 2011-08-04 ltx/data_paper/DataPaper.tex
edits to introduction

@@
 If electrical seizures are recorded, a medication plan is prescribed.
-The choice of medication is not based on the data acquired from the EEG, but based on the clinician's experience with similar cases and sometimes trial and error because similar electrographic seizure can have fundamentally different mechanisms of initiation (JTs paper).
+The choice of medication is not based on the data acquired from the EEG, but based on the clinician's experience with similar cases and sometimes trial and error because similar electrographic seizure can have fundamentally different mechanisms of initiation (ref JTs paper).
 Ideally in epilepsy monitoring we would like to image the concentration of ions, the synaptic dynamics, the connectivity strength and structure etc.
@@
 
+A key development in making this framework possible is the unscented Kalman filter. blah. 
 Contributions from other groups...

### 2011-08-04 ltx/data_paper/DataPaper.tex
edit to introduction

@@
 
-Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics.
-They perform a stability analysis of the network in terms of total connectivity and time delays in the presence of noise.
-Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.
+Another recent approach uses graph theory \cite{Albert2002,Bang-Jensen2010} for large-scale neural networks and employs realistic anatomical connectivity from the CoCoMac database \cite{Kotter2004} to model the brain's resting state activity \cite{Ghosh2008,Deco2009}.
+Each node in the network is described by a physiologically reasonable neural population model of their internal dynamics.
+The authors perform stability analysis on the network based on total connectivity and time delays in the presence of noise.
+Such an approach has the potential to model a virtual brain which can incorporate data from individual patients, giving insights into how patients' specific features can affect its large-scale neural dynamics \cite{Jirsa2010,Deco2010}.
 

### 2011-08-04 ltx/data_paper/DataPaper.tex
minor edit to introduction

@@
 
-The human brain brain is arguably the most complicated system known to man.
+The human brain is arguably the most complicated system known to man.
 The development of a complete theory for its function is one of the greatest challenges faced by scientists today.
@@
 By assimilating experimental or clinical measurements with mathematical models one can infer unmeasured or latent system properties or parameters.
-Inference of patient-specific parameters has the the potential to revolutionise the treatment of disease.
+Inference of patient-specific parameters has the potential to revolutionise the treatment of disease.
 Typically, one can measure the blood-oxygen level dependent signal through fMRI or the electromagnetic fields of the brain through EEG or MEG.

### 2011-08-04 ltx/data_paper/DataPaper.tex
minor edit

@@
 \end{equation}
-Complex conjugate operator essentially reflects the connectivity kernel through the origin in the spatial domain, therefore, if the connectivity kernel is isotropic, the complex conjugate operator can be dropped.
+The complex conjugate operator essentially reflects the connectivity kernel through the origin in the spatial domain, therefore, if the connectivity kernel is isotropic, the complex conjugate operator can be dropped.
 % Alternatively, the convolution can be written as a system of linear equations by forming the convolution (Toeplitz) matrix.

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to introduction

--- 2011-08-04 ltx/data_paper/DataPaper.tex
@@
 The development of a complete theory for its function is one of the greatest challenges faced by scientists today.
-To address this challenge, researchers have naturally used both theoretical and experimental frameworks to develop and test hypotheses investigating brain function.
+To address this challenge, researchers have naturally used both theoretical and experimental frameworks to develop and test hypotheses.
 Experimental frameworks are typically designed to uncover causal relationships between the systems properties or parameters and its function (reverse engineering the brain).
@@
 
-Although the predictive explanatory power of the theoretical models is rather vast when they are tuned to mimic experimental conditions, a limitation has been establishing a rigorous method for choosing model parameters in more general situations.
-For example, over the last decade it has come to light that there is a significant variability in parameters of neural models across subjects (ref Marder 2006).
-For example, it has been shown that a target network behaviour may be achieved by continuum of parameter combinations (Tail wagging the ref).
+Although the predictive explanatory power of the theoretical models is rather vast when they are tuned to mimic experimental conditions, a major limitation has been in establishing a rigorous method for choosing model parameters in more general situations.
+For example, over the last decade it has come to light that there is significant variability in neural systems across subjects despite seemingly similar network activity (ref Marder 2006).
+It has been shown that a target network behaviour may be achieved by continuum of parameter combinations (Tail wagging the ref).
 We expect an analogous situation in disease states and pathological activity such as epileptic seizures.
@@
 In clinical neurology, these measurement modalities give a kind or a `where and when' indication of the presence of a pathology, but provide little information on the causative mechanisms for disease.
-A classic example of this is in epilepsy management, where the disease is diagnosed using EEG.
-If electrical seizures are recorded, a medication plan is prescribed.
-The choice of medication is not based on the data acquired from the EEG, but based on the clinician's experience with similar cases and sometimes trial and error because similar electrographic seizure can have fundamentally different mechanisms of initiation (ref JTs paper).
+A classic example of this is in epilepsy management, where the disease is diagnosed using EEG by identifying electrographic seizures.
+If electrical seizures are recorded with EEG, a medication plan is prescribed.
+The choice of medication is not based on the data acquired with the EEG, but based on the clinician's experience and the patient’s circumstance, then the treatment plan is often modified based on trial and error.
+This process of searching for the best drug combination is often required similar electrographic seizures can have fundamentally different mechanisms of initiation (ref JTs paper).
 Ideally in epilepsy monitoring we would like to image the concentration of ions, the synaptic dynamics, the connectivity strength and structure etc.
 to better inform a treatment plan by understand physiological changes that lead to seizures.
-This is also highly desirable for epileptic seizure prediction..
+This is also highly desirable for epileptic seizure prediction.
 
@@
 
-Another recent approach uses graph theory \cite{Albert2002,Bang-Jensen2010} for large-scale neural networks and employs realistic anatomical connectivity from the CoCoMac database \cite{Kotter2004} to model the brain's resting state activity \cite{Ghosh2008,Deco2009}.
-Each node in the network is described by a physiologically reasonable neural population model of their internal dynamics.
-The authors perform stability analysis on the network based on total connectivity and time delays in the presence of noise.
-Such an approach has the potential to model a virtual brain which can incorporate data from individual patients, giving insights into how patients' specific features can affect its large-scale neural dynamics \cite{Jirsa2010,Deco2010}.
+Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics.
+They perform a stability analysis of the network in terms of total connectivity and time delays in the presence of noise.
+Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.
 

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to results discussion and the conclusion

@@
 Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
-\begin{equation}
+\begin{equation}\label{eq:AnalyticSupportCalculation}
  \sigma_d^2=\sigma_{mm\gamma}^2-4\sigma_m^2.
@@
 The observation noise and the field disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
-Data was generated employing state-space equation (\ref{eq:finalformstatespacemodel}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model.
+Data was generated employing state-space equation (\ref{eq:LS-finalformstatespacemodel}-\ref{eq:LS-QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5$~mm) basis functions with $\sigma_{\phi}^2=1.58$~mm$^2$, assuming the observed field can be fully described by the decomposed IDE model.
 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach the steady state.
-Observation noise variance was set to 0.2.
-All the other parameters for the simulation were chosen as that of Chapter 2 (see Table~\ref{tab:Parameters}).
-
-The correlation analysis described in \S\ref{subsec:CorrAnal} were applied to the generated data in order to approximate the unknown supports of both the connectivity kernel and disturbance covariance function.
+The observation noise variance was set to 0.2.
+All the other parameters for the simulation were chosen as that of Chapter~\ref{LSChapter} (see Table~\ref{tab:LS-Parameters}).
+
+\subsection{Correlation analysis}
+The correlation analysis described in \S\ref{subsec:CorrAnal} were applied to the generated data in order to approximate the unknown supports of both the connectivity kernel and the disturbance covariance function.
 In doing so, the unknown parameters $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
@@
 As mentioned before the power spectral densities are non-negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
-The minimum value of the power spectral density was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for varying  $\sigma^2_{\varepsilon}$ around the calculated limit.
-This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted.
-The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and threshold for values less than 0.01.
-By fitting a Gaussian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was analytically calculated  using \eqref{eq:EM-AnalyticSupportCalculation}.
-Alternatively deconvolution can be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.%Figure 1 here
+The minimum value of the power spectral densities was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for varying  $\sigma^2_{\varepsilon}$ around the calculated limit.
+This figure shows that for the values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for the values above 0.23 the shape of the disturbance covariance function is distorted.
+The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and thresholded for values less than 0.01.
+By fitting a Gaussian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$, was known the width of the disturbance covariance function, $\sigma_{\gamma}^2$, was analytically calculated  using \eqref{eq:AnalyticSupportCalculation}.
+Alternatively deconvolution can be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
+The effect of the observation noise variance on the connectivity kernel support is very much like that of the disturbance covariance function, where an initial guess can be made in a similar manner.
+To study the influence of the synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, on the resultant support of the connectivity kernel different values of the synaptic time constant, $\tau$, in a physiologically plausible range were considered, while noting that the chosen values should be higher than the sampling time, $T_s$.
+In fact synaptic parameter in \eqref{eq:EM-Fourier_TF_of_Kernel}  acts as a scaling factor --- dilating or shrinking the estimated support --- since subtracting a constant in the frequency domain only affects the value at the origin in the spatial domain.
+The results of the correlation analysis for the connectivity kernel are shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised kernel estimate for varying synaptic time constants while holding the observation noise fixed.
+Note for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in a negative value at the origin.
+The result suggested that a support of approximately $\left[-5,5 \right] $ is a reasonable choice for the spatial extent of the connectivity kernel.
 \begin{figure}[!ht]
@@
 \end{figure}
-The effect of the observation noise variance on the connectivity kernel support is very much like to that of the disturbance covariance function where an initial guess can be made in a similar manner.
-To study the influence of the synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, on the resultant support of the connectivity kernel different values of synaptic time constant, $\tau$, in a physiologically plausible range were considered  while noting that the chosen values should be higher than the sampling time, $T_s$.
-In fact synaptic parameter in \eqref{eq:EM-Fourier_TF_of_Kernel}  acts like a scaling factor, dilating or shrinking the estimated support, as the subtracting a constant in a frequency domain only affects the value at the origin in the spatial domain.
-The results of the correlation analysis for the connectivity kernel are shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised  estimate for varying synaptic time constants while holding the observation noise fixed.
-Note  for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
-The result suggested that a support of approximately $\left[-5,5 \right] $ is a reasonable choice for the spatial extent of the connectivity kernel.
-
-The estimated supports were then employed in the EM algorithm described in \S\ref{subsec:EM-EMAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the parameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
-A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25~mm$ spacing were used to cover the estimated kernel support where $\sigma_{\psi}^2=3.5$.
+\subsection{State and parameter estimation}
+The estimated supports were employed in the EM algorithm described in \S\ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the parameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$.
+A  square grid of $n_{\theta}=25$ (5 by 5) basis functions with $2.25$~mm spacing were used to cover the estimated kernel support where $\sigma_{\psi}^2=3.5$~mm$^2$.
 This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions.
-The depicted support was obtained by normalising and thresholding for values less than 0.01.
+The depicted support was obtained by normalising and thresholding the result for the  values less than 0.01.
 The red circle shows the estimated support which encompasses the non-zero values (black area) after thresholding.
@@
 \end{figure}
-Figure~\ref{fig:EM-Histogram} depicts the histogram of the non-kernel parameter estimates from 100 simulations where the true parameter value is shown by the solid line and the mean parameter estimate is shown by the dotted line.
+Figure~\ref{fig:EM-Histogram} depicts the histogram of the non-kernel parameter estimates from 100 simulations where the true parameter values are shown by the solid lines and the mean parameter estimates are shown by the dotted lines.
 These histograms indicate small bias in the parameter estimates with small standard deviations of 0.004, 0.0013 and 0.0012 for Figure~\ref{fig:EM-Histogram}(a), (b) and (c) respectively.
@@
 Examples of the neural field reconstruction are given in Figure~\ref{fig:FieldEstimates}.
-The figure shows snapshots at three different time instants of the true and estimated neural fields.
-In each subplot neural activity is plotted against spatial index in 1-D to provide a better comparison between the true and estimated underlying fields.
+The figure shows snapshots of the true and estimated neural fields at three different time instants.
+In each subplot the neural activity is plotted against the spatial index in one dimension to provide a better comparison between the true and the estimated underlying fields.
 \begin{figure}[!ht]
@@
 Plot of the lower bound on the log-likelihood function versus iterations of the EM is shown in Figure~\ref{fig:LowerBound}.
-In general, for the non-linear dynamical systems the actual lower bound cannot be calculated analytically, therefore an approximate of the lower bound obtained by URTSS is shown.
-The mean change in the lower bound in consecutive iterations dropped below 0.009 percent after 15 iterations, confirming
-that the algorithm converged to a steady value.
+In general, for non-linear dynamical systems the actual lower bound cannot be calculated analytically, therefore an approximate of the lower bound obtained by the URTSS is shown.
+The mean change in the lower bound in consecutive iterations dropped below 0.009 percent after 15 iterations, confirming that the algorithm converged to a steady value.
 \begin{figure}[!ht]
@@
 \end{figure}
-To further illustrate the convergence of the algorithm the parameter estimates averaged over 100 realisation is also shown in Figure~\ref{fig:EM-ParameterConvergence}, demonstrating the convergence of the parameter estimates.
+To further investigate the convergence property of the algorithm the parameter estimates averaged over 100 realisations are also shown in Figure~\ref{fig:EM-ParameterConvergence}, demonstrating the convergence of the EM algorithm.
 \begin{figure}[!ht]
@@
 \section{Discussion}\label{sec:EM-Discussion}
-The correlation analysis specifies approximate supports for both the disturbance covariance function and connectivity kernel.
-Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly, the analysis also assumes the sigmoidal firing rate in the active region, as a result  the kernel and disturbance amplitudes cannot be inferred only through the correlation analysis.
-This step might be considered as a prerequisite for the EM algorithm described in \S\ref{subsec:EM-EMAlgorithm} where the approximated supports are used to estimate the gain of the kernel and field disturbance variance.
+The correlation analysis specifies approximate supports for both the disturbance covariance function and the connectivity kernel.
+Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly.
+The analysis also assumes the sigmoidal firing rate in the active region and as a result  the kernel and disturbance amplitudes cannot be inferred only through the correlation analysis.
+This step might be considered as a prerequisite for the EM algorithm described in \S\ref{sec:EstimationAlgorithm} where the approximated supports are used to estimate the gain of the kernel and the field disturbance variance.
 Knowing the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition is significantly reduced  compared to the case where the basis functions are arranged across the entire spatial domain.
-This also improves the uncertainty of the estimates as lower number of unknown parameters need to be estimated.
+This also improves the uncertainty of the estimates as a lower number of unknown parameters need to be estimated.
 The approximated support of the disturbance covariance function facilitates the application of the EM algorithm.
@@
 The additional Taylor approximation step introduced in the E-step of the algorithm resembles the extended Kalman filtering \cite{Jazwinski1970,Chui2009}.
-EKF approximates a stationary non-linear dynamic system with a linear non-stationary one using first order Taylor expansion around the state estimates.
-This might imply that the extended Kalman smoother is a better candidate (in terms of implementation) for the state inference in the proposed algorithm.
-However, extended Kalman smoother (EKS) requires re-linearising about the backwards estimates which in turn necessitates the non-linear mapping to be uniquely invertible.
+The EKF approximates a stationary non-linear dynamic system with a linear non-stationary one using the first order Taylor expansion around the state estimates.
+This might imply that the extended Kalman smoother (EKS) is a better candidate --- in terms of implementation --- for the state inference in the proposed algorithm.
+However, the EKS requires re-linearising about the backward estimates which in turn necessitates the non-linear mapping to be uniquely invertible.
 Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation.
-In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the constructed lower bound will be more accurate, resulting in a better parameter estimation.
-
-While EKS has been  applied in the EM algorithm for learning non-linear models \cite{Ghahramani1999} this is the first work (to the best author's knowledge) where the URTSS is used in this context.
+In addition, the URTSS provides better state estimations compared to the EKS \cite{Haykin2001} and therefore the constructed lower bound will be more accurate, resulting in a better parameter estimation.
+
+While the EKS has been  applied in the EM algorithm for learning non-linear models \cite{Ghahramani1999} this is the first work (to the best author's knowledge) where the URTSS is used in this context.
 However, as in the case of the EKS the stability of the algorithm cannot be ensured.
-This is because the use of EKS or URTSS represents an approximation to the exact E-step.
-As a result the maximisation of the approximated lower bound might not necessairly increase the log-likelihood function.
-Nevertheless, it is envisaged that the use of URTSS will provide a more stable algorithm due to its superior performance.
+This is because the use of the EKS or URTSS represents an approximation to the exact E-step.
+As a result the maximisation of the approximated lower bound might not necessarily increase the log-likelihood function.
+Nevertheless, it is envisaged that the use of the URTSS will provide a more stable algorithm due to its superior performance.
 
@@
 global (local) maximum or a saddle point.
-If the sequence of EM is trapped in a saddle point a small random perturbation diverges the algorithm from such a stationary value \cite{McLachlan1997}.
+If the sequence of the EM is trapped in a saddle point a small random perturbation diverges the algorithm from such a stationary value \cite{McLachlan1997}.
 In general convergence of the EM algorithm to any stationary points either global (local) maxima or saddle points depends on the initialisation.
@@
 
-Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
+Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviour higher order terms might need to be included, this however introduces intractable computational complexity.
 \section{Conclusion}
-In this paper, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
+In this chapter, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data, where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
 It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified.
 This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process.
-In addition to the connectivity kernel weights, synaptic parameter, observation noise and disturbance variances were also identified.
-The empirical distributions of the estimated non-kernel parameters showed small bias with very smalll standard deviations.
+In addition to the connectivity kernel weights and the synaptic parameter, the observation noise and disturbance variances were also identified.
+The empirical distributions of the estimated non-kernel parameters showed small bias with very small standard deviations.
 

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to results discussion and the conclusion

@@
 where $\mathbf{e}_t \sim\mathcal{N}(\mathbf 0,\boldsymbol\Sigma_e)$. The covariance matrix is defined as (see the Supporting Information, S1, for the derivation)
-\begin{equation}
+\begin{equation}\label{eq:CovarianceMatrix}
 	\boldsymbol\Sigma_e \triangleq \sigma_d^2\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}.
@@
 \end{align}
-Note that the disturbance covariance matrix, $\boldsymbol\Sigma_e$, can be written as the product of the unknown parameter, $\sigma_d^2$ with a constant matrix, $\tilde{\boldsymbol\Sigma}_e$, where the constant part can be calculated (\parham{from \eqref{eq:DisturbanceCovariance}}) using the estimated support for the disturbance covariance function, $\gamma$, from the correlation analysis (see \eqref{eq:EM-MMGFourier2}).
+Note the disturbance covariance matrix, $\boldsymbol\Sigma_e$, can be written as a product of the unknown parameter, $\sigma_d^2$, with the constant matrix, $\tilde{\boldsymbol\Sigma}_e$, where the constant part can be calculated from \eqref{eq:CovarianceMatrix} using the estimated support of the disturbance covariance function (see \eqref{eq:EM-MMGFourier2}).
 This simplifies the M-step significantly as the estimation of the entire covariance matrix  reduces to the estimation of the single scalar  $\sigma_d^2$.
 By expanding the exponent in \eqref{eq:EM-twicelog1} and \eqref{eq:EM-twicelog2}, twice the logarithm of the results give
-\begin{align}\label{eq:CondititionDist1}
-2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],
-\end{align}
-\begin{align}
-2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\xi, \sigma_d)&=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta\nonumber \\
-&+\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t -\frac{1}{\sigma_e^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta\nonumber\nonumber \\
-& -\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
+\begin{align}\label{eq:EM-CondititionDist1}
+&2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],\\
+&2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\xi, \sigma_d)=-n_x\ln\sigma_d^2-\ln\mid\tilde{\boldsymbol\Sigma}_e\mid-\frac{1}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_{t+1}-\frac{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t+\nonumber \\
+&\frac{2\xi}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t -\frac{1}{\sigma_e^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta.
+\label{eq:EM-CondititionDist2}
 % &-\franc{\xi^2}{\sigma_d^2}\mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf x_t. \label{eq:CondititionDist2}
 \end{align}
-In the next step the above equations are rearranged to isolate the covariance and the cross-covariance terms, allowing the smoother outputs to be used.
+In the next step, the above equations are rearranged to isolate the covariance and cross-covariance terms such that  the smoother outputs can be used.
 In order to permute the matrices, the scalar nature of the likelihood is exploited, this way the trace operator can be applied to express the likelihood in a more compact form.
-Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become
-\begin{align}\label{eq:Qfunctiontrace1}
-  2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) &= -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace
-\end{align}
-\begin{align}
- 2 \ln &p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi, \sigma_d) =-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta \nonumber \\
+Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:EM-CondititionDist1} and \eqref{eq:EM-CondititionDist2} become
+\begin{align}\label{eq:EM-Qfunctiontrace1}
+ & 2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right) = -n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace  \\
+&2 \ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi, \sigma_d) =-n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace\mathbf x_{t+1} \mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace \nonumber \\
 &+\frac{2\xi}{\sigma_d^2} \mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{1}{\sigma_d^2}\boldsymbol\theta^\top \mathbf q^\top(\mathbf x_t)\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta-\frac{2\xi}{\sigma_d^2} \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q(\mathbf x_t)\boldsymbol\theta \nonumber \\
-&-\frac{\xi^2}{\sigma_d^2}\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace. \label{eq:Qfunctiontrace2}
-\end{align}
-Substituting  \eqref{eq:Qfunctiontrace1} and \eqref{eq:Qfunctiontrace2} back into \eqref{eq:QIntermsofJointDist} and taking the expectation of the log-likelihood function at all time instants gives the required lower-bound.
+&+\frac{2}{\sigma_d^2}\mathbf x_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}\mathbf q( \mathbf x_t)\boldsymbol\theta .\label{eq:EM-Qfunctiontrace2}
+\end{align}
+Substituting  \eqref{eq:EM-Qfunctiontrace1} and \eqref{eq:EM-Qfunctiontrace2} back into \eqref{eq:QIntermsofJointDist} and taking the expectation of the log-likelihood function at all time instants gives the required lower-bound.
 Note that the expectation distributes over the trace sum.

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to results discussion and the conclusion

@@
 The third term in \eqref{eq:Voldermont} is obtained using the same method in \cite{Shumway2000}, i.e.
-by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1}^b \mathbf{\hat{x}}_{t+1}^{b\top} \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1} and then exploiting the expression given in \eqref{eq:EM-Xi0derivation1} .
-By defining $\Xi$-variables as
+by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1}^b \mathbf{\hat{x}}_{t+1}^{b\top} \mathbf C^\top$ to the expectation of the second term in \eqref{eq:EM-Qfunctiontrace1} and then exploiting the expression given in \eqref{eq:EM-Xi0derivation1} .
+By defining $\boldsymbol\Xi$-variables as
 \begin{align}
@@
 \end{align}
-The covariance and cross-covariance terms in \eqref{eq:VoldermontwitXivariables}, consist of both the linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
+The covariance and cross-covariance terms in \eqref{eq:VoldermontwitXivariables} consist of both the linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and the non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$.
 Finding the linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly from the smoother outputs, i.e.
@@
 \end{align}
-However calculation of the non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case.
-Therefore, an additional Taylor expansion step to the URTSS algorithm is also created to linearise $\mathbf q(\mathbf{x}_t)$, enabling the  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$ using the smoother outputs.
+However, calculation of the non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case.
+Therefore, an additional Taylor expansion step to the URTSS algorithm is also created to linearise $\mathbf q(\mathbf{x}_t)$, enabling the calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$ from the smoother outputs.
 This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function at each time instant  around the smoothed state, $\hat{\mathbf x}_t^b$, i.e.

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to results discussion and the conclusion

@@
  \end{align}
-substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:EM-Stateequationnonlinearity},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained
+substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained
 \begin{equation}\label{eq:qTaylor}
@@
 Variable &Equation&Order\\ \hline\\
-$\mathbf q(\mathbf{x}_t)$&\eqref{eq:EM-Stateequationnonlinearity}&$O(n_xn_{\theta}n_r)$\\
+$\mathbf q(\mathbf{x}_t)$&\eqref{eq:QmatrixForSigmapoints}&$O(n_xn_{\theta}n_r)$\\
 $\boldsymbol\Xi_0, \boldsymbol\Xi_1, \boldsymbol\Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\

### 2011-08-16 ltx/data_paper/DataPaper.tex
started to edit results section

@@
 \section{Results}\label{sec:EM-Results}
-This section demonstrates the identification of the proposed IDE model using simulated data.
-The observation noise and the field disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
+In this section, a demonstration of the estimation framework for the proposed IDE neural field model is provided.
+To demonstrate the estimation procedure, simulated data is used to establish a ground truth for a comparison.
+The parameters of the observation noise and the field disturbance were assumed to be unknown, and therefore, were inferred from data.
+to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
 Data was generated employing state-space equation (\ref{eq:LS-finalformstatespacemodel}-\ref{eq:LS-QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5$~mm) basis functions with $\sigma_{\phi}^2=1.58$~mm$^2$, assuming the observed field can be fully described by the decomposed IDE model.
@@
 
-\subsection{Correlation analysis}
+\subsection{Correlation Analysis}
 The correlation analysis described in \S\ref{subsec:CorrAnal} were applied to the generated data in order to approximate the unknown supports of both the connectivity kernel and the disturbance covariance function.

### 2011-08-17 ltx/data_paper/DataPaper.tex
edits to results section correltation analysis

@@
 \end{equation}
-where over-bar denotes complex conjugate operator. Finally, an expression for the kernel is obtained by taking the inverse Fourier tranform 
+where over-bar denotes complex conjugate operator. Finally, an expression for the kernel is obtained by taking the inverse Fourier transform 
 \begin{equation}\label{eq:KernelSolution}
@@
 \end{align}
-By using similar arguments that were used in the derivation for the connectivity kernel support, the autocorrelation can be simplified by recognizing that
+By using similar arguments that were used in the derivation for the connectivity kernel support, the autocorrelation can be simplified by recognising that
 \begin{align}\label{eq:EM-Autoterm1}
@@
 To demonstrate the estimation procedure, simulated data is used to establish a ground truth for a comparison.
-The parameters of the observation noise and the field disturbance were assumed to be unknown, and therefore, were inferred from data.
-to the estimation algorithm and no assumption were made on the shape of the connectivity kernel.
-Data was generated employing state-space equation (\ref{eq:LS-finalformstatespacemodel}-\ref{eq:LS-QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5$~mm) basis functions with $\sigma_{\phi}^2=1.58$~mm$^2$, assuming the observed field can be fully described by the decomposed IDE model.
-100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach the steady state.
-The observation noise variance was set to 0.2.
-All the other parameters for the simulation were chosen as that of Chapter~\ref{LSChapter} (see Table~\ref{tab:LS-Parameters}).
-
-\subsection{Correlation Analysis}
-The correlation analysis described in \S\ref{subsec:CorrAnal} were applied to the generated data in order to approximate the unknown supports of both the connectivity kernel and the disturbance covariance function.
+The parameters of the model that are estimated include the synaptic time constant, the shape of the connectivity kernel, the field disturbance properties and the observation noise properties.
+All the parameters for the simulated data given in Table~\ref{tab:LS-Parameters}.
+To demonstrate the estimation procedure, a Monte Carlo simulation was employed where 100 realisations of 500 ms of data were generated.
+The first 100 ms of each realisation was discarded allowing the model's dynamics to stabilise from the initial conditions.
+
+\subsection{Estimation of Connectivity Kernel and Field Disturbance Support }
+The correlation analysis, described in \S\ref{subsec:CorrAnal}, was applied to the simulated data to estimate the unknown support of both the connectivity kernel and the disturbance covariance function.
+The goal of the estimation procedure for the kernel support is to constrain to positioning and number of kernel basis functions.
+
+From equation~\ref{eq:KernelSolution} it is clear that the an initial estimate of the synaptic time constant is required to estimate the shape of the connectivity kernel from data.
+\dean{Maybe we can say something like:} From equation~\ref{eq:EM-Fourier_TF_of_Kernel}, it can be seen the an error in the estimate of the value of the synaptic time constant will yield either shift up or down in the frequency domain.
+Since the goal of the procedure is to constrain the positioning of connectivity kernel basis functions, the initial estimate of the time constant should be conservatively \dean{higher (or lower?)}, which will result in a dilation of shape of the kernel (shift lower in the frequency domain).
+If the shape of the kernel estimate is wider than the actual kernel, then we can be sure that the positioning of the basis functions will capture the connectivity structure once the basis function coefficients have been estimated.
+If the kernel shape is too narrow, then the parameter values associated with the basis function can not compensate.
+
+In addition to the synaptic time constant, an initial guess for the observation noise variance is also required.
+
 In doing so, the unknown parameters $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
@@
 First consider \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
-As mentioned before the power spectral densities are non-negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
-The minimum value of the power spectral densities was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for varying  $\sigma^2_{\varepsilon}$ around the calculated limit.
+As mentioned before, the power spectral densities are non-negative.
+Therefore, the minimum values of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen (\dean{these aren't chosen, they are calculated from data, right?
+Not sure what you mean.
+Do mean the initial guess of `$\sigma^2_{\varepsilon}$' should be chosen such that ...?
+or $\sigma^2_{\varepsilon}$ is bounded by...}) as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
+The minimum value of the power spectral densities was found to be 0.23.
+
+Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for varying  $\sigma^2_{\varepsilon}$ around the calculated limit.
 This figure shows that for the values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for the values above 0.23 the shape of the disturbance covariance function is distorted.

### 2011-08-18 ltx/data_paper/DataPaper.tex
edits to correlation analysis results and methods

@@
 since the disturbance and measurement noise are assumed to be independent of the observations and temporally white. 
-The cross-correlation is further simplified by recognizing that the first term on right hand side of equation~\eqref{eq:EM-ExpectationToCancelNoise} can be written as 
+The cross-correlation is further simplified by recognising that the first term on right hand side of equation~\eqref{eq:EM-ExpectationToCancelNoise} can be written as 
 \begin{align}
@@
  \begin{equation}
-	f\left(v_t(\mathbf{r})\right) \approx \varsigma v_t(\mathbf{r})
-\end{equation} 
+	f\left(v_t(\mathbf{r})\right) \approx \varsigma v_t(\mathbf{r}).
+\end{equation} 
+\dean{I think we should use this activation function (this will fix the distortion across the $x=0,y=0$ axis):
+The function linearised about the firing threshold is 
+\begin{align}
+	\hat{f}(v_t\left(\mathbf{r}\right)) &= f(v_0) + f'(v_0)(v_t\left(\mathbf{r}\right) - v_0) \\
+	&= \frac{2 + \varsigma(v_t\left(\mathbf{r}\right) - v_0)}{4}. \label{eq:LinearActivationFunction} 
+\end{align}}
 Substituting the linear activation function back into equation~\eqref{eq:EM-before_linearization} yields
@@
 \end{align}
-To isolate the kernel, the order of the convolution and cross-correlation is reversed by recognizing that a property $(a \ast b)(\boldsymbol\iota) \star c(\boldsymbol\iota) = a(-\boldsymbol\iota)\ast(b \star c)(\boldsymbol\iota)$ \parham{(see Appendix for proof)}.
+To isolate the kernel, the order of the convolution and cross-correlation is reversed by recognising that a property $(a \ast b)(\boldsymbol\iota) \star c(\boldsymbol\iota) = a(-\boldsymbol\iota)\ast(b \star c)(\boldsymbol\iota)$ \parham{(see Appendix for proof)}.
 Therefore,
@@
 \end{equation}
-From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect guess of the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion becomes insignificant.
-The denominator in \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of the noise-free observations and is a non-negative and real quantity.
-This  is known as Weiner-Khintchine (W-K) theorem in signal processing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}.
+From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in the initial estimate of $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect guess of the observation noise will result in a distortion in the zero frequency (offset) component of the kernel, however if the signal-to-noise ratio is high such a distortion becomes insignificant.
+
+The denominator of equation \eqref{eq:EM-Fourier_TF_of_Kernel} is equivalent to the power spectral density (PSD) of the noise-free observations.
+By the Weiner-Khintchine theorem (WKT) the PSD is non-negative and a real quantity.
+The WKT states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}.
+\dean{The WKT allows us establish the bounds}
+\begin{align}
+	\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right] - \sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\}\ge&0 \\
+	\implies & \mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\}\ge\mathcal{F}\{\sigma_{\varepsilon}^2 \delta(\boldsymbol\iota))\}\ge0 \\
+	\implies & \min_f\mathcal{F}\{(\mathbf{E}\left[R_{y_ty_t}(\boldsymbol\iota)\right]\}\ge\sigma_{\varepsilon}^2\ge0. \label{eq:BoundOnObsVariance}
+\end{align}
 The numerator is also known as the cross-spectrum or cross-spectral density.
+
 Since the connectivity kernel is a real function, the following relation holds \cite{Bracewell2000}
@@
 
-From equation~\ref{eq:KernelSolution} it is clear that the an initial estimate of the synaptic time constant is required to estimate the shape of the connectivity kernel from data.
-\dean{Maybe we can say something like:} From equation~\ref{eq:EM-Fourier_TF_of_Kernel}, it can be seen the an error in the estimate of the value of the synaptic time constant will yield either shift up or down in the frequency domain.
+From equation~\ref{eq:KernelSolution}, it is clear that the an initial estimate of the synaptic time constant is required to estimate the shape of the connectivity kernel from data.
+\dean{Maybe we can say something like:} From equation~\ref{eq:EM-Fourier_TF_of_Kernel}, it can be seen the an error in the estimate of the value of the synaptic time constant will yield either shift up or down in the frequency domain, which leads to a constriction or dial.
 Since the goal of the procedure is to constrain the positioning of connectivity kernel basis functions, the initial estimate of the time constant should be conservatively \dean{higher (or lower?)}, which will result in a dilation of shape of the kernel (shift lower in the frequency domain).
@@
 
-In addition to the synaptic time constant, an initial guess for the observation noise variance is also required.
-
-In doing so, the unknown parameters $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.
-To form a more accurate initial guess of the unknown parameters and explore the effect of the chosen initial guess on the estimated supports several tests were performed.
-First consider \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
-As mentioned before, the power spectral densities are non-negative.
-Therefore, the minimum values of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen (\dean{these aren't chosen, they are calculated from data, right?
-Not sure what you mean.
-Do mean the initial guess of `$\sigma^2_{\varepsilon}$' should be chosen such that ...?
-or $\sigma^2_{\varepsilon}$ is bounded by...}) as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$.
-The minimum value of the power spectral densities was found to be 0.23.
+In addition to the synaptic time constant, an initial guess for the observation noise variance, $\sigma_{\epsilon}^2$, is also required.
+From equation~\eqref{eq:BoundOnObsVariance}, the value of $\sigma_{\epsilon}^2$ is bounded.
+Using the artificial data, the upper bound on $\sigma_{\epsilon}^2$ (the minimum value of the power spectral densities) was found to be approximately $0.23$.
+
+To explored the sensitivity of the initial guess of $\sigma_{\epsilon}^2$, several tests were performed.
+\dean{The connectivity kernel should come first when presenting the results, since the derivation is presented first in the method section.} First consider \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function.
 

### 2011-08-18 ltx/data_paper/DataPaper.tex
correction to analytic gamma width
minor correction to disturbance support

@@
 If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} is then required.
-Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
+Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_{\gamma}$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving
 \begin{equation}\label{eq:AnalyticSupportCalculation}
- \sigma_d^2=\sigma_{mm\gamma}^2-4\sigma_m^2.
+ \sigma_{\gamma}^2=\sigma_{mm\gamma}^2-2\sigma_m^2.
 \end{equation}

### 2011-08-20 ltx/data_paper/DataPaper.tex
minor correction to M step
correction to the computational complexity table

@@
 \begin{align}\label{eq:Voldermont}
- \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2\nonumber \\
+ \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-Tn_y\ln \sigma_{\epsilon}^2-Tn_x\ln\sigma_d^2\nonumber \\
 & -\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b)^\top+\mathbf C \mathbf P_{t+1}^b\mathbf C^\top\right] \right\rbrace\nonumber \\
@@
  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\boldsymbol\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}^b)^\top+\mathbf C \mathbf P_{t+1}^b\mathbf C^\top\right] \right\rbrace\nonumber \\
-&-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace
+&-Tn_y\ln \sigma_{\epsilon}^2-Tn_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace
  \nonumber \\
@@
 \begin{equation}\label{eq:Qpartialxi}
- \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5,
-\end{equation}
-setting \eqref{eq:Qpartialxi} to zero and solving for $\xi$ gives
+ \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5\boldsymbol\theta,
+\end{equation}
+Substituting for $\boldsymbol\theta$ from \eqref{eq:thetahat} and then setting the result to zero and solving for $\xi$ gives
 \begin{equation}\label{eq:xihat}
@@
 \begin{equation}
-  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace,
+  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-Tn_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace,
 \end{equation}
@@
 \begin{equation}\label{eq:sigmaepsilonhat}
- \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace.
+ \hat{\sigma}_{\epsilon}^2=\frac{1}{Tn_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace.
 \end{equation}
@@
 \begin{align}
- \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace  \nonumber \\
+ \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -Tn_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace  \nonumber \\
 &+\frac{\xi^2}{\sigma_d^4}\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1} \right\rbrace-\frac{2}{\sigma_d^4}\boldsymbol\Xi_3\boldsymbol\theta +\frac{1}{\sigma_d^4}\boldsymbol\theta^\top \boldsymbol\Xi_4\boldsymbol\theta+\frac{2\xi}{\sigma_d^4} \boldsymbol\Xi_5 \boldsymbol\theta,
@@
 \begin{align}\label{eq:sigmadhat}
-\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+\hat{\sigma}_d^2&=\frac{1}{Tn_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
 2\xi\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\xi^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace\right.\nonumber \\ &\left.-2\boldsymbol\Xi_3\boldsymbol\theta+\boldsymbol\theta^\top\boldsymbol \Xi_4\boldsymbol\theta+2\xi\boldsymbol\Xi_5 \boldsymbol\theta\right].
@@
  \frac{\partial \mathcal Q^2}{\partial^2\boldsymbol\theta}&\biggr\rvert_{\boldsymbol\theta=\hat{\boldsymbol\theta}}&&=-\frac{2}{\sigma_d^2}\boldsymbol\Xi_4 \label{eq:SecondDerivativetheta} \\
- \frac{\partial \mathcal Q^2}{\partial^2\sigma_{\epsilon}^2}&\biggr\rvert_{\sigma_{\epsilon}=\hat{\sigma}_{\epsilon}}&&=-\frac{(T-1)n_y}{\hat{\sigma}_{\epsilon}^4} \label{eq:SecondDerivativenoise} \\
- \frac{\partial \mathcal Q^2}{\partial^2\sigma_{d}^2}&\biggr\rvert_{{\sigma}_{d}=\hat{\sigma}_{d}}&&= -\frac{(T-1)n_x}{\hat{\sigma}_{d}^4} \label{eq:SecondDerivativedisturbance}
+ \frac{\partial \mathcal Q^2}{\partial^2\sigma_{\epsilon}^2}&\biggr\rvert_{\sigma_{\epsilon}=\hat{\sigma}_{\epsilon}}&&=-\frac{Tn_y}{\hat{\sigma}_{\epsilon}^4} \label{eq:SecondDerivativenoise} \\
+ \frac{\partial \mathcal Q^2}{\partial^2\sigma_{d}^2}&\biggr\rvert_{{\sigma}_{d}=\hat{\sigma}_{d}}&&= -\frac{Tn_x}{\hat{\sigma}_{d}^4} \label{eq:SecondDerivativedisturbance}
 \end{alignat}
@@
 $\boldsymbol\Xi_0, \boldsymbol\Xi_1, \boldsymbol\Xi_2$&\eqref{eq:Xi0Gibson}, \eqref{eq:Xi1Gibson}, \eqref{eq:Xi2Gibson}&$O(Tn_x^2)$\\
-$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
+$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
 $\boldsymbol\Xi_4$&\eqref{eq:Xi4Ap}&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_x^3n_{\theta}n_r)$\\
@@
  \hat{\boldsymbol \theta}&=\boldsymbol\Xi_4^{-1}\left(\boldsymbol\Xi_3^\top-\hat{\xi}\boldsymbol\Xi_5^\top \right)\nonumber\\
-\hat{\sigma}_{\epsilon}^2&=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace \nonumber\\
-\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
+\hat{\sigma}_{\epsilon}^2&=\frac{1}{Tn_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace \nonumber\\
+\hat{\sigma}_d^2&=\frac{1}{Tn_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
 2\hat{\xi}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\hat{\xi}^2\mathrm{tr} \left\lbrace\boldsymbol\Xi_2\tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace\right.\nonumber \\ &\left.-2\boldsymbol\Xi_3\hat{\boldsymbol\theta}+\hat{\boldsymbol\theta}^\top\boldsymbol \Xi_4\hat{\boldsymbol\theta}+2\hat{\xi}\boldsymbol\Xi_5 \hat{\boldsymbol\theta}\right] \nonumber

### 2011-08-25 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 \section{Discussion}\label{sec:EM-Discussion}
-The correlation analysis specifies approximate supports for both the disturbance covariance function and the connectivity kernel.
+This paper is an extension of previous work in developing a framework for subject-specific neural field modelling.
+The extensions of the previous work include a method for estimating the support of the connectivity kernel and disturbance covariance, and the development of an EM framework for the neural field equations using the URTSS.
+The EM framework combined with the estimation of the support of the disturbance enables estimation of the temporal disturbance and noise characteristics of the system.
+Furthermore, by estimating the support of the connectivity kernel we are able to relax the strong assumption of isotropy in the estimated connectivity structure.
+
+\subsection{Correlation Analysis}
+The correlation analysis specifies an approximation for the support of both the disturbance covariance function and the connectivity kernel.
 Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly.
@@
 
+\subsection{Development of the EM for the URTSS}
 The additional Taylor approximation step introduced in the E-step of the algorithm resembles the extended Kalman filtering \cite{Jazwinski1970,Chui2009}.
@@
 Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviour higher order terms might need to be included, this however introduces intractable computational complexity.
+
 \section{Conclusion}

### 2011-08-25 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly.
-The analysis also assumes the sigmoidal firing rate in the active region and as a result  the kernel and disturbance amplitudes cannot be inferred only through the correlation analysis.
-This step might be considered as a prerequisite for the EM algorithm described in \S\ref{sec:EstimationAlgorithm} where the approximated supports are used to estimate the gain of the kernel and the field disturbance variance.
-Knowing the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition is significantly reduced  compared to the case where the basis functions are arranged across the entire spatial domain.
-This also improves the uncertainty of the estimates as a lower number of unknown parameters need to be estimated.
+
+The derivation for the closed-form solution of the kernel requires linearisation of the sigmoidal activation function about the firing threshold.
+Therefore, the resulting kernel estimate is simply used as a guide to constrain the placement of basis function and the corresponding coefficients must still be inferred using the EM algorithm for an accurate representation of the connectivity structure.
+In fact, the correlation analysis can be considered a prerequisite for the EM algorithm described in \S\ref{sec:EstimationAlgorithm}, where the approximated supports are used to estimate the gain of the kernel and the field disturbance variance.
+
+An alternative to estimating the support of the connectivity kernel is to place a regular grid of connectivity kernel basis function over the entire spatial domain of the field.
+However, the estimate of the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition can be significantly reduced.
+This also improves the uncertainty in the estimated coefficients, as a lower number of unknown parameters are estimated.
 The approximated support of the disturbance covariance function facilitates the application of the EM algorithm.

### 2011-08-25 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 \end{figure}
+
 \section{Discussion}\label{sec:EM-Discussion}
@@
 
-An alternative to estimating the support of the connectivity kernel is to place a regular grid of connectivity kernel basis function over the entire spatial domain of the field.
-However, the estimate of the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition can be significantly reduced.
+An alternative to estimating the support of the kernel is to place a regular grid of connectivity kernel basis function over the entire spatial domain of the field.
+However, the estimate of the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions can be significantly reduced.
 This also improves the uncertainty in the estimated coefficients, as a lower number of unknown parameters are estimated.
-The approximated support of the disturbance covariance function facilitates the application of the EM algorithm.
+The approximated support of the disturbance covariance function facilitates the application of the EM algorithm for estimating the temporal variance in the disturbance signal.
 This way the disturbance covariance matrix can be decomposed into two parts: an unknown scalar and a constant matrix depending only on the inferred spatial support.
@@
 \subsection{Development of the EM for the URTSS}
-The additional Taylor approximation step introduced in the E-step of the algorithm resembles the extended Kalman filtering \cite{Jazwinski1970,Chui2009}.
-The EKF approximates a stationary non-linear dynamic system with a linear non-stationary one using the first order Taylor expansion around the state estimates.
+The additional Taylor approximation step introduced in the E-step of the algorithm resembles the extended Kalman filter (EKF) \cite{Jazwinski1970,Chui2009}.
+The EKF approximates a stationary nonlinear dynamical system with a linear nonstationary one using the first-order Taylor expansion around the state estimates.
 This might imply that the extended Kalman smoother (EKS) is a better candidate --- in terms of implementation --- for the state inference in the proposed algorithm.
-However, the EKS requires re-linearising about the backward estimates which in turn necessitates the non-linear mapping to be uniquely invertible.
+However, the EKS requires re-linearising about the backward estimates, which in turn necessitates the nonlinear mapping to be uniquely invertible.
 Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation.
@@
 
-While the EKS has been  applied in the EM algorithm for learning non-linear models \cite{Ghahramani1999} this is the first work (to the best author's knowledge) where the URTSS is used in this context.
-However, as in the case of the EKS the stability of the algorithm cannot be ensured.
-This is because the use of the EKS or URTSS represents an approximation to the exact E-step.
-As a result the maximisation of the approximated lower bound might not necessarily increase the log-likelihood function.
+While the EKS has been applied in the EM algorithm for learning nonlinear models \cite{Ghahramani1999}, this is the first work (to the best author's knowledge) where the URTSS is used in this context.
+However, as in the case of the EKS, the stability of the algorithm cannot be ensured.
+This is because the EKS or URTSS provides an approximation to the exact E-step.
+Following this, the maximisation of the approximated lower bound is not guaranteed to increase the log-likelihood function.
 Nevertheless, it is envisaged that the use of the URTSS will provide a more stable algorithm due to its superior performance.

### 2011-08-26 ltx/data_paper/DataPaper.tex
edits to discussion

@@
 However, as in the case of the EKS, the stability of the algorithm cannot be ensured.
-This is because the EKS or URTSS provides an approximation to the exact E-step.
+This is because the EKS and the URTSS provide an approximation to the exact E-step.
 Following this, the maximisation of the approximated lower bound is not guaranteed to increase the log-likelihood function.
-Nevertheless, it is envisaged that the use of the URTSS will provide a more stable algorithm due to its superior performance.
-
-Typically a sequence of likelihood values converge to some stationary points i.e.
+Nevertheless, it is envisaged that the use of the EM algorithm using the URTSS will provide a more stable algorithm due to the superior performance of the UKF over the EKF.
+
+Typically, a sequence of likelihood values will converge to a stationary point i.e.
 global (local) maximum or a saddle point.
-If the sequence of the EM is trapped in a saddle point a small random perturbation diverges the algorithm from such a stationary value \cite{McLachlan1997}.
-In general convergence of the EM algorithm to any stationary points either global (local) maxima or saddle points depends on the initialisation.
-Here a bounded sequence of the state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and parameter estimations.
-
-Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviour higher order terms might need to be included, this however introduces intractable computational complexity.
+If the sequence of the EM is trapped in a saddle point, a small random perturbation diverges the algorithm from the local maxima \cite{McLachlan1997}.
+In general, convergence of the EM algorithm to any stationary point (ie.
+global maxima, local maxima or saddle point) depends on the initialisation.
+In the examples presented in this paper, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
+
+The first-order Taylor expansion provides a good local approximation of the sigmoid function, thus the EM provides a good approximation to the lower bound of the likelihood function.
+However, in a general settings with a more complicated nonlinearity, higher-order terms may be required to provide a good approximation.
+However, using higher-order terms introduces intractable computational complexity.
 

### 2011-08-26 ltx/data_paper/DataPaper.tex
edits to conclusion

@@
 \section{Conclusion}
-In this chapter, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data, where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.
-It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified.
-This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process.
-In addition to the connectivity kernel weights and the synaptic parameter, the observation noise and disturbance variances were also identified.
-The empirical distributions of the estimated non-kernel parameters showed small bias with very small standard deviations.
+In this chapter, a method has been developed to estimate the states and parameters of a spatially continuous neural field model from electrophysiological data.
+The novel aspects of this chapter include an estimator for the kernel spatial support and the field disturbance characteristics.
+The derivations and computational results demonstrate that by choosing the synaptic time constant and the observation noise variance within a plausible range, the unknown supports can be identified.
+The inclusion of this step facilitates the use of the EM algorithm, where the complexity is decreased and the accuracy is improved by reducing the number of unknown variables.
+In addition to the connectivity kernel weights and the synaptic parameter, the observation noise and disturbance variances were identified.
+The results using simulated data demonstrated good estimation performance, where the distributions of the estimated non-kernel parameters showed small bias with very small standard deviations.
+
+The data-driven modelling framework presented in this chapter provides a much needed link between theoretical and experimental neuroscience.
+By establishing this link, patient-specific systems neuroscience may eventually be used in a clinical setting, which has the potential to revolutionise  neurosciences and neurology.
 

### 2011-11-07 src/Matlab/Create_C.m
update to BREAINIDE talk

@@ -1,15 +1,0 @@
-% create C matrix for getting observations in the reduced model
-
-
-% define analytic inner product of sensors and basis functions
-a = pi / ( (sigma_phi^2+sigma_m^2)/(sigma_phi^2*sigma_m^2) );
-b = 1/(sigma_phi^2+sigma_m^2);
-
-% now define the observation matrix
-C = zeros(NSensors_xy^2,L );
-for n=1:NSensors_xy^2
-    for nn=1:L
-        mu_phi_minus_mu_y = mu_m(:,n)-mu_phi(:,nn);
-        C(n,nn) = a*exp(-b*(mu_phi_minus_mu_y)'*mu_phi_minus_mu_y);
-    end
-end

### 2011-11-07 src/Matlab/Create_Gamma.m

@@ -1,18 +1,0 @@
-% define gamma analytically
-
-% Gamma = [phi_1 x phi_1, phi_1 x phi_2, ..., phi_1 x phi_n
-%                   phi_2 x phi_1, ...                      , phi_2 x phi_n
-%                       ...
-%                   phi_n x phi_1, ...                      , phi_n x phi_n]
-% where x is inner product
-a = pi*sigma_phi^2/2;
-b = 1/(2*sigma_phi^2);
-
-Gamma = zeros(L,L);       % initialize for speed
-for n=1:L
-    for nn=1:L
-        mu_n_minus_mu_m = mu_phi(:,n)-mu_phi(:,nn);
-        Gamma(n,nn) = a*exp(-b*(mu_n_minus_mu_m)'*mu_n_minus_mu_m);
-    end
-end
-inv_Gamma = inv(Gamma);

### 2011-11-07 src/Matlab/Create_Psi.m

@@ -1,7 +1,7 @@
 
 
 % now form the matrix
-% these are the coefficients for the convolution of psi and phi
+% these are the coefficients for the analytic convolution of psi and phi
 psi_phi_coefficient(1) = pi*sigma_psi(1)^2*sigma_phi^2 / (sigma_psi(1)^2+sigma_phi^2);
 psi_phi_coefficient(2) = pi*sigma_psi(2)^2*sigma_phi^2 / (sigma_psi(2)^2+sigma_phi^2);
 psi_phi_coefficient(3) = pi*sigma_psi(3)^2*sigma_phi^2 / (sigma_psi(3)^2+sigma_phi^2);

### 2011-11-07 src/Matlab/Create_Sigma_e.m

@@ -1,20 +1,0 @@
-% create Sigma_e
-% this is the covariance matrix of the reduced model
-
-% find the convolution of phi and gamma
-phi_gamma_coefficient = (pi*sigma_gamma^2*sigma_phi^2) / (sigma_gamma^2+sigma_phi^2);
-phi_gamma_conv_var = sigma_gamma^2+sigma_phi^2;
-
-% find the inner product of the resulting convolution with phi
-a = pi / ( (phi_gamma_conv_var + sigma_phi^2) / (phi_gamma_conv_var * sigma_phi^2) );
-b = 1 / (sigma_phi^2+phi_gamma_conv_var);
-inner_prod = zeros(L,L);       % initialize for speed
-for n=1:L
-    for nn=1:L
-        mu_n_minus_mu_m = mu_phi(:,n)-mu_phi(:,nn);
-        inner_prod(n,nn) = gamma_weight*phi_gamma_coefficient*a*exp(-b*(mu_n_minus_mu_m)'*mu_n_minus_mu_m);
-    end
-end
-
-Sigma_e = inv_Gamma*inner_prod*inv_Gamma';
-

### 2011-11-07 src/Matlab/Create_phi.m

@@ -1,24 +1,0 @@
-% Create phi, the basis functions for the decomposition
-
-% first get them in 2D format
-phi = zeros(L,NPoints,NPoints);
-for n=1:L
-    phi(n,:,:) = Define2DGaussian(mu_phi(1,n), mu_phi(2,n), sigma_phi^2, 0,NPoints,SpaceMin,SpaceMax);
-%     imagesc(r,r,squeeze(phi(n,:,:)))
-%     axis xy
-%     drawnow
-end
-
-% now in vector format
-phi_unwrapped = zeros(L,NPoints^2);
-for n=1:L
-    temp = Define2DGaussian(mu_phi(1,n), mu_phi(2,n), sigma_phi^2, 0,NPoints,SpaceMin,SpaceMax);
-    phi_unwrapped(n,:) = temp(:);
-end
-
-% Check against Parham's value
-% ~~~~~~~~~~~~~~~~~~
-% load Phi_values
-% figure
-% imagesc(Phi_values - phi_unwrapped)
-% colorbar

### 2011-11-07 src/Matlab/Define2DGaussian.m

@@ -1,23 +1,0 @@
-function z = Define2DGaussian(xmu, ymu, var, rho,SpacePoints,SpaceMin,SpaceMax)
-
-% make a contour plot and a surface plot of a 2D Gaussian 
-% xmu, ymu - mean of x, y 
-% xvar, yvar - variance of x, y 
-% rho correlation coefficient between x and y
-
-sd = sqrt(var); % std deviation on x axis 
-% ysd = sqrt(yvar); % std deviation on y axis
-if (abs(rho) >= 1.0)
-    disp('error: rho must lie between -1 and 1');
-    return 
-end
-covxy = rho*sd*sd;                % calculation of the covariance
-C = [var covxy; covxy var];   % the covariance matrix 
-A = inv(C);                                 % the inverse covariance matrix
-
-x = linspace(SpaceMin,SpaceMax,SpacePoints);    % xmu-PlotWidth*maxsd:0.1:xmu+PlotWidth*maxsd; % location of points at which x is calculated 
-[X, Y] = meshgrid(x,x);                                         % matrices used for plotting
-
-% Compute value of Gaussian pdf at each point in the grid 
-z =  exp(-(A(1,1)*(X-xmu).^2 + 2*A(1,2)*(X-xmu).*(Y-ymu) + A(2,2)*(Y-ymu).^2));
-

### 2011-11-07 src/Matlab/Set_Parameters.m

@@ -1,205 +1,0 @@
-% set all the parameters for the model and the estimator
-
-% if we are running a batch than we dont want to clear things
-if exist('RunningBatch','var') == 0
-%     clear
-    close all
-%     clc
-end
-
-% spatial parameters
-% ~~~~~~~~~~~
-Delta = 0.5;                          % space step for the spatial discretisation
-Delta_squared = Delta^2;
-SpaceMax = 10;                    % maximum space in mm
-SpaceMin = -SpaceMax;         % minimum space in mm
-NPoints = (SpaceMax-SpaceMin)/Delta+1;
-r = linspace(SpaceMin,SpaceMax,NPoints);      % define space
-
-EstimationSpaceMax = 10;
-EstimationSpaceMin = -10;
-
-% temporal parameters
-% ~~~~~~~~~~~~~
-Ts = 1e-3;          % sampling period (s)
-T = 1000;            % maximum time (ms)
-
-% kernel parameters
-% ~~~~~~~~~~~
-theta(1) = 100.0;           % local kernel amplitude
-theta(2) = -80;             % surround kernel amplitude
-theta(3) = 5;               % lateral kernel amplitude
-
-sigma_psi(1) = 1.8;     % local kernel width
-sigma_psi(2) = 2.4;     % surround kernel width
-sigma_psi(3) = 6;       % lateral kernel width
-
-psi_0 = Define2DGaussian(0,0, sigma_psi(1)^2, 0,NPoints,SpaceMin,SpaceMax);
-psi_1 = Define2DGaussian(0,0, sigma_psi(2)^2, 0,NPoints,SpaceMin,SpaceMax);
-psi_2 = Define2DGaussian(0,0, sigma_psi(3)^2, 0,NPoints,SpaceMin,SpaceMax);
-w = theta(1)*psi_0 + theta(2)*psi_1 + theta(3)*psi_2;       % the kernel
-
-W = fft2(w);                                                                       % the fft of the kernel
-Ts_W = W*Ts;                        % FFT of kernel times the time step
-% ~~~~~~~~~~~~~~~~~~~~~~
-
-% ~~~~~~~~~~~~~~~~~~~~~~
-% triangle field basis function parameters
-% ~~~~~~~~~~~~~~~~~~~
[…]
